### 2022-01-20 README.Rmd
Init

---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The International Crisis Behavior Events (ICBe)
-----------------------------

This is a github repository for the International Crisis Behavior Events (ICBe) dataset. Submit any issues regarding the dataset, paper, or github repository using [the issues tab](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/issues/new/choose).

# The Paper:

[Introducing the International Crisis Behavior Event (ICBe) Dataset](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)

## The Authors:

- [Rex W. Douglass](http://www.rexdouglass.com), [Thomas Leo Scherer](http://tlscherer.com/), [J. Andrés Gannon](https://jandresgannon.com/), [Erik Gartzke](http://erikgartzke.com/), [Jon Lindsay](https://www.jonrlindsay.com/), [Shannon Carcelli](https://www.shannoncarcelli.com/), Jonathan Wilkenfeld, David M. Quinn, Catherine Aiken, Jose Miguel Cabezas Navarro, Neil Lund, Egle Murauskaite, and Diana Partridge.

# ICBe Dataset

- ICBe Dataset
- [ICBEdataset Codebook](https://docs.google.com/document/d/1aJkweohbfIWtNpJw1CmXbeIiK6czbJ5iPyKwiYP1YlU/edit?usp=sharing)

## ICBe raw data

 - Agreed Data, long form (LINK NEEDED)
 - Agreed Data, wide form (LINK NEEDED)
 - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
    + values may contain multiple entries separating with a semicolon
 - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
    + each row contains identifying information for a coder-crisis-event-sentence
    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
    + each value contains a single entry
 - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.

Replication Code and Analysis
-----------------------------

### Self Contained Package

All of the files necessary for reproducing our analysis are including in a self contained R package "ICBEdataset" You can install the package icb from github with:

``` r
# install.packages("devtools")
devtools::install_github("centerforpeaceandsecuritystudies/ICBEdataset")
```

## RMarkdown files
 - [01_compile_saves](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/01_compile_saves.html)
    + compiles the original coding files into `./data/icb_coder_crisis_sentence_event.tsv`
    + the original coding files are not on the public repository; this can only be run by authors
 - [02_align_sentences](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/02_align_sentences.html)
    + aligns codings from multiple GUI versions on similar source sentences
    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
 - [03_format_and_clean](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/03_format_and_clean.html)
    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
 - [04_aggregation](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/04_aggregation.html)
    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.

 - [05a_data_summary](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/05a_data_summary.html)
    + coding information, sentence root, time, coder confidence
 - [05b_data_summary](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/05b_data_summary.html)
    + actions, speech, thought

## Other data inputs:

### ICBe prep
- Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates [available online](https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit#gid=0) and  ./data/icb_manual_recording_master_sheet.xlsx
  + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).
- [Lit review and tree/leaf codebook](https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit#gid=1604363724)

### Existing datasets
- [The ICB project](https://sites.duke.edu/icbdata/) system-level (./data/icb1v14.Rds) and actor-level (./data/icb2v14.Rds) datasets.
- [ICEWS data sample](https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/28075/WNOBVV&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData).

### Acknowledgementes

### 2022-01-20 replication_data/rmd/01_compile_saves_and_align.Rmd
Init

---
title: "01_compile_saves"
output:
  html_document:
    df_print: paged
  toc: yes
editor_options:
  chunk_output_type: inline
---
  <style>
  body {
    position: absolute;
    left: 0px;
    max-width: 2000px;
  }
body .main-container {
  max-width: 2000px;
}
</style>

This notebook walks through the creation of the crisisno-sentenceno-sentence key

Library Loads

```{r}
`%>%` <- magrittr::`%>%`
fromscratch=T #global flag for whether to regenerate files form scratch or load presaved ones

```

Load and anonymize original individual save files from the gui

```{r, include=FALSE}

devtools::load_all(".")

# events <- load_raw_events(fromscratch = F)

```

```{r warning=FALSE}

#Only a project lead can run this code. Copy (NEVER MOVE) the original save files to the data_temp folder. And then verify that that data_temp is on the gitignore list so it never gets committed.
path <- paste0(here::here(), "/replication_data/ignore/icb_worker_saves") #this folder is copied over from the dropbox folder and never committed to github
files_worker_saves <- list.files(path = path, pattern = ".Rdata", all.files = FALSE, full.names = T, recursive = T, ignore.case = FALSE, include.dirs = FALSE)

if(length(files_worker_saves)==0){print("Original save files not found locally, will load premade anonymized file instead")
  }else{print("Original save files found, can regenerate anonymized if desired.")}

```

```{r warning=FALSE}

#Only execute if both (1) the original save files are available locally (2) fromscratch is requested
if(fromscratch & length(files_worker_saves)>0){

    #### CODE TO LOAD EVENT LEVEL DATA

    print(length(files_worker_saves)) #how many saved files we show

    # creates a list of event 'vectors' and names them based on the paths
    icb_worker_saves <- lapply(files_worker_saves, readRDS) #Read the files into memory in parallel
    names(icb_worker_saves) <- files_worker_saves

    # save the path name of with each row
    for(i in 1:length(icb_worker_saves)){
      #print(i)
      icb_worker_saves[[i]]$savefile <- files_worker_saves[i]
    }

    # reshape the work rows into a list of dataframes
    icb_worker_saves_dfs_list <- list()
    for(q in names(icb_worker_saves) ){
      #print(q)
      temp=unlist(icb_worker_saves[[q]]); #This is a named vector where names are keys, and values are values. One for every single response for a saved email-crisis.name
      df <- data.frame(varname = names(temp), value = temp, stringsAsFactors = F) #convert to dataframe
      tokens <- strsplit(df$varname,"_")
      icb_worker_saves_dfs_list[[q]]  <- df %>% 
        dplyr::mutate(sentence_number = sapply(tokens, FUN=function(x) x[1])) %>%
        dplyr::mutate(event_number = sapply(tokens, FUN=function(x) x[2])) %>%
        dplyr::mutate(email = df$value[df$varname=="email"]) %>%
        dplyr::mutate(input_crisis = df$value[df$varname=="input_crisis"]) %>%
        dplyr::mutate(savefile = q) %>% 
        dplyr::mutate(sentence_number_int =  as.numeric(gsub("s","",sentence_number))) %>% #These throw warnings
        dplyr::mutate(event_number_int =  as.numeric(gsub("e","",event_number))) %>%
        dplyr::select(-sentence_number, -event_number ) %>%
        dplyr::filter(!varname %in% c("email", "input_crisis", "savebutton", "savebutton2", "startbutton", "practice1", "practice2", "practice3", "practice4", "sentencenumber","crisis", "savefile")) %>%
        dplyr::select(-starts_with("sentencenumber") ) # filter out variables with varnames that contain "sentencenumber"

    }

    #table(icb_long$email) %>% sort()
    expert1 <- c("4fb99e72","f1a62076","3ee0cdf1")                                                                  
    expert2 <- c('890f3f5e','a6323005')    
    expert3 <- c("6e1ad8fc","c252a171","e7f1167f")
    expert4 <- c("d9d78123","d7b84c6b","e0741cd9")                                                                  
    expert5 <- c('052c88eb')    
    expert6 <- c('7559b489','6158e8c6')

    #icb_long %>% dplyr::count(email,input_crisis) %>% count(email)

    emails <- dplyr::bind_rows(icb_worker_saves_dfs_list) %>% dplyr::count(email) #132
    emails_to_keep <- emails %>% dplyr::filter(n>3000) %>% dplyr::pull(email) #we're going to reject any with less than 3,000 filled out values
    #That's 115

    icb_long <- dplyr::bind_rows(icb_worker_saves_dfs_list) %>%
                dplyr::filter(value!="") %>%
                dplyr::filter(email %in% emails_to_keep) %>%
                dplyr::filter(!is.na(event_number_int) & !is.na(sentence_number_int)) %>%

                dplyr::mutate(varname=stringr::str_replace(varname, "s[0-9]*_e[0-9]*_","")) %>%
                dplyr::mutate(varname=stringr::str_replace(varname, "actor1","actor_a")) %>%
                dplyr::mutate(varname=stringr::str_replace(varname, "actor2","actor_b")) %>%
                dplyr::mutate(varname=stringr::str_replace(varname, "s[0-9]*_","")) %>%
                dplyr::mutate(varname=stringr::str_replace(varname, "[0-9]*$","")) %>%

                #This trick lets us replace email addresses without having to write them in the code
                dplyr::group_by(email) %>%
                  dplyr::mutate(email_crc32= digest::digest(email[1],'crc32') ) %>% #anonymize
                dplyr::ungroup() %>%

                dplyr::group_by(savefile) %>%
                dplyr::mutate(savefile_crc32= digest::digest(savefile[1],'crc32') ) %>% #anonymize
                dplyr::ungroup() %>%

                dplyr::mutate(email_id=email_crc32) %>% 
                dplyr::mutate(email_id= ifelse(email_id %in% expert1, "expert1", email_id)) %>%
                dplyr::mutate(email_id= ifelse(email_id %in% expert2, "expert2", email_id)) %>%
                dplyr::mutate(email_id= ifelse(email_id %in% expert3, "expert3", email_id)) %>%
                dplyr::mutate(email_id= ifelse(email_id %in% expert4, "expert4", email_id)) %>%
                dplyr::mutate(email_id= ifelse(email_id %in% expert5, "expert5", email_id)) %>%
                dplyr::mutate(email_id= ifelse(email_id %in% expert6, "expert6", email_id)) %>%

                dplyr::select(-email,-savefile) %>% #anonymize
                dplyr::filter(email_id!="delete") %>%
                dplyr::mutate(email_id= ifelse(email_id %>% stringr::str_detect("expert"), email_id, paste0("undergrad",email_id))) %>%

                dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int, varname ) #%>%
                #filter(email_id %in% c('expert1','expert2','expert3','expert4','expert5','expert6')) #Restricting to just the experts

    dim(icb_long) #993,600     10

    # check for the presence of every crisis
    setdiff(1:476, icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort())
    #The only crisis for which we have no codings ever is 474 which is also missing from the official list here and so may never have had text for us to look at
    #https://duke.app.box.com/s/ddtpva1v33dzyom0j7obk7whitmouzr1

    # create "wide" dataset
    icb_wide <- icb_long %>% 
                dplyr::group_by(savefile_crc32, email_crc32, email_id, input_crisis, sentence_number_int, event_number_int, varname) %>%
                dplyr::summarize(value=paste(value, collapse=";")) %>%
                tidyr::pivot_wider( id_cols=c('savefile_crc32', 'email_crc32', 'email_id', 'input_crisis', 'sentence_number_int', 'event_number_int'),
                             names_from='varname',
                             values_from='value') %>%
                dplyr::arrange(savefile_crc32, email_id, email_crc32,input_crisis,sentence_number_int,event_number_int) %>% 
                dplyr::group_by(savefile_crc32 , input_crisis ) %>% tidyr::fill(icb_survey_version, crisis, crisno,sentence,section,lastviewed,sentence_events, .direction = c("down"))

    #None of these error sentences
    errors <-  icb_wide %>% dplyr::group_by(savefile_crc32 , input_crisis ) %>% dplyr::filter(crisno!=crisno[1]) #There was a bug in the saving script that would save extra sentences from a different crisis if the last one edited was longer than the current one

    icb_wide <- icb_wide %>% dplyr::group_by(savefile_crc32 , input_crisis ) %>% dplyr::filter(crisno==crisno[1]) #This removes any observations within a save file that are from a crisis number different than the first crisis number mentioned in the file

    # create copy of initial variables in case others get edited
    icb_wide$raw_crisis <- icb_wide$crisis
    icb_wide$raw_crisno <- icb_wide$crisno
    icb_wide$raw_sentence <- icb_wide$sentence
    icb_wide$raw_sentence_number_int <- icb_wide$sentence_number_int

    newname_order <- c(
      "icb_survey_version",
      "email_id",
      "email_crc32",
      "lastviewed",
      "input_crisis",
      "crisis",
      "crisno",

      "section",
      "sentence",
      "sentence_events",
      #"sentence_number",
      # "sentencenumber",
      "sentence_number_int",
      #"event_number",
      "event_number_int",
      "event_type",
      "raterconfidence",
      "raterconfidence_reason",
      "raterconfidence_reason_survey",

      "date",
      "think_sentence_events",

      "think_actor_a",
      "think_actor_a_other",
      "thinkkind",

      "say_actor_a",
      "say_actor_a_other",
      "say_actor_b",
      "say_actor_b_other"   ,

      "sayintkind",
      "sayintkind_react",
      "consequence",

      "condition",

      "do_actor_a",
      "do_actor_a_other",
      "do_actor_b"          ,
      "do_actor_b_other",

      "condition_do_actor_a",
      "condition_do_actor_a_other",
      "condition_do_actor_b",
      "condition_do_actor_b_other" ,

      "condition_act_cooperative",
      "condition_act_descalate",
      "condition_act_escalate",
      "condition_act_uncooperative",

      "condition_do_interact_kind",
      "condition_do_kind",
      "condition_interact_decreasecoop",
      "condition_interact_descalate",
      "condition_interact_domains",
      "condition_interact_escalate",
      "condition_interact_fatalities",
      "condition_interact_forces",
      "condition_interact_geoscope",
      "condition_interact_increasecoop",
      "condition_interact_location",
      "condition_interact_location_other",
      "condition_interact_territory",
      "condition_interact_units",

      "do_duration",
      "do_interact_kind",
      "do_kind",
      "do_timing",
      "do_timing_reorder",

      "act_cooperative",
      "act_descalate",
      "act_escalate",
      "act_uncooperative",

      "interact_decreasecoop",
      "interact_descalate",
      "interact_domains",
      "interact_escalate",
      "interact_fatalities",
      "interact_forces",
      "interact_geoscope",
      "interact_increasecoop",
      "interact_location",
      "interact_location_other",
      "interact_territory",
      "interact_units",

      "raw_crisis",
      "raw_crisno",
      "raw_sentence",
      "raw_sentence_number_int",
      "savefile_crc32"
    )

    setdiff(newname_order, names(icb_wide) )
    setdiff(names(icb_wide), newname_order )

    #problem sometimes I use a and sometimes I use 1 or 2
    icb_wide <- icb_wide[newname_order]
    icb_coder_crisis_sentence_event <- icb_wide
    remove(icb_wide)
    saveRDS(icb_coder_crisis_sentence_event,
            file=paste0(here::here(),"/replication_data/temp/icb_coder_crisis_sentence_event.Rds"))
  }  else  {
    icb_coder_crisis_sentence_event <-
      readRDS(file=paste0(here::here(),"/replication_data/temp/icb_coder_crisis_sentence_event.Rds"))
}

```

Check if any crises are missing, throw an error if it's not just 474
```{r}
setdiff( c(1:476), icb_coder_crisis_sentence_event$crisno)

 if(length(setdiff( c(1:476), icb_coder_crisis_sentence_event$crisno)) > 1) stop('Multiple Crisis Missing! Check icb_worker_saves')

```

## Sentence Alignment

This section realigns source sentences from multiple versions of the coding GUI

This Rmd sometimes gets warning the warning `Unknown or uninitialised column: 'crisisno_crisis_version'.` It cannot be reliably reproduced; so far have not found unwanted repercussions.

Trim extra white space from all sentences
```{r}
# use 'icb_wide' as shorthand for icb_coder_crisis_sentence_event
icb_wide <- icb_coder_crisis_sentence_event %>% 
  dplyr::mutate(sentence = trimws(sentence))

```

### Which crisis have crisis-sentence_numbers that have different sentences?

```{r}

# give each sentence a crisisno-sentence code
icb_wide$raw_crisno_sentno <- paste0("c", icb_wide$raw_crisno, "-s", icb_wide$raw_sentence_number_int)

# check that each crisno_sentno has only one sentence associated with it.
unique_sent <- unique(icb_wide[,c("sentence", "raw_crisno_sentno")])
dup_sent <- names(table(unique_sent$raw_crisno_sentno)[table(unique_sent$raw_crisno_sentno)>1]) 
  #list of the sentences that multiple sentences assigned to them.

dup_cris <- as.numeric(names(table(icb_wide$raw_crisno[icb_wide$raw_crisno_sentno %in% dup_sent]))) 
  # list of the afflicted sentences

sort(dup_cris)

```

What crisis names match those crisis numbers?

```{r}
sort(unique(icb_wide$crisis[icb_wide$crisno %in% dup_cris]))
```

Does that get all the crises with names that end in a number?

```{r}
grep('2', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)
grep('3', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)
grep('4', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)

```
It doesn't miss any that ends in 2 or 3 or 4. There are some that end in 1, but if there isn't a 2 that follows them then it's a different issue.

```{r}
grep('1', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)

# check to make sure those crises ending in '1' don't have another version without the 1
setdiff(grep('1', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE), 
        unique(icb_wide$crisis[(icb_wide$crisno %in% unique(icb_wide$crisno[(icb_wide$crisis %in% grep('1', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE))]))]))
```

# Set all crises to have the same crisis name
```{r}
#### standardize
crisiskey <- read.csv(paste0(here::here(), "/replication_data/in/icb1v12crisisnames.csv")) # standardize crisis

```

```{r}
icb_wide <- icb_wide %>% 
  dplyr::select(!crisis) %>% 
  dplyr::left_join(crisiskey %>% 
                     dplyr::rename(crisis = icb_crisname, raw_crisis = raw_crisname) %>% 
                     dplyr::select(crisis, raw_crisis))
```

```{r}
sort(unique(icb_wide$crisis[icb_wide$crisno %in% dup_cris]))

```

which crises have mismatching sentences in the same version?

check crisisname-version-sentence

```{r}

icb_wide$raw_crisno_version_sentno <- paste0(icb_wide$raw_crisno, "v", icb_wide$icb_survey_version, "-s", icb_wide$raw_sentence_number_int)
icb_wide$crisisno_crisis_version <- paste0(icb_wide$raw_crisno, "_", icb_wide$raw_crisis, "_", icb_wide$icb_survey_version)

# check that each crisno_sentno has only one sentence associated with it.
unique_vsent <- unique(icb_wide[,c("sentence", "raw_crisno_sentno")])

#list of the sentences that multiple sentences assigned to them.
dup_vsent <- names(table(unique_vsent$raw_crisno_sentno)[table(unique_vsent$raw_crisno_sentno)>1])

# list of crises with the afflicted sentences
dup_vcris <- names(table(icb_wide$crisisno_crisis_version[icb_wide$raw_crisno_sentno %in% dup_vsent])) 
sort(dup_vcris)

```

40 crisis have different sentence numbers in the same crisis:

### Create a csv to hand clean the sentence codes of.

```{r}

sentencekey_toclean <- unique(icb_wide[,c("email_id", "raw_crisis","raw_crisno","raw_sentence", "sentence", "raw_sentence_number_int", "raw_crisno_sentno", "icb_survey_version")])

sentencekey_toclean <- sentencekey_toclean[sentencekey_toclean$raw_crisno %in% dup_cris,]
sentencekey_toclean$raw_crisno <- as.numeric(sentencekey_toclean$raw_crisno)
sentencekey_toclean$raw_sentence_number_int <- as.numeric(sentencekey_toclean$raw_sentence_number_int)

sentencekey_toclean <- sentencekey_toclean[with(sentencekey_toclean, order(raw_crisno, raw_crisis, email_id, icb_survey_version, raw_sentence_number_int)),]

```

```{r}
table(sentencekey_toclean$raw_crisis, sentencekey_toclean$icb_survey_version)
```

To prep for cleaning, make an "raw_crisis"

```{r}

sentencekey_toclean$crisisno_crisis_version <- paste0(sentencekey_toclean$raw_crisno, "_",
                                                      sentencekey_toclean$raw_crisis, "_",
                                                      sentencekey_toclean$icb_survey_version)

sentencekey_toclean <- sentencekey_toclean %>% 
  dplyr::mutate(conflict_sent = ifelse(raw_crisno_sentno %in% dup_vsent, 1, 0))

# line above requres setdiff1 from below

write.csv(sentencekey_toclean, file=paste0(here::here(), "/replication_data/temp/sentencekey_toclean.csv"))
```

Check if there is a pattern between versions or coders. None apparant. 
```{r}

dup_cris_vec <- icb_wide$crisno %in% dup_cris

table(icb_wide$icb_survey_version, dup_cris_vec)
#table(icb_wide$email_cr32, dup_cris_vec)

```

### Load in sentence alignment key

```{r}
# load key dataset
#sentence_alignment_key_raw <- readODS::read_ods(paste0(here::here(), "/data/sentence_alignment_key.ods"))
sentence_alignment_key_raw <- readr::read_csv(paste0(here::here(), "/replication_data/in/sentence_alignment_key.csv"))
sentence_alignment_key_raw$crisno <- as.character(sentence_alignment_key_raw$crisno)

#reformat
sentence_alignment_key <- rbind(
  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence1")], "sentence1", "sentence"),
  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence2")], "sentence2", "sentence"),
  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence3")], "sentence3", "sentence"),
  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence4")], "sentence4", "sentence")) %>% 
  dplyr::filter(!is.na(sentence)) %>% 
  unique()

# Create an index to find crisis-sentences with multiple sentences
# sentence_alignment_key <- sentence_alignment_key %>% group_by(crisno, sentence_number_int_aligned) %>% mutate(id = row_number()) %>% dplyr::filter(id > 2)

```

The original read in changed, so check that the sentence alignment key contains all and only the sentences originally exported for alignment
```{r}
setdiff1 <- (setdiff(unique(sentencekey_toclean$sentence), unique(sentence_alignment_key$sentence)))
# what toclean has that is missing from alignment key

if(length(setdiff1)>0){
  sentencekey_toclean <- sentencekey_toclean %>% dplyr::mutate(sent_unfixed = ifelse(sentence %in% setdiff1 & conflict_sent==1, 1, 0))
  write.csv(sentencekey_toclean, file=paste0(here::here(), "/replication_data/temp/sentencekey_toclean.csv"))
  warning("alignment key may be incomplete")
}

```

```{r}
# what alignment key has that is missing from 'to clean'

setdiff2 <- data.frame(setdiff(unique(sentence_alignment_key$sentence), unique(sentencekey_toclean$raw_sentence)))
head(setdiff2)
```

```{r}
# crises that alignment key has that is missing from 'to clean' (ok if there are extra)
setdiff3 <- setdiff(unique(sentence_alignment_key$crisno), unique(sentencekey_toclean$raw_crisno))
setdiff3
```

```{r}
# crises that 'to clean' has that is missing from  alignment key(should be empty)
setdiff4 <- setdiff(unique(sentencekey_toclean$raw_crisno), unique(sentence_alignment_key$crisno))
setdiff4
```

```{r}

#drop duplicates and missing
sentence_alignment_key <- unique(sentence_alignment_key[complete.cases(sentence_alignment_key),])

#eyeball key, checking crisis number, that sentence_number is generally decreasing (but gaps allowed and expected!), and that no sentences are NA
table(sentence_alignment_key$crisno)
table(sentence_alignment_key$sentence_number_int_aligned)
table(is.na(sentence_alignment_key$sentence))
```

```{r}
# merge alignment sentence numbers
icb_wide_aligned <- icb_wide %>% dplyr::left_join(sentence_alignment_key)

# look at alignment outcomes
#dim(events) 
dim(icb_wide_aligned) # number of rows should be identical with one column added
table(icb_wide_aligned$crisno)
table(is.na(icb_wide_aligned$crisno))
table(icb_wide_aligned$sentence_number_int_aligned)
table(is.na(icb_wide_aligned$sentence_number_int_aligned))
```
if no alignment was needed, pass `sentence_number_int_aligned` the value in `sentence_number_int`
```{r}

icb_wide_aligned$sentence_number_int_aligned[is.na(icb_wide_aligned$sentence_number_int_aligned)] <- icb_wide_aligned$sentence_number_int[is.na(icb_wide_aligned$sentence_number_int_aligned)]
table(icb_wide_aligned$sentence_number_int_aligned)
table(is.na(icb_wide_aligned$sentence_number_int_aligned))
```

save dataset with alignment
```{r}
saveRDS(icb_wide_aligned %>% dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int),
     file=paste0(here::here(),"/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds"))
```

### 2022-01-20 replication_data/rmd/02_format_and_clean.rmd
Init

---
title: "02_format_and_clean"
output:
  html_document:
    df_print: paged
  toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

`%>%` <- magrittr::`%>%`
```

# Load and transform wide to long

read in icb_coder_crisis_sentence_event_aligned.Rds
```{r}
icb_wide_aligned_raw <- readRDS(file=paste0(here::here(),"/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds")) %>% 
                    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), sentence_number_int_aligned3 =
                                    stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>%
                    dplyr::mutate(email_crisis_sent_event =
                                    paste0(email_id,"_",crisno3,"_",sentence_number_int_aligned3,"_",event_number_int)) %>%
                    dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
                    dplyr::arrange(crisno, sentence_number_int, event_number_int) %>%

                    ####################Where we kill unhelpful events
                    #There are 2 legitimate kinds of rows
                    dplyr::filter(
                      event_number_int==0 & sentence_events %in% c('Background', 'Covered by Previous Sentence','Error','No Action') |
                      event_number_int>0 & event_type %in% c('Action', 'Speech','Thought' )
                    ) #%>%

dim(icb_wide_aligned_raw) #87710    85
```

Remove variables used earlier for compiling the individual codings
```{r}
icb_wide_aligned <- icb_wide_aligned_raw %>% dplyr::ungroup() %>% 
  dplyr::select(
               # -lastviewed, 
               # -input_crisis, 
                -sentence_number_int, -raw_crisis, -raw_crisno, -raw_sentence, -savefile_crc32, -raw_crisno_sentno, -raw_crisno_version_sentno, -crisisno_crisis_version) %>%
  dplyr::mutate(icb_survey_version = ifelse(is.na(icb_survey_version), 1.1, icb_survey_version))
dim(icb_wide_aligned) #52929    78

```

Initial coding edits (spelling, formatting, etc)
```{r}
icb_wide_aligned <- icb_wide_aligned %>% 
                      dplyr::rename(act_deescalate = act_descalate) %>% 
                      dplyr::rename(interact_deescalate = interact_descalate) %>% 
                      dplyr::rename(condition_act_deescalate = condition_act_descalate) %>% 
                      dplyr::rename(condition_interact_deescalate = condition_interact_descalate) %>% 
                      dplyr::mutate(sayintkind_react = ifelse(sayintkind_react=="This Sentence", raw_sentence_number_int,
                                                                         stringr::str_replace(sayintkind_react, "Sentence ","")))
dim(icb_wide_aligned) #52929    78

```

Where a coder looked at the same crisis twice, drop the earlier version and the earlier date
```{r}
icb_wide_aligned <- icb_wide_aligned %>% 
                      dplyr::group_by(email_crisis_sent_event) %>% 
                      dplyr::slice_max(icb_survey_version) %>%
                      dplyr::ungroup()

icb_wide_aligned <- icb_wide_aligned %>% 
                    dplyr::group_by(email_crisis_sent_event) %>% 
                    dplyr::slice_max(lastviewed) %>%
                    dplyr::ungroup()
dim(icb_wide_aligned) #87710    77
```

Drop a small subset where it appears that a coder looked at the same crisis twice but one of the times was logged incorrectly
```{r}
icb_wide_aligned <- icb_wide_aligned %>% dplyr::left_join(
                    icb_wide_aligned %>% dplyr::select(email_crisis_sent_event, event_number_int) %>% dplyr::filter(
                    (icb_wide_aligned %>% dplyr::select(email_crisis_sent_event, event_number_int) %>% 
                       duplicated()) == TRUE) %>% 
                      dplyr::mutate(duplicate = 1)) %>% 
                    dplyr::mutate(mismatch = crisis != input_crisis) %>% 
                    dplyr::filter(!(mismatch %in% TRUE & duplicate %in% 1)) %>%
                    dplyr::select(-mismatch, -duplicate)

dim(icb_wide_aligned) #51098    78

```

Pivot to long form 
```{r}

icb_long <- icb_wide_aligned %>% dplyr::ungroup() %>% 
             dplyr::relocate(sentence_events, .after = event_number_int) %>%
             tidyr::pivot_longer(
               cols = c(sentence_events:interact_units), #  changed this to be inclusive of event type and sentence_events 
               names_to = "variable",
               #names_prefix = "wk",
               values_to = "value",
               values_drop_na = TRUE
             ) %>% dplyr::ungroup() %>% 
  dplyr::mutate(value=value %>% tolower %>% trimws())
dim(icb_long) #491757     15

```

Now split values with a list (separated by a semicolon)

```{r}

icb_long_split <- icb_long %>% 
                  dplyr::mutate(value = strsplit(as.character(value), ";")) %>% 
                  tidyr::unnest(value) %>%
                  dplyr::mutate(value=value %>% tolower %>% trimws())
dim(icb_long_split) #536397     15

```

# Define subsets of variables

```{r}

vars <- c(
"sentence_events", "event_type", "raterconfidence", "raterconfidence_reason",
"raterconfidence_reason_survey", "date", "think_sentence_events", "think_actor_a", "think_actor_a_other", 
"thinkkind", "say_actor_a", "say_actor_a_other", "say_actor_b", "say_actor_b_other",
"sayintkind", "sayintkind_react", "consequence", "condition", "do_actor_a",
 "do_actor_a_other", "do_actor_b", "do_actor_b_other", "condition_do_actor_a",
"condition_do_actor_a_other", "condition_do_actor_b", "condition_do_actor_b_other",
 "condition_act_cooperative", "condition_act_deescalate", "condition_act_escalate",
"condition_act_uncooperative", "condition_do_interact_kind", "condition_do_kind",
"condition_interact_decreasecoop",  "condition_interact_deescalate",
"condition_interact_domains", "condition_interact_escalate", "condition_interact_fatalities",
"condition_interact_forces", "condition_interact_geoscope", "condition_interact_increasecoop",
"condition_interact_location", "condition_interact_location_other", "condition_interact_territory",
"condition_interact_units", "do_duration", "do_interact_kind", "do_kind", "do_timing",
"do_timing_reorder", "act_cooperative", "act_deescalate", "act_escalate",
"act_uncooperative", "interact_decreasecoop", "interact_deescalate", "interact_domains",
"interact_escalate", "interact_fatalities", "interact_forces", "interact_geoscope",
"interact_increasecoop",  "interact_location", "interact_location_other", "interact_territory",
"interact_units" )

vars_actor <- c("think_actor_a",
             "think_actor_a_other",
             "say_actor_a",
             "say_actor_a_other",
             "say_actor_b",
             "say_actor_b_other",
             "do_actor_a",
             "do_actor_a_other",
             "do_actor_b",
             "do_actor_b_other", 
             "condition_do_actor_a",
             "condition_do_actor_a_other",
             "condition_do_actor_b",
             "condition_do_actor_b_other")

vars_act <- c("act_cooperative",
              "act_uncooperative",
              "act_deescalate",
              "act_escalate",
              "interact_decreasecoop",
              "interact_increasecoop",
              "interact_deescalate",
              "interact_escalate",
              "condition_act_cooperative",
              "condition_act_uncooperative",
              "condition_act_deescalate",
              "condition_act_escalate",
              "condition_interact_decreasecoop",
              "condition_interact_increasecoop",
              "condition_interact_deescalate",
              "condition_interact_escalate")

# saveRDS(vars_actor, paste0(here::here(), "/replication_data/temp/","vars_actor.Rds"))
# saveRDS(vars_act, paste0(here::here(), "/replication_data/temp/","vars_act.Rds"))

vars_say <- c("sayintkind", "sayintkind_react","consequence","condition")
vars_think <- c("think_sentence_events", "thinkkind", "thinkkind_clean")

# Duplicate variables, same options for each in these types
vars_act_kind <- c("do_kind", "condition_do_kind", "do_interact_kind", "condition_do_interact_kind")
vars_fatalities <- c("interact_fatalities", "condition_interact_fatalities")
vars_forces <- c("interact_forces", "condition_interact_forces")
vars_geoscope <- c("interact_geoscope", "condition_interact_geoscope")
vars_location <- c("interact_location", "condition_interact_location")
vars_location_other <- c("interact_location_other", "condition_interact_location_other")
vars_territory <- c("interact_territory", "condition_interact_territory")

# NEED TO ADD TO CODEBOOK
vars_domains <- c("interact_domains", "condition_interact_domains")
vars_units <- c("interact_units", "condition_interact_units")

```

```{r}
# are all variables in vars?
setdiff(unique(icb_long_split$variable), vars)

# do the subsets cover everything in vars?
setdiff(vars, c(vars_actor, vars_act, vars_act_kind, vars_fatalities, vars_forces, vars_geoscope, vars_location, vars_location_other, vars_territory, vars_domains, vars_units, vars_say, vars_think))
```

# Load and apply normalizations

Load normalization dictionaries

```{r message=FALSE}
target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
# in not working, run googledrive::drive_auth() and select new token

dictionary_actions  <- readxl::read_excel(target_file, sheet="actions") %>% dplyr::distinct()
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno,value, value_normalized=value_normalized_wikidata_id) %>% dplyr::distinct()

#Locations and dates are both really hard to do
dictionary_locations <- readxl::read_excel(target_file, sheet="locations", na = c("", "NA")) 
dictionary_dates <- readxl::read_excel(target_file, sheet="dates", col_types="text") #This is the tricky one and why he had to add values

```

```{r}
# Create dateset to reconnect location dictionary to individual rows through 'sentence_number_int_aligned'
location_merge_directory <- icb_wide_aligned %>% 
    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), 
                  sentence_number_int_aligned3 = stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>% 
  dplyr::mutate(email_crisis_sent_event = paste(email_id,crisno3,sentence_number_int_aligned3,event_number_int, sep="_")) %>%
  dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
  dplyr::mutate(crisis_sent = paste0(crisno,"_",sentence_number_int_aligned)) %>%
  dplyr::select(crisno, email_crisis_sent_event, do_actor_a, do_actor_b, interact_location, interact_location_other) %>% 
  dplyr::mutate(do_actor_a=strsplit(do_actor_a, ";")) %>% tidyr::unnest(do_actor_a) %>%
  dplyr::mutate(do_actor_b=strsplit(do_actor_b, ";")) %>% tidyr::unnest(do_actor_b) %>%
  dplyr::mutate(interact_location_other=strsplit(interact_location_other, ";")) %>% tidyr::unnest(interact_location_other) %>%
  dplyr::mutate(do_actor_a=tolower(do_actor_a), do_actor_b=tolower(do_actor_b),
                interact_location_other=trimws(tolower(interact_location_other))) %>%
  dplyr::left_join(dictionary_locations %>%
                     dplyr::mutate() %>% 
                     dplyr::mutate(interact_location_other = tolower(interact_location_other)) %>% 
                     dplyr::select(do_actor_a, do_actor_b, interact_location, interact_location_other, norm_name)) %>%
  dplyr::mutate(crisno = as.numeric(crisno)) %>% 
  unique() %>% 
  dplyr::filter(!is.na(interact_location_other))

```

Apply the cleaning dictionaries to the relevant subsets

```{r}
  #ACTOR
icb_long_actor_clean <- icb_long_split %>% 
  dplyr::filter(variable %in% vars_actor) %>%
    dplyr::left_join(tibble::tibble(variable=vars_actor) %>% 
                       dplyr::mutate(temp="temp") %>%
                       dplyr::left_join(dictionary_actors %>% dplyr::mutate(temp="temp")) %>%
                       dplyr::select(-temp) %>% 
                       dplyr::select(crisno, variable, value, value_normalized) %>%
                     dplyr::mutate(crisno = as.character(crisno)) %>%
                     # dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized)) %>% 
                       unique(),
                     by=c('crisno','variable','value')) %>%
    dplyr::mutate(variable_normalized = paste0(variable, "_clean")) %>% 
  dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";")) %>% 
  tidyr::unnest(value_normalized) %>%
  dplyr::mutate(value_normalized=value_normalized %>% trimws())

# check for unmatched
icb_long_actor_clean %>% dplyr::filter(is.na(value_normalized)) %>% dplyr::select(crisno, variable, value)
```

```{r}
  #ACTION
icb_long_action_clean <- icb_long_split %>% 
                        dplyr::filter(variable %in% vars_act) %>% 
                        dplyr::left_join(dplyr::bind_rows(dictionary_actions,
                                         dictionary_actions %>% 
                                           dplyr::mutate(variable = paste0("condition_", variable)) %>% 
                                           dplyr::mutate(variable_normalized = ifelse(is.na(variable_normalized), 
                                                                                            variable_normalized, 
                                                                                            paste0("condition_", variable_normalized)))) %>% 
                                           dplyr::select(variable, value, variable_normalized, value_normalized) %>%
                                           dplyr::mutate(variable_normalized = ifelse(!is.na(value_normalized) & is.na(variable_normalized), 
                                                                                   variable, variable_normalized)),
                                         by=c('variable','value'))

# check for unmatched
icb_long_action_clean %>% dplyr::filter(is.na(value_normalized)) %>% dplyr::select(crisno, variable, value, variable_normalized, value_normalized) 
```

```{r}
 #LOCATION
icb_long_location_clean <- icb_long_split %>% 
  dplyr::filter(variable == "interact_location_other") %>% 
  dplyr::full_join(location_merge_directory %>%
                     dplyr::mutate(crisno = as.character(crisno)) %>% 
                     dplyr::rename(value = interact_location_other)) %>% 
  dplyr::rename(value_normalized = norm_name) %>%
  dplyr::mutate(variable_normalized = "interact_location_other_clean") %>%   
  dplyr::select(-do_actor_a, -do_actor_b, -interact_location) %>% 
  dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))
```

```{r}
  #DATES
icb_long_dates_clean <- icb_long_split %>% 
  dplyr::filter(variable=="date") %>% 
  dplyr::left_join(dictionary_dates %>% 
                   dplyr::select(-coder, -notes) %>%
                   dplyr::rename(value=date_orig)) %>%
  tidyr::pivot_longer(cols = point_in_time:latest_date2,
               names_to = "variable_normalized",
               values_to = "value_normalized",
               values_drop_na = TRUE) %>%
  dplyr::mutate(variable_normalized = ifelse(variable_normalized %in% c("point_in_time2", "point_in_time3", "point_in_time4", "point_in_time5"), "point_in_time", variable_normalized))

```

```{r}
# combine cleaned variables

icb_long_clean <- icb_long_split %>% 
  dplyr::left_join(icb_long_action_clean, by=names(icb_long_split)) %>% 
  dplyr::left_join(icb_long_actor_clean, by=names(icb_long_split), suffix = c("", ".actor")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.actor, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.actor, value_normalized))) %>%
      dplyr::select(-variable_normalized.actor, -value_normalized.actor) %>% 
  dplyr::left_join(icb_long_location_clean, by=names(icb_long_split), suffix = c("", ".location")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.location, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.location, value_normalized))) %>%
      dplyr::select(-variable_normalized.location, -value_normalized.location) %>% 
  dplyr::full_join(icb_long_dates_clean, by=names(icb_long_split), suffix = c("", ".date")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.date, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.date, value_normalized))) %>%
      dplyr::select(-variable_normalized.date, -value_normalized.date)

```

```{r}
# As the dictionaries translate some groups into multiple values, need to split out rows with multiple values

icb_long_clean <- icb_long_clean %>% 
  dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";")) %>% 
  tidyr::unnest(value_normalized) %>%
  dplyr::mutate(value_normalized=value_normalized %>% trimws()) %>% 
  dplyr::mutate(crisno=as.numeric(crisno)) %>% 
  dplyr::mutate(value=tolower(value))

dim(icb_long_clean) #507699
```

```{r}
# Fix several typos:

print(paste("change 'premption' to 'preemption'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "premption")==TRUE) %>% nrow(), "times."))
icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "premption", "preemption"))

print(paste("change 'disaprove' to 'disapprove'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "disaprove")==TRUE) %>% nrow(), "times."))
icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "disaprove", "disapprove"))

print(paste("change 'uncoperative' to 'uncooperative'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "uncoperative")==TRUE) %>% nrow(), "times."))
icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "uncoperative", "uncooperative"))

print(paste("change 'capitol' to 'capital'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "capitol")==TRUE) %>% nrow(), "times."))
icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "capitol", "capital"))

print(paste("change 'survailance' to 'surveillance'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "survailance")==TRUE) %>% nrow(), "times."))
icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "survailance", "surveillance"))

```

Create variable "preceding_event"
Create a lead / lag that points to the previous event by group

Create variable "previous_event_timing"
```{r}
alignment_key <- icb_wide_aligned_raw %>% 
  dplyr::ungroup() %>% 
  dplyr::select(email_id, crisno, sentence, raw_sentence_number_int, sentence_number_int_aligned, crisisno_crisis_version) %>% 
  dplyr::mutate(crisno = as.numeric(crisno))
```

```{r}
icb_long_preceding_event <- icb_long_clean %>% 
  # get do_timing_reorder and do_timing variables
  dplyr::filter(variable=="do_timing_reorder") %>% 
  dplyr::mutate(value = as.numeric(stringr::str_remove(value, "sentence "))) %>% 
  dplyr::rename(prior_sent_raw = value) %>% 
  # merge in "crisisno_crisis_version""
  dplyr::left_join(alignment_key %>% 
                     dplyr::select(email_id, crisno, sentence, crisisno_crisis_version)) %>% 
  dplyr::left_join(alignment_key %>% 
                     dplyr::select(-sentence) %>%
                     dplyr::rename(prior_sent_raw = raw_sentence_number_int, 
                                   prior_sent_aligned = sentence_number_int_aligned) %>% 
                     dplyr::mutate(prior_sent_raw = as.numeric(prior_sent_raw))) %>%
  dplyr::rename(value = prior_sent_raw) %>% 
  dplyr::mutate(value = as.character(value)) %>% 
  dplyr::mutate(variable_normalized = "do_timing_reorder_clean") %>% 
  dplyr::mutate(value_normalized = ifelse(value==1, "drop", prior_sent_aligned)) %>%
  dplyr::select(-c(crisisno_crisis_version, prior_sent_aligned)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert5_397_080_1" & variable_normalized=="do_timing_reorder_clean", 60)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert5_403_064_1" & variable_normalized=="do_timing_reorder_clean", 60)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert5_403_099_1" & variable_normalized=="do_timing_reorder_clean", 53)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_115_006_1" & variable_normalized=="do_timing_reorder_clean", 4)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_115_006_2" & variable_normalized=="do_timing_reorder_clean", 4)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_119_031_1" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_123_010_1" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_123_011_1" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_149_017_1" & variable_normalized=="do_timing_reorder_clean", 11)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_149_018_1" & variable_normalized=="do_timing_reorder_clean", 12)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_152_029_1" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_152_029_2" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_152_031_1" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_342_013_2" & variable_normalized=="do_timing_reorder_clean", 9)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_186_018_1" & variable_normalized=="do_timing_reorder_clean", 15)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_233_009_1" & variable_normalized=="do_timing_reorder_clean", 3)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_240_009_1" & variable_normalized=="do_timing_reorder_clean", 14)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_241_015_1" & variable_normalized=="do_timing_reorder_clean", 13)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_252_020_1" & variable_normalized=="do_timing_reorder_clean", 7)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_256_026_1" & variable_normalized=="do_timing_reorder_clean", 16)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_264_025_1" & variable_normalized=="do_timing_reorder_clean", 16)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_264_026_1" & variable_normalized=="do_timing_reorder_clean", 16)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_299_020_1" & variable_normalized=="do_timing_reorder_clean", 18)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_330_015_1" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_330_015_2" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_348_042_1" & variable_normalized=="do_timing_reorder_clean", 25)) %>%
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="undergrada31ef865_410_025_1" & variable_normalized=="do_timing_reorder_clean", 24))

```

```{r}
icb_long_think_event <- icb_long_clean %>% 
  # get do_timing_reorder and do_timing variables
  dplyr::filter(variable=="think_sentence_events") %>% 
  dplyr::mutate(value = trimws(stringr::str_remove(value, "sentence "))) %>% 
  # dplyr::mutate(value = if(value %in% c("act in this sentence", "speech in this sentence")), raw_sentence_number_int, value) %>%
  dplyr::rename(think_sent_raw = value) %>% 
  # merge in "crisisno_crisis_version""
  dplyr::left_join(alignment_key %>% 
                     dplyr::select(email_id, crisno, sentence, crisisno_crisis_version)) %>% 
  dplyr::left_join(alignment_key %>% 
                     dplyr::select(-sentence) %>%
                     dplyr::rename(think_sent_raw = raw_sentence_number_int, 
                                   think_sent_aligned = sentence_number_int_aligned) %>% 
                     dplyr::mutate(think_sent_raw = trimws(as.character(think_sent_raw)))) %>%
  # dplyr::filter(prior_sent_raw != 1) %>% # drop if prior_sentence==1 which seems to be GUI default
  dplyr::rename(value = think_sent_raw) %>% 
  dplyr::mutate(value = as.character(value)) %>% 
  dplyr::mutate(variable_normalized = "think_sentence_events_clean") %>% 
  dplyr::mutate(value_normalized = ifelse(value %in% c("act in this sentence", "speech in this sentence"), 
                                          sentence_number_int_aligned, think_sent_aligned)) %>%
  dplyr::mutate(value_normalized = as.character(value_normalized)) %>%
  dplyr::select(-c(crisisno_crisis_version, think_sent_aligned)) %>% 
  # clean up some NAs
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_392_017_1" & variable_normalized=="think_sentence_events", 16)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert3_007_007_1" & variable_normalized=="think_sentence_events", 7)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_173_012_1" & variable_normalized=="think_sentence_events", 11)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_203_004_1" & variable_normalized=="think_sentence_events", 3)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_253_012_1" & variable_normalized=="think_sentence_events", 9)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="undergrad32faf6f6_004_016_1" & variable_normalized=="think_sentence_events", 15)) %>% 
  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="undergraddb11c211_092_008_1" & variable_normalized=="think_sentence_events", 6))
```

```{r}
icb_long_clean  <- dplyr::bind_rows(
  icb_long_clean %>% 
    #dplyr::mutate(event_number_int = as.character(event_number_int)) %>% 
    dplyr::filter(variable!="do_timing_reorder") %>% 
    dplyr::filter(variable!="think_sentence_events"),
  icb_long_preceding_event,
  icb_long_think_event
)

rm(icb_long_preceding_event, icb_long_think_event)

```

```{r}
icb_long_clean <- icb_long_clean %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value, value_normalized)))
```

Join in google sheet of tree simplification and drop variables that we replace

```{r message=FALSE}

full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing", sheet="Codebook in Tree Form")

full_tree <- full_tree %>% dplyr::filter(!is.na(leaf) & leaf!='')

#The leafs aren't unique here because you can get to the same branch multiple ways

#This ignores conditions FYI
#Behavior # 3 bits
#think_aggression #1 bit
#say_aggression #1 bit
#do_aggression #1 bit
#Do_Armed_Unarmed #1 bit
#do_Act_Interact #1 bit
#full_tree$leaf_Simplified %>% unique() %>% length() #66 bits

#Only 70 bits total

#That's only another 29 bits

full_tree$leaf_think_simplified %>% unique() %>% length() #6
full_tree$leaf_say_simplified %>% unique() %>% length() #5
full_tree$leaf_do_simplified %>% unique() %>% length() #18

# full_tree$think_type_l0 %>% unique() %>% length() #6
# full_tree$say_type_l0 %>% unique() %>% length() #5
# full_tree$do_type_l0 %>% unique() %>% length() #18

```

```{r}

drops <- c(
'interact_escalate',
'interact_deescalate',
'act_uncooperative',
'act_deescalate',
'act_cooperative',
'do_interact_kind',
'do_kind',
'interact_decreasecoop',
'interact_increasecoop',
'interact_deescalate',
'act_escalate',
'condition_interact_deescalate',
'condition_interact_escalate',
'condition_interact_increasecoop',
'condition_interact_decreasecoop',
'condition_act_cooperative',
'condition_act_deescalate',
'condition_act_escalate',
'condition_act_uncooperative',
'do_interact_kind',
'interact_escalate',
'sayintkind',
'sayintkind_react',
'interact_deescalate',
'interact_decreasecoop',
'act_escalate',
'act_uncooperative',
'act_deescalate',
'act_cooperative',
'act_descalate', 
'act_escalate',
'act_uncooperative',
'interact_decreasecoop',
'interact_descalate',
'interact_deescalate', #there's a mispelling here
'interact_escalate',
'interact_increasecoop',
'thinkkind',
'sayintkind'
) %>% unique()

icb_long_clean2 <- icb_long_clean %>% 
                            dplyr::distinct() %>%
                            dplyr::mutate(variable_normalized= variable_normalized %>%
                                            stringr::str_replace("_other_clean","")) %>% 
  #We want to collapse others in with regulars
                            dplyr::mutate(variable_normalized= variable_normalized %>% 
                                            stringr::str_replace("_clean","")) %>% 
  #These only exist with actors now
                            dplyr::mutate(variable_normalized= variable_normalized %>% 
                                            stringr::str_replace("_other","")) %>% 
  #Only really matters for location_other

                            dplyr::filter(value_normalized!='drop') %>%
                            dplyr::filter(email_id!='expert3') %>% #expert3 Looks broken all the time
                            #I'm going to move to a structure where event numbers can have a subsection that is condition rather than keeping it in the variable names
                            dplyr::mutate(event_number_int_condition=variable_normalized %>%
                                            stringr::str_detect('condition_') %>% as.numeric() ) %>%
                            dplyr::mutate(variable_normalized=variable_normalized %>%
                                            stringr::str_replace('condition_',''))

temp_wide <- icb_long_clean2 %>%
             dplyr::select(icb_survey_version, email_id,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
             dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
             dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower()) %>%
             dplyr::filter(variable_normalized %in% (c( 'sentence_events', drops ) %>% trimws() %>% tolower()) ) %>%
             dplyr::distinct() %>% 
             dplyr::left_join(full_tree %>% 
                       dplyr::rename(value_normalized=leaf)  %>% 
                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) 
                       )

temp_long <- temp_wide %>% 
         dplyr::select(-variable_normalized,-value_normalized) %>%
         tidyr::pivot_longer(-c(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section, sentence,   event_number_int,event_number_int_condition),
                      names_to='variable_normalized' , values_to= 'value_normalized')  %>%
         dplyr::filter(!is.na(value_normalized))

icb_long_clean_final <- icb_long_clean2 %>%
                   dplyr::select(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section,  sentence,  event_number_int, event_number_int_condition, variable_normalized, value_normalized) %>%
                  rbind(temp_long) %>% dplyr::distinct() %>% 
                  dplyr::filter(!variable_normalized %in% drops)

```

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
```

# create wide file

```{r}

listtostring <- function(x){
  x %>% unlist() %>% paste(., collapse="; ")
}

paste_rex <- function(x){ x %>% sort() %>% paste( sep=";", collapse=";")   } 
icb_wide_clean <- icb_long_clean_final %>% 
  #dplyr::select(-variable,-value) %>%
  tidyr::pivot_wider(names_from=variable_normalized, values_from=value_normalized, values_fn=paste_rex)  %>%

  dplyr::filter(!(event_number_int==0 & sentence_events %in% c('1','2','3'))) #It does not appear that we ever need an e0 if number of events is greater than zero
  #There's also a weird situation where they sometimes created events without tagging it as a think, do,say

saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))

```

### 2022-01-20 replication_data/rmd/03_aggregation.Rmd
Init

---
title: "03_aggregation"
output:
  html_document:
    df_print: paged
  toc: yes
editor_options:
  chunk_output_type: inline
---

# Intro

## Library Loads

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

`%>%` <- magrittr::`%>%`

rex_paste <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}
rex_count <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}

```

## Hand coded aggregations

```{r}

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))

#icb_long_clean_original_393_43 <- icb_long_clean_original %>% filter(crisno==393 & sentence_number_int_aligned==43 ) %>% janitor::remove_empty() 
#Choose the most common sentence for each
sentences <- icb_long_clean %>% dplyr::count(crisno,sentence_number_int_aligned,sentence) %>% arrange(crisno, sentence_number_int_aligned, desc(n)) %>% 
  group_by(crisno, sentence_number_int_aligned) %>% filter(row_number()==1) %>% dplyr::select(-n)

```

# Sentence Level Agreement

Unanimous exact agreement- every expert coder chose the exact same options across all events for that question
Majority exact agreement- at least 2/3 of expert coders chose exactly the same options across all event for that question
This aggregates across conditions too

```{r}

keep_crisis=393
keep_sentence=38

options(warn = -1) #Groups that have no values generate max errors
#This doesn't have this yet
#event_number_int,  event_number_int_condition
rex_paste <- function(x){ paste0(x  %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
temp_long <- 
  icb_long_clean %>% 
    #filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% #for debugging
    dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, event_number_int_condition,variable_normalized, value_normalized) %>% 
    dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
    dplyr::group_by(crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    dplyr::select(-event_number_int) %>%
    dplyr::distinct() %>%
    dplyr::mutate(
      email_id = email_id %>% as.factor(), 
      #crisno= crisno %>% as.factor(),
      #sentence_number_int_aligned= sentence_number_int_aligned %>% as.factor(),
      crisno_sentence_number_int_aligned= paste0(crisno, "_", sentence_number_int_aligned) %>% as.factor(), #make sure these are the only factors or it'll try to criss cross sentence number and crisno etc.
      section= section %>% as.character(),
      sentence= sentence %>% as.character(),
      variable_normalized= variable_normalized %>% as.factor()
    ) %>%
    dplyr::select(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    distinct() %>%
    dplyr::group_by(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, 
             variable_normalized,.drop=FALSE) %>% 
      #This drop false means every coder gets a '' whether they filled in that variable or not #section, sentence going to have to ignore the sentence text for now
      #You'll get a warning about adding it as a group
      summarise(value_normalized=value_normalized %>% rex_paste() ) %>%
    #that will add in dead ones now we want to split them back out
    dplyr::mutate(value_normalized = value_normalized %>% stringr::str_replace_all(";;",";")) %>% 
    dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";", fixed=T)) %>% 
    tidyr::unnest(value_normalized) %>%
    dplyr::distinct() %>%
    #add a confidence score for every token
    dplyr::mutate(confidence=ifelse(variable_normalized=='raterconfidence', value_normalized, NA)) %>%

    dplyr::mutate(confidence=confidence %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
    dplyr::mutate(confidence_expert= email_id %>% stringr::str_detect('expert') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
    dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%

    dplyr::group_by(crisno,sentence_number_int_aligned) %>%
      dplyr::mutate(
        total_coders=email_id %>% unique() %>% length(),
        total_coders_expert=email_id %>% unique() %>% stringr::str_detect('expert') %>% sum() ,
        total_coders_undergrad=email_id %>% unique() %>% stringr::str_detect('undergrad') %>% sum()
      ) %>%
    dplyr::ungroup() %>%

    #Selected By
    dplyr::group_by(crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
      dplyr::mutate(
        selected_by_experts=email_id %>% unique() %>% stringr::str_detect('expert') %>% sum() ,
        selected_by_undergrads=email_id %>% unique() %>% stringr::str_detect('undergrad') %>% sum()
      ) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(selected_by_any=selected_by_experts+selected_by_undergrads) %>%
    dplyr::left_join(sentences) %>%
    dplyr::mutate(
        selected_by_any_perc=selected_by_any/total_coders,
        selected_by_experts_perc=selected_by_experts/total_coders_expert ,
        selected_by_undergrads_perc=selected_by_undergrads/total_coders_undergrad ,
    ) %>%
    dplyr::ungroup()

```

```{r}

#We have to compile confidence separately
sentence_confidence_scores <- temp_long %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, confidence,confidence_expert,confidence_undergrad) %>% distinct() %>% 
  mutate(confidence= confidence %>% replace(., !is.finite(.), NA),
         confidence_expert = confidence_expert %>% replace(., !is.finite(.), NA),
         confidence_undergrad = confidence_undergrad %>% replace(., !is.finite(.), NA)
         ) %>% 
  dplyr::select(-email_id) %>%
  group_by(crisno, sentence_number_int_aligned) %>%
  summarise_all(mean, na.rm=T) %>%
  mutate(confidence= confidence %>% replace(., !is.finite(.), NA),
         confidence_expert = confidence_expert %>% replace(., !is.finite(.), NA),
         confidence_undergrad = confidence_undergrad %>% replace(., !is.finite(.), NA)
         )

codings_long <- temp_long %>%
                mutate(
                       expert_majority=(selected_by_experts>(total_coders_expert/2) & selected_by_experts>=2) %>% as.integer() ,
                       undergrad_majority= (selected_by_undergrads > (total_coders_undergrad/2) & total_coders_undergrad>=2 ) %>% as.integer()  ,
                       expert_or_undergrad_majority= ( expert_majority | (undergrad_majority & selected_by_experts>=1) ) %>% as.integer() 
                ) %>%
                group_by(crisno,sentence_number_int_aligned, variable_normalized, value_normalized) %>%
                  mutate(
                        total_coders_expert=total_coders_expert %>% replace(., is.nan(.), NA) %>% mean(na.rm=T) %>% replace(., is.nan(.), NA),
                        total_coders_undergrad=total_coders_undergrad %>% replace(., is.nan(.), NA) %>% mean(na.rm=T) %>% replace(., is.nan(.), NA)
                  ) %>%
                ungroup() %>%
                dplyr::select(-email_id) %>%
                dplyr::select(-confidence,-confidence_expert,-confidence_undergrad) %>%
                distinct() %>% #bc expert majority is maxed now these rows should be fine
                left_join(sentence_confidence_scores) %>%
                arrange(crisno,sentence_number_int_aligned, event_number_int_condition, 
                        variable_normalized, expert_majority %>% desc(), undergrad_majority %>% desc(), undergrad_majority %>% desc(), selected_by_any %>% desc() ) #event_number_int

options(warn = 1)

```

# Agreed

```{r}

#this has to be temp because we actually do a lot of filtering at the wide stage and so need to go back to long
#What we could do is say if there's
codings_long_agreement <- codings_long %>%

                          mutate(keep_majority_expert= 
                                    (selected_by_experts>=2 & #selected by at least two experts
                                     expert_majority==1)   %>% as.numeric()
                           ) %>%
                           mutate(keep_majority_undergrad= (selected_by_experts>=1 & expert_majority==0 & undergrad_majority==1)  %>% as.numeric() ) %>%

                           mutate(keep_majority= (keep_majority_expert | keep_majority_undergrad) %>% as.integer() ) %>%

                           group_by(crisno, sentence_number_int_aligned, event_number_int_condition, variable_normalized) %>%
                                mutate(keep_majority_max=keep_majority %>% max(na.rm=T)) %>%
                                mutate(selected_by_any_max= (selected_by_any* (value_normalized!='')) %>% max(na.rmt=T) ) %>% #only consider non missing
                           ungroup() %>%
                           mutate(keep_leftstanding = (keep_majority_max==0 & #Wasn't picked by a majority
                                                         selected_by_experts>=1 & #was picked by a least one expert
                                                         (value_normalized!='' & selected_by_any_max %in% selected_by_any) #Has the most total votes
                                                       ) %>% as.numeric() ) %>%
                           mutate(keep = ( keep_majority==1 | keep_leftstanding==1 ) %>% as.numeric() )

codings_long_agreement_393_43 <- codings_long_agreement %>% filter(crisno==393 & sentence_number_int_aligned==43 ) %>% janitor::remove_empty() 
codings_long_agreement_393_59 <- codings_long_agreement %>% filter(crisno==393 & sentence_number_int_aligned==59 )
codings_long_agreement_393_38 <- codings_long_agreement %>% filter(crisno==393 & sentence_number_int_aligned==38 )
codings_long_agreement_284_16 <- codings_long_agreement %>% filter(crisno==284 & sentence_number_int_aligned==16 )

codings_long_agreed <- codings_long_agreement %>%
                           filter(value_normalized!='')  %>%
                           filter(keep==1) %>% 
                           group_by(crisno, sentence_number_int_aligned) %>%
                              mutate(no_events= max( variable_normalized=="Event_Any" & value_normalized=="no") ) %>% #make sure you do the filter or this won't twork
                           ungroup()

dim(codings_long_agreed) #249,840     19  tokens that have agreement
codings_long_agreed %>% dplyr::select(keep_majority_expert, keep_majority_undergrad, keep_majority, keep_leftstanding) %>% summarise_all(sum)

(table(expert_majority=codings_long$expert_majority,
      undergrad_majority=codings_long$undergrad_majority) / nrow(codings_long) ) %>% round(2)
#               undergrad_majority
#expert_majority    0    1
#              0 0.40 0.04
#              1 0.40 0.16

#
#
#
#Maybe we use this as a screen on the original codings and then collect what survived to make subevents?
rex_paste <- function(x){ paste0(x %>% unlist() %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
codings_wide_agreed <- icb_long_clean  %>% arrange(crisno,sentence_number_int_aligned) %>%
                        #filter(crisno==59) %>%
                        inner_join(codings_long_agreed) %>% #only keep ones that show up in both
                        filter(email_id %>% str_detect('expert') ) %>%
                        dplyr::select(email_id,crisno,sentence_number_int_aligned, event_number_int, event_number_int_condition, sentence,variable_normalized, value_normalized) %>%
                        distinct() %>%
                        pivot_wider(id_cols=c(email_id,crisno,sentence_number_int_aligned, sentence,event_number_int, event_number_int_condition), 
                                    names_from=variable_normalized, values_from=value_normalized, values_fn=rex_paste) %>%
                        distinct() %>%
                        group_by(crisno,sentence_number_int_aligned, event_number_int_condition, sentence, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>%
                          dplyr::summarise_all(rex_paste)
                        #filter(crisno==59 & sentence_number_int_aligned==3) 
codings_wide_agreed[codings_wide_agreed == ""]<-NA
#do the filters here after guaranteeing NAs

#Kill degenerate events
#We have a problem in that we want to reject certain kinds of events but we need to switch them to no events not drop the sentence all together
#This pruning basically works as intended but we need to go back and fill in null codings with a no event coding
codings_wide_agreed_pruned <- codings_wide_agreed %>% 
                              arrange(crisno,sentence_number_int_aligned) %>%
                              #filter(crisno==2 ) %>% #& sentence %>% str_detect('assassinated')

                              #A number of things stop making sense at this level
                              dplyr::select(-behavior) %>%
                              dplyr::select(-event_type) %>%
                              dplyr::select(-event_any) %>%
                              dplyr::select(-event_count) %>%
                              dplyr::select(-raterconfidence) %>%
                              dplyr::select(-event_number_int) %>%
                              dplyr::select(-email_id) %>%

                              #mutate(reject_eventbutnobehavior=!event_any %in% "no" & is.na(behavior)) %>% #it's pre NA conversion below so ''
                              #there's a degenerate kind of actor group where behavior wasn't agreed upon by everyone but there's still some info. This effectively requires each sentence to only have one kind of event, think, say, do but the details might differ slightly by different sets of actors involved.   
                              #I don't know why but the actos are infact NAs, I guess because of the group
                              mutate(reject_degendactorsdo  = !is.na(do_actor_b) & is.na(do_actor_a)     )  %>% 
                              mutate(reject_degendactorssay = !is.na(say_actor_b) & is.na(say_actor_a)   )  %>% 
                              mutate(reject_degendactorsall = is.na(do_actor_b) & is.na(do_actor_a) & is.na(say_actor_b) & is.na(say_actor_a) & is.na(think_actor_a)  ) %>%  #I guess we're just going to reject background codings all together

                              mutate(reject_degenleafdo    = !is.na(do_actor_a) & is.na(leaf_do_original)          ) %>% #kill off pairings that have a do but no do actor a
                              mutate(reject_degenleafsay   = !is.na(say_actor_a) & is.na(leaf_say_original)        ) %>%
                              mutate(reject_degenleafthink = !is.na(think_actor_a) & is.na(leaf_think_original)    ) %>%

                              mutate(reject_degenleafdo2   = is.na(do_actor_a) & !is.na(leaf_do_original)  ) %>% #kill of pairings that have a leaf but no actor
                              mutate(reject_degenleafsay2  = is.na(say_actor_a) & !is.na(leaf_say_original) ) %>%
                              mutate(reject_degenleafthink2= is.na(think_actor_a) & !is.na(leaf_think_original) ) %>%

                              #arrange(crisno,sentence_number_int_aligned) %>%
                              #mutate(crisno_sent= paste0(crisno,"_",sentence_number_int_aligned)) %>%
                              #group_by(crisno_sent) %>%
                              #  mutate(event_any_max= max( !event_any %in% 'no' ) ) %>%
                              #  mutate(reject_nullevent = event_any_max>0 & event_any %in% c("no")  ) %>% #If any group has events then drop any groups without events
                              #ungroup() %>%
                              rowwise() %>%
                                mutate(reject= 
                                               #reject_eventbutnobehavior +
                                               reject_degendactorsdo +
                                               reject_degendactorssay +
                                               reject_degendactorsall +
                                               reject_degenleafdo +
                                               reject_degenleafsay +
                                               reject_degenleafthink +
                                               reject_degenleafdo2 +
                                               reject_degenleafsay2 +
                                               reject_degenleafthink2 #+
                                               #reject_nullevent
                                         ) %>% 
                              ungroup()

#codings_wide_agreed_pruned  %>% t() %>% View() #%>% filter(sentence_number_int_aligned==12 )
#rejects <- codings_wide_agreed_pruned %>% filter(reject>0 ) 
#dim(rejects)   #19346    60
#rejects %>% t() %>% View()
#codings_wide_agreed_pruned %>% filter(crisno==2 & sentence_number_int_aligned==11) 
#codings_wide_agreed %>% filter(crisno==2 & sentence_number_int_aligned==11)

#codings_wide_agreed_384_43 <- codings_wide_agreed_pruned %>% filter(crisno==384 & sentence_number_int_aligned==43)  
#codings_wide_agreed_284_24 <- codings_wide_agreed_pruned %>% filter(crisno==284 & sentence_number_int_aligned==24)  
#codings_wide_agreed_447_14 <- codings_wide_agreed_pruned %>% filter(crisno==447 & sentence_number_int_aligned==14)

#codings_wide_agreed_2_11 <- codings_wide_agreed_pruned %>% filter(crisno==2 & sentence_number_int_aligned==11)

#codings_wide_agreed %>% filter(crisno==265 & sentence_number_int_aligned==28)

codings_wide_agreed_pruned_final <- codings_wide_agreed_pruned %>% 
                                    filter(reject==0) %>% dplyr::select(-starts_with("reject")) %>%
                                    right_join(codings_wide_agreed_pruned %>% dplyr::select(crisno,sentence_number_int_aligned,event_number_int_condition,sentence) %>% distinct() ) %>%

                                    #Generate final event ordering
                                    rowwise() %>%
                                    mutate(final_event_ordering=ifelse(!is.na(do_timing_reorder),
                                                                       #If more than one get past filter we take the smaller
                                                                       (do_timing_reorder %>% str_split(pattern=';', simplify = T) %>% unlist() %>% as.numeric() %>% min(na.rm=T)) +0.5,

                                                                       as.numeric(sentence_number_int_aligned) ) ) %>%
                                    ungroup() %>%
                                    arrange(crisno, final_event_ordering, sentence_number_int_aligned) %>% relocate(final_event_ordering, .after = sentence_number_int_aligned) %>%
                                    group_by(crisno) %>%
                                    mutate(final_event_ordering=row_number()) %>%
                                    ungroup()

```

# Codings wide agree labeled

```{r}

library(glue)

glue_rex <- function(x) glue(x, .open = "{|",.close = "|}", .envir = parent.frame()) #escape variables in the more complicated {||} syntax
target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
convert_qcode_to_english <- function(crisis, qcodes){
    crisis_actors <- dictionary_actors_labels %>% filter(crisno==crisis)
    crisis_actors_set <- crisis_actors$value_normalized_label
    names(crisis_actors_set) <- crisis_actors$value_normalized
    actors_english <- crisis_actors_set[qcodes %>% str_split(";") %>% unlist()]  %>% na.omit() %>% paste0(collapse=";")
    if(length(actors_english)==0){actors_english=NA}
    return(actors_english)
}
codings_wide_agreed_pruned_labeled <- NULL
codings_wide_agreed_pruned_labeled <-  codings_wide_agreed_pruned_final %>% 
  mutate(crisno_sent=paste0(crisno,'.',sentence_number_int_aligned)) %>%
  rowwise() %>%
  mutate(say_actor_a_labels=  convert_qcode_to_english(crisno, say_actor_a)) %>%
  mutate(say_actor_b_labels=  convert_qcode_to_english(crisno, say_actor_b)) %>%
  mutate(do_actor_a_labels=  convert_qcode_to_english(crisno, do_actor_a)) %>%
  mutate(do_actor_b_labels=  convert_qcode_to_english(crisno, do_actor_b)) %>%
  mutate(think_actor_a_labels=  convert_qcode_to_english(crisno, think_actor_a)) %>%
  mutate(think_sentence=ifelse(
      !is.na(leaf_think_original) & !is.na(think_sentence_events) , 
      glue_rex("[{|think_actor_a_labels|}]{.underline text.color='black'} experienced a 
                          [{|leaf_think_original|}]{.underline text.color='black'} about 
                          [{|think_sentence_events|}]{.underline text.color='black'}."),
            glue_rex("[{|think_actor_a_labels|}]{.underline text.color='black'} experienced a 
                          [{|leaf_think_original|}]{.underline text.color='black'}.")
  )) %>%
  mutate(say_sentence=ifelse(
      !is.na(leaf_say_original) , 
      glue_rex("[{|say_actor_a_labels|}]{.underline text.color='black'} initiated
                        [{|leaf_say_original|}]{.underline text.color='black'} toward  
                        [{|say_actor_b_labels|}]{.underline text.color='black'}.") ,
      ''
  )) %>%

  mutate(consequence_sentence=ifelse(
    consequence %in% "will happen" , 
    glue_rex("That the following will [happen]{.underline text.color='black'}.") ,
    glue_rex("That if the following [won't happen]{.underline text.color='black'}.")
  )) %>%

  mutate(condition_sentence=ifelse(
    condition %in% "happens" , 
    glue_rex("If the following [happens]{.underline text.color='black'}.") ,
    glue_rex("If the following [does not happen]{.underline text.color='black'}.")
  ))  %>%

  mutate(do_sentence=ifelse(
    !is.na(leaf_do_original) & !is.na(do_actor_b), 
    glue_rex("[{|do_actor_a_labels|}]{.underline text.color='black'} 
              initiated 
              [{|leaf_do_original|}]{.underline text.color='black'}
              toward 
              [{|do_actor_b_labels|}]{.underline text.color='black'}." ) ,
    glue_rex("[{|do_actor_a_labels|}]{.underline text.color='black'} 
              initiated 
              [{|leaf_do_original|}]{.underline text.color='black'}")
   )) %>%

   mutate(codings_sentence=NA) %>%

   #
   mutate(codings_sentence=ifelse( is.na(leaf_say_original) & is.na(leaf_do_original) & is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("No events.")
                                   ,codings_sentence)) %>%

   mutate(codings_sentence=ifelse( is.na(leaf_say_original) & is.na(leaf_do_original) & !is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|think_sentence|}")
                                   ,codings_sentence)) %>%

    mutate(codings_sentence=ifelse( !is.na(leaf_say_original) & is.na(leaf_do_original) & is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|say_sentence|}")
                                   ,codings_sentence)) %>%

    mutate(codings_sentence=ifelse( is.na(leaf_say_original) & !is.na(leaf_do_original) & is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|do_sentence|}")
                                   ,codings_sentence)) %>%

    #Condition sentence
    mutate(codings_sentence=ifelse( is.na(leaf_say_original) & !is.na(leaf_do_original) & is.na(leaf_think_original) & is.na(consequence) & !is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("[Condition] {|do_sentence|}")
                                   ,codings_sentence)) %>%

    mutate(codings_sentence=ifelse( is.na(leaf_say_original) & !is.na(leaf_do_original) & !is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|think_sentence|} {|do_sentence|}")
                                   ,codings_sentence)) %>%

    mutate(codings_sentence=ifelse( !is.na(leaf_say_original) & is.na(leaf_do_original) & !is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|think_sentence|} {|say_sentence|}")
                                   ,codings_sentence)) %>%

    mutate(codings_sentence=ifelse( !is.na(leaf_say_original) & !is.na(leaf_do_original) & !is.na(leaf_think_original) & is.na(consequence) & is.na(condition)  & event_number_int_condition %in% 0,
                                   glue_rex("{|think_sentence|} {|say_sentence|} {|do_sentence|}")
                                   ,codings_sentence)) %>%

    mutate(codings_sentence=ifelse( !is.na(leaf_say_original) & !is.na(leaf_do_original) & is.na(leaf_think_original) & is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|say_sentence|} {|do_sentence|}")
                                   ,codings_sentence)) %>%

   mutate(codings_sentence=ifelse( !is.na(leaf_say_original) & !is.na(leaf_do_original) & is.na(leaf_think_original) & !is.na(consequence) & is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|say_sentence|} {|consequence_sentence|} {|do_sentence|}")
                                   ,codings_sentence))  %>%

    mutate(codings_sentence=ifelse( !is.na(leaf_say_original) & !is.na(leaf_do_original) & is.na(leaf_think_original) & !is.na(consequence) & !is.na(condition) & event_number_int_condition %in% 0,
                                   glue_rex("{|say_sentence|} {|consequence_sentence|} {|do_sentence|} {|condition_sentence|}")
                                   ,codings_sentence))

#codings_wide_agreed_labeled %>% dplyr::select(codings_sentence, contains('actor'), contains('_original'), consequence, condition, event_number_int_condition) #%>% View()

#codings_wide_agreed_labeled %>% dplyr::select(contains('actor'), contains('_original'), consequence, condition, event_number_int_condition, contains('_sentence')) #%>% View()

(codings_wide_agreed_pruned_labeled_2_11 <- codings_wide_agreed_pruned_labeled %>% filter(crisno==2, sentence_number_int_aligned==11) %>% 
                                    dplyr::select(crisno, sentence_number_int_aligned, contains('actor'), contains('_original'), consequence, condition, event_number_int_condition, contains('_sentence')) ) #%>% View()

(codings_wide_agreed_pruned_labeled_28_5 <- codings_wide_agreed_pruned_labeled %>% filter(crisno==28, sentence_number_int_aligned==5) %>% 
                                    dplyr::select(crisno, sentence_number_int_aligned, contains('actor'), contains('_original'), consequence, condition, event_number_int_condition, contains('_sentence')) ) #%>% View()

(codings_wide_agreed_pruned_labeled_34_17 <- codings_wide_agreed_pruned_labeled %>% filter(crisno==34, sentence_number_int_aligned==17) %>% 
                                    dplyr::select(crisno, sentence_number_int_aligned, contains('actor'), contains('_original'), consequence, condition, event_number_int_condition, contains('_sentence')) ) #%>% View()

```

Iterate and visualize sentences until convinced the translation is right

```{r, eval=F}

codings_wide_agreed_labeled_sample_ft <- 
      codings_wide_agreed_pruned_labeled %>%
                group_by(crisno, sentence_number_int_aligned, crisno_sent, sentence) %>%
                summarize(codings_sentence = paste(codings_sentence, collapse="\n")) %>%
                dplyr::select(crisno_sent, sentence, codings_sentence)  %>%
                dplyr::filter(codings_sentence!="No events.") %>%
                group_by(crisno) %>%
                sample_n(size=1) %>%
                ungroup() %>%
                dplyr::select(crisno_sent, sentence, codings_sentence) %>%
                as_flextable() %>%
                colformat_md() %>% 
                flextable::fontsize(size = 7, part = "all") %>%
                flextable::bg( i = which( 1:nrow(codings_wide_agreed_pruned_labeled) %% 2 == 1)  , j=1:ncol(events_df), part = "body", bg = "#EFEFEF") %>%
                flextable::width(j = 1, width=0.3, unit = "in") %>%
                flextable::width(j = 2, width=3, unit = "in") %>%
                flextable::width(j = 3, width=3, unit = "in")

codings_wide_agreed_labeled_sample_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_labeled_sample_ft.Rds'))
codings_wide_agreed_labeled_sample_ft

```

# Validation Tests

```{r, eval=F}

keep_crisis=393
keep_sentence=38

(a <- icb_long_clean_original %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(b <- temp_long %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(c <- temp_wide %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty() )#%>% t()  ) #%>% View()
(d <- icb_long_clean %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(e <- codings_long %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(f <- codings_long_agreement %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()   ) #%>% View()
(g <- codings_long_agreed %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()   ) #%>% View()
(e <- codings_wide_agreed  %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% janitor::remove_empty()  ) %>% t() #%>% View()

```

```{r, eval=T}

saveRDS(codings_long, paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds"))

saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))

```

### 2022-01-20 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
Init

---
title: |
  | DRAFT, NOT FOR DISTRIBUTION 
  | Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises
author:
  - Rex W. Douglass^[Department of Political Science, University of California, San Diego, CA, USA.]
  - Thomas Leo Scherer^[Department of Political Science, University of California, San Diego, CA, USA.]
  - J. Andrés Gannon^[Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.]
  - Erik Gartzke^[Department of Political Science, University of California, San Diego, CA, USA.]
  - Jon Lindsay^[School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.]
  - Shannon Carcelli^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - Jonathan Wilkenfeld^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - David M. Quinn^[Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.]
  - Catherine Aiken^[Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.]
  - Jose Miguel Cabezas Navarro^[Society and Health Research Center, Universidad Mayor, Santiago, Chile.]
  - Neil Lund^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - Egle Murauskaite^[ICONS Project // START,  University of Maryland, College Park, MD, USA.]
  - Diana Partridge^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]

date: "`r Sys.Date()`"
abstract:  How do international crises unfold? We conceive of international affairs as a strategic chess game between adversaries, necessitating a systematic way to measure pieces, moves, and gambits accurately and consistently over different contexts and periods. We develop such a measurement strategy with an ontology of crisis actions and interactions and apply it to a high-quality corpus of crisis narratives recorded by the International Crisis Behavior (ICB) Project. We demonstrate that the ontology has high coverage over most of the thoughts, speech, and actions contained in these narratives and produces high inter-coder agreement when applied by human coders. We introduce a new crisis event dataset ICB Events (ICBe). We find that ICBe captures the process of a crisis with greater accuracy and granularity than other well-regarded events or crisis datasets. We make the data, replication material, and additional visualizations available at a companion website www.crisisevents.org.

site: bookdown::bookdown_site
keywords:
  - International Crisis Behavior
  - Event data
bibliography: ICBintro.bib
output: 
  bookdown::pdf_document2:
    toc: false
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
#  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
  - \usepackage{eso-pic,graphicx,transparent}
  - \usepackage[perpage]{footmisc}

---

```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
#International Crisis Behavior Events (ICBe) Dataset
knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F

TLS = FALSE
```

```{r, eval=T, echo=F, cache=F}

#library(pacman)
library(googlesheets4)
library(tidyverse)
library(janitor)
library(flextable)
set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`. You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
library(ftExtra)
options(tidyverse.quiet = TRUE)
options(gargle_oauth_email = TRUE)

#install.packages('stargazer')
#install.packages('kableExtra')
#! sh: 1: pdflatex: not found
#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended

#! LaTeX Error: File `letltxmacro.sty' not found.
#sudo apt-get install texlive-latex-extra

```

```{r, echo=F}
#Notes
#https://tex.stackexchange.com/questions/83440/inputenc-error-unicode-char-u8-not-set-up-for-use-with-latex
#- \DeclareUnicodeCharacter{00A0}{ }

```

```{r, include=FALSE}
# options(tinytex.verbose = TRUE)
```

```{r, echo=FALSE}

`%>%` <- magrittr::`%>%`

```

```{r, echo=FALSE}

codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/codings_wide_agreed.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/codings_long_agreed.Rds'))
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))

#Load original icb data

#oh is it because break is reserved in R? lol
#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()

#somehow break of all things is a b roken name
#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))

```

```{r include=F}
#Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))

n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)

avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)

avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)

events_per_sentence <- icb_wide_clean %>%
  filter(!is.na(sentence_number_int_aligned)) %>%
  dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) %>%  #event_number_int
  group_by(email_id,crisno,sentence_number_int_aligned) %>%
  summarise(event_count = sum(!is.na(event_type) ) ) %>%
  mutate_all(as.numeric) %>%
  group_by(crisno,sentence_number_int_aligned) %>%
  summarise(
    event_count_min=event_count %>% min(),
    event_count_mean=event_count %>% mean(na.rm=T),
    event_count_max=event_count %>% max()
  ) %>%
  arrange(crisno,sentence_number_int_aligned)

events_per_crisis <- events_per_sentence %>% group_by(crisno) %>% summarise(event_count_mean_sum=sum(event_count_mean))

crisis_text_counts <- icb_wide_clean %>%
  #mutate( input_crisis = input_crisis %>% str_replace_all("[^A-Za-z0-9 ]","") ) %>% #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
  #https://www.google.com/search?q=R+replace+00A0&oq=R+replace+00A0&aqs=chrome..69i57j0i20i263i512j0i512l2j69i65j69i60l3.1744j0j7&sourceid=chrome&ie=UTF-8
  dplyr::select(crisno, sentence) %>%
  #mutate(input_crisis = input_crisis %>% stringr::str_to_title()) %>%
  #mutate(input_crisis = input_crisis %>% stringr::str_replace_all('[0-9]$','')) %>%
  mutate(sentence = sentence %>% stringr::str_to_lower()) %>%
  distinct() %>%
  #filter(!is.na(input_crisis)) %>%
  filter(!is.na(sentence)) %>%
  mutate(word_count=str_count(sentence, '\\w+')) %>%
  group_by(crisno) %>%
  summarise(
    sentence_count=n(),
    word_count=sum(word_count)
  )

#Even type

library(sjmisc)
event_type_per_sentence <- icb_wide_clean %>%
  filter(!is.na(sentence_number_int_aligned)) %>%
  dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type)  %>%
  to_dummy(event_type, suffix = "label") %>%
  bind_cols( icb_wide_clean %>%
               filter(!is.na(sentence_number_int_aligned)) %>%
               dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) ) %>%

  group_by(email_id,crisno,sentence_number_int_aligned) %>%
  summarise_if( is.numeric, sum ) %>%

  group_by(crisno,sentence_number_int_aligned) %>%
  summarise_if( is.numeric, mean, na.rm=T ) %>%
  arrange(crisno,sentence_number_int_aligned)

event_type_per_sentence_totals <- event_type_per_sentence %>% ungroup() %>% summarise_if( is.numeric, sum, na.rm=T ) %>% dplyr::select(-crisno)
event_type_per_sentence_totals_perc <- event_type_per_sentence_totals/sum(event_type_per_sentence_totals)

```

```{r , message=F}

icb_text <- icb_wide_clean %>% dplyr::select(crisno,sentence_number_int_aligned, sentence) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)

fromscratch=F
if(fromscratch){

  library("spacyr")
  #spacy_install()
  spacy_initialize(model = "en_core_web_sm")

  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
  parsed_consolidated <- nounphrase_consolidate(parsed)
  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]

  parsed %>% saveRDS(paste0(here::here(), "/replication_data/temp/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/replication_data/temp/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/replication_data/temp/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/replication_data/temp/entities.Rds"))

}

entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
entities$crisno <- icb_text$crisno[entities$doc_id_num]
entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()

target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")

if(!TLS){
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit#gid=0", path=target_file, type = "xlsx", overwrite=T)
}
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()

verbs_sentence <- parsed %>% filter(pos=="VERB")

verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()

entities_per_sentence <- entities %>%
  count(doc_id) %>%
  summarise(
    entities_per_sentence_min=min(n),
    entities_per_sentence_mean=mean(n),
    entities_per_sentence_max=max(n),
  )

```

```{r, messages=F, results='hide', warnings=F, include=FALSE}

#wordnet rdf (in tripple format)
fromscratch=F

ym   4
wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )

subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
subject_headings_verbs <- subject_headings %>%
  filter(value %>% str_detect('-v>')) %>%
  mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>%
  mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
  separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
  mutate(b = b %>% str_replace_all('\\"| \\.',""))

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F #, show_col_types=F)
)
names(wordnet_list) <- filenames

hypernyms <- wordnet_list[['wn_hyp.csv']] %>%
  dplyr::select(a=X1,b=X2) %>%
  left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>%
  left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )

library(igraph)
g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)

wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )

wordnet_verbs <- wordnet %>% filter(tense=='v')

verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
#dim(verbs_sentence_wordnet) #227,426

#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances

```

```{r, echo=F, messages=F, warnings=F, results='hide', eval=T}

fromsrcatch=F
if(fromsrcatch){
  #py$sentences
  #py$glosses
  sentences_embeddings <- py$sentences_embeddings
  glosses_embeddings <- py$glosses_embeddings

  rownames(sentences_embeddings) <- py$sentences #[1:100]
  rownames(glosses_embeddings) <- py$glosses #[1:100]
  dim(glosses_embeddings)

  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
  gloss_clean <- verbs_sentence_wordnet$gloss
  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
  dim(glosses_embeddings_expanded)

  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
  table(condition_sentences_embeddings) #all are in it
  sentences_clean <- verbs_sentence_wordnet$sentence
  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
  dim(sentences_embeddings_expanded)

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

} else {

  verbs_sentence_wordnet <- readRDS(paste0(here::here(),"/data_replication/temp/verbs_sentence_wordnet.Rds"))

}

verbs_sentence_wordnet_top <- verbs_sentence_wordnet %>% group_by(crisno, sentence_number_int_aligned, token_id) %>% filter(row_number()==1)
verbs_sentence_wordnet_top_unique <- verbs_sentence_wordnet_top %>% ungroup() %>% dplyr::select(lemma, wordnetid,tense, gloss) %>% group_by(lemma, wordnetid,tense, gloss) %>% count() %>% arrange(desc(n))

```

\AddToShipoutPictureFG{
  \AtPageCenter{% or \AtTextCenter
    \makebox[0pt]{\rotatebox[origin=c]{45}{%
      \scalebox{5}{\texttransparent{0.1}{Unrefereed Preprint}}%
    }}
  }
}

# Introduction

If we record every event between countries in all of diplomacy, military conflict, and international political economy, how much information would this chronicle amount to, and how surprised would we be to see something new? In other words, what is the entropy of international relations? This record could, in principle, be unbounded. Still, the central conceit of political science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015]. If so, then these events can be systematically measured. Massive effort is expended in social science recording these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.

Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations (IR). We develop a large, flexible ontology of international events with the help of both human coders and natural language processing. We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999;@brecherCrisisEscalationWar2000;@wilkenfeldInterstateCrisesViolence2000;@jamesWhatWeKnow2019;@iakhnisCrisesWorldPolitics2019]. The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes. We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative. We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts. As should come as no surprise to anyone who works with event data, we find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode. The underlying fine-grained variation in international affairs that we care about is unrecognizable through the lens of current quantification efforts.

This is a measurement paper and therefore makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches. The article organizes that argument into eight sections. Section 2 defines the task of event extraction and proposes evaluation criteria for objectively gauging the performance of that task. Section 3 is a literature review that synthesizes a reasonable prior belief behind the existence of the unobserved latent concept we intend to measure and highlights existing current approaches for measuring them. Section 4 details our proposed method for measuring events, including the ICB Events (ICBe) dataset's ontology, coding procedures, and methodology. Section 5 demonstrates the internal validity of our coding exercise, the high agreement between coders and their self-reported confidence in codings, and external validity in the form of high coherence in side-by-side comparisons of source sentences and resulting codings. Section 6 evaluates internal validity by showing that like-codings cluster when their source sentences are mapped into semantic space. Section 7 offers a comparison against existing systems with case studies at the crisis level where we show both much higher recall of events that occurred and precision in what those events were and how they fit into the overall macro-level event. A final section concludes.

<!--Section 7 moves from qualitative comparison to an objective criteria with multiple choice reading comprehension questions about each crisis drawn from the original ICB project, where we show LSTMs trained on ICBe sequences can answer substantive macro level questions but not when trained on existing event project codings. -->

# Task Definition and Ground Truth

We consider the task of high-coverage information extraction from a historical episode between two or more states (e.g., the Cuban Missile Crisis). A historical episode is demarcated by a period of time $[T_{start}, T_{end}] \in T$ and a set of players $p \in P$. We posit that an episode can be divided into unique discrete events, $e \in E$, each consisting of a time period, one or more players, and a single behavior $e \equiv \{T_e, P_e, B_e\}$. The task is to produce sequences of parsimonious events that still reconstruct the important details of the original macro narrative.

We take as ground truth an unusually high-quality corpus of historical narratives and quantitative codings from the International Crisis Behavior (ICB) project [@brecherInternationalCrisisBehavior2017; @brecher_study_1997]. Their domain is 20th and 21st-century crises, defined as a change in the type or an increase in the intensity of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies or case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988]. The corpus is unique in IR because it is designed to be used in downstream quantitative coding projects. Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001]. Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p. 59]. Each of the `r n_crisis %>% scales::comma()` crises $c \in C$ are listed with summary information in Appendix \ref{app:crises}.

# Prior Beliefs and Existing State of the Art

Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$ and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$. We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table \ref{tbl:litreview}. The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology. We employ a metaphor of international affairs as a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do). Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict). The resulting codebook for events includes 117 different verbs and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]

The second axis (columns) represents sources of evidence for our concept priors and the existing state of the art. The first column ('Literature') maps each type of information to recent studies documenting its importance to IR. The second column ('ICB Corpus') documents the presence of that information in the ICB Corpus as identified by an expert review and natural language processing (Appendix \ref{app:verbs}). The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013]. Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].

```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}

#Lit review
#child=c('ICBEdataset_paper_litreviewtable.Rmd')
flextable::set_flextable_defaults(fonts_ignore=TRUE)
library(flextable)
library(ftExtra)
litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))

if(!TLS){
  litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 4, part="body")
}

litreview_ft %>%
  flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable_to_rmd()
```

# ICBe Coding and Aggregation Process

Each crisis was assigned to at least two expert coders, 3 to 5 novice coders, with a third tie-breaking expert coder assigned to sentences with high disagreement. Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook, while novice coders were undergraduate students who engaged in classroom workshops. Each coder was instructed to thoroughly read and familiarize themselves with the full text. Once a coder felt that they understood the crisis, the coder was presented with a novel graphic user interface (GUI) that steps the coder through the narrative sentence by sentence (Figure \ref{fig:coding_gui}).

\begin{figure}[H]
\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{figures/gui_example}}
\end{figure}

The GUI and the ontology follow a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020]. Proceeding in order, coders chose the number of events (0-3), the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities. Identifying armed means triggered questions regarding force size, fatalities, domains, units, etc. Location and timing information is always collected, each calling for specific answers when possible and general approximations. Together, this process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag. The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.

A novel feature of the ontology is that thought, speech, and do behaviors can be nested into combinations so that any unique combination is reachable if warranted by the event. For example, a speech could be about a threat to perform a do unless another do is performed, and each can be specified in full detail. Likewise, a thought can be about a fully defined speech or do. For example, in the Cuban Missile Crisis, the United States became aware that the Soviet Union performed an interaction of placing missile sites in Cuba. Through compounding, we can capture what players were said to have known, learned, or felt about specific fully described behaviors.

```{r include=FALSE}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)

avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)

avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
```

# Internal Measurement Validity -- Intercoder Agreement and Aggregating Disagreements

```{r, eval=T}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))

codings_long_agreement <- readRDS(file=paste0(here::here(),  '/replication_data/temp/codings_long_agreement.Rds'))

means1 <- codings_long_agreement %>%
  filter(value_normalized!='') %>%
  filter(total_coders>1) %>% #about 9k only had one coder
  #filter(selected_by_experts>=1) %>%
  dplyr::select(All=selected_by_any_perc,Experts=selected_by_experts_perc,Undergraduates=selected_by_undergrads_perc) %>% summarise_all(mean, na.rm=T)
means1_keep <- codings_long_agreement %>%
  filter(value_normalized!='') %>%
  filter(total_coders>1) %>% #about 9k only had one coder
  #filter(selected_by_experts>=1) %>%
  filter(keep==1) %>% dplyr::select(Accepted=selected_by_any_perc) %>% summarise_all(mean, na.rm=T)
meansall <- bind_rows(means1,means1_keep) %>% mutate(x=1) %>% pivot_longer(cols=c(-x)) %>% na.omit()

```

One form of internal validity for these codings is high agreement between coders when applying the ontology. We employ three ways to evaluate and maximize agreement: (1) multiple expert and novice coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence. The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.). There were `r icb_long_clean %>% pull(email_id) %>% unique() %>% length()` coders (including `r icb_long_clean %>% filter(email_id %>% str_detect("expert")) %>% pull(email_id) %>% unique() %>% length()` expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus. Of those, there were `r codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma()` unique sentence-tags applied by at least one coder. We ask how much support those possible tags received across coders, and how we should adjudicate disagreements when a tag was not chosen by every coder.

We evaluate agreement as the percentage of coders who voted for a tag proposed by any coder (Figure \ref{fig:intercoderagreement}). The average agreement across all coders is `r means1$All %>% round(2) %>% scales::percent()` (`r means1$Experts %>% round(2) %>% scales::percent()` across experts and `r means1$Undergraduates %>% round(2) %>% scales::percent()` across undergraduates). A post-aggregation algorithm described below raises mean agreement considerably to `r means1_keep$Accepted %>% round(2) %>% scales::percent()`. Further, there is expected heterogeneity in agreement with higher agreement for coarse, high-level decisions near the root of the ontology than for fine-grained, high-dimensional concepts further down the tree.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
# #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
# 
# 
# # moved to ICBEdataset_paper_PlotInterCoderAgreement
# p_percent_chose_tag_by_concept <- readRDS(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.Rds'))
# 
# ggplot2::ggsave(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.png'), 
#                 plot = p_percent_chose_tag_by_concept, width=8, height=6)
# 
# # created in ICBEdataset_paper_PlotInterCoderAgreement.Rmd. Has \\label{fig:intercoderagreement}. 
```

<!-- moved to paper/figure/ICBEdataset_paper_PlotInterCoderAgreement -->

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
\centering{\includegraphics[width=15cm]{figures/p_percent_chose_tag_by_concept.png}}
\end{figure}

To understand when and why coders disagree, we required self-reported confidence scores and reasons for low confidence. Overall, expert coders self-reported a high level of confidence in their own codings, reporting low confidence only about 20% of the time. When coders reported low confidence, they cited a mismatch between the ontology and the text about half of the time ("survey doesn't fit event" 45%) and noted a lack of information or confused writing in the source text the other half ("more knowledge needed" 40%, "confusing sentence" 6%). In addition, we observed that individual coders exhibit nontrivial coding styles. Some coders are more expressive and apply multiple tags per concept, while others focus on only the single best match and differ in how many events to code. We also observed unintended synonymity (e.g., the same information can be framed as a threat to do something or a promise not to do something if a condition is met).

This data-generating process suggests a theoretically motivated algorithm for aggregating over disagreements (Algorithm 1). We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of novice votes. If neither majority exists, we accept the one token with the most votes. This leaves `r codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()` (`r (codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() / codings_long_agreement %>% filter(value_normalized!='') %>% nrow()) %>% round(2) %>% scales::percent()`) accepted tokens. In practice, this screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts. A final step handles possible disagreement over the number of events or participants in the events. An event is emitted for each unique set of actors along with their surviving tags.

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Coder-Sentence-Tokens}
\KwResult{Sentence-Events}
\ForEach{sentence in sentences}{
  \ForEach{concept in concepts}{
    \ForEach{token in tokens}{
      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
    }
    \If{sum(accepted) == 0}{
      sort tags by votes;
      head 1;
      accept; \tcc*[f]{If still no tag, take one with most votes}
    }
  }
  \ForEach{ActorSet in unique(ActorSets)}{
    emit event;
  }
}
\caption{Aggregating Coder-Tokens into Sentence-Events}
\end{algorithm}

# Sentence Level Intrinsic Evaluation

Next, we ask whether codings agree with the raw source material at the sentence level. There are `r icb_long_clean %>% dplyr::select(sentence) %>% distinct() %>% nrow()  %>% scales::comma()` distinct sentences in the corpus. We start with a high-level view, taking the sentence texts and embedding them into a latent semantic space with a large language model specializing in sentence similarity, Sentence-BERT [@reimersSentenceBERTSentenceEmbeddings2019].^[We preprocess sentences to replace named entities with a generic Entity token.] Sentence embeddings are shown in Figure \ref{fig:semantic_embeddings}, disaggregated by four high-level ontology questions and each possible tag. Superficially, user applied tags tend to separate and cluster across semantic space in ways that suggests they are cueing on information actually provided by the text of the source sentence.

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
# MOVED TO figures/ICBEdataset_paper_figure_prep.Rmd

# #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
# p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/paper/figures/p_semantic_embeddings.Rds'))
# ggsave(file=paste0(here::here(), '//paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
```

\begin{figure}[H]
\caption{ICBe event codings in comparison to Semantic Embeddings from the Sentence-BERT large language model\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=15cm]{figures/p_semantic_embeddings.png}}
\textit{Notes:}
\end{figure}

Going further, we examine accepted tokens side-by-side with the original source material. We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tbl:15samplesentences}, 50 more in the online Appendix \ref{app:50samplesentences}, and the full set online. To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined). At the sentence level, we find codings accurately reflect the key events of the text. Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}

codings_wide_agreed_embeded_stratified_sample_ft_smaller <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds')) %>%
  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15) \\label{tbl:15samplesentences}") 
codings_wide_agreed_embeded_stratified_sample_ft_smaller

```

# Episode Level Intrinsic Evaluation and Comparison to State of the Art

To demonstrate validity at the level of entire episodes, we conduct two qualitative case studies; we choose the Cuban Missile Crisis for being very high stakes and widely recognized and the DRC Civil War for being particularly complicated, lengthy, and modern. In addition, we provide visualizations for every crisis with side-by-side comparisons across datasets on the companion website. Our goals are as follows: (1) establish necessary and secondary details of each crisis from secondary historical sources independent of the ICB corpus; (2) evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'; and (3) assess the recall of key events by the ICBe codings in comparison to the existing state-of-the-art datasets. For an event dataset to have good performance, it must both have high recall of salient facts, catching the key details and not just the trivia, and good precision, recording only events that actually occurred without distracting duplicates, miscodings, or other apparent examples of measurement error.

## Case Study: Cuban Missiles Crisis (1962)

The Cuban Missile Crisis occurred between the United States, the Soviet Union, and Cuba from October 16, 1962, to November 20, 1962. There are two critical points of context. First, the United States and Soviet Union enjoyed only a partial mutually assured destruction nuclear posture; the United States had accurate short-range ballistic missiles (SRBMs) in Europe and ICBMs, and the Soviet Union only had long-range, slow to arm, and relatively inaccurate ICBMs. Second, the United States launched the unsuccessful Bay of Pigs invasion of Cuba in April 1961.

The Soviet Union and Cuba reached an agreement to stage Soviet troops, tactical nuclear weapons, and medium-range ballistic missiles (MRBMs) in Cuba in May 1962. U.S. intelligence suspected these plans in August, and their presence was later confirmed by reconnaissance flights (October 14), ultimately triggering the main arc of the crisis.

The two great powers responded with both escalation and de-escalation. As escalations, the United States prepared a complete invasion of Cuba (October 17) and raised the nuclear alert status to DEFCON 3 (October 22) then partially to DEFCON 2 (October 24) [@brugioniEyeballEyeballStory1991]. Likewise, the Soviet Union mobilized (October 11) and went on alert (October 22). As de-escalations, the United States sought a diplomatic solution and imposed a naval blockade as a non-violent military measure to buy time while preventing further Soviet reinforcements from reaching Cuba. The main arc concludes with an agreement by the Soviet Union to withdraw entirely from Cuba, the U.S. agreeing never to invade Cuba, and a clandestine agreement by the U.S. to retire MRBMs based in Turkey.

A secondary crisis arc included several dangerous steps. Cuba mobilized all of its forces in preparation for an invasion (October 22). The United States continued aggressive violations of Cuban airspace by reconnaissance flights leading to the shooting down of a U.S. U-2 (October 27). Both sides went ahead with previously scheduled nuclear weapons tests (October 27-28). Finally, Cuba extended the crisis after the United States and Soviet Union reached their agreement, attempting and failing to retain Soviet bombers.

The precision and overall coherence of ICBe codings are shown in a side-by-side comparison of the source narrative and codings in Appendix \ref{app:ft_sentence_table_196} and via the crisis map in Figure \ref{fig:196metromap} below. The entire back-and-forth of the conflict can be directly read from the timeline. The deployment of the missiles is recorded as the cause of the crisis for the United States. The United States is recorded as demanding specifically that they be removed. After the agreement is reached, the fulfillment of that obligation is recorded with the withdrawal of the missiles specifically and the end of the blockade. There are some details lost in the translation. The tit-for-tat details of the agreement, particularly the exchange of missiles in Turkey, are lost. The detail of the missiles deployed to Cuba being nuclear is not recorded at first because the narrative only refers to them as missiles initially, but is later recorded correctly when the narrative becomes explicit. The brief Cuban gambit to keep some weapons is present in the ICB narrative but mostly ignored by the coders as of low importance. In sum, the ICBe codings correctly record the cause, response, and resolution of the crisis, the correct order of moves, and the size of the stakes at play. In comparison crisis maps of Cameo (Phoenix) (Figure \ref{fig:196metromap_phoenix}), ICB Dyadic Codings (Figure \ref{fig:196metromap_icb}), and MIDs (Figure \ref{fig:196metromap_mids}) in Appendix \ref{app:ft_sentence_table_196} do not reflect the overlying macro story nor the specific details of interest.

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
# moved to figures/ICBEdataset_paper_figure_prep.Rmd

# #ICBe  196
# library(ggplot2)
# p_metro_map_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_196.Rds'))
# actor_colors <- p_metro_map_196$actor_colors
# ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_196.png'),
#        plot = p_metro_map_196 +
#          theme(plot.margin=unit(c(0,0,0,0),"in")) +
#          scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
#          scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
#        width=12, height=14)

```

\begin{figure}[H]
\caption{Cuban Missile Crisis according to ICBe (us) \label{fig:196metromap}}
\centering{\includegraphics[width=19cm]{figures/p_metro_map_196.png}}
\end{figure}

Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tbl:casestudy196}. ICBe records 8 of 10 critical events identified by the case history. It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors. It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.

Only three other datasets have temporal coverage of this case. The Cline Historical Phoenix event dataset, which is based on Cameo dictionary codings of the New York Times and Wall Street Journal articles, only includes events that could be loosely mapped to one key turning point, the withdraw of missiles and peaceful resolution of the crisis. Two episode-level datasets contain temporal information on this crisis. A dyadic version of the original ICB dataset [@hewittDyadicProcessesInternational2003] contains information on 6 of the critical events, but describes them in terms that are too vague to reconstruct the episode. For example, the deployment of nuclear weapons is described only as an "external change," and the response of mobilizations for war and the blockade are a "non-violent military act." The Dyadic Militarized Interstate Disputes (MIDs) dataset [@maozDyadicMilitarizedInterstate2019] includes only two possible mappings, a 'show of troops' near the start of the crisis, and a 'yield to' near the end.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
CaseStudy196_ft %>%
  flextable::set_caption("Cuban Missile Crisis ground truth and event data \\label{tbl:casestudy196}") %>%
    flextable::width( j = 1, width=0.5)  %>%
    flextable::width( j = 2, width=1.25)  %>%
    flextable::width( j = 3, width=0.5) %>%
    flextable::width( j = 4, width=1.1) %>%
    flextable::width( j = 5, width=1) %>%
    flextable::width( j = 6, width=0.75) %>%
    flextable::width( j = 7, width=0.65)

```

## Case Study: DRC Civil War (1998)

The civil war in the Democratic Republic of Congo (DRC), also called the Second Congo War and the Great African War, took place between 29 July 1998 and 30 July 2002 and included Angola, Chad, the DRC, Namibia, Rwanda, Uganda, and Zimbabwe. The necessary background for the episode is that in May 1997 Rwandan-backed rebels helped install Laurent Kabila as President of the DRC. The main arc of the episode begins a year later when Kabila then seeks to distance himself from Rwanda and demands that the rebels leave DRC territory (July 27, 1998). The main response is that they refuse and instead begin a campaign for the capital, still backed by Rwanda. The main arc ends with the DRC successfully defending against the campaign and reaching a peace agreement with Rwanda (July 30, 2002), Uganda (September 6, 2002), and other participants, including rebel groups (December 17, 2002) [@lansfordPoliticalHandbookWorld2021; @kisanganiHistoricalDictionaryDemocratic2010].

A secondary arc concerns third-party involvement and political upheaval within the DRC. First, the conflict brings Uganda in on the side of Rwanda, and Angola, Namibia, Zimbabwe, and Chad in on the side of the DRC. Second, a United Nations-sponsored mediation produced a failed cease-fire (July 10, 1999) and a U.N. peacekeeping mission (MONUC) (September 30) [@lansfordPoliticalHandbookWorld2021; @kisanganiHistoricalDictionaryDemocratic2010]. Finally, Laurent Kabila was assassinated (January 17, 2001) and was succeeded by his son Joseph Kabila (January 24), who showed a higher tolerance of U.N. involvement [@schererPeaceKeepsUnited2015].

Precision and overall narrative coherence for the DRC case is strong, as demonstrated by side-by-side ICBe event codings in Appendix \ref{app:ft_sentence_table_426}, and shown visually as a crisis map in Figure \ref{fig:426metromap} below. The overall details of the crisis can be read from the timeline, particularly the invasion by Uganda and Rwanda of the DRC, several short-lived cease fires,  the shift in internal politics of the DRC due to the assassination and leadership change, a U.N. intervention, and final formal agreements to end the crisis. The role of the numerous third parties (Chad, Zimbabwe, Angola, and Namibia) who intervened on different sides is less clear. Similarly, the group structure of sub-national actors, who are represented as agents acting on behalf of Rwanda and Uganda, is ambiguous.

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

# moved to figures/ICBEdataset_paper_figure_prep.Rmd

# #ICBe  426
# p_metro_map_426 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_426.Rds'))
# actor_colors <- p_metro_map_426$actor_colors
# ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_426.png'),
#        plot = p_metro_map_426 +
#          theme(plot.margin=unit(c(0,0,0,0),"in")) +
#          scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
#          scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
#        width=12, height=14)

#devtools::install_github('davidgohel/ggiraph')

```

\begin{figure}[H]
\caption{DRC Civil War according to ICBe (us)  \label{fig:426metromap}}
\centering{\includegraphics[width=19cm]{figures/p_metro_map_426.png}}
\end{figure}

By comparison, crisis maps of Cameo (Phoenix) (Figure \ref{fig:426metromap_phoenix}), ICEWS (Figure \ref{fig:426metromap_icews}), and Terrier (Figure \ref{fig:426metromap_terrier}), are unintelligible despite deduplication and heavy filtering of irrelevant or uninteresting events. The automated dictionary coding of news articles produces too many irrelevant events between unimportant actors or describes important events too vaguely to be used directly, and instead may only be interpretable in terms of weighted counts over time [@terechshenkoHotCollarLatent2020]. ICB Dyadic Events (Figure \ref{fig:426metromap_icb}), MIDs Incidents (Figure \ref{fig:426metromap_mids_incidents}), and MIDs Episodes (Figure \ref{fig:426metromap_mids}) do a good job showing the start and stop of conflict and between which actors, but lose any detailed context.

Recall of critical events is shown in Table \ref{tbl:casestudy426} below. ICBe records 10 of 14 critical events identified by the case history. It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N. peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC. These details were under-textualized in the ICB narrative. Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets. As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events. Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event. The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila. The MIDs incident-level dataset includes possible coverage of 4 events. MIDs episode-level data incorporates possible coverage of 6 events. Finally, Dyadic ICB data cover 7 events.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
CaseStudy426_ft  %>%
  flextable::set_caption("DRC Civil War ground truth and event data \\label{tbl:casestudy426}") %>%
      width(j=1, width=0.5) %>%
      width(j=2, width=0.75) %>%
      width(j=3, width=0.3) %>%
      width(j=4, width=0.65) %>%
      width(j=5, width=1.0) %>%
      width(j=6, width=0.5) %>%
      width(j=7, width=0.75) %>%
      width(j=8, width=0.75) %>%
      width(j=9, width=0.5) %>%
      width(j=10, width=0.5)

```

# Conclusion

We investigated event extraction from narratives describing key historical episodes in international relations. We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record. We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts. Multiple validity checks find the resulting codings have high internal validity (e.g. intercoder agreement) and external validity (i.e. matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes). Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.

We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing. The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project. These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g. escalation and de-escalation of conflicts). Second, we provide a coder-level disaggregation with multiple codings of each sentence  by experts and novices that allows for the introduction of uncertainty and human interpretation of events. Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing. Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).

#### Acknowledgments:
We would like to thank the ICB Project and its directors and contributors for their foundational work and their help with this effort. We would like to make a special acknowledgment to Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.

We thank the many undergraduate coders for their patience and dedication. Thanks to the Center for Peace and Security Studies and its membership for comments. Thank you to the many research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang. This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.

#### Author contributions (alphabetical):
<!-- following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit -->
Conceptualization: R.W.D., E.G., J.L.;
Methodology: R.W.D., T.L.S.;
Software: R.W.D.;
Validation: R.W.D., T.L.S.;
Formal Analysis: R.W.D., T.L.S.;
Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;
Data Curation: R.W.D., D.Q., T.L.S., J.W.;
Writing - Original Draft: R.W.D., T.L.S.;
Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
Visualization: R.W.D., T.L.S.;
Supervision: E.G.;
Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
Funding Acquisition: E.G., J.L.

\newpage
# References

<!-- uses zotero folder ICBintro -->
<div id="refs"></div>
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html -->
<!-- may require additional software -->

\newpage

# Online Appendix

## Appendix 1: ICB Crises and Summary Information {#app:crises}

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
#ICBEdataset_paper_appendixICBCrises.Rmd
crisis_text_counts_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/ft_crisis_text_counts.Rds'))
crisis_text_counts_ft
```

## Appendix 2: Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
#, child=c('ICBEdataset_paper_appendixVerbMeanings.Rmd')

verbs_sentence_wordnet_top_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
verbs_sentence_wordnet_top_ft
```

## Appendix 3: Sentence Examples {#app:50samplesentences}

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
  flextable::set_caption("ICBe Codings for 50 Sample Sentences \\label{tbl:50samplesentences}")

codings_wide_agreed_embeded_stratified_sample_ft %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.5) %>%
      flextable::width( j = 3, width=3.5)
```

## Appendix 4: Cuban Missile Crisis {#app:ft_sentence_table_196}

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
ft_sentence_table_196 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_196.Rds'))  %>%
  flextable::set_caption("ICBe Codings for Cuban Missile Crisis (Crisis 196) \\label{tbl:ft_sentence_table_196}") 
ft_sentence_table_196 %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.25) %>%
      flextable::width( j = 3, width=3.25)
```

\begin{figure}[H]
\caption{Cuban Missile Crisis according to Phoenix \label{fig:196metromap_phoenix}}
\centering{\includegraphics[width=19cm]{figures/p_phoenix_metro_plot_196.png}}
\end{figure}

\begin{figure}[H]
\caption{Cuban Missile Crisis according to ICB \label{fig:196metromap_icb}}
\centering{\includegraphics[width=19cm]{figures/p_icb_metro_plot_196.png}}
\end{figure}

\begin{figure}[H]
\caption{Cuban Missile Crisis according to MIDs Episodes \label{fig:196metromap_mids}}
\centering{\includegraphics[width=19cm]{figures/p_mids_metro_plot_196.png}}
\end{figure}

## Appendix 5: DRC {#app:ft_sentence_table_426}

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
ft_sentence_table_426 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_426.Rds'))  %>%
  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426) \\label{tbl:ft_sentence_table_426}") 
ft_sentence_table_426 %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.25) %>%
      flextable::width( j = 3, width=3.25)
```

\begin{figure}[H]
\caption{DRC Civil War according to Phoenix \label{fig:426metromap_phoenix}}
\centering{\includegraphics[width=19cm]{figures/p_phoenix_metro_plot_426.png}}
\end{figure}

\begin{figure}[H]
\caption{DRC Civil War according to ICEWS \label{fig:426metromap_icews}}
\centering{\includegraphics[width=19cm]{figures/p_icews_metro_plot_426.png}}
\end{figure}

\begin{figure}[H]
\caption{DRC Civil War according to Terrier \label{fig:426metromap_terrier}}
\centering{\includegraphics[width=19cm]{figures/p_terrier_metro_plot_426.png}}
\end{figure}

\begin{figure}[H]
\caption{DRC Civil War according to Dyadic ICB \label{fig:426metromap_icb}}
\centering{\includegraphics[width=19cm]{figures/p_icb_metro_plot_426.png}}
\end{figure}

\begin{figure}[H]
\caption{DRC Civil War according to MIDs Incidents \label{fig:426metromap_mids_incidents}}
\centering{\includegraphics[width=19cm]{figures/p_mids_incidents_metro_plot_426.png}}
\end{figure}

\begin{figure}[H]
\caption{DRC Civil War according to MIDs Episodes \label{fig:426metromap_mids}}
\centering{\includegraphics[width=19cm]{figures/p_mids_metro_plot_426.png}}
\end{figure}

### 2022-01-20 replication_paper/rmd/CaseStudy196.Rmd
Init

---
title: "CaseStudy196.Rmd"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}

library(pacman)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}

CaseStudy196 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", sheet="CaseStudy196")

```

```{r, echo=FALSE, results='asis', include=T, cache=F, ft.arraystretch=0.75}

#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
# NOTE: If one of the citations is degenerate this will thow an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
set_flextable_defaults(fonts_ignore=TRUE)

n=nrow(CaseStudy196)
CaseStudy196_ft <- NULL
CaseStudy196_ft <- CaseStudy196 %>%
      flextable::as_flextable() %>%
      add_header( 
                  "Actor"="Ground Truth",
                  "Event"="Ground Truth",
                  "Date"="Ground Truth",
                  "ICBe (us)"="Events",
                  "Cameo (Phoenix)"="Events",
                  "ICB Dyadic"="Episodes",
                  "MIDs"="Episodes",
                  top = TRUE ) %>%

      #set_header_labels(
      #  values = list("...1" = "" , "...2" = "" ) 
      #  ) %>%
      merge_h(part = "header") %>%

      #bg( i=1:(n) , j = condition, part = "body", bg = "#EFEFEF") %>%
      #bg( i=2 , j = condition, part = "header", bg = "#EFEFEF") %>%
      bg( i = which( 1:nrow(CaseStudy196) %% 2 == 1)  , j=1:ncol(CaseStudy196), part = "body", bg = "#EFEFEF") %>%
      #width(j = 1, width=1.25) %>%
      #width(j = 2:ncol(lit_review_alt), width=0.25) %>%
      flextable::fontsize(size = 7, part = "all") %>%
      #flextable::rotate(i=2, rotation="tbrl",part="header") %>%
      #flextable::set_header_labels( values = list(x1 = "", x2 = "")) %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

      flextable::colformat_char(
          j = 1:ncol(CaseStudy196),
          na_str = "",
          prefix = "",
          suffix = ""
      ) %>%

      #hline(i=c(1), j=3:ncol(lit_review_alt),  border = NULL, part = "header") %>%
      #hline(i=c(2,3,7,10,15, 19, 27), border = NULL, part = "body") %>% #,10,14, 20,27,37, n

      #set_table_properties(layout="autofit")  %>%
      #vline( i = 1:2, j = c(1,2,3,7)+2, border = NULL, part = "header") %>%
      vline( i = 1:2, j = c(3,5), border = NULL, part = "header")  %>%
      vline( i = 1:(n), j = c(3,5), border = NULL, part = "body")

      #autofit()
      #fit_to_width(max_width=12) #This is crazy slow
      #flextable::autofit() 
      #set_table_properties(width = 1, layout = "autofit")

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

CaseStudy196_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/CaseStudy196_ft.Rds'))

CaseStudy196_ft

```

### 2022-01-20 replication_paper/rmd/CaseStudy426.Rmd
Init

---
title: "CaseStudy426.Rmd"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}

library(pacman)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}

CaseStudy426 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", sheet="CaseStudy426")

```

```{r, echo=FALSE, results='asis', include=T, cache=F, ft.arraystretch=0.75}

#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
# NOTE: If one of the citations is degenerate this will thow an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
set_flextable_defaults(fonts_ignore=TRUE)

n=nrow(CaseStudy426)
CaseStudy426_ft <- NULL
CaseStudy426_ft <- CaseStudy426 %>%
      flextable::as_flextable() %>%
      add_header( 
                  "Actor(s)"="Ground Truth",
                  "Event"="Ground Truth",
                  "Date"="Ground Truth",
                  "ICBe (us)"="Events",
                  "Phoenix"="Events",
                  "Terrier"="Events",
                  "ICEWS"="Events",
                  "MIDs Incidents"="Events",
                  "MIDs"="Episodes",
                  "ICB Dyadic"="Episodes",
                  top = TRUE ) %>%

      #set_header_labels(
      #  values = list("...1" = "" , "...2" = "" ) 
      #  ) %>%
      merge_h(part = "header") %>%

      #bg( i=1:(n) , j = condition, part = "body", bg = "#EFEFEF") %>%
      #bg( i=2 , j = condition, part = "header", bg = "#EFEFEF") %>%
      bg( i = which( 1:nrow(CaseStudy426) %% 2 == 1)  , j=1:ncol(CaseStudy426), part = "body", bg = "#EFEFEF") %>%
      #width(j = 1, width=1.25) %>%
      #width(j = 2:ncol(lit_review_alt), width=0.25) %>%
      flextable::fontsize(size = 7, part = "all") %>%
      #flextable::rotate(i=2, rotation="tbrl",part="header") %>%
      #flextable::set_header_labels( values = list(x1 = "", x2 = "")) %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

      flextable::colformat_char(
          j = 1:ncol(CaseStudy426),
          na_str = "",
          prefix = "",
          suffix = ""
      ) %>%

      #hline(i=c(1), j=3:ncol(lit_review_alt),  border = NULL, part = "header") %>%
      #hline(i=c(2,3,7,10,15, 19, 27), border = NULL, part = "body") %>% #,10,14, 20,27,37, n

      #set_table_properties(layout="autofit")  %>%
      #vline( i = 1:2, j = c(1,2,3,7)+2, border = NULL, part = "header") %>%
      vline( i = 1:2, j = c(3,8), border = NULL, part = "header")  %>%
      vline( i = 1:(n), j = c(3,8), border = NULL, part = "body")

      #autofit()
      #fit_to_width(max_width=12) #This is crazy slow
      #flextable::autofit() 
      #set_table_properties(width = 1, layout = "autofit")

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

CaseStudy426_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/CaseStudy426_ft.Rds'))

CaseStudy426_ft

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_appendix.Rmd
Init

---
title: "Online Appendix: Supporting Information for _Introducing the International Crisis Behavior Event (ICBe) Dataset_"
authors:
  - name: Shannon Carcelli
    department: Department of Political Science
    affiliation: University of Maryland, College Park
    location: 
    email: 
  - name: Rex W. Douglass
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: 
  - name: J Andrés Gannon
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: 
  - name: Erik Gartzke
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: 
  - name: Jon Lindsay
    department: Munk School of Global Affairs and Public Policy and Department of Political Science
    affiliation: University of Toronto
    location: Toronto, ON, Canada
    email: jon.lindsay@utoronto.ca
  - name: Thomas Leo Scherer
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: tlscherer@ucsd.edu
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
---

```{r echo=FALSE}
`%>%` <- magrittr::`%>%`
```

<!-- # (APPENDIX) Appendix {-}  -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html -->
<!-- may require additional software -->

\begin{figure}[h]
\caption{Action Event Classification Tree\label{fig:event_action_tree}}
\centering{\includegraphics[width=17cm]{figures/event_action_tree}}
\end{figure}

\begin{figure}[h]
\caption{Graphical User Interface (GUI) for coding ICBED\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{figures/gui_example}}
\end{figure}

\begin{figure}
\caption{Crisis Actors counts for ICB Project system-level data and for ICBe \label{fig:actors_by_crisis}}
\centering{\includegraphics[width=17cm]{figures/actors_by_crisis}}
\textit{Notes:} The number of perceived actors in each crisis as recorded by the ICB Project vs. the number of actors recorded in the ICBe dataset, with and without non-state actors.
\end{figure}

```{r echo=FALSE}
read.csv(paste0(here::here(), "/inst/extdata/","icb1v14.csv")) %>% dplyr::count(crismg) %>% 
  dplyr::mutate(crismg = dplyr::recode(crismg, `1` = "1: Negotiation", `2`="2: Adjudication", `3`= "3: Mediation", `4` = "4: Multiple excluding violence", `5` = "5: Non-military pressure", `6` = "6: Non-violent military", `7` = "7: Multiple including violence", `8` = "8: Violence")) %>%
  dplyr::rename(`Management Technique` = crismg) %>% 
  kableExtra::kbl(caption="Count of ICB Project Crisis-Level Management Technique \\label{tbl:ICBproject_crisis_management_technique}") %>% kableExtra::row_spec(0,bold=TRUE)
```

```{r echo=FALSE}
event_percent_diff_by_crismg <- readRDS(file=paste0(here::here(), "/data/event_percent_diff_by_crismg.rds"))

event_percent_diff_by_crismg_tableprep <- event_percent_diff_by_crismg %>% 
    dplyr::mutate(action_type = dplyr::recode(action_type, `thinkkind` = "Think", `sayintkind`="Speech", 
                                       `act_cooperative_clean` = "Cooperative", 
                                       `act_descalate_clean` = "De-escalatory ", 
                                       `act_escalate_clean` = "Escalatory", 
                                       `act_uncooperative_clean` = "Uncooperative", 
                                       `interact_decreasecoop_clean` = "Uncooperative", 
                                       `interact_increasecoop_clean` = "Cooperative", 
                                       `interact_descalate_clean` = "De-escalatory ", 
                                       `interact_escalate_clean` = "Escalatory")) %>% 
  dplyr::arrange(desc(All)) %>% 
  dplyr::slice_head(n=20)

event_percent_diff_by_crismg_tableprep <- dplyr::bind_cols(event_percent_diff_by_crismg_tableprep[1:3],
  lapply(event_percent_diff_by_crismg_tableprep[4:11], function(x) {
  x.c <- paste0(ifelse(x > 0, "+", ""), round(x, digits = 2))}))
```

```{r echo=FALSE}
event_percent_diff_by_crismg_tableprep %>%  dplyr::mutate(action = dplyr::recode(action, `invasion/occupation` = "invasion / occupation")) %>% 
  dplyr::rename(`All Crises` = "All", `CMT 1: Negotiation` = "1: Negotiation", `CMT 2: Adjud`="2: Adjudication", `CMT 3: Medi`= "3: Mediation", `CMT 4: Multi no violence` = "4: Multiple excluding violence", `CMT 5: Non-mil pressure` = "5: Non-military pressure", `CMT 6: Non-violent mil` = "6: Non-violent military", `CMT 7: Multi with violence` = "7: Multiple including violence", `CMT 8: Violence` = "8: Violence") %>% 
  dplyr::select(-`CMT 2: Adjud`, -`CMT 3: Medi`, -`CMT 5: Non-mil pressure`) %>%
  kableExtra::kbl(caption="Average Percentage of Event Types in a Crisis by Management Technique (CMT) \\label{tbl:crismg_count_mean_table}")  %>%
  # kableExtra::kable_styling() %>% 
  kableExtra::column_spec(2, latex_column_spec = "p{1.8cm}") %>%
  kableExtra::column_spec(4, latex_column_spec = "p{1.2cm}") %>%
  #kableExtra::column_spec(5, latex_column_spec = "p{.8cm}") %>%
  #kableExtra::column_spec(6, latex_column_spec = "p{.8cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{1.4cm}") %>%
  #kableExtra::column_spec(8, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(6, latex_column_spec = "p{1.4cm}") %>%
  kableExtra::column_spec(7, latex_column_spec = "p{1.4cm}") %>%
  kableExtra::column_spec(8, latex_column_spec = "p{1.4cm}")
  # kableExtra::column_spec(8, width = "1.4cm") %>% 
  # kableExtra::collapse_rows()
```

\begin{figure}
\caption{Crisis event counts from Phoenix and ICB for crises with and without USA\label{fig:phoenix_event_counts_usa}}
\centering{\includegraphics[width=17cm]{figures/phoenix_event_counts_usa}}
\end{figure}

```{r echo=FALSE, message=FALSE}
readRDS(file=paste0(here::here(), "/data/liberia_sierraleone_phoenix.Rds"))%>% 
  kableExtra::kbl(caption="Phoenix Events for Liberia / Sierra Leone (Crisis 395) \\label{tbl:liberia_sierraleone_phoenix}") %>%  
  kableExtra::column_spec(4, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{7cm}")
  # kableExtra::column_spec(2, width = "1cm")
```

```{r echo=FALSE, message=FALSE}
readRDS(file=paste0(here::here(), "/data/liberia_sierraleone_extended.Rds")) %>% 
  kableExtra::kbl(caption="Extended Phoenix Events for Liberia / Sierra Leone (Crisis 395) \\label{tbl:liberia_sierraleone_phoenix_extended}") %>%  
  kableExtra::column_spec(4, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{7cm}")
  # kableExtra::column_spec(2, width = "1cm")
```

```{r echo=FALSE, message=FALSE}
drc_icb <- readRDS(file=paste0(here::here(),"/data/drc_icb.Rds"))

drc_required_phoenix <- readRDS(file=paste0(here::here(), "/data/drc_required_phoenix.Rds"))

drc_required_phoenix_table <- readRDS(file=paste0(here::here(), "/data/drc_required_phoenix_table.Rds"))

```

```{r echo=FALSE, message=FALSE}
data.frame(lapply(drc_icb, function(x) {gsub("democratic_republic_of_the_congo", "DRC", x)})) %>% 
  dplyr::select(-sentence_number_int_aligned) %>% 
  dplyr::slice(16:41) %>%
  kableExtra::kbl(caption="ICBe Dataset for DRC Civil War (Crisis 426) around August 1998 \\label{tbl:drc_icb}") %>%
  kableExtra::column_spec(1, latex_column_spec = "p{1.8cm}") %>%
  kableExtra::column_spec(2, latex_column_spec = "p{3.5cm}") %>%
  kableExtra::column_spec(3, latex_column_spec = "p{2.5cm}") %>% 
  kableExtra::column_spec(5, latex_column_spec = "p{3.5cm}")
```

```{r echo=FALSE, message=FALSE}
drc_required_phoenix_table %>% 
  dplyr::select(`Story Date`, Source, Target, `Event Code`, Event, Corpus) %>% 
  dplyr::slice_head(n=20) %>%
  kableExtra::kbl(caption="First 20 Phoenix Events (DRC-required) for DRC Civil War (Crisis 426) \\label{tbl:drc_civil_war_start_phoenix}") %>%  
  kableExtra::column_spec(4, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{7cm}")
  # kableExtra::column_spec(2, width = "1cm")
```

```{r echo=FALSE, message=FALSE}
drc_required_phoenix %>% dplyr::filter(year == "2001" & month == "01") %>% dplyr::count(EventDescription, sort=TRUE) %>%
  kableExtra::kbl(caption="Phoenix Events (DRC-required) for January 2001 DRC Civil War (Crisis 426) \\label{tbl:drc_civil_war_jan2001_phoenix}")
  # kableExtra::column_spec(2, width = "1cm")
```

### 2022-01-20 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
Init

---
title: "Metro Maps"
output: html_document
---

# Metro Maps

```{r}

#devtools::install_github('davidgohel/ggiraph')
library(ggplot2)
library(ggiraph)

library(flextable)
library(ftExtra)
library(tidyverse)
library(googlesheets4)
library(RColorBrewer)
library(tidyverse)
library(ggraph)
#library(edgebundle)
library(igraph)
library(stringr)

rex_paste <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}
rex_count <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}

```

# Common Preprocessing and Loads

```{r echo=FALSE, include=FALSE, eval=T}

icb_crises <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds") )

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))

crisno_name_years <- icb_crises %>% dplyr::select(crisno, crisname, yrtrig, yrterm)

target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)

dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()

codings_long <- readRDS( paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds")) 
codings_long_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))

#Design specification
#Time flows downward
#Each actor gets a line
#Spacing between lines should be dynamic, to allow for readability between
#We want the name of each actor to be labeled at the start of their line
#Unilateral actions printed above

actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)

```

# ICBe

## ICBe metro plots

```{r}

#codings_wide_agreed_pruned_labeled %>% dplyr::select(start_time)

icbe_metro_plots <- function(crisis=196, prune_rare=T){

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/paper/figures/metro_plots/p_metro_plot_",crisis,".Rds")

  codings_wide_agreed_subset <- codings_wide_agreed %>% 
                                 ungroup() %>%
                                 dplyr::filter(crisno==crisis) %>%  #417 196
                                 dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))  %>%
                                 mutate(point_in_time_year = point_in_time %>% substr(start=1, stop=4) %>% as.numeric() ) %>%
                                 mutate(point_in_time_month = point_in_time %>% substr(start=6, stop=7) %>% as.numeric() )

  codings_wide_agreed_subset_diad <- codings_wide_agreed_subset %>% 
                                    mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a) %>%
                                    mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a) %>%
                                    mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b) %>%
                                    mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
                                    mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b) %>%
                                    dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
                                                  sent=final_event_ordering,
                                                  think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,leaf_think_original, leaf_say_original, leaf_do_original,
                                                  point_in_time_year, point_in_time_month) %>% distinct() %>%
                                        filter(!duplicated(paste(sentence_number_int_aligned,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, leaf_think_original, leaf_say_original, leaf_do_original)))

  notes=NULL
  if(prune_rare==T){
    actor_sent_counts <- 
      bind_rows(
          codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
          codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
          codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
          codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a),
          codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
        ) %>% 
          na.omit() %>%
          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

      singleton_actors <- actor_sent_counts %>% filter(n==1) %>% pull(actor)
      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
      if(left_over_count<=3){
        #Skip pruning if it leaves less than 3 actors
      } else {

        actor_map <- dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) 
        actor_singleton_labels <- actor_map$value_normalized_label
        names(actor_singleton_labels) <- actor_map$actor
        actor_singleton_labels <- actor_singleton_labels[singleton_actors]

        notes <- paste("Not shown: ", paste( actor_singleton_labels, collapse="; " ))

        #Easiest thing is to just prune the original data
        codings_wide_agreed_subset <- codings_wide_agreed_subset %>%
          filter(!(
                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
                say_actor_a %in% singleton_actors |
                say_actor_b %in% singleton_actors |
                do_actor_a %in% singleton_actors |
                do_actor_b %in% singleton_actors 
          ) )

        codings_wide_agreed_subset_diad <- codings_wide_agreed_subset_diad %>%
          filter(!(
                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
                say_actor_a %in% singleton_actors |
                say_actor_b %in% singleton_actors |
                do_actor_a %in% singleton_actors |
                do_actor_b %in% singleton_actors 
          ) )
      }
  }

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  #Order actors by how many interactions they have together
  temp <- bind_rows(
    codings_wide_agreed_subset_diad  %>% 
      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
    codings_wide_agreed_subset_diad %>% 
      filter(is.na(leaf_say_original)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
  )  %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("actor_2", "actor_1", "sent"))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  temp_list <- list()
  for(i in 1:nrow(temp2_wide)){
    temp_list[[as.character(i)]] <- cutree(hc, k=i)
  }

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
            )  %>%
            filter(!is.na(actor)) %>%
           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                      mutate(x=max(x)+50) %>%
                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
                      na.omit() %>% 
                      distinct() %>%  
                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                      group_by(sent) %>%
                       filter(year_float==min(year_float)) %>%
                      ungroup() %>% as.data.frame() %>%
                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                      filter(!duplicated(year_float ) ) %>%
                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

    #Units
  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here, '/paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*10)

  fatalities <-   codings_wide_agreed_subset %>% 
        dplyr::select(crisno, sent=final_event_ordering, do_actor_b, interact_fatalities) %>% na.omit() %>% #filter(interact_fatalities!='none') %>%
        mutate(interact_fatalities = strsplit(as.character(interact_fatalities), ";")) %>% unnest(interact_fatalities) %>%
        mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b) %>%
        mutate(actor_sent= do_actor_b %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
        left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
        rename(actor=do_actor_b) %>%
        #dplyr::select(-sent, -do_actor_b) %>%
        distinct() %>% 
        mutate(interact_fatalities=interact_fatalities %>% factor(levels=c('none','individuals','tens','hundreds','thousands','tens of thousands','hundreds of thousands')) %>% as.numeric() ) %>%
        arrange(actor_sent, interact_fatalities) %>%
        group_by(actor_sent) %>%
          filter(interact_fatalities==max(interact_fatalities, na.rm=T)) %>%
        ungroup()

  #table(codings_wide_agreed$interact_fatalities)
  #table(codings_wide_agreed$interact_domains)
  #table(codings_wide_agreed$interact_forces)

  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here(), "/paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*5)

  ####Actor lavels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
    rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)

  ######Monads
  codings_wide_agreed_subset_monad <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(sentence_number_int_aligned, sent, actor=think_actor_a,leaf=leaf_think_original) ,
                      codings_wide_agreed_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sentence_number_int_aligned, sent,actor=say_actor_a,leaf=leaf_say_original) ,
                      codings_wide_agreed_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select(sentence_number_int_aligned, sent,actor=do_actor_a,leaf=leaf_do_original) 
            ) %>% 
            na.omit() %>% 
            distinct() %>% 
            filter(!duplicated(paste(sentence_number_int_aligned,actor,leaf))) %>%
            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
            distinct() %>% 
            group_by(sent,actor,actor_sent) %>%
              summarise(leaf=paste(leaf, collapse="\n") ) %>%
            left_join( codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent,x,y))

  ######Directed
  codings_wide_agreed_subset_directed <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% filter(is.na(leaf_do_original)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf_say_original) ,
                      codings_wide_agreed_subset_diad %>% filter(!is.na(leaf_do_original)) %>% mutate(leaf=paste0(leaf_say_original,"-",leaf_do_original)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf),
                      codings_wide_agreed_subset_diad %>% filter(is.na(leaf_say_original)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf_do_original) 
            ) %>% 
            na.omit() %>% 
            distinct() %>% 
            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
           arrange(sent, actor_sent_1,leaf) %>%
           filter(actor_sent_1!=actor_sent_2) #there's a bug where you get the same node on both sides somehow
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  #debug
  codings_wide_agreed_subset_directed <- codings_wide_agreed_subset_directed  %>% 
           group_by(sent, leaf) %>%
               mutate(bundle_count=n()) %>%
               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
            ungroup() #%>% 
            #filter(bundle_count>1)

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf2, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1,
                       bundle_count=codings_wide_agreed_subset_directed$bundle_count
                       )

    #https://www.flaticon.com/free-icons/aircraft-carrier
  #install.packages('ggimage')
  library(ggimage)

  #hbundle <- edge_bundle_hammer(g, xy, bw = 0.7, decay = 0.5)

  ######Put it all together
  p_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +

          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T & bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +
              #Grouped Edges
              geom_edge_parallel(aes(  
                                  colour=actor,
                                  label=leaf,
                                  filter=eventedge==T & bundle_count>1
                                  ),
                              vjust = -0.75,
                              lineheight = .75,
                              sep = unit(5, 'mm'), 
                              edge_width=0.4,  #0.25
                              show.legend = F,
                              arrow = arrow(length = unit(1, 'mm')),
                              label_size=4,
                              check_overlap=T,
                              start_cap = circle(3, 'mm'),
                              end_cap = circle(3, 'mm'),
                              angle_calc = 'along'
                             ) +

              #Time edges
              geom_edge_link(aes(
                              edge_colour=actor,
                              filter=timeedge==T
                              ),
                              edge_width=0.1, 
                              show.legend = F,
                              check_overlap=T
                             ) +
              geom_node_point(aes(color=actor),size=1,stroke=0.5) +

              geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap = T) +
              geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap = T) +
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=qcode), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
                        check_overlap = T) + #-45
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") +
              ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  if(prune_rare==T & !is.null(notes)){
     p_metro_map <- p_metro_map + labs(caption = notes)
  }

  p_metro_map$actor_colors <- actor_colors #we have to smuggle the variable containing the colors out in the object 
  p_metro_map$sentence_count <- codings_wide_agreed_subset$final_event_ordering %>% unique() %>% length()
  p_metro_map$codings_wide_agreed_subset <- codings_wide_agreed_subset

  p_metro_map   %>% saveRDS(save_file)

  return(NULL)
}

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icbe_metro_plots(x))

```

## ICBe Tables

Go ahead an out the sentence tables too here why not

```{r}

icb_sentence_tables <- function(crisis=196){
  print(crisis)
  ft_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/paper/tables/sentence_tables/ft_sentence_table_",crisis,".Rds")

  temp <- codings_wide_agreed %>% 
          filter(crisno==crisis) %>%
              group_by(crisno, final_event_ordering, crisno_sent, sentence) %>%
                summarize(codings_sentence = paste(codings_sentence, collapse="\n")) %>%
              ungroup() %>%
              dplyr::select(id=crisno_sent, sentence, codings_sentence)

  temp_ft <- temp %>%
              as_flextable() %>%
              colformat_md(j=3) %>% #There can be bad unicode characters in the sentence so make sure you only make the coded sentence markdown
              flextable::fontsize(size = 7, part = "all") %>%
              flextable::bg( i = which( 1:nrow(temp) %% 2 == 1)  , j=1:3, part = "body", bg = "#EFEFEF") %>%
              flextable::width(j = 1, width=0.3, unit = "in") %>%
              flextable::width(j = 2, width=4, unit = "in") %>%
              flextable::width(j = 3, width=4, unit = "in")

  temp_ft  %>% saveRDS(save_file)
}

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icb_sentence_tables(x))

```

# Dyadic Mids

## Data Loads

```{r}

mid_df <- data.frame(
  stringsAsFactors = FALSE,
               act = c(1L,2L,3L,4L,5L,6L,7L,8L,
                       9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
                       20L,21L,22L),
         act_label = c("1. None (1)",
                       "2. Threat to use force (2)","3. Threat to blockade (2)",
                       "4. Threat to occupy terr. (2)","5. Threat to declare war (2)",
                       "6. Threat to join war (2)","7. Show of troops (3)",
                       "8. Show of ships (3)","9. Show of planes (3)","10. Alert (3)",
                       "12. Mobilization (3)","13. Fortify border (3)",
                       "14. Border violation (4)","15. Blockade (4)",
                       "16. Occupation of territory (4)","17. Seizure (4)","18. Clash (4)",
                       "19. Raid (4)","20. Declaration of war (4)",
                       "22. Begin interstate war (5)","23. Join interstate war (5)",
                       "24. Use CBR Weapons (5)")
) %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )

mid_df2 <- data.frame(
  stringsAsFactors = FALSE,
                outcome = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                outcome_label = c("0. Ongoing MID",
                       "1. Victory for State A","2. Victory for state B",
                       "3. Yield by State A","4. Yield by State B","5. Stalemate",
                       "6. Compromise","7. Released (for seizures)","8. Unclear",
                       "-9 Missing")
) %>% mutate(outcome_label= outcome_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )

dyadic_mid <- read_csv(paste0(here::here(), "/data_other_datasets/mids/Dyadic MIDs 4.02/dyadic_mid_4.02.csv"))

dyadic_mid_clean <- dyadic_mid %>% distinct() %>%
                      left_join(actor_translator %>% dplyr::select(statea=COWcode, actor_1=QCode_name, actor_1_qcode=QCode)) %>%
                      left_join(actor_translator %>% dplyr::select(stateb=COWcode, actor_2=QCode_name, actor_2_qcode=QCode)) %>%
                      left_join(mid_df  %>% dplyr::select( mid5hiacta=act , leaf_1=act_label )) %>%
                      left_join(mid_df  %>% dplyr::select( mid5hiactb=act , leaf_2=act_label )) %>%
                      left_join(mid_df2  %>% dplyr::select( outcome=outcome , outcome_label=outcome_label ))

```

##  Mids plots

```{r}

mids_metro_plots <- function(crisis=196, prune_rare=T){

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/paper/figures/metro_plots/p_mids_metro_plot_",crisis,".Rds")

  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm

  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple

  actor_sent_counts <- 
    bind_rows(
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
      ) %>% 
        na.omit() %>%
        mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

  dyadic_mid_clean_subset <- dyadic_mid_clean %>%
                             filter( actor_1_qcode %in% actor_sent_counts$actor & actor_2_qcode %in% actor_sent_counts$actor ) %>%
                             filter(strtyr>=year_start & endyear<=year_end) 
  dim(dyadic_mid_clean_subset) #
  if(nrow(dyadic_mid_clean_subset)==0 | 
     (c(dyadic_mid_clean_subset$namea,dyadic_mid_clean_subset$nameb) %>% na.omit() %>% unique() %>%  length())<2  #Reject if not 2 actors
     ){
    print("No mids events for this crisis")
    return()
  }

  dyadic_mid_clean_dyad <- 
    bind_rows(
      dyadic_mid_clean_subset %>% dplyr::select(year=strtyr,month=strtmnth,day=strtday, actor_1,actor_2, leaf=leaf_1) , #
      dyadic_mid_clean_subset %>% dplyr::select(year=endyear,month=endmnth,day=endday, actor_1,actor_2, leaf=outcome_label)
  ) %>% mutate(leaf=ifelse(leaf=="Yield by State A" , "Yield to",leaf)) %>%
    filter(!leaf %in% "Yield by State B") %>%
    mutate(sent= ( year+(month/12)+(day/31/1000) ) %>% rank() %>% round())

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  codings_wide_agreed_subset_diad <- dyadic_mid_clean_dyad %>% dplyr::select(year, month, sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
  #Order actors by how many interactions they have together
  temp <- codings_wide_agreed_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  temp_list <- list()
  for(i in 1:nrow(temp2_wide)){
    temp_list[[as.character(i)]] <- cutree(hc, k=i)
  }

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                    mutate(x=max(x)+50) %>%
                    dplyr::select(sent, year, month,x,y) %>%
                    na.omit() %>% 
                    distinct() %>%  
                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                    mutate(year_float=year+(month/12)) %>%
                    group_by(sent) %>%
                    filter(year_float==min(year_float)) %>%
                    ungroup() %>% as.data.frame() %>%
                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                    filter(!duplicated(year_float ) ) %>%
                    mutate(label=paste0(year,"-",month.abb[month]))

  ####Actor lavels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
    #rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)

  ######Directed
  codings_wide_agreed_subset_directed <- 
            dyadic_mid_clean_dyad %>% 
            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1)

    p_mids_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T #& bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  p_mids_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
  p_mids_metro_map$actor_colors <- actor_colors
  p_mids_metro_map$dyadic_mid_clean <- dyadic_mid_clean

  p_mids_metro_map %>% saveRDS(save_mids_file)
}

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) mids_metro_plots(x))

```

# MIDs Incidents

## Load data

```{r}

mid_df <- data.frame(
  stringsAsFactors = FALSE,
               act = c(1L,2L,3L,4L,5L,6L,7L,8L,
                       9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
                       20L,21L,22L),
         act_label = c("1. None (1)",
                       "2. Threat to use force (2)","3. Threat to blockade (2)",
                       "4. Threat to occupy terr. (2)","5. Threat to declare war (2)",
                       "6. Threat to join war (2)","7. Show of troops (3)",
                       "8. Show of ships (3)","9. Show of planes (3)","10. Alert (3)",
                       "12. Mobilization (3)","13. Fortify border (3)",
                       "14. Border violation (4)","15. Blockade (4)",
                       "16. Occupation of territory (4)","17. Seizure (4)","18. Clash (4)",
                       "19. Raid (4)","20. Declaration of war (4)",
                       "22. Begin interstate war (5)","23. Join interstate war (5)",
                       "24. Use CBR Weapons (5)") 
) %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') %>% trimws() )

mid_df2 <- data.frame(
  stringsAsFactors = FALSE,
                outcome = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                outcome_label = c("0. Ongoing MID",
                       "1. Victory for State A","2. Victory for state B",
                       "3. Yield by State A","4. Yield by State B","5. Stalemate",
                       "6. Compromise","7. Released (for seizures)","8. Unclear",
                       "-9 Missing")
) %>% mutate(outcome_label= outcome_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )

mid_df3 <- data.frame(
  stringsAsFactors = FALSE,
          revtype1 = c(0L, 1L, 2L, 3L, 4L),
    revtype1_label = c("Not applicable","Territory",
                       "Policy","Regime/government","Other")
)

mid_df4 <- data.frame(
  stringsAsFactors = FALSE,
          fatality = c(0L, 1L, 2L, 3L, 4L, 5L, 6L),
    fatality_label = c("None","1-25 deaths",
                       "26-100 deaths","101-250 deaths","251-500 deaths",
                       "501-999 deaths","> 999 deaths")
)

midip <- read_csv(paste0(here::here(), '/data_other_datasets/mids_incidents/MIDIP_5.01.csv'))

midii <- read_csv(paste0(here::here(), '/data_other_datasets/mids_incidents/MIDI_5.01.csv'))

midip_clean <- midip %>% distinct() %>%
                      left_join(actor_translator %>% dplyr::select(ccode=COWcode, actor=QCode_name, actor_qcode=QCode)) %>%
                      left_join(mid_df  %>% dplyr::select( action=act , act_label=act_label )) %>%
                      left_join(mid_df3  %>% dplyr::select( revtype1=revtype1 , revtype1_label=revtype1_label ))  %>%
                      left_join(mid_df4  %>% dplyr::select( fatality=fatality , fatality_label=fatality_label ))

#Create a dyadic list
temp1 <- midip_clean %>% 
         mutate(start=styear+((stmon*30)+stday)/365) %>%
         mutate(end=endyear+((endmon*30)+endday)/365) %>%
         dplyr::select(stday, stmon, styear, endday, start, end, incidnum, sidea, actor, actor_qcode,
                       act_label,revtype1_label,fatality_label) %>% arrange(incidnum, sidea, actor_qcode) %>% distinct()
temp2 <- temp1 %>% dplyr::select(stday, stmon, styear, endday, 
                                 start, end,incidnum, sidea_1=sidea, actor_1=actor, actor_1_qcode=actor_qcode,act_1_label=act_label,
                                 revtype1_1_label=revtype1_label,fatality_1_label=fatality_label) %>%
          full_join(temp1 %>% dplyr::select(start, end,incidnum, sidea_2=sidea, actor_2=actor, actor_2_qcode=actor_qcode,act_2_label=act_label,revtype1_2_label=revtype1_label,fatality_2_label=fatality_label
                                            )) %>%
          filter(sidea_1!=sidea_2) %>%
          mutate(actor_12_qcode=paste0(actor_1_qcode, "_", actor_2_qcode))
temp3 <- temp1 %>% dplyr::select(start, end,incidnum, sidea_1=sidea, actor_1=actor, actor_1_qcode=actor_qcode,
                                 act_1_label=act_label,revtype1_1_label=revtype1_label,fatality_1_label=fatality_label) %>%
          full_join(temp1 %>% dplyr::select(start, end,incidnum, sidea_2=sidea, actor_2=actor, actor_2_qcode=actor_qcode,act_2_label=act_label,revtype1_2_label=revtype1_label,fatality_2_label=fatality_label)) %>%
          filter(sidea_1!=sidea_2) %>%
          mutate(actor_12_qcode=paste0(actor_2_qcode, "_", actor_1_qcode))

midip_dyads <- bind_rows(temp2, temp3)

```

## Plot

```{r}

mids_incidents_metro_plots <- function(crisis=196, prune_rare=T){

  print(crisis)
  #crisis=426
  save_mids_incidents_file <- paste0(here::here(), "/paper/figures/metro_plots/p_mids_incidents_metro_plot_",crisis,".Rds")

  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm

  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple

  dyad_sent_counts <- 
    bind_rows(
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor_1_qcode=say_actor_a, actor_2_qcode=say_actor_b),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor_1_qcode=do_actor_a, actor_2_qcode=do_actor_b)
   )   %>% distinct() %>% na.omit()  %>% 
        mutate(actor_1_qcode = strsplit(as.character(actor_1_qcode), ";")) %>% unnest(actor_1_qcode) %>% distinct() %>%
        mutate(actor_2_qcode = strsplit(as.character(actor_2_qcode), ";")) %>% unnest(actor_2_qcode) %>% distinct() %>% 
        count(actor_1_qcode , actor_2_qcode) %>% arrange(desc(n))  %>%
          mutate(actor_12_qcode=paste0(actor_1_qcode, "_", actor_2_qcode))

  #What mids involve those dyads?
  relevant_incidnum <- midip_dyads %>% filter(actor_12_qcode %in% dyad_sent_counts$actor_12_qcode) %>% pull(incidnum) %>% unique()

  actor_sent_counts <- 
    bind_rows(
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
      ) %>% 
        na.omit() %>%
        mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

  #Subset incients to be within the time frame and the right incidents and the right actors
  incident_mid_clean_subset <- midip_dyads %>%
                               filter( incidnum %in% relevant_incidnum ) %>% #a dispute with a relvant dyad
                               filter( actor_12_qcode %in% dyad_sent_counts$actor_12_qcode ) %>% #an actor in our data
                               filter(start>=year_start & end<=year_end+1) #allow for an extra year at the end

  #Reject if no rows or less than 2 actors
  dim(incident_mid_clean_subset) #
  if(nrow(incident_mid_clean_subset)==0 | 
     (c(incident_mid_clean_subset$actor_1,incident_mid_clean_subset$actor_2) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
     ){
    print("No mids events for this crisis")
    return()
  }

  #we can do pseudo dyads within incidum numbers

  dyadic_mid_clean_dyad <- 
    bind_rows(
      incident_mid_clean_subset %>% 
        mutate(label=
                 paste0( act_1_label %>% replace_na(''),", ", revtype1_2_label %>% replace_na('') ,", ", fatality_1_label %>% replace_na('')) %>% trimws() %>%
                 str_replace_all("None|Not applicable","") %>% trimws() %>% str_replace("^,|,$|","") %>% trimws()
               ) %>%
        dplyr::select(stday, stmon, styear, endday, start,   end, start, actor_1=actor_1,actor_2=actor_2, leaf=label) 
  ) %>%
    mutate(sent= start %>% rank() %>% round())

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  codings_wide_agreed_subset_diad <- dyadic_mid_clean_dyad %>% dplyr::select(styear, stmon, sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
  #Order actors by how many interactions they have together
  temp <- codings_wide_agreed_subset_diad  %>% dplyr::select(-styear, -stmon) %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(styear, stmon, sent=sent, actor=actor_1) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(styear, stmon, sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                    mutate(x=max(x)+50) %>%
                    dplyr::select(sent, point_in_time_year=styear, point_in_time_month=stmon,x,y) %>%
                    na.omit() %>% 
                    distinct() %>%  
                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                    mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                    group_by(sent) %>%
                    filter(year_float==min(year_float)) %>%
                    ungroup() %>% as.data.frame() %>%
                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                    filter(!duplicated(year_float ) ) %>%
                    mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

  ####Actor levels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
    #rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)

  ######Directed
  codings_wide_agreed_subset_directed <- 
            dyadic_mid_clean_dyad %>% 
            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1)

    p_mids_incident_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T #& bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45

              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  p_mids_incident_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
  p_mids_incident_metro_map$actor_colors <- actor_colors
  p_mids_incident_metro_map$incident_mid_clean_subset <- incident_mid_clean_subset

  p_mids_incident_metro_map %>% saveRDS(save_mids_incidents_file)
}

icb_crises %>% filter(yrtrig>=1990) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) mids_incidents_metro_plots(x))

```

# ICB

## Data Loads

```{r}

#Note yemen 679 doesn't show up in this data
icb_df <- data.frame(
  stringsAsFactors = FALSE,
          icb_name = c("Afghanistan","Albania",
                       "Algeria","Andorra","Angola","Antigua & Barbuda",
                       "Argentina","Armenia","Australia","Austria","Azerbaijan",
                       "Bahamas","Bahrain","Bangladesh","Barbados","Belarus",
                       "Belgium","Belize","Benin (Dahomey)","Bhutan","Bolivia",
                       "Bosnia","Botswana","Brazil","Brunei","Bulgaria",
                       "Burkina Faso (Upper Volta)","Burma (see Myanmar)",
                       "Burundi","Cambodia","Cameroon","Canada","Cape Verde",
                       "Central African Republic","Chad","Chile","China",
                       "China","Colombia","Comoros","Congo Brazzaville",
                       "Congo, Democratic","Costa Rica","Cote D’Ivoire","Croatia",
                       "Cuba","Cyprus","Czech Republic","Czechoslovakia",
                       "Dahomey (see Benin)","Denmark","Djibouti (Somalia Fr.)",
                       "Dominica","Dominican Republic","Ecuador","Egypt (UAR)",
                       "El Salvador","Equatorial Guinea","Eritrea","Estonia",
                       "Ethiopia","Federated States of Micronesia","Fiji",
                       "Finland","Formosa","France","French West Africa",
                       "Gabon","Gambia","Georgia",
                       "German Democratic Republic (East Germany)",
                       "Germany (German Federal Republic, West Germany)","Germany (Prussia)","Ghana",
                       "Great Britain (see United Kingdom)","Greece","Grenada","Guatemala",
                       "Guinea","Guinea Bissau","Guyana","Haiti","Hijaz (Hejaz)",
                       "Honduras","Hungary","Iceland","India","Indonesia",
                       "Iran","Iraq","Ireland (Eire)","Israel","Italy",
                       "Ivory Coast (see Cote D’Ivoire)","Jamaica","Japan",
                       "Jordan","Kazakhstan","Kenya","Korea","Kosovo","Kuwait",
                       "Kyrgyz Republic","Laos","Latvia","Lebanon","Lesotho",
                       "Liberia","Libya","Liechtenstein","Lithuania",
                       "Luxemberg","Macedonia","Madagascar (Malagasy Republic)",
                       "Malawi","Malaysia","Maldives","Mali","Malta",
                       "Marshall Islands","Mauritania","Mauritius","Mexico","Moldova",
                       "Monaco","Mongolia","Morocco","Mozambique",
                       "Myanmar (Burma)","Najd (Nejd)","Namibia (South West Africa)",
                       "Nepal","Netherlands","Nevis","New Zealand",
                       "Nicaragua","Niger","Nigeria",
                       "North Korea (People’s Republic of Korea)","Norway","Oman","Pakistan","Palau","Panama",
                       "Papua and New Guinea","Paraguay","Peru",
                       "Philippines","Poland","Portugal","Principe","Qatar",
                       "Republic of (Congo Kinshasa) (Zaire)","Rhodesia (see Zimbabwe)",
                       "Rumania","Russia (Soviet Union)","Rwanda",
                       "San Marino","Sao Tome","Saudi Arabia","Senegal",
                       "Serbia (see Yugoslavia)","Seychelles","Sierra Leone","Singapore",
                       "Slovakia","Slovenia","Solomons","Somalia",
                       "Somalia Fr. (see Djibouti)","South Africa",
                       "South Korea (Republic of Korea)","South Sudan",
                       "South West Africa (see Namibia)","Spain","Spanish Sahara (see Western Sahara)",
                       "Sri Lanka (Ceylon)","St. Kitts","St. Lucia",
                       "St. Vincent & The Grenadines","Sudan","Surinam","Swaziland",
                       "Sweden","Switzerland","Syria","Taiwan (China",
                       "Tajikistan","Tanzania","Thailand","Tibet","Togo",
                       "Trinidad & Tobago","Tunisia","Turkey","Turkmenistan","Uganda",
                       "Ukraine","United Arab Emirates",
                       "United Kingdom (Great Britain)","Upper Volta (see Burkina Faso)","Uruguay",
                       "USA","USSR (see Russia)","Uzbekistan","Vanuatu",
                       "Venezuela","Vichy France",
                       "Vietnam, Democratic Republic of (North Vietnam)","Vietnam, Republic of (South Vietnam)",
                       "Western Sahara (Spanish Sahara)","Western Samoa",
                       "Yemen (Arab Republic of Yemen, North Yemen)",
                       "Yemen, People’s Republic of (South Yemen)","Yugoslavia (Serbia)",
                       "Zambia","Zanzibar","Zimbabwe (Rhodesia)"),
       icb_letters = c("AFG","ALB","ALG","AND",
                       "ANG","AAB","ARG","ARM","AUL","AUS","AZE","BHM",
                       "BAH","BNG","BAR","BLR","BEL","BLZ","BEN","BHU","BOL",
                       "BOS","BOT","BRA","BRU","BUL","BFO",NA,"BUI",
                       "CAM","CAO","CAN","CAP","CEN","CHA","CHL",NA,"CHN",
                       "COL","COM","CON","DRC","COS","CDI","CRO","CUB",
                       "CYP","CZR","CZE",NA,"DEN","DJI","DMA","DOM",
                       "ECU","EGY","SAL","EQG","ERI","EST","ETH","FSM","FIJ",
                       "FIN","TAW","FRN","FWA","GAB","GAM","GRG","GDR",
                       "GFR","GMY","GHA",NA,"GRC","GRN","GUA","GUI",
                       "GNB","GUY","HAI","HIJ","HON","HUN","ICE","IND",
                       "INS","IRN","IRQ","IRE","ISR","ITA",NA,"JAM","JPN",
                       "JOR","KZK","KEN","KOR","KOS","KUW","KYR","LAO",
                       "LAT","LEB","LES","LBR","LIB","LIE","LIT","LUX",
                       "MAC","MAG","MAW","MAL","MAD","MLI","MLT","MSI",
                       "MAA","MAS","MEX","MLD","MNC","MON","MOR","MZM","MYA",
                       "NAJ","NAM","NEP","NTH","SKN","NEW","NIC","NIR",
                       "NIG","PRK","NOR","OMA","PAK","PAL","PAN","PNG",
                       "PAR","PER","PHI","POL","POR","STP","QAT","DRC",
                       NA,"RUM","RUS","RWA","SNM",NA,"SAU","SEN",NA,
                       "SEY","SIE","SIN","SLO","SLV","SOL","SOM",NA,"SAF",
                       "ROK","SSD",NA,"SPN",NA,"SRI",NA,"SLU","SVG",
                       "SUD","SUR","SWA","SWD","SWZ","SYR",NA,"TAJ","TAZ",
                       "THI","TBT","TOG","TRI","TUN","TUR","TKM","UGA",
                       "UKR","UAE","UKG",NA,"URU","USA",NA,"UZB","VAN",
                       "VEN","VFR","DRV","RVN","SPA","WSM","YEM","YPR",
                       "YUG","ZAM","ZAN","ZIM"),
          icb_code = c("700","339","615","232",
                       "540","058","160","371","900","305","373","031",
                       "692","771","053","370","211","080","434","760","145",
                       "346","571","140","835","355","439",NA,"516",
                       "811","471","020","402","482","483","155",NA,"710",
                       "100","581","484","490","094","437","344","040",
                       "352","316","315",NA,"390","522","054","042",
                       "130","651","092","411","531","366","530","987","950",
                       "375","713","220","480","481","420","372","265",
                       "260","255","452",NA,"350","55","090","438",
                       "404","110","041","671","091","310","395","750","850",
                       "630","645","205","666","325",NA,"051","740",
                       "663","705","501","730","347","690","703","812",
                       "367","660","570","450","620","223","368","212",
                       "343","580","553","820","781","432","338","983","435",
                       "590","070","359","221","712","600","541","775",
                       "672","565","790","210","060","920","093","436",
                       "475","731","385","698","770","986","095","910",
                       "150","135","840","290","235","403","694","490",NA,
                       "360","365","517","331",NA,"670","433",NA,"591",
                       "451","830","317","349","940","520",NA,"560",
                       "732","626",NA,"230",NA,"780",NA,"056","057","625",
                       "115","572","380","225","652",NA,"702","510",
                       "800","711","461","052","616","640","701","500",
                       "369","696","200",NA,"165","002",NA,"704","935",
                       "101","219","816","817","605","990","678","680",
                       "345","551","511","552")
)

df_IWCA <- data.frame(
  stringsAsFactors = FALSE,
              IWCA = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L, 10L),
        IWCA_label = c("not an intra-war crisis (IWC)",
                       "Entry of a major actor into an ongoing war",
                       "Perceived high probability of a major actor entering a war",
                       "Exit of a major actor",
                       "Perceived high probability of major power exiting a war",
                       "Technological escalation of a war","Major non-technological escalation",
                       "Defeat in a significant battle","Internal deterioration","Other")
)

df_break <- 
data.frame(
  stringsAsFactors = FALSE,
             BREAK = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
       BREAK_label = c("Verbal act","Political act",
                       "Economic act","External change",
                       "Other non-violent act",
                       "Internal verbal or physical challenge to regime or elite","Non-violent military act","Indirect violent act",
                       "Violent act")
)

icbdy_20 <- read_tsv(here::here(), "/data_other_datasets/icb_dyad/icbdy_20.dat")

icbdy_20_clean <- icbdy_20 %>%
                  left_join( icb_df %>% dplyr::select(STATEA=icb_code, actor_1=icb_name ) %>% mutate(STATEA=STATEA %>% as.numeric())  ) %>%
                  left_join( icb_df %>% dplyr::select(STATEB=icb_code, actor_2=icb_name ) %>% mutate(STATEB=STATEB %>% as.numeric())  ) %>%
                  left_join(df_IWCA %>% dplyr::select(IWCA=IWCA, IWCA_label=IWCA_label )  ) %>%
                  left_join(df_IWCA %>% dplyr::select(IWCB=IWCA, IWCB_label=IWCA_label )  )

icb_diadic <- icbdy_20_clean %>% dplyr::select(CRISNO, NAMEA, NAMEB,  STATEA, STATEB, actor_1,actor_2, IWCA_label,IWCB_label) #%>% filter(is.na(actor_1) | is.na(actor_2))

icb2v14 <- read_csv(here::here(), "/data_other_datasets/icb/icb2v14.csv")

df_trigger <- data.frame(
  stringsAsFactors = FALSE,
            triggr = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                    triggr_label = c("Verbal act","Political act","Economic act",
                                     "External change","Other non-violent act",
                                     "Internal verbal or physical challenge to regime or elite",
                                     "Non-violent military act","Indirect violent act","Violent act")
              )

df_majres <- data.frame(
  stringsAsFactors = FALSE,
            majres = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                   majres_label = c("No response-inaction","Verbal act",
                                    "Political act","Economic act",
                                    "Other non-violent act",
                                    "Non-violent military act",
                                    "Multiple including non-violent military act",
                                    "Violent military act",
                                    "Multiple including violent military act")
             )

df_outcome <- 
data.frame(
  stringsAsFactors = FALSE,
            outcom = c(1L, 2L, 3L, 4L, 5L),
      outcom_label = c("Victory", "Compromise", "Stalemate", "Defeat", "Other")
)

df_outfor <- 
data.frame(
  stringsAsFactors = FALSE,
            outfor = c(1L,2L,3L,4L,5L,6L,7L,8L,
                       9L,10L,11L,12L,13L,14L,15L),
      outfor_label = c("Formal agreement - voluntary",
                       "Semi-formal agreement - voluntary",
                       "Tacit understanding","Unilateral - self","Unilateral - ally",
                       "Unilateral - adversary","Compliance","Imposed - imposer",
                       "Imposed - imposee","Spillover",
                       "Other - global organization intervention","Other - ally",
                       "Other - internal or non-state actor","Other - misc.","Faded")
)

icb2v14_clean <- icb2v14 %>% 
                 left_join(icb_df %>% dplyr::select(cracid=icb_code, actor_label=icb_name ) %>% mutate(cracid=cracid %>% as.numeric()) ) %>%  #you can't actually match on the letter codes you have to match on the numbers, uhhhhhg
                 left_join( df_trigger  ) %>% 
                 left_join( df_majres ) %>% 
                 left_join( df_outcome ) %>% 
                 left_join( df_outfor )

icb_monadic <-  
  bind_rows(
   icb2v14_clean%>% mutate(sent= yrtrig + tidyr::replace_na((motrig/12),0) + tidyr::replace_na(datrig/31/12,0) ) %>% mutate(type='start') %>% dplyr::select(year=yrtrig, month=motrig, crisno,type, sent, actor_label, leaf=triggr_label),
   icb2v14_clean %>% mutate(sent= yerres + tidyr::replace_na((monres/12),0) + tidyr::replace_na(dayres/31/12,0) ) %>% mutate(type='mid') %>% dplyr::select(year=yerres, month=monres, crisno,type, sent, actor_label, leaf=majres_label),
   icb2v14_clean %>% mutate(sent= yrterm + tidyr::replace_na((moterm/12),0) + tidyr::replace_na(daterm/31/12,0) ) %>% mutate(type='end') %>% dplyr::select(year=yrterm, month=moterm, crisno,type, sent, actor_label, leaf=outfor_label)
  ) %>% as.data.frame()

```

## ICB Function

```{r}

icb_metro_plots <- function(crisis=196, prune_rare=T){

    print(crisis)
    save_icb_file <- paste0(here::here(), "/paper/figures/metro_plots/p_icb_metro_plot_",crisis,".Rds")

    icb_diadic_subset <- icb_diadic %>% filter(CRISNO==crisis) #Not all of them are diadic apparently
    icb_monadic_subset <- icb_monadic %>% rename(actor=actor_label) %>% filter(crisno==crisis) %>%
                       mutate(sent=sent %>% rank() %>% round()) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") ))   %>% arrange(sent, actor)

    g <- make_empty_graph(n = 0, directed = TRUE)
      #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

    codings_wide_agreed_subset_diad <- bind_rows(
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>% 
                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>% rename(actor_2=actor_1,actor_1=actor_2),
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>%
                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),

            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>%
                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>% rename(actor_2=actor_1,actor_1=actor_2),
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>% 
                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),

            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>% rename(actor_2=actor_1,actor_1=actor_2),
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),

          ) %>% dplyr::select(year, month,sent, actor_1, actor_2, leaf) %>% distinct() %>% na.omit()

     if(nrow(codings_wide_agreed_subset_diad)==0){
      print("No dyadic icb rows skipping")
      return()
    }

    #Order actors by how many interactions they have together
    temp <- codings_wide_agreed_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()

    temp2 <- bind_rows(
      temp,
      temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
    ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

    temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
    rownames(temp2_wide) <- temp2_wide$actor_1
    temp2_wide$actor_1 <- NULL
    temp2_wide <- temp2_wide %>% as.matrix()
    temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
    temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
    hc <- hclust(temp2_wide %>% as.dist(), method="single")

    temp_list <- list()
    for(i in 1:nrow(temp2_wide)){
      temp_list[[as.character(i)]] <- cutree(hc, k=i)
    }

    #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
    #  arrange(across(starts_with("V")))
    ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

    #####Nodes
    codings_wide_agreed_subset_nodes <- 
              bind_rows(
                        codings_wide_agreed_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_1) ,
                        codings_wide_agreed_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_2) 
              ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
              mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                     y=sent*-1 *100)

    actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
    actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
    names(actor_colors) = levels(actors)

    date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                        mutate(x=max(x)+50) %>%
                        dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
                        na.omit() %>% 
                        distinct() %>%  
                        mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                        mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                        group_by(sent) %>%
                        filter(year_float==min(year_float)) %>%
                        ungroup() %>% as.data.frame() %>%
                        filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                        filter(!duplicated(year_float ) ) %>%
                        mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

    ####Actor levels
    codings_wide_agreed_subset_nodes_min <- 
                  codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
                  #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
                  #rename(qcode=actor, actor=value_normalized_label) %>%
                  rowwise() %>%
                  mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

    for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
      g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                  actor = codings_wide_agreed_subset_nodes$actor[i], 
                                  sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
    }

    xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

    #####Time Edges
    codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

    g <- g %>% 
         add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                   actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)

    ######Directed
    codings_wide_agreed_subset_directed <- 
              codings_wide_agreed_subset_diad %>% 
              dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
              mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
                summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
              #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

    g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                         timeedge=F, 
                         leaf=codings_wide_agreed_subset_directed$leaf, 
                         eventedge=T,
                         actor=codings_wide_agreed_subset_directed$actor_1)

    p_icb_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T #& bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

      p_icb_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
      p_icb_metro_map$actor_colors <- actor_colors
      p_icb_metro_map$icb_monadic_subset <- icb_monadic_subset

      p_icb_metro_map %>% saveRDS(save_icb_file)

}

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icb_metro_plots(x))

```

# GED

## Data Loads

```{r}

df1 <- data.frame(
        stringsAsFactors = FALSE,
        type_of_violence = c(1L, 2L, 3L),
                               type_of_violence_label = c("state-based conflict","non-state conflict","one-sided violence")
)

ged211 <- read_csv(here::here(), "/data_other_datasets/ucdp_ged/ged211.csv")

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

ged211_clean <- ged211 %>%
                left_join(actor_translator %>% dplyr::select(side_a_new_id=UCDPcode,actor_1=QCode_name, actor_1_qcode=QCode) ) %>%
                left_join(actor_translator %>% dplyr::select(side_b_new_id=UCDPcode,actor_2=QCode_name, actor_2_qcode=QCode) ) %>%
                filter(!is.na(actor_1_qcode) & !is.na(actor_2_qcode)) %>%
                mutate(actor_12_qcode=paste0(actor_1_qcode,"_",actor_2_qcode)) %>%
                dplyr::select(-source_office, -source_date, -source_headline, -source_original)

#There's only 11 that overlap
#Q1009_Q1033   Q148_Q668   Q424_Q869   Q668_Q843   Q736_Q419   Q794_Q801   Q796_Q817    Q804_Q30  Q958_Q1049   Q977_Q986   Q986_Q115 
#          9           2          24        1049          26          67          80           2          27           2          34

```

## Ged Plots

```{r}

ucdp_ged_metro_plots <- function(crisis=466, prune_rare=T){

    print(crisis)
    #crisis=426
    save_ucdp_incidents_file <- paste0(here::here(), "/paper/figures/metro_plots/p_ucdp_metro_plot_",crisis,".Rds")

    year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
    year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm

    start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
    end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple

    dyad_sent_counts <- 
      bind_rows(
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor_1_qcode=say_actor_a, actor_2_qcode=say_actor_b),
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor_1_qcode=do_actor_a, actor_2_qcode=do_actor_b)
     )   %>% distinct() %>% na.omit()  %>% 
          mutate(actor_1_qcode = strsplit(as.character(actor_1_qcode), ";")) %>% unnest(actor_1_qcode) %>% distinct() %>%
          mutate(actor_2_qcode = strsplit(as.character(actor_2_qcode), ";")) %>% unnest(actor_2_qcode) %>% distinct() %>% 
          count(actor_1_qcode , actor_2_qcode) %>% arrange(desc(n))  %>%
            mutate(actor_12_qcode=paste0(actor_1_qcode, "_", actor_2_qcode))

    actor_sent_counts <- 
      bind_rows(
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a),
          codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
        ) %>% 
          na.omit() %>%
          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

    #Subset incients to be within the time frame and the right incidents and the right actors
    incident_ucdp_clean_subset <- ged211_clean %>%
                                   filter( actor_12_qcode %in% dyad_sent_counts$actor_12_qcode ) %>% #an actor in our data
                                   filter(year>=year_start & year<=year_end) #allow for an extra year at the end

  #Reject if no rows or less than 2 actors
  dim(incident_ucdp_clean_subset) #
  if(nrow(incident_ucdp_clean_subset)==0 | 
     (c(incident_ucdp_clean_subset$actor_1,incident_ucdp_clean_subset$actor_2) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
     ){
    print("No mids events for this crisis")
    return()
  }

  #we can do pseudo dyads within incidum numbers
  dyadic_ucdp_clean_dyad <- 
    bind_rows(

      #A killed B
      incident_ucdp_clean_subset %>% 
        filter(gwnob==country_id) %>% #happened in B
        mutate(label= paste0( best, " deaths"  ) %>% trimws()  ) %>% dplyr::select(date_start, actor_1=actor_1,actor_2=actor_2, leaf=label),
      #B killed A
      incident_ucdp_clean_subset %>% 
        filter(gwnoa==country_id) %>% #happened in A
        mutate(label= paste0( best, " deaths"  ) %>% trimws()  ) %>% dplyr::select(date_start, actor_1=actor_2,actor_2=actor_1, leaf=label)

  ) %>% distinct() %>%
    mutate(sent= date_start %>% rank() %>% round())

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  codings_wide_agreed_subset_diad <- dyadic_ucdp_clean_dyad %>% dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
  #Order actors by how many interactions they have together
  temp <- codings_wide_agreed_subset_diad  %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent=sent, actor=actor_1) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  ####Actor levels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
    #rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)

  ######Directed
  codings_wide_agreed_subset_directed <- 
            dyadic_ucdp_clean_dyad %>% 
            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1)

    p_ucdp_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T #& bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  p_ucdp_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
  p_ucdp_metro_map$actor_colors <- actor_colors
  p_ucdp_metro_map$incident_ucdp_clean_subset <- incident_ucdp_clean_subset

  p_ucdp_metro_map %>% saveRDS(save_ucdp_incidents_file)
}

icb_crises %>% filter(yrtrig>=1989) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) ucdp_ged_metro_plots(x))

```

# Cameo Systems

```{r}

CAMEO_eventcodes <- read_tsv(here::here(), "/data_other_datasets/icews/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()

cameo_code_rejects <- c('Make statement, not specified below', 'Consult, not specified below','Praise or endorse','Accuse, not specified below',
                        'Make statement, not specified below','Meet at a third location','Consult, not specified below')

#Comment to not reject
role_rejects <- c(
  "Agriculture-focused actors",
  "Business (NOT MNCs)",
  "Civilians",
  "Criminal actors",
  "Development-focused actors" ,
  "Education-focused actors",
  "Elites, celebrities",
  "Environment-focused actors",
  #"Government",
  "Health-focused actors",
  "Human rights-focused actors",
  #"Intelligence agencies",
  "Judicial actors",
  "Labor-focused actors",
  "Law enforcement agencies",
  "Legislative bodies/actors",
  "Media-related actors/organizations",
  #"Military",
  #"Opposition groups (often parliamentary)" ,
  #"Political party",
  #"Radical/extremist/fundamentalist",
  #"Rebels/insurgents",
  "Refugee-focused actors" #,
  #"Unaffiliated armed forces"  
)

cameo_role_codes <- data.frame(
       stringsAsFactors = FALSE,
                   role_code = c("GOV","SPY","OPP",
                            "MIL","PTY","REB","EDU","COP","JUD","CRM",
                            "BUS","MED","CVL","UAF","AGR","ELI","DEV","ENV",
                            "HLH","HRI","LAB","LEG","REF","MOD","RAD"),
  role_code_label = c("Government",
                            "Intelligence agencies",
                            "Opposition groups (often parliamentary)",
                            "Military",
                            "Political party",
                            "Rebels/insurgents",
                            "Education-focused actors",
                            "Law enforcement agencies",
                            "Judicial actors",
                            "Criminal actors",
                            "Business (NOT MNCs)",
                            "Media-related actors/organizations",
                            "Civilians",
                            "Unaffiliated armed forces",
                            "Agriculture-focused actors",
                            "Elites, celebrities",
                            "Development-focused actors",
                            "Environment-focused actors",
                            "Health-focused actors",
                            "Human rights-focused actors",
                            "Labor-focused actors",
                            "Legislative bodies/actors",
                            "Refugee-focused actors",
                            "Moderate/mainstream group",
                            "Radical/extremist/fundamentalist")
) %>% janitor::clean_names()

  subject_rejects <- c(
  "ACTIVISM,1" , "ACTIVISM,2" , "AGRICULTURE,1" , "AGRICULTURE,2" , "AGRICULTURE,3" , "AGRICULTURE,4" , 
  "BAILOUT,1" , "BANKRUPTCY,1" , 
   "BLACK_MARKET,1" , "CHECKPOINT,1" , 
   "CIVIL_SOCIETY,1" , "CLIMATE_CHANGE,1" , "COAL,1" , "COAL,2" , "COAL,3" , "COMMON_ROBBERY,1" , "CORRUPTION,1" , "CORRUPTION,2"     , 
    "DISCRIMINATION,1" , "DISEASE,1" , "DISEASE,2" , "DISEASE,3" , "DISEASE,4" , 
    "DRUG_CARTELS,1" , "DRUG_TRADE,1" , "DRUGS,1" , "DRUGS,2" , "DRUGS,3" , 
    "EXCHANGE_RATE,1" , "FOOD_SECURITY,1" , 
       "HOUSING_PRICES,1" , 
          "ELECTRICITY_OUTAGE,1" , 
          "INT_FINANCIAL_INST,1" , "INT_FINANCIAL_INST,2" , "INTEREST_RATES,1" , "INTEREST_RATES,2" , "LABOR_STRIKE,1" , 
   "LABOR_UNIONS,1" , "LABOR_UNIONS,2" , "LABOR_UNIONS,4" , "LANDMINE,1" , "LGBT,1" , "LITERACY,1" , "MEDIA_CENSORSHIP,1" , "MONOPOLY,1" , 
   "MONOPOLY,2" , 
    "ORGANIZED_CRIME,1" , 
    "POSTSECONDARY_EDUCATION,1" , "POSTSECONDARY_EDUCATION,2" , "POSTSECONDARY_EDUCATION,3" , "POVERTY,1" , "PRIVATIZATION,1" , "PRIVATIZATION,2" , 
   "PUBLIC_TRANSIT,1" , "PUBLIC_TRANSIT,2" , "PUBLIC_TRANSIT,3" , "RAPE,1" , "REFUGEES,1" , "REFUGEES,2" , "REFUGEES,3" , "RENEWABLE_ENERGY,1" , 
   "SCHOOLS,1" , "SCHOOLS,2" , "SCHOOLS,3" , 
   "SEXTRANS_DISEASE,1" , "SHORTAGE,1" , "SOCIAL_MOVEMENT,1" , "STUDENTS,1" , "STUDENTS,2" , "STUDENTS,3" , "SUBSIDIES,1" , 
   "TEACHERS,1" , "TEACHERS,2" , 
    "UNEMPLOYMENT,1" , "VACCINATION,1" , 
   "VACCINATION,2" , "YOUTH_MOVEMENT,1" 
  )

  # "AIRSTRIKE,1"                 "AIRSTRIKE,2"                
  # "ASSASSINATION,1"                      "BIOLOGICAL_WEAPONS,1"                  "CHEMICAL_WEAPONS,1"          "CHEMICAL_WEAPONS,2"         
  # "COUP_DISCUSSION,1"           "CYBER_SECURITY,1"               "DRONE,1"                    
  # "EARLY_CHILDHOOD_EDUCATION,1" "ECONOMIC_MOVEMENT,1"         "ELECTION,1"                 
  # "ELECTION,2"                    "EUROPEAN_UNION,1"            "EUROPEAN_UNION,2"              "FOREIGN_AID,1"                    
  # "HUMAN_RIGHTS,1"              "HUMAN_RIGHTS,2"              "HUMAN_RIGHTS,3"              "ID_ARMS_DEAL,1"              "ID_ATROCITY,1"               "ID_ATROCITY,2"               "ID_DEMOCRACY,1"              "ID_DEMOCRACY,2"            
  # "ID_EXTREMISM,1"              "ID_EXTREMISM,2"              "ID_IMMIGRATION,1"            "ID_IMMIGRATION,2"            "ID_JIHAD,1"                  "ID_JIHAD,2"                  "ID_JIHAD,3"                  "ID_PROLIFERATION,1"        
  # "ID_SMUGGLING,1"              "ID_TORTURE,1"                "IED,1"                            "NAMED_TERROR_GROUP,1"        "NAMED_TERROR_GROUP,2"        "NATIONAL_MOVEMENT,1"         "NATURAL_DISASTER,1"          "NATURAL_DISASTER,2"   # "NATURAL_GAS,1"               "NEW_CONSTRUCTION,1"         
  # "NUCLEAR_ENERGY,1"            "NUCLEAR_ENERGY,2"            "NUCLEAR_WEAPONS,1"           "NUCLEAR_WEAPONS,2"           "NUCLEAR_WEAPONS,3"           "OIL,1"                            "PEACEKEEPERS,1"             
  # "POLITICAL_PRISONER,1"        "POLITICAL_PRISONER,2"                 
  # "RETALIATION,1"               "SANCTIONS,1"                 "SANCTIONS,2"                      "SECURITY_SERVICES,1"         "SECURITY_SERVICES,2"        
  # "SUICIDE_ATTACK,1"           
  # "TERROR,1"                    "TERROR,2"                    "TOURISM,1"                   "TOURISM,2"                               "VIOLENT_UNREST,1"            "WATER_SECURITY,1"            "WMD,1"

#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/data_temp/CAMEO.eventcodes.txt")) %>% janitor::clean_names()

```

## ICEWS

### Data Loads

```{r}

kill_sectors <- c(
  'Police,Government',
'Social,Media',
'Government,Judicial',
'Media,Social',
'Judicial,Government',
'Dissident,Criminals / Gangs',
'Criminals / Gangs,Dissident',
'Social,Legal',
'Legal,Social',
'Social,Business',
'Business,Social',
'Social,Education',
'Education,Social',
'Social,Labor',
'Labor,Social',
'Local,Provincial,Government',
'Social,National Religious',
'National Religious,Social',
'Local,Government,Provincial',
'Government,Finance / Economy / Commerce / Trade Ministry,Executive',
'Executive,Interior / Home Ministry,Government',
'Medical / Health NGOs,Nongovernmental Organizations / Activists',
'Government,Interior / Home Ministry,Executive',
'Social,Media,News',
'Social,Agricultural',
'Social,News,Media',
'News,Media,Social',
'Media,News,Social',
'Social,Medical / Health',
'Medical / Health,Social',
'Ideological,Center Left,Executive,Parties,(National) Major Party,Executive Office,Government',
'Social,Refugees / Displaced',
'Agricultural,Social',
'Ideological,Center Left,Parties,(National) Major Party',
'Dissident,Nongovernmental Organization (International),Parties,(National) Major Party',
'Parties,(National) Major Party,Center Left,Ideological',
'Refugees / Displaced,Social',
'Dissident,Exiles',
'Party',
'Parties',
"General Population",
"^Elite$"
)
kill_sectors_regex <- paste0(kill_sectors, collapse="|")

files <- list.files(path = paste0(here::here(), "/data_other_datasets/icews/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
dim(icews)

CAMEO_eventcodes <- read_tsv(paste0(here::here(),"/data_other_datasets/icews/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()

codes_used <-icews %>% count(cameo_code)

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

#Rex start here tomorrow, figure out how to do this join correctly
actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
#%>% mutate(icews=ifelse(ICEWS_Country=="International Government Organizations", ICEWS_Actor.Name, ICEWS_Country))

#Going to heavily filter on source sectors and source name
#c(icews$source_sectors,icews$source_name) %>% table()

#This doesn't totally work because India has 3 copies. The lower thing gets a different q code than the higher thing, so we first have to try to match on the lower, and if that fails match on the higher kinda
#Indian Administered Kashmir		India

dim(icews) #15,751,586
icews_clean <- icews %>% 
               left_join(CAMEO_eventcodes %>% mutate(cameoeventcode=cameoeventcode) %>%  #You have 
                           dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  )  %>%
                filter(source_country %in% na.omit(actor_translator$ICEWS_Country) | source_name %in% na.omit(actor_translator$ICEWS_Actor.Name)) %>%
                filter(target_country %in% na.omit(actor_translator$ICEWS_Country) | target_name %in% na.omit(actor_translator$ICEWS_Actor.Name) ) %>%
                filter(!source_sectors %>% str_detect(kill_sectors_regex)) %>%
                filter(!target_sectors %>% str_detect(kill_sectors_regex)) %>%
                #Just apply the wikidata actor labels
                #mutate(source=ifelse(is.na(source_country) , source_name, source_country)) %>%
                #mutate(target=ifelse(is.na(target_country) ,target_name , target_country)) %>%
                left_join( actor_translator_icews %>% dplyr::select(source_name=ICEWS_Actor.Name,  source_q_code_actor=QCode, source_q_label_actor=QCode_name) %>% distinct() %>% na.omit() ) %>%
                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(source_country=ICEWS_Country,  source_q_code_country=QCode, source_q_label_country=QCode_name) %>% distinct() %>% na.omit() ) %>%
                mutate(source_q_code=ifelse(!is.na(source_q_code_actor) , source_q_code_actor, source_q_code_country)) %>%
                mutate(source_label=ifelse(!is.na(source_q_code_actor) , source_q_label_actor, source_q_label_country)) %>%

                left_join( actor_translator_icews %>% dplyr::select(target_name=ICEWS_Actor.Name,  target_q_code_actor=QCode, target_q_label_actor=QCode_name) %>% distinct() %>% na.omit() ) %>%
                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(target_country=ICEWS_Country,  target_q_code_country=QCode, target_q_label_country=QCode_name) %>% distinct() %>% na.omit() ) %>%
                mutate(target_q_code=ifelse(!is.na(target_q_code_actor) , target_q_code_actor, target_q_code_country)) %>%
                mutate(target_label=ifelse(!is.na(target_q_code_actor) , target_q_label_actor, target_q_label_country)) %>%

                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(country=ICEWS_Country,  country_q_code=QCode) %>% distinct() %>% na.omit() )

dim(icews_clean) #1,965,573 it's still too many but it's just close enough now #1,965,573

#source_sectors_n <- icews_clean %>% count(source_sectors) %>% arrange(desc(n)) #there are 243k unique sectors, they're nested so you can blacklist larger ones with a regex and it'll catch lower
#source_sectors_n %>% write_csv(paste0(here::here(), "/data_out/icews_sectors.csv"))

```

### Plots

```{r}

icews_metro_plots <- function(crisis=426, topactor=F, exclude='', save_icews_file=NULL){

  print(crisis)
  #crisis=426
  #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
  #save_icews_file = paste0(here::here(), "/paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  if(is.null(savefile)){
    save_icews_file <- paste0(here::here(), "/paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
  }

  date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-31"))

  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm

  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple

  actor_sent_counts <- 
    bind_rows(
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a),
        codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
      ) %>% 
        na.omit() %>%
        mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

  #Only consider diads that appear in our data
  qcodes <- codings_long_agreement %>% dplyr::filter(crisno==crisis & variable_normalized %>% str_detect('actor') & value_normalized!='') %>% pull(value_normalized) %>% unique() %>% na.omit()
  actors_translator <- actor_translator %>% filter(QCode %in% qcodes ) %>% janitor::clean_names() %>%
                       mutate(icews_actor = ifelse(icews_country %in% "International Government Organizations", icews_actor_name,icews_country))

  if(nrow(actors_translator)<2 ){
    print("Not enough actors")
    return()
  }

  diads_qcodes <- bind_rows(
                codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% 
                  dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
                codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% 
                  dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% filter(is.na(say_actor_a)) %>% 
                  dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
                ) %>% 
                mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a) %>%
                mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b) %>%
                na.omit() %>% 
                distinct() %>%
                left_join(actors_translator %>% dplyr::select(actor_a=q_code, source_label=q_code_name) ) %>% #source_sectors
                left_join(actors_translator %>% dplyr::select(actor_b=q_code, target_label=q_code_name) )  %>%  #target_sectors
                mutate(source_target_actor=paste0(actor_a, "_", actor_b) ) %>%

                filter(actor_a!=actor_b) #Decide to exclude when the target is the same as the source

  #phoenix_clean$joined_issues %>% unique()
  #install.packages('parsedate')
  library(parsedate)

  #Ok the IOs are just NA
  #icews_clean_actors_source <- icews_clean %>% dplyr::select(source_name, source_sectors, source_country) %>% count(source_name, source_sectors, source_country)
  #icews_clean_actors_target <- icews_clean %>% dplyr::select(target_name, target_sectors, target_country) %>% count(target_name, target_sectors, target_country)

  icews_clean_subset <- icews_clean %>%

                        mutate(source_target_actor=paste0(source_q_code, "_", target_q_code) ) %>%
                       filter(
                              event_date>=date_start & #Require it to be between the dates of the crisis
                              event_date<=date_end  &
                              source_target_actor %in% diads_qcodes$source_target_actor #require it to be between actors in ICBe  
                              ) %>%
                        mutate(country_valid = is.na(country_q_code) | (country_q_code %in% c(diads_qcodes$actor_a, diads_qcodes$actor_b) ) )  %>%
                        filter(country_valid==T) %>%
                        filter(! cameo_label %in%  cameo_code_rejects) %>% #reject thost common but worthless event types
                       #
                       dplyr::select(event_date,
                                     source_target_actor,
                                     source_label,
                                     target_label,

                                     source_name,
                                     source_sectors,
                                     source_country,
                                     source_q_code,

                                     target_name,
                                     target_sectors,
                                     target_country,
                                     target_q_code,
                                     #same_target_source,
                                     #code, root_code, 
                                     cameo_label, 
                                     country,
                                     country_q_code
                                     #cameo_event_root_label,
                                     #joined_issues,placename, countryname, joined_issues, process
                                     ) %>%
                       distinct() %>%
                       mutate(year = event_date %>% lubridate::year()  )  %>%
                       mutate(month = event_date %>% lubridate::month()  )  %>%
                       mutate(day = event_date %>% lubridate::day()  ) %>%
                       arrange(year,month, day) %>%
                       mutate(sent= year*10000+month*100+day   )  %>% 
                       mutate(sent= as.factor(sent - min(sent, na.rm=T) + 1) %>% as.numeric()  )  %>%
                       filter(!source_label %in% exclude) %>%
                       filter(!target_label %in% exclude)

  #For crises with too many events we subset it to just dyadic events with
  notes <- NULL
  if(topactor & nrow(icews_clean_subset)>100){
    diads_qcodes <- diads_qcodes %>% filter(actor_a== actor_sent_counts$actor[1] | actor_b==actor_sent_counts$actor[1]) #
    icews_clean_subset <- icews_clean_subset %>% filter( source_target_actor %in% diads_qcodes$source_target_actor )
    notes <- "Note: Showing only dyadic events with top actor"
  }

  #This has to come after
  #dim(icews_clean_subset) #11,092
  if(nrow(icews_clean_subset)==0 | 
     (c(icews_clean_subset$source_label,icews_clean_subset$target_label) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
     ){
    print("No ICEWs events for this crisis")
    return()
  }

  library(ggraph)
  library(RColorBrewer)

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  codings_wide_agreed_subset_diad <- icews_clean_subset %>% 
                                     dplyr::select(year, month, sent=sent, actor_1=source_label, actor_2=target_label, cameo_event_label=cameo_label ) %>% distinct() %>%
                                     mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below','') %>% tolower() )  
  #Order actors by how many interactions they have together
  temp <- codings_wide_agreed_subset_diad  %>% dplyr::select(-cameo_event_label, -year, -month) %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #If we're down to one actor we're going to put it in the center and then put other nearby
  if(topactor & nrow(icews_clean_subset)>100){
    ideal_ordering <- c(codings_wide_agreed_subset_diad$actor_1, codings_wide_agreed_subset_diad$actor_2) %>% table() %>% sort() %>% names() %>% rev()
    ideal_ordering <- c(ideal_ordering[c(F,T)] %>% rev(), ideal_ordering[c(T,F)])
  }

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_1) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                    mutate(x=max(x)+50) %>%
                    dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
                    na.omit() %>% 
                    distinct() %>%  
                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                    mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                    group_by(sent) %>%
                    filter(year_float==min(year_float)) %>%
                    ungroup() %>% as.data.frame() %>%
                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                    filter(!duplicated(year_float ) ) %>%
                    mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

  ####Actor lavels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
    #rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F,
                 bundle_count=1)

  ######Directed
  codings_wide_agreed_subset_directed <- 
            icews_clean_subset %>% 
            dplyr::select(sent=sent, actor_1=source_label, actor_2=target_label, cameo_event_label=cameo_label ) %>% distinct() %>%
            mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below',''))  %>% na.omit()  %>% distinct() %>% 
            mutate(leaf = cameo_event_label %>% tolower() )  %>% 
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor1_actor2= actor_1 %>% paste0("_", actor_2)) %>%
            arrange(actor1_actor2, sent) %>%

            group_by(sent,actor1_actor2, actor_1, actor_2, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) %>%
            arrange(actor1_actor2,sent) %>%
            group_by(actor1_actor2) %>%
              mutate(leaf_dupe=leaf==lag(leaf)) %>%
              mutate(sent_gap= sent - lag(sent)  ) %>%
            ungroup()
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  codings_wide_agreed_subset_directed <- codings_wide_agreed_subset_directed  %>% 
                                         filter(!( leaf_dupe %in% T & !is.na(sent_gap) & sent_gap<=31)) %>% #reject the same kind of event within a directed diad that occures again within 31 days back to back
                                         group_by(sent, leaf) %>%
                                             mutate(bundle_count=n()) %>%
                                             mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
                                          ungroup() #%>% 
          #filter(bundle_count>1)
  #dim(codings_wide_agreed_subset_directed) #1826 bundled

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf2, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1,
                       bundle_count=codings_wide_agreed_subset_directed$bundle_count
                       )

  ######Put it all together
  p_icews_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T & bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +
              #Grouped Edges
              geom_edge_parallel(aes(  
                                  colour=actor,
                                  label=leaf,
                                  filter=eventedge==T & bundle_count>1
                                  ),
                              vjust = -0.75,
                              lineheight = .75,
                              sep = unit(5, 'mm'), 
                              edge_width=0.4,  #0.25
                              show.legend = F,
                              arrow = arrow(length = unit(1, 'mm')),
                              label_size=4,
                              check_overlap=T,
                              start_cap = circle(3, 'mm'),
                              end_cap = circle(3, 'mm'),
                              angle_calc = 'along'
                             ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  if(!is.null(notes)){
     p_icews_metro_map <- p_icews_metro_map + labs(caption = notes)
  }

  p_icews_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
  p_icews_metro_map$actor_colors <- actor_colors
  p_icews_metro_map$icews_clean_subset <- icews_clean_subset

  p_icews_metro_map  %>% saveRDS(save_icews_file)

}

icb_crises %>% filter(yrtrig>=1995) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) icews_metro_plots(x))

```

## Phoenix

### Data Loads

```{r}

library(tidyverse)
library(countrycode)
library(igraph)
library(ggraph)

a <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
b  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
c  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
d  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
e <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))

phoenix <- bind_rows(a, b, c, d , e)

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

#8,491,556
library(stringr)
phoenix_clean <- phoenix %>% 
                 filter(source_root!='' & target_root!='') %>%
                 mutate(same_target_source=source_root==target_root) %>%
                 mutate(date_simple=as.numeric(year) + (as.numeric(month)/12) ) %>%

                 #mutate(code=code %>% str_pad(4, pad = "0") %>% str_replace("0{1,3}","0")) %>%
                 #mutate(root_code=root_code %>% str_pad(2, pad = "0") %>% str_replace("0{1,3}","0")) %>%

                 left_join(CAMEO_eventcodes %>% dplyr::select(code=cameoeventcode     , cameo_event_label=eventdescription) ) %>%

                 left_join(CAMEO_eventcodes %>% dplyr::select(root_code=cameoeventcode, cameo_event_root_label=eventdescription) %>% filter(nchar(root_code)==2)) %>%

                 mutate(joined_issues=ifelse( joined_issues=='',";", joined_issues)  ) %>% #Apparently unnesting an empty string just gets dropped
                 mutate(joined_issues = strsplit(as.character(joined_issues), ";") ) %>%  unnest(joined_issues)  %>% #This drops if the row is missing, I did not know that was it

                 left_join(cameo_role_codes %>% dplyr::select(source_agent=role_code, source_agent_label=role_code_label) %>% distinct() %>% na.omit() ) %>%
                 left_join(cameo_role_codes %>% dplyr::select(target_agent=role_code, target_agent_label=role_code_label) %>% distinct() %>% na.omit() ) %>%
                 left_join(cameo_role_codes %>% dplyr::select(source_others=role_code, source_others_label=role_code_label) %>% distinct() %>% na.omit() ) %>%
                 left_join(cameo_role_codes %>% dplyr::select(target_others=role_code, target_others_label=role_code_label) %>% distinct() %>% na.omit() )  %>% 
                   distinct() %>%
                   filter(
                     !source_others_label %in% role_rejects &
                     !target_others_label %in% role_rejects &
                     !source_agent_label %in% role_rejects &
                     !target_agent_label %in% role_rejects 
                     ) %>%
                 #Just apply the actor labels
                 left_join(actor_translator %>% dplyr::select(source_root=phoenix_2020, source_root_label=QCode_name, source_root_qcode=QCode) %>% distinct() %>% na.omit() ) %>%
                 left_join(actor_translator %>% dplyr::select(target_root=phoenix_2020, target_root_label=QCode_name, target_root_qcode=QCode) %>% distinct() %>% na.omit() )

dim(phoenix_clean) #2,813,748 #2912035 #3,508,495 #4,854,787

```

### Plot

[@althausClineCenterHistorical2020a]

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

phoenix_metro_plots <- function(crisis=196, topactor=F){

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_phoenix_file <- paste0(here::here(), "/paper/figures/metro_plots/p_phoenix_metro_plot_",crisis,".Rds")

  date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-31"))

  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm

  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple

  actor_sent_counts <- 
        bind_rows(
            #codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
            #codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
            #codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
            codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a), #Going to organize around actions
            codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
          ) %>% 
            na.omit() %>%
            mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

  #Only consider diads that appear in our data
  qcodes <- codings_long_agreement %>% dplyr::filter(crisno==crisis & variable_normalized %>% str_detect('actor') & value_normalized!='') %>% pull(value_normalized) %>% unique() %>% na.omit()
  diads_qcodes <- bind_rows(
                    codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>%
                      dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
                    codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>%
                      filter(is.na(say_actor_a)) %>% dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
                  ) %>% 
                  mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a) %>%
                  mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b) %>%
                  na.omit() %>% distinct()

  actors_translator <- actor_translator %>% filter(QCode %in% qcodes ) %>% janitor::clean_names()

  diads_qcodes <- bind_rows(
                  codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% 
                    dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
                  codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% 
                    dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% filter(is.na(say_actor_a)) %>% 
                    dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
                  ) %>% 
                  mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a) %>%
                  mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b) %>%
                  na.omit() %>% 
                  distinct() %>%
                  left_join(actors_translator %>% dplyr::select(actor_a=q_code, phoenix_2020_a=phoenix_2020) ) %>%
                  left_join(actors_translator %>% dplyr::select(actor_b=q_code, phoenix_2020_b=phoenix_2020) )  %>% 
                  mutate(source_root_target=paste0(actor_a, "_", actor_b) ) %>%

                  filter(actor_a!=actor_b) #Decide to exclude when the target is the same as the source

  #phoenix_clean$joined_issues %>% unique()
  #install.packages('parsedate')
  library(parsedate)
  phoenix_clean_subset <- phoenix_clean %>% 
                           mutate(source_root_target=paste0(source_root_qcode, "_", target_root_qcode) ) %>%

                           filter(
                                  source_root_target %in% diads_qcodes$source_root_target & 
                                  #target_root %in% na.omit(actors_translator_subset$phoenix_2020) & 
                                  #source_root %in% na.omit(actors_translator_subset$phoenix_2020) &
                                  year>=year_start &
                                  year<=year_end   
                                  #date_simple>=start_simple & 
                                  #date_simple<=end_simple 
                                  ) %>%
                           filter( countryname %in%  na.omit(c('',actors_translator$terrier, actors_translator$icb_letters, actors_translator$phoenix_2020))  ) %>% #also reject anything geotagged not in an actor
                           mutate(crisis_dates= (date_simple>=start_simple & date_simple<=end_simple ) %>% as.numeric()) %>%
                           #Just apply the actor labels
                           distinct()   %>%

                           #
                           dplyr::select(crisis_dates,
                                         story_date, year, month, day, 
                                         source_root_target,
                                         source_root_qcode,
                                         target_root_qcode,
                                         source, source_root, source_agent, source_others,
                                         target, target_root, target_agent, target_others,
                                         source_root_label, source_agent_label, source_others_label,
                                         target_root_label, target_agent_label, target_others_label,
                                         same_target_source,
                                         code, root_code, 
                                         cameo_event_label, 
                                         cameo_event_root_label,
                                         joined_issues,placename, countryname, joined_issues, process) %>%

                           dplyr::select(-process) %>%
                           distinct() %>%

                           #Reject sub actors that we don't think are relevant
                           filter(
                             !source_agent_label %in% role_rejects &
                             !target_agent_label %in% role_rejects &
                             !source_others_label %in% role_rejects &
                             !target_others_label %in% role_rejects
                           ) %>%

                           #Reject subjects we don't think are relevant
                           filter(!joined_issues %in% subject_rejects) %>%

                           filter(crisis_dates==T) %>% #limit to just the crisis dates

                           filter(!cameo_event_label %in% cameo_code_rejects) %>%

                           #Restrict to NYT or max source
                           #group_by(process) %>%
                           #  mutate(process_n=n()) %>%
                           # ungroup() %>%
                           #filter(process_n==max(process_n)) %>% #Always pick the source with the most events #process=="NYT_Pre0101991_V1"
                           arrange(year,month, day) %>%
                           mutate(sent= as.numeric(year)*10000+as.numeric(month)*100+as.numeric(day)   )  %>% 
                           mutate(sent= as.factor(sent - min(sent, na.rm=T) + 1) %>% as.numeric()  ) %>%
                          mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below|,  not specified below',''))

  #For crises with too many events we subset it to just dyadic events with
  notes <- NULL
  if(topactor & nrow(phoenix_clean_subset)>100){
    diads_qcodes <- diads_qcodes %>% filter(actor_a == actor_sent_counts$actor[1] | actor_b == actor_sent_counts$actor[1]) #
    phoenix_clean_subset <- phoenix_clean_subset %>% filter( source_root_target %in% diads_qcodes$source_root_target )
    notes <- "Note: Showing only dyadic events with top actor"
  }

  dim(phoenix_clean_subset) #
  if(nrow(phoenix_clean_subset)==0 | 
     (c(phoenix_clean_subset$source_root_label,phoenix_clean_subset$target_root_label) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
     ){
    print("No Phoenix events for this crisis")
    return()
  }

  library(ggraph)
  library(RColorBrewer)

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  #phoenix_clean$year <- phoenix_clean$story_date %>% lubridate::year()
  #phoenix_clean$month <- phoenix_clean$story_date %>% lubridate::month()

  codings_wide_agreed_subset_diad <- phoenix_clean_subset %>% 
                                     dplyr::select(year, month, sent=sent, actor_1=source_root_label, actor_2=target_root_label, cameo_event_label ) %>% distinct() %>%
                                     mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below','') %>% tolower() ) 
  #Order actors by how many interactions they have together
  temp <- codings_wide_agreed_subset_diad  %>% dplyr::select(-year, -month, -cameo_event_label) %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  temp_list <- list()
  for(i in 1:nrow(temp2_wide)){
    temp_list[[as.character(i)]] <- cutree(hc, k=i)
  }

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #If we're down to one actor we're going to put it in the center and then put other nearby
  if(topactor & nrow(phoenix_clean_subset)>100){
    ideal_ordering <- c(codings_wide_agreed_subset_diad$actor_1, codings_wide_agreed_subset_diad$actor_2) %>% table() %>% sort() %>% names() %>% rev()
    ideal_ordering <- c(ideal_ordering[c(F,T)] %>% rev(), ideal_ordering[c(T,F)])
  }

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                    mutate(x=max(x)+50) %>%
                    mutate(year=year %>% as.numeric() ) %>%
                    mutate(month=month %>% as.numeric() ) %>%
                    dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
                    na.omit() %>% 
                    distinct() %>%  
                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                    mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                    group_by(sent) %>%
                    filter(year_float==min(year_float)) %>%
                    ungroup() %>% as.data.frame() %>%
                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                    filter(!duplicated(year_float ) ) %>%
                    mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

  ####Actor lavels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
    #rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F,
                 bundle_count=1)

  ######Directed
  codings_wide_agreed_subset_directed <- 
            phoenix_clean_subset %>% 
            dplyr::select(sent=sent, actor_1=source_root_label, actor_2=target_root_label, cameo_event_label ) %>% distinct() %>%
            mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below',''))  %>% na.omit()  %>% distinct() %>% 
            mutate(leaf = cameo_event_label %>% tolower() )  %>% 
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor1_actor2= actor_1 %>% paste0("_", actor_2)) %>%
            arrange(actor1_actor2, sent) %>%

            group_by(sent,actor1_actor2, actor_1, actor_2, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) %>%
            arrange(actor1_actor2,sent) %>%
            group_by(actor1_actor2) %>%
              mutate(leaf_dupe=leaf==lag(leaf)) %>%
              mutate(sent_gap= sent - lag(sent)  ) %>%
            ungroup()
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  codings_wide_agreed_subset_directed <- codings_wide_agreed_subset_directed  %>% 
                                         filter(!( leaf_dupe %in% T & !is.na(sent_gap) & sent_gap<=31)) %>% #reject the same kind of event within a directed diad that occures again within 31 days back to back
                                         group_by(sent, leaf) %>%
                                             mutate(bundle_count=n()) %>%
                                             mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
                                          ungroup() #%>% 
          #filter(bundle_count>1)
  #dim(codings_wide_agreed_subset_directed) #1826 bundled

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf2, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1,
                       bundle_count=codings_wide_agreed_subset_directed$bundle_count
                       )

  ######Put it all together
  p_phoenix_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T & bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +
              #Grouped Edges
              geom_edge_parallel(aes(  
                                  colour=actor,
                                  label=leaf,
                                  filter=eventedge==T & bundle_count>1
                                  ),
                              vjust = -0.75,
                              lineheight = .75,
                              sep = unit(5, 'mm'), 
                              edge_width=0.4,  #0.25
                              show.legend = F,
                              arrow = arrow(length = unit(1, 'mm')),
                              label_size=4,
                              check_overlap=T,
                              start_cap = circle(3, 'mm'),
                              end_cap = circle(3, 'mm'),
                              angle_calc = 'along'
                             ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  if(!is.null(notes)){
     p_phoenix_metro_map <- p_phoenix_metro_map + labs(caption = notes)
  }

  p_phoenix_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
  p_phoenix_metro_map$actor_colors <- actor_colors
  p_phoenix_metro_map$phoenix_clean_subset <- phoenix_clean_subset

  p_phoenix_metro_map  %>% saveRDS(save_phoenix_file)

}

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) phoenix_metro_plots(x))

```

## Terrier

### Data Loads

https://osf.io/4m2u7/

```{r}

df <- data.frame(
       stringsAsFactors = FALSE,
                   agent = c("GOV","SPY","OPP",
                            "MIL","PTY","REB","EDU","COP","JUD","CRM",
                            "BUS","MED","CVL","UAF","AGR","ELI","DEV","ENV",
                            "HLH","HRI","LAB","LEG","REF","MOD","RAD"),
                    agent_label = c("Government",
                            "Intelligence agencies",
                            "Opposition groups (often parliamentary)",
                            "Military",
                            "Political party",
                            "Rebels/insurgents",
                            "Education-focused actors",
                            "Law enforcement agencies",
                            "Judicial actors",
                            "Criminal actors",
                            "Business (NOT MNCs)",
                            "Media-related actors/organizations",
                            "Civilians",
                            "Unaffiliated armed forces",
                            "Agriculture-focused actors",
                            "Elites, celebrities",
                            "Development-focused actors",
                            "Environment-focused actors",
                            "Health-focused actors",
                            "Human rights-focused actors",
                            "Labor-focused actors",
                            "Legislative bodies/actors",
                            "Refugee-focused actors",
                            "Moderate/mainstream group",
                            "Radical/extremist/fundamentalist")
) %>% janitor::clean_names()

files <- list.files(path = paste0(here::here(), "/data_other_datasets/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/data_other_datasets/terrier/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
#codes_used <-terrier_clean %>% count(cameo_code)

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

#Maybe it's just ISO3 country codes?
terrier_clean <- terrier %>% 
    dplyr::select(
      cameo_code=x3,
      src_country=x8,
      src_agent=x9,
      src_other_agent=x10,

      target_country=x12 ,
      target_agent=x13,
      target_other_agent=x14,

      year=x17,
      month=x18,
      day=x19#,
      #random_text=x28
    ) %>% 
    filter(!is.na(src_country) & !is.na(target_country)) %>%
    distinct() %>% 
     mutate(cameo_code=cameo_code %>% as.numeric()) %>% 
     left_join(CAMEO_eventcodes %>% mutate(cameoeventcode=cameoeventcode %>% as.numeric(cameoeventcode)) %>%
                 dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  ) %>%
    mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
    distinct() %>%

   mutate(src_other_agent=ifelse( src_other_agent=='',";", src_other_agent)  ) %>% #Apparently unnesting an empty string just gets dropped
   mutate(src_other_agent = strsplit(as.character(src_other_agent), ";") ) %>%  unnest(src_other_agent)  %>% #This drops if the row is missing, I did not know that was it

   mutate(target_other_agent=ifelse( target_other_agent=='',";", target_other_agent)  ) %>% #Apparently unnesting an empty string just gets dropped
   mutate(target_other_agent = strsplit(as.character(target_other_agent), ";") ) %>%  unnest(target_other_agent)  %>% #This drops if the row is missing, I did not know that was it

   left_join(df %>% dplyr::select(src_other_agent=agent   , src_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
   left_join(df %>% dplyr::select(target_other_agent=agent, target_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%

   left_join(df %>% dplyr::select(src_agent=agent, src_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
   left_join(df %>% dplyr::select(target_agent=agent, target_agent_label=agent_label) %>% distinct() %>% na.omit() )  %>% 
   distinct() %>%
   filter(
     !src_other_agent_label %in% role_rejects &
     !target_other_agent_label %in% role_rejects &
     !src_agent_label %in% role_rejects &
     !target_agent_label %in% role_rejects 
     ) %>% 
  left_join(actor_translator %>% dplyr::select(src_country=terrier,actor_1_qcode=QCode,actor_1=QCode_name) ) %>%
  left_join(actor_translator %>% dplyr::select(target_country=terrier,actor_2_qcode=QCode,actor_2=QCode_name) ) %>%
  filter(!is.na(actor_1_qcode) & !is.na(actor_2_qcode) ) %>%
  mutate(source_root_target=paste0(src_country, "_", target_country) ) %>%
  mutate(
  event_date= lubridate::as_date(paste0( year, "-", month,"-",day ))
  )
dim(terrier_clean) #2,049,759

#For now
#IGO 223751 for now we're going to exclue just generic Intergovernmental organization and multiinational corps
#MNC 62721
#terrier_clean %>% dplyr::select(src_country, actor_1) %>% filter(is.na(actor_1)) %>% count(src_country) %>% View()

#terrier_clean %>% 
#  dplyr::select(src_agent_label,  src_other_agent_label, target_agent_label, target_other_agent_label, cameo_label) %>% 
#  count(src_agent_label,  src_other_agent_label, target_agent_label, target_other_agent_label, cameo_label) %>% arrange(desc(n)) %>% View()

```

### Plot

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

terrier_metro_plots <- function(crisis=196, topactor=F){

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_terrier_file <- paste0(here::here(), "/paper/figures/metro_plots/p_terrier_metro_plot_",crisis,".Rds")

  date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-31"))

  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm

  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple

  actor_sent_counts <- 
        bind_rows(
            #codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=think_actor_a),
            #codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_a),
            #codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=say_actor_b),
            codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_a), #Going to organize around actions
            codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=final_event_ordering,actor=do_actor_b)
          ) %>% 
            na.omit() %>%
            mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

  #Only consider diads that appear in our data
  qcodes <- codings_long_agreement %>% dplyr::filter(crisno==crisis & variable_normalized %>% str_detect('actor') & value_normalized!='') %>% pull(value_normalized) %>% unique() %>% na.omit()
  actors_translator <- actor_translator %>% filter(QCode %in% qcodes ) %>% janitor::clean_names()

  diads_qcodes <- bind_rows(
                  codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% 
                    dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
                  codings_wide_agreed %>% dplyr::filter(crisno==crisis  ) %>% 
                    dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% filter(is.na(say_actor_a)) %>% 
                    dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
                  ) %>% 
                  mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a) %>%
                  mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b) %>%
                  na.omit() %>% 
                  distinct() %>%
                  left_join(actors_translator %>% dplyr::select(actor_a=q_code, terrier_a=terrier) ) %>% #I think we can reuse Phoenix or maybe not? no probably not
                  left_join(actors_translator %>% dplyr::select(actor_b=q_code, terrier_b=terrier) )  %>% 
                  mutate(source_root_target=paste0(terrier_a, "_", terrier_b) ) %>%

                  filter(terrier_a!=terrier_b) #Decide to exclude when the target is the same as the source

  #phoenix_clean$joined_issues %>% unique()
  #install.packages('parsedate')
  library(parsedate)
  terrier_clean_subset <- terrier_clean %>%

                           filter(
                                  source_root_target %in% diads_qcodes$source_root_target & 
                                  #target_root %in% na.omit(actors_translator_subset$phoenix_2020) & 
                                  #source_root %in% na.omit(actors_translator_subset$phoenix_2020) &
                                  event_date>=date_start &
                                  event_date<=date_end   
                                  #date_simple>=start_simple & 
                                  #date_simple<=end_simple 
                                  ) %>%

                           #
                           dplyr::select(event_date,year,month,
                                         actor_1, actor_1_qcode,
                                         actor_2, actor_2_qcode,
                                         src_country, src_agent_label, src_other_agent_label, target_country, target_agent_label, target_other_agent_label,
                                         source_root_target,
                                         cameo_label) %>%

                           distinct() %>%
                           mutate(year = event_date %>% lubridate::year()  )  %>%
                           mutate(month = event_date %>% lubridate::month()  )  %>%
                           mutate(day = event_date %>% lubridate::day()  ) %>%
                           arrange(year,month, day) %>%
                           mutate(sent= year*10000+month*100+day   )  %>% 
                           mutate(sent= as.factor(sent - min(sent, na.rm=T) + 1) %>% as.numeric()  )

  #For crises with too many events we subset it to just dyadic events with
  notes <- NULL
  if(topactor & nrow(terrier_clean_subset)>100){
    diads_qcodes <- diads_qcodes %>% filter(actor_a == actor_sent_counts$actor[1] | actor_b == actor_sent_counts$actor[1]) #
    terrier_clean_subset <- terrier_clean_subset %>% filter( source_root_target %in% diads_qcodes$source_root_target )
    notes <- "Note: Showing only dyadic events with top actor"
  }

  dim(terrier_clean_subset) #
  if(nrow(terrier_clean_subset)==0 | 
     (c(terrier_clean_subset$actor_1,terrier_clean_subset$actor_2) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
     ){
    print("No terrier events for this crisis")
    return()
  }

  library(ggraph)
  library(RColorBrewer)

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  codings_wide_agreed_subset_diad <- terrier_clean_subset %>% 
                                     dplyr::select(year, month, sent=sent, actor_1=actor_1, actor_2=actor_2, cameo_label ) %>% distinct() %>%
                                     mutate(cameo_label=cameo_label %>% str_replace(', not specified below','') %>% tolower() ) 
  #Order actors by how many interactions they have together
  temp <- codings_wide_agreed_subset_diad  %>% dplyr::select(-year, -month , -cameo_label) %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  temp_list <- list()
  for(i in 1:nrow(temp2_wide)){
    temp_list[[as.character(i)]] <- cutree(hc, k=i)
  }

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #If we're down to one actor we're going to put it in the center and then put other nearby
  if(topactor & nrow(terrier_clean_subset)>100){
    ideal_ordering <- c(codings_wide_agreed_subset_diad$actor_1, codings_wide_agreed_subset_diad$actor_2) %>% table() %>% sort() %>% names() %>% rev()
    ideal_ordering <- c(ideal_ordering[c(F,T)] %>% rev(), ideal_ordering[c(T,F)])
  }

  #####Nodes
  codings_wide_agreed_subset_nodes <- 
            bind_rows(
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
                      codings_wide_agreed_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- codings_wide_agreed_subset_nodes  %>%
                      mutate(x=max(x)+50) %>%
                      mutate(year=year %>% as.numeric()) %>%
                      mutate(month=month %>% as.numeric()) %>%
                      dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
                      na.omit() %>% 
                      distinct() %>%  
                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                      group_by(sent) %>%
                      filter(year_float==min(year_float)) %>%
                      ungroup() %>% as.data.frame() %>%
                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                      filter(!duplicated(year_float ) ) %>%
                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

  ####Actor lavels
  codings_wide_agreed_subset_nodes_min <- 
    codings_wide_agreed_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
    #rename(qcode=actor, actor=value_normalized_label) %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(codings_wide_agreed_subset_nodes)){
    g <- g %>%  add_vertices(1, name=codings_wide_agreed_subset_nodes$actor_sent[i],
                                actor = codings_wide_agreed_subset_nodes$actor[i], 
                                sent = codings_wide_agreed_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(codings_wide_agreed_subset_nodes$x, codings_wide_agreed_subset_nodes$y )

  #####Time Edges
  codings_wide_agreed_subset_nodes_edges_time <- cbind(codings_wide_agreed_subset_nodes, bind_rows(codings_wide_agreed_subset_nodes[-1,],codings_wide_agreed_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(codings_wide_agreed_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=codings_wide_agreed_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F,
                 bundle_count=1)

  ######Directed
  codings_wide_agreed_subset_directed <- 
            terrier_clean_subset %>% 
            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, cameo_label ) %>% distinct() %>%
            mutate(cameo_label=cameo_label %>% str_replace(', not specified below',''))  %>% na.omit()  %>% distinct() %>% 
            mutate(leaf = cameo_label %>% tolower() )  %>% 
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor1_actor2= actor_1 %>% paste0("_", actor_2)) %>%
            arrange(actor1_actor2, sent) %>%

            group_by(sent,actor1_actor2, actor_1, actor_2, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) %>%
            arrange(actor1_actor2,sent) %>%
            group_by(actor1_actor2) %>%
              mutate(leaf_dupe=leaf==lag(leaf)) %>%
              mutate(sent_gap= sent - lag(sent)  ) %>%
            ungroup()
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  codings_wide_agreed_subset_directed <- codings_wide_agreed_subset_directed  %>% 
                                         filter(!( leaf_dupe %in% T & !is.na(sent_gap) & sent_gap<=31)) %>% #reject the same kind of event within a directed diad that occures again within 31 days back to back
                                         group_by(sent, leaf) %>%
                                             mutate(bundle_count=n()) %>%
                                             mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
                                          ungroup() #%>% 
          #filter(bundle_count>1)
  #dim(codings_wide_agreed_subset_directed) #1826 bundled

  g <- g %>% add_edges(codings_wide_agreed_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=codings_wide_agreed_subset_directed$leaf2, 
                       eventedge=T,
                       actor=codings_wide_agreed_subset_directed$actor_1,
                       bundle_count=codings_wide_agreed_subset_directed$bundle_count
                       )

  ######Put it all together
  p_terrier_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T & bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=T,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +
              #Grouped Edges
              geom_edge_parallel(aes(  
                                  colour=actor,
                                  label=leaf,
                                  filter=eventedge==T & bundle_count>1
                                  ),
                              vjust = -0.75,
                              lineheight = .75,
                              sep = unit(5, 'mm'), 
                              edge_width=0.4,  #0.25
                              show.legend = F,
                              arrow = arrow(length = unit(1, 'mm')),
                              label_size=4,
                              check_overlap=T,
                              start_cap = circle(3, 'mm'),
                              end_cap = circle(3, 'mm'),
                              angle_calc = 'along'
                             ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=codings_wide_agreed_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap = T) + #-45
              geom_text(data=codings_wide_agreed_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  if(!is.null(notes)){
     p_terrier_metro_map <- p_terrier_metro_map + labs(caption = notes)
  }

  p_terrier_metro_map$sentence_count <- codings_wide_agreed_subset_nodes$sent %>% unique() %>% length()
  p_terrier_metro_map$actor_colors <- actor_colors
  p_terrier_metro_map$terrier_clean_subset <- terrier_clean_subset

  p_terrier_metro_map  %>% saveRDS(save_terrier_file)

}

icb_crises %>% filter(yrtrig>=1977) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
Init

---
title: 'Intercoder ICBEdataset_figure_semantic_embeddings'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

# Intro

## Library Loads

```{r}

library(flextable); library(ftExtra)
library(tidyverse)
library(googlesheets4)

```

```{r}

codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/codings_wide_agreed.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/codings_long_agreed.Rds'))
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
codings_long <- readRDS(file=paste0(here::here(), '/data_out/codings_long.Rds'))
codings_long_agreement <- readRDS(file=paste0(here::here(), '/data_out/codings_long_agreement.Rds'))

```

```{r}

sentences_unique <- icb_long_clean %>% dplyr::select(sentence) %>% distinct() %>% pull(sentence) %>% unique() %>% na.omit()
length(sentences_unique )

sentences_unique_sanitized <- sentences_unique %>% str_replace_all("[A-Z][a-z]*","Entity")
#sentences_unique_sanitized %>% as.data.frame() %>% View()

```

```{r, messages=F, results='hide'}
library(reticulate)
#py_discover_config()
use_python("/home/skynet3/anaconda3/bin/python/")

```

```{python}
#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers

fromscratch=True

if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=r.sentences_unique_sanitized
  len(sentences) #10383
  model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  sentences_embeddings = model.encode(sentences) #[0:100]
else:
  print("Skipping")

```

```{r}

sentences_embeddings <- py$sentences_embeddings
dim(sentences_embeddings)

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umap(sentences_embeddings  )

sentences_embeded <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()
sentences_embeded$sentence <- sentences_unique

codings_long_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)

codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_data/temp/codings_long_agreed_embeded.Rds'))

codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_data/out/codings_wide_agreed.Rds'))
codings_wide_agreed_embeded <- codings_wide_agreed %>% ungroup() %>% left_join(sentences_embeded)

codings_wide_agreed_embeded_stratified_sample  <- codings_wide_agreed_embeded %>% 
                                                  mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
                                                  dplyr::group_by(UMAP1_round,UMAP2_round) %>%
                                                  arrange(UMAP1,UMAP2) %>%
                                                  filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] )

sampled <- codings_wide_agreed_embeded_stratified_sample %>% ungroup() %>% mutate(crisno_sent=paste0(crisno,'.',sentence_number_int_aligned)) %>%
  dplyr::select(crisno_sent, UMAP1,UMAP2) %>% distinct()

codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_data/temp/codings_wide_agreed_embeded.Rds'))

var_keep <- c('Behavior','do_aggression','Do_Armed_Unarmed','leaf_do_original') %>% tolower() #'Event_Any',

value_means <- codings_long_agreed_embeded %>%
      dplyr::filter(variable_normalized %in% var_keep) %>% 
      dplyr::mutate(variable_normalized=variable_normalized %>% as.factor()) %>%
      dplyr::mutate(value_normalized=value_normalized %>% as.factor()) %>%
      dplyr::select(variable_normalized,value_normalized,UMAP1,UMAP2) %>%
      group_by(variable_normalized, value_normalized) %>% 
      summarise_all(median) %>%
      group_by(variable_normalized) %>%
          mutate(variable_normalized_count=  min(n(),4)  ) %>%
      ungroup()

codings_long_agreed_embeded_subset <- codings_long_agreed_embeded %>%
                                      dplyr::filter(variable_normalized %in% var_keep) %>%
                                      dplyr::mutate(value_normalized=value_normalized %>% as.factor())

library(RColorBrewer)
brewer_pal_info_df <- brewer.pal.info %>% add_rownames( var = "rowname") %>% arrange()
brewer_list <- list() 
for(i in c(11, 1:nrow(brewer_pal_info_df))){
  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
}
posible_colors <- unlist(brewer_list) %>% unique(brewer_list) #%>% sample()

value_normalized=codings_long_agreed_embeded_subset$value_normalized %>% unique() %>% as.factor()
value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
names(value_normalized_colors) = levels(value_normalized)

p_semantic_embeddings <-
      codings_long_agreed_embeded_subset %>%
      ggplot(aes(x=UMAP1,y=UMAP2, color=value_normalized )) +
        geom_point(size=0.5, alpha=0.5) + 
        geom_text(data=sampled, aes(x=UMAP1, y=UMAP2, label=crisno_sent), color='black',size=1.5) +

        facet_wrap( ~ variable_normalized) + 
        theme_bw() +
        theme(legend.position = "none") + 
        geom_label(data=value_means,
                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, label=value_normalized, size=50),inherit.aes=F, # #variable_normalized_count
                   colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")) + 
        labs(
            title = "Variation in Tags by Semantic Embeddings of Source Sentences",
            subtitle = "Sentences Embedding Sentence-BERT, UMAP Projection ",
            caption = ""
        ) +
       scale_color_manual(values = value_normalized_colors) +
       scale_fill_manual(values = value_normalized_colors)

p_semantic_embeddings   %>% saveRDS(paste0(here::here(), '/paper_replication/figures/p_semantic_embeddings.Rds'))
p_semantic_embeddings

```

```{r}

codings_wide_agreed_embeded_stratified_sample  <- codings_wide_agreed_embeded %>% 
                                                  mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
                                                  dplyr::group_by(UMAP1_round,UMAP2_round) %>%
                                                  arrange(UMAP1,UMAP2) %>%
                                                  filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] )

```

```{r}

codings_wide_agreed_embeded_stratified_sample_table <-       codings_wide_agreed_embeded_stratified_sample %>%
                                                              group_by(crisno, sentence_number_int_aligned, crisno_sent, sentence) %>%
                                                                summarize(codings_sentence = paste(codings_sentence, collapse="\n")) %>%
                                                              ungroup() %>%
                                                              dplyr::select(crisno_sent, sentence, codings_sentence)  %>%
                                                              dplyr::filter(codings_sentence!="No events.") %>%
                                                              dplyr::select(id=crisno_sent, sentence, codings_sentence)

n=nrow(codings_wide_agreed_embeded_stratified_sample_table)
k=ncol(codings_wide_agreed_embeded_stratified_sample_table)
codings_wide_agreed_embeded_stratified_sample_ft <- 
            codings_wide_agreed_embeded_stratified_sample_table %>%
            as_flextable() %>%
            colformat_md(j=3) %>% 
            flextable::fontsize(size = 7, part = "all") %>%
            flextable::bg( i = which( 1:n %% 2 == 1)  , j=1:3, part = "body", bg = "#EFEFEF") %>%
            flextable::width(j = 1, width=0.3, unit = "in") %>%
            flextable::width(j = 2, width=3, unit = "in") %>%
            flextable::width(j = 3, width=3, unit = "in")

codings_wide_agreed_embeded_stratified_sample_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds'))
codings_wide_agreed_embeded_stratified_sample_ft

#Smaller for main paper
temp2 <- codings_wide_agreed_embeded_stratified_sample_table[rep_len(c(T,F,F),length.out=nrow(codings_wide_agreed_embeded_stratified_sample_table)),] 
n=nrow(temp2)
codings_wide_agreed_embeded_stratified_sample_ft_smaller <- 
            temp2 %>%
            as_flextable() %>%
            colformat_md(j=3) %>% 
            flextable::fontsize(size = 7, part = "all") %>%
            flextable::bg( i = which( 1:n %% 2 == 1)  , j=1:3, part = "body", bg = "#EFEFEF") %>%
            flextable::width(j = 1, width=0.3, unit = "in") %>%
            flextable::width(j = 2, width=3, unit = "in") %>%
            flextable::width(j = 3, width=3, unit = "in")

codings_wide_agreed_embeded_stratified_sample_ft_smaller  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds'))
codings_wide_agreed_embeded_stratified_sample_ft_smaller

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_InterCoderByLevels.Rmd
Init

---
title: "Untitled"
output: html_document
---

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

```

```{r, echo=FALSE}

icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds")) #%>% 
                  #mutate(temp_row_id=paste(email_id, crisno,sentence_number_int_aligned, variable, sep="_")) %>%
                  #mutate(cleaned=temp_row_id %>% str_detect("_clean")) %>%
                  #mutate(temp_row_id= temp_row_id %>% str_replace("_clean","")) %>%
                  #arrange(desc(cleaned), temp_row_id) %>% 
                  #filter(!duplicated(temp_row_id)) %>%
                  #mutate(variable= variable %>% str_replace("_clean",""))

icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))

```

```{r}

full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
                                       sheet="Codebook in Tree Form")

full_tree <- full_tree %>% filter(!is.na(Leaf) & Leaf!='')
#The leafs aren't unique here because you can get to the same branch multiple ways

#This ignores conditions FYI
#Behavior # 3 bits
#think_aggression #1 bit
#say_aggression #1 bit
#do_aggression #1 bit
#Do_Armed_Unarmed #1 bit
#do_Act_Interact #1 bit
#full_tree$Leaf_Simplified %>% unique() %>% length() #66 bits

#Only 70 bits total

#That's only another 29 bits
full_tree$Think_Type_L0 %>% unique() %>% length() #6
full_tree$Say_Type_L0 %>% unique() %>% length() #5
full_tree$Do_Type_L0 %>% unique() %>% length() #18

```

```{r}

library(dplyr, warn.conflicts = FALSE)
options(warn=-1)

icb_long_clean$email_id_expert <- icb_long_clean$email_id %>% str_detect("grad|postgrad")

#icb_long_clean %>% dplyr::select(variable) %>% distinct() %>% View()

paste_collapse=function(x) paste(x %>% sort(), collapse=";") %>% str_replace_all("https://en.wikipedia.org/wiki/",'') #sorting removes the order indeterminacy
actors_clean <- icb_long_clean %>%
                filter(variable %>% str_detect('actor') & variable %>% str_detect('clean')) %>%
                mutate(variable=variable %>%str_replace('other_','')) %>% #removing the text other from the variable will auto include it in our list here
                pivot_wider(names_from=variable,
                            values_from=value,
                            values_fn=paste_collapse
                            ) %>%
                 dplyr::mutate(think_actor_a_clean = strsplit(as.character(think_actor_a_clean), ";")) %>% tidyr::unnest(think_actor_a_clean) %>% dplyr::mutate(think_actor_a_clean=think_actor_a_clean %>% trimws()) %>%
                 dplyr::mutate(say_actor_a_clean = strsplit(as.character(say_actor_a_clean), ";")) %>% tidyr::unnest(say_actor_a_clean) %>% dplyr::mutate(say_actor_a_clean=say_actor_a_clean %>% trimws()) %>%
                 dplyr::mutate(say_actor_b_clean = strsplit(as.character(say_actor_b_clean), ";")) %>% tidyr::unnest(say_actor_b_clean) %>% dplyr::mutate(say_actor_b_clean=say_actor_b_clean %>% trimws()) %>%
                 dplyr::mutate(do_actor_a_clean = strsplit(as.character(do_actor_a_clean), ";")) %>% tidyr::unnest(do_actor_a_clean) %>% dplyr::mutate(do_actor_a_clean=do_actor_a_clean %>% trimws()) %>%
                 dplyr::mutate(do_actor_b_clean = strsplit(as.character(do_actor_b_clean), ";")) %>% tidyr::unnest(do_actor_b_clean) %>% dplyr::mutate(do_actor_b_clean=do_actor_b_clean %>% trimws()) 
                  #currently ignoring condition
dim(actors_clean)

#I think we convert this to actor-event, where every lhs actor mentioned gets a row and then we ask what people thought THEY did in that sentence
temp_long <- icb_long_clean %>%
             filter(!variable %>% str_detect('actor') ) %>%
            dplyr::select(email_id,  crisno, sentence_number_int_aligned,  event_number_int,  variable, value) %>%
            filter(variable %in% c('sentence_events',
                                   'act_cooperative',
                                   'act_descalate', 
                                   'act_escalate',
                                   'act_uncooperative',
                                   'interact_decreasecoop',
                                   'interact_descalate',
                                   'interact_escalate',
                                   'interact_increasecoop',
                                   'thinkkind',
                                   'sayintkind'
                                   ) 
                        ) %>% distinct() %>% 
                  mutate(value= value %>% trimws() %>% tolower()) %>%
                  #left_join(full_tree %>% dplyr::select(Behavior, value=Leaf) %>% 
                  #            mutate(value= value %>% trimws() %>% tolower())) %>%
                  left_join(full_tree %>% dplyr::rename(value=Leaf)  %>%
                              mutate(value= value %>% trimws() %>% tolower()) ) %>%
              group_by(email_id,  crisno, sentence_number_int_aligned) %>%
                mutate(event_number_int_max=max(event_number_int, na.rm=T)) %>%
              ungroup() %>%
              full_join(
                actors_clean %>% dplyr::select(email_id,  crisno, sentence_number_int_aligned,  event_number_int,  contains('actor')) %>%
                  dplyr::select(-condition_do_actor_a_clean,-condition_do_actor_b_clean) #ignoring conditions for now
              )

#temp_long %>% dplyr::select(value, Behavior) %>% distinct() %>% View()

#i_think_actor_a=, #we're going to join on these
#i_say_actor_a=,
#i_say_actor_b=,
#i_do_actor_a=,
#i_do_actor_b=,

#Starting first with the 63% of the time they saw only 1 event
events_variable_value <- temp_long %>%
                                #filter(!is.na(Behavior )) %>%
                                #filter(event_number_int_max==1) %>%

                                mutate(index=paste(crisno , sentence_number_int_aligned ,  think_actor_a_clean,say_actor_a_clean,say_actor_b_clean,do_actor_a_clean,do_actor_b_clean, sep="_")) %>% #add actors to this
                                filter(!index %>% str_detect('_NA_NA_NA_NA_NA')) %>% #ignore 
                                dplyr::select(email_id,
                                              index, 
                                              #contains('actor'),
                                              Event_Count,
                                              Behavior,
                                              think_aggression,
                                              say_aggression,
                                              do_aggression,
                                              Do_Armed_Unarmed,
                                              do_Act_Interact,
                                              Think_Type_L0,
                                              Say_Type_L0,
                                              Do_Type_L0,
                                              Leaf_Simplified#,
                                              #variable,
                                              #value
                                              )

#This actually takes a while now that there are dead
library(fastDummies)
#I think we do physically have to go to wide
events_wide_i <- events_variable_value %>% 
                                       rename(i_email_id=email_id,
                                              i_Event_Count=Event_Count,
                                              i_Behavior=Behavior,
                                              i_think_aggression=think_aggression,
                                              i_say_aggression=say_aggression,
                                              i_do_aggression=do_aggression,
                                              i_Do_Armed_Unarmed=Do_Armed_Unarmed,
                                              i_do_Act_Interact=do_Act_Interact,
                                              i_Think_Type_L0=Think_Type_L0,
                                              i_Say_Type_L0=Say_Type_L0,
                                              i_Do_Type_L0=Do_Type_L0,
                                              i_Leaf_Simplified=Leaf_Simplified
                                              ) %>%
                                       #fastDummies::dummy_cols(select_columns='a_Event_Count', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Behavior', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_think_aggression', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_say_aggression', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_do_aggression', remove_selected_columns=T, ignore_na = T) %>%

                                       fastDummies::dummy_cols(select_columns='i_Do_Armed_Unarmed', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_do_Act_Interact', remove_selected_columns=T, ignore_na = T) %>%  
                                       fastDummies::dummy_cols(select_columns='i_Think_Type_L0', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Say_Type_L0', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Do_Type_L0', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Leaf_Simplified', remove_selected_columns=T, ignore_na = T) %>%
                                       group_by(i_email_id,index) %>%
                                        summarise_all(max, na.rm=T) %>% #max not sum
                                       ungroup() %>%
                                       mutate_if(is.numeric, function(x) ifelse(is.infinite(x), 0, x))
dim(events_wide_i) #113049    116
events_wide_j <- events_wide_i
names(events_wide_j) <- events_wide_j %>% names() %>% str_replace("^i_","j_")
dim(events_wide_j) #67558   106

#This is going to be a million?
diads_wide <-  events_wide_i %>%

               left_join(events_wide_j, by=c('index'='index') ) %>% 
               filter(i_email_id!=j_email_id) %>% 
               #rowwise() %>%
               mutate(ij_email_id= ifelse( i_email_id>=j_email_id,paste0(i_email_id,j_email_id),paste0(j_email_id,i_email_id) ) ) %>%
               mutate(index_ij_email_id=paste0(index,ij_email_id)) %>%
               filter(!duplicated(index_ij_email_id)) %>%
               arrange(index) %>%
               ungroup() %>%
               mutate_if(is.numeric, function(x) ifelse(is.infinite(x), 0, x))
dim(diads_wide) #204,781    213

variables <- setdiff( names(diads_wide) %>% str_replace("ij_|i_|j_","") %>% unique(), c('index_ij_email_id','email_id','index',"ij_email_id","index_ij_email_id","match_i_email_id","index_email_id"  ))
diads_wide <- as.data.frame(diads_wide)
for(q in variables){
  print(q)
  newvar <- paste0("match_",q)
  a_oldvar <- paste0("i_",q)
  b_oldvar <- paste0("j_",q)
  diads_wide[,newvar] <-  0 #default 0
  diads_wide[,newvar] <-  ifelse(diads_wide[,a_oldvar] %in% 1 &  diads_wide[,b_oldvar] %in% 1, 1,  diads_wide[,newvar])  #if both 1 then 1
  diads_wide[,newvar] <-  ifelse(diads_wide[,a_oldvar] %in% 0 &  diads_wide[,b_oldvar] %in% 0, NA, diads_wide[,newvar])  #if both 0 then NA
}

diads_matches <- diads_wide %>% 
                 dplyr::select(index_ij_email_id,  starts_with("match"))  %>%
                 dplyr::select(-ends_with("_NA"))

final_counts_numerator <- diads_matches %>% summarise_if(is.numeric, sum, na.rm=T)
final_counts_denominator <- diads_matches %>% summarise_if(is.numeric, ~sum(is.finite(.x)) )

final_scores <- final_counts_numerator / final_counts_denominator
#One takeaway is that because coders split on act vs interact is artificially drops the agreement

#New plan, we're going to pull out those dimensions seperately
#final_scores %>% round(2) %>% t()  %>% as.data.frame() %>%  tibble::rownames_to_column( "VALUE") %>% View()
options(warn=0)

final_scores_df <- data.frame(varname= names(final_scores),  final_scores=final_scores %>% round(2) %>% t(),final_counts_numerator=final_counts_numerator%>% t()) %>% filter(final_counts_numerator>1)
#final_scores_df %>% View() 
#cor(final_scores_df) #.64 correlation between agreement and how often its used

p_intercoder_agreement <- final_scores_df %>%
                                  mutate(grouping=NA) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Event_Count'), 'Event_Count' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('match_Behavior_'), 'Behavior' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('think_aggression'), 'Aggression (think)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('say_aggression_'), 'Aggression (say)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('do_aggression_'), 'Aggression (do)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Do_Armed_Unarmed'), 'Armed or Unarmed Agents' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('do_Act_Interact'), 'Action or Interaction' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Think_Type_L0'), 'Think (L0)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Say_Type_L0'), 'Say (L0)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Do_Type_L0'), 'Do (L0)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Leaf_Simplified'), 'Leaf Simplified' ,  grouping)) %>%
                                  mutate(grouping=grouping %>% factor(levels=c('Event_Count', 'Behavior','Aggression (think)','Aggression (say)','Aggression (do)',
                                                                               'Armed or Unarmed Agents','Action or Interaction',
                                                                               'Think (L0)','Say (L0)','Do (L0)','Leaf Simplified') %>% rev() ) ) %>%
                                  ggplot(aes(x=final_scores, y=grouping)) + 
                                  geom_boxplot() +
                                  xlab("Intercoder Agreemnt (Experts, positives only, Single Event Sentences)") +
                                  ylab("Psuedo Ontology Tree Depth")

```

```{r, eval=F}
p_intercoder_agreement
```

```{r}

library(dplyr, warn.conflicts = FALSE)
options(warn=-1)

icb_long_clean$email_id_expert <- icb_long_clean$email_id %>% str_detect("grad|postgrad")

#icb_long_clean %>% dplyr::select(variable) %>% distinct() %>% View()

temp_long <- icb_long_clean %>%
                      dplyr::select(email_id,  email_id_expert, crisno, sentence_number_int_aligned,  event_number_int,  variable, value) %>%
                      filter(variable %in% c('sentence_events',
                                             'act_cooperative',
                                             'act_descalate', 
                                             'act_escalate',
                                             'act_uncooperative',
                                             'interact_decreasecoop',
                                             'interact_descalate',
                                             'interact_escalate',
                                             'interact_increasecoop',
                                             'thinkkind',
                                             'sayintkind'
                                             ) 
                        ) %>% distinct() %>% 
                  mutate(value= value %>% trimws() %>% tolower()) %>%
                  #left_join(full_tree %>% dplyr::select(Behavior, value=Leaf) %>% 
                  #            mutate(value= value %>% trimws() %>% tolower())) %>%
                  left_join(full_tree %>% dplyr::rename(value=Leaf)  %>%
                              mutate(value= value %>% trimws() %>% tolower()) ) %>%
              group_by(email_id,  crisno, sentence_number_int_aligned) %>%
                mutate(event_number_int_max=max(event_number_int, na.rm=T)) %>%
              ungroup()

#temp_long %>% dplyr::select(value, Behavior) %>% distinct() %>% View()

#Starting first with the 63% of the time they saw only 1 event
events_variable_value <- temp_long %>%
                                #filter(!is.na(Behavior )) %>%
                                #filter(event_number_int_max==1) %>%

                                mutate(index=paste(crisno , sentence_number_int_aligned ,  event_number_int, sep="_")) %>%
                                dplyr::select(email_id, index, 
                                              Event_Count,
                                              Behavior,
                                              think_aggression,
                                              say_aggression,
                                              do_aggression,
                                              Do_Armed_Unarmed,
                                              do_Act_Interact,
                                              Think_Type_L0,
                                              Say_Type_L0,
                                              Do_Type_L0,
                                              Leaf_Simplified#,
                                              #variable,
                                              #value
                                              )

#This actually takes a while now that there are dead
library(fastDummies)
#I think we do physically have to go to wide
events_wide_a <- events_variable_value %>% 
                                       rename(a_email_id=email_id,
                                              a_Event_Count=Event_Count,
                                              a_Behavior=Behavior,
                                              a_think_aggression=think_aggression,
                                              a_say_aggression=say_aggression,
                                              a_do_aggression=do_aggression,
                                              a_Do_Armed_Unarmed=Do_Armed_Unarmed,
                                              a_do_Act_Interact=do_Act_Interact,
                                              a_Think_Type_L0=Think_Type_L0,
                                              a_Say_Type_L0=Say_Type_L0,
                                              a_Do_Type_L0=Do_Type_L0,
                                              a_Leaf_Simplified=Leaf_Simplified
                                              ) %>%
                                       fastDummies::dummy_cols(select_columns='a_Event_Count', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_Behavior', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_think_aggression', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_say_aggression', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_do_aggression', remove_selected_columns=T) %>%

                                       fastDummies::dummy_cols(select_columns='a_Do_Armed_Unarmed', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_do_Act_Interact', remove_selected_columns=T) %>%  
                                       fastDummies::dummy_cols(select_columns='a_Think_Type_L0', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_Say_Type_L0', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_Do_Type_L0', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='a_Leaf_Simplified', remove_selected_columns=T) %>%
                                       group_by(a_email_id,index) %>%
                                       summarise_all(max, na.rm=T) %>% #max not sum
                                       ungroup()
dim(events_wide_a) #12368   159

events_wide_b <- events_variable_value %>% 
                                       rename(b_email_id=email_id,
                                              b_Event_Count=Event_Count,
                                              b_Behavior=Behavior,
                                              b_think_aggression=think_aggression,
                                              b_say_aggression=say_aggression,
                                              b_do_aggression=do_aggression,
                                              b_Do_Armed_Unarmed=Do_Armed_Unarmed,
                                              b_do_Act_Interact=do_Act_Interact,
                                              b_Think_Type_L0=Think_Type_L0,
                                              b_Say_Type_L0=Say_Type_L0,
                                              b_Do_Type_L0=Do_Type_L0,
                                              b_Leaf_Simplified=Leaf_Simplified
                                              ) %>%
                                       fastDummies::dummy_cols(select_columns='b_Event_Count', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_Behavior', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_think_aggression', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_say_aggression', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_do_aggression', remove_selected_columns=T) %>%

                                       fastDummies::dummy_cols(select_columns='b_Do_Armed_Unarmed', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_do_Act_Interact', remove_selected_columns=T) %>%  
                                       fastDummies::dummy_cols(select_columns='b_Think_Type_L0', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_Say_Type_L0', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_Do_Type_L0', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='b_Leaf_Simplified', remove_selected_columns=T) %>%
                                       group_by(b_email_id,index) %>%
                                       summarise_all(max, na.rm=T) %>% #max not sum
                                       ungroup()
dim(events_wide_b) #12368   159

diads_wide <-  events_wide_a %>%
               left_join(events_wide_b, by=c('index'='index') ) %>% 
               filter(a_email_id!=b_email_id) %>% 
               #rowwise() %>%
               mutate(ab_email_id= ifelse( a_email_id>=b_email_id,paste0(a_email_id,b_email_id),paste0(b_email_id,a_email_id) ) ) %>%
               mutate(index_ab_email_id=paste0(index,ab_email_id)) %>%
               filter(!duplicated(index_ab_email_id)) %>%
               arrange(index) %>%
               ungroup() %>%
               mutate_if(is.numeric, function(x) ifelse(is.infinite(x), 0, x))

variables <- setdiff( names(diads_wide) %>% str_replace("a_|b_","") %>% unique(), c('index_ab_email_id','email_id','index','aemail_id','index_aemail_id'))
diads_wide <- as.data.frame(diads_wide)
for(q in variables){
  print(q)
  newvar <- paste0("match_",q)
  a_oldvar <- paste0("a_",q)
  b_oldvar <- paste0("b_",q)
  diads_wide[,newvar] <-  0 #default 0
  diads_wide[,newvar] <-  ifelse(diads_wide[,a_oldvar] %in% 1 &  diads_wide[,b_oldvar] %in% 1, 1,  diads_wide[,newvar])  #if both 1 then 1
  diads_wide[,newvar] <-  ifelse(diads_wide[,a_oldvar] %in% 0 &  diads_wide[,b_oldvar] %in% 0, NA, diads_wide[,newvar])  #if both 0 then NA
}

diads_matches <- diads_wide %>% 
                 dplyr::select(index_ab_email_id,  starts_with("match"))  %>%
                 dplyr::select(-ends_with("_NA"))

final_counts_numerator <- diads_matches %>% summarise_if(is.numeric, sum, na.rm=T)
final_counts_denominator <- diads_matches %>% summarise_if(is.numeric, ~sum(is.finite(.x)) )

final_scores <- final_counts_numerator / final_counts_denominator
#One takeaway is that because coders split on act vs interact is artificially drops the agreement

#New plan, we're going to pull out those dimensions seperately
#final_scores %>% round(2) %>% t()  %>% as.data.frame() %>%  tibble::rownames_to_column( "VALUE") %>% View()
options(warn=0)

final_scores_df_novices <- data.frame(varname= names(final_scores),  final_scores=final_scores %>% round(2) %>% t(),final_counts_numerator=final_counts_numerator%>% t()) %>% filter(final_counts_numerator>1)
#final_scores_df %>% View() 
#cor(final_scores_df) #.64 correlation between agreement and how often its used

p_intercoder_agreement_novice <- final_scores_df_novices %>%
  mutate(grouping=NA) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Event_Count'), 'Event_Count' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('match_Behavior_'), 'Behavior' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('think_aggression'), 'Aggression (think)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('say_aggression_'), 'Aggression (say)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('do_aggression_'), 'Aggression (do)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Do_Armed_Unarmed'), 'Armed or Unarmed Agents' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('do_Act_Interact'), 'Action or Interaction' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Think_Type_L0'), 'Think (L0)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Say_Type_L0'), 'Say (L0)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Do_Type_L0'), 'Do (L0)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Leaf_Simplified'), 'Leaf Simplified' ,  grouping)) %>%
  mutate(grouping=grouping %>% factor(levels=c('Event_Count', 'Behavior','Aggression (think)','Aggression (say)','Aggression (do)',
                                               'Armed or Unarmed Agents','Action or Interaction',
                                               'Think (L0)','Say (L0)','Do (L0)','Leaf Simplified') %>% rev() ) ) %>%
  ggplot(aes(x=final_scores, y=grouping)) + 
  geom_boxplot() +
  xlab("Intercoder Agreemnt (Experts, positives only, Single Event Sentences)") +
  ylab("Psuedo Ontology Tree Depth")

```

```{r}

p_intercoder_agreement_both <- bind_rows(
  final_scores_df_novices %>% mutate(coder="novices") ,
  final_scores_df_experts %>% mutate(coder="experts") 
) %>%
  mutate(coder = coder %>% factor(levels=c('novices','experts')  )) %>%
  mutate(grouping=NA) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Event_Count'), 'Event_Count' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('match_Behavior_'), 'Behavior' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('think_aggression'), 'Aggression (think)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('say_aggression_'), 'Aggression (say)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('do_aggression_'), 'Aggression (do)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Do_Armed_Unarmed'), 'Armed or Unarmed Agents' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('do_Act_Interact'), 'Action or Interaction' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Think_Type_L0'), 'Think (L0)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Say_Type_L0'), 'Say (L0)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Do_Type_L0'), 'Do (L0)' ,  grouping)) %>%
  mutate(grouping=ifelse(varname %>% str_detect('Leaf_Simplified'), 'Leaf Simplified' ,  grouping)) %>%
  mutate(grouping=grouping %>% factor(levels=c('Event_Count', 'Behavior','Aggression (think)','Aggression (say)','Aggression (do)',
                                               'Armed or Unarmed Agents','Action or Interaction',
                                               'Think (L0)','Say (L0)','Do (L0)','Leaf Simplified') %>% rev() ) ) %>%
  ggplot(aes(x=final_scores, y=grouping, color=coder)) + 
  geom_boxplot() +
  ggtitle("Intercoder Agreement") +
  xlab("Probability Others Assigned Tag Given Anyone Did") +
  ylab("Psuedo Ontology Tree Depth")

p_intercoder_agreement_both

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_InternalValidity.Rmd
Init

---
title: "InternalMeasurementValidity.Rmd"
output: html_document
---

```{r}
library(flextable)
library(tidyverse)

```

```{r, echo=FALSE}

icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds"))
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))

```

```{r echo=FALSE, include=T, eval=T}

library(janitor)
#table(icb_wide_clean$email_id )
icb_wide_clean$email_id_expert <- icb_wide_clean$email_id %>% str_detect("grad|postgrad")

#icb_wide_clean$email_id_expert 
#icb_wide_clean$raterconfidence
#icb_wide_clean$raterconfidence_reason

icb_wide_clean %>% 
  tabyl(email_id_expert, raterconfidence, show_na = FALSE) %>%
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns()

icb_wide_clean  %>%
    mutate(raterconfidence_reason = raterconfidence_reason %>% str_replace_all("other|;","") %>% trimws() ) %>%
    filter(raterconfidence_reason!='')  %>%
    tabyl(raterconfidence_reason, show_na = FALSE) %>%
    arrange(desc(n)) %>%
    head() %>%
    mutate(percent=percent %>% round(2))

icb_long_clean$email_id_expert <- icb_long_clean$email_id %>% str_detect("grad|postgrad")

temp <- icb_long_clean %>%
        dplyr::select(email_id, email_id_expert, crisno, sentence_number_int_aligned, variable, value) %>%
        filter(!variable %in% c('date','say_actor_a','say_actor_b','do_actor_a','do_actor_b','think_actor_a','think_sentence_events','do_timing_reorder','sayintkind_react','do_timing_reorder',
                                'coder_crisis_order','point_in_time','start_time','end_time','earliest_date','preceding_event',
                                'act_cooperative','act_descalate act_escalate', 'act_uncooperative', 'interact_decreasecoop', 'interact_descalate', 'interact_escalate', 'interact_increasecoop',
                                'act_descalate','act_escalate','thinkkind','act_descalate','act_escalate','raterconfidence_reason_survey','raterconfidence_reason') &
                 !variable %>% str_detect("condition|actor|location_other|date|time")
               )

var_names <- temp %>% pull(variable) %>% unique()
library(fastDummies)
temp_wide <- temp %>% mutate(variable_value=paste0(variable,";",value)) %>% dplyr::select(-variable,-value) %>% dummy_cols(select_columns='variable_value', remove_selected_columns=T) 
dim(temp_wide)

temp_mean_expert <- temp_wide %>%
                    group_by(email_id_expert,email_id,crisno,sentence_number_int_aligned) %>% #max for that person across all events they found
                    summarise_if(is.numeric, max) %>%
                    dplyr::select(-email_id) %>%
                    group_by(email_id_expert,crisno,sentence_number_int_aligned) %>% #max for that person across all events they found
                    summarise_if(is.numeric, mean) %>%
                    ungroup()

temp_mean_expert_lomg <- temp_mean_expert %>%
                          filter(email_id_expert==T) %>%
                          ungroup() %>%
                          dplyr::select(-email_id_expert) %>% #,-email_id
                          pivot_longer(cols=-c(crisno,sentence_number_int_aligned)) %>%
                          mutate(value= abs(value-0.5)*2) %>% #0 means completely disagree 1 means completely agree
                          group_by(name) %>%
                          summarise(value=mean(value))

#only positives
temp_mean_expert_lomg_onlypos <- temp_mean_expert %>%
                                filter(email_id_expert==T) %>%
                                ungroup() %>%
                                dplyr::select(-email_id_expert) %>%
                                pivot_longer(cols=-c(crisno,sentence_number_int_aligned)) %>%
                                filter(value>0) %>% #only consider agreement when at least one coder uses the tag in that sentence
                                mutate(value= abs(value-0.5)*2) %>% #0 means completely disagree 1 means completely agree
                                rename(agreement=value) %>%
                                separate(name, c("variable", "value"), ";" ) %>%
                                group_by(variable) %>%
                                mutate(agreement_a=mean(agreement)) %>%
                                group_by(variable,value) %>%
                                mutate(agreement_b=mean(agreement)) %>%
                                ungroup() %>%
                                dplyr::select(-crisno, -sentence_number_int_aligned, -agreement) %>%
                                distinct()

#Confidence
temp2_confidence <- icb_long_clean %>%
                      dplyr::select(email_id, email_id_expert, crisno, sentence_number_int_aligned, raterconfidence, variable, value) %>%
                      filter(email_id_expert==T) %>%
                      filter(!variable %in% c('date','say_actor_a','say_actor_b','do_actor_a','do_actor_b','think_actor_a','think_sentence_events','do_timing_reorder','sayintkind_react','do_timing_reorder',
                                              'coder_crisis_order','point_in_time','start_time','end_time','earliest_date','preceding_event',
                                              'act_cooperative','act_descalate act_escalate', 'act_uncooperative', 'interact_decreasecoop', 'interact_descalate', 'interact_escalate', 'interact_increasecoop',
                                              'act_descalate','act_escalate','thinkkind','act_descalate','act_escalate','raterconfidence_reason_survey','raterconfidence_reason') &
                               !variable %>% str_detect("condition|actor|location_other|date|time")
                             ) %>%
                      mutate(raterconfidence=factor(raterconfidence, levels=c('None', 'Low', 'High',  'Complete') )) %>% 
                      group_by(variable) %>%
                      mutate(raterconfidence_a=raterconfidence %>% as.numeric() %>% mean(na.rm=T) %>% round(2)) %>%
                      group_by(variable, value) %>%
                      mutate(raterconfidence_b=raterconfidence %>% as.numeric() %>% mean(na.rm=T) %>% round(2)) %>%
                      ungroup() %>%
                      dplyr::select(-email_id, -email_id_expert, -crisno, -sentence_number_int_aligned, -raterconfidence) %>%
                      distinct()

```

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}

intercoder_agreement_and_confidence_by_item <- temp_mean_expert_lomg_onlypos %>% 
                                                mutate(variable=variable %>% str_replace_all("variable_value_|clean",""))  %>%
                                                mutate(variable=variable %>% str_replace_all("_",""))  %>%
                                                left_join(temp2_confidence %>% 
                                                                  mutate(variable=variable %>% str_replace_all("variable_value_|clean",""))  %>%
                                                                  mutate(variable=variable %>% str_replace_all("_","")) 
                                                          ) %>%
                                                dplyr::arrange(desc(agreement_a), desc(agreement_b)) %>%
                                                mutate(agreement_a=agreement_a %>% round(3)) %>% 
                                                mutate(agreement_b=agreement_b %>% round(3))

temp2 <- 
intercoder_agreement_and_confidence_by_item %>%
  mutate(variable= paste0(variable, ' (', round(agreement_a*100,0),'%)'  )) %>% #round(raterconfidence_a,2)
  mutate(value= paste0(value, ' (', round(agreement_b*100,0),'%)'  )) %>% #,round(raterconfidence_b,2),  
  arrange(agreement_a %>% desc(),agreement_b %>% desc()) %>%
  group_by(agreement_a,variable) %>%
  summarise(value=paste0(value,collapse=", ")) %>%
  arrange(agreement_a %>% desc() ) %>%
  ungroup() %>%
  dplyr::select(-agreement_a) %>%
  mutate(variable=variable %>% str_replace("dointeractkind","Interaction")) %>%
  mutate(variable=variable %>% str_replace("interactdomains","Domain")) %>%
  mutate(variable=variable %>% str_replace("actuncooperative","Act-Uncooperative")) %>%
  mutate(variable=variable %>% str_replace("sayintkind","Speech")) %>%
  mutate(variable=variable %>% str_replace("actcooperative","Act-cooperative")) %>%
  mutate(variable=variable %>% str_replace("dokind","Act")) %>%
  mutate(variable=variable %>% str_replace("consequence","Consequence")) %>%
  mutate(variable=variable %>% str_replace("interactunits","Units")) %>%
  mutate(variable=variable %>% str_replace("interactincreasecoop","Interaction-Cooperative")) %>%
  mutate(variable=variable %>% str_replace("interactlocation","Location")) %>%
  mutate(variable=variable %>% str_replace("interactescalate"    ,"Interaction-Escalate")) %>%
  mutate(variable=variable %>% str_replace("dotiming","Timing")) %>%
  mutate(variable=variable %>% str_replace("interactterritory","Territory")) %>%
  mutate(variable=variable %>% str_replace("interactgeoscope","Geographic Scope")) %>%
  mutate(variable=variable %>% str_replace("interactdecreasecoop","Interaction-Uncooperative")) %>%
  mutate(variable=variable %>% str_replace("interactdescalate","Interaction-Deescalate")) %>%
  mutate(variable=variable %>% str_replace("doduration","Duration")) %>%
  mutate(variable=variable %>% str_replace("actescalate","Act-Escalate")) %>%
  mutate(variable=variable %>% str_replace("interactfatalities","Fatalities")) %>%
  mutate(variable=variable %>% str_replace("interactforces","Forces")) %>%
  mutate(variable=variable %>% str_replace("actdescalate"   ,"Act-Deescalate"))

temp2 %>%
  flextable::flextable() %>%
  flextable::bg( i = which( 1:nrow(temp2) %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
  #merge_v(part = "body") %>% 
  #flextable::width( j = 1, width=7) %>%
  flextable::fontsize(size = 8, part = "body") %>%
  #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
  flextable::padding(padding = 0, part = "body")  %>%
  flextable::merge_v(part = "body", combine = FALSE) %>%
  flextable::width( j = 1, width=1)    %>%
  flextable::width( j = 2, width=6)

# intercoder_agreement_and_confidence_by_item %>%
#                   flextable::flextable() %>%
#                   flextable::bg( i = which( 1:nrow(temp_mean_expert_lomg_onlypos) %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
#                   #merge_v(part = "body") %>% 
#                   #flextable::width( j = 1, width=7) %>%
#                   flextable::fontsize(size = 6, part = "body") %>%
#                   #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
#                   flextable::padding(padding = 0, part = "body")  %>%
#                   flextable::merge_v(part = "body", combine = FALSE)

#Note Average intercoder agreement and self reported confidence look uncorrelated at the item level. I think it's because they're correlated at the sentence level, not the item level.
p_item_confidence_vs_agreement <- 
  intercoder_agreement_and_confidence_by_item %>%
  ggplot(aes(x=raterconfidence_b  ,y=agreement_b )) +
  geom_point() +
  geom_quantile(method = "rqss")

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
Init

---
title: 'Intercoder Agreement'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

# Intro

## Library Loads

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

```

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds"))

codings_long <- readRDS(paste0(here::here(), '/data_out/codings_long.Rds'))
codings_long_agreement <- readRDS( paste0(here::here(), '/data_out/codings_long_agreement.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/data_out/codings_long_agreed.Rds'))
codings_wide_agreed <- readRDS( paste0(here::here(), '/data_out/codings_wide_agreed.Rds'))

```

Self Reported Confidence and Percent Agreement

```{r}

confidence_totals <- bind_rows(
  icb_long_clean %>% filter(email_id %>% str_detect('expert') & variable_normalized=='raterconfidence' ) %>% count(value_normalized) %>% mutate(coder="expert") %>% mutate(n= (n/sum(n)*100) %>% round(1) %>% paste0("%") ),
  icb_long_clean %>% filter(email_id %>% str_detect('undergrad') & variable_normalized=='raterconfidence' ) %>% count(value_normalized)  %>% mutate(coder="undergrad") %>% mutate(n=(n/sum(n)*100) %>% round(1) %>% paste0("%"))
) %>%
  mutate(confidence=value_normalized %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
  mutate(x=0.05)

c1 <- codings_long_agreement  %>% filter(keep==T) %>% dplyr::select(selected_by_perc=selected_by_any_perc,confidence=confidence)  %>% mutate(name="Accepted_Either")
c2 <- codings_long_agreement %>% dplyr::select(selected_by_perc=selected_by_any_perc,confidence=confidence) %>% mutate(name="Accepted_Either")
c3 <- codings_long_agreement %>% dplyr::select(selected_by_perc=selected_by_experts_perc,confidence=confidence_expert) %>% mutate(name="Experts")
c4 <- codings_long_agreement %>% dplyr::select(selected_by_perc=selected_by_undergrads_perc,confidence=confidence_undergrad) %>% mutate(name="Undergraduates")
bind_rows(c1,c2,c3,c4) %>% na.omit() %>%
  ggplot(aes(x=confidence, y=selected_by_perc, color=name)) + geom_smooth() #geom_point()

library(ggExtra)
p1_confidence_agreement <-   codings_long_agreement %>% #codings_long %>%  codings_long_agreement
    mutate(confidence=confidence %>% round() %>% as.factor() ) %>%
    filter(value_normalized!='') %>%
    filter(total_coders>1) %>% #about 9k only had one coder
    filter(selected_by_experts>=1) %>%
    dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc,keep,confidence) %>%
    group_by(confidence) %>%
    summarise(
        Accepted_Either=selected_by_any_perc[keep==1] %>% mean(na.rm=T), 
        Either=selected_by_any_perc %>% mean(na.rm=T), 
        Experts=selected_by_experts_perc %>% mean(na.rm=T), 
        Undergraduates=selected_by_undergrads_perc %>% mean(na.rm=T)
    ) %>%
    filter(!is.na(confidence)) %>%
    #mutate(variable_normalized=fct_reorder(variable_normalized, Either)) %>%
    pivot_longer(c(-confidence)) %>%
    ggplot(aes(x=selected_by_any_perc, y=confidence)) + 
    #geom_boxplot() + 
    geom_point(aes(x=value, color=name )) +
    xlab("Percent of Coders") +
    ylab("Confidence") +
    labs(title = "Percent of Coders who Chose a Tag by Confidence and Type of Coder"#,
          #subtitle = "Plot of length by dose",
          #caption = "Data source: ToothGrowth"
         ) + 
    theme_bw()
p1_confidence_agreement + theme(legend.position="bottom")

```

```{r}

#Calculate average agreements by group
means1 <- codings_long_agreement %>% 
              filter(value_normalized!='') %>%
              filter(total_coders>1) %>% #about 9k only had one coder
              #filter(selected_by_experts>=1) %>%
              dplyr::select(All=selected_by_any_perc,Experts=selected_by_experts_perc,Undergraduates=selected_by_undergrads_perc) %>% summarise_all(mean, na.rm=T)
means1_keep <- codings_long_agreement %>% 
      filter(value_normalized!='') %>%
    filter(total_coders>1) %>% #about 9k only had one coder
    #filter(selected_by_experts>=1) %>%
  filter(keep==1) %>% dplyr::select(Accepted=selected_by_any_perc) %>% summarise_all(mean, na.rm=T)
meansall <- bind_rows(means1,means1_keep) %>% mutate(x=1) %>% pivot_longer(cols=c(-x)) %>% na.omit()

#These are all by definition chosen by at least 1
#Do we further require at least 1 expert as with our aggregations?
p_percent_chose_tag_by_concept <- 
  codings_long_agreement %>% #codings_long %>%  codings_long_agreement
    mutate(variable_normalized=variable_normalized %>% str_replace_all("_"," ") %>% tolower() ) %>%
    filter(value_normalized!='') %>%
    filter(total_coders>1) %>% #about 9k only had one coder
    #filter(selected_by_experts>=1) %>%
    dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc,keep) %>%
    group_by(variable_normalized) %>%
      summarise(
          N=n(),
          Accepted=selected_by_any_perc[keep==1] %>% mean(na.rm=T), 
          All=selected_by_any_perc %>% mean(na.rm=T), 
          Experts=selected_by_experts_perc %>% mean(na.rm=T), 
          Undergraduates=selected_by_undergrads_perc %>% mean(na.rm=T)
      ) %>%
    filter(N>10) %>%
    dplyr::select(-N) %>%
    mutate(variable_normalized=fct_reorder(variable_normalized, Accepted)) %>%
    pivot_longer(c(-variable_normalized)) %>%
    ggplot(aes(x=selected_by_any_perc, y=variable_normalized)) + 
    #geom_boxplot() + 
    geom_point(aes(x=value, color=name )) +
    xlab("Percent of Coders that selected Tag") +
    ylab("") +
    labs(
      # title = "Intercoder Agreement by Concept/Type",
      # subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
          caption = paste0("Point = mean by concept; Line = mean by group\nUnit of Analysis: Tag chosen by any Coder, N=", codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma(), "; Accepted Tokens=", codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()),
         color = "Codings"
         ) + 
    theme_bw() +
    theme(legend.position="bottom") +
    geom_vline(data=meansall, aes(xintercept = value, color = name), linetype="solid", size=1, alpha=0.5)

```

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

p_percent_chose_tag_by_concept %>% saveRDS(paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.Rds'))
p_percent_chose_tag_by_concept

ggplot2::ggsave(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.png'), 
                plot = p_percent_chose_tag_by_concept, width=8, height=6)
#table(expert_majority=codings_long$expert_majority,
#      undergrad_majority=codings_long$undergrad_majority)

#58% of tokens including null have agreement from either experts, undergrads, or both
#(table(expert_majority=codings_long$expert_majority,
#      undergrad_majority=codings_long$undergrad_majority) / nrow(codings_long) ) %>% round(2)

#table(codings_long$value_normalized != "")
# FALSE   TRUE 
#480,239 408,126 #about the same number of null tokens as non null ones
```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_TableExampleSentenceCoding.Rmd
Init

---
title: "Example Sentence Coding"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(igraph)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
sentence_example_sheet <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
                                                    sheet="Sentence Tree Example Table")

```

```{r, echo=FALSE, results='asis', include=T, cache=F, ft.arraystretch=1}

sentence="'A crisis began for the Soviet Union, when the United States threatened to invade Cuba unless nuclear weapons were removed from its soil.'"

set_flextable_defaults(fonts_ignore=TRUE)

full_tree_ft <- sentence_example_sheet %>%
      flextable::flextable() %>%
      add_header( "x1"=sentence,
                  "x2"=sentence,
                  "x3"=sentence,
                  #"x7"=sentence,
                  #"x8"=sentence,
                  #"x9"=sentence,
                  #"x10"=sentence,
                  top = TRUE ) %>%
      merge_h(part = "header") %>%
      flextable::width( j = 1, width=1) %>%
      flextable::fontsize(size = 7, part = "body") %>%
      merge_v( j = 1,  part = "body", combine = T) %>%
      #flextable::width( j = 1, width=.11) %>%
      flextable::width( j = 2, width=1.5) %>%
      flextable::width( j = 3, width=4) %>%
      valign(j = 1, valign = "top", part = "body") %>%
      flextable::line_spacing( space = 1, part = "body") #%>% #i=1:nrow(lit_review_alt),
      #flextable::padding(padding = 0, part = "body")

full_tree_ft

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_TableSentenceExamples.Rmd
Init

---
title: "Table Sentences"
output: html_document
---

# Convert codings to sentences

```{r}

#names(codings_wide_agreed)
library(tidyverse)
library(flextable)
library(ftExtra)
library(glue)

codings_long_agreement <- readRDS( paste0(here::here(), "ICBEdataset/data_out/codings_long_agreement.Rds")) 
codings_long_agreement_1_3 <- codings_long_agreement %>% filter(crisno==1 & sentence_number_int_aligned==3)
codings_long_agreement_2_11 <- codings_long_agreement %>% filter(crisno==2 & sentence_number_int_aligned==11)
codings_long_agreement_252_5 <- codings_long_agreement %>% filter(crisno==253 & sentence_number_int_aligned==5)
codings_long_agreement_209_3 <- codings_long_agreement %>% filter(crisno==209 & sentence_number_int_aligned==3)
codings_long_agreement_265_28 <- codings_long_agreement %>% filter(crisno==265 & sentence_number_int_aligned==28) #
codings_long_agreement_457_4 <- codings_long_agreement %>% filter(crisno==457 & sentence_number_int_aligned==4) #
codings_long_agreement_384_43 <- codings_long_agreement %>% filter(crisno==384 & sentence_number_int_aligned==43) #

#You have to rerun the embeddings too
codings_wide_agreed_embeded <- readRDS( paste0(here::here(), "ICBEdataset/data_out/codings_wide_agreed_embeded.Rds")) 
codings_wide_agreed_embeded_2_11 <- codings_wide_agreed_embeded %>% filter(crisno==2 & sentence_number_int_aligned==11)
codings_wide_agreed_embeded_265_28 <- codings_wide_agreed_embeded %>% filter(crisno==265 & sentence_number_int_aligned==28) #behavior is missing for one of them, do we want to call that degenerate?
codings_wide_agreed_embeded_384_43 <- codings_wide_agreed_embeded %>% filter(crisno==384 & sentence_number_int_aligned==43) #behavior is missing for one of them, do we want to call that degenerate?

codings_wide_agreed_embeded_stratified_sample  <- codings_wide_agreed_embeded %>% 
                                                  mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
                                                  dplyr::group_by(UMAP1_round,UMAP2_round) %>%
                                                  arrange(UMAP1,UMAP2) %>%
                                                  filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] )

#https://github.com/tidyverse/glue/issues/42
#On why you have to include parent frame https://github.com/tidyverse/glue/issues/42
glue_rex <- function(x) glue(x, .open = "{|",.close = "|}", .envir = parent.frame()) #escape variables in the more complicated {||} syntax
events <- NULL
event_to_sentence_rex <- function(events){

  sentence <- paste0("'",events[1,]$sentence,"'")
  df_temp <- NULL
  df_temp <- data.frame(
      type = c('E1','E2','E3','E4','E5','E6','E7','E8'), 
      text = c(NA,NA,NA,NA,NA,NA,NA,NA)
      )

  #debug

  #events %>% janitor::remove_empty() %>% t() %>% View()
  for(j in 1:nrow(events)){
    print(j)
    e1 <- NULL
    e1 <- events[j,, drop=F]
    #Replace the q codes with names
    crisis_actors <- dictionary_actors_labels %>% filter(crisno==e1$crisno)
    crisis_actors_set <- crisis_actors$value_normalized_label
    names(crisis_actors_set) <- crisis_actors$value_normalized

    e1$say_actor_a <- crisis_actors_set[e1$say_actor_a %>% str_split(";") %>% unlist()]  %>% na.omit() %>% paste0(collapse=";")
    e1$say_actor_b <- crisis_actors_set[e1$say_actor_b %>% str_split(";") %>% unlist()] %>% na.omit() %>% paste0(collapse=";")
    e1$do_actor_a <- crisis_actors_set[e1$do_actor_a %>% str_split(";") %>% unlist()] %>% na.omit() %>% paste0(collapse=";")
    e1$do_actor_b <- crisis_actors_set[e1$do_actor_b %>% str_split(";") %>% unlist()] %>% na.omit() %>% paste0(collapse=";")
    e1$think_actor_a <- crisis_actors_set[e1$think_actor_a %>% str_split(";") %>% unlist()] %>% na.omit() %>% paste0(collapse=";")
    e1[e1==''] <- NA #

    think=NA
    think=glue_rex("[{|e1$think_actor_a|}]{.underline text.color='black'} experienced a 
                    [{|e1$leaf_think_original|}]{.underline text.color='black'} about 
                    [{|e1$think_sentence_events|}]{.underline text.color='black'}.")

    say=NA
    say= glue_rex("[{|e1$say_actor_a|}]{.underline text.color='black'} initiated
                  [{|e1$leaf_say_original|}]{.underline text.color='black'} toward  
                  [{|e1$say_actor_b|}]{.underline text.color='black'}.")

    consequence=NA
    consequence=ifelse(
      e1$consequence %in% "will happen",
      glue_rex("That the following will [happen]{.underline text.color='black'}.") ,
      consequence
    )
    consequence=ifelse(
      e1$consequence %in% "won't happen",
      glue_rex("That if the following [won't happen]{.underline text.color='black'}.") ,
      consequence
    )

    condition=NA
    condition=ifelse(
      e1$condition %in% "happens",
      glue_rex("If the following [happens]{.underline text.color='black'}.") ,
      condition
    )
    condition=ifelse(
      e1$condition %in% "does not happen",
      glue_rex("If the following [does not happen]{.underline text.color='black'}.") ,
      condition
    )

    do=NA
    do=ifelse(
      !is.na(e1$do_actor_b) & e1$event_number_int_condition %in% 0,
      glue_rex("[{|e1$do_actor_a|}]{.underline text.color='black'} 
                initiated 
                [{|e1$leaf_do_original|}]{.underline text.color='black'}
                toward 
                [{|e1$do_actor_b|}]{.underline text.color='black'}." ) ,
      do
    )
    #in a way that was [{|ifelse(e1$do_aggression=='more aggression','escalatory/uncooperative ', 'de-escalatory/cooperative')|}]{.underline text.color='black'}
    do=ifelse(
      is.na(e1$do_actor_b) & e1$event_number_int_condition %in% 0,
      glue_rex("[{|e1$do_actor_a|}]{.underline text.color='black'} 
                initiated 
                [{|e1$leaf_do_original|}]{.underline text.color='black'}." ) ,
      do
    )

    do=ifelse(
      !is.na(e1$do_actor_b) & e1$event_number_int_condition %in% 1,
      glue_rex("(Condition) [{|e1$do_actor_a|}]{.underline text.color='black'} 
                initiated
                [{|e1$leaf_do_original|}]{.underline text.color='black'} [{|e1$do_actor_b|}]{.underline text.color='black'}.") ,
      do
    )
    do=ifelse(
      is.na(e1$do_actor_b) & e1$event_number_int_condition %in% 1,
      glue_rex("(Condition) [{|e1$do_actor_a|}]{.underline text.color='black'} 
                initiated
                [{|e1$leaf_do_original|}]{.underline text.color='black'}.")  ,
      do
    )

    #There should be 6! possibilities
    is.na(leaf_say_original) & is.na(leaf_do_original) & is.na(leaf_think_original)

    final_coding=NA
    final_coding = ifelse(e1$behavior %>% is.na(), glue_rex("No events."), final_coding )
    final_coding = ifelse(e1$behavior %in% "think",glue_rex("{|think|}"),final_coding)
    final_coding = ifelse(e1$behavior %in% "say",glue_rex("{|say|}"),final_coding)
    final_coding = ifelse(e1$behavior %in% "do;think",glue_rex("{|think|} {|do|}"),final_coding)

    final_coding = ifelse(e1$behavior %in% "say;think",glue_rex("{|think|} {|say|}"),final_coding)
    final_coding = ifelse(e1$behavior %in% "do;say;think",glue_rex("{|think|} {|say|} {|do|}"),final_coding)

    final_coding = ifelse(e1$behavior %in% "do",glue_rex("{|do|}"),final_coding)
    final_coding = ifelse(e1$behavior %in% "do;say",glue_rex("{|say|} {|do|}"),final_coding)
    final_coding = ifelse(e1$behavior %in% "do;say" & !is.na(consequence),glue_rex("{|say|} {|consequence|} {|do|}"),final_coding)
    final_coding = ifelse(e1$behavior %in% "do;say" & !is.na(consequence) & !is.na(condition),glue_rex("{|say|} {|consequence|} {|do|} {|condition|}"),final_coding)

    if(length(final_coding)>0){
     df_temp$text[j] <- final_coding
    } else {next}
    #print(df_temp)
  }
  #print(df_temp)
  df_collapsed <- df_temp %>% mutate(text=text %>% as.character() )  %>% na.omit() %>% dplyr::select(text) %>% summarise(events=text %>% paste( collapse="\n"))
  df_collapsed$sentence <- sentence
  df_collapsed <- df_collapsed %>% dplyr::select(sentence, events)
  return(df_collapsed)
}

#df_final <- NA
#keep_crisis=447
#keep_sentence=14
#events <- codings_wide_agreed_embeded  %>% dplyr::filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  #%>% janitor::remove_empty()  #don't remove empties or it'll destroy comparisons
#asdfasdf <- event_to_sentence_rex(events1)

#asdfasdf %>%
#  dplyr::select(-type) %>%
#  na.omit() %>%
#  as_flextable() %>%
#  colformat_md() %>% 
#  width(width = 8)

event_lists <- list()
cases <- codings_wide_agreed_embeded_stratified_sample %>% ungroup() %>% dplyr::select(crisno,sentence_number_int_aligned) %>% distinct()
for(i in 1:nrow(cases)){
    print(i)
    events <- NULL
    events <- codings_wide_agreed_embeded_stratified_sample %>% filter(crisno==cases[i,]$crisno & sentence_number_int_aligned==cases[i,]$sentence_number_int_aligned)
    event_lists[[as.character(i)]] <- event_to_sentence_rex(events)
    event_lists[[as.character(i)]]$ID=paste0(cases[i,]$crisno,'.',sentence_number_int_aligned=cases[i,]$sentence_number_int_aligned)
}

events_df <- bind_rows(event_lists) %>%
  filter(!events %in% "No events.")
events_ft <- events_df %>%
              dplyr::select(ID, sentence, events)  %>%
              #dplyr::select(-type) %>%
              na.omit() %>%
              as_flextable() %>%
              colformat_md() %>% 
              flextable::fontsize(size = 7, part = "all") %>%
              flextable::bg( i = which( 1:nrow(events_df) %% 2 == 1)  , j=1:ncol(events_df), part = "body", bg = "#EFEFEF") %>%
              flextable::width(j = 1, width=0.3, unit = "in") %>%
              flextable::width(j = 2, width=3, unit = "in") %>%
              flextable::width(j = 3, width=3, unit = "in")

events_ft  %>% saveRDS(paste0(here::here(), "ICBEdataset/paper/tables/events_ft.Rds"))
events_ft

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixPlayersandAgents.Rmd
Init

---
title: "Appendix ICBe Players and Agents"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)
library(googlesheets4)

```

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}
target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

```

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}

actor_agents <- dictionary_actors %>%
  #dplyr::select(Player=value_normalized_label, Qcode=value_normalized_wikidata_id, Piece=value_disaggregated_wikidata_label, Qcode_=value_disaggregated_wikidata_id) %>% 
  filter(!is.na(value_normalized) & value_normalized!='') %>%
  mutate(
    value_normalized_label = value_normalized_label %>% str_replace_all("[^A-Za-z0-9 ]",""),   #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
    value_disaggregated_wikidata_label = value_disaggregated_wikidata_label %>% str_replace_all("[^A-Za-z0-9 ]",""),   #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
  ) %>%
  mutate(Player=paste0(value_normalized_label, " (",value_normalized_wikidata_id,")"),
         Piece=paste0(value_disaggregated_wikidata_label, " (",value_disaggregated_wikidata_id,")") 
         ) %>%
  mutate(Piece= ifelse(Piece %in% "NA (NA)" |  Piece==Player, "",Piece) ) %>%
  dplyr::select(Player,Piece) %>% 
  arrange(Player,Piece) %>% 
  distinct() %>%
  group_by(Player) %>%
  summarise(Piece= paste0(Piece, collapse=" ; ")) %>%
  mutate(Piece= Piece %>% str_replace_all(" ;  ; ","") ) %>%
  mutate(Piece= Piece %>% str_replace_all("^ ; | ; $","") ) %>%
  mutate(Player_Pieces = paste0(Player , " {", Piece, "}")) %>%
  mutate(Player_Pieces= Player_Pieces %>% str_replace_all(" \\{\\}","") )   %>%

  dplyr::select(Player_Pieces)

library(officer) #needed for fp_border(color="gray")
actor_agents_ft <- 
actor_agents %>% 
      dplyr::select(Player_Pieces) %>%
      flextable::as_flextable() %>%
      bg( i = which( 1:nrow(actor_agents) %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
      #merge_v(part = "body") %>% 
      flextable::width( j = 1, width=7) %>%
      flextable::fontsize(size = 6, part = "body") %>%
      #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      #hline(i=which( actor_agents$Player!=c(actor_agents$Player[2:length(actor_agents$Player)], NA) ), border = fp_border(color="gray", width = 0.25), part = "body")

      #add_header( "IR Player_Pieces"="Citations"

      #            top = TRUE ) %>%
      set_header_labels(
        values = list("Player_Pieces" = "Players {Agents}" ) 
        )

actor_agents_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/actor_agents_ft.Rds'))
actor_agents_ft

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbCoarsened.Rmd
Init

---
title: "Appendix ICB Corpus Verb Coarsened Meanings"
output: html_document
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)
p_load(tidyverse)
p_load(igraph)
p_load(flextable)
p_load(ftExtra)
p_load(googlesheets4)

```

```{r}
icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
```

```{r , message=F}

icb_text <- icb_wide_clean %>% dplyr::select(crisno,sentence_number_int_aligned, sentence) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)

fromscratch=F
if(fromscratch){

  p_load("spacyr")
  #spacy_install() 
  spacy_initialize(model = "en_core_web_sm")

  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
  parsed_consolidated <- nounphrase_consolidate(parsed)
  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]

  parsed %>% saveRDS(paste0(here::here(), "/data/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/data/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/data/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/data/entities.Rds"))

}

entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
entities$crisno <- icb_text$crisno[entities$doc_id_num]
entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()

verbs_sentence <- parsed %>% filter(pos=="VERB")

verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()

entities_per_sentence <- entities %>% 
  count(doc_id) %>% 
  summarise(
    entities_per_sentence_min=min(n),
    entities_per_sentence_mean=mean(n),
    entities_per_sentence_max=max(n),
  )

```

```{r, messages=F, results='hide', warnings=F, include=FALSE}

#wordnet rdf (in tripple format)
fromscratch=F

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )

subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
subject_headings_verbs <- subject_headings %>%
                          filter(value %>% str_detect('-v>')) %>% 
                          mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>% 
                          mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
                          separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
                          mutate(b = b %>% str_replace_all('\\"| \\.',""))

#subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('00002137')) #the first digit is for part of speech so we can remove that if we subset to just verbs

#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)

wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F, show_col_types=F)
names(wordnet_list) <- filenames

hypernyms <- wordnet_list[['wn_hyp.csv']] %>% 
              dplyr::select(a=X1,b=X2) %>% 
              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>% 
              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )

library(igraph)
g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)

wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )

wordnet_verbs <- wordnet %>% filter(tense=='v')

verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
#dim(verbs_sentence_wordnet) #227,426

#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances

```

```{r, echo=F, messages=F, warnings=F, results='hide'}

fromsrcatch=F
if(fromsrcatch){
  #py$sentences
  #py$glosses
  sentences_embeddings <- py$sentences_embeddings
  glosses_embeddings <- py$glosses_embeddings

  rownames(sentences_embeddings) <- py$sentences #[1:100]
  rownames(glosses_embeddings) <- py$glosses #[1:100]
  dim(glosses_embeddings)

  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
  gloss_clean <- verbs_sentence_wordnet$gloss
  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
  dim(glosses_embeddings_expanded)

  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
  table(condition_sentences_embeddings) #all are in it
  sentences_clean <- verbs_sentence_wordnet$sentence
  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
  dim(sentences_embeddings_expanded)

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))

} else {

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds") )

}

verbs_sentence_wordnet_top <- verbs_sentence_wordnet %>% group_by(crisno, sentence_number_int_aligned, token_id) %>% filter(row_number()==1)
verbs_sentence_wordnet_top_unique <- verbs_sentence_wordnet_top %>% ungroup() %>% dplyr::select(lemma, wordnetid,tense, gloss) %>% group_by(lemma, wordnetid,tense, gloss) %>% count() %>% arrange(desc(n))

#length(verbs_sentence_wordnet_top_unique$wordnetid) #3312 wordnetids but only 2,470 have hyponyms
verbs_sentence_wordnet_top_unique_nodes <- V(g_hypernyms)[name %in% verbs_sentence_wordnet_top_unique$wordnetid]

#g_hypernyms_verbs_used <- subcomponent(g_hypernyms, verbs_sentence_wordnet_top_unique_nodes, mode = c("out"))

g_hypernyms_verbs_used_list <- lapply(verbs_sentence_wordnet_top_unique_nodes,
                                 FUN=function(x) subcomponent(g_hypernyms, x, mode = c("out"))$name
                                 )

g_hypernyms_verbs_used <- NULL
g_hypernyms_verbs_used <- subgraph(g_hypernyms, V(g_hypernyms)[name %in% unlist(g_hypernyms_verbs_used_list )] )
g_hypernyms_verbs_used_df <- as_edgelist(g_hypernyms_verbs_used, names = TRUE)
roots <- setdiff(g_hypernyms_verbs_used_df[,2],g_hypernyms_verbs_used_df[,1])

subject_headings_verbs_toadd <- subject_headings_verbs %>% filter(a %in% roots) #I want to add these edges to the graph
#V(g_hypernyms_verbs_used) #This is only 1600

#Add the new body labels
g_hypernyms_verbs_used <- g_hypernyms_verbs_used %>% add_vertices(nv=length(unique(subject_headings_verbs_toadd$b)), name = unique(subject_headings_verbs_toadd$b))
#V(g_hypernyms_verbs_used)
#Add edges from the degenerate roots to the domains
g_hypernyms_verbs_used <- g_hypernyms_verbs_used %>%  add_edges(subject_headings_verbs_toadd %>% as.matrix() %>% t() %>% as.vector())
#V(g_hypernyms_verbs_used)
#is_simple(g_hypernyms_verbs_used)
#is_dag(g_hypernyms_verbs_used)
g_hypernyms_verbs_used <- g_hypernyms_verbs_used %>% simplify( remove.multiple = TRUE, remove.loops = TRUE)
#is_simple(g_hypernyms_verbs_used)

g_hypernyms_verbs_used_3hops <- ego(g_hypernyms_verbs_used, order = 1, nodes = V(g_hypernyms_verbs_used)[name %in% unique(subject_headings_verbs_toadd$b)], mode = c("all", "out","in"), mindist = 0)
g_hypernyms_verbs_used_3hops_list <- lapply(g_hypernyms_verbs_used_3hops,
                                 FUN=function(x) subcomponent(g_hypernyms_verbs_used, x, mode = c("all"))$name
                                 )  
g_hypernyms_verbs_used_3hops <- subgraph(g_hypernyms_verbs_used, V(g_hypernyms_verbs_used)[name %in% unlist(g_hypernyms_verbs_used_3hops_list )] )
g_hypernyms_verbs_used_3hops_df <- as_edgelist(g_hypernyms_verbs_used_3hops, names = TRUE)

require(tidygraph)
lemma_df <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(name=X1, lemma=X3) %>% mutate(name=name %>% as.character) %>% 
            group_by(name) %>% summarise(lemma=paste0(lemma, collapse=";"))
rownames(lemma_df) <- lemma_df$name

first_two_hops <- g_hypernyms_verbs_used_3hops_df %>% as_tibble() %>% 
                    left_join(lemma_df %>% rename(V1=name, lemma1=lemma)) %>%
                    left_join(lemma_df %>% rename(V2=name, lemma2=lemma)) %>%
                    dplyr::select(wordnetid_hop0=V2, wordnetid_hop1=V1,lemma1_hop0=lemma2, lemma1_hop1=lemma1)

first_two_hops_appendix <- first_two_hops %>% filter(wordnetid_hop1 %in% roots) %>% distinct() %>% arrange(lemma1_hop0,lemma1_hop1) %>% arrange(wordnetid_hop0,lemma1_hop1) %>% dplyr::select(wordnetid_hop0,lemma1_hop1)

first_two_hops_collapsed <- first_two_hops %>% 
                            dplyr::select(lemma1_hop0, lemma1_hop1) %>%
                            group_by(lemma1_hop0) %>%
                            summarise(
                              lemma1_hop1 = paste0(lemma1_hop1, collapse=" | ")
                            ) %>%
                            arrange(lemma1_hop0)

tblg_hypernyms_verbs_used <- g_hypernyms_verbs_used %>% as_tbl_graph()
V(tblg_hypernyms_verbs_used)$lemma <- lemma_df[V(tblg_hypernyms_verbs_used)$name,]$lemma
condition <- V(tblg_hypernyms_verbs_used)$lemma %>% is.na()
V(tblg_hypernyms_verbs_used)$lemma[condition] <- V(tblg_hypernyms_verbs_used)$name[condition]

g_hypernyms_verbs_used_rooted <- g_hypernyms_verbs_used %>% add_vertices(nv=1, name = "verbs")
#V(g_hypernyms_verbs_used_rooted)
root_df <- data.frame(a=unique(subject_headings_verbs_toadd$b)); root_df$b <- "verbs"

#Add edges from the degenerate roots to the domains
g_hypernyms_verbs_used_rooted <- g_hypernyms_verbs_used_rooted %>%  add_edges(root_df[,c('a','b')] %>% as.matrix() %>% t() %>% as.vector())
#as_edgelist(g_hypernyms_verbs_used_rooted, names = TRUE)

tblg_hypernyms_verbs_used_rooted <- g_hypernyms_verbs_used_rooted %>% as_tbl_graph()
V(tblg_hypernyms_verbs_used_rooted)$lemma <- lemma_df[V(tblg_hypernyms_verbs_used_rooted)$name,]$lemma
condition <- V(tblg_hypernyms_verbs_used_rooted)$lemma %>% is.na()
V(tblg_hypernyms_verbs_used_rooted)$lemma[condition] <- V(tblg_hypernyms_verbs_used_rooted)$name[condition]

library(data.tree)
library(networkD3) 
df_hypernyms_verbs_used_rooted <- g_hypernyms_verbs_used_rooted %>% as_edgelist( names = TRUE) %>% as.data.frame()
df_hypernyms_verbs_used_rooted_labeled <- df_hypernyms_verbs_used_rooted %>% as_tibble() %>% 
                                          left_join(lemma_df %>% rename(V1=name, lemma1=lemma)) %>%
                                          left_join(lemma_df %>% rename(V2=name, lemma2=lemma)) %>%
                                          mutate(lemma1=ifelse(is.na(lemma1), V1, lemma1)) %>%
                                          mutate(lemma2=ifelse(is.na(lemma2), V2, lemma2)) #%>%
                                          #dplyr::select(lemma1,lemma2)

library("dendextend")

tree_hypernyms_verbs_used_rooted <- df_hypernyms_verbs_used_rooted_labeled %>% as.Node(mode="network")
tree_hypernyms_verbs_used_rooted_table <- tree_hypernyms_verbs_used_rooted %>% ToDataFrameTypeCol()

tree_hypernyms_verbs_used_rooted_table_ready <- 
                                            tree_hypernyms_verbs_used_rooted_table %>% 
                                                                      left_join(lemma_df %>% dplyr::rename(level_3=name, lemma3=lemma)) %>% 
                                                                      left_join(lemma_df %>% dplyr::rename(level_4=name, lemma4=lemma)) %>%
                                                                      dplyr::select(level1=level_2, level2=lemma3, level3=lemma4) %>%
                                                                      arrange(level1,level2,level3) %>% distinct()

```

```{r, eval=T, echo=F, results="markup", include=T, message=F, cache=F, ft.arraystretch=0.75}

set_flextable_defaults(fonts_ignore=TRUE)

first_two_hops_collapsed_ft <- tree_hypernyms_verbs_used_rooted_table_ready %>%
        ungroup() %>% 
        group_by(level1, level2) %>%
        summarise(level3 = paste0(level3, collapse=" | ")) %>%
        ungroup() %>%
        #dplyr::select(-level2, -level3) %>%
        mutate(level1=level1 %>% str_replace_all("[^A-Za-z0-9 ;]","") %>% str_replace_all("verb","")    ) %>%
        mutate(level2=level2 %>% str_replace_all("[^A-Za-z0-9 ;\\|]","") %>% str_replace_all(";","; ") ) %>%
        mutate(level3=level3 %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%

        #head(200) %>%
        #dplyr::select(n, lemma, gloss ) %>% #wordnetid
        #mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.]','')) %>%
        dplyr::select(VerbGroup=level1,VerbLevel1=level2,VerbLevel2=level3) %>%
        group_by(VerbGroup) %>%
        flextable::as_flextable() %>%

        #bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6) %>% 
        #rotate(rotation="tbrl",part="header") %>%
        #set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is crazy slow
        #flextable::autofit() 
        #fit_to_width(max_width = 8, max_iter = 40) %>%
        #width(j = 1, width=0.75) %>%
        flextable::width(j = 1, width=1.5) %>%
        flextable::width(j = 2, width=5) #%>%
        #merge_v(j = 1, part = "body", combine = T) #%>%
        #hline(j = 1, border = NULL, part = "body")

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/paper/tables/first_two_hops_collapsed_ft.Rds'))
first_two_hops_collapsed_ft

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbDomains.Rmd
Init

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbCoarsened.Rmd
@@
 ---
-title: "Appendix ICB Corpus Verb Coarsened Meanings"
+title: "Appendix Verb Domains"
 output: html_document
@@
 p_load(tidyverse)
-p_load(igraph)
 p_load(flextable)
@@
 p_load(googlesheets4)
+library(googlesheets4)
 
@@
 
-```{r, eval=T, echo=F, results="markup", include=T, message=F, cache=F, ft.arraystretch=0.75}
+```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F}
 
+domains <- verbs_sentence_wordnet_top %>% ungroup() %>%  
+            dplyr::select(wordnetid) %>%
+            mutate(wordnetid=wordnetid %>% as.character() ) %>% 
+            left_join(subject_headings_verbs %>% dplyr::select(wordnetid=a,domain=b)) %>%
+            count(domain) %>% 
+            arrange(desc(n)) %>% 
+            na.omit() %>%
+            mutate(perc= round( n/sum(n) * 100 ) ) %>%
+  left_join(
+    tree_hypernyms_verbs_used_rooted_table_ready %>%
+  dplyr::select(level1,level2) %>% distinct() %>% group_by(level1) %>% summarise(level2=level2 %>% paste0(collapse=" | ") ) %>% dplyr::select(domain=level1,Sysnets=level2)
+  )
+
+p_load(flextable)
+p_load(ftExtra)
 set_flextable_defaults(fonts_ignore=TRUE)
 
-first_two_hops_collapsed_ft <- tree_hypernyms_verbs_used_rooted_table_ready %>%
+domains_ft <- domains %>%
         ungroup() %>% 
-        group_by(level1, level2) %>%
-        summarise(level3 = paste0(level3, collapse=" | ")) %>%
-        ungroup() %>%
-        #dplyr::select(-level2, -level3) %>%
-        mutate(level1=level1 %>% str_replace_all("[^A-Za-z0-9 ;]","") %>% str_replace_all("verb","")    ) %>%
-        mutate(level2=level2 %>% str_replace_all("[^A-Za-z0-9 ;\\|]","") %>% str_replace_all(";","; ") ) %>%
-        mutate(level3=level3 %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%
-
-        #head(200) %>%
-        #dplyr::select(n, lemma, gloss ) %>% #wordnetid
-        #mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.]','')) %>%
-        dplyr::select(VerbGroup=level1,VerbLevel1=level2,VerbLevel2=level3) %>%
-        group_by(VerbGroup) %>%
+        mutate(Sysnets=Sysnets %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%
         flextable::as_flextable() %>%
 
-        #bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
+        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
         #width(j = 1, width=1.25) %>%
         #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
-        flextable::fontsize(size = 6) %>% 
+        flextable::fontsize(size = 8, part = "body" ) %>% 
         #rotate(rotation="tbrl",part="header") %>%
-        #set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
+        set_header_labels( values = list(crisno = "#", input_crisis = "Name", sentence_count="Sentences", word_count="Words", event_count_mean_sum="Events")) %>%
         #align(align = "center", part = "body") %>%
         #align(align = "center", part = "header") %>%
+        set_table_properties(layout="autofit") %>%  
         flextable::padding(padding = 0, part = "all") %>%
-        flextable::line_spacing(space = 1, part = "body") %>%
+        flextable::line_spacing(space = 1, part = "body") #%>%
         #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
+
+      #autofit()
       #fit_to_width(max_width=12) #This is crazy slow
       #flextable::autofit() 
-        #fit_to_width(max_width = 8, max_iter = 40) %>%
-        #width(j = 1, width=0.75) %>%
-        flextable::width(j = 1, width=1.5) %>%
-        flextable::width(j = 2, width=5) #%>%
-        #merge_v(j = 1, part = "body", combine = T) #%>%
-        #hline(j = 1, border = NULL, part = "body")
+      #set_table_properties(width = 1, layout = "autofit")
 
@@
 
-first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/paper/tables/first_two_hops_collapsed_ft.Rds'))
-first_two_hops_collapsed_ft
+domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
+domains_ft
 

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbMeanings.Rmd
Init

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbDomains.Rmd
@@
 ---
-title: "Appendix Verb Domains"
+title: "Verb Meanings found in the ICB Corpus (top 200)"
 output: html_document
@@
 library(pacman)
+p_load(igraph)
 p_load(tidyverse)
@@
 #wordnet rdf (in tripple format)
+#wordnet rdf (in tripple format)
 fromscratch=F
@@
 #wordnet csv
-filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
+filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"))
 filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)
@@
 names(wordnet_list) <- filenames
+
+#wordnet_list[[8]]
+#wordnet_list[[16]]
+#wordnet_list[[19]]
+
+wordnet_list[["wn_cls.csv"]]
+
+wordnet_list[["wn_vgp.csv"]]
 
@@
 
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds") )
+  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))
 
@@
 V(tblg_hypernyms_verbs_used)$lemma[condition] <- V(tblg_hypernyms_verbs_used)$name[condition]
+#
+library(ggraph)
+p <- tblg_hypernyms_verbs_used %>% 
+      ggraph(  layout = "sugiyama") + 
+      coord_flip() +
+      geom_edge_link(width=0.5, alpha=0.25 )  + 
+      geom_node_label(aes(label = lemma), repel = TRUE, size=3)
+
+ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)
+
+#
 
@@
 V(tblg_hypernyms_verbs_used_rooted)$lemma[condition] <- V(tblg_hypernyms_verbs_used_rooted)$name[condition]
+
+library(ggraph)
+p_rooted <- tblg_hypernyms_verbs_used_rooted %>% 
+            ggraph(  layout = "sugiyama") + 
+            coord_flip() +
+            geom_edge_elbow(width=0.5, alpha=0.25 )  + 
+            geom_node_label(aes(label = lemma), repel = TRUE, size=3)
+
+ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)
 
@@
 
+#dendrogram_hypernyms_verbs_used_rooted <- tree_hypernyms_verbs_used_rooted %>% as.dendrogram() #dengraom kills the internal labels and there's a better one anyway
+#rn_hypernyms_verbs_used_rooted <- dendrogram_hypernyms_verbs_used_rooted %>% as.radialNetwork()     
+#lol <- ToListExplicit(tree_hypernyms_verbs_used_rooted, unname = TRUE) #data.tree will go straight to list https://stackoverflow.com/questions/36273730/turning-relationship-data-into-hierarchical-list-in-r
+#d3_dendrogram <- diagonalNetwork(List = lol, fontSize = 8, opacity = 0.9)
+
+#karate_d3 <- igraph_to_networkD3(g_hypernyms_verbs_used_rooted)
+
+#diagonalNetwork(List = karate_d3$links) #, fontSize = 10, opacity = 0.9
+#as.radialNetwork(d, root)
+
+#library(dendextend)
+#library(ggdendro)
+#dendro_hypernyms_verbs_used <- as.dendro(segments=karate_d3$links, labels=karate_d3$nodes, class="hclust")
+
+#dendrogram_hypernyms_verbs_used <- dendro_hypernyms_verbs_used
+#attr(dendrogram_hypernyms_verbs_used,"class") <- "dendrogram"
+#as.radialNetwork(dendrogram_hypernyms_verbs_used)
+
+## Convert to list format
+#Flare <- jsonlite::fromJSON("https://raw.githubusercontent.com/christophergandrud/d3Network/master/JSONdata/flare.json", simplifyDataFrame = FALSE)
+#diagonalNetwork(List = Flare) #, fontSize = 10, opacity = 0.9
+
+#require(graphics); require(utils)
+#hc <- hclust(dist(USArrests), "ave")
+#(dend1 <- as.dendrogram(hc)) # "print()" method
+
 ```
 
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F}
+```{r, eval=T, echo=F, results="markup", include=T, message=T, cache=F, ft.arraystretch=0.75}
 
-domains <- verbs_sentence_wordnet_top %>% ungroup() %>%  
-            dplyr::select(wordnetid) %>%
-            mutate(wordnetid=wordnetid %>% as.character() ) %>% 
-            left_join(subject_headings_verbs %>% dplyr::select(wordnetid=a,domain=b)) %>%
-            count(domain) %>% 
-            arrange(desc(n)) %>% 
-            na.omit() %>%
-            mutate(perc= round( n/sum(n) * 100 ) ) %>%
-  left_join(
-    tree_hypernyms_verbs_used_rooted_table_ready %>%
-  dplyr::select(level1,level2) %>% distinct() %>% group_by(level1) %>% summarise(level2=level2 %>% paste0(collapse=" | ") ) %>% dplyr::select(domain=level1,Sysnets=level2)
-  )
+set_flextable_defaults(fonts_ignore=TRUE)
+n_keep=200
+verbs_sentence_wordnet_top_ft <-
+        verbs_sentence_wordnet_top_unique %>%
+        ungroup() %>% 
+        head(n_keep) %>%
+        dplyr::select(n, lemma, gloss ) %>% #wordnetid
+        mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.\"]','')) %>%
 
-p_load(flextable)
-p_load(ftExtra)
-set_flextable_defaults(fonts_ignore=TRUE)
-
-domains_ft <- domains %>%
-        ungroup() %>% 
-        mutate(Sysnets=Sysnets %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%
         flextable::as_flextable() %>%
@@
         #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
-        flextable::fontsize(size = 8, part = "body" ) %>% 
+        flextable::fontsize(size = 6, part = "all") %>% 
         #rotate(rotation="tbrl",part="header") %>%
-        set_header_labels( values = list(crisno = "#", input_crisis = "Name", sentence_count="Sentences", word_count="Words", event_count_mean_sum="Events")) %>%
+        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
         #align(align = "center", part = "body") %>%
         #align(align = "center", part = "header") %>%
-        set_table_properties(layout="autofit") %>%  
         flextable::padding(padding = 0, part = "all") %>%
-        flextable::line_spacing(space = 1, part = "body") #%>%
+        flextable::line_spacing(space = 1, part = "body") %>%
         #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
-
-      #autofit()
         #fit_to_width(max_width=12) #This is crazy slow
@@
 
+      bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
+      #merge_v(part = "body") %>% 
+      flextable::width( j = 1, width=0.3) %>%
+      flextable::width( j = 2, width=.75) %>%
+      flextable::width( j = 3, width=6) %>%
+      #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
+      flextable::padding(padding = 0, part = "body") %>%
+      #hline(i=which( actor_agents$Player!=c(actor_agents$Player[2:length(actor_agents$Player)], NA) ), border = fp_border(color="gray", width = 0.25), part = "body")
+
+      #add_header( "IR Player_Pieces"="Citations"
+
+      #            top = TRUE ) %>%
+      set_header_labels(
+        values = list(
+          "uses" = "Count",
+          'lemma'='Lemma',
+          'gloss'='Gloss'
+          ) 
+        )
+
 #https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
 
-domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
-domains_ft
+verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
+verbs_sentence_wordnet_top_ft
 

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbTrees.Rmd
Init

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbDomains.Rmd
@@
 ---
-title: "Appendix Verb Domains"
+title: "AppendixVerbTrees.Rmd"
 output: html_document
@@
 
-```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
-library(pacman)
-p_load(tidyverse)
-p_load(flextable)
-p_load(ftExtra)
-p_load(googlesheets4)
-library(googlesheets4)
-
-```
-
-```{r}
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
-```
-
-```{r , message=F}
-
-icb_text <- icb_wide_clean %>% dplyr::select(crisno,sentence_number_int_aligned, sentence) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)
-
-# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)
-
-fromscratch=F
-if(fromscratch){
-
-  p_load("spacyr")
-  #spacy_install() 
-  spacy_initialize(model = "en_core_web_sm")
-
-  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
-  parsed_consolidated <- nounphrase_consolidate(parsed)
-  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
-  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
-  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
-  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]
-
-  parsed %>% saveRDS(paste0(here::here(), "/data/parsed.Rds"))
-
-  entities <- entity_extract(parsed, type = "all")
-  entities %>% saveRDS(paste0(here::here(), "/data/entities.Rds"))
-
-} else {
-  parsed <- readRDS(paste0(here::here(), "/data/parsed.Rds"))
-  entities <- readRDS(paste0(here::here(), "/data/entities.Rds"))
-
-}
-
-entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
-entities$crisno <- icb_text$crisno[entities$doc_id_num]
-entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()
-
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
-dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
-
-unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
-unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
-
-verbs_sentence <- parsed %>% filter(pos=="VERB")
-
-verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()
-
-entities_per_sentence <- entities %>% 
-  count(doc_id) %>% 
-  summarise(
-    entities_per_sentence_min=min(n),
-    entities_per_sentence_mean=mean(n),
-    entities_per_sentence_max=max(n),
-  )
-
-```
-
-```{r, messages=F, results='hide', warnings=F, include=FALSE}
-
-#wordnet rdf (in tripple format)
-fromscratch=F
-
-wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )
-
-subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
-subject_headings_verbs <- subject_headings %>%
-                          filter(value %>% str_detect('-v>')) %>% 
-                          mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>% 
-                          mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
-                          separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
-                          mutate(b = b %>% str_replace_all('\\"| \\.',""))
-
-#subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('00002137')) #the first digit is for part of speech so we can remove that if we subset to just verbs
-
-#wordnet csv
-filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
-filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)
-
-wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F, show_col_types=F)
-names(wordnet_list) <- filenames
-
-hypernyms <- wordnet_list[['wn_hyp.csv']] %>% 
-              dplyr::select(a=X1,b=X2) %>% 
-              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>% 
-              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )
-
-library(igraph)
-g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)
-
-wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )
-
-wordnet_verbs <- wordnet %>% filter(tense=='v')
-
-verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
-#dim(verbs_sentence_wordnet) #227,426
-
-#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances
-
-```
-
-```{r, echo=F, messages=F, warnings=F, results='hide'}
+```{r, echo=F, messages=F, warnings=F, results='hide', eval=T}
 
@@
   verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
-  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))
+  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))
 
@@
 
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds") )
+  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))
 
@@
 V(tblg_hypernyms_verbs_used)$lemma[condition] <- V(tblg_hypernyms_verbs_used)$name[condition]
+#
+library(ggraph)
+p <- tblg_hypernyms_verbs_used %>% 
+      ggraph(  layout = "sugiyama") + 
+      coord_flip() +
+      geom_edge_link(width=0.5, alpha=0.25 )  + 
+      geom_node_label(aes(label = lemma), repel = TRUE, size=3)
+
+ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)
+
+#
 
@@
 
-library(data.tree)
-library(networkD3) 
-df_hypernyms_verbs_used_rooted <- g_hypernyms_verbs_used_rooted %>% as_edgelist( names = TRUE) %>% as.data.frame()
-df_hypernyms_verbs_used_rooted_labeled <- df_hypernyms_verbs_used_rooted %>% as_tibble() %>% 
-                                          left_join(lemma_df %>% rename(V1=name, lemma1=lemma)) %>%
-                                          left_join(lemma_df %>% rename(V2=name, lemma2=lemma)) %>%
-                                          mutate(lemma1=ifelse(is.na(lemma1), V1, lemma1)) %>%
-                                          mutate(lemma2=ifelse(is.na(lemma2), V2, lemma2)) #%>%
-                                          #dplyr::select(lemma1,lemma2)
+library(ggraph)
+p_rooted <- tblg_hypernyms_verbs_used_rooted %>% 
+            ggraph(  layout = "sugiyama") + 
+            coord_flip() +
+            geom_edge_elbow(width=0.5, alpha=0.25 )  + 
+            geom_node_label(aes(label = lemma), repel = TRUE, size=3)
 
-library("dendextend")
-
-tree_hypernyms_verbs_used_rooted <- df_hypernyms_verbs_used_rooted_labeled %>% as.Node(mode="network")
-tree_hypernyms_verbs_used_rooted_table <- tree_hypernyms_verbs_used_rooted %>% ToDataFrameTypeCol()
-
-tree_hypernyms_verbs_used_rooted_table_ready <- 
-                                            tree_hypernyms_verbs_used_rooted_table %>% 
-                                                                      left_join(lemma_df %>% dplyr::rename(level_3=name, lemma3=lemma)) %>% 
-                                                                      left_join(lemma_df %>% dplyr::rename(level_4=name, lemma4=lemma)) %>%
-                                                                      dplyr::select(level1=level_2, level2=lemma3, level3=lemma4) %>%
-                                                                      arrange(level1,level2,level3) %>% distinct()
+ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)
 
 ```
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F}
-
-domains <- verbs_sentence_wordnet_top %>% ungroup() %>%  
-            dplyr::select(wordnetid) %>%
-            mutate(wordnetid=wordnetid %>% as.character() ) %>% 
-            left_join(subject_headings_verbs %>% dplyr::select(wordnetid=a,domain=b)) %>%
-            count(domain) %>% 
-            arrange(desc(n)) %>% 
-            na.omit() %>%
-            mutate(perc= round( n/sum(n) * 100 ) ) %>%
-  left_join(
-    tree_hypernyms_verbs_used_rooted_table_ready %>%
-  dplyr::select(level1,level2) %>% distinct() %>% group_by(level1) %>% summarise(level2=level2 %>% paste0(collapse=" | ") ) %>% dplyr::select(domain=level1,Sysnets=level2)
-  )
-
-p_load(flextable)
-p_load(ftExtra)
-set_flextable_defaults(fonts_ignore=TRUE)
-
-domains_ft <- domains %>%
-        ungroup() %>% 
-        mutate(Sysnets=Sysnets %>% str_replace_all("[^A-Za-z0-9 ;\\|]","")) %>%
-        flextable::as_flextable() %>%
-
-        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
-        #width(j = 1, width=1.25) %>%
-        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
-        flextable::fontsize(size = 8, part = "body" ) %>% 
-        #rotate(rotation="tbrl",part="header") %>%
-        set_header_labels( values = list(crisno = "#", input_crisis = "Name", sentence_count="Sentences", word_count="Words", event_count_mean_sum="Events")) %>%
-        #align(align = "center", part = "body") %>%
-        #align(align = "center", part = "header") %>%
-        set_table_properties(layout="autofit") %>%  
-        flextable::padding(padding = 0, part = "all") %>%
-        flextable::line_spacing(space = 1, part = "body") #%>%
-        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
-
-      #autofit()
-      #fit_to_width(max_width=12) #This is crazy slow
-      #flextable::autofit() 
-      #set_table_properties(width = 1, layout = "autofit")
-
-#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
-
-domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
-domains_ft
-
-```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
Init

---
title: 'ICBEdataset_paper_prep_metro_map'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \usepackage{float}
---

# Intro

## Library Loads

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)
library(janitor)
library(ftExtra)
library(igraph)

set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`. You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
options(tidyverse.quiet = TRUE)
options(gargle_oauth_email = TRUE)

icb_crises <- read.csv(paste0(here::here(), "/inst/extdata/","icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds"))

```

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
# MOVED TO figures/ICBEdataset_figure_semantic_embeddings.Rmd

#child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/paper/figures/p_semantic_embeddings.Rds'))
ggsave(file=paste0(here::here(), '//paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
```

#Case  196 Cuban Missile

```{r}

crisis=196
plot_title <- icb_crises %>%
            filter(crisno==crisis) %>%
            #mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>%
            mutate(title= crisname %>% paste0( " (", yrtrig, "-",yrterm,")")) %>%
            pull(title)

```

## ICBe Crisis Map

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  196
library(ggplot2)
p_metro_map_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_196.Rds'))
actor_colors <- p_metro_map_196$actor_colors
ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_196.png'),
       plot = p_metro_map_196 +
         theme(plot.margin=unit(c(0,0,0,0),"in")) +
         scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
         scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
       width=12, height=14)

```

## Phoenix Crisis Map

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  196
library(ggplot2)
p_phoenix_metro_plot_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
actor_colors <- p_phoenix_metro_plot_196$actor_colors

save_file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds')

subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- readRDS(save_file) +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_phoenix_metro_plot_196.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## Dyadic ICB

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_icb_metro_plot_196.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## MIDs

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_mids_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption) #tag original to bottom
p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_mids_metro_plot_196.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

# Crisis 426

```{r}

crisis=426
plot_title <- icb_crises %>%
            filter(crisno==crisis) %>%
            #mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>%
            mutate(title= crisname %>% paste0( " (", yrtrig, "-",yrterm,")")) %>%
            pull(title)

```

## ICBe

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

# #ICBe  426
p_metro_map_426 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_426.Rds'))
actor_colors <- p_metro_map_426$actor_colors
ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_426.png'),
      plot = p_metro_map_426 +
        theme(plot.margin=unit(c(0,0,0,0),"in")) +
        scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
        scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
      width=12, height=14)

devtools::install_github('davidgohel/ggiraph')

```

## Phoenix Crisis Map

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
#ICBe  426
library(ggplot2)
p_metro_plot <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_426.Rds'))
actor_colors <- p_metro_plot$actor_colors

save_file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_426.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_phoenix_metro_plot_426.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## ICEWs Crisis Map

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_icews_metro_plot_426.Rds')
p_metro_plot <- readRDS(file=save_file)
actor_colors <- p_metro_plot$actor_colors

subtitle="ICEWS Dyadic Events"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Integrated Crisis Early Warning System (ICEWS) (Boschee et al. 2018)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_icews_metro_plot_426.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## Terrier Crisis Map

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_terrier_metro_plot_426.Rds')
p_metro_plot <- readRDS(file=save_file)
actor_colors <- p_metro_plot$actor_colors

subtitle="Terrier Dyadic Events"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
             Data: TERRIER (Temporally Extended, Regular, Reproducible International Event Records) (Liang et al. 2018)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_terrier_metro_plot_426.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## Dyadic ICB

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_icb_metro_plot_426.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_icb_metro_plot_426.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## MIDs

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_mids_metro_plot_426.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption) #tag original to bottom
p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_mids_metro_plot_426.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

## MIDs

```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

library(ggplot2)
save_file=paste0(here::here(), '/paper/figures/metro_plots/p_mids_incidents_metro_plot_426.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors

subtitle="Militerized Interstate Dispute Incidents"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Militerized Interstate Dispute Incidents 5.0 (MIDs) (Palmer et al. 2021)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_metro_plot <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    title = plot_title ,
    subtitle = subtitle ,
    caption = caption
  ) +
   theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
ggsave(file=paste0(here::here(), '/paper/figures/p_mids_incidents_metro_plot_426.png'),
       plot = p_metro_plot ,
       width=12, height=14)

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_uncertainty.Rmd
Init

---
title: "Uncertainty"
output: html_document
---

# Intro

## Library Loads

```{r}
library(flextable)
library(tidyverse)
library(googlesheets4)

```

```{r}

#Takes a while
rex_paste <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}
rex_count <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}

```
## Hand coded aggregations

```{r}

full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
                                       sheet="Codebook in Tree Form")

full_tree <- full_tree %>% filter(!is.na(Leaf) & Leaf!='')
#The leafs aren't unique here because you can get to the same branch multiple ways

#This ignores conditions FYI
#Behavior # 3 bits
#think_aggression #1 bit
#say_aggression #1 bit
#do_aggression #1 bit
#Do_Armed_Unarmed #1 bit
#do_Act_Interact #1 bit
#full_tree$Leaf_Simplified %>% unique() %>% length() #66 bits

#Only 70 bits total

#That's only another 29 bits
full_tree$Think_Type_L0 %>% unique() %>% length() #6
full_tree$Say_Type_L0 %>% unique() %>% length() #5
full_tree$Do_Type_L0 %>% unique() %>% length() #18

```

## Data loads

```{r, echo=FALSE}

drops <- c(
'interact_escalate',
'interact_deescalate',
'act_uncooperative',
'act_deescalate',
'act_cooperative',
'do_interact_kind',
'do_kind',
'interact_decreasecoop',
'interact_increasecoop',
'interact_deescalate',
'act_escalate',
'condition_interact_deescalate',
'condition_interact_escalate',
'condition_interact_increasecoop',
'condition_interact_decreasecoop',
'condition_act_cooperative',
'condition_act_deescalate',
'condition_act_escalate',
'condition_act_uncooperative',
'do_interact_kind',
'interact_escalate',
'sayintkind',
'sayintkind_react',
'interact_deescalate',
'interact_decreasecoop',
'act_escalate',
'act_uncooperative',
'act_deescalate',
'act_cooperative',
'act_descalate', 
'act_escalate',
'act_uncooperative',
'interact_decreasecoop',
'interact_descalate',
'interact_deescalate', #there's a mispelling here
'interact_escalate',
'interact_increasecoop',
'thinkkind',
'sayintkind'
) %>% unique()

#sentence_variabe_agreement_minimum <- sentence_variabe_agreement

icb_long_clean_original <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds")) %>% 
                            #filter(crisno==421 & sentence_number_int_aligned==16 ) %>%
                            distinct() %>%
                            mutate(variable_normalized= variable_normalized %>% str_replace("_other_clean","")) %>% #We want to collapse others in with regulars
                            mutate(variable_normalized= variable_normalized %>% str_replace("_clean","")) %>% #These only exist with actors now
                            mutate(variable_normalized= variable_normalized %>% str_replace("_other","")) %>% #Only really matters for location_other

                            filter(value_normalized!='drop') %>%
                            filter(email_id!='expert3') %>% #expert3 Looks broken all the time
                            #I'm going to move to a structure where event numbers can have a subsection that is condition rather than keeping it in the variable names
                            mutate(event_number_int_condition=variable_normalized %>% str_detect('condition_') %>% as.numeric() ) %>%
                            mutate(variable_normalized=variable_normalized %>% str_replace('condition_',''))

icb_long_clean_original_393_43 <- icb_long_clean_original %>% filter(crisno==393 & sentence_number_int_aligned==43 ) %>% janitor::remove_empty()

sentences <- icb_long_clean_original %>% dplyr::count(crisno,sentence_number_int_aligned,sentence) %>% arrange(crisno, sentence_number_int_aligned, desc(n)) %>% 
  group_by(crisno, sentence_number_int_aligned) %>% filter(row_number()==1) %>% dplyr::select(-n)

temp_wide <- icb_long_clean_original %>%
             dplyr::select(icb_survey_version, email_id,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
             filter(variable_normalized %in% c(
                                   'sentence_events',
                                   drops
                                   ) 
                        ) %>% distinct() %>% 
                  mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
                  left_join(full_tree %>% dplyr::rename(value_normalized=Leaf)  %>%
                              mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) )

temp_long <- temp_wide %>% 
         dplyr::select(-variable_normalized,-value_normalized) %>%
         pivot_longer(-c(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section, sentence,   event_number_int,event_number_int_condition), names_to='variable_normalized' , values_to= 'value_normalized')  %>%
         filter(!is.na(value_normalized))

icb_long_clean <- icb_long_clean_original %>%
                   dplyr::select(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section,  sentence,  event_number_int, event_number_int_condition, variable_normalized,value_normalized) %>%
                  rbind(temp_long) %>% distinct() %>%

                  filter(!variable_normalized %in% drops)

```

# Sentence Level Agreement

Unanimous exact agreement- every expert coder chose the exact same options across all events for that question
Majority exact agreement- at least 2/3 of expert coders chose exactly the same options across all event for that question
This aggregates across conditions too

```{r}

options(warn = -1) #Groups that have no values generate max errors
#This doesn't have this yet
#event_number_int,  event_number_int_condition
temp_long <- 
  icb_long_clean  %>%
    dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, event_number_int_condition,variable_normalized, value_normalized) %>% 
    dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
    group_by(crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
    dplyr::select(-event_number_int) %>%
    distinct() %>%
    mutate(
      email_id = email_id %>% as.factor(), 
      #crisno= crisno %>% as.factor(),
      #sentence_number_int_aligned= sentence_number_int_aligned %>% as.factor(),
      crisno_sentence_number_int_aligned= paste0(crisno, "_", sentence_number_int_aligned) %>% as.factor(), #make sure these are the only factors or it'll try to criss cross sentence number and crisno etc.
      section= section %>% as.character(),
      sentence= sentence %>% as.character(),
      variable_normalized= variable_normalized %>% as.factor()
    ) %>%
    group_by(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, 
             variable_normalized,.drop=FALSE) %>% #This drop false means every coder gets a '' whether they filled in that variable or not #section, sentence going to have to ignore the sentence text for now
      summarise(value_normalized=value_normalized %>% rex_paste() ) %>%
    #that will add in dead ones now we want to split them back out
    mutate(value_normalized = value_normalized %>% str_replace_all(";;",";")) %>% 
    mutate(value_normalized = strsplit(as.character(value_normalized), ";", fixed=T)) %>% 
    unnest(value_normalized) %>%

    #add a confidence score for every token
    mutate(confidence=ifelse(variable_normalized=='raterconfidence', value_normalized, NA)) %>%

    mutate(confidence=confidence %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
    mutate(confidence_expert= email_id %>% str_detect('expert') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
    mutate(confidence_undergrad= email_id %>% str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%

    group_by(crisno,sentence_number_int_aligned) %>%
      mutate(
        total_coders=email_id %>% unique() %>% length(),
        total_coders_expert=email_id %>% unique() %>% str_detect('expert') %>% sum() ,
        total_coders_undergrad=email_id %>% unique() %>% str_detect('undergrad') %>% sum()
      ) %>%
    ungroup() %>%

    #Selected By
    group_by(crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
      mutate(
        selected_by_experts=email_id %>% unique() %>% str_detect('expert') %>% sum() ,
        selected_by_undergrads=email_id %>% unique() %>% str_detect('undergrad') %>% sum()
      ) %>%
    ungroup() %>%
    mutate(selected_by_any=selected_by_experts+selected_by_undergrads) %>%
    left_join(sentences) %>%
    mutate(
        selected_by_any_perc=selected_by_any/total_coders,
        selected_by_experts_perc=selected_by_experts/total_coders_expert ,
        selected_by_undergrads_perc=selected_by_undergrads/total_coders_undergrad ,
    ) %>%
    ungroup()

#We have to compile confidence seperately
sentence_confidence_scores <- temp_long %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, confidence,confidence_expert,confidence_undergrad) %>% distinct() %>% 
  mutate(confidence= confidence %>% replace(., !is.finite(.), NA),
         confidence_expert = confidence_expert %>% replace(., !is.finite(.), NA),
         confidence_undergrad = confidence_undergrad %>% replace(., !is.finite(.), NA)
         ) %>% 
  dplyr::select(-email_id) %>%
  group_by(crisno, sentence_number_int_aligned) %>%
  summarise_all(mean, na.rm=T) %>%
  mutate(confidence= confidence %>% replace(., !is.finite(.), NA),
         confidence_expert = confidence_expert %>% replace(., !is.finite(.), NA),
         confidence_undergrad = confidence_undergrad %>% replace(., !is.finite(.), NA)
         )

codings_long <- temp_long %>%
                mutate(
                       expert_majority=(selected_by_experts>(total_coders_expert/2) & selected_by_experts>=2) %>% as.integer() ,
                       undergrad_majority= (selected_by_undergrads > (total_coders_undergrad/2) & total_coders_undergrad>=2 ) %>% as.integer()  ,
                       expert_or_undergrad_majority= ( expert_majority | (undergrad_majority & selected_by_experts>=1) ) %>% as.integer() 
                ) %>%
                group_by(crisno,sentence_number_int_aligned, variable_normalized, value_normalized) %>%
                  mutate(
                        total_coders_expert=total_coders_expert %>% replace(., is.nan(.), NA) %>% mean(na.rm=T) %>% replace(., is.nan(.), NA),
                        total_coders_undergrad=total_coders_undergrad %>% replace(., is.nan(.), NA) %>% mean(na.rm=T) %>% replace(., is.nan(.), NA)
                  ) %>%
                ungroup() %>%
                dplyr::select(-email_id) %>%
                dplyr::select(-confidence,-confidence_expert,-confidence_undergrad) %>%
                distinct() %>% #bc expert majority is maxed now these rows should be fine
                left_join(sentence_confidence_scores) %>%
                arrange(crisno,sentence_number_int_aligned, event_number_int_condition, 
                        variable_normalized, expert_majority %>% desc(), undergrad_majority %>% desc(), undergrad_majority %>% desc(), selected_by_any %>% desc() ) #event_number_int

options(warn = 1)

```

Self Reported Confidence and Percent Agreement

```{r}

confidence_totals <- bind_rows(
  icb_long_clean %>% filter(email_id %>% str_detect('expert') & variable_normalized=='raterconfidence' ) %>% count(value_normalized) %>% mutate(coder="expert") %>% mutate(n= (n/sum(n)*100) %>% round(1) %>% paste0("%") ),
  icb_long_clean %>% filter(email_id %>% str_detect('undergrad') & variable_normalized=='raterconfidence' ) %>% count(value_normalized)  %>% mutate(coder="undergrad") %>% mutate(n=(n/sum(n)*100) %>% round(1) %>% paste0("%"))
) %>%
  mutate(confidence=value_normalized %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
  mutate(x=0.05)

library(ggExtra)
p1_confidence_agreement <- 
  bind_rows(
    codings_long %>% dplyr::select(variable_normalized, value_normalized,  confidence=confidence_expert,  selected_by_perc=selected_by_experts_perc)  %>% mutate(coder="expert"),
    codings_long %>% dplyr::select(variable_normalized, value_normalized,  confidence=confidence_undergrad,  selected_by_perc=selected_by_undergrads_perc)  %>% mutate(coder="undergrad")
  ) %>% 
    filter(value_normalized!='' & is.finite(confidence)) %>%
    filter(selected_by_perc>0) %>% #only consider tokens that were selected at all by that group
    mutate(confidence=confidence %>% round() %>% as.factor() ) %>%
    group_by(confidence, coder) %>%
      mutate(selected_by_perc_mean=selected_by_perc %>% mean(na.rm=T))  %>%
    ungroup() %>%
    ggplot(aes(x=selected_by_perc,y=confidence, color=coder ))  + geom_boxplot(notch=T) + ggtitle('Individual Self Reported Confidence Predicts Intercoder Agreement') + theme_bw() +
    theme(legend.position="bottom") +
    xlab("Percent of Coders that Selected a Token") +
    ylab("Self Reported Confidence in Sentence Coding") +
    geom_text(data=confidence_totals %>% filter(coder=="expert"), aes(label=n,x=x, y=confidence-0.1, color=coder)) +
    geom_text(data=confidence_totals %>% filter(coder=="undergrad"), aes(label=n,x=x, y=confidence+0.3, color=coder)) +
    geom_point(aes(x=selected_by_perc_mean,y=confidence, color=coder ))
p1_confidence_agreement
#ggMarginal(p1_confidence_agreement,type = "histogram", groupColour = TRUE)
```

```{r}

#These are all by definition chosen by at least 1
p_percent_chose_tag_by_concept <- 
codings_long %>% 
  filter(value_normalized!='') %>%
  filter(total_coders>1) %>% #about 9k only had one coder
  dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc) %>%
  group_by(variable_normalized) %>%
    mutate(selected_by_any_perc_mean=selected_by_any_perc %>% mean()) %>%
  ungroup() %>%
  mutate(variable_normalized=fct_reorder(variable_normalized, selected_by_any_perc_mean)) %>%
  ggplot(aes(x=selected_by_any_perc, y=variable_normalized)) + geom_boxplot() + geom_point(aes(x=selected_by_any_perc_mean), color="red") +
  xlab("Percent of All Coders") +
  ylab("Concept") +
  labs(title = "Percent of All Coders who Chose Tag by Concept"#,
        #subtitle = "Plot of length by dose",
        #caption = "Data source: ToothGrowth"
       ) + 
  theme_bw()
p_percent_chose_tag_by_concept

table(expert_majority=codings_long$expert_majority,
      undergrad_majority=codings_long$undergrad_majority)

#58% of tokens including null have agreement from either experts, undergrads, or both
(table(expert_majority=codings_long$expert_majority,
      undergrad_majority=codings_long$undergrad_majority) / nrow(codings_long) ) %>% round(2)

table(codings_long$value_normalized != "")
# FALSE   TRUE 
#480,239 408,126 #about the same number of null tokens as non null ones
```

#Agreed

```{r}

#What we could do is say if there's
codings_long_agreement <- codings_long %>%
                          mutate(keep_majority_expert= 
                                    (selected_by_experts>=2 & #selected by at least two experts
                                     expert_majority==1)   
                           ) %>%
                           mutate(keep_majority_undergrad= (selected_by_experts>=1 & expert_majority==0 & undergrad_majority==1)  %>% as.numeric() ) %>%
                           mutate(keep_majority= (keep_majority_expert | keep_majority_undergrad) %>% as.integer() ) %>%
                           group_by(crisno, sentence_number_int_aligned, event_number_int_condition, variable_normalized) %>%
                                mutate(keep_majority_max=keep_majority %>% max(na.rm=T)) %>%
                                mutate(selected_by_any_max= selected_by_any %>% max(na.rmt=T)) %>%
                           ungroup() %>%
                           mutate(keep_leftstanding = (keep_majority==0 & #Wasn't picked by a majority
                                                         selected_by_experts>=1 & #was picked by a least one expert
                                                         selected_by_any_max==selected_by_any #Has the most total votes
                                                       ) %>% as.numeric() ) %>%
                           mutate(keep = ( keep_majority==1 | keep_leftstanding==1 ) %>% as.numeric() )

codings_long_agreement_393_43 <- codings_long_agreement %>% filter(crisno==393 & sentence_number_int_aligned==43 ) %>% janitor::remove_empty() 
codings_long_agreement_393_59 <- codings_long_agreement %>% filter(crisno==393 & sentence_number_int_aligned==59 )
codings_long_agreement_393_38 <- codings_long_agreement %>% filter(crisno==393 & sentence_number_int_aligned==38 )
codings_long_agreement_284_16 <- codings_long_agreement %>% filter(crisno==284 & sentence_number_int_aligned==16 )

codings_long_agreed <- codings_long_agreement %>%
                           filter(value_normalized!='')  %>%
                           filter(keep==1) %>% 
                           group_by(crisno, sentence_number_int_aligned) %>%
                              mutate(no_events= max( variable_normalized=="Event_Any" & value_normalized=="no") ) %>% #make sure you do the filter or this won't twork
                           ungroup()

dim(codings_long_agreed) #249,840     19  tokens that have agreement
codings_long_agreed %>% dplyr::select(keep_majority_expert, keep_majority_undergrad, keep_majority, keep_leftstanding) %>% summarise_all(sum)

(table(expert_majority=codings_long$expert_majority,
      undergrad_majority=codings_long$undergrad_majority) / nrow(codings_long) ) %>% round(2)
#               undergrad_majority
#expert_majority    0    1
#              0 0.40 0.04
#              1 0.40 0.16

#
#
#
#Maybe we use this as a screen on the original codings and then collect what survived to make subevents?
rex_paste <- function(x){ paste0(x %>% sort() %>% unique(), collapse=";")  }
codings_wide_agreed <- icb_long_clean  %>%
                      inner_join(codings_long_agreed) %>%
                      filter(email_id %>% str_detect('expert') ) %>%
                      dplyr::select(email_id,crisno,sentence_number_int_aligned, event_number_int, event_number_int_condition, sentence,variable_normalized, value_normalized) %>%
                      pivot_wider(id_cols=c(email_id,crisno,sentence_number_int_aligned, sentence,event_number_int, event_number_int_condition), names_from=variable_normalized, values_from=value_normalized, values_fn=rex_paste) %>%
                      group_by(crisno,sentence_number_int_aligned, event_number_int_condition, sentence, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>%
                      summarise_all(rex_paste)

codings_wide_agreed[codings_wide_agreed==""]<-NA

```
Validation Tests

```{r, eval=F}

keep_crisis=393
keep_sentence=38

(a <- icb_long_clean_original %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(b <- temp_long %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(c <- temp_wide %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty() )#%>% t()  ) #%>% View()
(d <- icb_long_clean %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(e <- codings_long %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()  ) #%>% View()
(f <- codings_long_agreement %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()   ) #%>% View()
(g <- codings_long_agreed %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence ) %>% janitor::remove_empty()   ) #%>% View()
(e <- codings_wide_agreed  %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% janitor::remove_empty()  ) %>% t() #%>% View()

```

```{r, eval=F}

write_csv(codings_long_agreed, paste0(here::here(), "/data_out/codings_long_agreed.csv"))
write_csv(codings_wide_agreed, paste0(here::here(), "/data_out/codings_wide_agreed.csv"))

```

# Convert codings to sentences

```{r}

#names(codings_wide_agreed)
library(ftExtra)
library(flextable)
library(ftExtra)
library(flextable)
library(glue)

#https://github.com/tidyverse/glue/issues/42
#On why you have to include parent frame https://github.com/tidyverse/glue/issues/42
glue_rex <- function(x) glue(x, .open = "{|",.close = "|}", .envir = parent.frame()) #escape variables in the more complicated {||} syntax
events <- NULL
event_to_sentence_rex <- function(events){

  sentence <- paste0("'",events[1,]$sentence,"'")
  df_temp <- NULL
  df_temp <- data.frame(
      type = c('S','E1','E2','E3','E4','E5','E6'), 
      text = c(sentence,NA,NA,NA,NA,NA,NA)
      )

  for(i in 1:nrow(events)){
    print(i)
    e1 <- NULL
    e1 <- events[i,, drop=F]
    say=NA
    say= glue_rex("[{|e1$say_actor_a|}]{.underline shading.color='white'} made an 
                  [{|ifelse(e1$say_aggression=='more aggression','aggressive', 'unaggressive')|}]{.underline shading.color='white'} 
                  [{|e1$leaf_say_simplified|}]{.underline shading.color='white'} to 
                  [{|e1$say_actor_b|}]{.underline shading.color='white'}.")

    consequence=NA
    consequence=ifelse(
      e1$consequence=="will happen",
      glue_rex("That the following will [happen]{.underline shading.color='white'}.") ,
      consquence
    )
    consequence=ifelse(
      e1$consequence=="won't happen",
      glue_rex("That if the following [won't happen]{.underline shading.color='white'}.") ,
      consequence
    )

    condition=NA
    condition=ifelse(
      e1$condition=="happens",
      glue_rex("If the following [happens]{.underline shading.color='white'}.") ,
      condition
    )
    condition=ifelse(
      e1$condition=="does not happen",
      glue_rex("If the following [does not happen]{.underline shading.color='white'}.") ,
      condition
    )

    do=NA
    do=ifelse(
      e1$do_Act_Interact=="Interact" & e1$event_number_int_condition==0,
      glue_rex("[{|e1$do_actor_a|}]{.underline shading.color='white'} 
                [{|ifelse(e1$do_aggression=='more aggression','aggressively', 'unaggressively')|}]{.underline shading.color='white'} 
                [{|e1$leaf_do_simplified|}]{.underline shading.color='white'} [{|e1$do_actor_b|}]{.underline shading.color='white'}.") ,
      do
    )
    do=ifelse(
      e1$do_Act_Interact=="Act" & e1$event_number_int_condition==0,
      glue_rex("[{|e1$do_actor_a|}]{.underline shading.color='white'} 
                [{|ifelse(e1$do_aggression=='more aggression','aggressively', 'unaggressively')|}]{.underline shading.color='white'} 
                [{|e1$leaf_do_simplified|}]{.underline shading.color='white'}.")  ,
      do
    )

    do=ifelse(
      e1$do_Act_Interact=="Interact" & e1$event_number_int_condition==1,
      glue_rex("(Condition) [{|e1$do_actor_a|}]{.underline shading.color='white'} 
                [{|ifelse(e1$do_aggression=='more aggression','aggressively', 'unaggressively')|}]{.underline shading.color='white'} 
                [{|e1$leaf_do_simplified|}]{.underline shading.color='white'} [{|e1$do_actor_b|}]{.underline shading.color='white'}.") ,
      do
    )
    do=ifelse(
      e1$do_Act_Interact=="Act" & e1$event_number_int_condition==1,
      glue_rex("(Condition) [{|e1$do_actor_a|}]{.underline shading.color='white'} 
                [{|ifelse(e1$do_aggression=='more aggression','aggressively', 'unaggressively')|}]{.underline shading.color='white'} 
                [{|e1$leaf_do_simplified|}]{.underline shading.color='white'}.")  ,
      do
    )

    final_coding=NA
    final_coding = ifelse(
      e1$Behavior=="Do",
      glue_rex("{|do|}"),
      final_coding
    )
    final_coding = ifelse(
      e1$Behavior=="Do;Say",
      glue_rex("{|say|} {|do|})"),
      final_coding
    )

    final_coding = ifelse(
      e1$Behavior=="Do;Say" & !is.na(consequence),
      glue_rex("{|say|} {|consequence|} {|do|}"),
      final_coding
    )
    final_coding = ifelse(
      e1$Behavior=="Do;Say" & !is.na(consequence) & !is.na(condition),
      glue_rex("{|say|} {|consequence|} {|do|} {|condition|}"),
      final_coding
    )

    if(length(final_coding)>0){
     df_temp$text[i+1] <- final_coding
    } else {next}
    #print(df_temp)
  }
  #print(df_temp)
  return(df_temp %>% mutate(text=text %>% as.character() )  %>% na.omit())
}

df_final <- NA
events1 <- codings_wide_agreed  %>% filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% janitor::remove_empty()  
asdfasdf <- event_to_sentence_rex(events1)

df_temp %>%
  dplyr::select(-type) %>%
  na.omit() %>%
  as_flextable() %>%
  colformat_md() %>% 
  width(width = 8)

```

# Old Ideas

```{r echo=FALSE, include=T, eval=F}

library(janitor)
#table(icb_wide_clean$email_id )
icb_wide_clean$email_id_expert <- icb_wide_clean$email_id %>% str_detect("grad|postgrad")

#icb_wide_clean$email_id_expert 
#icb_wide_clean$raterconfidence
#icb_wide_clean$raterconfidence_reason

icb_wide_clean %>% 
  tabyl(email_id_expert, raterconfidence, show_na = FALSE) %>%
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns()

icb_wide_clean  %>%
    mutate(raterconfidence_reason = raterconfidence_reason %>% str_replace_all("other|;","") %>% trimws() ) %>%
    filter(raterconfidence_reason!='')  %>%
    tabyl(raterconfidence_reason, show_na = FALSE) %>%
    arrange(desc(n)) %>%
    head() %>%
    mutate(percent=percent %>% round(2))

icb_long_clean$email_id_expert <- icb_long_clean$email_id %>% str_detect("grad|postgrad")

temp <- icb_long_clean %>%
        dplyr::select(email_id, email_id_expert, crisno, sentence_number_int_aligned, variable, value) %>%
        filter(!variable %in% c('date','say_actor_a','say_actor_b','do_actor_a','do_actor_b','think_actor_a','think_sentence_events','do_timing_reorder','sayintkind_react','do_timing_reorder',
                                'coder_crisis_order','point_in_time','start_time','end_time','earliest_date','preceding_event',
                                'act_cooperative','act_descalate act_escalate', 'act_uncooperative', 'interact_decreasecoop', 'interact_descalate', 'interact_escalate', 'interact_increasecoop',
                                'act_descalate','act_escalate','thinkkind','act_descalate','act_escalate','raterconfidence_reason_survey','raterconfidence_reason') &
                 !variable %>% str_detect("condition|actor|location_other|date|time")
               )

var_names <- temp %>% pull(variable) %>% unique()
library(fastDummies)
temp_wide <- temp %>% mutate(variable_value=paste0(variable,";",value)) %>% dplyr::select(-variable,-value) %>% dummy_cols(select_columns='variable_value', remove_selected_columns=T) 
dim(temp_wide)

temp_mean_expert <- temp_wide %>%
                    group_by(email_id_expert,email_id,crisno,sentence_number_int_aligned) %>% #max for that person across all events they found
                    summarise_if(is.numeric, max) %>%
                    dplyr::select(-email_id) %>%
                    group_by(email_id_expert,crisno,sentence_number_int_aligned) %>% #max for that person across all events they found
                    summarise_if(is.numeric, mean) %>%
                    ungroup()

temp_mean_expert_lomg <- temp_mean_expert %>%
                          filter(email_id_expert==T) %>%
                          ungroup() %>%
                          dplyr::select(-email_id_expert) %>% #,-email_id
                          pivot_longer(cols=-c(crisno,sentence_number_int_aligned)) %>%
                          mutate(value= abs(value-0.5)*2) %>% #0 means completely disagree 1 means completely agree
                          group_by(name) %>%
                          summarise(value=mean(value))

#only positives
temp_mean_expert_lomg_onlypos <- temp_mean_expert %>%
                                filter(email_id_expert==T) %>%
                                ungroup() %>%
                                dplyr::select(-email_id_expert) %>%
                                pivot_longer(cols=-c(crisno,sentence_number_int_aligned)) %>%
                                filter(value>0) %>% #only consider agreement when at least one coder uses the tag in that sentence
                                mutate(value= abs(value-0.5)*2) %>% #0 means completely disagree 1 means completely agree
                                rename(agreement=value) %>%
                                separate(name, c("variable", "value"), ";" ) %>%
                                group_by(variable) %>%
                                mutate(agreement_a=mean(agreement)) %>%
                                group_by(variable,value) %>%
                                mutate(agreement_b=mean(agreement)) %>%
                                ungroup() %>%
                                dplyr::select(-crisno, -sentence_number_int_aligned, -agreement) %>%
                                distinct()

#Confidence
temp2_confidence <- icb_long_clean %>%
                      dplyr::select(email_id, email_id_expert, crisno, sentence_number_int_aligned, raterconfidence, variable, value) %>%
                      filter(email_id_expert==T) %>%
                      filter(!variable %in% c('date','say_actor_a','say_actor_b','do_actor_a','do_actor_b','think_actor_a','think_sentence_events','do_timing_reorder','sayintkind_react','do_timing_reorder',
                                              'coder_crisis_order','point_in_time','start_time','end_time','earliest_date','preceding_event',
                                              'act_cooperative','act_descalate act_escalate', 'act_uncooperative', 'interact_decreasecoop', 'interact_descalate', 'interact_escalate', 'interact_increasecoop',
                                              'act_descalate','act_escalate','thinkkind','act_descalate','act_escalate','raterconfidence_reason_survey','raterconfidence_reason') &
                               !variable %>% str_detect("condition|actor|location_other|date|time")
                             ) %>%
                      mutate(raterconfidence=factor(raterconfidence, levels=c('None', 'Low', 'High',  'Complete') )) %>% 
                      group_by(variable) %>%
                      mutate(raterconfidence_a=raterconfidence %>% as.numeric() %>% mean(na.rm=T) %>% round(2)) %>%
                      group_by(variable, value) %>%
                      mutate(raterconfidence_b=raterconfidence %>% as.numeric() %>% mean(na.rm=T) %>% round(2)) %>%
                      ungroup() %>%
                      dplyr::select(-email_id, -email_id_expert, -crisno, -sentence_number_int_aligned, -raterconfidence) %>%
                      distinct()

```

```{r, eval=F, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}

intercoder_agreement_and_confidence_by_item <- temp_mean_expert_lomg_onlypos %>% 
                  mutate(variable=variable %>% str_replace_all("variable_value_|clean",""))  %>%
                  mutate(variable=variable %>% str_replace_all("_",""))  %>%
                  left_join(temp2_confidence %>% 
                                    mutate(variable=variable %>% str_replace_all("variable_value_|clean",""))  %>%
                                    mutate(variable=variable %>% str_replace_all("_","")) 
                            ) %>%
                  dplyr::arrange(desc(agreement_a), desc(agreement_b)) %>%
                  mutate(agreement_a=agreement_a %>% round(3)) %>% 
                  mutate(agreement_b=agreement_b %>% round(3))

intercoder_agreement_and_confidence_by_item %>%
                  flextable::as_flextable() %>%
                  flextable::bg( i = which( 1:nrow(temp_mean_expert_lomg_onlypos) %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
                  #merge_v(part = "body") %>% 
                  #flextable::width( j = 1, width=7) %>%
                  flextable::fontsize(size = 6, part = "body") %>%
                  #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
                  flextable::padding(padding = 0, part = "body")  %>%
                  flextable::merge_v(part = "body", combine = FALSE)

#Note Average intercoder agreement and self reported confidence look uncorrelated at the item level. I think it's because they're correlated at the sentence level, not the item level.
intercoder_agreement_and_confidence_by_item %>%
  ggplot(aes(x=agreement_b,y=raterconfidence_b)) +
  geom_point() + geom_smooth()

```

```{r, eval=F}

temp_jaccard <- icb_long_clean %>%
                      filter(email_id_expert==T) %>%
                      dplyr::select(email_id,  crisno, sentence_number_int_aligned,  variable, value) %>%

                      filter(!variable %in% c('date','say_actor_a','say_actor_b','do_actor_a','do_actor_b','think_actor_a','think_sentence_events','do_timing_reorder','sayintkind_react','do_timing_reorder',
                                              'coder_crisis_order','point_in_time','start_time','end_time','earliest_date','preceding_event',
                                              'act_cooperative','act_descalate act_escalate', 'act_uncooperative', 'interact_decreasecoop', 'interact_descalate', 'interact_escalate', 'interact_increasecoop',
                                              'act_descalate','act_escalate','thinkkind','act_descalate','act_escalate','raterconfidence_reason_survey','raterconfidence_reason') &
                               !variable %>% str_detect("condition|actor|location_other|date|time")
                             )

library(fastDummies)
temp_jaccard_wide <- temp_jaccard %>% mutate(variable_value=paste0(variable,";",value)) %>% dplyr::select(-variable,-value) %>% dummy_cols(select_columns='variable_value', remove_selected_columns=T) 
dim(temp_jaccard_wide)

temp_jaccard_wide %>% 
  #group_by(email_id,crisno,sentence_number_int_aligned) %>%
  pivot_longer(-c(email_id,crisno,sentence_number_int_aligned)) %>%
  arrange(email_id,crisno,sentence_number_int_aligned, name) %>%
  summarise()

```

### 2022-01-20 replication_paper/rmd/ICBEdataset_paper_uncertainty_bayesian.Rmd
Init

---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Pull specific examples

```{r, eval=F}

rex_paste <- function(x) { x %>% unique() %>% na.omit() %>% paste0(sep=";", collapse=";")}
rex_count <- function(x) { x %>% unique() %>% na.omit() %>% paste0(sep=";", collapse=";")}
sentence_variable_widecoder_Event_Any <-icb_long_clean  %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, variable_normalized, value_normalized) %>% 
  dplyr::filter(variable_normalized=='Event_Any') %>%
  dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
  dplyr::select(-variable_normalized, -event_number_int) %>%
  group_by(crisno,sentence_number_int_aligned) %>%
    mutate(coders=email_id %>% unique() %>% length()) %>%
    mutate(answers_unique=value_normalized %>% unique() %>% length()) %>%
    mutate(answer_modal= value_normalized %>% table() %>% sort() %>% rev() %>% .[1]) %>%
  ungroup() %>%
  mutate(answer_modal_perc= round( answer_modal/coders,2 )) %>%
  pivot_wider(id_cols=c(crisno,sentence_number_int_aligned, section, sentence,coders,answers_unique,answer_modal,answer_modal_perc), names_from=email_id,values_from=value_normalized, values_fn=rex_paste) %>%
  arrange(crisno,sentence_number_int_aligned)

#sentence_variable_widecoder %>%   View()

hist(sentence_variable_widecoder$answer_modal_perc)
table(sentence_variable_widecoder$answer_modal_perc)

```

```{r}

```

```{r, eval=F}

rex_paste <- function(x) { x %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";") %>% str_replace_all(";;",";")  } #
rex_count <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")  %>% str_replace_all(";;",";") } #

rex_count <- function(x) { x %>% na.omit() %>% table() %>% sort() %>% rev() %>% .[1] } #

temp2 <-icb_long_clean  %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, variable_normalized, value_normalized) %>% 
  #dplyr::filter(variable_normalized=='Event_Any') %>%
  dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
  dplyr::select(-event_number_int) %>%
  group_by(email_id, crisno,sentence_number_int_aligned, section, sentence,variable_normalized) %>%
    summarise(value_normalized=value_normalized %>% rex_paste() )

a <- icb_long_clean %>% filter(sentence %>% str_detect("And when Ethiopia perceived war as imminen")) 
a <- icb_long_clean %>% filter(crisno==47 & sentence_number_int_aligned==40) 
a %>% View()

b <- a %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, variable_normalized, value_normalized) %>% 
  #dplyr::filter(variable_normalized=='Event_Any') %>%
  dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
  dplyr::select(-event_number_int) %>%
  group_by(email_id, crisno,sentence_number_int_aligned, section, sentence,variable_normalized) %>%
    summarise(value_normalized=value_normalized %>% rex_paste() ) %>%
  group_by(crisno,sentence_number_int_aligned) %>%
    mutate(coders=email_id %>% unique() %>% length()) %>%
  ungroup() %>%
  group_by(crisno,sentence_number_int_aligned,variable_normalized) %>%
    mutate(coders=email_id %>% unique() %>% length()) %>%
    mutate(answers_unique=value_normalized %>% na.omit() %>% unique() %>% length()) %>%
    mutate(answer_modal= value_normalized %>% na.omit() %>% table() %>% sort() %>% rev() %>% .[1] ) %>%
    mutate(answer_modal_perc= round( answer_modal/coders,2 )) %>%
  ungroup() %>%
  pivot_wider(id_cols=c(crisno,sentence_number_int_aligned, section, sentence,variable_normalized,coders,answers_unique,answer_modal,answer_modal_perc), names_from=email_id,values_from=value_normalized, values_fn=rex_paste) %>%
  arrange(crisno,sentence_number_int_aligned,variable_normalized)

```

```{r}

icb_long_clean  %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, variable_normalized, value_normalized) %>% 
  dplyr::filter(variable_normalized=='sentence_events') %>%
  dplyr::select(-variable_normalized, -event_number_int) %>%
  pivot_wider(id_cols=c(crisno,sentence_number_int_aligned, section, sentence), names_from=email_id,values_from=value_normalized, values_fn=rex_paste) %>%
  arrange(crisno,sentence_number_int_aligned) %>%
  View()

temp <-icb_long_clean  %>% 
  dplyr::select(email_id,crisno,sentence_number_int_aligned, section, sentence, event_number_int, variable_normalized, value_normalized) %>% 
  dplyr::filter(variable_normalized=='Event_Count') %>%
  dplyr::filter(value_normalized!='' & !is.na(value_normalized)) %>%
  dplyr::select(-variable_normalized, -event_number_int) %>%
  group_by(crisno,sentence_number_int_aligned) %>%
    mutate(coders=email_id %>% unique() %>% length()) %>%
    mutate(answers_unique=value_normalized %>% unique() %>% length()) %>%
    mutate(answer_modal= value_normalized %>% table() %>% sort() %>% rev() %>% .[1]) %>%
  ungroup() %>%
  mutate(answer_modal_perc= round( answer_modal/coders,2 )) %>%
  pivot_wider(id_cols=c(crisno,sentence_number_int_aligned, section, sentence,coders,answers_unique,answer_modal,answer_modal_perc), names_from=email_id,values_from=value_normalized, values_fn=rex_paste) %>%
  arrange(crisno,sentence_number_int_aligned)

temp %>%   View()

hist(temp$answer_modal_perc)

```

Experimenting with flattening strategies

```{r}

#icb_long_clean %>%  filter(variable %>% str_detect('date')) %>%  pull(value) %>% tolower() %>% trimws() %>% unique() %>% length()  #9667
#icb_long_clean %>% filter(variable %>% str_detect('actor')) %>% pull(value) %>% tolower() %>% trimws() %>% unique() %>% length()  #2090
#icb_long_clean %>% filter(variable %>% str_detect('location')) %>% pull(value) %>% tolower() %>% trimws() %>% unique() %>% length()  #3766

icb_long_clean %>%   filter(!variable %>% str_detect('date|actor|location|sentence|reorder|react')) %>% dplyr::select(variable_normalized,value_normalized) %>% distinct() %>% nrow()  #3766

icb_long_clean %>% 
  filter(!variable %>% str_detect('date|actor|location|sentence|reorder|react|coder_crisis_order|preceding_event|time|condition_|raterconfidence_reason_survey|raterconfidence')) %>% 
  mutate(value=value %>% tolower()) %>% 
  dplyr::count(variable,value) %>%
  filter(n>1) #%>%  View() #About 270 unique values that show up more than once

icb_long_clean %>% 
  filter(variable %>% str_detect('actor')) %>% 
  mutate(value=value %>% tolower()) %>% 
  dplyr::count(variable,value) %>%
  filter(n>1) #%>%  View() #About 270 unique values that show up more than once

coder_sentence_event_dummy <-
          icb_long_clean %>% 
          dplyr::rename(variable =variable_normalized,value =value_normalized) %>%
          filter(!variable %>% str_detect('date|actor|location|think_sentence_events|reorder|react|coder_crisis_order|preceding_event|time|condition_|raterconfidence_reason_survey|raterconfidence')) %>% 
          mutate(value=value %>% tolower()) %>%
          dplyr::select(email_id,crisno,sentence_number_int_aligned,event_number_int, variable, value) %>% 
          mutate(variable=variable %>% str_replace('_other','')) %>% #make sure we kill others, don't care if it's an other
          distinct() %>%
          mutate(var_value=paste(variable,value,sep=";")) %>%
          fastDummies::dummy_cols(select_columns='var_value', remove_selected_columns=T) %>%
          dplyr::select(-variable, -value, -event_number_int) %>%
          group_by(crisno,sentence_number_int_aligned, email_id) %>%
            summarise_all(max, na.rm=T) 
dim(coder_sentence_event_dummy) #16031   252 other values
names(coder_sentence_event_dummy) <- names(coder_sentence_event_dummy) %>% str_replace('var_value_','')
names(coder_sentence_event_dummy)

#coder_sentence_event_dummy %>% dplyr::select(email_id,crisno,sentence_number_int_aligned, contains("event_type")) %>% View()
#coder_sentence_event_dummy %>% dplyr::select(email_id,crisno,sentence_number_int_aligned, contains("sentence_events")) %>% View()

coder_sentence_event_dummy_sentence <- coder_sentence_event_dummy %>% 
                                        dplyr::select(-email_id) %>%
                                        group_by(crisno,sentence_number_int_aligned) %>%
                                          mutate(coders=1) %>%
                                          summarise_all(sum, na.rm=T) %>%
                                        pivot_longer(cols=c(-crisno,-sentence_number_int_aligned)) %>%
                                        filter(value>0) %>%
                                        group_by(crisno,sentence_number_int_aligned) %>%
                                          mutate(coders=ifelse(name=="coders", value, NA)) %>%
                                          mutate(value=(value-1)/ (max(coders, na.rm=T)-1) ) %>%
                                        ungroup()  %>%
                                        mutate(value_count=1) %>%
                                        group_by(name) %>%
                                          mutate(value_count = value_count %>% sum() ) %>%
                                        ungroup()  %>%
                                        filter(name!='coders') %>%
                                        filter(value_count>1)
table(coder_sentence_event_dummy_sentence$value)
summary(coder_sentence_event_dummy_sentence$value)

coder_sentence_event_dummy_sentence %>% dplyr::select(name, value_count) %>% distinct() %>% View()

coder_sentence_event_dummy_sentence %>%
  group_by(name) %>%
  summarise(value_mean=mean(value, na.rm=T)) %>% View()

coder_sentence_event_dummy_sentence %>%
  group_by(name) %>%
  summarise(value_mean=mean(value, na.rm=T)) %>% pull(value_mean) %>% summary()

coder_sentence_event_dummy_sentence %>% 
  separate(name, c("A", "B"), sep=";") %>%
  group_by(A) %>%
  summarise(value_mean=mean(value, na.rm=T)) %>% View()

actor_keep <- icb_long_clean %>% 
                dplyr::select(-variable,-value) %>% dplyr::rename(variable =variable_normalized,value =value_normalized) %>%
                filter(variable %>% str_detect('actor')) %>% 
                filter(!variable %in% non_clean_versions) %>%
                mutate(value=value %>% tolower()) %>% 
                dplyr::count(value) %>%
                filter(n>1) %>% 
                na.omit() %>%
                mutate(value=value %>% str_replace('https://en.wikipedia.org/wiki/','')) %>%
                filter(!value %in% c("no_cleaning", "drop"))
                #View() #About 395

coder_sentence_event_actor_dummy <-
          icb_long_clean %>% 
          dplyr::select(-variable,-value) %>%
          dplyr::rename(variable =variable_normalized,value =value_normalized) %>%
          filter(variable %>% str_detect('actor|sentence_events')) %>% 
          filter(!variable %in% non_clean_versions)  %>%
          mutate(value=value %>% tolower()) %>%
          mutate(value=value %>% str_replace('https://en.wikipedia.org/wiki/','')) %>%
          filter(value %in% c(actor_keep$value) | event_number_int=='0' ) #I think as long as we add event_number_int then we get a row for every coder including who said no events

#Whether the actor is mentioned at all
c <- coder_sentence_event_actor_dummy %>% 
      dplyr::select(email_id,crisno,sentence_number_int_aligned,event_number_int, variable, value) %>% 
      mutate(variable=variable %>% str_replace('_clean','')) %>%
      mutate(variable=variable %>% str_replace('_other','')) %>% #make sure we kill others, don't care if it's an other
      mutate(variable=variable %>% str_replace('_a$|_b$','')) %>%
      mutate(variable=variable %>% str_replace('^do_|^say_|condition_do_|think_','')) %>%
      distinct() %>%
      mutate(var_value=paste(variable,value,sep=";")) %>%
      fastDummies::dummy_cols(select_columns='var_value', remove_selected_columns=T) %>%
      dplyr::select(-variable, -value, -event_number_int) %>%
      group_by(crisno,sentence_number_int_aligned, email_id) %>%
        summarise_all(max, na.rm=T) 
names(c) <- names(c) %>% str_replace('var_value_','')
dim(c) #26789 336

c_sentence <- c %>% 
              #dplyr::select(-email_id) %>%
              group_by(crisno,sentence_number_int_aligned) %>%
              summarise_all(mean, na.rm=T) %>%
              pivot_longer(cols=c(-crisno,-sentence_number_int_aligned)) %>%
              filter(value>0) %>%
              filter(!name %>% str_detect('sentence_events'))

#Actors by type ignoring direction
b <- coder_sentence_event_actor_dummy %>% 
      dplyr::select(email_id,crisno,sentence_number_int_aligned,event_number_int, variable, value) %>% 
      mutate(variable=variable %>% str_replace('_clean','')) %>%
      mutate(variable=variable %>% str_replace('_other','')) %>% #make sure we kill others, don't care if it's an other
      mutate(variable=variable %>% str_replace('_a$|_b$','')) %>% 
      distinct() %>%
      mutate(var_value=paste(variable,value,sep=";")) %>%
      fastDummies::dummy_cols(select_columns='var_value', remove_selected_columns=T) %>%
      dplyr::select(-variable, -value, -event_number_int) %>%
      group_by(crisno,sentence_number_int_aligned, email_id) %>%
        summarise_all(max, na.rm=T) 
names(b) <- names(b) %>% str_replace('var_value_','')

b_sentence <- b %>% 
              #dplyr::select(-email_id) %>%
              group_by(crisno,sentence_number_int_aligned) %>%
                summarise_all(mean, na.rm=T) %>%
              pivot_longer(cols=c(-crisno,-sentence_number_int_aligned)) %>%
              filter(value>0) %>%
              filter(!name %>% str_detect('sentence_events'))
summary(b_sentence$value)
dim(b) #26789   918

#Actors by type and direction
a <- coder_sentence_event_actor_dummy %>% 
      dplyr::select(email_id,crisno,sentence_number_int_aligned,event_number_int, variable, value) %>% 
      mutate(variable=variable %>% str_replace('_clean','')) %>%
      mutate(variable=variable %>% str_replace('_other','')) %>% #make sure we kill others, don't care if it's an other
      distinct() %>%
      mutate(var_value=paste(variable,value,sep=";")) %>%
      fastDummies::dummy_cols(select_columns='var_value', remove_selected_columns=T) %>%
      dplyr::select(-variable, -value, -event_number_int) %>%
      group_by(crisno,sentence_number_int_aligned, email_id) %>%
        summarise_all(max, na.rm=T) 
names(a) <- names(a) %>% str_replace('var_value_','')
dim(a) #26789  1454

a_sentence <- a %>% 
              #dplyr::select(-email_id) %>%
              group_by(crisno,sentence_number_int_aligned) %>%
                summarise_all(mean, na.rm=T) %>%
              pivot_longer(cols=c(-crisno,-sentence_number_int_aligned)) %>%
              filter(value>0) %>%
              filter(!name %>% str_detect('sentence_events'))
summary(a_sentence$value)

#I Think what this means is that multiply these probabilities and it helps to

```

```{r}

library(dplyr, warn.conflicts = FALSE)
options(warn=-1)

icb_long_clean$email_id_expert <- icb_long_clean$email_id %>% str_detect("grad|postgrad")

#icb_long_clean %>% dplyr::select(variable) %>% distinct() %>% View()

paste_collapse=function(x) paste(x %>% sort(), collapse=";") %>% str_replace_all("https://en.wikipedia.org/wiki/",'') #sorting removes the order indeterminacy
actors_clean <- icb_long_clean %>%
                filter(variable %>% str_detect('actor') & variable %>% str_detect('clean')) %>%
                mutate(variable=variable %>%str_replace('other_','')) %>% #removing the text other from the variable will auto include it in our list here
                pivot_wider(names_from=variable,
                            values_from=value,
                            values_fn=paste_collapse
                            ) %>%
                 dplyr::mutate(think_actor_a_clean = strsplit(as.character(think_actor_a_clean), ";")) %>% tidyr::unnest(think_actor_a_clean) %>% dplyr::mutate(think_actor_a_clean=think_actor_a_clean %>% trimws()) %>%
                 dplyr::mutate(say_actor_a_clean = strsplit(as.character(say_actor_a_clean), ";")) %>% tidyr::unnest(say_actor_a_clean) %>% dplyr::mutate(say_actor_a_clean=say_actor_a_clean %>% trimws()) %>%
                 dplyr::mutate(say_actor_b_clean = strsplit(as.character(say_actor_b_clean), ";")) %>% tidyr::unnest(say_actor_b_clean) %>% dplyr::mutate(say_actor_b_clean=say_actor_b_clean %>% trimws()) %>%
                 dplyr::mutate(do_actor_a_clean = strsplit(as.character(do_actor_a_clean), ";")) %>% tidyr::unnest(do_actor_a_clean) %>% dplyr::mutate(do_actor_a_clean=do_actor_a_clean %>% trimws()) %>%
                 dplyr::mutate(do_actor_b_clean = strsplit(as.character(do_actor_b_clean), ";")) %>% tidyr::unnest(do_actor_b_clean) %>% dplyr::mutate(do_actor_b_clean=do_actor_b_clean %>% trimws()) 
                  #currently ignoring condition
dim(actors_clean)

#I think we convert this to actor-event, where every lhs actor mentioned gets a row and then we ask what people thought THEY did in that sentence
temp_long <- icb_long_clean %>%
             filter(!variable %>% str_detect('actor') ) %>%
            dplyr::select(icb_survey_version, email_id,  crisno, sentence_number_int_aligned, section, event_number_int,  variable, value) %>%
            filter(variable %in% c(
                                   'sentence_events',
                                   'act_cooperative',
                                   'act_descalate', 
                                   'act_escalate',
                                   'act_uncooperative',
                                   'interact_decreasecoop',
                                   'interact_descalate',
                                   'interact_escalate',
                                   'interact_increasecoop',
                                   'thinkkind',
                                   'sayintkind'
                                   ) 
                        ) %>% distinct() %>% 
                  mutate(value= value %>% trimws() %>% tolower()) %>%
                  #left_join(full_tree %>% dplyr::select(Behavior, value=Leaf) %>% 
                  #            mutate(value= value %>% trimws() %>% tolower())) %>%
                  left_join(full_tree %>% dplyr::rename(value=Leaf)  %>%
                              mutate(value= value %>% trimws() %>% tolower()) ) %>%
              group_by(email_id,  crisno, sentence_number_int_aligned) %>%
                mutate(event_number_int_max=max(event_number_int, na.rm=T)) %>%
              ungroup() %>%
              full_join(
                actors_clean %>% dplyr::select(email_id,  crisno, sentence_number_int_aligned,  event_number_int,  contains('actor')) %>%
                  dplyr::select(-condition_do_actor_a_clean,-condition_do_actor_b_clean) #ignoring conditions for now
              )

#temp_long %>% dplyr::select(value, Behavior) %>% distinct() %>% View()

#i_think_actor_a=, #we're going to join on these
#i_say_actor_a=,
#i_say_actor_b=,
#i_do_actor_a=,
#i_do_actor_b=,

#Starting first with the 63% of the time they saw only 1 event
events_variable_value <- temp_long %>%
                                #filter(!is.na(Behavior )) %>%
                                #filter(event_number_int_max==1) %>%

                                mutate(index=paste(crisno , sentence_number_int_aligned ,  think_actor_a_clean,say_actor_a_clean,say_actor_b_clean,do_actor_a_clean,do_actor_b_clean, sep="_")) %>% #add actors to this
                                #filter(!index %>% str_detect('_NA_NA_NA_NA_NA')) %>% #ignore 
                                dplyr::select(icb_survey_version,
                                              email_id,
                                              index, 
                                              crisno,
                                              sentence_number_int_aligned,
                                              section,
                                              #contains('actor'),
                                              Event_Count,
                                              Behavior,
                                              think_aggression,
                                              say_aggression,
                                              do_aggression,
                                              Do_Armed_Unarmed,
                                              do_Act_Interact,
                                              Think_Type_L0,
                                              Say_Type_L0,
                                              Do_Type_L0,
                                              Leaf_Simplified#,
                                              #variable,
                                              #value
                                              )

#This actually takes a while now that there are dead
library(fastDummies)
#I think we do physically have to go to wide
events_wide_i <- events_variable_value %>% 
                                       rename(i_email_id=email_id,
                                              i_Event_Count=Event_Count,
                                              i_Behavior=Behavior,
                                              i_think_aggression=think_aggression,
                                              i_say_aggression=say_aggression,
                                              i_do_aggression=do_aggression,
                                              i_Do_Armed_Unarmed=Do_Armed_Unarmed,
                                              i_do_Act_Interact=do_Act_Interact,
                                              i_Think_Type_L0=Think_Type_L0,
                                              i_Say_Type_L0=Say_Type_L0,
                                              i_Do_Type_L0=Do_Type_L0,
                                              i_Leaf_Simplified=Leaf_Simplified
                                              ) %>%
                                       fastDummies::dummy_cols(select_columns='i_Event_Count', remove_selected_columns=T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Behavior', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_think_aggression', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_say_aggression', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_do_aggression', remove_selected_columns=T, ignore_na = T) %>%

                                       fastDummies::dummy_cols(select_columns='i_Do_Armed_Unarmed', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_do_Act_Interact', remove_selected_columns=T, ignore_na = T) %>%  
                                       fastDummies::dummy_cols(select_columns='i_Think_Type_L0', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Say_Type_L0', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Do_Type_L0', remove_selected_columns=T, ignore_na = T) %>%
                                       fastDummies::dummy_cols(select_columns='i_Leaf_Simplified', remove_selected_columns=T, ignore_na = T) %>%
                                       group_by(i_email_id,index) %>%
                                        summarise_all(max, na.rm=T) %>% #max not sum
                                       ungroup() %>%
                                       mutate_if(is.numeric, function(x) ifelse(is.infinite(x), 0, x))
dim(events_wide_i) #113049    116
#events_wide_j <- events_wide_i
#names(events_wide_j) <- events_wide_j %>% names() %>% str_replace("^i_","j_")
#dim(events_wide_j) #67558   106
```

Let's take this in stages, how many events should be in that sentence?

```{r}

events_wide_i_event_count <- events_wide_i %>% 
                             dplyr::select(icb_survey_version, crisno,section,sentence_number_int_aligned,index,i_email_id,contains('Event_Count')) %>% 
                             mutate(index=index %>% str_replace("_[A-Za-z].*$",'')) %>% 
                             #mutate(crisis=crisis %>% str_replace("_[A-Za-z].*$",'')) %>% 
                             group_by(crisno,section,index, i_email_id) %>%
                             summarise_all(max, na.rm=T) %>%
                             janitor::clean_names() %>%
                             dplyr::select(-i_event_count_na) %>%
                             mutate(i_event_count_thresholded= ((i_event_count_1 + i_event_count_2 + i_event_count_3)>0 )%>% as.numeric())

#First decide whether 0 or more
#Then decide given that why or how many

events_wide_i_event_count_thresholded <- events_wide_i_event_count %>% 
                                         dplyr::select(icb_survey_version, index,i_email_id,crisno,section,sentence_number_int_aligned,i_event_count_thresholded) %>%
                                         mutate(expert=i_email_id %>% str_detect('grad') %>% as.numeric() )

events_wide_i_event_count_thresholded %>% saveRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))

```

```{r}

library(tidyverse)
events_wide_i_event_count_thresholded <- readRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))

library(brms)
xy_train <- events_wide_i_event_count_thresholded %>% 
  arrange(icb_survey_version, crisno, sentence_number_int_aligned) %>%
  filter(!is.na(section)) %>% #there is exactly one mising value for section and I don't know why
  group_by(i_email_id) %>%
     mutate(i_email_id_count=n()) %>%
  ungroup() %>%
  filter(i_email_id_count>100) #%>% #only care about grads with more than 100 coders
  #head(12000) #First confirm that we can fit all this with STAN and it matches
  #
dim(xy_train) #44743
xy_train$index %>% unique() %>% length() #1k #1500 #12332
xy_train$i_email_id %>% unique() %>% length() #76 #113

#xy_predict <- xy_train %>% 
#              dplyr::filter(i_email_id %>% str_detect('grad')) %>% ungroup()  %>%
#              tidyr::expand(crossing(index, i_email_id)) %>%
#              left_join(xy_train %>% dplyr::select(icb_survey_version, index, crisno, section,sentence_number_int_aligned) %>% distinct() %>% mutate(expert=1) )

#https://www.muscardinus.be/2017/07/lme4-random-effects/
#Implicit nesting
#With implicit nesting, the nesting is ‘defined’ in the data. That is each level of a random effect has a one-to-many relation with the levels of the lower random effect. E.g. each class id is unique for a given class in a given #school and cannot refer to a class in any other school. This is how we constructed the class2 variable in our data. With implicit nesting the code can be abbreviated to (1|A) + (1|B). Note that the (1|A) + (1|A:B) and (1|A/B) #notations remain valid.

#Full interaction
#This takes a long time to compile for some reason
formula_event_count <- bf(i_event_count_thresholded ~ 
                            1 + #an intercept across all sentences
                            # + #each crisis might have more or less events, Cuban Missile should be pretty weird and we probably want to handle it carefully
                            # + #we know the sections are different
                            #section +
                            #expert +
                            #section:expert +
                            #expert + #This is like a global intercept for expert
                            (1 + section + crisno | i_email_id) + #we additionally think individual coders behaved differently even when on the same text
                            #We let each sentence's theta have an novice level and an expert level
                            (1 + expert + icb_survey_version | index)  # + #leaving the properties of the sentence itself
                            #We let each crisis have an effect that varies by section
                            #(1 |  crisno)   #leaving the properties of the sentence itself
)

formula_event_count <- bf(i_event_count_thresholded ~ 
                            1 + 
                            (1 + section + crisno | i_email_id) 
                            (1 + expert + icb_survey_version | index)  
)

xy_train$w <- xy_train$expert*10 #experts are worth 10 undergrads
formula_event_count <- bf(i_event_count_thresholded|weights(w) ~ 
                            1 + 
                            icb_survey_version +
                            (1 | i_email_id) +
                            (1 | index) #+ expert   #conditioning on expert makes the model so slow
)

#library(lme4)
#lme_rasch = glmer(formula_event_count,
#                  xy_train, 
#                  family=binomial(link='logit'))
#summary(lme_rasch, cor=F)

get_prior(formula_event_count,
          data = xy_train,
          family = brmsfamily("bernoulli", "logit")
          )

#Pick some weak but at least not uniform priors
prior_event_count <- 
  prior("normal(0, 3)", class = "sd")  #+ 
  #The two random effects get priors, the fixed effects don
  #prior("cauchy(0,3)", class = "sd")  + 
  #prior("normal(0, 3)", class = "sd", group = "index") +
  #prior("normal(0, 3)", class = "sd", group = "i_email_id") #+
  prior("normal(0, 3)", class = "b") #+
  #prior("normal(0, 3)", class = "Intercept", group = "expert")

library(cmdstanr)
#install_cmdstan(cores = 4)
#We don't actually care about running this, we just want it to create the rstan for us to feed into numpyo
#oh fun, I have no way of knowing if these coefficients are ordered the same way in both numpyro and here. Better hope so.
file_rstan=paste0(here::here(), "/data_temp/fit_event_count/fit_event_count_fornumpyro.rstan")
fit_event_count_fornumpyro <- brm(
  formula = formula_event_count,
  data = xy_train, 
  family = brmsfamily("bernoulli", "logit"),
  prior = prior_event_count,
  file = paste0(here::here(), "/data_temp/fit_event_count/fit_event_count_fornumpyro"),
  save_model=file_rstan,
  #opencl = opencl(c(0, 0)),
  backend = "cmdstan",
  file_refit="always",
  warmup=1,
  iter=2,
  chains = 1, 
  cores = 1 
)

#Efit out the prior only part because it throws numpyro
tx  <- readLines(file_rstan) %>% paste(collapse="\n") #there's already a\n
tx  <- gsub(pattern = "  if \\(!prior_only\\) \\{", replace = "", x = tx)
tx  <- gsub(pattern = "  \\}\n  // priors including constants", replace = "", x = tx)
writeLines(tx, con=file_rstan)

#It looks like we can make the stan data here
standata_fornumpyro <- make_standata(
  formula = formula_event_count,
  data = xy_train, 
  family = brmsfamily("bernoulli", "logit"),
  warmup=1,
  iter=2,
  chains = 1, 
  cores = 1 
)

```

#need this too
```{r}

#Looks like the exact ordering of the fixed effects, good
colnames(standata_fornumpyro$X)

#fit_event_count_fornumpyro_summary <- summary(fit_event_count_fornumpyro)
#fit_event_count_fornumpyro_summary$fixed #IF these are in the same order then they match up
#Doesn't get us the random effects though

#fit_event_count_fornumpyro_coef <- coef(fit_event_count_fornumpyro) #This probably does but takes forever

```

```{r}

#Setting the priors radically slows it down now and I don't know why
fit_stan=F
library(tictoc)
if(fit_stan){
  tictoc::tic()
    file_rstan=paste0(here::here(), "/data_temp/fit_event_count/fit_event_count_fornumpyro.rstan")
    fit_event_count_for_comparison <- brm(
      formula = formula_event_count,
      data = xy_train, 
      family = brmsfamily("bernoulli", "logit"),
      prior = prior_event_count,
      file = paste0(here::here(), "/data_temp/fit_event_count/fit_event_count_fornumpyro"),
      save_model=file_rstan,
      #opencl = opencl(c(0, 0)), #is much slower for some reason
      backend = "cmdstan",
      file_refit="always",
      warmup=1000,
      iter=2000,
      chains = 4, 
      cores = 64,
      threads = threading(8)
    ) #is actually pretty fast on small models
  tictoc::toc() #Providing less prior made this go slower
  #takes about 10 minutes for 2k
  #Whole thing runs in 10 minutes now with reasonable priors and threading 8
  #17 seconds for 2k
  #threading(4) 116
  #threading(8) 90
  #threading(16) 189
  #Much faster with reasonable priors, gets it down to 90 seconds

  fit_event_count_for_comparison_coef <- coef(fit_event_count_for_comparison, probs = c(0.05,0.25,0.75, 0.95))
  fit_event_count_for_comparison_fixef <- fixef(fit_event_count_for_comparison)
  fit_event_count_for_comparison_ranef <- ranef(fit_event_count_for_comparison, probs = c(0.05, 0.95))

  sentences <- xy_train %>% group_by(index,expert) %>% 
    summarise(
                i_event_count_thresholded_pos=sum(i_event_count_thresholded==1),
                i_event_count_thresholded_neg=sum(i_event_count_thresholded==0)
              ) %>%
    mutate(i_event_count_thresholded_total=i_event_count_thresholded_pos-i_event_count_thresholded_neg) %>%
    pivot_longer(cols=i_event_count_thresholded_pos:i_event_count_thresholded_total) %>%
    mutate(name=name %>% paste0("_expert",expert)) %>% dplyr::select(-expert) %>%
    pivot_wider(id_cols=index) %>%
    rowwise() %>%
      mutate(i_event_count_thresholded_total= sum(i_event_count_thresholded_total_expert0,i_event_count_thresholded_total_expert1, na.rm=T)) %>%
    ungroup()
  sentences$theta <- fit_event_count_for_comparison_ranef$index[,, "Intercept"][,1] #The direction isn't identified so we have to flip this so it matches whatever the highest score is
  sentences$theta_Q5 <- fit_event_count_for_comparison_ranef$index[,, "Intercept"][,3] #The direction isn't identified so we have to flip this so it matches whatever the highest score is
  sentences$theta_Q95 <- fit_event_count_for_comparison_ranef$index[,, "Intercept"][,4] #The direction isn't identified so we have to flip this so it matches whatever the highest score is

  tictoc::tic()
    file_rstan_SVI=paste0(here::here(), "/data_temp/fit_event_count/fit_event_count_SVI.rstan")
    fit_event_count_for_comparison_SVI <- brm(
      formula = formula_event_count,
      data = xy_train, 
      family = brmsfamily("bernoulli", "logit"),
      prior = prior_event_count,
      file = paste0(here::here(), "/data_temp/fit_event_count/fit_event_count_SVI"),
      save_model=file_rstan_SVI,
      #opencl = opencl(c(0, 0)), #is much slower for some reason
      backend = "rstan", #have to use rstan, there's a bug report that's fixed this but not merged for cmdstan https://github.com/paul-buerkner/brms/issues/1189
      file_refit="always",
      #warmup=1000,
      iter=10000,
      chains = 4, 
      cores = 64,
      #threads = threading(8),
      algorithm = "meanfield",
      tol_rel_obj = 0.000000001
    ) #is actually pretty fast on small models
  tictoc::toc() #Providing less prior made this go slower

}

fit_event_count_for_comparison_summary <- summary(fit_event_count_for_comparison)
fit_event_count_for_comparison_SVI_summary <- summary(fit_event_count_for_comparison_SVI) #ok we're getting comparable results now

#Ok with reasonable priors for SVI and it agree
cor(fit_event_count_for_comparison_SVI_summary$fixed$Estimate, fit_event_count_for_comparison_summary$fixed$Estimate)
plot(fit_event_count_for_comparison_SVI_summary$fixed$Estimate, fit_event_count_for_comparison_summary$fixed$Estimate)

fit_event_count_for_comparison_coef <- coef(fit_event_count_for_comparison)
fit_event_count_for_comparison_SVI_coef <- coef(fit_event_count_for_comparison_SVI)

cor(fit_event_count_for_comparison_coef$index[,, "Intercept"][,1], fit_event_count_for_comparison_SVI_coef$index[,, "Intercept"][,1]) #0.9962559
plot(fit_event_count_for_comparison_coef$index[,, "Intercept"][,1], fit_event_count_for_comparison_SVI_coef$index[,, "Intercept"][,1])

cor(sentences$theta,sentences$i_event_count_thresholded)

```

```{r coef-item-va-1pl, echo=FALSE, fig.width=8, fig.cap = "Posterior means and 95\\% credible intervals of item parameters as estimated by model \\code{fit\\_va\\_1pl}."}
#coef_fit_event_count <- coef(fit_event_count)

fit_event_count_for_comparison_coef$index[, , "Intercept"] %>%
	as_tibble() %>% 
  #head(1000) %>%
  arrange(Estimate) %>%
	rownames_to_column() %>%
	rename(item = "rowname") %>%
	mutate(item = as.numeric(item)) %>%
	ggplot(aes(item, Estimate, ymin = Q5, ymax = Q95)) +
	geom_pointrange(aes(item, Estimate, ymin = Q5, ymax = Q95),color="grey", alpha=.2) +
	geom_pointrange(aes(item, Estimate, ymin = Q25, ymax = Q75),color="orange", alpha=.2) +
	geom_point(aes(item, Estimate),color="black", alpha=.2) +
	coord_flip() +
  ggtitle("Evidence that Sentence Has Event(s)",
          subtitle = "Bayesian IRT Model") +
	xlab( "Crisis_Sentence") +
	ylab( "Latent Variable- Sentence has event(s)")

```

```{r coef-item-va-1pl, echo=FALSE, fig.width=8, fig.cap = "Posterior means and 95\\% credible intervals of item parameters as estimated by model \\code{fit\\_va\\_1pl}."}

fit_event_count_for_comparison_coef$i_email_id[, , "Intercept"] %>%
  as.data.frame() %>%
  rownames_to_column() %>%
	as_tibble() %>%
  arrange(Estimate) %>%
  mutate(rowname=fct_reorder(rowname, Estimate)) %>%
	#rownames_to_column() %>%
  mutate(expert=rowname %>% str_detect("grad")) %>%
	#rename(item = "rowname") %>%
	#mutate(item = as.numeric(item)) %>%
	ggplot(aes(rowname, Estimate, ymin = Q2.5, ymax = Q97.5, color=expert)) +
	geom_pointrange() +
	coord_flip() +
	labs(x = "i_email_id")

```

```{r coef-item-va-1pl, echo=FALSE, fig.width=8, fig.cap = "Posterior means and 95\\% credible intervals of item parameters as estimated by model \\code{fit\\_va\\_1pl}."}

fit_event_count_for_comparison_coef$crisno[, , "Intercept"] %>%
  as.data.frame() %>%
  rownames_to_column() %>%
	as_tibble() %>%
  arrange(Estimate) %>%
  mutate(rowname=fct_reorder(rowname, Estimate)) %>%
	#rownames_to_column() %>%
  #mutate(expert=rowname %>% str_detect("grad")) %>%
	#rename(item = "rowname") %>%
	#mutate(item = as.numeric(item)) %>%
	ggplot(aes(rowname, Estimate, ymin = Q2.5, ymax = Q97.5)) +
	geom_pointrange() +
	coord_flip() +
	labs(x = "crisno")

```

```{python}

#Somehow 4k took numpyro 27 minutes which makes me think either it isn't optimized correctly or I've screwed up the cpu configuration. Going to switch to GPU and hope that fixes it.
import os
cwd = os.getcwd()
os.chdir('/mnt/8tb_a/rwd_github_private/ICBEdataset/data_temp/fit_event_count/')) #even though I changed it, it went and put the tmp file back in paper
from stannumpyro import NumPyroModel
from jax import random

import numpyro
import numpyro.distributions as dist
import jax
numpyro.set_platform("gpu")
#numpyro.set_host_device_count(4) #If on cpu pick the number of chains you expect to run
print(jax.__version__)
print(numpyro.__version__)
print(jax.config.FLAGS.jax_backend_target)
print(jax.lib.xla_bridge.get_backend().platform)

if __name__ == "__main__":

    stanfile = "/mnt/8tb_a/rwd_github_private/ICBEdataset/data_temp/fit_event_count/fit_event_count_fornumpyro.rstan"
    #eval $(opam env) #has to be run, currently doing it in profile
    #It doesn't let you run this twice! Had to restart python to get it to switch names
    #If you specify a build folder it throws an errob tu does make it
    model = NumPyroModel(stanfile=stanfile, recompile=True, mode='comprehensive', compiler=['stanc'] )

    data1 = {
        'J': 8,
        'y': [28.0, 8.0, -3.0, 7.0, -1.0, 1.0, 18.0, 12.0],
        'sigma': [15.0, 10.0, 16.0, 11.0, 9.0, 11.0, 10.0, 18.0]
    }

    data=r.standata_fornumpyro

    #Lists wasn't the problem
    #data_2=data
    #for key in data_2.keys():
    #  if type(data_2[key])==type(np.array(0)):
    #    data_2[key]=data_2[key].tolist()
    #data['grainsize']=100 #For some reason it expecs a grain size switched to commander stand and didn't get this error

    mcmc = model.mcmc(
        samples = 2000,
        warmups = 1000,
        chains=1,
        thin=1,
    ) #minute 40 for 2k samples 500 warmup 1 chain
    #falling back to cpu did not fix this error
    #TypeError: true_fun and false_fun output must have same type structure,
    #got PyTreeDef((None, CustomNode(<class 'numpyro.contrib.control_flow.util.PytreeTrace'>[({'_expr__8': {'_control_flow_done': True, 'type': 'sample', 'name': '_expr__8', 'kwargs': {'rng_key': None, 'sample_shape': ()}, 'scale': None, 'is_observed': True, 'cond_indep_stack': [], 'infer': {}}}, ['_expr__8'])], [{'_expr__8': {'args': (), 'fn': CustomNode(<class 'numpyro.distributions.distribution.Unit'>[None], [*]), 'intermediates': [], 'value': *}}]))) and
    #PyTreeDef((None, CustomNode(<class 'numpyro.contrib.control_flow.util.PytreeTrace'>[({}, [])], [{}]))).

    mcmc.run(random.PRNGKey(0), data) #amazingly it works #it can't handle threaded version
    print(mcmc.summary())
    results=mcmc.summary() #ok the first betas are the fixed effects

#ok 4 chains is 1:51 on cpu with numpyro

```

```{r}
py$results %>% View()

```

```{r}

#Just in practical terms, 40k takes way too long.

#install.packages("cmdstanr", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
#install_cmdstan()
library(cmdstanr)
#unlink(paste0(here::here(), "/data_temp/model_fits"), force = T, recursive = T)
library(tictoc)
tic()
  fit_event_count <- brm(
    formula = formula_event_count,
    data = xy_train, 
    family = brmsfamily("bernoulli", "logit"),
    prior = prior_event_count,
    file = paste0(here::here(), "/data_temp/fit_event_count/fit_event_count"),
    save_model=paste0(here::here(), "/data_temp/fit_event_count/fit_event_count.rstan"),
    chains = 4, 
    cores = 64, 
    #opencl = opencl(c(0, 0)),
    backend = "cmdstanr",
    threads = threading(4) #4k 0 was 17.2 #2 was 20.1, #4 was 15.1  #8 was 15.3 , 16 was 18.1
    #107.4 seconds., 4 69.5 seconds 8 77.7
    #20k 4 662.3
  )
toc()

pp <- predict(fit_event_count, newdata=xy_predict, probs = c(0.1, 0.90))

xy_predicted <- cbind(xy_predict , pp)

xy_predicted %>% 
  group_by(index, crisno,section,sentence_number_int_aligned) %>% 
  summarize(Estimate=mean(Estimate)) %>% 
  arrange(crisno,section,sentence_number_int_aligned) %>%
  left_join(xy_train %>% 
              filter(expert==1) %>%
              group_by(index) %>% 
              summarise(expert_mean= sum(i_event_count_thresholded)/length(i_event_count_thresholded) %>% round(2))
                        ) %>%
  left_join(xy_train %>% 
            filter(expert==0) %>%
            group_by(index) %>% 
            summarise(novice_mean= sum(i_event_count_thresholded)/length(i_event_count_thresholded) %>% round(2))
                      ) %>%
  left_join(xy_train %>% 
            #filter(expert==0) %>%
            group_by(index) %>% 
            summarise(all_mean= sum(i_event_count_thresholded)/length(i_event_count_thresholded) %>% round(2))
                      ) %>%
  View()

```

```{r}
summary(fit_event_count)
coef_fit_event_count <- coef(fit_event_count)
```

```{r}
coef_fit_event_count$index[, , "Intercept"] %>%
	as_tibble() %>% 
  View()
```

Ok wow, coder proclivities don't vary at all which means something very wrong has happened

```{r}
#

library(brms)
fit_event_count <- brm(
  formula = formula_event_count,
  data = xy_train, 
  family = brmsfamily("bernoulli", "logit"),
  prior = prior_event_count,
  file = paste0(here::here(), "/data_temp/fit_event_count/fit_event_count"),
  save_model=paste0(here::here(), "/data_temp/fit_event_count/fit_event_count.rstan"),
  chains = 4, 
  cores = 64, 
  #opencl = opencl(c(0, 0)),
  backend = "cmdstanr",
  iter = 1,
  warmup = 1,
  file_refit='always'
  #threads = threading(4) #killing the threads so the model is written simpler
)

```

```{r}

if (!require(devtools)) {
  install.packages("devtools")
}
#devtools::install_github("paul-buerkner/brms", build_vignettes = FALSE)
library(brms)

```

```{r}
data("VerbAgg", package = "lme4")
```

```{r head-VerbAgg, echo=FALSE}
head(VerbAgg, 10) %>%
	kable(
    caption = "First ten rows of the \\texttt{VerbAgg} data.",
    booktabs = TRUE,
    escape = FALSE
	)
```

Let us start by computing a simple 1PL model. For reasons discussed in Section
\ref{model}, I prefer to partially pool person and item parameters by specifying the
model as

```{r}
formula_va_1pl <- bf(r2 ~ 1 + (1 | item) + (1 | id))
```

If we wanted to specify non-hierarchical item parameters, instead,
we would have had to use the formula

```{r, eval = FALSE}
bf(r2 ~ 0 + item + (1 | id))
```

To impose a small amount of regularization on the model, I set
$\text{half-normal}(0, 3)$ priors on the hierarchical standard deviations of
person and items parameters. Given the scale of the logistic response function,
this can be regarded as a weakly informative prior.

```{r}
prior_va_1pl <- 
  prior("normal(0, 3)", class = "sd", group = "id") + 
  prior("normal(0, 3)", class = "sd", group = "item")
```

The model is then fit as follows:

```{r, include=FALSE}
fit_va_1pl <- brm(
  formula = formula_va_1pl,
  data = VerbAgg, 
  family = brmsfamily("bernoulli", "logit"),
  prior = prior_va_1pl,
  file = paste0(here::here(), "/data_temp/model_fits/fit_va_1pl")
)
fit_va_1pl <- add_criterion(fit_va_1pl, "loo")
```

```{r, eval=FALSE}
fit_va_1pl <- brm(
  formula = formula_va_1pl,
  data = VerbAgg, 
  family = brmsfamily("bernoulli", "logit"),
  prior = prior_va_1pl
)
```

To get a quick overview of the model results and convergence, we can summarize
the main parameters numerically using the `summary` method:

```{r}
summary(fit_va_1pl)
```

A graphical summary of the marginal posterior densities as well as the MCMC
chains is obtained via

```{r plot-va-1pl, fig.width=8, fig.cap="Summary of the posterior distribution of selected parameters obtained by model \\code{fit\\_va\\_1pl.}"}
plot(fit_va_1pl)
```

```{r coef-item-va-1pl, echo=FALSE, fig.width=8, fig.cap = "Posterior means and 95\\% credible intervals of item parameters as estimated by model \\code{fit\\_va\\_1pl}."}
coef_fit_va_1pl <- coef(fit_va_1pl)
coef_fit_va_1pl$item[, , "Intercept"] %>%
	as_tibble() %>%
	rownames_to_column() %>%
	rename(item = "rowname") %>%
	mutate(item = as.numeric(item)) %>%
	ggplot(aes(item, Estimate, ymin = Q2.5, ymax = Q97.5)) +
	geom_pointrange() +
	coord_flip() +
	labs(x = "Item Number")

```

```{r coef-person-va-1pl, echo=FALSE, fig.width=8, fig.height = 4, fig.cap = "Posterior means and 95\\% credible intervals of person parameters (sorted) as estimated by model \\code{fit\\_va\\_1pl}."}
ranef_va_1pl <- ranef(fit_va_1pl)
ranef_va_1pl$id[, , "Intercept"] %>%
	as_tibble() %>%
	rownames_to_column() %>%
	select(-Est.Error) %>%
	arrange(Estimate) %>%
	mutate(id = seq_len(n())) %>%
	ggplot(aes(id, Estimate, ymin = Q2.5, ymax = Q97.5)) +
	geom_pointrange(alpha = 0.7) +
	coord_flip() +
	labs(x = "Person Number (Sorted)")
```

Above, I split up the non-linear model into two parts, `eta` and `logalpha`,
each of which is in turn predicted by a linear formula. The parameter `eta`
represents the sum of person parameter and item easiness, whereas `logalpha`
represents the log discrimination. I modeled item easiness and discrimination
as correlated by using `|i|` in both varying item terms (see Section
\ref{brms}). I impose weakly informative priors both on the intercepts of
`eta` and `logalpha` (i.e., on the overall easiness and log discrimination) as
well as on the standard deviations of person and item parameters.

```{r}
formula_va_2pl <- bf(
  r2 ~ exp(logalpha) * eta,
  eta ~ 1 + (1 |i| item) + (1 | id),
  logalpha ~ 1 + (1 |i| item),
  nl = TRUE
)
```

```{r}
prior_va_2pl <- 
  prior("normal(0, 5)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "b", nlpar = "logalpha") +
  prior("constant(1)", class = "sd", group = "id", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "item", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "item", nlpar = "logalpha")
```

```{r, include = FALSE}
fit_va_2pl <- brm(
	formula = formula_va_2pl,
  data = VerbAgg, 
	family = brmsfamily("bernoulli", "logit"),
	prior = prior_va_2pl,
	inits = 0,
	file = paste0(here::here(), "/data_temp/model_fits/fit_va_2pl")
)
fit_va_2pl <- add_criterion(fit_va_2pl, "loo") 
```

```{r, eval = FALSE}
fit_va_2pl <- brm(
  formula = formula_va_2pl,
  data = VerbAgg, 
  family = brmsfamily("bernoulli", "logit"),
  prior = prior_va_2pl,
) 
```

```{r coef-item-va-2pl, echo=FALSE, fig.width=8, fig.height = 4, fig.cap="Posterior means and 95\\% credible intervals of item parameters as estimated by model \\code{fit\\_va\\_2pl}."}
coef_fit_va_2pl <- coef(fit_va_2pl)
eta <- coef_fit_va_2pl$item[, , "eta_Intercept"] %>%
	as_tibble() %>%
	rownames_to_column() 
alpha <- coef_fit_va_2pl$item[, , "logalpha_Intercept"] %>%
	exp() %>%
	as_tibble() %>%
	rownames_to_column()
bind_rows(eta, alpha, .id = "nlpar") %>%
	select(-Est.Error) %>%
	rename(item = "rowname") %>%
	mutate(item = as.numeric(item)) %>%
	mutate(nlpar = factor(nlpar, labels = c("Easiness", "Discrimination"))) %>%
	ggplot(aes(item, Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap("nlpar", scales = "free_x") +
	geom_pointrange() +
	coord_flip() +
	labs(x = "Item Number")
```

Diads

```{r}
#This is going to be a million?
diads_wide <-  events_wide_i %>%
               left_join(events_wide_j, by=c('index'='index') ) %>% 
               filter(i_email_id!=j_email_id) %>% 
               #rowwise() %>%
               mutate(ij_email_id= ifelse( i_email_id>=j_email_id,paste0(i_email_id,j_email_id),paste0(j_email_id,i_email_id) ) ) %>%
               mutate(index_ij_email_id=paste0(index,ij_email_id)) %>%
               filter(!duplicated(index_ij_email_id)) %>%
               arrange(index) %>%
               ungroup() %>%
               mutate_if(is.numeric, function(x) ifelse(is.infinite(x), 0, x))
dim(diads_wide) #204,781    213

variables <- setdiff( names(diads_wide) %>% str_replace("ij_|i_|j_","") %>% unique(), c('index_ij_email_id','email_id','index',"ij_email_id","index_ij_email_id","match_i_email_id","index_email_id"  ))
diads_wide <- as.data.frame(diads_wide)
for(q in variables){
  print(q)
  newvar <- paste0("match_",q)
  a_oldvar <- paste0("i_",q)
  b_oldvar <- paste0("j_",q)
  diads_wide[,newvar] <-  0 #default 0
  diads_wide[,newvar] <-  ifelse(diads_wide[,a_oldvar] %in% 1 &  diads_wide[,b_oldvar] %in% 1, 1,  diads_wide[,newvar])  #if both 1 then 1
  diads_wide[,newvar] <-  ifelse(diads_wide[,a_oldvar] %in% 0 &  diads_wide[,b_oldvar] %in% 0, NA, diads_wide[,newvar])  #if both 0 then NA
}

diads_matches <- diads_wide %>% 
                 dplyr::select(index_ij_email_id,  starts_with("match"))  %>%
                 dplyr::select(-ends_with("_NA"))

final_counts_numerator <- diads_matches %>% summarise_if(is.numeric, sum, na.rm=T)
final_counts_denominator <- diads_matches %>% summarise_if(is.numeric, ~sum(is.finite(.x)) )

final_scores <- final_counts_numerator / final_counts_denominator
#One takeaway is that because coders split on act vs interact is artificially drops the agreement

#New plan, we're going to pull out those dimensions seperately
#final_scores %>% round(2) %>% t()  %>% as.data.frame() %>%  tibble::rownames_to_column( "VALUE") %>% View()
options(warn=0)

final_scores_df <- data.frame(varname= names(final_scores),  final_scores=final_scores %>% round(2) %>% t(),final_counts_numerator=final_counts_numerator%>% t()) %>% filter(final_counts_numerator>1)
#final_scores_df %>% View() 
#cor(final_scores_df) #.64 correlation between agreement and how often its used

p_intercoder_agreement <- final_scores_df %>%
                                  mutate(grouping=NA) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Event_Count'), 'Event_Count' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('match_Behavior_'), 'Behavior' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('think_aggression'), 'Aggression (think)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('say_aggression_'), 'Aggression (say)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('do_aggression_'), 'Aggression (do)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Do_Armed_Unarmed'), 'Armed or Unarmed Agents' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('do_Act_Interact'), 'Action or Interaction' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Think_Type_L0'), 'Think (L0)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Say_Type_L0'), 'Say (L0)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Do_Type_L0'), 'Do (L0)' ,  grouping)) %>%
                                  mutate(grouping=ifelse(varname %>% str_detect('Leaf_Simplified'), 'Leaf Simplified' ,  grouping)) %>%
                                  mutate(grouping=grouping %>% factor(levels=c('Event_Count', 'Behavior','Aggression (think)','Aggression (say)','Aggression (do)',
                                                                               'Armed or Unarmed Agents','Action or Interaction',
                                                                               'Think (L0)','Say (L0)','Do (L0)','Leaf Simplified') %>% rev() ) ) %>%
                                  ggplot(aes(x=final_scores, y=grouping)) + 
                                  geom_boxplot() +
                                  xlab("Intercoder Agreemnt (Experts, positives only, Single Event Sentences)") +
                                  ylab("Psuedo Ontology Tree Depth")

```

```{r, eval=F}
p_intercoder_agreement
```

### 2022-01-20 README.Rmd
readme

@@
  - Agreed Data, wide form (LINK NEEDED)
- - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
-    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
-    + values may contain multiple entries separating with a semicolon
- - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
-    + each row contains identifying information for a coder-crisis-event-sentence
-    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
-    + each value contains a single entry
  - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
@@
 ## Other data inputs:
+ - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
+    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
+    + values may contain multiple entries separating with a semicolon
+ - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
+    + each row contains identifying information for a coder-crisis-event-sentence
+    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
+    + each value contains a single entry
 

### 2022-01-20 README.Rmd
win init and readme

--- 2022-01-20 README.Rmd
@@
 
+## Data:
+
 # ICBe Dataset
@@
 - [ICBEdataset Codebook](https://docs.google.com/document/d/1aJkweohbfIWtNpJw1CmXbeIiK6czbJ5iPyKwiYP1YlU/edit?usp=sharing)
+
+Replication Code and Analysis
+-----------------------------
+
+### Self Contained Package
+
+All of the files necessary for reproducing our analysis are including in a self contained R package "ICBEdataset" You can install the package icb from github with:
+
+``` r
+# install.packages("devtools")
+devtools::install_github("centerforpeaceandsecuritystudies/ICBEdataset")
+```
+
+## RMarkdown files
+ - 01_compile_saves_and_align
+    + compiles the original coding files into `./replication_data/temp/icb_coder_crisis_sentence_event.Rds`
+    + the original coding files are not on the public repository; this can only be run by authors
+    + aligns codings from multiple GUI versions on similar source sentences
+    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
+ - 02_format_and_clean
+    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
+ - 03_aggregation
+    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.
 
@@
 
-Replication Code and Analysis
------------------------------
-
-### Self Contained Package
-
-All of the files necessary for reproducing our analysis are including in a self contained R package "ICBEdataset" You can install the package icb from github with:
-
-``` r
-# install.packages("devtools")
-devtools::install_github("centerforpeaceandsecuritystudies/ICBEdataset")
-```
-
-## RMarkdown files
- - [01_compile_saves](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/01_compile_saves.html)
-    + compiles the original coding files into `./data/icb_coder_crisis_sentence_event.tsv`
-    + the original coding files are not on the public repository; this can only be run by authors
- - [02_align_sentences](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/02_align_sentences.html)
-    + aligns codings from multiple GUI versions on similar source sentences
-    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
- - [03_format_and_clean](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/03_format_and_clean.html)
-    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
- - [04_aggregation](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/04_aggregation.html)
-    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.
-
- - [05a_data_summary](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/05a_data_summary.html)
-    + coding information, sentence root, time, coder confidence
- - [05b_data_summary](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/05b_data_summary.html)
-    + actions, speech, thought
-
 ## Other data inputs:

### 2022-01-21 README.Rmd
paper start

@@
 ### ICBe prep
-- Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates [available online](https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit#gid=0) and  ./data/icb_manual_recording_master_sheet.xlsx
+- Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
   + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).

### 2022-01-21 replication_data/rmd/02_format_and_clean.rmd
paper start

@@
 saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
+saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/input/icb_long_clean.Rds"))
+
 ```

### 2022-01-21 replication_data/rmd/03_aggregation.Rmd
paper start

@@
 saveRDS(codings_long, paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
+saveRDS(codings_long, paste0(here::here(), "/replication_paper/data/in/codings_long.Rds"))
+
 saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds")) 
+saveRDS(codings_long_agreement, paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds"))
 
 saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
+saveRDS(codings_long_agreed, paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds"))
+
 saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds")) 
+saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds"))
 

### 2022-01-21 replication_paper/rmd/CaseStudy196.Rmd
paper start

@@
 ```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
-
-CaseStudy196 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", sheet="CaseStudy196")
+CaseStudy196 <- readxl::read_excel(paste0(here::here(),"/replication_paper/data/in/CaseStudies.xlsx"), sheet="CaseStudy196")
 
@@
 
-CaseStudy196_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/CaseStudy196_ft.Rds'))
+CaseStudy196_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
 

### 2022-01-21 replication_paper/rmd/CaseStudy426.Rmd
paper start

@@
 
-CaseStudy426 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", sheet="CaseStudy426")
+CaseStudy426 <- readxl::read_excel(paste0(here::here(),"/replication_paper/data/in/CaseStudies.xlsx"), sheet="CaseStudy426")
 
@@
 
-CaseStudy426_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/CaseStudy426_ft.Rds'))
+CaseStudy426_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
 

### 2022-01-21 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
paper start

@@
 ---
-title: "Metro Maps"
+title: "ICBEdataset figure Metro Maps"
 output: html_document
@@
 
-icb_crises <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) 
+icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
 #icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds") )
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))
 
@@
 
-target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 
@@
 
-codings_long <- readRDS( paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds")) 
-codings_long_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
-codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))
+codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds")) 
+codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
+codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds"))
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_file <- paste0(here::here(), "/paper/figures/metro_plots/p_metro_plot_",crisis,".Rds")
+  save_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_metro_plot_", crisis, ".Rds")
 
@@
               mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
-              mutate(IMAGE=paste0(here::here, '/paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
+              mutate(IMAGE=paste0(here::here, '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
               mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
@@
               mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
-              mutate(IMAGE=paste0(here::here(), "/paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
+              mutate(IMAGE=paste0(here::here(), "/replication_paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
               mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
@@
   ft_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_file <- paste0(here::here(), "/paper/tables/sentence_tables/ft_sentence_table_",crisis,".Rds")
+  save_file <- paste0(here::here(), "/replication_paper/tables/sentence_tables/ft_sentence_table_",crisis,".Rds")
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/paper/figures/metro_plots/p_mids_metro_plot_",crisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_mids_metro_plot_",crisis,".Rds")
 
@@
 
-midip <- read_csv(paste0(here::here(), '/data_other_datasets/mids_incidents/MIDIP_5.01.csv'))
-
-midii <- read_csv(paste0(here::here(), '/data_other_datasets/mids_incidents/MIDI_5.01.csv'))
+midip <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.csv'))
+
+midii <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.csv'))
 
@@
   #crisis=426
-  save_mids_incidents_file <- paste0(here::here(), "/paper/figures/metro_plots/p_mids_incidents_metro_plot_",crisis,".Rds")
+  save_mids_incidents_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_mids_incidents_metro_plot_",crisis,".Rds")
 
@@
 
-icbdy_20 <- read_tsv(here::here(), "/data_other_datasets/icb_dyad/icbdy_20.dat")
+icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
 
@@
 
-icb2v14 <- read_csv(here::here(), "/data_other_datasets/icb/icb2v14.csv")
+icb2v14 <- read_csv(here::here(), "/replication_paper/data/in/icb2v14.csv")
 
@@
     print(crisis)
-    save_icb_file <- paste0(here::here(), "/paper/figures/metro_plots/p_icb_metro_plot_",crisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icb_metro_plot_",crisis,".Rds")
 
@@
 
-ged211 <- read_csv(here::here(), "/data_other_datasets/ucdp_ged/ged211.csv")
-
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
+ged211 <- read_csv(here::here(), "/replication_paper/data/in/ucdp_ged/ged211.csv")
+
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
@@
     #crisis=426
-    save_ucdp_incidents_file <- paste0(here::here(), "/paper/figures/metro_plots/p_ucdp_metro_plot_",crisis,".Rds")
+    save_ucdp_incidents_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_ucdp_metro_plot_",crisis,".Rds")
 
@@
 
-CAMEO_eventcodes <- read_tsv(here::here(), "/data_other_datasets/icews/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()
+CAMEO_eventcodes <- read_tsv(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()
 
@@
 
-#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/data_temp/CAMEO.eventcodes.txt")) %>% janitor::clean_names()
+#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt")) %>% janitor::clean_names()
 
@@
 
-files <- list.files(path = paste0(here::here(), "/data_other_datasets/icews/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
+files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
 icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
@@
 
-CAMEO_eventcodes <- read_tsv(paste0(here::here(),"/data_other_datasets/icews/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()
+CAMEO_eventcodes <- read_tsv(paste0(here::here(),"/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()
 
@@
 
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
@@
   #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
-  #save_icews_file = paste0(here::here(), "/paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
+  #save_icews_file = paste0(here::here(), "/replication_paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
   plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
   if(is.null(savefile)){
-    save_icews_file <- paste0(here::here(), "/paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
+    save_icews_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
   }
@@
 
-a <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-b  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-c  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-d  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-e <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
+a <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
+b  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
+c  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
+d  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
+e <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_phoenix_file <- paste0(here::here(), "/paper/figures/metro_plots/p_phoenix_metro_plot_",crisis,".Rds")
+  save_phoenix_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_phoenix_metro_plot_",crisis,".Rds")
 
@@
 
-files <- list.files(path = paste0(here::here(), "/data_other_datasets/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
+files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
 terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
@@
 
-CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/data_other_datasets/terrier/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
+CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
 #codes_used <-terrier_clean %>% count(cameo_code)
 
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
@@
   plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_terrier_file <- paste0(here::here(), "/paper/figures/metro_plots/p_terrier_metro_plot_",crisis,".Rds")
+  save_terrier_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_terrier_metro_plot_",crisis,".Rds")
 

### 2022-01-26 README.Rmd
input datas

@@
 
-## ICBe raw data
+## ICBe data products
 
@@
  - Agreed Data, wide form (LINK NEEDED)
+ - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
+    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.
+
+### Additional data versions
  - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
@@
     + each value contains a single entry
- - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
-    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.
 
-## Other data inputs:
+## Data inputs:
 
-### ICBe prep
+### ICBe preperation
   - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
@@
 
-### Existing datasets
-- [The ICB project](https://sites.duke.edu/icbdata/) system-level (./data/icb1v14.Rds) and actor-level (./data/icb2v14.Rds) datasets.
-- [ICEWS data sample](https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/28075/WNOBVV&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData).
+### External datasets
+  - [The ICB project](https://sites.duke.edu/icbdata/) 
+    + System-level (./data/icb1v14.Rds) and Actor-level (./data/icb2v14.Rds) datasets
+    + Dyadic-Level Crisis Data ([source](https://sites.duke.edu/icbdata/data-collections/))
+  - [Militarized Interstate Disputes (MID)](https://correlatesofwar.org/data-sets/MIDs) version 5.01 at the incident level (MIDI 5.01) and incident-participant level (MIDIP 5.01) converted to Rds. 
+  - [UCDP Georeferenced Event Dataset (GED) Global version 21.1](https://ucdp.uu.se/downloads/index.html#ged_global)
+  - cameo.eventcode.txt adapted from [CAMEO Conflict and Mediation Event Observations Codebook](https://parusanalytics.com/eventdata/cameo.dir/CAMEO.09b6.pdf)
+  - [Phoenix Event data](https://databank.illinois.edu/datasets/IDB-2796521)
+  - [Terrier event data](https://osf.io/4m2u7/files/) 
+    + too large to include in the github repository
+    + to replicate, download the folder 'largegeolocatedata' to ICBEdata/replication_paper/data/ignore and decompress
+  - [ICEWS data sample](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/28075&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData)
+    + too large to include in the github repository
+    + to replicate, download the .tsv and .tab files to ICBEdata/replication_paper/data/ignore/icews_dataverse/ and decompress
 

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
input datas

@@
 target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
 # in not working, run googledrive::drive_auth() and select new token

### 2022-01-26 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
input datas

@@
 
-midip <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.csv'))
-
-midii <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.csv'))
+midii <- readRDS(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.Rds'))
+midip <- readRDS(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.Rds'))
 
@@
 
-icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
+#icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
+icbdy_20 <- readRDS(paste0(here::here(), '/replication_paper/data/in/icbdy_20.Rds'))
 
@@
 
-CAMEO_eventcodes <- read_tsv(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()
+CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()
 
@@
 
-files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
+files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/"), full.names = T)
 icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
+
 dim(icews)
@@
 icews_clean <- icews %>% 
-               left_join(CAMEO_eventcodes %>% mutate(cameoeventcode=cameoeventcode) %>%  #You have 
-                           dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  )  %>%
+               left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code) # %>%  #You have 
+                           # dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  
+                         )  %>%
                 filter(source_country %in% na.omit(actor_translator$ICEWS_Country) | source_name %in% na.omit(actor_translator$ICEWS_Actor.Name)) %>%
@@
 
-a <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-b  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-c  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-d  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
-e <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
+a <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-NYT_1980-2018.Rds'))
+b <- dplyr::bind_rows(
+  readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-SWB_1979-2019a.Rds')),
+  readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-SWB_1979-2019b.Rds')),          
+  readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixBLN-SWB_1979-2019c.Rds')))
+c <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixFBIS_1995-2004.Rds'))
+d <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixNYT_1945-2005.Rds'))
+e <- readRDS(paste0(here::here(), '/replication_paper/data/in/PhoenixWSJ_1945-2006.Rds'))
 
@@
 
-files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
+files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
 terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()

### 2022-01-26 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
input datas

@@
 
-codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/codings_wide_agreed.Rds'))
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/codings_long_agreed.Rds'))
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
-codings_long <- readRDS(file=paste0(here::here(), '/data_out/codings_long.Rds'))
-codings_long_agreement <- readRDS(file=paste0(here::here(), '/data_out/codings_long_agreement.Rds'))
+codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds")) 
+codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) 
+codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds"))
 
@@
 #py_discover_config()
+
 use_python("/home/skynet3/anaconda3/bin/python/")
@@
 
-codings_long_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
+codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
 codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)
 
-codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_data/temp/codings_long_agreed_embeded.Rds'))
+codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_long_agreed_embeded.Rds'))
 
-codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_data/out/codings_wide_agreed.Rds'))
+codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
 codings_wide_agreed_embeded <- codings_wide_agreed %>% ungroup() %>% left_join(sentences_embeded)
@@
 
-codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_data/temp/codings_wide_agreed_embeded.Rds'))
+codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_wide_agreed_embeded.Rds'))
 
@@
 
-p_semantic_embeddings   %>% saveRDS(paste0(here::here(), '/paper_replication/figures/p_semantic_embeddings.Rds'))
+p_semantic_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
 p_semantic_embeddings

### 2022-01-26 prune/ICBEdataset_paper_InterCoderByLevels.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_InterCoderByLevels.Rmd
@@
 ---
-title: "Untitled"
+title: "ICBEdataset_paper_InterCoderByLevels"
 output: html_document
@@
 library(tidyverse)
-library(googlesheets4)
-
 ```
@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds")) #%>% 
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) #%>% 
                   #mutate(temp_row_id=paste(email_id, crisno,sentence_number_int_aligned, variable, sep="_")) %>%
@@
 
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
 
@@
 
-full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
-                                       sheet="Codebook in Tree Form")
+target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
+full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")
 

### 2022-01-26 prune/ICBEdataset_paper_InternalValidity.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_InternalValidity.Rmd
@@
 ---
-title: "InternalMeasurementValidity.Rmd"
+title: "Internal Measurement Validity"
 output: html_document
@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds"))
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
 

### 2022-01-26 prune/ICBEdataset_paper_TableExampleSentenceCoding.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_TableExampleSentenceCoding.Rmd
@@
 p_load(ftExtra)
-p_load(googlesheets4)
-library(googlesheets4)
 
@@
 ```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
-sentence_example_sheet <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
-                                                    sheet="Sentence Tree Example Table")
+
+target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
+sentence_example_sheet    <- readxl::read_excel(target_file, sheet="Sentence Tree Example Table")
 

### 2022-01-26 prune/ICBEdataset_paper_TableSentenceExamples.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_TableSentenceExamples.Rmd
@@
 
-codings_long_agreement <- readRDS( paste0(here::here(), "ICBEdataset/data_out/codings_long_agreement.Rds")) 
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds")) 
 codings_long_agreement_1_3 <- codings_long_agreement %>% filter(crisno==1 & sentence_number_int_aligned==3)
@@
 #You have to rerun the embeddings too
-codings_wide_agreed_embeded <- readRDS( paste0(here::here(), "ICBEdataset/data_out/codings_wide_agreed_embeded.Rds")) 
+codings_wide_agreed_embeded <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed_embeded.Rds")) 
 codings_wide_agreed_embeded_2_11 <- codings_wide_agreed_embeded %>% filter(crisno==2 & sentence_number_int_aligned==11)
@@
 
-events_ft  %>% saveRDS(paste0(here::here(), "ICBEdataset/paper/tables/events_ft.Rds"))
+events_ft  %>% saveRDS(paste0(here::here(), "/replication_paper/tables/events_ft.Rds"))
 events_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixPlayersandAgents.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixPlayersandAgents.Rmd
@@
 p_load(ftExtra)
-p_load(googlesheets4)
-library(googlesheets4)
-
 ```
@@
 ```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, ft.arraystretch=0.75}
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
@@
 
-actor_agents_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/actor_agents_ft.Rds'))
+actor_agents_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/actor_agents_ft.Rds'))
 actor_agents_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixVerbCoarsened.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbCoarsened.Rmd
@@
 ```{r}
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/data/icb_wide_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
 ```
@@
 
-  parsed %>% saveRDS(paste0(here::here(), "/data/parsed.Rds"))
+  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
 
   entities <- entity_extract(parsed, type = "all")
-  entities %>% saveRDS(paste0(here::here(), "/data/entities.Rds"))
+  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
 
 } else {
-  parsed <- readRDS(paste0(here::here(), "/data/parsed.Rds"))
-  entities <- readRDS(paste0(here::here(), "/data/entities.Rds"))
+  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
+  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
 
@@
 
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
@@
 
-wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )
+wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/in/wordnet_rdf.Rds") )
 
@@
 #wordnet csv
-filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/") )
-filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)
+filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/") )
+filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)
 
@@
   verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
-  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))
+  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
 
@@
 
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds") )
+  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds") )
 
@@
 
-first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/paper/tables/first_two_hops_collapsed_ft.Rds'))
+first_two_hops_collapsed_ft  %>% saveRDS(here::here(), '/replication_paper/tables/first_two_hops_collapsed_ft.Rds')
 first_two_hops_collapsed_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixVerbDomains.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbDomains.Rmd
@@
 
-wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )
+wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )
 
@@
 
-domains_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/domains_ft.Rds'))
+domains_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/domains_ft.Rds'))
 domains_ft

### 2022-01-26 prune/ICBEdataset_paper_appendixVerbTrees.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_appendixVerbTrees.Rmd
@@
 
-fromsrcatch=F
-if(fromsrcatch){
+fromscratch=F
+if(fromscratch){
   #py$sentences
@@
   verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
-  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))
+  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
 
@@
 
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data/verbs_sentence_wordnet.Rds"))
+  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
 
@@
 
-ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)
+ggsave( filename=paste0(here::here(), "/replication_paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)
 
@@
 
-ggsave( filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)
+ggsave( filename=paste0(here::here(), "/replication_paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)
 

### 2022-01-26 prune/ICBEdataset_paper_uncertainty.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_uncertainty.Rmd
@@
 library(tidyverse)
-library(googlesheets4)
 
@@
 ```{r}
-
-full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing",
-                                       sheet="Codebook in Tree Form")
+target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
+full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")
 
@@
 
-write_csv(codings_long_agreed, paste0(here::here(), "/data_out/codings_long_agreed.csv"))
-write_csv(codings_wide_agreed, paste0(here::here(), "/data_out/codings_wide_agreed.csv"))
+# write_csv(codings_long_agreed, paste0(here::here(), "/data_out/codings_long_agreed.csv"))
+# write_csv(codings_wide_agreed, paste0(here::here(), "/data_out/codings_wide_agreed.csv"))
 

### 2022-01-26 prune/ICBEdataset_paper_uncertainty_bayesian.Rmd
paper rmds

--- 2022-01-20 replication_paper/rmd/ICBEdataset_paper_uncertainty_bayesian.Rmd
@@
 ---
-title: "Untitled"
+title: "Uncertainty Bayesian"
 output: html_document
@@
 table(sentence_variable_widecoder$answer_modal_perc)
-
-```
-
-```{r}
 
@@
 
-events_wide_i_event_count_thresholded %>% saveRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))
+# events_wide_i_event_count_thresholded %>% saveRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))
 
@@
 library(tidyverse)
-events_wide_i_event_count_thresholded <- readRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))
+# events_wide_i_event_count_thresholded <- readRDS(paste0(here::here(), '/data_temp/events_wide_i_event_count_thresholded.Rds'))
 

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
paper rmds

@@
 saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
-saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/input/icb_long_clean.Rds"))
+saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))
 
@@
 saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds")) 
+saveRDS(icb_wide_clean, paste0(here::here(), "/replication_paper/in/icb_wide_clean.Rds"))
 

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
paper rmds

@@
 ---
-title: 'Intercoder Agreement'
+title: 'Plot Intercoder Agreement'
 site: bookdown::bookdown_site
@@
 ```{r}
-icb_long_clean <- readRDS(file=paste0(here::here(), "/data/icb_long_clean.Rds"))
-
-codings_long <- readRDS(paste0(here::here(), '/data_out/codings_long.Rds'))
-codings_long_agreement <- readRDS( paste0(here::here(), '/data_out/codings_long_agreement.Rds'))
-codings_long_agreed <- readRDS( paste0(here::here(), '/data_out/codings_long_agreed.Rds'))
-codings_wide_agreed <- readRDS( paste0(here::here(), '/data_out/codings_wide_agreed.Rds'))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
+codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
+codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
+codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))
 
@@
 ```{r}
-
 confidence_totals <- bind_rows(
@@
 
-p_percent_chose_tag_by_concept %>% saveRDS(paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.Rds'))
+p_percent_chose_tag_by_concept %>% saveRDS(paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.Rds'))
 p_percent_chose_tag_by_concept
 
-ggplot2::ggsave(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.png'), 
+ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
                 plot = p_percent_chose_tag_by_concept, width=8, height=6)

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixVerbMeanings.Rmd
paper rmds

@@
 target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
 dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
@@
 #wordnet csv
-filenames <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"))
-filepaths <- list.files(path=paste0(here::here(), "/data_replication/in/wncsv-master/csv/"), full.names = T)
+filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"))
+filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)
 
@@
 
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/data_replication/temp/verbs_sentence_wordnet.Rds"))
+  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
 
@@
 
-ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)
+ggsave(filename=paste0(here::here(), "/replication_paper/figures/hypernyms_plot.pdf"), plot=p, height=100,width =32,limitsize = FALSE)
 
@@
 
-ggsave(filename=paste0(here::here(), "/paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)
+ggsave(filename=paste0(here::here(), "/replication_paper/figures/hypernyms_rooted_plot.pdf"), plot=p_rooted, height=100,width =32,limitsize = FALSE)
 
@@
 
-verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
+verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
 verbs_sentence_wordnet_top_ft

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
paper rmds

@@
 ---
-title: 'ICBEdataset_paper_prep_metro_map'
+title: 'ICBEdataset_paper_figure_prep'
 site: bookdown::bookdown_site
@@
 library(tidyverse)
-library(googlesheets4)
 library(janitor)
@@
 
-icb_crises <- read.csv(paste0(here::here(), "/inst/extdata/","icb1v14.csv")) 
+icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/","icb1v14.csv")) 
 #icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds"))
@@
 #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
-p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/paper/figures/p_semantic_embeddings.Rds'))
-ggsave(file=paste0(here::here(), '//paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
+p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
 ```
@@
 library(ggplot2)
-p_metro_map_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_196.Rds'))
+p_metro_map_196 <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_metro_plot_196.Rds'))
 actor_colors <- p_metro_map_196$actor_colors
-ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_196.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_metro_map_196.png'),
        plot = p_metro_map_196 +
@@
 library(ggplot2)
-p_phoenix_metro_plot_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
+p_phoenix_metro_plot_196 <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
 actor_colors <- p_phoenix_metro_plot_196$actor_colors
 
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds')
 
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_phoenix_metro_plot_196.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_icb_metro_plot_196.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_mids_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_mids_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_mids_metro_plot_196.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
        plot = p_metro_plot ,
@@
 # #ICBe  426
-p_metro_map_426 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_426.Rds'))
+p_metro_map_426 <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_metro_plot_426.Rds'))
 actor_colors <- p_metro_map_426$actor_colors
-ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_metro_map_426.png'),
       plot = p_metro_map_426 +
@@
 library(ggplot2)
-p_metro_plot <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_426.Rds'))
+p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_426.Rds'))
 actor_colors <- p_metro_plot$actor_colors
 
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_phoenix_metro_plot_426.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_426.Rds')
 subtitle="Phoenix Dyadic Events"
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_phoenix_metro_plot_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_426.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_icews_metro_plot_426.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_icews_metro_plot_426.Rds')
 p_metro_plot <- readRDS(file=save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_icews_metro_plot_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_icews_metro_plot_426.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_terrier_metro_plot_426.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_terrier_metro_plot_426.Rds')
 p_metro_plot <- readRDS(file=save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_terrier_metro_plot_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_terrier_metro_plot_426.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_icb_metro_plot_426.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_icb_metro_plot_426.Rds')
 p_metro_plot <- readRDS(save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_icb_metro_plot_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_426.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_mids_metro_plot_426.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_mids_metro_plot_426.Rds')
 p_metro_plot <- readRDS(save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_mids_metro_plot_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_426.png'),
        plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/paper/figures/metro_plots/p_mids_incidents_metro_plot_426.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_mids_incidents_metro_plot_426.Rds')
 p_metro_plot <- readRDS(save_file)
@@
    scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) 
-ggsave(file=paste0(here::here(), '/paper/figures/p_mids_incidents_metro_plot_426.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_incidents_metro_plot_426.png'),
        plot = p_metro_plot ,

### 2022-01-26 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
paper rmds
pruned

@@
 
-TLS = FALSE
+TLS = TRUE
 ```
@@
 
-  parsed %>% saveRDS(paste0(here::here(), "/replication_data/temp/parsed.Rds"))
+  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
 
   entities <- entity_extract(parsed, type = "all")
-  entities %>% saveRDS(paste0(here::here(), "/replication_data/temp/entities.Rds"))
+  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
 
 } else {
-  parsed <- readRDS(paste0(here::here(), "/replication_data/temp/parsed.Rds"))
-  entities <- readRDS(paste0(here::here(), "/replication_data/temp/entities.Rds"))
+  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
+  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
 
@@
 
-if(!TLS){
-downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit#gid=0", path=target_file, type = "xlsx", overwrite=T)
-}
 dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
@@
 
-ym   4
-wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )
+wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )
 
@@
 
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(),"/data_replication/temp/verbs_sentence_wordnet.Rds"))
+  verbs_sentence_wordnet <- readRDS(paste0(here::here(),"/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
 

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixICBCrises.Rmd
pruned

---
title: 'Appendix 1: ICB Crises and Summary Information'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)

library(flextable)
library(ftExtra)
library(tidyverse)

knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F

```

```{r}
#Load original icb data

icb_crises <- read_csv(file=paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) %>% janitor::clean_names() #somehow break of all things is a broken name
icb_actors <- read_csv(file=paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))

```

```{r}

#Select and recode our questions and answer

icb_recodes <- data.frame(
  stringsAsFactors = FALSE,
                              var = c("BREAK","BREAK","BREAK","BREAK","BREAK",
                                      "BREAK","BREAK","BREAK","BREAK",
                                      "BREAK","CENVIOSY","CENVIOSY","CENVIOSY",
                                      "CENVIOSY","CENVIOSY","CENVIOSY",
                                      "CHACTS","CHACTS","CHACTS","CHACTS","CHACTS",
                                      "CHACTS","CHACTS","CHALL","CHALL",
                                      "CHALL","CHALL","CHALL","CHALL","CHALL",
                                      "CRISMG","CRISMG","CRISMG","CRISMG",
                                      "CRISMG","CRISMG","CRISMG","CRISMG",
                                      "CRISMG","CRISMG","ETHCONF","ETHCONF",
                                      "ETHCONF","ETHCONF","ETHCONF","ETHCONF",
                                      "ETHNIC","ETHNIC","ETHNIC","ETHNIC",
                                      "ETHNIC","EXSAT","EXSAT","EXSAT","EXSAT",
                                      "EXSAT","EXSAT","EXSAT","EXSAT",
                                      "EXSAT","FOROUT","FOROUT","FOROUT","FOROUT",
                                      "FOROUT","FOROUT","FOROUT","FOROUT",
                                      "FOROUT","GLOBACTM","GLOBACTM",
                                      "GLOBACTM","GLOBACTM","GLOBACTM","GLOBACTM",
                                      "GLOBACTM","GLOBACTM","GLOBACTM",
                                      "GLOBACTM","GLOBACTM","GLOBACTM","GLOBACTM",
                                      "GLOBACTM","GLOBACTM","GLOBACTM",
                                      "GLOBEFCT","GLOBEFCT","GLOBEFCT","GLOBEFCT",
                                      "GLOBEFCT","GLOBEFCT","GLOBEFCT",
                                      "GLOBEFCT","GLOBEFCT","GLOBORG","GLOBORG",
                                      "GLOBORG","GLOBORG","GLOBORG","GLOBORG",
                                      "GLOBORG","GLOBORG","GRAVCR","GRAVCR",
                                      "GRAVCR","GRAVCR","GRAVCR","GRAVCR",
                                      "GRAVCR","GRAVCR","GRAVCR","GRAVCR",
                                      "HETERO","HETERO","HETERO","HETERO","HETERO",
                                      "HETERO","HETERO","ISSUES","ISSUES",
                                      "ISSUES","ISSUES","ISSUES","ISSUES",
                                      "ISSUES","MEDIATE","MEDIATE","MEDIATE",
                                      "MEDIATE","MEDIATE","MEDIATE","OUTESR",
                                      "OUTESR","OUTESR","OUTESR","OUTESR",
                                      "POWCH","POWCH","POWCH","POWCH","POWCH",
                                      "POWCH","POWCH","REGACTMB","REGACTMB",
                                      "REGACTMB","REGACTMB","REGACTMB",
                                      "REGACTMB","REGACTMB","REGACTMB","REGACTMB",
                                      "REGACTMB","REGACTMB","REGACTMB",
                                      "REGACTMB","REGACTMB","REGACTMB","REGACTMB",
                                      "REGORG","REGORG","REGORG","REGORG",
                                      "REGORG","REGORG","REGORG","REGORG",
                                      "REGORG","REGORG","REGORG","REGORG",
                                      "REGORG","REGORG","ROEFCT","ROEFCT","ROEFCT",
                                      "ROEFCT","ROEFCT","ROEFCT","ROEFCT",
                                      "ROEFCT","ROEFCT","RUGACH","RUGACH",
                                      "RUGACH","RUGACH","RUGACH","RUGACH",
                                      "RUGACH","SEVVIOSY","SEVVIOSY","SEVVIOSY",
                                      "SEVVIOSY","SEVVIOSY","SEVVIOSY",
                                      "SOGLACT","SOGLACT","SOGLACT","SOGLACT",
                                      "SOGLACT","SOGLACT","SOGLACT","SOGLACT",
                                      "SOGLACT","SOGLACT","SORACT","SORACT",
                                      "SORACT","SORACT","SORACT","SORACT",
                                      "SORACT","SORACT","SORACT","SORACT",
                                      "SOURDT","SOURDT","SOURDT","SOURDT","SOURDT",
                                      "SOURDT","SOURDT","SOURDT","SOURDT",
                                      "SUBOUT","SUBOUT","SUBOUT","SUBOUT",
                                      "SUEFAC","SUEFAC","SUEFAC","SUEFAC",
                                      "SUEFAC","SUEFAC","SUEFAC","SUEFCT",
                                      "SUEFCT","SUEFCT","SUEFCT","SUEFCT","SUEFCT",
                                      "SUEFCT","SUEFCT","SUINV","SUINV",
                                      "SUINV","SUINV","SUINV","SUINV","SUPACE",
                                      "SUPACE","SUPACE","SUPACE","SUPACE",
                                      "SUPACE","USEFAC","USEFAC","USEFAC",
                                      "USEFAC","USEFAC","USEFAC","USEFAC",
                                      "USEFCT","USEFCT","USEFCT","USEFCT",
                                      "USEFCT","USEFCT","USEFCT","USEFCT","USINV",
                                      "USINV","USINV","USINV","USINV",
                                      "USINV","USPACE","USPACE","USPACE","USPACE",
                                      "USPACE","USPACE","VIOL","VIOL",
                                      "VIOL","VIOL","VIOL","VIOL","TIMVIO",
                                      "TIMVIO","TIMVIO","TIMVIO","TIMVIO"),
                      description = c("BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS",
                                      "BREAK: BREAKPOINT (TRIGGER) TO INTERNATIONAL CRISIS","CENVIOSY: CENTRALITY OF VIOLENCE",
                                      "CENVIOSY: CENTRALITY OF VIOLENCE",
                                      "CENVIOSY: CENTRALITY OF VIOLENCE",
                                      "CENVIOSY: CENTRALITY OF VIOLENCE",
                                      "CENVIOSY: CENTRALITY OF VIOLENCE",
                                      "CENVIOSY: CENTRALITY OF VIOLENCE","CHACTS: CHANGE IN ACTORS",
                                      "CHACTS: CHANGE IN ACTORS",
                                      "CHACTS: CHANGE IN ACTORS","CHACTS: CHANGE IN ACTORS",
                                      "CHACTS: CHANGE IN ACTORS",
                                      "CHACTS: CHANGE IN ACTORS","CHACTS: CHANGE IN ACTORS",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CHALL: CHANGE IN ALLIANCE CONFIGURATION",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE",
                                      "CRISMG: CRISIS MANAGEMENT TECHNIQUE","ETHCONF: ETHNIC CONFLICT",
                                      "ETHCONF: ETHNIC CONFLICT",
                                      "ETHCONF: ETHNIC CONFLICT","ETHCONF: ETHNIC CONFLICT",
                                      "ETHCONF: ETHNIC CONFLICT",
                                      "ETHCONF: ETHNIC CONFLICT","ETHNIC: ETHNICITY",
                                      "ETHNIC: ETHNICITY","ETHNIC: ETHNICITY",
                                      "ETHNIC: ETHNICITY","ETHNIC: ETHNICITY",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "EXSAT: EXTENT OF SATISFACTION ABOUT OUTCOME",
                                      "FOROUT: FORM OF OUTCOME",
                                      "FOROUT: FORM OF OUTCOME","FOROUT: FORM OF OUTCOME",
                                      "FOROUT: FORM OF OUTCOME",
                                      "FOROUT: FORM OF OUTCOME","FOROUT: FORM OF OUTCOME",
                                      "FOROUT: FORM OF OUTCOME","FOROUT: FORM OF OUTCOME",
                                      "FOROUT: FORM OF OUTCOME",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBACTM: CONTENT OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBEFAC: MOST EFFECTIVE GLOBAL ORGANIZATION INVOLVEMENT",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GLOBORG: GLOBAL ORGANIZATION ORGAN MOST ACTIVE IN CRISIS",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED","GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "GRAVCR: GRAVITY OF VALUE THREATENED",
                                      "HETERO: HETEROGENEITY","HETERO: HETEROGENEITY",
                                      "HETERO: HETEROGENEITY","HETERO: HETEROGENEITY",
                                      "HETERO: HETEROGENEITY",
                                      "HETERO: HETEROGENEITY","HETERO: HETEROGENEITY",
                                      "ISSUES: ISSUES","ISSUES: ISSUES","ISSUES: ISSUES",
                                      "ISSUES: ISSUES","ISSUES: ISSUES",
                                      "ISSUES: ISSUES","ISSUES: ISSUES",
                                      "MEDIATE: DID MEDIATION OCCUR",
                                      "MEDIATE: DID MEDIATION OCCUR","MEDIATE: DID MEDIATION OCCUR",
                                      "MEDIATE: DID MEDIATION OCCUR",
                                      "MEDIATE: DID MEDIATION OCCUR",
                                      "MEDIATE: DID MEDIATION OCCUR",
                                      "OUTESR: ESCALATION OR REDUCTION OF TENSION",
                                      "OUTESR: ESCALATION OR REDUCTION OF TENSION",
                                      "OUTESR: ESCALATION OR REDUCTION OF TENSION",
                                      "OUTESR: ESCALATION OR REDUCTION OF TENSION",
                                      "OUTESR: ESCALATION OR REDUCTION OF TENSION",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "POWCH: CHANGE IN DISTRIBUTION OF POWER",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGACTMB: CONTENT OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "REGIONAL-SECURITY ORGANIZATION MOST ACTIVE IN CRISIS",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "ROEFCT: EFFECTIVENESS OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "RUGACH: CHANGE IN RULES OF THE GAME",
                                      "RUGACH: CHANGE IN RULES OF THE GAME","RUGACH: CHANGE IN RULES OF THE GAME",
                                      "RUGACH: CHANGE IN RULES OF THE GAME",
                                      "RUGACH: CHANGE IN RULES OF THE GAME",
                                      "RUGACH: CHANGE IN RULES OF THE GAME",
                                      "RUGACH: CHANGE IN RULES OF THE GAME",
                                      "SEVVIOSY: INTENSITY OF VIOLENCE",
                                      "SEVVIOSY: INTENSITY OF VIOLENCE",
                                      "SEVVIOSY: INTENSITY OF VIOLENCE","SEVVIOSY: INTENSITY OF VIOLENCE",
                                      "SEVVIOSY: INTENSITY OF VIOLENCE",
                                      "SEVVIOSY: INTENSITY OF VIOLENCE",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SOGLACT: SOURCE OF GLOBAL ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SORACT: SOURCE OF REGIONAL-SECURITY ORGANIZATION INVOLVEMENT",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SOURDT: SOURCES USED FOR CODING DATA",
                                      "SUBOUT: CONTENT OF OUTCOME","SUBOUT: CONTENT OF OUTCOME",
                                      "SUBOUT: CONTENT OF OUTCOME",
                                      "SUBOUT: CONTENT OF OUTCOME",
                                      "SUEFAC: MOST EFFECTIVE USSR ACTIVITY",
                                      "SUEFAC: MOST EFFECTIVE USSR ACTIVITY",
                                      "SUEFAC: MOST EFFECTIVE USSR ACTIVITY","SUEFAC: MOST EFFECTIVE USSR ACTIVITY",
                                      "SUEFAC: MOST EFFECTIVE USSR ACTIVITY",
                                      "SUEFAC: MOST EFFECTIVE USSR ACTIVITY",
                                      "SUEFAC: MOST EFFECTIVE USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUEFCT: EFFECTIVENESS OF USSR ACTIVITY",
                                      "SUINV: CONTENT OF USSR ACTIVITY",
                                      "SUINV: CONTENT OF USSR ACTIVITY",
                                      "SUINV: CONTENT OF USSR ACTIVITY",
                                      "SUINV: CONTENT OF USSR ACTIVITY",
                                      "SUINV: CONTENT OF USSR ACTIVITY","SUINV: CONTENT OF USSR ACTIVITY",
                                      "SUPACE: USSR ACTIVITY AND PACE OF ABATEMENT",
                                      "SUPACE: USSR ACTIVITY AND PACE OF ABATEMENT",
                                      "SUPACE: USSR ACTIVITY AND PACE OF ABATEMENT",
                                      "SUPACE: USSR ACTIVITY AND PACE OF ABATEMENT",
                                      "SUPACE: USSR ACTIVITY AND PACE OF ABATEMENT",
                                      "SUPACE: USSR ACTIVITY AND PACE OF ABATEMENT",
                                      "USEFAC: MOST EFFECTIVE US ACTIVITY",
                                      "USEFAC: MOST EFFECTIVE US ACTIVITY",
                                      "USEFAC: MOST EFFECTIVE US ACTIVITY",
                                      "USEFAC: MOST EFFECTIVE US ACTIVITY",
                                      "USEFAC: MOST EFFECTIVE US ACTIVITY","USEFAC: MOST EFFECTIVE US ACTIVITY",
                                      "USEFAC: MOST EFFECTIVE US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USEFCT: EFFECTIVENESS OF US ACTIVITY",
                                      "USINV: CONTENT OF US ACTIVITY",
                                      "USINV: CONTENT OF US ACTIVITY","USINV: CONTENT OF US ACTIVITY",
                                      "USINV: CONTENT OF US ACTIVITY",
                                      "USINV: CONTENT OF US ACTIVITY",
                                      "USINV: CONTENT OF US ACTIVITY",
                                      "USPACE: US ACTIVITY AND PACE OF ABATEMENT",
                                      "USPACE: US ACTIVITY AND PACE OF ABATEMENT",
                                      "USPACE: US ACTIVITY AND PACE OF ABATEMENT",
                                      "USPACE: US ACTIVITY AND PACE OF ABATEMENT",
                                      "USPACE: US ACTIVITY AND PACE OF ABATEMENT",
                                      "USPACE: US ACTIVITY AND PACE OF ABATEMENT",
                                      "VIOL: VIOLENCE","VIOL: VIOLENCE","VIOL: VIOLENCE",
                                      "VIOL: VIOLENCE","VIOL: VIOLENCE",
                                      "VIOL: VIOLENCE","TIMVIO: TIMING OF VIOLENCE",
                                      "TIMVIO: TIMING OF VIOLENCE",
                                      "TIMVIO: TIMING OF VIOLENCE",
                                      "TIMVIO: TIMING OF VIOLENCE","TIMVIO: TIMING OF VIOLENCE"),
                            value = c(1L,2L,3L,4L,5L,6L,7L,8L,9L,99L,1L,
                                      2L,3L,4L,9L,95L,1L,2L,3L,4L,5L,
                                      9L,95L,1L,2L,3L,4L,5L,9L,95L,1L,
                                      2L,3L,4L,5L,6L,7L,8L,9L,95L,1L,
                                      2L,3L,4L,9L,95L,1L,2L,3L,9L,95L,
                                      1L,2L,3L,4L,5L,6L,7L,9L,95L,1L,
                                      2L,3L,4L,5L,6L,7L,9L,95L,0L,1L,
                                      10L,11L,12L,13L,2L,3L,4L,5L,6L,7L,
                                      8L,9L,95L,99L,0L,1L,2L,3L,4L,5L,
                                      6L,9L,95L,0L,1L,2L,3L,4L,5L,9L,
                                      95L,0L,1L,2L,3L,4L,5L,6L,7L,9L,
                                      95L,1L,2L,3L,4L,5L,9L,95L,1L,2L,3L,
                                      4L,5L,9L,95L,1L,2L,3L,4L,9L,95L,
                                      1L,2L,3L,9L,95L,1L,2L,3L,4L,5L,
                                      9L,95L,0L,1L,10L,11L,12L,13L,2L,
                                      3L,4L,5L,6L,7L,8L,9L,95L,99L,0L,
                                      1L,10L,11L,2L,3L,4L,5L,6L,7L,8L,
                                      9L,95L,99L,0L,1L,2L,3L,4L,5L,6L,
                                      9L,95L,1L,2L,3L,4L,5L,9L,95L,1L,
                                      2L,3L,4L,9L,95L,0L,1L,2L,3L,4L,
                                      5L,6L,7L,9L,95L,0L,1L,2L,3L,4L,5L,
                                      6L,7L,9L,95L,1L,2L,3L,4L,5L,6L,
                                      7L,9L,95L,1L,2L,9L,95L,1L,2L,3L,
                                      4L,5L,9L,95L,1L,2L,3L,4L,5L,6L,
                                      9L,95L,1L,2L,3L,4L,9L,95L,1L,2L,
                                      3L,4L,9L,95L,1L,2L,3L,4L,5L,9L,
                                      95L,1L,2L,3L,4L,5L,6L,9L,95L,1L,
                                      2L,3L,4L,9L,95L,1L,2L,3L,4L,9L,
                                      95L,1L,2L,3L,4L,9L,95L,1L,2L,3L,4L,
                                      95L),
                             text = c("VERBAL ACT","POLITICAL ACT",
                                      "ECONOMIC ACT","EXTERNAL CHANGE",
                                      "OTHER NON-VIOLENT ACT","INTERNAL CHALLENGE",
                                      "NON-VIOLENT MILITARY","INDIRECT VIOLENT",
                                      "VIOLENT ACT","MD","NO VIOLENCE AS CMT",
                                      "VIOLENCE MINOR","VIOLENCE IMPORTANT",
                                      "VIOLENCE PREEMINENT","MD",
                                      "Coding pending - see processing note","NO CHANGE",
                                      "CHANGE REG ORIENTATION","CHANGE REGIME TYPE",
                                      "CREATE-ELIM ACTOR","INTERIM CASE","MD",
                                      "Coding pending - see processing note",
                                      "NO CHANGE ALLIANCE","INC-DEC COHESION",
                                      "ENTRY-EXIT ALLIANCE","FORM-ELIM ALLIANCE",
                                      "INTERIM CASE","MD",
                                      "Coding pending - see processing note","NEGOTIATION",
                                      "ADJUD OR ARBITRATION","MEDIATION","MULT NO VIOLENCE",
                                      "NON-MILITARY PRESSURE",
                                      "NON-VIOL MILITARY","MULT INC VIOLENCE","VIOLENCE","MD",
                                      "Coding pending - see processing note",
                                      "SECESSIONIST","IRREDENTIST","OTHER",
                                      "NON-ETHNIC","MD",
                                      "Coding pending - see processing note","SECESSIONIST CONFLICT",
                                      "IRREDENTIST CONFLICT",
                                      "NON-ETHNIC CONFLICT","MD",
                                      "Coding pending - see processing note","ALL SATISFIED",
                                      "MOSTLY SATISFIED","EQUALLY MIXED","MOSTLY DISSATISFIED",
                                      "ALL DISSATISFIED","SINGLE ACTOR CASE",
                                      "NO ADVERSARIAL ACTOR","MD",
                                      "Coding pending - see processing note",
                                      "FORMAL AGREEMENT","SEMI-FORMAL AGREE",
                                      "TACIT UNDRSTND","UNILATERAL ACT","IMPOSED AGREEMENT",
                                      "OTHER","FADED","MD",
                                      "Coding pending - see processing note","GO NOT EXIST",
                                      "NO ACTIVITY","OBSERVER GROUP",
                                      "AUTH MIL FORCE MEMBERS","EMERGENCY MIL FORCE",
                                      "GENERAL-OTHER","DISC NO RESOLUTION",
                                      "FACT-FINDING","GOOD OFFICES","CONDEMNATION",
                                      "CALL FOR ACTION","MEDIATION","ARBITRATION",
                                      "SANCTIONS",
                                      "Coding pending - see processing note","MD","GO NOT EXIST",
                                      "NO GO ACTIVITY","GO ACT ESCALATED",
                                      "GO ACT NOT CONTRIB","GO ACT MARGINAL",
                                      "GO ACT IMPORTANT","GO ACT MOST IMPORT","MD",
                                      "Coding pending - see processing note",
                                      "GO NOT EXIST","NO GO ACTIVITY","GENERAL",
                                      "SECRETARY GENERAL","GENERAL ASSEMBLY",
                                      "SECURITY COUNCIL","MD",
                                      "Coding pending - see processing note","ECONOMIC THREAT",
                                      "LIMITED MIL DAMAGE","POLITICAL THREAT",
                                      "TERRITORIAL THREAT","THREAT TO INFLUENCE",
                                      "THREAT OF GRAVE DAMAGE",
                                      "THREAT TO EXISTENCE","OTHER","MD",
                                      "Coding pending - see processing note","NONE","ONE ATTRIBUTE",
                                      "TWO ATTRIBUTES","THREE ATTRIBUTES",
                                      "ALL 4 ATTRIBUTES","MD",
                                      "Coding pending - see processing note","1 ISS NOT MIL-SEC",
                                      "2 ISS NOT MIL-SEC","ONLY MIL-SEC",
                                      "2 ISS INC MIL-SEC","3 ISSUES","MD",
                                      "Coding pending - see processing note",
                                      "NO MEDIATION","REQUESTED NOT SUPPLIED",
                                      "OFFERED NOT ACCEPTED","MEDIATION OCCURRED","-",
                                      "Coding pending - see processing note",
                                      "ESCALATION OF TENSION",
                                      "REDUCTION OF TENSION","RECENT CASE","MD",
                                      "Coding pending - see processing note","NO CHANGE",
                                      "CHANGE REL POWER","CHANGE RANK",
                                      "CHANGE COMPOSITION","INTERIM CASE","MD",
                                      "Coding pending - see processing note",
                                      "RO NOT EXIST","NO RO ACTIVITY","OBSERVER FORCE",
                                      "EMERGENCY MIL FORCE","MULTIPLE",
                                      "GENERAL-OTHER","DISC NO RESOLUTION",
                                      "FACT-FINDING","GOOD OFFICES","CONDEMNATION",
                                      "CALL FOR ACTION","MEDIATION","ARBITRATION",
                                      "SANCTIONS",
                                      "Coding pending - see processing note","MD","RO NOT EXIST",
                                      "NO RO INVOLVEMENT","OTHER","MULTIPLE","LAS",
                                      "NATO","OAS","OAU","SEATO","WTO","CENTO",
                                      "COUNCIL OF EUROPE",
                                      "Coding pending - see processing note","MD","RO NOT EXIST",
                                      "NO RO ACTIVITY","RO ESCALATED",
                                      "RO NOT CONTRIBUTE","RO MARGINAL","RO IMPORTANT",
                                      "RO MOST IMPORTANT","MD",
                                      "Coding pending - see processing note","NO CHANGE",
                                      "DECLINE IN CONSENSUS","BRKDN IN CONSENSUS",
                                      "CREATE-ELIM RULES","INTERIM CASE",
                                      "MD","Coding pending - see processing note",
                                      "NO VIOLENCE AS CMT","MINOR CLASHES",
                                      "SERIOUS CLASHES","FULL SCALE WAR","MD",
                                      "Coding pending - see processing note",
                                      "GO NOT EXIST","GO NOT APPROACHED",
                                      "CRISIS ACTOR","THIRD PARTY","US","USSR",
                                      "INITIATED BY GO","MULTIPLE","MD",
                                      "Coding pending - see processing note",
                                      "RO NOT EXIST","RO NOT APPROACHED","CRISIS ACTOR",
                                      "THIRD PARTY","US","USSR",
                                      "INITIATED BY RO","MULTIPLE","MD",
                                      "Coding pending - see processing note","COMBINED",
                                      "COMBINED NO DOCS","COMBINED NON MEM",
                                      "COMBINED NO ART","COMG NO DOCS & MEM",
                                      "CHRON ARCHIVES","CHRON ARCH & MEM","MD",
                                      "Coding pending - see processing note",
                                      "AMBIGUOUS OUTCOME","DEFINITIVE OUTCOME","MD",
                                      "Coding pending - see processing note",
                                      "NO INVOLVEMENT","INEFFECTIVE",
                                      "EFF LOW LEVEL ACT","EFF COVERT OR SEMIL",
                                      "EFF MILITARY ACT","MD",
                                      "Coding pending - see processing note","NO INVOLVEMENT",
                                      "INV ESCALATED","INV NOT CONTRIBUTE","MARGINAL",
                                      "IMPORTANT","MOST IMPORTANT","MD",
                                      "Coding pending - see processing note",
                                      "NO INVOLVEMENT","LOW INVOLVEMENT","SEMI MIL-COVERT",
                                      "DIRECT MILITARY INV","MD",
                                      "Coding pending - see processing note",
                                      "NO INVOLVEMENT","DELAY TERMINATION",
                                      "ACT NOT EFFECTIVE","CONTRIBUTED TO TERM","MD",
                                      "Coding pending - see processing note",
                                      "NO INVOLVEMENT","INEFFECTIVE","EFF LOW LEVEL ACT",
                                      "EFF COVERT OR SEMIL",
                                      "EFF MILITARY ACT","MD",
                                      "Coding pending - see processing note","NO INVOLVEMENT","INV ESCALATED",
                                      "INV NOT CONTRIBUTE","MARGINAL",
                                      "IMPORTANT","MOST IMPORTANT","MD",
                                      "Coding pending - see processing note",
                                      "NO INVOLVEMENT","LOW INVOLVEMENT","SEMI MIL-COVERT",
                                      "DIRECT MILITARY INV","MD",
                                      "Coding pending - see processing note","NO INVOLVEMENT",
                                      "DELAY TERMINATION","ACT NOT EFFECTIVE",
                                      "CONTRIBUTED TO TERM","MD",
                                      "Coding pending - see processing note","NO VIOLENCE",
                                      "MINOR CLASHES","SERIOUS CLASHES",
                                      "WAR","MD",
                                      "Coding pending - see processing note","NO VIOLENCE","VIOL PRIOR CRISIS",
                                      "VIOL TRIG CRISIS","VIOL SUBSEQ TRIGGER",
                                      "Coding pending - see processing note")
               )

icb_recodes_clean <- 
    icb_recodes %>% 
      mutate(question=description %>% str_replace(".*: ","") %>% str_to_sentence() %>% paste0("?")) %>%
      mutate(answer=text %>% str_to_sentence() )  %>%
      mutate(var=var %>% tolower()) %>%
      dplyr::select(var, value, question, answer)

icb_crises_qa <- icb_crises %>%
                dplyr::select(crisno, crisname, start=yrtrig, end=yrterm, starts_with(icb_recodes_clean$var %>% unique())) %>% #grab all
                pivot_longer(-c(crisno, crisname,start,end), names_to="var") %>% 
                left_join(icb_recodes_clean )

qa_unique <- icb_crises_qa  %>% arrange(var, value) %>% dplyr::select(question, answer) %>% distinct() %>% na.omit()

q_unique <- qa_unique %>% dplyr::select(question) %>% distinct()

icb_crises_qa_wide <- icb_crises_qa %>% 
  filter(var %in% (c("break", 'GRAVCR','CENVIOSY','SEVVIOSY','CHACTS','CHALL','EXSAT','FOROUT') %>% tolower() ) ) %>% 
  dplyr::select(crisno,crisname,start, end, question,answer) %>%
  na.omit() %>%
  pivot_wider(id_cols=c(crisno, crisname,start,end), 
              names_from=question,values_from=answer, values_fn=function(x) paste0(x, collapse=";") )

```

```{r include=F}
#Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_crc32)) %>% dplyr::select(crisno, email_crc32) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)

avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)

avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_crc32)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)

events_per_sentence <- icb_wide_clean %>% 
                        filter(!is.na(sentence_number_int_aligned)) %>%
                        dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) %>%  #event_number_int
                        group_by(email_id,crisno,sentence_number_int_aligned) %>% 
                        summarise(event_count = sum(!is.na(event_type) ) ) %>%
                        mutate_all(as.numeric) %>%
                        group_by(crisno,sentence_number_int_aligned) %>% 
                        summarise(
                          event_count_min=event_count %>% min(),
                          event_count_mean=event_count %>% mean(na.rm=T),
                          event_count_max=event_count %>% max()
                          ) %>%
                        arrange(crisno,sentence_number_int_aligned)

events_per_crisis <- events_per_sentence %>% group_by(crisno) %>% summarise(event_count_mean_sum=sum(event_count_mean))

crisis_text_counts <- icb_wide_clean %>% 
  mutate( input_crisis = input_crisis %>% str_replace_all("[^A-Za-z0-9 ]","") ) %>% #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
  #https://www.google.com/search?q=R+replace+00A0&oq=R+replace+00A0&aqs=chrome..69i57j0i20i263i512j0i512l2j69i65j69i60l3.1744j0j7&sourceid=chrome&ie=UTF-8
  dplyr::select(crisno, input_crisis, sentence) %>% 
  #mutate(input_crisis = input_crisis %>% stringr::str_to_title()) %>% 
  mutate(input_crisis = input_crisis %>% stringr::str_replace_all('[0-9]$','')) %>% 
  mutate(sentence = sentence %>% stringr::str_to_lower()) %>% 
  distinct() %>% 
  filter(!is.na(input_crisis)) %>% 
  filter(!is.na(sentence)) %>% 
  mutate(word_count=str_count(sentence, '\\w+')) %>%
  group_by(crisno, input_crisis) %>%
  summarise(
    sentence_count=n(),
    word_count=sum(word_count)
  )

#Even type

library(sjmisc)
event_type_per_sentence <- icb_wide_clean %>% 
                            filter(!is.na(sentence_number_int_aligned)) %>%
                            dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type)  %>% 
                            to_dummy(event_type, suffix = "label") %>% 
                            bind_cols( icb_wide_clean %>% 
                            filter(!is.na(sentence_number_int_aligned)) %>%
                            dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) ) %>%

                            group_by(email_id,crisno,sentence_number_int_aligned) %>% 
                            summarise_if( is.numeric, sum ) %>%

                            group_by(crisno,sentence_number_int_aligned) %>% 
                            summarise_if( is.numeric, mean, na.rm=T ) %>%
                            arrange(crisno,sentence_number_int_aligned)

event_type_per_sentence_totals <- event_type_per_sentence %>% ungroup() %>% summarise_if( is.numeric, sum, na.rm=T ) %>% dplyr::select(-crisno)
event_type_per_sentence_totals_perc <- event_type_per_sentence_totals/sum(event_type_per_sentence_totals)

```

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}

p_load(flextable)
p_load(ftExtra)
set_flextable_defaults(fonts_ignore=TRUE)

crisis_text_counts_ft <- 
        crisis_text_counts %>%
        ungroup() %>% 
        left_join(events_per_sentence %>% dplyr::select(crisno, event_count_mean) %>% 
                    group_by(crisno) %>% summarise(event_count_mean_sum=sum(event_count_mean)) %>% distinct() %>%
                    mutate(event_count_mean_sum = event_count_mean_sum %>% round(1)) ) %>%
        left_join(icb_crises_qa_wide %>% 
                    dplyr::select(-crisname)
                  ) %>%
        mutate(input_crisis=input_crisis %>% tolower()) %>%
        dplyr::select(-word_count)  %>%
        dplyr::select(crisno,
                      input_crisis,
                      start,
                      end,
                      sentence_count,
                      event_count_mean_sum,
                      "Breakpoint (trigger) to international crisis?",  
                      "Gravity of value threatened?",
                      "Intensity of violence?",
                      "Form of outcome?",
                      "Extent of satisfaction about outcome?"
                      ) %>%

        flextable::as_flextable() %>%

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6, part = "all" ) %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( 
          values = list(crisno = "#", 
                        input_crisis = "Name", 
                        start="Start",
                        end="End",
                        sentence_count="Sent.", 
                        event_count_mean_sum="Events" ,
                        "Breakpoint (trigger) to international crisis?"="Trigger",
                        "Centrality of violence?"="Violence",
                        #"Change in actors?"="Change in Actors",
                        #"Change in alliance configuration?"="Change in Alliance",
                        "Extent of satisfaction about outcome?"="Satisfaction",
                        "Form of outcome?"="Outcome",
                        "Gravity of value threatened?"="Gravity",
                        "Intensity of violence?"="Intensity"
                        )
          ) %>% # , word_count="Words"
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        #set_table_properties(layout="autofit") %>%  
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        bg( i = which( 1:nrow(crisis_text_counts) %% 2 == 1)  , part = "body", bg = "#EFEFEF") %>%
        flextable::width( j = 1, width=0.2) %>%
        flextable::width( j = 2, width=1) %>%  
        flextable::width( j = 3, width=0.2) %>% colformat_num(j=3, big.mark="", decimal.mark = "",na_str = "") %>%
        flextable::width( j = 4, width=0.2) %>% colformat_num(j=4, big.mark="", decimal.mark = "",na_str = "") %>%
        flextable::width( j = 5, width=0.2) %>% 
        flextable::width( j = 6, width=0.3) %>% 
        flextable::width( j = 7:11, width=0.9)

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

crisis_text_counts_ft  %>% saveRDS(paste0(here::here(), "/replication_paper/tables/ft_crisis_text_counts.Rds"))

crisis_text_counts_ft
```

### 2022-01-26 README.Rmd
01 and 02 fix

@@
 
-# The Paper:
+## The Paper:
 
-[Introducing the International Crisis Behavior Event (ICBe) Dataset](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)
+[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)
+
+## The Data:
+
+The agreed datasets are the final, dataset used in much of the paper and figures.
+It includes our best efforts at cleaning the data and reconciling intercoder agreement.
+The dataset is available in long and wide format.
+  - [codings_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_long_agreed.Rds)
+  - [codings_wide_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_wide_agreed.Rds)
+
+The initial codings pre-cleaning and reconciling intercoder agreement are also available. 
+  - [icb_coder_crisis_sentence_event_aligned.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds)
+
+The coding and cleaning process are described in the paper with additional information and details about the variables in the codebook.
+  - [ICBEdataset Codebook](https://docs.google.com/document/d/1aJkweohbfIWtNpJw1CmXbeIiK6czbJ5iPyKwiYP1YlU/edit?usp=sharing)
 
@@
 
-- [Rex W.
+[Rex W.
 Douglass](http://www.rexdouglass.com), [Thomas Leo Scherer](http://tlscherer.com/), [J.
@@
 
-## Data:
+## Citation:
+For any use of the dataset or paper, please cite:
 
-# ICBe Dataset
-
-- ICBe Dataset
-- [ICBEdataset Codebook](https://docs.google.com/document/d/1aJkweohbfIWtNpJw1CmXbeIiK6czbJ5iPyKwiYP1YlU/edit?usp=sharing)
+Douglass, Rex W.,  Thomas Leo Scherer, J.
+Andrés Gannon, Erik Gartzke, Jon Lindsay, Shannon Carcelli, Jonathan Wiklenfeld, David M.
+Quinn, Catherine Aiken, Jose Miguel Cabezas Navarro, Neil Lund, Egle Murauskaite, and Diana Partridge.
+2022.
+"Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises." Unpublished Manuscript.
+Retrieved from https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset.
 
@@
 
-All of the files necessary for reproducing our analysis are including in a self contained R package "ICBEdataset" You can install the package icb from github with:
-
-``` r
-# install.packages("devtools")
-devtools::install_github("centerforpeaceandsecuritystudies/ICBEdataset")
-```
+All of the files used to create the datasets, tables, figures.
 
 ## RMarkdown files
+
+### Replication Data
+
  - 01_compile_saves_and_align
@@
     + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.
+
+### Replication Paper
+
+  - CaseStudy196
+  - CaseStudy426
+  - ICBEdataset_figure_metro_maps
+  - ICBEdataset_figure_semantic_embeddings
+  - ICBEdataset_paper_appendixICBCrises
+  - ICBEdataset_paper_appendixVerbMeanings
+  - ICBEdataset_paper_figure_prep
+  - ICBEdataset_paper_PlotInterCoderAgreement
 
@@
 
-### ICBe preperation
+### ICBe preparation
   - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
@@
 
-### Acknowledgementes
+### Acknowledgements

### 2022-01-26 replication_data/rmd/01_compile_saves_and_align.Rmd
01 and 02 fix

@@
     saveRDS(icb_coder_crisis_sentence_event,
-            file=paste0(here::here(),"/replication_data/temp/icb_coder_crisis_sentence_event.Rds"))
+            file=paste0(here::here(),"/replication_data/in/icb_coder_crisis_sentence_event.Rds"))
   }  else  {
     icb_coder_crisis_sentence_event <-
-      readRDS(file=paste0(here::here(),"/replication_data/temp/icb_coder_crisis_sentence_event.Rds"))
+      readRDS(file=paste0(here::here(),"/replication_data/in/icb_coder_crisis_sentence_event.Rds"))
 }

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
01 and 02 fix

@@
 ```{r message=FALSE}
-
-full_tree <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit?usp=sharing", sheet="Codebook in Tree Form")
+target_file <- paste0(here::here(),"/replication_data/in/icbe_litreview_trees_sentences.xlsx")
+full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")
 
@@
 saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds")) 
-saveRDS(icb_wide_clean, paste0(here::here(), "/replication_paper/in/icb_wide_clean.Rds"))
+saveRDS(icb_wide_clean, paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
 

### 2022-01-26 prune/ICBEdataset_paper_InterCoderByLevels.Rmd
fixes

@@
 
-target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
+target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
 full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

### 2022-01-26 prune/ICBEdataset_paper_TableExampleSentenceCoding.Rmd
fixes

@@
 
-target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
+target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
 sentence_example_sheet    <- readxl::read_excel(target_file, sheet="Sentence Tree Example Table")

### 2022-01-26 prune/ICBEdataset_paper_uncertainty.Rmd
fixes

@@
 ```{r}
-target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
+target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
 full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
fixes

@@
 temp_wide <- icb_long_clean2 %>%
-             dplyr::select(icb_survey_version, email_id,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
+             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
              dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
@@
          dplyr::select(-variable_normalized,-value_normalized) %>%
-         tidyr::pivot_longer(-c(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section, sentence,   event_number_int,event_number_int_condition),
+         tidyr::pivot_longer(-c(icb_survey_version, email_id,  input_crisis, crisno, sentence_number_int_aligned, section, sentence,   event_number_int,event_number_int_condition),
                       names_to='variable_normalized' , values_to= 'value_normalized')  %>%
@@
 icb_long_clean_final <- icb_long_clean2 %>%
-                   dplyr::select(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section,  sentence,  event_number_int, event_number_int_condition, variable_normalized, value_normalized) %>%
+                   dplyr::select(icb_survey_version, email_id, input_crisis, crisno, sentence_number_int_aligned, section,  sentence,  event_number_int, event_number_int_condition, variable_normalized, value_normalized) %>%
                   rbind(temp_long) %>% dplyr::distinct() %>% 

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixICBCrises.Rmd
fixes

@@
 ```{r include=F}
-#Load the ICB wide codings
+# #Load the ICB wide codings
 icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
@@
 
-avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_crc32)) %>% dplyr::select(crisno, email_crc32) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
+avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
 
@@
 
-avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_crc32)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
+avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
 

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixVerbMeanings.Rmd
fixes

@@
 
-target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
 dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

### 2022-01-26 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
fixes
paper rmds

@@
 
-library(flextable); library(ftExtra)
+library(flextable)
+library(ftExtra)
 library(tidyverse)
-library(googlesheets4)
 
@@
 
-codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_long_agreed_embeded.Rds'))
+codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/codings_long_agreed_embeded.Rds'))
 
@@
 
-codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_wide_agreed_embeded.Rds'))
+codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/codings_wide_agreed_embeded.Rds'))
 
@@
 p_semantic_embeddings
+
+ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
 

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
paper rmds

@@
 ```{r}
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
-codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
-codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
-codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) 
+codings_long <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_long.Rds'))
+codings_long_agreement <- readRDS( paste0(here::here(), '/replication_paper/data/in/codings_long_agreement.Rds'))
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_paper/data/in/codings_long_agreed.Rds'))
+codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
 

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
paper rmds

@@
 
-icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/","icb1v14.csv")) 
+icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
 #icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds"))
@@
 #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
-p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
+# p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
+# ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
 ```

### 2022-01-27 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
heresy

@@
               mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
-              mutate(IMAGE=paste0(here::here, '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
+              mutate(IMAGE=paste0(here::here(), '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
               mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%

### 2022-01-31 README.Rmd
bibfix

@@
 ---
-output: github_document
+output: 
+  github_document:
+      toc: true
 ---
@@
 ``` 
+[![CC BY-NC-SA 4.0][cc-by-nc-sa-shield]][cc-by-nc-sa]
 
@@
 The dataset is available in long and wide format.
+
   - [codings_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_long_agreed.Rds)
@@
 
-### Acknowledgements
+### License
+
+This work is licensed under a
+[Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License][cc-by-nc-sa].
+
+[![CC BY-NC-SA 4.0][cc-by-nc-sa-image]][cc-by-nc-sa]
+
+[cc-by-nc-sa]: http://creativecommons.org/licenses/by-nc-sa/4.0/
+[cc-by-nc-sa-image]: https://licensebuttons.net/l/by-nc-sa/4.0/88x31.png
+[cc-by-nc-sa-shield]: https://img.shields.io/badge/License-CC%20BY--NC--SA%204.0-lightgrey.svg

### 2022-01-31 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
paper
remove distrib warning

@@
 title: |
-  | DRAFT, NOT FOR DISTRIBUTION 
   | Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises
@@
 
-TLS = TRUE
+TLS = FALSE
 ```

### 2022-02-02 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
sentences_embeddings save

@@
 library(reticulate)
-#py_discover_config()
+py_discover_config()
 
-use_python("/home/skynet3/anaconda3/bin/python/")
+#use_python("/home/skynet3/anaconda3/bin/python/")
+use_python("/home/tlscherer/anaconda3/bin/python")
 
@@
 
-fromscratch=True
+fromscratch=False
 
@@
 ```{r}
+fromscratch = FALSE
 
+if(fromscratch){
   sentences_embeddings <- py$sentences_embeddings
   dim(sentences_embeddings)
+  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
+}else{
+  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
+  dim(sentences_embeddings)
+}
+
+```
+
+```{r}
 
@@
 library(umapr)
-embedding <- umap(sentences_embeddings  )
+embedding <- umap(sentences_embedding)
 
@@
 codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
-codings_wide_agreed_embeded <- codings_wide_agreed %>% ungroup() %>% left_join(sentences_embeded)
+codings_wide_agreed_embeded <- codings_wide_agreed %>% dplyr::ungroup() %>% dplyr::left_join(sentences_embeded)
 
@@
 
+```
+
+```{r}
+# codings_long_agreed_embeded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/codings_long_agreed_embeded.Rds'))
+# codings_wide_agreed_embeded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/codings_wide_agreed_embeded.Rds'))
+
 var_keep <- c('Behavior','do_aggression','Do_Armed_Unarmed','leaf_do_original') %>% tolower() #'Event_Any',
@@
       dplyr::select(variable_normalized,value_normalized,UMAP1,UMAP2) %>%
-      group_by(variable_normalized, value_normalized) %>% 
-      summarise_all(median) %>%
-      group_by(variable_normalized) %>%
-          mutate(variable_normalized_count=  min(n(),4)  ) %>%
-      ungroup()
+      dplyr::group_by(variable_normalized, value_normalized) %>% 
+      dplyr::summarise_all(median) %>%
+      dplyr::group_by(variable_normalized) %>%
+          dplyr::mutate(variable_normalized_count=  min(dplyr::n(),4)  ) %>%
+      dplyr::ungroup()
 
@@
 library(RColorBrewer)
-brewer_pal_info_df <- brewer.pal.info %>% add_rownames( var = "rowname") %>% arrange()
+brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange()
 brewer_list <- list() 
@@
 
+library(ggplot2)
 p_semantic_embeddings <-

### 2022-02-03 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
embed

@@
 
+To set python, set it in ~/.Renviron.
+`use_python()` doesn't seem to work as desired.
+See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
+
 ```{r, messages=F, results='hide'}
 library(reticulate)
-py_discover_config()
+reticulate::py_discover_config()
 
 #use_python("/home/skynet3/anaconda3/bin/python/")
-use_python("/home/tlscherer/anaconda3/bin/python")
+#use_python("/home/tlscherer/anaconda3/bin/python3")
 
@@
 ```
+The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.
 
@@
 library(umapr)
-embedding <- umap(sentences_embedding)
+embedding <- umapr::umap(sentences_embeddings)
 
@@
 posible_colors <- unlist(brewer_list) %>% unique(brewer_list)  #%>% sample()
+posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0")] # drop white
 
 value_normalized=codings_long_agreed_embeded_subset$value_normalized %>% unique() %>% as.factor()
-value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a brewer pallet with lots of values and then assign it to specific values
 names(value_normalized_colors) = levels(value_normalized)
+
+# do leaf originals to keep labels for
+do_leaf_keep <- codings_long_agreed_embeded_subset %>% dplyr::filter(variable_normalized=="leaf_do_original") %>% dplyr::count(value_normalized) %>% arrange(desc(n)) %>% dplyr::slice_head(n=10)
+
+value_means <- value_means %>% dplyr::mutate(label=ifelse(
+  variable_normalized=="leaf_do_original" & !(value_normalized %in% do_leaf_keep$value_normalized), 0, 1))
 
@@
         theme(legend.position = "none") + 
-        geom_label(data=value_means,
-                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, label=value_normalized, size=50),inherit.aes=F, # #variable_normalized_count
+        geom_label(data=subset(value_means, label==1),
+                   aes(x=UMAP1,y=UMAP2, fill = value_normalized, 
+                       label=value_normalized, size=50), size = 3, inherit.aes=F, # #variable_normalized_count
                    colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")) + 

### 2022-02-04 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
refactored crisis maps

@@
 
-codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icbe_metro_plots(x))
+c(196, 426) %>% sapply(FUN=function(x) icbe_metro_plots(x))
 
@@
 
-codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icb_sentence_tables(x))
+c(196, 426) %>% sapply(FUN=function(x) icb_sentence_tables(x))
 
@@
 
-dyadic_mid <- read_csv(paste0(here::here(), "/data_other_datasets/mids/Dyadic MIDs 4.02/dyadic_mid_4.02.csv"))
+dyadic_mid <- read_csv(paste0(here::here(), "/replication_paper/data/in/dyadic_mid_4.02.csv"))
 
@@
 
-codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) mids_metro_plots(x))
+c(196, 426) %>% sapply(FUN=function(x) mids_metro_plots(x))
 
@@
 
-icb_crises %>% filter(yrtrig>=1990) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) mids_incidents_metro_plots(x))
+icb_crises %>% filter(yrtrig>=1990 & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) mids_incidents_metro_plots(x))
 
@@
 
-icb2v14 <- read_csv(here::here(), "/replication_paper/data/in/icb2v14.csv")
+icb2v14 <- read_csv(paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))
 
@@
 
-codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icb_metro_plots(x))
+c(196, 426) %>% sapply(FUN=function(x) icb_metro_plots(x))
 
@@
 
-ged211 <- read_csv(here::here(), "/replication_paper/data/in/ucdp_ged/ged211.csv")
+ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged/ged211.csv"))
 
@@
 
-icb_crises %>% filter(yrtrig>=1989) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) ucdp_ged_metro_plots(x))
+icb_crises %>% filter(yrtrig>=1989 & crisno %in% c(196, 426) ) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) ucdp_ged_metro_plots(x))
 
@@
 
-files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/"), full.names = T)
+files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T)
 icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
@@
 
-icews_metro_plots <- function(crisis=426, topactor=F, exclude='', save_icews_file=NULL){
+icews_metro_plots <- function(crisis=426, topactor=F, exclude='', savefile=NULL){
 
@@
   if(is.null(savefile)){
-    save_icews_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
+    savefile <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
   }
@@
 
-  p_icews_metro_map  %>% saveRDS(save_icews_file)
-
-}
-
-icb_crises %>% filter(yrtrig>=1995) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) icews_metro_plots(x))
+  p_icews_metro_map  %>% saveRDS(savefile)
+
+}
+
+icb_crises %>% filter(yrtrig>=1995  & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) icews_metro_plots(x))
 
@@
 
-phoenix <- bind_rows(a, b, c, d , e)
+phoenix <- bind_rows(a %>% mutate_all(as.character),
+                     b %>% mutate_all(as.character),
+                     c %>% mutate_all(as.character),
+                     d %>% mutate_all(as.character) ,
+                     e %>% mutate_all(as.character)
+                     )
 
@@
 
-                 left_join(CAMEO_eventcodes %>% dplyr::select(code=cameoeventcode     , cameo_event_label=eventdescription) ) %>%
-
-                 left_join(CAMEO_eventcodes %>% dplyr::select(root_code=cameoeventcode, cameo_event_root_label=eventdescription) %>% filter(nchar(root_code)==2)) %>%
+                 left_join(CAMEO_eventcodes %>% dplyr::select(code=cameo_code     , cameo_event_label=cameo_label) ) %>%
+
+                 left_join(CAMEO_eventcodes %>% dplyr::select(root_code=cameo_code, cameo_event_root_label=cameo_label) %>% filter(nchar(root_code)==2)) %>%
 
@@
 
-codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) phoenix_metro_plots(x))
+c(196, 426) %>% sapply(FUN=function(x) phoenix_metro_plots(x))
 
@@
 
-files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
+files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
 terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
@@
      mutate(cameo_code=cameo_code %>% as.numeric()) %>% 
-     left_join(CAMEO_eventcodes %>% mutate(cameoeventcode=cameoeventcode %>% as.numeric(cameoeventcode)) %>%
-                 dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  ) %>%
+     left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code %>% as.numeric()) %>%
+                 dplyr::select(cameo_code=cameo_code, cameo_label= cameo_label)  ) %>%
     mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
@@
 
-icb_crises %>% filter(yrtrig>=1977) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))
+icb_crises %>% filter(yrtrig>=1977 & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))
 

### 2022-02-04 replication_data/rmd/01_compile_saves_and_align.Rmd
Consolidated save files, names, and locations

@@
 saveRDS(icb_wide_aligned %>% dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int),
-     file=paste0(here::here(),"/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds"))
+     file=paste0(here::here(),"/replication_data/temp/ICBe_V1_long_unclean.Rds"))
 ```

### 2022-02-04 replication_data/rmd/02_format_and_clean.rmd
Consolidated save files, names, and locations

@@
 ```{r}
-icb_wide_aligned_raw <- readRDS(file=paste0(here::here(),"/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds")) %>% 
+icb_wide_aligned_raw <- readRDS(file=paste0(here::here(),"/replication_data/temp/ICBe_V1_long_unclean.Rds")) %>% 
                     dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), sentence_number_int_aligned3 =
@@
 ```{r}
-saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
-saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))
+saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
 
@@
 
-saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds")) 
-saveRDS(icb_wide_clean, paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
+saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
 

### 2022-02-04 replication_data/rmd/03_aggregation.Rmd
input datas
Consolidated save files, names, and locations

--- 2022-01-20 replication_data/rmd/03_aggregation.Rmd
@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
 
@@
 
-Iterate and visualize sentences until convinced the translation is right
-
-```{r, eval=F}
-
-codings_wide_agreed_labeled_sample_ft <- 
-      codings_wide_agreed_pruned_labeled %>%
-                group_by(crisno, sentence_number_int_aligned, crisno_sent, sentence) %>%
-                summarize(codings_sentence = paste(codings_sentence, collapse="\n")) %>%
-                dplyr::select(crisno_sent, sentence, codings_sentence)  %>%
-                dplyr::filter(codings_sentence!="No events.") %>%
-                group_by(crisno) %>%
-                sample_n(size=1) %>%
-                ungroup() %>%
-                dplyr::select(crisno_sent, sentence, codings_sentence) %>%
-                as_flextable() %>%
-                colformat_md() %>% 
-                flextable::fontsize(size = 7, part = "all") %>%
-                flextable::bg( i = which( 1:nrow(codings_wide_agreed_pruned_labeled) %% 2 == 1)  , j=1:ncol(events_df), part = "body", bg = "#EFEFEF") %>%
-                flextable::width(j = 1, width=0.3, unit = "in") %>%
-                flextable::width(j = 2, width=3, unit = "in") %>%
-                flextable::width(j = 3, width=3, unit = "in")
-
-codings_wide_agreed_labeled_sample_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_labeled_sample_ft.Rds'))
-codings_wide_agreed_labeled_sample_ft
-
-```
-
 # Validation Tests
@@
 
-saveRDS(codings_long, paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
-saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds"))
-
-saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
-saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))
+saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds")) 
+saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreed.Rds")) 
+saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/ICBe_V1_wide_agreed.Rds"))
 

### 2022-02-04 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
Consolidated save files, names, and locations

@@
 
-codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/codings_wide_agreed.Rds'))
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/codings_long_agreed.Rds'))
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
+codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))
 
@@
 #Load the ICB wide codings
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))
 
@@
 ```{r include=FALSE}
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_wide_clean.Rds"))
+
 n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
@@
 ```{r, eval=T}
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
-
-codings_long_agreement <- readRDS(file=paste0(here::here(),  '/replication_data/temp/codings_long_agreement.Rds'))
 
@@
 The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.).
-There were `r icb_long_clean %>% pull(email_id) %>% unique() %>% length()` coders (including `r icb_long_clean %>% filter(email_id %>% str_detect("expert")) %>% pull(email_id) %>% unique() %>% length()` expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus.
+There were 113 coders (including 5 expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus.
 Of those, there were `r codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma()` unique sentence-tags applied by at least one coder.

### 2022-02-04 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
Consolidated save files, names, and locations

@@
 
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
+codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))
+
 icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))
-
 crisno_name_years <- icb_crises %>% dplyr::select(crisno, crisname, yrtrig, yrterm)
@@
 dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
-
-codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds")) 
-codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
-codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds"))
 

### 2022-02-04 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
Consolidated save files, names, and locations

@@
 
+#Load it here before the python reticulate business
+#devtools::install_github("ropenscilabs/umapr")
+library(umapr)
+
 ```
@@
 
-codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds")) 
-codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) 
-codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
+codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))
 
@@
 
-#devtools::install_github("ropenscilabs/umapr")
-library(umapr)
 embedding <- umapr::umap(sentences_embeddings)
@@
 
-codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
 codings_long_agreed_embeded <- codings_long_agreed %>% ungroup() %>% left_join(sentences_embeded)
@@
 
-codings_wide_agreed <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))
 codings_wide_agreed_embeded <- codings_wide_agreed %>% dplyr::ungroup() %>% dplyr::left_join(sentences_embeded)
@@
 library(RColorBrewer)
-brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange()
+brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange() %>% filter(category %in% "qual" & rowname %in% c('Dark2','Set2','Paired','Accent','Set1'))
 brewer_list <- list() 
-for(i in c(11, 1:nrow(brewer_pal_info_df))){
+for(i in 1:nrow(brewer_pal_info_df)){
   brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
@@
 posible_colors <- unlist(brewer_list) %>% unique(brewer_list)  #%>% sample()
-posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0")] # drop white
+posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0", "#FFD92F","#FFFF33")] # drop white
 
-value_normalized=codings_long_agreed_embeded_subset$value_normalized %>% unique() %>% as.factor()
+value_normalized= codings_long_agreed_embeded_subset %>% count(value_normalized) %>% arrange(desc(n)) %>% filter(n>100) %>% pull(value_normalized) %>% factor()
 value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a brewer pallet with lots of values and then assign it to specific values
-names(value_normalized_colors) = levels(value_normalized)
+names(value_normalized_colors) = as.character(value_normalized)
 
@@
 
-value_means <- value_means %>% dplyr::mutate(label=ifelse(
+value_means <- value_means %>% 
+                dplyr::mutate(label=ifelse(
                 variable_normalized=="leaf_do_original" & !(value_normalized %in% do_leaf_keep$value_normalized), 0, 1))
@@
         geom_text(data=sampled, aes(x=UMAP1, y=UMAP2, label=crisno_sent), color='black',size=1.5) + 
-
         facet_wrap( ~ variable_normalized) + 

### 2022-02-04 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
Consolidated save files, names, and locations

--- 2022-01-26 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
@@
 ```{r}
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
-codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
-codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
-codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
+codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))
 

### 2022-02-04 replication_paper/rmd/ICBEdataset_paper_appendixICBCrises.Rmd
Consolidated save files, names, and locations

@@
 icb_actors <- read_csv(file=paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))
+
+# #Load the ICB wide codings
+icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
 
@@
 ```{r include=F}
-# #Load the ICB wide codings
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
 n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()

### 2022-02-04 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
Consolidated save files, names, and locations

@@
 library(ggplot2)
-p_phoenix_metro_plot_196 <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
+p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
 actor_colors <- p_phoenix_metro_plot_196$actor_colors

### 2022-02-04 README.Rmd
readme

@@
 
-The initial codings pre-cleaning and reconciling intercoder agreement are also available. 
-  - [icb_coder_crisis_sentence_event_aligned.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/icb_coder_crisis_sentence_event_aligned.Rds)
-
 The coding and cleaning process are described in the paper with additional information and details about the variables in the codebook.
@@
  - 01_compile_saves_and_align
-    + compiles the original coding files into `./replication_data/temp/icb_coder_crisis_sentence_event.Rds`
-    + the original coding files are not on the public repository; this can only be run by authors
+    + compiles the original coding files into `./replication_data/in/icb_coder_crisis_sentence_event.Rds`.
+The original coding files are not on the public repository.
+Public users will load `icb_coder_crisis_sentence_event.Rds` directly.
     + aligns codings from multiple GUI versions on similar source sentences
-    + creates `./data/icb_code_crisis_sentence_event_aligned.Rds`
+    + creates `./replication_data/temp/ICBe_V1_long_unclean.Rds.Rds` (not included in online repo)
  - 02_format_and_clean
-    + applies cleaning dictionaries to create `./data/icb_wide_clean.Rds` and `./data/icb_long_clean.Rds`.
+    + applies cleaning dictionaries to create `./replication_data/temp/ICBe_V1_long_clean.Rds` and `./replication_data/temp/ICBe_V1_long_clean.Rds` (not included in online repo)
  - 03_aggregation
-    + applies aggregation algorithm to create `./data_out/codings_long.Rds`, `./data_out/codings_long_agreement.Rds`, `./data_out/codings_long_agreed.Rds`, `./data_out/codings_wide_agreed.Rds`.
+    + applies aggregation algorithm to create `./replication_data/out/ICBe_V1_long_agreement.Rds`, `./replication_data/out/ICBe_V1_long_agreed.Rds`, `./replication_data/out/ICBe_V1_wide_agreed.Rds`.
 
@@
   - CaseStudy196
+      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
   - CaseStudy426
@@
   - ICBEdataset_paper_figure_prep
+  - ICBEdataset_paper_litreviewtable
   - ICBEdataset_paper_PlotInterCoderAgreement

### 2022-02-07 README.Rmd
paper run1

@@
   - CaseStudy426
+      + creates DRC Civil War comparison table `/tables/CaseStudy426_ft.Rds`. 
   - ICBEdataset_figure_metro_maps
+      + creates the metroplot figures in `/figures/metro_plots/.`.
   - ICBEdataset_figure_semantic_embeddings
@@
     + to replicate, download the folder 'largegeolocatedata' to ICBEdata/replication_paper/data/ignore and decompress
-  - [ICEWS data sample](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/28075&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData)
+  - [ICEWS data](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/28075&version=30.0)
     + too large to include in the github repository
-    + to replicate, download the .tsv and .tab files to ICBEdata/replication_paper/data/ignore/icews_dataverse/ and decompress
+    + to replicate, download folder 'dataverse_files' to ICBEdata/replication_paper/data/ignore/ and decompress
 

### 2022-02-07 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
paper run1

@@
   actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
-  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #pick a bewer pallet with lots of values and then assign it to specific values
   names(actor_colors) = levels(actors)
@@
 
-Go ahead an out the sentence tables too here why not
+out the sentence tables
 
@@
 
-ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged/ged211.csv"))
+load(paste0(here::here(), "/replication_paper/data/in/GEDEvent_v21_1.RData"))
+ged211 <- GEDEvent_v21_1
+
+#ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged211.csv"))
 
@@
 
+if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"))){
+  stop("Missing 'UCDP Georeferenced Event Dataset (GED)'. See README.")
+}
+
 files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T)
@@
 
-#Rex start here tomorrow, figure out how to do this join correctly
 actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
@@
 
+if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
+  stop("Missing Terrier event data. See README.")
+}
+
 files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
@@
 
+```
+
+```{r}
 #Maybe it's just ISO3 country codes?
-terrier_clean <- terrier %>% 
+terrier_clean_temp <- terrier %>% 
     dplyr::select(
@@
     mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
-    distinct() %>%
+    distinct()
+
+#done
+
+```
+
+```{r}
+terrier_clean_temp <- terrier_clean_temp %>%
 
@@
    left_join(df %>% dplyr::select(src_other_agent=agent   , src_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
-   left_join(df %>% dplyr::select(target_other_agent=agent, target_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
-
+   left_join(df %>% dplyr::select(target_other_agent=agent, target_other_agent_label=agent_label) %>% distinct() %>% na.omit() )
+
+```
+
+```{r}
+terrier_clean <- terrier_clean_temp %>%
      left_join(df %>% dplyr::select(src_agent=agent, src_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
@@
 
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
+```{r}
 
@@
 
+```
+
+```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
+
 icb_crises %>% filter(yrtrig>=1977 & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))

### 2022-02-07 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
paper run1

--- 2022-02-02 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
@@
 
+To set python, better to set it in ~/.Renviron.
+`use_python()` doesn't seem to work as desired.
+See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
+
 ```{r, messages=F, results='hide'}
 library(reticulate)
-py_discover_config()
+reticulate::py_discover_config()
 
 #use_python("/home/skynet3/anaconda3/bin/python/")
-use_python("/home/tlscherer/anaconda3/bin/python")
+#use_python("/home/tlscherer/anaconda3/bin/python3")
 
@@
 #devtools::install_github("ropenscilabs/umapr")
+library(umap)
 library(umapr)

### 2022-02-08 README.Rmd
readme and plot colors

@@
 
-[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)
+[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)
 
@@
 
-The agreed datasets are the final, dataset used in much of the paper and figures.
+The agreed datasets are the final dataset used in much of the paper and figures.
 It includes our best efforts at cleaning the data and reconciling intercoder agreement.
@@
 
-  - [codings_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_long_agreed.Rds)
-  - [codings_wide_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_wide_agreed.Rds)
+  - [ICBe_V1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
+      + All coded values and information about how often they were selected by coders.  
+  - [ICBe_V1_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_long_agreed.Rds)
+      + `ICBe_V1_long_agreement.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
+  - [ICBe_V1_wide_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
+      + `ICBe_V1_long_agreed.Rds` in wide form where each row is an event.
 
@@
   - ICBEdataset_figure_metro_maps
-      + creates the metroplot figures in `/figures/metro_plots/.`.
+      + creates the metroplot Rds files in `/figures/metro_plots/.`.
   - ICBEdataset_figure_semantic_embeddings
+      + creates the figure `/figures/p_semantic_embeddings.png` and the `/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds` and `/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds`
   - ICBEdataset_paper_appendixICBCrises
+      +  creates `/tables/ft_crisis_text_counts.Rds`.
   - ICBEdataset_paper_appendixVerbMeanings
+      + creates `/tables/verbs_sentence_wordnet_top_ft.Rds`
   - ICBEdataset_paper_figure_prep
+      + creates the metroplot pngs in `/figures/.`.
   - ICBEdataset_paper_litreviewtable
+      + creates the table `/tables/litreview_ft.Rds`. 
   - ICBEdataset_paper_PlotInterCoderAgreement
-
-## ICBe data products
-
- - Agreed Data, long form (LINK NEEDED)
- - Agreed Data, wide form (LINK NEEDED)
- - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
-    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.
-
-### Additional data versions
- - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
-    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
-    + values may contain multiple entries separating with a semicolon
- - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
-    + each row contains identifying information for a coder-crisis-event-sentence
-    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
-    + each value contains a single entry
+      + creates the figure `figures/p_percent_chose_tag_by_concept.png`
 
@@
 ### ICBe preparation
-  - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
-    + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).
-  - [Lit review and tree/leaf codebook](https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit#gid=1604363724)
+  - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates `/replication_paper/data/in/icb_manual_recording_master_sheet.xlsx`
+  - Lit review and tree/leaf codebook: `/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx`
+  - Case study tables: `/replication_paper/data/in/CaseStudies.xlsx`
 

### 2022-02-08 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
readme and plot colors

@@
 A historical episode is demarcated by a period of time $[T_{start}, T_{end}] \in T$ and a set of players $p \in P$.
-We posit that an episode can be divided into unique discrete events, $e \in E$, each consisting of a time period, one or more players, and a single behavior $e \equiv \{T_e, P_e, B_e\}$.
+We posit that an episode can be divided into unique discrete events, $e \in E$, each consisting of a time period, one or more players, and a single behavior ($b \in B$) so that $e \equiv \{T_e, P_e, B_e\}$.
 The task is to produce sequences of parsimonious events that still reconstruct the important details of the original macro narrative.

### 2022-02-08 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
readme and plot colors

@@
 p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
-actor_colors <- p_phoenix_metro_plot_196$actor_colors
+actor_colors <- p_metro_plot$actor_colors
 

### 2022-02-14 README.Rmd
lit and tables

@@
   - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates `/replication_paper/data/in/icb_manual_recording_master_sheet.xlsx`
-  - Lit review and tree/leaf codebook: `/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx`
+  - Lit review and tree/leaf codebook: `replication_data/in/icbe_litreview_trees_sentences.xlsx` and `/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx`
   - Case study tables: `/replication_paper/data/in/CaseStudies.xlsx`

### 2022-02-14 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
lit and tables

@@
 Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$ and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$.
-We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table \ref{tbl:litreview}.
-The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
+We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table 1.
+<!-- {tbl:litreview}  -->The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
 We employ a metaphor of international affairs as a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
@@
 
-```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
+```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 
@@
 litreview_ft %>%
-  flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
+  flextable::set_caption(caption = "Prior Beliefs, State of the Art, and Existing Data") %>%
+  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
   flextable_to_rmd()
@@
 Going further, we examine accepted tokens side-by-side with the original source material.
-We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tbl:15samplesentences}, 50 more in the online Appendix \ref{app:50samplesentences}, and the full set online.
+We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table 2,<!-- \ref{tbl:15samplesentences} --> 50 more in the Appendix \ref{app:50samplesentences}, and the full set online.
 To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined).
@@
 codings_wide_agreed_embeded_stratified_sample_ft_smaller <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds')) %>%
-  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15) \\label{tbl:15samplesentences}") 
+  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15)") 
 codings_wide_agreed_embeded_stratified_sample_ft_smaller
@@
 
-Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tbl:casestudy196}.
-ICBe records 8 of 10 critical events identified by the case history.
+Recall of critical events for ICBe and other state-of-the-art systems are shown in Table 3.<!-- \ref{tbl:casestudy196} --> ICBe records 8 of 10 critical events identified by the case history.
 It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors.
@@
 CaseStudy196_ft %>%
-  flextable::set_caption("Cuban Missile Crisis ground truth and event data \\label{tbl:casestudy196}") %>%
+  flextable::set_caption("Cuban Missile Crisis ground truth and event data") %>%
     flextable::width( j = 1, width=0.5)  %>%
@@
 
-Recall of critical events is shown in Table \ref{tbl:casestudy426} below.
-ICBe records 10 of 14 critical events identified by the case history.
+Recall of critical events is shown in Table 4 below.<!-- \ref{tbl:casestudy426} --> ICBe records 10 of 14 critical events identified by the case history.
 It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N.
@@
 CaseStudy426_ft  %>%
-  flextable::set_caption("DRC Civil War ground truth and event data \\label{tbl:casestudy426}") %>%
+  flextable::set_caption("DRC Civil War ground truth and event data") %>%
       width(j=1, width=0.5) %>%
@@
 
-# Online Appendix
+# Appendix
 
@@
 codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
-  flextable::set_caption("ICBe Codings for 50 Sample Sentences \\label{tbl:50samplesentences}")
+  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:50samplesentences}
 
@@
 ft_sentence_table_196 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_196.Rds'))  %>%
-  flextable::set_caption("ICBe Codings for Cuban Missile Crisis (Crisis 196) \\label{tbl:ft_sentence_table_196}") 
+  flextable::set_caption("ICBe Codings for Cuban Missile Crisis (Crisis 196)") # \\label{tbl:ft_sentence_table_196}
 ft_sentence_table_196 %>%
@@
 ft_sentence_table_426 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_426.Rds'))  %>%
-  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426) \\label{tbl:ft_sentence_table_426}") 
+  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426)") #\\label{tbl:ft_sentence_table_426}
 ft_sentence_table_426 %>%

### 2022-02-14 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
fix

@@
 
-TLS = FALSE
 ```
@@
 
-if(!TLS){
 litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 4, part="body")
-}
 
@@
 Going further, we examine accepted tokens side-by-side with the original source material.
-We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table 2,<!-- \ref{tbl:15samplesentences} --> 50 more in the Appendix \ref{app:50samplesentences}, and the full set online.
+We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tab:fifteensamplesentences}, 50 more in the Appendix \ref{app:50samplesentences}, and the full set online.
 To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined).
@@
 
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
+```{r fifteensamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}
 
@@
 
-Recall of critical events for ICBe and other state-of-the-art systems are shown in Table 3.<!-- \ref{tbl:casestudy196} --> ICBe records 8 of 10 critical events identified by the case history.
+Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tab:casestudy196}.
+ICBe records 8 of 10 critical events identified by the case history.
 It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors.
@@
 
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
+```{r casestudy196, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
 CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
@@
 
-Recall of critical events is shown in Table 4 below.<!-- \ref{tbl:casestudy426} --> ICBe records 10 of 14 critical events identified by the case history.
+Recall of critical events is shown in Table \ref{tab:casestudy426} below.
+ICBe records 10 of 14 critical events identified by the case history.
 It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N.
@@
 
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
+```{r casestudy426, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
 CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
@@
 
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
+```{r fiftysamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
 codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
-  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:50samplesentences}
+  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:fiftysamplesentences}
 

### 2022-02-16 README.Rmd
ArXiv readme

@@
 
-[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)
+[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf).
+
+The [ArXiv pre-print](https://arxiv.org/abs/2202.07081) was posted on February 15, 2022.
 
@@
 2022.
-"Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises." Unpublished Manuscript.
-Retrieved from https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset.
+"Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises." arXiv:2202.07081 [cs, stat].
+http://arxiv.org/abs/2202.07081.
 

### 2022-02-17 replication_data/rmd/03_aggregation.Rmd
tsvs

@@
 saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds")) 
+readr::write_tsv(codings_long_agreement, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.tsv"))
+
 saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreed.Rds")) 
+readr::write_tsv(codings_long_agreed, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreed.tsv"))
+
 saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/ICBe_V1_wide_agreed.Rds")) 
+readr::write_tsv(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/ICBe_V1_wide_agreed.tsv"))
 

### 2022-03-22 replication_data/rmd/02_format_and_clean.rmd
tsvs

@@
 dim(icb_wide_aligned_raw) #87710    85
+
+dim(unique(icb_wide_aligned_raw))
 ```
@@
 
+Drop other instances where coder enters the same information twice
+
+```{r}
+
+# YUGOSLAVIA I: CROATIA-SLOVENIA1 and YUGOSLAVIA I: CROATIA-SLOVENIA2 overlap for one coder, otherwise rows are identical
+
+# z1 <- icb_wide_aligned %>% dplyr::filter(email_id == "expert1" & input_crisis=="YUGOSLAVIA I: CROATIA-SLOVENIA1" & sentence_number_int_aligned %in% c(37:50))
+# z2 <- icb_wide_aligned %>% dplyr::filter(email_id == "expert1" & input_crisis=="YUGOSLAVIA I: CROATIA-SLOVENIA2" & sentence_number_int_aligned %in% c(37:50))
+# z1==z2
+
+icb_wide_aligned <- icb_wide_aligned %>% dplyr::filter(!(email_id == "expert1" & input_crisis=="YUGOSLAVIA I: CROATIA-SLOVENIA2" & sentence_number_int_aligned %in% c(37:50)))
+
+# one coders entry for SAND WALL appear in duplicate
+icb_wide_aligned <- icb_wide_aligned %>% dplyr::mutate(duplicate = duplicated(icb_wide_aligned))
+icb_wide_aligned <- icb_wide_aligned %>% dplyr::filter(!(email_id == "undergrad49addaea" & input_crisis=="SAND WALL" & duplicate==TRUE)) %>% dplyr::select(-duplicate)
+
+```
+
+```{r}
+# check for duplicates (should be empty)
+icb_wide_aligned %>% dplyr::filter(icb_wide_aligned %>% dplyr::select(-input_crisis) %>% duplicated())
+```
+
 Pivot to long form 
@@
 
+```
+```{r}
+# Check that each entry has only one event_type entry (should be all false)
+icb_long %>% dplyr::filter(variable=="event_type") %>% dplyr::select(email_crisis_sent_event) %>% duplicated() %>% table()
 ```
@@
 
+```
+
+```{r}
+
 icb_long_clean2 <- icb_long_clean %>% 
@@
 
+# THIS IS WHERE I AM
+# give every entry its own event_type var to control merging (avoid merging in details for actions that were 'thought about' or 'said')
+# confirm that no email_crisis_sent_event have more than one event_type entry
+icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
+  dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
+  dplyr::rename(event_type=value_normalized) %>% dplyr::count(email_crisis_sent_event) %>% dplyr::filter(n>1)
+
+icb_long_clean2 <- icb_long_clean2 %>% 
+  dplyr::left_join(icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
+                     dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
+                     dplyr::rename(event_type=value_normalized))
+
+```
+
+```{r}
 temp_wide <- icb_long_clean2 %>%
-             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
+             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, event_type, variable_normalized, value_normalized) %>%
              dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
@@
              dplyr::left_join(full_tree %>% 
-                       dplyr::rename(value_normalized=leaf)  %>% 
-                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) 
-                       )
+                       dplyr::rename(value_normalized=leaf, variable_normalized=leaf_var)  %>% 
+                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>% 
+                       dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower())
+                       ) %>% 
+  dplyr::select(-event_type) #no longer needed after merge
 
@@
 saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
+
+# readr::write_tsv(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.tsv"))
 
@@
 
+# readr::write_tsv(icb_wide_clean, paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.tsv"))
+
 ```

### 2022-03-22 replication_data/rmd/03_aggregation.Rmd

@@
 rex_paste <- function(x){ paste0(x  %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
-temp_long <- 
+temp_long_step1 <- 
   icb_long_clean %>% 
@@
       variable_normalized= variable_normalized %>% as.factor()
-    ) %>%
+    )
+
+```
+
+```{r}
+
+temp_long_step2 <- temp_long_step1 %>%
     dplyr::select(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, variable_normalized, value_normalized) %>%
@@
     dplyr::mutate(confidence=ifelse(variable_normalized=='raterconfidence', value_normalized, NA)) %>%
-
     dplyr::mutate(confidence=confidence %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
     dplyr::mutate(confidence_expert= email_id %>% stringr::str_detect('expert') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
-    dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
+    dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) )
+
+```
+
+```{r}
+temp_long <- temp_long_step2 %>%
 

### 2022-03-22 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
tree fix

@@
 #child=c('ICBEdataset_paper_litreviewtable.Rmd')
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
 library(flextable)
 library(ftExtra)
+flextable::set_flextable_defaults(fonts_ignore=TRUE)
 litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))
@@
   # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
-  flextable_to_rmd()
+  flextable::flextable_to_rmd()
 ```

### 2022-03-22 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
tree fix

@@
         mutate(label=
-                 paste0( act_1_label %>% replace_na(''),", ", revtype1_2_label %>% replace_na('') ,", ", fatality_1_label %>% replace_na('')) %>% trimws() %>%
+                 paste0( act_1_label %>% tidyr::replace_na(''),", ", revtype1_2_label %>% tidyr::replace_na('') ,", ", fatality_1_label %>% tidyr::replace_na('')) %>% trimws() %>%
                  str_replace_all("None|Not applicable","") %>% trimws() %>% str_replace("^,|,$|","") %>% trimws()

### 2022-03-22 README.Rmd
tsv to readme
plot reorder

@@
 The dataset is available in long and wide format.
+The data is also available in .tsv format in the same folders.
 
@@
 
-  - CaseStudy196
+  - 04_ICBEdataset_paper_litreviewtable
+      + creates the table `/tables/litreview_ft.Rds`.
+  - 05_ICBEdataset_paper_PlotInterCoderAgreement
+      + creates the figure `figures/p_percent_chose_tag_by_concept.png`
+  - 06_ICBEdataset_figure_metro_maps
+      + creates the metroplot Rds files in `/figures/metro_plots/.`.
+  - 07_ICBEdataset_figure_semantic_embeddings
+      + creates the figure `/figures/p_semantic_embeddings.png` and the `/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds` and `/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds`
+  - 08_CaseStudy196
       + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
-  - CaseStudy426
+  - 09_CaseStudy426
       + creates DRC Civil War comparison table `/tables/CaseStudy426_ft.Rds`. 
-  - ICBEdataset_figure_metro_maps
-      + creates the metroplot Rds files in `/figures/metro_plots/.`.
-  - ICBEdataset_figure_semantic_embeddings
-      + creates the figure `/figures/p_semantic_embeddings.png` and the `/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds` and `/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds`
-  - ICBEdataset_paper_appendixICBCrises
+  - 10_ICBEdataset_paper_figure_prep
+      + creates the metroplot pngs in `/figures/.`.
+  - 11_ICBEdataset_paper_appendixICBCrises
       +  creates `/tables/ft_crisis_text_counts.Rds`.
-  - ICBEdataset_paper_appendixVerbMeanings
+  - 12_ICBEdataset_paper_appendixVerbMeanings
       + creates `/tables/verbs_sentence_wordnet_top_ft.Rds`
-  - ICBEdataset_paper_figure_prep
-      + creates the metroplot pngs in `/figures/.`.
-  - ICBEdataset_paper_litreviewtable
-      + creates the table `/tables/litreview_ft.Rds`. 
-  - ICBEdataset_paper_PlotInterCoderAgreement
-      + creates the figure `figures/p_percent_chose_tag_by_concept.png`
 

### 2022-03-22 replication_paper/rmd/10_ICBEdataset_paper_figure_prep.Rmd
plot reorder

--- 2022-02-08 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
@@
 p_metro_plot <- readRDS(file=paste0(here::here(), '/replication_paper/figures/metro_plots/p_phoenix_metro_plot_196.Rds'))
+
 actor_colors <- p_metro_plot$actor_colors

### 2022-03-23 replication_data/rmd/03_aggregation.Rmd

--- 2022-02-17 replication_data/rmd/03_aggregation.Rmd
@@
 ```{r}
+my.max <- function(x) ifelse( !all(is.na(x)), max(x, na.rm=T), NA)
 
@@
 rex_paste <- function(x){ paste0(x  %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
-temp_long <- 
+
+for(crisis in unique(icb_long_clean$crisno)){
+  print(crisis)
+
+  temp_long_partial <- 
     icb_long_clean %>% 
+      dplyr::filter(crisno == crisis) %>%
       #filter(crisno==keep_crisis & sentence_number_int_aligned==keep_sentence )  %>% #for debugging
@@
       distinct() %>%
-    dplyr::group_by(email_id , crisno,sentence_number_int_aligned, event_number_int_condition, 
+      dplyr::group_by(email_id , crisno, sentence_number_int_aligned, event_number_int_condition, 
                variable_normalized,.drop=FALSE) %>% 
@@
       dplyr::mutate(confidence=ifelse(variable_normalized=='raterconfidence', value_normalized, NA)) %>%
-
       dplyr::mutate(confidence=confidence %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
-    dplyr::mutate(confidence_expert= email_id %>% stringr::str_detect('expert') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
-    dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% max(na.rm=T) ) %>%
+      dplyr::mutate(confidence_expert= email_id %>% stringr::str_detect('expert') %>% ifelse(confidence,NA) %>% my.max() ) %>%
+      dplyr::mutate(confidence_undergrad= email_id %>% stringr::str_detect('undergrad') %>% ifelse(confidence,NA) %>% my.max() )  %>%
 
@@
 
+ if(exists("temp_long")){
+   temp_long <- dplyr::bind_rows(temp_long, temp_long_partial)
+   }else{
+     temp_long <- temp_long_partial
+   }
+}
 ```

### 2022-03-23 replication_paper/rmd/04_ICBEdataset_paper_litreviewtable.Rmd

---
title: 'LitReviewTable.Rmd'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
library(pacman)

p_load(flextable)
p_load(ftExtra)

```

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
lit_review_pull    <- readxl::read_excel(target_file, sheet="DatasetsComparisonLitReview")

```

```{r, echo=FALSE, results='asis', include=T, cache=F, ft.arraystretch=0.75}

#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
# NOTE: If one of the citations is degenerate this will throw an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
set_flextable_defaults(fonts_ignore=TRUE)

lit_review_alt <- lit_review_pull %>%
                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`) #%>% 
                  #dplyr::filter(is.na(group))

n=nrow(lit_review_alt)
ft <- NULL
ft <- lit_review_alt %>%
      flextable::as_flextable() %>%
      add_header( 
                  #"ICB Corpus"="Corpus",
                  "ICBe (us)"="Events Datasets",
                  "Cameo"="Events Datasets",
                  "MIDs Incidents"="Events Datasets",
                  "UCDP-GED"="Events Datasets",
                  "ICB"="Episodes Datasets",
                  "COW"="Episodes Datasets",
                  "MIDs"="Episodes Datasets",
                  top = TRUE ) %>%

      set_header_labels(
        values = list("...1" = "" , "...2" = "" ) 
        ) %>%
      merge_h(part = "header") %>%

      #bg( i=1:(n) , j = condition, part = "body", bg = "#EFEFEF") %>%
      #bg( i=2 , j = condition, part = "header", bg = "#EFEFEF") %>%
      bg( i = which( 1:nrow(lit_review_alt) %% 2 == 1)  , j=3:ncol(lit_review_alt), part = "body", bg = "#EFEFEF") %>%
      #width(j = 1, width=1.25) %>%
      #width(j = 2:ncol(lit_review_alt), width=0.25) %>%
      flextable::fontsize(size = 7, part = "all") %>%
      flextable::rotate(i=2, rotation="tbrl",part="header") %>%
      #flextable::set_header_labels( values = list(x1 = "", x2 = "")) %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

      flextable::colformat_char(
          j = 1:ncol(lit_review_alt),
          na_str = "",
          prefix = "",
          suffix = ""
      ) %>%

      hline(i=c(1), j=3:ncol(lit_review_alt),  border = NULL, part = "header") %>%
      hline(i=c(2,3,7,10,15, 19, 27), border = NULL, part = "body") %>% #,10,14, 20,27,37, n

      #set_table_properties(layout="autofit")  %>%
      vline( i = 1:2, j = c(1,2,3,7)+2, border = NULL, part = "header") %>%
      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
      vline( i = 1:(n), j = c(1,2,3,7)+2, border = NULL, part = "body")

      #autofit()
      #fit_to_width(max_width=12) #This is crazy slow
      #flextable::autofit() 
      #set_table_properties(width = 1, layout = "autofit")

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

litreview_ft <- ft %>% 
  flextable::width( j = 3, width=2) %>% 
  flextable::width( j = 4, width=1.5) %>% 
  flextable::width( j = (3+2):ncol(lit_review_alt), width=0.33) %>%
  flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
  flextable::padding(padding = 0, part = "body") %>%
  #merge_v( j = 1,  part = "body", combine = T) %>%
  #merge_v( j = 2,  part = "body", combine = T) %>%
  #merge_h( i = 1:2,  part = "body") %>%

  merge_at(i = 4:7, j = 1:2, part = "body") %>%
  merge_at(i = 8:10, j = 1:2, part = "body") %>%
  merge_at(i = 11:15, j = 1:2, part = "body") %>%
  merge_at(i = 16:19, j = 1:2, part = "body") %>%

  merge_at(i = 20:n, j = 1, part = "body") %>%
  merge_at(i = 20:28, j = 2, part = "body") %>%
  merge_at(i = 29:n, j = 2, part = "body") %>%

  #merge_v( j = 1,  part = "body", combine = T) %>%

  #merge_at(i = NULL, j = NULL, part = "body") %>%
  #merge_at(i = NULL, j = NULL, part = "body") %>%

  flextable::rotate(j=1, rotation="tbrl",part="all") %>%
  flextable::rotate(j=2, rotation="tbrl",part="all") %>%
  flextable::width( j = 1:2, width=0.1)  %>%
  flextable::width( j = 3, width=2.5)  %>%
  flextable::width( j = 4, width=1.5)  %>%
  flextable::width( j = 5:12, width=0.25)  %>%
  ftExtra::colformat_md(j = 4, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above

litreview_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))

litreview_ft

```

```{r}

n=nrow(lit_review_alt)
ft <- NULL
temp <- lit_review_alt[,-c(4,5)]
ft <- temp %>% 
      flextable::as_flextable() %>%

      bg( i = which( 1:nrow(temp) %% 2 == 1)  , j=3:ncol(temp), part = "body", bg = "#EFEFEF") %>%
      flextable::fontsize(size = 7, part = "all") %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

      flextable::colformat_char(
          j = 1:ncol(temp),
          na_str = "",
          prefix = "",
          suffix = ""
      ) %>%
        set_header_labels(
        values = list("...1" = "" , "...2" = "" ) 
        ) %>%
      merge_h(part = "header") %>%

      hline(i=c(1), j=3:ncol(temp),  border = NULL, part = "header") %>%
      hline(i=c(2,3,7,10,15, 19, 27), border = NULL, part = "body") %>% 
      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
      vline( i = 1:(n), j = c(0,4)+3, border = NULL, part = "body") %>%
      flextable::width( j = 3, width=3) %>%
      flextable::line_spacing( space = 0.75, part = "body") %>% 
      flextable::padding(padding = 0, part = "body") %>%

      merge_at(i = 4:7, j = 1:2, part = "body") %>%
      merge_at(i = 8:10, j = 1:2, part = "body") %>%
      merge_at(i = 11:15, j = 1:2, part = "body") %>%
      merge_at(i = 16:19, j = 1:2, part = "body") %>%

      merge_at(i = 20:n, j = 1, part = "body") %>%
      merge_at(i = 20:28, j = 2, part = "body") %>%
      merge_at(i = 29:n, j = 2, part = "body") %>%
      flextable::rotate(j=1, rotation="tbrl",part="all") %>%
      flextable::rotate(j=2, rotation="tbrl",part="all") %>%
      flextable::width( j = 1:2, width=0.1)  %>%
      flextable::width( j = 3, width=4)  %>%
      flextable::width( j = 4:ncol(temp), width=0.25)

```

### 2022-03-23 replication_paper/rmd/07_ICBEdataset_figure_semantic_embeddings.Rmd

--- 2022-02-04 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
@@
 
-library(RColorBrewer)
-brewer_pal_info_df <- brewer.pal.info %>% dplyr::add_rownames( var = "rowname") %>% dplyr::arrange() %>% filter(category %in% "qual" & rowname %in% c('Dark2','Set2','Paired','Accent','Set1'))
-brewer_list <- list() 
-for(i in 1:nrow(brewer_pal_info_df)){
-  brewer_list[[as.character(i)]] <- brewer.pal(n=brewer_pal_info_df$maxcolors[i], brewer_pal_info_df$rowname[i])
-}
-posible_colors <- unlist(brewer_list) %>% unique(brewer_list)  #%>% sample()
-posible_colors <- posible_colors[! posible_colors %in% c("#FFFFFF", "#FFFF99", "#E6F598", "#E0E0E0", "#FFD92F","#FFFF33")] # drop white
+value_means <- value_means %>% 
+  #dplyr::mutate(UMAP1 = UMAP1+1, UMAP2 = UMAP2+1) %>% 
+  dplyr::mutate(UMAP1=replace(UMAP1, value_normalized=='invasion/occupation', as.numeric(value_means[value_normalized=='invasion/occupation','UMAP1'])+.5)) %>%
+  dplyr::mutate(UMAP1=replace(UMAP1, value_normalized=='meeting', as.numeric(value_means[value_normalized=='meeting','UMAP1'])-.3)) %>%
+  dplyr::mutate(UMAP2=replace(UMAP2, value_normalized=='invasion/occupation', as.numeric(value_means[value_normalized=='invasion/occupation','UMAP2'])-.7)) %>%
+  dplyr::mutate(UMAP2=replace(UMAP2, value_normalized=='meeting', as.numeric(value_means[value_normalized=='meeting','UMAP2'])-.3))
 
-value_normalized= codings_long_agreed_embeded_subset %>% count(value_normalized) %>% arrange(desc(n)) %>% filter(n>100) %>% pull(value_normalized) %>% factor()
-value_normalized_colors = posible_colors[1:length(value_normalized)] #ok so pick a brewer pallet with lots of values and then assign it to specific values
+```
+
+```{r}
+do_leaf_all <- codings_long_agreed_embeded_subset %>% dplyr::filter(variable_normalized=="leaf_do_original") %>% dplyr::count(value_normalized) %>% arrange(desc(n)) 
+do_leaf_grey <- do_leaf_all %>% dplyr::slice_tail(n=(nrow(do_leaf_all)-10))
+
+value_normalized = codings_long_agreed_embeded_subset %>% count(variable_normalized, value_normalized) %>% arrange(variable_normalized, desc(n)) %>% pull(value_normalized) %>% factor()
+
+# safe_colorblind_palette <- c(#"#88CCEE", drop light blue
+#   "#CC6677", 
+#   #"#DDCC77", drop yellow
+#   "#117733", "#332288", "#AA4499", "#44AA99", "#999933", "#882255", "#661100", "#6699CC"#, "#888888" drop grey
+#   )
+
+# https://jacksonlab.agronomy.wisc.edu/2016/05/23/15-level-colorblind-friendly-palette/
+  pal <- c(#"#000000",
+  "#6db6ff","#004949","#ff6db6", 
+  #"#ffb6db", "#24ff24",
+ "#db6d00","#b66dff","#009292",
+ #"#b6dbff",
+ "#920000","#924900","#006ddb","#490092"
+ #,"#ffff6d"
+ )
+
+value_normalized_colors = rep(pal, ceiling(length(value_normalized)/length(pal)))
 names(value_normalized_colors) = as.character(value_normalized)
 
-# do leaf originals to keep labels for
-do_leaf_keep <- codings_long_agreed_embeded_subset %>% dplyr::filter(variable_normalized=="leaf_do_original") %>% dplyr::count(value_normalized) %>% arrange(desc(n)) %>% dplyr::slice_head(n=10)
+value_normalized_colors[names(value_normalized_colors) %in% do_leaf_grey$value_normalized] <- "#c8c8c8"
 
+```
+
+```{r}
 value_means <- value_means %>% 
                 dplyr::mutate(label=ifelse(
-                variable_normalized=="leaf_do_original" & !(value_normalized %in% do_leaf_keep$value_normalized), 0, 1))
+                variable_normalized=="leaf_do_original" & value_normalized %in% do_leaf_grey$value_normalized, 0, 1))
 

### 2022-03-24 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
paper edits

@@
 If so, then these events can be systematically measured.
-Massive effort is expended in social science recording these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
+Massive effort is expended in social science recording these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
+On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
 
@@
 We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999;@brecherCrisisEscalationWar2000;@wilkenfeldInterstateCrisesViolence2000;@jamesWhatWeKnow2019;@iakhnisCrisesWorldPolitics2019].
+We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherCrisisEscalationWar2000; @wilkenfeldInterstateCrisesViolence2000; @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019].
 The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
@@
 Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-The resulting codebook for events includes 117 different verbs and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
+The resulting codebook for events includes 117 different behaviors and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
 
@@
 The second column ('ICB Corpus') documents the presence of that information in the ICB Corpus as identified by an expert review and natural language processing (Appendix \ref{app:verbs}).
-The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].
-Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Absent datasets include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], and SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000] (see histories [@merrittMeasuringEventsInternational1994] and [@schrodtTwentyYearsKansas2006]).] Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
 
@@
 
-Each crisis was assigned to at least two expert coders, 3 to 5 novice coders, with a third tie-breaking expert coder assigned to sentences with high disagreement.
-Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook, while novice coders were undergraduate students who engaged in classroom workshops.
-Each coder was instructed to thoroughly read and familiarize themselves with the full text.
+Each crisis was assigned to at least two expert coders, 3 to 5 undergrad coders, with a third tie-breaking expert coder assigned to sentences with high disagreement.^[Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
+Undergrad coders were students who engaged in classroom workshops.
+Coders worked independently with the codebook after a practice coding where an expert answered questions.] Each coder was instructed to thoroughly read and familiarize themselves with the full text.
 Once a coder felt that they understood the crisis, the coder was presented with a novel graphic user interface (GUI) that steps the coder through the narrative sentence by sentence (Figure \ref{fig:coding_gui}).
@@
 
+Without an existing validation dataset, we cannot use traditional measures of validity.
+We instead examine agreement between coders, juxtaposition with source sentences, and case study comparisons with peer datasets.
 One form of internal validity for these codings is high agreement between coders when applying the ontology.
-We employ three ways to evaluate and maximize agreement: (1) multiple expert and novice coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence.
+We employ three ways to evaluate and maximize agreement: (1) multiple expert and undergrad coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence.
 The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.).
@@
 This data-generating process suggests a theoretically motivated algorithm for aggregating over disagreements (Algorithm 1).
-We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of novice votes.
+We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of undergrad votes.
 If neither majority exists, we accept the one token with the most votes.
 This leaves `r codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()` (`r (codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() / codings_long_agreement %>% filter(value_normalized!='') %>% nrow()) %>% round(2) %>% scales::percent()`) accepted tokens.
-In practice, this screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
+In practice, this screens noisy tags that no expert considered possible but leverages undergrad knowledge to tie-break between equally plausible tags chosen by experts.
 A final step handles possible disagreement over the number of events or participants in the events.
@@
       \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
-      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
+      \uElseIf{undergrad votes > undergrad voters/2}{accept; \tcc*[f]{Or a majority of undergrad votes}}
     }
@@
 
-To demonstrate validity at the level of entire episodes, we conduct two qualitative case studies; we choose the Cuban Missile Crisis for being very high stakes and widely recognized and the DRC Civil War for being particularly complicated, lengthy, and modern.
-In addition, we provide visualizations for every crisis with side-by-side comparisons across datasets on the companion website.
-Our goals are as follows: (1) establish necessary and secondary details of each crisis from secondary historical sources independent of the ICB corpus; (2) evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'; and (3) assess the recall of key events by the ICBe codings in comparison to the existing state-of-the-art datasets.
+To demonstrate validity at the level of entire episodes, we conduct two qualitative case studies.
+We choose cases where Phoenix had substantially more relevant events (included crisis actors in crisis time span) then ICBe, likely exacerbating the well-known poor coherence of automated codings but increasing the likelihood of capturing key events.
+The two cases also differ in useful ways; the Cuban Missile Crisis is high stakes and widely recognized and the DRC Civil War for being particularly complicated, lengthy, and modern.
+
+For each case we first establish necessary and secondary details of each crisis from secondary historical sources independent of the ICB corpus.
+We then evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'.^[The project website has such visualizations for every crisis.].
+Finally we compare the recall of key events by ICBe and the existing state-of-the-art datasets.
 For an event dataset to have good performance, it must both have high recall of salient facts, catching the key details and not just the trivia, and good precision, recording only events that actually occurred without distracting duplicates, miscodings, or other apparent examples of measurement error.
@@
 By comparison, crisis maps of Cameo (Phoenix) (Figure \ref{fig:426metromap_phoenix}), ICEWS (Figure \ref{fig:426metromap_icews}), and Terrier (Figure \ref{fig:426metromap_terrier}), are unintelligible despite deduplication and heavy filtering of irrelevant or uninteresting events.
-The automated dictionary coding of news articles produces too many irrelevant events between unimportant actors or describes important events too vaguely to be used directly, and instead may only be interpretable in terms of weighted counts over time [@terechshenkoHotCollarLatent2020].
+The real-time of advantage of automated dictionary coding of news articles comes at the price of producing too many irrelevant events between unimportant actors or describes important events too vaguely to be used directly, and instead may only be interpretable in terms of weighted counts over time [@terechshenkoHotCollarLatent2020].
 ICB Dyadic Events (Figure \ref{fig:426metromap_icb}), MIDs Incidents (Figure \ref{fig:426metromap_mids_incidents}), and MIDs Episodes (Figure \ref{fig:426metromap_mids}) do a good job showing the start and stop of conflict and between which actors, but lose any detailed context.
@@
 escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence  by experts and novices that allows for the introduction of uncertainty and human interpretation of events.
+Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
@@
 Thanks to the Center for Peace and Security Studies and its membership for comments.
-Thank you to the many research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
+Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
+Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
 This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.

### 2022-03-24 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
edits knitted

@@
 The second column ('ICB Corpus') documents the presence of that information in the ICB Corpus as identified by an expert review and natural language processing (Appendix \ref{app:verbs}).
-The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Absent datasets include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], and SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000] (see histories [@merrittMeasuringEventsInternational1994] and [@schrodtTwentyYearsKansas2006]).] Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Absent datasets include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], and SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
 
@@
 For each case we first establish necessary and secondary details of each crisis from secondary historical sources independent of the ICB corpus.
-We then evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'.^[The project website has such visualizations for every crisis.].
-Finally we compare the recall of key events by ICBe and the existing state-of-the-art datasets.
+We then evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'.^[The project website has such visualizations for every crisis.] Finally we compare the recall of key events by ICBe and the existing state-of-the-art datasets.
 For an event dataset to have good performance, it must both have high recall of salient facts, catching the key details and not just the trivia, and good precision, recording only events that actually occurred without distracting duplicates, miscodings, or other apparent examples of measurement error.

### 2022-03-24 replication_data/rmd/02_format_and_clean.rmd
condition location update

@@
 dictionary_locations <- readxl::read_excel(target_file, sheet="locations", na = c("", "NA")) 
+dictionary_condition_locations <- readxl::read_excel(target_file, sheet="condition_locations", na = c("", "NA")) 
 dictionary_dates <- readxl::read_excel(target_file, sheet="dates", col_types="text") #This is the tricky one and why he had to add values
@@
   dplyr::filter(!is.na(interact_location_other))
+
+condition_location_merge_directory <- icb_wide_aligned %>% 
+    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), 
+                  sentence_number_int_aligned3 = stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>% 
+  dplyr::mutate(email_crisis_sent_event = paste(email_id,crisno3,sentence_number_int_aligned3,event_number_int, sep="_")) %>%
+  dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
+  dplyr::mutate(crisis_sent = paste0(crisno,"_",sentence_number_int_aligned)) %>%
+  dplyr::select(crisno, email_crisis_sent_event, do_actor_a, do_actor_b, condition_interact_location, condition_interact_location_other) %>% 
+  dplyr::mutate(do_actor_a=strsplit(do_actor_a, ";")) %>% tidyr::unnest(do_actor_a) %>%
+  dplyr::mutate(do_actor_b=strsplit(do_actor_b, ";")) %>% tidyr::unnest(do_actor_b) %>%
+  dplyr::mutate(condition_interact_location_other=strsplit(condition_interact_location_other, ";")) %>% tidyr::unnest(condition_interact_location_other) %>%
+  dplyr::mutate(do_actor_a=tolower(do_actor_a), do_actor_b=tolower(do_actor_b),
+                condition_interact_location_other=trimws(tolower(condition_interact_location_other))) %>%
+  dplyr::left_join(dictionary_condition_locations %>%
+                     dplyr::mutate() %>% 
+                     dplyr::mutate(condition_interact_location_other = tolower(condition_interact_location_other)) %>% 
+                     dplyr::select(do_actor_a, do_actor_b, condition_interact_location, condition_interact_location_other, norm_name)) %>%
+  dplyr::mutate(crisno = as.numeric(crisno)) %>% 
+  unique() %>% 
+  dplyr::filter(!is.na(condition_interact_location_other))
 
@@
   dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))
+
+icb_long_condition_location_clean <- icb_long_split %>% 
+  dplyr::filter(variable == "condition_interact_location_other") %>% 
+  dplyr::full_join(condition_location_merge_directory %>%
+                     dplyr::mutate(crisno = as.character(crisno)) %>% 
+                     dplyr::rename(value = condition_interact_location_other)) %>% 
+  dplyr::rename(value_normalized = norm_name) %>%
+  dplyr::mutate(variable_normalized = "condition_interact_location_other_clean") %>%   
+  dplyr::select(-do_actor_a, -do_actor_b, -condition_interact_location) %>% 
+  dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))
+
 ```
@@
       dplyr::select(-variable_normalized.location, -value_normalized.location) %>% 
+  dplyr::left_join(icb_long_condition_location_clean, by=names(icb_long_split), suffix = c("", ".condition_location")) %>% 
+      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.condition_location, variable_normalized))) %>%
+      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.condition_location, value_normalized))) %>%
+      dplyr::select(-variable_normalized.condition_location, -value_normalized.condition_location) %>% 
   dplyr::full_join(icb_long_dates_clean, by=names(icb_long_split), suffix = c("", ".date")) %>% 
@@
 ```{r}
-# Fix several typos:
+# Fix typos:
 
@@
 ```{r}
-
 icb_long_clean2 <- icb_long_clean %>% 
   dplyr::distinct() %>%
+  dplyr::mutate(variable_normalized= variable_normalized %>%
+                  stringr::str_replace("interact_location_other_clean","interact_location_defined")) %>%
+  dplyr::mutate(variable_normalized= variable_normalized %>%
+                  stringr::str_replace("condition_interact_location_other","condition_interact_location_defined")) %>% 
   dplyr::mutate(variable_normalized= variable_normalized %>%
@@
   #Only really matters for location_other
-
   dplyr::filter(value_normalized!='drop') %>%
@@
 
-# THIS IS WHERE I AM
 # give every entry its own event_type var to control merging (avoid merging in details for actions that were 'thought about' or 'said')
@@
                      dplyr::rename(event_type=value_normalized))
+
+# icb_long_clean %>% dplyr::select(variable_normalized) %>% table()
+# 
+# icb_long_clean %>% dplyr::filter(variable_normalized=="interact_location") %>% dplyr::select(value_normalized) %>% table()
+# icb_long_clean %>% dplyr::filter(variable_normalized=="condition_interact_location_other") %>% dplyr::select(value_normalized) %>% table()
+# 
+# icb_long_clean2 %>% dplyr::filter(variable_normalized=="interact_location") %>% dplyr::select(value_normalized) %>% table()
+# icb_long_clean2 %>% dplyr::filter(variable_normalized=="interact_location_defined") %>% dplyr::select(value_normalized) %>% table()
+# 
+# temp <- icb_wide_aligned_raw %>% dplyr::select("do_actor_a", "do_actor_b", "condition_interact_location", "condition_interact_location_other") %>% dplyr::filter(!is.na(condition_interact_location_other))
 

### 2022-03-24 replication_data/rmd/03_aggregation.Rmd
condition location update

@@
    }
+
+  # for debugging
+    # try(if("icb_survey_version" %in% names(temp_long$icb_survey_version)) stop("icb_survey_version appeared..."))
+
 }
@@
 
+```
+
+```{r}
+
 #
@@
                         #filter(crisno==59) %>%
-                        inner_join(codings_long_agreed) %>% #only keep ones that show up in both
+                        dplyr::inner_join(codings_long_agreed) %>% #only keep ones that show up in both
                         filter(email_id %>% str_detect('expert') ) %>%

### 2022-03-24 replication_paper/rmd/05_ICBEdataset_paper_PlotInterCoderAgreement.Rmd
plot reorder
condition location update

--- 2022-02-04 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
@@
 ```{r}
+#codings_long_agreement <- codings_long_agreement %>% dplyr::filter(event_number_int_condition == 0)
 
@@
     filter(total_coders>1) %>% #about 9k only had one coder
+  # filter(event_number_int_condition==0) %>%
     #filter(selected_by_experts>=1) %>%

### 2022-03-24 replication_paper/rmd/05_ICBEdataset_paper_PlotInterCoderAgreement.Rmd
drop date from agreement

@@
     filter(total_coders>1) %>% #about 9k only had one coder
+  filter(variable_normalized!="date")%>%
   # filter(event_number_int_condition==0) %>%

### 2022-07-17 replication_corpus/rmd/download_and_clean.Rmd
v1.1

---
title: "corpus download and clean"
output: html_document
date: '2022-05-16'
---

```{r setup, include=FALSE, eval=F}
knitr::opts_chunk$set(echo = TRUE)

# library(rvest)
# urls = paste0("http://www.icb.umd.edu/dataviewer/?crisno=",1:487)
# loose_list <- list()
# for(i in 1:length(urls)){
#   try({
#     df <- data.frame(text=urls[i] %>% read_html %>% html_text )  %>% 
#       mutate(url=urls[i]) %>%
#       mutate(crisno=i)
#     loose_list[[file]] <- df
#   })
# }
# cuban_missile_loose <- bind_rows(loose_list) %>% 
#   group_by(url) %>%
#   summarise(text=paste(text, collapse="\n"))  %>% screen_rex()
# dim(cuban_missile_loose) #958
# cuban_missile_loose$short <- NA

fromscratch=F
if(fromscratch){
  urls <- readLines("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/sheet1.xml.rels")[[2]] %>%
    str_replace_all("Target=","\n") %>%
    str_replace_all("TargetMode=","\n") %>%  
    str_replace_all("Type=","\n") %>%
    str_split("\n") %>% unique() %>%
    as.data.frame() %>% setNames("V1") %>% 
    filter(!V1 %>% str_detect("hyperlink|External|Relationships")) %>%
    mutate(V1 = V1 %>% str_replace_all('\"','') %>% trimws() )
  urls$V1 %>% sapply(FUN= function(x) try({ drive_download(x) })  )
  #Google drive download
  library("googledrive")
  #https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB 
  setwd("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/crisis_texts/")
  getwd()
  temp <- drive_download(file="https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB" ) # type = "csv",
}
#Nope the original csv files are broken. I'm going to have to reparse them from the website
#icb_long  %>%
#  dplyr::select(sentence_hash) %>% distinct() %>% View()
#There are 4 not in the icb long #397 403 451 459 474
setdiff(1:476, icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort())
icb_crisis_summaries_20150604 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/icb_crisis_summaries_20150604.csv")
icb_crisis_summaries_20150604_handadditions <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/icb_crisis_summaries_20150604_handadditions.csv") #this gets us 1 to 455
icb_crisis_summaries <- bind_rows(icb_crisis_summaries_20150604,icb_crisis_summaries_20150604_handadditions) %>%
  mutate(background = background %>% stringi::stri_enc_toutf8(validate=T)) %>% #there are non utf-8 characters
  mutate(text = text %>% stringi::stri_enc_toutf8(validate=T))

#459 is in ours but not the original
#397 403 451 459 there are 4 crises is in the text that aren't in our codings
setdiff(icb_crisis_summaries$crisno %>% unique(), icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort()) #
#And none that our in our codings that aren't in the text
setdiff(icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort(), icb_crisis_summaries$crisno %>% unique() ) #

```

```{r}

#Note I had to manually recreate the 001 crisis because it was just a dump of a large text file containing first 200ish crises
files <- list.files(path = "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/crisis_texts/", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE)

filed_df <- data.frame(file=files) %>%
            mutate(filetype=NA) %>%
            mutate(filetype=ifelse(file %>% str_detect("pdf$"), "pdf", filetype)) %>%
            mutate(filetype=ifelse(file %>% str_detect("txt$"), "txt", filetype)) %>%
            mutate(filetype=ifelse(file %>% str_detect("docx$"), "docx", filetype)) %>%
            mutate(text=NA)
n=nrow(filed_df)
path <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/crisis_texts/"
library(pdftools)
library(textreadr)
for(i in 1:n){
  if(filed_df$filetype[i]=="txt"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i]) %>% readLines() %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
  if(filed_df$filetype[i]=="docx"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i])  %>% read_docx() %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
  if(filed_df$filetype[i]=="pdf"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i])  %>% pdftools::pdf_text() %>% str_replace_all("1\n|2\n|3\n|4\n",' ') %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
}

#Some had both a background and pre-crisis
filed_df_clean <- filed_df %>%
                  mutate(text = text %>%
                    str_replace_all("\\(see Background and Pre-crisis, Case #7\\)","(see Case #7\\)")  %>%  #replace one parenthetical that breaks things
                    str_replace_all("see Background to","")    %>%
                    str_replace_all("Summary of World Broadcasts","SWB")  %>%
                    str_replace_all(
  "BACKGROUND|PRE-CRISIS|Background and Pre-Crisis:|Background:|Crisis:|Sources:|References:|Summary:|Summary|Background and Pre-crisis|Background |Background |Pre-crisis |Sources |Summary |Precrisis: |Crisis: |Bibliography","\n")  %>% 
                    str_replace_all(" Crisis On the morning of","\nOn the morning of")  %>% 
                    str_replace_all("Crisis A crisis for Pakistan","\nA crisis for Pakistan") 
                  ) %>% 
                  mutate(text = strsplit(as.character(text), "\n")) %>% 
                  unnest(text) %>%
                  mutate(text_nchar=text %>% nchar() )  %>%
                  group_by(file) %>%
                    mutate(i=row_number()) %>%
                    mutate(crisis_title=text[1] %>% trimws() ) %>%
                    mutate(references=text[max(i)] %>% trimws() ) %>%
                    filter(i!=1) %>% #remove the title
                    filter(i!=max(i)) %>%  #remove the references
                  ungroup()  %>%
                  add_count(file) %>%
                  mutate(text=text %>% trimws() %>%
                    str_replace_all("^ {0,}: {0,}","") %>% 
                    trimws()
                    ) %>%
                  filter(text!='') %>%
                  mutate(crisno=file %>% str_replace_all("[^0-9]","") %>% substring(1,3) %>% as.numeric())

filed_df_clean$file %>% table() %>% table()

icb_corpus <- filed_df_clean %>%
  arrange(crisno, i) %>%
  group_by(crisno) %>%
  summarise(
    crisis_title=crisis_title[1], 
    text=text %>% paste(collapse=" "),
    references=references[1],
    file=file[1]
  )

icb_corpus %>% saveRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_corpus_V1.0_May_16_2022.Rds")

#icb_corpus$text %>% writeLines("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/test.txt")

```

### 2022-07-17 replication_data/rmd/01_compile_saves_and_align.Rmd
v1.1

@@
 ---
+
+```{=html}
 <style>
@@
 </style>
-
+```
 This notebook walks through the creation of the crisisno-sentenceno-sentence key
@@
 ```{r}
+library(tidyverse)
 `%>%` <- magrittr::`%>%`
@@
 files_worker_saves <- list.files(path = path, pattern = ".Rdata", all.files = FALSE, full.names = T, recursive = T, ignore.case = FALSE, include.dirs = FALSE)
+length(files_worker_saves) #32748
 
+#First confirm how many emails
+files_worker_saves %>% str_replace(".*\\/",'') %>% str_replace("_.*",'') %>% unique() %>% length() #141 possible
+
+files_worker_saves <- files_worker_saves[!files_worker_saves %>% str_detect("[0-9][0-9]\\.[0-9][0-9]\\.[0-9][0-9].Rdata")] #exclude the date stamped ones
+length(files_worker_saves) #1965
 if(length(files_worker_saves)==0){print("Original save files not found locally, will load premade anonymized file instead")
   }else{print("Original save files found, can regenerate anonymized if desired.")}
+
+files_worker_saves %>% str_replace(".*\\/",'') %>% str_replace("_.*",'') %>% unique() %>% length() #140 possible
+
+df <- data.frame(file=files_worker_saves)
 
@@
 
+    #("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/ignore/icb_worker_saves/nlundumd.edu_163_EGYPT-SUDAN_BORDER_I.Rdata" %>% str_match(pattern="^.*?_([0-9]*)_"))[2]
     # reshape the work rows into a list of dataframes
@@
         dplyr::mutate(email = df$value[df$varname=="email"]) %>%
-        dplyr::mutate(input_crisis = df$value[df$varname=="input_crisis"]) %>%
         dplyr::mutate(savefile = q) %>% 
@@
         dplyr::select(-sentence_number, -event_number ) %>%
-        dplyr::filter(!varname %in% c("email", "input_crisis", "savebutton", "savebutton2", "startbutton", "practice1", "practice2", "practice3", "practice4", "sentencenumber","crisis", "savefile")) %>%
-        dplyr::select(-starts_with("sentencenumber") ) # filter out variables with varnames that contain "sentencenumber"
+        dplyr::filter(!varname %in% 
+                        c("email", "input_crisis", "savebutton", "savebutton2", "startbutton", "practice1", "practice2", "practice3", "practice4", "sentencenumber","crisis", "savefile")) %>%
+        dplyr::select(-starts_with("sentencenumber") ) %>% 
+        filter(value!='') %>%
+        filter(!is.na(sentence_number_int)) %>% #there are a few broken questions
+        group_by(sentence_number_int) %>%
+          dplyr::mutate(input_crisis = value[varname %>% str_detect("crisis") ]) %>%
+          dplyr::mutate(crisno = value[varname %>% str_detect("crisno") ]) %>% #You can't actually trust the original gui crisis number, always trust the file name instead
+        ungroup() %>%
+        #There are two instances where the filename is wrong which is why we go with the GUI reported coding
+        #rowwise() %>%
+        #  dplyr::mutate(crisno_filenamereported = (savefile %>% str_match("_([0-9]{1,3})_") )[2] %>% as.numeric()  ) %>% #You can't actually trust the original gui crisis number, always trust the file name instead
+        #ungroup() %>%
+        arrange(sentence_number_int) %>% #make sure you order but sentence int so you select on the first sentence
+        #Using spans later I've confirmed that when the gui and the file name disagree, the gui was always right
+        #So there's a kind of file that was just completely wrong and there's another kind that had the wrong file named assigned for some reason, e.g. in an earlier gui bug (n=2)
+        #So what we're going to do is ask if the gui report varies within a crisis and if so we're going to drop the second that appears and keep the first
+        filter(crisno==crisno[1])  #require every one to match the very first gui report one in the file
+        #This is what we originally did just using the name of the crisis and not the number
+        #filter(input_crisis==input_crisis[1]) #There's a bug where extra sentences were tagged after a gui switch, they have the wrong input crisis which this screens
+        #We've now moved rejecting sentences from the wrong narrative to the spans section. We'll check to see if that sentence shows up and if not kill it.
+
+      # filter out variables with varnames that contain "sentencenumber"
 
     }
+    length(icb_worker_saves_dfs_list)
 
@@
     expert4 <- c("d9d78123","d7b84c6b","e0741cd9")                                                                  
-    expert5 <- c('052c88eb')    
+    expert5 <- c('052c88eb',"77f0bb72")    
     expert6 <- c('7559b489','6158e8c6')       
+    expert7 <- c('414ee682') #"example" #was a concensus coding we created for training purposes and should be considered expert
 
-    #icb_long %>% dplyr::count(email,input_crisis) %>% count(email)
+   	emails_crisno <- dplyr::bind_rows(icb_worker_saves_dfs_list) %>% filter(varname %>% str_detect("sentence_events")) %>% dplyr::count(email, crisno)
+    crises_per_coder <- emails_crisno %>% dplyr::count(email)
+    sentences_per_coder <- dplyr::bind_rows(icb_worker_saves_dfs_list) %>% filter(varname %>% str_detect("sentence_events")) %>% dplyr::count(email) #this is roughly the number of sentences per coder
+    coder_statistics <- sentences_per_coder %>% rename(n_sentences=n) %>% full_join(crises_per_coder  %>% rename(n_crises=n) ) %>%
+                          rowwise() %>%
+                            dplyr::mutate(email_crc32= digest::digest(email[1],'crc32') )  %>%
+                          ungroup() %>%
+                          dplyr::mutate(email_id=email_crc32) %>% 
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert1, "expert1", email_id)) %>%
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert2, "expert2", email_id)) %>%
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert3, "expert3", email_id)) %>%
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert4, "expert4", email_id)) %>%
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert5, "expert5", email_id)) %>%
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert6, "expert6", email_id)) %>%
+                          dplyr::mutate(email_id= ifelse(email_crc32 %in% expert7, "expert7", email_id)) %>%
+                          mutate(status="keep") %>%
+                          mutate(status=ifelse( email_crc32 %in% c("6e1ad8fc"), "reject",  status )) %>% #test email account
+                          mutate(status=ifelse( email %in% c("unit_test","example"), "reject",  status )) %>% #test email account
+                          mutate(status=ifelse( n_crises==1 | n_sentences<66, "reject",  status )) %>%  #only one crisis or less than 66 sentences
+                          mutate(status=ifelse( email_crc32 %in% c('414ee682',"e0741cd9","6158e8c6","77f0bb72","3ee0cdf1"), "keep",  status )) %>% #there are few email misspellings we want to keep
+                          mutate(expert = email_id %>% str_detect("expert") %>% as.integer())
 
-    emails <- dplyr::bind_rows(icb_worker_saves_dfs_list) %>% dplyr::count(email) #132
-    emails_to_keep <- emails %>% dplyr::filter(n>3000) %>% dplyr::pull(email) #we're going to reject any with less than 3,000 filled out values
-    #That's 115
-
+    #emails_to_keep <- sentences_per_coder %>% dplyr::filter(n>=88) %>% dplyr::pull(email) #we're going to reject any with less than 88 filled out sentences
+    #That's 117
+    #emails_to_reject <- crises_per_coder %>% filter(n==1) %>% pull(email)
     icb_long <- dplyr::bind_rows(icb_worker_saves_dfs_list) %>%
                 dplyr::filter(value!="") %>% 
-                dplyr::filter(email %in% emails_to_keep) %>%
+                left_join(coder_statistics %>% dplyr::select(email,email_crc32, email_id, status, expert)) %>%
+                dplyr::filter(status %in% "keep"  ) %>% 
                 dplyr::filter(!is.na(event_number_int) & !is.na(sentence_number_int)) %>%
@@
 
-                dplyr::mutate(email_id=email_crc32) %>% 
-                dplyr::mutate(email_id= ifelse(email_id %in% expert1, "expert1", email_id)) %>%
-                dplyr::mutate(email_id= ifelse(email_id %in% expert2, "expert2", email_id)) %>%
-                dplyr::mutate(email_id= ifelse(email_id %in% expert3, "expert3", email_id)) %>%
-                dplyr::mutate(email_id= ifelse(email_id %in% expert4, "expert4", email_id)) %>%
-                dplyr::mutate(email_id= ifelse(email_id %in% expert5, "expert5", email_id)) %>%
-                dplyr::mutate(email_id= ifelse(email_id %in% expert6, "expert6", email_id)) %>%
+                dplyr::select(-email,-savefile) %>% #anonymize
 
-                dplyr::select(-email,-savefile) %>% #anonymize
-                dplyr::filter(email_id!="delete") %>%
-                dplyr::mutate(email_id= ifelse(email_id %>% stringr::str_detect("expert"), email_id, paste0("undergrad",email_id))) %>%
+                dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int, varname ) %>%
+                group_by(savefile_crc32, sentence_number_int) %>%
+                  mutate(sentence=(value[varname=="sentence"][1])) %>%
+                ungroup() %>% 
+                mutate(sentence_clean= sentence %>% 
+                         str_replace("Pre-crisis|Precrisis","") %>% #we
+                         str_replace("Background|BACKGROUND","") %>% 
+                         str_replace("^\\(","") %>% 
+                         str_replace("\\)$","") %>% 
+                         str_replace('^ \\\\"',"") %>% 
+                         trimws()  ) #%>% 
+                #mutate(sentence_hash = paste0(crisno, sentence_clean %>% tolower() %>% str_replace_all("[^a-z]", "" ) ) )
 
-                dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int, varname ) #%>%
-                #filter(email_id %in% c('expert1','expert2','expert3','expert4','expert5','expert6')) #Restricting to just the experts
+    #
+    coders_per_crisis <- icb_long %>% dplyr::select(crisno,  email_id, expert) %>% distinct() #%>% dplyr::count(crisno)
+    coders_per_crisis_tally <- coders_per_crisis %>% mutate(novice=expert==0) %>% group_by(crisno) %>% summarise( expert=sum(expert==1), novice=sum(novice==1) )
+    crisis_sentences_per_coder <- icb_long%>% filter(varname %>% str_detect("sentence_events")) %>% dplyr::count(email_id, crisno)
+    #
+    #devtools::install_github("ropensci/textreuse", build_vignettes = TRUE)
+    #install.packages("text.alignment")
+    #library(textreuse)
+    library(tictoc)
+    library(text.alignment)
 
-    dim(icb_long) #993,600     10
+    if(fromscratch){
+      icb_crisis_summaries <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_corpus_V1.0_May_16_2022.Rds")
+      #Do a round first based on the file name
+      icb_long_crisis_sentence_unique <- icb_long %>% dplyr::select(crisno,  sentence_clean) %>% distinct() %>%  #we have to check two different crises, the one that was reported and the file name
+        mutate(crisno= crisno %>% as.numeric()) %>%
+        left_join(icb_crisis_summaries %>% dplyr::select(crisno,text) ) %>%
+        janitor::clean_names()
+      icb_long_crisis_sentence_unique$sentence_clean_hash_match_similarty=NA
+      icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_start=NA
+      icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_end=NA
+      #Ya I'm just going to have to remove parenthetical again, there's no avoiding it
+      tic()
+        for(i in 1:nrow(icb_long_crisis_sentence_unique)){
+          #print(i)
+          if(i %% 100 ==0) {print(i)}
+          if(!is.na(icb_long_crisis_sentence_unique$sentence_clean[i]) & nchar(icb_long_crisis_sentence_unique$sentence_clean[i])>5){ #there are some broken sentences with few or no characters
+            temp1 <- text.alignment::smith_waterman(icb_long_crisis_sentence_unique$sentence_clean[i] , icb_long_crisis_sentence_unique$text[i])
+            icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_start[i]=temp1$b$alignment$from
+            icb_long_crisis_sentence_unique$sentence_clean_hash_match_location_end[i]=temp1$b$alignment$to
+            icb_long_crisis_sentence_unique$sentence_clean_hash_match_similarty[i]=temp1$similarity        
+          }
+        }
+      toc() #878.328 sec elapsed
+    icb_long_crisis_sentence_unique %>% saveRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_long_crisis_sentence_unique.Rds")
+    }
+    icb_long_crisis_sentence_unique <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_long_crisis_sentence_unique.Rds")
 
-    # check for the presence of every crisis
-    setdiff(1:476, icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort())
-    #The only crisis for which we have no codings ever is 474 which is also missing from the official list here and so may never have had text for us to look at
-    #https://duke.app.box.com/s/ddtpva1v33dzyom0j7obk7whitmouzr1
-
-    # create "wide" dataset
-    icb_wide <- icb_long %>% 
-                dplyr::group_by(savefile_crc32, email_crc32, email_id, input_crisis, sentence_number_int, event_number_int, varname) %>%
-                dplyr::summarize(value=paste(value, collapse=";")) %>%
-                tidyr::pivot_wider( id_cols=c('savefile_crc32', 'email_crc32', 'email_id', 'input_crisis', 'sentence_number_int', 'event_number_int'),
-                             names_from='varname',
-                             values_from='value') %>%
-                dplyr::arrange(savefile_crc32, email_id, email_crc32,input_crisis,sentence_number_int,event_number_int) %>% 
-                dplyr::group_by(savefile_crc32 , input_crisis ) %>% tidyr::fill(icb_survey_version, crisis, crisno,sentence,section,lastviewed,sentence_events, .direction = c("down"))
-
-    #None of these error sentences
-    errors <-  icb_wide %>% dplyr::group_by(savefile_crc32 , input_crisis ) %>% dplyr::filter(crisno!=crisno[1]) #There was a bug in the saving script that would save extra sentences from a different crisis if the last one edited was longer than the current one
-
-    icb_wide <- icb_wide %>% dplyr::group_by(savefile_crc32 , input_crisis ) %>% dplyr::filter(crisno==crisno[1]) #This removes any observations within a save file that are from a crisis number different than the first crisis number mentioned in the file
-
-    # create copy of initial variables in case others get edited
-    icb_wide$raw_crisis <- icb_wide$crisis
-    icb_wide$raw_crisno <- icb_wide$crisno
-    icb_wide$raw_sentence <- icb_wide$sentence
-    icb_wide$raw_sentence_number_int <- icb_wide$sentence_number_int
-
-    newname_order <- c(
-      "icb_survey_version",
-      "email_id",
-      "email_crc32",
-      "lastviewed",
-      "input_crisis",
-      "crisis",
-      "crisno",
-
-      "section",
-      "sentence",
-      "sentence_events",
-      #"sentence_number",
-      # "sentencenumber",
-      "sentence_number_int",
-      #"event_number",
-      "event_number_int",
-      "event_type",
-      "raterconfidence",
-      "raterconfidence_reason",
-      "raterconfidence_reason_survey",
-
-      "date",
-      "think_sentence_events",
-
-      "think_actor_a",
-      "think_actor_a_other",
-      "thinkkind",
-
-      "say_actor_a",
-      "say_actor_a_other",
-      "say_actor_b",
-      "say_actor_b_other"   ,
-
-      "sayintkind",
-      "sayintkind_react",
-      "consequence",
-
-      "condition",
-
-      "do_actor_a",
-      "do_actor_a_other",
-      "do_actor_b"          ,
-      "do_actor_b_other",
-
-      "condition_do_actor_a",
-      "condition_do_actor_a_other",
-      "condition_do_actor_b",
-      "condition_do_actor_b_other" ,
-
-      "condition_act_cooperative",
-      "condition_act_descalate",
-      "condition_act_escalate",
-      "condition_act_uncooperative",
-
-      "condition_do_interact_kind",
-      "condition_do_kind",
-      "condition_interact_decreasecoop",
-      "condition_interact_descalate",
-      "condition_interact_domains",
-      "condition_interact_escalate",
-      "condition_interact_fatalities",
-      "condition_interact_forces",
-      "condition_interact_geoscope",
-      "condition_interact_increasecoop",
-      "condition_interact_location",
-      "condition_interact_location_other",
-      "condition_interact_territory",
-      "condition_interact_units",
-
-      "do_duration",
-      "do_interact_kind",
-      "do_kind",
-      "do_timing",
-      "do_timing_reorder",
-
-      "act_cooperative",
-      "act_descalate",
-      "act_escalate",
-      "act_uncooperative",
-
-      "interact_decreasecoop",
-      "interact_descalate",
-      "interact_domains",
-      "interact_escalate",
-      "interact_fatalities",
-      "interact_forces",
-      "interact_geoscope",
-      "interact_increasecoop",
-      "interact_location",
-      "interact_location_other",
-      "interact_territory",
-      "interact_units",
-
-      "raw_crisis",
-      "raw_crisno",
-      "raw_sentence",
-      "raw_sentence_number_int",
-      "savefile_crc32"
+    icb_long_spans <- icb_long %>% 
+                      mutate(crisno = crisno %>% as.numeric()) %>%
+                      left_join(icb_long_crisis_sentence_unique %>%
+                                filter(!is.na(sentence_clean_hash_match_location_start)) %>%
+                                rowwise() %>%
+                                  mutate(sentence_span_text=text %>% substring(first=sentence_clean_hash_match_location_start, last=sentence_clean_hash_match_location_end) %>% trimws() ) %>%
+                                ungroup() %>%
+                      dplyr::select(crisno,
+                                    sentence_clean,
+                                    sentence_span_score=sentence_clean_hash_match_similarty,
+                                    sentence_span_start=sentence_clean_hash_match_location_start,
+                                    sentence_span_end=sentence_clean_hash_match_location_end,
+                                    sentence_span_text
                                     ) 
-
-    setdiff(newname_order, names(icb_wide) )
-    setdiff(names(icb_wide), newname_order )
-
-    #problem sometimes I use a and sometimes I use 1 or 2
-    icb_wide <- icb_wide[newname_order]
-    icb_coder_crisis_sentence_event <- icb_wide
-    remove(icb_wide)
-    saveRDS(icb_coder_crisis_sentence_event,
-            file=paste0(here::here(),"/replication_data/in/icb_coder_crisis_sentence_event.Rds"))
+                      ) %>% dplyr::select(-sentence_number_int) #nuke sentence number here and replace it later based on span
+    dim(icb_long_spans) #880,593
+    saveRDS(icb_long_spans ,
+            file=paste0(here::here(),"/replication_data/in/icb_long_spans.Rds")) #note "input crisis" is broken
   }  else  {
-    icb_coder_crisis_sentence_event <-
-      readRDS(file=paste0(here::here(),"/replication_data/in/icb_coder_crisis_sentence_event.Rds"))
+    icb_long_spans <-
+      readRDS(file=paste0(here::here(),"/replication_data/in/icb_long_spans.Rds"))
 }
@@
 ```
-
-Check if any crises are missing, throw an error if it's not just 474
-```{r}
-setdiff( c(1:476), icb_coder_crisis_sentence_event$crisno)
-
- if(length(setdiff( c(1:476), icb_coder_crisis_sentence_event$crisno)) > 1) stop('Multiple Crisis Missing! Check icb_worker_saves')
-
-```
-
-## Sentence Alignment
-
-This section realigns source sentences from multiple versions of the coding GUI
-
-This Rmd sometimes gets warning the warning `Unknown or uninitialised column: 'crisisno_crisis_version'.` It cannot be reliably reproduced; so far have not found unwanted repercussions.
-
-Trim extra white space from all sentences
-```{r}
-# use 'icb_wide' as shorthand for icb_coder_crisis_sentence_event
-icb_wide <- icb_coder_crisis_sentence_event %>% 
-  dplyr::mutate(sentence = trimws(sentence))
-
-```
-
-### Which crisis have crisis-sentence_numbers that have different sentences?
-
-```{r}
-
-# give each sentence a crisisno-sentence code
-icb_wide$raw_crisno_sentno <- paste0("c", icb_wide$raw_crisno, "-s", icb_wide$raw_sentence_number_int)
-
-# check that each crisno_sentno has only one sentence associated with it.
-unique_sent <- unique(icb_wide[,c("sentence", "raw_crisno_sentno")])
-dup_sent <- names(table(unique_sent$raw_crisno_sentno)[table(unique_sent$raw_crisno_sentno)>1]) 
-  #list of the sentences that multiple sentences assigned to them.
-
-dup_cris <- as.numeric(names(table(icb_wide$raw_crisno[icb_wide$raw_crisno_sentno %in% dup_sent]))) 
-  # list of the afflicted sentences
-
-sort(dup_cris)
-
-```
-
-What crisis names match those crisis numbers?
-
-```{r}
-sort(unique(icb_wide$crisis[icb_wide$crisno %in% dup_cris]))
-```
-
-Does that get all the crises with names that end in a number?
-
-```{r}
-grep('2', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)
-grep('3', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)
-grep('4', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)
-
-```
-It doesn't miss any that ends in 2 or 3 or 4. There are some that end in 1, but if there isn't a 2 that follows them then it's a different issue.
-
-```{r}
-grep('1', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE)
-
-# check to make sure those crises ending in '1' don't have another version without the 1
-setdiff(grep('1', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE), 
-        unique(icb_wide$crisis[(icb_wide$crisno %in% unique(icb_wide$crisno[(icb_wide$crisis %in% grep('1', unique(icb_wide$crisis[!(icb_wide$crisno %in% dup_cris)]), value=TRUE))]))]))
-```
-
-# Set all crises to have the same crisis name
-```{r}
-#### standardize
-crisiskey <- read.csv(paste0(here::here(), "/replication_data/in/icb1v12crisisnames.csv")) # standardize crisis
-
-```
-
-```{r}
-icb_wide <- icb_wide %>% 
-  dplyr::select(!crisis) %>% 
-  dplyr::left_join(crisiskey %>% 
-                     dplyr::rename(crisis = icb_crisname, raw_crisis = raw_crisname) %>% 
-                     dplyr::select(crisis, raw_crisis))
-```
-
-```{r}
-sort(unique(icb_wide$crisis[icb_wide$crisno %in% dup_cris]))
-
-```
-
-which crises have mismatching sentences in the same version?
-
-check crisisname-version-sentence
-
-```{r}
-
-icb_wide$raw_crisno_version_sentno <- paste0(icb_wide$raw_crisno, "v", icb_wide$icb_survey_version, "-s", icb_wide$raw_sentence_number_int)
-icb_wide$crisisno_crisis_version <- paste0(icb_wide$raw_crisno, "_", icb_wide$raw_crisis, "_", icb_wide$icb_survey_version)
-
-# check that each crisno_sentno has only one sentence associated with it.
-unique_vsent <- unique(icb_wide[,c("sentence", "raw_crisno_sentno")])
-
-#list of the sentences that multiple sentences assigned to them.
-dup_vsent <- names(table(unique_vsent$raw_crisno_sentno)[table(unique_vsent$raw_crisno_sentno)>1])
-
-# list of crises with the afflicted sentences
-dup_vcris <- names(table(icb_wide$crisisno_crisis_version[icb_wide$raw_crisno_sentno %in% dup_vsent])) 
-sort(dup_vcris)
-
-```
-
-40 crisis have different sentence numbers in the same crisis:
-
-### Create a csv to hand clean the sentence codes of.
-
-```{r}
-
-sentencekey_toclean <- unique(icb_wide[,c("email_id", "raw_crisis","raw_crisno","raw_sentence", "sentence", "raw_sentence_number_int", "raw_crisno_sentno", "icb_survey_version")])
-
-sentencekey_toclean <- sentencekey_toclean[sentencekey_toclean$raw_crisno %in% dup_cris,]
-sentencekey_toclean$raw_crisno <- as.numeric(sentencekey_toclean$raw_crisno)
-sentencekey_toclean$raw_sentence_number_int <- as.numeric(sentencekey_toclean$raw_sentence_number_int)
-
-sentencekey_toclean <- sentencekey_toclean[with(sentencekey_toclean, order(raw_crisno, raw_crisis, email_id, icb_survey_version, raw_sentence_number_int)),]
-
-```
-
-```{r}
-table(sentencekey_toclean$raw_crisis, sentencekey_toclean$icb_survey_version)
-```
-
-To prep for cleaning, make an "raw_crisis"
-
-```{r}
-
-sentencekey_toclean$crisisno_crisis_version <- paste0(sentencekey_toclean$raw_crisno, "_",
-                                                      sentencekey_toclean$raw_crisis, "_",
-                                                      sentencekey_toclean$icb_survey_version)
-
-sentencekey_toclean <- sentencekey_toclean %>% 
-  dplyr::mutate(conflict_sent = ifelse(raw_crisno_sentno %in% dup_vsent, 1, 0))
-
-# line above requres setdiff1 from below
-
-write.csv(sentencekey_toclean, file=paste0(here::here(), "/replication_data/temp/sentencekey_toclean.csv"))
-```
-
-Check if there is a pattern between versions or coders. None apparant. 
-```{r}
-
-dup_cris_vec <- icb_wide$crisno %in% dup_cris
-
-table(icb_wide$icb_survey_version, dup_cris_vec)
-#table(icb_wide$email_cr32, dup_cris_vec)
-
-```
-
-### Load in sentence alignment key
-
-```{r}
-# load key dataset
-#sentence_alignment_key_raw <- readODS::read_ods(paste0(here::here(), "/data/sentence_alignment_key.ods"))
-sentence_alignment_key_raw <- readr::read_csv(paste0(here::here(), "/replication_data/in/sentence_alignment_key.csv"))
-sentence_alignment_key_raw$crisno <- as.character(sentence_alignment_key_raw$crisno)
-
-#reformat
-sentence_alignment_key <- rbind(
-  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence1")], "sentence1", "sentence"),
-  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence2")], "sentence2", "sentence"),
-  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence3")], "sentence3", "sentence"),
-  data.table::setnames(sentence_alignment_key_raw[,c("crisno", "sentence_number_int_aligned", "sentence4")], "sentence4", "sentence")) %>% 
-  dplyr::filter(!is.na(sentence)) %>% 
-  unique()
-
-# Create an index to find crisis-sentences with multiple sentences
-# sentence_alignment_key <- sentence_alignment_key %>% group_by(crisno, sentence_number_int_aligned) %>% mutate(id = row_number()) %>% dplyr::filter(id > 2)
-
-```
-
-The original read in changed, so check that the sentence alignment key contains all and only the sentences originally exported for alignment
-```{r}
-setdiff1 <- (setdiff(unique(sentencekey_toclean$sentence), unique(sentence_alignment_key$sentence)))
-# what toclean has that is missing from alignment key
-
-if(length(setdiff1)>0){
-  sentencekey_toclean <- sentencekey_toclean %>% dplyr::mutate(sent_unfixed = ifelse(sentence %in% setdiff1 & conflict_sent==1, 1, 0))
-  write.csv(sentencekey_toclean, file=paste0(here::here(), "/replication_data/temp/sentencekey_toclean.csv"))
-  warning("alignment key may be incomplete")
-}
-
-```
-
-```{r}
-# what alignment key has that is missing from 'to clean'
-
-setdiff2 <- data.frame(setdiff(unique(sentence_alignment_key$sentence), unique(sentencekey_toclean$raw_sentence)))
-head(setdiff2)
-```
-
-```{r}
-# crises that alignment key has that is missing from 'to clean' (ok if there are extra)
-setdiff3 <- setdiff(unique(sentence_alignment_key$crisno), unique(sentencekey_toclean$raw_crisno))
-setdiff3
-```
-
-```{r}
-# crises that 'to clean' has that is missing from  alignment key(should be empty)
-setdiff4 <- setdiff(unique(sentencekey_toclean$raw_crisno), unique(sentence_alignment_key$crisno))
-setdiff4
-```
-
-```{r}
-
-#drop duplicates and missing
-sentence_alignment_key <- unique(sentence_alignment_key[complete.cases(sentence_alignment_key),])
-
-#eyeball key, checking crisis number, that sentence_number is generally decreasing (but gaps allowed and expected!), and that no sentences are NA
-table(sentence_alignment_key$crisno)
-table(sentence_alignment_key$sentence_number_int_aligned)
-table(is.na(sentence_alignment_key$sentence))
-```
-
-```{r}
-# merge alignment sentence numbers
-icb_wide_aligned <- icb_wide %>% dplyr::left_join(sentence_alignment_key)
-
-# look at alignment outcomes
-#dim(events) 
-dim(icb_wide_aligned) # number of rows should be identical with one column added
-table(icb_wide_aligned$crisno)
-table(is.na(icb_wide_aligned$crisno))
-table(icb_wide_aligned$sentence_number_int_aligned)
-table(is.na(icb_wide_aligned$sentence_number_int_aligned))
-```
-if no alignment was needed, pass `sentence_number_int_aligned` the value in `sentence_number_int`
-```{r}
-
-icb_wide_aligned$sentence_number_int_aligned[is.na(icb_wide_aligned$sentence_number_int_aligned)] <- icb_wide_aligned$sentence_number_int[is.na(icb_wide_aligned$sentence_number_int_aligned)]
-table(icb_wide_aligned$sentence_number_int_aligned)
-table(is.na(icb_wide_aligned$sentence_number_int_aligned))
-```
-
-save dataset with alignment
-```{r}
-saveRDS(icb_wide_aligned %>% dplyr::arrange(savefile_crc32, sentence_number_int, event_number_int),
-     file=paste0(here::here(),"/replication_data/temp/ICBe_V1_long_unclean.Rds"))
-```

### 2022-07-17 replication_data/rmd/02_format_and_clean.rmd
v1.1

--- 2022-02-04 replication_data/rmd/02_format_and_clean.rmd
@@
 
+library(tidyverse)
+
 `%>%` <- magrittr::`%>%`
-```
-
-# Load and transform wide to long
-
-read in icb_coder_crisis_sentence_event_aligned.Rds
-```{r}
-icb_wide_aligned_raw <- readRDS(file=paste0(here::here(),"/replication_data/temp/ICBe_V1_long_unclean.Rds")) %>% 
-                    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), sentence_number_int_aligned3 =
-                                    stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>%
-                    dplyr::mutate(email_crisis_sent_event =
-                                    paste0(email_id,"_",crisno3,"_",sentence_number_int_aligned3,"_",event_number_int)) %>%
-                    dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
-                    dplyr::arrange(crisno, sentence_number_int, event_number_int) %>%
-
-                    ####################Where we kill unhelpful events
-                    #There are 2 legitimate kinds of rows
-                    dplyr::filter(
-                      event_number_int==0 & sentence_events %in% c('Background', 'Covered by Previous Sentence','Error','No Action') |
-                      event_number_int>0 & event_type %in% c('Action', 'Speech','Thought' )
-                    ) #%>%
-
-dim(icb_wide_aligned_raw) #87710    85
-```
-
-Remove variables used earlier for compiling the individual codings
-```{r}
-icb_wide_aligned <- icb_wide_aligned_raw %>% dplyr::ungroup() %>% 
-  dplyr::select(
-               # -lastviewed, 
-               # -input_crisis, 
-                -sentence_number_int, -raw_crisis, -raw_crisno, -raw_sentence, -savefile_crc32, -raw_crisno_sentno, -raw_crisno_version_sentno, -crisisno_crisis_version) %>%
-  dplyr::mutate(icb_survey_version = ifelse(is.na(icb_survey_version), 1.1, icb_survey_version))
-dim(icb_wide_aligned) #52929    78
 
@@
 
-Initial coding edits (spelling, formatting, etc)
+This assigns sentence numbers by the text spans instead of the original gui
+
 ```{r}
-icb_wide_aligned <- icb_wide_aligned %>% 
-                      dplyr::rename(act_deescalate = act_descalate) %>% 
-                      dplyr::rename(interact_deescalate = interact_descalate) %>% 
-                      dplyr::rename(condition_act_deescalate = condition_act_descalate) %>% 
-                      dplyr::rename(condition_interact_deescalate = condition_interact_descalate) %>% 
-                      dplyr::mutate(sayintkind_react = ifelse(sayintkind_react=="This Sentence", raw_sentence_number_int,
-                                                                         stringr::str_replace(sayintkind_react, "Sentence ","")))
-dim(icb_wide_aligned) #52929    78
+
+icb_long_spans <- readRDS(file=paste0(here::here(),"/replication_data/in/icb_long_spans.Rds"))
+
+coders_per_crisis <- icb_long_spans %>% dplyr::select(crisno,  email_id, expert) %>% distinct() #%>% dplyr::count(crisno)
+coders_per_crisis_tally <- coders_per_crisis %>% mutate(novice=expert==0) %>% group_by(crisno) %>% summarise( expert=sum(expert==1), novice=sum(novice==1) )
+crisis_sentences_per_coder <- icb_long_spans %>% filter(varname %>% str_detect("sentence_events")) %>% dplyr::count(email_id, crisno)
+
+dim(icb_long_spans) #767100     16
+icb_long_spans_clean <- icb_long_spans %>%
+      filter(!is.na(sentence_span_start) & sentence_span_score>0.35 & sentence_clean!='PRE-CRISIS') %>%
+      group_by(crisno) %>%
+        mutate(sentence_number_int_aligned=sentence_span_start %>% as.factor() %>% as.integer() ) %>%
+      ungroup() %>%
+      filter(!varname %in% c('sentence_number_int', 'raw_crisis', 'raw_crisno', 'raw_sentence', 'savefile_crc32', 'raw_crisno_sentno', 'raw_crisno_version_sentno', 'crisisno_crisis_version')) %>%
+      mutate(varname=varname %>% recode(act_descalate = 'act_deescalate', interact_descalate = 'interact_deescalate', condition_act_descalate = 'condition_act_deescalate', 
+                                        condition_interact_descalate = 'condition_interact_deescalate' ) ) %>%
+  filter(!varname %in% c("sentence","text")) %>% 
+  dplyr::mutate(value = strsplit(as.character(value), ";")) %>% 
+  tidyr::unnest(value) %>%
+  dplyr::mutate(value=value %>% tolower %>% trimws()) %>% 
+  filter(!duplicated(paste(email_id, crisno,  sentence_number_int_aligned, event_number_int, varname,value)))  %>%
+  mutate(sentencenumber_original= value %>% as.numeric() ) %>% #do this out of the loop or the warnings slow everything down
+  group_by(email_id, crisno, input_crisis,sentence_number_int_aligned ) %>% 
+    mutate(sentencenumber_original= ifelse(varname %in%  'sentencenumber', value, NA) ) %>%
+    mutate(sentencenumber_original= sentencenumber_original %>% max(na.rm=T)) %>%
+  ungroup()
+
+dim(icb_long_spans_clean) #715451
+
+varname_count <- icb_long_spans_clean %>% count(varname)
+value_count <- icb_long_spans_clean %>% count(value)
+
+#dplyr::mutate(sayintkind_react = ifelse(sayintkind_react=="This Sentence", raw_sentence_number_int,
+#                                                   stringr::str_replace(sayintkind_react, "Sentence ","")))
+
+#we basically don't believe 'sentence  1' that just means earlier
+
+#Map the original sentence reorder to the new span numbers
+icb_long_spans_clean %>% filter(varname %in% c('do_timing','do_timing','think_sentence_events','sayintkind_react','do_timing_reorder')) %>% count(varname, value) %>% View()
+
+alter_allignment <- icb_long_spans_clean %>% 
+                    dplyr::select(crisno, email_id, input_crisis, sentence_number_int_aligned,sentencenumber_original) %>% distinct()
+
+reorder_normalized <- icb_long_spans_clean %>% 
+                      filter(varname %in% c('do_timing','do_timing','think_sentence_events','sayintkind_react','do_timing_reorder')) %>%
+                      dplyr::select(crisno, email_id, input_crisis, varname, value,sentence_number_int_aligned,sentencenumber_original) %>%
+                      mutate(value_normalized = value %>% str_replace("sentence  |sentence ","") %>% trimws() %>% as.numeric() ) %>%
+                      left_join(
+                        alter_allignment %>% dplyr::select(crisno , email_id ,input_crisis  ,value_normalized_new=sentence_number_int_aligned ,value_normalized=sentencenumber_original) %>%
+                          mutate(value_normalized=value_normalized %>% as.numeric(), value_normalized_new= value_normalized_new %>% as.numeric() )
+                        ) %>%
+                      mutate(value_normalized = ifelse(!is.na(value_normalized_new) , value_normalized_new, value_normalized) ) %>%
+                      dplyr::select(-value_normalized_new) %>%
+                      mutate(value_normalized = ifelse(value %in% c("act in this sentence","speech in this sentence","this sentence") , sentence_number_int_aligned, value_normalized) ) %>%
+                      mutate(value_normalized=value_normalized %>% as.character()) %>%
+                      #reorders were broken and set to default sentence 1 so drop them without loss of info
+                      mutate(value_normalized = ifelse(value %in% c("sentence  1|1") & varname %in% "do_timing_reorder" , "drop", value_normalized) ) %>%
+                      filter(!is.na(value_normalized)) 
+dim(reorder_normalized)
 
@@
 
-Where a coder looked at the same crisis twice, drop the earlier version and the earlier date
-```{r}
-icb_wide_aligned <- icb_wide_aligned %>% 
-                      dplyr::group_by(email_crisis_sent_event) %>% 
-                      dplyr::slice_max(icb_survey_version) %>%
-                      dplyr::ungroup()
+```{r, eval=T}
+# Fix typos:
 
-icb_wide_aligned <- icb_wide_aligned %>% 
-                    dplyr::group_by(email_crisis_sent_event) %>% 
-                    dplyr::slice_max(lastviewed) %>%
-                    dplyr::ungroup()
-dim(icb_wide_aligned) #87710    77
-```
+print(paste("change 'premption' to 'preemption'", icb_long_spans_clean %>% dplyr::filter(stringr::str_detect(value, "premption")==TRUE) %>% nrow(), "times."))
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "premption", "preemption"))
 
-Drop a small subset where it appears that a coder looked at the same crisis twice but one of the times was logged incorrectly
-```{r}
-icb_wide_aligned <- icb_wide_aligned %>% dplyr::left_join(
-                    icb_wide_aligned %>% dplyr::select(email_crisis_sent_event, event_number_int) %>% dplyr::filter(
-                    (icb_wide_aligned %>% dplyr::select(email_crisis_sent_event, event_number_int) %>% 
-                       duplicated()) == TRUE) %>% 
-                      dplyr::mutate(duplicate = 1)) %>% 
-                    dplyr::mutate(mismatch = crisis != input_crisis) %>% 
-                    dplyr::filter(!(mismatch %in% TRUE & duplicate %in% 1)) %>%
-                    dplyr::select(-mismatch, -duplicate)
+print(paste("change 'disaprove' to 'disapprove'", icb_long_spans_clean %>% dplyr::filter(stringr::str_detect(value, "disaprove")==TRUE) %>% nrow(), "times."))
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "disaprove", "disapprove"))
 
-dim(icb_wide_aligned) #51098    78
+print(paste("change 'uncoperative' to 'uncooperative'", icb_long_spans_clean %>% dplyr::filter(stringr::str_detect(value, "uncoperative")==TRUE) %>% nrow(), "times."))
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "uncoperative", "uncooperative"))
 
-```
+print(paste("change 'capitol' to 'capital'", icb_long_spans_clean %>% dplyr::filter(stringr::str_detect(value, "capitol")==TRUE) %>% nrow(), "times."))
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "capitol", "capital"))
 
-Pivot to long form 
-```{r}
+print(paste("change 'survailance' to 'surveillance'", icb_long_spans_clean %>% dplyr::filter(stringr::str_detect(value, "survailance")==TRUE) %>% nrow(), "times."))
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "survailance", "surveillance"))
 
-icb_long <- icb_wide_aligned %>% dplyr::ungroup() %>% 
-             dplyr::relocate(sentence_events, .after = event_number_int) %>%
-             tidyr::pivot_longer(
-               cols = c(sentence_events:interact_units), #  changed this to be inclusive of event type and sentence_events 
-               names_to = "variable",
-               #names_prefix = "wk",
-               values_to = "value",
-               values_drop_na = TRUE
-             ) %>% dplyr::ungroup() %>% 
-  dplyr::mutate(value=value %>% tolower %>% trimws())
-dim(icb_long) #491757     15
+print(paste("change 'disaprove' to 'disapprove'", icb_long_spans_clean %>% dplyr::filter(stringr::str_detect(value, "disaprove")==TRUE) %>% nrow(), "times."))
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "disaprove", "disapprove"))
 
-```
+#Clean up some dates
+icb_long_spans_clean <- icb_long_spans_clean %>% dplyr::mutate(value = stringr::str_replace(value, "17 july 2004", "17 July 2014"))
 
-Now split values with a list (separated by a semicolon)
-
-```{r}
-
-icb_long_split <- icb_long %>% 
-                  dplyr::mutate(value = strsplit(as.character(value), ";")) %>% 
-                  tidyr::unnest(value) %>%
-                  dplyr::mutate(value=value %>% tolower %>% trimws())
-dim(icb_long_split) #536397     15
-
-```
-
-# Define subsets of variables
-
-```{r}
-
-vars <- c(
-"sentence_events", "event_type", "raterconfidence", "raterconfidence_reason",
-"raterconfidence_reason_survey", "date", "think_sentence_events", "think_actor_a", "think_actor_a_other", 
-"thinkkind", "say_actor_a", "say_actor_a_other", "say_actor_b", "say_actor_b_other",
-"sayintkind", "sayintkind_react", "consequence", "condition", "do_actor_a",
- "do_actor_a_other", "do_actor_b", "do_actor_b_other", "condition_do_actor_a",
-"condition_do_actor_a_other", "condition_do_actor_b", "condition_do_actor_b_other",
- "condition_act_cooperative", "condition_act_deescalate", "condition_act_escalate",
-"condition_act_uncooperative", "condition_do_interact_kind", "condition_do_kind",
-"condition_interact_decreasecoop",  "condition_interact_deescalate",
-"condition_interact_domains", "condition_interact_escalate", "condition_interact_fatalities",
-"condition_interact_forces", "condition_interact_geoscope", "condition_interact_increasecoop",
-"condition_interact_location", "condition_interact_location_other", "condition_interact_territory",
-"condition_interact_units", "do_duration", "do_interact_kind", "do_kind", "do_timing",
-"do_timing_reorder", "act_cooperative", "act_deescalate", "act_escalate",
-"act_uncooperative", "interact_decreasecoop", "interact_deescalate", "interact_domains",
-"interact_escalate", "interact_fatalities", "interact_forces", "interact_geoscope",
-"interact_increasecoop",  "interact_location", "interact_location_other", "interact_territory",
-"interact_units" )
-
-vars_actor <- c("think_actor_a",
-             "think_actor_a_other",
-             "say_actor_a",
-             "say_actor_a_other",
-             "say_actor_b",
-             "say_actor_b_other",
-             "do_actor_a",
-             "do_actor_a_other",
-             "do_actor_b",
-             "do_actor_b_other", 
-             "condition_do_actor_a",
-             "condition_do_actor_a_other",
-             "condition_do_actor_b",
-             "condition_do_actor_b_other")
-
-vars_act <- c("act_cooperative",
-              "act_uncooperative",
-              "act_deescalate",
-              "act_escalate",
-              "interact_decreasecoop",
-              "interact_increasecoop",
-              "interact_deescalate",
-              "interact_escalate",
-              "condition_act_cooperative",
-              "condition_act_uncooperative",
-              "condition_act_deescalate",
-              "condition_act_escalate",
-              "condition_interact_decreasecoop",
-              "condition_interact_increasecoop",
-              "condition_interact_deescalate",
-              "condition_interact_escalate")
-
-# saveRDS(vars_actor, paste0(here::here(), "/replication_data/temp/","vars_actor.Rds"))
-# saveRDS(vars_act, paste0(here::here(), "/replication_data/temp/","vars_act.Rds"))
-
-vars_say <- c("sayintkind", "sayintkind_react","consequence","condition")
-vars_think <- c("think_sentence_events", "thinkkind", "thinkkind_clean")
-
-# Duplicate variables, same options for each in these types
-vars_act_kind <- c("do_kind", "condition_do_kind", "do_interact_kind", "condition_do_interact_kind")
-vars_fatalities <- c("interact_fatalities", "condition_interact_fatalities")
-vars_forces <- c("interact_forces", "condition_interact_forces")
-vars_geoscope <- c("interact_geoscope", "condition_interact_geoscope")
-vars_location <- c("interact_location", "condition_interact_location")
-vars_location_other <- c("interact_location_other", "condition_interact_location_other")
-vars_territory <- c("interact_territory", "condition_interact_territory")
-
-# NEED TO ADD TO CODEBOOK
-vars_domains <- c("interact_domains", "condition_interact_domains")
-vars_units <- c("interact_units", "condition_interact_units")
-
-```
-
-```{r}
-# are all variables in vars?
-setdiff(unique(icb_long_split$variable), vars)
-
-# do the subsets cover everything in vars?
-setdiff(vars, c(vars_actor, vars_act, vars_act_kind, vars_fatalities, vars_forces, vars_geoscope, vars_location, vars_location_other, vars_territory, vars_domains, vars_units, vars_say, vars_think))
 ```
@@
 ```{r message=FALSE}
+
 target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
@@
 
+#Paper 2 will take dates and time seriously we ignore now
+#What we're going to do is generate several new long variables and let it allow for agreements across coders
+dictionary_dates <- readxl::read_excel(target_file, sheet="dates", col_types="text") %>%
+                    dplyr::select(-coder, -notes)   %>% distinct() %>% 
+                    tidyr::pivot_longer(cols=-c(date_orig)) %>% 
+                    filter(!is.na(value)) 
+dictionary_dates$decade <- ( dictionary_dates$value %>% stringi::stri_match_first(regex="([0-9]{3}[A-Z])") )[,2] 
+dictionary_dates$year <- ( dictionary_dates$value %>% stringi::stri_match_first(regex="([0-9]{4})") )[,2] %>% as.numeric()
+dictionary_dates$month <- ( dictionary_dates$value %>% stringi::stri_match_first(regex="[Y0-9]{4}-([0-9]{1,2})") )[,2] %>% as.numeric()
+dictionary_dates$day <- ( dictionary_dates$value %>% stringi::stri_match_first(regex="[Y0-9]{4}-[M0-9]{1,2}-([0-9]{1,2})") )[,2] %>% as.numeric()
+
+dictionary_dates <- dictionary_dates %>% 
+                    mutate(month=ifelse(str_detect(value, "Jan|jan"),1, month)) %>%
+                    mutate(month=ifelse(str_detect(value, "Feb|feb"), 2, month)) %>%
+                    mutate(month=ifelse(str_detect(value, "March|mar"),3, month)) %>%
+                    mutate(month=ifelse(str_detect(value, "April|apr"),4, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "May|may"),5, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "June|jun"),6, month)) %>%
+                    mutate(month=ifelse(str_detect(value, "July|jul"),7, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "Aug|aug"),8, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "Sep|sep"),9, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "Oct|oct"),10, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "Nov|nov"),11, month) )%>%
+                    mutate(month=ifelse(str_detect(value, "Dec|dec"),12, month) )%>%
+
+                    #filter(value=="circa autumn 1947") %>%
+                    mutate(decade = ifelse(!is.na(year), floor(as.numeric(year)/10)*10  ,  as.numeric(str_extract(decade, "[0-9]{3}"))*10  ) %>% as.numeric()  ) %>% 
+                    mutate(year_part = NA ) %>%
+
+                    mutate(year_part = ifelse( (!is.na(year) & is.na(month) & str_detect(value, "beginning|early|first half|second quarter|first quarter") ) | 
+                                                 ( !is.na(month) & month<=4 ) , 1 , year_part ) ) %>%
+
+                    mutate(year_part = ifelse( (!is.na(year) & is.na(month) & str_detect(value, "middle|summer|autumn") ) |  ( !is.na(month) & month>=5 & month<=8 ), 2 , year_part ) )  %>%
+
+                    mutate(year_part = ifelse(  (!is.na(year) & is.na(month) & str_detect(value, "end") ) |  ( !is.na(month) & month>=9 )  , 3 , year_part )   ) %>%
+
+                    mutate(month_part = NA ) %>%
+                    mutate(month_part = ifelse( ( !is.na(year) & !is.na(month) & is.na(day) & str_detect(value, "beginning|early|first half")) |  ( !is.na(day) & day<=9 ) , 1 , month_part ) ) %>%
+                    mutate(month_part = ifelse( (!is.na(year) & !is.na(month) & is.na(day) & str_detect(value, "middle")) |  (!is.na(day) &  day>=10 & day<=20 ), 2 , month_part ) )  %>%
+                    mutate(month_part = ifelse( (!is.na(year) & !is.na(month) & is.na(day) & str_detect(value, "end")) |  (!is.na(day) &  day>=21 ), 3 , month_part ) ) %>%
+                    dplyr::select(date_orig,  name, ,value , decade , year ,year_part , month , month_part, day ) %>%
+                    arrange(decade,year, year_part, month, month_part, day) %>%
+                    mutate(varname="date") %>%
+                    mutate(varname_normalized="date" %>% paste0("_",name)) %>%
+                    mutate(varname_normalized = ifelse(varname_normalized %in% c('date_earliest_date',
+                                                                                 'date_earliest_date2',
+                                                                                 'date_point_in_time',
+                                                                                 'date_point_in_time2',
+                                                                                 'date_point_in_time3',
+                                                                                 'date_point_in_time4',
+                                                                                 'date_point_in_time5',
+                                                                                 'date_start_time',
+                                                                                 'date_start_time2'
+                                                                                 ) , 
+                                                       "date_earliest" , varname_normalized   )) %>%
+                    mutate(varname_normalized = ifelse(varname_normalized %in% c('date_earliest_end_date',
+                                                                                 'date_end_time',
+                                                                                 'date_end_time2',
+                                                                                 'date_latest_date',
+                                                                                 'date_latest_date2',
+                                                                                 'date_latest_start_date'),  
+                                                       "date_latest" , varname_normalized   ))
+
+dictionary_dates %>% count(varname_normalized)
+
+dates_normalized <- dictionary_dates %>% 
+                    dplyr::select(date_orig, varname_normalized, decade , year, year_part, month, month_part,   day)  %>% 
+                    pivot_longer(cols=-c(date_orig, varname_normalized)) %>%
+                    mutate(varname_normalized=varname_normalized %>% paste0("_",name)) %>%
+                    dplyr::select(value_normalized = value , value=date_orig, varname_normalized )
+
 dictionary_actions  <- readxl::read_excel(target_file, sheet="actions") %>% dplyr::distinct() 
-dictionary_actors    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno,value, value_normalized=value_normalized_wikidata_id) %>% dplyr::distinct()
+dictionary_actors    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno,value, value_qcode=value_normalized_wikidata_id, value_normalized=value_normalized_label) %>% dplyr::distinct() %>%
+                        full_join(varname_count %>% dplyr::select(varname) %>% filter(varname %>% str_detect("actor")),  by = character())
 
 #Locations and dates are both really hard to do
-dictionary_locations <- readxl::read_excel(target_file, sheet="locations", na = c("", "NA")) 
-dictionary_dates <- readxl::read_excel(target_file, sheet="dates", col_types="text") #This is the tricky one and why he had to add values
+dictionary_locations <- readxl::read_excel(target_file, sheet="locations", na = c("", "NA")) %>% 
+                        dplyr::select(value=interact_location_other, value_normalized=norm_name, value_qcode= norm_qcode) %>% distinct() %>%
+                        full_join(varname_count %>% dplyr::select(varname) %>% filter(varname %>% str_detect("location_other")),  by = character())
+dictionary_condition_locations <- readxl::read_excel(target_file, sheet="condition_locations", na = c("", "NA")) %>% 
+                                  dplyr::select(value=condition_interact_location_other, value_normalized=norm_name, value_qcode= norm_qcode) %>% distinct() %>%
+                        full_join(varname_count %>% dplyr::select(varname) %>% filter(varname %>% str_detect("location_other")),  by = character())
 
-```
+dictionary_domains <- data.frame(
+  stringsAsFactors = FALSE,
+           varname = c("interact_domains",
+                       "interact_domains","interact_domains","interact_domains",
+                       "interact_domains","condition_interact_domains",
+                       "condition_interact_domains","condition_interact_domains",
+                       "condition_interact_domains","condition_interact_domains"),
+             value = c("land","sea","air","wmd",
+                       "space","land","sea","air","wmd","space"),
+  value_normalized = c("land","sea","air","wmd",
+                       "space","land","sea","air","wmd","space"),
+       value_qcode = c("Q183366","Q15324","Q272730",
+                       "Q49394","Q4169","Q183366","Q15324","Q272730",
+                       "Q49394","Q4169")
+)
 
-```{r}
-# Create dateset to reconnect location dictionary to individual rows through 'sentence_number_int_aligned'
-location_merge_directory <- icb_wide_aligned %>% 
-    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), 
-                  sentence_number_int_aligned3 = stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>% 
-  dplyr::mutate(email_crisis_sent_event = paste(email_id,crisno3,sentence_number_int_aligned3,event_number_int, sep="_")) %>%
-  dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
-  dplyr::mutate(crisis_sent = paste0(crisno,"_",sentence_number_int_aligned)) %>%
-  dplyr::select(crisno, email_crisis_sent_event, do_actor_a, do_actor_b, interact_location, interact_location_other) %>% 
-  dplyr::mutate(do_actor_a=strsplit(do_actor_a, ";")) %>% tidyr::unnest(do_actor_a) %>%
-  dplyr::mutate(do_actor_b=strsplit(do_actor_b, ";")) %>% tidyr::unnest(do_actor_b) %>%
-  dplyr::mutate(interact_location_other=strsplit(interact_location_other, ";")) %>% tidyr::unnest(interact_location_other) %>%
-  dplyr::mutate(do_actor_a=tolower(do_actor_a), do_actor_b=tolower(do_actor_b),
-                interact_location_other=trimws(tolower(interact_location_other))) %>%
-  dplyr::left_join(dictionary_locations %>%
-                     dplyr::mutate() %>% 
-                     dplyr::mutate(interact_location_other = tolower(interact_location_other)) %>% 
-                     dplyr::select(do_actor_a, do_actor_b, interact_location, interact_location_other, norm_name)) %>%
-  dplyr::mutate(crisno = as.numeric(crisno)) %>% 
-  unique() %>% 
-  dplyr::filter(!is.na(interact_location_other))
+dictionary_units <- data.frame(
+  stringsAsFactors = FALSE,
+                               varname = c("interact_units",
+                                           "interact_units","interact_units",
+                                           "interact_units","interact_units",
+                                           "interact_units","interact_units",
+                                           "interact_units","interact_units",
+                                           "interact_units","interact_units",
+                                           "interact_units","interact_units","interact_units",
+                                           "interact_units",
+                                           "condition_interact_units","condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units","condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units","condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units",
+                                           "condition_interact_units","condition_interact_units"),
+                                 value = c("troops","armor",
+                                           "artillery","fighters","bombers",
+                                           "surface ships","missiles","nuclear",
+                                           "aircraft carriers","surveillance",
+                                           "submarines","survailance","chemical",
+                                           "satellites","biological","troops",
+                                           "armor","artillery","fighters",
+                                           "bombers","surface ships","missiles",
+                                           "nuclear","aircraft carriers",
+                                           "surveillance","submarines","survailance",
+                                           "chemical","satellites",
+                                           "biological"),
+                      value_normalized = c("troops","armor",
+                                           "artillery","fighters","bombers",
+                                           "surface ships","missiles","nuclear",
+                                           "aircraft carriers","surveillance",
+                                           "submarines","surveillance","chemical",
+                                           "satellites","biological","troops",
+                                           "armor","artillery","fighters",
+                                           "bombers","surface ships","missiles",
+                                           "nuclear","aircraft carriers",
+                                           "surveillance","submarines",
+                                           "surveillance","chemical","satellites",
+                                           "biological"),
+                           value_qcode = c("Q4991371","Q920182",
+                                           "Q64418","Q127771","Q170877","Q11446",
+                                           "Q974850","Q12802","Q17205",
+                                           "Q3041792","Q2811","Q3041792","Q3639228",
+                                           "Q26540","Q170907","Q4991371",
+                                           "Q920182","Q64418","Q127771",
+                                           "Q170877","Q11446","Q974850","Q12802",
+                                           "Q17205","Q3041792","Q2811",
+                                           "Q3041792","Q3639228","Q26540","Q170907")
+                    )
 
-```
+dictionary_counts <- data.frame(
+  stringsAsFactors = FALSE,
+           varname = c("interact_forces",
+                       "interact_forces","interact_forces","interact_forces",
+                       "interact_forces","interact_forces","interact_forces",
+                       "condition_interact_forces","condition_interact_forces",
+                       "condition_interact_forces","condition_interact_forces",
+                       "condition_interact_forces","condition_interact_forces",
+                       "condition_interact_forces","interact_fatalities",
+                       "interact_fatalities","interact_fatalities","interact_fatalities",
+                       "interact_fatalities","interact_fatalities",
+                       "interact_fatalities","condition_interact_fatalities",
+                       "condition_interact_fatalities","condition_interact_fatalities",
+                       "condition_interact_fatalities",
+                       "condition_interact_fatalities","condition_interact_fatalities",
+                       "condition_interact_fatalities"),
+             value = c("none","individuals","tens",
+                       "hundreds","thousands","tens of thousands",
+                       "hundreds of thousands","none","individuals","tens","hundreds",
+                       "thousands","tens of thousands","hundreds of thousands",
+                       "none","individuals","tens","hundreds","thousands",
+                       "tens of thousands","hundreds of thousands","none",
+                       "individuals","tens","hundreds","thousands",
+                       "tens of thousands","hundreds of thousands"),
+  value_normalized = c("none","individuals","tens",
+                       "hundreds","thousands","tens of thousands",
+                       "hundreds of thousands","none","individuals","tens","hundreds",
+                       "thousands","tens of thousands","hundreds of thousands",
+                       "none","individuals","tens","hundreds","thousands",
+                       "tens of thousands","hundreds of thousands","none",
+                       "individuals","tens","hundreds","thousands",
+                       "tens of thousands","hundreds of thousands"),
+       value_qcode = c("Q176799","Q176799","Q176799",
+                       "Q176799","Q176799","Q176799","Q176799","Q176799",
+                       "Q176799","Q176799","Q176799","Q176799","Q176799",
+                       "Q176799",NA,"Q1056901","Q1056901","Q1056901",
+                       "Q1056901","Q1056901","Q1056901",NA,"Q1056901","Q1056901",
+                       "Q1056901","Q1056901","Q1056901","Q1056901")
+)
 
-Apply the cleaning dictionaries to the relevant subsets
+normalization_dictionaries <- bind_rows(dictionary_actions %>% rename(varname=variable, varname_normalized=variable_normalized),
+                                        dictionary_locations,
+                                        dictionary_condition_locations,
+                                        dictionary_units,
+                                        dictionary_domains,
+                                        dictionary_counts
+                                        )
 
-```{r}
-  #ACTOR
-icb_long_actor_clean <- icb_long_split %>% 
-  dplyr::filter(variable %in% vars_actor) %>%
-    dplyr::left_join(tibble::tibble(variable=vars_actor) %>% 
-                       dplyr::mutate(temp="temp") %>%
-                       dplyr::left_join(dictionary_actors %>% dplyr::mutate(temp="temp")) %>%
-                       dplyr::select(-temp) %>% 
-                       dplyr::select(crisno, variable, value, value_normalized) %>%
-                     dplyr::mutate(crisno = as.character(crisno)) %>%
-                     # dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized)) %>% 
-                       unique(),
-                     by=c('crisno','variable','value')) %>%
-    dplyr::mutate(variable_normalized = paste0(variable, "_clean")) %>% 
-  dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";")) %>% 
-  tidyr::unnest(value_normalized) %>%
-  dplyr::mutate(value_normalized=value_normalized %>% trimws())
+icb_long_spans_clean_normalized <- icb_long_spans_clean %>%
+                                   #Add in dates
+                                   mutate(varname_normalized=NA, value_normalized=NA, value_qcode=NA) %>%
+                                   left_join(dates_normalized %>% dplyr::select(value,varname_normalized2=varname_normalized, value_normalized2=value_normalized ) %>% mutate(varname="date") ) %>%
+                                   mutate(value_normalized= coalesce(value_normalized2) %>% as.character() ) %>% #we're
+                                   mutate(varname_normalized= coalesce(varname_normalized2,varname_normalized) %>% as.character()  ) %>%
+                                   dplyr::select(-value_normalized2,-varname_normalized2) %>% 
+                                   filter(!(varname %in% "date" & is.na(value_normalized) ) ) %>% #as long as we keep this up first it'll be fine
+                                   #Add in the dictionaries
+                                   left_join(normalization_dictionaries %>%
+                                               dplyr::select(varname,value,value_normalized2=value_normalized,varname_normalized2=varname_normalized ,value_qcode2=value_qcode ) 
+                                             ) %>%
+                                   mutate(value_normalized= coalesce(value_normalized2,value_normalized)) %>%
+                                   mutate(value_qcode= coalesce(value_qcode2,value_qcode)) %>%
+                                   mutate(varname_normalized= coalesce(varname_normalized2,varname_normalized)) %>%
+                                   dplyr::select(-value_normalized2,-varname_normalized2, -value_qcode2) %>% 
+                                   filter(!value_normalized %in% c("drop","not a location","nonspecific" )  ) %>%
+                                   #Add in the actors
+                                   left_join(dictionary_actors %>% rename(value_normalized2=value_normalized, value_qcode2=value_qcode)) %>%
+                                   mutate(value_normalized= coalesce(value_normalized2,value_normalized)) %>%
+                                   mutate(value_qcode= coalesce(value_qcode2,value_qcode)) %>%
+                                   dplyr::select(-value_normalized2,-value_qcode2) %>% 
+                                   filter(!value_normalized %in% "drop") %>%
+                                   #Add in the reorders
+                                   left_join(reorder_normalized %>% dplyr::select(crisno, email_id, input_crisis,varname,value,
+                                                                                  sentence_number_int_aligned, value_normalized2=value_normalized) %>%
+                                               mutate(value_normalized2= value_normalized2 %>% as.character() )) %>%
+                                   mutate(value_normalized= coalesce(value_normalized2,value_normalized)) %>%
+                                   dplyr::select(-value_normalized2) %>%
 
-# check for unmatched
-icb_long_actor_clean %>% dplyr::filter(is.na(value_normalized)) %>% dplyr::select(crisno, variable, value)
-```
-
-```{r}
-  #ACTION
-icb_long_action_clean <- icb_long_split %>% 
-                        dplyr::filter(variable %in% vars_act) %>% 
-                        dplyr::left_join(dplyr::bind_rows(dictionary_actions,
-                                         dictionary_actions %>% 
-                                           dplyr::mutate(variable = paste0("condition_", variable)) %>% 
-                                           dplyr::mutate(variable_normalized = ifelse(is.na(variable_normalized), 
-                                                                                            variable_normalized, 
-                                                                                            paste0("condition_", variable_normalized)))) %>% 
-                                           dplyr::select(variable, value, variable_normalized, value_normalized) %>%
-                                           dplyr::mutate(variable_normalized = ifelse(!is.na(value_normalized) & is.na(variable_normalized), 
-                                                                                   variable, variable_normalized)),
-                                         by=c('variable','value'))
-
-# check for unmatched
-icb_long_action_clean %>% dplyr::filter(is.na(value_normalized)) %>% dplyr::select(crisno, variable, value, variable_normalized, value_normalized) 
-```
-
-```{r}
- #LOCATION
-icb_long_location_clean <- icb_long_split %>% 
-  dplyr::filter(variable == "interact_location_other") %>% 
-  dplyr::full_join(location_merge_directory %>%
-                     dplyr::mutate(crisno = as.character(crisno)) %>% 
-                     dplyr::rename(value = interact_location_other)) %>% 
-  dplyr::rename(value_normalized = norm_name) %>%
-  dplyr::mutate(variable_normalized = "interact_location_other_clean") %>%   
-  dplyr::select(-do_actor_a, -do_actor_b, -interact_location) %>% 
-  dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))
-```
-
-```{r}
-  #DATES
-icb_long_dates_clean <- icb_long_split %>% 
-  dplyr::filter(variable=="date") %>% 
-  dplyr::left_join(dictionary_dates %>% 
-                   dplyr::select(-coder, -notes) %>%
-                   dplyr::rename(value=date_orig)) %>%
-  tidyr::pivot_longer(cols = point_in_time:latest_date2,
-               names_to = "variable_normalized",
-               values_to = "value_normalized",
-               values_drop_na = TRUE) %>%
-  dplyr::mutate(variable_normalized = ifelse(variable_normalized %in% c("point_in_time2", "point_in_time3", "point_in_time4", "point_in_time5"), "point_in_time", variable_normalized))
-
-```
-
-```{r}
-# combine cleaned variables
-
-icb_long_clean <- icb_long_split %>% 
-  dplyr::left_join(icb_long_action_clean, by=names(icb_long_split)) %>% 
-  dplyr::left_join(icb_long_actor_clean, by=names(icb_long_split), suffix = c("", ".actor")) %>% 
-      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.actor, variable_normalized))) %>%
-      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.actor, value_normalized))) %>%
-      dplyr::select(-variable_normalized.actor, -value_normalized.actor) %>% 
-  dplyr::left_join(icb_long_location_clean, by=names(icb_long_split), suffix = c("", ".location")) %>% 
-      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.location, variable_normalized))) %>%
-      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.location, value_normalized))) %>%
-      dplyr::select(-variable_normalized.location, -value_normalized.location) %>% 
-  dplyr::full_join(icb_long_dates_clean, by=names(icb_long_split), suffix = c("", ".date")) %>% 
-      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.date, variable_normalized))) %>%
-      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.date, value_normalized))) %>%
-      dplyr::select(-variable_normalized.date, -value_normalized.date)
-
-```
-
-```{r}
-# As the dictionaries translate some groups into multiple values, need to split out rows with multiple values
-
-icb_long_clean <- icb_long_clean %>% 
                                    dplyr::mutate(value_normalized = strsplit(as.character(value_normalized), ";")) %>% 
@@
                                    dplyr::mutate(crisno=as.numeric(crisno)) %>% 
-  dplyr::mutate(value=tolower(value))
+                                   dplyr::mutate(value=tolower(value)) %>%
 
-dim(icb_long_clean) #507699
-```
+                                   mutate(varname_normalized=coalesce(varname_normalized, varname)) %>%
+                                   mutate(value_normalized=coalesce(value_normalized, value)) %>%
+                                   mutate(varname_normalized=varname_normalized %>% str_replace("_other","")) %>%  #We collapse other into just the normal flow here
+                                   filter(!value_qcode %in% "drop") %>%
+                                   filter(!value_normalized %in% "drop")
+dim(icb_long_spans_clean_normalized) #953,335 #788,194 #835,319 #813,817 #815,679
 
-```{r}
-# Fix several typos:
+# Normalize Dates and Sequencing
 
-print(paste("change 'premption' to 'preemption'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "premption")==TRUE) %>% nrow(), "times."))
-icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "premption", "preemption"))
-
-print(paste("change 'disaprove' to 'disapprove'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "disaprove")==TRUE) %>% nrow(), "times."))
-icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "disaprove", "disapprove"))
-
-print(paste("change 'uncoperative' to 'uncooperative'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "uncoperative")==TRUE) %>% nrow(), "times."))
-icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "uncoperative", "uncooperative"))
-
-print(paste("change 'capitol' to 'capital'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "capitol")==TRUE) %>% nrow(), "times."))
-icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "capitol", "capital"))
-
-print(paste("change 'survailance' to 'surveillance'", icb_long_clean %>% dplyr::filter(stringr::str_detect(value, "survailance")==TRUE) %>% nrow(), "times."))
-icb_long_clean <- icb_long_clean %>% dplyr::mutate(value = stringr::str_replace(value, "survailance", "surveillance"))
+icb_long_spans_clean_normalized %>% saveRDS(paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
 
@@
 Create variable "previous_event_timing"
-```{r}
+```{r, eval=F}
 alignment_key <- icb_wide_aligned_raw %>% 
@@
 
-```{r}
-icb_long_preceding_event <- icb_long_clean %>% 
-  # get do_timing_reorder and do_timing variables
-  dplyr::filter(variable=="do_timing_reorder") %>% 
-  dplyr::mutate(value = as.numeric(stringr::str_remove(value, "sentence "))) %>% 
-  dplyr::rename(prior_sent_raw = value) %>% 
-  # merge in "crisisno_crisis_version""
-  dplyr::left_join(alignment_key %>% 
-                     dplyr::select(email_id, crisno, sentence, crisisno_crisis_version)) %>% 
-  dplyr::left_join(alignment_key %>% 
-                     dplyr::select(-sentence) %>%
-                     dplyr::rename(prior_sent_raw = raw_sentence_number_int, 
-                                   prior_sent_aligned = sentence_number_int_aligned) %>% 
-                     dplyr::mutate(prior_sent_raw = as.numeric(prior_sent_raw))) %>%
-  dplyr::rename(value = prior_sent_raw) %>% 
-  dplyr::mutate(value = as.character(value)) %>% 
-  dplyr::mutate(variable_normalized = "do_timing_reorder_clean") %>% 
-  dplyr::mutate(value_normalized = ifelse(value==1, "drop", prior_sent_aligned)) %>%
-  dplyr::select(-c(crisisno_crisis_version, prior_sent_aligned)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert5_397_080_1" & variable_normalized=="do_timing_reorder_clean", 60)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert5_403_064_1" & variable_normalized=="do_timing_reorder_clean", 60)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert5_403_099_1" & variable_normalized=="do_timing_reorder_clean", 53)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_115_006_1" & variable_normalized=="do_timing_reorder_clean", 4)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_115_006_2" & variable_normalized=="do_timing_reorder_clean", 4)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_119_031_1" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_123_010_1" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_123_011_1" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_149_017_1" & variable_normalized=="do_timing_reorder_clean", 11)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_149_018_1" & variable_normalized=="do_timing_reorder_clean", 12)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_152_029_1" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_152_029_2" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_152_031_1" & variable_normalized=="do_timing_reorder_clean", 22)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_342_013_2" & variable_normalized=="do_timing_reorder_clean", 9)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_186_018_1" & variable_normalized=="do_timing_reorder_clean", 15)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_233_009_1" & variable_normalized=="do_timing_reorder_clean", 3)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_240_009_1" & variable_normalized=="do_timing_reorder_clean", 14)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_241_015_1" & variable_normalized=="do_timing_reorder_clean", 13)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_252_020_1" & variable_normalized=="do_timing_reorder_clean", 7)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_256_026_1" & variable_normalized=="do_timing_reorder_clean", 16)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_264_025_1" & variable_normalized=="do_timing_reorder_clean", 16)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_264_026_1" & variable_normalized=="do_timing_reorder_clean", 16)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_299_020_1" & variable_normalized=="do_timing_reorder_clean", 18)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_330_015_1" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_330_015_2" & variable_normalized=="do_timing_reorder_clean", 8)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_348_042_1" & variable_normalized=="do_timing_reorder_clean", 25)) %>%
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="undergrada31ef865_410_025_1" & variable_normalized=="do_timing_reorder_clean", 24))
-
-```
-
-```{r}
-icb_long_think_event <- icb_long_clean %>% 
-  # get do_timing_reorder and do_timing variables
-  dplyr::filter(variable=="think_sentence_events") %>% 
-  dplyr::mutate(value = trimws(stringr::str_remove(value, "sentence "))) %>% 
-  # dplyr::mutate(value = if(value %in% c("act in this sentence", "speech in this sentence")), raw_sentence_number_int, value) %>%
-  dplyr::rename(think_sent_raw = value) %>% 
-  # merge in "crisisno_crisis_version""
-  dplyr::left_join(alignment_key %>% 
-                     dplyr::select(email_id, crisno, sentence, crisisno_crisis_version)) %>% 
-  dplyr::left_join(alignment_key %>% 
-                     dplyr::select(-sentence) %>%
-                     dplyr::rename(think_sent_raw = raw_sentence_number_int, 
-                                   think_sent_aligned = sentence_number_int_aligned) %>% 
-                     dplyr::mutate(think_sent_raw = trimws(as.character(think_sent_raw)))) %>%
-  # dplyr::filter(prior_sent_raw != 1) %>% # drop if prior_sentence==1 which seems to be GUI default
-  dplyr::rename(value = think_sent_raw) %>% 
-  dplyr::mutate(value = as.character(value)) %>% 
-  dplyr::mutate(variable_normalized = "think_sentence_events_clean") %>% 
-  dplyr::mutate(value_normalized = ifelse(value %in% c("act in this sentence", "speech in this sentence"), 
-                                          sentence_number_int_aligned, think_sent_aligned)) %>%
-  dplyr::mutate(value_normalized = as.character(value_normalized)) %>%
-  dplyr::select(-c(crisisno_crisis_version, think_sent_aligned)) %>% 
-  # clean up some NAs
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_392_017_1" & variable_normalized=="think_sentence_events", 16)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert3_007_007_1" & variable_normalized=="think_sentence_events", 7)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_173_012_1" & variable_normalized=="think_sentence_events", 11)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert4_203_004_1" & variable_normalized=="think_sentence_events", 3)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="expert2_253_012_1" & variable_normalized=="think_sentence_events", 9)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="undergrad32faf6f6_004_016_1" & variable_normalized=="think_sentence_events", 15)) %>% 
-  dplyr::mutate(value_normalized=replace(value_normalized, email_crisis_sent_event=="undergraddb11c211_092_008_1" & variable_normalized=="think_sentence_events", 6))
-```
-
-```{r}
-icb_long_clean  <- dplyr::bind_rows(
-  icb_long_clean %>% 
-    #dplyr::mutate(event_number_int = as.character(event_number_int)) %>% 
-    dplyr::filter(variable!="do_timing_reorder") %>% 
-    dplyr::filter(variable!="think_sentence_events"),
-  icb_long_preceding_event,
-  icb_long_think_event
-)
-
-rm(icb_long_preceding_event, icb_long_think_event)
-
-```
-
-```{r}
-icb_long_clean <- icb_long_clean %>% 
-      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable, variable_normalized))) %>%
-      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value, value_normalized)))
-```
-
 Join in google sheet of tree simplification and drop variables that we replace
 
-```{r message=FALSE}
+```{r message=FALSE, eval=F}
 target_file <- paste0(here::here(),"/replication_data/in/icbe_litreview_trees_sentences.xlsx")
@@
 
-```{r}
-
-drops <- c(
-'interact_escalate',
-'interact_deescalate',
-'act_uncooperative',
-'act_deescalate',
-'act_cooperative',
-'do_interact_kind',
-'do_kind',
-'interact_decreasecoop',
-'interact_increasecoop',
-'interact_deescalate',
-'act_escalate',
-'condition_interact_deescalate',
-'condition_interact_escalate',
-'condition_interact_increasecoop',
-'condition_interact_decreasecoop',
-'condition_act_cooperative',
-'condition_act_deescalate',
-'condition_act_escalate',
-'condition_act_uncooperative',
-'do_interact_kind',
-'interact_escalate',
-'sayintkind',
-'sayintkind_react',
-'interact_deescalate',
-'interact_decreasecoop',
-'act_escalate',
-'act_uncooperative',
-'act_deescalate',
-'act_cooperative',
-'act_descalate', 
-'act_escalate',
-'act_uncooperative',
-'interact_decreasecoop',
-'interact_descalate',
-'interact_deescalate', #there's a mispelling here
-'interact_escalate',
-'interact_increasecoop',
-'thinkkind',
-'sayintkind'
-) %>% unique()
-
+```{r, eval=F}
 icb_long_clean2 <- icb_long_clean %>% 
   dplyr::distinct() %>%
+  dplyr::mutate(variable_normalized= variable_normalized %>%
+                  stringr::str_replace("interact_location_other_clean","interact_location_defined")) %>%
+  dplyr::mutate(variable_normalized= variable_normalized %>%
+                  stringr::str_replace("condition_interact_location_other","condition_interact_location_defined")) %>% 
   dplyr::mutate(variable_normalized= variable_normalized %>%
@@
 
+# give every entry its own event_type var to control merging (avoid merging in details for actions that were 'thought about' or 'said')
+# confirm that no email_crisis_sent_event have more than one event_type entry
+icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
+  dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
+  dplyr::rename(event_type=value_normalized) %>% dplyr::count(email_crisis_sent_event) %>% dplyr::filter(n>1)
+
+icb_long_clean2 <- icb_long_clean2 %>% 
+  dplyr::left_join(icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
+                     dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
+                     dplyr::rename(event_type=value_normalized))
+
+# icb_long_clean %>% dplyr::select(variable_normalized) %>% table()
+# 
+# icb_long_clean %>% dplyr::filter(variable_normalized=="interact_location") %>% dplyr::select(value_normalized) %>% table()
+# icb_long_clean %>% dplyr::filter(variable_normalized=="condition_interact_location_other") %>% dplyr::select(value_normalized) %>% table()
+# 
+# icb_long_clean2 %>% dplyr::filter(variable_normalized=="interact_location") %>% dplyr::select(value_normalized) %>% table()
+# icb_long_clean2 %>% dplyr::filter(variable_normalized=="interact_location_defined") %>% dplyr::select(value_normalized) %>% table()
+# 
+# temp <- icb_wide_aligned_raw %>% dplyr::select("do_actor_a", "do_actor_b", "condition_interact_location", "condition_interact_location_other") %>% dplyr::filter(!is.na(condition_interact_location_other))
+
+```
+
+```{r, eval=F}
 temp_wide <- icb_long_clean2 %>%
-             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
+             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, event_type, variable_normalized, value_normalized) %>%
              dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
@@
 ```
-
-Save icb_long_clean!
-```{r}
-saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
-
-```
-
-# create wide file
-
-```{r}
-
-listtostring <- function(x){
-  x %>% unlist() %>% paste(., collapse="; ")
-}
-
-paste_rex <- function(x){ x %>% sort() %>% paste( sep=";", collapse=";")   } 
-icb_wide_clean <- icb_long_clean_final %>% 
-  #dplyr::select(-variable,-value) %>%
-  tidyr::pivot_wider(names_from=variable_normalized, values_from=value_normalized, values_fn=paste_rex)  %>%
-
-  dplyr::filter(!(event_number_int==0 & sentence_events %in% c('1','2','3'))) #It does not appear that we ever need an e0 if number of events is greater than zero
-  #There's also a weird situation where they sometimes created events without tagging it as a think, do,say
-
-saveRDS(icb_wide_clean, paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
-
-```

### 2022-07-17 replication_data/rmd/03_aggregation.Rmd
v1.1

@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds")) %>%
+                  filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
+                  select(-sentence, -sentence_clean, -varname, -value, -status) %>% 
+                  distinct()
+dim(icb_long_clean)  
+#icb_long_clean %>% count(varname_normalized) %>% arrange(desc(n)) %>% View()
+
+coders_per_crisis <- icb_long_clean %>% dplyr::select(crisno,  email_id, expert) %>% distinct() #%>% dplyr::count(crisno)
+coders_per_crisis_tally <- coders_per_crisis %>% mutate(novice=expert==0) %>% group_by(crisno) %>% summarise( expert=sum(expert==1), novice=sum(novice==1) )
+crisis_sentences_per_coder <- icb_long_clean %>% filter(varname_normalized %>% str_detect("sentence_events")) %>% dplyr::count(email_id, crisno)
 
@@
 #Choose the most common sentence for each
-sentences <- icb_long_clean %>% dplyr::count(crisno,sentence_number_int_aligned,sentence) %>% arrange(crisno, sentence_number_int_aligned, desc(n)) %>% 
-  group_by(crisno, sentence_number_int_aligned) %>% filter(row_number()==1) %>% dplyr::select(-n)
+sentences <- icb_long_clean %>% dplyr::count(crisno,sentence_number_int_aligned,sentence_span_text) %>% arrange(crisno, sentence_number_int_aligned, desc(n)) %>% 
+              group_by(crisno, sentence_number_int_aligned) %>% filter(row_number()==1) %>% dplyr::select(-n) %>%
+              ungroup()
+
+crises <- icb_long_clean %>% arrange(crisno,sentence_number_int_aligned) %>% dplyr::select(input_crisis, crisno) %>% group_by(crisno) %>% filter(row_number()==1) %>% ungroup()
 
@@
 
-Unanimous exact agreement- every expert coder chose the exact same options across all events for that question
-Majority exact agreement- at least 2/3 of expert coders chose exactly the same options across all event for that question
-This aggregates across conditions too
+This is a calculation of token level agreement. It is the first part of Algorithm 1.
 
 ```{r}
+
+coders_per_crisis <- icb_long_clean %>% 
+                              dplyr::select(crisno, sentence_number_int_aligned, email_id) %>%
+                              distinct() %>%
+                              count(crisno,email_id) %>% #just confirming that each coder put something for at least five sentences ( they all did)
+                              mutate(expert=email_id %>% str_detect('expert') %>% as.integer() )  %>%
+                              count(crisno, expert) %>%
+                              pivot_wider(id_cols=crisno, values_from=n, names_from=expert) %>%
+                              janitor::clean_names() %>% 
+                              mutate(x0= x0 %>% replace_na(0) ) %>%
+                              mutate(x1= x1 %>% replace_na(0) ) %>%
+                              rename(coders_novice=x0, coders_expert=x1)
+
+votes_per_crisis_sentence <- icb_long_clean %>%
+                            mutate(expert=email_id %>% str_detect('expert') %>% as.integer() ) %>% #redundant now
+                            #there are dupes here and I don't know why
+                            dplyr::select(crisno,sentence_number_int_aligned, sentence_span_text, varname_normalized, value_normalized, expert, email_id) %>% distinct() %>%
+                            count(crisno,sentence_number_int_aligned, sentence_span_text, varname_normalized, value_normalized, expert) %>%
+                            pivot_wider(id_cols=c(crisno,sentence_number_int_aligned, sentence_span_text, varname_normalized, value_normalized), values_from=n, names_from=expert) %>%
+                            janitor::clean_names() %>% 
+                            mutate(x0= x0 %>% replace_na(0) ) %>%
+                            mutate(x1= x1 %>% replace_na(0) ) %>%
+                            rename(votes_novice=x0, votes_expert=x1) %>%
+                            left_join(coders_per_crisis) %>%
+                            mutate(percent_expert= (votes_expert/coders_expert) %>% replace_na(0)) %>%
+                            mutate(percent_novice= (votes_novice/coders_novice) %>% replace_na(0)) %>%
+                            mutate(votes_total=votes_expert+votes_novice) %>%
+                            mutate(algo1_part1 = as.numeric(
+                                     percent_expert>=0.5  #majority of experts
+                                   )) %>%
+                            mutate(algo1_part2 = as.numeric(
+                                     votes_expert>0 & #At least one expert
+                                     percent_novice>=0.5 #and majority of novices
+                                   )) %>%
+                            #If still no majority pick the expert aproved option with the most total votes
+                            group_by(crisno,sentence_number_int_aligned, sentence_span_text, varname_normalized) %>%
+                                mutate(algo1_part3 = as.numeric(  max(algo1_part1)==0 & 
+                                                                    max(algo1_part2)==0 &
+                                                                    votes_expert>0 & #at least one expert
+                                                                    votes_total==max(votes_total) & #
+                                                                    votes_total>1 #require at least 2 votes this is important
+                                                                  ) ) %>% #no options were picked yet and this one has the most votes (at least 1 expert)
+                            ungroup() %>%
+                            mutate(algo1 = as.numeric( algo1_part1 | algo1_part2 | algo1_part3) )  %>%
+                            arrange(crisno,sentence_number_int_aligned, sentence_span_text, varname_normalized, desc(algo1))
+
+table(votes_per_crisis_sentence$algo1) #215619 #281663 #148732 #137153 #149,102
+
+```
+
+# Accepted Events
+
+This is the second part of Algorithm 1.
+
+```{r}
+
+icb_long_clean_accepted <- icb_long_clean %>% 
+                           left_join(votes_per_crisis_sentence %>% dplyr::select(crisno,sentence_number_int_aligned,varname_normalized,value_normalized,algo1) ) %>%
+                           filter(algo1==1) %>% 
+                           filter(email_id %>% str_detect('expert')) #we already require at least one expert vote
+dim(icb_long_clean_accepted) #200700 accepted tokens
+#Now we need to collect the surviving tokens by the events they 
+paste_rex=function(x) { x %>% str_split(";") %>% unlist()  %>% unique() %>% sort() %>% paste(collapse=";")}
+icb_events <- icb_long_clean_accepted %>%
+              dplyr::select(email_id, crisno, sentence_number_int_aligned, event_number_int, varname_normalized, value_normalized) %>% distinct() %>%
+              arrange(email_id, crisno, sentence_number_int_aligned, event_number_int, varname_normalized, value_normalized) %>% 
+              pivot_wider(id_cols=c( email_id, crisno, sentence_number_int_aligned, event_number_int), names_from=varname_normalized, values_from=value_normalized, values_fn=paste_rex) %>% #within a single event from that coder
+              filter(!is.na(do_actor_a)    | 
+                     !is.na(do_actor_b)    | 
+                     !is.na(think_actor_a) | 
+                     !is.na(say_actor_a)   | 
+                     !is.na(say_actor_b) #remember to go back and collapse the others again
+              ) %>%
+              mutate(do_actor_b  = ifelse( do_actor_a==do_actor_b, '', do_actor_b ) ) %>% #There was a degenerate option to put the same actor in both A and B if it was acting alone
+              mutate(say_actor_b = ifelse( say_actor_a==say_actor_b, '', say_actor_b ) ) %>%
+              pivot_longer(cols=-c(email_id, crisno, sentence_number_int_aligned, event_number_int, think_actor_a,say_actor_a,say_actor_b, do_actor_a,do_actor_b), 
+                           names_to="varname_normalized",
+                           values_to="value_normalized",
+                           values_transform=as.character) %>%
+              dplyr::select(-email_id,-event_number_int) %>% #remove the person and event info
+              pivot_wider(id_cols=c(  crisno, sentence_number_int_aligned, do_actor_a, do_actor_b, think_actor_a, say_actor_a ,say_actor_b),
+                          names_from=varname_normalized, values_from=value_normalized, values_fn=paste_rex) %>% #collapse back down again
+              full_join(sentences) %>%
+              left_join(crises %>% rename(crisis_text=input_crisis) ) %>%
+              relocate(sentence_span_text, .after = sentence_number_int_aligned) %>%
+              relocate(crisis_text, .after = crisno) %>% 
+              arrange( crisno, sentence_number_int_aligned)
+
+dim(icb_events) #15465 #17625 #18372 #17678 #14264
+
+```
+
+## Events long
+
+```{r}
+
+#Qcodes
+Qcodes <- icb_long_clean %>% dplyr::select(crisno, varname_normalized, value_normalized, value_qcode) %>% distinct() %>% filter(!is.na(value_qcode))
+
+#This loses the structure of the diad, we need a new notion of an actor set
+icb_events_long <- icb_events %>%
+                   mutate(actor_set = paste0( think_actor_a,";",say_actor_a,";",say_actor_b,";",do_actor_a,";",do_actor_b)) %>%
+                   pivot_longer(cols=-c(crisno, crisis_text, sentence_number_int_aligned, sentence_span_text, actor_set), 
+                                 names_to="varname_normalized",
+                                 values_to="value_normalized",
+                                 values_transform=as.character) %>%
+                   filter(!is.na(value_normalized)) %>% 
+                   mutate(value_normalized = strsplit(as.character(value_normalized), ";")) %>% 
+                   unnest(value_normalized) %>% 
+                   distinct() %>% 
+                   left_join(Qcodes)
+
+```
+
+```{r, eval=T}
+
+saveRDS(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds")) 
+readr::write_tsv(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.tsv"))
+
+saveRDS(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.Rds")) 
+readr::write_tsv(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.tsv"))
+
+saveRDS(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
+readr::write_tsv(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.tsv"))
+
+saveRDS(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
+readr::write_tsv(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.tsv"))
+
+```
+
+# Refactored Below
+
+```{r, eval=F}
+
 my.max <- function(x) ifelse( !all(is.na(x)), max(x, na.rm=T), NA)
@@
 rex_paste <- function(x){ paste0(x  %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
-
+temp_long_list <- list()
 for(crisis in unique(icb_long_clean$crisno)){
@@
 
- if(exists("temp_long")){
-   temp_long <- dplyr::bind_rows(temp_long, temp_long_partial)
-   }else{
-     temp_long <- temp_long_partial
+  temp_long_list[[as.character(crisis)]] <- temp_long_partial
 }
 
+temp_long <- dplyr::bind_rows(temp_long_list)
+#table(temp_long$crisno) %>% length() 475
 # for debugging
@@
 
-}
 ```
 
-```{r}
+```{r, eval=F}
 
@@
                 mutate(
-                       expert_majority=(selected_by_experts>(total_coders_expert/2) & selected_by_experts>=2) %>% as.integer() ,
+                       expert_majority=(selected_by_experts>(total_coders_expert/2) ) %>% as.integer() , #& selected_by_experts>=2 there are 31 crises with just 1 expert coder
                        undergrad_majority= (selected_by_undergrads > (total_coders_undergrad/2) & total_coders_undergrad>=2 ) %>% as.integer()  ,
@@
 
-# Agreed
-
-```{r}
+```{r, eval=F}
 
 #this has to be temp because we actually do a lot of filtering at the wide stage and so need to go back to long
-#What we could do is say if there's
 codings_long_agreement <- codings_long %>%
-
+                          #If picked by a majority of experts then in automatically
                           mutate(keep_majority_expert= 
-                                    (selected_by_experts>=2 & #selected by at least two experts
-                                     expert_majority==1)   %>% as.numeric()
+                                    (expert_majority==1)   %>% as.numeric() #selected_by_experts>=2 & #selected by a majority of experts
                            ) %>%
+                           #If picked by any expert and a majority of undergrads then keep
                            mutate(keep_majority_undergrad= (selected_by_experts>=1 & expert_majority==0 & undergrad_majority==1)  %>% as.numeric() ) %>%
-
+                           #if either majority keep
                            mutate(keep_majority= (keep_majority_expert | keep_majority_undergrad) %>% as.integer() ) %>%
@@
                            ungroup() %>%
+                           #If a question still doesn't achieve a majority then pick the answer that just recieved the most votes (and at least 1 expert vote)
                            mutate(keep_leftstanding = (keep_majority_max==0 & #Wasn't picked by a majority
@@
 
-```{r}
+```{r, eval=F}
 
@@
 
-# Codings wide agree labeled
-
-```{r}
+```{r, eval=F}
 
@@
 ```
-
-```{r, eval=T}
-
-saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds")) 
-readr::write_tsv(codings_long_agreement, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.tsv"))
-
-saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreed.Rds")) 
-readr::write_tsv(codings_long_agreed, paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreed.tsv"))
-
-saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/ICBe_V1_wide_agreed.Rds")) 
-readr::write_tsv(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/ICBe_V1_wide_agreed.tsv"))
-
-```

### 2022-07-17 replication_data/rmd/04_validation.Rmd
v1.1

---
title: "04_validation"
output:
  html_document:
    df_print: paged
  toc: yes
editor_options:
  chunk_output_type: inline
---

## R Markdown

```{r, eval=F }

ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
dim(ICBe_events_agreed)

icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
dim(icb_events_long)

country_flags <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/countries.csv" %>% read_csv(col_names=F)
library(WikidataR)# install.packages("WikidataR","WikidataQueryServiceR")
#https://commons.wikimedia.org/wiki/File:Flag_of_the_United_Nations.svg
UN <- get_item("Q1065")[[1]]$claims$P41

library(countrycode)
flag_codes1 <- 
  bind_rows(
    icb_events_long %>%
    filter(varname_normalized %>% str_detect("actor")) %>%
    dplyr::select(value_normalized, value_qcode) %>%
    distinct() ,

    actor_translator %>% mutate(value_normalized=coalesce(QCode_name,ICEWS_Actor.Name , ICEWS_Country, COWname , UCDPname )) %>% dplyr::select(value_normalized, value_qcode=QCode) %>% distinct()
  ) %>% 
  filter(!duplicated(value_qcode)) %>%
  rowwise() %>%
  mutate(qcode_n= (value_qcode %>% str_split(';'))[[1]] %>% length()) %>%
  filter(qcode_n==1) %>%
  left_join(country_flags %>% dplyr::select(value_normalized=X1, country_code2digit1=X3) ) %>% 
  left_join(country_flags %>% dplyr::select(value_normalized=X2, country_code2digit2=X3) ) %>% 
  mutate(country_code2digit3=value_normalized %>% countrycode::countrycode( origin = 'country.name', destination = 'iso2c')) %>%
  mutate(country_code_iso3c=value_normalized %>% countrycode::countrycode( origin = 'country.name', destination = 'iso3c')) %>%
  mutate(unicode_symbol=value_normalized %>% countrycode::countrycode( origin = 'country.name', destination = 'unicode.symbol')) %>%
  mutate(country_code2digit = coalesce(country_code2digit1,country_code2digit2, country_code2digit3))

flag_codes1$wikidata_flag <- NA
flag_codes1$wikidata_iso3c <- NA

for(i in 1:nrow(flag_codes1)){
  if(!is.na(flag_codes1$wikidata_flag[i])){next}
  flag <- NULL
  iso3c <- NULL
  qcode <- str_split(flag_codes1$value_qcode[i] , ";")[[1]] %>% trimws()
  if(length(qcode)>1){next} #multi qcode rows are bad
  print(qcode)
  try({
    item <- get_item(qcode)[[1]]
    try({
      flag <- item$claims$P41$mainsnak$datavalue$value[1]
      if(class(flag)=="character"){
        flag_codes1$wikidata_flag[i]<-flag
      }
    })
    try({
      iso3c <- item$claims$P984$mainsnak$datavalue$value[1]
      if(class(iso3c)=="character"){
        flag_codes1$wikidata_iso3c[i]<-iso3c
      }
    })
  })
}

library(rvest)
library(jsonlite)
flag_codes1$wikidata_flag_url <- "https://commons.wikimedia.org/wiki/File:" %>% paste0(flag_codes1$wikidata_flag)
flag_codes1$wikidata_flag_url[is.na(flag_codes1$wikidata_flag)]<- NA
flag_codes1$wikidata_flag_url_file <- NA

#which(flag_codes1$value_qcode=="Q347")
for(i in 1:nrow(flag_codes1)){
  print(i)
  if(is.na(flag_codes1$wikidata_flag_url[i])){ next }
  destfile_svg <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/{flag_codes1$value_qcode[i]}.svg")
  destfile_png <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/{flag_codes1$value_qcode[i]}.png")

  if(!file.exists(destfile_svg) & !file.exists(destfile_png)){
    try({
      html <- flag_codes1$wikidata_flag_url[i] %>% str_replace_all(" ","_") %>% read_html()
      links <- html   %>% html_nodes("a") %>% html_attr("href") 
      df = data.frame(link=links) %>% distinct()
      image_url <- df %>% filter(link %>% str_detect("^http.*?svg$")) %>% filter(row_number()==1) %>% pull(link)
      if(length(image_url)!=0){
              flag_codes1$wikidata_flag_url_file[i] <- image_url
              download.file(url=image_url, destfile=destfile_svg)
      } else {
              image_url <- df %>% filter(link %>% str_detect("^http.*?png$")) %>% filter(row_number()==1) %>% pull(link)
              flag_codes1$wikidata_flag_url_file[i] <- image_url
              download.file(url=image_url, destfile=destfile_png)
      }
    })
  } else {
    print("Already exists")
  }
}

flag_folder <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/"
flag_files <- list.files(path = flag_folder, pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

flag_files_short <- flag_files %>% str_replace("\\..*$","")
flag_codes1$file_exists <- flag_codes1$value_qcode %in% flag_files_short

```

## Resave Small Flags

```{r}

library(tidyverse)
library(magick) #switching to magick which handles transparency correctly
library(imager); #install.packages("imager")
flag_folder <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/"
flag_folder_small <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"
#20x16 pixels
file="Q15180"

flag_files <- list.files(path = flag_folder, pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
for( file in flag_files){

  file_short <- NULL
  file_short <- file %>% str_replace("\\..*$","")
  outfile <- NULL
  outfile <- paste0(flag_folder_small, file_short, ".png")
  if(!file.exists(outfile)){
    print(file)
    im <- NULL
    infile <- NULL
    infile <- paste0(flag_folder, file)
    try({ #nevermind apparently if you convert too many files in a row image magick runs out of some internal memory "session: cache resources exhausted "
      im <- image_read(infile) #load.image(infile)
      im_small <- NULL
      im_small <- im %>% image_scale("20x16") #resize(im, 20, 16)
      im_small %>% image_write(path=outfile, format = "png") #save.image(outfile)
      next
    })
    try({
      im <- load.image(infile)
      im_small <- NULL
      im_small <- resize(im, 20, 16)
      im_small %>% save.image(outfile)
    })
  }
}

```

## Including Plots

```{r pressure, echo=FALSE}

ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
dim(ICBe_events_agreed)

icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
dim(icb_events_long)

ICBe_events_agreed$interact_forces %>% unique()
ICBe_events_agreed$interact_fatalities %>% unique()

ICBe_events_agreed$interact_domains %>% unique()
ICBe_events_agreed$interact_territory %>% unique()
ICBe_events_agreed$interact_geoscope  %>% unique()

#![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/cub.png)

paste_vars <- c("think_actor_a","thinkkind",
"say_actor_a", "sayintkind", "say_actor_b",
"condition",
"do_actor_a" ,               
#"do_kind", "do_interact_kind" , #leaving this out because it rarely helps
"interact_increasecoop" , "interact_decreasecoop" ,  "interact_escalate"  , "interact_deescalate" , "act_cooperative","act_deescalate","act_escalate","act_uncooperative"   ,           
"do_actor_b",
"interact_units",
"interact_domains",
"interact_geoscope",
"interact_territory",
"interact_forces",
"interact_fatalities",
"consequence",
"condition_do_actor_a" ,               
#"condition_do_kind", "condition_do_interact_kind" , 
"condition_interact_increasecoop" , "condition_interact_decreasecoop" ,  "condition_interact_escalate"  , "condition_interact_deescalate" , "condition_act_cooperative","condition_act_deescalate","condition_act_escalate","condition_act_uncooperative"   ,           
"condition_do_actor_b",
"condition_interact_units",
"condition_interact_domains",
"condition_interact_geoscope",
"condition_interact_territory",
"condition_interact_forces",
"condition_interact_fatalities"
)

#We are going to exclude from descriptions common and not particularly informative values "country" "no clear change"
values_exclude <- c('country','no clear change',"none")
flag_files_small_short <- list.files(path = flag_folder, pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE) %>% str_replace("\\..*$","")

#"individuals", "hundreds","thousands","tens of thousands", "hundreds of thousands"

icb_events_long_markdown <- icb_events_long %>%
                              filter(varname_normalized %in% paste_vars) %>%
                              mutate(varname_normalized = varname_normalized %>% factor(levels=paste_vars)) %>%
                              arrange(crisno, sentence_number_int_aligned, actor_set, varname_normalized, value_normalized, value_qcode) %>%
                              filter(!value_normalized %in% values_exclude) %>%
                              rowwise() %>%
                                mutate( value_markdown =  glue::glue("![]({flag_folder_small}/{value_qcode}.png)") )  %>% 
                                mutate( value_markdown = ifelse(is.na(value_qcode) | !value_qcode %in%  flag_files_small_short ,value_normalized, value_markdown ) ) %>% #if the q code is missing or the image is missing fall back to text
                                mutate(value_markdown= ifelse(value_normalized=="individuals",value_markdown %>% paste0("1s") ,value_markdown )) %>%
                                mutate(value_markdown= ifelse(value_normalized=="tens",value_markdown %>% paste0("10s"),value_markdown)) %>%
                                mutate(value_markdown= ifelse(value_normalized=="hundreds",value_markdown %>% paste0("100s"),value_markdown)) %>%
                                mutate(value_markdown= ifelse(value_normalized=="thousands",value_markdown %>% paste0("1ks"),value_markdown)) %>%
                                mutate(value_markdown= ifelse(value_normalized=="tens of thousands",value_markdown %>% paste0("10ks"),value_markdown)) %>%
                                mutate(value_markdown= ifelse(value_normalized=="hundreds of thousands",value_markdown %>% paste0("100ks"),value_markdown)) %>%
                              ungroup()

#Make a sentence level markdown summary                                      
icb_events_long_narratives_sentences <- icb_events_long_markdown %>%
                              group_by(crisno, sentence_number_int_aligned, sentence_span_text, actor_set, varname_normalized) %>%
                                summarise( 
                                    value_markdown = paste0(value_markdown , collapse=";")
                                  )  %>%
                              mutate(value_markdown = ifelse(varname_normalized=="think_actor_a", paste0("- ", value_markdown), value_markdown ) ) %>%
                              mutate(value_markdown = ifelse(varname_normalized=="say_actor_a", paste0(" - ", value_markdown), value_markdown ) ) %>%
                              mutate(value_markdown = ifelse(varname_normalized=="do_actor_a", paste0(" - ", value_markdown), value_markdown ) ) %>%
                              mutate(value_markdown = ifelse(varname_normalized=="consequence", paste0(" -C- ", value_markdown), value_markdown ) ) %>%
                              group_by(crisno, sentence_number_int_aligned,sentence_span_text,  actor_set) %>%
                                filter(is.na(lag(value_markdown)) | (value_markdown!=lag(value_markdown))) %>% #with the dashes added above it should allow us to remove dupes in the middle
                                summarise( 
                                    value_markdown = paste0(value_markdown, collapse=" ")
                                  ) %>% ungroup()

ICBe_events_agreed_markdown <- ICBe_events_agreed %>% left_join(icb_events_long_narratives_sentences)

ft <- ICBe_events_agreed_markdown %>%
      filter(crisno==196) %>%
      group_by(crisno, sentence_number_int_aligned) %>%
        filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
      ungroup() %>%
      mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
      mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
      mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text)) %>%
      dplyr::select(C=crisno, S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown) %>%
      #head(100) %>%
      flextable::as_flextable() %>%
      flextable::width( j = 1, width=0.25)  %>% 
      flextable::width( j = 2, width=0.25)  %>% 
      flextable::width( j = 3, width=5.0)  %>% 
      flextable::width( j = 4, width=5.0)  %>% 
      flextable::fontsize(size = 9, part = "all") %>%
      ftExtra::colformat_md(j = 4, part="body")
ft

#Make a narrative level markdown summary
icb_events_long_narratives <- icb_events_long_markdown %>%
                              #filter(crisno==196) %>%
                              group_by(crisno, varname_normalized) %>%
                                summarise( 
                                    value_markdown = paste0(value_markdown %>% sort() %>% unique() %>% trimws(), collapse=";") %>% trimws()
                                  )  %>%
                              #mutate(value_markdown = ifelse(varname_normalized=="think_actor_a", paste0("", value_markdown), value_markdown ) ) %>%
                              #mutate(value_markdown = ifelse(varname_normalized=="say_actor_a", paste0("BREAK", value_markdown), value_markdown ) ) %>%
                              #mutate(value_markdown = ifelse(varname_normalized=="do_actor_a", paste0("BREAK", value_markdown), value_markdown ) ) %>%
                              #mutate(value_markdown = ifelse(varname_normalized=="interact_units", paste0("BREAK", value_markdown), value_markdown ) ) %>%
                              #mutate(value_markdown = ifelse(varname_normalized=="consequence", paste0("BREAK -C- ", value_markdown), value_markdown ) ) %>%
                              group_by(crisno) %>%
                              summarise( 
                                  value_markdown = paste0(value_markdown %>% trimws(), collapse=" ") %>% trimws()
                              ) %>% ungroup() #%>% 
                              #mutate(value_markdown = strsplit(as.character(value_markdown), "BREAK")) %>% 
                              #unnest(value_markdown)

icb_events_long_narratives_brokenup <- icb_events_long_markdown %>%
                                        mutate(var_group=NA) %>%
                                        mutate(var_group = ifelse(varname_normalized %>% str_detect("actor"),"actors",var_group)) %>%
                                        mutate(var_group = ifelse(varname_normalized %>% str_detect("coop|escalate"),"act",var_group)) %>%
                                        mutate(var_group = ifelse(varname_normalized %>% str_detect("actor"),"actors",var_group)) %>%
                                        mutate(var_group = ifelse(varname_normalized %>% str_detect("units|domains"),"units_domains",var_group)) %>%
                                        mutate(var_group = ifelse(varname_normalized %>% str_detect("forces|fatalities"),"forces_fatalities",var_group)) %>%
                                        #filter(crisno==196) %>%
                                        group_by(crisno, var_group) %>%
                                          summarise( 
                                              value_markdown = paste0(value_markdown %>% sort() %>% unique() %>% trimws(), collapse=";") %>% trimws()
                                            )  %>%
                                        #mutate(value_markdown = ifelse(varname_normalized=="think_actor_a", paste0("", value_markdown), value_markdown ) ) %>%
                                        #mutate(value_markdown = ifelse(varname_normalized=="say_actor_a", paste0("BREAK", value_markdown), value_markdown ) ) %>%
                                        #mutate(value_markdown = ifelse(varname_normalized=="do_actor_a", paste0("BREAK", value_markdown), value_markdown ) ) %>%
                                        #mutate(value_markdown = ifelse(varname_normalized=="interact_units", paste0("BREAK", value_markdown), value_markdown ) ) %>%
                                        #mutate(value_markdown = ifelse(varname_normalized=="consequence", paste0("BREAK -C- ", value_markdown), value_markdown ) ) %>%
                                        group_by(crisno, var_group) %>%
                                        summarise( 
                                            value_markdown = paste0(value_markdown %>% trimws(), collapse=" ") %>% trimws()
                                        ) %>% ungroup()

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds")) %>%
                  filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
                  select(-sentence, -sentence_clean, -varname, -value, -status) %>% 
                  distinct()

ICBe_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds"))

icb_crises <- read_csv(file=paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) %>% janitor::clean_names() #somehow break of all things is a broken name

ICBe_crises_markdown <- ICBe_events_agreed %>%
  #filter(crisno==196) %>%
  group_by(crisno, crisis_text) %>%
  summarise(
    n_sentence_number_int_aligned  = sentence_number_int_aligned %>% unique() %>% length(),
    n_events = sum(!is.na(do_actor_a) | !is.na(say_actor_a) | !is.na(think_actor_a))
  )  %>% distinct() %>% 
  left_join(icb_crises %>% dplyr::select(crisno, yrtrig,yrterm) %>% distinct() ) %>%
  left_join( ICBe_long_agreement %>% dplyr::select(crisno,, coders_expert, coders_novice,) %>% distinct() ) %>% 
  left_join(icb_events_long_narratives_brokenup %>%
              filter(!is.na(var_group)) %>%
              pivot_wider(id_cols=crisno, names_from=var_group, values_from=value_markdown)
              ) %>%
  ungroup()

ft <- ICBe_crises_markdown %>% ungroup() %>%
      #filter(crisno %in% c(1:100) ) %>%
      dplyr::select(crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events,  coders_expert, coders_novice, actors, units_domains, forces_fatalities, act) %>%
      mutate(crisno = crisno %>% as.character() ) %>%
      mutate(yrtrig = yrtrig %>% as.character() ) %>%
      mutate(yrterm = yrterm %>% as.character() ) %>%
      #group_by(crisno, sentence_number_int_aligned) %>%
      #  filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
      #ungroup() %>%
      #mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
      #mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
      #mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text)) %>%
      #dplyr::select(C=crisno, S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown) %>%
      #head(100) %>%
      flextable::as_flextable() %>%
      flextable::set_header_labels(values = 
          list(crisno = "#",
                crisis_text = "Title",
                yrtrig = "Start",
                yrterm = "End",
                n_sentence_number_int_aligned = "#S",
                n_events = "#E",
                coders_expert = "#Exp",
                coders_novice = "#Nov"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::add_header(values = 
          list(crisno = "Crisis",
                crisis_text = "Crisis",
                yrtrig = "Years",
                yrterm = "Years",
                n_sentence_number_int_aligned = "Counts",
                n_events = "Counts",
                coders_expert = "Coders",
                coders_novice = "Coders"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::merge_h(part = "header" ) %>%
      flextable::width( j = 1, width=0.1)  %>% 
      flextable::width( j = 2, width=0.5)  %>% 
      flextable::width( j = 3, width=0.1)  %>% 
      flextable::width( j = 4, width=0.1)  %>% 
      flextable::width( j = 5, width=0.1)  %>% 
      flextable::width( j = 6, width=0.1)  %>% 
      flextable::width( j = 7, width=0.1)  %>% 
      flextable::width( j = 8, width=0.1)  %>% 
      flextable::width( j = 9, width=2.0)  %>% 
      flextable::width( j = 10, width=1.0)  %>%
      flextable::width( j = 11, width=1.0)  %>%
      flextable::width( j = 12, width=3.0)  %>%

      flextable::fontsize(size = 9, part = "all") %>%
      #flextable::merge_v(j=1:8) %>%
      ftExtra::colformat_md(j = 9:12, part="body")
ft

```

```{r, eval=T}

saveRDS(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
readr::write_tsv(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.tsv"))

saveRDS(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds")) 
readr::write_tsv(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.tsv"))

```

### 2022-07-17 replication_paper/pnas_draft/SI_appendix.Rmd
v1.1

--- 2022-03-22 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
@@
 ---
-title: |
-  | Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises
+title: "Introducing ICBe: Supplementary Information Appendix"
+
+# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
 author:
-  - Rex W. Douglass^[Department of Political Science, University of California, San Diego, CA, USA.]
-  - Thomas Leo Scherer^[Department of Political Science, University of California, San Diego, CA, USA.]
-  - J. Andrés Gannon^[Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.]
-  - Erik Gartzke^[Department of Political Science, University of California, San Diego, CA, USA.]
-  - Jon Lindsay^[School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.]
-  - Shannon Carcelli^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
-  - Jonathan Wilkenfeld^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
-  - David M. Quinn^[Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.]
-  - Catherine Aiken^[Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.]
-  - Jose Miguel Cabezas Navarro^[Society and Health Research Center, Universidad Mayor, Santiago, Chile.]
-  - Neil Lund^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
-  - Egle Murauskaite^[ICONS Project // START,  University of Maryland, College Park, MD, USA.]
-  - Diana Partridge^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
+  - name: Rex W. Douglass
+    affiliation: a,1,2
+  - name: Thomas Leo Scherer
+    affiliation: a
+  - name: J. Andrés Gannon
+    affiliation: b
+  - name: Erik Gartzke
+    affiliation: a
+  - name: Jon Lindsay
+    affiliation: c
+  - name: Shannon Carcelli
+    affiliation: d
+  - name: Jonathan Wilkenfeld
+    affiliation: d
+  - name: David M. Quinn
+    affiliation: e
+  - name: Catherine Aiken
+    affiliation: f
+  - name: Jose Miguel Cabezas Navarro
+    affiliation: g
+  - name: Neil Lund
+    affiliation: d
+  - name: Egle Murauskaite
+    affiliation: h
+  - name: Diana Partridge
+    affiliation: h
 
-date: "`r Sys.Date()`"
-abstract:  How do international crises unfold?
-We conceive of international affairs as a strategic chess game between adversaries, necessitating a systematic way to measure pieces, moves, and gambits accurately and consistently over different contexts and periods.
-We develop such a measurement strategy with an ontology of crisis actions and interactions and apply it to a high-quality corpus of crisis narratives recorded by the International Crisis Behavior (ICB) Project.
-We demonstrate that the ontology has high coverage over most of the thoughts, speech, and actions contained in these narratives and produces high inter-coder agreement when applied by human coders.
-We introduce a new crisis event dataset ICB Events (ICBe).
-We find that ICBe captures the process of a crisis with greater accuracy and granularity than other well-regarded events or crisis datasets.
-We make the data, replication material, and additional visualizations available at a companion website www.crisisevents.org.
+address:
+  - code: a
+    address: Department of Political Science, University of California, San Diego, CA, USA.
+  - code: b
+    address: Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.
+  - code: c
+    address: School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.
+  - code: d
+    address: Department of Government and Politics, University of Maryland, College Park, MD, USA.
+  - code: e
+    address: Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.
+  - code: f
+    address: Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.
+  - code: g
+    address: Society and Health Research Center, Universidad Mayor, Santiago, Chile.
+  - code: h
+    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
+  - code: i
+    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
 
-site: bookdown::bookdown_site
-keywords:
-  - International Crisis Behavior
-  - Event data
+corresponding_author:
+  code: 2
+  text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"
+
+# For footer text
+lead_author_surname: Douglass
+
 bibliography: ICBintro.bib
+csl: pnas.csl
+
+## change to true to add optional line numbering
+lineno: false
+
 output:
-  bookdown::pdf_document2:
-    toc: false
-    keep_tex: true
+  pdf_document:
+    toc: true
+    toc_depth: 2
+
+#Disabled several the caused errors
 header-includes:
@@
   - \usepackage{caption}
-  - \usepackage[capposition=top]{floatrow}
+#  - \usepackage[capposition=top]{floatrow}
   - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
@@
   - \AtBeginEnvironment{lltable}{\singlespacing}
-  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
+#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
   - \usepackage{subcaption}
@@
   - \usepackage{float}
-  - \usepackage{eso-pic,graphicx,transparent}
-  - \usepackage[perpage]{footmisc}
-
+#  - \usepackage{eso-pic,graphicx,transparent}
+#  - \usepackage[perpage]{footmisc}
+  - \usepackage[algo2e]{algorithm2e}
+  - \usepackage{algorithm}% http://ctan.org/pkg/algorithms
+  - \usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
+#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
 ---
 
-```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
-#International Crisis Behavior Events (ICBe) Dataset
-knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
+```{r, eval=T, echo=F, cache=F, results='hide', message=F}
 
-```
-
-```{r, eval=T, echo=F, cache=F}
+knitr::opts_chunk$set(echo = TRUE)
 
@@
 
-```{r, echo=F}
-#Notes
-#https://tex.stackexchange.com/questions/83440/inputenc-error-unicode-char-u8-not-set-up-for-use-with-latex
-#- \DeclareUnicodeCharacter{00A0}{ }
+# SI Figures
 
-```
-
-```{r, include=FALSE}
-# options(tinytex.verbose = TRUE)
-```
-
-```{r, echo=FALSE}
-
-`%>%` <- magrittr::`%>%`
-
-```
-
-```{r, echo=FALSE}
-
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
-codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))
-
-#Load original icb data
-
-#oh is it because break is reserved in R? lol
-#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
-icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
-
-#somehow break of all things is a b roken name
-#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
-icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))
-
-```
-
-```{r include=F}
-#Load the ICB wide codings
-
-n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
-n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
-n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
-n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
-n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()
-
-avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
-
-events_per_sentence <- icb_wide_clean %>%
-  filter(!is.na(sentence_number_int_aligned)) %>%
-  dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) %>%  #event_number_int
-  group_by(email_id,crisno,sentence_number_int_aligned) %>%
-  summarise(event_count = sum(!is.na(event_type) ) ) %>%
-  mutate_all(as.numeric) %>%
-  group_by(crisno,sentence_number_int_aligned) %>%
-  summarise(
-    event_count_min=event_count %>% min(),
-    event_count_mean=event_count %>% mean(na.rm=T),
-    event_count_max=event_count %>% max()
-  ) %>%
-  arrange(crisno,sentence_number_int_aligned)
-
-events_per_crisis <- events_per_sentence %>% group_by(crisno) %>% summarise(event_count_mean_sum=sum(event_count_mean))
-
-crisis_text_counts <- icb_wide_clean %>%
-  #mutate( input_crisis = input_crisis %>% str_replace_all("[^A-Za-z0-9 ]","") ) %>% #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
-  #https://www.google.com/search?q=R+replace+00A0&oq=R+replace+00A0&aqs=chrome..69i57j0i20i263i512j0i512l2j69i65j69i60l3.1744j0j7&sourceid=chrome&ie=UTF-8
-  dplyr::select(crisno, sentence) %>%
-  #mutate(input_crisis = input_crisis %>% stringr::str_to_title()) %>%
-  #mutate(input_crisis = input_crisis %>% stringr::str_replace_all('[0-9]$','')) %>%
-  mutate(sentence = sentence %>% stringr::str_to_lower()) %>%
-  distinct() %>%
-  #filter(!is.na(input_crisis)) %>%
-  filter(!is.na(sentence)) %>%
-  mutate(word_count=str_count(sentence, '\\w+')) %>%
-  group_by(crisno) %>%
-  summarise(
-    sentence_count=n(),
-    word_count=sum(word_count)
-  )
-
-#Even type
-
-library(sjmisc)
-event_type_per_sentence <- icb_wide_clean %>%
-  filter(!is.na(sentence_number_int_aligned)) %>%
-  dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type)  %>%
-  to_dummy(event_type, suffix = "label") %>%
-  bind_cols( icb_wide_clean %>%
-               filter(!is.na(sentence_number_int_aligned)) %>%
-               dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) ) %>%
-
-  group_by(email_id,crisno,sentence_number_int_aligned) %>%
-  summarise_if( is.numeric, sum ) %>%
-
-  group_by(crisno,sentence_number_int_aligned) %>%
-  summarise_if( is.numeric, mean, na.rm=T ) %>%
-  arrange(crisno,sentence_number_int_aligned)
-
-event_type_per_sentence_totals <- event_type_per_sentence %>% ungroup() %>% summarise_if( is.numeric, sum, na.rm=T ) %>% dplyr::select(-crisno)
-event_type_per_sentence_totals_perc <- event_type_per_sentence_totals/sum(event_type_per_sentence_totals)
-
-```
-
-```{r , message=F}
-
-icb_text <- icb_wide_clean %>% dplyr::select(crisno,sentence_number_int_aligned, sentence) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)
-
-# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)
-
-fromscratch=F
-if(fromscratch){
-
-  library("spacyr")
-  #spacy_install()
-  spacy_initialize(model = "en_core_web_sm")
-
-  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
-  parsed_consolidated <- nounphrase_consolidate(parsed)
-  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
-  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
-  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
-  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]
-
-  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
-
-  entities <- entity_extract(parsed, type = "all")
-  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
-
-} else {
-  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
-  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
-
-}
-
-entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
-entities$crisno <- icb_text$crisno[entities$doc_id_num]
-entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()
-
-target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
-
-dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
-actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
-
-unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
-unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
-
-verbs_sentence <- parsed %>% filter(pos=="VERB")
-
-verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()
-
-entities_per_sentence <- entities %>%
-  count(doc_id) %>%
-  summarise(
-    entities_per_sentence_min=min(n),
-    entities_per_sentence_mean=mean(n),
-    entities_per_sentence_max=max(n),
-  )
-
-```
-
-```{r, messages=F, results='hide', warnings=F, include=FALSE}
-
-#wordnet rdf (in tripple format)
-fromscratch=F
-
-wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )
-
-subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
-subject_headings_verbs <- subject_headings %>%
-  filter(value %>% str_detect('-v>')) %>%
-  mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>%
-  mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
-  separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
-  mutate(b = b %>% str_replace_all('\\"| \\.',""))
-
-#wordnet csv
-filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/") )
-filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)
-
-wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F #, show_col_types=F)
-)
-names(wordnet_list) <- filenames
-
-hypernyms <- wordnet_list[['wn_hyp.csv']] %>%
-  dplyr::select(a=X1,b=X2) %>%
-  left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>%
-  left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )
-
-library(igraph)
-g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)
-
-wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )
-
-wordnet_verbs <- wordnet %>% filter(tense=='v')
-
-verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
-#dim(verbs_sentence_wordnet) #227,426
-
-#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances
-
-```
-
-```{r, echo=F, messages=F, warnings=F, results='hide', eval=T}
-
-fromscratch=F
-if(fromscratch){
-  #py$sentences
-  #py$glosses
-  sentences_embeddings <- py$sentences_embeddings
-  glosses_embeddings <- py$glosses_embeddings
-
-  rownames(sentences_embeddings) <- py$sentences #[1:100]
-  rownames(glosses_embeddings) <- py$glosses #[1:100]
-  dim(glosses_embeddings)
-
-  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
-  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
-  gloss_clean <- verbs_sentence_wordnet$gloss
-  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
-  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
-  dim(glosses_embeddings_expanded)
-
-  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
-  table(condition_sentences_embeddings) #all are in it
-  sentences_clean <- verbs_sentence_wordnet$sentence
-  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
-  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
-  dim(sentences_embeddings_expanded)
-
-  #Isn't it just one minus the other?
-  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
-  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
-  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
-
-} else {
-
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(),"/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
-
-}
-
-verbs_sentence_wordnet_top <- verbs_sentence_wordnet %>% group_by(crisno, sentence_number_int_aligned, token_id) %>% filter(row_number()==1)
-verbs_sentence_wordnet_top_unique <- verbs_sentence_wordnet_top %>% ungroup() %>% dplyr::select(lemma, wordnetid,tense, gloss) %>% group_by(lemma, wordnetid,tense, gloss) %>% count() %>% arrange(desc(n))
-
-```
-
-\AddToShipoutPictureFG{
-  \AtPageCenter{% or \AtTextCenter
-    \makebox[0pt]{\rotatebox[origin=c]{45}{%
-      \scalebox{5}{\texttransparent{0.1}{Unrefereed Preprint}}%
-    }}
-  }
-}
-
-# Introduction
-
-If we record every event between countries in all of diplomacy, military conflict, and international political economy, how much information would this chronicle amount to, and how surprised would we be to see something new?
-In other words, what is the entropy of international relations?
-This record could, in principle, be unbounded.
-Still, the central conceit of political science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured.
-Massive effort is expended in social science recording these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations (IR).
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999;@brecherCrisisEscalationWar2000;@wilkenfeldInterstateCrisesViolence2000;@jamesWhatWeKnow2019;@iakhnisCrisesWorldPolitics2019].
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
-As should come as no surprise to anyone who works with event data, we find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
-The underlying fine-grained variation in international affairs that we care about is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper and therefore makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections.
-Section 2 defines the task of event extraction and proposes evaluation criteria for objectively gauging the performance of that task.
-Section 3 is a literature review that synthesizes a reasonable prior belief behind the existence of the unobserved latent concept we intend to measure and highlights existing current approaches for measuring them.
-Section 4 details our proposed method for measuring events, including the ICB Events (ICBe) dataset's ontology, coding procedures, and methodology.
-Section 5 demonstrates the internal validity of our coding exercise, the high agreement between coders and their self-reported confidence in codings, and external validity in the form of high coherence in side-by-side comparisons of source sentences and resulting codings.
-Section 6 evaluates internal validity by showing that like-codings cluster when their source sentences are mapped into semantic space.
-Section 7 offers a comparison against existing systems with case studies at the crisis level where we show both much higher recall of events that occurred and precision in what those events were and how they fit into the overall macro-level event.
-A final section concludes.
-
-<!--Section 7 moves from qualitative comparison to an objective criteria with multiple choice reading comprehension questions about each crisis drawn from the original ICB project, where we show LSTMs trained on ICBe sequences can answer substantive macro level questions but not when trained on existing event project codings.
--->
-
-# Task Definition and Ground Truth
-
-We consider the task of high-coverage information extraction from a historical episode between two or more states (e.g., the Cuban Missile Crisis).
-A historical episode is demarcated by a period of time $[T_{start}, T_{end}] \in T$ and a set of players $p \in P$.
-We posit that an episode can be divided into unique discrete events, $e \in E$, each consisting of a time period, one or more players, and a single behavior ($b \in B$) so that $e \equiv \{T_e, P_e, B_e\}$.
-The task is to produce sequences of parsimonious events that still reconstruct the important details of the original macro narrative.
-
-We take as ground truth an unusually high-quality corpus of historical narratives and quantitative codings from the International Crisis Behavior (ICB) project [@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type or an increase in the intensity of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies or case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
-The corpus is unique in IR because it is designed to be used in downstream quantitative coding projects.
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
-59].
-Each of the `r n_crisis %>% scales::comma()` crises $c \in C$ are listed with summary information in Appendix \ref{app:crises}.
-
-# Prior Beliefs and Existing State of the Art
-
-Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$ and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$.
-We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table 1.
-<!-- {tbl:litreview}  -->The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of international affairs as a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-The resulting codebook for events includes 117 different verbs and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
-
-The second axis (columns) represents sources of evidence for our concept priors and the existing state of the art.
-The first column ('Literature') maps each type of information to recent studies documenting its importance to IR.
-The second column ('ICB Corpus') documents the presence of that information in the ICB Corpus as identified by an expert review and natural language processing (Appendix \ref{app:verbs}).
-The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].
-Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
-
-```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#Lit review
-#child=c('ICBEdataset_paper_litreviewtable.Rmd')
-library(flextable)
-library(ftExtra)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))
-
-litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 4, part="body")
-
-litreview_ft %>%
-  flextable::set_caption(caption = "Prior Beliefs, State of the Art, and Existing Data") %>%
-  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
-  flextable::flextable_to_rmd()
-```
-
-# ICBe Coding and Aggregation Process
-
-Each crisis was assigned to at least two expert coders, 3 to 5 novice coders, with a third tie-breaking expert coder assigned to sentences with high disagreement.
-Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook, while novice coders were undergraduate students who engaged in classroom workshops.
-Each coder was instructed to thoroughly read and familiarize themselves with the full text.
-Once a coder felt that they understood the crisis, the coder was presented with a novel graphic user interface (GUI) that steps the coder through the narrative sentence by sentence (Figure \ref{fig:coding_gui}).
+## S1: Graphical User Interface {#app:gui}
 
@@
 \caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
-\centering{\includegraphics[width=17cm]{figures/gui_example}}
+\centering{\includegraphics[width=17cm]{../figures/gui_example}}
 \end{figure}
 
-The GUI and the ontology follow a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].
-Proceeding in order, coders chose the number of events (0-3), the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Identifying armed means triggered questions regarding force size, fatalities, domains, units, etc.
-Location and timing information is always collected, each calling for specific answers when possible and general approximations.
-Together, this process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
+## S# : Algorithm 1 {#app:algo1}
 
-A novel feature of the ontology is that thought, speech, and do behaviors can be nested into combinations so that any unique combination is reachable if warranted by the event.
-For example, a speech could be about a threat to perform a do unless another do is performed, and each can be specified in full detail.
-Likewise, a thought can be about a fully defined speech or do.
-For example, in the Cuban Missile Crisis, the United States became aware that the Soviet Union performed an interaction of placing missile sites in Cuba.
-Through compounding, we can capture what players were said to have known, learned, or felt about specific fully described behaviors.
+\begin{algorithm}[H]
+\SetAlgoLined
+\KwData{Coder-Sentence-Tokens}
+\KwResult{Sentence-Events}
+\ForEach{sentence in sentences}{
+  \ForEach{concept in concepts}{
+    \ForEach{token in tokens}{
+      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
+      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
+      \uElseIf{undergrad votes > undergrad voters/2}{accept; \tcc*[f]{Or a majority of undergrad votes}}
+    }
+    \If{sum(accepted) == 0}{
+      sort tags by votes;
+      head 1;
+      accept; \tcc*[f]{If still no tag, take one with most votes}
+    }
+  }
+  \ForEach{ActorSet in unique(ActorSets)}{
+    emit event;
+  }
+}
+\caption{Aggregating Coder-Tokens into Sentence-Events}
+\end{algorithm}
 
-```{r include=FALSE}
-
-n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
-n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
-n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
-n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
-n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()
-
-avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
-```
-
-# Internal Measurement Validity -- Intercoder Agreement and Aggregating Disagreements
-
-```{r, eval=T}
-
-means1 <- codings_long_agreement %>%
-  filter(value_normalized!='') %>%
-  filter(total_coders>1) %>% #about 9k only had one coder
-  #filter(selected_by_experts>=1) %>%
-  dplyr::select(All=selected_by_any_perc,Experts=selected_by_experts_perc,Undergraduates=selected_by_undergrads_perc) %>% summarise_all(mean, na.rm=T)
-means1_keep <- codings_long_agreement %>%
-  filter(value_normalized!='') %>%
-  filter(total_coders>1) %>% #about 9k only had one coder
-  #filter(selected_by_experts>=1) %>%
-  filter(keep==1) %>% dplyr::select(Accepted=selected_by_any_perc) %>% summarise_all(mean, na.rm=T)
-meansall <- bind_rows(means1,means1_keep) %>% mutate(x=1) %>% pivot_longer(cols=c(-x)) %>% na.omit()
-
-```
-
-One form of internal validity for these codings is high agreement between coders when applying the ontology.
-We employ three ways to evaluate and maximize agreement: (1) multiple expert and novice coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence.
-The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.).
-There were 113 coders (including 5 expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus.
-Of those, there were `r codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma()` unique sentence-tags applied by at least one coder.
-We ask how much support those possible tags received across coders, and how we should adjudicate disagreements when a tag was not chosen by every coder.
-
-We evaluate agreement as the percentage of coders who voted for a tag proposed by any coder (Figure \ref{fig:intercoderagreement}).
-The average agreement across all coders is `r means1$All %>% round(2) %>% scales::percent()` (`r means1$Experts %>% round(2) %>% scales::percent()` across experts and `r means1$Undergraduates %>% round(2) %>% scales::percent()` across undergraduates).
-A post-aggregation algorithm described below raises mean agreement considerably to `r means1_keep$Accepted %>% round(2) %>% scales::percent()`.
-Further, there is expected heterogeneity in agreement with higher agreement for coarse, high-level decisions near the root of the ontology than for fine-grained, high-dimensional concepts further down the tree.
+## S# : Intercoder Agreement {#app:intercoderagreement}
 
@@
 \caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
-\centering{\includegraphics[width=15cm]{figures/p_percent_chose_tag_by_concept.png}}
+\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_concept.png}}
 \end{figure}
 
-To understand when and why coders disagree, we required self-reported confidence scores and reasons for low confidence.
-Overall, expert coders self-reported a high level of confidence in their own codings, reporting low confidence only about 20% of the time.
-When coders reported low confidence, they cited a mismatch between the ontology and the text about half of the time ("survey doesn't fit event" 45%) and noted a lack of information or confused writing in the source text the other half ("more knowledge needed" 40%, "confusing sentence" 6%).
-In addition, we observed that individual coders exhibit nontrivial coding styles.
-Some coders are more expressive and apply multiple tags per concept, while others focus on only the single best match and differ in how many events to code.
-We also observed unintended synonymity (e.g., the same information can be framed as a threat to do something or a promise not to do something if a condition is met).
+# SI Tables
 
-This data-generating process suggests a theoretically motivated algorithm for aggregating over disagreements (Algorithm 1).
-We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of novice votes.
-If neither majority exists, we accept the one token with the most votes.
-This leaves `r codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()` (`r (codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() / codings_long_agreement %>% filter(value_normalized!='') %>% nrow()) %>% round(2) %>% scales::percent()`) accepted tokens.
-In practice, this screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
-A final step handles possible disagreement over the number of events or participants in the events.
-An event is emitted for each unique set of actors along with their surviving tags.
-
-\begin{algorithm}[H]
-\SetAlgoLined
-\KwData{Coder-Sentence-Tokens}
-\KwResult{Sentence-Events}
-\ForEach{sentence in sentences}{
-  \ForEach{concept in concepts}{
-    \ForEach{token in tokens}{
-      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
-      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
-      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
-    }
-    \If{sum(accepted) == 0}{
-      sort tags by votes;
-      head 1;
-      accept; \tcc*[f]{If still no tag, take one with most votes}
-    }
-  }
-  \ForEach{ActorSet in unique(ActorSets)}{
-    emit event;
-  }
-}
-\caption{Aggregating Coder-Tokens into Sentence-Events}
-\end{algorithm}
-
-# Sentence Level Intrinsic Evaluation
-
-Next, we ask whether codings agree with the raw source material at the sentence level.
-There are `r icb_long_clean %>% dplyr::select(sentence) %>% distinct() %>% nrow()  %>% scales::comma()` distinct sentences in the corpus.
-We start with a high-level view, taking the sentence texts and embedding them into a latent semantic space with a large language model specializing in sentence similarity, Sentence-BERT [@reimersSentenceBERTSentenceEmbeddings2019].^[We preprocess sentences to replace named entities with a generic Entity token.] Sentence embeddings are shown in Figure \ref{fig:semantic_embeddings}, disaggregated by four high-level ontology questions and each possible tag.
-Superficially, user applied tags tend to separate and cluster across semantic space in ways that suggests they are cueing on information actually provided by the text of the source sentence.
-
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-# MOVED TO figures/ICBEdataset_paper_figure_prep.Rmd
-
-# #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
-# p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/paper/figures/p_semantic_embeddings.Rds'))
-# ggsave(file=paste0(here::here(), '//paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
-```
-
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from the Sentence-BERT large language model\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=15cm]{figures/p_semantic_embeddings.png}}
-\textit{Notes:}
-\end{figure}
-
-Going further, we examine accepted tokens side-by-side with the original source material.
-We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tab:fifteensamplesentences}, 50 more in the Appendix \ref{app:50samplesentences}, and the full set online.
-To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined).
-At the sentence level, we find codings accurately reflect the key events of the text.
-Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.
-
-```{r fifteensamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}
-
-codings_wide_agreed_embeded_stratified_sample_ft_smaller <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds')) %>%
-  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15)") 
-codings_wide_agreed_embeded_stratified_sample_ft_smaller
-
-```
-
-# Episode Level Intrinsic Evaluation and Comparison to State of the Art
-
-To demonstrate validity at the level of entire episodes, we conduct two qualitative case studies; we choose the Cuban Missile Crisis for being very high stakes and widely recognized and the DRC Civil War for being particularly complicated, lengthy, and modern.
-In addition, we provide visualizations for every crisis with side-by-side comparisons across datasets on the companion website.
-Our goals are as follows: (1) establish necessary and secondary details of each crisis from secondary historical sources independent of the ICB corpus; (2) evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'; and (3) assess the recall of key events by the ICBe codings in comparison to the existing state-of-the-art datasets.
-For an event dataset to have good performance, it must both have high recall of salient facts, catching the key details and not just the trivia, and good precision, recording only events that actually occurred without distracting duplicates, miscodings, or other apparent examples of measurement error.
-
-## Case Study: Cuban Missiles Crisis (1962)
-
-The Cuban Missile Crisis occurred between the United States, the Soviet Union, and Cuba from October 16, 1962, to November 20, 1962.
-There are two critical points of context.
-First, the United States and Soviet Union enjoyed only a partial mutually assured destruction nuclear posture; the United States had accurate short-range ballistic missiles (SRBMs) in Europe and ICBMs, and the Soviet Union only had long-range, slow to arm, and relatively inaccurate ICBMs.
-Second, the United States launched the unsuccessful Bay of Pigs invasion of Cuba in April 1961.
-
-The Soviet Union and Cuba reached an agreement to stage Soviet troops, tactical nuclear weapons, and medium-range ballistic missiles (MRBMs) in Cuba in May 1962.
-U.S.
-intelligence suspected these plans in August, and their presence was later confirmed by reconnaissance flights (October 14), ultimately triggering the main arc of the crisis.
-
-The two great powers responded with both escalation and de-escalation.
-As escalations, the United States prepared a complete invasion of Cuba (October 17) and raised the nuclear alert status to DEFCON 3 (October 22) then partially to DEFCON 2 (October 24) [@brugioniEyeballEyeballStory1991].
-Likewise, the Soviet Union mobilized (October 11) and went on alert (October 22).
-As de-escalations, the United States sought a diplomatic solution and imposed a naval blockade as a non-violent military measure to buy time while preventing further Soviet reinforcements from reaching Cuba.
-The main arc concludes with an agreement by the Soviet Union to withdraw entirely from Cuba, the U.S.
-agreeing never to invade Cuba, and a clandestine agreement by the U.S.
-to retire MRBMs based in Turkey.
-
-A secondary crisis arc included several dangerous steps.
-Cuba mobilized all of its forces in preparation for an invasion (October 22).
-The United States continued aggressive violations of Cuban airspace by reconnaissance flights leading to the shooting down of a U.S.
-U-2 (October 27).
-Both sides went ahead with previously scheduled nuclear weapons tests (October 27-28).
-Finally, Cuba extended the crisis after the United States and Soviet Union reached their agreement, attempting and failing to retain Soviet bombers.
-
-The precision and overall coherence of ICBe codings are shown in a side-by-side comparison of the source narrative and codings in Appendix \ref{app:ft_sentence_table_196} and via the crisis map in Figure \ref{fig:196metromap} below.
-The entire back-and-forth of the conflict can be directly read from the timeline.
-The deployment of the missiles is recorded as the cause of the crisis for the United States.
-The United States is recorded as demanding specifically that they be removed.
-After the agreement is reached, the fulfillment of that obligation is recorded with the withdrawal of the missiles specifically and the end of the blockade.
-There are some details lost in the translation.
-The tit-for-tat details of the agreement, particularly the exchange of missiles in Turkey, are lost.
-The detail of the missiles deployed to Cuba being nuclear is not recorded at first because the narrative only refers to them as missiles initially, but is later recorded correctly when the narrative becomes explicit.
-The brief Cuban gambit to keep some weapons is present in the ICB narrative but mostly ignored by the coders as of low importance.
-In sum, the ICBe codings correctly record the cause, response, and resolution of the crisis, the correct order of moves, and the size of the stakes at play.
-In comparison crisis maps of Cameo (Phoenix) (Figure \ref{fig:196metromap_phoenix}), ICB Dyadic Codings (Figure \ref{fig:196metromap_icb}), and MIDs (Figure \ref{fig:196metromap_mids}) in Appendix \ref{app:ft_sentence_table_196} do not reflect the overlying macro story nor the specific details of interest.
-
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-# moved to figures/ICBEdataset_paper_figure_prep.Rmd
-
-# #ICBe  196
-# library(ggplot2)
-# p_metro_map_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_196.Rds'))
-# actor_colors <- p_metro_map_196$actor_colors
-# ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_196.png'),
-#        plot = p_metro_map_196 +
-#          theme(plot.margin=unit(c(0,0,0,0),"in")) +
-#          scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-#          scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
-#        width=12, height=14)
-
-```
-
-\begin{figure}[H]
-\caption{Cuban Missile Crisis according to ICBe (us) \label{fig:196metromap}}
-\centering{\includegraphics[width=19cm]{figures/p_metro_map_196.png}}
-\end{figure}
-
-Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tab:casestudy196}.
-ICBe records 8 of 10 critical events identified by the case history.
-It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors.
-It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.
-
-Only three other datasets have temporal coverage of this case.
-The Cline Historical Phoenix event dataset, which is based on Cameo dictionary codings of the New York Times and Wall Street Journal articles, only includes events that could be loosely mapped to one key turning point, the withdraw of missiles and peaceful resolution of the crisis.
-Two episode-level datasets contain temporal information on this crisis.
-A dyadic version of the original ICB dataset [@hewittDyadicProcessesInternational2003] contains information on 6 of the critical events, but describes them in terms that are too vague to reconstruct the episode.
-For example, the deployment of nuclear weapons is described only as an "external change," and the response of mobilizations for war and the blockade are a "non-violent military act." The Dyadic Militarized Interstate Disputes (MIDs) dataset [@maozDyadicMilitarizedInterstate2019] includes only two possible mappings, a 'show of troops' near the start of the crisis, and a 'yield to' near the end.
-
-```{r casestudy196, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
-CaseStudy196_ft %>%
-  flextable::set_caption("Cuban Missile Crisis ground truth and event data") %>%
-    flextable::width( j = 1, width=0.5)  %>%
-    flextable::width( j = 2, width=1.25)  %>%
-    flextable::width( j = 3, width=0.5) %>%
-    flextable::width( j = 4, width=1.1) %>%
-    flextable::width( j = 5, width=1) %>%
-    flextable::width( j = 6, width=0.75) %>%
-    flextable::width( j = 7, width=0.65)
-
-```
-
-## Case Study: DRC Civil War (1998)
-
-The civil war in the Democratic Republic of Congo (DRC), also called the Second Congo War and the Great African War, took place between 29 July 1998 and 30 July 2002 and included Angola, Chad, the DRC, Namibia, Rwanda, Uganda, and Zimbabwe.
-The necessary background for the episode is that in May 1997 Rwandan-backed rebels helped install Laurent Kabila as President of the DRC.
-The main arc of the episode begins a year later when Kabila then seeks to distance himself from Rwanda and demands that the rebels leave DRC territory (July 27, 1998).
-The main response is that they refuse and instead begin a campaign for the capital, still backed by Rwanda.
-The main arc ends with the DRC successfully defending against the campaign and reaching a peace agreement with Rwanda (July 30, 2002), Uganda (September 6, 2002), and other participants, including rebel groups (December 17, 2002) [@lansfordPoliticalHandbookWorld2021; @kisanganiHistoricalDictionaryDemocratic2010].
-
-A secondary arc concerns third-party involvement and political upheaval within the DRC.
-First, the conflict brings Uganda in on the side of Rwanda, and Angola, Namibia, Zimbabwe, and Chad in on the side of the DRC.
-Second, a United Nations-sponsored mediation produced a failed cease-fire (July 10, 1999) and a U.N.
-peacekeeping mission (MONUC) (September 30) [@lansfordPoliticalHandbookWorld2021; @kisanganiHistoricalDictionaryDemocratic2010].
-Finally, Laurent Kabila was assassinated (January 17, 2001) and was succeeded by his son Joseph Kabila (January 24), who showed a higher tolerance of U.N.
-involvement [@schererPeaceKeepsUnited2015].
-
-Precision and overall narrative coherence for the DRC case is strong, as demonstrated by side-by-side ICBe event codings in Appendix \ref{app:ft_sentence_table_426}, and shown visually as a crisis map in Figure \ref{fig:426metromap} below.
-The overall details of the crisis can be read from the timeline, particularly the invasion by Uganda and Rwanda of the DRC, several short-lived cease fires,  the shift in internal politics of the DRC due to the assassination and leadership change, a U.N.
-intervention, and final formal agreements to end the crisis.
-The role of the numerous third parties (Chad, Zimbabwe, Angola, and Namibia) who intervened on different sides is less clear.
-Similarly, the group structure of sub-national actors, who are represented as agents acting on behalf of Rwanda and Uganda, is ambiguous.
-
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-
-# moved to figures/ICBEdataset_paper_figure_prep.Rmd
-
-# #ICBe  426
-# p_metro_map_426 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_426.Rds'))
-# actor_colors <- p_metro_map_426$actor_colors
-# ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_426.png'),
-#        plot = p_metro_map_426 +
-#          theme(plot.margin=unit(c(0,0,0,0),"in")) +
-#          scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-#          scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
-#        width=12, height=14)
-
-#devtools::install_github('davidgohel/ggiraph')
-
-```
-
-\begin{figure}[H]
-\caption{DRC Civil War according to ICBe (us)  \label{fig:426metromap}}
-\centering{\includegraphics[width=19cm]{figures/p_metro_map_426.png}}
-\end{figure}
-
-By comparison, crisis maps of Cameo (Phoenix) (Figure \ref{fig:426metromap_phoenix}), ICEWS (Figure \ref{fig:426metromap_icews}), and Terrier (Figure \ref{fig:426metromap_terrier}), are unintelligible despite deduplication and heavy filtering of irrelevant or uninteresting events.
-The automated dictionary coding of news articles produces too many irrelevant events between unimportant actors or describes important events too vaguely to be used directly, and instead may only be interpretable in terms of weighted counts over time [@terechshenkoHotCollarLatent2020].
-ICB Dyadic Events (Figure \ref{fig:426metromap_icb}), MIDs Incidents (Figure \ref{fig:426metromap_mids_incidents}), and MIDs Episodes (Figure \ref{fig:426metromap_mids}) do a good job showing the start and stop of conflict and between which actors, but lose any detailed context.
-
-Recall of critical events is shown in Table \ref{tab:casestudy426} below.
-ICBe records 10 of 14 critical events identified by the case history.
-It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N.
-peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC.
-These details were under-textualized in the ICB narrative.
-Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets.
-As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events.
-Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event.
-The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila.
-The MIDs incident-level dataset includes possible coverage of 4 events.
-MIDs episode-level data incorporates possible coverage of 6 events.
-Finally, Dyadic ICB data cover 7 events.
-
-```{r casestudy426, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
-CaseStudy426_ft  %>%
-  flextable::set_caption("DRC Civil War ground truth and event data") %>%
-      width(j=1, width=0.5) %>%
-      width(j=2, width=0.75) %>%
-      width(j=3, width=0.3) %>%
-      width(j=4, width=0.65) %>%
-      width(j=5, width=1.0) %>%
-      width(j=6, width=0.5) %>%
-      width(j=7, width=0.75) %>%
-      width(j=8, width=0.75) %>%
-      width(j=9, width=0.5) %>%
-      width(j=10, width=0.5)
-
-```
-
-# Conclusion
-
-We investigated event extraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal validity (e.g.
-intercoder agreement) and external validity (i.e.
-matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes).
-Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence  by experts and novices that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
-
-#### Acknowledgments:
-We would like to thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We would like to make a special acknowledgment to Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-
-We thank the many undergraduate coders for their patience and dedication.
-Thanks to the Center for Peace and Security Studies and its membership for comments.
-Thank you to the many research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
-
-#### Author contributions (alphabetical):
-<!-- following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit -->
-Conceptualization: R.W.D., E.G., J.L.;
-Methodology: R.W.D., T.L.S.;
-Software: R.W.D.;
-Validation: R.W.D., T.L.S.;
-Formal Analysis: R.W.D., T.L.S.;
-Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;
-Data Curation: R.W.D., D.Q., T.L.S., J.W.;
-Writing - Original Draft: R.W.D., T.L.S.;
-Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
-Visualization: R.W.D., T.L.S.;
-Supervision: E.G.;
-Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
-Funding Acquisition: E.G., J.L.
-
-\newpage
-# References
-
-<!-- uses zotero folder ICBintro -->
-<div id="refs"></div>
-<!-- https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html -->
-<!-- may require additional software -->
-
-\newpage
-
-# Appendix
-
-## Appendix 1: ICB Crises and Summary Information {#app:crises}
+## SI Table 1: ICB Crises and Summary Information {#app:crises}
 
@@
 \caption{Cuban Missile Crisis according to Phoenix \label{fig:196metromap_phoenix}}
-\centering{\includegraphics[width=19cm]{figures/p_phoenix_metro_plot_196.png}}
+\centering{\includegraphics[width=19cm]{../figures/p_phoenix_metro_plot_196.png}}
 \end{figure}
@@
 \caption{Cuban Missile Crisis according to ICB \label{fig:196metromap_icb}}
-\centering{\includegraphics[width=19cm]{figures/p_icb_metro_plot_196.png}}
+\centering{\includegraphics[width=19cm]{../figures/p_icb_metro_plot_196.png}}
 \end{figure}
@@
 \caption{Cuban Missile Crisis according to MIDs Episodes \label{fig:196metromap_mids}}
-\centering{\includegraphics[width=19cm]{figures/p_mids_metro_plot_196.png}}
+\centering{\includegraphics[width=19cm]{../figures/p_mids_metro_plot_196.png}}
 \end{figure}
-
-## Appendix 5: DRC {#app:ft_sentence_table_426}
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-ft_sentence_table_426 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_426.Rds'))  %>%
-  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426)") #\\label{tbl:ft_sentence_table_426}
-ft_sentence_table_426 %>%
-      flextable::width( j = 1, width=0.3) %>%
-      flextable::width( j = 2, width=3.25) %>%
-      flextable::width( j = 3, width=3.25)
-```
-
-\begin{figure}[H]
-\caption{DRC Civil War according to Phoenix \label{fig:426metromap_phoenix}}
-\centering{\includegraphics[width=19cm]{figures/p_phoenix_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to ICEWS \label{fig:426metromap_icews}}
-\centering{\includegraphics[width=19cm]{figures/p_icews_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to Terrier \label{fig:426metromap_terrier}}
-\centering{\includegraphics[width=19cm]{figures/p_terrier_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to Dyadic ICB \label{fig:426metromap_icb}}
-\centering{\includegraphics[width=19cm]{figures/p_icb_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to MIDs Incidents \label{fig:426metromap_mids_incidents}}
-\centering{\includegraphics[width=19cm]{figures/p_mids_incidents_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to MIDs Episodes \label{fig:426metromap_mids}}
-\centering{\includegraphics[width=19cm]{figures/p_mids_metro_plot_426.png}}
-\end{figure}

### 2022-07-17 replication_paper/pnas_draft/appendix.Rmd
v1.1

---
title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"

#https://bookdown.org/yihui/bookdown/a-single-document.html
#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
output: 
  bookdown::pdf_book:
    toc: yes
    latex_engine: xelatex

bibliography: ICBintro.bib

#Disabled several the caused errors
header-includes:
# - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
# - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
#  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage{algorithm}
  - \usepackage[algo2e]{algorithm2e}
  - \usepackage{amsmath}
  - \usepackage{afterpage}
  - \usepackage{placeins}
  - \usepackage{rotating, float, caption}
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined

---

```{r library loads, eval=T, echo=F, cache=F, results='hide', message=F}

flag_folder_small="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"

knitr::opts_chunk$set(echo = F, echo=F, cache=F, results='hide', message=F, warning=F) #Global options

#library(pacman)
library(googlesheets4)
library(tidyverse)
library(janitor)
library(flextable)
library(ggplot2)
library(cowplot)
library(ggtext)
#set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`. You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
library(ftExtra)
options(tidyverse.quiet = TRUE)
options(gargle_oauth_email = TRUE)

#install.packages('stargazer')
#install.packages('kableExtra')
#! sh: 1: pdflatex: not found
#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended

#! LaTeX Error: File `letltxmacro.sty' not found.
#sudo apt-get install texlive-latex-extra

library(pacman)
library(igraph)
library(tidyverse)
library(flextable)
library(ftExtra)

```

```{r data loads, eval=T, echo=F, cache=F, results='hide', message=F}

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )

ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
dim(ICBe_events_agreed)

icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
dim(icb_events_long)

ICBe_crises_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds"))

ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))

#oh is it because break is reserved in R? lol
#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)

#somehow break of all things is a b roken name
#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))

```

# Appendix A Corpus and Cases
\hphantom{em}
## Table A1: ICBe Crises and Summary Information {#app:crises}
\hphantom{em}

```{r ICBe Crisis Summaries, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F}

#The answer is I have to include it as an image, none of the table options were compiling correctly without error
#,  ft.arraystretch=0.75

temp_all <-  ICBe_crises_markdown %>% ungroup() %>% dplyr::select(
                    crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events, 
                    coders_expert , 
                    coders_novice ,
                    actors , 
                    units_domains, 
                    forces_fatalities
                    ) %>%
              mutate_all(as.character) %>%
              mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II"))

convert_to_ft <- function(x){
     x %>% flextable::as_flextable() %>%
      flextable::set_header_labels(values =
          list(crisno = "#",
                crisis_text = "Title",
                yrtrig = "Start",
                yrterm = "End",
                n_sentence_number_int_aligned = "Sent.",
                n_events = "Events",
                coders_expert = "Exp.",
                coders_novice = "Nov.",
                actors = "Actors",
                units_domains = "Units/Domains",
                forces_fatalities = "Forces/Fatalities"
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::add_header(values =
          list(crisno = "Crisis",
                crisis_text = "Crisis",
                yrtrig = "Years",
                yrterm = "Years",
                n_sentence_number_int_aligned = "Counts",
                n_events = "Counts",
                coders_expert = "Coders",
                coders_novice = "Coders"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::merge_h(part = "header" ) %>%
      flextable::width( j = 1, width=0.3)  %>%
      flextable::width( j = 2, width=2.75)  %>%
      flextable::width( j = 3, width=0.6)  %>%
      flextable::width( j = 4, width=0.6)  %>%
      flextable::width( j = 5, width=0.25)  %>%
      flextable::width( j = 6, width=0.25)  %>%
      flextable::width( j = 7, width=0.25)  %>%
      flextable::width( j = 8, width=0.35)  %>%
      flextable::width( j = 9, width=2.5)  %>%
      flextable::width( j = 10, width=1.5)  %>%
      flextable::width( j = 11, width=1.0)  %>%
      flextable::fontsize(size = 9, part = "all") %>%
      flextable::padding(padding = 0.1, part = "all") %>%
      flextable::line_spacing(space = 1, part = "body") %>%
      flextable::bg( i = which( 1:nrow(x) %% 2 == 1)  , part = "body", bg = "#EFEFEF") %>%
      ftExtra::colformat_md(j = 9:11, part="body")
}

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png", zoom=1)

```

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png"}}
\end{figure}

## Table A2: Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}
\hphantom{em}

```{r , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

#Switched to spans here
icb_text <- ICBe_events_agreed %>% dplyr::select(crisno,sentence_number_int_aligned, sentence=sentence_span_text) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)

fromscratch=F
if(fromscratch){
  #Here we use spacy to extract verbs from the sentences
  p_load("spacyr")
  #spacy_install() 
  spacy_initialize(model = "en_core_web_sm")

  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
  parsed_consolidated <- nounphrase_consolidate(parsed)
  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]

  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

}

entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
entities$crisno <- icb_text$crisno[entities$doc_id_num]
entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()

verbs_sentence <- parsed %>% filter(pos=="VERB")

verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()

entities_per_sentence <- entities %>% 
  count(doc_id) %>% 
  summarise(
    entities_per_sentence_min=min(n),
    entities_per_sentence_mean=mean(n),
    entities_per_sentence_max=max(n),
  )

```

```{r, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

#wordnet rdf (in tripple format)
#wordnet rdf (in tripple format)
fromscratch=F

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )
subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
subject_headings_verbs <- subject_headings %>%
                          filter(value %>% str_detect('-v>')) %>% 
                          mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>% 
                          mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
                          separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
                          mutate(b = b %>% str_replace_all('\\"| \\.',""))

#subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('00002137')) #the first digit is for part of speech so we can remove that if we subset to just verbs
#wordnet csv
filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"))
filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)

wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F, show_col_types=F)
names(wordnet_list) <- filenames

#wordnet_list[[8]]
#wordnet_list[[16]]
#wordnet_list[[19]]

#wordnet_list[["wn_cls.csv"]]
#wordnet_list[["wn_vgp.csv"]]

hypernyms <- wordnet_list[['wn_hyp.csv']] %>% 
              dplyr::select(a=X1,b=X2) %>% 
              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>% 
              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )

library(igraph)
g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)

wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )

wordnet_verbs <- wordnet %>% filter(tense=='v')

verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
#oh got it this is all possible matching glosses per ICBe sentence
#dim(verbs_sentence_wordnet) #227,426

#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances

gloss_unique <- verbs_sentence_wordnet$gloss %>% unique() #how are there so few unique glosses?
length(gloss_unique) #And there's also about 5k unique glosses

sentences_unique <- verbs_sentence_wordnet$sentence %>% unique()
length(sentences_unique) #11769

```

```{r python load, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

library(reticulate)
reticulate::py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

```

```{python embed glosses, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers

fromscratch=False

if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  glosses=np.array(r.gloss_unique) #sentences_unique_sanitized
  glosses_chars = np.array([len(q) for q in glosses])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(glosses) #4977
  n=len(glosses)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  glosses_chunks=[glosses[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(glosses_chunks)
  len(glosses_chunks[0])  
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  glosses_embeddings = np.vstack([model.encode(q) for q in glosses_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  glosses_embeddings.shape #(4977, 768)

else:
  print("Skipping")

```

```{python embed sentences for wordnet , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

#Now embed the sentences from above (note this is raw original sentences not the normalized ones used in the main paper)
#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers

fromscratch=False
if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #12161 12162
  n=len(sentences)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #(12103, 768)

else:
  print("Skipping")

```

```{r wordnet trees, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

fromsrcatch=F
if(fromsrcatch){
  #py$sentences
  #py$glosses
  glosses_embeddings <- py$glosses_embeddings
  sentences_embeddings <- py$sentences_embeddings

  rownames(sentences_embeddings) <- py$sentences #[1:100] 
  dim(sentences_embeddings)
  rownames(glosses_embeddings) <- py$glosses #[1:100]
  dim(glosses_embeddings)

  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
  gloss_clean <- verbs_sentence_wordnet$gloss
  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
  dim(glosses_embeddings_expanded)

  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
  table(condition_sentences_embeddings) #all are in it
  sentences_clean <- verbs_sentence_wordnet$sentence
  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
  dim(sentences_embeddings_expanded)

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

} else {

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

}

verbs_sentence_wordnet_top <- verbs_sentence_wordnet %>% group_by(crisno, sentence_number_int_aligned, token_id) %>% filter(row_number()==1)
verbs_sentence_wordnet_top_unique <- verbs_sentence_wordnet_top %>% ungroup() %>% dplyr::select(lemma, wordnetid,tense, gloss) %>% group_by(lemma, wordnetid,tense, gloss) %>% count() %>% arrange(desc(n))

```

```{r create verb table , eval=T, echo=F, results="markup", include=T, message=T, cache=F, ft.arraystretch=0.75}

set_flextable_defaults(fonts_ignore=TRUE)
n_keep=200
verbs_sentence_wordnet_top_ft <-
        verbs_sentence_wordnet_top_unique %>%
        ungroup() %>% 
        head(n_keep) %>%
        dplyr::select(n, lemma, gloss ) %>% #wordnetid
        mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.\"]','')) %>%

        flextable::as_flextable() %>%

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6, part = "all") %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is crazy slow
        #flextable::autofit() 
        #set_table_properties(width = 1, layout = "autofit")

      bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
      #merge_v(part = "body") %>% 
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=.75) %>%
      flextable::width( j = 3, width=6) %>%
      #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      #hline(i=which( actor_agents$Player!=c(actor_agents$Player[2:length(actor_agents$Player)], NA) ), border = fp_border(color="gray", width = 0.25), part = "body")

      #add_header( "IR Player_Pieces"="Citations"

      #            top = TRUE ) %>%
      set_header_labels(
        values = list(
          "uses" = "Count",
          'lemma'='Lemma',
          'gloss'='Gloss'
          ) 
        )

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html

verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))

```

```{r verb table , eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
#, child=c('ICBEdataset_paper_appendixVerbMeanings.Rmd')

verbs_sentence_wordnet_top_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
verbs_sentence_wordnet_top_ft
```

# Appendix B: Coding Process
\hphantom{em}

## Figure B1: Graphical User Interface {#app:gui}
\hphantom{em}

\begin{figure}[H]
\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{../figures/gui_example}}
\end{figure}

## Algorithm B2: Coding Aggregation and Filtering {#app:algo1}
\hphantom{em}

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Coder-Sentence-Tokens}
\KwResult{Sentence-Events}
\ForEach{sentence in sentences}{
  \ForEach{concept in concepts}{
    \ForEach{token in tokens}{
      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
    }
    \If{sum(accepted) == 0}{
      sort tags by votes;
      head 1;
      accept; \tcc*[f]{If still no tag, take one with most votes}
    }
  }
  \ForEach{ActorSet in unique(ActorSets)}{
    emit event;
  }
}
\caption{Aggregating Coder-Tokens into Sentence-Events}
\end{algorithm}

## Figure B3 : Intercoder Agreement {#app:intercoderagreement}
\hphantom{em}

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

fromscratch=F
if(fromscratch){
  means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
                     #filter(votes_total>1) %>% #
                     group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                     dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)

  means_group_keep <- codings_long_agreement %>% filter(value_normalized!='') %>% 
                      filter(algo1==1) %>%
                      #filter(votes_total>1) %>%
                      group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                      dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean)

  means_group <- bind_rows( means_group_any %>% pivot_longer(c(Experts, Novices)),  means_group_keep %>% pivot_longer(c(Experts_keep, Novices_keep)) )

  #Calculate average agreements by group
  means_all <- codings_long_agreement %>% 
                #This is top 1 agreement
                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% 
                arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                group_by(varname_normalized) %>%
                mutate(n=n()) %>%
                #filter(votes_total>1) %>% #about 9k only had one coder
                #filter(selected_by_experts>=1) %>%
                dplyr::select(Experts=percent_expert,Novices=percent_novice,n) %>% 
                summarise_all(mean, na.rm=T)

  means_keap <- codings_long_agreement %>% 
                #Algo 1 agreement
                filter(algo1==1) %>% 
                #This is top 1 agreement
                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                group_by(varname_normalized) %>%
                #filter(votes_total>1) %>% #What work is this doing?
                #filter(selected_by_experts>=1) %>%
                dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean, na.rm=T)

  factor_order <- means_keap %>% arrange(desc(Experts_keep)) %>% pull(varname_normalized)
  p_percent_chose_tag_by_concept <- 
  means_all %>% full_join(means_keap) %>% mutate(varname_normalized = varname_normalized %>% factor(levels=factor_order %>% rev)) %>%
    filter(n>100) %>% dplyr::select(-n) %>% #require at least 100 examples
  pivot_longer(c(-varname_normalized)) %>%
      ggplot(aes(x=selected_by_any_perc, y=varname_normalized)) + 
      #geom_boxplot() + 
      geom_point(aes(x=value, color=name )) +
      xlab("Percent of Coders that selected Tag") +
      ylab("") +
      labs(
        title = "Intercoder Agreement by Concept (Top 1 Tags)",
        subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
        caption = paste0("Mean by Concept (Point); Mean by Group (Line)"), 
       color = "Codings"
       ) + 
      theme_bw() +
      theme(legend.position="bottom") +
      geom_vline(data=means_group, aes(xintercept = value, color = name), linetype="solid", size=1, alpha=0.5)

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

```

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_concept.png}}
\end{figure}

## Figure B4 : Intercoder Agreement by Confidence {#app:agreement_by_confidence}
\hphantom{em}

```{r intercoder agreement , eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

fromscratch=F
if(fromscratch){
  raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value) %>% distinct()

  temp <- codings_long_agreement %>% 
                #Algo 1 agreement
                filter(algo1==1) %>% 
                #This is top 1 agreement
                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>%                    left_join(raterconfidence) %>% 
                group_by(raterconfidence)

  p_percent_chose_tag_by_confidence <- temp %>%
    dplyr::select(percent_expert,raterconfidence) %>%
    filter(raterconfidence!='NA') %>%
    ggplot(aes(x=percent_expert, y=raterconfidence)) + geom_boxplot(notch=T) +
    xlab("Percent of Coders that selected Tag") +
    ylab("Self Reported Confidence") +
    labs(
      title = "Observed Intercoder Agreement by Self Reported Confidence"#,
      #subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
      #caption = paste0("Mean by Concept (Point); Mean by Group (Line)"), 
      #color = "Codings"
     ) + 
    theme_bw() +
    theme(legend.position="bottom")

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

```

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_confidence.png}}
\end{figure}

# Appendix C: Recall
\hphantom{em}

## Algorithm C1: Synthetic Narratives
\hphantom{em}

A synthetic narrative is constructed as follows. First, compile a large corpus, $D$, of timelines, encyclopedia entries, journal articles, news reports, websites, and government documents. Next, segment into sentences, $s \in S$, clean, filter, and break into simpler concise sentences, $s^* \in S^*$, using a large natural language model, BART [@lewisBARTDenoisingSequencetoSequence2019], fine-tuned on summarization tasks, distilbart-cnn-12-6 [@shleiferPretrainedSummarizationDistillation2020]. Then, calculate semantic similarity between each $S*$ by embedding them with a different large language model, MPNet [@songMPNetMaskedPermuted], fine tuned to identify paraphrasing [@reimersSentenceBERTSentenceEmbeddings2019;@reimersMakingMonolingualSentence2020]. Next, constructed an undirected weighted graph of pair above 95th percentile cosine similarity and hierarchically cluster them into potential events $e^* \in E^*$ [@clausetFindingCommunityStructure2004]. The resulting set of $E^*$ are small enough to check by hand, summarize, and place in chronological order. The relevant formulas and algorithm are shown below.

Cosine Similarity
\begin{equation}
cosine\;similarity = \frac{a \cdot b}{ || a  ||\;|| b  || }
\end{equation}

Adjacency Matrix
\begin{equation} \label{eq:sclrec2}
A_{vw}= \begin{cases} 1 \text{ if vertices v and w are connected} \\ 0 \text{ otherwise } \end{cases}
\end{equation}

Identity Function
\begin{equation}
\delta(i,j)= \begin{cases} 1 \text{ if i=j} \\ 0 \text{ otherwise } \end{cases}
\end{equation}

Degree of a vertex
\begin{equation}
k_v = \sum_{w}A_{vw}
\end{equation}

Modularity - Is the difference between observed within-community edges and average expected edges on a random graph
\begin{equation} \label{eq:sclrec2}
Q = \frac{1}{2m}\sum_{vw}[A_{vw}-\frac{k_vk_w}{2m}]\delta(C_w,C_w)
\end{equation}

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Document-Sentences}
\KwResult{Event-Mentions}
\tcc{ Embed text as a 768 dimensional semantic vector with a large language model}
\ForEach{document in Document}{
  \ForEach{sentence in sentence}{
    embedding=distilbart-cnn-6-6(sentence);
  }
}

similarity = cosine similarity(embeddings,embeddings);

\tcc{ Threshold similarity matrix and create weighted undirected graph }

\tcc{ Frame as adding edges so efficient nearest neighbor lookup can be used }

g=EmptyUndirectedWeightedGraph();\tcc*[f]{Sparse undirected graph to store edges}

\ForEach{v in 1:rows(similarity)}{
  \ForEach{w in 1:cols(similarity)}{ 
    \lIf{similarity[v,w]>0.96 and doc(V)!=doc(W)}{append edge v<->w to g}\tcc*[f]{If similar append as undirected edge to graph}
  }
}

\tcc{ Community detection with greedy hierarchically clustering (Clauset et al. 2004)}

gClustered=EmptyUndirectedGraph(vertices(g)); \tcc*[f]{Sparse undirected graph to store edges}
dendrogram=list()
\While{length(edges(g))>1}{

  \ForEach{edge in edges(g)}{
    Qpossible[edge]=Q(gClustered + edge)
  }

  \ForEach{ edge in edges(g) } {
    \tcc{ Add the edge with the maximum increase in modularity }
    \tcc{ Remove from original graph as a housekeeping trick }
    \lIf{ QPossible[edge]=max(QPossible) }{ append edge to gClustered and remove edge from g; append QPossible to dendrogram }
  }
}
\tcc{ Cut the dendrogram to maximize modularity and return event clusters}
\Return dendrogram where Q(dendrogram)==max(dendrogram) \tcc*[f]{}
\caption{Clustering and counting sentences about the same event}
\end{algorithm}

## Table C2: Synthetic Narrative Matches Cuban Missile
\hphantom{em}

<!-- Gibler's Narratives

MID#27 
Dispute Number: 27 
Date(s): July 25, 1961 to October 28, 1961 
Participants:  2  United  States  of  America,  200  United  Kingdom,  220  France,  260  
German  Federal  Republic/265  German  Democratic  Republic,  290  Poland,  315  
Czechoslovakia, 365 Russia 
Outcome (and Settlement): Unclear (None) 
Fatalities: None 
Narrative:  The  Soviet  Union  for  several  months  leading  up  to  this  dispute  had  
increasingly  become  stern  in  its  wishes  for  a  united  Germany.  This  sternness  on  
Khrushchev’s part manifested itself in a treaty deadline, set for December 1961. In a  
public address on July 25, 1961, President Kennedy made a request for congressional  
authorization to mobilize selected military units to respond to the threat to Berlin. On  
August 13, the East German government released a declaration that stated that in the  
face of aggressive aspirations, East Germany would take the necessary measures to  
guarantee the security of the German Democratic Republic. The East German military  
fortified its borders with West Berlin and began to build a wall on the border in the  
city. In addition, barricades were built that encircled West Berlin, blockading it from  
East  Germany  entirely.  Two  Russian  divisions  were  reported  to  be  equipped  with  
armor and artillery. 
In response to this blockade, the United States, Britain, and France initiated a troop  
buildup in West Germany and West Berlin on August 17. On October 17, Khrush- 
chev announced that it appeared the West wanted to negotiate, and thus the need for  
the  December  deadline  was  unnecessary.  In  direct  contrast  to  his  words  however,  
on October 27, Soviet tanks were moved up to the sector boundary, amounting to a  
standoff with previously deployed American tanks. As soon as the Soviet government  
heard of this movement they called the forces back. The Soviet tanks withdrew from  
their positions on the morning of October 28. This action marked the end of the Berlin  
Crisis of 1961.

MID#61 
Dispute Number: 61 
Date(s): August 1, 1962 to December 12, 1962 
Participants: 2 United States of America/365 Russia, 40 Cuba  
Outcome (and Settlement): Yield by side B (Negotiated)  
Fatalities: None 
Narrative:  Tensions  between  the  United  States  and  Cuba  were  high  after  Castro  
removed Batista and came to power in 1959. US policy sought the overthrow of the  
Castro regime in Cuba, and in 1961 the United States supported a group of Cuban  
exiles in the unsuccessful Bay of Pigs invasion. In September 1962 the situation in  
Cuba escalated. 
   On  September  3,  the  Soviets  announced  that  it  would  send  arms  and  technical  
experts to Cuba and help Cuba expand its steel production. Four days later Kennedy  
requested activation of 150,000 reservists, and Congress approved the measure a week  
later. On September 22, the Soviets reiterated that the weapons they sent to Cuba were  
defensive only, and three days later Castro announced that Cuba would lease a port  
to the Soviets for fishing. In early October the United States was examining ways to  
end Cuban trade with the Western states. Castro then mobilized the Cuban forces in  
mid-October. 
   On October 22, US President Kennedy gave a public address in which he stated the  
United States had photographic evidence of Soviet missiles in Cuba that were capable  
of delivering nuclear weapons to much of the Americas; Kennedy announced a quar- 
antine/blockade of Cuba to begin two days later. The Organization of American States  
then passed a resolution calling for removal of Soviet weapons, and the UN Security  
Council debated the dispute. The Soviet Union accused the United States of piracy  
and flaunting international law in implementing a blockade of defensive weapons, and  
the Security Council requested UN Secretary-General U Thant to mediate the dispute. 
   Meanwhile, the leaders of the two countries sent letters back and forth. On October  
26, Khrushchev sent a letter in which he offered to withdraw the missiles in exchange  
for an end to the blockade and a guarantee that the United States would not invade  
Cuba.  Khrushchev  then  sent  another  letter  the  next  day  that  proposed  the  Soviets  
would withdraw the missiles from Cuba if the United States would withdraw its mis- 
siles from Turkey. On October 28, Khrushchev announced over Moscow Radio that  
the  Soviet  Union  would  withdraw  the  weapons  under  international  supervision.  In  
addition, Kennedy secretly agreed to withdraw US missiles from Turkey over four to  
five months. 
   The United States and Soviet Union continued discussions. A couple issues arose  
in  implementing  the  agreement  they  had  made:  first,  the  Soviets  did  not  consider  
IL-28 bombers to be offensive, and, second, Castro refused to allow verification mis- 
sions. On November 20, Kennedy gave a press conference that announced solutions  
to these problems. The Soviets would withdraw the IL-28s within 30 days; the United  
Nations would not send a verification team, but the Soviets would allow US ships to  
stop  and  inspect  departing  Soviet  ships.  The  United  States  would  also  use  its  own  
reconnaissance methods for verification and would lift the blockade. On December  
11, Khrushchev wrote to Kennedy that the Soviets had completed removing the mis- 
siles from Cuba. 
Coding changes: Start Date changed from January 28, 1962.

MID#246 
Dispute Number: 246 
Date(s): May 1960 to April 19, 1961 
Participants: 365 Russia, 40 Cuba/2 United States of America 
Outcome (and Settlement): Unclear (None) 
Fatalities: None 
Narrative: In 1960, after the Cuban Revolution and the victory of the Communists in  
taking control of the government, Cuba began to nationalize foreign industries in its  
territory. This greatly upset the United States, and the American government began to  
try and coerce Cuba to cooperate with its policies. On April 22, 1960, Fidel Castro, the  
new premier of Cuba, accused the United States and its forces at Guantanamo Bay of  
aiding counterrevolutionaries and of planning an invasion of Cuba. A Cuban attack on  
a US submarine operating off the Cuban coast then occurred in May. Cuba asserted that  
the submarine had violated Cuba’s territorial waters. 
The Soviet Union entered the dispute on the side of Cuba on July 9, when Premier  
Khrushchev  threatened  to  retaliate  with  rockets  should  the  United  States  intervene  
militarily  in  Cuba.  This  tension  increased  through  1960  and  into  1961,  culminating  
in the Bay of Pigs invasion, supported by Central Intelligence Agency–trained Cuban  
exiles April 14–20, 1961. The Soviet Union again warned the United States that mili- 
tary intervention in Cuba would mean certain conflict between the super powers. 
Coding changes: Start Date changed from April 22, 1960. End Date changed from  
April 26, 1961.

MID#253 
Dispute Number: 253 
Date(s): April 9, 1960 to July 1, 1960 
Participants: 2 United States of America, 385 Norway, 640 Turkey, 740 Japan, 770  
Pakistan/365 Russia 
Outcome (and Settlement): Released (Negotiated) 
Fatalities: 1–25 deaths 
Narrative: In an effort to monitor Soviet nuclear capabilities the United States flew  
U-2  reconnaissance  missions  high  over  the  USSR  from  1956,  believing  its  planes  
were  undetected.  On  May  1,  1960,  the  Soviets  downed  a  US  U-2  piloted  by  Gary  
Powers. Then on July 1, the Soviets downed a US Air Force RB-47 over the Barentz  
Sea, killing four crew members and capturing the other two. In August the Soviets  
convicted Powers of espionage and sentenced him to 10 years in prison. The Soviets  
sought an end to US overflights. 
   The Soviets pursued action in the UN Security Council and General Assembly, but  
every resolution was voted down. However, US overflights did end. Powers’s flight  
was the last authorized by the president and records indicate that the US government  
undertook no more. The Soviets released RB-47 personnel McKone and Olmstead on  
January 25, 1961. 
   Powers and American student Pryor were exchanged for Soviet spy Rudolf Abel  
on February 10, 1962. 
Coding changes: Start Date changed from May 1, 1960. End Date changed from July  
18, 1960. Fatalities changed from None.

MID#1353 
Dispute Number: 1353 
Date(s): January 6, 1962 to February 20, 1973 
Participants: 365 Russia, 710 China, 816 Vietnam/2 United States of America, 200  
United Kingdom, 800 Thailand, 812 Laos, 900 Australia, 920 New Zealand 
Outcome (and Settlement): Compromise (Negotiated) 
Fatalities: Missing 
Narrative: This dispute began in early 1962 when Pathet Lao communist rebels, with  
support from North Vietnam, laid siege to Nam Tha, near the Thai border. On Febru- 
ary 13, Thai troops were deployed to the Lao border. On May 6, Pathet Lao forces  
attacked Nam Tha while Royal Lao forces ceded territory without a fight. The United  
States responded on May 12 by sending the Seventh Fleet to the Gulf of Siam and  
placing troops on alert. 
   The 1,000 US marines already in Thailand for bilateral training were also moved  
to  the  border.  Civil  war  fighting  continued  throughout  the  decade,  with  occasional  
transnational incidents affecting numerous neighbors and those countries fighting in  
Vietnam. Thailand took a direct role by training Laotian pilots, and South Vietnam  
trained Laotian officers. The United States and Soviets supplied the fighting forces  
and guarded their interests in the region. 
   The overall fight was largely static until 1969, when Pathet Lao began to achieve  
battlefield victories. Then, by 1972, Pathet Lao controlled two-thirds of the country.  
Discussions between the Laotian government and the Pathet Lao began in 1970, and  
formal negotiations took place in Vientiane from October 1972. These talks did not  
advance, though, until the United States applied pressure to the Laotian government.  
The United States wanted to enter the Paris Peace talks for Vietnam with the Laotian  
war already concluded. On February 20, 1973, representatives from the Laotian gov- 
ernment and Pathet Lao signed the Vientiane Agreement. 
Coding changes: End Date changed from February 15, 1973.

MID#2219 
Dispute Number: 2219 
Date(s): November 19, 1961 to August 14, 1962 
Participants:  265  German  Democratic  Republic,  365  Russia/2  United  States  of  
America, 260 German Federal Republic 
Outcome (and Settlement): Unclear (None) 
Fatalities: 1–25 deaths 
Narrative: On November 22, 1961, an intensified border fortification effort in East  
Berlin began when East German forces erected a new barbed wire fence along the  
Spree  River.  This  effort  triggered  an  increase  in  what  were  already  tense  relations  
between the two Germanys. Border police skirmishes along the border of East and  
West Berlin were not uncommon. For example, on April 21, 1962, a brief gun battle  
took place when Eastern border police threw tear gas canisters over the border into  
West  Berlin.  The  United  States  joined  the  dispute  on  December  3,  1961,  when  it  
deployed  troops  to  monitor  the  west  side  of  the  Berlin  wall  at  the  Friedrichstrasse  
checkpoint. The Soviet Union joined the dispute on February 15, 1962, when Soviet  
MIGs began harassing aircrafts that were too close to East German airspace. The last  
incident in this dispute occurred on August 14, 1962, when border police exchanged  
fire across the border near Kassel.

MID#3361 
Dispute Number: 3361 
Date(s): December 1961 to December 1962 
Participants: 2 United States of America/365 Russia, 710 China, 816 Vietnam 
Outcome (and Settlement): Unclear (None) 
Fatalities: None 
Narrative:  The  United  States  deployed  two  Army  helicopter  companies  to  South  
Vietnam, and American advisers began participating in South Vietnamese operations.  
China and the Soviet Union warned the United States not to attack North Vietnam. 
Coding changes: End Date changed from February 26, 1962. 
-->

```{r}

cuba_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names()

replace_emoticons_cuba <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
}

ft_cuba_recall<- cuba_recall %>% 
                            dplyr::select(date, event, documents, icb_narrative, icbe=ic_be, icb, mids, phoenix_2)  %>%
                            mutate(event = event %>% replace_emoticons_cuba() ) %>%
                            flextable::as_flextable() %>%
                            flextable::set_header_labels(values =
                            list(
                                  event = "Event",
                                  documents = "Mentions",
                                  icb_narrative = "ICB Narrative",
                                  icbe = "ICBe",
                                  icb = "ICB",
                                  mids="MIDs",
                                  phoenix_2="Phoenix"
                                 ) ) %>%
                            flextable::width( j = 1, width=0.25)  %>% 
                            flextable::width( j =2, width=2.0)  %>% 
                            flextable::width( j = 6:8, width=2.0)  %>% 
                            flextable::fontsize(size = 7, part = "all") %>%
                            #valign(j = 1:3, valign = "top", part = "body") %>%
                            flextable::line_spacing( space = 1.0, part = "all") %>% 
                            padding( padding = 1, part = "all") %>% 
                            bg( i = which( (1:nrow(cuba_recall) %% 2)==1   ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                            ftExtra::colformat_md(j = 2, part="body")

ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"

```

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png}}
\end{figure}
\clearpage

```{r}

crimea_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names()

replace_emoticons_crimea <- function(x){
      x %>%
            #https://emojiterra.com/flag-for-united-states/
            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
            #https://emojiterra.com/flag-for-russia/
            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
            #Ukraine
            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
            #Crimea
            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ") %>%
            #EU
            str_replace_all('\U0001f1EA\U0001f1FA',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q458.png) ")
}

ft_crimea_recall<- crimea_recall %>% 
                            dplyr::select(date, event, documents=n_sources, icb_narrative, icbe=ic_be,  phoenix, terrier, icews)  %>%
                            mutate(event = event %>% replace_emoticons_crimea() ) %>%
                            mutate(date = date %>% as.Date()) %>%
                            flextable::as_flextable() %>%
                            flextable::set_header_labels(values =
                            list(
                                  event = "Event",
                                  documents = "Mentions",
                                  icb_narrative = "ICB Narrative",
                                  icbe = "ICBe",
                                  phoenix="Phoenix",
                                  terrier="Terrier",
                                  icews="ICEWS"
                                 ) ) %>%
                            flextable::width( j = 1, width=1.0)  %>% 
                            flextable::width( j =2, width=2.0)  %>% 
                            flextable::width( j = 6:8, width=2.0)  %>% 
                            flextable::fontsize(size = 7, part = "all") %>%
                            #valign(j = 1:3, valign = "top", part = "body") %>%
                            flextable::line_spacing( space = 1.0, part = "all") %>% 
                            padding( padding = 1, part = "all") %>% 
                            bg( i = which( (1:nrow(crimea_recall) %% 2)==1   ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                            ftExtra::colformat_md(j = 2, part="body")

ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"

```

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png}}
\end{figure}
\clearpage

## Table C3: Synthetic Narrative Matches Crimea-Donbas
\hphantom{em}

# Appendix D: Precision

\hphantom{em}

\clearpage

## Figure D1 Crimea-Donbos 
\hphantom{em}

```{r crimea case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}

#Move this to the appendix

#<!-- Rex remember that sentence 19 broken and cuts off 
#"Ukraine’s major response to its crisis was verbal and began on 27 February, when it sent a note to Russia demanding that Russian troops stay on base in Crimea, called for #calm, and discussed the" -->

#Loaded above now 
#ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
fromscratch=F
if(fromscratch){
  temp <- ICBe_events_agreed_markdown %>%
          filter(crisno==471) %>%
          group_by(crisno, sentence_number_int_aligned) %>%
            filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
          ungroup() %>%
          mutate(banding=sentence_number_int_aligned %% 2)
  temp$is_subsstring <- NA
  for(i in 1:nrow(temp)){
    temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
                                                                                  pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
                                                                                ) %>% replace_na(0) %>%  sum()
  }
  temp <-temp %>%
          mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
          group_by(sentence_number_int_aligned) %>%
            filter(value_markdown!='' | length(value_markdown)==1) %>%
          ungroup() %>%
          mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
          mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
          mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
        #head(100) %>%

  ft_crimea_precision_part1 <- temp %>% 
                              dplyr::select(S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
                              filter(row_number()<=61) %>%
                              flextable::as_flextable() %>%
                              flextable::width( j = 1, width=0.25)  %>% 
                              #flextable::width( j = 2, width=0.25)  %>% 
                              flextable::width( j = 2, width=8.0)  %>% 
                              flextable::width( j = 3, width=4.0)  %>% 
                              flextable::fontsize(size = 9, part = "all") %>%
                              valign(j = 1:3, valign = "top", part = "body") %>%
                              flextable::line_spacing( space = 1.0, part = "all") %>% 
                              padding( padding = 1, part = "all") %>% 
                              bg( i = which( temp$banding[1:61]==1 ) , part = "body", bg = "#EFEFEF", j=1:3) %>%
                              ftExtra::colformat_md(j = 3, part="body")
  #ft_cuba_precision

  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"

  ft_crimea_precision_part2 <- temp %>%
                        dplyr::select(S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
                          filter(row_number()>=62  ) %>%
                        flextable::as_flextable() %>%
                        flextable::width( j = 1, width=0.25)  %>% 
                        #flextable::width( j = 2, width=0.25)  %>% 
                        flextable::width( j = 2, width=8.0)  %>% 
                        flextable::width( j = 3, width=4.0)  %>% 
                        flextable::fontsize(size = 9, part = "all") %>%
                        valign(j = 1:3, valign = "top", part = "body") %>%
                        flextable::line_spacing( space = 1.0, part = "all") %>% 
                        padding( padding = 1, part = "all") %>% 
                        bg( i = which( temp$banding[62:111]==1 ) , part = "body", bg = "#EFEFEF", j=1:3) %>%
                        ftExtra::colformat_md(j = 3, part="body")
  #ft_cuba_precision

  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"

  temp <- NULL

}
```

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

## Table D2: Stratified Sentence Examples

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_sample_precision_precision.png"}}
\end{figure}
\clearpage

## Figure D3 Crisis Maps Cuban Missiles

\hphantom{em}

```{r crisis maps common functions, eval=T, results='hide', echo=F, include=T, message=F, cache=F}

global_check_overlap=F
library(igraph)
library(RColorBrewer)
library(ggraph)
target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()

actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
                                sheet="actor_translator") #%>% janitor::clean_names() 
#Convert to a local file for pushing
#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
library(pals); #install.packages('pals')
pallet <- pals::glasbey()
pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
library(colorspace)
#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))

crisno_name_years <- icb_crises %>% dplyr::select(crisno, crisname, yrtrig, yrterm)

CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cccc') %>% janitor::clean_names()

cameo_role_codes <- data.frame(
       stringsAsFactors = FALSE,
                   role_code = c("GOV","SPY","OPP",
                            "MIL","PTY","REB","EDU","COP","JUD","CRM",
                            "BUS","MED","CVL","UAF","AGR","ELI","DEV","ENV",
                            "HLH","HRI","LAB","LEG","REF","MOD","RAD"),
  role_code_label = c("Government",
                            "Intelligence agencies",
                            "Opposition groups (often parliamentary)",
                            "Military",
                            "Political party",
                            "Rebels/insurgents",
                            "Education-focused actors",
                            "Law enforcement agencies",
                            "Judicial actors",
                            "Criminal actors",
                            "Business (NOT MNCs)",
                            "Media-related actors/organizations",
                            "Civilians",
                            "Unaffiliated armed forces",
                            "Agriculture-focused actors",
                            "Elites, celebrities",
                            "Development-focused actors",
                            "Environment-focused actors",
                            "Health-focused actors",
                            "Human rights-focused actors",
                            "Labor-focused actors",
                            "Legislative bodies/actors",
                            "Refugee-focused actors",
                            "Moderate/mainstream group",
                            "Radical/extremist/fundamentalist")
) %>% janitor::clean_names()

  subject_rejects <- c(
  "ACTIVISM,1" , "ACTIVISM,2" , "AGRICULTURE,1" , "AGRICULTURE,2" , "AGRICULTURE,3" , "AGRICULTURE,4" , 
  "BAILOUT,1" , "BANKRUPTCY,1" , 
   "BLACK_MARKET,1" , "CHECKPOINT,1" , 
   "CIVIL_SOCIETY,1" , "CLIMATE_CHANGE,1" , "COAL,1" , "COAL,2" , "COAL,3" , "COMMON_ROBBERY,1" , "CORRUPTION,1" , "CORRUPTION,2"     , 
    "DISCRIMINATION,1" , "DISEASE,1" , "DISEASE,2" , "DISEASE,3" , "DISEASE,4" , 
    "DRUG_CARTELS,1" , "DRUG_TRADE,1" , "DRUGS,1" , "DRUGS,2" , "DRUGS,3" , 
    "EXCHANGE_RATE,1" , "FOOD_SECURITY,1" , 
       "HOUSING_PRICES,1" , 
          "ELECTRICITY_OUTAGE,1" , 
          "INT_FINANCIAL_INST,1" , "INT_FINANCIAL_INST,2" , "INTEREST_RATES,1" , "INTEREST_RATES,2" , "LABOR_STRIKE,1" , 
   "LABOR_UNIONS,1" , "LABOR_UNIONS,2" , "LABOR_UNIONS,4" , "LANDMINE,1" , "LGBT,1" , "LITERACY,1" , "MEDIA_CENSORSHIP,1" , "MONOPOLY,1" , 
   "MONOPOLY,2" , 
    "ORGANIZED_CRIME,1" , 
    "POSTSECONDARY_EDUCATION,1" , "POSTSECONDARY_EDUCATION,2" , "POSTSECONDARY_EDUCATION,3" , "POVERTY,1" , "PRIVATIZATION,1" , "PRIVATIZATION,2" , 
   "PUBLIC_TRANSIT,1" , "PUBLIC_TRANSIT,2" , "PUBLIC_TRANSIT,3" , "RAPE,1" , "REFUGEES,1" , "REFUGEES,2" , "REFUGEES,3" , "RENEWABLE_ENERGY,1" , 
   "SCHOOLS,1" , "SCHOOLS,2" , "SCHOOLS,3" , 
   "SEXTRANS_DISEASE,1" , "SHORTAGE,1" , "SOCIAL_MOVEMENT,1" , "STUDENTS,1" , "STUDENTS,2" , "STUDENTS,3" , "SUBSIDIES,1" , 
   "TEACHERS,1" , "TEACHERS,2" , 
    "UNEMPLOYMENT,1" , "VACCINATION,1" , 
   "VACCINATION,2" , "YOUTH_MOVEMENT,1" 
  )

cameo_actor_codes <- data.frame(
  stringsAsFactors = FALSE,
                                   code = c("ABN","ABW","ACC",
                                            "ADB","AEA","AEU","AFB","AFG",
                                            "AFGGOVTAL","AFGREBTAL","AFR","AFU",
                                            "AGO","AGOCAB","AGOREBUNI","AGR",
                                            "AGR","AIA","AIE","ALA","ALB",
                                            "ALQ","AMN","AMU","AND","ANT",
                                            "APE","ARB","ARB","ARBBTH","ARE",
                                            "ARG","ARL","ARM","ASA","ASA",
                                            "ASF","ASM","ASN","ATG","ATH",
                                            "ATH","AUS","AUT","AZE","BAH",
                                            "BCA","BDI","BEL","BEN","BFA",
                                            "BGD","BGR","BHR","BHS","BIH","BIH",
                                            "BIHBHF","BIHSRP","BIS","BLK",
                                            "BLR","BLZ","BMU","BOL","BRA",
                                            "BRB","BRN","BTN","BUD","BUD",
                                            "BUS","BUS","BUS","BWA","CAF",
                                            "CAN","CAS","CAU","CEM","CEU",
                                            "CFR","CHE","CHL","CHN","CHNTIC",
                                            "CHR","CHR","CHRCPT","CHRCTH",
                                            "CHRDOX","CHRJHW","CHRLDS","CHRMRN",
                                            "CHRPRO","CHRRAD","CIS","CIV",
                                            "CIV","CMN","CMR","CNY","COD",
                                            "COD Bangladesh","COE","COG","COG",
                                            "COK","COL","COL","COM","CON",
                                            "CON","COP","CPC","CPV","CRB",
                                            "CRI","CRM","CRM","CRO","CSK",
                                            "CSS","CTH","CUB","CVL","CVL",
                                            "CVL","CWN","CYM","CYP","CYPGRK",
                                            "CYPTRK","CZA","CZE","DDR","DEU",
                                            "DEV","DEV","DJI","DMA","DNK",
                                            "DOM","DZA","DZAGOVFLN",
                                            "DZAGOVMSP","DZAGOVRND","DZAOPPENN",
                                            "DZAOPPFIS","DZAOPPFLN","DZAOPPMSP",
                                            "DZAREBFIS","DZAREBGIA","DZAREBGSP",
                                            "EAC","EAF","EBR","ECU","EDU",
                                            "EDU","EEC","EEU","EFT","EGY",
                                            "EGYREBMBR","EIN","EIN","ELI","ELI",
                                            "ENV","ENV","ENV","ERI","ESH",
                                            "ESP","ESPBSQ","EST","ETH",
                                            "EUR","FID","FIN","FJI","FLK","FLK",
                                            "FRA","FRO","FRY","FRYKSV",
                                            "FRYMTN","FRYSRB","FRYVVD","FSM",
                                            "FSM","GAB","GBR","GBRREBIRA",
                                            "GEO","GGY","GHA","GIB","GIN","GLP",
                                            "GMB","GME","GMW","GNB","GNQ",
                                            "GOS","GOV","GOV","GRC","GRD",
                                            "GRL","GTM","GUF","GUM","GUY",
                                            "GYP","GZA","HCH","HCR","HIN",
                                            "HIN","HKG","HKG","HLH","HLH",
                                            "HMS","HND","HRI","HRV","HRV",
                                            "HRW","HTI","HUN","HUT","IAD","IAE",
                                            "ICC","ICG","ICJ","ICO","IDB",
                                            "IDN","IGC","IGO","IGO",
                                            "IGOAFRAFU","IGOAFRAGRIAC","IGOAFRBUSCES",
                                            "IGOAFRBUSCFA","IGOAFRDEVAFB",
                                            "IGOAFRDEVATD","IGOAFRDEVNEP",
                                            "IGOAFROAU","IGOAFRPAP","IGOAGRCPA",
                                            "IGOAGRCPC","IGOAGRICO","IGOAGRIGC",
                                            "IGOARBAPE","IGOARBDEVABD",
                                            "IGOBUSBIS","IGOBUSGOE","IGOBUSGOS",
                                            "IGOBUSGSS","IGOBUSHIP","IGOBUSIMF",
                                            "IGOBUSOPC","IGOBUSPRC","IGOBUSWTO",
                                            "IGOCAFBCA","IGOCAFCEM",
                                            "IGOCAFECA","IGOCASCIS","IGOCOPITP",
                                            "IGOCWN","IGOEAFDEVIAD","IGOEAFEAC",
                                            "IGOEURBUSEFT","IGOEURCOE",
                                            "IGOEURDEVEBR","IGOEUREEC","IGOEURSCE",
                                            "IGOJUDICC","IGOLEGIPU","IGOMEAACC",
                                            "IGOMEAAEU","IGOMEAAMF",
                                            "IGOMEAAMU","IGOMEAARL","IGOMOSDEVIDB",
                                            "IGOMOSOIC","IGONAFCSS","IGONON",
                                            "IGOOAS","IGOPGSGCC","IGOPKO",
                                            "IGOSAFDEVSAD","IGOSASSAA","IGOSEAASN",
                                            "IGOSEADEVADB","IGOSEASOT","IGOUNO",
                                            "IGOUNOAGRFAO","IGOUNOAIE",
                                            "IGOUNODEVWBK","IGOUNOHLHWHO",
                                            "IGOUNOHRIHCH","IGOUNOIAE","IGOUNOJUDICJ",
                                            "IGOUNOJUDWCT","IGOUNOKID",
                                            "IGOUNOLABILO","IGOUNOREFHCR","IGOUNOWFP",
                                            "IGOWAFDEVWAM","IGOWAFUEM",
                                            "IGOWAFWAD","IGOWAFWAS","IGOWEU",
                                            "IGOWSTNAT","IHF","ILO","IMF","IMG",
                                            "IMGMOSALQ","IMGSEAMOSASF",
                                            "IMGSEAMOSJMA","IMY","IND","INDKAS",
                                            "INS","INT","IPU","IRC","IRL",
                                            "IRN","IRQ","IRQBAG","IRQKURKDP",
                                            "ISI","ISL","ISR","ISRGOVCMN",
                                            "ISRGOVLBA","ISRGOVLKD","ISRGOVMRZ",
                                            "ISRGOVSHA","ISROPPLBA","ISROPPLKD",
                                            "ISROPPMRZ","ISROPPSHA","ISRSET",
                                            "ITA","ITP","JAM","JAN","JAN",
                                            "JEW","JEW","JEWHSD","JEWUDX",
                                            "JMA","JOR","JOROPPIAF","JPN",
                                            "JUD","JUD","JUR","KAS","KAZ","KEN",
                                            "KGZ","KHM","KHMREBKMR","KID",
                                            "KIR","KNA","KNA","KOR","KOR",
                                            "KSV","KUR","KWT","LAB","LAB",
                                            "LAM","LAO","LBN","LBNREBAML",
                                            "LBNREBASL","LBNREBHEZ","LBR",
                                            "LBRBOM","LBRBON","LBRCAP","LBRGBA",
                                            "LBRGGC","LBRGOVLAP","LBRGOVNDP",
                                            "LBRGOVNPF","LBRGOVUPP","LBRKRH",
                                            "LBRKRU","LBRLOF","LBRMAN","LBRMNT",
                                            "LBRMRG","LBRMRY","LBRNIM",
                                            "LBROPPALC","LBROPPLAP","LBROPPNDM",
                                            "LBROPPNDP","LBROPPUPP","LBRREBAFL",
                                            "LBRREBINP","LBRREBLPC",
                                            "LBRREBLUR","LBRREBNPF","LBRREBULM",
                                            "LBRRVC","LBRSIN","LBY","LCA","LEG",
                                            "LEG","LIE","LKA","LKAREBJVP",
                                            "LSO","LTU","LUX","LVA","MAC",
                                            "MAR","MARREBPLS","MCO","MDA","MDE",
                                            "MDG","MDT","MDV","MEA","MED",
                                            "MED","MEX","MHL","MIL","MIL",
                                            "MKD","MLI","MLT","MMR","MMR",
                                            "MNC","MNC","MNE","MNG","MNP",
                                            "MOD","MOD","MOS","MOS","MOSALE",
                                            "MOSDRZ","MOSRAD","MOSSFI",
                                            "MOSSHI","MOSSUN","MOZ","MRT","MSF",
                                            "MSR","MTN","MTQ","MUS","MWI",
                                            "MYS","MYT","NAF","NAM","NAT",
                                            "NCL","NER","NFK","NGA","NGAABI",
                                            "NGAABU","NGAADA","NGAAKI","NGAANB",
                                            "NGABAU","NGABAY","NGABIA",
                                            "NGABNU","NGABOR","NGACRR","NGADEL",
                                            "NGAEBO","NGAEKI","NGAENU",
                                            "NGAGOM","NGAHAU","NGAIBO","NGAIJW",
                                            "NGAIMO","NGAJIG","NGAKAD","NGAKAN",
                                            "NGAKAT","NGAKEB","NGAKOG",
                                            "NGAKWA","NGALAG","NGANAS","NGANDR",
                                            "NGANGR","NGANNG","NGAOGO",
                                            "NGAOGU","NGAOND","NGAOPPANP",
                                            "NGAOPPCFD","NGAOPPNDC","NGAOSU","NGAOYO",
                                            "NGAPLA","NGAREBMAD","NGARIV",
                                            "NGASOK","NGATAR","NGATIV","NGAYOB",
                                            "NGAYRB","NGAZAM","NGM",
                                            "NGMGRP","NGO","NGO","NGOCHRCSI",
                                            "NGOHLHCRC","NGOHLHIRC","NGOHLHMSF",
                                            "NGOHLHRCR","NGOHRIAMN","NGOHRIFID",
                                            "NGOHRIHRW","NGOHRIIHF","NGOICG",
                                            "NGOJUDJUR","NGOREFIOM","NGOUAJ",
                                            "NGOWEF","NGOXFM","NIC","NIU",
                                            "NIU","NLD","NMR","NOR","NPL",
                                            "NRU","NZL","OAS","OAU","OCC",
                                            "OIC","OMN","OPC","OPP","OPP","PAG",
                                            "PAK","PAKKAS","PAL","PALPLO",
                                            "PALREBANO","PALREBPLF","PAN",
                                            "PCN","PER","PGS","PHL","PLW",
                                            "PNG","PNGBOU","POL","PPL","PRI",
                                            "PRK","PRK","PRO","PRT","PRY",
                                            "PSE","PSE","PSEGOVFTA","PSEGOVHMS",
                                            "PSEGZS","PSEREBAAM","PSEREBDFL",
                                            "PSEREBHMS","PSEREBISJ",
                                            "PSEREBPFL","PSEWSB","PTY","PYF","QAT",
                                            "RAD","RAD","REB","REB","REB",
                                            "REF","REF","REL","REU","ROM",
                                            "ROU","RUS","RUSCNY","RWA",
                                            "RWAGOVRPF","RWAUAFRPF","SAA","SAD",
                                            "SAF","SAM","SAS","SAU","SCG","SCG",
                                            "SCGKSV","SCGMTN","SCGSRB",
                                            "SCGVVD","SCN","SDN","SDNDFR",
                                            "SDNREBNDA","SDNREBSPL","SEA","SEN",
                                            "SENREBMDF","SER","SGP","SHI",
                                            "SHN","SHN","SIK","SIK","SJM","SLA",
                                            "SLB","SLE","SLEREBKAM",
                                            "SLEREBRUF","SLV","SMR","SNL","SOM",
                                            "SOT","SPM","SPY","SPY","SRB",
                                            "SRB","SRBKSV","SRBVVD","SRP","SSD",
                                            "STP","SUN","SUR","SVK","SVN",
                                            "SWE","SWZ","SYC","SYR","TAM",
                                            "TAM","TAO","TAO","TCA","TCD",
                                            "TER","TGO","THA","TJK","TKL",
                                            "TKM","TMP","TMP","TON","TRG",
                                            "TRK","TTO","TUN","TUR","TURANK",
                                            "TURGOVAKP","TURGOVANP","TURGOVCHP",
                                            "TURGOVDSP","TURGOVDYP",
                                            "TURGOVMHP","TURGOVREP","TURIST","TURIZM",
                                            "TUROPPAKP","TUROPPANP",
                                            "TUROPPCHP","TUROPPDSP","TUROPPDTP",
                                            "TUROPPDYP","TUROPPFAZ","TUROPPHDP",
                                            "TUROPPMHP","TUROPPREP","TURREBDSL",
                                            "TURREBPKK","TURSOE","TUT","TUV",
                                            "TWN","TZA","UAF","UAF","UER",
                                            "UGA","UGAREBADF","UGAREBLRA",
                                            "UIG","UIG","UIS","UKR","UNO",
                                            "UNR","URY","USA","USR","UZB",
                                            "VAT","VCT","VEN","VGB","VIR","VIR",
                                            "VNM","VNM","VUT","WAD","WAF",
                                            "WAS","WBK","WCT","WEF","WFP",
                                            "WHO","WLF","WSM","WST","WST",
                                            "WTO","XFM","YEM","YMN","YMS",
                                            "YUG","YUG","YUGBSN","YUGCTA",
                                            "YUGKSV","YUGMCD","YUGMTN","YUGSLN",
                                            "YUGSRB","YUGVVD","ZAF","ZMB",
                                            "ZRO","ZWE"),
                                   name = c("ethnic Albanian",
                                            "Aruba","Arab Cooperation Council",
                                            "Asian Development Bank",
                                            "Association of Southeast Asian Nations Defense Ministers",
                                            "Arab Economic Unity Council","African Development Bank",
                                            "Afghanistan","Taliban (d.r.)",
                                            "Taliban (d.r.)","Africa","African Union",
                                            "Angola","Cabinda Enclave",
                                            "National Union for the Total Independence of Angola (UNITA)",
                                            "Agriculture (secondary role code)",
                                            "Agriculture-focused actors","Anguilla",
                                            "International Energy Agency",
                                            "˚Aland Islands","Albania","Al Qaeda",
                                            "Amnesty International",
                                            "Arab Maghreb Union","Andorra",
                                            "Netherlands Antilles",
                                            "Org of Arab Petroleum Exporting Countries","Arab (ethnic group)",
                                            "Arab","Baath Party",
                                            "United Arab Emirates","Argentina","Arab League",
                                            "Armenia","Asia (region)","Asia",
                                            "Abu Sayyaf","American Samoa",
                                            "Association of Southeast Asian Nations","Antigua and Barbuda",
                                            "Agnostic/Atheist","Atheist/Agnostic",
                                            "Australia","Austria","Azerbaijan",
                                            "Bahai",
                                            "Bank of Central African States","Burundi","Belgium","Benin",
                                            "Burkina Faso","Bangladesh",
                                            "Bulgaria","Bahrain","Bahamas",
                                            "Bosnia and Herzegovina (d.r.)",
                                            "Bosnia and Herzegovina",
                                            "Bosniak/Croat Federation of Bosnia and Herzegovina (d.r.)",
                                            "Bosnian Serb Republika Srpska (d.r.)",
                                            "Bank for International Settlements","Balkans","Belarus",
                                            "Belize","Bermuda","Bolivia","Brazil",
                                            "Barbados","Brunei Darussalam",
                                            "Bhutan","Buddhist","Buddhism",
                                            "Business (secondary role code)",
                                            "Business (NOT MNCs)","Business",
                                            "Botswana","Central African Republic",
                                            "Canada","Central Asia","Caucasus",
                                            "Cmn Mrkt for East and Southern Africa","Central Europe",
                                            "Central Africa","Switzerland","Chile","China",
                                            "Tibet","Christian",
                                            "Christianity","Coptic","Catholic","Orthodox",
                                            "Jehovah’s Witnesses",
                                            "Latter Day Saints","Maronite","Protestant",
                                            "“fundamentalist” Christian",
                                            "Commonwealth of Independent States",
                                            "Cte d’Ivoire (Ivory Coast)",
                                            "Cote d'Ivoire","Communist Party","Cameroon",
                                            "Chechnya",
                                            "Democratic Republic of the Congo (Kinshasa)",
                                            "Congo, Democratic Republic of",
                                            "Council of Europe",
                                            "People’s Republic of the Congo (Brazzaville)",
                                            "Congo, Republic of","Cook Islands","Colombia",
                                            "Columbia","Comoros","Confucian",
                                            "Confucianism",
                                            "Law enforcement agencies",
                                            "Association of Coffee Producing States","Cape Verde","Caribbean",
                                            "Costa Rica",
                                            "Criminal (secondary role code)","Criminal actors",
                                            "ethnic Croat","Czechoslovakia",
                                            "Community of Sahel-Saharan States",
                                            "Catholic","Cuba",
                                            "Civilian (secondary role code)","Civilians",
                                            "Civilian individuals/groups",
                                            "Commonwealth of Nations","Cayman Islands",
                                            "Cyprus","Greek Cypriot",
                                            "Turkish Cypriot","Czechoslovakia",
                                            "Czech Republic","East Germany","Germany",
                                            "Development (secondary role code)",
                                            "Development-focused actors","Djibouti",
                                            "Dominica","Denmark",
                                            "Dominican Republic","Algeria",
                                            "National Liberation Front (FLN)",
                                            "Movement of the Society for Peace",
                                            "Democratic National Rally","Ennahda Movement",
                                            "Islamic Salvation Front",
                                            "National Liberation Front (FLN)",
                                            "Movement of the Society for Peace",
                                            "Islamic Salvation Army",
                                            "Armed Islamic Group (GIA)","Salafist Group",
                                            "East African Community","Eastern Africa",
                                            "European Bank for Reconstruct and Dev","Ecuador",
                                            "Education (secondary role code)",
                                            "Education-focused actors","European Union",
                                            "Eastern Europe",
                                            "European Free Trade Association","Egypt","Muslim Brotherhood",
                                            "East Indies (region)",
                                            "East Indies","Elites (secondary role code)",
                                            "Elites, celebrities",
                                            "Environment (secondary role code)",
                                            "Environment-focused actors","Environmental",
                                            "Eritrea","Western Sahara","Spain",
                                            "Basque","Estonia","Ethiopia",
                                            "Europe",
                                            "International Federation of Human Rights","Finland","Fiji",
                                            "Falkland Islands (Malvinas)",
                                            "Falkland Islands","France",
                                            "Faeroe Islands",
                                            "Federal Republic of Yugoslavia","Kosovo (d.r.)",
                                            "Montenegro (d.r.)","Serbia (d.r.)",
                                            "Vojvodina (d.r.)","Micronesia",
                                            "Micronesia, Federated States of","Gabon",
                                            "United Kingdom","Irish Republican Army",
                                            "Georgia","Guernsey","Ghana",
                                            "Gibraltar","Guinea","Guadeloupe",
                                            "Gambia",
                                            "Democratic Republic of Germany (East Berlin)",
                                            "Federal Republic of Germany (Bonn)","Guinea-Bissau",
                                            "Equatorial Guinea",
                                            "Group of seven","Government (primary role code",
                                            "Government","Greece","Grenada",
                                            "Greenland","Guatemala",
                                            "French Guiana","Guam","Guyana","Gypsy",
                                            "Gaza Strip",
                                            "UN High Commission for Human Rights",
                                            "UN High Commission for Refugees","Hindu","Hinduism",
                                            "Hong Kong (Special Administrative Region of China)","Hong Kong",
                                            "Health (secondary role code)",
                                            "Health-focused actors","Hamas","Honduras",
                                            "Human rights-focused actors",
                                            "Croatia (d.r.)","Croatia",
                                            "Human Rights Watch","Haiti","Hungary",
                                            "Hutu (ethnic group)",
                                            "Intergovernmental Auth. on Development",
                                            "International Atomic Energy Agency",
                                            "International Criminal Court",
                                            "International Crisis Group",
                                            "International Court of Justice",
                                            "International Cocoa Organization",
                                            "Islamic Development Bank","Indonesia",
                                            "International Grains Council",
                                            "Inter-governmental organizations",
                                            "Inter-Government Organizations","African Union",
                                            "Inter-African Coffee Organization (IACO)",
                                            "Common Market for Eastern and Southern Africa",
                                            "Franc Zone Financial Community of Africa",
                                            "African Development Bank",
                                            "Eastern and Southern African Trade and Development Bank",
                                            "New Economic Partnership for Africa’s Development",
                                            "Organization of African Unity (OAU)",
                                            "Pan African Parliament",
                                            "Cocoa Producer’s Alliance",
                                            "Association of Coffee Producing Countries",
                                            "International Cocoa Organization (ICCO)",
                                            "International Grains Council",
                                            "Organization of Arab Petroleum Exporting Countries (OAPEC)",
                                            "Arab Bank for Economic Development in Africa",
                                            "Bank for International Settlements",
                                            "Group of Eight (G-8)","Group of Seven (G-7)",
                                            "Group of Seventy-Seven (G-77)",
                                            "Highly Indebted Poor Countries (HIPC)",
                                            "International Monetary Fund (IMF)",
                                            "Organization of Petroleum Exporting Countries (OPEC)","Paris Club",
                                            "World Trade Organization (WTO)",
                                            "Bank of Central African States (BEAC)",
                                            "Monetary and Economic Community of Central Africa (CEMAC)",
                                            "Economic Community of Central African States",
                                            "Commonwealth of Independent States","Interpol",
                                            "Commonwealth of Nations",
                                            "Intergovernmental Authority on Development (IGAD)",
                                            "East African Community",
                                            "European Free Trade Association","Council of Europe",
                                            "European Bank for Reconstruction and Development","European Union",
                                            "Council of Security and Cooperation in Europe (OSCE)",
                                            "International Criminal Court",
                                            "Inter-Parliamentary Union","Arab Cooperation Council",
                                            "Arab Economic Unity Council",
                                            "Arab Monetary Fund for Economic and Social Development","Arab Maghreb Union",
                                            "Arab League",
                                            "Islamic Development Bank",
                                            "Organization of Islamic Conferences (OIC)",
                                            "Community of Sahel-Saharan States (CENSAD)",
                                            "Organization of Non-Aligned Countries",
                                            "Organization of American States",
                                            "Gulf Cooperation Council",
                                            "Peacekeeping force (organization unknown)",
                                            "Southern African Development Community",
                                            "South Asian Association",
                                            "Association of Southeast Asian Nations (ASEAN)","Asian Development Bank",
                                            "Southeast Asia Collective Defense Treaty (SEATO)","United Nations",
                                            "United Nations Food and Agriculture Organization",
                                            "International Energy Agency","The World Bank",
                                            "World Health Organization (WHO)",
                                            "United Nations High Commission for Human Rights (OHCHR)",
                                            "International Atomic Energy Agency (IAEA)",
                                            "International Court of Justice (ICJ)",
                                            "International War Crimes Tribunals",
                                            "United Nations Children’s Fund (UNICEF)",
                                            "International Labor Organization",
                                            "United Nations High Commission for Refugees (OHCR)","World Food Program",
                                            "West Africa Monetary and Economic Union",
                                            "Economic and Monetary Union of West Africa (UEMOA)",
                                            "West Africa Development Bank",
                                            "Economic Community of West African States (ECOWAS)",
                                            "Western European Union",
                                            "North Atlantic Treaty Organization (NATO)",
                                            "Internat. Helsinki Fed for Human Rights",
                                            "International Labor Organization","International Monetary Fund",
                                            "International Militarized Group",
                                            "Al Qaeda","Abu Sayyaf",
                                            "Jemaah Islamiya","Isle of Man","India",
                                            "Indian-controlled Kashmir",
                                            "Insurgents",
                                            "Ambiguous international or transnational actor",
                                            "Inter-Parliamentary Union",
                                            "International Red Cross","Ireland","Iran","Iraq",
                                            "Baghdad",
                                            "Kurdish Democratic Party (KDP)","ISIS/ISIL","Iceland","Israel",
                                            "Israeli Communist Party (d.r.)",
                                            "Israeli Labor Party (d.r.)",
                                            "Likud Party (d.r.)","Meretz Party (d.r.)",
                                            "Shas Party (d.r.)",
                                            "Israeli Labor Party (d.r.)",
                                            "Likud Party (d.r.)","Meretz Party (d.r.)",
                                            "Shas Party (d.r.)","Israeli Settlers",
                                            "Italy","Interpol","Jamaica","Jain",
                                            "Jainism","Jew","Judaism",
                                            "Hasidic Jew","Ultra-Orthodox Jew",
                                            "Jemaah Islamiya","Jordan",
                                            "Islamic Action Front","Japan",
                                            "Judiciary (primary role code)","Judicial actors",
                                            "International Commission of Jurists",
                                            "Kashmir","Kazakhstan","Kenya",
                                            "Kyrgyzstan","Cambodia",
                                            "Khmer Rouge",
                                            "United Nations Children's Fund","Kiribati","Saint Kitts-Nevis",
                                            "Saint Kitts and Nevis",
                                            "Republic of Korea (Seoul)",
                                            "Korea, Republic of","Kosovo","Kurd (ethnic group)",
                                            "Kuwait",
                                            "Labor (secondary role code)","Labor-focused actors",
                                            "Latin America","Laos","Lebanon",
                                            "Amal Militia","South Lebanon Army",
                                            "Hezbullah","Liberia","Bomi (Liberia)",
                                            "Bong (Liberia)",
                                            "Grand Cape Mount (Liberia)",
                                            "Grand Bassa (Liberia)","Grand Gedeh (Liberia)",
                                            "Liberia Action Party (d.r.)",
                                            "National Democratic Party of Liberia (d.r.)",
                                            "National Patriotic Front of Liberia (NPFL) (d.r.)",
                                            "United People’s Party (d.r.)","Krahn (ethnic group)",
                                            "Grand Kru (Liberia)",
                                            "Lofa (Liberia)",
                                            "Mandingo, Mandingoe (ethnic group)","Montserrado (Liberia)",
                                            "Margibi (Liberia)","Maryland (Liberia)",
                                            "Nimba (Liberia)",
                                            "All Liberia Coalition Party",
                                            "Liberia Action Party (d.r.)","New Deal Movement",
                                            "National Democratic Party of Liberia (d.r.)",
                                            "United People’s Party (d.r.)","Armed Forces of Liberia (d.r.)",
                                            "Independent NPFL",
                                            "Liberia Peace Council",
                                            "Liberians United for Reconciliation and Democracy (LURD)",
                                            "National Patriotic Front of Liberia (NPFL) (d.r.)",
                                            "United Liberation Front for Democracy",
                                            "Rivercess (Liberia)","Sino (Liberia)","Libya",
                                            "Saint Lucia",
                                            "Legislature (secondary role code)",
                                            "Legislative bodies/actors","Liechtenstein","Sri Lanka",
                                            "People’s Liberation Front",
                                            "Lesotho","Lithuania","Luxembourg",
                                            "Latvia",
                                            "Macao (Special Administrative Region of China)","Morocco",
                                            "Polisario Guerillas","Monaco",
                                            "Moldova","Middle East","Madagascar",
                                            "Mediterranean","Maldives",
                                            "Middle East","Medical (secondary role code)",
                                            "Media-related actors/organizations","Mexico","Marshall Islands",
                                            "MIlitary (primary role code)",
                                            "Military","Macedonia","Mali","Malta",
                                            "Myanmar (Burma)","Myanmar",
                                            "Multi-national corporation",
                                            "Multinational Corporation","Montenegro",
                                            "Mongolia","Northern Mariana Islands",
                                            "Moderate (tertiary role code)",
                                            "Moderate/mainstream group","Muslim",
                                            "Islam","Alewi","Druze",
                                            "“Fundamentalist,” “radical,” “extremist” Muslim","Sufi","Shia","Sunni",
                                            "Mozambique","Mauritania",
                                            "Doctors Without Borders","Montserrat",
                                            "Montenegro","Martinique","Mauritius",
                                            "Malawi","Malaysia","Mayotte",
                                            "North Africa","Namibia",
                                            "North Atlantic Treaty Organization","New Caledonia",
                                            "Niger","Norfolk Island",
                                            "Nigeria","Abia (Nigeria)",
                                            "Abuja (Nigeria)","Adamawa (Nigeria)",
                                            "Akwa Ibom (Nigeria)","Anambra (Nigeria)",
                                            "Bauchi (Nigeria)",
                                            "Bayelsa (Nigeria)","Biafra (Nigeria)",
                                            "Benue (Nigeria)","Borno (Nigeria)",
                                            "Cross River (Nigeria)","Delta (Nigeria)",
                                            "Edo (Nigeria)","Ekiti (Nigeria)",
                                            "Enugu (Nigeria)","Gombe (Nigeria)",
                                            "Hausa (ethnic group)",
                                            "Ibo, Igbo (ethnic group)",
                                            "Ijaws (ethnic group)","Imo (Nigeria)",
                                            "Jigawa (Nigeria)","Kaduna (Nigeria)",
                                            "Kano (Nigeria)","Katsina (Nigeria)",
                                            "Kebbi (Nigeria)","Kogi (Nigeria)",
                                            "Kwara (Nigeria)","Lagos (Nigeria)",
                                            "Nassarawa (Nigeria)",
                                            "Niger Delta Region (Nigeria)","Niger (Nigeria)",
                                            "North Nigeria (Nigeria)",
                                            "Ogoni (ethnic group)","Ogun (Nigeria)",
                                            "Ondo (Nigeria)",
                                            "All Nigeria People’s Party","Campaign for Democracy",
                                            "National Democratic Coalition of Nigeria (NADECO)","Osun (Nigeria)",
                                            "Oyo (Nigeria)","Plateu State (Nigeria)",
                                            "Movement for the Advancement of Democracy (MAD)","Rivers (Nigeria)",
                                            "Sokoto (Nigeria)",
                                            "Taraba (Nigeria)","Tiv (ethnic group, language)",
                                            "Yobe (Nigeria)",
                                            "Yoruba (ethnic group)","Zamfara (Nigeria)",
                                            "Non-governmental movements","Greenpeace",
                                            "Non-governmental organizations",
                                            "Non-Governmental Organization",
                                            "Christian Solidarity International",
                                            "International Fed. of Red Cross and Red Crescent (ICRC)","Red Cross",
                                            "Medecins Sans Frontieres (Doctors Without Borders)","Red Crescent",
                                            "Amnesty International",
                                            "International Federation of Human Rights (FIDH)",
                                            "Human Rights Watch",
                                            "International Helsinki Federation for Human Rights","International Crisis Group",
                                            "International Commission of Jurists",
                                            "International Organization for Migration","Union of Arab Journalists",
                                            "World Economic Forum","Oxfam",
                                            "Nicaragua","Niue","Niue Island",
                                            "Netherlands","North America",
                                            "Norway","Nepal","Nauru","New Zealand",
                                            "Organization of American States",
                                            "Organization of African Unity",
                                            "Occupied",
                                            "International Cocoa Organization","Oman",
                                            "Org. of Petroleum Exporting Countries",
                                            "Opposition (primary role code)",
                                            "Opposition groups (often parliamentary)",
                                            "Animist/Pagan","Pakistan",
                                            "Pakistani-controlled Kashmir","Palestinian",
                                            "Palestine Liberation Organization",
                                            "Abu Nidal Organization",
                                            "Palestine Liberation Front","Panama","Pitcairn",
                                            "Peru","Persian Gulf",
                                            "Philippines","Palau","Papua New Guinea",
                                            "Bougainville","Poland","Papel",
                                            "Puerto Rico",
                                            "Democratic People’s Rep. of Korea (Pyongyang)",
                                            "Korea, Democratic People's Republic of",
                                            "Protestant","Portugal","Paraguay",
                                            "Palestinian Occupied Territories",
                                            "Palestine","Fatah (d.r.)",
                                            "Hamas (d.r.)","Gaza Strip",
                                            "Al Aqsa Martyrs Brigade",
                                            "Democratic Front for the Liberation of Palestine (DFLP)",
                                            "Hamas (d.r.)",
                                            "Palestinian Islamic Jihad",
                                            "People’s Front for the Liberation of Palestine (PFLP)",
                                            "West Bank","Political party",
                                            "French Polynesia","Qatar",
                                            "Radical (tertiary role code)",
                                            "Radical/extremist/fundamentalist",
                                            "Rebel (primary role code)","Rebels/insurgents",
                                            "Rebel / insurgents",
                                            "Refugee (secondary role code)","Refugee-focused actors",
                                            "Unspecified religious","Runion",
                                            "Romania","Romania","Russia",
                                            "Chechnya","Rwanda",
                                            "Rwandan Patriotic Front (d.r.)",
                                            "Rwandan Patriotic Front (d.r.)",
                                            "South Asian Association",
                                            "Southern African Development Community","Southern Africa",
                                            "South America","South Asia",
                                            "Saudi Arabia","Serbia and Montenegro (d.r.)",
                                            "Serbia and Montenegro",
                                            "Kosovo (d.r.)","Montenegro (d.r.)",
                                            "Serbia (d.r.)","Vojvodina (d.r.)",
                                            "Scandinavia","Sudan","Darfur",
                                            "National Democratic Alliance",
                                            "Sudan People’s Liberation Army","Southeast Asia",
                                            "Senegal",
                                            "Movement of Democratic Forces of Casamance","ethnic Serb",
                                            "Singapore","Shia",
                                            "Saint Helena","Shintoism","Sikh","Sikhism",
                                            "Svalbard and Jan Mayen Islands",
                                            "Slav","Solomon Islands",
                                            "Sierra Leone","Kamojor militia",
                                            "Revolutionary United Front","El Salvador",
                                            "San Marino","Sinhalese (ethnic group)",
                                            "Somalia",
                                            "SE Asia Collective Defense Treaty",
                                            "Saint Pierre and Miquelon","Spy (primary role code)",
                                            "Intelligence agencies",
                                            "Serbia (d.r.)","Serbia","Kosovo (d.r.)",
                                            "Vojvodina (d.r.)","Republica Srpska",
                                            "South Sudan",
                                            "Sao Tome and Principe","Soviet Union","Suriname",
                                            "Slovakia","Slovenia","Sweden",
                                            "Swaziland","Seychelles","Syria",
                                            "Tamil (ethnic group)","Tamil","Taoist",
                                            "Taoism","Turks and Caicos Islands",
                                            "Chad",
                                            "Terai (region in northern India/southern Nepal)","Togo",
                                            "Thailand","Tajikistan","Tokelau",
                                            "Turkmenistan",
                                            "East Timor (Timor-Leste)","East Timor","Tonga",
                                            "Tuareg (ethnic group)","ethnic Turk",
                                            "Trinidad and Tobago","Tunisia",
                                            "Turkey","Ankara",
                                            "Justice and Development Party (AKP) (d.r.)",
                                            "Motherland Party (ANAP) (d.r.)",
                                            "Republican People’s Party (CHP) (d.r.)",
                                            "Democratic Left Party (DSP) (d.r.)",
                                            "True Path Party (DYP) (d.r.)",
                                            "National Action Party (MHP) (d.r.)",
                                            "Welfare Party (Refah) (d.r.)","Istanbul",
                                            "Izmir",
                                            "Justice and Development Party (AKP) (d.r.)",
                                            "Motherland Party (ANAP) (d.r.)",
                                            "Republican People’s Party (CHP) (d.r.)",
                                            "Democratic Left Party (DSP) (d.r.)",
                                            "Democratic Society Party (DTP)",
                                            "True Path Party (DYP) (d.r.)",
                                            "Virtue Party (Fazilet)",
                                            "Democratic People’s Party (DEHAP/HADEP)",
                                            "National Action Party (MHP) (d.r.)",
                                            "Welfare Party (Refah) (d.r.)","Dev-Sol",
                                            "Kurdistan Workers’ Party (PKK)",
                                            "Southeast Turkey","Tutsi (ethnic group)",
                                            "Tuvalu","Taiwan","Tanzania",
                                            "Unidentified Armed Force (tertiary role code)","Unaffiliated armed forces",
                                            "International Academy of Architecture","Uganda",
                                            "Allied Democratic Forces","Lord’s Resistance Army",
                                            "Uighur (Chinese ethnic minority)",
                                            "Uighur","Unidentified state actors",
                                            "Ukraine","United Nations",
                                            "Unrecognized","Uruguay","United States",
                                            "Union of Soviet Socialist Republics (USSR)","Uzbekistan",
                                            "Holy See (Vatican City)",
                                            "Saint Vincent and the Grenadines","Venezuela",
                                            "British Virgin Islands",
                                            "U.S. Virigin Islands","U.S. Virgin Islands",
                                            "Vietnam","Viet Nam","Vanuatu",
                                            "West African Development Bank","West Africa",
                                            "Econ Community of West African States","World Bank",
                                            "International War Crimes Tribunals",
                                            "World Economic Forum","World Food Program",
                                            "World Health Organization",
                                            "Wallis and Futuna Islands","Samoa",
                                            "“the West”","the West",
                                            "World Trade Organization","Oxfam","Yemen",
                                            "North Yemen","South Yemen",
                                            "Socialist Federal Republic of Yugoslavia (d.r.)",
                                            "Yugoslavia",
                                            "Yugoslavia’s Republic of Bosnia (d.r.)",
                                            "Yugoslavia’s Republic of Croatia (d.r.)",
                                            "Kosovo (d.r.)",
                                            "Yugoslavia’s Republic of Macedonia (d.r.)",
                                            "Montenegro (d.r.)",
                                            "Yugoslavia’s Republic of Slovenia (d.r.)",
                                            "Yugoslavia’s Republic of Serbia (d.r.)","Vojvodina (d.r.)",
                                            "South Africa","Zambia",
                                            "Zoroastrian","Zimbabwe")
                     )

cameo_actor_codes <- cameo_actor_codes %>% filter(!duplicated(code)) %>% 
  mutate(name = name %>% 
           str_replace_all("\\(secondary role code\\)|\\(primary role code\\)","") %>% 
           str_replace_all("\\(secondary role code\\)|\\(secondary role code|\\(primary role code|\\(primary role code\\)","")   %>% 
           str_replace_all(" \\)","")   %>% 
           trimws()
         )
dim(cameo_actor_codes)

```

```{r ICB Data Loads , eval=T, results='hide', echo=F, include=T, message=F, cache=F}
#ICB Data Loads

#Note yemen 679 doesn't show up in this data
icb_df <- data.frame(
  stringsAsFactors = FALSE,
          icb_name = c("Afghanistan","Albania",
                       "Algeria","Andorra","Angola","Antigua & Barbuda",
                       "Argentina","Armenia","Australia","Austria","Azerbaijan",
                       "Bahamas","Bahrain","Bangladesh","Barbados","Belarus",
                       "Belgium","Belize","Benin (Dahomey)","Bhutan","Bolivia",
                       "Bosnia","Botswana","Brazil","Brunei","Bulgaria",
                       "Burkina Faso (Upper Volta)","Burma (see Myanmar)",
                       "Burundi","Cambodia","Cameroon","Canada","Cape Verde",
                       "Central African Republic","Chad","Chile","China",
                       "China","Colombia","Comoros","Congo Brazzaville",
                       "Congo, Democratic","Costa Rica","Cote D’Ivoire","Croatia",
                       "Cuba","Cyprus","Czech Republic","Czechoslovakia",
                       "Dahomey (see Benin)","Denmark","Djibouti (Somalia Fr.)",
                       "Dominica","Dominican Republic","Ecuador","Egypt (UAR)",
                       "El Salvador","Equatorial Guinea","Eritrea","Estonia",
                       "Ethiopia","Federated States of Micronesia","Fiji",
                       "Finland","Formosa","France","French West Africa",
                       "Gabon","Gambia","Georgia",
                       "German Democratic Republic (East Germany)",
                       "Germany (German Federal Republic, West Germany)","Germany (Prussia)","Ghana",
                       "Great Britain (see United Kingdom)","Greece","Grenada","Guatemala",
                       "Guinea","Guinea Bissau","Guyana","Haiti","Hijaz (Hejaz)",
                       "Honduras","Hungary","Iceland","India","Indonesia",
                       "Iran","Iraq","Ireland (Eire)","Israel","Italy",
                       "Ivory Coast (see Cote D’Ivoire)","Jamaica","Japan",
                       "Jordan","Kazakhstan","Kenya","Korea","Kosovo","Kuwait",
                       "Kyrgyz Republic","Laos","Latvia","Lebanon","Lesotho",
                       "Liberia","Libya","Liechtenstein","Lithuania",
                       "Luxemberg","Macedonia","Madagascar (Malagasy Republic)",
                       "Malawi","Malaysia","Maldives","Mali","Malta",
                       "Marshall Islands","Mauritania","Mauritius","Mexico","Moldova",
                       "Monaco","Mongolia","Morocco","Mozambique",
                       "Myanmar (Burma)","Najd (Nejd)","Namibia (South West Africa)",
                       "Nepal","Netherlands","Nevis","New Zealand",
                       "Nicaragua","Niger","Nigeria",
                       "North Korea (People’s Republic of Korea)","Norway","Oman","Pakistan","Palau","Panama",
                       "Papua and New Guinea","Paraguay","Peru",
                       "Philippines","Poland","Portugal","Principe","Qatar",
                       "Republic of (Congo Kinshasa) (Zaire)","Rhodesia (see Zimbabwe)",
                       "Rumania","Russia (Soviet Union)","Rwanda",
                       "San Marino","Sao Tome","Saudi Arabia","Senegal",
                       "Serbia (see Yugoslavia)","Seychelles","Sierra Leone","Singapore",
                       "Slovakia","Slovenia","Solomons","Somalia",
                       "Somalia Fr. (see Djibouti)","South Africa",
                       "South Korea (Republic of Korea)","South Sudan",
                       "South West Africa (see Namibia)","Spain","Spanish Sahara (see Western Sahara)",
                       "Sri Lanka (Ceylon)","St. Kitts","St. Lucia",
                       "St. Vincent & The Grenadines","Sudan","Surinam","Swaziland",
                       "Sweden","Switzerland","Syria","Taiwan (China",
                       "Tajikistan","Tanzania","Thailand","Tibet","Togo",
                       "Trinidad & Tobago","Tunisia","Turkey","Turkmenistan","Uganda",
                       "Ukraine","United Arab Emirates",
                       "United Kingdom (Great Britain)","Upper Volta (see Burkina Faso)","Uruguay",
                       "USA","USSR (see Russia)","Uzbekistan","Vanuatu",
                       "Venezuela","Vichy France",
                       "Vietnam, Democratic Republic of (North Vietnam)","Vietnam, Republic of (South Vietnam)",
                       "Western Sahara (Spanish Sahara)","Western Samoa",
                       "Yemen (Arab Republic of Yemen, North Yemen)",
                       "Yemen, People’s Republic of (South Yemen)","Yugoslavia (Serbia)",
                       "Zambia","Zanzibar","Zimbabwe (Rhodesia)"),
       icb_letters = c("AFG","ALB","ALG","AND",
                       "ANG","AAB","ARG","ARM","AUL","AUS","AZE","BHM",
                       "BAH","BNG","BAR","BLR","BEL","BLZ","BEN","BHU","BOL",
                       "BOS","BOT","BRA","BRU","BUL","BFO",NA,"BUI",
                       "CAM","CAO","CAN","CAP","CEN","CHA","CHL",NA,"CHN",
                       "COL","COM","CON","DRC","COS","CDI","CRO","CUB",
                       "CYP","CZR","CZE",NA,"DEN","DJI","DMA","DOM",
                       "ECU","EGY","SAL","EQG","ERI","EST","ETH","FSM","FIJ",
                       "FIN","TAW","FRN","FWA","GAB","GAM","GRG","GDR",
                       "GFR","GMY","GHA",NA,"GRC","GRN","GUA","GUI",
                       "GNB","GUY","HAI","HIJ","HON","HUN","ICE","IND",
                       "INS","IRN","IRQ","IRE","ISR","ITA",NA,"JAM","JPN",
                       "JOR","KZK","KEN","KOR","KOS","KUW","KYR","LAO",
                       "LAT","LEB","LES","LBR","LIB","LIE","LIT","LUX",
                       "MAC","MAG","MAW","MAL","MAD","MLI","MLT","MSI",
                       "MAA","MAS","MEX","MLD","MNC","MON","MOR","MZM","MYA",
                       "NAJ","NAM","NEP","NTH","SKN","NEW","NIC","NIR",
                       "NIG","PRK","NOR","OMA","PAK","PAL","PAN","PNG",
                       "PAR","PER","PHI","POL","POR","STP","QAT","DRC",
                       NA,"RUM","RUS","RWA","SNM",NA,"SAU","SEN",NA,
                       "SEY","SIE","SIN","SLO","SLV","SOL","SOM",NA,"SAF",
                       "ROK","SSD",NA,"SPN",NA,"SRI",NA,"SLU","SVG",
                       "SUD","SUR","SWA","SWD","SWZ","SYR",NA,"TAJ","TAZ",
                       "THI","TBT","TOG","TRI","TUN","TUR","TKM","UGA",
                       "UKR","UAE","UKG",NA,"URU","USA",NA,"UZB","VAN",
                       "VEN","VFR","DRV","RVN","SPA","WSM","YEM","YPR",
                       "YUG","ZAM","ZAN","ZIM"),
          icb_code = c("700","339","615","232",
                       "540","058","160","371","900","305","373","031",
                       "692","771","053","370","211","080","434","760","145",
                       "346","571","140","835","355","439",NA,"516",
                       "811","471","020","402","482","483","155",NA,"710",
                       "100","581","484","490","094","437","344","040",
                       "352","316","315",NA,"390","522","054","042",
                       "130","651","092","411","531","366","530","987","950",
                       "375","713","220","480","481","420","372","265",
                       "260","255","452",NA,"350","55","090","438",
                       "404","110","041","671","091","310","395","750","850",
                       "630","645","205","666","325",NA,"051","740",
                       "663","705","501","730","347","690","703","812",
                       "367","660","570","450","620","223","368","212",
                       "343","580","553","820","781","432","338","983","435",
                       "590","070","359","221","712","600","541","775",
                       "672","565","790","210","060","920","093","436",
                       "475","731","385","698","770","986","095","910",
                       "150","135","840","290","235","403","694","490",NA,
                       "360","365","517","331",NA,"670","433",NA,"591",
                       "451","830","317","349","940","520",NA,"560",
                       "732","626",NA,"230",NA,"780",NA,"056","057","625",
                       "115","572","380","225","652",NA,"702","510",
                       "800","711","461","052","616","640","701","500",
                       "369","696","200",NA,"165","002",NA,"704","935",
                       "101","219","816","817","605","990","678","680",
                       "345","551","511","552")
)

df_IWCA <- data.frame(
  stringsAsFactors = FALSE,
              IWCA = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L, 10L),
        IWCA_label = c("not an intra-war crisis (IWC)",
                       "Entry of a major actor into an ongoing war",
                       "Perceived high probability of a major actor entering a war",
                       "Exit of a major actor",
                       "Perceived high probability of major power exiting a war",
                       "Technological escalation of a war","Major non-technological escalation",
                       "Defeat in a significant battle","Internal deterioration","Other")
)

df_break <- 
data.frame(
  stringsAsFactors = FALSE,
             BREAK = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
       BREAK_label = c("Verbal act","Political act",
                       "Economic act","External change",
                       "Other non-violent act",
                       "Internal verbal or physical challenge to regime or elite","Non-violent military act","Indirect violent act",
                       "Violent act")
)

#icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
icbdy_20 <- readRDS(paste0(here::here(), '/replication_paper/data/in/icbdy_20.Rds'))

icbdy_20_clean <- icbdy_20 %>%
                  left_join( icb_df %>% dplyr::select(STATEA=icb_code, actor_1=icb_name ) %>% mutate(STATEA=STATEA %>% as.numeric())  ) %>%
                  left_join( icb_df %>% dplyr::select(STATEB=icb_code, actor_2=icb_name ) %>% mutate(STATEB=STATEB %>% as.numeric())  ) %>%
                  left_join(df_IWCA %>% dplyr::select(IWCA=IWCA, IWCA_label=IWCA_label )  ) %>%
                  left_join(df_IWCA %>% dplyr::select(IWCB=IWCA, IWCB_label=IWCA_label )  )

icb_diadic <- icbdy_20_clean %>% dplyr::select(CRISNO, NAMEA, NAMEB,  STATEA, STATEB, actor_1,actor_2, IWCA_label,IWCB_label) #%>% filter(is.na(actor_1) | is.na(actor_2))

icb2v14 <- read_csv(paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))

df_trigger <- data.frame(
  stringsAsFactors = FALSE,
            triggr = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                    triggr_label = c("Verbal act","Political act","Economic act",
                                     "External change","Other non-violent act",
                                     "Internal verbal or physical challenge to regime or elite",
                                     "Non-violent military act","Indirect violent act","Violent act")
              )

df_majres <- data.frame(
  stringsAsFactors = FALSE,
            majres = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                   majres_label = c("No response-inaction","Verbal act",
                                    "Political act","Economic act",
                                    "Other non-violent act",
                                    "Non-violent military act",
                                    "Multiple including non-violent military act",
                                    "Violent military act",
                                    "Multiple including violent military act")
             )

df_outcome <- 
data.frame(
  stringsAsFactors = FALSE,
            outcom = c(1L, 2L, 3L, 4L, 5L),
      outcom_label = c("Victory", "Compromise", "Stalemate", "Defeat", "Other")
)

df_outfor <- 
data.frame(
  stringsAsFactors = FALSE,
            outfor = c(1L,2L,3L,4L,5L,6L,7L,8L,
                       9L,10L,11L,12L,13L,14L,15L),
      outfor_label = c("Formal agreement - voluntary",
                       "Semi-formal agreement - voluntary",
                       "Tacit understanding","Unilateral - self","Unilateral - ally",
                       "Unilateral - adversary","Compliance","Imposed - imposer",
                       "Imposed - imposee","Spillover",
                       "Other - global organization intervention","Other - ally",
                       "Other - internal or non-state actor","Other - misc.","Faded")
)

icb2v14_clean <- icb2v14 %>% 
                 left_join(icb_df %>% dplyr::select(cracid=icb_code, actor_label=icb_name ) %>% mutate(cracid=cracid %>% as.numeric()) ) %>%  #you can't actually match on the letter codes you have to match on the numbers, uhhhhhg
                 left_join( df_trigger  ) %>% 
                 left_join( df_majres ) %>% 
                 left_join( df_outcome ) %>% 
                 left_join( df_outfor )

icb_monadic <-  
  bind_rows(
   icb2v14_clean%>% mutate(sent= yrtrig + tidyr::replace_na((motrig/12),0) + tidyr::replace_na(datrig/31/12,0) ) %>% mutate(type='start') %>% dplyr::select(year=yrtrig, month=motrig, crisno,type, sent, actor_label, leaf=triggr_label),
   icb2v14_clean %>% mutate(sent= yerres + tidyr::replace_na((monres/12),0) + tidyr::replace_na(dayres/31/12,0) ) %>% mutate(type='mid') %>% dplyr::select(year=yerres, month=monres, crisno,type, sent, actor_label, leaf=majres_label),
   icb2v14_clean %>% mutate(sent= yrterm + tidyr::replace_na((moterm/12),0) + tidyr::replace_na(daterm/31/12,0) ) %>% mutate(type='end') %>% dplyr::select(year=yrterm, month=moterm, crisno,type, sent, actor_label, leaf=outfor_label)
  ) %>% as.data.frame()

```

```{r icb crisis maps, eval=T, results='hide', echo=F, include=T, message=F, cache=F}

library(igraph)
library(ggraph)
#ICB Function {Plots
icb_crisismaps <- function(thiscrisis=196, prune_rare=T){

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icb_metro_plot_",thiscrisis,".Rds")

    icb_diadic_subset <- icb_diadic %>% filter(CRISNO==thiscrisis) #Not all of them are diadic apparently
    icb_monadic_subset <- icb_monadic %>% rename(actor=actor_label) %>% filter(crisno==thiscrisis) %>%
                       mutate(sent=sent %>% rank() %>% round()) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") ))   %>% arrange(sent, actor)

    g <- make_empty_graph(n = 0, directed = TRUE)
      #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

    icb_events_subset_diad <- bind_rows(
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>% 
                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>%
              rename(actor_2=actor_1,actor_1=actor_2),
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>%
                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),

            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>%
                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>%
              rename(actor_2=actor_1,actor_1=actor_2),
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>% 
                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),

            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>%
              rename(actor_2=actor_1,actor_1=actor_2),
            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),

          ) %>% dplyr::select(year, month,sent, actor_1, actor_2, leaf) %>% distinct() %>% na.omit()

     if(nrow(icb_events_subset_diad)==0){
      print("No dyadic icb rows skipping")
      return()
    }

    #Order actors by how many interactions they have together
    temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()

    temp2 <- bind_rows(
      temp,
      temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
    ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

    temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
    rownames(temp2_wide) <- temp2_wide$actor_1
    temp2_wide$actor_1 <- NULL
    temp2_wide <- temp2_wide %>% as.matrix()
    temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
    temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
    hc <- hclust(temp2_wide %>% as.dist(), method="single")

    temp_list <- list()
    for(i in 1:nrow(temp2_wide)){
      temp_list[[as.character(i)]] <- cutree(hc, k=i)
    }

    #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
    #  arrange(across(starts_with("V")))
    ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

    #####Nodes
    icb_events_subset_nodes <- 
              bind_rows(
                        icb_events_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_1) ,
                        icb_events_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_2) 
              ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
              mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                     y=sent*-1 *100)

    #we centralize everything in qcodes so colors should be consistent across plots for the same actors    
    icbe_actor_to_qcode <- icb_events_long %>%
                       dplyr::filter(crisno==thiscrisis  ) %>% 
                       filter(varname_normalized %>% str_detect("actor")) %>% 
                       dplyr::select(value_normalized,value_qcode) %>% 
                       na.omit() %>% distinct()

    actor_colors_df <- icbe_actor_to_qcode %>%
      left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
    actor_colors <- actor_colors_df$actor_color
    names(actor_colors) = actor_colors_df$value_normalized

    actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
    actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
    names(actor_colors) = levels(actors)

    date_sineposts <- icb_events_subset_nodes  %>%
                        mutate(x=max(x)+50) %>%
                        dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
                        na.omit() %>% 
                        distinct() %>%  
                        mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                        mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                        group_by(sent) %>%
                        filter(year_float==min(year_float)) %>%
                        ungroup() %>% as.data.frame() %>%
                        filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                        filter(!duplicated(year_float ) ) %>%
                        mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

    ####Actor levels
    icb_events_subset_nodes_min <- 
                  icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
                  #left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
                  #rename(qcode=actor, actor=value_normalized_label) %>%
                  rowwise() %>%
                  mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

    for(i in 1:nrow(icb_events_subset_nodes)){
      g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
                                  actor = icb_events_subset_nodes$actor[i], 
                                  sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
    }

    xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )

    #####Time Edges
    icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% 
      janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

    g <- g %>% 
         add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                   actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)

    ######Directed
    icb_events_subset_directed <- 
              icb_events_subset_diad %>% 
              dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
              mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
                summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
              #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

    g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                         timeedge=F, 
                         leaf=icb_events_subset_directed$leaf, 
                         eventedge=T,
                         actor=icb_events_subset_directed$actor_1)

    p_icb_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T #& bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=global_check_overlap,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

      p_icb_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
      p_icb_metro_map$actor_colors <- actor_colors
      p_icb_metro_map$icb_monadic_subset <- icb_monadic_subset

      p_icb_metro_map %>% saveRDS(save_icb_file)

}

c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x))

```

```{r mids data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

mid4_df <- data.frame(
  stringsAsFactors = FALSE,
               act = c(1L,2L,3L,4L,5L,6L,7L,8L,
                       9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
                       20L,21L,22L),
         act_label = c("1. None (1)",
                       "2. Threat to use force (2)",
                       "3. Threat to blockade (2)",
                       "4. Threat to occupy terr. (2)",
                       "5. Threat to declare war (2)",
                       "6. Threat to join war (2)",
                       "7. Show of troops (3)",
                       "8. Show of ships (3)",
                       "9. Show of planes (3)",
                       "10. Alert (3)",
                       "12. Mobilization (3)",
                       "13. Fortify border (3)",
                       "14. Border violation (4)",
                       "15. Blockade (4)",
                       "16. Occupation of territory (4)",
                       "17. Seizure (4)",
                       "18. Clash (4)",
                       "19. Raid (4)",
                       "20. Declaration of war (4)",
                       "22. Begin interstate war (5)",
                       "23. Join interstate war (5)",
                       "24. Use CBR Weapons (5)")
) %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )

mid_df <- data.frame(
  stringsAsFactors = FALSE,
               act = c(0L,1L,2L,3L,4L,5L,6L,7L,
                       8L,9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
                       20L,21L),
         act_label = c("No militarized action (1)",
                       "Threat to use force (2)","Threat to blockade (2)",
                       "Threat to occupy terr. (2)","Threat to declare war (2)",
                       "Threat to use CBR weapons","Threat to join war (2)",
                       "Show of force (3)","Alert (3)","Nuclear alert (3)",
                       "Mobilization (3)","Fortify border (3)","Border violation (4)",
                       "Blockade (4)","Occupation of territory (4)",
                       "Seizure (4)","Attack (4)","Clash (4)","Declaration of war (4)",
                       "Use of CBR weapons (4)","Begin interstate war (5)",
                       "Join interstate war (5)")
)  %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )

mid_df2 <- data.frame(
  stringsAsFactors = FALSE,
                outcome = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
                outcome_label = c("0. Ongoing MID",
                       "1. Victory for State A","2. Victory for state B",
                       "3. Yield by State A","4. Yield by State B","5. Stalemate",
                       "6. Compromise","7. Released (for seizures)","8. Unclear",
                       "-9 Missing")
) %>% mutate(outcome_label= outcome_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )

dyadic_mid <- read_csv(paste0(here::here(), "/replication_paper/data/in/dyadic_mid_4.02.csv"))

dyadic_mid_clean <- dyadic_mid %>% distinct() %>%
                      left_join(actor_translator %>% dplyr::select(statea=COWcode, actor_1=QCode_name, actor_1_qcode=QCode)) %>% #I think we add color here
                      left_join(actor_translator %>% dplyr::select(stateb=COWcode, actor_2=QCode_name, actor_2_qcode=QCode)) %>%
                      left_join(mid_df  %>% dplyr::select( mid5hiacta=act , leaf_1=act_label )) %>%
                      left_join(mid_df  %>% dplyr::select( mid5hiactb=act , leaf_2=act_label )) %>%
                      left_join(mid_df2  %>% dplyr::select( outcome=outcome , outcome_label=outcome_label ))

```

```{r mids crisismaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F }

mids_crisismaps <- function(thiscrisis=196, prune_rare=T){

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_mids_metro_plot_",thiscrisis,".Rds")

  year_start <-icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
  year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm

  start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
  end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple

  actor_sent_counts <- icb_events_long %>%
                       dplyr::filter(crisno==thiscrisis  ) %>% 
                       filter(varname_normalized %>% str_detect("actor")) %>% 
                       dplyr::select(sent=sentence_number_int_aligned,value_normalized,value_qcode) %>% 
                       na.omit() %>%
                       count(value_normalized,value_qcode) %>% arrange(n %>% desc() )

  dyadic_mid_clean_subset <- dyadic_mid_clean %>%
                             filter( actor_1_qcode %in% actor_sent_counts$value_qcode & actor_2_qcode %in% actor_sent_counts$value_qcode ) %>%
                             filter(strtyr>=year_start & endyear<=year_end) %>% arrange(strtyr, strtmnth, endday)
  dim(dyadic_mid_clean_subset) #
  if(nrow(dyadic_mid_clean_subset)==0 | 
     (c(dyadic_mid_clean_subset$namea,dyadic_mid_clean_subset$nameb) %>% na.omit() %>% unique() %>%  length())<2  #Reject if not 2 actors
     ){
    print("No mids events for this crisis")
    return()
  }

  dyadic_mid_clean_dyad <- 
    bind_rows(
      dyadic_mid_clean_subset %>% dplyr::select(year=strtyr,month=strtmnth,day=strtday, actor_1,actor_2, leaf=leaf_1) , #
      dyadic_mid_clean_subset %>% dplyr::select(year=endyear,month=endmnth,day=endday, actor_1,actor_2, leaf=outcome_label)
  ) %>% mutate(leaf=ifelse(leaf=="Yield by State A" , "Yield to",leaf)) %>%
    filter(!leaf %in% "Yield by State B") %>%
    mutate(sent= ( year+(month/12)+(day/31/1000) ) %>% rank() %>% round())

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  icb_events_subset_diad <- dyadic_mid_clean_dyad %>% dplyr::select(year, month, sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
  #Order actors by how many interactions they have together
  temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()

  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)

  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")

  temp_list <- list()
  for(i in 1:nrow(temp2_wide)){
    temp_list[[as.character(i)]] <- cutree(hc, k=i)
  }

  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
  #  arrange(across(starts_with("V")))
  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first

  #####Nodes
  icb_events_subset_nodes <- 
            bind_rows(
                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  #we centralize everything in qcodes so colors should be consistent across plots for the same actors    
  icbe_actor_to_qcode <- icb_events_long %>%
                     dplyr::filter(crisno==thiscrisis  ) %>% 
                     filter(varname_normalized %>% str_detect("actor")) %>% 
                     dplyr::select(value_normalized,value_qcode) %>% 
                     na.omit() %>% distinct()

  actor_colors_df <- icbe_actor_to_qcode %>%
    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
  actor_colors <- actor_colors_df$actor_color
  names(actor_colors) = actor_colors_df$value_normalized

  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

  date_sineposts <- icb_events_subset_nodes  %>%
                    mutate(x=max(x)+50) %>%
                    dplyr::select(sent, year, month,x,y) %>%
                    na.omit() %>% 
                    distinct() %>%  
                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                    mutate(year_float=year+(month/12)) %>%
                    group_by(sent) %>%
                    filter(year_float==min(year_float)) %>%
                    ungroup() %>% as.data.frame() %>%
                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                    filter(!duplicated(year_float ) ) %>%
                    mutate(label=paste0(year,"-",month.abb[month]))

  ####Actor lavels
  icb_events_subset_nodes_min <- 
    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    rowwise() %>%
    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))

  for(i in 1:nrow(icb_events_subset_nodes)){
    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
                                actor = icb_events_subset_nodes$actor[i], 
                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )

  #####Time Edges
  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)

  ######Directed
  icb_events_subset_directed <- 
            dyadic_mid_clean_dyad %>% 
            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))

  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=icb_events_subset_directed$leaf, 
                       eventedge=T,
                       actor=icb_events_subset_directed$actor_1)

    p_mids_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Time edges
          geom_edge_link(aes(
                          edge_colour=actor,
                          filter=timeedge==T
                          ),
                          edge_width=0.1, 
                          show.legend = F
                         ) +
          geom_node_point(aes(color=actor),size=1,stroke=0.5) +

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                              colour=actor,
                              label=leaf,
                              filter=eventedge==T #& bundle_count==1
                              ),
                          vjust = -0.75,
                          lineheight = .75,
                          sep = unit(1, 'mm'), 
                          edge_width=0.25, 
                          show.legend = F,
                          arrow = arrow(length = unit(2, 'mm')),
                          label_size=3,
                          check_overlap=global_check_overlap,
                          start_cap = circle(3, 'mm'),
                          end_cap = circle(3, 'mm'),
                          angle_calc = 'along'
                         ) +

              #Not in phoenix
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
              #Not in phoenix
              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #Not in phoenix
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  p_mids_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
  p_mids_metro_map$actor_colors <- actor_colors
  p_mids_metro_map$dyadic_mid_clean <- dyadic_mid_clean

  p_mids_metro_map %>% saveRDS(save_mids_file)
}

c(196, 471) %>% sapply(FUN=function(x) mids_crisismaps(x))

```

```{r phoenix data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F,}
#[@althausClineCenterHistorical2020a]
#https://databank.illinois.edu/datasets/IDB-2796521

library(tidyverse)
library(countrycode)
library(igraph)
library(ggraph)

#8,491,556
library(stringr)
fromscratch=F
if(fromscratch){

  convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()

  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid() 
  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid() 
  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()

  setdiff(events_nyt2$aid , meta1_nyt2$aid) %>% length() #0 #316,201 #yup that was it if you import as numeric it converts to scientific internally and breaks everything 
  setdiff(meta1_nyt2$aid , events_nyt2$aid) %>% length() #0 #613,981 #Have to keep as a string throughout

  phoenix <- bind_rows(events_nyt2 %>% left_join(meta1_nyt2),
                       events_swb %>% left_join(meta2_swb),
                       events_fbis %>% left_join(meta_fbis),
                       events_nyt %>% left_join(meta_nyt),
                       events_wsj %>% left_join(meta_wsj)
                       )

  target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
  actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

  root_codes <- phoenix$root_code %>% unique()

  #library("remotes")
  #remotes::install_github("andybega/icews")
  library(icews)
  data("cameo_codes") #we're going to grab the cameo codes from the ICEWS package because they're a nightmare
  cameo_codes_goldstein <- cameo_codes %>% left_join(goldstein_mappings) %>% mutate(name=name %>% tolower())

  phoenix_clean <- phoenix %>% 
                   #head(10000) %>%
                   left_join(cameo_codes_goldstein %>% dplyr::select(code=cameo_code , cameo_event_label=name,
                                                                     cameo_penta_category=penta_category, cameo_quad_category=quad_category, 
                                                                     cameo_goldstein=goldstein, cameo_lvl0=lvl0 ) ) %>%
                   left_join(    cameo_codes_goldstein %>% filter(level==0) %>% dplyr::select(cameo_lvl0=lvl0, cameo_lvl0_label=name)) %>% #
                   #
                   left_join(cameo_actor_codes %>% dplyr::select(source=code, source_label=name)  )  %>%
                   left_join(cameo_actor_codes %>% dplyr::select(target=code, target_label=name)  )  %>%
                   #
                   left_join(cameo_actor_codes %>% dplyr::select(source_root=code, source_label=name)  )  %>%
                   left_join(cameo_actor_codes %>% dplyr::select(target_root=code, target_label=name)  )  %>%
                   #
                   left_join(cameo_actor_codes %>% dplyr::select(source_agent=code, source_agent_label=name) %>% distinct() %>% na.omit() ) %>%
                   left_join(cameo_actor_codes %>% dplyr::select(target_agent=code, target_agent_label=name) %>% distinct() %>% na.omit() ) %>%
                   #
                   separate(source_others, c("source_others1", "source_others2", "source_others3"), sep = ";", remove=F, extra="drop") %>% 
                   separate(target_others, c("target_others1", "target_others2", "target_others3"), sep = ";", remove=F, extra="drop") %>%
                   left_join(cameo_actor_codes %>% dplyr::select(source_others1=code, source_others1_label=name) %>% distinct() %>% na.omit() ) %>%
                   left_join(cameo_actor_codes %>% dplyr::select(target_others1=code, target_others1_label=name) %>% distinct() %>% na.omit() )  %>% 
                   left_join(cameo_actor_codes %>% dplyr::select(source_others2=code, source_others2_label=name) %>% distinct() %>% na.omit() ) %>%
                   left_join(cameo_actor_codes %>% dplyr::select(target_others2=code, target_others2_label=name) %>% distinct() %>% na.omit() )  %>% 
                   left_join(cameo_actor_codes %>% dplyr::select(source_others3=code, source_others3_label=name) %>% distinct() %>% na.omit() ) %>%
                   left_join(cameo_actor_codes %>% dplyr::select(target_others3=code, target_others3_label=name) %>% distinct() %>% na.omit() )  %>%

                   mutate(date_simple=as.numeric(year) + (as.numeric(month)/12) ) %>%

                   mutate(joined_issues=ifelse( joined_issues=='',";", joined_issues)  ) %>% #Apparently unnesting an empty string just gets dropped
                   mutate(joined_issues = strsplit(as.character(joined_issues), ";") ) %>%  unnest(joined_issues)  %>% #This drops if the row is missing, I did not know that was it
                   #
                   left_join(actor_translator %>% dplyr::select(source_root=phoenix_2020, source_root_label=QCode_name, source_root_qcode=QCode) %>% distinct() %>% na.omit() ) %>%
                   left_join(actor_translator %>% dplyr::select(target_root=phoenix_2020, target_root_label=QCode_name, target_root_qcode=QCode) %>% distinct() %>% na.omit() ) %>%
                   mutate(month_label = lubridate::month(month %>% as.numeric(),label=TRUE,abbr=F)) %>%
                   mutate(source_agent_label = source_agent_label %>% tolower()) %>%
                   mutate(target_agent_label = target_agent_label %>% tolower()) %>%
                   mutate(source_others1_label=source_others1_label %>% tolower()) %>%
                   mutate(target_others1_label=target_others1_label %>% tolower()) %>%
                   mutate(source_others2_label=source_others2_label %>% tolower()) %>%
                   mutate(target_others2_label=target_others2_label %>% tolower()) %>%
                   mutate(source_others3_label=source_others3_label %>% tolower()) %>%
                   mutate(target_others3_label=target_others3_label %>% tolower()) %>%
                   unite(text, 
                          source_root_label, source_agent_label, source_others1_label, source_others2_label, source_others3_label,
                          cameo_event_label, 
                          target_agent_label, target_root_label, target_others1_label, target_others2_label, target_others3_label, 
                          sep=" ", remove = F, na.rm = T) %>%
                    mutate(text = ifelse(!is.na(placename),paste0(text, " in ", placename),text) ) %>% 
                    mutate(text = ifelse(!is.na(joined_issues),paste0(text, " on the topic of ", joined_issues %>% tolower() %>% str_replace(",[0-9]","") ),text) ) %>% 
                    mutate(text = paste0("On ", month_label, " ",day %>% as.numeric()," ",year, ", ", text)) %>%
                    mutate(text=text %>% str_replace(", not specified below","")) %>% 
                    arrange(year, month, day)  %>% mutate(date = paste(day,"-",month,"-",year) %>% lubridate::dmy())

  dim(phoenix_clean) #8,495,402 #3,721,110 #2,813,748 #2912035 #3,508,495 #4,854,787
  phoenix_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") )

  library(dplyr)
  library(digest)
  keep_list <- c("Ukraine", "Russia","Russian Federation", 'North Atlantic Treaty Organization','NATO', 'European Union', 'Crimea','Donbas') #, 'United Nations'
  phoenix_clean_471 <- phoenix_clean %>% 
                        mutate(year = year %>% as.numeric() ) %>%
                       filter( year>= 2013 & year<= 2015 ) %>%
                       #filter( date>= as.Date("2013-01-01") & date<= as.Date("2015-12-31") ) %>%
                       filter( text %>% str_detect(paste0(c(keep_list,keep_list %>% tolower()),collapse="|"))) 
  dim(phoenix_clean_471) #68,334

  phoenix_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471.tsv")
  dim(phoenix_clean_471)

  phoenix_clean_471 %>%
    unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
    write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471_small.tsv")

  library(dplyr)
  library(digest)
  keep_list <- c("Cuba", "Russia","Russian Federation", 'North Atlantic Treaty Organization','NATO', 'United States') #, 'United Nations'
  phoenix_clean_196 <- phoenix_clean %>% 
                       mutate(year = year %>% as.numeric() ) %>%
                       filter( year>= 1958 & year<= 1963 ) %>%
                       #filter( date>= as.Date("2013-01-01") & date<= as.Date("2015-12-31") ) %>%
                       filter( text %>% str_detect(paste0(c(keep_list,keep_list %>% tolower()),collapse="|"))) 
  dim(phoenix_clean_196) #62,192

  phoenix_clean_196 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196.tsv")
  dim(phoenix_clean_196)

  phoenix_clean_196 %>%
    unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
    dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
    write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196_small.tsv")

}

```

```{r phoenix_barmaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

library(ggplot2)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)

phoenix_barmaps <- function(thiscrisis=196, topactor=F){

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_",thiscrisis,".Rds")

    date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==thiscrisis,]$motrig, "-01"))
    date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrterm , "-", icb_crises[icb_crises$crisno==thiscrisis,]$moterm, "-01"))
    date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()

    year_start <-icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
    year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm

    start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
    end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple

    actors <- icb_events_long %>% filter(crisno %in% thiscrisis) %>% filter(varname_normalized %>% str_detect('actor')) %>% 
              dplyr::select(value_normalized,value_qcode) %>% distinct()

    phoenix_clean_subset <- phoenix_clean %>% 
                            mutate(story_date = story_date %>% lubridate::mdy()) %>%
                            filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
                            unite('dyad_a', source_root_label, source_agent_label, source_others1_label, source_others2_label, source_others3_label, na.rm = TRUE, remove = FALSE) %>%
                            unite('dyad_b', target_root_label, target_agent_label, target_others1_label, target_others2_label, target_others3_label, na.rm = TRUE, remove = FALSE) %>%
                            mutate(dyad=paste0(dyad_a,"->",dyad_b)) %>%
                            mutate(dyad_event=paste0(dyad, "_", cameo_event_label)) %>%
                            mutate(dyad_penta_category=paste0(dyad, "_", cameo_penta_category)) %>%
                            mutate(dyad_lvl0_label=paste0(dyad, "_", cameo_lvl0_label)) %>%

                            unite('temp', everything() , na.rm = TRUE, remove = FALSE) %>%
                            filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>%
                            dplyr::select(-temp)

    dim(phoenix_clean_subset)

    dyad_event_counts <-     phoenix_clean_subset  %>% 
                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                             count(cameo_penta_category, dyad_penta_category) %>% 
                             group_by(cameo_penta_category) %>%
                             arrange(cameo_penta_category,  desc(n) ) %>% 
                             filter(row_number()<=10) %>% ungroup()

    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset

    phoenix_clean_subset_top10 <- phoenix_clean_subset %>% 
                                  filter(dyad_penta_category %in% dyad_event_counts$dyad_penta_category  ) %>%
                                  mutate(dyad_markdown=dyad)
    for(i in 1:nrow(names_to_qcodes)){
      phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  )) 
    }
    library(ggtext)
    phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government","gov")) %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("\\(tertiary role code\\)","")) %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force"))

    p_phoenix_penta <- phoenix_clean_subset_top10 %>%
          filter(!is.na(cameo_penta_category)) %>%
          group_by(dyad_markdown, cameo_penta_category, date) %>%
          summarise(mean_goldstein=mean(cameo_goldstein), n=n()) %>%
          group_by(cameo_penta_category, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
          mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_penta_category)) %>%
          ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
          geom_tile() + theme_bw() +
          tidytext::scale_y_reordered() +
          geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
          geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
          facet_wrap(~cameo_penta_category, scale="free_y", ncol=1)  +
          theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +
          scale_fill_gradient2() +
          theme(legend.position="none") +
         ylab("") + xlab("")

    p_phoenix_penta %>% saveRDS(save_file_penta)

    #cameo_lvl0_label
    dyad_event_counts <-     phoenix_clean_subset  %>% 
                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                             count(cameo_lvl0_label, dyad_lvl0_label) %>% 
                             group_by(cameo_lvl0_label) %>%
                             arrange(cameo_lvl0_label,  desc(n) ) %>% 
                             filter(row_number()<=10) %>% ungroup()

    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset

    phoenix_clean_subset_top10 <- phoenix_clean_subset %>% 
                                  filter(dyad_lvl0_label %in% dyad_event_counts$dyad_lvl0_label  ) %>%
                                  mutate(dyad_markdown=dyad)
    for(i in 1:nrow(names_to_qcodes)){
      phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  )) 
    }
    library(ggtext)
    phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government","gov")) %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("\\(tertiary role code\\)","")) %>%
                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force"))

    phoenix_clean_subset_top10_day <- phoenix_clean_subset_top10 %>%
                                      mutate(story_date=paste(month, day, year, sep="/")) %>%
                                      filter(!is.na(cameo_lvl0_label)) %>%
                                      mutate(date = story_date %>% lubridate::mdy()) %>%
                                      group_by(dyad_markdown, cameo_lvl0_label, date) %>%
                                      summarise(mean_goldstein=mean(cameo_goldstein), n=n())

    p_phoenix_lv0 <- phoenix_clean_subset_top10_day %>%
                      group_by(cameo_lvl0_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
                      mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_lvl0_label)) %>%
                      ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
                      geom_tile() + theme_bw() +
                      tidytext::scale_y_reordered() +
                      geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
                      geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
                      facet_wrap(~cameo_lvl0_label, scale="free_y", ncol=3)  +
                      theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +
                      scale_fill_gradient2() +
                      theme(legend.position="none") +
                      ylab("") + xlab("")

        p_phoenix_lv0 %>% saveRDS(save_file_lv0)

}

fromscratch=F
if(fromscratch){
  phoenix_clean <- arrow::read_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") ) 
  c(196, 471) %>% sapply(FUN=function(x) phoenix_barmaps(x))
}

```

```{r Terrierr Data Loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

#https://osf.io/4m2u7/

terrier_agent_labels <- data.frame(
       stringsAsFactors = FALSE,
                   agent = c("GOV","SPY","OPP",
                            "MIL","PTY","REB","EDU","COP","JUD","CRM",
                            "BUS","MED","CVL","UAF","AGR","ELI","DEV","ENV",
                            "HLH","HRI","LAB","LEG","REF","MOD","RAD"),
                    agent_label = c("Government",
                            "Intelligence agencies",
                            "Opposition groups (often parliamentary)",
                            "Military",
                            "Political party",
                            "Rebels/insurgents",
                            "Education-focused actors",
                            "Law enforcement agencies",
                            "Judicial actors",
                            "Criminal actors",
                            "Business (NOT MNCs)",
                            "Media-related actors/organizations",
                            "Civilians",
                            "Unaffiliated armed forces",
                            "Agriculture-focused actors",
                            "Elites, celebrities",
                            "Development-focused actors",
                            "Environment-focused actors",
                            "Health-focused actors",
                            "Human rights-focused actors",
                            "Labor-focused actors",
                            "Legislative bodies/actors",
                            "Refugee-focused actors",
                            "Moderate/mainstream group",
                            "Radical/extremist/fundamentalist")
) %>% janitor::clean_names() %>%
  mutate(agent_label = agent_label %>% tolower() )

if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
  stop("Missing Terrier event data. See README.")
}

#if(file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
#  terrier_fromscratch <-readline(prompt="Load original Terrier data? (T/F)")
#}
#terrier_fromscratch <- terrier_fromscratch %in% "T"

#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
#codes_used <-terrier_clean %>% count(cameo_code)

#Switching to data table with dplyr wrapper
library(data.table)
library(dtplyr)
library(dplyr, warn.conflicts = FALSE)
terrier_fromscratch <- F
if(terrier_fromscratch){
    files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
    terrier <- rbindlist(lapply(files, FUN=function(x) fread(x,header=F, colClasses=paste0(rep('character',50), collapse='')  )  ) ) #%>% janitor::clean_names()
    dim(terrier) #28,438,029 #28,370,448       28

    actor_translator_terrier <- actor_translator %>% dplyr::select( terrier,  QCode, QCode_name) %>% filter(!duplicated(terrier)) %>% as.data.table() %>% na.omit()

    #library("remotes")
    #remotes::install_github("andybega/icews")
    library(icews)
    data("cameo_codes") #we're going to grab the cameo codes from the ICEWS package because they're a nightmare
    cameo_codes_goldstein <- cameo_codes %>% left_join(goldstein_mappings) %>% mutate(name=name %>% tolower())

    library(tictoc)
    tictoc::tic()
    dim(terrier) #28,438,029
    #terrier_clean_temp %>% as.data.table() %>% dim()
    #Maybe it's just ISO3 country codes?
    terrier_clean_temp <- terrier %>% 
        #head(100000) %>% 
        as_tibble() %>%
        dplyr::select(
          #id=V1,
          hash=V2,
          cameo_code=V3,
          src_country=V8,
          src_agent=V9,
          src_other_agent=V10,

          target_country=V12 ,
          target_agent=V13,
          target_other_agent=V14,

          year=V17,
          month=V18,
          day=V19,
          where=V21#,
          #source=V7
          #random_text=x28
        ) %>% 
        left_join(cameo_codes_goldstein %>% mutate(cameo_code=cameo_code ) %>% dplyr::select(cameo_code=cameo_code, cameo_label= name, cameo_goldstein=goldstein,
                                                                                             cameo_penta_category=penta_category, cameo_lvl0=lvl0)  ) %>% #
        left_join(    cameo_codes_goldstein %>% filter(level==0) %>% dplyr::select(cameo_lvl0=lvl0, cameo_lvl0_label=name)) %>% #
        mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%

        mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>% 
        tidyr::separate(target_other_agent, c("target_other_agent1", "target_other_agent2", "target_other_agent3",
                                              'trash1','trash2','trash3','trash4','trash5','trash6','trash7','trash8','trash9','trash10'), sep = ";", remove=F, extra="drop") %>%
        dplyr::select(-starts_with("trash")) %>%
        tidyr::separate(src_other_agent   , c("src_other_agent1"   , "src_other_agent2"   , "src_other_agent3",
                                              'trash1','trash2','trash3','trash4','trash5','trash6','trash7','trash8','trash9','trash10','trash11'), sep = ";", remove=F, extra="drop") %>%
        dplyr::select(-starts_with("trash")) %>%

        left_join(cameo_actor_codes %>% dplyr::select(src_country=code, src_country_label= name) %>% as.data.table()  ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(target_country=code, target_country_label= name) %>% as.data.table()  ) %>%

        left_join(cameo_actor_codes %>% dplyr::select(src_agent=code, src_agent_label= name) %>% as.data.table()  ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(src_other_agent1=code, src_other_agent1_label= name) %>% as.data.table()  ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(src_other_agent2=code, src_other_agent2_label= name) %>% as.data.table()  ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(src_other_agent3=code, src_other_agent3_label= name) %>% as.data.table()  ) %>%

        left_join(cameo_actor_codes %>% dplyr::select(target_agent=code, target_agent_label= name) %>% as.data.table()   ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(target_other_agent1=code, target_other_agent1_label= name) %>% as.data.table()  ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(target_other_agent2=code, target_other_agent2_label= name) %>% as.data.table()  ) %>%
        left_join(cameo_actor_codes %>% dplyr::select(target_other_agent3=code, target_other_agent3_label= name) %>% as.data.table()  ) %>%

        left_join(actor_translator_terrier %>% dplyr::select(src_country   = terrier, actor_1_qcode = QCode, actor_1_label=QCode_name) %>% as.data.table() %>% na.omit() ) %>%
        left_join(actor_translator_terrier %>% dplyr::select(target_country= terrier, actor_2_qcode = QCode, actor_2_label=QCode_name) %>% as.data.table() %>% na.omit()  ) %>%
        mutate(month_label = lubridate::month(month %>% as.numeric(),label=TRUE,abbr=F)) %>%
        mutate(cameo_label = cameo_label %>% tolower() ) %>% 
                       mutate(year= year %>% as.numeric() ) %>% 
                       mutate(month= month %>% as.numeric() ) %>% 
                       mutate(day= day %>% as.numeric() )  %>%
       as_tibble()
    tictoc::toc() #313.74 
    dim(terrier_clean_temp) #31,117,198 #39322909

    #terrier_clean_temp %>% saveRDS( here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
    library(arrow) #you have to actually load the library
    terrier_clean_temp  %>%
      arrow::write_parquet(here::here("replication_paper", "data", "ignore", "terrier_clean.parquet") )
}

```

```{r terrier_barmaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

library(ggplot2)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)

terrier_barmaps <- function(thiscrisis=471, topactor=F){

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_terrier_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_terrier_plot_lv0_",thiscrisis,".Rds")

    date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==thiscrisis,]$motrig, "-01"))
    date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrterm , "-", icb_crises[icb_crises$crisno==thiscrisis,]$moterm, "-01"))
    date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()

    year_start <-icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
    year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm

    start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
    end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple

    actors <- icb_events_long %>% filter(crisno %in% thiscrisis) %>% filter(varname_normalized %>% str_detect('actor')) %>% 
              dplyr::select(value_normalized,value_qcode) %>% distinct()

    terrier_clean_subset <- terrier_clean %>% 
                    mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() ) %>%
                    filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
                    unite('temp', src_country_label,src_agent_label,src_other_agent1_label,src_other_agent2_label,src_other_agent3_label,
                          target_country_label, target_agent_label,target_other_agent1_label,target_other_agent2_label,target_other_agent3_label,
                          where,
                          na.rm = TRUE, remove = FALSE) %>%
                    filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>%
                    unite('dyad_a', src_country_label,src_agent_label,src_other_agent1_label,src_other_agent2_label,src_other_agent3_label, na.rm = TRUE, remove = FALSE) %>%
                    unite('dyad_b', target_country_label, target_agent_label,target_other_agent1_label,target_other_agent2_label,target_other_agent3_label, na.rm = TRUE, remove = FALSE) %>%
                    mutate(dyad=paste0(dyad_a,"->",dyad_b)) %>%
                    mutate(dyad_event=paste0(dyad, "_", cameo_label)) %>%
                    mutate(dyad_penta_category=paste0(dyad, "_", cameo_penta_category)) %>%
                    mutate(dyad_lvl0_category=paste0(dyad, "_", cameo_lvl0_label)) %>%
                    dplyr::select(-temp)

    dim(terrier_clean_subset) #928,640

    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset

    #Penta
    dyad_event_counts <-     terrier_clean_subset  %>% 
                         mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                         filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                         count(cameo_penta_category, dyad_penta_category) %>% 
                         group_by(cameo_penta_category) %>%
                         arrange(cameo_penta_category,  desc(n) ) %>% 
                         filter(row_number()<=10) %>% ungroup()

    terrier_clean_subset_top10 <- terrier_clean_subset %>% 
                                  filter(dyad_penta_category %in% dyad_event_counts$dyad_penta_category  ) %>%
                                  mutate(dyad_markdown=dyad)

    terrier_clean_subset_top10_day <- terrier_clean_subset_top10 %>%
          mutate(story_date=paste(month, day, year, sep="/")) %>%
          filter(!is.na(cameo_penta_category)) %>%
          mutate(date = story_date %>% lubridate::mdy()) %>%
          group_by(dyad_markdown, cameo_penta_category, date) %>%
          summarise(mean_goldstein=mean(cameo_goldstein), n=n())

    for(i in 1:nrow(names_to_qcodes)){
      #print(i)
      terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
    } #This is a bottleneck now and needs to move to after the group
    library(ggtext)
    terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all(fixed("(tertiary role code)"),"")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil."))

    p_terrier_penta <-  terrier_clean_subset_top10_day %>%
          group_by(cameo_penta_category, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
          mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_penta_category)) %>%
          ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
          geom_tile() + theme_bw() +
          tidytext::scale_y_reordered() +
          geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
          geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
          facet_wrap(~cameo_penta_category, scale="free_y", ncol=1)  +
      theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +   scale_fill_gradient2() +
          theme(legend.position="none") +
         ylab("") + xlab("")

    p_terrier_penta %>% saveRDS(save_file_penta)

    #_lvl0
    dyad_event_counts <-     terrier_clean_subset  %>% 
                         mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                         filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                         count(cameo_lvl0_label, dyad_lvl0_category) %>% 
                         group_by(cameo_lvl0_label) %>%
                         arrange(cameo_lvl0_label,  desc(n) ) %>% 
                         filter(row_number()<=10) %>% ungroup()

    terrier_clean_subset_top10 <- terrier_clean_subset %>% 
                                  filter(dyad_lvl0_category %in% dyad_event_counts$dyad_lvl0_category  ) %>%
                                  mutate(dyad_markdown=dyad)

    terrier_clean_subset_top10_day <- terrier_clean_subset_top10 %>%
          mutate(story_date=paste(month, day, year, sep="/")) %>%
          filter(!is.na(cameo_penta_category)) %>%
          mutate(date = story_date %>% lubridate::mdy()) %>%
          group_by(dyad_markdown, cameo_lvl0_label, date) %>%
          summarise(mean_goldstein=mean(cameo_goldstein), n=n())

    for(i in 1:nrow(names_to_qcodes)){
      #print(i)
      terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
    } #This is a bottleneck now and needs to move to after the group
    library(ggtext)
    terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Inter-governmental organizations","IGOs")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government[^a-z]|Government[^a-z]","gov")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all(fixed("(tertiary role code)"),"")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil."))

    p_terrier_lv0 <-  terrier_clean_subset_top10_day %>%
          group_by(cameo_lvl0_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
          mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_lvl0_label)) %>%
          ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
          geom_tile() + theme_bw() +
          tidytext::scale_y_reordered() +
          geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
          geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
          facet_wrap(~cameo_lvl0_label, scale="free_y", ncol=3)  +
      theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) + 
       scale_fill_gradient2() +
          theme(legend.position="none") +
         ylab("") + xlab("")

    p_terrier_lv0 %>% saveRDS(save_file_lv0)

}

fromscratch=F
if(fromscratch){
  #done
  #install.packages("arrow")
  terrier_clean <-  arrow::read_parquet( here::here("replication_paper", "data", "ignore", "terrier_clean.parquet")) #203mb
  dim(terrier_clean) #28,438,029 #39,322,909 #7,847,463

  c(196, 471) %>% sapply(FUN=function(x) terrier_barmaps(x))
}

```

```{r ICEWS data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

fromscratch=F
if(fromscratch){
  #accidentally loaded the pdfs
  files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T, pattern = ".tab$|.tsv$")
  icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x, show_col_types = FALSE) )  ) %>% janitor::clean_names() %>% distinct()
  dim(icews) #18,403,260 #15,751,586

  codes_used <-icews %>% count(cameo_code)

  actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
  #%>% mutate(icews=ifelse(ICEWS_Country=="International Government Organizations", ICEWS_Actor.Name, ICEWS_Country))

  #Going to heavily filter on source sectors and source name
  #c(icews$source_sectors,icews$source_name) %>% table()

  #This doesn't totally work because India has 3 copies. The lower thing gets a different q code than the higher thing, so we first have to try to match on the lower, and if that fails match on the higher kinda
  #Indian Administered Kashmir		India

    #library("remotes")
  #remotes::install_github("andybega/icews")
  library(icews)
  data("cameo_codes") #we're going to grab the cameo codes from the ICEWS package because they're a nightmare
  cameo_codes_goldstein <- cameo_codes %>% left_join(goldstein_mappings) %>% mutate(name=name %>% tolower())

  dim(icews) #18,403,260 #15,751,586
  icews_clean <- icews %>% 
                 #filter(event_id==20776790) %>% 
                 #head(10000) %>%
                 mutate_if(is.character, na_if, "null") %>%
                 mutate_if(is.character, na_if, "NULL") %>%
                 #head(1000) %>%
                 mutate(where = coalesce(city, district,province)) %>%
                 left_join(cameo_codes_goldstein %>% mutate(cameo_code=cameo_code ) %>%
                             dplyr::select(cameo_code=cameo_code, cameo_label= name, cameo_goldstein=goldstein, cameo_penta_category=penta_category,
                                           cameo_lvl0=lvl0)  ) %>% #it's that insane cameo code bug
                 left_join(    cameo_codes_goldstein %>% filter(level==0) %>% dplyr::select(cameo_lvl0=lvl0, cameo_lvl0_label=name)) %>% #it's that insane cameo code bug    
                 mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%

                left_join( actor_translator_icews %>% dplyr::select(source_name=ICEWS_Actor.Name,  source_q_code_actor=QCode, source_q_label_actor=QCode_name) %>% 
                             distinct() %>% na.omit() ) %>%
                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% 
                             dplyr::select(source_country=ICEWS_Country,  source_q_code_country=QCode, source_q_label_country=QCode_name) %>% 
                             distinct() %>% na.omit() ) %>%
                mutate(source_q_code=ifelse(!is.na(source_q_code_actor) , source_q_code_actor, source_q_code_country)) %>%
                mutate(source_label=ifelse(!is.na(source_q_code_actor) , source_q_label_actor, source_q_label_country)) %>%

                left_join( actor_translator_icews %>% dplyr::select(target_name=ICEWS_Actor.Name,  target_q_code_actor=QCode, target_q_label_actor=QCode_name) %>% 
                             distinct() %>% na.omit() ) %>%
                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% 
                             dplyr::select(target_country=ICEWS_Country,  target_q_code_country=QCode, target_q_label_country=QCode_name) %>%
                             distinct() %>% na.omit() ) %>%
                mutate(target_q_code=ifelse(!is.na(target_q_code_actor) , target_q_code_actor, target_q_code_country)) %>%
                mutate(target_label=ifelse(!is.na(target_q_code_actor) , target_q_label_actor, target_q_label_country)) %>%

                mutate(source_target_q_code= paste0(source_q_code,"_",target_q_code)) %>%

                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(country=ICEWS_Country,  country_q_code=QCode) %>% distinct() %>% na.omit() ) %>%
                mutate(year = event_date %>% lubridate::year()  )  %>%
                mutate(month = event_date %>% lubridate::month()  )  %>%
                mutate(day = event_date %>% lubridate::day()  )  %>%
                mutate(month_label = lubridate::month(month %>% as.numeric(),label=TRUE,abbr=F)) %>%
                mutate(source_sectors = source_sectors %>% tolower()) %>%
                mutate(target_sectors = target_sectors %>% tolower()) %>%
                mutate(cameo_label = cameo_label %>% str_replace(", not specified below","") ) %>%
                mutate(who_a = coalesce(source_name,source_sectors %>% tolower(), source_label ) ) %>%
                mutate(who_b = coalesce(target_name,target_sectors %>% tolower(), target_label ) ) %>%
                mutate(who_a = ifelse(who_a %in% source_country, NA, who_a)) %>%
                mutate(who_b = ifelse(who_b %in% target_country, NA, who_b)) %>%
                unite(text, 
                      source_country,who_a,  
                      cameo_label, 
                      who_b, target_country, sep=" ", remove = F, na.rm = T) %>%
                mutate(text = ifelse(!is.na(where),paste0(text, " in ", where),text) ) %>% 
                mutate(text = paste0("On ", month_label, " ",day," ",year, ", ", text))

    dim(icews_clean) #17,541,701 #1,965,573 it's still too many but it's just close enough now #1,965,573

    icews_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )

    #icews_clean %>% count(source_country) %>% dim() #233
    #icews_clean %>% count(source_country, source_sectors) %>% dim() #404673
    #icews_clean %>% count(source_country, source_sectors, source_name) %>% dim() #569374
    #icews_clean %>% count(cameo_label) %>% dim() #272

    dim(icews_clean) #17,541,701
    library(dplyr)
    library(digest)
    keep_list <- c("Ukraine", "Russia","Russian Federation", 'North Atlantic Treaty Organization', 'NATO', 'European Union', 'Crimea','Donbas','Donetsk', 'Luhansk' ) #, 'United Nations'
    keep_list <- c(keep_list, keep_list %>% tolower())
    icews_clean_471 <- icews_clean %>% 
                       filter( event_date>= as.Date("2013-01-01") & event_date<= as.Date("2015-12-31") ) %>%
                      unite('temp', country , target_name , target_country, where , 
                            source_q_label_country,target_q_label_country,  source_label, target_label,who_a, who_b,province, district, city,
                            na.rm = TRUE, remove = FALSE) %>% #this is probably slow need to check
                       filter( temp %>% str_detect(paste0(keep_list,collapse="|"))) %>%
                       dplyr::select(-temp)
    dim(icews_clean_471) #281,427

    icews_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")

    icews_clean_471 %>%
      unite('actors_left' , source_country, source_label, source_name, source_sectors,  sep=" ", , na.rm =T, remove=F) %>%
      unite('actors_right', target_country, target_label, target_name, target_sectors, sep=" ", , na.rm =T, remove=F) %>%
      dplyr::select(event_id, year, month, day, actors_left, actors_right,cameo_event_label=cameo_label, text ) %>% 
      write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")

}

```

```{r icews_barmaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

library(ggplot2)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)

icews_barmaps <- function(thiscrisis=471, topactor=F){

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icews_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icews_plot_lv0_",thiscrisis,".Rds")

    date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==thiscrisis,]$motrig, "-01"))
    date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrterm , "-", icb_crises[icb_crises$crisno==thiscrisis,]$moterm, "-01"))
    date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()

    year_start <- icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
    year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm

    start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
    end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple

    actors <- icb_events_long %>% filter(crisno %in% thiscrisis) %>% filter(varname_normalized %>% str_detect('actor')) %>% 
              dplyr::select(value_normalized,value_qcode) %>% distinct()
    #library(re2r) #didn't speed it up and enabling parallel was actually slower, not sure what's going on usually very fast
    library(tictoc)
    tictoc::tic() 
    icews_clean_subset <- icews_clean %>% 
                          mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() ) %>%
                          filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
                          unite('temp', country , target_name , target_country, where , 
                                source_q_label_country,target_q_label_country,  source_label, target_label,who_a, who_b,province, district, city,
                                na.rm = TRUE, remove = FALSE) %>% #this is probably slow need to check
                          filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>% #this is slow and maybe replacing with re2r will fix
                          unite('dyad_a', source_name ,  na.rm = TRUE, remove = FALSE) %>%
                          unite('dyad_b', target_name ,  na.rm = TRUE, remove = FALSE) %>%
                          mutate(dyad=paste0(dyad_a,"->",dyad_b)) %>%
                          mutate(dyad_event=paste0(dyad, "_", cameo_label)) %>%
                          mutate(dyad_penta_category=paste0(dyad, "_", cameo_penta_category)) %>%
                          mutate(dyad_lv10=paste0(dyad, "_", cameo_lvl0_label)) %>%
                          dplyr::select(-temp)
    tictoc::toc() #85.212
    dim(icews_clean_subset) #441,588 #586,406

    #Penta
    dyad_event_counts <-     icews_clean_subset  %>% 
                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                             count(cameo_penta_category, dyad_penta_category) %>% 
                             group_by(cameo_penta_category) %>%
                             arrange(cameo_penta_category,  desc(n) ) %>% 
                             filter(row_number()<=10) %>% ungroup()

    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset

    icews_clean_subset_top10 <- icews_clean_subset %>% 
                                filter(dyad_penta_category %in% dyad_event_counts$dyad_penta_category  )

    icews_clean_subset_top10_day <- icews_clean_subset_top10 %>%
                                    mutate(story_date=paste(month, day, year, sep="/")) %>%
                                    filter(!is.na(cameo_penta_category)) %>%
                                    mutate(date = story_date %>% lubridate::mdy()) %>%
                                    group_by(dyad_markdown=dyad, cameo_penta_category, date) %>% #rename dyad dyad_markdown here
                                    summarise(mean_goldstein=mean(cameo_goldstein), n=n())

    for(i in 1:nrow(names_to_qcodes)){
      #print(i)
      icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
    } #This is a bottleneck now and needs to move to after the group
    library(ggtext)
    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))

    p_icews_penta <-  icews_clean_subset_top10_day %>%
            group_by(cameo_penta_category, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
            mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_penta_category)) %>%
            ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
            geom_tile() + theme_bw() +
            tidytext::scale_y_reordered() +
            geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
            geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
            facet_wrap(~cameo_penta_category, scale="free_y", ncol=1)  +
            theme(plot.margin = unit(c(0,0,0,0), "cm")) + 
            theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) + 
            scale_fill_gradient2() +
            theme(legend.position="none") +
            ylab("") + xlab("")  #+
            #geomtextpath::geom_textvline(xintercept = as.Date('2015-02-21'), label="MINSK II" , linetype="dotted", color = "red", size=3)  #+
            #labs(subtitle=keys %>% paste(collapse="; "))

    p_icews_penta %>% saveRDS(save_file_penta)

    #lv0
    dyad_event_counts <-     icews_clean_subset  %>% 
                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                             count(cameo_lvl0_label, dyad_lv10) %>% 
                             group_by(cameo_lvl0_label) %>%
                             arrange(cameo_lvl0_label,  desc(n) ) %>% 
                             filter(row_number()<=10) %>% ungroup()

    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset

    icews_clean_subset_top10 <- icews_clean_subset %>% 
                                filter(dyad_lv10 %in% dyad_event_counts$dyad_lv10  ) %>%
                                mutate(dyad_markdown=dyad)

    dyad_unique <-     bind_rows(
      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_a) %>% distinct(),
      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_b) %>% distinct()
    ) %>% distinct() %>% mutate(dyad_unique_markup = dyad_unique)

    for(i in 1:nrow(names_to_qcodes)){
      #print(i)
      dyad_unique <- dyad_unique %>% dplyr::mutate(dyad_unique_markup = dyad_unique_markup %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
      #print(head(dyad_unique,2))
    }

    icews_clean_subset_top10_day <- icews_clean_subset_top10 %>%
                                    left_join(dyad_unique %>% dplyr::select(dyad_a=dyad_unique, dyad_a_markup=dyad_unique_markup) ) %>%
                                    left_join(dyad_unique %>% dplyr::select(dyad_b=dyad_unique, dyad_b_markup=dyad_unique_markup) ) %>%
                                    mutate(dyad_markdown=paste0(dyad_a_markup,"->",dyad_b_markup)) %>%
                                    mutate(story_date=paste(month, day, year, sep="/")) %>%
                                    filter(!is.na(cameo_lvl0_label)) %>%
                                    mutate(date = story_date %>% lubridate::mdy()) %>%
                                    group_by(dyad_markdown, cameo_lvl0_label, date) %>%
                                    summarise(mean_goldstein=mean(cameo_goldstein), n=n())

    library(ggtext)
    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))

    p_icews_lv0 <-  icews_clean_subset_top10_day %>%
            group_by(cameo_lvl0_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
            mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_lvl0_label)) %>%
            ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
            geom_tile() + theme_bw() +
            tidytext::scale_y_reordered() +
            geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
            geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
            facet_wrap(~cameo_lvl0_label, scale="free_y", ncol=3)  +
            theme(plot.margin = unit(c(0,0,0,0), "cm")) +
            theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +
            scale_fill_gradient2() +
            theme(legend.position="none") +
            ylab("") + xlab("")

    p_icews_lv0 %>% saveRDS(save_file_lv0)

    #Make one more special grouping for the main paper
    dyad_event_counts <-     icews_clean_subset  %>% 
                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
                             count(cameo_label, dyad_event) %>%  #down to the lowest level of aggregation
                             group_by(cameo_label) %>%
                             arrange(cameo_label,  desc(n) ) %>% 
                             filter(row_number()<=10) %>% ungroup()

    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset

    icews_clean_subset_top10 <- icews_clean_subset %>% 
                                filter(dyad_event %in% dyad_event_counts$dyad_event  ) %>%
                                mutate(dyad_markdown=dyad)

    dyad_unique <-     bind_rows(
      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_a) %>% distinct(),
      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_b) %>% distinct()
    ) %>% distinct() %>% mutate(dyad_unique_markup = dyad_unique)

    for(i in 1:nrow(names_to_qcodes)){
      #print(i)
      dyad_unique <- dyad_unique %>% dplyr::mutate(dyad_unique_markup = dyad_unique_markup %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
      #print(head(dyad_unique,2))
    }

    icews_clean_subset_top10_day <- icews_clean_subset_top10 %>%
                                    left_join(dyad_unique %>% dplyr::select(dyad_a=dyad_unique, dyad_a_markup=dyad_unique_markup) ) %>%
                                    left_join(dyad_unique %>% dplyr::select(dyad_b=dyad_unique, dyad_b_markup=dyad_unique_markup) ) %>%
                                    mutate(dyad_markdown=paste0(dyad_a_markup,"->",dyad_b_markup)) %>%
                                    mutate(story_date=paste(month, day, year, sep="/")) %>%
                                    filter(!is.na(cameo_label)) %>%
                                    mutate(date = story_date %>% lubridate::mdy()) %>%
                                    group_by(dyad_markdown, cameo_label, date) %>%
                                    summarise(mean_goldstein=mean(cameo_goldstein), n=n())

    library(ggtext)
    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
    icews_clean_subset_top10_day %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")
    #just out the tsv and plot how you want in the main paper

}

fromscratch=F
if(fromscratch){
  #done
  #install.packages("arrow")
  icews_clean <-  arrow::read_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )

  c( 471) %>% sapply(FUN=function(x) icews_barmaps(x))
}

```

```{r crisis 196, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_196_icb <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  )

save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
p_196_phoenix <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  )

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_mids_metro_plot_196.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_196_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_phoenix_plot_penta_196.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_196_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

library(cowplot)
p_196_combined <- 
           plot_grid(
            p_196_icb  +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
           scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
           scale_y_continuous(expand = expansion(mult = c(0.15, 0.15))) ,

           p_196_mids +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
           scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
           scale_y_continuous(expand = expansion(mult = c(0.15, 0.15))) ,

           p_196_phoenix +
           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") 
           #scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
           #scale_y_continuous(expand = expansion(mult = c(0.8, 0.2))) ,  
           ,
           labels = c('ICB','MIDs','Phoenix'), align = "h", ncol = 3 , rel_widths = c(1, 1,1) 
)

save_plot(file=paste0(here::here(), '/replication_paper/figures/p_196_combined.png'),
          p_196_combined, base_height = 12, base_width = 20)
#I'm just going to rotate on disk and load it as a normal figure
#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
```

\begin{sideways}%[htbp]
\centering{\includegraphics[width=21cm]{../figures/p_196_combined.png}}
\end{sideways}
\clearpage

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_196.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
\centering{\includegraphics[width=21cm]{../figures/p_phoenix_plot_lv0_196.png}}
\end{sidewaysfigure}
\clearpage

## Figure D4 Crisis Maps Crimea-Donbas

\hphantom{em}

```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

#\caption{Crisis Maps - Cuban Missile Crisis}
#\captionof{figure}{Crisis Maps - Cuban Missile Crisis }
#\caption{Crisis Maps - Cuban Missile Crisis \label{fig:p_196_combined}}
#\begin{sidewaysfigure}[ht]
#\end{sidewaysfigure}

#Crisis maps for the non ICBe datasets for the two case studies

library(ggplot2)
library(cowplot)
library(ggtext)

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_mids_metro_plot_471.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_471_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_phoenix_plot_penta_471.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_471_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_terrier_plot_penta_471.Rds')
subtitle="Terrier Dyadic Events"
caption=paste0("Data: Terrier (Grant et al. 2021)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_471_terrier <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )

save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icews_plot_penta_471.Rds')
p_471_icews <- readRDS(save_file)

library(cowplot)
p_471_combined <- 
           plot_grid(

           p_471_mids +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
           scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
           scale_y_continuous(expand = expansion(mult = c(0.15, 0.15))) + ylab('') ,

           p_471_phoenix +
           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") + ylab('') , #+
           #scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
           #scale_y_continuous(expand = expansion(mult = c(0.8, 0.2))) ,

           p_471_terrier +
           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") + ylab('') , #+
           #scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
           #scale_y_continuous(expand = expansion(mult = c(0.8, 0.2))) ,  
           p_471_icews +
           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") + ylab('') , #+

           labels = c('MIDs','Phoenix', 'Terrier', 'ICEWs'), align = "h", ncol = 4 , rel_widths = c(1, 1,1,1) 
)

save_plot(file=paste0(here::here(), '/replication_paper/figures/p_471_combined.png'),
          p_471_combined, base_height = 12, base_width = 25)

```

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
\centering{\includegraphics[width=21cm]{../figures/p_471_combined.png}}
\end{sidewaysfigure}
\clearpage

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_471.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
\centering{\includegraphics[width=21cm]{../figures/p_phoenix_plot_lv0_471.png}}
\end{sidewaysfigure}
\clearpage

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_terrier_plot_lv0_471.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
\centering{\includegraphics[width=21cm]{../figures/p_terrier_plot_lv0_471.png}}
\end{sidewaysfigure}
\clearpage

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_icews_plot_lv0_471.Rds")
  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
\centering{\includegraphics[width=21cm]{../figures/p_icews_plot_lv0_471.png}}
\end{sidewaysfigure}
\clearpage

# References

\hphantom{em}

### 2022-07-17 replication_paper/pnas_draft/paper.Rmd
v1.1

---
title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Rex W. Douglass
    affiliation: a,1,2
  - name: Thomas Leo Scherer
    affiliation: a
  - name: J. Andrés Gannon
    affiliation: b
  - name: Erik Gartzke
    affiliation: a
  - name: Jon Lindsay
    affiliation: c
  - name: Shannon Carcelli
    affiliation: d
  - name: Jonathan Wilkenfeld
    affiliation: d
  - name: David M. Quinn
    affiliation: e
  - name: Catherine Aiken
    affiliation: f
  - name: Jose Miguel Cabezas Navarro
    affiliation: g
  - name: Neil Lund
    affiliation: d
  - name: Egle Murauskaite
    affiliation: h
  - name: Diana Partridge
    affiliation: h

address:
  - code: a
    address: Department of Political Science, University of California, San Diego, CA, USA.
  - code: b
    address: Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.
  - code: c
    address: School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.
  - code: d
    address: Department of Government and Politics, University of Maryland, College Park, MD, USA.
  - code: e
    address: Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.
  - code: f
    address: Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.
  - code: g
    address: Society and Health Research Center, Universidad Mayor, Santiago, Chile.
  - code: h
    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
  - code: i
    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.

corresponding_author:
  code: 2
  text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"

# For footer text
lead_author_surname: Douglass

#following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
author_contributions: |
  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.

## Remove this if not required
conflict_of_interest: |
  Please declare any conflict of interest here.

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.

significance: |
  Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.

acknowledgements: |
  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort. We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.  We thank the many undergraduate coders for their patience and dedication. Thanks to the Center for Peace and Security Studies and its membership for comments. Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback. Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang. This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.

keywords:
  - Diplomacy
  - War
  - Crises
  - International Affairs
  - Computational Social Science

## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
pnas_type: pnasresearcharticle

bibliography: ICBintro.bib
csl: pnas.csl

## change to true to add optional line numbering
lineno: false

#https://bookdown.org/yihui/bookdown/a-single-document.html
#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
output: 
  bookdown::pdf_book:
    toc: no
    base_format: rticles::pnas_article
    latex_engine: xelatex

#Disabled several the caused errors
header-includes:
  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
#  - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
#  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
#  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
#  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
#  - \usepackage{subfigure}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage[algo2e]{algorithm2e}
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
---

```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
#International Crisis Behavior Events (ICBe) Dataset
knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F

```

```{r, eval=T, echo=F, cache=F}

#library(pacman)
library(googlesheets4)
library(tidyverse)
library(janitor)
library(flextable)
set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`. You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
library(ftExtra)
options(tidyverse.quiet = TRUE)
options(gargle_oauth_email = TRUE)

#install.packages('stargazer')
#install.packages('kableExtra')
#! sh: 1: pdflatex: not found
#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended

#! LaTeX Error: File `letltxmacro.sty' not found.
#sudo apt-get install texlive-latex-extra

#install.packages('tinytex')
#tinytex::install_tinytex()

```

```{r, echo=F}
#Notes
#https://tex.stackexchange.com/questions/83440/inputenc-error-unicode-char-u8-not-set-up-for-use-with-latex
#- \DeclareUnicodeCharacter{00A0}{ }

```

```{r, include=FALSE}
# options(tinytex.verbose = TRUE)
```

```{r, echo=FALSE}

`%>%` <- magrittr::`%>%`

```

```{r, echo=FALSE}

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )

ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
dim(ICBe_events_agreed)
icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
dim(icb_events_long)

#oh is it because break is reserved in R? lol
#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()

#somehow break of all things is a b roken name
#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))

```

<!-- note: please start your introduction without including the word "Introduction" as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs. -->

If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new? In other words, what is the entropy of international relations? This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015]. If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017. On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.

Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations. We develop a large, flexible ontology of international events with the help of both human coders and natural language processing. We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherCrisisEscalationWar2000; @wilkenfeldInterstateCrisesViolence2000; @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019]. The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes. We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative. We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts. We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode. The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.

This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches. The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision. A final section concludes.

Task Definition {.unnumbered}
========================================

We consider the measurement task of abstracting discrete events about a historical episode in international relations. The easiest way to convey the task is with an example. Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine readable abstractive events. Formally, a historical episode, $H$, is demarcated by a period of time $[T_{start}, T_{end}] \in T$, a set of Players $p \in P$, and a set of behaviors they undertook during that time $b \in B$. International Relations, $IR$, is the system of regularities that govern the strategic interactions that world actors make during a historical episode, given their available options, preferences, beliefs, and expectations of choices made by others. We observe neither $H$ nor $IR$ directly. Rather the Historical Record, $HR$, produces documents $d \in D$ containing some relevant and true (as well as irrelevant and untrue) information about behaviors that were undertaken recorded in the form of unstructured natural language text. The task is to combine informative priors about $IR$ with an unstructured corpus $D$ to produce a series of structured discrete events, $e \in E$, that have high coverage, precision, and recall over what actually took place in history, $H$.

```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}

ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))

temp <- ICBe_events_agreed_markdown %>%
        filter(crisno==196) %>%
        group_by(crisno, sentence_number_int_aligned) %>%
          filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
        ungroup() %>%
        mutate(banding=sentence_number_int_aligned %% 2)
temp$is_subsstring <- NA
for(i in 1:nrow(temp)){
  temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
                                                                                pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
                                                                              ) %>% replace_na(0) %>%  sum()
}
temp <-temp %>%
        mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
        group_by(sentence_number_int_aligned) %>%
          filter(value_markdown!='' | length(value_markdown)==1) %>%
        ungroup() %>%
        mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
        mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
        mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
      #head(100) %>%
ft_cuba_precision <- temp %>%
                     dplyr::select(S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
                      flextable::as_flextable() %>%
        flextable::set_header_labels(values =
        list(
              S = "S",
              ICB = "Natural Language Sentences (ICB Corpus)",
              ICBe = "Machine Readable Events (ICBe)"
             ) ) %>%

                      flextable::width( j = 1, width=0.25)  %>% 
                      #flextable::width( j = 2, width=0.25)  %>% 
                      flextable::width( j = 2, width=8.0)  %>% 
                      flextable::width( j = 3, width=8.0)  %>% 
                      flextable::fontsize(size = 9, part = "all") %>%
                      valign(j = 1:3, valign = "top", part = "body") %>%
                      flextable::line_spacing( space = 1.0, part = "all") %>% 
                      padding( padding = 1, part = "all") %>% 
                      bg( i = which( temp$banding==1 ) , part = "body", bg = "#EFEFEF", j=1:3) %>%
                      ftExtra::colformat_md(j = 3, part="body")
#ft_cuba_precision

ft_cuba_precision %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png", zoom=1) # webshot = "webshot2"
temp <- NULL

```

<!--- REX Remember to put in a Legend for the Icons ---->

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=22cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png"}}
\end{figure}
\clearpage
\twocolumn

Corpus  {.unnumbered}
========================================

For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997]. Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988]. Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p. 59]. Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001]. The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.

Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art {.unnumbered}
========================================

Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record. We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.

The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology. We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do). Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict). We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors, and provide a full codebook in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]

We base our informed priors primarily on two sources of information. The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept. Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text. Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).

The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage. They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Additional relevant but dated or too small of an overlap in domain include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010]. With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See [@balaliCOfEEComprehensiveOntology2021] for a recent review of ontological depth and availability of Gold Standard example text.]

\clearpage
\onecolumn

```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

#target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
#lit_review_pull    <- readxl::read_excel(target_file, sheet="DatasetsComparisonLitReview")

library(googlesheets4) #Do this high up so you get the prompt early
library(lubridate, warn.conflicts = FALSE)
lit_review_pull <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/14RHRKgQGHj7Zr4_xt4fq2bIE7mDNayLKj89tYmOOfHQ/edit?usp=sharing", 
                                sheet="DatasetsComparisonLitReview") #%>% janitor::clean_names() 
dim(lit_review_pull)

library(flextable)
library(ftExtra)
library(tidyverse)
flextable::set_flextable_defaults(fonts_ignore=TRUE)

#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
# NOTE: If one of the citations is degenerate this will throw an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
set_flextable_defaults(fonts_ignore=TRUE)

lit_review_alt <- lit_review_pull %>% 
                  mutate(Literature =   paste0(" [",Literature %>% str_replace("; {0,}$","") ,"]")) %>%
                  mutate(Concept= Concept %>% paste0(Literature)) %>%
                  mutate(Concept = Concept %>% str_replace(fixed("[NA]"),"") ) %>%
                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
                  #dplyr::filter(is.na(group))

n=nrow(lit_review_alt)
k=ncol(lit_review_alt)
horizontal = c(1,k)
r_intro= lit_review_pull$...1 %in% "Domain" %>% sum() #changed to domain
r_players= ( lit_review_pull$...1 %in% "Players" %>% sum() ) + r_intro
r_pieces= ( lit_review_pull$...1 %in% "Pieces" %>% sum() ) + r_players
r_think= ( lit_review_pull$...1 %in% "Think" %>% sum() ) + r_pieces
r_say= ( lit_review_pull$...1 %in% "Say" %>% sum() ) + r_think
r_unarmed= ( lit_review_pull$...2 %in% "Unarmed" %>% sum() ) + r_say
r_armed= ( lit_review_pull$...2 %in% "Armed" %>% sum() ) + r_unarmed
ft <- NULL

library(officer)
big_border = fp_border(color="black", width = 2)

bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
litreview_ft_pnas <- lit_review_alt %>%
      flextable::as_flextable() %>%

      #add_header( 
      #        #"ICB Corpus"="Corpus",
      #        "ICBe"="Ours",
      #        "Phoenix"="CAMEO Dictionary\nSystems",
      #        "Terrier"="CAMEO Dictionary\nSystems",
      #        "ICEWs"="CAMEO Dictionary\nSystems",
      #        "MIDs Events"="Disputes",
      #        "UCDP-GED"="Violence",
      #        "ICB"="Crises",
      #        "COW"="Wars",
      #        "MIDs"="Disputes",
      #        top = T ) %>%

      add_header( 
                  #"ICB Corpus"="Corpus",
                  "ICBe"="Events Datasets",
                  "Phoenix"="Events Datasets",
                  "Terrier"="Events Datasets",
                  "ICEWs"="Events Datasets",
                  "MIDs Incidents"="Events Datasets",
                  "UCDP-GED"="Events Datasets",
                  "ICB"="Episodes Datasets",
                  "COW"="Episodes Datasets",
                  "MIDs"="Episodes Datasets",
                  top = T ) %>%

      set_header_labels(
        values = list("...1" = "" , "...2" = "" ) 
        ) %>%

      merge_h(part = "header") %>% #it's this merge that's killing us

      #Global Borders
      flextable::border_remove() %>% 
      #ok so because of our horizontal merging of headers, we have to manually place a right bar at j=10 2 short of the full width
      flextable::border_outer( part="all", border = big_border ) %>% #this will have a gap
      border(j=10:k, i=1 , part="header", border.right = big_border ) %>% #this fills the gap
      #There's another gap on the bottom left
      border(j=1, i=(n-15):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
      border(j=2, i=(n-5):n , part="body", border.bottom =  big_border ) %>% #this fills the gap

      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      flextable::fontsize(size = 7, part = "all") %>%
      #Banding
      bg( i = bands  , j=3:k, part = "body", bg = "#EFEFEF") %>%

      flextable::rotate(i=2, , j=3:k, rotation="tbrl",part="header") %>%
      flextable::align(align = "center", part = "body") %>%
      flextable::align(align = "center", part = "header")   %>%

      flextable::colformat_char(
          j = 1:ncol(lit_review_alt),
          na_str = "",
          prefix = "",
          suffix = ""
      ) %>%
      #Domains
      hline(i=c(r_intro), border = NULL, part = "body") %>% 
      merge_at(i = 1:r_intro, j = 1:2, part = "body") %>%  
      merge_at(i = 4, j = 5:7, part = "body") %>%
      merge_at(i = 5, j = 5:7, part = "body") %>%
      merge_at(i = 6, j = 5:7, part = "body") %>%
      merge_at(i = 7, j = 5:7, part = "body") %>%

      #players
      hline(i=c(r_players), border = NULL, part = "body") %>% 
      merge_at(i = (r_intro+1):r_players, j = 1:2, part = "body") %>%  
      #pieces
      hline(i=c(r_pieces), border = NULL, part = "body") %>% 
      merge_at(i = (r_players+1):r_pieces, j = 1:2, part = "body") %>%  
      #think
      hline(i=c(r_think), border = NULL, part = "body") %>% 
      merge_at(i = (r_pieces+1):r_think, j = 1:2, part = "body") %>%  
      #say
      hline(i=c(r_say), border = NULL, part = "body") %>% 
      merge_at(i = (r_think+1):r_say, j = 1:2, part = "body") %>%
      #Do
      merge_at(i = (r_say+1):r_armed, j = 1, part = "body") %>%

      #n_unarmed
      hline(i=c(r_unarmed), border = NULL, part = "body") %>% 
      merge_at(i = (r_say+1):r_unarmed, j = 2, part = "body") %>%  
      #n_armed
      #hline(i=c(r_armed), border = NULL, part = "body") %>% 
      merge_at(i = (r_unarmed+1):r_armed, j = 2, part = "body") %>%

      #set_table_properties(layout="autofit")  %>%
      vline( i = 1:2, j = c(3,9), border = NULL, part = "header") %>%
      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
      vline( i = 1:(n), j = c(3,9), border = NULL, part = "body")  %>%

      flextable::width( j = 3, width=3) %>% 
      flextable::width( j = (4):k, width=0.25) %>%
      flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%

      flextable::rotate(j=1, rotation="tbrl",part="all") %>%
      flextable::rotate(j=2, rotation="tbrl",part="all") %>%
      flextable::width( j = 1:2, width=0.1)  %>%
      ftExtra::colformat_md(j = 3, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
#litreview_ft_pnas

#litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
litreview_ft_pnas %>% 
  ftExtra::colformat_md(j = 3, part="body") %>%
  flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable::flextable_to_rmd()

```

\clearpage
\twocolumn

```{r , eval=T, results='hide', echo=F, include=T, message=F, cache=F}

n_crisis <- ICBe_events_agreed %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- ICBe_events_agreed %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
#n_events <- ICBe_events_agreed %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
#n_events_cuba <- ICBe_events_agreed %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_long_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

avg_coders_per_crisis <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)

avg_coders_per_sentence <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)

```

ICBe Coding Process {.unnumbered}
========================================

The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag. The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig. B1). Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities. Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g. force size, fatalities, domains, units, etc. A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g. an offer for the U.S.S.R. to remove missiles from Cuba in exchange for the U.S. removing missiles from Turkey. Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.

Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.^[Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook. Undergraduate coders were students who engaged in classroom workshops.] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc. We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders. This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.

```{r}
#We calculate means in the SI appendix on agreement
means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
                   group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                   dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)

means_group_keep <- codings_long_agreement %>% filter(value_normalized!='') %>% 
                    filter(algo1==1) %>%
                    group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                    dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean)
```

Internal Consistency {.unnumbered}
========================================

We evaluate the internal validity of the coding process in several ways. For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig. B3). Across all concepts, the Top 1 Tag Agreement was low among novices (`r means_group_any$Novices %>% round(2) %>% scales::percent()`), moderate for experts (`r means_group_any$Experts %>% round(2) %>% scales::percent()`), and high (`r means_group_keep$Experts_keep %>% round(2) %>% scales::percent()`) following the consensus screening procedure.

We attribute the remaining disagreement primarily to three sources. First, we required coders to rate their confidence which was observed to be low for 20% of sentences- half due to a mismatch between the ontology and the text ("survey doesn't fit event"-45%) and half due to a lack of information or confused writing in the source text ("more knowledge needed"-40%, "confusing sentence"-6%). Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig. B4). Second, as intended agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50%-60%). Third, individual coders exhibiting nontrivial coding styles, e.g. some more expressive applying many tags per concept while others focused on only the single best match. We further observed unintended synonymity, e.g. the same information can be framed as either a threat to do something or a promise not to do something.

Case Study Selection {.unnumbered}
========================================

The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems. We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website. In this paper, we focus on two deep case studies. The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles). The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas). Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers. We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.

Recall {.unnumbered}
========================================

Recall measures the share of desired information recovered by a sequence of coded events, $Pr(E|H)$, and is poorly defined for historical episodes. First, there is no genuine ground truth about what occurred, only surviving texts about it. Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia. History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events. The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals. We need a yardstick for history.

Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative. For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents. Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts. The more accounts that mention a detail, the more central it is to understanding the true historical episode. The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing. With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context. Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.

Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2. Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.

From them, we draw several stylized facts. First, there is substantial variation in which details any one document will choose to include. Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative. Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details. Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g. the U.S. was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g. a long term lease on naval facilities in Crimea. Fourth, we find variation between the two cases. Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting. The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.

We find substantive variation in recall across systems. Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark. The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions. The two episode level datasets have very low coverage of contextual details. The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier. ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable. Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.

```{r cuban case study recall, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

#
#Lit review
#child=c('ICBEdataset_paper_litreviewtable.Rmd')
library(tidyverse)
library(flextable)
library(ftExtra)
flextable::set_flextable_defaults(fonts_ignore=TRUE)

library(googlesheets4) #Do this high up so you get the prompt early
library(lubridate, warn.conflicts = FALSE)
case_study_cuban <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names() 
dim(case_study_cuban)
#case_study_cuban$date <- case_study_cuban$date %>% lapply(FUN=function(x) { ifelse(is.null(x), "", x[[1]] %>% as.character() )   }   ) %>% unlist() %>% as.Date()

#Replace emoticons with images
replace_emoticons <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
}

temp1 <- case_study_cuban %>% 
                #filter(!is.na(date)) %>%
                #head(2) %>%
                mutate(date=date %>% anytime::anydate()) %>%
                mutate(year=year(date) %>% as.character() ) %>%
                mutate(month=month(date) %>% as.character()) %>%
                mutate(day=day(date) %>% as.character()) %>%
                mutate(documents = documents %>% as.numeric()) %>%
                mutate(Rank=rank(-documents, ties.method="first")  ) %>%
                dplyr::select(Y=year,M=month, D=day, Rank, Event=event, Docs=documents, icb_narrative=icb_narrative, ICBe=ic_be, ICB=icb, MIDs=mids, phoenix=phoenix) %>% 
                mutate(Event= Event %>%  replace_emoticons) %>% 
                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
                mutate(ICB = ifelse(!is.na(ICB) & !ICB %in% 0, "✓", NA)) %>%
                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0, "✓", NA)) %>%
                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0, "✓", NA)) %>%
                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0, "✓", NA)) %>%

                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
                mutate(YMD=paste(Y,
                                 M %>% str_pad(2, pad = "0") ,
                                 D %>% str_pad(2, pad = "0"), 
                                 sep="-") %>% trimws() %>%
                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
                                 str_replace_all("^NA-","") %>% 
                                 str_replace_all("^-00|^00","") %>% 
                                 str_replace_all("^-00|^00","") %>% 
                                 str_replace_all("^-","") 
                       ) %>%
                dplyr::select(-Y,-M,-D) %>%
                relocate(YMD, .before = Rank) %>%
                dplyr::select(-Rank)
dim(temp1)

#banding <- temp %>% mutate(date=as.Date(paste(Y,M,D, sep="-")) %>% as.numeric() %>% as.factor() %>% as.numeric() ) %>% pull(date) %% 2
banding <- 1:nrow(temp1) %% 2
k=ncol(temp1)
ft <- temp1   %>%
      flextable::as_flextable() %>% 
      flextable::set_header_labels(values =
        list(
              Event = "Ground\nTruth\nEvents",
              icb_narrative = "ICB Corpus",
              ICB = "ICB",
              MIDs = "MIDs",
              phoenix = "Phoenix"
             ) ) %>%
      flextable::width( j = 1, width=0.6)  %>% 
      #flextable::width( j = 2, width=0.025)  %>%
      #flextable::width( j = 3, width=0.025)  %>%
      #flextable::width( j = 5, width=0.025) %>%
      flextable::width( j = 2, width=3.0)  %>%
      flextable::width( j = 3, width=0.03) %>%
      flextable::width( j = 4:k, width=0.15) %>% #icb
      #merge_v( j = 1,  part = "body", combine = T) %>%
      #merge_v( j = 3,  part = "body", combine = F) %>%
      #merge_v( j = 4,  part = "body", combine = F) %>%

      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
      align(i = 1,  align = "center", part = "header") %>%
      valign(j = 1:2, valign = "center", part = "all") %>%
      align(i = NULL, j = 1, align = "right", part = "body")  %>%
      align(i = NULL, j = 2, align = "left", part = "body")  %>%
      #align(i = NULL, j = 2, align = "center", part = "body")  %>%
      #align(i = NULL, j = 3, align = "left", part = "body")  %>%
      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      flextable::fontsize(size = 7, part = "all") %>%
      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
      vline(j=c(1,2,3,4,5,6,7),  border = NULL, part = "all") %>%
      hline(i=c(26,46)) %>%
      ftExtra::colformat_md(j = 2, part="body") 
      #ftExtra::colformat_md(j = 6, part="body")

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_recall.png", zoom=1, webshot = "webshot2") # webshot = "webshot2"

#Ok rather than try to match up we're going to do this by hand now

```

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

library(googlesheets4) #Do this high up so you get the prompt early
library(lubridate, warn.conflicts = FALSE)
case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names() 
dim(case_study_crimea)

#Replace emoticons with images
replace_emoticons_crimea <- function(x){
      x %>%
            #https://emojiterra.com/flag-for-united-states/
            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
            #https://emojiterra.com/flag-for-russia/
            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
            #Ukraine
            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
            #
            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ")
}

rex_date <- function(x){
  a <- x[1] %>% as.character() %>% unlist()
  if(is.null(a)){return('')}
  return(a)
}
case_study_crimea$date <- sapply(sapply(case_study_crimea$date, as.character), rex_date)
temp2 <- case_study_crimea %>% 
                filter(keep %in% 1) %>%
                #filter(!is.na(date)) %>%
                #head(2) %>%
                mutate(date=date %>% anytime::anydate()) %>%
                mutate(year=year(date) %>% as.character() ) %>%
                mutate(month=month(date) %>% as.character()) %>%
                mutate(day=day(date) %>% as.character()) %>%
                mutate(n_sources = n_sources %>% as.numeric()) %>%
                mutate(Rank=rank(-n_sources, ties.method="first")  ) %>%
                dplyr::select(Y=year,M=month, D=day, Rank,  Event=event, Docs=n_sources, 
                              icb_narrative=icb_narrative, ICBe=ic_be, MIDs=mids, phoenix, terrier, icews ) %>%  #, ICB=icb, MIDs=mids, phoenix=phoenix
                mutate(Event= Event %>%  replace_emoticons_crimea) %>%
                arrange(Y %>% as.numeric() ,M %>% as.numeric()  ,D %>% as.numeric() ) %>%
                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
                mutate(YMD=paste(Y,
                                 M %>% str_pad(2, pad = "0") ,
                                 D %>% str_pad(2, pad = "0"), 
                                 sep="-") %>% trimws() %>%
                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
                                 str_replace_all("^NA-","") %>% 
                                 str_replace_all("^-00|^00","") %>% 
                                 str_replace_all("^-00|^00","") %>% 
                                 str_replace_all("^-","") 
                       ) %>%
                dplyr::select(-Y,-M,-D) %>%
                relocate(YMD, .before = Rank) %>%
                dplyr::select(-Rank) %>% 
                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
                mutate(icews = ifelse(!is.na(icews) & !icews %in% 0 , "✓", NA)) %>%
                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0  , "✓", NA)) %>%
                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0  , "✓", NA)) %>%
                mutate(terrier = ifelse(!is.na(terrier) & !terrier %in% 0  , "✓", NA))  %>%
                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0  , "✓", NA))

dim(temp2)

banding <- 1:nrow(temp2) %% 2
k=ncol(temp2)
ft <- temp2  %>%
      flextable::as_flextable() %>% 
      flextable::set_header_labels(values =
        list(
              Event = "Ground\nTruth\nEvents",
              icb_narrative = "ICB Corpus",
              ICBe = "ICBe",
              MIDs="MIDs",
              icews_hash = "ICEWS"
             ) ) %>%
      flextable::width( j = 1, width=0.6)  %>% 
      flextable::width( j = 2, width=3.0)  %>%
      flextable::width( j = 3:k, width=0.15) %>% #icb
      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
      align(i = 1,  align = "center", part = "header") %>%
      valign(j = 1:2, valign = "center", part = "all") %>%
      align(i = NULL, j = 1, align = "right", part = "body")  %>%
      align(i = NULL, j = 2, align = "left", part = "body")  %>%
      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      flextable::fontsize(size = 7, part = "all") %>%
      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
      vline(j=1:k,  border = NULL, part = "all") %>%
      #hline(i=c(26,46)) %>%
      ftExtra::colformat_md(j = 2, part="body") 
      #ftExtra::colformat_md(j = 6, part="body")

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_recall.png",
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"

```

```{r, recall combined, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

temp3 <- temp1 %>% mutate(row=row_number()) %>% full_join(temp2 %>% mutate(row=row_number()), by='row') %>% 
         mutate(row="") #we're going to use this as our vertical break

n_left <- (!is.na(temp3$Event.x) ) %>% sum()
n_right <- (!is.na(temp3$Event.y) ) %>% sum()

k=ncol(temp3)
kleft=ncol(temp1)
kright=ncol(temp2)
left_end=kleft
right_start=left_end+2
left=c(1:left_end)
right=c(right_start:k)
horizontal = c(left,right)
dates=c(1,right_start)
events = dates + 1
checkmarks = c((events[1]+1):left_end , (events[2]+1):k)

library(officer)
big_border = fp_border(color="black", width = 2)

banding1 <- 1:nrow(temp1) %% 2
banding2 <- 1:nrow(temp2) %% 2
ft <- temp3  %>%
      flextable::as_flextable() %>%

      flextable::line_spacing( space = 1.0, part = "all") %>% # 
      flextable::padding(padding = 0, part = "body") %>%
      flextable::fontsize(size = 7, part = "all") %>%
      bg( i = which( banding1==1 ) , part = "body", bg = "#EFEFEF", j=left) %>%
      bg( i = which( banding2==1 ) , part = "body", bg = "#EFEFEF", j=right) %>%

      #Headers
      flextable::set_header_labels(values =
        list(
              YMD.x = "YMD",
              Event.x = "Synthetic Narrative",
              Docs.x = "Mentions",
              icb_narrative.x = "ICB Corpus",
              ICBe.x = "ICBe",
              ICB = "ICB",
              MIDs.x = "MIDs",
              phoenix.x = "Phoenix",
              phoenix.y = "Phoenix",
              row="",
              YMD.y = "YMD",
              Event.y = "Synthetic Narrative",
              Docs.y = "Mentions",
              icb_narrative.y = "ICB Corpus",
              ICBe.y = "ICBe",
              icews = "ICEWS",
              MIDs.y = "MIDs",
              terrier="Terrier"
             ) ) %>%

      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbass (2014)"), colwidths = c(kleft, 1,kright) ) %>%

      #Global
      flextable::border_remove() %>% 
      #Left border
      border(j=1, i=1:n_left , part="body", border.left =  big_border ) %>% #
      border(j=1, i=1:2 , part="header", border.left =  big_border ) %>% #

      border(j=left_end, i=1:2 , part="header", border.right =  big_border ) %>% #
      border(j=left_end, i=1:n_left , part="body", border.right =  big_border ) %>% #

      border(j=1:left_end, i=n_left , part="body", border.bottom =  big_border ) %>% #
      border(j=1:left_end, i=1 , part="body", border.top =  big_border ) %>% #
      border(j=1:left_end, i=1:2 , part="header", border.top =  big_border ) %>% #

      #Right border
      border(j=right_start, i=1:n_right , part="body", border.left =  big_border ) %>% #
      border(j=k, i=1:n_right , part="body", border.right =  big_border ) %>% #

      border(j=right_start, i=1:2 , part="header", border.left =  big_border ) %>% #
      border(j=k, i=1:2 , part="header", border.right =  big_border ) %>% #
      border(j=1:k, i=1 , part="header", border.right =  big_border ) %>% #

      border(j=right_start:k, i=n_right , part="body", border.bottom =  big_border ) %>% #
      border(j=right_start:k, i=1 , part="body", border.top =  big_border ) %>% #
      border(j=right_start:k, i=1:2 , part="header", border.top =  big_border ) %>% #

      vline(i=1:n_left, j=1:(left_end-1),  border = NULL, part = "body")  %>%
      vline(i=1:n_right,j=right_start:(k-1),  border = NULL, part = "body")  %>%
      vline(i=2, j=1:(left_end-1),  border = NULL, part = "header")  %>%
      vline(i=2,j=right_start:(k-1),  border = NULL, part = "header")  %>%

      #
      hline(i=c(26,46), j=left,  border = NULL, part = "body")  %>%
      hline(i=c(11), j=right,  border = NULL, part = "body")  %>%

      #Header
      flextable::rotate(i=2, , j=3:left_end, rotation="tbrl", part="header") %>% 
      flextable::rotate(i=2, , j=(left_end+4):k, rotation="tbrl", part="header") %>%

      valign(j = 1:2, valign = "center", part = "all") %>%
      align(i = 2, j = NULL, align = "center", part = "header")  %>%

      #break
      flextable::width( j = left_end+1, width=0.25)  %>%

      #Dates
      flextable::width( j = dates, width=0.6)  %>% 
      align(i = NULL, j = dates, align = "right", part = "body")   %>%

      #events
      flextable::width( j = events, width=2.50)  %>%
      align(i = NULL, j = events, align = "left", part = "body")  %>%
      ftExtra::colformat_md(j = events, part="body") %>%

      #Checkmarks
      flextable::width( j = checkmarks, width=0.05) %>%
      align(i = NULL, j = checkmarks, align = "center", part = "body")

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea.png", zoom=1, webshot = "webshot2") # webshot = "webshot2"

```

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

#Recall Summary Statistics
#, icb_narrative_cd=icb_narrative.y, icews_cd=icews_hash
temp1_long <- temp1 %>% dplyr::select(docs=Docs, ICB_Narrative=icb_narrative, ICBe=ICBe, ICB=ICB,MIDs=MIDs,Phoenix=phoenix) %>% mutate(crisis="Cuban Missile Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>% 
              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))

temp2_long <- temp2 %>% dplyr::select(docs=Docs,ICB_Narrative=icb_narrative,ICBe=ICBe,MIDs=MIDs , Phoenix=phoenix, Terrier=terrier, ICEWS= icews) %>% mutate(crisis="Crimea-Donbas Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>% 
              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))

temp3_long <- bind_rows(temp1_long,temp2_long)

Y_hat <- temp3_long %>% dplyr::select(name) %>% distinct()
mylogit <- glm(value ~ name, data = temp3_long, family = "binomial")
Y_hat$fit <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$fit
Y_hat$se <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$se.fit
Y_hat$name <- Y_hat$name %>% fct_reorder(Y_hat$fit)

#Y_hat %>% ggplot(aes(name, fit)) +
#          geom_point(size=4) +
#          geom_errorbar(aes(ymin = fit-(1.98*se), ymax = fit+(1.98*se)), width = 0.1, linetype="solid") + coord_flip()  + theme_bw() + 
#          ylab("Mean Recall") + xlab("")

#temp3_long_means <- temp3_long %>% 
#                    group_by(name) %>%
#                    summarise(value= value %>%mean() %>% round(2))

#temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + geom_point() +
#  geom_smooth(method = "glm", method.args = list(family = "binomial"), se=F) + 
#  ylab("Recall") + xlab("Document Mentions (Log)") +
#  facet_wrap(~crisis, scales="free_x")

library(geomtextpath)
temp3_long$crisis <- factor(temp3_long$crisis, levels= temp3_long$crisis %>% as.character() %>% unique() %>% sort() %>% rev() )
p_recall <- temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + 
  #geom_point() +
  geom_textsmooth(aes(label = name), size=3, method = "glm", method.args = list(family = "binomial"), se=F) + 
  ylab("Recall") + xlab("Document Mentions (Log)") +
  facet_wrap(~crisis, scales="free_x") +
  theme_bw() +
  theme(legend.position="none")

#p_recall

ggsave(file=paste0(here::here(), '/replication_paper/figures/p_recall.png'),
       plot = p_recall ,
       width=5, height=3.0)

library(magick)
tiger <- image_read("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea.png")
tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png")

```

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure}
\clearpage
\twocolumn

Precision {.unnumbered}
========================================

The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, $Pr(H|E)$. It does little good to recall a historical event but too vaguely (e.g. MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g. ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications. ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable. You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move. We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig. D3 and D4) and all crises on the companion website.

```{r crisis map function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

global_check_overlap=F
library(igraph)
library(RColorBrewer)
library(ggraph)
target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()

actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
                                sheet="actor_translator") #%>% janitor::clean_names() 
#Convert to a local file for pushing
#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
library(pals); #install.packages('pals')
pallet <- c(pals::glasbey(),  pals::alphabet2())
pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
library(colorspace)
#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))

icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){

  icb_events_subset <-  ICBe_events_agreed %>% 
                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
                         tidyr::fill(decade, .direction="downup") %>%
                         tidyr::fill(year, .direction="downup") %>%
                         tidyr::fill(month, .direction="downup") %>%
                         tidyr::fill(day, .direction="downup") %>% 
                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
                         arrange(decade, year,month,day) %>%
                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order

  icb_events_subset_diad <- icb_events_subset %>% 
                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
                                                    sent,
                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
                                                    thinkkind, sayintkind, dokind,
                                                    point_in_time_year, point_in_time_month
                                                    ) %>% distinct() %>%
                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))

  notes=NULL
  if(prune_rare==T){
    actor_sent_counts <- 
      bind_rows(
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
        ) %>% 
          na.omit() %>%
          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

      #New pruning rule, either singletons or actors with less than 10% of the max actor
      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
      if(left_over_count<3){
        #Skip pruning if it leaves less than 3 actors
      } else {

        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
        actor_singleton_labels <- actor_map$value_normalized_label
        names(actor_singleton_labels) <- actor_map$actor
        actor_singleton_labels <- actor_singleton_labels[singleton_actors]

        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")

        #Easiest thing is to just prune the original data
        icb_events_subset <- icb_events_subset %>%
          filter(!(
                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
                say_actor_a %in% singleton_actors |
                say_actor_b %in% singleton_actors |
                do_actor_a %in% singleton_actors |
                do_actor_b %in% singleton_actors 
          ) )

          #recreate diads again using the new sentence numbers
          icb_events_subset_diad <- icb_events_subset %>% 
                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
                                                            sent,
                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
                                                            thinkkind, sayintkind, dokind,
                                                            point_in_time_year, point_in_time_month
                                                            ) %>% distinct() %>%
                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
                                        filter(!(
                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
                                              say_actor_a %in% singleton_actors |
                                              say_actor_b %in% singleton_actors |
                                              do_actor_a %in% singleton_actors |
                                              do_actor_b %in% singleton_actors 
                                        ) ) %>% 
                                       arrange(sent) %>%
                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
      }
  }

  g <- make_empty_graph(n = 0, directed = TRUE)
    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,

  #Order actors by how many interactions they have together
  temp <- bind_rows(
    icb_events_subset_diad  %>% 
      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
    icb_events_subset_diad %>% 
      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
  )  %>% arrange(actor_1, actor_2) %>% distinct()

  #new plan is to minimize the number of crossovers
  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("actor_2", "actor_1", "sent"))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
  rowwise() %>%
  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
  arrange(desc(n))

  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")
  diag(temp2_wide) <- 0
  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue

  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events

  #####Nodes
  icb_events_subset_nodes <- 
            bind_rows(
                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
            )  %>%
            filter(!is.na(actor)) %>%
           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  icbe_actor_to_qcode <- icb_events_long %>%
                         dplyr::filter(crisno==thiscrisis  ) %>% 
                         filter(varname_normalized %>% str_detect("actor")) %>% 
                         dplyr::select(value_normalized,value_qcode) %>% 
                         na.omit() %>% distinct()

  actor_colors_df <- icbe_actor_to_qcode %>%
    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
  actor_colors <- actor_colors_df$actor_color
  names(actor_colors) = actor_colors_df$value_normalized

  date_sineposts <- icb_events_subset_nodes  %>%
                      mutate(x=max(x)+50) %>%
                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
                      na.omit() %>% 
                      distinct() %>%  
                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                      group_by(sent) %>%
                       filter(year_float==min(year_float)) %>%
                      ungroup() %>% as.data.frame() %>%
                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                      filter(!duplicated(year_float ) ) %>%
                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

  ####Actor levels
  icb_events_subset_nodes_min <- 
    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
    rowwise() #%>%
    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors

  for(i in 1:nrow(icb_events_subset_nodes)){
    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
                                actor = icb_events_subset_nodes$actor[i], 
                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
  }

  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )

  #####Time Edges
  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()

  g <- g %>% 
       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)

  ######Monads
  icb_events_subset_monad <- 
            bind_rows(
                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
            ) %>% 
            na.omit() %>% 
            distinct() %>% 
            filter(!duplicated(paste(sent,actor,leaf))) %>%
            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
            distinct() %>% 
            group_by(sent,actor,actor_sent) %>%
              summarise(leaf=paste(leaf, collapse="\n") ) %>%
            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))

  ######Directed
  icb_events_subset_directed <- 
            #We need to enumerate all the possibilities
            bind_rows(
              #Do alone
              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
              #Say alone
              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
              #Say Do
              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf) 
            ) %>% 
            na.omit() %>% 
            distinct() %>% 
            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
            arrange(sent, actor_sent_1,leaf) %>%
            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
           #It is actually easier just to rejex out some dupes
            mutate(leaf = leaf %>%
                     str_replace("accept\naccept","accept") %>%
                   str_replace("appeal\nappeal","appeal") %>%
                   str_replace("reject\nreject","reject") %>%
                   str_replace("express intent\nexpress intent","express intent") 
                   ) %>%
           arrange(sent, actor_sent_1,leaf) %>%
           filter(actor_sent_1!=actor_sent_2)

  #debug
  icb_events_subset_directed <- icb_events_subset_directed  %>% 
           group_by(sent, leaf) %>%
               mutate(bundle_count=n()) %>%
               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
            ungroup()

  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                       timeedge=F, 
                       leaf=icb_events_subset_directed$leaf2, 
                       eventedge=T,
                       actor=icb_events_subset_directed$actor_1,
                       bundle_count=icb_events_subset_directed$bundle_count
                       )

  ######Put it all together
  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
  p_metro_map <- g %>%  
          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel

          #Event edges
          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
          geom_edge_arc(aes(  
                            colour=actor,
                            label=leaf,
                            filter=eventedge==T & bundle_count==1 
                            ),
                        label_colour=NA, 
                        vjust = -0.75,
                        lineheight = .75,
                        sep = unit(1, 'mm'), 
                        edge_width=0.25, 
                        show.legend = F,
                        arrow = arrow(length = unit(2, 'mm')),
                        label_size=3,
                        check_overlap=global_check_overlap,
                        start_cap = circle(3, 'mm'),
                        end_cap = circle(3, 'mm'),
                        angle_calc = 'along' #,
                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
                       ) +
              #Grouped Edges
              geom_edge_parallel(aes(  
                                  colour=actor,
                                  label=leaf,
                                  filter=eventedge==T & bundle_count>1
                                  ),
                              vjust = -0.75,
                              lineheight = .75,
                              sep = unit(5, 'mm'), 
                              edge_width=0.4,  #0.25
                              show.legend = F,
                              arrow = arrow(length = unit(1, 'mm')),
                              label_size=4,
                              check_overlap=global_check_overlap,
                              start_cap = circle(3, 'mm'),
                              end_cap = circle(3, 'mm'),
                              angle_calc = 'along'
                             ) +

              #Time edges
              geom_edge_link(aes(
                              edge_colour=actor,
                              filter=timeedge==T
                              ),
                              edge_width=0.1, 
                              show.legend = F,
                              check_overlap=global_check_overlap
                             ) +
              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
              #Fatalities
              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +

              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
              #Add Actor Names
              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
                        check_overlap=global_check_overlap) + #-45
              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
              scale_color_manual(values = actor_colors)  +
              scale_edge_color_manual(values = actor_colors) +
              #theme_bw() + 
              #labs( title = plot_title ) +
              theme_graph() +
              theme(legend.position = "none") #+
              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)

  if(prune_rare==T & !is.null(notes)){
     p_metro_map <- p_metro_map + labs(caption = notes)
  }

  return(p_metro_map)
}

```

```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

library(ggplot2)
library(cowplot)

p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      caption = NULL
    ) +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))

p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      caption = NULL
    ) +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))

p_precision_combined <- plot_grid(
            p_196_icbe +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
               p_471_icbe +
    theme(plot.margin=unit(c(0,0,0,0),"in")) +
   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )

save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
          p_precision_combined, base_height = 14, base_width = 18)

```

\clearpage
\onecolumn
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps  \label{fig:p_precision_combined}}
\centering{\includegraphics[width=24cm]{../figures/p_precision_combined.png}}
\end{sidewaysfigure}
\clearpage
\twocolumn

We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text. We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website. We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).

We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark. Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to. Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology. If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]

```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

library(flextable)
library(ftExtra)
library(tidyverse)

#Load it here before the python reticulate business
#devtools::install_github("ropenscilabs/umapr")
#library(umapr)

ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))

ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
                                                 str_replace_all("[0-9]{4}","Entity") %>% #All years with entity
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("[0-9]","") %>%  #replace all digits with blanks
                                                 str_replace_all(" {1,}"," ")   
                                               )  #

sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
                    dplyr::select(sentences_unique_sanitized) %>% 
                    distinct() %>%
                    pull(sentences_unique_sanitized) %>% 
                    unique() %>% na.omit()
length(sentences_unique ) #12162
head(sentences_unique)

```

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

#To set python, set it in ~/.Renviron. `use_python()` doesn't seem to work as desired. See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).

library(reticulate)
reticulate::py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

```

```{python, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers

fromscratch=False

if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #12161 12162
  n=len(sentences)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #(12103, 768)

else:
  print("Skipping")

```

```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}

fromscratch = FALSE
if(fromscratch){
  sentences_embeddings <- py$sentences_embeddings
  dim(sentences_embeddings)
  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
}else{
  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
  dim(sentences_embeddings)
}

```

```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.  
embedding <- umapr::umap(sentences_embeddings)
#plot(embedding[,c('UMAP1','UMAP2')])

sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()

sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique

ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
                                        left_join(sentences_embeded_umap) %>% 
                                        left_join(sentences_embeded_mpnet)

ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))

ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
                                                arrange(UMAP1,UMAP2) %>%
                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis

```

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

library(cowplot)
ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))

value_means <- ICBe_events_agreed_markdown_embedded %>%
               dplyr::select(UMAP1,UMAP2, contains("escalate"),contains("coop"),contains("sayintkind"), contains("thinkkind")) %>%
               pivot_longer(cols=-c(UMAP1,UMAP2)) %>% filter(!is.na(value) & value!='') %>% 
               mutate(value = value %>% str_split(";")) %>% 
               unnest(value) %>% 
               mutate(value = value %>% str_trim()) %>%
               filter(!value %>% str_detect("sentence|^[0-9]")) %>%
               mutate(color=NA) %>%
               mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
               mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
               mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
               mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
               mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
               mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
               dplyr::select(-name) %>%
               group_by(color, value) %>%
               mutate(n=n()) %>%
               filter(n>20) %>% #note require at least 20 examples of that tag
               dplyr::summarise_all(median)

value_normalized_colors <- value_means$color 
names(value_normalized_colors) = value_means$value

library(ggplot2)
library(ggrepel)
p_semantic_embeddings <-
      ICBe_events_agreed_markdown_embedded %>%
      ggplot(aes(x=UMAP2,y=UMAP1)) +
      geom_point(size=0.5, alpha=0.25) + 
      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
      theme_bw() +
      theme(legend.position = "none") + 
      geom_label(data=value_means,
                 aes(x=UMAP2,y=UMAP1, fill = value %>% as.factor(), label=value, size=50), size = 2.5, inherit.aes=F, 
                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
                 ) +   
      #geom_label_repel(data=value_means,
      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
      #           min.segment.length = 0
      #           ) + 
      labs(
          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
          caption = ""
      ) +
     scale_color_manual(values = value_normalized_colors) +
     scale_fill_manual(values = value_normalized_colors) +
     scale_x_continuous(expand = c(0, 0)) +
     scale_y_continuous( expand = c(0, 0)) #+
     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
     #coord_flip()

ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)

#Now do the dendro
library(ggdendro)
#We actually need the raw embeddings

#Rex Note to take only one per sentence

#This is unreasonably slow because it's large and in tidy. Couldn't do it every time if we wanted to.
value_highdim <- ICBe_events_agreed_markdown_embedded %>%
                 dplyr::select(starts_with("V",  ignore.case = F), contains("escalate"),contains("coop"),contains("sayintkind"), 
                               contains("thinkkind"), crisno, sentence_number_int_aligned) %>% 
                 pivot_longer(cols=-c(starts_with("V",  ignore.case = F), crisno, sentence_number_int_aligned) ) %>%
                 filter(!is.na(value) & value!='') %>% #40,898
                 filter(!value %>% str_detect("sentence|^[0-9]")) %>% 
                 mutate(value = value %>% str_split(";")) %>% 
                 unnest(value) %>% 
                 mutate(value = value %>% str_trim())   %>% #
                 mutate(color=NA) %>%
                 mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
                 mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
                 mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
                 mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
                 mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
                 mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
                 dplyr::select(-name) %>%
                 group_by(color, value) %>%
                  mutate(n=n()) %>% 
                 ungroup() %>%
                 arrange(n, value) %>%
                 filter(!duplicated( paste(crisno, sentence_number_int_aligned)) ) %>% #only take one per sentence to break mechanically induced correlations
                 filter(n>20)

dim(value_highdim)

value_highdim_medians <- value_highdim %>% 
                           group_by(color, value) %>%
                           dplyr::summarise_all(median)

value_normalized_colors <- value_highdim_medians$color 
names(value_normalized_colors) = value_highdim_medians$value

m <- value_highdim_medians %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix() 
rownames(m) <- value_highdim_medians$value
d <- m %>% dist()
hc <- hclust(d, method="ward.D2")
library(ggplot2)
library(ggdendro)
hcdata <- dendro_data(hc, type = "rectangle")
p_dendro <- ggplot() +
            geom_segment(data = segment(hcdata), 
                         aes(x = x, y = y, xend = xend, yend = yend)
            ) +
            geom_text(data = label(hcdata) %>% mutate(color=value_highdim_medians$color ), 
                      aes(x = x, y = y, label = label, hjust = 0, color=color[hc$order]), 
                      size = 3
            ) +
            coord_flip() +
            scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
            scale_y_reverse( expand = c(0.1, 0.0, 0.0, 5.0)) +  #limits = c(-10, 10),
            theme_bw() +
            theme(legend.position="none")
#p_dendro

p_combined <- plot_grid(
  p_semantic_embeddings + xlab("") + ylab("") + 
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
  p_dendro  + xlab("") + ylab("") + 
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),  
  labels = c('',''),
  align = "v", ncol = 2, rel_widths = c(3, 1)  )
#p_combined

ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)

```

\clearpage
\onecolumn
\begin{figure}[H]
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{../figures/p_semantic_embeddings_dendro.png}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to visually recognizable. }
\end{figure}
\clearpage
\twocolumn

Finally, how does ICBe's precision compare to the existing state of the art? The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis. On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible. Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.

```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

library(ggplot2)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggtext)

icews_clean_471 <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")
dim(icews_clean_471) #270,642
icews_clean_471_small <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")

icews_clean_subset_top10_day <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")

keys <- c("sign formal agreement") #"express accord", #,"declare truce, ceasefire"
events1 <- icews_clean_subset_top10_day %>% 
           filter(cameo_label %in% keys) %>% 
           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
p1 <- events1 %>%
      ggplot( aes(x = date, y = dyad_markdown)) + #
      geom_tile(fill="lightblue") + theme_bw() +
      geomtextpath::geom_textvline(xintercept = as.Date('2013-11-21'), label="Reject EU\nTrade Deal" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-18'), label="Annex Crimea" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-09-06'), label="MINSK I" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2015-02-21'), label="MINSK II" , linetype="dotted", color = "red", size=3) +
      ylab("") + xlab("") +
      labs(subtitle=keys %>% paste(collapse="; ")) +
      tidytext::scale_y_reordered()

keys <- c("reject plan, agreement to settle dispute") #"express accord", #,"declare truce, ceasefire"
events2 <- icews_clean_subset_top10_day %>% 
           filter(cameo_label %in% keys) %>% 
           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
p2 <- events2 %>%
      ggplot( aes(x = date, y = dyad_markdown)) + #
      geom_tile(fill="lightblue") + theme_bw() +
      geomtextpath::geom_textvline(xintercept = as.Date('2013-11-21'), label="Reject EU\nTrade Deal" , linetype="dotted", color = "red", size=3) +
      ylab("") + xlab("") +
      labs(subtitle=keys %>% paste(collapse="; ")) +
      tidytext::scale_y_reordered()

#,"fight with artillery and tanks","Use unconventional violence", "fight with small arms and light weapons","Mobilize or increase armed forces","Demonstrate military or police power", "Violate ceasefire", "Occupy territory"
keys <- c("use conventional military force")
events3 <- icews_clean_subset_top10_day %>% 
           filter(cameo_label %in% keys) %>% 
           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
p3 <- events3 %>%
      ggplot( aes(x = date, y = dyad_markdown)) + #
      geom_tile(fill="lightblue") + theme_bw() +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-02-27'), label="Seize Gov Building Crimea" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-02-18'), label="Rus Annex Crimea" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-16'), label="Fighting Donbas" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-04-06'), label="Fighting Donbas" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-09-06'), label="Continued Fighting Donbas" , linetype="dotted", color = "red", size=3) +
      ylab("") + xlab("") +
      labs(subtitle=keys %>% paste(collapse="; ")) +
      tidytext::scale_y_reordered()

#,"Refuse to ease economic sanctions, boycott, or embargo", "Reduce or stop economic assistance","Reduce or stop material aid","Impose blockade, restrict movement", "Reduce or stop military assistance"
keys <- c("impose embargo, boycott, or sanctions")
events4 <- icews_clean_subset_top10_day %>% 
           filter(cameo_label %in% keys) %>% 
           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
p4 <- events4 %>%
      ggplot( aes(x = date, y = dyad_markdown)) + #
      geom_tile(fill="lightblue") + theme_bw() +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-17'), label="US-EU Sanction Rus" , linetype="dotted", color = "red", size=3) +
      geomtextpath::geom_textvline(xintercept = as.Date('2014-07-17'), label="EU Sanctions Rus\nRus Sanctions Ukr" , linetype="dotted", color = "red", size=3) +
      ylab("") + xlab("") +
      labs(subtitle=keys %>% paste(collapse="; ")) +
      tidytext::scale_y_reordered()

library(cowplot)
p_ICEWS <- plot_grid(
           p1 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
           p2 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
           p3 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
           p4 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
           #labels = c('Cuban Missiles','Crimea-Donbas'), 
           align = "v", ncol = 1 , rel_widths = c(1) )

save_plot(file=paste0(here::here(),
                      '/replication_paper/figures/p_precision_icews.png'),
          p_ICEWS, base_height = 10, base_width = 14)

```

However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe. For example, [@terechshenkoHotCollarLatent2020] attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline. Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g. geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks].

We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event. We choose four event types around key moments in the crisis. The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized. The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal. Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns. Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions. In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.

\clearpage
\onecolumn
\begin{figure}[H]
\caption{ ICEWs Counts of Events per Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
\centering{\includegraphics[width=17cm]{../figures/p_precision_icews.png}}
\textit{Notes:Unit of analysis is the Dyad-Day. Edges <-> indicates undirected dyad and -> indicates directed dyad. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Event types are grouped by hand along similar themes. Blue bars indicate an event recorded by ICEWs for that dyad on that day. }
\end{figure}
\clearpage
\twocolumn

<!--
286 Sign formal agreement
Reject 99

crisis.
ICEWS Precision bad for networks  for 
See [@althausTotalErrorApproach2022] for 19 types of errors in event data.
Agreement between ICEWS, GED, and CINEP [@stundalHumanRightsViolations2021]
ICEWs and 
ICEWs protest events about 80% precision [@wangGrowingPainsGlobal2016],

Dictionary based NLP systems based on large news corpora produce many thousands events over a short time which are unintelligible from the standpoint of micro or macro precision as analyzed above.

Dictionary methods are effectively topic detectors. Dozens of events about signing a deal with the EU that didn't happen.

Next, we make available visualizations of every datum in ICBe alongside each of its contemporary competitors in full on the companion website. For ICBe, we show the original source text alongside an iconographic representation of coded events as in Figure 1. 
-->

Conclusion {#format .unnumbered}
========================================

We investigated event extraction from narratives describing key historical episodes in international relations. We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record. We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts. Multiple validity checks find the resulting codings have high internal validity (e.g. intercoder agreement) and external validity (i.e. matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes). Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.

We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing. The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project. These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g. escalation and de-escalation of conflicts). Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events. Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing. Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).

<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
\showmatmethods
\showacknow
\pnasbreak

### 2022-07-17 replication_paper/pnas_draft/paper.tex
v1.1

\documentclass[9pt,twocolumn,twoside,]{pnas-new}

% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{xr} \externaldocument{appendix}
\usepackage[utf8]{inputenc}
\usepackage{pifont}
\usepackage{newunicodechar}
\newunicodechar{✓}{\ding{51}}
\newunicodechar{✗}{\ding{55}}
\usepackage{array}
\usepackage{ctable}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[parfill]{parskip}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{cellspace}
\setlength\cellspacetoplimit{0.8ex}
\renewcommand{\arraystretch}{0.8}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\usepackage{subcaption}
\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
\usepackage{float}
\usepackage[algo2e]{algorithm2e}
\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}

\templatetype{pnasresearcharticle}  % Choose template

\title{Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises}

\author[a,1,2]{Rex W. Douglass}
\author[a]{Thomas Leo Scherer}
\author[b]{J. Andrés Gannon}
\author[a]{Erik Gartzke}
\author[c]{Jon Lindsay}
\author[d]{Shannon Carcelli}
\author[d]{Jonathan Wilkenfeld}
\author[e]{David M. Quinn}
\author[f]{Catherine Aiken}
\author[g]{Jose Miguel Cabezas Navarro}
\author[d]{Neil Lund}
\author[h]{Egle Murauskaite}
\author[h]{Diana Partridge}

  \affil[a]{Department of Political Science, University of California, San Diego, CA, USA.}
  \affil[b]{Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.}
  \affil[c]{School of Cybersecurity and Privacy \textbar{} Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.}
  \affil[d]{Department of Government and Politics, University of Maryland, College Park, MD, USA.}
  \affil[e]{Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.}
  \affil[f]{Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.}
  \affil[g]{Society and Health Research Center, Universidad Mayor, Santiago, Chile.}
  \affil[h]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
  \affil[i]{ICONS Project // START, University of Maryland, College Park, MD, USA.}

% Please give the surname of the lead author for the running footer
\leadauthor{Douglass}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.}

\authorcontributions{Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D., J.A.G., E.G., T.L.S.;
Visualization: R.W.D., T.L.S.; Supervision: E.G.; Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.}

\authordeclaration{Please declare any conflict of interest here.}

\correspondingauthor{\textsuperscript{2} To whom correspondence should be addressed. E-mail: \href{mailto:rexdouglass@gmail.com}{\nolinkurl{rexdouglass@gmail.com}}}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 \keywords{  Diplomacy |  War |  Crises |  International Affairs |  Computational Social Science  }

\begin{abstract}
How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

\acknow{We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort. We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day. We thank the many undergraduate coders for their patience and dedication. Thanks to the Center for Peace and Security Studies and its membership for comments. Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback. Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang. This project was supported by a grant from the Office of Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.}

If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new? In other words, what is the entropy of international relations? This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive (1, 2). If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.\footnote{See work on crises (3, 4), militarized disputes (5--7), wars (8, 9), organized violence (10, 11), political violence (12), sanctions (13), trade (14), and international agreements (15--17), dispute resolution (17, 18), and diplomacy (19, 20).} With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.\footnote{See (21); (22); (23); (24); (25); (26). On event-extraction from images and social-media see (27) and (28).} How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.

Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations. We develop a large, flexible ontology of international events with the help of both human coders and natural language processing. We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises (1, 29--32). The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes. We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative. We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts. We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode. The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.

This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches. The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision. A final section concludes.

\hypertarget{task-definition}{%
\section*{Task Definition}\label{task-definition}}
\addcontentsline{toc}{section}{Task Definition}

We consider the measurement task of abstracting discrete events about a historical episode in international relations. The easiest way to convey the task is with an example. Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine readable abstractive events. Formally, a historical episode, \(H\), is demarcated by a period of time \([T_{start}, T_{end}] \in T\), a set of Players \(p \in P\), and a set of behaviors they undertook during that time \(b \in B\). International Relations, \(IR\), is the system of regularities that govern the strategic interactions that world actors make during a historical episode, given their available options, preferences, beliefs, and expectations of choices made by others. We observe neither \(H\) nor \(IR\) directly. Rather the Historical Record, \(HR\), produces documents \(d \in D\) containing some relevant and true (as well as irrelevant and untrue) information about behaviors that were undertaken recorded in the form of unstructured natural language text. The task is to combine informative priors about \(IR\) with an unstructured corpus \(D\) to produce a series of structured discrete events, \(e \in E\), that have high coverage, precision, and recall over what actually took place in history, \(H\).

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=22cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png"}}
\end{figure}
\clearpage
\twocolumn

\hypertarget{corpus}{%
\section*{Corpus}\label{corpus}}
\addcontentsline{toc}{section}{Corpus}

For our corpus, \(D\), we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project (\(n=471\))(SI Appendix, Table A1)(33, 34). Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system (3).\footnote{On near crises see (32).} Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict (3, 35--42). Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources (33, 43). Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity (44). The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.

\hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}

Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record. We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.

The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology. We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do). Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict). We find 464 actors and 117 different behaviors, and provide a full codebook in the online material.\footnote{See the Github Repository \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}

We base our informed priors primarily on two sources of information. The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept. Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text. Verbs were matched to the most likely definition found in Wordnet (45), tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).

The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage. They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11, 47).\footnote{Additional relevant but dated or too small of an overlap in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51), SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories in (54) and (55)).} The final set of columns compares episode-level datasets beginning with the original ICB project (3, 4, 56); the Militarized Interstate Disputes dataset (5, 6, 57, 58), and the Correlates of War (8). With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.\footnote{See (53) for a recent review of ontological depth and availability of Gold Standard example text.}

\clearpage
\onecolumn

{[}1{]} 37 17

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.75}

\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}

\caption{Ontological coverage of ICBe versus existing State of the Art
}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{15k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\end{longtable}

\clearpage
\twocolumn

\hypertarget{icbe-coding-process}{%
\section*{ICBe Coding Process}\label{icbe-coding-process}}
\addcontentsline{toc}{section}{ICBe Coding Process}

The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details (59).\footnote{This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag. The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.} Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig. B1). Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players (\(P\)), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities. Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.~force size, fatalities, domains, units, etc. A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.~an offer for the U.S.S.R. to remove missiles from Cuba in exchange for the U.S. removing missiles from Turkey. Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.

Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.\footnote{Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook. Undergraduate coders were students who engaged in classroom workshops.} For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=971,547), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc. We then aggregate those tags into final events (n=18,309), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders. This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.

\hypertarget{internal-consistency}{%
\section*{Internal Consistency}\label{internal-consistency}}
\addcontentsline{toc}{section}{Internal Consistency}

We evaluate the internal validity of the coding process in several ways. For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig. B3). Across all concepts, the Top 1 Tag Agreement was low among novices (34\%), moderate for experts (65\%), and high (87\%) following the consensus screening procedure.

We attribute the remaining disagreement primarily to three sources. First, we required coders to rate their confidence which was observed to be low for 20\% of sentences- half due to a mismatch between the ontology and the text (``survey doesn't fit event''-45\%) and half due to a lack of information or confused writing in the source text (``more knowledge needed''-40\%, ``confusing sentence''-6\%). Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig. B4). Second, as intended agreement is higher (75-80\%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50\%-60\%). Third, individual coders exhibiting nontrivial coding styles, e.g.~some more expressive applying many tags per concept while others focused on only the single best match. We further observed unintended synonymity, e.g.~the same information can be framed as either a threat to do something or a promise not to do something.

\hypertarget{case-study-selection}{%
\section*{Case Study Selection}\label{case-study-selection}}
\addcontentsline{toc}{section}{Case Study Selection}

The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems. We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website. In this paper, we focus on two deep case studies. The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles). The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas). Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers. We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.

\hypertarget{recall}{%
\section*{Recall}\label{recall}}
\addcontentsline{toc}{section}{Recall}

Recall measures the share of desired information recovered by a sequence of coded events, \(Pr(E|H)\), and is poorly defined for historical episodes. First, there is no genuine ground truth about what occurred, only surviving texts about it. Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia. History suffers from what is known as the Coastline Paradox (60) --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events. The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals. We need a yardstick for history.

Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative. For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents. Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts. The more accounts that mention a detail, the more central it is to understanding the true historical episode. The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing. With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context. Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.

Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2. Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.

From them, we draw several stylized facts. First, there is substantial variation in which details any one document will choose to include. Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative. Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details. Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g.~the U.S. was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection (61) and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.~a long term lease on naval facilities in Crimea. Fourth, we find variation between the two cases. Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting. The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.

We find substantive variation in recall across systems. Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark. The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions. The two episode level datasets have very low coverage of contextual details. The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier. ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable. Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure}
\clearpage
\twocolumn

\hypertarget{precision}{%
\section*{Precision}\label{precision}}
\addcontentsline{toc}{section}{Precision}

The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, \(Pr(H|E)\). It does little good to recall a historical event but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between 1995-2019) to be useful for downstream applications. ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable. You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move. We call this visualization a crisis map, a directed graph interesected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig. D3 and D4) and all crises on the companion website.

\clearpage
\onecolumn
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps  \label{fig:p_precision_combined}}
\centering{\includegraphics[width=24cm]{../figures/p_precision_combined.png}}
\end{sidewaysfigure}
\clearpage
\twocolumn

We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text. We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website. We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).

We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark. Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to. Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.\footnote{We preprocess sentences to replace named entities with a generic Entity token.} Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology. If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.\footnote{Hierchcial clustering on cosine similarity and with Ward's method.}

\clearpage
\onecolumn
\begin{figure}[H]
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{../figures/p_semantic_embeddings_dendro.png}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to visually recognizable. }
\end{figure}
\clearpage
\twocolumn

Finally, how does ICBe's precision compare to the existing state of the art? The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis. On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible. Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.

However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe. For example, (62) attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline. Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.~geolocation (63), protest events (80\%) (64), anti-government protest networks (46.1\%) (65).

We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event. We choose four event types around key moments in the crisis. The start of the crisis revolves around the Ukraine backing out of trade deal with the EU in favor of Russia, but the ``sign formal agreement'' acts more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized. The switch is caught by the ``reject plan, agreement to settle dispute'', but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal. Events for ``use conventional military force'' capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns. Likewise, ``impose embargo, boycott, or sanctions'' captures the start of waves of sanctions and from who but are effectively costantly as the news coverage does not distinguish between subtle changes or additions. In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.

\clearpage
\onecolumn
\begin{figure}[H]
\caption{ ICEWs Counts of Events per Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
\centering{\includegraphics[width=17cm]{../figures/p_precision_icews.png}}
\textit{Notes:Unit of analysis is the Dyad-Day. Edges <-> indicates undirected dyad and -> indicates directed dyad. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Event types are grouped by hand along similar themes. Blue bars indicate an event recorded by ICEWs for that dyad on that day. }
\end{figure}
\clearpage
\twocolumn

\hypertarget{format}{%
\section*{Conclusion}\label{format}}
\addcontentsline{toc}{section}{Conclusion}

We investigated event extraction from narratives describing key historical episodes in international relations. We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record. We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts. Multiple validity checks find the resulting codings have high internal validity (e.g.~intercoder agreement) and external validity (i.e.~matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes). Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.

We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing. The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project. These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.~escalation and de-escalation of conflicts). Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events. Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing. Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).

\showmatmethods
\showacknow
\pnasbreak

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{Brecher M (1999) International studies in the twentieth century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA} presidential address. \emph{International Studies Quarterly} 43(2):213--264.}

\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{Reiter D (2015) \href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu Rev Polit Sci} 18(1):481--499.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{Brecher M, Wilkenfeld J (1982) \href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}. \emph{World Politics} 34(3):380--417.}

\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The {International Crisis Behavior Project}. doi:\href{https://doi.org/10.1093/acrefore/9780190228637.013.1638}{10.1093/acrefore/9780190228637.013.1638}.}

\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{Palmer G, et al. (2021) \href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset}, 2011--2014: {Procedures}, coding rules, and description}. \emph{Conflict Management and Peace Science}:0738894221995743.}

\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts}, 1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \& Littlefield}) Available at: \url{https://books.google.com?id=_4VTDwAAQBAJ}.}

\leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
\CSLLeftMargin{7. }
\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP (2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0: {Logic}, {Characteristics}, and {Comparisons} to {Alternative Datasets}}. \emph{Journal of Conflict Resolution} 63(3):811--835.}

\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war: 1816-2007} ({CQ Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
\CSLLeftMargin{9. }
\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016) \href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at {Interstate Wars}, 1816--2007}. \emph{Journal of Conflict Resolution} 60(5):956--976.}

\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED Codebook} version 5.0} ({Department of Peace and Conflict Research, Uppsala University}).}

\leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{Pettersson T, Eck K (2018) \href{https://doi.org/10.1177/0022343318784101}{Organized violence, 1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}

\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
\CSLLeftMargin{12. }
\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010) Introducing {ACLED}: An armed conflict location and event dataset: Special data feature. \emph{Journal of peace research} 47(5):651--660.}

\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The global sanctions data base}. \emph{European Economic Review} 129:103561.}

\leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
\CSLLeftMargin{14. }
\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the {Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}

\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{Kinne BJ (2020) \href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution} 64(4):729--755.}

\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
\CSLLeftMargin{16. }
\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018) \href{https://doi.org/10.1177/0738894216646978}{The {International Border Agreements Dataset}}. \emph{Conflict Management and Peace Science} 35(5):559--576.}

\leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
\CSLLeftMargin{17. }
\CSLRightInline{Vabulas F, Snidal D (2021) \href{https://doi.org/10.1177/0022343320943920}{Cooperation under autonomy: {Building} and analyzing the {Informal Intergovernmental Organizations} 2.0 dataset}. \emph{Journal of Peace Research} 58(4):859--869.}

\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
\CSLLeftMargin{18. }
\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017) \href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates} of {War Territorial Claims Data}, 1816--20011}. \emph{Journal of Peace Research} 54(1):99--108.}

\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
\CSLLeftMargin{19. }
\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020) \href{https://doi.org/10.1177/0022343320929740}{What are the drivers of diplomacy? {Introducing} and testing new annual dyadic data measuring diplomatic exchange}. \emph{Journal of Peace Research}:0022343320929740.}

\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
\CSLLeftMargin{20. }
\CSLRightInline{Sechser TS (2011) \href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent Threats}, 1918--2001}. \emph{Conflict Management and Peace Science} 28(4):377--401.}

\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
\CSLLeftMargin{21. }
\CSLRightInline{Li Q, et al. (2021) A {Comprehensive Survey} on {Schema-based Event Extraction} with {Deep Learning}. Available at: \url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10, 2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{Halterman A (2020) Extracting {Political Events} from {Text Using Syntax} and {Semantics}.}

\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018) Phoenix {Real-Time Event Data}. Available at: \url{http://eventdata.utdallas.edu}.}

\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
\CSLLeftMargin{24. }
\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data. \emph{Harvard Dataverse} 12.}

\leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing the {UCDP Candidate Events Dataset}. \emph{Research \& Politics} 7(3):2053168020935257.}

\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017) {OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/} {[}Accessed September 1, 2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
\CSLLeftMargin{27. }
\CSLRightInline{Zhang H, Pan J (2019) \href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning Approach} for {Identifying Collective Action Events} with {Text} and {Image Data} from {Social Media}}. \emph{Sociological Methodology} 49(1):1--57.}

\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{Steinert-Threlkeld ZC (2019) \href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
\CSLLeftMargin{29. }
\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis escalation to war: {Findings} from the {International Crisis Behavior Project}. \emph{What Do We Know About War}.}

\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
\CSLLeftMargin{30. }
\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and violence: Twentieth-century findings. \emph{Handbook of war studies II}:282--300.}

\leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
\CSLLeftMargin{31. }
\CSLRightInline{James P (2019) \href{https://doi.org/10.1177/0738894218793135}{What do we know about crisis, escalation and war? {A} visual assessment of the {International Crisis Behavior Project}}. \emph{Conflict Management and Peace Science} 36(1):3--19.}

\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
\CSLLeftMargin{32. }
\CSLRightInline{Iakhnis E, James P (2019) \href{https://doi.org/10.1177/0738894219855610}{Near crises in world politics: {A} new dataset}. \emph{Conflict Management and Peace Science}:0738894219855610.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D (2017) \emph{International {Crisis Behavior Data Codebook}} Available at: \url{http://sites.duke.edu/icbdata/data-collections/}.}

\leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
\CSLLeftMargin{34. }
\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of {Crisis}} ({University of Michigan Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
\CSLLeftMargin{35. }
\CSLRightInline{Holsti OR (1965) \href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The American Political Science Review} 59(2):365--378.}

\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June} 24-30, 1950} ({Free Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision: {Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}

\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among nations: {Bargaining} and decision making in international crises} ({Princeton University Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
\CSLLeftMargin{39. }
\CSLRightInline{Gavin FJ (2014) \href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies} 37(2):319--331.}

\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American} foreign policy: {Theory} and practice} ({Columbia University Press}).}

\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{Gaddis JL (1987) \href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}: {Historians}, {Political Scientists}, and the {Enrichment} of {Security Studies}}. \emph{International Security} 12(1):3--21.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
\CSLLeftMargin{42. }
\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management. \emph{Journal of Conflict Resolution} 32(3):426--456.}

\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of {Asian} security: {Using Europe} to study {Asia}. \emph{Journal of Global Security Studies} 4(3):393--401.}

\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
\CSLLeftMargin{44. }
\CSLRightInline{Hewitt JJ (2001) \href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to {Teach Conflict} and {Crisis Analysis}}. \emph{Int Stud Perspect} 2(4):371--383.}

\leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
\CSLLeftMargin{45. }
\CSLRightInline{Miller GA (1995) \href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical database for {English}}. \emph{Commun ACM} 38(11):39--41.}

\leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
\CSLLeftMargin{46. }
\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA (2019) Cline {Center Historical Phoenix Event Data Variable Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}

\leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
\CSLLeftMargin{47. }
\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP} georeferenced event dataset. \emph{Journal of Peace Research} 50(4):523--532.}

\leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
\CSLLeftMargin{48. }
\CSLRightInline{Leng RJ, Singer JD (1988) \href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}: {The BCOW Typology} and {Its Applications}}. \emph{International Studies Quarterly} 32(2):155--173.}

\leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
\CSLLeftMargin{49. }
\CSLRightInline{McClelland C (1978) World event/interaction survey, 1966-1978. \emph{WEIS Codebook ICPSR} 5211.}

\leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
\CSLLeftMargin{50. }
\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events} of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968: {Version} 1. doi:\href{https://doi.org/10.3886/ICPSR05205.V1}{10.3886/ICPSR05205.V1}.}

\leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
\CSLLeftMargin{51. }
\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}: {Computer-aided} system for analysis of local conflicts. \emph{MIT Center for International Studies, Cambridge}.}

\leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
\CSLLeftMargin{52. }
\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm}, {Hierarchical}, and {Contextually-Sensitive International Conflict Dataset}, 1937-1985: {Version} 1. doi:\href{https://doi.org/10.3886/ICPSR02292.V1}{10.3886/ICPSR02292.V1}.}

\leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
\CSLLeftMargin{53. }
\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A Comprehensive Ontology} for {Event Extraction} from text. doi:\href{https://doi.org/10.48550/arXiv.2107.10326}{10.48550/arXiv.2107.10326}.}

\leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
\CSLLeftMargin{54. }
\CSLRightInline{Merritt RL (1994) Measuring events for international political analysis. \emph{International Interactions} 20(1-2):3--33.}

\leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
\CSLLeftMargin{55. }
\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas} event data system project. \emph{The political methodologist} 14(1):2--8.}

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
\CSLLeftMargin{56. }
\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D International {Crisis Behavior Data Codebook}, {Version} 12. 69.}

\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
\CSLLeftMargin{57. }
\CSLRightInline{Braithwaite A (2010) \href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing} the {Militarized Interstate Dispute Location} dataset}. \emph{Journal of Peace Research} 47(1):91--98.}

\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
\CSLLeftMargin{58. }
\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University College London}.}

\leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
\CSLLeftMargin{59. }
\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain knowledge: Using hierarchies to improve deep classifiers. Available at: \url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}

\leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
\CSLLeftMargin{60. }
\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of nature} ({Freeman}, {New York}).}

\leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
\CSLLeftMargin{61. }
\CSLRightInline{Cormac R, Aldrich RJ (2018) \href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert action and implausible deniability}. \emph{International Affairs} 94(3):477--494.}

\leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
\CSLLeftMargin{62. }
\CSLRightInline{Terechshenko Z (2020) \href{https://doi.org/10.1177/0022343320962546}{Hot under the collar: {A} latent measure of interstate hostility}. \emph{Journal of Peace Research} 57(6):764--776.}

\leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
\CSLLeftMargin{63. }
\CSLRightInline{Cook SJ, Weidmann NB (2019) \href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}: {Improving Event Analysis} with {Report-Level Data}}. \emph{American Journal of Political Science} 63(1):250--264.}

\leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
\CSLLeftMargin{64. }
\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of protest event analysis. \emph{Contention in times of crisis: Recession and political protest in thirty Euro-pean countries}:49--78.}

\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
\CSLLeftMargin{65. }
\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event Data}: {Evidence} from the {ICEWS Dataset}.}

\end{CSLReferences}

% Bibliography
% \bibliography{pnas-sample}

\end{document}

### 2022-07-17 replication_paper/pnas_draft/pnas_draft.Rmd
v1.1

--- 2022-03-24 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
@@
 ---
-title: |
-  | Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises
+title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"
+
+# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
 author:
-  - Rex W. Douglass^[Department of Political Science, University of California, San Diego, CA, USA.]
-  - Thomas Leo Scherer^[Department of Political Science, University of California, San Diego, CA, USA.]
-  - J. Andrés Gannon^[Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.]
-  - Erik Gartzke^[Department of Political Science, University of California, San Diego, CA, USA.]
-  - Jon Lindsay^[School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.]
-  - Shannon Carcelli^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
-  - Jonathan Wilkenfeld^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
-  - David M. Quinn^[Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.]
-  - Catherine Aiken^[Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.]
-  - Jose Miguel Cabezas Navarro^[Society and Health Research Center, Universidad Mayor, Santiago, Chile.]
-  - Neil Lund^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
-  - Egle Murauskaite^[ICONS Project // START,  University of Maryland, College Park, MD, USA.]
-  - Diana Partridge^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
+  - name: Rex W. Douglass
+    affiliation: a,1,2
+  - name: Thomas Leo Scherer
+    affiliation: a
+  - name: J. Andrés Gannon
+    affiliation: b
+  - name: Erik Gartzke
+    affiliation: a
+  - name: Jon Lindsay
+    affiliation: c
+  - name: Shannon Carcelli
+    affiliation: d
+  - name: Jonathan Wilkenfeld
+    affiliation: d
+  - name: David M. Quinn
+    affiliation: e
+  - name: Catherine Aiken
+    affiliation: f
+  - name: Jose Miguel Cabezas Navarro
+    affiliation: g
+  - name: Neil Lund
+    affiliation: d
+  - name: Egle Murauskaite
+    affiliation: h
+  - name: Diana Partridge
+    affiliation: h
 
-date: "`r Sys.Date()`"
-abstract:  How do international crises unfold?
+address:
+  - code: a
+    address: Department of Political Science, University of California, San Diego, CA, USA.
+  - code: b
+    address: Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.
+  - code: c
+    address: School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.
+  - code: d
+    address: Department of Government and Politics, University of Maryland, College Park, MD, USA.
+  - code: e
+    address: Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.
+  - code: f
+    address: Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.
+  - code: g
+    address: Society and Health Research Center, Universidad Mayor, Santiago, Chile.
+  - code: h
+    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
+  - code: i
+    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
+
+corresponding_author:
+  code: 2
+  text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"
+
+# For footer text
+lead_author_surname: Douglass
+
+#following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
+author_contributions: |
+  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
+  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
+
+## Remove this if not required
+conflict_of_interest: |
+  Please declare any conflict of interest here.
+
+#Please provide an abstract of no more than 250 words in a single paragraph.
+Abstracts should explain to the general reader the major contributions of the article.
+References in the abstract must be cited in full within the abstract itself and cited in the text.
+abstract: |
+  How do international crises unfold?
 We conceive of international affairs as a strategic chess game between adversaries, necessitating a systematic way to measure pieces, moves, and gambits accurately and consistently over different contexts and periods.
 We develop such a measurement strategy with an ontology of crisis actions and interactions and apply it to a high-quality corpus of crisis narratives recorded by the International Crisis Behavior (ICB) Project.
-We demonstrate that the ontology has high coverage over most of the thoughts, speech, and actions contained in these narratives and produces high inter-coder agreement when applied by human coders.
+We demonstrate that the ontology has high coverage over most of the thoughts, speech, and actions contained in international crises and produces high inter-coder agreement when applied by human coders.
 We introduce a new crisis event dataset ICB Events (ICBe).
-We find that ICBe captures the process of a crisis with greater accuracy and granularity than other well-regarded events or crisis datasets.
+We find that ICBe captures the process of a crisis with greater accuracy and granularity than other well-regarded event or episode level datasets.
 We make the data, replication material, and additional visualizations available at a companion website www.crisisevents.org.
 
-site: bookdown::bookdown_site
+significance: |
+  Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
+The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership.
+The Significance Statement appears in the paper itself and is required for all research papers.
+
+acknowledgements: |
+  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
+We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
+We thank the many undergraduate coders for their patience and dedication.
+Thanks to the Center for Peace and Security Studies and its membership for comments.
+Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
+Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
+This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
+
 keywords:
-  - International Crisis Behavior
-  - Event data
+  - Diplomacy
+  - War
+  - Crises
+  - International Affairs
+  - Computational Social Science
+
+## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
+pnas_type: pnasresearcharticle
+
 bibliography: ICBintro.bib
-output: 
-  bookdown::pdf_document2:
-    toc: false
-    keep_tex: true
+csl: pnas.csl
+
+## change to true to add optional line numbering
+lineno: false
+
+output: rticles::pnas_article
+
+#Disabled several the caused errors
 header-includes:
@@
   - \usepackage{titlesec}
-#  - \usepackage[parfill]{parskip}
+  - \usepackage[parfill]{parskip}
   - \usepackage{makecell}
@@
   - \usepackage{float}
-  - \usepackage{eso-pic,graphicx,transparent}
-  - \usepackage[perpage]{footmisc}
-
+#  - \usepackage{eso-pic,graphicx,transparent}
+#  - \usepackage[perpage]{footmisc}
+  - \usepackage[algo2e]{algorithm2e}
+#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
 ---
@@
 
-\AddToShipoutPictureFG{
-  \AtPageCenter{% or \AtTextCenter
-    \makebox[0pt]{\rotatebox[origin=c]{45}{%
-      \scalebox{5}{\texttransparent{0.1}{Unrefereed Preprint}}%
-    }}
-  }
-}
+<!-- note: please start your introduction without including the word "Introduction" as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.
+-->
 
-# Introduction
-
-If we record every event between countries in all of diplomacy, military conflict, and international political economy, how much information would this chronicle amount to, and how surprised would we be to see something new?
+If we recorded every event between countries in all of diplomacy, military conflict, and international political economy, how much information would this chronicle amount to, and how surprised would we be to see something new?
 In other words, what is the entropy of international relations?
-This record could, in principle, be unbounded.
-Still, the central conceit of political science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured.
-Massive effort is expended in social science recording these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
+This record could, in principle, be unbounded, but the central conceit of political science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
+If so, then these events can be systematically measured, and accordingly massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
 On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
@@
 
-<!--Section 7 moves from qualitative comparison to an objective criteria with multiple choice reading comprehension questions about each crisis drawn from the original ICB project, where we show LSTMs trained on ICBe sequences can answer substantive macro level questions but not when trained on existing event project codings.
--->
-
-# Task Definition and Ground Truth
+Task Definition and Ground Truth {.unnumbered}
+========================================
 
@@
 
-We take as ground truth an unusually high-quality corpus of historical narratives and quantitative codings from the International Crisis Behavior (ICB) project [@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type or an increase in the intensity of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies or case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
+We take as ground truth an unusually high-quality corpus of historical narratives from the International Crisis Behavior (ICB) project (SI Appendix, Table \ref{app:crises})[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
+Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies or case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
 The corpus is unique in IR because it is designed to be used in downstream quantitative coding projects.
@@
 59].
-Each of the `r n_crisis %>% scales::comma()` crises $c \in C$ are listed with summary information in Appendix \ref{app:crises}.
 
-# Prior Beliefs and Existing State of the Art
+Prior Beliefs and Existing State of the Art {.unnumbered}
+========================================
 
-Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$ and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$.
+Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$, and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$.
 We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table 1.
@@
 The second axis (columns) represents sources of evidence for our concept priors and the existing state of the art.
-The first column ('Literature') maps each type of information to recent studies documenting its importance to IR.
-The second column ('ICB Corpus') documents the presence of that information in the ICB Corpus as identified by an expert review and natural language processing (Appendix \ref{app:verbs}).
-The third set of columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Absent datasets include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], and SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+The columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Absent datasets include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], and SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+
+\clearpage
+\onecolumn
 
@@
 flextable::set_flextable_defaults(fonts_ignore=TRUE)
-litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))
+litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
 
-litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 4, part="body")
+litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 3, part="body")
 
@@
   flextable::flextable_to_rmd()
+
 ```
 
-# ICBe Coding and Aggregation Process
+\clearpage
+\twocolumn
+
+ICBe Coding and Aggregation Process {#author-affiliations .unnumbered}
+----------------------------------------
+
+The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
+S\ref{app:gui}).
+Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
+Some additional details like location and timing information was always collected while other deatils were only collected if appropriate, e.g.
+force size, fatalities, domains, units, etc.
+A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
+an offer for the U.S.S.R.
+to remove missiles from Cuba in exchange for U.S.
+removing missiles from Turkey.
+Through compounding, we can capture what actors were said to have known, learned, or said about specific fully described behaviors.
 
@@
 Undergrad coders were students who engaged in classroom workshops.
-Coders worked independently with the codebook after a practice coding where an expert answered questions.] Each coder was instructed to thoroughly read and familiarize themselves with the full text.
-Once a coder felt that they understood the crisis, the coder was presented with a novel graphic user interface (GUI) that steps the coder through the narrative sentence by sentence (Figure \ref{fig:coding_gui}).
+Coders worked independently with the codebook after a practice coding where an expert answered questions.] The highly expressive ontology created challenges in aggregating and evaluating beliefs across coders.
+Traditional measures
 
-\begin{figure}[H]
-\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
-\centering{\includegraphics[width=17cm]{figures/gui_example}}
-\end{figure}
-
-The GUI and the ontology follow a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].
-Proceeding in order, coders chose the number of events (0-3), the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Identifying armed means triggered questions regarding force size, fatalities, domains, units, etc.
-Location and timing information is always collected, each calling for specific answers when possible and general approximations.
-Together, this process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
-
-A novel feature of the ontology is that thought, speech, and do behaviors can be nested into combinations so that any unique combination is reachable if warranted by the event.
-For example, a speech could be about a threat to perform a do unless another do is performed, and each can be specified in full detail.
-Likewise, a thought can be about a fully defined speech or do.
-For example, in the Cuban Missile Crisis, the United States became aware that the Soviet Union performed an interaction of placing missile sites in Cuba.
-Through compounding, we can capture what players were said to have known, learned, or felt about specific fully described behaviors.
+This data-generating process suggests a theoretically motivated algorithm for aggregating over disagreements (SI Appendix, Fig.
+S\ref{app:algo1}).
+We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of undergrad votes.
+If neither majority exists, we accept the one token with the most votes.
+This leaves `r codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()` (`r (codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() / codings_long_agreement %>% filter(value_normalized!='') %>% nrow()) %>% round(2) %>% scales::percent()`) accepted tokens.
+In practice, this screens noisy tags that no expert considered possible but leverages undergrad knowledge to tie-break between equally plausible tags chosen by experts.
+A final step handles possible disagreement over the number of events or participants in the events.
+An event is emitted for each unique set of actors along with their surviving tags.
 
@@
 ```
-
-# Internal Measurement Validity -- Intercoder Agreement and Aggregating Disagreements
 
@@
 
-Without an existing validation dataset, we cannot use traditional measures of validity.
-We instead examine agreement between coders, juxtaposition with source sentences, and case study comparisons with peer datasets.
 One form of internal validity for these codings is high agreement between coders when applying the ontology.
@@
 
-We evaluate agreement as the percentage of coders who voted for a tag proposed by any coder (Figure \ref{fig:intercoderagreement}).
+We evaluate agreement as the percentage of coders who voted for a tag proposed by any coder (SI Appendix, Fig.
+S\ref{app:intercoderagreement}).
 The average agreement across all coders is `r means1$All %>% round(2) %>% scales::percent()` (`r means1$Experts %>% round(2) %>% scales::percent()` across experts and `r means1$Undergraduates %>% round(2) %>% scales::percent()` across undergraduates).
@@
 Further, there is expected heterogeneity in agreement with higher agreement for coarse, high-level decisions near the root of the ontology than for fine-grained, high-dimensional concepts further down the tree.
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-# #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
-# 
-# 
-# # moved to ICBEdataset_paper_PlotInterCoderAgreement
-# p_percent_chose_tag_by_concept <- readRDS(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.Rds'))
-# 
-# ggplot2::ggsave(file=paste0(here::here(), '/paper/figures/p_percent_chose_tag_by_concept.png'), 
-#                 plot = p_percent_chose_tag_by_concept, width=8, height=6)
-# 
-# # created in ICBEdataset_paper_PlotInterCoderAgreement.Rmd. Has \\label{fig:intercoderagreement}. 
-```
-
-<!-- moved to paper/figure/ICBEdataset_paper_PlotInterCoderAgreement -->
-
-\begin{figure}[H]
-\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
-\centering{\includegraphics[width=15cm]{figures/p_percent_chose_tag_by_concept.png}}
-\end{figure}
 
@@
 
-This data-generating process suggests a theoretically motivated algorithm for aggregating over disagreements (Algorithm 1).
-We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of undergrad votes.
-If neither majority exists, we accept the one token with the most votes.
-This leaves `r codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()` (`r (codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() / codings_long_agreement %>% filter(value_normalized!='') %>% nrow()) %>% round(2) %>% scales::percent()`) accepted tokens.
-In practice, this screens noisy tags that no expert considered possible but leverages undergrad knowledge to tie-break between equally plausible tags chosen by experts.
-A final step handles possible disagreement over the number of events or participants in the events.
-An event is emitted for each unique set of actors along with their surviving tags.
-
-\begin{algorithm}[H]
-\SetAlgoLined
-\KwData{Coder-Sentence-Tokens}
-\KwResult{Sentence-Events}
-\ForEach{sentence in sentences}{
-  \ForEach{concept in concepts}{
-    \ForEach{token in tokens}{
-      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
-      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
-      \uElseIf{undergrad votes > undergrad voters/2}{accept; \tcc*[f]{Or a majority of undergrad votes}}
-    }
-    \If{sum(accepted) == 0}{
-      sort tags by votes;
-      head 1;
-      accept; \tcc*[f]{If still no tag, take one with most votes}
-    }
-  }
-  \ForEach{ActorSet in unique(ActorSets)}{
-    emit event;
-  }
-}
-\caption{Aggregating Coder-Tokens into Sentence-Events}
-\end{algorithm}
-
-# Sentence Level Intrinsic Evaluation
+Sentence Level Intrinsic Evaluation {#format .unnumbered}
+----------------------------------------
 
@@
 
+\clearpage
+\onecolumn
 \begin{figure}[H]
 \caption{ICBe event codings in comparison to Semantic Embeddings from the Sentence-BERT large language model\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=15cm]{figures/p_semantic_embeddings.png}}
+\centering{\includegraphics[width=15cm]{../figures/p_semantic_embeddings.png}}
 \textit{Notes:}
 \end{figure}
+\clearpage
+\twocolumn
 
@@
 
+\clearpage
+\onecolumn
 ```{r fifteensamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}
@@
 ```
+\clearpage
+\twocolumn
 
-# Episode Level Intrinsic Evaluation and Comparison to State of the Art
+Episode Level Intrinsic Evaluation and Comparison to State of the Art {#format .unnumbered}
+----------------------------------------
 
@@
 
-## Case Study: Cuban Missiles Crisis (1962)
+Case Study: Cuban Missiles Crisis (1962) {#format .unnumbered}
+----------------------------------------
 
@@
 
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-# moved to figures/ICBEdataset_paper_figure_prep.Rmd
-
-# #ICBe  196
-# library(ggplot2)
-# p_metro_map_196 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_196.Rds'))
-# actor_colors <- p_metro_map_196$actor_colors
-# ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_196.png'),
-#        plot = p_metro_map_196 +
-#          theme(plot.margin=unit(c(0,0,0,0),"in")) +
-#          scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-#          scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
-#        width=12, height=14)
-
-```
-
+\clearpage
+\onecolumn
 \begin{figure}[H]
 \caption{Cuban Missile Crisis according to ICBe (us) \label{fig:196metromap}}
-\centering{\includegraphics[width=19cm]{figures/p_metro_map_196.png}}
+\centering{\includegraphics[width=19cm]{../figures/p_metro_map_196.png}}
 \end{figure}
+\clearpage
+\twocolumn
 
@@
 
+\clearpage
+\onecolumn
 ```{r casestudy196, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
@@
 ```
+\clearpage
+\twocolumn
 
-## Case Study: DRC Civil War (1998)
-
-The civil war in the Democratic Republic of Congo (DRC), also called the Second Congo War and the Great African War, took place between 29 July 1998 and 30 July 2002 and included Angola, Chad, the DRC, Namibia, Rwanda, Uganda, and Zimbabwe.
-The necessary background for the episode is that in May 1997 Rwandan-backed rebels helped install Laurent Kabila as President of the DRC.
-The main arc of the episode begins a year later when Kabila then seeks to distance himself from Rwanda and demands that the rebels leave DRC territory (July 27, 1998).
-The main response is that they refuse and instead begin a campaign for the capital, still backed by Rwanda.
-The main arc ends with the DRC successfully defending against the campaign and reaching a peace agreement with Rwanda (July 30, 2002), Uganda (September 6, 2002), and other participants, including rebel groups (December 17, 2002) [@lansfordPoliticalHandbookWorld2021; @kisanganiHistoricalDictionaryDemocratic2010].
-
-A secondary arc concerns third-party involvement and political upheaval within the DRC.
-First, the conflict brings Uganda in on the side of Rwanda, and Angola, Namibia, Zimbabwe, and Chad in on the side of the DRC.
-Second, a United Nations-sponsored mediation produced a failed cease-fire (July 10, 1999) and a U.N.
-peacekeeping mission (MONUC) (September 30) [@lansfordPoliticalHandbookWorld2021; @kisanganiHistoricalDictionaryDemocratic2010].
-Finally, Laurent Kabila was assassinated (January 17, 2001) and was succeeded by his son Joseph Kabila (January 24), who showed a higher tolerance of U.N.
-involvement [@schererPeaceKeepsUnited2015].
-
-Precision and overall narrative coherence for the DRC case is strong, as demonstrated by side-by-side ICBe event codings in Appendix \ref{app:ft_sentence_table_426}, and shown visually as a crisis map in Figure \ref{fig:426metromap} below.
-The overall details of the crisis can be read from the timeline, particularly the invasion by Uganda and Rwanda of the DRC, several short-lived cease fires,  the shift in internal politics of the DRC due to the assassination and leadership change, a U.N.
-intervention, and final formal agreements to end the crisis.
-The role of the numerous third parties (Chad, Zimbabwe, Angola, and Namibia) who intervened on different sides is less clear.
-Similarly, the group structure of sub-national actors, who are represented as agents acting on behalf of Rwanda and Uganda, is ambiguous.
-
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-
-# moved to figures/ICBEdataset_paper_figure_prep.Rmd
-
-# #ICBe  426
-# p_metro_map_426 <- readRDS(file=paste0(here::here(), '/paper/figures/metro_plots/p_metro_plot_426.Rds'))
-# actor_colors <- p_metro_map_426$actor_colors
-# ggsave(file=paste0(here::here(), '/paper/figures/p_metro_map_426.png'),
-#        plot = p_metro_map_426 +
-#          theme(plot.margin=unit(c(0,0,0,0),"in")) +
-#          scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-#          scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))),
-#        width=12, height=14)
-
-#devtools::install_github('davidgohel/ggiraph')
-
-```
-
-\begin{figure}[H]
-\caption{DRC Civil War according to ICBe (us)  \label{fig:426metromap}}
-\centering{\includegraphics[width=19cm]{figures/p_metro_map_426.png}}
-\end{figure}
-
-By comparison, crisis maps of Cameo (Phoenix) (Figure \ref{fig:426metromap_phoenix}), ICEWS (Figure \ref{fig:426metromap_icews}), and Terrier (Figure \ref{fig:426metromap_terrier}), are unintelligible despite deduplication and heavy filtering of irrelevant or uninteresting events.
-The real-time of advantage of automated dictionary coding of news articles comes at the price of producing too many irrelevant events between unimportant actors or describes important events too vaguely to be used directly, and instead may only be interpretable in terms of weighted counts over time [@terechshenkoHotCollarLatent2020].
-ICB Dyadic Events (Figure \ref{fig:426metromap_icb}), MIDs Incidents (Figure \ref{fig:426metromap_mids_incidents}), and MIDs Episodes (Figure \ref{fig:426metromap_mids}) do a good job showing the start and stop of conflict and between which actors, but lose any detailed context.
-
-Recall of critical events is shown in Table \ref{tab:casestudy426} below.
-ICBe records 10 of 14 critical events identified by the case history.
-It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N.
-peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC.
-These details were under-textualized in the ICB narrative.
-Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets.
-As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events.
-Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event.
-The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila.
-The MIDs incident-level dataset includes possible coverage of 4 events.
-MIDs episode-level data incorporates possible coverage of 6 events.
-Finally, Dyadic ICB data cover 7 events.
-
-```{r casestudy426, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
-CaseStudy426_ft  %>%
-  flextable::set_caption("DRC Civil War ground truth and event data") %>%
-      width(j=1, width=0.5) %>%
-      width(j=2, width=0.75) %>%
-      width(j=3, width=0.3) %>%
-      width(j=4, width=0.65) %>%
-      width(j=5, width=1.0) %>%
-      width(j=6, width=0.5) %>%
-      width(j=7, width=0.75) %>%
-      width(j=8, width=0.75) %>%
-      width(j=9, width=0.5) %>%
-      width(j=10, width=0.5)
-
-```
-
-# Conclusion
+Conclusion {#format .unnumbered}
+----------------------------------------
 
@@
 
-#### Acknowledgments:
-We would like to thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We would like to make a special acknowledgment to Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-
-We thank the many undergraduate coders for their patience and dedication.
-Thanks to the Center for Peace and Security Studies and its membership for comments.
-Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
-Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
-
-#### Author contributions (alphabetical):
-<!-- following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit -->
-Conceptualization: R.W.D., E.G., J.L.;
-Methodology: R.W.D., T.L.S.;
-Software: R.W.D.;
-Validation: R.W.D., T.L.S.;
-Formal Analysis: R.W.D., T.L.S.;
-Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;
-Data Curation: R.W.D., D.Q., T.L.S., J.W.;
-Writing - Original Draft: R.W.D., T.L.S.;
-Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
-Visualization: R.W.D., T.L.S.;
-Supervision: E.G.;
-Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
-Funding Acquisition: E.G., J.L.
-
-\newpage
-# References
-
-<!-- uses zotero folder ICBintro -->
-<div id="refs"></div>
-<!-- https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html -->
-<!-- may require additional software -->
-
-\newpage
-
-# Appendix
-
-## Appendix 1: ICB Crises and Summary Information {#app:crises}
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
-#ICBEdataset_paper_appendixICBCrises.Rmd
-crisis_text_counts_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/ft_crisis_text_counts.Rds'))
-crisis_text_counts_ft
-```
-
-## Appendix 2: Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
-#, child=c('ICBEdataset_paper_appendixVerbMeanings.Rmd')
-
-verbs_sentence_wordnet_top_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
-verbs_sentence_wordnet_top_ft
-```
-
-## Appendix 3: Sentence Examples {#app:50samplesentences}
-
-```{r fiftysamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
-  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:fiftysamplesentences}
-
-codings_wide_agreed_embeded_stratified_sample_ft %>%
-      flextable::width( j = 1, width=0.3) %>%
-      flextable::width( j = 2, width=3.5) %>%
-      flextable::width( j = 3, width=3.5)
-```
-
-## Appendix 4: Cuban Missile Crisis {#app:ft_sentence_table_196}
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-ft_sentence_table_196 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_196.Rds'))  %>%
-  flextable::set_caption("ICBe Codings for Cuban Missile Crisis (Crisis 196)") # \\label{tbl:ft_sentence_table_196}
-ft_sentence_table_196 %>%
-      flextable::width( j = 1, width=0.3) %>%
-      flextable::width( j = 2, width=3.25) %>%
-      flextable::width( j = 3, width=3.25)
-```
-
-\begin{figure}[H]
-\caption{Cuban Missile Crisis according to Phoenix \label{fig:196metromap_phoenix}}
-\centering{\includegraphics[width=19cm]{figures/p_phoenix_metro_plot_196.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{Cuban Missile Crisis according to ICB \label{fig:196metromap_icb}}
-\centering{\includegraphics[width=19cm]{figures/p_icb_metro_plot_196.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{Cuban Missile Crisis according to MIDs Episodes \label{fig:196metromap_mids}}
-\centering{\includegraphics[width=19cm]{figures/p_mids_metro_plot_196.png}}
-\end{figure}
-
-## Appendix 5: DRC {#app:ft_sentence_table_426}
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-ft_sentence_table_426 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_426.Rds'))  %>%
-  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426)") #\\label{tbl:ft_sentence_table_426}
-ft_sentence_table_426 %>%
-      flextable::width( j = 1, width=0.3) %>%
-      flextable::width( j = 2, width=3.25) %>%
-      flextable::width( j = 3, width=3.25)
-```
-
-\begin{figure}[H]
-\caption{DRC Civil War according to Phoenix \label{fig:426metromap_phoenix}}
-\centering{\includegraphics[width=19cm]{figures/p_phoenix_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to ICEWS \label{fig:426metromap_icews}}
-\centering{\includegraphics[width=19cm]{figures/p_icews_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to Terrier \label{fig:426metromap_terrier}}
-\centering{\includegraphics[width=19cm]{figures/p_terrier_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to Dyadic ICB \label{fig:426metromap_icb}}
-\centering{\includegraphics[width=19cm]{figures/p_icb_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to MIDs Incidents \label{fig:426metromap_mids_incidents}}
-\centering{\includegraphics[width=19cm]{figures/p_mids_incidents_metro_plot_426.png}}
-\end{figure}
-
-\begin{figure}[H]
-\caption{DRC Civil War according to MIDs Episodes \label{fig:426metromap_mids}}
-\centering{\includegraphics[width=19cm]{figures/p_mids_metro_plot_426.png}}
-\end{figure}
+<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
+\showmatmethods
+\showacknow
+\pnasbreak

### 2022-07-17 replication_paper/rmd/CrisisMaps.Rmd
v1.1

--- 2022-07-17 replication_paper/pnas_draft/appendix.Rmd
@@
 ---
-title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"
-
-#https://bookdown.org/yihui/bookdown/a-single-document.html
-#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
-#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
-#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
-output: 
-  bookdown::pdf_book:
-    toc: yes
-    latex_engine: xelatex
-
-bibliography: ICBintro.bib
-
-#Disabled several the caused errors
-header-includes:
-# - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
-# - \usepackage{tinytex}
-  - \usepackage[utf8]{inputenc}
-  - \usepackage{pifont}
-  - \usepackage{newunicodechar}
-  - \newunicodechar{✓}{\ding{51}}
-  - \newunicodechar{✗}{\ding{55}}
-  - \usepackage{array}
-  - \usepackage{ctable} # added for demo
-  - \usepackage{natbib} #added for latex citation within huxtable
-  - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage{wrapfig}
-  - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{titlesec}
-#  - \usepackage[parfill]{parskip}
-  - \usepackage{makecell}
-  - \usepackage{graphicx}
-  - \usepackage{caption}
-#  - \usepackage[capposition=top]{floatrow}
-  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
-  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
-#  - \DeclareUnicodeCharacter{00A0}{ }
-  - \usepackage{setspace}
-  - \usepackage{cellspace}
-  - \setlength\cellspacetoplimit{0.8ex}
-  - \renewcommand{\arraystretch}{0.8}
-  - \AtBeginEnvironment{tabular}{\singlespacing}
-  - \AtBeginEnvironment{lltable}{\singlespacing}
-#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-  - \usepackage{subcaption}
-  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
-  - \usepackage{float}
-#  - \usepackage{eso-pic,graphicx,transparent}
-#  - \usepackage[perpage]{footmisc}
-  - \usepackage{algorithm}
-  - \usepackage[algo2e]{algorithm2e}
-  - \usepackage{amsmath}
-  - \usepackage{afterpage}
-  - \usepackage{placeins}
-  - \usepackage{rotating, float, caption}
-#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
-
+title: "ICBEdataset figure Metro Maps"
+output: html_document
 ---
 
-```{r library loads, eval=T, echo=F, cache=F, results='hide', message=F}
-
-flag_folder_small="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"
-
-knitr::opts_chunk$set(echo = F, echo=F, cache=F, results='hide', message=F, warning=F) #Global options
-
-#library(pacman)
-library(googlesheets4)
-library(tidyverse)
-library(janitor)
-library(flextable)
+# Metro Maps
+
+```{r}
+global_check_overlap=F
+```
+
+```{r}
+
+#devtools::install_github('davidgohel/ggiraph')
 library(ggplot2)
-library(cowplot)
-library(ggtext)
-#set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`.
-You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
-library(ftExtra)
-options(tidyverse.quiet = TRUE)
-options(gargle_oauth_email = TRUE)
-
-#install.packages('stargazer')
-#install.packages('kableExtra')
-#! sh: 1: pdflatex: not found
-#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended
-
-#! LaTeX Error: File `letltxmacro.sty' not found.
-#sudo apt-get install texlive-latex-extra
-
-library(pacman)
-library(igraph)
-library(tidyverse)
+library(ggiraph)
+
 library(flextable)
 library(ftExtra)
+library(tidyverse)
+library(googlesheets4)
+library(RColorBrewer)
+library(tidyverse)
+library(ggraph)
+#library(edgebundle)
+library(igraph)
+library(stringr)
+
+rex_paste <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}
+rex_count <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}
 
@@
 
-```{r data loads, eval=T, echo=F, cache=F, results='hide', message=F}
-
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )
-
-ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
-dim(ICBe_events_agreed)
-
-icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
-dim(icb_events_long)
-
-ICBe_crises_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds"))
-
-ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
-
-#oh is it because break is reserved in R? lol
-#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
-icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
+# Common Preprocessing and Loads
+
+```{r echo=FALSE, include=FALSE, eval=T}
+
+icb_events_long <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1.1_events_agreed_long.Rds'))
+icb_events <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1.1_events_agreed.Rds'))
+
+icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
+#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds") )
+
+crisno_name_years <- icb_crises %>% dplyr::select(crisno, crisname, yrtrig, yrterm)
+
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
+dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
+                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
+
+#Design specification
+#Time flows downward
+#Each actor gets a line
+#Spacing between lines should be dynamic, to allow for readability between
+#We want the name of each actor to be labeled at the start of their line
+#Unilateral actions printed above
+
+#dpr/lpr is broken
+actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
+                                sheet="actor_translator") #%>% janitor::clean_names() 
+#Convert to a local file for pushing
+#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
+pallet <- setdiff(c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Paired")), c("#666666", "#999999", "#FFFF99","#FFFF33"))
+actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
+
 icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
@@
 
-#somehow break of all things is a b roken name
-#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
-icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))
-
 ```
 
-# Appendix A Corpus and Cases
-\hphantom{em}
-## Table A1: ICBe Crises and Summary Information {#app:crises}
-\hphantom{em}
-
-```{r ICBe Crisis Summaries, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F}
-
-#The answer is I have to include it as an image, none of the table options were compiling correctly without error
-#,  ft.arraystretch=0.75
-
-temp_all <-  ICBe_crises_markdown %>% ungroup() %>% dplyr::select(
-                    crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events, 
-                    coders_expert , 
-                    coders_novice ,
-                    actors , 
-                    units_domains, 
-                    forces_fatalities
+# ICBe
+
+## ICBe metro plots
+
+```{r}
+
+#icb_events_pruned_labeled %>% dplyr::select(start_time)
+
+icbe_metro_plots <- function(crisis=196, prune_rare=T){
+
+  print(crisis)
+  #crisis=471
+  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
+  save_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_metro_plot_", crisis, ".Rds")
+
+  icb_events_subset <-  icb_events %>% 
+                                 ungroup() %>%
+                                 dplyr::filter(crisno==crisis) %>%  #417 196
+                                 dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
+                                 #dplyr::select(date) %>% #for date debugging
+                                 #mutate(date_asdate=date %>% str_replace_all("th|end of|after",'') %>% trimws() %>% anytime::anydate(useR=F)) %>%
+                                 #mutate(year = date %>% stringr::str_extract(pattern = "[0-9]{4}") %>% as.numeric() ) %>%
+                                 #mutate(year = lubridate::year(date_asdate)) %>% #This should all be considered hacky approximations
+                                 #mutate(year = ifelse(year<1900, NA, year)) %>%
+                                 mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
+                                 mutate(year=date_earliest_year %>% as.numeric() ) %>%
+                                 mutate(month= date_earliest_month %>% as.numeric() ) %>%
+                                 mutate(day= date_earliest_day %>% as.numeric()  ) %>%
+                                 arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
+                                 tidyr::fill(decade, .direction="downup") %>%
+                                 tidyr::fill(year, .direction="downup") %>%
+                                 tidyr::fill(month, .direction="downup") %>%
+                                 tidyr::fill(day, .direction="downup") %>% 
+                                 mutate(point_in_time_year = year %>% as.numeric())  %>% 
+                                 mutate(point_in_time_month = month %>% as.numeric()) %>% 
+                                 arrange(decade, year,month,day) %>%
+                                 mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
+
+  icb_events_subset_diad <- icb_events_subset %>% 
+                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
+                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
+                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
+                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
+                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
+                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
+                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
+                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
+                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
+                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
+                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
+                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
+                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
+                                                    sent,
+                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
+                                                    thinkkind, sayintkind, dokind,
+                                                    point_in_time_year, point_in_time_month
+                                                    ) %>% distinct() %>%
+                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
+
+  notes=NULL
+  if(prune_rare==T){
+    actor_sent_counts <- 
+      bind_rows(
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
         ) %>% 
-              mutate_all(as.character) %>%
-              mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II"))
-
-convert_to_ft <- function(x){
-     x %>% flextable::as_flextable() %>%
-      flextable::set_header_labels(values =
-          list(crisno = "#",
-                crisis_text = "Title",
-                yrtrig = "Start",
-                yrterm = "End",
-                n_sentence_number_int_aligned = "Sent.",
-                n_events = "Events",
-                coders_expert = "Exp.",
-                coders_novice = "Nov.",
-                actors = "Actors",
-                units_domains = "Units/Domains",
-                forces_fatalities = "Forces/Fatalities"
-                #value_markdown = "Abstract"
+          na.omit() %>%
+          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+      #New pruning rule, either singletons or actors with less than 10% of the max actor
+      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
+      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
+      if(left_over_count<3){
+        #Skip pruning if it leaves less than 3 actors
+      } else {
+
+        actor_map <- dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) 
+        actor_singleton_labels <- actor_map$value_normalized_label
+        names(actor_singleton_labels) <- actor_map$actor
+        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
+
+        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
+
+        #Easiest thing is to just prune the original data
+        icb_events_subset <- icb_events_subset %>%
+          filter(!(
+                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
+                say_actor_a %in% singleton_actors |
+                say_actor_b %in% singleton_actors |
+                do_actor_a %in% singleton_actors |
+                do_actor_b %in% singleton_actors 
+          ) )
+
+          #recreate diads again using the new sentence numbers
+          icb_events_subset_diad <- icb_events_subset %>% 
+                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
+                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
+                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
+                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
+                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
+                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
+                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
+                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
+                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
+                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
+                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
+                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
+                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
+                                                            sent,
+                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
+                                                            thinkkind, sayintkind, dokind,
+                                                            point_in_time_year, point_in_time_month
+                                                            ) %>% distinct() %>%
+                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
+                                        filter(!(
+                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
+                                              say_actor_a %in% singleton_actors |
+                                              say_actor_b %in% singleton_actors |
+                                              do_actor_a %in% singleton_actors |
+                                              do_actor_b %in% singleton_actors 
                                         ) ) %>% 
-      flextable::add_header(values =
-          list(crisno = "Crisis",
-                crisis_text = "Crisis",
-                yrtrig = "Years",
-                yrterm = "Years",
-                n_sentence_number_int_aligned = "Counts",
-                n_events = "Counts",
-                coders_expert = "Coders",
-                coders_novice = "Coders"#,
-                #value_markdown = "Abstract"
-               ) ) %>%
-      flextable::merge_h(part = "header" ) %>%
-      flextable::width( j = 1, width=0.3)  %>%
-      flextable::width( j = 2, width=2.75)  %>%
-      flextable::width( j = 3, width=0.6)  %>%
-      flextable::width( j = 4, width=0.6)  %>%
-      flextable::width( j = 5, width=0.25)  %>%
-      flextable::width( j = 6, width=0.25)  %>%
-      flextable::width( j = 7, width=0.25)  %>%
-      flextable::width( j = 8, width=0.35)  %>%
-      flextable::width( j = 9, width=2.5)  %>%
-      flextable::width( j = 10, width=1.5)  %>%
-      flextable::width( j = 11, width=1.0)  %>%
-      flextable::fontsize(size = 9, part = "all") %>%
-      flextable::padding(padding = 0.1, part = "all") %>%
-      flextable::line_spacing(space = 1, part = "body") %>%
-      flextable::bg( i = which( 1:nrow(x) %% 2 == 1)  , part = "body", bg = "#EFEFEF") %>%
-      ftExtra::colformat_md(j = 9:11, part="body")
-}
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png", zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png", zoom=1)
+                                       arrange(sent) %>%
+                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
+      }
+  }
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  #Order actors by how many interactions they have together
+  temp <- bind_rows(
+    icb_events_subset_diad  %>% 
+      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
+    icb_events_subset_diad %>% 
+      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
+  )  %>% arrange(actor_1, actor_2) %>% distinct()
+
+  #new plan is to minimize the number of crossovers
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("actor_2", "actor_1", "sent"))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
+  rowwise() %>%
+  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
+  arrange(desc(n))
+
+  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+  diag(temp2_wide) <- 0
+  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
+
+  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
+            )  %>%
+            filter(!is.na(actor)) %>%
+           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  icbe_actor_to_qcode <- icb_events_long %>%
+                         dplyr::filter(crisno==crisis  ) %>% 
+                         filter(varname_normalized %>% str_detect("actor")) %>% 
+                         dplyr::select(value_normalized,value_qcode) %>% 
+                         na.omit() %>% distinct()
+
+  actor_colors_df <- icbe_actor_to_qcode %>%
+    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
+  actor_colors <- actor_colors_df$actor_color
+  names(actor_colors) = actor_colors_df$value_normalized
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                      mutate(x=max(x)+50) %>%
+                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
+                      na.omit() %>% 
+                      distinct() %>%  
+                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                      group_by(sent) %>%
+                       filter(year_float==min(year_float)) %>%
+                      ungroup() %>% as.data.frame() %>%
+                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                      filter(!duplicated(year_float ) ) %>%
+                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+  # #Units
+  # units <-   icb_events_subset %>% dplyr::select(sent, do_actor_a, interact_units) %>% na.omit()  %>% 
+  #             mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
+  #             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
+  #             mutate(IMAGE=paste0(here::here(), '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
+  #             mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+  #             left_join(icb_events_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
+  #             dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
+  #             arrange(actor_sent, interact_units) %>%
+  #             group_by(actor_sent) %>%
+  #               mutate(units_count=n()) %>%
+  #               mutate(middle=units_count/2) %>%
+  #               mutate(units_number=row_number()) %>%
+  #               mutate(offeset=(middle-units_number)*10)  
+  #   
+  # fatalities <-   icb_events_subset %>% 
+  #                 dplyr::select(crisno, sent, do_actor_b, interact_fatalities) %>% na.omit() %>% #filter(interact_fatalities!='none') %>%
+  #                 mutate(interact_fatalities = strsplit(as.character(interact_fatalities), ";")) %>% unnest(interact_fatalities) %>%
+  #                 mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b) %>%
+  #                 mutate(actor_sent= do_actor_b %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+  #                 left_join(icb_events_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
+  #                 rename(actor=do_actor_b) %>%
+  #                 #dplyr::select(-sent, -do_actor_b) %>%
+  #                 distinct() %>% 
+  #                 mutate(interact_fatalities=interact_fatalities %>% 
+  #                          factor(levels=c('none','individuals','tens','hundreds','thousands','tens of thousands','hundreds of thousands')) %>% as.numeric() ) %>%
+  #                 arrange(actor_sent, interact_fatalities) %>%
+  #                 group_by(actor_sent) %>%
+  #                   filter(interact_fatalities==max(interact_fatalities, na.rm=T)) %>%
+  #                 ungroup()
+  #   
+  # 
+  # #table(icb_events$interact_fatalities)
+  # #table(icb_events$interact_domains)
+  # #table(icb_events$interact_forces)
+  # 
+  # 
+  # units <-   icb_events_subset %>% 
+  #             dplyr::select(sent, do_actor_a, interact_units) %>% na.omit()  %>% 
+  #             mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
+  #             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
+  #             mutate(IMAGE=paste0(here::here(), "/replication_paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
+  #             mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+  #             left_join(icb_events_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
+  #             dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
+  #             arrange(actor_sent, interact_units) %>%
+  #             group_by(actor_sent) %>%
+  #               mutate(units_count=n()) %>%
+  #               mutate(middle=units_count/2) %>%
+  #               mutate(units_number=row_number()) %>%
+  #               mutate(offeset=(middle-units_number)*5)
+
+  ####Actor levels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
+    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
+    rowwise() #%>%
+    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
+
+  ######Monads
+  icb_events_subset_monad <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
+                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
+                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
+            ) %>% 
+            na.omit() %>% 
+            distinct() %>% 
+            filter(!duplicated(paste(sent,actor,leaf))) %>%
+            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
+            distinct() %>% 
+            group_by(sent,actor,actor_sent) %>%
+              summarise(leaf=paste(leaf, collapse="\n") ) %>%
+            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
+
+  ######Directed
+  icb_events_subset_directed <- 
+            #We need to enumerate all the possibilities
+            bind_rows(
+              #Do alone
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
+              #Say alone
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
+              #Say Do
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
+                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf) ,
+              ##Think Do
+              #icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+              #  mutate(leaf=paste0(thinkkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf) ,
+              ##Think Say Do
+              #icb_events_subset_diad %>% filter(!is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
+              #  mutate(leaf=paste0(thinkkind,"-",sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf) ,
+            ) %>% 
+            na.omit() %>% 
+            distinct() %>% 
+            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            arrange(sent, actor_sent_1,leaf) %>%
+            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
+           #It is actually easier just to rejex out some dupes
+            mutate(leaf = leaf %>%
+                     str_replace("accept\naccept","accept") %>%
+                   str_replace("appeal\nappeal","appeal") %>%
+                   str_replace("reject\nreject","reject") %>%
+                   str_replace("express intent\nexpress intent","express intent") 
+                   ) %>%
+           arrange(sent, actor_sent_1,leaf) %>%
+           filter(actor_sent_1!=actor_sent_2) #there's a bug where you get the same node on both sides somehow
+            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  #debug
+  icb_events_subset_directed <- icb_events_subset_directed  %>% 
+           group_by(sent, leaf) %>%
+               mutate(bundle_count=n()) %>%
+               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
+            ungroup() #%>% 
+            #filter(bundle_count>1)
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf2, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1,
+                       bundle_count=icb_events_subset_directed$bundle_count
+                       )
+
+    #https://www.flaticon.com/free-icons/aircraft-carrier
+  #install.packages('ggimage')
+  library(ggimage)
+
+  #hbundle <- edge_bundle_hammer(g, xy, bw = 0.7, decay = 0.5)
+
+  ######Put it all together
+  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
+  p_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                            colour=actor,
+                            label=leaf,
+                            filter=eventedge==T & bundle_count==1 
+                            ),
+                        label_colour=NA, 
+                        vjust = -0.75,
+                        lineheight = .75,
+                        sep = unit(1, 'mm'), 
+                        edge_width=0.25, 
+                        show.legend = F,
+                        arrow = arrow(length = unit(2, 'mm')),
+                        label_size=3,
+                        check_overlap=global_check_overlap,
+                        start_cap = circle(3, 'mm'),
+                        end_cap = circle(3, 'mm'),
+                        angle_calc = 'along' #,
+                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
+                       ) +
+              #Grouped Edges
+              geom_edge_parallel(aes(  
+                                  colour=actor,
+                                  label=leaf,
+                                  filter=eventedge==T & bundle_count>1
+                                  ),
+                              vjust = -0.75,
+                              lineheight = .75,
+                              sep = unit(5, 'mm'), 
+                              edge_width=0.4,  #0.25
+                              show.legend = F,
+                              arrow = arrow(length = unit(1, 'mm')),
+                              label_size=4,
+                              check_overlap=global_check_overlap,
+                              start_cap = circle(3, 'mm'),
+                              end_cap = circle(3, 'mm'),
+                              angle_calc = 'along'
+                             ) +
+
+              #Time edges
+              geom_edge_link(aes(
+                              edge_colour=actor,
+                              filter=timeedge==T
+                              ),
+                              edge_width=0.1, 
+                              show.legend = F,
+                              check_overlap=global_check_overlap
+                             ) +
+              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+              #Fatalities
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
+
+              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
+              #Add Actor Names
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
+                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
+                        check_overlap=global_check_overlap) + #-45
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  if(prune_rare==T & !is.null(notes)){
+     p_metro_map <- p_metro_map + labs(caption = notes)
+  }
+
+  p_metro_map$actor_colors <- actor_colors #we have to smuggle the variable containing the colors out in the object 
+  p_metro_map$sentence_count <- icb_events_subset$sentence_number_int_aligned %>% unique() %>% length()
+  p_metro_map$icb_events_subset <- icb_events_subset
+
+  p_metro_map   %>% saveRDS(save_file)
+
+  return(NULL)
+}
+
+c(196, 471) %>% sapply(FUN=function(x) icbe_metro_plots(x))
 
@@
 
-\begin{figure}[H]
-\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png"}}
-\end{figure}
-
-\begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png"}}
-\end{figure}
-
-## Table A2: Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}
-\hphantom{em}
-
-```{r , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-#Switched to spans here
-icb_text <- ICBe_events_agreed %>% dplyr::select(crisno,sentence_number_int_aligned, sentence=sentence_span_text) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)
-
-# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)
-
-fromscratch=F
-if(fromscratch){
-  #Here we use spacy to extract verbs from the sentences
-  p_load("spacyr")
-  #spacy_install() 
-  spacy_initialize(model = "en_core_web_sm")
-
-  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
-  parsed_consolidated <- nounphrase_consolidate(parsed)
-  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
-  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
-  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
-  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]
-
-  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
-
-  entities <- entity_extract(parsed, type = "all")
-  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
-
-} else {
-  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
-  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))
-
-}
-
-entities$doc_id_num <- entities$doc_id %>% str_replace_all("text","") %>% as.numeric()
-entities$crisno <- icb_text$crisno[entities$doc_id_num]
-entities_unique <- entities %>% dplyr::select(entity,entity_type) %>% mutate(entity = entity %>% str_to_lower() %>% str_replace_all("[^A-Za-z0-9]","") ) %>% distinct()
-
-target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
-dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
-
-unique_agent_q_codes <- dictionary_actors$value_disaggregated_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
-unique_actor_q_codes <- dictionary_actors$value_normalized_wikidata_id %>% na.omit() %>% unique() %>% str_split(";") %>% unlist() %>% trimws() %>% unique()
-
-verbs_sentence <- parsed %>% filter(pos=="VERB")
-
-verbs <- parsed %>% filter(pos=="VERB") %>% dplyr::select(lemma, pos) %>% distinct()
-
-entities_per_sentence <- entities %>% 
-  count(doc_id) %>% 
-  summarise(
-    entities_per_sentence_min=min(n),
-    entities_per_sentence_mean=mean(n),
-    entities_per_sentence_max=max(n),
+## ICBe Tables
+
+out the sentence tables 
+We do this with the markdown versions now
+
+```{r, eval=F}
+
+icb_sentence_tables <- function(crisis=196){
+  print(crisis)
+  ft_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
+  save_file <- paste0(here::here(), "/replication_paper/tables/sentence_tables/ft_sentence_table_",crisis,".Rds")
+
+  temp <- icb_events %>% 
+          filter(crisno==crisis) %>%
+              group_by(crisno, sentence_number_int_aligned, crisno_sent, sentence) %>%
+                summarize(codings_sentence = paste(codings_sentence, collapse="\n")) %>%
+              ungroup() %>%
+              dplyr::select(id=crisno_sent, sentence, codings_sentence)
+
+  temp_ft <- temp %>%
+              as_flextable() %>%
+              colformat_md(j=3) %>% #There can be bad unicode characters in the sentence so make sure you only make the coded sentence markdown
+              flextable::fontsize(size = 7, part = "all") %>%
+              flextable::bg( i = which( 1:nrow(temp) %% 2 == 1)  , j=1:3, part = "body", bg = "#EFEFEF") %>%
+              flextable::width(j = 1, width=0.3, unit = "in") %>%
+              flextable::width(j = 2, width=4, unit = "in") %>%
+              flextable::width(j = 3, width=4, unit = "in")
+
+  temp_ft  %>% saveRDS(save_file)
+}
+
+c(196, 471) %>% sapply(FUN=function(x) icb_sentence_tables(x))
+
+```
+
+# ICB
+
+## Data Loads
+
+```{r}
+
+#Note yemen 679 doesn't show up in this data
+icb_df <- data.frame(
+  stringsAsFactors = FALSE,
+          icb_name = c("Afghanistan","Albania",
+                       "Algeria","Andorra","Angola","Antigua & Barbuda",
+                       "Argentina","Armenia","Australia","Austria","Azerbaijan",
+                       "Bahamas","Bahrain","Bangladesh","Barbados","Belarus",
+                       "Belgium","Belize","Benin (Dahomey)","Bhutan","Bolivia",
+                       "Bosnia","Botswana","Brazil","Brunei","Bulgaria",
+                       "Burkina Faso (Upper Volta)","Burma (see Myanmar)",
+                       "Burundi","Cambodia","Cameroon","Canada","Cape Verde",
+                       "Central African Republic","Chad","Chile","China",
+                       "China","Colombia","Comoros","Congo Brazzaville",
+                       "Congo, Democratic","Costa Rica","Cote D’Ivoire","Croatia",
+                       "Cuba","Cyprus","Czech Republic","Czechoslovakia",
+                       "Dahomey (see Benin)","Denmark","Djibouti (Somalia Fr.)",
+                       "Dominica","Dominican Republic","Ecuador","Egypt (UAR)",
+                       "El Salvador","Equatorial Guinea","Eritrea","Estonia",
+                       "Ethiopia","Federated States of Micronesia","Fiji",
+                       "Finland","Formosa","France","French West Africa",
+                       "Gabon","Gambia","Georgia",
+                       "German Democratic Republic (East Germany)",
+                       "Germany (German Federal Republic, West Germany)","Germany (Prussia)","Ghana",
+                       "Great Britain (see United Kingdom)","Greece","Grenada","Guatemala",
+                       "Guinea","Guinea Bissau","Guyana","Haiti","Hijaz (Hejaz)",
+                       "Honduras","Hungary","Iceland","India","Indonesia",
+                       "Iran","Iraq","Ireland (Eire)","Israel","Italy",
+                       "Ivory Coast (see Cote D’Ivoire)","Jamaica","Japan",
+                       "Jordan","Kazakhstan","Kenya","Korea","Kosovo","Kuwait",
+                       "Kyrgyz Republic","Laos","Latvia","Lebanon","Lesotho",
+                       "Liberia","Libya","Liechtenstein","Lithuania",
+                       "Luxemberg","Macedonia","Madagascar (Malagasy Republic)",
+                       "Malawi","Malaysia","Maldives","Mali","Malta",
+                       "Marshall Islands","Mauritania","Mauritius","Mexico","Moldova",
+                       "Monaco","Mongolia","Morocco","Mozambique",
+                       "Myanmar (Burma)","Najd (Nejd)","Namibia (South West Africa)",
+                       "Nepal","Netherlands","Nevis","New Zealand",
+                       "Nicaragua","Niger","Nigeria",
+                       "North Korea (People’s Republic of Korea)","Norway","Oman","Pakistan","Palau","Panama",
+                       "Papua and New Guinea","Paraguay","Peru",
+                       "Philippines","Poland","Portugal","Principe","Qatar",
+                       "Republic of (Congo Kinshasa) (Zaire)","Rhodesia (see Zimbabwe)",
+                       "Rumania","Russia (Soviet Union)","Rwanda",
+                       "San Marino","Sao Tome","Saudi Arabia","Senegal",
+                       "Serbia (see Yugoslavia)","Seychelles","Sierra Leone","Singapore",
+                       "Slovakia","Slovenia","Solomons","Somalia",
+                       "Somalia Fr. (see Djibouti)","South Africa",
+                       "South Korea (Republic of Korea)","South Sudan",
+                       "South West Africa (see Namibia)","Spain","Spanish Sahara (see Western Sahara)",
+                       "Sri Lanka (Ceylon)","St. Kitts","St. Lucia",
+                       "St. Vincent & The Grenadines","Sudan","Surinam","Swaziland",
+                       "Sweden","Switzerland","Syria","Taiwan (China",
+                       "Tajikistan","Tanzania","Thailand","Tibet","Togo",
+                       "Trinidad & Tobago","Tunisia","Turkey","Turkmenistan","Uganda",
+                       "Ukraine","United Arab Emirates",
+                       "United Kingdom (Great Britain)","Upper Volta (see Burkina Faso)","Uruguay",
+                       "USA","USSR (see Russia)","Uzbekistan","Vanuatu",
+                       "Venezuela","Vichy France",
+                       "Vietnam, Democratic Republic of (North Vietnam)","Vietnam, Republic of (South Vietnam)",
+                       "Western Sahara (Spanish Sahara)","Western Samoa",
+                       "Yemen (Arab Republic of Yemen, North Yemen)",
+                       "Yemen, People’s Republic of (South Yemen)","Yugoslavia (Serbia)",
+                       "Zambia","Zanzibar","Zimbabwe (Rhodesia)"),
+       icb_letters = c("AFG","ALB","ALG","AND",
+                       "ANG","AAB","ARG","ARM","AUL","AUS","AZE","BHM",
+                       "BAH","BNG","BAR","BLR","BEL","BLZ","BEN","BHU","BOL",
+                       "BOS","BOT","BRA","BRU","BUL","BFO",NA,"BUI",
+                       "CAM","CAO","CAN","CAP","CEN","CHA","CHL",NA,"CHN",
+                       "COL","COM","CON","DRC","COS","CDI","CRO","CUB",
+                       "CYP","CZR","CZE",NA,"DEN","DJI","DMA","DOM",
+                       "ECU","EGY","SAL","EQG","ERI","EST","ETH","FSM","FIJ",
+                       "FIN","TAW","FRN","FWA","GAB","GAM","GRG","GDR",
+                       "GFR","GMY","GHA",NA,"GRC","GRN","GUA","GUI",
+                       "GNB","GUY","HAI","HIJ","HON","HUN","ICE","IND",
+                       "INS","IRN","IRQ","IRE","ISR","ITA",NA,"JAM","JPN",
+                       "JOR","KZK","KEN","KOR","KOS","KUW","KYR","LAO",
+                       "LAT","LEB","LES","LBR","LIB","LIE","LIT","LUX",
+                       "MAC","MAG","MAW","MAL","MAD","MLI","MLT","MSI",
+                       "MAA","MAS","MEX","MLD","MNC","MON","MOR","MZM","MYA",
+                       "NAJ","NAM","NEP","NTH","SKN","NEW","NIC","NIR",
+                       "NIG","PRK","NOR","OMA","PAK","PAL","PAN","PNG",
+                       "PAR","PER","PHI","POL","POR","STP","QAT","DRC",
+                       NA,"RUM","RUS","RWA","SNM",NA,"SAU","SEN",NA,
+                       "SEY","SIE","SIN","SLO","SLV","SOL","SOM",NA,"SAF",
+                       "ROK","SSD",NA,"SPN",NA,"SRI",NA,"SLU","SVG",
+                       "SUD","SUR","SWA","SWD","SWZ","SYR",NA,"TAJ","TAZ",
+                       "THI","TBT","TOG","TRI","TUN","TUR","TKM","UGA",
+                       "UKR","UAE","UKG",NA,"URU","USA",NA,"UZB","VAN",
+                       "VEN","VFR","DRV","RVN","SPA","WSM","YEM","YPR",
+                       "YUG","ZAM","ZAN","ZIM"),
+          icb_code = c("700","339","615","232",
+                       "540","058","160","371","900","305","373","031",
+                       "692","771","053","370","211","080","434","760","145",
+                       "346","571","140","835","355","439",NA,"516",
+                       "811","471","020","402","482","483","155",NA,"710",
+                       "100","581","484","490","094","437","344","040",
+                       "352","316","315",NA,"390","522","054","042",
+                       "130","651","092","411","531","366","530","987","950",
+                       "375","713","220","480","481","420","372","265",
+                       "260","255","452",NA,"350","55","090","438",
+                       "404","110","041","671","091","310","395","750","850",
+                       "630","645","205","666","325",NA,"051","740",
+                       "663","705","501","730","347","690","703","812",
+                       "367","660","570","450","620","223","368","212",
+                       "343","580","553","820","781","432","338","983","435",
+                       "590","070","359","221","712","600","541","775",
+                       "672","565","790","210","060","920","093","436",
+                       "475","731","385","698","770","986","095","910",
+                       "150","135","840","290","235","403","694","490",NA,
+                       "360","365","517","331",NA,"670","433",NA,"591",
+                       "451","830","317","349","940","520",NA,"560",
+                       "732","626",NA,"230",NA,"780",NA,"056","057","625",
+                       "115","572","380","225","652",NA,"702","510",
+                       "800","711","461","052","616","640","701","500",
+                       "369","696","200",NA,"165","002",NA,"704","935",
+                       "101","219","816","817","605","990","678","680",
+                       "345","551","511","552")
 )
 
+df_IWCA <- data.frame(
+  stringsAsFactors = FALSE,
+              IWCA = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L, 10L),
+        IWCA_label = c("not an intra-war crisis (IWC)",
+                       "Entry of a major actor into an ongoing war",
+                       "Perceived high probability of a major actor entering a war",
+                       "Exit of a major actor",
+                       "Perceived high probability of major power exiting a war",
+                       "Technological escalation of a war","Major non-technological escalation",
+                       "Defeat in a significant battle","Internal deterioration","Other")
+)
+
+df_break <- 
+data.frame(
+  stringsAsFactors = FALSE,
+             BREAK = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
+       BREAK_label = c("Verbal act","Political act",
+                       "Economic act","External change",
+                       "Other non-violent act",
+                       "Internal verbal or physical challenge to regime or elite","Non-violent military act","Indirect violent act",
+                       "Violent act")
+)
+
+#icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
+icbdy_20 <- readRDS(paste0(here::here(), '/replication_paper/data/in/icbdy_20.Rds'))
+
+icbdy_20_clean <- icbdy_20 %>%
+                  left_join( icb_df %>% dplyr::select(STATEA=icb_code, actor_1=icb_name ) %>% mutate(STATEA=STATEA %>% as.numeric())  ) %>%
+                  left_join( icb_df %>% dplyr::select(STATEB=icb_code, actor_2=icb_name ) %>% mutate(STATEB=STATEB %>% as.numeric())  ) %>%
+                  left_join(df_IWCA %>% dplyr::select(IWCA=IWCA, IWCA_label=IWCA_label )  ) %>%
+                  left_join(df_IWCA %>% dplyr::select(IWCB=IWCA, IWCB_label=IWCA_label )  )
+
+icb_diadic <- icbdy_20_clean %>% dplyr::select(CRISNO, NAMEA, NAMEB,  STATEA, STATEB, actor_1,actor_2, IWCA_label,IWCB_label) #%>% filter(is.na(actor_1) | is.na(actor_2))
+
+icb2v14 <- read_csv(paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))
+
+df_trigger <- data.frame(
+  stringsAsFactors = FALSE,
+            triggr = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
+                    triggr_label = c("Verbal act","Political act","Economic act",
+                                     "External change","Other non-violent act",
+                                     "Internal verbal or physical challenge to regime or elite",
+                                     "Non-violent military act","Indirect violent act","Violent act")
+              )
+
+df_majres <- data.frame(
+  stringsAsFactors = FALSE,
+            majres = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
+                   majres_label = c("No response-inaction","Verbal act",
+                                    "Political act","Economic act",
+                                    "Other non-violent act",
+                                    "Non-violent military act",
+                                    "Multiple including non-violent military act",
+                                    "Violent military act",
+                                    "Multiple including violent military act")
+             )
+
+df_outcome <- 
+data.frame(
+  stringsAsFactors = FALSE,
+            outcom = c(1L, 2L, 3L, 4L, 5L),
+      outcom_label = c("Victory", "Compromise", "Stalemate", "Defeat", "Other")
+)
+
+df_outfor <- 
+data.frame(
+  stringsAsFactors = FALSE,
+            outfor = c(1L,2L,3L,4L,5L,6L,7L,8L,
+                       9L,10L,11L,12L,13L,14L,15L),
+      outfor_label = c("Formal agreement - voluntary",
+                       "Semi-formal agreement - voluntary",
+                       "Tacit understanding","Unilateral - self","Unilateral - ally",
+                       "Unilateral - adversary","Compliance","Imposed - imposer",
+                       "Imposed - imposee","Spillover",
+                       "Other - global organization intervention","Other - ally",
+                       "Other - internal or non-state actor","Other - misc.","Faded")
+)
+
+icb2v14_clean <- icb2v14 %>% 
+                 left_join(icb_df %>% dplyr::select(cracid=icb_code, actor_label=icb_name ) %>% mutate(cracid=cracid %>% as.numeric()) ) %>%  #you can't actually match on the letter codes you have to match on the numbers, uhhhhhg
+                 left_join( df_trigger  ) %>% 
+                 left_join( df_majres ) %>% 
+                 left_join( df_outcome ) %>% 
+                 left_join( df_outfor )
+
+icb_monadic <-  
+  bind_rows(
+   icb2v14_clean%>% mutate(sent= yrtrig + tidyr::replace_na((motrig/12),0) + tidyr::replace_na(datrig/31/12,0) ) %>% mutate(type='start') %>% dplyr::select(year=yrtrig, month=motrig, crisno,type, sent, actor_label, leaf=triggr_label),
+   icb2v14_clean %>% mutate(sent= yerres + tidyr::replace_na((monres/12),0) + tidyr::replace_na(dayres/31/12,0) ) %>% mutate(type='mid') %>% dplyr::select(year=yerres, month=monres, crisno,type, sent, actor_label, leaf=majres_label),
+   icb2v14_clean %>% mutate(sent= yrterm + tidyr::replace_na((moterm/12),0) + tidyr::replace_na(daterm/31/12,0) ) %>% mutate(type='end') %>% dplyr::select(year=yrterm, month=moterm, crisno,type, sent, actor_label, leaf=outfor_label)
+  ) %>% as.data.frame()
+
 ```
 
-```{r, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-#wordnet rdf (in tripple format)
-#wordnet rdf (in tripple format)
-fromscratch=F
-
-wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )
-subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('http://purl.org/dc/terms/subject'))
-subject_headings_verbs <- subject_headings %>%
-                          filter(value %>% str_detect('-v>')) %>% 
-                          mutate(value=value %>% str_replace("<http://wordnet-rdf.princeton.edu/id/","2")) %>% 
-                          mutate(value=value %>% str_replace("-v> <http://purl.org/dc/terms/subject> ","\t")) %>%
-                          separate(value, c("a", "b"), extra = "drop", fill = "right", sep="\t") %>%
-                          mutate(b = b %>% str_replace_all('\\"| \\.',""))
-
-#subject_headings <- wordnet_rdf %>% as_tibble() %>% filter(value %>% str_detect('00002137')) #the first digit is for part of speech so we can remove that if we subset to just verbs
-#wordnet csv
-filenames <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"))
-filepaths <- list.files(path=paste0(here::here(), "/replication_paper/data/in/wncsv-master/csv/"), full.names = T)
-
-wordnet_list <- lapply(filepaths, read_csv, col_names=F, progress=F, show_col_types=F)
-names(wordnet_list) <- filenames
-
-#wordnet_list[[8]]
-#wordnet_list[[16]]
-#wordnet_list[[19]]
-
-#wordnet_list[["wn_cls.csv"]]
-#wordnet_list[["wn_vgp.csv"]]
-
-hypernyms <- wordnet_list[['wn_hyp.csv']] %>% 
-              dplyr::select(a=X1,b=X2) %>% 
-              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(a=X1, a_lemma=X3) ) %>% 
-              left_join(wordnet_list[["wn_s.csv"]] %>% dplyr::select(b=X1, b_lemma=X3) )
-
-library(igraph)
-g_hypernyms <-  graph_from_data_frame(hypernyms, directed = TRUE)
-
-wordnet <- wordnet_list[["wn_s.csv"]] %>% dplyr::select(wordnetid=X1, lemma=X3, tense=X4) %>% full_join( wordnet_list[['wn_g.csv']] %>% dplyr::select(wordnetid=X1, gloss=X2) )
-
-wordnet_verbs <- wordnet %>% filter(tense=='v')
-
-verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
-#oh got it this is all possible matching glosses per ICBe sentence
-#dim(verbs_sentence_wordnet) #227,426
-
-#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances
-
-gloss_unique <- verbs_sentence_wordnet$gloss %>% unique() #how are there so few unique glosses?
-length(gloss_unique) #And there's also about 5k unique glosses
-
-sentences_unique <- verbs_sentence_wordnet$sentence %>% unique()
-length(sentences_unique) #11769
+## ICB Function
+
+```{r}
+
+icb_metro_plots <- function(crisis=196, prune_rare=T){
+
+    print(crisis)
+    save_icb_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icb_metro_plot_",crisis,".Rds")
+
+    icb_diadic_subset <- icb_diadic %>% filter(CRISNO==crisis) #Not all of them are diadic apparently
+    icb_monadic_subset <- icb_monadic %>% rename(actor=actor_label) %>% filter(crisno==crisis) %>%
+                       mutate(sent=sent %>% rank() %>% round()) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") ))   %>% arrange(sent, actor)
+
+    g <- make_empty_graph(n = 0, directed = TRUE)
+      #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+    icb_events_subset_diad <- bind_rows(
+            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>% 
+                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>% rename(actor_2=actor_1,actor_1=actor_2),
+            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>%
+                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),
+
+            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>%
+                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>% rename(actor_2=actor_1,actor_1=actor_2),
+            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>% 
+                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),
+
+            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
+                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>% rename(actor_2=actor_1,actor_1=actor_2),
+            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
+                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),
+
+          ) %>% dplyr::select(year, month,sent, actor_1, actor_2, leaf) %>% distinct() %>% na.omit()
+
+     if(nrow(icb_events_subset_diad)==0){
+      print("No dyadic icb rows skipping")
+      return()
+    }
+
+    #Order actors by how many interactions they have together
+    temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()
+
+    temp2 <- bind_rows(
+      temp,
+      temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
+    ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
+
+    temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+    rownames(temp2_wide) <- temp2_wide$actor_1
+    temp2_wide$actor_1 <- NULL
+    temp2_wide <- temp2_wide %>% as.matrix()
+    temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
+    temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+    hc <- hclust(temp2_wide %>% as.dist(), method="single")
+
+    temp_list <- list()
+    for(i in 1:nrow(temp2_wide)){
+      temp_list[[as.character(i)]] <- cutree(hc, k=i)
+    }
+
+    #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
+    #  arrange(across(starts_with("V")))
+    ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+    #####Nodes
+    icb_events_subset_nodes <- 
+              bind_rows(
+                        icb_events_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_1) ,
+                        icb_events_subset_diad %>% dplyr::select(year, month,sent=sent, actor=actor_2) 
+              ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+              mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                     y=sent*-1 *100)
+
+    actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
+    actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+    names(actor_colors) = levels(actors)
+
+    date_sineposts <- icb_events_subset_nodes  %>%
+                        mutate(x=max(x)+50) %>%
+                        dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
+                        na.omit() %>% 
+                        distinct() %>%  
+                        mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                        mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                        group_by(sent) %>%
+                        filter(year_float==min(year_float)) %>%
+                        ungroup() %>% as.data.frame() %>%
+                        filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                        filter(!duplicated(year_float ) ) %>%
+                        mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+    ####Actor levels
+    icb_events_subset_nodes_min <- 
+                  icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+                  #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+                  #rename(qcode=actor, actor=value_normalized_label) %>%
+                  rowwise() %>%
+                  mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
+
+    for(i in 1:nrow(icb_events_subset_nodes)){
+      g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                  actor = icb_events_subset_nodes$actor[i], 
+                                  sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+    }
+
+    xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+    #####Time Edges
+    icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+    g <- g %>% 
+         add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                   actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)
+
+    ######Directed
+    icb_events_subset_directed <- 
+              icb_events_subset_diad %>% 
+              dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
+              mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+              mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+              group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+                summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
+              #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+    g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                         timeedge=F, 
+                         leaf=icb_events_subset_directed$leaf, 
+                         eventedge=T,
+                         actor=icb_events_subset_directed$actor_1)
+
+    p_icb_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Time edges
+          geom_edge_link(aes(
+                          edge_colour=actor,
+                          filter=timeedge==T
+                          ),
+                          edge_width=0.1, 
+                          show.legend = F
+                         ) +
+          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                              colour=actor,
+                              label=leaf,
+                              filter=eventedge==T #& bundle_count==1
+                              ),
+                          vjust = -0.75,
+                          lineheight = .75,
+                          sep = unit(1, 'mm'), 
+                          edge_width=0.25, 
+                          show.legend = F,
+                          arrow = arrow(length = unit(2, 'mm')),
+                          label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+
+              #Not in phoenix
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
+              #Not in phoenix
+              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #Not in phoenix
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+      p_icb_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+      p_icb_metro_map$actor_colors <- actor_colors
+      p_icb_metro_map$icb_monadic_subset <- icb_monadic_subset
+
+      p_icb_metro_map %>% saveRDS(save_icb_file)
+
+}
+
+c(196, 471) %>% sapply(FUN=function(x) icb_metro_plots(x))
 
@@
 
-```{r python load, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-library(reticulate)
-reticulate::py_discover_config()
-
-#use_python("/home/skynet3/anaconda3/bin/python/")
-#use_python("/home/tlscherer/anaconda3/bin/python3")
+# Dyadic Mids
+
+## Data Loads
+
+```{r}
+
+mid4_df <- data.frame(
+  stringsAsFactors = FALSE,
+               act = c(1L,2L,3L,4L,5L,6L,7L,8L,
+                       9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
+                       20L,21L,22L),
+         act_label = c("1. None (1)",
+                       "2. Threat to use force (2)",
+                       "3. Threat to blockade (2)",
+                       "4. Threat to occupy terr. (2)",
+                       "5. Threat to declare war (2)",
+                       "6. Threat to join war (2)",
+                       "7. Show of troops (3)",
+                       "8. Show of ships (3)",
+                       "9. Show of planes (3)",
+                       "10. Alert (3)",
+                       "12. Mobilization (3)",
+                       "13. Fortify border (3)",
+                       "14. Border violation (4)",
+                       "15. Blockade (4)",
+                       "16. Occupation of territory (4)",
+                       "17. Seizure (4)",
+                       "18. Clash (4)",
+                       "19. Raid (4)",
+                       "20. Declaration of war (4)",
+                       "22. Begin interstate war (5)",
+                       "23. Join interstate war (5)",
+                       "24. Use CBR Weapons (5)")
+) %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
+
+mid_df <- data.frame(
+  stringsAsFactors = FALSE,
+               act = c(0L,1L,2L,3L,4L,5L,6L,7L,
+                       8L,9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
+                       20L,21L),
+         act_label = c("No militarized action (1)",
+                       "Threat to use force (2)","Threat to blockade (2)",
+                       "Threat to occupy terr. (2)","Threat to declare war (2)",
+                       "Threat to use CBR weapons","Threat to join war (2)",
+                       "Show of force (3)","Alert (3)","Nuclear alert (3)",
+                       "Mobilization (3)","Fortify border (3)","Border violation (4)",
+                       "Blockade (4)","Occupation of territory (4)",
+                       "Seizure (4)","Attack (4)","Clash (4)","Declaration of war (4)",
+                       "Use of CBR weapons (4)","Begin interstate war (5)",
+                       "Join interstate war (5)")
+)  %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
+
+mid_df2 <- data.frame(
+  stringsAsFactors = FALSE,
+                outcome = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
+                outcome_label = c("0. Ongoing MID",
+                       "1. Victory for State A","2. Victory for state B",
+                       "3. Yield by State A","4. Yield by State B","5. Stalemate",
+                       "6. Compromise","7. Released (for seizures)","8. Unclear",
+                       "-9 Missing")
+) %>% mutate(outcome_label= outcome_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
+
+dyadic_mid <- read_csv(paste0(here::here(), "/replication_paper/data/in/dyadic_mid_4.02.csv"))
+
+dyadic_mid_clean <- dyadic_mid %>% distinct() %>%
+                      left_join(actor_translator %>% dplyr::select(statea=COWcode, actor_1=QCode_name, actor_1_qcode=QCode)) %>% #I think we add color here
+                      left_join(actor_translator %>% dplyr::select(stateb=COWcode, actor_2=QCode_name, actor_2_qcode=QCode)) %>%
+                      left_join(mid_df  %>% dplyr::select( mid5hiacta=act , leaf_1=act_label )) %>%
+                      left_join(mid_df  %>% dplyr::select( mid5hiactb=act , leaf_2=act_label )) %>%
+                      left_join(mid_df2  %>% dplyr::select( outcome=outcome , outcome_label=outcome_label ))
 
@@
 
-```{python embed glosses, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
-#pip install -U sentence-transformers
-
-fromscratch=False
-
-if fromscratch:
-  from sentence_transformers import SentenceTransformer
-  import numpy as np
-  glosses=np.array(r.gloss_unique) #sentences_unique_sanitized
-  glosses_chars = np.array([len(q) for q in glosses])
-  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
-  len(glosses) #4977
-  n=len(glosses)
-  chunk_length=100
-  n_chunks = int(np.ceil(n/chunk_length)) #can only 
-  glosses_chunks=[glosses[i:i + chunk_length] for i in range(0, n, chunk_length)]
-  len(glosses_chunks)
-  len(glosses_chunks[0])  
-  model = SentenceTransformer('paraphrase-mpnet-base-v2')
-  glosses_embeddings = np.vstack([model.encode(q) for q in glosses_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
-  glosses_embeddings.shape #(4977, 768)
-
-else:
-  print("Skipping")
-
-```
-
-```{python embed sentences for wordnet , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-#Now embed the sentences from above (note this is raw original sentences not the normalized ones used in the main paper)
-#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
-#pip install -U sentence-transformers
-
-fromscratch=False
-if fromscratch:
-  from sentence_transformers import SentenceTransformer
-  import numpy as np
-  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
-  sentence_chars = np.array([len(q) for q in sentences])
-  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
-  len(sentences) #12161 12162
-  n=len(sentences)
-  chunk_length=100
-  n_chunks = int(np.ceil(n/chunk_length)) #can only 
-  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
-  len(sentences_chunks)
-  len(sentences_chunks[0])  
-  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
-  model = SentenceTransformer('paraphrase-mpnet-base-v2')
-  #sentences
-  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
-  #temp = model.encode(sentences_chunks[0])
-  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
-  sentences_embeddings.shape #(12103, 768)
-
-else:
-  print("Skipping")
-
-```
-
-```{r wordnet trees, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-fromsrcatch=F
-if(fromsrcatch){
-  #py$sentences
-  #py$glosses
-  glosses_embeddings <- py$glosses_embeddings
-  sentences_embeddings <- py$sentences_embeddings
-
-  rownames(sentences_embeddings) <- py$sentences #[1:100] 
-  dim(sentences_embeddings)
-  rownames(glosses_embeddings) <- py$glosses #[1:100]
-  dim(glosses_embeddings)
-
-  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
-  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
-  gloss_clean <- verbs_sentence_wordnet$gloss
-  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
-  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
-  dim(glosses_embeddings_expanded)
-
-  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
-  table(condition_sentences_embeddings) #all are in it
-  sentences_clean <- verbs_sentence_wordnet$sentence
-  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
-  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
-  dim(sentences_embeddings_expanded)
-
-  #Isn't it just one minus the other?
-  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
-  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
-  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
-
-} else {
-
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
-
-}
-
-verbs_sentence_wordnet_top <- verbs_sentence_wordnet %>% group_by(crisno, sentence_number_int_aligned, token_id) %>% filter(row_number()==1)
-verbs_sentence_wordnet_top_unique <- verbs_sentence_wordnet_top %>% ungroup() %>% dplyr::select(lemma, wordnetid,tense, gloss) %>% group_by(lemma, wordnetid,tense, gloss) %>% count() %>% arrange(desc(n))
-
-```
-
-```{r create verb table , eval=T, echo=F, results="markup", include=T, message=T, cache=F, ft.arraystretch=0.75}
-
-set_flextable_defaults(fonts_ignore=TRUE)
-n_keep=200
-verbs_sentence_wordnet_top_ft <-
-        verbs_sentence_wordnet_top_unique %>%
-        ungroup() %>% 
-        head(n_keep) %>%
-        dplyr::select(n, lemma, gloss ) %>% #wordnetid
-        mutate(gloss=gloss %>% str_replace_all('[^A-Za-z0-9 ,.\"]','')) %>%
-
-        flextable::as_flextable() %>%
-
-        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
-        #width(j = 1, width=1.25) %>%
-        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
-        flextable::fontsize(size = 6, part = "all") %>% 
-        #rotate(rotation="tbrl",part="header") %>%
-        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
-        #align(align = "center", part = "body") %>%
-        #align(align = "center", part = "header") %>%
-        flextable::padding(padding = 0, part = "all") %>%
-        flextable::line_spacing(space = 1, part = "body") %>%
-        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
-        #fit_to_width(max_width=12) #This is crazy slow
-        #flextable::autofit() 
-        #set_table_properties(width = 1, layout = "autofit")
-
-      bg( i = which( 1:n_keep %% 2 == 1), part = "body", bg = "#EFEFEF") %>%
-      #merge_v(part = "body") %>% 
-      flextable::width( j = 1, width=0.3) %>%
-      flextable::width( j = 2, width=.75) %>%
-      flextable::width( j = 3, width=6) %>%
-      #flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      #hline(i=which( actor_agents$Player!=c(actor_agents$Player[2:length(actor_agents$Player)], NA) ), border = fp_border(color="gray", width = 0.25), part = "body")
-
-      #add_header( "IR Player_Pieces"="Citations"
-
-      #            top = TRUE ) %>%
-      set_header_labels(
-        values = list(
-          "uses" = "Count",
-          'lemma'='Lemma',
-          'gloss'='Gloss'
-          ) 
-        )
-
-#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
-
-verbs_sentence_wordnet_top_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
-
-```
-
-```{r verb table , eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}
-#, child=c('ICBEdataset_paper_appendixVerbMeanings.Rmd')
-
-verbs_sentence_wordnet_top_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/verbs_sentence_wordnet_top_ft.Rds'))
-verbs_sentence_wordnet_top_ft
-```
-
-# Appendix B: Coding Process
-\hphantom{em}
-
-## Figure B1: Graphical User Interface {#app:gui}
-\hphantom{em}
-
-\begin{figure}[H]
-\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
-\centering{\includegraphics[width=17cm]{../figures/gui_example}}
-\end{figure}
-
-## Algorithm B2: Coding Aggregation and Filtering {#app:algo1}
-\hphantom{em}
-
-\begin{algorithm}[H]
-\SetAlgoLined
-\KwData{Coder-Sentence-Tokens}
-\KwResult{Sentence-Events}
-\ForEach{sentence in sentences}{
-  \ForEach{concept in concepts}{
-    \ForEach{token in tokens}{
-      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
-      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
-      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
-    }
-    \If{sum(accepted) == 0}{
-      sort tags by votes;
-      head 1;
-      accept; \tcc*[f]{If still no tag, take one with most votes}
-    }
-  }
-  \ForEach{ActorSet in unique(ActorSets)}{
-    emit event;
-  }
-}
-\caption{Aggregating Coder-Tokens into Sentence-Events}
-\end{algorithm}
-
-## Figure B3 : Intercoder Agreement {#app:intercoderagreement}
-\hphantom{em}
-
-```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-
-fromscratch=F
-if(fromscratch){
-  means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
-                     #filter(votes_total>1) %>% #
-                     group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                     dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)
-
-  means_group_keep <- codings_long_agreement %>% filter(value_normalized!='') %>% 
-                      filter(algo1==1) %>%
-                      #filter(votes_total>1) %>%
-                      group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                      dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean)
-
-  means_group <- bind_rows( means_group_any %>% pivot_longer(c(Experts, Novices)),  means_group_keep %>% pivot_longer(c(Experts_keep, Novices_keep)) )
-
-  #Calculate average agreements by group
-  means_all <- codings_long_agreement %>% 
-                #This is top 1 agreement
-                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% 
-                arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                group_by(varname_normalized) %>%
-                mutate(n=n()) %>%
-                #filter(votes_total>1) %>% #about 9k only had one coder
-                #filter(selected_by_experts>=1) %>%
-                dplyr::select(Experts=percent_expert,Novices=percent_novice,n) %>% 
-                summarise_all(mean, na.rm=T)
-
-  means_keap <- codings_long_agreement %>% 
-                #Algo 1 agreement
-                filter(algo1==1) %>% 
-                #This is top 1 agreement
-                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                group_by(varname_normalized) %>%
-                #filter(votes_total>1) %>% #What work is this doing?
-                #filter(selected_by_experts>=1) %>%
-                dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean, na.rm=T)
-
-  factor_order <- means_keap %>% arrange(desc(Experts_keep)) %>% pull(varname_normalized)
-  p_percent_chose_tag_by_concept <- 
-  means_all %>% full_join(means_keap) %>% mutate(varname_normalized = varname_normalized %>% factor(levels=factor_order %>% rev)) %>%
-    filter(n>100) %>% dplyr::select(-n) %>% #require at least 100 examples
-  pivot_longer(c(-varname_normalized)) %>%
-      ggplot(aes(x=selected_by_any_perc, y=varname_normalized)) + 
-      #geom_boxplot() + 
-      geom_point(aes(x=value, color=name )) +
-      xlab("Percent of Coders that selected Tag") +
-      ylab("") +
-      labs(
-        title = "Intercoder Agreement by Concept (Top 1 Tags)",
-        subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
-        caption = paste0("Mean by Concept (Point); Mean by Group (Line)"), 
-       color = "Codings"
-       ) + 
-      theme_bw() +
-      theme(legend.position="bottom") +
-      geom_vline(data=means_group, aes(xintercept = value, color = name), linetype="solid", size=1, alpha=0.5)
-
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
-                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
-}
-
-```
-
-\begin{figure}[H]
-\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
-\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_concept.png}}
-\end{figure}
-
-## Figure B4 : Intercoder Agreement by Confidence {#app:agreement_by_confidence}
-\hphantom{em}
-
-```{r intercoder agreement , eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-
-fromscratch=F
-if(fromscratch){
-  raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
-                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value) %>% distinct()
-
-  temp <- codings_long_agreement %>% 
-                #Algo 1 agreement
-                filter(algo1==1) %>% 
-                #This is top 1 agreement
-                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>%                    left_join(raterconfidence) %>%
-                group_by(raterconfidence)
-
-  p_percent_chose_tag_by_confidence <- temp %>%
-    dplyr::select(percent_expert,raterconfidence) %>%
-    filter(raterconfidence!='NA') %>%
-    ggplot(aes(x=percent_expert, y=raterconfidence)) + geom_boxplot(notch=T) +
-    xlab("Percent of Coders that selected Tag") +
-    ylab("Self Reported Confidence") +
-    labs(
-      title = "Observed Intercoder Agreement by Self Reported Confidence"#,
-      #subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
-      #caption = paste0("Mean by Concept (Point); Mean by Group (Line)"), 
-      #color = "Codings"
-     ) + 
-    theme_bw() +
-    theme(legend.position="bottom")
-
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_confidence.png'), 
-                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
-}
-
-```
-
-\begin{figure}[H]
-\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
-\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_confidence.png}}
-\end{figure}
-
-# Appendix C: Recall
-\hphantom{em}
-
-## Algorithm C1: Synthetic Narratives
-\hphantom{em}
-
-A synthetic narrative is constructed as follows.
-First, compile a large corpus, $D$, of timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
-Next, segment into sentences, $s \in S$, clean, filter, and break into simpler concise sentences, $s^* \in S^*$, using a large natural language model, BART [@lewisBARTDenoisingSequencetoSequence2019], fine-tuned on summarization tasks, distilbart-cnn-12-6 [@shleiferPretrainedSummarizationDistillation2020].
-Then, calculate semantic similarity between each $S*$ by embedding them with a different large language model, MPNet [@songMPNetMaskedPermuted], fine tuned to identify paraphrasing [@reimersSentenceBERTSentenceEmbeddings2019;@reimersMakingMonolingualSentence2020].
-Next, constructed an undirected weighted graph of pair above 95th percentile cosine similarity and hierarchically cluster them into potential events $e^* \in E^*$ [@clausetFindingCommunityStructure2004].
-The resulting set of $E^*$ are small enough to check by hand, summarize, and place in chronological order.
-The relevant formulas and algorithm are shown below.
-
-Cosine Similarity
-\begin{equation}
-cosine\;similarity = \frac{a \cdot b}{ || a  ||\;|| b  || }
-\end{equation}
-
-Adjacency Matrix
-\begin{equation} \label{eq:sclrec2}
-A_{vw}= \begin{cases} 1 \text{ if vertices v and w are connected} \\ 0 \text{ otherwise } \end{cases}
-\end{equation}
-
-Identity Function
-\begin{equation}
-\delta(i,j)= \begin{cases} 1 \text{ if i=j} \\ 0 \text{ otherwise } \end{cases}
-\end{equation}
-
-Degree of a vertex
-\begin{equation}
-k_v = \sum_{w}A_{vw}
-\end{equation}
-
-Modularity - Is the difference between observed within-community edges and average expected edges on a random graph
-\begin{equation} \label{eq:sclrec2}
-Q = \frac{1}{2m}\sum_{vw}[A_{vw}-\frac{k_vk_w}{2m}]\delta(C_w,C_w)
-\end{equation}
-
-\begin{algorithm}[H]
-\SetAlgoLined
-\KwData{Document-Sentences}
-\KwResult{Event-Mentions}
-\tcc{ Embed text as a 768 dimensional semantic vector with a large language model}
-\ForEach{document in Document}{
-  \ForEach{sentence in sentence}{
-    embedding=distilbart-cnn-6-6(sentence);
-  }
-}
-
-similarity = cosine similarity(embeddings,embeddings);
-
-\tcc{ Threshold similarity matrix and create weighted undirected graph }
-
-\tcc{ Frame as adding edges so efficient nearest neighbor lookup can be used }
-
-g=EmptyUndirectedWeightedGraph();\tcc*[f]{Sparse undirected graph to store edges}
-
-\ForEach{v in 1:rows(similarity)}{
-  \ForEach{w in 1:cols(similarity)}{ 
-    \lIf{similarity[v,w]>0.96 and doc(V)!=doc(W)}{append edge v<->w to g}\tcc*[f]{If similar append as undirected edge to graph}
-  }
-}
-
-\tcc{ Community detection with greedy hierarchically clustering (Clauset et al. 2004)}
-
-gClustered=EmptyUndirectedGraph(vertices(g)); \tcc*[f]{Sparse undirected graph to store edges}
-dendrogram=list()
-\While{length(edges(g))>1}{
-
-  \ForEach{edge in edges(g)}{
-    Qpossible[edge]=Q(gClustered + edge)
-  }
-
-  \ForEach{ edge in edges(g) } {
-    \tcc{ Add the edge with the maximum increase in modularity }
-    \tcc{ Remove from original graph as a housekeeping trick }
-    \lIf{ QPossible[edge]=max(QPossible) }{ append edge to gClustered and remove edge from g; append QPossible to dendrogram }
-  }
-}
-\tcc{ Cut the dendrogram to maximize modularity and return event clusters}
-\Return dendrogram where Q(dendrogram)==max(dendrogram) \tcc*[f]{}
-\caption{Clustering and counting sentences about the same event}
-\end{algorithm}
-
-## Table C2: Synthetic Narrative Matches Cuban Missile
-\hphantom{em}
-
-<!-- Gibler's Narratives
+##  Mids plots
+
+Gibler's Narratives
 
@@
 Coding changes: End Date changed from February 26, 1962.
--->
 
@@
 
-cuba_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names()
-
-replace_emoticons_cuba <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
-        #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
-        #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
-        #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
-        #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
-}
-
-ft_cuba_recall<- cuba_recall %>% 
-                            dplyr::select(date, event, documents, icb_narrative, icbe=ic_be, icb, mids, phoenix_2)  %>%
-                            mutate(event = event %>% replace_emoticons_cuba() ) %>%
-                            flextable::as_flextable() %>%
-                            flextable::set_header_labels(values =
-                            list(
-                                  event = "Event",
-                                  documents = "Mentions",
-                                  icb_narrative = "ICB Narrative",
-                                  icbe = "ICBe",
-                                  icb = "ICB",
-                                  mids="MIDs",
-                                  phoenix_2="Phoenix"
-                                 ) ) %>%
-                            flextable::width( j = 1, width=0.25)  %>% 
-                            flextable::width( j =2, width=2.0)  %>% 
-                            flextable::width( j = 6:8, width=2.0)  %>% 
-                            flextable::fontsize(size = 7, part = "all") %>%
-                            #valign(j = 1:3, valign = "top", part = "body") %>%
-                            flextable::line_spacing( space = 1.0, part = "all") %>% 
-                            padding( padding = 1, part = "all") %>% 
-                            bg( i = which( (1:nrow(cuba_recall) %% 2)==1   ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
-                            ftExtra::colformat_md(j = 2, part="body")
-
-ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"
+mids_metro_plots <- function(crisis=196, prune_rare=T){
+
+  print(crisis)
+  #crisis=471
+  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
+  save_mids_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_mids_metro_plot_",crisis,".Rds")
+
+  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
+  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm
+
+  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
+  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple
+
+  actor_sent_counts <- icb_events_long %>%
+                       dplyr::filter(crisno==crisis  ) %>% 
+                       filter(varname_normalized %>% str_detect("actor")) %>% 
+                       dplyr::select(sent=sentence_number_int_aligned,value_normalized,value_qcode) %>% 
+                       na.omit() %>%
+                       count(value_normalized,value_qcode) %>% arrange(n %>% desc() )
+
+  dyadic_mid_clean_subset <- dyadic_mid_clean %>%
+                             filter( actor_1_qcode %in% actor_sent_counts$value_qcode & actor_2_qcode %in% actor_sent_counts$value_qcode ) %>%
+                             filter(strtyr>=year_start & endyear<=year_end) %>% arrange(strtyr, strtmnth, endday)
+  dim(dyadic_mid_clean_subset) #
+  if(nrow(dyadic_mid_clean_subset)==0 | 
+     (c(dyadic_mid_clean_subset$namea,dyadic_mid_clean_subset$nameb) %>% na.omit() %>% unique() %>%  length())<2  #Reject if not 2 actors
+     ){
+    print("No mids events for this crisis")
+    return()
+  }
+
+  dyadic_mid_clean_dyad <- 
+    bind_rows(
+      dyadic_mid_clean_subset %>% dplyr::select(year=strtyr,month=strtmnth,day=strtday, actor_1,actor_2, leaf=leaf_1) , #
+      dyadic_mid_clean_subset %>% dplyr::select(year=endyear,month=endmnth,day=endday, actor_1,actor_2, leaf=outcome_label)
+  ) %>% mutate(leaf=ifelse(leaf=="Yield by State A" , "Yield to",leaf)) %>%
+    filter(!leaf %in% "Yield by State B") %>%
+    mutate(sent= ( year+(month/12)+(day/31/1000) ) %>% rank() %>% round())
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  icb_events_subset_diad <- dyadic_mid_clean_dyad %>% dplyr::select(year, month, sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
+  #Order actors by how many interactions they have together
+  temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()
+
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
+
+  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+
+  temp_list <- list()
+  for(i in 1:nrow(temp2_wide)){
+    temp_list[[as.character(i)]] <- cutree(hc, k=i)
+  }
+
+  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
+  #  arrange(across(starts_with("V")))
+  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
+                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
+            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  names(actor_colors) = levels(actors)
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                    mutate(x=max(x)+50) %>%
+                    dplyr::select(sent, year, month,x,y) %>%
+                    na.omit() %>% 
+                    distinct() %>%  
+                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                    mutate(year_float=year+(month/12)) %>%
+                    group_by(sent) %>%
+                    filter(year_float==min(year_float)) %>%
+                    ungroup() %>% as.data.frame() %>%
+                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                    filter(!duplicated(year_float ) ) %>%
+                    mutate(label=paste0(year,"-",month.abb[month]))
+
+  ####Actor lavels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+    #rename(qcode=actor, actor=value_normalized_label) %>%
+    rowwise() %>%
+    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)
+
+  ######Directed
+  icb_events_subset_directed <- 
+            dyadic_mid_clean_dyad %>% 
+            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
+            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1)
+
+    p_mids_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Time edges
+          geom_edge_link(aes(
+                          edge_colour=actor,
+                          filter=timeedge==T
+                          ),
+                          edge_width=0.1, 
+                          show.legend = F
+                         ) +
+          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                              colour=actor,
+                              label=leaf,
+                              filter=eventedge==T #& bundle_count==1
+                              ),
+                          vjust = -0.75,
+                          lineheight = .75,
+                          sep = unit(1, 'mm'), 
+                          edge_width=0.25, 
+                          show.legend = F,
+                          arrow = arrow(length = unit(2, 'mm')),
+                          label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+
+              #Not in phoenix
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
+              #Not in phoenix
+              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #Not in phoenix
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  p_mids_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+  p_mids_metro_map$actor_colors <- actor_colors
+  p_mids_metro_map$dyadic_mid_clean <- dyadic_mid_clean
+
+  p_mids_metro_map %>% saveRDS(save_mids_file)
+}
+
+c(196, 471) %>% sapply(FUN=function(x) mids_metro_plots(x))
 
@@
 
-\begin{figure}[H]
-\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png}}
-\end{figure}
-\clearpage
+# MIDs Incidents
+
+## Load data
 
@@
 
-crimea_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names()
-
-replace_emoticons_crimea <- function(x){
-      x %>%
-            #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
-            #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
-            #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
-            #Crimea
-            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ") %>%
-            #EU
-            str_replace_all('\U0001f1EA\U0001f1FA',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q458.png) ")
-}
-
-ft_crimea_recall<- crimea_recall %>% 
-                            dplyr::select(date, event, documents=n_sources, icb_narrative, icbe=ic_be,  phoenix, terrier, icews)  %>%
-                            mutate(event = event %>% replace_emoticons_crimea() ) %>%
-                            mutate(date = date %>% as.Date()) %>%
-                            flextable::as_flextable() %>%
-                            flextable::set_header_labels(values =
-                            list(
-                                  event = "Event",
-                                  documents = "Mentions",
-                                  icb_narrative = "ICB Narrative",
-                                  icbe = "ICBe",
-                                  phoenix="Phoenix",
-                                  terrier="Terrier",
-                                  icews="ICEWS"
-                                 ) ) %>%
-                            flextable::width( j = 1, width=1.0)  %>% 
-                            flextable::width( j =2, width=2.0)  %>% 
-                            flextable::width( j = 6:8, width=2.0)  %>% 
-                            flextable::fontsize(size = 7, part = "all") %>%
-                            #valign(j = 1:3, valign = "top", part = "body") %>%
-                            flextable::line_spacing( space = 1.0, part = "all") %>% 
-                            padding( padding = 1, part = "all") %>% 
-                            bg( i = which( (1:nrow(crimea_recall) %% 2)==1   ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
-                            ftExtra::colformat_md(j = 2, part="body")
-
-ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"
+mid_df <- data.frame(
+  stringsAsFactors = FALSE,
+               act = c(1L,2L,3L,4L,5L,6L,7L,8L,
+                       9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
+                       20L,21L,22L),
+         act_label = c("1. None (1)",
+                       "2. Threat to use force (2)","3. Threat to blockade (2)",
+                       "4. Threat to occupy terr. (2)","5. Threat to declare war (2)",
+                       "6. Threat to join war (2)","7. Show of troops (3)",
+                       "8. Show of ships (3)","9. Show of planes (3)","10. Alert (3)",
+                       "12. Mobilization (3)","13. Fortify border (3)",
+                       "14. Border violation (4)","15. Blockade (4)",
+                       "16. Occupation of territory (4)","17. Seizure (4)","18. Clash (4)",
+                       "19. Raid (4)","20. Declaration of war (4)",
+                       "22. Begin interstate war (5)","23. Join interstate war (5)",
+                       "24. Use CBR Weapons (5)") 
+) %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') %>% trimws() )
+
+mid_df2 <- data.frame(
+  stringsAsFactors = FALSE,
+                outcome = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
+                outcome_label = c("0. Ongoing MID",
+                       "1. Victory for State A","2. Victory for state B",
+                       "3. Yield by State A","4. Yield by State B","5. Stalemate",
+                       "6. Compromise","7. Released (for seizures)","8. Unclear",
+                       "-9 Missing")
+) %>% mutate(outcome_label= outcome_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
+
+mid_df3 <- data.frame(
+  stringsAsFactors = FALSE,
+          revtype1 = c(0L, 1L, 2L, 3L, 4L),
+    revtype1_label = c("Not applicable","Territory",
+                       "Policy","Regime/government","Other")
+)
+
+mid_df4 <- data.frame(
+  stringsAsFactors = FALSE,
+          fatality = c(0L, 1L, 2L, 3L, 4L, 5L, 6L),
+    fatality_label = c("None","1-25 deaths",
+                       "26-100 deaths","101-250 deaths","251-500 deaths",
+                       "501-999 deaths","> 999 deaths")
+)
+
+midii <- readRDS(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.Rds'))
+midip <- readRDS(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.Rds'))
+
+midip_clean <- midip %>% distinct() %>%
+                      left_join(actor_translator %>% dplyr::select(ccode=COWcode, actor=QCode_name, actor_qcode=QCode)) %>%
+                      left_join(mid_df  %>% dplyr::select( action=act , act_label=act_label )) %>%
+                      left_join(mid_df3  %>% dplyr::select( revtype1=revtype1 , revtype1_label=revtype1_label ))  %>%
+                      left_join(mid_df4  %>% dplyr::select( fatality=fatality , fatality_label=fatality_label ))
+
+#Create a dyadic list
+temp1 <- midip_clean %>% 
+         mutate(start=styear+((stmon*30)+stday)/365) %>%
+         mutate(end=endyear+((endmon*30)+endday)/365) %>%
+         dplyr::select(stday, stmon, styear, endday, start, end, incidnum, sidea, actor, actor_qcode,
+                       act_label,revtype1_label,fatality_label) %>% arrange(incidnum, sidea, actor_qcode) %>% distinct()
+temp2 <- temp1 %>% dplyr::select(stday, stmon, styear, endday, 
+                                 start, end,incidnum, sidea_1=sidea, actor_1=actor, actor_1_qcode=actor_qcode,act_1_label=act_label,
+                                 revtype1_1_label=revtype1_label,fatality_1_label=fatality_label) %>%
+          full_join(temp1 %>% dplyr::select(start, end,incidnum, sidea_2=sidea, actor_2=actor, actor_2_qcode=actor_qcode,act_2_label=act_label,revtype1_2_label=revtype1_label,fatality_2_label=fatality_label
+                                            )) %>%
+          filter(sidea_1!=sidea_2) %>%
+          mutate(actor_12_qcode=paste0(actor_1_qcode, "_", actor_2_qcode))
+temp3 <- temp1 %>% dplyr::select(start, end,incidnum, sidea_1=sidea, actor_1=actor, actor_1_qcode=actor_qcode,
+                                 act_1_label=act_label,revtype1_1_label=revtype1_label,fatality_1_label=fatality_label) %>%
+          full_join(temp1 %>% dplyr::select(start, end,incidnum, sidea_2=sidea, actor_2=actor, actor_2_qcode=actor_qcode,act_2_label=act_label,revtype1_2_label=revtype1_label,fatality_2_label=fatality_label)) %>%
+          filter(sidea_1!=sidea_2) %>%
+          mutate(actor_12_qcode=paste0(actor_2_qcode, "_", actor_1_qcode))
+
+midip_dyads <- bind_rows(temp2, temp3)
 
@@
 
-\begin{figure}[H]
-\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png}}
-\end{figure}
-\clearpage
-
-## Table C3: Synthetic Narrative Matches Crimea-Donbas
-\hphantom{em}
-
-# Appendix D: Precision
-
-\hphantom{em}
-
-\clearpage
-
-## Figure D1 Crimea-Donbos 
-\hphantom{em}
-
-```{r crimea case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
-#Move this to the appendix
-
-#<!-- Rex remember that sentence 19 broken and cuts off 
-#"Ukraine’s major response to its crisis was verbal and began on 27 February, when it sent a note to Russia demanding that Russian troops stay on base in Crimea, called for #calm, and discussed the" -->
-
-#Loaded above now 
-#ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
-fromscratch=F
-if(fromscratch){
-  temp <- ICBe_events_agreed_markdown %>%
-          filter(crisno==471) %>%
-          group_by(crisno, sentence_number_int_aligned) %>%
-            filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
-          ungroup() %>%
-          mutate(banding=sentence_number_int_aligned %% 2)
-  temp$is_subsstring <- NA
-  for(i in 1:nrow(temp)){
-    temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
-                                                                                  pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
-                                                                                ) %>% replace_na(0) %>%  sum()
-  }
-  temp <-temp %>%
-          mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
-          group_by(sentence_number_int_aligned) %>%
-            filter(value_markdown!='' | length(value_markdown)==1) %>%
-          ungroup() %>%
-          mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
-          mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
-          mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
-        #head(100) %>%
-
-  ft_crimea_precision_part1 <- temp %>% 
-                              dplyr::select(S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
-                              filter(row_number()<=61) %>%
-                              flextable::as_flextable() %>%
-                              flextable::width( j = 1, width=0.25)  %>% 
-                              #flextable::width( j = 2, width=0.25)  %>% 
-                              flextable::width( j = 2, width=8.0)  %>% 
-                              flextable::width( j = 3, width=4.0)  %>% 
-                              flextable::fontsize(size = 9, part = "all") %>%
-                              valign(j = 1:3, valign = "top", part = "body") %>%
-                              flextable::line_spacing( space = 1.0, part = "all") %>% 
-                              padding( padding = 1, part = "all") %>% 
-                              bg( i = which( temp$banding[1:61]==1 ) , part = "body", bg = "#EFEFEF", j=1:3) %>%
-                              ftExtra::colformat_md(j = 3, part="body")
-  #ft_cuba_precision
-
-  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"
-
-  ft_crimea_precision_part2 <- temp %>%
-                        dplyr::select(S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
-                          filter(row_number()>=62  ) %>%
-                        flextable::as_flextable() %>%
-                        flextable::width( j = 1, width=0.25)  %>% 
-                        #flextable::width( j = 2, width=0.25)  %>% 
-                        flextable::width( j = 2, width=8.0)  %>% 
-                        flextable::width( j = 3, width=4.0)  %>% 
-                        flextable::fontsize(size = 9, part = "all") %>%
-                        valign(j = 1:3, valign = "top", part = "body") %>%
-                        flextable::line_spacing( space = 1.0, part = "all") %>% 
-                        padding( padding = 1, part = "all") %>% 
-                        bg( i = which( temp$banding[62:111]==1 ) , part = "body", bg = "#EFEFEF", j=1:3) %>%
-                        ftExtra::colformat_md(j = 3, part="body")
-  #ft_cuba_precision
-
-  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"
-
-  temp <- NULL
-
-}
+## Plot
+
+```{r}
+
+mids_incidents_metro_plots <- function(crisis=196, prune_rare=T){
+
+  print(crisis)
+  #crisis=471
+  save_mids_incidents_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_mids_incidents_metro_plot_",crisis,".Rds")
+
+  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
+  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm
+
+  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
+  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple
+
+  dyad_sent_counts <- 
+    bind_rows(
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor_1_qcode=say_actor_a, actor_2_qcode=say_actor_b),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor_1_qcode=do_actor_a, actor_2_qcode=do_actor_b)
+   )   %>% distinct() %>% na.omit()  %>% 
+        mutate(actor_1_qcode = strsplit(as.character(actor_1_qcode), ";")) %>% unnest(actor_1_qcode) %>% distinct() %>%
+        mutate(actor_2_qcode = strsplit(as.character(actor_2_qcode), ";")) %>% unnest(actor_2_qcode) %>% distinct() %>% 
+        count(actor_1_qcode , actor_2_qcode) %>% arrange(desc(n))  %>%
+          mutate(actor_12_qcode=paste0(actor_1_qcode, "_", actor_2_qcode))
+
+  #What mids involve those dyads?
+  relevant_incidnum <- midip_dyads %>% filter(actor_12_qcode %in% dyad_sent_counts$actor_12_qcode) %>% pull(incidnum) %>% unique()
+
+  actor_sent_counts <- 
+    bind_rows(
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+      ) %>% 
+        na.omit() %>%
+        mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+  #Subset incients to be within the time frame and the right incidents and the right actors
+  incident_mid_clean_subset <- midip_dyads %>%
+                               filter( incidnum %in% relevant_incidnum ) %>% #a dispute with a relvant dyad
+                               filter( actor_12_qcode %in% dyad_sent_counts$actor_12_qcode ) %>% #an actor in our data
+                               filter(start>=year_start & end<=year_end+1) #allow for an extra year at the end
+
+  #Reject if no rows or less than 2 actors
+  dim(incident_mid_clean_subset) #
+  if(nrow(incident_mid_clean_subset)==0 | 
+     (c(incident_mid_clean_subset$actor_1,incident_mid_clean_subset$actor_2) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
+     ){
+    print("No mids events for this crisis")
+    return()
+  }
+
+  #we can do pseudo dyads within incidum numbers
+
+  dyadic_mid_clean_dyad <- 
+    bind_rows(
+      incident_mid_clean_subset %>% 
+        mutate(label=
+                 paste0( act_1_label %>% tidyr::replace_na(''),", ", revtype1_2_label %>% tidyr::replace_na('') ,", ", fatality_1_label %>% tidyr::replace_na('')) %>% trimws() %>%
+                 str_replace_all("None|Not applicable","") %>% trimws() %>% str_replace("^,|,$|","") %>% trimws()
+               ) %>%
+        dplyr::select(stday, stmon, styear, endday, start,   end, start, actor_1=actor_1,actor_2=actor_2, leaf=label) 
+  ) %>%
+    mutate(sent= start %>% rank() %>% round())
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  icb_events_subset_diad <- dyadic_mid_clean_dyad %>% dplyr::select(styear, stmon, sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
+  #Order actors by how many interactions they have together
+  temp <- icb_events_subset_diad  %>% dplyr::select(-styear, -stmon) %>% arrange(actor_1, actor_2) %>% distinct()
+
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
+
+  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+
+  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
+  #  arrange(across(starts_with("V")))
+  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(styear, stmon, sent=sent, actor=actor_1) ,
+                      icb_events_subset_diad %>% dplyr::select(styear, stmon, sent=sent, actor=actor_2) 
+            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  names(actor_colors) = levels(actors)
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                    mutate(x=max(x)+50) %>%
+                    dplyr::select(sent, point_in_time_year=styear, point_in_time_month=stmon,x,y) %>%
+                    na.omit() %>% 
+                    distinct() %>%  
+                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                    mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                    group_by(sent) %>%
+                    filter(year_float==min(year_float)) %>%
+                    ungroup() %>% as.data.frame() %>%
+                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                    filter(!duplicated(year_float ) ) %>%
+                    mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+  ####Actor levels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+    #rename(qcode=actor, actor=value_normalized_label) %>%
+    rowwise() %>%
+    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)
+
+  ######Directed
+  icb_events_subset_directed <- 
+            dyadic_mid_clean_dyad %>% 
+            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
+            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1)
+
+    p_mids_incident_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Time edges
+          geom_edge_link(aes(
+                          edge_colour=actor,
+                          filter=timeedge==T
+                          ),
+                          edge_width=0.1, 
+                          show.legend = F
+                         ) +
+          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                              colour=actor,
+                              label=leaf,
+                              filter=eventedge==T #& bundle_count==1
+                              ),
+                          vjust = -0.75,
+                          lineheight = .75,
+                          sep = unit(1, 'mm'), 
+                          edge_width=0.25, 
+                          show.legend = F,
+                          arrow = arrow(length = unit(2, 'mm')),
+                          label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+
+              #Not in phoenix
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
+              #Not in phoenix
+              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #Not in phoenix
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  p_mids_incident_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+  p_mids_incident_metro_map$actor_colors <- actor_colors
+  p_mids_incident_metro_map$incident_mid_clean_subset <- incident_mid_clean_subset
+
+  p_mids_incident_metro_map %>% saveRDS(save_mids_incidents_file)
+}
+
+icb_crises %>% filter(yrtrig>=1990 & crisno %in% c(196, 471)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) mids_incidents_metro_plots(x))
+
 ```
 
-\begin{figure}[H]
-\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png}}
-\end{figure}
-\clearpage
-
-\begin{figure}[H]
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png}}
-\end{figure}
-\clearpage
-
-## Table D2: Stratified Sentence Examples
-
-\hphantom{em}
-\begin{figure}[H]
-\caption{ Stratified Sentence Examples  \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_sample_precision_precision.png"}}
-\end{figure}
-\clearpage
-
-## Figure D3 Crisis Maps Cuban Missiles
-
-\hphantom{em}
-
-```{r crisis maps common functions, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
-global_check_overlap=F
-library(igraph)
-library(RColorBrewer)
-library(ggraph)
+# GED
+
+## Data Loads
+
+```{r}
+
+df1 <- data.frame(
+        stringsAsFactors = FALSE,
+        type_of_violence = c(1L, 2L, 3L),
+                               type_of_violence_label = c("state-based conflict","non-state conflict","one-sided violence")
+)
+
+load(paste0(here::here(), "/replication_paper/data/in/GEDEvent_v21_1.RData"))
+ged211 <- GEDEvent_v21_1
+
+#ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged211.csv"))
+
 target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
-dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
-                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
-
-actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
-                                sheet="actor_translator") #%>% janitor::clean_names() 
-#Convert to a local file for pushing
-#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
-pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
-library(pals); #install.packages('pals')
-pallet <- pals::glasbey()
-pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
-library(colorspace)
-#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
-pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
-actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
-
-crisno_name_years <- icb_crises %>% dplyr::select(crisno, crisname, yrtrig, yrterm)
-
-CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cccc') %>% janitor::clean_names()
+actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
+
+ged211_clean <- ged211 %>%
+                left_join(actor_translator %>% dplyr::select(side_a_new_id=UCDPcode,actor_1=QCode_name, actor_1_qcode=QCode) ) %>%
+                left_join(actor_translator %>% dplyr::select(side_b_new_id=UCDPcode,actor_2=QCode_name, actor_2_qcode=QCode) ) %>%
+                filter(!is.na(actor_1_qcode) & !is.na(actor_2_qcode)) %>%
+                mutate(actor_12_qcode=paste0(actor_1_qcode,"_",actor_2_qcode)) %>%
+                dplyr::select(-source_office, -source_date, -source_headline, -source_original)
+
+#There's only 11 that overlap
+#Q1009_Q1033   Q148_Q668   Q424_Q869   Q668_Q843   Q736_Q419   Q794_Q801   Q796_Q817    Q804_Q30  Q958_Q1049   Q977_Q986   Q986_Q115 
+#          9           2          24        1049          26          67          80           2          27           2          34
+
+```
+
+## Ged Plots
+
+```{r}
+
+ucdp_ged_metro_plots <- function(crisis=466, prune_rare=T){
+
+    print(crisis)
+    #crisis=471
+    save_ucdp_incidents_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_ucdp_metro_plot_",crisis,".Rds")
+
+    year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
+    year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm
+
+    start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
+    end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple
+
+    dyad_sent_counts <- 
+      bind_rows(
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor_1_qcode=say_actor_a, actor_2_qcode=say_actor_b),
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor_1_qcode=do_actor_a, actor_2_qcode=do_actor_b)
+     )   %>% distinct() %>% na.omit()  %>% 
+          mutate(actor_1_qcode = strsplit(as.character(actor_1_qcode), ";")) %>% unnest(actor_1_qcode) %>% distinct() %>%
+          mutate(actor_2_qcode = strsplit(as.character(actor_2_qcode), ";")) %>% unnest(actor_2_qcode) %>% distinct() %>% 
+          count(actor_1_qcode , actor_2_qcode) %>% arrange(desc(n))  %>%
+            mutate(actor_12_qcode=paste0(actor_1_qcode, "_", actor_2_qcode))
+
+    actor_sent_counts <- 
+      bind_rows(
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
+          icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+        ) %>% 
+          na.omit() %>%
+          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+    #Subset incients to be within the time frame and the right incidents and the right actors
+    incident_ucdp_clean_subset <- ged211_clean %>%
+                                   filter( actor_12_qcode %in% dyad_sent_counts$actor_12_qcode ) %>% #an actor in our data
+                                   filter(year>=year_start & year<=year_end) #allow for an extra year at the end
+
+  #Reject if no rows or less than 2 actors
+  dim(incident_ucdp_clean_subset) #
+  if(nrow(incident_ucdp_clean_subset)==0 | 
+     (c(incident_ucdp_clean_subset$actor_1,incident_ucdp_clean_subset$actor_2) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
+     ){
+    print("No mids events for this crisis")
+    return()
+  }
+
+  #we can do pseudo dyads within incidum numbers
+  dyadic_ucdp_clean_dyad <- 
+    bind_rows(
+
+      #A killed B
+      incident_ucdp_clean_subset %>% 
+        filter(gwnob==country_id) %>% #happened in B
+        mutate(label= paste0( best, " deaths"  ) %>% trimws()  ) %>% dplyr::select(date_start, actor_1=actor_1,actor_2=actor_2, leaf=label),
+      #B killed A
+      incident_ucdp_clean_subset %>% 
+        filter(gwnoa==country_id) %>% #happened in A
+        mutate(label= paste0( best, " deaths"  ) %>% trimws()  ) %>% dplyr::select(date_start, actor_1=actor_2,actor_2=actor_1, leaf=label)
+
+  ) %>% distinct() %>%
+    mutate(sent= date_start %>% rank() %>% round())
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  icb_events_subset_diad <- dyadic_ucdp_clean_dyad %>% dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
+  #Order actors by how many interactions they have together
+  temp <- icb_events_subset_diad  %>% arrange(actor_1, actor_2) %>% distinct()
+
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
+
+  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+
+  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
+  #  arrange(across(starts_with("V")))
+  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent=sent, actor=actor_1) ,
+                      icb_events_subset_diad %>% dplyr::select(sent=sent, actor=actor_2) 
+            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  names(actor_colors) = levels(actors)
+
+  ####Actor levels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+    #rename(qcode=actor, actor=value_normalized_label) %>%
+    rowwise() %>%
+    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)
+
+  ######Directed
+  icb_events_subset_directed <- 
+            dyadic_ucdp_clean_dyad %>% 
+            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
+            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1)
+
+    p_ucdp_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Time edges
+          geom_edge_link(aes(
+                          edge_colour=actor,
+                          filter=timeedge==T
+                          ),
+                          edge_width=0.1, 
+                          show.legend = F
+                         ) +
+          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                              colour=actor,
+                              label=leaf,
+                              filter=eventedge==T #& bundle_count==1
+                              ),
+                          vjust = -0.75,
+                          lineheight = .75,
+                          sep = unit(1, 'mm'), 
+                          edge_width=0.25, 
+                          show.legend = F,
+                          arrow = arrow(length = unit(2, 'mm')),
+                          label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+
+              #Not in phoenix
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
+              #Not in phoenix
+              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #Not in phoenix
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  p_ucdp_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+  p_ucdp_metro_map$actor_colors <- actor_colors
+  p_ucdp_metro_map$incident_ucdp_clean_subset <- incident_ucdp_clean_subset
+
+  p_ucdp_metro_map %>% saveRDS(save_ucdp_incidents_file)
+}
+
+icb_crises %>% filter(yrtrig>=1989 & crisno %in% c(196, 471) ) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) ucdp_ged_metro_plots(x))
+
+```
+
+# Cameo Systems
+
+```{r}
+
+CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()
+
+cameo_code_rejects <- c('Make statement, not specified below', 'Consult, not specified below','Praise or endorse','Accuse, not specified below',
+                        'Make statement, not specified below','Meet at a third location','Consult, not specified below')
+
+#Comment to not reject
+role_rejects <- c(
+  "Agriculture-focused actors",
+  "Business (NOT MNCs)",
+  "Civilians",
+  "Criminal actors",
+  "Development-focused actors" ,
+  "Education-focused actors",
+  "Elites, celebrities",
+  "Environment-focused actors",
+  #"Government",
+  "Health-focused actors",
+  "Human rights-focused actors",
+  #"Intelligence agencies",
+  "Judicial actors",
+  "Labor-focused actors",
+  "Law enforcement agencies",
+  "Legislative bodies/actors",
+  "Media-related actors/organizations",
+  #"Military",
+  #"Opposition groups (often parliamentary)" ,
+  #"Political party",
+  #"Radical/extremist/fundamentalist",
+  #"Rebels/insurgents",
+  "Refugee-focused actors" #,
+  #"Unaffiliated armed forces"  
+)
 
@@
   )
+
+  # "AIRSTRIKE,1"                 "AIRSTRIKE,2"                
+  # "ASSASSINATION,1"                      "BIOLOGICAL_WEAPONS,1"                  "CHEMICAL_WEAPONS,1"          "CHEMICAL_WEAPONS,2"         
+  # "COUP_DISCUSSION,1"           "CYBER_SECURITY,1"               "DRONE,1"                    
+  # "EARLY_CHILDHOOD_EDUCATION,1" "ECONOMIC_MOVEMENT,1"         "ELECTION,1"                 
+  # "ELECTION,2"                    "EUROPEAN_UNION,1"            "EUROPEAN_UNION,2"              "FOREIGN_AID,1"                    
+  # "HUMAN_RIGHTS,1"              "HUMAN_RIGHTS,2"              "HUMAN_RIGHTS,3"              "ID_ARMS_DEAL,1"              "ID_ATROCITY,1"               "ID_ATROCITY,2"               "ID_DEMOCRACY,1"              "ID_DEMOCRACY,2"
+  # "ID_EXTREMISM,1"              "ID_EXTREMISM,2"              "ID_IMMIGRATION,1"            "ID_IMMIGRATION,2"            "ID_JIHAD,1"                  "ID_JIHAD,2"                  "ID_JIHAD,3"                  "ID_PROLIFERATION,1"
+  # "ID_SMUGGLING,1"              "ID_TORTURE,1"                "IED,1"                            "NAMED_TERROR_GROUP,1"        "NAMED_TERROR_GROUP,2"        "NATIONAL_MOVEMENT,1"         "NATURAL_DISASTER,1"          "NATURAL_DISASTER,2"   # "NATURAL_GAS,1"               "NEW_CONSTRUCTION,1"
+  # "NUCLEAR_ENERGY,1"            "NUCLEAR_ENERGY,2"            "NUCLEAR_WEAPONS,1"           "NUCLEAR_WEAPONS,2"           "NUCLEAR_WEAPONS,3"           "OIL,1"                            "PEACEKEEPERS,1"
+  # "POLITICAL_PRISONER,1"        "POLITICAL_PRISONER,2"                 
+  # "RETALIATION,1"               "SANCTIONS,1"                 "SANCTIONS,2"                      "SECURITY_SERVICES,1"         "SECURITY_SERVICES,2"        
+  # "SUICIDE_ATTACK,1"           
+  # "TERROR,1"                    "TERROR,2"                    "TOURISM,1"                   "TOURISM,2"                               "VIOLENT_UNREST,1"            "WATER_SECURITY,1"            "WMD,1"
+
+#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt")) %>% janitor::clean_names()
 
@@
 
-```{r ICB Data Loads , eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-#ICB Data Loads
-
-#Note yemen 679 doesn't show up in this data
-icb_df <- data.frame(
-  stringsAsFactors = FALSE,
-          icb_name = c("Afghanistan","Albania",
-                       "Algeria","Andorra","Angola","Antigua & Barbuda",
-                       "Argentina","Armenia","Australia","Austria","Azerbaijan",
-                       "Bahamas","Bahrain","Bangladesh","Barbados","Belarus",
-                       "Belgium","Belize","Benin (Dahomey)","Bhutan","Bolivia",
-                       "Bosnia","Botswana","Brazil","Brunei","Bulgaria",
-                       "Burkina Faso (Upper Volta)","Burma (see Myanmar)",
-                       "Burundi","Cambodia","Cameroon","Canada","Cape Verde",
-                       "Central African Republic","Chad","Chile","China",
-                       "China","Colombia","Comoros","Congo Brazzaville",
-                       "Congo, Democratic","Costa Rica","Cote D’Ivoire","Croatia",
-                       "Cuba","Cyprus","Czech Republic","Czechoslovakia",
-                       "Dahomey (see Benin)","Denmark","Djibouti (Somalia Fr.)",
-                       "Dominica","Dominican Republic","Ecuador","Egypt (UAR)",
-                       "El Salvador","Equatorial Guinea","Eritrea","Estonia",
-                       "Ethiopia","Federated States of Micronesia","Fiji",
-                       "Finland","Formosa","France","French West Africa",
-                       "Gabon","Gambia","Georgia",
-                       "German Democratic Republic (East Germany)",
-                       "Germany (German Federal Republic, West Germany)","Germany (Prussia)","Ghana",
-                       "Great Britain (see United Kingdom)","Greece","Grenada","Guatemala",
-                       "Guinea","Guinea Bissau","Guyana","Haiti","Hijaz (Hejaz)",
-                       "Honduras","Hungary","Iceland","India","Indonesia",
-                       "Iran","Iraq","Ireland (Eire)","Israel","Italy",
-                       "Ivory Coast (see Cote D’Ivoire)","Jamaica","Japan",
-                       "Jordan","Kazakhstan","Kenya","Korea","Kosovo","Kuwait",
-                       "Kyrgyz Republic","Laos","Latvia","Lebanon","Lesotho",
-                       "Liberia","Libya","Liechtenstein","Lithuania",
-                       "Luxemberg","Macedonia","Madagascar (Malagasy Republic)",
-                       "Malawi","Malaysia","Maldives","Mali","Malta",
-                       "Marshall Islands","Mauritania","Mauritius","Mexico","Moldova",
-                       "Monaco","Mongolia","Morocco","Mozambique",
-                       "Myanmar (Burma)","Najd (Nejd)","Namibia (South West Africa)",
-                       "Nepal","Netherlands","Nevis","New Zealand",
-                       "Nicaragua","Niger","Nigeria",
-                       "North Korea (People’s Republic of Korea)","Norway","Oman","Pakistan","Palau","Panama",
-                       "Papua and New Guinea","Paraguay","Peru",
-                       "Philippines","Poland","Portugal","Principe","Qatar",
-                       "Republic of (Congo Kinshasa) (Zaire)","Rhodesia (see Zimbabwe)",
-                       "Rumania","Russia (Soviet Union)","Rwanda",
-                       "San Marino","Sao Tome","Saudi Arabia","Senegal",
-                       "Serbia (see Yugoslavia)","Seychelles","Sierra Leone","Singapore",
-                       "Slovakia","Slovenia","Solomons","Somalia",
-                       "Somalia Fr. (see Djibouti)","South Africa",
-                       "South Korea (Republic of Korea)","South Sudan",
-                       "South West Africa (see Namibia)","Spain","Spanish Sahara (see Western Sahara)",
-                       "Sri Lanka (Ceylon)","St. Kitts","St. Lucia",
-                       "St. Vincent & The Grenadines","Sudan","Surinam","Swaziland",
-                       "Sweden","Switzerland","Syria","Taiwan (China",
-                       "Tajikistan","Tanzania","Thailand","Tibet","Togo",
-                       "Trinidad & Tobago","Tunisia","Turkey","Turkmenistan","Uganda",
-                       "Ukraine","United Arab Emirates",
-                       "United Kingdom (Great Britain)","Upper Volta (see Burkina Faso)","Uruguay",
-                       "USA","USSR (see Russia)","Uzbekistan","Vanuatu",
-                       "Venezuela","Vichy France",
-                       "Vietnam, Democratic Republic of (North Vietnam)","Vietnam, Republic of (South Vietnam)",
-                       "Western Sahara (Spanish Sahara)","Western Samoa",
-                       "Yemen (Arab Republic of Yemen, North Yemen)",
-                       "Yemen, People’s Republic of (South Yemen)","Yugoslavia (Serbia)",
-                       "Zambia","Zanzibar","Zimbabwe (Rhodesia)"),
-       icb_letters = c("AFG","ALB","ALG","AND",
-                       "ANG","AAB","ARG","ARM","AUL","AUS","AZE","BHM",
-                       "BAH","BNG","BAR","BLR","BEL","BLZ","BEN","BHU","BOL",
-                       "BOS","BOT","BRA","BRU","BUL","BFO",NA,"BUI",
-                       "CAM","CAO","CAN","CAP","CEN","CHA","CHL",NA,"CHN",
-                       "COL","COM","CON","DRC","COS","CDI","CRO","CUB",
-                       "CYP","CZR","CZE",NA,"DEN","DJI","DMA","DOM",
-                       "ECU","EGY","SAL","EQG","ERI","EST","ETH","FSM","FIJ",
-                       "FIN","TAW","FRN","FWA","GAB","GAM","GRG","GDR",
-                       "GFR","GMY","GHA",NA,"GRC","GRN","GUA","GUI",
-                       "GNB","GUY","HAI","HIJ","HON","HUN","ICE","IND",
-                       "INS","IRN","IRQ","IRE","ISR","ITA",NA,"JAM","JPN",
-                       "JOR","KZK","KEN","KOR","KOS","KUW","KYR","LAO",
-                       "LAT","LEB","LES","LBR","LIB","LIE","LIT","LUX",
-                       "MAC","MAG","MAW","MAL","MAD","MLI","MLT","MSI",
-                       "MAA","MAS","MEX","MLD","MNC","MON","MOR","MZM","MYA",
-                       "NAJ","NAM","NEP","NTH","SKN","NEW","NIC","NIR",
-                       "NIG","PRK","NOR","OMA","PAK","PAL","PAN","PNG",
-                       "PAR","PER","PHI","POL","POR","STP","QAT","DRC",
-                       NA,"RUM","RUS","RWA","SNM",NA,"SAU","SEN",NA,
-                       "SEY","SIE","SIN","SLO","SLV","SOL","SOM",NA,"SAF",
-                       "ROK","SSD",NA,"SPN",NA,"SRI",NA,"SLU","SVG",
-                       "SUD","SUR","SWA","SWD","SWZ","SYR",NA,"TAJ","TAZ",
-                       "THI","TBT","TOG","TRI","TUN","TUR","TKM","UGA",
-                       "UKR","UAE","UKG",NA,"URU","USA",NA,"UZB","VAN",
-                       "VEN","VFR","DRV","RVN","SPA","WSM","YEM","YPR",
-                       "YUG","ZAM","ZAN","ZIM"),
-          icb_code = c("700","339","615","232",
-                       "540","058","160","371","900","305","373","031",
-                       "692","771","053","370","211","080","434","760","145",
-                       "346","571","140","835","355","439",NA,"516",
-                       "811","471","020","402","482","483","155",NA,"710",
-                       "100","581","484","490","094","437","344","040",
-                       "352","316","315",NA,"390","522","054","042",
-                       "130","651","092","411","531","366","530","987","950",
-                       "375","713","220","480","481","420","372","265",
-                       "260","255","452",NA,"350","55","090","438",
-                       "404","110","041","671","091","310","395","750","850",
-                       "630","645","205","666","325",NA,"051","740",
-                       "663","705","501","730","347","690","703","812",
-                       "367","660","570","450","620","223","368","212",
-                       "343","580","553","820","781","432","338","983","435",
-                       "590","070","359","221","712","600","541","775",
-                       "672","565","790","210","060","920","093","436",
-                       "475","731","385","698","770","986","095","910",
-                       "150","135","840","290","235","403","694","490",NA,
-                       "360","365","517","331",NA,"670","433",NA,"591",
-                       "451","830","317","349","940","520",NA,"560",
-                       "732","626",NA,"230",NA,"780",NA,"056","057","625",
-                       "115","572","380","225","652",NA,"702","510",
-                       "800","711","461","052","616","640","701","500",
-                       "369","696","200",NA,"165","002",NA,"704","935",
-                       "101","219","816","817","605","990","678","680",
-                       "345","551","511","552")
+## ICEWS
+
+### Data Loads
+
+```{r}
+
+kill_sectors <- c(
+'Police,Government',
+'Social,Media',
+'Government,Judicial',
+'Media,Social',
+'Judicial,Government',
+'Dissident,Criminals / Gangs',
+'Criminals / Gangs,Dissident',
+'Social,Legal',
+'Legal,Social',
+'Social,Business',
+'Business,Social',
+'Social,Education',
+'Education,Social',
+'Social,Labor',
+'Labor,Social',
+'Local,Provincial,Government',
+'Social,National Religious',
+'National Religious,Social',
+'Local,Government,Provincial',
+'Government,Finance / Economy / Commerce / Trade Ministry,Executive',
+'Executive,Interior / Home Ministry,Government',
+'Medical / Health NGOs,Nongovernmental Organizations / Activists',
+'Government,Interior / Home Ministry,Executive',
+'Social,Media,News',
+'Social,Agricultural',
+'Social,News,Media',
+'News,Media,Social',
+'Media,News,Social',
+'Social,Medical / Health',
+'Medical / Health,Social',
+'Ideological,Center Left,Executive,Parties,(National) Major Party,Executive Office,Government',
+'Social,Refugees / Displaced',
+'Agricultural,Social',
+'Ideological,Center Left,Parties,(National) Major Party',
+'Dissident,Nongovernmental Organization (International),Parties,(National) Major Party',
+'Parties,(National) Major Party,Center Left,Ideological',
+'Refugees / Displaced,Social',
+'Dissident,Exiles',
+'Party',
+'Parties',
+"General Population",
+"^Elite$"
 )
-
-df_IWCA <- data.frame(
-  stringsAsFactors = FALSE,
-              IWCA = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L, 10L),
-        IWCA_label = c("not an intra-war crisis (IWC)",
-                       "Entry of a major actor into an ongoing war",
-                       "Perceived high probability of a major actor entering a war",
-                       "Exit of a major actor",
-                       "Perceived high probability of major power exiting a war",
-                       "Technological escalation of a war","Major non-technological escalation",
-                       "Defeat in a significant battle","Internal deterioration","Other")
-)
-
-df_break <- 
-data.frame(
-  stringsAsFactors = FALSE,
-             BREAK = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
-       BREAK_label = c("Verbal act","Political act",
-                       "Economic act","External change",
-                       "Other non-violent act",
-                       "Internal verbal or physical challenge to regime or elite","Non-violent military act","Indirect violent act",
-                       "Violent act")
-)
-
-#icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")
-icbdy_20 <- readRDS(paste0(here::here(), '/replication_paper/data/in/icbdy_20.Rds'))
-
-icbdy_20_clean <- icbdy_20 %>%
-                  left_join( icb_df %>% dplyr::select(STATEA=icb_code, actor_1=icb_name ) %>% mutate(STATEA=STATEA %>% as.numeric())  ) %>%
-                  left_join( icb_df %>% dplyr::select(STATEB=icb_code, actor_2=icb_name ) %>% mutate(STATEB=STATEB %>% as.numeric())  ) %>%
-                  left_join(df_IWCA %>% dplyr::select(IWCA=IWCA, IWCA_label=IWCA_label )  ) %>%
-                  left_join(df_IWCA %>% dplyr::select(IWCB=IWCA, IWCB_label=IWCA_label )  )
-
-icb_diadic <- icbdy_20_clean %>% dplyr::select(CRISNO, NAMEA, NAMEB,  STATEA, STATEB, actor_1,actor_2, IWCA_label,IWCB_label) #%>% filter(is.na(actor_1) | is.na(actor_2))
-
-icb2v14 <- read_csv(paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))
-
-df_trigger <- data.frame(
-  stringsAsFactors = FALSE,
-            triggr = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
-                    triggr_label = c("Verbal act","Political act","Economic act",
-                                     "External change","Other non-violent act",
-                                     "Internal verbal or physical challenge to regime or elite",
-                                     "Non-violent military act","Indirect violent act","Violent act")
-              )
-
-df_majres <- data.frame(
-  stringsAsFactors = FALSE,
-            majres = c(1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
-                   majres_label = c("No response-inaction","Verbal act",
-                                    "Political act","Economic act",
-                                    "Other non-violent act",
-                                    "Non-violent military act",
-                                    "Multiple including non-violent military act",
-                                    "Violent military act",
-                                    "Multiple including violent military act")
-             )
-
-df_outcome <- 
-data.frame(
-  stringsAsFactors = FALSE,
-            outcom = c(1L, 2L, 3L, 4L, 5L),
-      outcom_label = c("Victory", "Compromise", "Stalemate", "Defeat", "Other")
-)
-
-df_outfor <- 
-data.frame(
-  stringsAsFactors = FALSE,
-            outfor = c(1L,2L,3L,4L,5L,6L,7L,8L,
-                       9L,10L,11L,12L,13L,14L,15L),
-      outfor_label = c("Formal agreement - voluntary",
-                       "Semi-formal agreement - voluntary",
-                       "Tacit understanding","Unilateral - self","Unilateral - ally",
-                       "Unilateral - adversary","Compliance","Imposed - imposer",
-                       "Imposed - imposee","Spillover",
-                       "Other - global organization intervention","Other - ally",
-                       "Other - internal or non-state actor","Other - misc.","Faded")
-)
-
-icb2v14_clean <- icb2v14 %>% 
-                 left_join(icb_df %>% dplyr::select(cracid=icb_code, actor_label=icb_name ) %>% mutate(cracid=cracid %>% as.numeric()) ) %>%  #you can't actually match on the letter codes you have to match on the numbers, uhhhhhg
-                 left_join( df_trigger  ) %>% 
-                 left_join( df_majres ) %>% 
-                 left_join( df_outcome ) %>% 
-                 left_join( df_outfor )
-
-icb_monadic <-  
+kill_sectors_regex <- paste0(kill_sectors, collapse="|")
+
+if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"))){
+  stop("Missing 'UCDP Georeferenced Event Dataset (GED)'. See README.")
+}
+
+CAMEO_eventcodes <- read_tsv(paste0(here::here(),"/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
+actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
+
+fromscratch=F
+if(fromscratch){
+  #accidentally loaded the pdfs
+  files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T, pattern = ".tab$|.tsv$")
+  icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x, show_col_types = FALSE) )  ) %>% janitor::clean_names() %>% distinct()
+  dim(icews) #18,403,260 #15,751,586
+
+  codes_used <-icews %>% count(cameo_code)
+
+  actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
+  #%>% mutate(icews=ifelse(ICEWS_Country=="International Government Organizations", ICEWS_Actor.Name, ICEWS_Country))
+
+  #Going to heavily filter on source sectors and source name
+  #c(icews$source_sectors,icews$source_name) %>% table()
+
+  #This doesn't totally work because India has 3 copies.
+The lower thing gets a different q code than the higher thing, so we first have to try to match on the lower, and if that fails match on the higher kinda
+  #Indian Administered Kashmir		India
+
+  dim(icews) #18,403,260 #15,751,586
+  icews_clean <- icews %>% 
+                 #filter(event_id==20776790) %>% 
+                 #head(1000) %>%
+                 mutate_if(is.character, na_if, "null") %>%
+                 mutate_if(is.character, na_if, "NULL") %>%
+                 #head(1000) %>%
+                 mutate(where = coalesce(city, district,province)) %>%
+                 left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code) %>% mutate(cameo_label=cameo_label %>% tolower() ) # %>%  #You have 
+                           # dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  
+                         )  %>%
+                #This requires either the source country to be in the actors list
+                #Temporarily disable
+                filter(source_country %in% na.omit(actor_translator$ICEWS_Country) | source_name %in% na.omit(actor_translator$ICEWS_Actor.Name) | 
+                       target_country %in% na.omit(actor_translator$ICEWS_Actor.Name) |  target_name %in% na.omit(actor_translator$ICEWS_Actor.Name) ) %>%
+
+                #filter(target_country %in% na.omit(actor_translator$ICEWS_Country) | target_name %in% na.omit(actor_translator$ICEWS_Actor.Name) ) %>% #ommitting this for now
+                #filter(!source_sectors %>% str_detect(kill_sectors_regex)) %>% #try to remember why we filter this
+                #filter(!target_sectors %>% str_detect(kill_sectors_regex)) %>%
+                #Just apply the wikidata actor labels
+                #mutate(source=ifelse(is.na(source_country) , source_name, source_country)) %>%
+                #mutate(target=ifelse(is.na(target_country) ,target_name , target_country)) %>%
+                left_join( actor_translator_icews %>% dplyr::select(source_name=ICEWS_Actor.Name,  source_q_code_actor=QCode, source_q_label_actor=QCode_name) %>% 
+                             distinct() %>% na.omit() ) %>%
+                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% 
+                             dplyr::select(source_country=ICEWS_Country,  source_q_code_country=QCode, source_q_label_country=QCode_name) %>% 
+                             distinct() %>% na.omit() ) %>%
+                mutate(source_q_code=ifelse(!is.na(source_q_code_actor) , source_q_code_actor, source_q_code_country)) %>%
+                mutate(source_label=ifelse(!is.na(source_q_code_actor) , source_q_label_actor, source_q_label_country)) %>%
+
+                left_join( actor_translator_icews %>% dplyr::select(target_name=ICEWS_Actor.Name,  target_q_code_actor=QCode, target_q_label_actor=QCode_name) %>% 
+                             distinct() %>% na.omit() ) %>%
+                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% 
+                             dplyr::select(target_country=ICEWS_Country,  target_q_code_country=QCode, target_q_label_country=QCode_name) %>%
+                             distinct() %>% na.omit() ) %>%
+                mutate(target_q_code=ifelse(!is.na(target_q_code_actor) , target_q_code_actor, target_q_code_country)) %>%
+                mutate(target_label=ifelse(!is.na(target_q_code_actor) , target_q_label_actor, target_q_label_country)) %>%
+
+                mutate(source_target_q_code= paste0(source_q_code,"_",target_q_code)) %>%
+
+                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(country=ICEWS_Country,  country_q_code=QCode) %>% distinct() %>% na.omit() ) %>%
+                mutate(year = event_date %>% lubridate::year()  )  %>%
+                mutate(month = event_date %>% lubridate::month()  )  %>%
+                mutate(day = event_date %>% lubridate::day()  )  %>%
+                mutate(month_label = lubridate::month(month %>% as.numeric(),label=TRUE,abbr=F)) %>%
+                mutate(source_sectors = source_sectors %>% tolower()) %>%
+                mutate(target_sectors = target_sectors %>% tolower()) %>%
+                mutate(cameo_label = cameo_label %>% str_replace(", not specified below","") ) %>%
+                mutate(who_a = coalesce(source_name,source_sectors %>% tolower(), source_label ) ) %>%
+                mutate(who_b = coalesce(target_name,target_sectors %>% tolower(), target_label ) ) %>%
+                mutate(who_a = ifelse(who_a %in% source_country, NA, who_a)) %>%
+                mutate(who_b = ifelse(who_b %in% target_country, NA, who_b)) %>%
+                unite(text, 
+                      source_country,who_a,  
+                      cameo_label, 
+                      who_b, target_country, sep=" ", remove = F, na.rm = T) %>%
+                mutate(text = ifelse(!is.na(where),paste0(text, " in ", where),text) ) %>% 
+                mutate(text = paste0("On ", month_label, " ",day," ",year, ", ", text))
+
+    dim(icews_clean) #17,541,701 #1,965,573 it's still too many but it's just close enough now #1,965,573
+
+    icews_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "in", "icews_clean.parquet") )
+}
+#done
+#install.packages("arrow")
+icews_clean <-  arrow::read_parquet(here::here("replication_paper", "data", "in", "icews_clean.parquet") )
+
+icews_clean %>% count(source_country) %>% dim() #233
+icews_clean %>% count(source_country, source_sectors) %>% dim() #404673
+icews_clean %>% count(source_country, source_sectors, source_name) %>% dim() #569374
+icews_clean %>% count(cameo_label) %>% dim() #272
+
+dim(icews_clean) #17,541,701
+library(dplyr)
+library(digest)
+keep_list <- c("Ukraine", "Russia","Russian Federation", 'North Atlantic Treaty Organization', 'NATO', 'European Union', 'Crimea','Donbas','Donetsk', 'Luhansk' ) #, 'United Nations'
+keep_list <- c(keep_list, keep_list %>% tolower())
+icews_clean_471 <- icews_clean %>% 
+                   filter( event_date>= as.Date("2013-01-01") & event_date<= as.Date("2015-12-31") ) %>%
+                   unite(temp_all, everything()) %>%
+                   filter( temp_all %>% str_detect(paste0(keep_list,collapse="|"))) %>%
+                   dplyr::select(-temp_all)
+dim(icews_clean_471) #281,427
+
+icews_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")
+
+icews_clean_471 %>%
+  unite('actors_left' , source_country, source_label, source_name, source_sectors,  sep=" ", , na.rm =T, remove=F) %>%
+  unite('actors_right', target_country, target_label, target_name, target_sectors, sep=" ", , na.rm =T, remove=F) %>%
+  dplyr::select(event_id, year, month, day, actors_left, actors_right,cameo_event_label=cameo_label, text ) %>% 
+  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")
+
+```
+
+### Plots
+
+```{r}
+
+icews_metro_plots <- function(crisis=471, topactor=F, exclude='', savefile=NULL){
+
+  print(crisis)
+  #crisis=471
+  #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
+  #save_icews_file = paste0(here::here(), "/replication_paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
+  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
+  if(is.null(savefile)){
+    savefile <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
+    extract_savefile <- paste0(here::here(), "/replication_paper/data/out/dataset_extracts/extract_icews_",crisis,".tsv")
+  }
+
+  date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
+  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-01")) #, "-28" #damn it the day is what got me if the month-day pair is imposible
+  date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()
+
+  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
+  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm
+
+  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
+  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple
+
+  actor_sent_counts <- 
     bind_rows(
-   icb2v14_clean%>% mutate(sent= yrtrig + tidyr::replace_na((motrig/12),0) + tidyr::replace_na(datrig/31/12,0) ) %>% mutate(type='start') %>% dplyr::select(year=yrtrig, month=motrig, crisno,type, sent, actor_label, leaf=triggr_label),
-   icb2v14_clean %>% mutate(sent= yerres + tidyr::replace_na((monres/12),0) + tidyr::replace_na(dayres/31/12,0) ) %>% mutate(type='mid') %>% dplyr::select(year=yerres, month=monres, crisno,type, sent, actor_label, leaf=majres_label),
-   icb2v14_clean %>% mutate(sent= yrterm + tidyr::replace_na((moterm/12),0) + tidyr::replace_na(daterm/31/12,0) ) %>% mutate(type='end') %>% dplyr::select(year=yrterm, month=moterm, crisno,type, sent, actor_label, leaf=outfor_label)
-  ) %>% as.data.frame()
-
-```
-
-```{r icb crisis maps, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
-library(igraph)
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
+        icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+      ) %>% 
+        na.omit() %>%
+        mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+  #Only consider diads that appear in our data
+  qcodes <- icb_events_long %>% dplyr::filter(crisno==crisis & varname_normalized %>% str_detect('actor') & value_normalized!='') %>% pull(value_qcode) %>% unique() %>% na.omit()
+  actors_translator <- actor_translator %>% filter(QCode %in% qcodes ) %>% janitor::clean_names() %>%
+                       mutate(icews_actor = ifelse(icews_country %in% "International Government Organizations", icews_actor_name,icews_country))
+
+  to_qcode <-   icb_events_long %>%
+                   dplyr::filter(crisno==crisis  ) %>% 
+                   filter(varname_normalized %>% str_detect("actor")) %>% 
+                   dplyr::select(value_normalized,value_qcode) %>% 
+                   na.omit() %>% distinct()
+
+  if(nrow(actors_translator)<2 ){
+    print("Not enough actors")
+    return()
+  }
+
+  diads_qcodes <- bind_rows(
+                  icb_events %>% dplyr::filter(crisno==crisis  ) %>% 
+                    dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
+                  icb_events %>% dplyr::filter(crisno==crisis  ) %>% 
+                    dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% filter(is.na(say_actor_a)) %>% 
+                    dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
+                  ) %>% 
+                  mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a, keep_empty =T) %>%
+                  mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b, keep_empty =T) %>%
+                  na.omit() %>% 
+                  distinct() %>%
+                  left_join(to_qcode %>% dplyr::select(actor_a=value_normalized, actor_a_qcode=value_qcode) ) %>%
+                  left_join(to_qcode %>% dplyr::select(actor_b=value_normalized, actor_b_qcode=value_qcode) )  %>%
+
+                  left_join(actors_translator %>% dplyr::select(actor_a=q_code, source_q_code=q_code_name) ) %>% #source_sectors
+                  left_join(actors_translator %>% dplyr::select(actor_b=q_code, target_q_code=q_code_name) )  %>%  #target_sectors
+                  mutate(source_target_actor=paste0(actor_a, "_", actor_b) ) %>%
+                  mutate(source_target_q_code= paste0(actor_a_qcode,"_",actor_b_qcode)) %>%
+
+                  filter(actor_a!=actor_b) #Decide to exclude when the target is the same as the source
+
+  #phoenix_clean$joined_issues %>% unique()
+  #install.packages('parsedate')
+  library(parsedate)
+
+  #Ok the IOs are just NA
+  #icews_clean_actors_source <- icews_clean %>% dplyr::select(source_name, source_sectors, source_country) %>% count(source_name, source_sectors, source_country)
+  #icews_clean_actors_target <- icews_clean %>% dplyr::select(target_name, target_sectors, target_country) %>% count(target_name, target_sectors, target_country)
+
+  icews_clean_subset <- icews_clean %>%
+
+                        mutate(source_target_actor=paste0(source_q_code, "_", target_q_code) ) %>%
+                        filter(
+                              event_date>=date_start & #Require it to be between the dates of the crisis
+                              event_date<=date_end  &
+                              source_target_q_code %in% diads_qcodes$source_target_q_code #require it to be between actors in ICBe  
+                              ) %>%
+                        mutate(country_valid = is.na(country_q_code) | (country_q_code %in% c(diads_qcodes$actor_a_qcode, diads_qcodes$actor_b_qcode) ) )  %>%
+                        filter(country_valid==T) %>%
+                        filter(! cameo_label %in%  cameo_code_rejects) %>% #reject thost common but worthless event types
+                       #
+                       dplyr::select(event_date,
+                                     source_target_actor,
+                                     source_label,
+                                     target_label,
+
+                                     source_name,
+                                     source_sectors,
+                                     source_country,
+                                     source_q_code,
+
+                                     target_name,
+                                     target_sectors,
+                                     target_country,
+                                     target_q_code,
+                                     #same_target_source,
+                                     #code, root_code, 
+                                     cameo_label, 
+                                     country,
+                                     country_q_code
+                                     #cameo_event_root_label,
+                                     #joined_issues,placename, countryname, joined_issues, process
+                                     ) %>%
+                       distinct() %>%
+                       mutate(year = event_date %>% lubridate::year()  )  %>%
+                       mutate(month = event_date %>% lubridate::month()  )  %>%
+                       mutate(day = event_date %>% lubridate::day()  ) %>%
+                       arrange(year,month, day) %>%
+                       mutate(sent= year*10000+month*100+day   )  %>% 
+                       mutate(sent= as.factor(sent - min(sent, na.rm=T) + 1) %>% as.numeric()  )  %>%
+                       mutate(crisno=crisis)
+                       #filter(!source_label %in% exclude) %>%
+                       #filter(!target_label %in% exclude) #I'm not sure why but I wanted to kill some specific countries before
+
+  icews_clean_subset %>%  write_tsv(extract_savefile)
+
+  icews_clean_subset %>%
+    count(year, month, source_label,target_label,cameo_label) %>%
+    write_tsv(paste0(here::here(), "/replication_paper/data/out/dataset_extracts/extract_count_icews_",crisis,".tsv"))
+
+  #For crises with too many events we subset it to just dyadic events with
+  notes <- NULL
+  if(topactor & nrow(icews_clean_subset)>100){
+    diads_qcodes <- diads_qcodes %>% filter(actor_a== actor_sent_counts$actor[1] | actor_b==actor_sent_counts$actor[1]) #
+    icews_clean_subset <- icews_clean_subset %>% filter( source_target_actor %in% diads_qcodes$source_target_actor )
+    notes <- "Note: Showing only dyadic events with top actor"
+  }
+
+  #This has to come after
+  #dim(icews_clean_subset) #11,092
+  if(nrow(icews_clean_subset)==0 | 
+     (c(icews_clean_subset$source_label,icews_clean_subset$target_label) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
+     ){
+    print("No ICEWs events for this crisis")
+    return()
+  }
+
   library(ggraph)
-#ICB Function {Plots
-icb_crisismaps <- function(thiscrisis=196, prune_rare=T){
-
-    print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icb_metro_plot_",thiscrisis,".Rds")
-
-    icb_diadic_subset <- icb_diadic %>% filter(CRISNO==thiscrisis) #Not all of them are diadic apparently
-    icb_monadic_subset <- icb_monadic %>% rename(actor=actor_label) %>% filter(crisno==thiscrisis) %>%
-                       mutate(sent=sent %>% rank() %>% round()) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") ))   %>% arrange(sent, actor)
+  library(RColorBrewer)
 
@@
 
-    icb_events_subset_diad <- bind_rows(
-            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>% 
-                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>%
-              rename(actor_2=actor_1,actor_1=actor_2),
-            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="start") %>%
-                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),
-
-            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>%
-                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>%
-              rename(actor_2=actor_1,actor_1=actor_2),
-            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="mid") %>% 
-                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),
-
-            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
-                                                                                 mutate(actor_1=actor) %>% dplyr::select(year, month,sent, actor_1,leaf) ) %>%
-              rename(actor_2=actor_1,actor_1=actor_2),
-            icb_diadic_subset %>% dplyr::select(actor_1,actor_2) %>% left_join(icb_monadic_subset %>% filter(type=="end") %>% 
-                                                                                 mutate(actor_2=actor) %>% dplyr::select(year, month,sent, actor_2,leaf) ),
-
-          ) %>% dplyr::select(year, month,sent, actor_1, actor_2, leaf) %>% distinct() %>% na.omit()
-
-     if(nrow(icb_events_subset_diad)==0){
-      print("No dyadic icb rows skipping")
-      return()
-    }
-
+  icb_events_subset_diad <- icews_clean_subset %>% 
+                                     dplyr::select(year, month, sent=sent, actor_1=source_label, actor_2=target_label, cameo_event_label=cameo_label ) %>% distinct() %>%
+                                     mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below','') %>% tolower() )  
   #Order actors by how many interactions they have together
-    temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()
+  temp <- icb_events_subset_diad  %>% dplyr::select(-cameo_event_label, -year, -month) %>% arrange(actor_1, actor_2) %>% distinct()
 
@@
 
-    temp_list <- list()
-    for(i in 1:nrow(temp2_wide)){
-      temp_list[[as.character(i)]] <- cutree(hc, k=i)
-    }
-
   #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
@@
   ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+  #If we're down to one actor we're going to put it in the center and then put other nearby
+  if(topactor & nrow(icews_clean_subset)>100){
+    ideal_ordering <- c(icb_events_subset_diad$actor_1, icb_events_subset_diad$actor_2) %>% table() %>% sort() %>% names() %>% rev()
+    ideal_ordering <- c(ideal_ordering[c(F,T)] %>% rev(), ideal_ordering[c(T,F)])
+  }
 
@@
                    y=sent*-1 *100)
-
-    #we centralize everything in qcodes so colors should be consistent across plots for the same actors    
-    icbe_actor_to_qcode <- icb_events_long %>%
-                       dplyr::filter(crisno==thiscrisis  ) %>% 
-                       filter(varname_normalized %>% str_detect("actor")) %>% 
-                       dplyr::select(value_normalized,value_qcode) %>% 
-                       na.omit() %>% distinct()
-
-    actor_colors_df <- icbe_actor_to_qcode %>%
-      left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
-    actor_colors <- actor_colors_df$actor_color
-    names(actor_colors) = actor_colors_df$value_normalized
 
@@
 
-    ####Actor levels
+  ####Actor lavels
   icb_events_subset_nodes_min <- 
     icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
-                  #left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
     #rename(qcode=actor, actor=value_normalized_label) %>%
@@
   #####Time Edges
-    icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% 
-      janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
 
@@
        add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                   actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F,
+                 bundle_count=1)
 
@@
   icb_events_subset_directed <- 
-              icb_events_subset_diad %>% 
-              dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
+            icews_clean_subset %>% 
+            dplyr::select(sent=sent, actor_1=source_label, actor_2=target_label, cameo_event_label=cameo_label ) %>% distinct() %>%
+            mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below',''))  %>% na.omit()  %>% distinct() %>% 
+            mutate(leaf = cameo_event_label %>% tolower() )  %>% 
             mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
             mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-              group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
-                summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
+            mutate(actor1_actor2= actor_1 %>% paste0("_", actor_2)) %>%
+            arrange(actor1_actor2, sent) %>%
+
+            group_by(sent,actor1_actor2, actor_1, actor_2, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) %>%
+            arrange(actor1_actor2,sent) %>%
+            group_by(actor1_actor2) %>%
+              mutate(leaf_dupe=leaf==lag(leaf)) %>%
+              mutate(sent_gap= sent - lag(sent)  ) %>%
+            ungroup()
             #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  icb_events_subset_directed <- icb_events_subset_directed  %>% 
+                                         filter(!( leaf_dupe %in% T & !is.na(sent_gap) & sent_gap<=31)) %>% #reject the same kind of event within a directed diad that occures again within 31 days back to back
+                                         group_by(sent, leaf) %>%
+                                             mutate(bundle_count=n()) %>%
+                                             mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
+                                          ungroup() #%>% 
+          #filter(bundle_count>1)
+  #dim(icb_events_subset_directed) #1826 bundled
 
@@
                        timeedge=F, 
-                         leaf=icb_events_subset_directed$leaf, 
+                       leaf=icb_events_subset_directed$leaf2, 
                        eventedge=T,
-                         actor=icb_events_subset_directed$actor_1)
-
-    p_icb_metro_map <- g %>%  
+                       actor=icb_events_subset_directed$actor_1,
+                       bundle_count=icb_events_subset_directed$bundle_count
+                       )
+
+  ######Put it all together
+  p_icews_metro_map <- g %>%  
           ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
@@
                               label=leaf,
-                              filter=eventedge==T #& bundle_count==1
+                              filter=eventedge==T & bundle_count==1
                               ),
@@
                           label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+              #Grouped Edges
+              geom_edge_parallel(aes(  
+                                  colour=actor,
+                                  label=leaf,
+                                  filter=eventedge==T & bundle_count>1
+                                  ),
+                              vjust = -0.75,
+                              lineheight = .75,
+                              sep = unit(5, 'mm'), 
+                              edge_width=0.4,  #0.25
+                              show.legend = F,
+                              arrow = arrow(length = unit(1, 'mm')),
+                              label_size=4,
                               check_overlap=global_check_overlap,
@@
 
-      p_icb_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
-      p_icb_metro_map$actor_colors <- actor_colors
-      p_icb_metro_map$icb_monadic_subset <- icb_monadic_subset
-
-      p_icb_metro_map %>% saveRDS(save_icb_file)
-
-}
-
-c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x))
+  if(!is.null(notes)){
+     p_icews_metro_map <- p_icews_metro_map + labs(caption = notes)
+  }
+
+  p_icews_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+  p_icews_metro_map$actor_colors <- actor_colors
+  p_icews_metro_map$icews_clean_subset <- icews_clean_subset
+
+  p_icews_metro_map  %>% saveRDS(savefile)
+
+}
+
+icb_crises %>% filter(yrtrig>=1995  & crisno %in% c(196, 471)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) icews_metro_plots(x))
 
@@
 
-```{r mids data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-mid4_df <- data.frame(
-  stringsAsFactors = FALSE,
-               act = c(1L,2L,3L,4L,5L,6L,7L,8L,
-                       9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
-                       20L,21L,22L),
-         act_label = c("1. None (1)",
-                       "2. Threat to use force (2)",
-                       "3. Threat to blockade (2)",
-                       "4. Threat to occupy terr. (2)",
-                       "5. Threat to declare war (2)",
-                       "6. Threat to join war (2)",
-                       "7. Show of troops (3)",
-                       "8. Show of ships (3)",
-                       "9. Show of planes (3)",
-                       "10. Alert (3)",
-                       "12. Mobilization (3)",
-                       "13. Fortify border (3)",
-                       "14. Border violation (4)",
-                       "15. Blockade (4)",
-                       "16. Occupation of territory (4)",
-                       "17. Seizure (4)",
-                       "18. Clash (4)",
-                       "19. Raid (4)",
-                       "20. Declaration of war (4)",
-                       "22. Begin interstate war (5)",
-                       "23. Join interstate war (5)",
-                       "24. Use CBR Weapons (5)")
-) %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
-
-mid_df <- data.frame(
-  stringsAsFactors = FALSE,
-               act = c(0L,1L,2L,3L,4L,5L,6L,7L,
-                       8L,9L,10L,11L,12L,13L,14L,15L,16L,17L,18L,19L,
-                       20L,21L),
-         act_label = c("No militarized action (1)",
-                       "Threat to use force (2)","Threat to blockade (2)",
-                       "Threat to occupy terr. (2)","Threat to declare war (2)",
-                       "Threat to use CBR weapons","Threat to join war (2)",
-                       "Show of force (3)","Alert (3)","Nuclear alert (3)",
-                       "Mobilization (3)","Fortify border (3)","Border violation (4)",
-                       "Blockade (4)","Occupation of territory (4)",
-                       "Seizure (4)","Attack (4)","Clash (4)","Declaration of war (4)",
-                       "Use of CBR weapons (4)","Begin interstate war (5)",
-                       "Join interstate war (5)")
-)  %>% mutate(act_label= act_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
-
-mid_df2 <- data.frame(
-  stringsAsFactors = FALSE,
-                outcome = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L),
-                outcome_label = c("0. Ongoing MID",
-                       "1. Victory for State A","2. Victory for state B",
-                       "3. Yield by State A","4. Yield by State B","5. Stalemate",
-                       "6. Compromise","7. Released (for seizures)","8. Unclear",
-                       "-9 Missing")
-) %>% mutate(outcome_label= outcome_label %>% str_replace('[0-9]{1,2}\\. ','') %>% str_replace('\\([1-9]\\)','') )
-
-dyadic_mid <- read_csv(paste0(here::here(), "/replication_paper/data/in/dyadic_mid_4.02.csv"))
-
-dyadic_mid_clean <- dyadic_mid %>% distinct() %>%
-                      left_join(actor_translator %>% dplyr::select(statea=COWcode, actor_1=QCode_name, actor_1_qcode=QCode)) %>% #I think we add color here
-                      left_join(actor_translator %>% dplyr::select(stateb=COWcode, actor_2=QCode_name, actor_2_qcode=QCode)) %>%
-                      left_join(mid_df  %>% dplyr::select( mid5hiacta=act , leaf_1=act_label )) %>%
-                      left_join(mid_df  %>% dplyr::select( mid5hiactb=act , leaf_2=act_label )) %>%
-                      left_join(mid_df2  %>% dplyr::select( outcome=outcome , outcome_label=outcome_label ))
-
-```
-
-```{r mids crisismaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F }
-
-mids_crisismaps <- function(thiscrisis=196, prune_rare=T){
-
-  print(thiscrisis)
-  #thiscrisis=471
-  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_mids_metro_plot_",thiscrisis,".Rds")
-
-  year_start <-icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
-  year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm
-
-  start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
-  end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple
-
-  actor_sent_counts <- icb_events_long %>%
-                       dplyr::filter(crisno==thiscrisis  ) %>% 
-                       filter(varname_normalized %>% str_detect("actor")) %>% 
-                       dplyr::select(sent=sentence_number_int_aligned,value_normalized,value_qcode) %>% 
-                       na.omit() %>%
-                       count(value_normalized,value_qcode) %>% arrange(n %>% desc() )
-
-  dyadic_mid_clean_subset <- dyadic_mid_clean %>%
-                             filter( actor_1_qcode %in% actor_sent_counts$value_qcode & actor_2_qcode %in% actor_sent_counts$value_qcode ) %>%
-                             filter(strtyr>=year_start & endyear<=year_end) %>% arrange(strtyr, strtmnth, endday)
-  dim(dyadic_mid_clean_subset) #
-  if(nrow(dyadic_mid_clean_subset)==0 | 
-     (c(dyadic_mid_clean_subset$namea,dyadic_mid_clean_subset$nameb) %>% na.omit() %>% unique() %>%  length())<2  #Reject if not 2 actors
-     ){
-    print("No mids events for this crisis")
-    return()
-  }
-
-  dyadic_mid_clean_dyad <- 
-    bind_rows(
-      dyadic_mid_clean_subset %>% dplyr::select(year=strtyr,month=strtmnth,day=strtday, actor_1,actor_2, leaf=leaf_1) , #
-      dyadic_mid_clean_subset %>% dplyr::select(year=endyear,month=endmnth,day=endday, actor_1,actor_2, leaf=outcome_label)
-  ) %>% mutate(leaf=ifelse(leaf=="Yield by State A" , "Yield to",leaf)) %>%
-    filter(!leaf %in% "Yield by State B") %>%
-    mutate(sent= ( year+(month/12)+(day/31/1000) ) %>% rank() %>% round())
-
-  g <- make_empty_graph(n = 0, directed = TRUE)
-    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
-
-  icb_events_subset_diad <- dyadic_mid_clean_dyad %>% dplyr::select(year, month, sent=sent, actor_1=actor_1, actor_2=actor_2 ) %>% distinct()
-  #Order actors by how many interactions they have together
-  temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month) %>% arrange(actor_1, actor_2) %>% distinct()
-
-  temp2 <- bind_rows(
-    temp,
-    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
-  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
-
-  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
-  rownames(temp2_wide) <- temp2_wide$actor_1
-  temp2_wide$actor_1 <- NULL
-  temp2_wide <- temp2_wide %>% as.matrix()
-  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
-  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
-  hc <- hclust(temp2_wide %>% as.dist(), method="single")
-
-  temp_list <- list()
-  for(i in 1:nrow(temp2_wide)){
-    temp_list[[as.character(i)]] <- cutree(hc, k=i)
-  }
-
-  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
-  #  arrange(across(starts_with("V")))
-  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
-
-  #####Nodes
-  icb_events_subset_nodes <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
-                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
-            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
-            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
-                   y=sent*-1 *100)
-
-  #we centralize everything in qcodes so colors should be consistent across plots for the same actors    
-  icbe_actor_to_qcode <- icb_events_long %>%
-                     dplyr::filter(crisno==thiscrisis  ) %>% 
-                     filter(varname_normalized %>% str_detect("actor")) %>% 
-                     dplyr::select(value_normalized,value_qcode) %>% 
-                     na.omit() %>% distinct()
-
-  actor_colors_df <- icbe_actor_to_qcode %>%
-    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
-  actor_colors <- actor_colors_df$actor_color
-  names(actor_colors) = actor_colors_df$value_normalized
-
-  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
-  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
-  names(actor_colors) = levels(actors)
-
-  date_sineposts <- icb_events_subset_nodes  %>%
-                    mutate(x=max(x)+50) %>%
-                    dplyr::select(sent, year, month,x,y) %>%
-                    na.omit() %>% 
-                    distinct() %>%  
-                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
-                    mutate(year_float=year+(month/12)) %>%
-                    group_by(sent) %>%
-                    filter(year_float==min(year_float)) %>%
-                    ungroup() %>% as.data.frame() %>%
-                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
-                    filter(!duplicated(year_float ) ) %>%
-                    mutate(label=paste0(year,"-",month.abb[month]))
-
-  ####Actor lavels
-  icb_events_subset_nodes_min <- 
-    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
-    rowwise() %>%
-    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
-
-  for(i in 1:nrow(icb_events_subset_nodes)){
-    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
-                                actor = icb_events_subset_nodes$actor[i], 
-                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
-  }
-
-  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
-
-  #####Time Edges
-  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
-
-  g <- g %>% 
-       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F)
-
-  ######Directed
-  icb_events_subset_directed <- 
-            dyadic_mid_clean_dyad %>% 
-            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, leaf ) %>% distinct() %>%
-            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
-              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) #%>%
-            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
-
-  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                       timeedge=F, 
-                       leaf=icb_events_subset_directed$leaf, 
-                       eventedge=T,
-                       actor=icb_events_subset_directed$actor_1)
-
-    p_mids_metro_map <- g %>%  
-          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
-
-          #Time edges
-          geom_edge_link(aes(
-                          edge_colour=actor,
-                          filter=timeedge==T
-                          ),
-                          edge_width=0.1, 
-                          show.legend = F
-                         ) +
-          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
-
-          #Event edges
-          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
-          geom_edge_arc(aes(  
-                              colour=actor,
-                              label=leaf,
-                              filter=eventedge==T #& bundle_count==1
-                              ),
-                          vjust = -0.75,
-                          lineheight = .75,
-                          sep = unit(1, 'mm'), 
-                          edge_width=0.25, 
-                          show.legend = F,
-                          arrow = arrow(length = unit(2, 'mm')),
-                          label_size=3,
-                          check_overlap=global_check_overlap,
-                          start_cap = circle(3, 'mm'),
-                          end_cap = circle(3, 'mm'),
-                          angle_calc = 'along'
-                         ) +
-
-              #Not in phoenix
-              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
-              #Not in phoenix
-              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
-              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
-              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
-              scale_color_manual(values = actor_colors)  +
-              scale_edge_color_manual(values = actor_colors) +
-              #theme_bw() + 
-              #labs( title = plot_title ) +
-              theme_graph() +
-              theme(legend.position = "none") #+
-              #Not in phoenix
-              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
-
-  p_mids_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
-  p_mids_metro_map$actor_colors <- actor_colors
-  p_mids_metro_map$dyadic_mid_clean <- dyadic_mid_clean
-
-  p_mids_metro_map %>% saveRDS(save_mids_file)
-}
-
-c(196, 471) %>% sapply(FUN=function(x) mids_crisismaps(x))
-
-```
-
-```{r phoenix data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F,}
-#[@althausClineCenterHistorical2020a]
-#https://databank.illinois.edu/datasets/IDB-2796521
+## Phoenix
+
+https://databank.illinois.edu/datasets/IDB-2796521
+
+### Data Loads
+
+```{r}
 
@@
 
-  root_codes <- phoenix$root_code %>% unique()
-
-  #library("remotes")
-  #remotes::install_github("andybega/icews")
-  library(icews)
-  data("cameo_codes") #we're going to grab the cameo codes from the ICEWS package because they're a nightmare
-  cameo_codes_goldstein <- cameo_codes %>% left_join(goldstein_mappings) %>% mutate(name=name %>% tolower())
-
   phoenix_clean <- phoenix %>% 
                    #head(10000) %>%
-                   left_join(cameo_codes_goldstein %>% dplyr::select(code=cameo_code , cameo_event_label=name,
-                                                                     cameo_penta_category=penta_category, cameo_quad_category=quad_category, 
-                                                                     cameo_goldstein=goldstein, cameo_lvl0=lvl0 ) ) %>%
-                   left_join(    cameo_codes_goldstein %>% filter(level==0) %>% dplyr::select(cameo_lvl0=lvl0, cameo_lvl0_label=name)) %>% #
-                   #
+                   #filter(source_root!='' & target_root!='') %>%
                    left_join(cameo_actor_codes %>% dplyr::select(source=code, source_label=name)  )  %>%
@@
 
+                   #mutate(code=code %>% str_pad(4, pad = "0") %>% str_replace("0{1,3}","0")) %>%
+                   #mutate(root_code=root_code %>% str_pad(2, pad = "0") %>% str_replace("0{1,3}","0")) %>%
+
+                   left_join(CAMEO_eventcodes %>% dplyr::select(code=cameo_code     , cameo_event_label=cameo_label) ) %>%
+
+                   left_join(CAMEO_eventcodes %>% dplyr::select(root_code=cameo_code, cameo_event_root_label=cameo_label) %>% filter(nchar(root_code)==2)) %>%
+
                    mutate(joined_issues=ifelse( joined_issues=='',";", joined_issues)  ) %>% #Apparently unnesting an empty string just gets dropped
                    mutate(joined_issues = strsplit(as.character(joined_issues), ";") ) %>%  unnest(joined_issues)  %>% #This drops if the row is missing, I did not know that was it
-                   #
+
+                   distinct() %>%
+                   #filter(
+                   #   !source_others_label %in% role_rejects &
+                   #    !target_others_label %in% role_rejects &
+                   #    !source_agent_label %in% role_rejects &
+                   #    !target_agent_label %in% role_rejects 
+                   #) %>%
+                   #Just apply the actor labels
                    left_join(actor_translator %>% dplyr::select(source_root=phoenix_2020, source_root_label=QCode_name, source_root_qcode=QCode) %>% distinct() %>% na.omit() ) %>%
                    left_join(actor_translator %>% dplyr::select(target_root=phoenix_2020, target_root_label=QCode_name, target_root_qcode=QCode) %>% distinct() %>% na.omit() ) %>%
+                   mutate(cameo_event_label = cameo_event_label %>% str_replace("Meet at a ÒhirdÓlocation","Meet at a third location")) %>% #I don't know why but this is broken so sub it out
                    mutate(month_label = lubridate::month(month %>% as.numeric(),label=TRUE,abbr=F)) %>%
+                   mutate(cameo_label = cameo_event_label %>% tolower() ) %>%
                    mutate(source_agent_label = source_agent_label %>% tolower()) %>%
@@
                           source_root_label, source_agent_label, source_others1_label, source_others2_label, source_others3_label,
-                          cameo_event_label, 
+                          cameo_label, 
                           target_agent_label, target_root_label, target_others1_label, target_others2_label, target_others3_label, 
@@
   dim(phoenix_clean) #8,495,402 #3,721,110 #2,813,748 #2912035 #3,508,495 #4,854,787
-  phoenix_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") )
+  phoenix_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "in", "phoenix_clean.parquet") )
+}
+phoenix_clean <- arrow::read_parquet(here::here("replication_paper", "data", "in", "phoenix_clean.parquet") )
 
@@
 
-}
-
 ```
 
-```{r phoenix_barmaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(readr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-
-phoenix_barmaps <- function(thiscrisis=196, topactor=F){
-
-    print(thiscrisis)
-    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_",thiscrisis,".Rds")
-
-    date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==thiscrisis,]$motrig, "-01"))
-    date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrterm , "-", icb_crises[icb_crises$crisno==thiscrisis,]$moterm, "-01"))
+### Plot
+
+[@althausClineCenterHistorical2020a]
+
+```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
+
+phoenix_metro_plots <- function(crisis=196, topactor=F){
+
+  print(crisis)
+  #crisis=471
+  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
+  save_phoenix_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_phoenix_metro_plot_",crisis,".Rds")
+
+  date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
+  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-01"))
   date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()
 
-    year_start <-icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
-    year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm
-
-    start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
-    end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple
-
-    actors <- icb_events_long %>% filter(crisno %in% thiscrisis) %>% filter(varname_normalized %>% str_detect('actor')) %>% 
-              dplyr::select(value_normalized,value_qcode) %>% distinct()
-
+  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
+  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm
+
+  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
+  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple
+
+  actor_sent_counts <- 
+        bind_rows(
+            #icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+            #icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+            #icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+            icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a), #Going to organize around actions
+            icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+          ) %>% 
+            na.omit() %>%
+            mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+  #Only consider diads that appear in our data
+  qcodes <- icb_events_long %>% dplyr::filter(crisno==crisis & varname_normalized %>% str_detect('actor') & value_normalized!='') %>% pull(value_qcode) %>% unique() %>% na.omit()
+  actors_translator <- actor_translator %>% filter(QCode %in% qcodes ) %>% janitor::clean_names()
+
+  to_qcode <-   icb_events_long %>%
+                   dplyr::filter(crisno==crisis  ) %>% 
+                   filter(varname_normalized %>% str_detect("actor")) %>% 
+                   dplyr::select(value_normalized,value_qcode) %>% 
+                   na.omit() %>% distinct()
+
+  diads_qcodes <- bind_rows(
+                  icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% 
+                    dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
+                  icb_events %>% dplyr::filter(crisno==crisis  ) %>% 
+                    dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% filter(is.na(say_actor_a)) %>% 
+                    dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
+                  ) %>% 
+                  mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a, keep_empty=T) %>%
+                  mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b, keep_empty=T) %>%
+                  na.omit() %>% 
+                  distinct() %>%
+                  left_join(to_qcode %>% dplyr::select(actor_a=value_normalized, actor_a_qcode=value_qcode) ) %>%
+                  left_join(to_qcode %>% dplyr::select(actor_b=value_normalized, actor_b_qcode=value_qcode) )  %>%
+
+                  left_join(actors_translator %>% dplyr::select(actor_a_qcode=q_code, phoenix_2020_a=phoenix_2020) ) %>%
+                  left_join(actors_translator %>% dplyr::select(actor_b_qcode=q_code, phoenix_2020_b=phoenix_2020) )  %>% 
+                  mutate(source_root_target=paste0(actor_a_qcode, "_", actor_b_qcode) ) %>%
+
+                  filter(actor_a!=actor_b) #Decide to exclude when the target is the same as the source
+
+  #phoenix_clean$joined_issues %>% unique()
+  #install.packages('parsedate')
+  library(parsedate)
   phoenix_clean_subset <- phoenix_clean %>%
-                            mutate(story_date = story_date %>% lubridate::mdy()) %>%
-                            filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
-                            unite('dyad_a', source_root_label, source_agent_label, source_others1_label, source_others2_label, source_others3_label, na.rm = TRUE, remove = FALSE) %>%
-                            unite('dyad_b', target_root_label, target_agent_label, target_others1_label, target_others2_label, target_others3_label, na.rm = TRUE, remove = FALSE) %>%
-                            mutate(dyad=paste0(dyad_a,"->",dyad_b)) %>%
-                            mutate(dyad_event=paste0(dyad, "_", cameo_event_label)) %>%
-                            mutate(dyad_penta_category=paste0(dyad, "_", cameo_penta_category)) %>%
-                            mutate(dyad_lvl0_label=paste0(dyad, "_", cameo_lvl0_label)) %>%
-
-                            unite('temp', everything() , na.rm = TRUE, remove = FALSE) %>%
-                            filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>%
-                            dplyr::select(-temp)
-
-    dim(phoenix_clean_subset)
-
-    dyad_event_counts <-     phoenix_clean_subset  %>% 
-                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                             count(cameo_penta_category, dyad_penta_category) %>% 
-                             group_by(cameo_penta_category) %>%
-                             arrange(cameo_penta_category,  desc(n) ) %>% 
-                             filter(row_number()<=10) %>% ungroup()
-
-    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
-                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
-    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
-                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset
-
-    phoenix_clean_subset_top10 <- phoenix_clean_subset %>% 
-                                  filter(dyad_penta_category %in% dyad_event_counts$dyad_penta_category  ) %>%
-                                  mutate(dyad_markdown=dyad)
-    for(i in 1:nrow(names_to_qcodes)){
-      phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
-                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  )) 
-    }
-    library(ggtext)
-    phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government","gov")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("\\(tertiary role code\\)","")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force"))
-
-    p_phoenix_penta <- phoenix_clean_subset_top10 %>%
-          filter(!is.na(cameo_penta_category)) %>%
-          group_by(dyad_markdown, cameo_penta_category, date) %>%
-          summarise(mean_goldstein=mean(cameo_goldstein), n=n()) %>%
-          group_by(cameo_penta_category, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-          mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_penta_category)) %>%
-          ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
-          geom_tile() + theme_bw() +
-          tidytext::scale_y_reordered() +
-          geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
-          geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
-          facet_wrap(~cameo_penta_category, scale="free_y", ncol=1)  +
-          theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +
-          scale_fill_gradient2() +
-          theme(legend.position="none") +
-         ylab("") + xlab("")
-
-    p_phoenix_penta %>% saveRDS(save_file_penta)
-
-    #cameo_lvl0_label
-    dyad_event_counts <-     phoenix_clean_subset  %>% 
-                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                             count(cameo_lvl0_label, dyad_lvl0_label) %>% 
-                             group_by(cameo_lvl0_label) %>%
-                             arrange(cameo_lvl0_label,  desc(n) ) %>% 
-                             filter(row_number()<=10) %>% ungroup()
-
-    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
-                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
-    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
-                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset
-
-    phoenix_clean_subset_top10 <- phoenix_clean_subset %>% 
-                                  filter(dyad_lvl0_label %in% dyad_event_counts$dyad_lvl0_label  ) %>%
-                                  mutate(dyad_markdown=dyad)
-    for(i in 1:nrow(names_to_qcodes)){
-      phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
-                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  )) 
-    }
-    library(ggtext)
-    phoenix_clean_subset_top10 <- phoenix_clean_subset_top10 %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government","gov")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("\\(tertiary role code\\)","")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force"))
-
-    phoenix_clean_subset_top10_day <- phoenix_clean_subset_top10 %>%
-                                      mutate(story_date=paste(month, day, year, sep="/")) %>%
-                                      filter(!is.na(cameo_lvl0_label)) %>%
-                                      mutate(date = story_date %>% lubridate::mdy()) %>%
-                                      group_by(dyad_markdown, cameo_lvl0_label, date) %>%
-                                      summarise(mean_goldstein=mean(cameo_goldstein), n=n())
-
-    p_phoenix_lv0 <- phoenix_clean_subset_top10_day %>%
-                      group_by(cameo_lvl0_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-                      mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_lvl0_label)) %>%
-                      ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
-                      geom_tile() + theme_bw() +
-                      tidytext::scale_y_reordered() +
-                      geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
-                      geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
-                      facet_wrap(~cameo_lvl0_label, scale="free_y", ncol=3)  +
-                      theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +
-                      scale_fill_gradient2() +
-                      theme(legend.position="none") +
-                      ylab("") + xlab("")
-
-        p_phoenix_lv0 %>% saveRDS(save_file_lv0)
-
-}
-
-fromscratch=F
-if(fromscratch){
-  phoenix_clean <- arrow::read_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") ) 
-  c(196, 471) %>% sapply(FUN=function(x) phoenix_barmaps(x))
-}
+
+                           mutate(source_root_target=paste0(source_root_qcode, "_", target_root_qcode) ) %>%
+                           filter(!is.na(source_root_qcode)) %>%
+                           filter(!is.na(target_root_qcode)) %>%
+
+                           filter(
+                                  source_root_target %in% diads_qcodes$source_root_target & 
+                                  #target_root %in% na.omit(actors_translator_subset$phoenix_2020) & 
+                                  #source_root %in% na.omit(actors_translator_subset$phoenix_2020) &
+                                  year>=year_start &
+                                  year<=year_end   
+                                  #date_simple>=start_simple & 
+                                  #date_simple<=end_simple 
+                                  ) %>%
+                           filter( countryname %in%  na.omit(c('',actors_translator$terrier, actors_translator$icb_letters, actors_translator$phoenix_2020))  ) %>% 
+                           #also reject anything geotagged not in an actor
+                           mutate(crisis_dates= (date_simple>=start_simple & date_simple<=end_simple ) %>% as.numeric()) %>%
+                           #Just apply the actor labels
+                           distinct()   %>%
+
+                           #
+                           dplyr::select(crisis_dates,
+                                         story_date, year, month, day, 
+                                         source_root_target,
+                                         source_root_qcode,
+                                         target_root_qcode,
+                                         source, source_root, source_agent, source_others,
+                                         target, target_root, target_agent, target_others,
+                                         source_root_label, source_agent_label, source_others_label,
+                                         target_root_label, target_agent_label, target_others_label,
+                                         same_target_source,
+                                         code, root_code, 
+                                         cameo_event_label, 
+                                         cameo_event_root_label,
+                                         joined_issues,placename, countryname, joined_issues, process) %>%
+
+                           dplyr::select(-process) %>%
+                           distinct() %>%
+
+                           #Reject sub actors that we don't think are relevant
+                           filter(
+                             !source_agent_label %in% role_rejects &
+                             !target_agent_label %in% role_rejects &
+                             !source_others_label %in% role_rejects &
+                             !target_others_label %in% role_rejects
+                           ) %>%
+
+                           #Reject subjects we don't think are relevant
+                           filter(!joined_issues %in% subject_rejects) %>%
+
+                           filter(crisis_dates==T) %>% #limit to just the crisis dates
+
+                           filter(!cameo_event_label %in% cameo_code_rejects) %>%
+
+                           #Restrict to NYT or max source
+                           #group_by(process) %>%
+                           #  mutate(process_n=n()) %>%
+                           # ungroup() %>%
+                           #filter(process_n==max(process_n)) %>% #Always pick the source with the most events #process=="NYT_Pre0101991_V1"
+
+                           arrange(year,month, day) %>%
+                           mutate(sent= as.numeric(year)*10000+as.numeric(month)*100+as.numeric(day)   )  %>% 
+                           mutate(sent= as.factor(sent - min(sent, na.rm=T) + 1) %>% as.numeric()  ) %>%
+                           mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below|,  not specified below',''))
+
+  extract_savefile <- paste0(here::here(), "/replication_paper/data/out/dataset_extracts/extract_phoenix_",crisis,".tsv")
+  phoenix_clean_subset %>%  write_tsv(extract_savefile)
+
+  #For crises with too many events we subset it to just dyadic events with
+  notes <- NULL
+  if(topactor & nrow(phoenix_clean_subset)>100){
+    diads_qcodes <- diads_qcodes %>% filter(actor_a == actor_sent_counts$actor[1] | actor_b == actor_sent_counts$actor[1]) #
+    phoenix_clean_subset <- phoenix_clean_subset %>% filter( source_root_target %in% diads_qcodes$source_root_target )
+    notes <- "Note: Showing only dyadic events with top actor"
+  }
+
+  dim(phoenix_clean_subset) #
+  if(nrow(phoenix_clean_subset)==0 | 
+     (c(phoenix_clean_subset$source_root_label,phoenix_clean_subset$target_root_label) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
+     ){
+    print("No Phoenix events for this crisis")
+    return()
+  }
+
+  library(ggraph)
+  library(RColorBrewer)
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  #phoenix_clean$year <- phoenix_clean$story_date %>% lubridate::year()
+  #phoenix_clean$month <- phoenix_clean$story_date %>% lubridate::month()
+
+  icb_events_subset_diad <- phoenix_clean_subset %>% 
+                                     dplyr::select(year, month, sent=sent, actor_1=source_root_label, actor_2=target_root_label, cameo_event_label ) %>% distinct() %>%
+                                     mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below','') %>% tolower() ) 
+  #Order actors by how many interactions they have together
+  temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month, -cameo_event_label) %>% arrange(actor_1, actor_2) %>% distinct()
+
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
+
+  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+
+  temp_list <- list()
+  for(i in 1:nrow(temp2_wide)){
+    temp_list[[as.character(i)]] <- cutree(hc, k=i)
+  }
+
+  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
+  #  arrange(across(starts_with("V")))
+  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+  #If we're down to one actor we're going to put it in the center and then put other nearby
+  if(topactor & nrow(phoenix_clean_subset)>100){
+    ideal_ordering <- c(icb_events_subset_diad$actor_1, icb_events_subset_diad$actor_2) %>% table() %>% sort() %>% names() %>% rev()
+    ideal_ordering <- c(ideal_ordering[c(F,T)] %>% rev(), ideal_ordering[c(T,F)])
+  }
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
+                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
+            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  names(actor_colors) = levels(actors)
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                    mutate(x=max(x)+50) %>%
+                    mutate(year=year %>% as.numeric() ) %>%
+                    mutate(month=month %>% as.numeric() ) %>%
+                    dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
+                    na.omit() %>% 
+                    distinct() %>%  
+                    mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                    mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                    group_by(sent) %>%
+                    filter(year_float==min(year_float)) %>%
+                    ungroup() %>% as.data.frame() %>%
+                    filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                    filter(!duplicated(year_float ) ) %>%
+                    mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+  ####Actor lavels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+    #rename(qcode=actor, actor=value_normalized_label) %>%
+    rowwise() %>%
+    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F,
+                 bundle_count=1)
+
+  ######Directed
+  icb_events_subset_directed <- 
+            phoenix_clean_subset %>% 
+            dplyr::select(sent=sent, actor_1=source_root_label, actor_2=target_root_label, cameo_event_label ) %>% distinct() %>%
+            mutate(cameo_event_label=cameo_event_label %>% str_replace(', not specified below',''))  %>% na.omit()  %>% distinct() %>% 
+            mutate(leaf = cameo_event_label %>% tolower() )  %>% 
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor1_actor2= actor_1 %>% paste0("_", actor_2)) %>%
+            arrange(actor1_actor2, sent) %>%
+
+            group_by(sent,actor1_actor2, actor_1, actor_2, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) %>%
+            arrange(actor1_actor2,sent) %>%
+            group_by(actor1_actor2) %>%
+              mutate(leaf_dupe=leaf==lag(leaf)) %>%
+              mutate(sent_gap= sent - lag(sent)  ) %>%
+            ungroup()
+            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  icb_events_subset_directed <- icb_events_subset_directed  %>% 
+                                         filter(!( leaf_dupe %in% T & !is.na(sent_gap) & sent_gap<=31)) %>% #reject the same kind of event within a directed diad that occures again within 31 days back to back
+                                         group_by(sent, leaf) %>%
+                                             mutate(bundle_count=n()) %>%
+                                             mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
+                                          ungroup() #%>% 
+          #filter(bundle_count>1)
+  #dim(icb_events_subset_directed) #1826 bundled
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf2, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1,
+                       bundle_count=icb_events_subset_directed$bundle_count
+                       )
+
+  ######Put it all together
+  p_phoenix_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Time edges
+          geom_edge_link(aes(
+                          edge_colour=actor,
+                          filter=timeedge==T
+                          ),
+                          edge_width=0.1, 
+                          show.legend = F
+                         ) +
+          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                              colour=actor,
+                              label=leaf,
+                              filter=eventedge==T & bundle_count==1
+                              ),
+                          vjust = -0.75,
+                          lineheight = .75,
+                          sep = unit(1, 'mm'), 
+                          edge_width=0.25, 
+                          show.legend = F,
+                          arrow = arrow(length = unit(2, 'mm')),
+                          label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+              #Grouped Edges
+              geom_edge_parallel(aes(  
+                                  colour=actor,
+                                  label=leaf,
+                                  filter=eventedge==T & bundle_count>1
+                                  ),
+                              vjust = -0.75,
+                              lineheight = .75,
+                              sep = unit(5, 'mm'), 
+                              edge_width=0.4,  #0.25
+                              show.legend = F,
+                              arrow = arrow(length = unit(1, 'mm')),
+                              label_size=4,
+                              check_overlap=global_check_overlap,
+                              start_cap = circle(3, 'mm'),
+                              end_cap = circle(3, 'mm'),
+                              angle_calc = 'along'
+                             ) +
+
+              #Not in phoenix
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
+              #Not in phoenix
+              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #Not in phoenix
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  if(!is.null(notes)){
+     p_phoenix_metro_map <- p_phoenix_metro_map + labs(caption = notes)
+  }
+
+  p_phoenix_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+  p_phoenix_metro_map$actor_colors <- actor_colors
+  p_phoenix_metro_map$phoenix_clean_subset <- phoenix_clean_subset
+
+  p_phoenix_metro_map  %>% saveRDS(save_phoenix_file)
+
+}
+
+c(196, 471) %>% sapply(FUN=function(x) phoenix_metro_plots(x))
 
@@
 
-```{r Terrierr Data Loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-#https://osf.io/4m2u7/
+## Terrier
+
+### Data Loads
+
+https://osf.io/4m2u7/
+
+```{r}
 
@@
 
-#if(file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
-#  terrier_fromscratch <-readline(prompt="Load original Terrier data? (T/F)")
-#}
-#terrier_fromscratch <- terrier_fromscratch %in% "T"
-
-#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
+terrier_fromscratch <- F
+if(file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
+  terrier_fromscratch <-readline(prompt="Load original Terrier data? (T/F)")
+}
+terrier_fromscratch <- terrier_fromscratch %in% "T"
+
+CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
 #codes_used <-terrier_clean %>% count(cameo_code)
+
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
+actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")
 
@@
 library(dplyr, warn.conflicts = FALSE)
-terrier_fromscratch <- F
 if(terrier_fromscratch){
@@
   dim(terrier) #28,438,029 #28,370,448       28
+}
+
+```
+
+```{r}
+
+cameo_actor_codes <- cameo_actor_codes %>% as.data.table()
+actor_translator <- actor_translator %>% as.data.table()
 
@@
 
-    #library("remotes")
-    #remotes::install_github("andybega/icews")
-    library(icews)
-    data("cameo_codes") #we're going to grab the cameo codes from the ICEWS package because they're a nightmare
-    cameo_codes_goldstein <- cameo_codes %>% left_join(goldstein_mappings) %>% mutate(name=name %>% tolower())
-
+#572c7b89172ab83171badfa0
+terrier_fromscratch=T
+if(terrier_fromscratch){
   library(tictoc)
-    tictoc::tic()
+  tic()
   dim(terrier) #28,438,029
@@
       #head(100000) %>%
-        as_tibble() %>%
       dplyr::select(
@@
       ) %>% 
-        left_join(cameo_codes_goldstein %>% mutate(cameo_code=cameo_code ) %>% dplyr::select(cameo_code=cameo_code, cameo_label= name, cameo_goldstein=goldstein,
-                                                                                             cameo_penta_category=penta_category, cameo_lvl0=lvl0)  ) %>% #
-        left_join(    cameo_codes_goldstein %>% filter(level==0) %>% dplyr::select(cameo_lvl0=lvl0, cameo_lvl0_label=name)) %>% #
-        mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
-
+      left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code ) %>% dplyr::select(cameo_code=cameo_code, cameo_label= cameo_label)  ) %>% #it's that insane cameo code bug
       mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>% 
@@
       dplyr::select(-starts_with("trash")) %>%
+      #filter(!is.na(src_country) | !is.na(target_country)) %>% #require at least one side to be a country
+      #distinct() %>% 
+      #mutate(cameo_code=cameo_code ) %>%  #it's that insane cameo code bug
 
@@
                      mutate(day= day %>% as.numeric() )  %>%
-       as_tibble()
-    tictoc::toc() #313.74 
+      as.data.table()
+  toc() #313.74 
   dim(terrier_clean_temp) #31,117,198 #39322909
@@
   terrier_clean_temp  %>%
-      arrow::write_parquet(here::here("replication_paper", "data", "ignore", "terrier_clean.parquet") )
-}
-
-```
-
-```{r terrier_barmaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(readr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-
-terrier_barmaps <- function(thiscrisis=471, topactor=F){
-
-    print(thiscrisis)
-    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_terrier_plot_lv0_",thiscrisis,".Rds")
-
-    date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==thiscrisis,]$motrig, "-01"))
-    date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrterm , "-", icb_crises[icb_crises$crisno==thiscrisis,]$moterm, "-01"))
-    date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()
-
-    year_start <-icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
-    year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm
-
-    start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
-    end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple
-
-    actors <- icb_events_long %>% filter(crisno %in% thiscrisis) %>% filter(varname_normalized %>% str_detect('actor')) %>% 
-              dplyr::select(value_normalized,value_qcode) %>% distinct()
-
-    terrier_clean_subset <- terrier_clean %>% 
-                    mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() ) %>%
-                    filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
-                    unite('temp', src_country_label,src_agent_label,src_other_agent1_label,src_other_agent2_label,src_other_agent3_label,
-                          target_country_label, target_agent_label,target_other_agent1_label,target_other_agent2_label,target_other_agent3_label,
-                          where,
-                          na.rm = TRUE, remove = FALSE) %>%
-                    filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>%
-                    unite('dyad_a', src_country_label,src_agent_label,src_other_agent1_label,src_other_agent2_label,src_other_agent3_label, na.rm = TRUE, remove = FALSE) %>%
-                    unite('dyad_b', target_country_label, target_agent_label,target_other_agent1_label,target_other_agent2_label,target_other_agent3_label, na.rm = TRUE, remove = FALSE) %>%
-                    mutate(dyad=paste0(dyad_a,"->",dyad_b)) %>%
-                    mutate(dyad_event=paste0(dyad, "_", cameo_label)) %>%
-                    mutate(dyad_penta_category=paste0(dyad, "_", cameo_penta_category)) %>%
-                    mutate(dyad_lvl0_category=paste0(dyad, "_", cameo_lvl0_label)) %>%
-                    dplyr::select(-temp)
-
-    dim(terrier_clean_subset) #928,640
-
-    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
-                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
-    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
-                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset
-
-    #Penta
-    dyad_event_counts <-     terrier_clean_subset  %>% 
-                         mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                         filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                         count(cameo_penta_category, dyad_penta_category) %>% 
-                         group_by(cameo_penta_category) %>%
-                         arrange(cameo_penta_category,  desc(n) ) %>% 
-                         filter(row_number()<=10) %>% ungroup()
-
-    terrier_clean_subset_top10 <- terrier_clean_subset %>% 
-                                  filter(dyad_penta_category %in% dyad_event_counts$dyad_penta_category  ) %>%
-                                  mutate(dyad_markdown=dyad)
-
-    terrier_clean_subset_top10_day <- terrier_clean_subset_top10 %>%
-          mutate(story_date=paste(month, day, year, sep="/")) %>%
-          filter(!is.na(cameo_penta_category)) %>%
-          mutate(date = story_date %>% lubridate::mdy()) %>%
-          group_by(dyad_markdown, cameo_penta_category, date) %>%
-          summarise(mean_goldstein=mean(cameo_goldstein), n=n())
-
-    for(i in 1:nrow(names_to_qcodes)){
-      #print(i)
-      terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
-                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
-    } #This is a bottleneck now and needs to move to after the group
-    library(ggtext)
-    terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all(fixed("(tertiary role code)"),"")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil."))
-
-    p_terrier_penta <-  terrier_clean_subset_top10_day %>%
-          group_by(cameo_penta_category, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-          mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_penta_category)) %>%
-          ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
-          geom_tile() + theme_bw() +
-          tidytext::scale_y_reordered() +
-          geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
-          geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
-          facet_wrap(~cameo_penta_category, scale="free_y", ncol=1)  +
-      theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +   scale_fill_gradient2() +
-          theme(legend.position="none") +
-         ylab("") + xlab("")
-
-    p_terrier_penta %>% saveRDS(save_file_penta)
-
-    #_lvl0
-    dyad_event_counts <-     terrier_clean_subset  %>% 
-                         mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                         filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                         count(cameo_lvl0_label, dyad_lvl0_category) %>% 
-                         group_by(cameo_lvl0_label) %>%
-                         arrange(cameo_lvl0_label,  desc(n) ) %>% 
-                         filter(row_number()<=10) %>% ungroup()
-
-    terrier_clean_subset_top10 <- terrier_clean_subset %>% 
-                                  filter(dyad_lvl0_category %in% dyad_event_counts$dyad_lvl0_category  ) %>%
-                                  mutate(dyad_markdown=dyad)
-
-    terrier_clean_subset_top10_day <- terrier_clean_subset_top10 %>%
-          mutate(story_date=paste(month, day, year, sep="/")) %>%
-          filter(!is.na(cameo_penta_category)) %>%
-          mutate(date = story_date %>% lubridate::mdy()) %>%
-          group_by(dyad_markdown, cameo_lvl0_label, date) %>%
-          summarise(mean_goldstein=mean(cameo_goldstein), n=n())
-
-    for(i in 1:nrow(names_to_qcodes)){
-      #print(i)
-      terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
-                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
-    } #This is a bottleneck now and needs to move to after the group
-    library(ggtext)
-    terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Inter-governmental organizations","IGOs")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government[^a-z]|Government[^a-z]","gov")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all(fixed("(tertiary role code)"),"")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil."))
-
-    p_terrier_lv0 <-  terrier_clean_subset_top10_day %>%
-          group_by(cameo_lvl0_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-          mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_lvl0_label)) %>%
-          ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
-          geom_tile() + theme_bw() +
-          tidytext::scale_y_reordered() +
-          geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
-          geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
-          facet_wrap(~cameo_lvl0_label, scale="free_y", ncol=3)  +
-      theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) + 
-       scale_fill_gradient2() +
-          theme(legend.position="none") +
-         ylab("") + xlab("")
-
-    p_terrier_lv0 %>% saveRDS(save_file_lv0)
-
-}
-
-fromscratch=F
-if(fromscratch){
+    arrow::write_parquet(here::here("replication_paper", "data", "in", "terrier_clean.parquet") )
+}
 #done
 #install.packages("arrow")
-  terrier_clean <-  arrow::read_parquet( here::here("replication_paper", "data", "ignore", "terrier_clean.parquet")) #203mb
-  dim(terrier_clean) #28,438,029 #39,322,909 #7,847,463
-
-  c(196, 471) %>% sapply(FUN=function(x) terrier_barmaps(x))
-}
+terrier_clean <-  arrow::read_parquet( here::here("replication_paper", "data", "in", "terrier_clean.parquet")) #203mb
+dim(terrier_clean) #39,322,909 #7,847,463
+
+library(dplyr)
+library(digest)
+keep_list <- c("Ukraine", "Russia","Russian Federation", 'North Atlantic Treaty Organization','NATO', 'European Union', 'Crimea','Donbas') #, 'United Nations'
+tic()
+terrier_clean_471 <- terrier_clean %>% 
+                     mutate(year= year %>% as.numeric() ) %>%
+                     filter( year>= 2013 & year<= 2015 )  %>% #it's 10 million
+                      #This is the only step we can't do in data.table
+                      as_tibble() %>%
+                      unite(text,  #Unite has to be done in tibble it can't be done in lazy data.table
+                            src_country_label,src_agent_label, src_other_agent1_label, src_other_agent2_label, src_other_agent3_label, 
+                            cameo_label, 
+                            target_agent_label, target_other_agent1_label, target_other_agent2_label, target_other_agent3_label, target_country_label, sep=" ", remove = F, na.rm = T) %>%
+                      mutate(text = ifelse(!is.na(where) & where!='',paste0(text, " in ", where),text) ) %>% 
+                      mutate(text = paste0("On ", month_label, " ",day," ",year, ", ", text))   %>%
+                     filter( text %>% str_detect(paste0(c(keep_list,keep_list %>% tolower()),collapse="|"))) 
+toc()
+dim(terrier_clean_471) #638,169 #1,616,930 #9,868,735 #402437 #382,434
+
+terrier_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/terrier_clean_471.tsv")
+dim(terrier_clean_471)  #638,169 #1,616,930
+
+terrier_clean_471 %>%
+  unite('actors_left' , src_country_label,src_agent_label, src_other_agent1_label, src_other_agent2_label, src_other_agent3_label, sep=" ", , na.rm =T, remove=F) %>%
+  unite('actors_right', target_country_label, target_agent_label, target_other_agent1_label, target_other_agent2_label, target_other_agent3_label, sep=" ", , na.rm =T, remove=F) %>%
+  dplyr::select(hash, year, month, day, actors_left, actors_right,cameo_event_label=cameo_label, text ) %>% 
+                     mutate(year= year %>% as.numeric() ) %>% 
+                     mutate(month= month %>% as.numeric() ) %>% 
+                     mutate(day= day %>% as.numeric() )  %>% 
+  group_by(year, month, day, actors_left, actors_right,cameo_event_label, text) %>%
+  summarise(hash = paste0(hash,collapse=";")) %>%
+  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/terrier_clean_471_small.tsv")
+#164,707 unique events with multiple sources per it seems
 
@@
 
-```{r ICEWS data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-fromscratch=F
-if(fromscratch){
-  #accidentally loaded the pdfs
-  files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T, pattern = ".tab$|.tsv$")
-  icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x, show_col_types = FALSE) )  ) %>% janitor::clean_names() %>% distinct()
-  dim(icews) #18,403,260 #15,751,586
-
-  codes_used <-icews %>% count(cameo_code)
-
-  actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
-  #%>% mutate(icews=ifelse(ICEWS_Country=="International Government Organizations", ICEWS_Actor.Name, ICEWS_Country))
-
-  #Going to heavily filter on source sectors and source name
-  #c(icews$source_sectors,icews$source_name) %>% table()
-
-  #This doesn't totally work because India has 3 copies.
-The lower thing gets a different q code than the higher thing, so we first have to try to match on the lower, and if that fails match on the higher kinda
-  #Indian Administered Kashmir		India
-
-    #library("remotes")
-  #remotes::install_github("andybega/icews")
-  library(icews)
-  data("cameo_codes") #we're going to grab the cameo codes from the ICEWS package because they're a nightmare
-  cameo_codes_goldstein <- cameo_codes %>% left_join(goldstein_mappings) %>% mutate(name=name %>% tolower())
-
-  dim(icews) #18,403,260 #15,751,586
-  icews_clean <- icews %>% 
-                 #filter(event_id==20776790) %>% 
-                 #head(10000) %>%
-                 mutate_if(is.character, na_if, "null") %>%
-                 mutate_if(is.character, na_if, "NULL") %>%
-                 #head(1000) %>%
-                 mutate(where = coalesce(city, district,province)) %>%
-                 left_join(cameo_codes_goldstein %>% mutate(cameo_code=cameo_code ) %>%
-                             dplyr::select(cameo_code=cameo_code, cameo_label= name, cameo_goldstein=goldstein, cameo_penta_category=penta_category,
-                                           cameo_lvl0=lvl0)  ) %>% #it's that insane cameo code bug
-                 left_join(    cameo_codes_goldstein %>% filter(level==0) %>% dplyr::select(cameo_lvl0=lvl0, cameo_lvl0_label=name)) %>% #it's that insane cameo code bug    
-                 mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
-
-                left_join( actor_translator_icews %>% dplyr::select(source_name=ICEWS_Actor.Name,  source_q_code_actor=QCode, source_q_label_actor=QCode_name) %>% 
-                             distinct() %>% na.omit() ) %>%
-                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% 
-                             dplyr::select(source_country=ICEWS_Country,  source_q_code_country=QCode, source_q_label_country=QCode_name) %>% 
-                             distinct() %>% na.omit() ) %>%
-                mutate(source_q_code=ifelse(!is.na(source_q_code_actor) , source_q_code_actor, source_q_code_country)) %>%
-                mutate(source_label=ifelse(!is.na(source_q_code_actor) , source_q_label_actor, source_q_label_country)) %>%
-
-                left_join( actor_translator_icews %>% dplyr::select(target_name=ICEWS_Actor.Name,  target_q_code_actor=QCode, target_q_label_actor=QCode_name) %>% 
-                             distinct() %>% na.omit() ) %>%
-                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% 
-                             dplyr::select(target_country=ICEWS_Country,  target_q_code_country=QCode, target_q_label_country=QCode_name) %>%
-                             distinct() %>% na.omit() ) %>%
-                mutate(target_q_code=ifelse(!is.na(target_q_code_actor) , target_q_code_actor, target_q_code_country)) %>%
-                mutate(target_label=ifelse(!is.na(target_q_code_actor) , target_q_label_actor, target_q_label_country)) %>%
-
-                mutate(source_target_q_code= paste0(source_q_code,"_",target_q_code)) %>%
-
-                left_join( actor_translator_icews %>% filter(is.na(ICEWS_Actor.Name)) %>% dplyr::select(country=ICEWS_Country,  country_q_code=QCode) %>% distinct() %>% na.omit() ) %>%
+```{r}
+if(terrier_fromscratch){
+terrier_clean <- terrier_clean_temp %>%
+     left_join(df %>% dplyr::select(src_agent=agent, src_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
+   left_join(df %>% dplyr::select(target_agent=agent, target_agent_label=agent_label) %>% distinct() %>% na.omit() )  %>% 
+   distinct() %>%
+   filter(
+     !src_other_agent_label %in% role_rejects &
+     !target_other_agent_label %in% role_rejects &
+     !src_agent_label %in% role_rejects &
+     !target_agent_label %in% role_rejects 
+     ) %>% 
+  left_join(actor_translator %>% dplyr::select(src_country=terrier,actor_1_qcode=QCode,actor_1=QCode_name) ) %>%
+  left_join(actor_translator %>% dplyr::select(target_country=terrier,actor_2_qcode=QCode,actor_2=QCode_name) ) %>%
+  filter(!is.na(actor_1_qcode) & !is.na(actor_2_qcode) ) %>%
+  mutate(source_root_target=paste0(actor_1_qcode, "_", actor_2_qcode) ) %>%
+  mutate(
+  event_date= lubridate::as_date(paste0( year, "-", month,"-",day ))
+  )
+dim(terrier_clean) #2,049,759
+
+saveRDS(terrier_clean, here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
+}
+
+#For now
+#IGO 223751 for now we're going to exclude just generic Intergovernmental organization and multinational corps
+#MNC 62721
+#terrier_clean %>% dplyr::select(src_country, actor_1) %>% filter(is.na(actor_1)) %>% count(src_country) %>% View()
+
+#terrier_clean %>% 
+#  dplyr::select(src_agent_label,  src_other_agent_label, target_agent_label, target_other_agent_label, cameo_label) %>% 
+#  count(src_agent_label,  src_other_agent_label, target_agent_label, target_other_agent_label, cameo_label) %>% arrange(desc(n)) %>% View()
+
+if(!terrier_fromscratch){
+  terrier_clean <- readRDS(here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
+}
+
+```
+
+### Plot
+
+```{r}
+
+terrier_metro_plots <- function(crisis=471, topactor=F){
+
+  print(crisis)
+  #crisis=471
+  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
+  save_terrier_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_terrier_metro_plot_",crisis,".Rds")
+  extract_savefile <- paste0(here::here(), "/replication_paper/data/out/dataset_extracts/extract_terrier_",crisis,".tsv")
+
+  date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
+  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-01"))
+  date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()
+
+  year_start <-icb_crises[icb_crises$crisno==crisis,]$yrtrig
+  year_end   <- icb_crises[icb_crises$crisno==crisis,]$yrterm
+
+  start_simple <- icb_crises[icb_crises$crisno==crisis,]$start_simple
+  end_simple <- icb_crises[icb_crises$crisno==crisis,]$end_simple
+
+  actor_sent_counts <- 
+        bind_rows(
+            #icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+            #icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+            #icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+            icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a), #Going to organize around actions
+            icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+          ) %>% 
+            na.omit() %>%
+            mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+  #Only consider diads that appear in our data
+  qcodes <- icb_events_long %>% dplyr::filter(crisno==crisis & varname_normalized %>% str_detect('actor') & value_qcode!='') %>% pull(value_qcode) %>% unique() %>% na.omit()
+  actors_translator <- actor_translator %>% filter(QCode %in% qcodes ) %>% janitor::clean_names()
+
+  to_qcode <-   icb_events_long %>%
+                 dplyr::filter(crisno==crisis  ) %>% 
+                 filter(varname_normalized %>% str_detect("actor")) %>% 
+                 dplyr::select(value_normalized,value_qcode) %>% 
+                 na.omit() %>% distinct()
+
+  diads_qcodes <- bind_rows(
+                  icb_events %>% dplyr::filter(crisno==crisis  ) %>% dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% 
+                    dplyr::select(actor_a=say_actor_a, actor_b= say_actor_b),
+                  icb_events %>% dplyr::filter(crisno==crisis  ) %>% 
+                    dplyr::select(think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>% filter(is.na(say_actor_a)) %>% 
+                    dplyr::select(actor_a=do_actor_a, actor_b=do_actor_b)
+                  ) %>% 
+                  mutate(actor_a = strsplit(as.character(actor_a), ";")) %>%  unnest(actor_a, keep_empty=T) %>%
+                  mutate(actor_b = strsplit(as.character(actor_b), ";")) %>%  unnest(actor_b, keep_empty=T) %>%
+                  na.omit() %>% 
+                  distinct() %>%
+                  left_join(to_qcode %>% dplyr::select(actor_a=value_normalized, actor_a_qcode=value_qcode) ) %>%
+                  left_join(to_qcode %>% dplyr::select(actor_b=value_normalized, actor_b_qcode=value_qcode) )  %>% 
+                  #
+                  left_join(actors_translator %>% dplyr::select(actor_a_qcode=q_code, terrier_a=terrier) ) %>% #I think we can reuse Phoenix or maybe not? no probably not
+                  left_join(actors_translator %>% dplyr::select(actor_b_qcode=q_code, terrier_b=terrier) )  %>% 
+                  mutate(source_root_target=paste0(actor_a_qcode, "_", actor_b_qcode) ) %>%
+
+                  filter(terrier_a!=terrier_b) #Decide to exclude when the target is the same as the source
+
+  #phoenix_clean$joined_issues %>% unique()
+  #install.packages('parsedate')
+  library(parsedate)
+  terrier_clean_subset <- terrier_clean %>% 
+                          mutate(source_root_target= paste0(actor_1_qcode,"_", actor_2_qcode)) %>%
+                           dplyr::filter(
+                                  source_root_target %in% diads_qcodes$source_root_target,
+
+                                  #target_root %in% na.omit(actors_translator_subset$phoenix_2020) & 
+                                  #source_root %in% na.omit(actors_translator_subset$phoenix_2020) &
+                                  event_date>=date_start &
+                                  event_date<=date_end   
+                                  #date_simple>=start_simple & 
+                                  #date_simple<=end_simple 
+                                  ) %>%
+
+                           #
+                           dplyr::select(event_date,year,month,
+                                         actor_1, actor_1_qcode,
+                                         actor_2, actor_2_qcode,
+                                         src_country, src_agent_label, src_other_agent_label, target_country, target_agent_label, target_other_agent_label,
+                                         source_root_target,
+                                         cameo_label) %>%
+
+                           distinct() %>%
                            mutate(year = event_date %>% lubridate::year()  )  %>%
@@
                            mutate(day = event_date %>% lubridate::day()  ) %>%
-                mutate(month_label = lubridate::month(month %>% as.numeric(),label=TRUE,abbr=F)) %>%
-                mutate(source_sectors = source_sectors %>% tolower()) %>%
-                mutate(target_sectors = target_sectors %>% tolower()) %>%
-                mutate(cameo_label = cameo_label %>% str_replace(", not specified below","") ) %>%
-                mutate(who_a = coalesce(source_name,source_sectors %>% tolower(), source_label ) ) %>%
-                mutate(who_b = coalesce(target_name,target_sectors %>% tolower(), target_label ) ) %>%
-                mutate(who_a = ifelse(who_a %in% source_country, NA, who_a)) %>%
-                mutate(who_b = ifelse(who_b %in% target_country, NA, who_b)) %>%
-                unite(text, 
-                      source_country,who_a,  
-                      cameo_label, 
-                      who_b, target_country, sep=" ", remove = F, na.rm = T) %>%
-                mutate(text = ifelse(!is.na(where),paste0(text, " in ", where),text) ) %>% 
-                mutate(text = paste0("On ", month_label, " ",day," ",year, ", ", text))
-
-    dim(icews_clean) #17,541,701 #1,965,573 it's still too many but it's just close enough now #1,965,573
-
-    icews_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )
-
-    #icews_clean %>% count(source_country) %>% dim() #233
-    #icews_clean %>% count(source_country, source_sectors) %>% dim() #404673
-    #icews_clean %>% count(source_country, source_sectors, source_name) %>% dim() #569374
-    #icews_clean %>% count(cameo_label) %>% dim() #272
-
-    dim(icews_clean) #17,541,701
-    library(dplyr)
-    library(digest)
-    keep_list <- c("Ukraine", "Russia","Russian Federation", 'North Atlantic Treaty Organization', 'NATO', 'European Union', 'Crimea','Donbas','Donetsk', 'Luhansk' ) #, 'United Nations'
-    keep_list <- c(keep_list, keep_list %>% tolower())
-    icews_clean_471 <- icews_clean %>% 
-                       filter( event_date>= as.Date("2013-01-01") & event_date<= as.Date("2015-12-31") ) %>%
-                      unite('temp', country , target_name , target_country, where , 
-                            source_q_label_country,target_q_label_country,  source_label, target_label,who_a, who_b,province, district, city,
-                            na.rm = TRUE, remove = FALSE) %>% #this is probably slow need to check
-                       filter( temp %>% str_detect(paste0(keep_list,collapse="|"))) %>%
-                       dplyr::select(-temp)
-    dim(icews_clean_471) #281,427
-
-    icews_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")
-
-    icews_clean_471 %>%
-      unite('actors_left' , source_country, source_label, source_name, source_sectors,  sep=" ", , na.rm =T, remove=F) %>%
-      unite('actors_right', target_country, target_label, target_name, target_sectors, sep=" ", , na.rm =T, remove=F) %>%
-      dplyr::select(event_id, year, month, day, actors_left, actors_right,cameo_event_label=cameo_label, text ) %>% 
-      write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")
-
-}
+                           arrange(year,month, day) %>%
+                           mutate(sent= year*10000+month*100+day   )  %>% 
+                           mutate(sent= as.factor(sent - min(sent, na.rm=T) + 1) %>% as.numeric()  ) %>%
+                           mutate(crisno=crisis)
+
+  terrier_clean_subset %>% write_tsv(extract_savefile) #It's 10k
+
+  #For crises with too many events we subset it to just dyadic events with
+  notes <- NULL
+  if(topactor & nrow(terrier_clean_subset)>100){
+    diads_qcodes <- diads_qcodes %>% filter(actor_a == actor_sent_counts$actor[1] | actor_b == actor_sent_counts$actor[1]) #
+    terrier_clean_subset <- terrier_clean_subset %>% filter( source_root_target %in% diads_qcodes$source_root_target )
+    notes <- "Note: Showing only dyadic events with top actor"
+  }
+
+  dim(terrier_clean_subset) #
+  if(nrow(terrier_clean_subset)==0 | 
+     (c(terrier_clean_subset$actor_1,terrier_clean_subset$actor_2) %>% na.omit() %>% unique() %>% length())<2  #Reject if not 2 actors
+     ){
+    print("No terrier events for this crisis")
+    return()
+  }
+
+  library(ggraph)
+  library(RColorBrewer)
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  icb_events_subset_diad <- terrier_clean_subset %>% 
+                                     dplyr::select(year, month, sent=sent, actor_1=actor_1, actor_2=actor_2, cameo_label ) %>% distinct() %>%
+                                     mutate(cameo_label=cameo_label %>% str_replace(', not specified below','') %>% tolower() ) 
+  #Order actors by how many interactions they have together
+  temp <- icb_events_subset_diad  %>% dplyr::select(-year, -month , -cameo_label) %>% arrange(actor_1, actor_2) %>% distinct()
+
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("story_date", "actor_2", "actor_1" ))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n)
+
+  temp2_wide <- temp2 %>% pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 - (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+
+  temp_list <- list()
+  for(i in 1:nrow(temp2_wide)){
+    temp_list[[as.character(i)]] <- cutree(hc, k=i)
+  }
+
+  #ideal_ordering <- bind_rows(temp_list) %>% t() %>% as.data.frame() %>% apply(1, paste, collapse='') %>% sort() %>% names() #this will break with more than 9
+  #  arrange(across(starts_with("V")))
+  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+
+  #If we're down to one actor we're going to put it in the center and then put other nearby
+  if(topactor & nrow(terrier_clean_subset)>100){
+    ideal_ordering <- c(icb_events_subset_diad$actor_1, icb_events_subset_diad$actor_2) %>% table() %>% sort() %>% names() %>% rev()
+    ideal_ordering <- c(ideal_ordering[c(F,T)] %>% rev(), ideal_ordering[c(T,F)])
+  }
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_1) ,
+                      icb_events_subset_diad %>% dplyr::select(year, month, sent=sent, actor=actor_2) 
+            ) %>% na.omit() %>% distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  names(actor_colors) = levels(actors)
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                      mutate(x=max(x)+50) %>%
+                      mutate(year=year %>% as.numeric()) %>%
+                      mutate(month=month %>% as.numeric()) %>%
+                      dplyr::select(sent, point_in_time_year=year, point_in_time_month=month,x,y) %>%
+                      na.omit() %>% 
+                      distinct() %>%  
+                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                      group_by(sent) %>%
+                      filter(year_float==min(year_float)) %>%
+                      ungroup() %>% as.data.frame() %>%
+                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                      filter(!duplicated(year_float ) ) %>%
+                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+  ####Actor lavels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    #left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>% #only need to do for our q codes
+    #rename(qcode=actor, actor=value_normalized_label) %>%
+    rowwise() %>%
+    mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n'))
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F,
+                 bundle_count=1)
+
+  ######Directed
+  icb_events_subset_directed <- 
+            terrier_clean_subset %>% 
+            dplyr::select(sent=sent, actor_1=actor_1, actor_2=actor_2, cameo_label ) %>% distinct() %>%
+            mutate(cameo_label=cameo_label %>% str_replace(', not specified below',''))  %>% na.omit()  %>% distinct() %>% 
+            mutate(leaf = cameo_label %>% tolower() )  %>% 
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor1_actor2= actor_1 %>% paste0("_", actor_2)) %>%
+            arrange(actor1_actor2, sent) %>%
+
+            group_by(sent,actor1_actor2, actor_1, actor_2, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") %>% tolower() ) %>%
+            arrange(actor1_actor2,sent) %>%
+            group_by(actor1_actor2) %>%
+              mutate(leaf_dupe=leaf==lag(leaf)) %>%
+              mutate(sent_gap= sent - lag(sent)  ) %>%
+            ungroup()
+            #filter(actor_sent_2 %>% str_detect("Q30") | actor_sent_1 %>% str_detect("Q30"))
+
+  icb_events_subset_directed <- icb_events_subset_directed  %>% 
+                                         filter(!( leaf_dupe %in% T & !is.na(sent_gap) & sent_gap<=31)) %>% #reject the same kind of event within a directed diad that occures again within 31 days back to back
+                                         group_by(sent, leaf) %>%
+                                             mutate(bundle_count=n()) %>%
+                                             mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>% #kill leaf titles past 1 #paste0(sent,"_",actor_1,"_",actor_sent_2)
+                                          ungroup() #%>% 
+          #filter(bundle_count>1)
+  #dim(icb_events_subset_directed) #1826 bundled
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf2, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1,
+                       bundle_count=icb_events_subset_directed$bundle_count
+                       )
+
+  ######Put it all together
+  p_terrier_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Time edges
+          geom_edge_link(aes(
+                          edge_colour=actor,
+                          filter=timeedge==T
+                          ),
+                          edge_width=0.1, 
+                          show.legend = F
+                         ) +
+          geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                              colour=actor,
+                              label=leaf,
+                              filter=eventedge==T & bundle_count==1
+                              ),
+                          vjust = -0.75,
+                          lineheight = .75,
+                          sep = unit(1, 'mm'), 
+                          edge_width=0.25, 
+                          show.legend = F,
+                          arrow = arrow(length = unit(2, 'mm')),
+                          label_size=3,
+                          check_overlap=global_check_overlap,
+                          start_cap = circle(3, 'mm'),
+                          end_cap = circle(3, 'mm'),
+                          angle_calc = 'along'
+                         ) +
+              #Grouped Edges
+              geom_edge_parallel(aes(  
+                                  colour=actor,
+                                  label=leaf,
+                                  filter=eventedge==T & bundle_count>1
+                                  ),
+                              vjust = -0.75,
+                              lineheight = .75,
+                              sep = unit(5, 'mm'), 
+                              edge_width=0.4,  #0.25
+                              show.legend = F,
+                              arrow = arrow(length = unit(1, 'mm')),
+                              label_size=4,
+                              check_overlap=global_check_overlap,
+                              start_cap = circle(3, 'mm'),
+                              end_cap = circle(3, 'mm'),
+                              angle_calc = 'along'
+                             ) +
+
+              #Not in phoenix
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0) + 
+              #Not in phoenix
+              #geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3) +
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor, color=actor), nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold") + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #Not in phoenix
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  if(!is.null(notes)){
+     p_terrier_metro_map <- p_terrier_metro_map + labs(caption = notes)
+  }
+
+  p_terrier_metro_map$sentence_count <- icb_events_subset_nodes$sent %>% unique() %>% length()
+  p_terrier_metro_map$actor_colors <- actor_colors
+  p_terrier_metro_map$terrier_clean_subset <- terrier_clean_subset
+
+  p_terrier_metro_map  %>% saveRDS(save_terrier_file)
+
+}
+
+icb_crises %>% filter(yrtrig>=1977 & crisno %in% c(196, 471)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))
 
 ```
-
-```{r icews_barmaps, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(readr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-
-icews_barmaps <- function(thiscrisis=471, topactor=F){
-
-    print(thiscrisis)
-    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icews_plot_lv0_",thiscrisis,".Rds")
-
-    date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==thiscrisis,]$motrig, "-01"))
-    date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==thiscrisis,]$yrterm , "-", icb_crises[icb_crises$crisno==thiscrisis,]$moterm, "-01"))
-    date_end <- date_end %>% lubridate::ceiling_date() %>% lubridate::as_date()
-
-    year_start <- icb_crises[icb_crises$crisno==thiscrisis,]$yrtrig
-    year_end   <- icb_crises[icb_crises$crisno==thiscrisis,]$yrterm
-
-    start_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$start_simple
-    end_simple <- icb_crises[icb_crises$crisno==thiscrisis,]$end_simple
-
-    actors <- icb_events_long %>% filter(crisno %in% thiscrisis) %>% filter(varname_normalized %>% str_detect('actor')) %>% 
-              dplyr::select(value_normalized,value_qcode) %>% distinct()
-    #library(re2r) #didn't speed it up and enabling parallel was actually slower, not sure what's going on usually very fast
-    library(tictoc)
-    tictoc::tic() 
-    icews_clean_subset <- icews_clean %>% 
-                          mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() ) %>%
-                          filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
-                          unite('temp', country , target_name , target_country, where , 
-                                source_q_label_country,target_q_label_country,  source_label, target_label,who_a, who_b,province, district, city,
-                                na.rm = TRUE, remove = FALSE) %>% #this is probably slow need to check
-                          filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>% #this is slow and maybe replacing with re2r will fix
-                          unite('dyad_a', source_name ,  na.rm = TRUE, remove = FALSE) %>%
-                          unite('dyad_b', target_name ,  na.rm = TRUE, remove = FALSE) %>%
-                          mutate(dyad=paste0(dyad_a,"->",dyad_b)) %>%
-                          mutate(dyad_event=paste0(dyad, "_", cameo_label)) %>%
-                          mutate(dyad_penta_category=paste0(dyad, "_", cameo_penta_category)) %>%
-                          mutate(dyad_lv10=paste0(dyad, "_", cameo_lvl0_label)) %>%
-                          dplyr::select(-temp)
-    tictoc::toc() #85.212
-    dim(icews_clean_subset) #441,588 #586,406
-
-    #Penta
-    dyad_event_counts <-     icews_clean_subset  %>% 
-                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                             count(cameo_penta_category, dyad_penta_category) %>% 
-                             group_by(cameo_penta_category) %>%
-                             arrange(cameo_penta_category,  desc(n) ) %>% 
-                             filter(row_number()<=10) %>% ungroup()
-
-    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
-                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
-    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
-                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset
-
-    icews_clean_subset_top10 <- icews_clean_subset %>% 
-                                filter(dyad_penta_category %in% dyad_event_counts$dyad_penta_category  )
-
-    icews_clean_subset_top10_day <- icews_clean_subset_top10 %>%
-                                    mutate(story_date=paste(month, day, year, sep="/")) %>%
-                                    filter(!is.na(cameo_penta_category)) %>%
-                                    mutate(date = story_date %>% lubridate::mdy()) %>%
-                                    group_by(dyad_markdown=dyad, cameo_penta_category, date) %>% #rename dyad dyad_markdown here
-                                    summarise(mean_goldstein=mean(cameo_goldstein), n=n())
-
-    for(i in 1:nrow(names_to_qcodes)){
-      #print(i)
-      icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
-                                    dplyr::mutate(dyad_markdown = dyad_markdown %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
-    } #This is a bottleneck now and needs to move to after the group
-    library(ggtext)
-    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
-
-    p_icews_penta <-  icews_clean_subset_top10_day %>%
-            group_by(cameo_penta_category, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-            mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_penta_category)) %>%
-            ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
-            geom_tile() + theme_bw() +
-            tidytext::scale_y_reordered() +
-            geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
-            geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
-            facet_wrap(~cameo_penta_category, scale="free_y", ncol=1)  +
-            theme(plot.margin = unit(c(0,0,0,0), "cm")) + 
-            theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) + 
-            scale_fill_gradient2() +
-            theme(legend.position="none") +
-            ylab("") + xlab("")  #+
-            #geomtextpath::geom_textvline(xintercept = as.Date('2015-02-21'), label="MINSK II" , linetype="dotted", color = "red", size=3)  #+
-            #labs(subtitle=keys %>% paste(collapse="; "))
-
-    p_icews_penta %>% saveRDS(save_file_penta)
-
-    #lv0
-    dyad_event_counts <-     icews_clean_subset  %>% 
-                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                             count(cameo_lvl0_label, dyad_lv10) %>% 
-                             group_by(cameo_lvl0_label) %>%
-                             arrange(cameo_lvl0_label,  desc(n) ) %>% 
-                             filter(row_number()<=10) %>% ungroup()
-
-    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
-                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
-    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
-                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset
-
-    icews_clean_subset_top10 <- icews_clean_subset %>% 
-                                filter(dyad_lv10 %in% dyad_event_counts$dyad_lv10  ) %>%
-                                mutate(dyad_markdown=dyad)
-
-    dyad_unique <-     bind_rows(
-      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_a) %>% distinct(),
-      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_b) %>% distinct()
-    ) %>% distinct() %>% mutate(dyad_unique_markup = dyad_unique)
-
-    for(i in 1:nrow(names_to_qcodes)){
-      #print(i)
-      dyad_unique <- dyad_unique %>% dplyr::mutate(dyad_unique_markup = dyad_unique_markup %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
-      #print(head(dyad_unique,2))
-    }
-
-    icews_clean_subset_top10_day <- icews_clean_subset_top10 %>%
-                                    left_join(dyad_unique %>% dplyr::select(dyad_a=dyad_unique, dyad_a_markup=dyad_unique_markup) ) %>%
-                                    left_join(dyad_unique %>% dplyr::select(dyad_b=dyad_unique, dyad_b_markup=dyad_unique_markup) ) %>%
-                                    mutate(dyad_markdown=paste0(dyad_a_markup,"->",dyad_b_markup)) %>%
-                                    mutate(story_date=paste(month, day, year, sep="/")) %>%
-                                    filter(!is.na(cameo_lvl0_label)) %>%
-                                    mutate(date = story_date %>% lubridate::mdy()) %>%
-                                    group_by(dyad_markdown, cameo_lvl0_label, date) %>%
-                                    summarise(mean_goldstein=mean(cameo_goldstein), n=n())
-
-    library(ggtext)
-    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
-
-    p_icews_lv0 <-  icews_clean_subset_top10_day %>%
-            group_by(cameo_lvl0_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-            mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_lvl0_label)) %>%
-            ggplot( aes(x = date, y = dyad_markdown, fill = mean_goldstein)) +
-            geom_tile() + theme_bw() +
-            tidytext::scale_y_reordered() +
-            geomtextpath::geom_textvline(xintercept = as.Date(date_start), label="Crisis Start (ICB)" , linetype="dotted", color = "black", size=3) +
-            geomtextpath::geom_textvline(xintercept = as.Date(date_end), label="Crisis End (ICB)" , linetype="dotted", color = "black", size=3) +
-            facet_wrap(~cameo_lvl0_label, scale="free_y", ncol=3)  +
-            theme(plot.margin = unit(c(0,0,0,0), "cm")) +
-            theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ) +
-            scale_fill_gradient2() +
-            theme(legend.position="none") +
-            ylab("") + xlab("")
-
-    p_icews_lv0 %>% saveRDS(save_file_lv0)
-
-    #Make one more special grouping for the main paper
-    dyad_event_counts <-     icews_clean_subset  %>% 
-                             mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() )  %>%
-                             filter(story_date>=(date_start %>% as.Date()) & story_date<=(date_end %>% as.Date() )) %>%
-                             count(cameo_label, dyad_event) %>%  #down to the lowest level of aggregation
-                             group_by(cameo_label) %>%
-                             arrange(cameo_label,  desc(n) ) %>% 
-                             filter(row_number()<=10) %>% ungroup()
-
-    names_to_qcodes <- actor_translator %>% dplyr::select(QCode, contains("name")) %>%
-                       pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
-    names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
-                       arrange(desc(nchar(value))) #sort by length so you never accidentally replace a subset
-
-    icews_clean_subset_top10 <- icews_clean_subset %>% 
-                                filter(dyad_event %in% dyad_event_counts$dyad_event  ) %>%
-                                mutate(dyad_markdown=dyad)
-
-    dyad_unique <-     bind_rows(
-      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_a) %>% distinct(),
-      icews_clean_subset_top10 %>% dplyr::select(dyad_unique=dyad_b) %>% distinct()
-    ) %>% distinct() %>% mutate(dyad_unique_markup = dyad_unique)
-
-    for(i in 1:nrow(names_to_qcodes)){
-      #print(i)
-      dyad_unique <- dyad_unique %>% dplyr::mutate(dyad_unique_markup = dyad_unique_markup %>% str_replace_all(names_to_qcodes$value[i], names_to_qcodes$markdown[i]  ))
-      #print(head(dyad_unique,2))
-    }
-
-    icews_clean_subset_top10_day <- icews_clean_subset_top10 %>%
-                                    left_join(dyad_unique %>% dplyr::select(dyad_a=dyad_unique, dyad_a_markup=dyad_unique_markup) ) %>%
-                                    left_join(dyad_unique %>% dplyr::select(dyad_b=dyad_unique, dyad_b_markup=dyad_unique_markup) ) %>%
-                                    mutate(dyad_markdown=paste0(dyad_a_markup,"->",dyad_b_markup)) %>%
-                                    mutate(story_date=paste(month, day, year, sep="/")) %>%
-                                    filter(!is.na(cameo_label)) %>%
-                                    mutate(date = story_date %>% lubridate::mdy()) %>%
-                                    group_by(dyad_markdown, cameo_label, date) %>%
-                                    summarise(mean_goldstein=mean(cameo_goldstein), n=n())
-
-    library(ggtext)
-    icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
-    icews_clean_subset_top10_day %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")
-    #just out the tsv and plot how you want in the main paper
-
-}
-
-fromscratch=F
-if(fromscratch){
-  #done
-  #install.packages("arrow")
-  icews_clean <-  arrow::read_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )
-
-  c( 471) %>% sapply(FUN=function(x) icews_barmaps(x))
-}
-
-```
-
-```{r crisis 196, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icb_metro_plot_196.Rds')
-p_metro_plot <- readRDS(save_file)
-actor_colors <- p_metro_plot$actor_colors
-subtitle="ICB Dyadic Events"
-caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
-             ", p_metro_plot$labels$caption) #tag original to bottom
-
-p_196_icb <- p_metro_plot +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  labs(
-    #title = plot_title ,
-    #subtitle = subtitle ,
-    #caption = caption
-  )
-
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icb_metro_plot_196.Rds')
-p_metro_plot <- readRDS(save_file)
-p_196_phoenix <- p_metro_plot +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  labs(
-    #title = plot_title ,
-    #subtitle = subtitle ,
-    #caption = caption
-  )
-
-## MIDs
-library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_mids_metro_plot_196.Rds') 
-p_metro_plot <- readRDS(save_file)
-actor_colors <- p_metro_plot$actor_colors
-subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
-caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
-                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
-             ", p_metro_plot$labels$caption
-             ) #tag original to bottom
-p_196_mids <- p_metro_plot +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  labs(
-    #title = plot_title ,
-    #subtitle = subtitle ,
-    #caption = caption
-  ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
-#       plot = p_metro_plot ,
-#       width=12, height=14)
-
-## Phoenix Crisis Map
-#ICBe  196
-library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_phoenix_plot_penta_196.Rds')
-subtitle="Phoenix Dyadic Events"
-caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
-             ", p_metro_plot$labels$caption) #tag original to bottom
-
-p_196_phoenix <- readRDS(save_file) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      #caption = caption
-    )
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
-#       plot = p_metro_plot ,
-#       width=12, height=14)
-
-library(cowplot)
-p_196_combined <- 
-           plot_grid(
-            p_196_icb  +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-           scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
-           scale_y_continuous(expand = expansion(mult = c(0.15, 0.15))) ,
-
-           p_196_mids +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-           scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
-           scale_y_continuous(expand = expansion(mult = c(0.15, 0.15))) ,
-
-           p_196_phoenix +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") 
-           #scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
-           #scale_y_continuous(expand = expansion(mult = c(0.8, 0.2))) ,  
-           ,
-           labels = c('ICB','MIDs','Phoenix'), align = "h", ncol = 3 , rel_widths = c(1, 1,1) 
-)
-
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_196_combined.png'),
-          p_196_combined, base_height = 12, base_width = 20)
-#I'm just going to rotate on disk and load it as a normal figure
-#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
-```
-
-\begin{sideways}%[htbp]
-\centering{\includegraphics[width=21cm]{../figures/p_196_combined.png}}
-\end{sideways}
-\clearpage
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_196.Rds")
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
-            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
-```
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=21cm]{../figures/p_phoenix_plot_lv0_196.png}}
-\end{sidewaysfigure}
-\clearpage
-
-## Figure D4 Crisis Maps Crimea-Donbas
-
-\hphantom{em}
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-#\caption{Crisis Maps - Cuban Missile Crisis}
-#\captionof{figure}{Crisis Maps - Cuban Missile Crisis }
-#\caption{Crisis Maps - Cuban Missile Crisis \label{fig:p_196_combined}}
-#\begin{sidewaysfigure}[ht]
-#\end{sidewaysfigure}
-
-#Crisis maps for the non ICBe datasets for the two case studies
-
-library(ggplot2)
-library(cowplot)
-library(ggtext)
-
-## MIDs
-library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_mids_metro_plot_471.Rds') 
-p_metro_plot <- readRDS(save_file)
-actor_colors <- p_metro_plot$actor_colors
-subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
-caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
-                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
-             ", p_metro_plot$labels$caption
-             ) #tag original to bottom
-p_471_mids <- p_metro_plot +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  labs(
-    #title = plot_title ,
-    #subtitle = subtitle ,
-    #caption = caption
-  ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
-#       plot = p_metro_plot ,
-#       width=12, height=14)
-
-## Phoenix Crisis Map
-#ICBe  196
-library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_phoenix_plot_penta_471.Rds')
-subtitle="Phoenix Dyadic Events"
-caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
-             ", p_metro_plot$labels$caption) #tag original to bottom
-
-p_471_phoenix <- readRDS(save_file) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      #caption = caption
-    )
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
-#       plot = p_metro_plot ,
-#       width=12, height=14)
-
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_terrier_plot_penta_471.Rds')
-subtitle="Terrier Dyadic Events"
-caption=paste0("Data: Terrier (Grant et al. 2021)
-             ", p_metro_plot$labels$caption) #tag original to bottom
-
-p_471_terrier <- readRDS(save_file) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      #caption = caption
-    )
-
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icews_plot_penta_471.Rds')
-p_471_icews <- readRDS(save_file)
-
-library(cowplot)
-p_471_combined <- 
-           plot_grid(
-
-           p_471_mids +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-           scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
-           scale_y_continuous(expand = expansion(mult = c(0.15, 0.15))) + ylab('') ,
-
-           p_471_phoenix +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") + ylab('') , #+
-           #scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
-           #scale_y_continuous(expand = expansion(mult = c(0.8, 0.2))) ,
-
-           p_471_terrier +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") + ylab('') , #+
-           #scale_x_continuous(expand = expansion(mult = c(0.2, 0.2))) +
-           #scale_y_continuous(expand = expansion(mult = c(0.8, 0.2))) ,  
-           p_471_icews +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) + theme(legend.position="none") + ylab('') , #+
-
-           labels = c('MIDs','Phoenix', 'Terrier', 'ICEWs'), align = "h", ncol = 4 , rel_widths = c(1, 1,1,1) 
-)
-
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_471_combined.png'),
-          p_471_combined, base_height = 12, base_width = 25)
-
-```
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
-\centering{\includegraphics[width=21cm]{../figures/p_471_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_471.Rds")
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
-            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
-```
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{../figures/p_phoenix_plot_lv0_471.png}}
-\end{sidewaysfigure}
-\clearpage
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_terrier_plot_lv0_471.Rds")
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
-            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
-```
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{../figures/p_terrier_plot_lv0_471.png}}
-\end{sidewaysfigure}
-\clearpage
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_icews_plot_lv0_471.Rds")
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),
-            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
-```
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{../figures/p_icews_plot_lv0_471.png}}
-\end{sidewaysfigure}
-\clearpage
-
-# References
-
-\hphantom{em}

### 2022-07-17 replication_paper/rmd/SyntheticNarrative_Crimea.Rmd
v1.1

---
title: "Synthetic Narrative Crimea-Donbas"
output: html_document
date: '2022-04-26'
---

#Create a Crimea  Corpus

```{python, eval=F}

fromscratch=True
if fromscratch:
  from internetarchive import download
  #help(download)
  destdir="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/internetarchive/"
  from internetarchive import search_items
  search_results=search_items(query="Crimea Russia Ukraine 2014 ", full_text_search=True) #AND date:[2022-12-30 TO 2022-12-31]
  search_results=[q for q in search_results]
  import random
  random.shuffle(search_results)
  len(search_results)
  for q in search_results:
    try:
      download(identifier=q['fields']['identifier'][0] ,destdir=destdir , verbose=True, ignore_existing=True, glob_pattern="*.txt") #if you don't remove pdfs, it'll crash later because there's a 1.7gb pdf in there lol
    except:
      pass

```

```{r}

#Be sure to run to delete exactly dupe files just to save you time
#rdfind -deleteduplicates true *

library(reticulate)

#pip install -U pip setuptools wheel
#pip install -U spacy
#python -m spacy download en_core_web_sm
library(tidyverse)
library(rvest)

screen_rex <- function(x){
  return( x %>%
                    filter(text %>% str_detect("Crimea|crimea")) %>%
                    filter(text %>% str_detect("Russia|russia")) %>%
                    filter(text %>% str_detect("Ukraine|ukraine")) %>%
                    filter(text %>% str_detect("2014")) %>%
                    filter(text %>% str_detect("Donbas|donbas")) %>%
                    filter(text %>% str_detect("Putin")) %>%
                    filter(text %>% str_detect("Yanukovych|Poroshenko|Turchynov")) #Needs to have either leader  
  )
}
#delete duplicate files from the directory just to be sure
#rdfind -deleteduplicates true

library(googlesheets4) #Do this high up so you get the prompt early
crimea_doc <- read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", 
                                sheet="CrimeaDonbass") %>% janitor::clean_names()
dim(crimea_doc) #126

#Factiva are rtf
#It was so slow that it was easier for me to just open them and save as txt
files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/factiva/", full.names = T, recursive = T,pattern="*.txt")
factiva_list <- list()
for(file in files){
  file_df <- file %>% read_lines() %>% as.data.frame()%>% setNames("text") %>% mutate(url=ifelse(text %>% str_detect("^Document "), text, NA )) %>% 
          tidyr::fill(url, .direction="up") %>% filter(!is.na(text) & text!='') %>% 
          group_by(url) %>%
          mutate(text=text %>% paste("\n")) %>%
          screen_rex()
  factiva_list[[file]] <- file_df
}
crimea_factiva <- bind_rows(factiva_list)
dim(crimea_factiva) #2 #233

#C4
#You have to do it like this otherwise you have to track the URLs of downloaded files too which is a headache and not all of them are still live
#https://c4-search.apps.allenai.org/?q=%2BCrimea+%2BRussia+%2BUkraine+%2B2014
files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/c4/",   , full.names = T, recursive = T,pattern="*.html")
c4_list <- list()
for(file in files){
  df <- data.frame(text=file %>% read_html %>% html_text )  %>% 
        mutate(text = strsplit(as.character(text), "\n")) %>% 
        unnest(text) %>%
        mutate(text=text %>% trimws()) %>%
        filter(text!='') %>%
        mutate(url=ifelse(text %>% str_detect('http'), text, NA )) %>%
        tidyr::fill(url) %>%
        filter(text!=url) %>% filter(!is.na(url)) %>% 
        group_by(url) %>%
        summarise(text=paste(text, collapse="\n")) %>%
        screen_rex() %>%
        mutate_all(as.character)
  c4_list[[file]] <- df
}
crimea_c4 <- bind_rows(c4_list)   %>% screen_rex()
dim(crimea_c4) #717 #425 #7492

#library(spacyr)
#spacy_install()
#spacy_download_langmodel("en")
#spacy_initialize()
#cuban_missile_clean_sentences <- spacy_parse(cuban_missile_clean$text, full_parse=F)
#dim(cuban_missile_clean_sentences)

#install.packages("pdftools")
#sudo add-apt-repository -y ppa:cran/poppler
#sudo apt-get update
#sudo apt-get install -y libpoppler-cpp-dev

files <- list.files(path = "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/",
                     pattern = "*.pdf$", all.files = FALSE,
            full.names = T, recursive = T,
            ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
library(pdftools)
pdf_text_list <- list()
for(file in files){
   outfile <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/text/{file %>% basename()}.txt")
   #print(file)
   if(!file.exists(outfile)){
      print(file)
      try({ suppressMessages(pdftools::pdf_text(file)) %>% unlist() %>% paste(collapse="\n ") %>% writeLines(con=outfile)   } )
   }
}

# 
#IA
#install.packages('readtext')
#https://cran.r-project.org/web/packages/readtext/vignettes/readtext_vignette.html#introduction
#The IA texts tend to be very large with lots of irrelevant so we the textreadr package for speed
#There are 70k texts, most are irrelevant. Screen them once here, and then screen some more and then save them compressed
#library(readtext)
#install.packages('textreadr')

command1 <- "cd '/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/internetarchive/' ; grep -l -r Crimea"
check1 <- system(command1, intern = T)
length(check1)
command2 <- "cd '/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/internetarchive/' ; grep -l -r Yanukovych"
check2 <- system(command2, intern = T)
length(check2)
command3 <- "cd '/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/internetarchive/' ; grep -l -r 2014"
check3 <- system(command3, intern = T)
length(check3)
command4 <- "cd '/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/internetarchive/' ; grep -l -r Russia"
check4 <- system(command4, intern = T)
length(check4)

checks <- intersect(intersect(intersect(check1, check2), check3), check4)
length(checks)
files_ia = "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/internetarchive/" %>% paste0(checks)

files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/loose_html", full.names = T, recursive = T,pattern="*.htm|*.html")
length(files)
loose_list <- list()
for(file in files){
   outfile <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/text/{file %>% basename()}.txt")
   #print(file)
   if(!file.exists(outfile)){
      print(file)
       try({
        file %>% read_html %>% html_text %>% writeLines(con=outfile) #it produces a lot of nontext garbage fyi
        })
   }
}

files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/crimea/text", full.names = T, recursive = T,pattern="*.txt$")
files <- c(files, files_ia)
length(files)
loose_list_text <- list()
for(file in files){
  try({
    df <- data.frame(text=file %>% readLines() %>% paste(collapse="\n"))  %>%
          mutate(url=file) %>%
          screen_rex()
    loose_list_text[[file]] <- df
  })
}
crimea_loose_list_text <- bind_rows(loose_list_text) %>%
  group_by(url) %>%
  summarise(text=paste(text, collapse="\n"))  %>% screen_rex()
dim(crimea_loose_list_text) #635 #6816

# "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban//zotero/7LU24CRX/filename.pdf" %>% str_replace(".*/(.*?.pdf)","\\1")
crimea <- bind_rows(
  #cuban_missile_pdfs %>%
  #mutate(url=url %>% str_replace(".*/(.*?.pdf)","\\1")) %>% 
  #         filter(!duplicated(url %>% tolower())) %>% filter(!duplicated(text %>% tolower() %>% trimws())),
  crimea_doc,
  crimea_factiva,
  crimea_c4,
  crimea_loose, #loose html
  crimea_loose_list_text #includes pdf and IA now
)   %>% screen_rex() 
dim(crimea) #1656 #1075 #14647 #14646 #7813 #4481 #321

"Second, the case is relatively well documented:in additionto the famous ExComm tapes (May and Zelikow 1997), declassification of the written recordhas been extensive." %>% str_replace_all("\\(.*?\\)","")

"asdfasdf (sdfasdf) asdadsasd" %>% str_replace_all("\\(.*?\\)","")
"asdfasdf [1-10] asdadsasd" %>% str_replace_all("\\[.*?\\]","")
"John F. Kennedy" %>% str_replace_all("( [A-Z])\\.","\\1")
"Cuban armed assistance to subversion in other parts of the Western Hemisphere. f." %>% str_replace_all(" [a-z]\\.","")
"Cuban armed assistance to subversion in other parts of the Western Hemisphere.1" %>% str_replace_all("([a-z]\\.) *[0-9]{1,2}","\\1")
"U.S. president Dwight D. Eisenhower (1890–1969; served 1953–61) halted U.S. importation of Cuban sugar" %>%
                                    str_replace_all("( [A-Z])\\. ","\\1 ")

"U.S. president Dwight D. Eisenhower (1890–1969; served 1953–61) halted U.S. importation of Cuban sugar" %>%
                                    str_replace_all("U\\.S\\. | US "," United States ")

"sasadfasdffds.1 asdfasdf" %>% str_replace_all("\\.[0-9] ","\\. ")
library(cld3); #install.packages('cld3')
crimea_clean <- crimea %>% ungroup() %>%
                       janitor::clean_names() %>%
                        mutate(text_nchar= text %>% nchar() ) %>% #there should never be an exact character count
                        filter(text_nchar>1000 & text_nchar<500000) %>%  #for some reason the length is much shorter, median 383
                        ungroup() %>% filter(!duplicated(text_nchar)) %>%
                        mutate(n_crimea = text %>% stringr::str_count(pattern = fixed("Crimea")) ) %>% #surprisingly it's not a lot of one offs, most seem to be about it
                        mutate(n_russia = text %>% stringr::str_count(pattern = fixed("Russia")) ) %>%
                       mutate(text= text %>% 
                                    str_replace_all("\\(.*?\\)","") %>% #parentheticals
                                    str_replace_all("\\[.*?\\]","") %>% #brackets citations
                                    str_replace_all("U\\.S\\. | US "," United States ") %>%
                                    str_replace_all("U\\.N\\. "," United Nations ") %>%
                                    str_replace_all("( [A-Z])\\. ","\\1 ") %>% #middle names
                                    str_replace_all(" [a-z]\\.","") %>% 
                                    str_replace_all("([a-z]\\.) *[0-9]{1,2}","\\1")  %>% 
                                    str_replace_all("Mr\\.","Mr ")  %>% 
                                    str_replace_all(" {3,}","\n")  %>%  
                                    str_replace_all("\\.[0-9] ","\\. ")  %>% 
                                    str_replace_all("  "," ") 
                        ) %>%
                        mutate(langauge=cld3::detect_language(text)) %>% 
                        filter(langauge=='en') 
table(crimea_clean$langauge) %>% sort()
hist(crimea_clean$text_nchar %>% log(), breaks=50)
table(crimea_clean$text_nchar) %>% sort()
dim(crimea_clean) #781 #8451 #8452 #10214 #1,636

#https://github.com/dselivanov/LSHR
library(devtools)
#install_github("dselivanov/LSHR")
library(LSHR) #install.packages('LSHR')
#devtools::install_github('dselivanov/text2vec')
library(text2vec)
it <- itoken(crimea_clean$text, preprocess_function = tolower, tokenizer = word_tokenizer)
dtm <- create_dtm(it, hash_vectorizer())
dtm = as(dtm, "RsparseMatrix")
hashfun_number = 120
s_curve <- get_s_curve(hashfun_number, n_bands_min = 5, n_rows_per_band_min = 5)
s_curve %>% ggplot(aes(x=similarity, y=probability_become_candidate, color=paste(n_bands,n_rows_per_band))) + geom_line()
seed = 1
pairs = get_similar_pairs(dtm, bands_number = 6, rows_per_band = 20, distance = 'cosine', seed = seed)
pairs[order(-N)]
temp <- pairs %>% filter(N==5) %>%
  mutate(id1_new =  ifelse(id1<id2, id1, id2) ) %>%
  mutate(id2_new =  ifelse(id1<id2, id2, id1) )
dim(temp) #now only 18 dupes
temp$a <- substr( crimea_clean$text[temp$id1_new],  1, 200)
temp$b <- substr( crimea_clean$text[temp$id2_new],  1, 200)

"https://doi.org/10.2307/2009577"
"Document: President Kennedy's statement on Soviet military" %>% str_replace_all("^.*?: ","")
"The discussion of the crisis by ExComm members shows awareness of and sensitivity to domestic political considerationsin the selection of the initial United States response to the Soviet missiles." %>% str_detect("[a-z0-9]\\.$")
'It can use them and it must not be treated lightly"; Khrushchev, cited in Abel, 191-92.' %>% str_detect(" [0-9]{3}(\\–|\\-)")
"On the Turkish issue, he faults Kennedy's refusal of the quid pro quo, since Kennedy had known for some time that our missiles in Turkey were obsolete; Stone, 21-22.
" %>% str_detect(" [0-9]{2,3}(\\–|\\-)[0-9]{2,3}")
"On April 12, 1961, the Soviets again led the way with the launch of Yuri Gagarin, a Russian cosmo¬ naut, into space to become the first human to leave Earth." %>% str_replace_all("- |¬ ","")
#install.packages('tidytext')
library(tidytext)
index <- setdiff(1:nrow(crimea_clean), temp$id2_new %>% unique())
crimea_clean_sentences <- crimea_clean[index,] %>% 
                                 ungroup() %>%
                                 mutate(text= text %>% str_replace_all("\n","  ") ) %>% #because pdfs are often parsed line by line
                                 mutate(text= text %>% str_replace_all(" {1,}"," ") ) %>%
                                 unnest_tokens(sentence, text, token="sentences", drop=T, to_lower=F) %>%
                                 mutate(sentence= sentence %>% str_replace_all("^.*?: ","") ) %>%
                                 mutate(sentence= sentence %>% str_replace_all("- |¬ ","") ) %>% #words broken across pages
                                 mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                                 mutate(sentence_nchar=sentence %>% nchar()) %>%
                                 mutate(sentence= sentence %>% trimws()) %>%
                                 filter(sentence_nchar>70 & sentence_nchar<600) %>%
                                 filter(!str_detect(sentence, "downloaded|Downloaded|Table|Figure|University|pp\\.|New York| file | [0-9]{3} | [0-9]{3}(\\–|\\-)|Box |IEEE|Memorandum|Transcript|Telegram|Kew Gardens| [0-9]{2,3}(\\–|\\-)[0-9]{2,3}|CHAPTER| cited|=|Cuban Missile Crisis|Book|Copyright|FRUS|http|JSTOR|researchers|archival|scholarship|recordings|File|Foreign Relations of the United States|Printing Office|Document|Minutes of|Summary|Record|vol\\.|No\\.|Issue|Paper|à| et | est |United States Government|American Foreign Policy|FO |PREM| box|Part| et | est |Acknowledgements|website|cookies|Privacy|©")) %>%
                                 mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                                 filter(sentence %>% str_detect("^[A-Z]")) %>% #has at least one capital letter
                                 filter(sentence %>% str_detect("[a-z0-9]\\.$")) %>% #ends in a letter/number and a period no questions
                                 #add_count(sentence) %>%
                                 ungroup() %>%
                                 mutate(dupe= sentence %>% tolower() %>% str_replace_all("[^a-z]","") %>% duplicated() ) %>%
                                 filter(!dupe) %>% #restrict to unique sentences
                                 group_by(url) %>%  
                                   mutate(sentence_n = n() ) %>% 
                                   mutate(sentence_number= row_number() ) %>%
                                   mutate(position= row_number()/n()) %>%
                                 ungroup() %>%
                                 filter(sentence_n<=20000 ) %>%
                                 filter(sentence_n>=10 ) #require at least 10 unique sentences per source

crimea_clean_sentences$sentence %>% tolower() %>% duplicated() %>% table()
dim(crimea_clean_sentences) #177,303 #153,580 #7882

#Less than 600 and greater than 50
hist(crimea_clean_sentences$sentence_nchar[crimea_clean_sentences$sentence_nchar], 60)
summary(crimea_clean_sentences$sentence_nchar) #Interquartile is 111 to 200

crimea_clean_sentences  %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_clean_sentences.tsv")
dim(crimea_clean_sentences) #177148 #1,566,467 #197,981 #115,146 #10074

```

```{r}

library(tidyverse)
crimea_clean_sentences <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_clean_sentences.tsv")

crimea_clean_sentences$url %>% unique() %>% length() #1,218 #993 #1568 #881 #999 #464 #558 unique sources #646 sources so far
crimea_clean_sentences$url %>% table() %>% as.vector() %>% summary() #median of 37 sentences per

crimea_clean_sentences_unique <- crimea_clean_sentences$sentence %>% unique()
length(crimea_clean_sentences_unique) #10075

#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
#    71     102     136     154     185     599     338 
summary(crimea_clean_sentences$sentence_nchar %>% as.numeric())
nchar("The Soviet commander in Cuba was authorised to use tactical nuclear weapons against United States forces should they invade, and as Soviet missiles were already installed, any attack on Cuba could have led to the outbreak of nuclear war.")
nchar("Soviet commander in Cuba authorised to use tactical nuclear weapons against U.S. forces if they invaded.") #104
nchar("Any attack on Cuba could have led to the outbreak of nuclear war.")

#Write out a folder of sentences to iterate over and summaries

#We save seperate files by url so we can parallize
dim(crimea_clean_sentences) #1,566,847 #this is so big now it's becoming slow to write out files
library(digest)
library(data.table)
crimea_clean_sentences_dt <- as.data.table(crimea_clean_sentences)
for(q in crimea_clean_sentences$url %>% unique() ) {

  outfile <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_original_crimea/{digest(q,'crc32')}.txt")

  if(!file.exists(outfile) ){
    print(outfile)
    writeLines( text=crimea_clean_sentences_dt[url==q,,]$sentence , con=outfile)
  }

}

```

Create additional simplified sentences

This takes the 3090 Ti more than all night to run alone

```{python}

import torch
use_cuda = torch.cuda.is_available()
if use_cuda:
    print('__CUDNN VERSION:', torch.backends.cudnn.version())
    print('__Number CUDA Devices:', torch.cuda.device_count())
    print('__CUDA Device Name:',torch.cuda.get_device_name(0))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)

import random
import os
from tqdm.auto import tqdm
import pandas as pd
from transformers import pipeline
from transformers.pipelines.pt_utils import KeyDataset
#I'm going to switch to a smaller model which is faster
#https://huggingface.co/sshleifer/distilbart-cnn-12-6
summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-6-6") #1 for small gpu 0 for big distilbart-cnn-12-6 #
from datasets import load_dataset
#What if we did it by url? Then we don't need to keep track of which sentences worked and didn't and if it fails we just lose one doc
directory="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_original_crimea/"
out_directory="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_sum_crimea/"
from os.path import exists
from datasets import Dataset
files=os.listdir(directory)
random.shuffle(files) #it's in place
for filename in files: #we use this hack here to keep from having to keep a lock file. Chances of both picking the same file very small unless towards the last few
    f_in = os.path.join(directory, filename)
    f_out=os.path.join(out_directory, filename)
    if not exists(f_out): #I'm eventually going to have to write a try for the one that fails on us
        my_file = open(f_in, "r")
        df = pd.DataFrame({"text": my_file.readlines() })
        dataset = Dataset.from_pandas(df ) #.head(1)
        results=[out for out in summarizer_distilbart(KeyDataset(dataset, "text"), num_beams=4, min_length=10, max_length=60, length_penalty=100.0, batch_size=32)] #32 was fastest
        #dataset = load_dataset('text', data_files={'train': [f_in]}, split="train") #same speed either way
        with open(f_out, 'w') as f:
          _ = f.write('\n'.join([q[0]['summary_text'] for q in results]))

```

Load the simplified sentences and add them to the pile

```{r}

#330,140 ok so not only have I only done half, I've also somehow not even done a third of all sentences

files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_sum_crimea/", full.names = T)
length(files)
sentences_sum_list <- list()
for(file in files){
  try({
    filename = basename(file)
    df=data.frame(sentence=readLines(file))
    df$url_hash <- filename %>% str_replace(".txt",'')
    sentences_sum_list[[file]] <- df
  })
}

library(digest)
url_hash_df <- crimea_clean_sentences %>% dplyr::select(url) %>% distinct() %>% rowwise() %>% mutate(url_hash=digest(url,'crc32')) %>% ungroup()

library(tidytext)
sentences_sum_df <- bind_rows(sentences_sum_list) %>%
                    left_join(url_hash_df) %>%
                     mutate(sentence=sentence %>% str_replace_all(" {1,}\\.",".") ) %>% #after summarizing it puts a space before the final punctuation
                     ungroup() %>%
                     mutate(sentence= sentence %>% str_replace_all("\n","  ") ) %>% #because pdfs are often parsed line by line
                     mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") ) %>% 
                     unnest_tokens(sentence, sentence, token="sentences", drop=T, to_lower=F) %>%
                     mutate(sentence= sentence %>% str_replace_all("^.*?: ","") ) %>%
                     mutate(sentence= sentence %>% str_replace_all("- |¬ ","") ) %>% #words broken across pages
                     mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                     mutate(sentence_nchar=sentence %>% nchar()) %>%
                     mutate(sentence= sentence %>% trimws()) %>%
                     filter(sentence_nchar>70 & sentence_nchar<600) %>%
                     filter(!str_detect(sentence, "downloaded|Downloaded|Table|Figure|University|pp\\.|New York| file | [0-9]{3} | [0-9]{3}(\\–|\\-)|Box |IEEE|Memorandum|Transcript|Telegram|Kew Gardens| [0-9]{2,3}(\\–|\\-)[0-9]{2,3}|CHAPTER| cited|=|Cuban Missile Crisis|Book|Copyright|FRUS|http|JSTOR|researchers|archival|scholarship|recordings|File|Foreign Relations of the United States|Printing Office|Document|Minutes of|Summary|Record|vol\\.|No\\.|Issue|Paper|à| et | est |United States Government|American Foreign Policy|FO |PREM| box|Part| et | est |Acknowledgements|website|cookies|Privacy")) %>%
                     mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                     filter(sentence %>% str_detect("^[A-Z]")) %>% #has at least one capital letter
                     filter(sentence %>% str_detect("[a-z0-9]\\.$")) %>% #ends in a letter/number and a period no questions
                     #add_count(sentence) %>%
                     ungroup() %>%
                     mutate(dupe= sentence %>% tolower() %>% str_replace_all("[^a-z]","") %>% duplicated() ) %>%
                     filter(!dupe)
dim(sentences_sum_df) #796,090

crimea_clean_sentences_withsum <- 
  bind_rows(crimea_clean_sentences %>% dplyr::select(url, sentence),
            sentences_sum_df %>% dplyr::select(url, sentence) ) %>%
       mutate(dupe= sentence %>% tolower() %>% str_replace_all("[^a-z]","") %>% duplicated() ) %>%
       filter(!dupe)
dim(crimea_clean_sentences_withsum) #3,080,369 #21437

#
crimea_clean_sentences_withsum %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_clean_sentences_withsum.tsv")

```

```{r}

crimea_clean_sentences <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_clean_sentences.tsv")

crimea_clean_sentences_withsum <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_clean_sentences_withsum.tsv") %>%
  rowwise() %>%
    mutate(url_hash= digest(url, 'crc32') ) %>%
  ungroup() %>%
  mutate(url_int=url %>% as.factor() %>% as.integer())

```

```{python}

#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers
import pickle
import numpy as np
from sentence_transformers import SentenceTransformer
fromscratch=True
if fromscratch:
  sentences=np.array(r.crimea_clean_sentences_withsum.sentence) #sentences_unique_sanitized
  url_ints = np.array(r.crimea_clean_sentences_withsum.url_int.values)
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #3,080,369
  n=len(sentences)
  chunk_length=200
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2') 
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/paraphrase-MiniLM-L6-v2')
  #
  #https://www.sbert.net/examples/applications/paraphrase-mining/README.html
  from sentence_transformers import SentenceTransformer, util
  #I don't know why but I had to set the query chunk size to smaller for it to work. I think it was silently failing.
  #sentences.shape 79,851  sentences, so 6,376,182,201 possible comparisons
  #We want a greedy matching across documents, pick a sentence, find its top pair in the next document, and so on
  #
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks]).astype('float32')  #This is what takes a whle #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #1,267,675 #124,808 #78225
  d=sentences_embeddings.shape[1]
  import faiss
  faiss.omp_set_num_threads(64)
  faiss.normalize_L2(sentences_embeddings) #If you normalize then you do get the right
  # build a flat (CPU) index
  index_flat = faiss.IndexFlatIP(d) #make sure you use IP so you get cosine distance https://github.com/facebookresearch/faiss/issues/95
  # make it into a gpu index
  #https://github.com/facebookresearch/faiss/wiki/Running-on-GPUs
  res = faiss.StandardGpuResources()  # use a single GPU
  gpu_index_flat = faiss.index_cpu_to_gpu(res, 0, index_flat)  
  gpu_index_flat.add(sentences_embeddings)
  k = 30   #it runs out of memory with 600k times 50. 30 works. #You can do 25 and miss almost no pairs over 0.9
  D, I = gpu_index_flat.search(sentences_embeddings, k)  #With a million this is no longer instant but it is going hard
  np.quantile( D[:,0], [0.01,0.05,0.1,0.5,0.9,0.95,0.99] ) #should be all 1s ish
  #1568 articles. If they were all identical that would mean for each sentence there would be 1568 other matches and no others so 1568*number of sentences on average (37) 58,016
  #58016/124808 #0.46% is then the upper bound, it's actually much smaller. There are so many pairings it's like 0.0000037 of pairs would be matches if it was just the same doc over and over
  np.quantile( D[:,1], [0.01,0.05,0.1,0.5,0.9,0.95,0.99] ) #We have to decide something here about what our prior is on how many paraphrased sentences there should be in a corpus. 0.95 would mean 1 in 20
  condition=D[:,1:]>=0.87 #0.87 
  np.sum(condition) #56,447 #28,189 #7809 or 3904.5 pairs  #1460 #6,240,376 #2,496,146 #1,248,071 #624,036
  A=np.where(condition)[0]
  A_id=url_ints[A]
  B=I[:,1:][condition]
  B_id=url_ints[B]
  condition2 = A_id != B_id #add a second condition where we require both nodes to live in different url_hash which should be an integer
  sum(condition2) #170,404
  edges=np.transpose(np.vstack([A,B]))[condition2,:]
  weights=D[:,1:][condition][condition2]
  vertices=np.unique(np.hstack([edges[:,0],edges[:,1]]))
  #
  #ids_strongly = np.unique(np.hstack([paraphrases_strongly[:,1],paraphrases_strongly[:,2]] ) ).astype("int")
  #ids_strongly = np.setxor1d(ids_strongly,list(dead)).astype("int")
  #sentences_strongly = sentences[ids_strongly]
  #sentences_embeddings_strongly = sentences_embeddings[ids_strongly,:]
  #sentences_embeddings_strongly.shape #78,225 #78,474
  #paraphrases_strongly = util.paraphrase_mining(model, sentences_strongly, show_progress_bar=True, top_k=300, batch_size=128, query_chunk_size=1000, max_pairs=30000000) 
  #paraphrases_strongly_array=   np.vstack(paraphrases_strongly)
  #paraphrases_strongly_array = paraphrases_strongly_array[paraphrases_strongly_array[:,0]>0.70, :] #require a certain proximity
  #paraphrases_strongly_array.shape
  #subset=np.sort( np.unique( np.hstack([paraphrases_strongly_array[:,1],paraphrases_strongly_array[:,2]]) ) ).astype('int')
  #sentences_strongly=sentences_strongly[subset,]
  #sentences_embeddings_strongly=sentences_embeddings_strongly[subset,]
  #sentences_embeddings_strongly.shape
  #
  import igraph
  import pandas as pd
  edges_df=pd.DataFrame(edges.astype('int')) #
  edges_df['weights']=weights
  edges_df['from']=edges_df[0]
  edges_df['to']=edges_df[1]
  condition=edges_df[0]<edges_df[1]
  edges_df['from'][condition]=edges_df[1][condition]
  edges_df['to'][condition]=edges_df[0][condition]
  edges_df=edges_df[['from','to','weights']].drop_duplicates()
  #
  #  
  g = igraph.Graph.DataFrame(edges_df, directed=False) #.simplify()
  g.es.attribute_names()
  len(g.es) #92,800
  len(g.vs)  #55,831 #47,846 #32,258 #32,916 #47363 #32916 nodes
  clustered=igraph.Graph.community_fastgreedy(g, weights=edges_df.weights.values ) # #wow did pretty well #weights=paraphrases_strongly[:,0]
  clustered.optimal_count
  clustered_cuts=clustered.as_clustering()
  len(clustered_cuts.membership) #32916 #ok so it cut 2824 sentences into 1269 clusters
  import scipy
  tabs=scipy.stats.contingency.crosstab(clustered_cuts.membership)
  #with np.printoptions(threshold=np.inf):
  #  print(np.sort(tabs[1])) #ok so there are a few big ones but mostly very small
  #
  import numpy as np
  import pandas as pd
  import matplotlib.pyplot as plt
  import genieclust
  import sklearn
  import umap
  x_train= sklearn.preprocessing.scale(sentences_embeddings[vertices,:]) #[0:10000,] #I think we have to scale it so euclidian distance is the same as cosine #_strongly
  x_train.shape
  x_train_umap = umap.UMAP().fit_transform(x_train) #
  #
  import fastcluster
  #clusters_ward = fastcluster.ward(x_train)
  from scipy.cluster.hierarchy import dendrogram
  #linkage = fastcluster.linkage_vector(x_train, method='ward', metric='euclidean')
  #labels = hierarchy.fcluster(linkage._Z, t=0.02, criterion='distance') - 1
  #dendrogram = hierarchy.dendrogram(linkage, no_plot=True, color_threshold=-np.inf)
  #                      
  #X=x_train                 
  #import scipy.cluster.hierarchy
  #g = genieclust.Genie(compute_full_tree=True)
  #g.fit(X)
  #linkage_matrix = np.column_stack([g.children_, g.distances_, g.counts_])
  #scipy.cluster.hierarchy.dendrogram(linkage_matrix,
  #    show_leaf_counts=False, no_labels=True)
  #plt.show()
  #g = genieclust.Genie(n_clusters=500, exact = True, compute_full_tree=False, affinity='cosinesimil', verbose=True) #, M=3
  #labels_genie = g.fit_predict(x_train) #it assigns non clusters to 0
  #np.max(labels_genie)
  #
  from plotnine import ggplot, geom_point, aes, stat_smooth, facet_wrap
  import pandas as pd
  x_train_umap_df=pd.DataFrame(x_train_umap, columns=['X','Y'])
  #x_train_umap_df['labels_genie']=labels_genie
  x_train_umap_df['labels_community_fastgreedy']=clustered_cuts.membership
  #x_train_umap_df['labels_genie_pos']=labels_genie>0
  #x_train_umap_df['labels_genie_noise']=labels_genie<0
  x_train_umap_df['sentence']=sentences[vertices]
  x_train_umap_df['labels']=x_train_umap_df['labels_community_fastgreedy']
  (ggplot(x_train_umap_df, aes('X', 'Y', color='factor(labels_community_fastgreedy)' )  ) + geom_point(size=0.1, show_legend=False)   ) #it just runs out of colors
  #
  #genieclust.plots.plot_scatter(x_train_umap, labels=labels_genie, alpha=0.5)
  #plt.title("(n=%d, true n_clusters=%d)" % (X.shape[0], n_clusters))
  #plt.axis("equal")
  #plt.show()
  #
  #(ggplot(x_train_umap_df, aes('X', 'Y', color='factor(labels_genie_noise)' )  ) + geom_point(size=0.1, show_legend=False)   )
  #
  #paraphrases_array.shape
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  #clusters = util.community_detection(sentences_embeddings, min_community_size=25, threshold=0.75) #if this is working, it's too slow to tell
  #
  #with open("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/x_train_umap_df.pickle", "wb") as outfile:
  # 	# "wb" argument opens the file in binary mode
  #pickle.dump(x_train_umap_df, outfile)
#
#

```

```{r}

#x_train= py$x_train
#library('fastcluster')
#hc <- hclust.vector(x_train, method="ward", members=NULL, metric='euclidean', p=NULL)
#g = genieclust.Genie(compute_full_tree=True)

#install.packages('genieclust')
#library(genieclust)
#?gclust

#install.packages('gputools')
library(reticulate)
library(tidyverse)
crimea_clean_sentences_withsum_clustered <- crimea_clean_sentences_withsum %>% left_join(py$x_train_umap_df)
dim(crimea_clean_sentences_withsum_clustered) #1,267,675 #648493
crimea_clean_sentences_withsum_clustered %>% pull(url) %>% unique()  %>% length() #1995 #1,998

crimea_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>=0) %>% pull(labels) %>% table()  %>% table()

crimea_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>=0) %>% pull(labels) %>% table() %>%  sort() %>% tail(10)

crimea_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>0) %>% pull(labels) %>% table() %>% as.vector() %>% summary()

crimea_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>0) %>% pull(labels) %>% table() %>% as.vector() %>% table()

crimea_case_study_events <- crimea_clean_sentences_withsum_clustered  %>%
                            filter(!is.na(labels) & labels>=0) %>% #-1 are the noise ones
                            group_by(labels) %>%
                            summarise(
                              n_sources=url %>% unique() %>% length(),
                              sentence= sentence %>% paste(collapse="\n")#,
                              #position=median(position) %>% round(2) #we lost position but I was coding date by hand anyway now so
                              ) %>%
                            #arrange(n_sources %>% desc() ) %>%
                            arrange(n_sources) %>%
                            filter(n_sources>=5)
dim(crimea_case_study_events) #410

table(crimea_case_study_events$n_sources)

crimea_case_study_events$sentence %>% str_detect("defcon|DEFCON") %>% table()

table(crimea_case_study_events$n_sources)

crimea_case_study_events  %>% write_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_case_study_events.csv") #summarization failed but otherwise good to go

```

```{python}

import pandas as pd
from transformers import pipeline
#summarizer = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
#summarizer = pipeline("summarization", device=0, model="sshleifer/distilbart-xsum-12-6") #noooooo
txt="All major United States mi]itary commands were placed on DEFCON-3 on 22 October, with SAC moving to DEFCON-2 on 24 October. It now appears that the commander of United States Air Forces Europe, General Truman Landon, ordered numerous operational activities commensurate with DEFCON-3 alert status, including increasing the number of nuclear- armed aircraft on Quick Reaction Alert .73 Additionally, the alert status  of the IRBMs in Britain and Italy was at fifteen minutes readiness and the British V-bomber force was brought to a high state of ground alert. In times of peace the United States armed forces are usually on DefCon5. Following this meeting Harkness presented Diefenbaker with a report showing that the United States military had moved to DEFCON 2, meaning the Americans were making immediate preparations for war. United States forces went from \"peace alert to Defcon 3 (war alert), and strategic air command Defcon 2\" , five divisions of armed strategic reserves were placed on alert. Tactical strike aircraft in Florida maintained high levels of alert, anywhere from pilots in their cockpits ready to launch to as long as a thirty- minute alert. TAC forces in Florida assumed a one-hour alert and prepared to go to a fifteen-minute alert, which involved pilots waiting in aircraft for launch orders. On October 22 United States armed forces moved to DEFCON-3, a height-  ened state of alert, upgraded to DEFCON-2, only one level short of war,  on October 25. On October 26, he learned that the Pentagon had moved United States forces from DEFCON 5, peacetime status, to DEFCON 2, just one away from war, and that United States hospitals had been ordered to prepare to receive casualties. Military forces of both nations were placed on maximum alert and United States nuclear bombers were ordered into the air. For the first and only time in its existence, the Strategic Air Command had been ordered to Defcom 2 status, one step short of all-out war. Harkness returned to his office and learned that parts of the United States military had raised their alert status to DEFCON 2, meaning that an imminent attack was now expected. Squadrons of B-52 nuclear bombers lifted off from their bases to join the Strategic Air Command's airborne alert as a precaution against surprise attack. On 24 October the United States' Strategic Air Command was placed on DEFCON- 2, a state of alert denoting readiness for combat. A high alert was immediately announced for air forces to bomb the exile troop's ships. Until  20 November, the United States Strategic Air Command remained on alert at  Defence Condition 2 , other  forces were held at DefCon 3, and the naval quarantine was maintained in  place. DEFCON ranged from DEFCON 5, which was simple preparedness, to DEFCON 1, which was the most serious alert of all, the DEFCON for war. A massive airborne alert was begun by U.S.- based B-52 bombers which were loaded with nuclear weapons and by KC-135 tankers. Bombers, especially the new B-52s, provided a much more reliable way of delivering nuclear weapons against Soviet targets than ICBMs, but they are slow and—if detected as they approached Soviet air space—would allow the Soviets to launch air defense aircraft as well as launch or disperse their nuclear forces. On the morning of October 24, the United States quarantine went into place, and the United States military went to DEFCON 2, the last level before nuclear war. U.S. military forces worldwide, with the exception of the United States Air Forces in Europe , are placed on DEFCON 3. ICBM missile crews are alerted and Polaris nuclear submarines in port are dispatched to preassigned stations at sea. DEFCON 3 means an increase in readiness above normal levels, specifically that air forces are ready to deploy in 15 minutes. The United States Strategic Air Command placed all its B-52 intercontinental bombers on 15-minute takeoff alert on October 20; on October 22, it placed them on a revolving airborne alert, with a percentage of bombers airborne at all times, ready to head over the North Pole toward the Soviet Union. ICBM crews were also placed on highest alert, ready to launch, and nuclear-armed Polaris submarines moved to their pre-assigned war stations at sea. United States ground and air forces were put on full alert, with B-52s of the Strategic Air Command ready to attack on a moment's notice. THE QUARANTINE On October 22, in anticipation of a Cuban and/or Soviet reaction to the quarantine, the joint chiefs of staff placed United States military forces worldwide on DEFCON 3 alert. The Joint Chiefs of Staff announced a military readiness status of DEFCON 3 as United States naval forces began implementation of the quarantine and plans accelerated for a military strike on Cuba. With no apparent end to the crisis in sight, United States forces were placed at DEFCON 2—meaning war involving the Strategic Air Command was imminent. ICBMs were prepared for launch, Polaris submarines were dispatched, and B-52 bombers were placed on alert. US Forces Go to DEFCON 2 In light of the latest U-2 photos, and with no peaceful end to the crisis in sight, the Joint Chiefs of Staff placed United States forces at readiness level DEFCON 2; an indication that war involving the Strategic Air Command was imminent. B52 nuclear bombers were deployed, so that one-eighth of them were airborne all the time. United States nuclear-armed bombers were placed on airborne alert, and some of the Soviet missiles and bombers in Cuba were not under the direct control of senior leadership in Moscow and thus could have been launched by less cautious military officers. Hundreds of nuclear bombers were in the air, and intercontinental ballistic missiles were put on a short fuse."
#len(txt)

txt= "All major United States mi]itary commands were placed on DEFCON-3 on 22 October, with SAC moving to DEFCON-2 on 24 October."
txt= "The Soviet commander in Cuba was authorised to use tactical nuclear weapons against United States forces should they invade, and as Soviet missiles were already installed, any attack on Cuba could have led to the outbreak of nuclear war."
summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
txt_summarized_distilbart = summarizer_distilbart(txt, min_length=10, max_length=40,length_penalty=3.0, truncation=False) #embarassingly slow #max_length=50, #, length_penalty=1500.0
txt_summarized_distilbart

#summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
#txt_summarized_distilbart = summarizer_distilbart(txt, min_length=10, max_length=20, length_penalty=200) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#txt_summarized_distilbart

#summarizer_bart = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
#txt_summarized_bart = summarizer_bart(txt, min_length=10, max_length=25, length_penalty=2.0) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#txt_summarized_bart

#Ok this is great. It splits long confusing sentences into individual ones. Perfect.
#summarizer_bart = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
#txt_summarized_bart = summarizer_bart(txt, num_beams=4, min_length=10, max_length=40, length_penalty=20.0) #Maybe it breaks it into individual sentences which we can use
#txt_summarized_bart
#df= pd.DataFrame.from_dict(txt_summarized)

#summarizer_mt5 = pipeline("summarization", device=0, model="csebuetnlp/mT5_multilingual_XLSum") #lol just continues to hallucinate
#txt_summarized_mt5 = summarizer_mt5(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#txt_summarized_mt5

#T5 just absolutely hallucinates things.
#summarizer = pipeline("summarization", device=0, model="csebuetnlp/mT5_multilingual_XLSum")
#txt_summarized_mT5_multilingual_XLSum = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_mT5_multilingual_XLSum= pd.DataFrame.from_dict(txt_summarized_mT5_multilingual_XLSum)

txt=[q[0:2000] for q in r.crimea_case_study_events['sentence'].values]  #first 2k characters
#Summarize with distilbart
summarizer = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
txt_summarized = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
len(txt_summarized[0]['summary_text'])
#txt_summarized[0]['summary_text']
df= pd.DataFrame.from_dict(txt_summarized)

#Summarize with bart-large-cnn
summarizer = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
txt_summarized_bart = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
df_bart= pd.DataFrame.from_dict(txt_summarized_bart)

#summarizer = pipeline("summarization", device=0, model="google/pegasus-xsum") #requires a short 512 tokens
#txt_summarized_pegasus_xsum = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_pegasus_xsum= pd.DataFrame.from_dict(txt_summarized_pegasus_xsum)

#summarizer = pipeline("summarization", device=0, model="google/pegasus-multi_news")
#txt_summarized_pegasus_multi_news = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_pegasus_multi_news = pd.DataFrame.from_dict(txt_summarized_pegasus_multi_news)

#summarizer = pipeline("summarization", device=0, model="google/pegasus-cnn_dailymail")
#txt_summarized_pegasus_cnn_dailymail = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_pegasus_cnn_dailymail = pd.DataFrame.from_dict(txt_summarized_pegasus_cnn_dailymail)

#Put on GPU
#https://github.com/huggingface/transformers/issues/2704

#txt=r.temp['sentence'].values[200]
#summarizer(txt[0:2], min_length=10, max_length=100) #crashes if I pass more than 1

#Token indices sequence length is longer than the specified maximum sequence length for this model (1313 > 1024). Running this sequence through the model will result in indexing errors
#txt=[q[0:2000] for q in r.temp['sentence'].values] #limit to first 4k
#summaries = [summarizer(q, min_length=10, max_length=100)  for q in txt] #

```

```{r}

crimea_case_study_events$summary_text_distilbart_cnn_12_6 = py$df$summary_text
crimea_case_study_events$summary_text_bart_large = py$df_bart$summary_text
#cuban_case_study_events$summary_text_mT5_multilingual_XLSum = py$df_mT5_multilingual_XLSum$summary_text
#
crimea_case_study_events  %>% write_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/crimea_case_study_events_summarized.csv") #summarization failed but otherwise good to go
dim(crimea_case_study_events) #486   4
crimea_case_study_events$n_sources %>% summary()

```

### 2022-07-17 replication_paper/rmd/SyntheticNarrative_CubanMissiles.Rmd
v1.1

---
title: "Synthetic Narrative Cuban Missiles"
output: html_document
date: '2022-04-26'
---

#Create a Cuban Missile Corpus

```{python, eval=F}
fromscratch=False
if fromscratch:
  from internetarchive import download
  #help(download)
  destdir="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/internetarchive/"
  from internetarchive import search_items
  search_results=search_items(query="Cuban Missile Crisis Khrushchev Kennedy Cuba nuclear 1962 Castro October", full_text_search=True)
  search_results=[q for q in search_results]
  import random
  random.shuffle(search_results)
  len(search_results)
  #for i in search_items('Cuban Missile Crisis'):
  #    print(i['identifier'])
  #download(identifier=search_results[0]['fields']['identifier'][0] ,destdir=destdir , verbose=True, ignore_existing=True, glob_pattern="**.txt") #search_results[0]['fields']['identifier'][0]
  for q in search_results:
    try:
      download(identifier=q['fields']['identifier'][0] ,destdir=destdir , verbose=True, ignore_existing=True, glob_pattern="*.txt") #if you don't remove pdfs, it'll crash later because there's a 1.7gb pdf in there lol
    except:
      pass

```

```{r}

library(reticulate)

#pip install -U pip setuptools wheel
#pip install -U spacy
#python -m spacy download en_core_web_sm
library(tidyverse)
library(rvest)

screen_rex <- function(x){
  return( x %>%
                    filter(text %>% str_detect("Cuban")) %>%
                    filter(text %>% str_detect("Missile")) %>%
                    filter(text %>% str_detect("Crisis")) %>%
                    filter(text %>% str_detect("Kennedy")) %>%
                    filter(text %>% str_detect("nuclear")) %>%
                    filter(text %>% str_detect("Khrushchev")) %>%
                    filter(text %>% str_detect("1962")) 
  )
}
#delete duplicate files from the directory just to be sure
#rdfind -deleteduplicates true

library(googlesheets4) #Do this high up so you get the prompt early
cuban_missile_doc <- read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", 
                                sheet="CubanMissilesNarratives") %>% janitor::clean_names()
dim(cuban_missile_doc)

#library(spacyr)
#spacy_install()
#spacy_download_langmodel("en")
#spacy_initialize()
#cuban_missile_clean_sentences <- spacy_parse(cuban_missile_clean$text, full_parse=F)
#dim(cuban_missile_clean_sentences)

#install.packages("pdftools")
#sudo add-apt-repository -y ppa:cran/poppler
#sudo apt-get update
#sudo apt-get install -y libpoppler-cpp-dev

#install.packages('striprtf')
#Surprisingly slow, faster to open and save as plain text and load from there
#cuban_missile_news <- striprtf::read_rtf("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/Factiva-25April20221633.rtf")

files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/loose_txt/", full.names = T, recursive = T,pattern="*.txt")
length(files)
loose_list_text <- list()
for(file in files){
  try({
    df <- data.frame(text=file %>% readLines() )  %>% 
          mutate(url=file) 
    loose_list_text[[file]] <- df
  })
}
cuban_missile_loose_list_text <- bind_rows(loose_list_text) %>% 
  group_by(url) %>%
  summarise(text=paste(text, collapse="\n"))  %>% screen_rex()
dim(cuban_missile_loose_list_text) #958
cuban_missile_loose_list_text$short <- NA

files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/loose_html/", full.names = T, recursive = T,pattern="*.htm*")
length(files)
loose_list <- list()
for(file in files){
  try({
    df <- data.frame(text=file %>% read_html %>% html_text )  %>% 
          mutate(url=file) %>% 
          screen_rex()
    loose_list[[file]] <- df
  })
}
cuban_missile_loose <- bind_rows(loose_list) %>% 
  group_by(url) %>%
  summarise(text=paste(text, collapse="\n"))  %>% screen_rex()
dim(cuban_missile_loose) #958
cuban_missile_loose$short <- NA

#IA
#install.packages('readtext')
#https://cran.r-project.org/web/packages/readtext/vignettes/readtext_vignette.html#introduction
library(readtext)
#install.packages('textreadr')
text <- textreadr::read_dir("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/internetarchive/", recursive=T, pattern="txt", verbose=T)
cuban_missile_ia <- text %>% dplyr::select(url=document, text=content) %>% group_by(url) %>% summarise(text=text %>% paste(collapse=" \n ")) %>%  screen_rex()
cuban_missile_ia$short <- NA

#C4
files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/c4/", full.names = T)
c4_list <- list()
for(file in files){
  df <- data.frame(text=file %>% read_html %>% html_text )  %>% 
        mutate(text = strsplit(as.character(text), "\n")) %>% 
        unnest(text) %>%
        mutate(text=text %>% trimws()) %>%
        filter(text!='') %>%
        mutate(url=ifelse(text %>% str_detect('http'), text, NA )) %>%
        fill(url) %>%
        filter(text!=url) %>% filter(!is.na(url)) %>% screen_rex()
  c4_list[[file]] <- df
}
cuban_missile_c4 <- bind_rows(c4_list) %>% 
  group_by(url) %>%
  summarise(text=paste(text, collapse="\n"))  %>% screen_rex()
dim(cuban_missile_c4) #958
cuban_missile_c4$short <- NA

#Ok this is trash, it only pulls 300 ish unique URLS and then dupes
#Bing search
fromscratch=FALSE
if(fromscratch){
  library(httr)
  server="https://api.bing.microsoft.com/v7.0/search"
  token = "cb169dcd50584785a82dd8852f283cf2"
  search_term = "'Cuban Missile Crisis' +Khrushchev +Cuba +Kennedy +Castro +nuclear' +1962 -Ukraine"
  url = paste0(server) #, "search"
  mkt = 'en-US'
  iter = seq(0, 10000, 50)
  result_list <- list()
  for(i in iter){ #[0:3]
    print(i)
    response = GET(url = url, 
                   query = list(q = search_term, mkt=mkt, count=50, offset=i), 
                   add_headers(`Ocp-Apim-Subscription-Key` = token)
                   )
    result_list[[as.character(i)]] <- response
    #Sys.sleep(1)
    #res = content(response, encoding = "json")
    result_list_parsed <- result_list %>% lapply(content, encoding = "json")
    #res
    result_list_df <- result_list_parsed  %>% lapply(FUN=function(x) { x$webPages$value %>% lapply(as.data.frame)  } ) %>% bind_rows() 
    #dim(result_list_df)
    #Parse the whole thing each loop both as a sleep and to make sure it's adding unique urls
    result_list_df$url %>% duplicated() %>% table() #11 dupes #failed horribly and most were dupes only 335 unique URLS

  }
  saveRDS(result_list_df, "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/bind_searches.Rds")
  result_list_df <- result_list_df %>% filter(!duplicated(url))
  library(rvest)
  #result_list_df
  #temp=result_list_df$url[1] %>% read_html() %>% html_text()
  result_list_df$text <- NA
  for(i in 1:nrow(result_list_df)){
    print(i) #273 hung
    try({result_list_df$text[i] <- result_list_df$url[i] %>% read_html %>% html_text}) #not fast
  }
  saveRDS(result_list_df, "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/bind_searches_df.Rds")
}

result_list_df <- readRDS( "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/bind_searches_df.Rds")  %>% screen_rex()

icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))

cuban_missile_icb <- icb_wide_clean %>% filter(crisno==196) %>% dplyr::select(sentence_number_int_aligned, text=sentence) %>% distinct() %>% mutate(url=paste("ICB_196_",sentence_number_int_aligned)) %>% select(-sentence_number_int_aligned)
cuban_missile_icb$short <- NA

cuban_missile_news <- read_lines("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/Factiva-25April20221633.txt")
length(cuban_missile_news)

"Document SLMO000020040704dk9400o8v" %>% str_detect("^Document ")
cuban_missile_news_df <- data.frame(text=cuban_missile_news) %>% mutate(url=ifelse(text %>% str_detect("^Document "), text, NA )) %>% fill(url, .direction="up") %>% filter(!is.na(text) & text!='')
cuban_missile_news_df$short=NA

files <- list.files(path = "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban/",
                    pattern = "*.pdf", all.files = FALSE,
           full.names = T, recursive = T,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

library(pdftools)
pdf_text_list <- list()
for(file in files){
  #print(file)
  try({ pdf_text_list[[file]] <- pdftools::pdf_text(file) %>% unlist() %>% paste(collapse="\n ")   } )
}
cuban_missile_pdfs <- data.frame(url=names(pdf_text_list)) 
cuban_missile_pdfs$text <- as.vector(unlist(pdf_text_list))
cuban_missile_pdfs$short <- NA

#cuban_missile_pdfs %>% filter(url %>% str_detect("NewsBank Multiple Articles.pdf")) %>% 
#    mutate(text = strsplit(as.character(text), "OpenURL Link")) %>% 
#    unnest(text) %>% group_by(url) %>% mutate(url=url %>% paste0(row_number()))
cuban_missile_pdfs <- cuban_missile_pdfs %>% 
    mutate(text = strsplit(as.character(text), "OpenURL Link")) %>% 
    unnest(text) %>% group_by(url) %>% mutate(url=url %>% paste0(row_number()))  %>% screen_rex()

"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/cuban//zotero/7LU24CRX/filename.pdf" %>% str_replace(".*/(.*?.pdf)","\\1")

cuban_missile <- bind_rows(
  cuban_missile_pdfs %>%
  mutate(url=url %>% str_replace(".*/(.*?.pdf)","\\1")) %>% 
           filter(!duplicated(url %>% tolower())) %>% filter(!duplicated(text %>% tolower() %>% trimws())),
  cuban_missile_doc,
  cuban_missile_news_df,
  cuban_missile_icb,
  result_list_df %>% dplyr::select(text, url) %>% mutate(short=NA),
  cuban_missile_c4,
  cuban_missile_ia,
  cuban_missile_loose,
  cuban_missile_loose_list_text
)   %>% screen_rex() 
dim(cuban_missile) #2067 #1548 #16819 #9093

"Second, the case is relatively well documented:in additionto the famous ExComm tapes (May and Zelikow 1997), declassification of the written recordhas been extensive." %>% str_replace_all("\\(.*?\\)","")

"asdfasdf (sdfasdf) asdadsasd" %>% str_replace_all("\\(.*?\\)","")
"asdfasdf [1-10] asdadsasd" %>% str_replace_all("\\[.*?\\]","")
"John F. Kennedy" %>% str_replace_all("( [A-Z])\\.","\\1")
"Cuban armed assistance to subversion in other parts of the Western Hemisphere. f." %>% str_replace_all(" [a-z]\\.","")
"Cuban armed assistance to subversion in other parts of the Western Hemisphere.1" %>% str_replace_all("([a-z]\\.) *[0-9]{1,2}","\\1")
"U.S. president Dwight D. Eisenhower (1890–1969; served 1953–61) halted U.S. importation of Cuban sugar" %>%
                                    str_replace_all("( [A-Z])\\. ","\\1 ")

"U.S. president Dwight D. Eisenhower (1890–1969; served 1953–61) halted U.S. importation of Cuban sugar" %>%
                                    str_replace_all("U\\.S\\. | US "," United States ")

"sasadfasdffds.1 asdfasdf" %>% str_replace_all("\\.[0-9] ","\\. ")
library(cld3); #install.packages('cld3')
cuban_missile_clean <- cuban_missile %>% ungroup() %>%
                       janitor::clean_names() %>%
                       mutate(text= text %>% 
                                    str_replace_all("\\(.*?\\)","") %>% #parentheticals
                                    str_replace_all("\\[.*?\\]","") %>% #brackets citations
                                    str_replace_all("U\\.S\\. | US "," United States ") %>%
                                    str_replace_all("U\\.N\\. "," United Nations ") %>%
                                    str_replace_all("( [A-Z])\\. ","\\1 ") %>% #middle names
                                    str_replace_all(" [a-z]\\.","") %>% 
                                    str_replace_all("([a-z]\\.) *[0-9]{1,2}","\\1")  %>% 
                                    str_replace_all("Mr\\.","Mr ")  %>% 
                                    str_replace_all(" {3,}","\n")  %>%  
                                    str_replace_all("\\.[0-9] ","\\. ")  %>% 
                                    str_replace_all("  "," ") 
                        ) %>%
                        mutate(langauge=cld3::detect_language(text)) %>% 
                        filter(langauge=='en') %>%
                        mutate(text_nchar= text %>% nchar() ) %>%
                        ungroup() %>% filter(!duplicated(text_nchar)) %>% #there should never be an exact character count
                        filter(text_nchar>1000) 
table(cuban_missile_clean$langauge) %>% sort()
hist(cuban_missile_clean$text_nchar %>% log(), breaks=50)
table(cuban_missile_clean$text_nchar) %>% sort()
dim(cuban_missile_clean) #1,636

#https://github.com/dselivanov/LSHR
library(devtools)
#install_github("dselivanov/LSHR")
library(LSHR) #install.packages('LSHR')
#devtools::install_github('dselivanov/text2vec')
library(text2vec)
it <- itoken(cuban_missile_clean$text, preprocess_function = tolower, tokenizer = word_tokenizer)
dtm <- create_dtm(it, hash_vectorizer())
dtm = as(dtm, "RsparseMatrix")
hashfun_number = 120
s_curve <- get_s_curve(hashfun_number, n_bands_min = 5, n_rows_per_band_min = 5)
s_curve %>% ggplot(aes(x=similarity, y=probability_become_candidate, color=paste(n_bands,n_rows_per_band))) + geom_line()
seed = 1
pairs = get_similar_pairs(dtm, bands_number = 6, rows_per_band = 20, distance = 'cosine', seed = seed)
pairs[order(-N)]
temp <- pairs %>% filter(N==5) %>%
  mutate(id1_new =  ifelse(id1<id2, id1, id2) ) %>%
  mutate(id2_new =  ifelse(id1<id2, id2, id1) )
dim(temp) #now only 18 dupes
temp$a <- substr( cuban_missile_clean$text[temp$id1_new],  1, 200)
temp$b <- substr( cuban_missile_clean$text[temp$id2_new],  1, 200)

"https://doi.org/10.2307/2009577"
"Document: President Kennedy's statement on Soviet military" %>% str_replace_all("^.*?: ","")
"The discussion of the crisis by ExComm members shows awareness of and sensitivity to domestic political considerationsin the selection of the initial United States response to the Soviet missiles." %>% str_detect("[a-z0-9]\\.$")
'It can use them and it must not be treated lightly"; Khrushchev, cited in Abel, 191-92.' %>% str_detect(" [0-9]{3}(\\–|\\-)")
"On the Turkish issue, he faults Kennedy's refusal of the quid pro quo, since Kennedy had known for some time that our missiles in Turkey were obsolete; Stone, 21-22.
" %>% str_detect(" [0-9]{2,3}(\\–|\\-)[0-9]{2,3}")
"On April 12, 1961, the Soviets again led the way with the launch of Yuri Gagarin, a Russian cosmo¬ naut, into space to become the first human to leave Earth." %>% str_replace_all("- |¬ ","")
#install.packages('tidytext')
library(tidytext)
index <- setdiff(1:nrow(cuban_missile_clean), temp$id2_new %>% unique())
cuban_missile_clean_sentences <- cuban_missile_clean[index,] %>% 
                                 ungroup() %>%
                                 mutate(text= text %>% str_replace_all("\n","  ") ) %>% #because pdfs are often parsed line by line
                                 mutate(text= text %>% str_replace_all(" {1,}"," ") ) %>%
                                 unnest_tokens(sentence, text, token="sentences", drop=T, to_lower=F) %>%
                                 mutate(sentence= sentence %>% str_replace_all("^.*?: ","") ) %>%
                                 mutate(sentence= sentence %>% str_replace_all("- |¬ ","") ) %>% #words broken across pages
                                 mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                                 mutate(sentence_nchar=sentence %>% nchar()) %>%
                                 mutate(sentence= sentence %>% trimws()) %>%
                                 filter(sentence_nchar>70 & sentence_nchar<600) %>%
                                 filter(!str_detect(sentence, "downloaded|Downloaded|Table|Figure|University|pp\\.|New York| file | [0-9]{3} | [0-9]{3}(\\–|\\-)|Box |IEEE|Memorandum|Transcript|Telegram|Kew Gardens| [0-9]{2,3}(\\–|\\-)[0-9]{2,3}|CHAPTER| cited|=|Cuban Missile Crisis|Book|Copyright|FRUS|http|JSTOR|researchers|archival|scholarship|recordings|File|Foreign Relations of the United States|Printing Office|Document|Minutes of|Summary|Record|vol\\.|No\\.|Issue|Paper|à| et | est |United States Government|American Foreign Policy|FO |PREM| box|Part| et | est |Acknowledgements|website|cookies|Privacy|©")) %>%
                                 mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                                 filter(sentence %>% str_detect("^[A-Z]")) %>% #has at least one capital letter
                                 filter(sentence %>% str_detect("[a-z0-9]\\.$")) %>% #ends in a letter/number and a period no questions
                                 #add_count(sentence) %>%
                                 ungroup() %>%
                                 mutate(dupe= sentence %>% tolower() %>% str_replace_all("[^a-z]","") %>% duplicated() ) %>%
                                 filter(!dupe) %>% #restrict to unique sentences
                                 group_by(url) %>%  
                                   mutate(sentence_n = n() ) %>% 
                                   mutate(sentence_number= row_number() ) %>%
                                   mutate(position= row_number()/n()) %>%
                                 ungroup() %>%
                                 filter(sentence_n<=20000 ) %>%
                                 filter(sentence_n>=10 | url %>% str_detect("ICB")) #require at least 10 unique sentences per source

cuban_missile_clean_sentences$sentence %>% tolower() %>% duplicated() %>% table()
dim(cuban_missile_clean_sentences) #600206 #124,808 #125018 #72576 #74385 #79851 #80529 #73,817

cuban_missile_clean_sentences %>% filter(url %>% str_detect("ICB"))

#Less than 600 and greater than 50
hist(cuban_missile_clean_sentences$sentence_nchar[cuban_missile_clean_sentences$sentence_nchar], 60)
summary(cuban_missile_clean_sentences$sentence_nchar) #Interquartile is 111 to 200

cuban_missile_clean_sentences  %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences.tsv")

```

```{r}

library(tidyverse)
cuban_missile_clean_sentences <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences.tsv")

cuban_missile_clean_sentences$url %>% unique() %>% length() #1,218 #993 #1568 #881 #999 #464 #558 unique sources #646 sources so far
cuban_missile_clean_sentences$url %>% table() %>% as.vector() %>% summary() #median of 37 sentences per

cuban_missile_clean_sentences_unique <- cuban_missile_clean_sentences$sentence %>% unique()
length(cuban_missile_clean_sentences_unique) #600,148 #179,217 #1002249 #125018 #82,280 #78,225 #81621 #73817 #There are 73,991 unique sentences

#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
#    71     102     136     154     185     599     338 
summary(cuban_missile_clean_sentences$sentence_nchar %>% as.numeric())
nchar("The Soviet commander in Cuba was authorised to use tactical nuclear weapons against United States forces should they invade, and as Soviet missiles were already installed, any attack on Cuba could have led to the outbreak of nuclear war.")
nchar("Soviet commander in Cuba authorised to use tactical nuclear weapons against U.S. forces if they invaded.") #104
nchar("Any attack on Cuba could have led to the outbreak of nuclear war.")

#Write out a folder of sentences to iterate over and summaries

#embarassingly slow and parallelizable
library(digest)
for(q in cuban_missile_clean_sentences$url %>% unique() ){
  cuban_missile_clean_sentences %>% filter(url==q) %>% pull(sentence) %>% #forgot to make it just long sentences, actually worked out I think
    writeLines(glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_original/{digest(q,'crc32')}.txt"))
}

```

Create additional simplified sentences

This takes the 3090 Ti more than all night to run alone

```{python}

import torch
use_cuda = torch.cuda.is_available()
if use_cuda:
    print('__CUDNN VERSION:', torch.backends.cudnn.version())
    print('__Number CUDA Devices:', torch.cuda.device_count())
    print('__CUDA Device Name:',torch.cuda.get_device_name(0))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)

import os
from tqdm.auto import tqdm
import pandas as pd
from transformers import pipeline
from transformers.pipelines.pt_utils import KeyDataset
summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #1 for small gpu 0 for big
from datasets import load_dataset
#What if we did it by url? Then we don't need to keep track of which sentences worked and didn't and if it fails we just lose one doc
directory="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_original/"
out_directory="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_sum/"
from os.path import exists
from datasets import Dataset
for filename in os.listdir(directory):
    f_in = os.path.join(directory, filename)
    f_out=os.path.join(out_directory, filename)
    if not exists(f_out): #I'm eventually going to have to write a try for the one that fails on us
        my_file = open(f_in, "r")
        df = pd.DataFrame({"text": my_file.readlines() })
        dataset = Dataset.from_pandas(df ) #.head(1)
        results=[out for out in summarizer_distilbart(KeyDataset(dataset, "text"), num_beams=4, min_length=10, max_length=60, length_penalty=100.0, batch_size=32)] #32 was fastest
        #dataset = load_dataset('text', data_files={'train': [f_in]}, split="train") #same speed either way
        with open(f_out, 'w') as f:
          _ = f.write('\n'.join([q[0]['summary_text'] for q in results]))

```

Load the simplified sentences and add them to the pile

```{r}

files <- list.files("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/sentences_sum/", full.names = T)
length(files)
sentences_sum_list <- list()
for(file in files){
  try({
    filename = basename(file)
    df=data.frame(sentence=readLines(file))
    df$url_hash <- filename %>% str_replace(".txt",'')
    sentences_sum_list[[file]] <- df
  })
}

library(digest)
url_hash_df <- cuban_missile_clean_sentences %>% dplyr::select(url) %>% distinct() %>% rowwise() %>% mutate(url_hash=digest(url,'crc32')) %>% ungroup()

library(tidytext)
sentences_sum_df <- bind_rows(sentences_sum_list) %>%
                    left_join(url_hash_df) %>%
                     mutate(sentence=sentence %>% str_replace_all(" {1,}\\.",".") ) %>% #after summarizing it puts a space before the final punctuation
                     ungroup() %>%
                     mutate(sentence= sentence %>% str_replace_all("\n","  ") ) %>% #because pdfs are often parsed line by line
                     mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") ) %>% 
                     unnest_tokens(sentence, sentence, token="sentences", drop=T, to_lower=F) %>%
                     mutate(sentence= sentence %>% str_replace_all("^.*?: ","") ) %>%
                     mutate(sentence= sentence %>% str_replace_all("- |¬ ","") ) %>% #words broken across pages
                     mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                     mutate(sentence_nchar=sentence %>% nchar()) %>%
                     mutate(sentence= sentence %>% trimws()) %>%
                     filter(sentence_nchar>70 & sentence_nchar<600) %>%
                     filter(!str_detect(sentence, "downloaded|Downloaded|Table|Figure|University|pp\\.|New York| file | [0-9]{3} | [0-9]{3}(\\–|\\-)|Box |IEEE|Memorandum|Transcript|Telegram|Kew Gardens| [0-9]{2,3}(\\–|\\-)[0-9]{2,3}|CHAPTER| cited|=|Cuban Missile Crisis|Book|Copyright|FRUS|http|JSTOR|researchers|archival|scholarship|recordings|File|Foreign Relations of the United States|Printing Office|Document|Minutes of|Summary|Record|vol\\.|No\\.|Issue|Paper|à| et | est |United States Government|American Foreign Policy|FO |PREM| box|Part| et | est |Acknowledgements|website|cookies|Privacy")) %>%
                     mutate(sentence= sentence %>% str_replace_all(" {1,}"," ") %>% trimws() ) %>%
                     filter(sentence %>% str_detect("^[A-Z]")) %>% #has at least one capital letter
                     filter(sentence %>% str_detect("[a-z0-9]\\.$")) %>% #ends in a letter/number and a period no questions
                     #add_count(sentence) %>%
                     ungroup() %>%
                     mutate(dupe= sentence %>% tolower() %>% str_replace_all("[^a-z]","") %>% duplicated() ) %>%
                     filter(!dupe)
dim(sentences_sum_df) #796,090

cuban_missile_clean_sentences_withsum <- 
  bind_rows(cuban_missile_clean_sentences %>% dplyr::select(url, sentence),
            sentences_sum_df %>% dplyr::select(url, sentence) ) %>%
       mutate(dupe= sentence %>% tolower() %>% str_replace_all("[^a-z]","") %>% duplicated() ) %>%
       filter(!dupe)
dim(cuban_missile_clean_sentences_withsum) #1,238,303 #1267675

#
cuban_missile_clean_sentences_withsum %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences_withsum.tsv")

```

```{r}

cuban_missile_clean_sentences <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences.tsv")

cuban_missile_clean_sentences_withsum <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences_withsum.tsv") %>%
  rowwise() %>%
    mutate(url_hash= digest(url, 'crc32') ) %>%
  ungroup() %>%
  mutate(url_int=url %>% as.factor() %>% as.integer())

```

```{python}

#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers
import pickle
import numpy as np
from sentence_transformers import SentenceTransformer
fromscratch=True
if fromscratch:
  sentences=np.array(r.cuban_missile_clean_sentences_withsum.sentence) #sentences_unique_sanitized
  url_ints = np.array(r.cuban_missile_clean_sentences_withsum.url_int.values)
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #648,266 #600148 #10383 12514
  n=len(sentences)
  chunk_length=200
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2') 
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/paraphrase-MiniLM-L6-v2')
  #
  #https://www.sbert.net/examples/applications/paraphrase-mining/README.html
  from sentence_transformers import SentenceTransformer, util
  #I don't know why but I had to set the query chunk size to smaller for it to work. I think it was silently failing.
  #sentences.shape 79,851  sentences, so 6,376,182,201 possible comparisons
  #We want a greedy matching across documents, pick a sentence, find its top pair in the next document, and so on
  #
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks]).astype('float32')  #This is what takes a whle #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #1,267,675 #124,808 #78225
  d=sentences_embeddings.shape[1]
  import faiss
  faiss.omp_set_num_threads(64)
  faiss.normalize_L2(sentences_embeddings) #If you normalize then you do get the right
  # build a flat (CPU) index
  index_flat = faiss.IndexFlatIP(d) #make sure you use IP so you get cosine distance https://github.com/facebookresearch/faiss/issues/95
  # make it into a gpu index
  #https://github.com/facebookresearch/faiss/wiki/Running-on-GPUs
  res = faiss.StandardGpuResources()  # use a single GPU
  gpu_index_flat = faiss.index_cpu_to_gpu(res, 0, index_flat)  
  gpu_index_flat.add(sentences_embeddings)
  k = 30   #it runs out of memory with 600k times 50. 30 works. #You can do 25 and miss almost no pairs over 0.9
  D, I = gpu_index_flat.search(sentences_embeddings, k)  #With a million this is no longer instant but it is going hard
  np.quantile( D[:,0], [0.01,0.05,0.1,0.5,0.9,0.95,0.99] ) #should be all 1s ish
  #1568 articles. If they were all identical that would mean for each sentence there would be 1568 other matches and no others so 1568*number of sentences on average (37) 58,016
  #58016/124808 #0.46% is then the upper bound, it's actually much smaller. There are so many pairings it's like 0.0000037 of pairs would be matches if it was just the same doc over and over
  np.quantile( D[:,1], [0.01,0.05,0.1,0.5,0.9,0.95,0.99] ) #We have to decide something here about what our prior is on how many paraphrased sentences there should be in a corpus. 0.95 would mean 1 in 20
  condition=D[:,1:]>=0.87 #0.87 
  np.sum(condition) #56,447 #28,189 #7809 or 3904.5 pairs  #1460 #6,240,376 #2,496,146 #1,248,071 #624,036
  A=np.where(condition)[0]
  A_id=url_ints[A]
  B=I[:,1:][condition]
  B_id=url_ints[B]
  condition2 = A_id != B_id #add a second condition where we require both nodes to live in different url_hash which should be an integer
  sum(condition2) #170,404
  edges=np.transpose(np.vstack([A,B]))[condition2,:]
  weights=D[:,1:][condition][condition2]
  vertices=np.unique(np.hstack([edges[:,0],edges[:,1]]))
  #
  #ids_strongly = np.unique(np.hstack([paraphrases_strongly[:,1],paraphrases_strongly[:,2]] ) ).astype("int")
  #ids_strongly = np.setxor1d(ids_strongly,list(dead)).astype("int")
  #sentences_strongly = sentences[ids_strongly]
  #sentences_embeddings_strongly = sentences_embeddings[ids_strongly,:]
  #sentences_embeddings_strongly.shape #78,225 #78,474
  #paraphrases_strongly = util.paraphrase_mining(model, sentences_strongly, show_progress_bar=True, top_k=300, batch_size=128, query_chunk_size=1000, max_pairs=30000000) 
  #paraphrases_strongly_array=   np.vstack(paraphrases_strongly)
  #paraphrases_strongly_array = paraphrases_strongly_array[paraphrases_strongly_array[:,0]>0.70, :] #require a certain proximity
  #paraphrases_strongly_array.shape
  #subset=np.sort( np.unique( np.hstack([paraphrases_strongly_array[:,1],paraphrases_strongly_array[:,2]]) ) ).astype('int')
  #sentences_strongly=sentences_strongly[subset,]
  #sentences_embeddings_strongly=sentences_embeddings_strongly[subset,]
  #sentences_embeddings_strongly.shape
  #
  import igraph
  import pandas as pd
  edges_df=pd.DataFrame(edges.astype('int')) #
  edges_df['weights']=weights
  edges_df['from']=edges_df[0]
  edges_df['to']=edges_df[1]
  condition=edges_df[0]<edges_df[1]
  edges_df['from'][condition]=edges_df[1][condition]
  edges_df['to'][condition]=edges_df[0][condition]
  edges_df=edges_df[['from','to','weights']].drop_duplicates()
  #
  #  
  g = igraph.Graph.DataFrame(edges_df, directed=False) #.simplify()
  g.es.attribute_names()
  len(g.es) #92,800
  len(g.vs)  #55,831 #47,846 #32,258 #32,916 #47363 #32916 nodes
  clustered=igraph.Graph.community_fastgreedy(g, weights=edges_df.weights.values ) # #wow did pretty well #weights=paraphrases_strongly[:,0]
  clustered.optimal_count
  clustered_cuts=clustered.as_clustering()
  len(clustered_cuts.membership) #32916 #ok so it cut 2824 sentences into 1269 clusters
  import scipy
  tabs=scipy.stats.contingency.crosstab(clustered_cuts.membership)
  #with np.printoptions(threshold=np.inf):
  #  print(np.sort(tabs[1])) #ok so there are a few big ones but mostly very small
  #
  import numpy as np
  import pandas as pd
  import matplotlib.pyplot as plt
  import genieclust
  import sklearn
  import umap
  x_train= sklearn.preprocessing.scale(sentences_embeddings[vertices,:]) #[0:10000,] #I think we have to scale it so euclidian distance is the same as cosine #_strongly
  x_train.shape
  x_train_umap = umap.UMAP().fit_transform(x_train) #
  #
  import fastcluster
  #clusters_ward = fastcluster.ward(x_train)
  from scipy.cluster.hierarchy import dendrogram
  #linkage = fastcluster.linkage_vector(x_train, method='ward', metric='euclidean')
  #labels = hierarchy.fcluster(linkage._Z, t=0.02, criterion='distance') - 1
  #dendrogram = hierarchy.dendrogram(linkage, no_plot=True, color_threshold=-np.inf)
  #                      
  #X=x_train                 
  #import scipy.cluster.hierarchy
  #g = genieclust.Genie(compute_full_tree=True)
  #g.fit(X)
  #linkage_matrix = np.column_stack([g.children_, g.distances_, g.counts_])
  #scipy.cluster.hierarchy.dendrogram(linkage_matrix,
  #    show_leaf_counts=False, no_labels=True)
  #plt.show()
  #g = genieclust.Genie(n_clusters=500, exact = True, compute_full_tree=False, affinity='cosinesimil', verbose=True) #, M=3
  #labels_genie = g.fit_predict(x_train) #it assigns non clusters to 0
  #np.max(labels_genie)
  #
  from plotnine import ggplot, geom_point, aes, stat_smooth, facet_wrap
  import pandas as pd
  x_train_umap_df=pd.DataFrame(x_train_umap, columns=['X','Y'])
  #x_train_umap_df['labels_genie']=labels_genie
  x_train_umap_df['labels_community_fastgreedy']=clustered_cuts.membership
  #x_train_umap_df['labels_genie_pos']=labels_genie>0
  #x_train_umap_df['labels_genie_noise']=labels_genie<0
  x_train_umap_df['sentence']=sentences[vertices]
  x_train_umap_df['labels']=x_train_umap_df['labels_community_fastgreedy']
  (ggplot(x_train_umap_df, aes('X', 'Y', color='factor(labels_community_fastgreedy)' )  ) + geom_point(size=0.1, show_legend=False)   ) #it just runs out of colors
  #
  #genieclust.plots.plot_scatter(x_train_umap, labels=labels_genie, alpha=0.5)
  #plt.title("(n=%d, true n_clusters=%d)" % (X.shape[0], n_clusters))
  #plt.axis("equal")
  #plt.show()
  #
  #(ggplot(x_train_umap_df, aes('X', 'Y', color='factor(labels_genie_noise)' )  ) + geom_point(size=0.1, show_legend=False)   )
  #
  #paraphrases_array.shape
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  #clusters = util.community_detection(sentences_embeddings, min_community_size=25, threshold=0.75) #if this is working, it's too slow to tell
  #
  #with open("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/x_train_umap_df.pickle", "wb") as outfile:
  # 	# "wb" argument opens the file in binary mode
  #pickle.dump(x_train_umap_df, outfile)
#
#

```

```{r}

#x_train= py$x_train
#library('fastcluster')
#hc <- hclust.vector(x_train, method="ward", members=NULL, metric='euclidean', p=NULL)
#g = genieclust.Genie(compute_full_tree=True)

#install.packages('genieclust')
#library(genieclust)
#?gclust

#install.packages('gputools')
library(reticulate)
library(tidyverse)
cuban_missile_clean_sentences_withsum_clustered <- cuban_missile_clean_sentences_withsum %>% left_join(py$x_train_umap_df)
dim(cuban_missile_clean_sentences_withsum_clustered) #1,267,675 #648493
cuban_missile_clean_sentences_withsum_clustered %>% pull(url) %>% unique()  %>% length() #1995 #1,998

cuban_missile_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>=0) %>% pull(labels) %>% table()  %>% table()

cuban_missile_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>=0) %>% pull(labels) %>% table() %>%  sort() %>% tail(10)

cuban_missile_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>0) %>% pull(labels) %>% table() %>% as.vector() %>% summary()

cuban_missile_clean_sentences_withsum_clustered %>% filter(!is.na(labels) & labels>0) %>% pull(labels) %>% table() %>% as.vector() %>% table()

cuban_case_study_events <- cuban_missile_clean_sentences_withsum_clustered  %>%
                            filter(!is.na(labels) & labels>=0) %>% #-1 are the noise ones
                            group_by(labels) %>%
                            summarise(
                              n_sources=url %>% unique() %>% length(),
                              sentence= sentence %>% paste(collapse="\n")#,
                              #position=median(position) %>% round(2) #we lost position but I was coding date by hand anyway now so
                              ) %>%
                            #arrange(n_sources %>% desc() ) %>%
                            arrange(n_sources) %>%
                            filter(n_sources>=5)
dim(cuban_case_study_events) #410

table(cuban_case_study_events$n_sources)

cuban_case_study_events$sentence %>% str_detect("defcon|DEFCON") %>% table()

table(cuban_case_study_events$n_sources)

```

```{python}

import pandas as pd
from transformers import pipeline
#summarizer = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
#summarizer = pipeline("summarization", device=0, model="sshleifer/distilbart-xsum-12-6") #noooooo
txt="All major United States mi]itary commands were placed on DEFCON-3 on 22 October, with SAC moving to DEFCON-2 on 24 October. It now appears that the commander of United States Air Forces Europe, General Truman Landon, ordered numerous operational activities commensurate with DEFCON-3 alert status, including increasing the number of nuclear- armed aircraft on Quick Reaction Alert .73 Additionally, the alert status  of the IRBMs in Britain and Italy was at fifteen minutes readiness and the British V-bomber force was brought to a high state of ground alert. In times of peace the United States armed forces are usually on DefCon5. Following this meeting Harkness presented Diefenbaker with a report showing that the United States military had moved to DEFCON 2, meaning the Americans were making immediate preparations for war. United States forces went from \"peace alert to Defcon 3 (war alert), and strategic air command Defcon 2\" , five divisions of armed strategic reserves were placed on alert. Tactical strike aircraft in Florida maintained high levels of alert, anywhere from pilots in their cockpits ready to launch to as long as a thirty- minute alert. TAC forces in Florida assumed a one-hour alert and prepared to go to a fifteen-minute alert, which involved pilots waiting in aircraft for launch orders. On October 22 United States armed forces moved to DEFCON-3, a height-  ened state of alert, upgraded to DEFCON-2, only one level short of war,  on October 25. On October 26, he learned that the Pentagon had moved United States forces from DEFCON 5, peacetime status, to DEFCON 2, just one away from war, and that United States hospitals had been ordered to prepare to receive casualties. Military forces of both nations were placed on maximum alert and United States nuclear bombers were ordered into the air. For the first and only time in its existence, the Strategic Air Command had been ordered to Defcom 2 status, one step short of all-out war. Harkness returned to his office and learned that parts of the United States military had raised their alert status to DEFCON 2, meaning that an imminent attack was now expected. Squadrons of B-52 nuclear bombers lifted off from their bases to join the Strategic Air Command's airborne alert as a precaution against surprise attack. On 24 October the United States' Strategic Air Command was placed on DEFCON- 2, a state of alert denoting readiness for combat. A high alert was immediately announced for air forces to bomb the exile troop's ships. Until  20 November, the United States Strategic Air Command remained on alert at  Defence Condition 2 , other  forces were held at DefCon 3, and the naval quarantine was maintained in  place. DEFCON ranged from DEFCON 5, which was simple preparedness, to DEFCON 1, which was the most serious alert of all, the DEFCON for war. A massive airborne alert was begun by U.S.- based B-52 bombers which were loaded with nuclear weapons and by KC-135 tankers. Bombers, especially the new B-52s, provided a much more reliable way of delivering nuclear weapons against Soviet targets than ICBMs, but they are slow and—if detected as they approached Soviet air space—would allow the Soviets to launch air defense aircraft as well as launch or disperse their nuclear forces. On the morning of October 24, the United States quarantine went into place, and the United States military went to DEFCON 2, the last level before nuclear war. U.S. military forces worldwide, with the exception of the United States Air Forces in Europe , are placed on DEFCON 3. ICBM missile crews are alerted and Polaris nuclear submarines in port are dispatched to preassigned stations at sea. DEFCON 3 means an increase in readiness above normal levels, specifically that air forces are ready to deploy in 15 minutes. The United States Strategic Air Command placed all its B-52 intercontinental bombers on 15-minute takeoff alert on October 20; on October 22, it placed them on a revolving airborne alert, with a percentage of bombers airborne at all times, ready to head over the North Pole toward the Soviet Union. ICBM crews were also placed on highest alert, ready to launch, and nuclear-armed Polaris submarines moved to their pre-assigned war stations at sea. United States ground and air forces were put on full alert, with B-52s of the Strategic Air Command ready to attack on a moment's notice. THE QUARANTINE On October 22, in anticipation of a Cuban and/or Soviet reaction to the quarantine, the joint chiefs of staff placed United States military forces worldwide on DEFCON 3 alert. The Joint Chiefs of Staff announced a military readiness status of DEFCON 3 as United States naval forces began implementation of the quarantine and plans accelerated for a military strike on Cuba. With no apparent end to the crisis in sight, United States forces were placed at DEFCON 2—meaning war involving the Strategic Air Command was imminent. ICBMs were prepared for launch, Polaris submarines were dispatched, and B-52 bombers were placed on alert. US Forces Go to DEFCON 2 In light of the latest U-2 photos, and with no peaceful end to the crisis in sight, the Joint Chiefs of Staff placed United States forces at readiness level DEFCON 2; an indication that war involving the Strategic Air Command was imminent. B52 nuclear bombers were deployed, so that one-eighth of them were airborne all the time. United States nuclear-armed bombers were placed on airborne alert, and some of the Soviet missiles and bombers in Cuba were not under the direct control of senior leadership in Moscow and thus could have been launched by less cautious military officers. Hundreds of nuclear bombers were in the air, and intercontinental ballistic missiles were put on a short fuse."
#len(txt)

txt= "All major United States mi]itary commands were placed on DEFCON-3 on 22 October, with SAC moving to DEFCON-2 on 24 October."
txt= "The Soviet commander in Cuba was authorised to use tactical nuclear weapons against United States forces should they invade, and as Soviet missiles were already installed, any attack on Cuba could have led to the outbreak of nuclear war."
summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
txt_summarized_distilbart = summarizer_distilbart(txt, min_length=10, max_length=40,length_penalty=3.0, truncation=False) #embarassingly slow #max_length=50, #, length_penalty=1500.0
txt_summarized_distilbart

#summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
#txt_summarized_distilbart = summarizer_distilbart(txt, min_length=10, max_length=20, length_penalty=200) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#txt_summarized_distilbart

#summarizer_bart = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
#txt_summarized_bart = summarizer_bart(txt, min_length=10, max_length=25, length_penalty=2.0) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#txt_summarized_bart

#Ok this is great. It splits long confusing sentences into individual ones. Perfect.
#summarizer_bart = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
#txt_summarized_bart = summarizer_bart(txt, num_beams=4, min_length=10, max_length=40, length_penalty=20.0) #Maybe it breaks it into individual sentences which we can use
#txt_summarized_bart
#df= pd.DataFrame.from_dict(txt_summarized)

#summarizer_mt5 = pipeline("summarization", device=0, model="csebuetnlp/mT5_multilingual_XLSum") #lol just continues to hallucinate
#txt_summarized_mt5 = summarizer_mt5(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#txt_summarized_mt5

#T5 just absolutely hallucinates things.
#summarizer = pipeline("summarization", device=0, model="csebuetnlp/mT5_multilingual_XLSum")
#txt_summarized_mT5_multilingual_XLSum = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_mT5_multilingual_XLSum= pd.DataFrame.from_dict(txt_summarized_mT5_multilingual_XLSum)

txt=[q[0:2000] for q in r.cuban_case_study_events['sentence'].values]  #first 2k characters
#Summarize with distilbart
summarizer = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
txt_summarized = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
len(txt_summarized[0]['summary_text'])
#txt_summarized[0]['summary_text']
df= pd.DataFrame.from_dict(txt_summarized)

#Summarize with bart-large-cnn
summarizer = pipeline("summarization", device=0, model="facebook/bart-large-cnn")
txt_summarized_bart = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
df_bart= pd.DataFrame.from_dict(txt_summarized_bart)

#summarizer = pipeline("summarization", device=0, model="google/pegasus-xsum") #requires a short 512 tokens
#txt_summarized_pegasus_xsum = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_pegasus_xsum= pd.DataFrame.from_dict(txt_summarized_pegasus_xsum)

#summarizer = pipeline("summarization", device=0, model="google/pegasus-multi_news")
#txt_summarized_pegasus_multi_news = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_pegasus_multi_news = pd.DataFrame.from_dict(txt_summarized_pegasus_multi_news)

#summarizer = pipeline("summarization", device=0, model="google/pegasus-cnn_dailymail")
#txt_summarized_pegasus_cnn_dailymail = summarizer(txt, min_length=50, max_length=100) #embarassingly slow #max_length=50, #, length_penalty=1500.0
#df_pegasus_cnn_dailymail = pd.DataFrame.from_dict(txt_summarized_pegasus_cnn_dailymail)

#Put on GPU
#https://github.com/huggingface/transformers/issues/2704

#txt=r.temp['sentence'].values[200]
#summarizer(txt[0:2], min_length=10, max_length=100) #crashes if I pass more than 1

#Token indices sequence length is longer than the specified maximum sequence length for this model (1313 > 1024). Running this sequence through the model will result in indexing errors
#txt=[q[0:2000] for q in r.temp['sentence'].values] #limit to first 4k
#summaries = [summarizer(q, min_length=10, max_length=100)  for q in txt] #

```

```{r}

cuban_case_study_events$summary_text_distilbart_cnn_12_6 = py$df$summary_text
cuban_case_study_events$summary_text_bart_large = py$df_bart$summary_text
#cuban_case_study_events$summary_text_mT5_multilingual_XLSum = py$df_mT5_multilingual_XLSum$summary_text
#
cuban_case_study_events  %>% write_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_case_study_events.csv")
dim(cuban_case_study_events) #486   4
cuban_case_study_events$n_sources %>% summary()

```

```{python, eval=F}

else:
  with open("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/cuba_embeddings.pickle", "rb") as f:
    unpickler = pickle.Unpickler(f)
    # if file is not empty scores will be equal
    # to the value unpickled
    sentences_embeddings = unpickler.load()

#More extras

  #res = faiss.StandardGpuResources()
  quantizer = faiss.IndexFlatL2(d)  # the other index
  nlist = 100
  #index = faiss.IndexIVFFlat(quantizer, d, nlist)
  #index.train(sentences_embeddings.astype('float32'))
  #index.is_trained
  index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
  index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
  #index.add(sentences_embeddings.astype('float32'))
  #gpu_index = faiss.index_cpu_to_gpu(res, 0, index)  
  #index.parallel_mode = 1
  #index.nprobe = 10
  distance, results = index.search(sentences_embeddings.astype('float32'), 5) #takes a while too
  #distance[:,1]
  #is it giving distance or similarity now?
  np.quantile( distance[:,1], [0.01,0.05,0.1,0.5,0.9,0.95,0.99] ) #you can see how the approximation perverts the distance #the median distance is .73 so that's good evidence we don't want to use that

  #It's fast because it's using torch.topk in the back
  #mining out high cor relationships is weird, crank top k and max pairs high and then threshold min cos later
  #This is a lot but it's still b
  #No matter what I do this takes about 2 min
  #paraphrases = paraphrase_mining_rex(model, sentences, show_progress_bar=True, top_k=500, batch_size=128*2, query_chunk_size=1000, max_pairs=60000000,min_score=0.8) #[0:2000] [0:10000] #60000000 400
  #len(paraphrases) #25,859,178 #19,490,957 #13,014,587
  #paraphrases_array=   np.vstack(paraphrases)
  #paraphrases_array.shape #25859178 #9,767,894
  #np.min(paraphrases_array[:,0])
  #condition= paraphrases_array[:,0]>0.8 #np.logical_and( ) #, paraphrases_array[:,0]<0.98
  #sum(condition) #2,038,562 #556,196 #545,160 #508242 #473,463
  #paraphrases_strongly = paraphrases_array[condition, :] #require a certain proximity
  #paraphrases_strongly.shape
  #np.min(paraphrases_array[:,0]) #the min it found was 0.7 already which is interesting
  #paraphrases_array.shape
  #We want to drop IDs that are too close
  #paraphrases_array_tooclose = paraphrases_array[paraphrases_array[:,0]>0.98, :] #thin any that are too close
  #paraphrases_array_tooclose.shape
  #protected=set()
  #dead=set()
  #for i in range(0,paraphrases_array_tooclose.shape[0]):
  #  a=int(paraphrases_array_tooclose[i,1])
  #  b=int(paraphrases_array_tooclose[i,2])
  #  if not a in protected and not a in dead and not b in protected and not b in dead: #if neither is assigned protect A
  #    protected.add(a)
  #  if a in protected and not a in dead and not b in protected and not b in dead: #
  #    dead.add(b)
  #  if not a in protected and not a in dead and b in dead: #if a isn't assigned but b is in dead protect a
  #    protected.add(a)
  #
  #
  #
#    
#Parallel version
#pool = model.start_multi_process_pool()
#emb = model.encode_multi_process(sentences, pool) #Compute the embeddings using the multi-process pool
#model.stop_multi_process_pool(pool) #Optional: Stop the proccesses in the pool
#
#sentences_embeddings.shape
#from sentence_transformers import SentenceTransformer, util
#cosine_scores = util.cos_sim(sentences_embeddings, sentences_embeddings)
#xxl
#  tensor([[1.0000, 0.7225, 0.8346, 0.9151, 0.9066],
#        [0.7225, 1.0000, 0.5697, 0.6481, 0.6713],
#        [0.8346, 0.5697, 1.0000, 0.7935, 0.7862],
#        [0.9151, 0.6481, 0.7935, 1.0000, 0.9403],
#        [0.9066, 0.6713, 0.7862, 0.9403, 1.0000]])
#xl
#tensor([[1.0000, 0.7127, 0.8432, 0.9232, 0.9157],
#        [0.7127, 1.0000, 0.5873, 0.6428, 0.6830],
#        [0.8432, 0.5873, 1.0000, 0.8099, 0.7972],
#        [0.9232, 0.6428, 0.8099, 1.0000, 0.9516],
#        [0.9157, 0.6830, 0.7972, 0.9516, 1.0000]])  
#sentences_embeddings = model.encode(sentences[0:1000]) #
#
#https://towardsdatascience.com/billion-scale-semantic-similarity-search-with-faiss-sbert-c845614962e2
from numba import cuda 
device = cuda.get_current_device()
device.reset()
import faiss
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
gpu_index = faiss.index_cpu_to_gpu(res, 0, index)
#faiss.write_index(index, 'abc_news')
#index = faiss.read_index('abc_news')
#import time
#def search(query):
# t=time.time()
# query_vector = model.encode([query])
# k = 5
# top_k = index.search(query_vector, k)
# print('totaltime: {}'.format(time.time()-t))
# return [sentences[_id] for _id in top_k[1].tolist()[0]]
#
n=sentences_embeddings.shape[0]
niter = 20 #doesn't improve after 20
verbose = True
d = sentences_embeddings.shape[1]

kmeans_125 = faiss.Kmeans(d, 125, niter=niter, verbose=verbose, gpu=True)
kmeans_125.train(sentences_embeddings)
D, cluster_125 = kmeans_125.index.search(sentences_embeddings, 1)

device.reset() #free up memory 
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
kmeans_250 = faiss.Kmeans(d, 250, niter=niter, verbose=verbose, gpu=True)
kmeans_250.train(sentences_embeddings)
D, cluster_250 = kmeans_250.index.search(sentences_embeddings, 1)

device.reset() #free up memory
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
kmeans_500 = faiss.Kmeans(d, 500, niter=niter, verbose=verbose, gpu=True)
kmeans_500.train(sentences_embeddings)
D, cluster_500 = kmeans_500.index.search(sentences_embeddings, 1)

device.reset() #free up memory
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
kmeans_1000 = faiss.Kmeans(d, 1000, niter=niter, verbose=verbose, gpu=True)
kmeans_1000.train(sentences_embeddings)
D, cluster_1000 = kmeans_1000.index.search(sentences_embeddings, 1)

device.reset() #free up memory
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
kmeans_2000 = faiss.Kmeans(d, 2000, niter=niter, verbose=verbose, gpu=True)
kmeans_2000.train(sentences_embeddings)
D, cluster_2000 = kmeans_2000.index.search(sentences_embeddings, 1)

device.reset() #free up memory
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
kmeans_4000 = faiss.Kmeans(d, 4000, niter=niter, verbose=verbose, gpu=True)
kmeans_4000.train(sentences_embeddings)
D, cluster_4000 = kmeans_4000.index.search(sentences_embeddings, 1)

device.reset() #free up memory
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
gpu_index = faiss.index_cpu_to_gpu(res, 0, index)
kmeans_8000 = faiss.Kmeans(d, 8000, niter=niter, verbose=verbose, gpu=True)
kmeans_8000.train(sentences_embeddings)
D, cluster_8000 = kmeans_8000.index.search(sentences_embeddings, 1)

device.reset() #free up memory 
res = faiss.StandardGpuResources()
index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
kmeans_16000 = faiss.Kmeans(d, 16000, niter=niter, verbose=verbose, gpu=True)
kmeans_16000.train(sentences_embeddings)
D, cluster_16000 = kmeans_16000.index.search(sentences_embeddings, 1)

device.reset() #free up memory

```

```{r, eval=F}

paraphrases_df <- as.data.frame(py$paraphrases_array) %>% arrange(V2, desc(V1)) %>% setNames(c('similarity', 'v1', 'v2'))
paraphrases_df$sentence1 = as.vector(unlist(py$sentences)[paraphrases_df$v1+1]) #remember to account for indexing
paraphrases_df$sentence2 = as.vector(unlist(py$sentences)[paraphrases_df$v2+1]) #remember to account for indexing
dim(paraphrases_df) #112,793

#We want to go further and also drop dupes of any sentences that are near exacts of each other, keep just one copy of them
paraphrases_df_dupes <- paraphrases_df %>% filter(similarity>0.93) %>% 
                        mutate(sentence1b = ifelse(sentence1>sentence2, sentence1, sentence2)) %>% 
                        mutate(sentence2b = ifelse(sentence1>sentence2, sentence2, sentence1)) %>% 
                        mutate(sentence1 = sentence1b) %>% 
                        mutate(sentence2 = sentence2b) %>% 
                        arrange(sentence1) %>%
                        mutate(dupe=  duplicated(sentence1))
glimpse(paraphrases_df_dupes)

todrop <- c(paraphrases_df_dupes$sentence1[paraphrases_df_dupes$dupe], paraphrases_df_dupes$sentence2 ) %>% unique()
#length(todrop)

paraphrases_df_urls <- paraphrases_df %>%
                       filter(!sentence1 %in% todrop) %>%
                       filter(!sentence2 %in% todrop) %>%
                       left_join( cuban_missile_clean_sentences %>% dplyr::select(url1=url, sentence1=sentence) ) %>%
                       left_join( cuban_missile_clean_sentences %>% dplyr::select(url2=url, sentence2=sentence) ) %>%
                       filter(url1!=url2) %>% dplyr::select(-v1,-v2) %>% 
                       mutate(V1_sentence_ordered=ifelse(sentence1<sentence2,sentence1,sentence2)) %>%
                       mutate(V2_sentence_ordered=ifelse(sentence1<sentence2,sentence2,sentence1)) %>%
                       dplyr::select(similaritya=similarity,sentence1=V1_sentence_ordered,sentence2=V2_sentence_ordered,url1,url2 ) %>% 
                       filter(similaritya<0.93  & similaritya>0.5 & trimws(tolower(sentence1))!=trimws(tolower(sentence2)) ) 
dim(paraphrases_df_urls) #106,875 #the good news is most are from different documents

#This is actually really tricky, we want to do greedy clustering without ever looping back into the first document
#I think we can actually do this with a series of joins

agg1 <- paraphrases_df_urls %>% 
        group_by(sentence1) %>% filter(similaritya==max(similaritya)) %>% ungroup() %>% 
        group_by(sentence2) %>% filter(similaritya==max(similaritya)) %>% ungroup()

agg2 <- agg1 %>% 
        left_join(paraphrases_df_urls %>%
                     rename(similarityb=similaritya,
                            sentence2=sentence1,
                            sentence3=sentence2,
                            url2=url1,
                            url3=url2
                            )
                  ) %>%
        filter(is.na(url3) | (url3!= url1 & url3!=url2)) %>%
        mutate(similarity_total = similaritya + similarityb) %>% 
        group_by(sentence1) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence2) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence3) %>% filter(similarity_total==max(similarity_total)) %>% ungroup()

#On 26 October, in one of several letters he exchan
agg3 <- agg2 %>% 
        left_join(paraphrases_df_urls %>%
                     rename(similarityc=similaritya,
                            sentence3=sentence1,
                            sentence4=sentence2,
                            url3=url1,
                            url4=url2
                            )
                  ) %>%
        filter(url4!= url1 & url4!=url2 & url4!=url3 ) %>%
        mutate(similarity_total = similaritya + similarityb + similarityc) %>% 
        group_by(sentence1) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence2) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence3) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence4) %>% filter(similarity_total==max(similarity_total)) %>% ungroup()

agg4 <- agg3 %>% 
        left_join(paraphrases_df_urls %>%
                     rename(similarityd=similaritya,
                            sentence4=sentence1,
                            sentence5=sentence2,
                            url4=url1,
                            url5=url2
                            )
                  ) %>%
        filter(url5!= url1 & url5!=url2 & url5!=url3 & url5!=url4 ) %>%
        mutate(similarity_total = similaritya + similarityb + similarityc + similarityd)  %>% 
        group_by(sentence1) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence2) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence3) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence4) %>% filter(similarity_total==max(similarity_total)) %>% ungroup()

agg5 <- agg4 %>% 
        left_join(paraphrases_df_urls %>%
                     rename(similaritye=similaritya,
                            sentence5=sentence1,
                            sentence6=sentence2,
                            url5=url1,
                            url6=url2
                            )
                  ) %>%
        filter(url6!= url1 & url6!=url2 & url6!=url3 & url6!=url4  & url6!=url5 ) %>%
        mutate(similarity_total = similaritya + similarityb + similarityc + similarityd + similaritye) %>% 
        group_by(sentence1) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence2) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence3) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence4) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>% 
        group_by(sentence5) %>% filter(similarity_total==max(similarity_total)) %>% ungroup() %>%
        mutate(cluster=row_number())

agg5 %>% dplyr::select(sentence6) %>% View()

temp <- agg5 %>% dplyr::select(cluster, starts_with('sentence')) %>% pivot_longer(-c(cluster)) %>%
  left_join(cuban_missile_clean_sentences %>% dplyr::select(value=sentence, position))

temp_collapse <- temp %>%
  group_by(cluster) %>%
  summarise(sentence=paste(value, collapse="\n"), position=mean(position)) %>%
  arrange(position)

temp_collapse  %>% as.data.frame() %>% write_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/temp_collapse.csv")

library(igraph)
library(lsa) ; #install.packages('lsa')
#g = make_graph("Zachary")
g <- graph_from_data_frame(paraphrases_df_subset[,c('V2','V3')], directed = FALSE, vertices = NULL)
#coords = layout_with_fr(g)
# plot the graph
#plot(g, layout=coords, vertex.label=NA, vertex.size=10)
c1 = cluster_fast_greedy(g)
#modularity(c1)
m <- membership(c1)
vertices <- bind_rows(
  paraphrases_df_subset %>% dplyr::select(v=V2, sentence=V2_sentence),
  paraphrases_df_subset %>% dplyr::select(v=V3, sentence=V3_sentence)
) %>% distinct() %>% arrange(v)
vertices$cluster <- as.vector(m)

paraphrases_df_subset  %>% as.data.frame() %>% write_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/paraphrases_df_subset.csv")

```

```{r, eval=F}

df = data.frame(
  sentence=cuban_missile_clean_sentences_unique,
  cluster_125=py$cluster_125,
  cluster_250=py$cluster_250,
  cluster_500=py$cluster_500,
  cluster_1000=py$cluster_1000,
  cluster_2000=py$cluster_2000,
  cluster_4000=py$cluster_4000,
  cluster_8000=py$cluster_8000,
  cluster_16000=py$cluster_16000
) %>%
  #add_count(cluster_1000) %>% 
  arrange(cluster_125, cluster_250, cluster_500, cluster_1000, cluster_2000,cluster_4000, cluster_8000,cluster_16000) #
#df$cluster_1000 %>% table() %>% sort()

#df %>% filter(cluster_1000==257)

cuban_missile_clean_sentences_clustered <- cuban_missile_clean_sentences %>% left_join(df) %>%
        arrange(cluster_125, cluster_250, cluster_500, cluster_1000, cluster_2000,cluster_4000, cluster_8000,cluster_16000)
saveRDS(cuban_missile_clean_sentences_clustered, "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences_clustered.Rds" )
```

It gets a little crash so it's best to do the above and then load a save from earlier, faster too

```{r, eval=F}

library(tidyverse)
cuban_missile_clean_sentences_clustered <- readRDS( "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_missile_clean_sentences_clustered.Rds" )

temp <- cuban_missile_clean_sentences_clustered  %>%
        #mutate(icb=url %>% str_detect("ICB")) %>%
        #mutate(sentence= ifelse(icb, paste("ICB- ", sentence) , sentence)) %>%
        #arrange(cluster_125, cluster_250, cluster_500, cluster_1000, cluster_2000,cluster_4000, cluster_8000,cluster_16000) %>% #somehow this arrange crashed it?
        group_by(cluster_16000) %>%
        summarise(
          n_sources=url %>% unique() %>% length(),
          sentence= sentence %>% paste(collapse="\n"),
          position=median(position)
          ) %>%
        arrange(n_sources %>% desc() ) %>%
        filter(n_sources>3)

temp  %>% write_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/cuban_case_study_events.csv")
dim(temp) #1019
temp$n_sources %>% summary()

```

```{python, eval=F}
  #print(out)

len(txt_summarized_distilbart)
#txt_summarized_bart
df_distilbart= pd.DataFrame.from_dict(txt_summarized_distilbart)

txt= "The Soviet commander in Cuba was authorised to use tactical nuclear weapons against United States forces should they invade, and as Soviet missiles were already installed, any attack on Cuba could have led to the outbreak of nuclear war."
summarizer_distilbart = pipeline("summarization", device=0, model="sshleifer/distilbart-cnn-12-6") #This is actually better than bart someone
txt_summarized_distilbart = summarizer_distilbart(txt, min_length=10, max_length=20,length_penalty=3.0, truncation=False) #embarassingly slow #max_length=50, #, length_penalty=1500.0
txt_summarized_distilbart
#' Soviet commander in Cuba authorised to use tactical nuclear weapons against U.S. forces if they invaded . Any attack on Cuba could have led to the outbreak of nuclear war .'

#https://github.com/vaibhavad/python-wrapper-OpenIE5
import pandas as pd
from pyopenie import OpenIE5
extractor = OpenIE5('http://localhost:8000')
extractions = extractor.extract("The U.S. president Barack Obama gave his speech to thousands of people.")
with open("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/in/case_studies/openie_sentences.txt", 'a', encoding = 'utf-8') as f:
  for k in range(0,r.cuban_missile_clean_sentences.shape[0] ):
    extraction=extractor.extract(r.cuban_missile_clean_sentences.sentence.values[k])
    df=pd.json_normalize(extraction)
    for i in range(0,df.shape[0]):
      url=r.cuban_missile_clean_sentences.url.values[k]
      txt=" ".join([df['extraction.arg1.text'].values[i], df['extraction.rel.text'].values[i], " ".join([q['text'] for q in df['extraction.arg2s'].values[i] ])  ])
      f.write(url + '\t' + txt + '\n')

import spacy                                                                                                                                               
import claucy                                                                                                                                               
nlp = spacy.load("en_core_web_sm")
claucy.add_to_pipe(nlp)                                                                                                                                     
doc = nlp("AE died in Princeton in 1955.")    
doc = nlp("Senior Kennedy administration officials, with the exception of independent CIA director John Mc-Cone, had assumed Moscow would never put long-range missiles into Cuba.")    
doc = nlp("The Soviet commander in Cuba was authorised to use tactical nuclear weapons against United States forces should they invade, and as Soviet missiles were already installed, any attack on Cuba could have led to the outbreak of nuclear war.")

doc._.clauses                                                                                                                                               
Out[6]: [<SV, AE, died, None, None, None, [in Princeton, in 1955]>]
propositions = doc._.clauses[0].to_propositions(as_text=True)                                                                                               
propositions

from allennlp.predictors.predictor import Predictor
import allennlp_models.tagging

predictor = Predictor.from_path("https://storage.googleapis.com/allennlp-public-models/openie-model.2020.03.26.tar.gz")
predictor.predict(sentence="In December, John decided to join the party.")

```

### 2022-07-17 replication_paper/rmd/old/04_ICBEdataset_paper_litreviewtable.Rmd
v1.1

--- 2022-03-23 replication_paper/rmd/04_ICBEdataset_paper_litreviewtable.Rmd
@@
 ```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
-library(pacman)
 
-p_load(flextable)
-p_load(ftExtra)
+library(flextable)
+library(ftExtra)
+library(tidyverse)
 
@@
 ```
+
+## Arxiv Version
 
@@
                   #"ICB Corpus"="Corpus",
-                  "ICBe (us)"="Events Datasets",
+                  "ICBe (ours)"="Events Datasets",
                   "Cameo"="Events Datasets",
@@
 
-```{r}
+## PNAS Version
 
+```{r, echo=FALSE, results='asis', include=T, cache=F, ft.arraystretch=0.75}
+
+#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
+# NOTE: If one of the citations is degenerate this will throw an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
+set_flextable_defaults(fonts_ignore=TRUE)
+
+lit_review_alt <- lit_review_pull%>% 
+                  mutate(Literature =   paste0("[",Literature %>% str_replace("; {0,}$","") ,"]")) %>%
+                  mutate(Concept= Concept %>% paste0(Literature)) %>%
+                  mutate(Concept = ifelse(Concept=="N[NA]", "N", Concept) ) %>%
+                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
+                  #dplyr::filter(is.na(group))
+
+n=nrow(lit_review_alt)
+ft <- NULL
+ft <- lit_review_alt %>%
+      flextable::as_flextable() %>%
+      add_header( 
+                  #"ICB Corpus"="Corpus",
+                  "ICBe (ours)"="Events Datasets",
+                  "Cameo"="Events Datasets",
+                  "MIDs Incidents"="Events Datasets",
+                  "UCDP-GED"="Events Datasets",
+                  "ICB"="Episodes Datasets",
+                  "COW"="Episodes Datasets",
+                  "MIDs"="Episodes Datasets",
+                  top = TRUE ) %>%
+
+      set_header_labels(
+        values = list("...1" = "" , "...2" = "" ) 
+        ) %>%
+      merge_h(part = "header") %>%
+
+      #bg( i=1:(n) , j = condition, part = "body", bg = "#EFEFEF") %>%
+      #bg( i=2 , j = condition, part = "header", bg = "#EFEFEF") %>%
+      bg( i = which( 1:nrow(lit_review_alt) %% 2 == 1)  , j=3:ncol(lit_review_alt), part = "body", bg = "#EFEFEF") %>%
+      #width(j = 1, width=1.25) %>%
+      #width(j = 2:ncol(lit_review_alt), width=0.25) %>%
+      flextable::fontsize(size = 7, part = "all") %>%
+      flextable::rotate(i=2, rotation="tbrl",part="header") %>%
+      #flextable::set_header_labels( values = list(x1 = "", x2 = "")) %>%
+      flextable::align(align = "center", part = "body") %>%
+      flextable::align(align = "center", part = "header")   %>%
+
+      flextable::colformat_char(
+          j = 1:ncol(lit_review_alt),
+          na_str = "",
+          prefix = "",
+          suffix = ""
+      ) %>%
+
+      #hline(i=c(1), j=3:ncol(lit_review_alt),  border = NULL, part = "header") %>%
+      hline(i=c(2,3,7,10,15, 19, 27), border = NULL, part = "body") %>% #,10,14, 20,27,37, n
+
+      #set_table_properties(layout="autofit")  %>%
+      vline( i = 1:2, j = c(3,7,10), border = NULL, part = "header") %>%
+      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
+      vline( i = 1:(n), j = c(3,7,10), border = NULL, part = "body")
+
+      #autofit()
+      #fit_to_width(max_width=12) #This is crazy slow
+      #flextable::autofit() 
+      #set_table_properties(width = 1, layout = "autofit")
+
+#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
+
+litreview_ft_pnas <- ft %>% 
+  flextable::width( j = 3, width=4) %>% 
+  flextable::width( j = (4):ncol(lit_review_alt), width=0.25) %>%
+  flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
+  flextable::padding(padding = 0, part = "body") %>%
+  #merge_v( j = 1,  part = "body", combine = T) %>%
+  #merge_v( j = 2,  part = "body", combine = T) %>%
+  #merge_h( i = 1:2,  part = "body") %>%
+
+  merge_at(i = 4:7, j = 1:2, part = "body") %>%
+  merge_at(i = 8:10, j = 1:2, part = "body") %>%
+  merge_at(i = 11:15, j = 1:2, part = "body") %>%
+  merge_at(i = 16:19, j = 1:2, part = "body") %>%
+
+  merge_at(i = 20:n, j = 1, part = "body") %>%
+  merge_at(i = 20:28, j = 2, part = "body") %>%
+  merge_at(i = 29:n, j = 2, part = "body") %>%
+
+  #hline(i=c(27), border = NULL, part = "body")  %>% #After the merge we have to put this hline back in  on second thought that doesn't put it back either
+
+  #merge_v( j = 1,  part = "body", combine = T) %>%
+
+  #merge_at(i = NULL, j = NULL, part = "body") %>%
+  #merge_at(i = NULL, j = NULL, part = "body") %>%
+
+  flextable::rotate(j=1, rotation="tbrl",part="all") %>%
+  flextable::rotate(j=2, rotation="tbrl",part="all") %>%
+  flextable::width( j = 1:2, width=0.1)  %>%
+  ftExtra::colformat_md(j = 3, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
+
+litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
+
+litreview_ft_pnas
+
+```
+
+```{r, eval=F}
+
+#For the website I think
 n=nrow(lit_review_alt)

### 2022-07-17 replication_paper/rmd/old/05_ICBEdataset_paper_PlotInterCoderAgreement.Rmd
v1.1

--- 2022-01-26 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
@@
 ```{r}
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
-codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
-codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
-codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))
-
-```
-
-Self Reported Confidence and Percent Agreement
-
-```{r}
-confidence_totals <- bind_rows(
-  icb_long_clean %>% filter(email_id %>% str_detect('expert') & variable_normalized=='raterconfidence' ) %>% count(value_normalized) %>% mutate(coder="expert") %>% mutate(n= (n/sum(n)*100) %>% round(1) %>% paste0("%") ),
-  icb_long_clean %>% filter(email_id %>% str_detect('undergrad') & variable_normalized=='raterconfidence' ) %>% count(value_normalized)  %>% mutate(coder="undergrad") %>% mutate(n=(n/sum(n)*100) %>% round(1) %>% paste0("%"))
-) %>%
-  mutate(confidence=value_normalized %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
-  mutate(x=0.05)
-
-c1 <- codings_long_agreement  %>% filter(keep==T) %>% dplyr::select(selected_by_perc=selected_by_any_perc,confidence=confidence)  %>% mutate(name="Accepted_Either")
-c2 <- codings_long_agreement %>% dplyr::select(selected_by_perc=selected_by_any_perc,confidence=confidence) %>% mutate(name="Accepted_Either")
-c3 <- codings_long_agreement %>% dplyr::select(selected_by_perc=selected_by_experts_perc,confidence=confidence_expert) %>% mutate(name="Experts")
-c4 <- codings_long_agreement %>% dplyr::select(selected_by_perc=selected_by_undergrads_perc,confidence=confidence_undergrad) %>% mutate(name="Undergraduates")
-bind_rows(c1,c2,c3,c4) %>% na.omit() %>%
-  ggplot(aes(x=confidence, y=selected_by_perc, color=name)) + geom_smooth() #geom_point()
-
-library(ggExtra)
-p1_confidence_agreement <-   codings_long_agreement %>% #codings_long %>%  codings_long_agreement
-    mutate(confidence=confidence %>% round() %>% as.factor() ) %>%
-    filter(value_normalized!='') %>%
-    filter(total_coders>1) %>% #about 9k only had one coder
-    filter(selected_by_experts>=1) %>%
-    dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc,keep,confidence) %>%
-    group_by(confidence) %>%
-    summarise(
-        Accepted_Either=selected_by_any_perc[keep==1] %>% mean(na.rm=T), 
-        Either=selected_by_any_perc %>% mean(na.rm=T), 
-        Experts=selected_by_experts_perc %>% mean(na.rm=T), 
-        Undergraduates=selected_by_undergrads_perc %>% mean(na.rm=T)
-    ) %>%
-    filter(!is.na(confidence)) %>%
-    #mutate(variable_normalized=fct_reorder(variable_normalized, Either)) %>%
-    pivot_longer(c(-confidence)) %>%
-    ggplot(aes(x=selected_by_any_perc, y=confidence)) + 
-    #geom_boxplot() + 
-    geom_point(aes(x=value, color=name )) +
-    xlab("Percent of Coders") +
-    ylab("Confidence") +
-    labs(title = "Percent of Coders who Chose a Tag by Confidence and Type of Coder"#,
-          #subtitle = "Plot of length by dose",
-          #caption = "Data source: ToothGrowth"
-         ) + 
-    theme_bw()
-p1_confidence_agreement + theme(legend.position="bottom")
 
@@
 
-#Calculate average agreements by group
-means1 <- codings_long_agreement %>% 
-              filter(value_normalized!='') %>%
-              filter(total_coders>1) %>% #about 9k only had one coder
-              #filter(selected_by_experts>=1) %>%
-              dplyr::select(All=selected_by_any_perc,Experts=selected_by_experts_perc,Undergraduates=selected_by_undergrads_perc) %>% summarise_all(mean, na.rm=T)
-means1_keep <- codings_long_agreement %>% 
-      filter(value_normalized!='') %>%
-    filter(total_coders>1) %>% #about 9k only had one coder
-    #filter(selected_by_experts>=1) %>%
-  filter(keep==1) %>% dplyr::select(Accepted=selected_by_any_perc) %>% summarise_all(mean, na.rm=T)
-meansall <- bind_rows(means1,means1_keep) %>% mutate(x=1) %>% pivot_longer(cols=c(-x)) %>% na.omit()
-
-#These are all by definition chosen by at least 1
-#Do we further require at least 1 expert as with our aggregations?
-p_percent_chose_tag_by_concept <- 
-  codings_long_agreement %>% #codings_long %>%  codings_long_agreement
-    mutate(variable_normalized=variable_normalized %>% str_replace_all("_"," ") %>% tolower() ) %>%
-    filter(value_normalized!='') %>%
-    filter(total_coders>1) %>% #about 9k only had one coder
-    #filter(selected_by_experts>=1) %>%
-    dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc,keep) %>%
-    group_by(variable_normalized) %>%
-      summarise(
-          N=n(),
-          Accepted=selected_by_any_perc[keep==1] %>% mean(na.rm=T), 
-          All=selected_by_any_perc %>% mean(na.rm=T), 
-          Experts=selected_by_experts_perc %>% mean(na.rm=T), 
-          Undergraduates=selected_by_undergrads_perc %>% mean(na.rm=T)
-      ) %>%
-    filter(N>10) %>%
-    dplyr::select(-N) %>%
-    mutate(variable_normalized=fct_reorder(variable_normalized, Accepted)) %>%
-    pivot_longer(c(-variable_normalized)) %>%
-    ggplot(aes(x=selected_by_any_perc, y=variable_normalized)) + 
-    #geom_boxplot() + 
-    geom_point(aes(x=value, color=name )) +
-    xlab("Percent of Coders that selected Tag") +
-    ylab("") +
-    labs(
-      # title = "Intercoder Agreement by Concept/Type",
-      # subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
-          caption = paste0("Point = mean by concept; Line = mean by group\nUnit of Analysis: Tag chosen by any Coder, N=", codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma(), "; Accepted Tokens=", codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()),
-         color = "Codings"
-         ) + 
-    theme_bw() +
-    theme(legend.position="bottom") +
-    geom_vline(data=meansall, aes(xintercept = value, color = name), linetype="solid", size=1, alpha=0.5)
-
 ```
@@
 
-p_percent_chose_tag_by_concept %>% saveRDS(paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.Rds'))
-p_percent_chose_tag_by_concept
-
-ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
-                plot = p_percent_chose_tag_by_concept, width=8, height=6)
 #table(expert_majority=codings_long$expert_majority,
@@
 ```
+
+```{r}
+
+```

### 2022-07-17 replication_paper/rmd/old/13_embedding.Rmd
v1.1

---
title: 'Intercoder ICBEdataset_figure_semantic_embeddings'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
---

# Intro

## Library Loads

```{r}

library(flextable)
library(ftExtra)
library(tidyverse)

#Load it here before the python reticulate business
#devtools::install_github("ropenscilabs/umapr")
#library(umapr)

```

```{r}

ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))

```

```{r}

ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
                                                 str_replace_all("[0-9]{4}","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all("Entity Entity","Entity") %>%
                                                 str_replace_all(" {1,}"," ") 
                                               )  #

sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
                    dplyr::select(sentences_unique_sanitized) %>% 
                    distinct() %>%
                    pull(sentences_unique_sanitized) %>% 
                    unique() %>% na.omit()
length(sentences_unique ) #12162
head(sentences_unique)

```

To set python, set it in ~/.Renviron. `use_python()` doesn't seem to work as desired. See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).

```{r, messages=F, results='hide'}

library(reticulate)
reticulate::py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

```

```{python}
#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
#pip install -U sentence-transformers

fromscratch=False

if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #12161 12162
  n=len(sentences)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #12161, 768
  #At this point we're done, we don't need to cluster for this step
  #Parallel version
  #pool = model.start_multi_process_pool()
  #emb = model.encode_multi_process(sentences, pool) #Compute the embeddings using the multi-process pool
  #model.stop_multi_process_pool(pool) #Optional: Stop the proccesses in the pool
  #
  #sentences_embeddings.shape
  #from sentence_transformers import SentenceTransformer, util
  #cosine_scores = util.cos_sim(sentences_embeddings, sentences_embeddings)
  #xxl
  #  tensor([[1.0000, 0.7225, 0.8346, 0.9151, 0.9066],
  #        [0.7225, 1.0000, 0.5697, 0.6481, 0.6713],
  #        [0.8346, 0.5697, 1.0000, 0.7935, 0.7862],
  #        [0.9151, 0.6481, 0.7935, 1.0000, 0.9403],
  #        [0.9066, 0.6713, 0.7862, 0.9403, 1.0000]])
  #xl
  #tensor([[1.0000, 0.7127, 0.8432, 0.9232, 0.9157],
  #        [0.7127, 1.0000, 0.5873, 0.6428, 0.6830],
  #        [0.8432, 0.5873, 1.0000, 0.8099, 0.7972],
  #        [0.9232, 0.6428, 0.8099, 1.0000, 0.9516],
  #        [0.9157, 0.6830, 0.7972, 0.9516, 1.0000]])  
  #sentences_embeddings = model.encode(sentences[0:1000]) #
  #
  #https://towardsdatascience.com/billion-scale-semantic-similarity-search-with-faiss-sbert-c845614962e2
  # from numba import cuda 
  # device = cuda.get_current_device()
  # device.reset()
  # import faiss
  # res = faiss.StandardGpuResources()
  # index = faiss.IndexIDMap(faiss.IndexFlatIP(768)) #Ip stands for inner product which is cosine on normalized vectors
  # index.add_with_ids(sentences_embeddings, np.array(range(0, len(sentences_embeddings))))
  # gpu_index = faiss.index_cpu_to_gpu(res, 0, index)
  # #faiss.write_index(index, 'abc_news')
  # #index = faiss.read_index('abc_news')
  # #import time
  # #def search(query):
  # # t=time.time()
  # # query_vector = model.encode([query])
  # # k = 5
  # # top_k = index.search(query_vector, k)
  # # print('totaltime: {}'.format(time.time()-t))
  # # return [sentences[_id] for _id in top_k[1].tolist()[0]]
  # #
  # n=sentences_embeddings.shape[0]
  # ncentroids = 50
  # niter = 20
  # verbose = True
  # d = sentences_embeddings.shape[1]
  # kmeans_125 = faiss.Kmeans(d, 125, niter=niter, verbose=verbose)
  # kmeans_125.train(sentences_embeddings)
  # D, cluster_125 = kmeans_125.index.search(sentences_embeddings, 1)
  # kmeans_250 = faiss.Kmeans(d, 250, niter=niter, verbose=verbose)
  # kmeans_250.train(sentences_embeddings)
  # D, cluster_250 = kmeans_250.index.search(sentences_embeddings, 1)
  # kmeans_500 = faiss.Kmeans(d, 500, niter=niter, verbose=verbose)
  # kmeans_500.train(sentences_embeddings)
  # D, cluster_500 = kmeans_500.index.search(sentences_embeddings, 1)
  # kmeans_1000 = faiss.Kmeans(d, 1000, niter=niter, verbose=verbose)
  # kmeans_1000.train(sentences_embeddings)
  # D, cluster_1000 = kmeans_1000.index.search(sentences_embeddings, 1)
  # kmeans_2000 = faiss.Kmeans(d, 2000, niter=niter, verbose=verbose)
  # kmeans_2000.train(sentences_embeddings)
  # D, cluster_2000 = kmeans_2000.index.search(sentences_embeddings, 1)

else:
  print("Skipping")

```

```{r, eval=F}

df = data.frame(
  sentences=py$sentences,
  cluster_125=py$cluster_125,
  cluster_250=py$cluster_250,
  cluster_500=py$cluster_500,
  cluster_1000=py$cluster_1000,
  cluster_2000=py$cluster_2000
) %>%
  add_count(cluster_1000) %>% arrange(cluster_125, cluster_250, cluster_500, cluster_1000, cluster_2000)
df$cluster_1000 %>% table() %>% sort()

df %>% filter(cluster_1000==257)

```

```{r}
fromscratch = FALSE

if(fromscratch){
  sentences_embeddings <- py$sentences_embeddings
  dim(sentences_embeddings)
  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
}else{
  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
  dim(sentences_embeddings)
}

```
The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.

```{r}

embedding <- umapr::umap(sentences_embeddings)
plot(embedding[,c('UMAP1','UMAP2')])

sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()

sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique

ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
                                        left_join(sentences_embeded_umap) %>% 
                                        left_join(sentences_embeded_mpnet)

ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))

ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
                                                arrange(UMAP1,UMAP2) %>%
                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis

```

```{r, eval=F}

#Moved a copy of this to the paper

ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))

#act_escalate
#act_deescalate
#act_uncooperative
#act_cooperative
#interact_escalate
#interact_deescalate
#interact_increasecoop
#interact_decreasecoop

value_means <- ICBe_events_agreed_markdown_embedded %>%
               dplyr::select(UMAP1,UMAP2, contains("escalate"),contains("coop"),contains("sayintkind"), contains("thinkkind")) %>%
               pivot_longer(cols=-c(UMAP1,UMAP2)) %>% filter(!is.na(value) & value!='') %>% 
               mutate(value = value %>% str_split(";")) %>% 
               unnest(value) %>% 
               mutate(value = value %>% str_trim()) %>%
               filter(!value %>% str_detect("sentence|^[0-9]")) %>%
               mutate(color=NA) %>%
               mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
               mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
               mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
               mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
               mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
               mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
               dplyr::select(-name) %>%
               group_by(color, value) %>%
               mutate(n=n()) %>%
               filter(n>20) %>%
               dplyr::summarise_all(median)

value_normalized_colors <- value_means$color 
names(value_normalized_colors) = value_means$value

library(ggplot2)
library(ggrepel)
p_semantic_embeddings <-
      ICBe_events_agreed_markdown_embedded %>%
      ggplot(aes(x=UMAP1,y=UMAP2)) +
      geom_point(size=0.5, alpha=0.25) + 
      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
      theme_bw() +
      theme(legend.position = "none") + 
      geom_label(data=value_means,
                 aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=50), size = 2.5, inherit.aes=F, 
                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
                 ) +   
      #geom_label_repel(data=value_means,
      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
      #           min.segment.length = 0
      #           ) + 
      labs(
          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
          caption = ""
      ) +
     scale_color_manual(values = value_normalized_colors) +
     scale_fill_manual(values = value_normalized_colors) +
     scale_x_continuous(expand = c(0, 0)) +
     scale_y_continuous( expand = c(0, 0)) + 
       coord_flip()

ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)

```

```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}

temp <- ICBe_events_agreed_markdown_embedded_sample %>%
        #filter(crisno==196) %>%
        group_by(crisno, sentence_number_int_aligned) %>%
          filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
        ungroup() %>%
        mutate(banding=sentence_number_int_aligned %% 2)
temp$is_subsstring <- NA
for(i in 1:nrow(temp)){
  temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
                                                                                pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
                                                                              ) %>% replace_na(0) %>%  sum()
}
temp <-temp %>%
        mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
        group_by(sentence_number_int_aligned) %>%
          filter(value_markdown!='' | length(value_markdown)==1) %>%
        ungroup() %>%
        mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
        mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
        mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
      #head(100) %>%
ft_sample_precision <- temp %>%
                     dplyr::select(C=crisno,S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
                      flextable::as_flextable() %>%
                      flextable::width( j = 1, width=0.25)  %>%
                      flextable::width( j = 2, width=0.25)  %>% 
                      flextable::width( j = 3, width=8.0)  %>% 
                      flextable::width( j = 4, width=8.0)  %>% 
                      flextable::fontsize(size = 9, part = "all") %>%
                      valign(j = 1:4, valign = "top", part = "body") %>%
                      flextable::line_spacing( space = 1.0, part = "all") %>% 
                      padding( padding = 1, part = "all") %>% 
                      bg( i = which( temp$banding==1 ) , part = "body", bg = "#EFEFEF", j=1:4) %>%
                      ftExtra::colformat_md(j = 4, part="body")
#ft_sample_precision

ft_sample_precision %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_sample_precision_precision.png", zoom=1) # webshot = "webshot2"
temp <- NULL

```

### 2022-07-17 replication_paper/rmd/old/SI1_Crises.Rmd
v1.1

---
title: "Untitled"
output: html_document
date: '2022-05-31'
---

```{r setup, include=FALSE}

ICBe_crises_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds"))

```

```{r}

crisis_text_counts_ft <- ICBe_crises_markdown %>% ungroup() %>%
      #filter(crisno %in% c(1:100) ) %>%
      dplyr::select(crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events,  coders_expert, coders_novice, actors, units_domains, forces_fatalities) %>%
      #act leaving off for the paper, may include in the website if room
      mutate(crisno = crisno %>% as.character() ) %>%
      mutate(yrtrig = yrtrig %>% as.character() ) %>%
      mutate(yrterm = yrterm %>% as.character() ) %>%
      #group_by(crisno, sentence_number_int_aligned) %>%
      #  filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
      #ungroup() %>%
      #mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
      #mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
      #mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text)) %>%
      #dplyr::select(C=crisno, S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown) %>%
      #head(100) %>%
      flextable::as_flextable() %>%
      flextable::set_header_labels(values = 
          list(crisno = "#",
                crisis_text = "Title",
                yrtrig = "Start",
                yrterm = "End",
                n_sentence_number_int_aligned = "#S",
                n_events = "#E",
                coders_expert = "#Exp",
                coders_novice = "#Nov"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::add_header(values = 
          list(crisno = "Crisis",
                crisis_text = "Crisis",
                yrtrig = "Years",
                yrterm = "Years",
                n_sentence_number_int_aligned = "Counts",
                n_events = "Counts",
                coders_expert = "Coders",
                coders_novice = "Coders"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::merge_h(part = "header" ) %>%
      flextable::width( j = 1, width=0.1)  %>% 
      flextable::width( j = 2, width=0.5)  %>% 
      flextable::width( j = 3, width=0.1)  %>% 
      flextable::width( j = 4, width=0.1)  %>% 
      flextable::width( j = 5, width=0.1)  %>% 
      flextable::width( j = 6, width=0.1)  %>% 
      flextable::width( j = 7, width=0.1)  %>% 
      flextable::width( j = 8, width=0.1)  %>% 
      flextable::width( j = 9, width=2.0)  %>% 
      flextable::width( j = 10, width=1.0)  %>%
      flextable::width( j = 11, width=1.0)  %>%
      #flextable::width( j = 12, width=3.0)  %>%

      flextable::fontsize(size = 9, part = "all") %>%
      #flextable::merge_v(j=1:8) %>%
      ftExtra::colformat_md(j = 9:11, part="body")
crisis_text_counts_ft

crisis_text_counts_ft  %>% saveRDS(paste0(here::here(), "/replication_paper/tables/ft_crisis_text_counts.Rds"))

```

### 2022-07-17 replication_paper/rmd/old/__PlotConfidence.Rmd
v1.1

---
title: 'Plot Confidence'
site: bookdown::bookdown_site
bibliography: ../ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
---

# Intro

## Library Loads

```{r}
library(flextable)
library(tidyverse)

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))

```

Self Reported Confidence and Percent Agreement

```{r, eval=F}

confidence_totals <- bind_rows(
  icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>% count(value_normalized) %>% mutate(coder="expert") %>% mutate(n= (n/sum(n)*100) %>% round(1) %>% paste0("%") ),
  icb_long_clean %>% filter(email_id %>% str_detect('undergrad') & varname_normalized=='raterconfidence' ) %>% count(value_normalized)  %>% mutate(coder="undergrad") %>% mutate(n=(n/sum(n)*100) %>% round(1) %>% paste0("%"))
) %>%
  mutate(confidence=value_normalized %>% factor(levels=c('none','low','high','complete')) %>% as.numeric() ) %>%
  mutate(x=0.05)

confidence_totals %>% dplyr::select(coder, value_normalized, n) %>% pivot_wider(id_cols=coder, names_from=value_normalized, values_from=n) %>% 
  dplyr::select(coder  , none,  low,  high,  complete      )

```

### 2022-07-17 replication_paper/rmd/old/__WordNetComparison.Rmd
v1.1

--- 2022-07-17 replication_paper/pnas_draft/pnas_draft.Rmd
@@
 ---
-title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"
-
-# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-author:
-  - name: Rex W. Douglass
-    affiliation: a,1,2
-  - name: Thomas Leo Scherer
-    affiliation: a
-  - name: J. Andrés Gannon
-    affiliation: b
-  - name: Erik Gartzke
-    affiliation: a
-  - name: Jon Lindsay
-    affiliation: c
-  - name: Shannon Carcelli
-    affiliation: d
-  - name: Jonathan Wilkenfeld
-    affiliation: d
-  - name: David M. Quinn
-    affiliation: e
-  - name: Catherine Aiken
-    affiliation: f
-  - name: Jose Miguel Cabezas Navarro
-    affiliation: g
-  - name: Neil Lund
-    affiliation: d
-  - name: Egle Murauskaite
-    affiliation: h
-  - name: Diana Partridge
-    affiliation: h
-
-address:
-  - code: a
-    address: Department of Political Science, University of California, San Diego, CA, USA.
-  - code: b
-    address: Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.
-  - code: c
-    address: School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.
-  - code: d
-    address: Department of Government and Politics, University of Maryland, College Park, MD, USA.
-  - code: e
-    address: Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.
-  - code: f
-    address: Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.
-  - code: g
-    address: Society and Health Research Center, Universidad Mayor, Santiago, Chile.
-  - code: h
-    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
-  - code: i
-    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
-
-corresponding_author:
-  code: 2
-  text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"
-
-# For footer text
-lead_author_surname: Douglass
-
-#following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
-author_contributions: |
-  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
-  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
-
-## Remove this if not required
-conflict_of_interest: |
-  Please declare any conflict of interest here.
-
-#Please provide an abstract of no more than 250 words in a single paragraph.
-Abstracts should explain to the general reader the major contributions of the article.
-References in the abstract must be cited in full within the abstract itself and cited in the text.
-abstract: |
-  How do international crises unfold?
-We conceive of international affairs as a strategic chess game between adversaries, necessitating a systematic way to measure pieces, moves, and gambits accurately and consistently over different contexts and periods.
-We develop such a measurement strategy with an ontology of crisis actions and interactions and apply it to a high-quality corpus of crisis narratives recorded by the International Crisis Behavior (ICB) Project.
-We demonstrate that the ontology has high coverage over most of the thoughts, speech, and actions contained in international crises and produces high inter-coder agreement when applied by human coders.
-We introduce a new crisis event dataset ICB Events (ICBe).
-We find that ICBe captures the process of a crisis with greater accuracy and granularity than other well-regarded event or episode level datasets.
-We make the data, replication material, and additional visualizations available at a companion website www.crisisevents.org.
-
-significance: |
-  Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
-The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership.
-The Significance Statement appears in the paper itself and is required for all research papers.
-
-acknowledgements: |
-  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-We thank the many undergraduate coders for their patience and dedication.
-Thanks to the Center for Peace and Security Studies and its membership for comments.
-Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
-Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
-
-keywords:
-  - Diplomacy
-  - War
-  - Crises
-  - International Affairs
-  - Computational Social Science
-
-## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
-pnas_type: pnasresearcharticle
-
-bibliography: ICBintro.bib
-csl: pnas.csl
-
-## change to true to add optional line numbering
-lineno: false
-
-output: rticles::pnas_article
-
-#Disabled several the caused errors
-header-includes:
-  - \usepackage[utf8]{inputenc}
-  - \usepackage{pifont}
-  - \usepackage{newunicodechar}
-  - \newunicodechar{✓}{\ding{51}}
-  - \newunicodechar{✗}{\ding{55}}
-  - \usepackage{array}
-  - \usepackage{ctable} # added for demo
-  - \usepackage{natbib} #added for latex citation within huxtable
-  - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage{wrapfig}
-  - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{titlesec}
-  - \usepackage[parfill]{parskip}
-  - \usepackage{makecell}
-  - \usepackage{graphicx}
-  - \usepackage{caption}
-#  - \usepackage[capposition=top]{floatrow}
-  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
-  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
-  - \DeclareUnicodeCharacter{00A0}{ }
-  - \usepackage{setspace}
-  - \usepackage{cellspace}
-  - \setlength\cellspacetoplimit{0.8ex}
-  - \renewcommand{\arraystretch}{0.8}
-  - \AtBeginEnvironment{tabular}{\singlespacing}
-  - \AtBeginEnvironment{lltable}{\singlespacing}
-#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-  - \usepackage{subcaption}
-  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
-  - \usepackage{float}
-#  - \usepackage{eso-pic,graphicx,transparent}
-#  - \usepackage[perpage]{footmisc}
-  - \usepackage[algo2e]{algorithm2e}
-#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
+title: "__WordNetComparison.Rmd"
+output: html_document
+date: '2022-05-18'
 ---
-
-```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
-#International Crisis Behavior Events (ICBe) Dataset
-knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
-
-```
-
-```{r, eval=T, echo=F, cache=F}
-
-#library(pacman)
-library(googlesheets4)
-library(tidyverse)
-library(janitor)
-library(flextable)
-set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`.
-You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
-library(ftExtra)
-options(tidyverse.quiet = TRUE)
-options(gargle_oauth_email = TRUE)
-
-#install.packages('stargazer')
-#install.packages('kableExtra')
-#! sh: 1: pdflatex: not found
-#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended
-
-#! LaTeX Error: File `letltxmacro.sty' not found.
-#sudo apt-get install texlive-latex-extra
-
-```
-
-```{r, echo=F}
-#Notes
-#https://tex.stackexchange.com/questions/83440/inputenc-error-unicode-char-u8-not-set-up-for-use-with-latex
-#- \DeclareUnicodeCharacter{00A0}{ }
-
-```
-
-```{r, include=FALSE}
-# options(tinytex.verbose = TRUE)
-```
 
@@
 
-`%>%` <- magrittr::`%>%`
-
-```
-
-```{r, echo=FALSE}
-
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_long_clean.Rds"))
-icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1_long_agreement.Rds") )
-codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1_long_agreed.Rds'))
-codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1_wide_agreed.Rds'))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
+#icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1_wide_clean.Rds"))
+codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )
+codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1.1_long_agreed.Rds'))
+codings_wide_agreed <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1.1_wide_agreed.Rds'))
 
@@
 
-n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
-n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
-n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
-n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
-n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()
+n_crisis <- codings_wide_agreed %>% dplyr::select(crisno) %>% unique() %>% nrow()
+n_sentences <- codings_wide_agreed %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
+n_events <- codings_wide_agreed %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
+n_events_cuba <- codings_wide_agreed %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
+n_coders <- codings_wide_agreed %>% dplyr::select(email_id) %>% unique() %>% nrow()
 
-avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
+avg_coders_per_crisis <- codings_wide_agreed %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
 
-avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
+avg_coders_per_sentence <- codings_wide_agreed %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
 
-avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
+avg_events_per_coder_crisis <- codings_wide_agreed %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
 
-events_per_sentence <- icb_wide_clean %>%
-  filter(!is.na(sentence_number_int_aligned)) %>%
-  dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) %>%  #event_number_int
-  group_by(email_id,crisno,sentence_number_int_aligned) %>%
-  summarise(event_count = sum(!is.na(event_type) ) ) %>%
-  mutate_all(as.numeric) %>%
-  group_by(crisno,sentence_number_int_aligned) %>%
-  summarise(
-    event_count_min=event_count %>% min(),
-    event_count_mean=event_count %>% mean(na.rm=T),
-    event_count_max=event_count %>% max()
-  ) %>%
-  arrange(crisno,sentence_number_int_aligned)
+#events_per_sentence <- codings_wide_agreed %>%
+#                      filter(!is.na(sentence_number_int_aligned)) %>%
+#                      dplyr::select(email_id, crisno,sentence_number_int_aligned,  event_type) %>%  #event_number_int
+#                      group_by(email_id,crisno,sentence_number_int_aligned) %>%
+#                      summarise(event_count = sum(!is.na(event_type) ) ) %>%
+#                      mutate_all(as.numeric) %>%
+#                      group_by(crisno,sentence_number_int_aligned) %>%
+#                      summarise(
+#                        event_count_min=event_count %>% min(),
+#                        event_count_mean=event_count %>% mean(na.rm=T),
+#                        event_count_max=event_count %>% max()
+#                      ) %>%
+#                      arrange(crisno,sentence_number_int_aligned)
+#
+#events_per_crisis <- events_per_sentence %>% group_by(crisno) %>% summarise(event_count_mean_sum=sum(event_count_mean))
 
-events_per_crisis <- events_per_sentence %>% group_by(crisno) %>% summarise(event_count_mean_sum=sum(event_count_mean))
-
-crisis_text_counts <- icb_wide_clean %>%
-  #mutate( input_crisis = input_crisis %>% str_replace_all("[^A-Za-z0-9 ]","") ) %>% #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
-  #https://www.google.com/search?q=R+replace+00A0&oq=R+replace+00A0&aqs=chrome..69i57j0i20i263i512j0i512l2j69i65j69i60l3.1744j0j7&sourceid=chrome&ie=UTF-8
-  dplyr::select(crisno, sentence) %>%
-  #mutate(input_crisis = input_crisis %>% stringr::str_to_title()) %>%
-  #mutate(input_crisis = input_crisis %>% stringr::str_replace_all('[0-9]$','')) %>%
-  mutate(sentence = sentence %>% stringr::str_to_lower()) %>%
-  distinct() %>%
-  #filter(!is.na(input_crisis)) %>%
-  filter(!is.na(sentence)) %>%
-  mutate(word_count=str_count(sentence, '\\w+')) %>%
-  group_by(crisno) %>%
-  summarise(
-    sentence_count=n(),
-    word_count=sum(word_count)
-  )
+#crisis_text_counts <- codings_wide_agreed %>%
+#  #mutate( input_crisis = input_crisis %>% str_replace_all("[^A-Za-z0-9 ]","") ) %>% #Throws a latex error  #inputenc Error: Unicode char \u8: not set up for use with LaTeX
+#  #https://www.google.com/search?q=R+replace+00A0&oq=R+replace+00A0&aqs=chrome..69i57j0i20i263i512j0i512l2j69i65j69i60l3.1744j0j7&sourceid=chrome&ie=UTF-8
+#  dplyr::select(crisno, sentence) %>%
+#  #mutate(input_crisis = input_crisis %>% stringr::str_to_title()) %>%
+#  #mutate(input_crisis = input_crisis %>% stringr::str_replace_all('[0-9]$','')) %>%
+#  mutate(sentence = sentence %>% stringr::str_to_lower()) %>%
+#  distinct() %>%
+#  #filter(!is.na(input_crisis)) %>%
+#  filter(!is.na(sentence)) %>%
+#  mutate(word_count=str_count(sentence, '\\w+')) %>%
+#  group_by(crisno) %>%
+#  summarise(
+#    sentence_count=n(),
+#    word_count=sum(word_count)
+#  )
 
@@
 library(sjmisc)
-event_type_per_sentence <- icb_wide_clean %>%
+event_type_per_sentence <- codings_wide_agreed %>%
   filter(!is.na(sentence_number_int_aligned)) %>%
@@
 
-icb_text <- icb_wide_clean %>% dplyr::select(crisno,sentence_number_int_aligned, sentence) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)
+icb_text <- codings_wide_agreed %>% dplyr::select(crisno,sentence_number_int_aligned, sentence_span_text) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)
 
@@
 
-  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
+  parsed <- spacy_parse(icb_text$sentence_span_text, nounphrase = TRUE)
   parsed_consolidated <- nounphrase_consolidate(parsed)
@@
 ```
-
-<!-- note: please start your introduction without including the word "Introduction" as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.
--->
-
-If we recorded every event between countries in all of diplomacy, military conflict, and international political economy, how much information would this chronicle amount to, and how surprised would we be to see something new?
-In other words, what is the entropy of international relations?
-This record could, in principle, be unbounded, but the central conceit of political science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured, and accordingly massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
-On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations (IR).
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherCrisisEscalationWar2000; @wilkenfeldInterstateCrisesViolence2000; @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019].
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
-As should come as no surprise to anyone who works with event data, we find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
-The underlying fine-grained variation in international affairs that we care about is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper and therefore makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections.
-Section 2 defines the task of event extraction and proposes evaluation criteria for objectively gauging the performance of that task.
-Section 3 is a literature review that synthesizes a reasonable prior belief behind the existence of the unobserved latent concept we intend to measure and highlights existing current approaches for measuring them.
-Section 4 details our proposed method for measuring events, including the ICB Events (ICBe) dataset's ontology, coding procedures, and methodology.
-Section 5 demonstrates the internal validity of our coding exercise, the high agreement between coders and their self-reported confidence in codings, and external validity in the form of high coherence in side-by-side comparisons of source sentences and resulting codings.
-Section 6 evaluates internal validity by showing that like-codings cluster when their source sentences are mapped into semantic space.
-Section 7 offers a comparison against existing systems with case studies at the crisis level where we show both much higher recall of events that occurred and precision in what those events were and how they fit into the overall macro-level event.
-A final section concludes.
-
-Task Definition and Ground Truth {.unnumbered}
-========================================
-
-We consider the task of high-coverage information extraction from a historical episode between two or more states (e.g., the Cuban Missile Crisis).
-A historical episode is demarcated by a period of time $[T_{start}, T_{end}] \in T$ and a set of players $p \in P$.
-We posit that an episode can be divided into unique discrete events, $e \in E$, each consisting of a time period, one or more players, and a single behavior ($b \in B$) so that $e \equiv \{T_e, P_e, B_e\}$.
-The task is to produce sequences of parsimonious events that still reconstruct the important details of the original macro narrative.
-
-We take as ground truth an unusually high-quality corpus of historical narratives from the International Crisis Behavior (ICB) project (SI Appendix, Table \ref{app:crises})[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies or case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
-The corpus is unique in IR because it is designed to be used in downstream quantitative coding projects.
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
-59].
-
-Prior Beliefs and Existing State of the Art {.unnumbered}
-========================================
-
-Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$, and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$.
-We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table 1.
-<!-- {tbl:litreview}  -->The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of international affairs as a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-The resulting codebook for events includes 117 different behaviors and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
-
-The second axis (columns) represents sources of evidence for our concept priors and the existing state of the art.
-The columns compare the ontologies of event-level datasets beginning with our contribution ICBe, then Cameo dictionary lookup based systems (Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018]; Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Absent datasets include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], and SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] Finally, the fourth set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
-
-\clearpage
-\onecolumn
-
-```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#Lit review
-#child=c('ICBEdataset_paper_litreviewtable.Rmd')
-library(flextable)
-library(ftExtra)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
-
-litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 3, part="body")
-
-litreview_ft %>%
-  flextable::set_caption(caption = "Prior Beliefs, State of the Art, and Existing Data") %>%
-  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
-  flextable::flextable_to_rmd()
-
-```
-
-\clearpage
-\twocolumn
-
-ICBe Coding and Aggregation Process {#author-affiliations .unnumbered}
-----------------------------------------
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-S\ref{app:gui}).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other deatils were only collected if appropriate, e.g.
-force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
-an offer for the U.S.S.R.
-to remove missiles from Cuba in exchange for U.S.
-removing missiles from Turkey.
-Through compounding, we can capture what actors were said to have known, learned, or said about specific fully described behaviors.
-
-Each crisis was assigned to at least two expert coders, 3 to 5 undergrad coders, with a third tie-breaking expert coder assigned to sentences with high disagreement.^[Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergrad coders were students who engaged in classroom workshops.
-Coders worked independently with the codebook after a practice coding where an expert answered questions.] The highly expressive ontology created challenges in aggregating and evaluating beliefs across coders.
-Traditional measures
-
-This data-generating process suggests a theoretically motivated algorithm for aggregating over disagreements (SI Appendix, Fig.
-S\ref{app:algo1}).
-We filter tokens to only those with (1) at least one expert coder vote and (2) a majority of expert votes or a majority of undergrad votes.
-If neither majority exists, we accept the one token with the most votes.
-This leaves `r codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()` (`r (codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() / codings_long_agreement %>% filter(value_normalized!='') %>% nrow()) %>% round(2) %>% scales::percent()`) accepted tokens.
-In practice, this screens noisy tags that no expert considered possible but leverages undergrad knowledge to tie-break between equally plausible tags chosen by experts.
-A final step handles possible disagreement over the number of events or participants in the events.
-An event is emitted for each unique set of actors along with their surviving tags.
-
-```{r include=FALSE}
-
-n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
-n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
-n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
-n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
-n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()
-
-avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_coders_per_sentence <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)
-```
-
-```{r, eval=T}
-
-means1 <- codings_long_agreement %>%
-  filter(value_normalized!='') %>%
-  filter(total_coders>1) %>% #about 9k only had one coder
-  #filter(selected_by_experts>=1) %>%
-  dplyr::select(All=selected_by_any_perc,Experts=selected_by_experts_perc,Undergraduates=selected_by_undergrads_perc) %>% summarise_all(mean, na.rm=T)
-means1_keep <- codings_long_agreement %>%
-  filter(value_normalized!='') %>%
-  filter(total_coders>1) %>% #about 9k only had one coder
-  #filter(selected_by_experts>=1) %>%
-  filter(keep==1) %>% dplyr::select(Accepted=selected_by_any_perc) %>% summarise_all(mean, na.rm=T)
-meansall <- bind_rows(means1,means1_keep) %>% mutate(x=1) %>% pivot_longer(cols=c(-x)) %>% na.omit()
-
-```
-
-One form of internal validity for these codings is high agreement between coders when applying the ontology.
-We employ three ways to evaluate and maximize agreement: (1) multiple expert and undergrad coders per sentence (often including a tie-breaking expert coder where there were disagreements), (2) a theoretically motivated scheme for aggregating across disagreements, and (3) survey questions on self-reported confidence and reasons for low confidence.
-The unit of analysis for these comparisons is the individually applied tag; every answer to every question in the ontology is a separate tag applied to that sentence (e.g., an actor, a behavior, a date, etc.).
-There were 113 coders (including 5 expert coders) who recorded `r icb_long_clean %>% nrow() %>% scales::comma()` coder-tags across the entire corpus.
-Of those, there were `r codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma()` unique sentence-tags applied by at least one coder.
-We ask how much support those possible tags received across coders, and how we should adjudicate disagreements when a tag was not chosen by every coder.
-
-We evaluate agreement as the percentage of coders who voted for a tag proposed by any coder (SI Appendix, Fig.
-S\ref{app:intercoderagreement}).
-The average agreement across all coders is `r means1$All %>% round(2) %>% scales::percent()` (`r means1$Experts %>% round(2) %>% scales::percent()` across experts and `r means1$Undergraduates %>% round(2) %>% scales::percent()` across undergraduates).
-A post-aggregation algorithm described below raises mean agreement considerably to `r means1_keep$Accepted %>% round(2) %>% scales::percent()`.
-Further, there is expected heterogeneity in agreement with higher agreement for coarse, high-level decisions near the root of the ontology than for fine-grained, high-dimensional concepts further down the tree.
-
-To understand when and why coders disagree, we required self-reported confidence scores and reasons for low confidence.
-Overall, expert coders self-reported a high level of confidence in their own codings, reporting low confidence only about 20% of the time.
-When coders reported low confidence, they cited a mismatch between the ontology and the text about half of the time ("survey doesn't fit event" 45%) and noted a lack of information or confused writing in the source text the other half ("more knowledge needed" 40%, "confusing sentence" 6%).
-In addition, we observed that individual coders exhibit nontrivial coding styles.
-Some coders are more expressive and apply multiple tags per concept, while others focus on only the single best match and differ in how many events to code.
-We also observed unintended synonymity (e.g., the same information can be framed as a threat to do something or a promise not to do something if a condition is met).
-
-Sentence Level Intrinsic Evaluation {#format .unnumbered}
-----------------------------------------
-
-Next, we ask whether codings agree with the raw source material at the sentence level.
-There are `r icb_long_clean %>% dplyr::select(sentence) %>% distinct() %>% nrow()  %>% scales::comma()` distinct sentences in the corpus.
-We start with a high-level view, taking the sentence texts and embedding them into a latent semantic space with a large language model specializing in sentence similarity, Sentence-BERT [@reimersSentenceBERTSentenceEmbeddings2019].^[We preprocess sentences to replace named entities with a generic Entity token.] Sentence embeddings are shown in Figure \ref{fig:semantic_embeddings}, disaggregated by four high-level ontology questions and each possible tag.
-Superficially, user applied tags tend to separate and cluster across semantic space in ways that suggests they are cueing on information actually provided by the text of the source sentence.
-
-```{r, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-# MOVED TO figures/ICBEdataset_paper_figure_prep.Rmd
-
-# #child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
-# p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/paper/figures/p_semantic_embeddings.Rds'))
-# ggsave(file=paste0(here::here(), '//paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
-```
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from the Sentence-BERT large language model\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=15cm]{../figures/p_semantic_embeddings.png}}
-\textit{Notes:}
-\end{figure}
-\clearpage
-\twocolumn
-
-Going further, we examine accepted tokens side-by-side with the original source material.
-We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tab:fifteensamplesentences}, 50 more in the Appendix \ref{app:50samplesentences}, and the full set online.
-To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined).
-At the sentence level, we find codings accurately reflect the key events of the text.
-Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.
-
-\clearpage
-\onecolumn
-```{r fifteensamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}
-
-codings_wide_agreed_embeded_stratified_sample_ft_smaller <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds')) %>%
-  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15)") 
-codings_wide_agreed_embeded_stratified_sample_ft_smaller
-
-```
-\clearpage
-\twocolumn
-
-Episode Level Intrinsic Evaluation and Comparison to State of the Art {#format .unnumbered}
-----------------------------------------
-
-To demonstrate validity at the level of entire episodes, we conduct two qualitative case studies.
-We choose cases where Phoenix had substantially more relevant events (included crisis actors in crisis time span) then ICBe, likely exacerbating the well-known poor coherence of automated codings but increasing the likelihood of capturing key events.
-The two cases also differ in useful ways; the Cuban Missile Crisis is high stakes and widely recognized and the DRC Civil War for being particularly complicated, lengthy, and modern.
-
-For each case we first establish necessary and secondary details of each crisis from secondary historical sources independent of the ICB corpus.
-We then evaluate the precision and overall coherence of ICBe codings using a type of timeline visualization we call a 'crisis map'.^[The project website has such visualizations for every crisis.] Finally we compare the recall of key events by ICBe and the existing state-of-the-art datasets.
-For an event dataset to have good performance, it must both have high recall of salient facts, catching the key details and not just the trivia, and good precision, recording only events that actually occurred without distracting duplicates, miscodings, or other apparent examples of measurement error.
-
-Case Study: Cuban Missiles Crisis (1962) {#format .unnumbered}
-----------------------------------------
-
-The Cuban Missile Crisis occurred between the United States, the Soviet Union, and Cuba from October 16, 1962, to November 20, 1962.
-There are two critical points of context.
-First, the United States and Soviet Union enjoyed only a partial mutually assured destruction nuclear posture; the United States had accurate short-range ballistic missiles (SRBMs) in Europe and ICBMs, and the Soviet Union only had long-range, slow to arm, and relatively inaccurate ICBMs.
-Second, the United States launched the unsuccessful Bay of Pigs invasion of Cuba in April 1961.
-
-The Soviet Union and Cuba reached an agreement to stage Soviet troops, tactical nuclear weapons, and medium-range ballistic missiles (MRBMs) in Cuba in May 1962.
-U.S.
-intelligence suspected these plans in August, and their presence was later confirmed by reconnaissance flights (October 14), ultimately triggering the main arc of the crisis.
-
-The two great powers responded with both escalation and de-escalation.
-As escalations, the United States prepared a complete invasion of Cuba (October 17) and raised the nuclear alert status to DEFCON 3 (October 22) then partially to DEFCON 2 (October 24) [@brugioniEyeballEyeballStory1991].
-Likewise, the Soviet Union mobilized (October 11) and went on alert (October 22).
-As de-escalations, the United States sought a diplomatic solution and imposed a naval blockade as a non-violent military measure to buy time while preventing further Soviet reinforcements from reaching Cuba.
-The main arc concludes with an agreement by the Soviet Union to withdraw entirely from Cuba, the U.S.
-agreeing never to invade Cuba, and a clandestine agreement by the U.S.
-to retire MRBMs based in Turkey.
-
-A secondary crisis arc included several dangerous steps.
-Cuba mobilized all of its forces in preparation for an invasion (October 22).
-The United States continued aggressive violations of Cuban airspace by reconnaissance flights leading to the shooting down of a U.S.
-U-2 (October 27).
-Both sides went ahead with previously scheduled nuclear weapons tests (October 27-28).
-Finally, Cuba extended the crisis after the United States and Soviet Union reached their agreement, attempting and failing to retain Soviet bombers.
-
-The precision and overall coherence of ICBe codings are shown in a side-by-side comparison of the source narrative and codings in Appendix \ref{app:ft_sentence_table_196} and via the crisis map in Figure \ref{fig:196metromap} below.
-The entire back-and-forth of the conflict can be directly read from the timeline.
-The deployment of the missiles is recorded as the cause of the crisis for the United States.
-The United States is recorded as demanding specifically that they be removed.
-After the agreement is reached, the fulfillment of that obligation is recorded with the withdrawal of the missiles specifically and the end of the blockade.
-There are some details lost in the translation.
-The tit-for-tat details of the agreement, particularly the exchange of missiles in Turkey, are lost.
-The detail of the missiles deployed to Cuba being nuclear is not recorded at first because the narrative only refers to them as missiles initially, but is later recorded correctly when the narrative becomes explicit.
-The brief Cuban gambit to keep some weapons is present in the ICB narrative but mostly ignored by the coders as of low importance.
-In sum, the ICBe codings correctly record the cause, response, and resolution of the crisis, the correct order of moves, and the size of the stakes at play.
-In comparison crisis maps of Cameo (Phoenix) (Figure \ref{fig:196metromap_phoenix}), ICB Dyadic Codings (Figure \ref{fig:196metromap_icb}), and MIDs (Figure \ref{fig:196metromap_mids}) in Appendix \ref{app:ft_sentence_table_196} do not reflect the overlying macro story nor the specific details of interest.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Cuban Missile Crisis according to ICBe (us) \label{fig:196metromap}}
-\centering{\includegraphics[width=19cm]{../figures/p_metro_map_196.png}}
-\end{figure}
-\clearpage
-\twocolumn
-
-Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tab:casestudy196}.
-ICBe records 8 of 10 critical events identified by the case history.
-It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors.
-It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.
-
-Only three other datasets have temporal coverage of this case.
-The Cline Historical Phoenix event dataset, which is based on Cameo dictionary codings of the New York Times and Wall Street Journal articles, only includes events that could be loosely mapped to one key turning point, the withdraw of missiles and peaceful resolution of the crisis.
-Two episode-level datasets contain temporal information on this crisis.
-A dyadic version of the original ICB dataset [@hewittDyadicProcessesInternational2003] contains information on 6 of the critical events, but describes them in terms that are too vague to reconstruct the episode.
-For example, the deployment of nuclear weapons is described only as an "external change," and the response of mobilizations for war and the blockade are a "non-violent military act." The Dyadic Militarized Interstate Disputes (MIDs) dataset [@maozDyadicMilitarizedInterstate2019] includes only two possible mappings, a 'show of troops' near the start of the crisis, and a 'yield to' near the end.
-
-\clearpage
-\onecolumn
-```{r casestudy196, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
-CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
-CaseStudy196_ft %>%
-  flextable::set_caption("Cuban Missile Crisis ground truth and event data") %>%
-    flextable::width( j = 1, width=0.5)  %>%
-    flextable::width( j = 2, width=1.25)  %>%
-    flextable::width( j = 3, width=0.5) %>%
-    flextable::width( j = 4, width=1.1) %>%
-    flextable::width( j = 5, width=1) %>%
-    flextable::width( j = 6, width=0.75) %>%
-    flextable::width( j = 7, width=0.65)
-
-```
-\clearpage
-\twocolumn
-
-Conclusion {#format .unnumbered}
-----------------------------------------
-
-We investigated event extraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal validity (e.g.
-intercoder agreement) and external validity (i.e.
-matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes).
-Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
-
-<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
-\showmatmethods
-\showacknow
-\pnasbreak

### 2022-07-17 replication_paper/rmd/old/cuban_missile_crisis_case_study_table.Rmd
v1.1

--- 2022-03-23 replication_paper/rmd/04_ICBEdataset_paper_litreviewtable.Rmd
@@
 ---
-title: 'LitReviewTable.Rmd'
-site: bookdown::bookdown_site
-bibliography: ../ICBintro.bib
-output: 
-  rticles::arxiv_article:
-    keep_tex: true
-header-includes:
-  - \usepackage[utf8]{inputenc}
-  - \usepackage{pifont}
-  - \usepackage{newunicodechar}
-  - \newunicodechar{✓}{\ding{51}}
-  - \newunicodechar{✗}{\ding{55}}
-  - \usepackage{array}
-  - \usepackage{ctable} # added for demo
-  - \usepackage{natbib} #added for latex citation within huxtable
-  - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage{wrapfig}
-  - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{titlesec}
-  - \usepackage[parfill]{parskip}
-  - \usepackage{makecell}
-  - \usepackage{graphicx}
-  - \usepackage{caption}
-  - \usepackage[capposition=top]{floatrow}
-  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
-  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
-  - \DeclareUnicodeCharacter{00A0}{ }
-  - \usepackage{setspace}
-  - \usepackage{cellspace}
-  - \setlength\cellspacetoplimit{0.8ex}
-  - \renewcommand{\arraystretch}{0.8}
-  - \AtBeginEnvironment{tabular}{\singlespacing}
-  - \AtBeginEnvironment{lltable}{\singlespacing}
+title: "Case Study:Cuban Missile"
+output: html_document
+date: '2022-05-13'
 ---
 
-```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
-library(pacman)
+```{r, eval=T, echo=F, cache=F, results='hide', message=F}
 
-p_load(flextable)
-p_load(ftExtra)
+knitr::opts_chunk$set(echo = TRUE)
+
+#library(pacman)
+library(googlesheets4)
+library(tidyverse)
+library(janitor)
+library(flextable)
+set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`.
+You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
+library(ftExtra)
+options(tidyverse.quiet = TRUE)
+options(gargle_oauth_email = TRUE)
+
+#install.packages('stargazer')
+#install.packages('kableExtra')
+#! sh: 1: pdflatex: not found
+#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended
+
+#! LaTeX Error: File `letltxmacro.sty' not found.
+#sudo apt-get install texlive-latex-extra
 
@@
 
-```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
-
-target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
-lit_review_pull    <- readxl::read_excel(target_file, sheet="DatasetsComparisonLitReview")
-
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
 
-```{r, echo=FALSE, results='asis', include=T, cache=F, ft.arraystretch=0.75}
+```{r pressure, echo=FALSE}
+library(googlesheets4) #Do this high up so you get the prompt early
+library(lubridate, warn.conflicts = FALSE)
+case_study_cuban <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
+                                sheet="Final") %>% janitor::clean_names() 
+dim(case_study_cuban)
+case_study_cuban$date <- case_study_cuban$date %>% lapply(FUN=function(x) { ifelse(is.null(x), "", x[[1]] %>% as.character() )   }   ) %>% unlist() %>% as.Date()
+
+case_study_cuban_clean <- case_study_cuban %>% 
+                          filter(!is.na(date))
 
@@
 set_flextable_defaults(fonts_ignore=TRUE)
+ft <- case_study_cuban_clean %>% flextable::as_flextable() %>% 
+  flextable::width( j = 2, width=2)  %>% 
+  flextable::width( j = 3, width=5) 
+ft
 
-lit_review_alt <- lit_review_pull %>%
-                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`) #%>% 
+ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/cuban_case_study_ft_pnas.Rds'))
+```
+
+```{r, eval=F}
+
+lit_review_alt <- case_study_cuban %>% 
+                  mutate(Literature = paste0("[",Literature,"]")) %>%
+                  mutate(Concept= Concept %>% paste0(Literature)) %>%
+                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
                   #dplyr::filter(is.na(group))
@@
 
-litreview_ft <- ft %>% 
-  flextable::width( j = 3, width=2) %>% 
-  flextable::width( j = 4, width=1.5) %>% 
-  flextable::width( j = (3+2):ncol(lit_review_alt), width=0.33) %>%
+litreview_ft_pnas <- ft %>% 
+  flextable::width( j = 3, width=4) %>% 
+  flextable::width( j = (4):ncol(lit_review_alt), width=0.25) %>%
   flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
@@
   flextable::width( j = 1:2, width=0.1)  %>%
-  flextable::width( j = 3, width=2.5)  %>%
-  flextable::width( j = 4, width=1.5)  %>%
-  flextable::width( j = 5:12, width=0.25)  %>%
-  ftExtra::colformat_md(j = 4, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
+  ftExtra::colformat_md(j = 3, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
 
-litreview_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))
+litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
 
-litreview_ft
+litreview_ft_pnas
 
 ```
-
-```{r}
-
-n=nrow(lit_review_alt)
-ft <- NULL
-temp <- lit_review_alt[,-c(4,5)]
-ft <- temp %>% 
-      flextable::as_flextable() %>%
-
-      bg( i = which( 1:nrow(temp) %% 2 == 1)  , j=3:ncol(temp), part = "body", bg = "#EFEFEF") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      flextable::align(align = "center", part = "body") %>%
-      flextable::align(align = "center", part = "header")   %>%
-
-      flextable::colformat_char(
-          j = 1:ncol(temp),
-          na_str = "",
-          prefix = "",
-          suffix = ""
-      ) %>%
-        set_header_labels(
-        values = list("...1" = "" , "...2" = "" ) 
-        ) %>%
-      merge_h(part = "header") %>%
-
-      hline(i=c(1), j=3:ncol(temp),  border = NULL, part = "header") %>%
-      hline(i=c(2,3,7,10,15, 19, 27), border = NULL, part = "body") %>% 
-      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
-      vline( i = 1:(n), j = c(0,4)+3, border = NULL, part = "body") %>%
-      flextable::width( j = 3, width=3) %>%
-      flextable::line_spacing( space = 0.75, part = "body") %>% 
-      flextable::padding(padding = 0, part = "body") %>%
-
-      merge_at(i = 4:7, j = 1:2, part = "body") %>%
-      merge_at(i = 8:10, j = 1:2, part = "body") %>%
-      merge_at(i = 11:15, j = 1:2, part = "body") %>%
-      merge_at(i = 16:19, j = 1:2, part = "body") %>%
-
-      merge_at(i = 20:n, j = 1, part = "body") %>%
-      merge_at(i = 20:28, j = 2, part = "body") %>%
-      merge_at(i = 29:n, j = 2, part = "body") %>%
-      flextable::rotate(j=1, rotation="tbrl",part="all") %>%
-      flextable::rotate(j=2, rotation="tbrl",part="all") %>%
-      flextable::width( j = 1:2, width=0.1)  %>%
-      flextable::width( j = 3, width=4)  %>%
-      flextable::width( j = 4:ncol(temp), width=0.25)
-
-```

### 2022-07-18 replication_data/rmd/01_compile_saves_and_align.Rmd
v1.1 first self contained hopefully

@@
 #Only a project lead can run this code. Copy (NEVER MOVE) the original save files to the data_temp folder. And then verify that that data_temp is on the gitignore list so it never gets committed.
-path <- paste0(here::here(), "/replication_data/ignore/icb_worker_saves") #this folder is copied over from the dropbox folder and never committed to github
+path <- paste0(here::here(), "/git_ignore_folder/icb_worker_saves") #this folder is copied over from the dropbox folder and never committed to github
 files_worker_saves <- list.files(path = path, pattern = ".Rdata", all.files = FALSE, full.names = T, recursive = T, ignore.case = FALSE, include.dirs = FALSE)

### 2022-07-18 replication_data/rmd/03_aggregation.Rmd
v1.1 first self contained hopefully

@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds")) %>%
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds")) %>%
                   filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
@@
 saveRDS(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds")) 
-readr::write_tsv(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.tsv"))
+#readr::write_tsv(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.tsv"))
 
 saveRDS(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.Rds")) 
-readr::write_tsv(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.tsv"))
+#readr::write_tsv(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.tsv"))
 
 saveRDS(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
-readr::write_tsv(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.tsv"))
+#readr::write_tsv(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.tsv"))
 
 saveRDS(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
-readr::write_tsv(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.tsv"))
+#readr::write_tsv(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.tsv"))
 

### 2022-07-18 replication_data/rmd/04_validation.Rmd
v1.1 first self contained hopefully

@@
 saveRDS(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
-readr::write_tsv(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.tsv"))
+#readr::write_tsv(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.tsv"))
 
 saveRDS(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds")) 
-readr::write_tsv(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.tsv"))
+#readr::write_tsv(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.tsv"))
 

### 2022-07-18 replication_paper/pnas_draft/appendix.Rmd
v1.1 first self contained hopefully

@@
 
+library(reticulate)
+reticulate::py_discover_config()
+#use_python("/home/skynet3/anaconda3/bin/python/")
+#use_python("/home/tlscherer/anaconda3/bin/python3")
+
 flag_folder_small="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"
@@
 
+#pip install -U pip setuptools wheel
+#pip install -U spacy
+#python -m spacy download en_core_web_sm
+library(rvest)
+
 ```
@@
 
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
+icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds"))
 codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png", zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png", zoom=1)
+  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png", zoom=1)
 
@@
 \caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png"}}
+\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png"}}
 \end{figure}
@@
 
-```{r python load, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-library(reticulate)
-reticulate::py_discover_config()
-
-#use_python("/home/skynet3/anaconda3/bin/python/")
-#use_python("/home/tlscherer/anaconda3/bin/python3")
-
-```
-
 ```{python embed glosses, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
@@
 #pip install -U sentence-transformers
+
+import torch
+use_cuda = torch.cuda.is_available()
+if use_cuda:
+    print('__CUDNN VERSION:', torch.backends.cudnn.version())
+    print('__Number CUDA Devices:', torch.cuda.device_count())
+    print('__CUDA Device Name:',torch.cuda.get_device_name(0))
+    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
+    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
+    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)
+
+import random
+import os
+from tqdm.auto import tqdm
+import pandas as pd
+from transformers import pipeline
+from transformers.pipelines.pt_utils import KeyDataset
 
@@
 ```{python embed sentences for wordnet , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
+
+#Make sure you have a gpu if you want to run thi
 
@@
   sentences_embeddings.shape #(12103, 768)
-
 else:
@@
 
-ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_cuba_recall.png}}
+\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png}}
 \end{figure}
@@
 
-ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_crimea_recall.png}}
+\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png}}
 \end{figure}
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part1.png}}
+\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_precision_part2.png}}
+\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png}}
 \end{figure}
@@
 
+```{r Stratified Sentence Examples, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
+
+temp <- ICBe_events_agreed_markdown %>% dplyr::select(
+  crisno, sentence_span_text,value_markdown,
+  act_cooperative , act_deescalate, act_escalate,act_uncooperative,
+  interact_decreasecoop,interact_deescalate,
+  interact_escalate, interact_increasecoop,
+  thinkkind,sayintkind
+) %>% pivot_longer(cols=-c(crisno, sentence_span_text,value_markdown)) %>% na.omit() %>% filter(value!='') %>% 
+    mutate(value = strsplit(as.character(value), ";")) %>% 
+    unnest(value)
+
+temp_sample <- temp %>% mutate(rand=runif(n())) %>% group_by(value)  %>% filter(rand==max(rand)) %>% ungroup() %>% arrange(name, value)
+
+ft_sample_precision_precision1 <- temp_sample %>% 
+                                  filter(row_number()<=56) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=8.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((1:56) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png", zoom=1) #
+
+ft_sample_precision_precision2 <- temp_sample %>% 
+                                  filter(row_number()>=57) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=8.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((1:59) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png", zoom=1) #
+
+```
+
 \hphantom{em}
 \begin{figure}[H]
-\caption{ Stratified Sentence Examples  \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/ft_sample_precision_precision.png"}}
+\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
+\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png"}}
+\end{figure}
+\clearpage
+
+\hphantom{em}
+\begin{figure}[H]
+\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png"}}
 \end{figure}
@@
     print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icb_metro_plot_",thiscrisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/figures/p_icb_metro_plot_",thiscrisis,".Rds")
 
@@
 
-c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x))
+c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x)) #This just runs every time no from scratch because the files are small
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_mids_metro_plot_",thiscrisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/figures/p_mids_metro_plot_",thiscrisis,".Rds")
 
@@
   convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
-  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-
-  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid()
-  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
-  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
-  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
-  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/temp/DOI-10-13012-b2idb-0647142_v3 (1)/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
+  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+
+  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid()
+  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
+  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
+  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
+  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
 
@@
   dim(phoenix_clean) #8,495,402 #3,721,110 #2,813,748 #2912035 #3,508,495 #4,854,787
-  phoenix_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") )
+  phoenix_clean %>% arrow::write_parquet(here::here("git_ignore_folder",  "phoenix_clean.parquet") )
 
@@
 
-  phoenix_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471.tsv")
+  #phoenix_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471.tsv")
   dim(phoenix_clean_471)
 
-  phoenix_clean_471 %>%
-    unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
-    unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
-    dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
-    write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471_small.tsv")
+  #phoenix_clean_471 %>%
+  #  unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
+  #  unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
+  #  dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
+  #  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471_small.tsv")
 
@@
 
-  phoenix_clean_196 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196.tsv")
-  dim(phoenix_clean_196)
-
-  phoenix_clean_196 %>%
-    unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
-    unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
-    dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
-    write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196_small.tsv")
+  #phoenix_clean_196 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196.tsv")
+  #dim(phoenix_clean_196)
+
+  #phoenix_clean_196 %>%
+  #  unite('actors_left' , source_label, source_root_label , source_agent_label, source_others1_label,source_others2_label,source_others3_label, sep=" ", , na.rm =T, remove=F) %>%
+  #  unite('actors_right', target_label, target_root_label , target_agent_label, target_others1_label,target_others2_label,target_others3_label, sep=" ", , na.rm =T, remove=F) %>%
+  #  dplyr::select(eid, year, month, day, actors_left, actors_right,cameo_event_label, text , title, primary_source, original_source) %>% 
+  #  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196_small.tsv")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_lv0_",thiscrisis,".Rds")
 
@@
 if(fromscratch){
-  phoenix_clean <- arrow::read_parquet(here::here("replication_paper", "data", "ignore", "phoenix_clean.parquet") ) 
+  phoenix_clean <- arrow::read_parquet(here::here("git_ignore_folder", "phoenix_clean.parquet") ) 
   c(196, 471) %>% sapply(FUN=function(x) phoenix_barmaps(x))
@@
 
-if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
-  stop("Missing Terrier event data. See README.")
-}
-
 #if(file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
@@
 if(terrier_fromscratch){
-    files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
+    files <- list.files(path = paste0(here::here(), "/git_ignore_folder/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
     terrier <- rbindlist(lapply(files, FUN=function(x) fread(x,header=F, colClasses=paste0(rep('character',50), collapse='')  )  ) ) #%>% janitor::clean_names()
@@
     terrier_clean_temp  %>%
-      arrow::write_parquet(here::here("replication_paper", "data", "ignore", "terrier_clean.parquet") )
+      arrow::write_parquet(here::here("git_ignore_folder", "terrier_clean.parquet") )
 }
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_terrier_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_terrier_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_terrier_plot_lv0_",thiscrisis,".Rds")
 
@@
   #install.packages("arrow")
-  terrier_clean <-  arrow::read_parquet( here::here("replication_paper", "data", "ignore", "terrier_clean.parquet")) #203mb
+  terrier_clean <-  arrow::read_parquet( here::here("git_ignore_folder", "terrier_clean.parquet")) #203mb
   dim(terrier_clean) #28,438,029 #39,322,909 #7,847,463
@@
   #accidentally loaded the pdfs
-  files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T, pattern = ".tab$|.tsv$")
+  files <- list.files(path = paste0(here::here(), "/git_ignore_folder/dataverse_files/"), full.names = T, pattern = ".tab$|.tsv$") #there's both tab and tsv for some reason
   icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x, show_col_types = FALSE) )  ) %>% janitor::clean_names() %>% distinct()
@@
 
-    icews_clean %>% arrow::write_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )
+    icews_clean %>% arrow::write_parquet(here::here("git_ignore_folder", "icews_clean.parquet") )
 
@@
 
-    icews_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")
-
-    icews_clean_471 %>%
-      unite('actors_left' , source_country, source_label, source_name, source_sectors,  sep=" ", , na.rm =T, remove=F) %>%
-      unite('actors_right', target_country, target_label, target_name, target_sectors, sep=" ", , na.rm =T, remove=F) %>%
-      dplyr::select(event_id, year, month, day, actors_left, actors_right,cameo_event_label=cameo_label, text ) %>% 
-      write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")
+    #icews_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")
+
+    #icews_clean_471 %>%
+    #  unite('actors_left' , source_country, source_label, source_name, source_sectors,  sep=" ", , na.rm =T, remove=F) %>%
+    #  unite('actors_right', target_country, target_label, target_name, target_sectors, sep=" ", , na.rm =T, remove=F) %>%
+    #  dplyr::select(event_id, year, month, day, actors_left, actors_right,cameo_event_label=cameo_label, text ) %>% 
+    #  write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/crisismaps/p_icews_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_icews_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_icews_plot_lv0_",thiscrisis,".Rds")
 
@@
   #install.packages("arrow")
-  icews_clean <-  arrow::read_parquet(here::here("replication_paper", "data", "ignore", "icews_clean.parquet") )
+  icews_clean <-  arrow::read_parquet(here::here("git_ignore_folder", "icews_clean.parquet") )
 
@@
 ## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_mids_metro_plot_196.Rds') 
+save_file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_phoenix_plot_penta_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_penta_196.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_196.Rds")
+  p_phoenix_plot_lv0_196 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_phoenix_plot_lv0_196.Rds")
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_mids_metro_plot_471.Rds') 
+save_file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_471.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_phoenix_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_penta_471.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_terrier_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_penta_471.Rds')
 subtitle="Terrier Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_icews_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_penta_471.Rds')
 p_471_icews <- readRDS(save_file)
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_phoenix_plot_lv0_471.Rds")
+  p_phoenix_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_phoenix_plot_lv0_471.Rds")
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_terrier_plot_lv0_471.Rds")
+  p_terrier_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_terrier_plot_lv0_471.Rds")
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisismaps/p_icews_plot_lv0_471.Rds")
+  p_icews_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_icews_plot_lv0_471.Rds")
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),

### 2022-07-18 replication_paper/pnas_draft/paper.Rmd
v1.1 first self contained hopefully

@@
 
-icews_clean_471 <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471.tsv")
-dim(icews_clean_471) #270,642
-icews_clean_471_small <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_small.tsv")
-
 icews_clean_subset_top10_day <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")
@@
 \begin{figure}[H]
-\caption{ ICEWs Counts of Events per Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
+\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
 \centering{\includegraphics[width=17cm]{../figures/p_precision_icews.png}}
@@
 Red text shows events from the synthetic narrative relative to that event category.
-Event types are grouped by hand along similar themes.
 Blue bars indicate an event recorded by ICEWs for that dyad on that day.

### 2022-07-18 replication_paper/pnas_draft/paper.tex
v1.1 first self contained hopefully

@@
 Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.\footnote{Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.} For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=971,547), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
+Undergraduate coders were students who engaged in classroom workshops.} For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=972,545), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
 We then aggregate those tags into final events (n=18,309), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
@@
 B3).
-Across all concepts, the Top 1 Tag Agreement was low among novices (34\%), moderate for experts (65\%), and high (87\%) following the consensus screening procedure.
+Across all concepts, the Top 1 Tag Agreement was low among novices (31\%), moderate for experts (65\%), and high (74\%) following the consensus screening procedure.
 
@@
 You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph interesected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
+We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
 D3 and D4) and all crises on the companion website.
@@
 We choose four event types around key moments in the crisis.
-The start of the crisis revolves around the Ukraine backing out of trade deal with the EU in favor of Russia, but the ``sign formal agreement'' acts more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
+The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but ``sign formal agreement'' events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
 The switch is caught by the ``reject plan, agreement to settle dispute'', but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
 Events for ``use conventional military force'' capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, ``impose embargo, boycott, or sanctions'' captures the start of waves of sanctions and from who but are effectively costantly as the news coverage does not distinguish between subtle changes or additions.
+Likewise, ``impose embargo, boycott, or sanctions'' captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
 In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.

### 2022-07-18 replication_paper/rmd/old/06_ICBEdataset_figure_metro_maps.Rmd
v1.1 first self contained hopefully

--- 2022-03-22 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
@@
 
+if(file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
+  terrier_fromscratch<-readline(prompt="Load original Terrier data? (T/F)")
+}
+
+if(terrier_fromscratch){
+
 files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
@@
 
+}
 ```
@@
 ```{r}
+
+if(terrier_fromscratch){
 #Maybe it's just ISO3 country codes?
@@
     distinct() 
-
+}
 #done
@@
 ```{r}
+if(terrier_fromscratch){
 terrier_clean_temp <- terrier_clean_temp %>%
@@
    left_join(df %>% dplyr::select(target_other_agent=agent, target_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) 
+}
 
@@
 ```{r}
+if(terrier_fromscratch){
 terrier_clean <- terrier_clean_temp %>%
@@
 
+saveRDS(terrier_clean, here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
+}
+
 #For now
-#IGO 223751 for now we're going to exclue just generic Intergovernmental organization and multiinational corps
+#IGO 223751 for now we're going to exclude just generic Intergovernmental organization and multinational corps
 #MNC 62721
@@
 
+if(!terrier_fromscratch){
+  terrier_clean <- readRDS(here::here("replication_paper", "data", "in", "terrier_clean.Rds"))
+}
+
 ```
@@
 
-terrier_metro_plots <- function(crisis=196, topactor=F){
+terrier_metro_plots <- function(crisis=426, topactor=F){
 
@@
   date_start <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrtrig , "-", icb_crises[icb_crises$crisno==crisis,]$motrig, "-01"))
-  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm, "-31"))
+  date_end <- lubridate::as_date(paste0(icb_crises[icb_crises$crisno==crisis,]$yrterm , "-", icb_crises[icb_crises$crisno==crisis,]$moterm+1, "-01"))
 
@@
 
-                           filter(
+                           dplyr::filter(
                                   source_root_target %in% diads_qcodes$source_root_target & 

### 2022-07-22 replication_data/rmd/01_compile_saves_and_align.Rmd
01-04 reproduce

@@
     if(fromscratch){
-      icb_crisis_summaries <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_corpus_V1.0_May_16_2022.Rds")
+      icb_crisis_summaries <- readRDS(here::here("replication_corpus", "data", "out", "icb_corpus_V1.0_May_16_2022.Rds"))
+
       #Do a round first based on the file name
@@
       toc() #878.328 sec elapsed
-    icb_long_crisis_sentence_unique %>% saveRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_long_crisis_sentence_unique.Rds")
+    icb_long_crisis_sentence_unique %>% saveRDS(here::here("replication_corpus", "data", "out", "icb_long_crisis_sentence_unique.Rds"))
     }
-    icb_long_crisis_sentence_unique <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_long_crisis_sentence_unique.Rds")
+    icb_long_crisis_sentence_unique <- readRDS(here::here("replication_corpus", "data", "out", "icb_long_crisis_sentence_unique.Rds"))
 

### 2022-07-22 replication_data/rmd/04_validation.Rmd
01-04 reproduce

@@
 
-country_flags <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/countries.csv" %>% read_csv(col_names=F)
+country_flags <- here::here("replication_data", "in", "countries.csv") %>% read_csv(col_names=F)
+
 library(WikidataR)# install.packages("WikidataR","WikidataQueryServiceR")
@@
   if(is.na(flag_codes1$wikidata_flag_url[i])){ next }
-  destfile_svg <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/{flag_codes1$value_qcode[i]}.svg")
-  destfile_png <- glue::glue("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/{flag_codes1$value_qcode[i]}.png")
+
+  destfile_svg <- glue::glue(here::here("replication_data", "in", "flags", "{flag_codes1$value_qcode[i]}.svg"))
+  destfile_png <- glue::glue(here::here("replication_data", "in", "flags", "{flag_codes1$value_qcode[i]}.png"))
 
@@
 
-flag_folder <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/"
+flag_folder <- here::here("replication_data", "in", "flags/")
 flag_files <- list.files(path = flag_folder, pattern = NULL, all.files = FALSE, full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
@@
 library(imager); #install.packages("imager")
-flag_folder <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags/"
-flag_folder_small <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"
+
+flag_folder <- here::here("replication_data", "in", "flags/")
+flag_folder_small <- here::here("replication_data", "in", "flags_small/")
 #20x16 pixels
@@
 
-#![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/cub.png)
+#![](here::here("replication_data", "pnas_draft", "cub.png"))
 

### 2022-07-22 replication_paper/pnas_draft/appendix.Rmd
01-04 reproduce

@@
 #use_python("/home/skynet3/anaconda3/bin/python/")
-#use_python("/home/tlscherer/anaconda3/bin/python3")
-
-flag_folder_small="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"
+#reticulate::use_python("/home/tlscherer/anaconda3/bin/python")
+
+flag_folder_small = here::here("replication_data", "in", "flags_small/")
 
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft1.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft2.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft3.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft4.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft5.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft6.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft7.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png", zoom=1)
+  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft8.png"), zoom=1)
 
@@
 \caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft1.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft1.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft2.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft2.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft3.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft3.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft4.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft4.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft5.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft5.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft6.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft6.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft7.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft7.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/crisis_text_counts_ft8.png"}}
+\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft8.png"}}
 \end{figure}
@@
 replace_emoticons_cuba <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
+  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
         #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
+        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
         #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
+        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
         #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
+        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
         #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
+        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
 }
@@
 
-ft_cuba_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png", zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_cuba_recall.png}}
+\centering{\includegraphics[height=21cm]{../figures/ft_cuba_recall.png}}
 \end{figure}
@@
             #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
+            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
             #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
+            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
             #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
+            str_replace_all('\U0001f1fA\U0001f1e6', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
             #Crimea
-            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ") %>%
+            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>%
             #EU
-            str_replace_all('\U0001f1EA\U0001f1FA',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q458.png) ")
+            str_replace_all('\U0001f1EA\U0001f1FA', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
 }
@@
 
-ft_crimea_recall %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png", zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_crimea_recall.png}}
+\centering{\includegraphics[height=21cm]{../figures/ft_crimea_recall.png}}
 \end{figure}
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png", zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png", zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part1.png}}
+\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part1.png}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/case_study_crimea_precision_part2.png}}
+\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part2.png}}
 \end{figure}
@@
 
-ft_sample_precision_precision1 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png", zoom=1) #
+ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision1.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision2 %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png", zoom=1) #
+ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision2.png"), zoom=1) #
 
@@
 \caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
-\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision1.png"}}
+\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision1.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/ft_sample_precision_precision2.png"}}
+\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision2.png"}}
 \end{figure}
@@
   convert_aid = function(x) { x %>% mutate(aid = aid %>% format( scientific = FALSE)) %>% mutate_all(as.character) }
-  meta1_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta2_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataBLN-SWB_1979-2019.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataFBIS_1995-2004.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataNYT_1945-2005.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-  meta_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/MetaDataWSJ_1945-2006.csv", col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
-
-  events_nyt2 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-NYT_1980-2018.csv", col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid()
-  events_swb <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixBLN-SWB_1979-2019.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
-  events_fbis <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixFBIS_1995-2004.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
-  events_nyt <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixNYT_1945-2005.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
-  events_wsj <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/git_ignore_folder/DOI-10-13012-b2idb-0647142_v3/PhoenixWSJ_1945-2006.csv", col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
+  meta1_nyt2 <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataBLN-NYT_1980-2018.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta2_swb <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataBLN-SWB_1979-2019.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta_fbis <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataFBIS_1995-2004.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta_nyt <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataNYT_1945-2005.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+  meta_wsj <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "MetaDataWSJ_1945-2006.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) #%>% convert_aid()
+
+  events_nyt2 <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixBLN-NYT_1980-2018.csv"), col_types=rep('c',50)  %>% paste0(collapse='')) # %>% convert_aid() 
+  events_swb <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixBLN-SWB_1979-2019.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid() 
+  events_fbis <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixFBIS_1995-2004.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
+  events_nyt <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixNYT_1945-2005.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()  
+  events_wsj <- read_csv(here::here("git_ignore_folder", "DOI-10-13012-b2idb-0647142_v3", "PhoenixWSJ_1945-2006.csv"), col_types=rep('c',50) %>% paste0(collapse='')) #%>% convert_aid()
 
@@
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
-    icews_clean_subset_top10_day %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")
+    icews_clean_subset_top10_day %>% write_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
     #just out the tsv and plot how you want in the main paper
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_phoenix_plot_lv0_196.Rds")
+  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_196.Rds"))
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_phoenix_plot_lv0_471.Rds")
+  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_471.Rds"))
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_terrier_plot_lv0_471.Rds")
+  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_terrier_plot_lv0_471.Rds"))
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/figures/p_icews_plot_lv0_471.Rds")
+  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_icews_plot_lv0_471.Rds"))
   save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),

### 2022-07-22 replication_paper/pnas_draft/paper.Rmd
01-04 reproduce

@@
 
-ft_cuba_precision %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png", zoom=1) # webshot = "webshot2"
+ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
@@
 \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=22cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png"}}
+\centering{\includegraphics[ height=22cm]{"./case_study_cuban_precision.png"}}
 \end{figure}
@@
 
+paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")
+
 #Replace emoticons with images
 replace_emoticons <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
+  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
         #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
+        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
         #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
+        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
         #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
+        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
         #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
+        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
 }
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_recall.png", zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
             #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
+            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
             #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
+            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
             #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
+            str_replace_all('\U0001f1fA\U0001f1e6',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
             #
-            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ")
+            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) "))
                             }
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_recall.png",
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
                   zoom=1, webshot = "webshot2") # webshot = "webshot2"
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea.png", zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 library(magick)
-tiger <- image_read("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea.png")
+
+tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
 tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))
@@
 combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png")
+image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))
 
@@
 \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png}}
+\centering{\includegraphics[height=18cm]{/recall_cuban_and_crimea_andcounts.png}}
 \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
@@
 
-icews_clean_subset_top10_day <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")
+icews_clean_subset_top10_day <- read_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
 

### 2022-07-22 replication_data/rmd/01_compile_saves_and_align.Rmd
Fix v1.1 file bug

--- 2022-07-18 replication_data/rmd/01_compile_saves_and_align.Rmd
@@
 files_worker_saves <- list.files(path = path, pattern = ".Rdata", all.files = FALSE, full.names = T, recursive = T, ignore.case = FALSE, include.dirs = FALSE)
-length(files_worker_saves) #32748
+length(files_worker_saves) #103170 #32748 #103170
 
@@
 files_worker_saves <- files_worker_saves[!files_worker_saves %>% str_detect("[0-9][0-9]\\.[0-9][0-9]\\.[0-9][0-9].Rdata")] #exclude the date stamped ones
-length(files_worker_saves) #1965
+length(files_worker_saves) #5943
 if(length(files_worker_saves)==0){print("Original save files not found locally, will load premade anonymized file instead")
@@
 
-df <- data.frame(file=files_worker_saves)
+df <- data.frame(file=files_worker_saves) %>%
+      mutate(filename=file %>% basename()) %>%
+      rowwise() %>%
+        mutate(size=  file.info(file)$size ) %>%
+      ungroup() %>%
+      arrange(desc(size)) %>%
+      filter(!duplicated(filename))
+dim(df) #1985
+files_worker_saves <- df$file
 
@@
     # creates a list of event 'vectors' and names them based on the paths
-    icb_worker_saves <- lapply(files_worker_saves, readRDS) #Read the files into memory in parallel
+    icb_worker_saves <- lapply(df$file, readRDS) #Read the files into memory in parallel
     names(icb_worker_saves) <- files_worker_saves

### 2022-07-22 replication_paper/pnas_draft/appendix.Rmd
Fix v1.1 file bug

--- 2022-07-18 replication_paper/pnas_draft/appendix.Rmd
@@
   raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
-                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value) %>% distinct()
+                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value_normalized) %>% distinct()
 

### 2022-07-22 replication_paper/pnas_draft/paper.Rmd
Fix v1.1 file bug

--- 2022-07-18 replication_paper/pnas_draft/paper.Rmd
@@
               #Do alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
               #Say alone
@@
               icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf) 
+                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
+              #Think Do
+              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
             ) %>% 

### 2022-07-22 replication_corpus/rmd/download_and_clean.Rmd

@@
 if(fromscratch){
-  urls <- readLines("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/sheet1.xml.rels")[[2]] %>%
+  urls <- readLines(here::here("replication_data", "in", "sheet1.xml.rels"))[[2]] %>%
     str_replace_all("Target=","\n") %>%
@@
   #https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB 
-  setwd("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/crisis_texts/")
+  setwd(here::here("replication_data", "in", "crisis_texts"))
   getwd()
@@
 setdiff(1:476, icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort())
-icb_crisis_summaries_20150604 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/icb_crisis_summaries_20150604.csv")
-icb_crisis_summaries_20150604_handadditions <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/icb_crisis_summaries_20150604_handadditions.csv") #this gets us 1 to 455
+icb_crisis_summaries_20150604 <- read_csv(here::here("replication_data", "in", "icb_crisis_summaries_20150604.csv"))
+
+icb_crisis_summaries_20150604_handadditions <- read_csv(here::here("replication_data", "in", "icb_crisis_summaries_20150604_handadditions.csv")) #this gets us 1 to 455
+
 icb_crisis_summaries <- bind_rows(icb_crisis_summaries_20150604,icb_crisis_summaries_20150604_handadditions) %>%
@@
 #Note I had to manually recreate the 001 crisis because it was just a dump of a large text file containing first 200ish crises
-files <- list.files(path = "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/crisis_texts/", pattern = NULL, all.files = FALSE,
+
+files <- list.files(path = here::here("replication_corpus", "data", "in", "crisis_texts/"), pattern = NULL, all.files = FALSE,
            full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE)
@@
 n=nrow(filed_df)
-path <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/crisis_texts/"
+path <- here::here("replication_corpus", "data", "in", "crisis_texts/")
 library(pdftools)
@@
 
-icb_corpus %>% saveRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_corpus_V1.0_May_16_2022.Rds")
+icb_corpus %>% saveRDS(here::here("replication_corpus", "data", "out", "icb_corpus_V1.0_May_16_2022.Rds"))
 

### 2022-07-23 replication_paper/pnas_draft/paper.Rmd
v1.1 fixed

@@
 \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{/recall_cuban_and_crimea_andcounts.png}}
+\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
 \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
@@
 save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
-          p_precision_combined, base_height = 14, base_width = 18)
+          p_precision_combined, base_height = 18, base_width = 24)
 

### 2022-07-23 replication_paper/pnas_draft/paper.tex
v1.1 fixed

@@
 
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
 
@@
 
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png}}
+\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
 \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.

### 2022-07-23 replication_paper/pnas_draft/paper.Rmd
1

@@
 
+ratio=1.5
+height=18
 save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = 24)
+          p_precision_combined, base_height = 18, base_width = height*ratio)
 

### 2022-07-25 replication_data/rmd/04_validation.Rmd
Fix v1.1 file bug
arxiv draft

@@
 
+file.copy(flag_folder_small, "/mnt/8tb_a/rwd_github_private/icbewebsite/", recursive=TRUE)
+
 ```
@@
 
-ICBe_events_agreed_markdown <- ICBe_events_agreed %>% left_join(icb_events_long_narratives_sentences)
+ICBe_events_agreed_markdown <- icb_events_long_narratives_sentences #ICBe_events_agreed %>% left_join(icb_events_long_narratives_sentences %>% dplyr::select(-sentence_span_text) )
 

### 2022-07-25 replication_paper/arxiv_draft/appendix.Rmd
arxiv draft

--- 2022-07-22 replication_paper/pnas_draft/appendix.Rmd
@@
 ---
-title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"
-
-#https://bookdown.org/yihui/bookdown/a-single-document.html
-#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
-#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
-#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
+title: "Introducing ICBe: Supplementary Information"
+
+csl: pnas.csl
+bibliography: paper.bib
+biblio-style: unsrt
 output: 
-  bookdown::pdf_book:
-    toc: yes
-    latex_engine: xelatex
-
-bibliography: ICBintro.bib
-
-#Disabled several the caused errors
+  pdf_document:
+    toc: true
+
 header-includes:
@@
   - \usepackage{ctable} # added for demo
-  - \usepackage{natbib} #added for latex citation within huxtable
+#  - \usepackage{natbib} #added for latex citation within huxtable
+#  - \usepackage{biblatex} #added for latex citation within huxtable
   - \usepackage{booktabs}
@@
   - \usepackage{graphicx}
-  - \usepackage{caption}
+#  - \usepackage{caption}
 #  - \usepackage[capposition=top]{floatrow}
-  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
-  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
+#  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
+#  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
 #  - \DeclareUnicodeCharacter{00A0}{ }
@@
 #  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
+#  - \usepackage{subfigure}
   - \usepackage{subcaption}
@@
 #  - \usepackage[perpage]{footmisc}
-  - \usepackage{algorithm}
-  - \usepackage[algo2e]{algorithm2e}
+  - \usepackage{algorithm2e}
   - \usepackage{amsmath}
-  - \usepackage{afterpage}
-  - \usepackage{placeins}
-  - \usepackage{rotating, float, caption}
+#  - \usepackage[backend = biber]{biblatex} #added in hopes of getting a bbl
 #https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
-
 ---
@@
 ```{r library loads, eval=T, echo=F, cache=F, results='hide', message=F}
+
+options(tinytex.clean=F)
 
@@
 ```
-
+\clearpage
 # Appendix A Corpus and Cases
-\hphantom{em}
 ## Table A1: ICBe Crises and Summary Information {#app:crises}
-\hphantom{em}
 
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft1.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft1.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft2.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft2.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft3.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft3.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft4.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft4.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft5.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft5.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft6.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft6.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft7.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft7.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft8.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft8.png"), zoom=1)
 
@@
 \begin{figure}[H]
-\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft1.png"}}
+\caption{ICBe Crises Summary Statistics}
+\centering{\includegraphics[ height=19cm]{"./crisis_text_counts_ft1.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft2.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft2.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft3.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft3.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft4.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft4.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft5.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft5.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft6.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft6.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft7.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft7.png"}}
 \end{figure}
+\clearpage
 
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft8.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft8.png"}}
 \end{figure}
+\clearpage
 
@@
 
+\clearpage
+
 # Appendix B: Coding Process
@@
 \caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
-\centering{\includegraphics[width=17cm]{../figures/gui_example}}
+\centering{\includegraphics[width=17cm]{./gui_example}}
 \end{figure}
+\clearpage
 
@@
       \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
-      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
-      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
+      \uElseIf{expert votes >= expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
+      \uElseIf{novice votes >= novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
     }
@@
 \end{algorithm}
+\clearpage
 
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_concept.png'), 
                   plot = p_percent_chose_tag_by_concept, width=8, height=8)
@@
 \caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
-\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_concept.png}}
+\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_concept.png}}
 \end{figure}
+\clearpage
 
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_confidence.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_confidence.png'), 
                   plot = p_percent_chose_tag_by_confidence, width=8, height=6)
@@
 \caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
-\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_confidence.png}}
+\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_confidence.png}}
 \end{figure}
+\clearpage
 
@@
 
-ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
-\centering{\includegraphics[height=21cm]{../figures/ft_cuba_recall.png}}
+\centering{\includegraphics[height=21cm]{./ft_cuba_recall.png}}
 \end{figure}
 \clearpage
+
+## Table C3: Synthetic Narrative Matches Crimea-Donbas
+\hphantom{em}
 
@@
 
-ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
-\centering{\includegraphics[height=21cm]{../figures/ft_crimea_recall.png}}
+\centering{\includegraphics[height=21cm]{./ft_crimea_recall.png}}
 \end{figure}
@@
 
-## Table C3: Synthetic Narrative Matches Crimea-Donbas
-\hphantom{em}
-
 # Appendix D: Precision
-
-\hphantom{em}
-
-\clearpage
-
 ## Figure D1 Crimea-Donbos 
@@
 #ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
-fromscratch=F
+fromscratch=T
 if(fromscratch){
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
-\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part1.png}}
+\centering{\includegraphics[height=19cm]{./case_study_crimea_precision_part1.png}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part2.png}}
+\centering{\includegraphics[height=21cm]{./case_study_crimea_precision_part2.png}}
 \end{figure}
@@
 
-temp <- ICBe_events_agreed_markdown %>% dplyr::select(
+temp <- ICBe_events_agreed %>% left_join(ICBe_events_agreed_markdown) %>% dplyr::select(
   crisno, sentence_span_text,value_markdown,
@@
 
+set.seed(1) 
 temp_sample <- temp %>% mutate(rand=runif(n())) %>% group_by(value)  %>% filter(rand==max(rand)) %>% ungroup() %>% arrange(name, value)
@@
 ft_sample_precision_precision1 <- temp_sample %>% 
-                                  filter(row_number()<=56) %>%
+                                  filter(row_number() %in% 1:22) %>%
                                   dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
@@
                                   flextable::width( j = 3, width=0.5)  %>% 
-                                  flextable::width( j = 4:5, width=8.0)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
                                   flextable::fontsize(size = 9, part = "all") %>%
@@
                                   padding( padding = 1, part = "all") %>% 
-                                  bg( i = which( ((1:56) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  bg( i = which( ((1:22) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                   ftExtra::colformat_md(j = 5, part="body")
 
-ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision1.png"), zoom=1) #
+ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision1.png"), zoom=1) #
 
 ft_sample_precision_precision2 <- temp_sample %>% 
-                                  filter(row_number()>=57) %>%
+                                  filter(row_number() %in% 23:54) %>%
                                   dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
@@
                                   padding( padding = 1, part = "all") %>% 
-                                  bg( i = which( ((1:59) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  bg( i = which( ((23:54) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                   ftExtra::colformat_md(j = 5, part="body")
 
-ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision2.png"), zoom=1) #
+ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision2.png"), zoom=1) #
+
+ft_sample_precision_precision3 <- temp_sample %>% 
+                                  filter(row_number() %in% 55:90) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((55:90) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision3.png"), zoom=1) #
+
+ft_sample_precision_precision4 <- temp_sample %>% 
+                                  filter(row_number() %in% 91:115) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((91:115) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision4.png"), zoom=1) #
 
@@
 \caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
-\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision1.png"}}
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision1.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision2.png"}}
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision2.png"}}
+\end{figure}
+\clearpage
+
+\hphantom{em}
+\begin{figure}[H]
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision3.png"}}
+\end{figure}
+\clearpage
+
+\hphantom{em}
+\begin{figure}[H]
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision4.png"}}
 \end{figure}
@@
     print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/figures/p_icb_metro_plot_",thiscrisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icb_metro_plot_",thiscrisis,".Rds")
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/figures/p_mids_metro_plot_",thiscrisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_mids_metro_plot_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_terrier_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_icews_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icews_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
 
@@
 ## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.Rds') 
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
   ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_penta_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_penta_196.Rds')
 subtitle="Phoenix Dyadic Events"
@@
     )
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_196_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_196_combined.png'),
           p_196_combined, base_height = 12, base_width = 20)
@@
 \begin{sideways}%[htbp]
-\centering{\includegraphics[width=21cm]{../figures/p_196_combined.png}}
+\centering{\includegraphics[width=21cm]{./p_196_combined.png}}
 \end{sideways}
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_196.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
+  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_phoenix_plot_lv0_196.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_lv0_196.png'),
             p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=21cm]{../figures/p_phoenix_plot_lv0_196.png}}
+\centering{\includegraphics[width=21cm]{./p_phoenix_plot_lv0_196.png}}
 \end{sidewaysfigure}
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_471.Rds') 
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_471.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_penta_471.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_terrier_plot_penta_471.Rds')
 subtitle="Terrier Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icews_plot_penta_471.Rds')
 p_471_icews <- readRDS(save_file)
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_471_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_471_combined.png'),
           p_471_combined, base_height = 12, base_width = 25)
@@
 \caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
-\centering{\includegraphics[width=21cm]{../figures/p_471_combined.png}}
+\centering{\includegraphics[width=21cm]{./p_471_combined.png}}
 \end{sidewaysfigure}
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
+  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_phoenix_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_lv0_471.png'),
             p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{../figures/p_phoenix_plot_lv0_471.png}}
+\centering{\includegraphics[width=21cm]{./p_phoenix_plot_lv0_471.png}}
 \end{sidewaysfigure}
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_terrier_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
+  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_terrier_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_terrier_plot_lv0_471.png'),
             p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{../figures/p_terrier_plot_lv0_471.png}}
+\centering{\includegraphics[width=21cm]{./p_terrier_plot_lv0_471.png}}
 \end{sidewaysfigure}
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_icews_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),
+  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_icews_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icews_plot_lv0_471.png'),
             p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{../figures/p_icews_plot_lv0_471.png}}
+\centering{\includegraphics[width=21cm]{./p_icews_plot_lv0_471.png}}
 \end{sidewaysfigure}

### 2022-07-25 replication_paper/arxiv_draft/paper.Rmd
arxiv draft

--- 2022-07-23 replication_paper/pnas_draft/paper.Rmd
@@
 ## Remove this if not required
-conflict_of_interest: |
-  Please declare any conflict of interest here.
+#conflict_of_interest: |
+#  Please declare any conflict of interest here.
 
@@
 We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
-We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
+We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
 We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
@@
 ## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
-pnas_type: pnasresearcharticle
-
-bibliography: ICBintro.bib
-csl: pnas.csl
 
@@
 #https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
-output: 
-  bookdown::pdf_book:
-    toc: no
-    base_format: rticles::pnas_article
-    latex_engine: xelatex
+#https://stackoverflow.com/questions/64700865/using-r-rstudio-knit-to-pdf-how-to-pass-custom-flags-to-the-pdflatex-command
+
+csl: pnas.csl
+bibliography: paper.bib
+biblio-style: unsrt
+output: rticles::arxiv_article
 
@@
 header-includes:
-  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
+#  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
 #  - \usepackage{tinytex}
@@
   - \usepackage[algo2e]{algorithm2e}
+#  - \usepackage[backend = biber]{biblatex} #added in hopes of getting a bbl
 #https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
@@
 #International Crisis Behavior Events (ICBe) Dataset
-knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
+knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warning=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
+
+#Execute these lines to get bbl files for the arxiv submission
+options(tinytex.clean=F)
 
@@
 -->
+\twocolumn
 
@@
 This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
+If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
 On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
@@
 
-```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
+```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
 
@@
         ungroup() %>%
-        mutate(banding=sentence_number_int_aligned %% 2)
+        mutate(banding=as.numeric(as.factor(sentence_number_int_aligned)) %% 2)
 temp$is_subsstring <- NA
@@
 
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","arxiv_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
@@
 \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=22cm]{"./case_study_cuban_precision.png"}}
+\centering{\includegraphics[ height=19cm]{"./case_study_cuban_precision.png"}}
 \end{figure}
@@
       flextable::as_flextable() %>%
-
-      #add_header( 
-      #        #"ICB Corpus"="Corpus",
-      #        "ICBe"="Ours",
-      #        "Phoenix"="CAMEO Dictionary\nSystems",
-      #        "Terrier"="CAMEO Dictionary\nSystems",
-      #        "ICEWs"="CAMEO Dictionary\nSystems",
-      #        "MIDs Events"="Disputes",
-      #        "UCDP-GED"="Violence",
-      #        "ICB"="Crises",
-      #        "COW"="Wars",
-      #        "MIDs"="Disputes",
-      #        top = T ) %>%
 
@@
 litreview_ft_pnas %>% 
-  ftExtra::colformat_md(j = 3, part="body") %>%
     flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
-  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
    flextable::flextable_to_rmd()
+
+#litreview_ft_pnas   %>% 
+#    #flextable::flextable_to_rmd()
+#    save_as_image(path=here::here("replication_paper", "arxiv_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
+    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_recall.png"),
                   zoom=1, webshot = "webshot2") # webshot = "webshot2"
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_recall.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'),
        plot = p_recall ,
@@
 
-tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))
+tiger <- image_read(here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"))
+tiger2 <- image_read(paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'))
 
 combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))
+image_write(combined, here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea_andcounts.png"))
 
@@
 
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
+p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
     labs(
@@
 
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
+p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
     labs(
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = 24)
+ratio=1.5
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_precision_combined.png'),
+          p_precision_combined, base_height = 18, base_width = height*ratio)
 
@@
 \caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=24cm]{../figures/p_precision_combined.png}}
+\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
 \end{sidewaysfigure}
@@
 
+newcolors <- pals::glasbey()
+
 value_means <- ICBe_events_agreed_markdown_embedded %>% 
-               dplyr::select(UMAP1,UMAP2, contains("escalate"),contains("coop"),contains("sayintkind"), contains("thinkkind")) %>%
-               pivot_longer(cols=-c(UMAP1,UMAP2)) %>% filter(!is.na(value) & value!='') %>% 
-               mutate(value = value %>% str_split(";")) %>% 
-               unnest(value) %>% 
-               mutate(value = value %>% str_trim()) %>%
-               filter(!value %>% str_detect("sentence|^[0-9]")) %>%
+               left_join(icb_events_long %>% 
+                           filter(varname_normalized %>% str_detect('escalate|coop|sayintkind|thinkkind')) %>%
+                           filter(!value_normalized %>% str_detect('^[0-9]*$'))) %>%
                mutate(color=NA) %>%
-               mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
-               dplyr::select(-name) %>%
-               group_by(color, value) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_escalate"),"red",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_deescalate"),"darkgreen",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("sayintkind"),"brown",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("thinkkind"),"darkorange",color)) %>%
+               dplyr::select(-varname_normalized,-value_qcode,-varname_normalized,-crisis_text,-crisno,-sentence_number_int_aligned,-sentence_span_text,
+                             -actor_set,-value_markdown,-sentence_span_text_clean,-sentences_unique_sanitized) %>% # 
+               group_by(color, value_normalized) %>%
                mutate(n=n()) %>%
                filter(n>20) %>% #note require at least 20 examples of that tag
-               dplyr::summarise_all(median)
+               dplyr::summarise_all(median) %>%
+              na.omit()
 
@@
       geom_label(data=value_means,
-                 aes(x=UMAP2,y=UMAP1, fill = value %>% as.factor(), label=value, size=50), size = 2.5, inherit.aes=F, 
+                 aes(x=UMAP2,y=UMAP1,
+                     fill = value_normalized %>% as.factor(),
+                     label=value_normalized, size=50
+                     ), size = 2.5,
+                 inherit.aes=F, 
                  colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
@@
       ) +
-     scale_color_manual(values = value_normalized_colors) +
+     #scale_color_manual(values = value_normalized_colors) +
      scale_fill_manual(values = value_normalized_colors) +
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
 
@@
 #Rex Note to take only one per sentence
-
-#This is unreasonably slow because it's large and in tidy. Couldn't do it every time if we wanted to.
-value_highdim <- ICBe_events_agreed_markdown_embedded %>%
-                 dplyr::select(starts_with("V",  ignore.case = F), contains("escalate"),contains("coop"),contains("sayintkind"), 
-                               contains("thinkkind"), crisno, sentence_number_int_aligned) %>% 
-                 pivot_longer(cols=-c(starts_with("V",  ignore.case = F), crisno, sentence_number_int_aligned) ) %>%
-                 filter(!is.na(value) & value!='') %>% #40,898
-                 filter(!value %>% str_detect("sentence|^[0-9]")) %>% 
-                 mutate(value = value %>% str_split(";")) %>% 
-                 unnest(value) %>% 
-                 mutate(value = value %>% str_trim())   %>% #
-                 mutate(color=NA) %>%
-                 mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
-                 dplyr::select(-name) %>%
-                 group_by(color, value) %>%
-                  mutate(n=n()) %>% 
-                 ungroup() %>%
-                 arrange(n, value) %>%
-                 filter(!duplicated( paste(crisno, sentence_number_int_aligned)) ) %>% #only take one per sentence to break mechanically induced correlations
-                 filter(n>20)
-
-dim(value_highdim)
-
-value_highdim_medians <- value_highdim %>% 
-                           group_by(color, value) %>%
-                           dplyr::summarise_all(median)
-
-value_normalized_colors <- value_highdim_medians$color 
-names(value_normalized_colors) = value_highdim_medians$value
-
-m <- value_highdim_medians %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix() 
-rownames(m) <- value_highdim_medians$value
+value_normalized_colors <- value_means$color 
+names(value_normalized_colors) = value_means$value_normalized
+
+m <- value_means %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix() 
+rownames(m) <- value_means$value_normalized
 d <- m %>% dist()
@@
             ) +
-            geom_text(data = label(hcdata) %>% mutate(color=value_highdim_medians$color ), 
-                      aes(x = x, y = y, label = label, hjust = 0, color=color[hc$order]), 
+            geom_text(data = ggdendro::label(hcdata) %>% mutate(color=value_normalized_colors[hcdata$labels$label] ), 
+                      aes(x = x, y = y, label = label, hjust = 0,
+                          color=label %>% as.factor()), 
                       size = 3
@@
             coord_flip() +
+            scale_color_manual(values = value_normalized_colors) +
             scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
 
@@
 \caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{../figures/p_semantic_embeddings_dendro.png}}
+\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
 \textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
@@
 The dendrogram shows hiearchical clustering of the tags.
-If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to visually recognizable.
+If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable.
 }
@@
 Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis.
+The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix Figure D3 and D4).
 On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
@@
 save_plot(file=paste0(here::here(),
-                      '/replication_paper/figures/p_precision_icews.png'),
+                      '/replication_paper/arxiv_draft/p_precision_icews.png'),
           p_ICEWS, base_height = 10, base_width = 14)
@@
 \caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{../figures/p_precision_icews.png}}
+\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
 \textit{Notes:Unit of analysis is the Dyad-Day.
@@
 
-We investigated event extraction from narratives describing key historical episodes in international relations.
+We investigated event abstraction from narratives describing key historical episodes in international relations.
 We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
@@
 
-<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
+<!-- PNAS lines Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references
 \showmatmethods
@@
 \pnasbreak
+-->

### 2022-07-25 replication_paper/arxiv_draft/paper.tex
arxiv draft

--- 2022-07-23 replication_paper/pnas_draft/paper.tex
@@
-\documentclass[9pt,twocolumn,twoside,]{pnas-new}
-
-% Use the lineno option to display guide line numbers if required.
-% Note that the use of elements such as single-column equations
-% may affect the guide line number alignment.
-
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
+\documentclass{article}
+
+\usepackage{arxiv}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{graphicx}
+
+\title{Introducing ICBe: Very High Recall and Precision Event Extraction
+from Narratives about International Crises}
+
+\author{
+  }
 
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 
@@
 
-\usepackage{xr} \externaldocument{appendix}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{ctable}
-\usepackage{natbib}
 \usepackage{booktabs}
@@
 \usepackage[algo2e]{algorithm2e}
-\usepackage{fontspec}
 \usepackage{multirow}
@@
 \usepackage{hyperref}
-
-\templatetype{pnasresearcharticle}  % Choose template
-
-\title{Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises}
-
-\author[a,1,2]{Rex W. Douglass}
-\author[a]{Thomas Leo Scherer}
-\author[b]{J. Andrés Gannon}
-\author[a]{Erik Gartzke}
-\author[c]{Jon Lindsay}
-\author[d]{Shannon Carcelli}
-\author[d]{Jonathan Wilkenfeld}
-\author[e]{David M. Quinn}
-\author[f]{Catherine Aiken}
-\author[g]{Jose Miguel Cabezas Navarro}
-\author[d]{Neil Lund}
-\author[h]{Egle Murauskaite}
-\author[h]{Diana Partridge}
-
-  \affil[a]{Department of Political Science, University of California, San Diego, CA, USA.}
-  \affil[b]{Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.}
-  \affil[c]{School of Cybersecurity and Privacy \textbar{} Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.}
-  \affil[d]{Department of Government and Politics, University of Maryland, College Park, MD, USA.}
-  \affil[e]{Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.}
-  \affil[f]{Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.}
-  \affil[g]{Society and Health Research Center, Universidad Mayor, Santiago, Chile.}
-  \affil[h]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
-  \affil[i]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Douglass}
-
-% Please add here a significance statement to explain the relevance of your work
-\significancestatement{Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
-Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
-This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods.
-It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.}
-
-\authorcontributions{Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D., J.A.G., E.G., T.L.S.;
-Visualization: R.W.D., T.L.S.; Supervision: E.G.; Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.}
-
-\authordeclaration{Please declare any conflict of interest here.}
-
-\correspondingauthor{\textsuperscript{2} To whom correspondence should be addressed. E-mail: \href{mailto:rexdouglass@gmail.com}{\nolinkurl{rexdouglass@gmail.com}}}
-
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
- \keywords{  Diplomacy |  War |  Crises |  International Affairs |  Computational Social Science  }
+\begin{document}
+\maketitle
 
 \begin{abstract}
-How do international crises unfold?
-We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
-We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
-We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
-We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+How do international crises unfold? We conceptualize of international
+relations as a strategic chess game between adversaries and develop a
+systematic way to measure pieces, moves, and gambits accurately and
+consistently over a hundred years of history. We introduce a new
+ontology and dataset of international events called ICBe based on a very
+high-quality corpus of narratives from the International Crisis Behavior
+(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
+precision than existing state of the art datasets and conduct two
+detailed case studies of the Cuban Missile Crisis (1962) and
+Crimea-Donbas Crisis (2014). We further introduce two new event
+visualizations (event icongraphy and crisis maps), an automated
+benchmark for measuring event recall using natural language processing
+(sythnetic narratives), and an ontology reconstruction task for
+objectively measuring event precision. We make the data, replication
+material, and visualizations of every historical episode available at a
+companion website www.crisisevents.org.
 \end{abstract}
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-\verticaladjustment{-2pt}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\acknow{We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-We thank the many undergraduate coders for their patience and dedication.
-Thanks to the Center for Peace and Security Studies and its membership for comments.
-Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
-Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.}
-
-If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
-In other words, what is the entropy of international relations?
-This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive (1, 2).
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.\footnote{See work on crises (3, 4), militarized disputes (5--7), wars (8, 9), organized violence (10, 11), political violence (12), sanctions (13), trade (14), and international agreements (15--17), dispute resolution (17, 18), and diplomacy (19, 20).} With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.\footnote{See (21); (22); (23); (24); (25); (26).
-On event-extraction from images and social-media see (27) and (28).} How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations.
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises (1, 29--32).
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
-We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
-The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision.
-A final section concludes.
+\keywords{
+    Diplomacy
+   \and
+    War
+   \and
+    Crises
+   \and
+    International Affairs
+   \and
+    Computational Social Science
+  }
+
+\twocolumn
+
+If we could record every important interaction between countries in all
+of diplomacy, military conflict, and international political economy,
+how much unique information would this chronicle amount to, and how
+surprised would we be to see something new? In other words, what is the
+entropy of international relations? This record could in principle be
+unbounded, but the central conceit of social science is that there are
+structural regularities that limit what actors can do, their best
+options, and even which actors are likely to survive (1, 2). If so, then
+these events can be systematically measured, and accordingly, massive
+effort is expended in social science attempting to record these
+regularities.\footnote{See work on crises (3, 4), militarized disputes
+  (5--7), wars (8, 9), organized violence (10, 11), political violence
+  (12), sanctions (13), trade (14), and international agreements
+  (15--17), dispute resolution (17, 18), and diplomacy (19, 20).} Thanks
+to improvements in natural language processing, more open-ended efforts
+have begun to capture entire unstructured streams of events from
+international news reports.\footnote{See (21); (22); (23); (24); (25);
+  (26). On event-extraction from images and social-media see (27) and
+  (28).} How close these efforts are to accurately measuring all or even
+most of what is essential in international relations is an open
+empirical question, one for which we provide new evidence here.
+
+Our contribution is a high coverage ontology and event dataset for key
+historical episodes in 20th and 21st-century international relations. We
+develop a large, flexible ontology of international events with the help
+of both human coders and natural language processing. We apply it
+sentence-by-sentence to an unusually high-quality corpus of historical
+narratives of international crises (1, 29--32). The result is a new
+lower bound estimate of how much actually happens between states during
+pivotal historical episodes. We then develop several methods for
+objectively gauging how well these event codings reconstruct the
+information contained in the original narrative. We conclude by
+benchmarking our event codings against several current state-of-the-art
+event data collection efforts. We find that existing systems produce
+sequences of events that do not contain enough information to
+reconstruct the underlying historical episode. The underlying
+fine-grained variation in international affairs is unrecognizable
+through the lens of current quantification efforts.
+
+This is a measurement paper that makes the following argument --- there
+is a real-world unobserved latent concept known as international
+relations, we propose a method for systematically measuring it, we
+successfully apply this method producing a new large scale set of
+measurements, those measurements exhibit several desirable kinds of
+internal and external validity, and those measurements out-perform other
+existing approaches. The article organizes that argument into eight
+sections: task definition; corpus; priors/existing state of the art;
+ICBe coding process; internal consistency; case study selection; recall;
+and precision. A final section concludes.
 
@@
 
-We consider the measurement task of abstracting discrete events about a historical episode in international relations.
-The easiest way to convey the task is with an example.
-Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine readable abstractive events.
-Formally, a historical episode, \(H\), is demarcated by a period of time \([T_{start}, T_{end}] \in T\), a set of Players \(p \in P\), and a set of behaviors they undertook during that time \(b \in B\).
-International Relations, \(IR\), is the system of regularities that govern the strategic interactions that world actors make during a historical episode, given their available options, preferences, beliefs, and expectations of choices made by others.
-We observe neither \(H\) nor \(IR\) directly.
-Rather the Historical Record, \(HR\), produces documents \(d \in D\) containing some relevant and true (as well as irrelevant and untrue) information about behaviors that were undertaken recorded in the form of unstructured natural language text.
-The task is to combine informative priors about \(IR\) with an unstructured corpus \(D\) to produce a series of structured discrete events, \(e \in E\), that have high coverage, precision, and recall over what actually took place in history, \(H\).
+We consider the measurement task of abstracting discrete events about a
+historical episode in international relations. The easiest way to convey
+the task is with an example. Figure 1 shows a narrative account of the
+Cuban Missile Crisis (1962) alongside a mapping from each natural
+language sentence to discrete machine readable abstractive events.
+Formally, a historical episode, \(H\), is demarcated by a period of time
+\([T_{start}, T_{end}] \in T\), a set of Players \(p \in P\), and a set
+of behaviors they undertook during that time \(b \in B\). International
+Relations, \(IR\), is the system of regularities that govern the
+strategic interactions that world actors make during a historical
+episode, given their available options, preferences, beliefs, and
+expectations of choices made by others. We observe neither \(H\) nor
+\(IR\) directly. Rather the Historical Record, \(HR\), produces
+documents \(d \in D\) containing some relevant and true (as well as
+irrelevant and untrue) information about behaviors that were undertaken
+recorded in the form of unstructured natural language text. The task is
+to combine informative priors about \(IR\) with an unstructured corpus
+\(D\) to produce a series of structured discrete events, \(e \in E\),
+that have high coverage, precision, and recall over what actually took
+place in history, \(H\).
 
@@
 
-For our corpus, \(D\), we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project (\(n=471\))(SI Appendix, Table A1)(33, 34).
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system (3).\footnote{On near crises see (32).} Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict (3, 35--42).
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources (33, 43).
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity (44).
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
+For our corpus, \(D\), we select a set of unusually high-quality
+historical narratives from the International Crisis Behavior (ICB)
+project (\(n=471\))(SI Appendix, Table A1)(33, 34). Their domain is 20th
+and 21st-century crises, defined as a change in the type, or an increase
+in the intensity, of disruptive interaction with a heightened
+probability of military hostilities that destabilizes states'
+relationships or challenges the structure of the international system
+(3).\footnote{On near crises see (32).} Crises are a significant focus
+of detailed single case studies and case comparisons because they
+provide an opportunity to examine behaviors in IR short of, or at least
+prior to, full conflict (3, 35--42). Case selection was exhaustive based
+on a survey of world news archives and region experts, cross-checked
+against other databases of war and conflict, and non-English sources
+(33, 43). Each narrative was written by consensus by a small number of
+scholars, using a uniform coding scheme, with similar specificity (44).
+The corpus is unique in IR because it is designed to be used in a
+downstream quantitative coding project.
 
 \hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
-\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
-\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}
-
-Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find 464 actors and 117 different behaviors, and provide a full codebook in the online material.\footnote{See the Github Repository \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet (45), tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).
-
-The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11, 47).\footnote{Additional relevant but dated or too small of an overlap in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51), SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories in (54) and (55)).} The final set of columns compares episode-level datasets beginning with the original ICB project (3, 4, 56); the Militarized Interstate Disputes dataset (5, 6, 57, 58), and the Correlates of War (8).
-With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.\footnote{See (53) for a recent review of ontological depth and availability of Gold Standard example text.}
+\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing
+State of the
+Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
+\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological
+Coverage, and the Existing State of the Art}
+
+Next we draw informative prior beliefs about the underlying process of
+IR that we expect to govern behavior during historical episodes and
+their conversion to the historical record. We organize our prior beliefs
+along two overarching axes, summarized in detail by Table 1.
+
+The first axis (rows) represents the types of information we expect to
+find in IR and forms the basis for our proposed ontology. We employ a
+metaphor of a chess game, with players (polities, rebel groups, IGOs,
+etc.), pieces (military platforms, civilians, domains), and behaviors
+(think, say, do). Precise sequencing is required to capture gambits
+(sequences of moves) and outcomes (victory, defeat, peace, etc.), while
+precise geo-coding is required to understand the chessboard (medium of
+conflict). We find 472 actors and 117 different behaviors, and provide a
+full codebook in the online material.\footnote{See the Github Repository
+  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
+
+We base our informed priors primarily on two sources of information. The
+first is the extensive existing measurement efforts of IR which we
+provide citations to alongside each concept. Second, we performed
+preliminary natural language processing of the corpus and identified
+named entities and behaviors mentioned in the text. Verbs were matched
+to the most likely definition found in Wordnet (45), tallied, and then
+aggregated into a smaller number hypernyms balancing conceptual detail
+and manageable sparsity for human coding (SI Appendix, Table A2).
+
+The second axis (columns) compares the very high ontological coverage of
+ICBe to existing state of the art systems in production and with global
+coverage. They begin with our contribution ICBe, alongside other
+event-level datasets including CAMEO dictionary lookup based systems
+(Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized
+Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11,
+47).\footnote{Additional relevant but dated or too small of an overlap
+  in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51),
+  SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories
+  in (54) and (55)).} The final set of columns compares episode-level
+datasets beginning with the original ICB project (3, 4, 56); the
+Militarized Interstate Disputes dataset (5, 6, 57, 58), and the
+Correlates of War (8). With the exception of large scale CAMEO
+dictionary based systems, the existing state of the art quantitative
+datasets ignore the vast majority of the information content found in
+international relations.\footnote{See (53) for a recent review of
+  ontological depth and availability of Gold Standard example text.}
 
@@
 
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{15k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
 
@@
 
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details (59).\footnote{This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.} Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-B1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players (\(P\)), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.~force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.~an offer for the U.S.S.R.
-to remove missiles from Cuba in exchange for the U.S.
-removing missiles from Turkey.
-Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-
-Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.\footnote{Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.} For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=972,545), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
-We then aggregate those tags into final events (n=18,309), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
-This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
+The ICBe ontology follows a hierarchical design philosophy where a
+smaller number of significant decisions are made early on and then
+progressively refined into more specific details (59).\footnote{This
+  process quickly focuses the coder on a smaller number of relevant
+  options while also allowing them to apply multiple tags if the
+  sentence explicitly includes more than one or there is insufficient
+  evidence to choose only one tag. The guided coding process also allows
+  for the possibility that earlier coarse decisions have less error than
+  later fine-grained decisions.} Each coder was instructed to first
+thoroughly read the full crisis narrative and then presented with a
+custom graphical user interface (SI Appendix, Fig. B1). Coders then
+proceeded sentence by sentence, choosing the number of events (0-3) that
+occurred, the highest behavior (thought, speech, or activity), a set of
+players (\(P\)), whether the means were primarily armed or unarmed,
+whether there was an increase or decrease in aggression
+(uncooperative/escalating or cooperative/de-escalating), and finally one
+or more non-mutually exclusive specific activities. Some additional
+details like location and timing information was always collected while
+other details were only collected if appropriate, e.g.~force size,
+fatalities, domains, units, etc. A unique feature of the ontology is
+that thought, speech, and do behaviors can be nested into combinations,
+e.g.~an offer for the U.S.S.R. to remove missiles from Cuba in exchange
+for the U.S. removing missiles from Turkey. Through compounding, the
+ontology can capture what players were said to have known, learned, or
+said about other specific fully described actions.
+
+Each crisis was typically assigned to 2 expert coders and 2 novice
+coders with an additional tie-breaking expert coder assigned to
+sentences with high disagreement.\footnote{Expert coders were graduate
+  students or postgraduates who collaboratively developed the ontology
+  and documentation for the codebook. Undergraduate coders were students
+  who engaged in classroom workshops.} For the purposes of measuring
+intercoder agreement and consensus, we temporarily disaggregate the unit
+of analysis to the Coder-Crisis-Sentence-Tag (n=993,740), where a tag is
+any unique piece of information a coder can associate with a sentence
+such as an actor, date, behavior, etc. We then aggregate those tags into
+final events (n=18,783), using a consensus procedure (SI Appendix,
+Algorithm B2) that requires a tag to have been chosen by at least one
+expert coder and either a majority of expert or novice coders. This
+screens noisy tags that no expert considered possible but leverages
+novice knowledge to tie-break between equally plausible tags chosen by
+experts.
 
@@
 We evaluate the internal validity of the coding process in several ways.
-For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig.
-B3).
-Across all concepts, the Top 1 Tag Agreement was low among novices (31\%), moderate for experts (65\%), and high (74\%) following the consensus screening procedure.
+For every tag applied we calculate the observed intercoder agreement as
+the percent of other coders who also applied that same tag (SI Appendix,
+Fig. B3). Across all concepts, the Top 1 Tag Agreement was low among
+novices (31\%), moderate for experts (65\%), and high (73\%) following
+the consensus screening procedure.
 
 We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to be low for 20\% of sentences- half due to a mismatch between the ontology and the text (``survey doesn't fit event''-45\%) and half due to a lack of information or confused writing in the source text (``more knowledge needed''-40\%, ``confusing sentence''-6\%).
-Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig.
-B4).
-Second, as intended agreement is higher (75-80\%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50\%-60\%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.~some more expressive applying many tags per concept while others focused on only the single best match.
-We further observed unintended synonymity, e.g.~the same information can be framed as either a threat to do something or a promise not to do something.
+First, we required coders to rate their confidence which was observed to
+be low for 20\% of sentences- half due to a mismatch between the
+ontology and the text (``survey doesn't fit event''-45\%) and half due
+to a lack of information or confused writing in the source text (``more
+knowledge needed''-40\%, ``confusing sentence''-6\%). Observed
+disagreement varied predictably with self reported confidence (SI
+Appendix, Fig. B4). Second, as intended agreement is higher (75-80\%)
+for questions with fewer options near the root of the ontology compared
+to agreement for questions near the leafs of the ontology (50\%-60\%).
+Third, individual coders exhibiting nontrivial coding styles, e.g.~some
+more expressive applying many tags per concept while others focused on
+only the single best match. We further observed unintended synonymity,
+e.g.~the same information can be framed as either a threat to do
+something or a promise not to do something.
 
@@
 
-The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website.
-In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
+The remaining two qualities we seek to measure are recall and precision
+of ICBe events in absolute terms and relative to other existing systems.
+We provide full ICB narratives, ICBe coding in an easy to read
+icongraphic form, and a wide range of visualizations for every case on
+the companion website. In this paper, we focus on two deep case studies.
+The first is the Cuban Missile Crisis (Figure 1) which took place
+primarily in the second half of 1962, involved the United States, the
+Soviet Union, and Cuba, and is widely known for bringing the world to
+the brink of nuclear war (hereafter Cuban Missiles). The second is the
+Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily
+in 2014, involved Russia, Ukraine, and NATO, and within a decade
+spiraled into a full scale invasion (herafter Crimea-Donbas). Both cases
+involve a superpower in crisis with a neighbor, initiated by a change
+from a friendly to hostile regime, with implications for economic and
+military security for the superpower, risked full scale invasion, and
+eventually invited intervention by opposing superpowers. We choose these
+cases because they are substantively significant to 20th and 21st
+century international relations, widely known across scientific
+disciplines and popular culture, and are sufficiently brief to evaluate
+in depth.
 
@@
 
-Recall measures the share of desired information recovered by a sequence of coded events, \(Pr(E|H)\), and is poorly defined for historical episodes.
-First, there is no genuine ground truth about what occurred, only surviving texts about it.
-Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox (60) --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events.
-The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
-We need a yardstick for history.
-
-Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative.
-For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
-Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts.
-The more accounts that mention a detail, the more central it is to understanding the true historical episode.
-The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing.
-With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
-Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
-
-Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts.
-First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative.
-Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details.
-Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g.~the U.S.
-was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection (61) and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.~a long term lease on naval facilities in Crimea.
-Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode level datasets have very low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
+Recall measures the share of desired information recovered by a sequence
+of coded events, \(Pr(E|H)\), and is poorly defined for historical
+episodes. First, there is no genuine ground truth about what occurred,
+only surviving texts about it. Second, there is no \textit{a priori}
+guide to what information is necessary detail and what is ignorable
+trivia. History suffers from what is known as the Coastline Paradox (60)
+--- it has a fractal dimension greater than one such that the more you
+zoom in the more detail you will find about individual events and in
+between every two discrete events. The ICBe ontology is a proposal about
+what information is important, but we need an independent benchmark to
+evaluate whether that proposal is a good one and that allows for
+comparing proposals from event projects that had different goals. We
+need a yardstick for history.
+
+Our strategy for dealing with both problems is a plausibly objective
+yardstick called a synthetic historical narrative. For both case
+studies, we collect a large diverse corpus of narratives spanning
+timelines, encyclopedia entries, journal articles, news reports,
+websites, and government documents. Using natural language processing
+(fully described in SI Appendix, Algorithm C1), we identify details that
+appear across multiple accounts. The more accounts that mention a
+detail, the more central it is to understanding the true historical
+episode. The theoretical motivation is that authors face word limits
+which force them to pick and choose which details to include, and they
+choose details which serve the specific context of the document they are
+producing. With a sufficiently large and diverse corpus of documents, we
+can vary the context while holding the overall episode constant and see
+which details tend to be invariant to context. Intuitively, a high
+quality event dataset should have high recall for context invariant
+details both because of their broader relevance and also because they
+are easier to find in source material.
+
+Synthetic historical narratives for Cuban Missiles (51 events drawn from
+2020 documents) and Crimea-Donbas (30 events drawn from 971 documents)
+appear in Figure 2. Each row represents a detail which appeared in at
+least five documents along with an approximate start date, a hand
+written summary, the number of documents it was mentioned in, and
+whether it could be identified in the text of our ICB corpus, in our
+ICBe events, or any of the competing systems.
+
+From them, we draw several stylized facts. First, there is substantial
+variation in which details any one document will choose to include. Our
+ground truth ICB narratives included 17/51 and 23/30 of the events from
+the synthetic narrative, while including other details that are not in
+the synthetic narrative. Second, mentions of a detail across accounts is
+exponentially distributed with context invariant details appearing
+dozens to hundreds of times more than context dependent details. Third,
+crisis start and stop dates are arbitrary and the historical record
+points to many precursor events as necessary detail for understanding
+later events, e.g.~the U.S. was in a \textit{de facto} grey scale war
+with Cuba before it invited Soviet military protection (61) and Ukraine
+provided several security guarantees to Russia that were potentially
+undone, e.g.~a long term lease on naval facilities in Crimea. Fourth, we
+find variation between the two cases. Cuban Missiles has a cleaner
+canonical end with the Soviets agreeing to withdraw missiles while
+Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II)
+but continued fighting. The canonical narrative of Cuban Missile also
+includes high level previously classified details, while the more recent
+Crimea-Donbas case reflects primarily public reporting.
+
+We find substantive variation in recall across systems. Recall for each
+increases in the number of document mentions which is an important sign
+of validity for both them and our benchmark. The one outlier is Phoenix
+which is so noisy that it's flat to decreasing in mentions. The two
+episode level datasets have very low coverage of contextual details. The
+two other dictionary systems ICEWs and Terrier have high coverage, with
+ICEWs outperforming Terrier. ICBe strictly dominates all of the systems
+but ICEWs in recall though we note that the small sample sizes mean
+these systems should be considered statistically indistinguishable.
+Importantly our corpus of ICB narratives has very high recall of
+frequently mentioned details giving us confidence in how those summaries
+were constructed, and ICBe lags only slightly behind showing that it
+left very little additional information on the table.
 
@@
 
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, \(Pr(H|E)\).
-It does little good to recall a historical event but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
-D3 and D4) and all crises on the companion website.
+The other side of event measurement is precision, the degree to which a
+sequence of events correctly and usefully describes the information in
+history, \(Pr(H|E)\). It does little good to recall a historical event
+but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a
+blockade, a show of force, and a stalemate) or with too much error
+(e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between
+1995-2019) to be useful for downstream applications. ICBe's ontology and
+coding system is designed to strike a balance so that the most important
+information is recovered accurately but also abstracted to a level that
+is still useful and interpretable. You should be able to lay out events
+of a crisis on a timeline, as in Figure 3, and read off the macro
+structure of an episode from each individual move. We call this
+visualization a crisis map, a directed graph intersected with a
+timeline, and provide crisis maps for every event dataset for each case
+study (SI Appendix, Fig. D3 and D4) and all crises on the companion
+website.
 
@@
 
-We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).
-
-We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark.
-Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.\footnote{We preprocess sentences to replace named entities with a generic Entity token.} Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.\footnote{Hierchcial clustering on cosine similarity and with Ward's method.}
+We further want to verify individual event codings, which we can do in
+the case of ICBe because each event is mapped to a specific span of
+text. We develop the iconography system for presenting event codings as
+coherent statements that can be compared side by side to the original
+source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI
+Appendix Table D1), and for every case on the companion website. We
+further provide a stratified sample of event codings alongside their
+source text (SI Appendix Table D2).
+
+We find both the visualizations of macro structure and head-to-head
+comparisons of ICBe codings to the raw text to strongly support the
+quality of ICBe, but as with recall we seek a more objective detached
+universal benchmark. Our proposed measure is a reconstruction task to
+see whether our intended ontology can be recovered through only
+unsupervised clustering of sentences they were applied to. Figure 4
+shows the location of every sentence from the ICBe corpus in semantic
+space as embeded using the same large language model as before, and the
+median location of each ICBe event tag applied to those
+sentences.\footnote{We preprocess sentences to replace named entities
+  with a generic Entity token.} Labels reflect the individual leaves of
+the ontology and colors reflect the higher level coerce branch nodes of
+the ontology. If ICBe has high precision, substantively similar tags
+ought to have been applied to substantively similar source text, which
+is what we see both in two dimensions in the main plot and via
+hierarchical clustering on all dimensions in the dendrogram along the
+righthand side.\footnote{Hierchcial clustering on cosine similarity and
+  with Ward's method.}
 
@@
 
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis.
-On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
-
-However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, (62) attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.~geolocation (63), protest events (80\%) (64), anti-government protest networks (46.1\%) (65).
-
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
-We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but ``sign formal agreement'' events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the ``reject plan, agreement to settle dispute'', but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
-Events for ``use conventional military force'' capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, ``impose embargo, boycott, or sanctions'' captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
-In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
+Finally, how does ICBe's precision compare to the existing state of the
+art? The crisis-maps reveal the episode level datasets like MIDs or the
+original ICB are too sparse and vague to reconstruct the structure of
+the crisis (SI Appendix Figure D3 and D4). On the other end of the
+spectrum, the high recall dictionary based event datasets like Terrier
+and ICEWs produce so many noisy events (several hundreds thousands) that
+even with heavy filtering their crisis maps are completely
+unintelligible. Further, because of copyright issues, none of these
+datasets directly provide the original text spans making event level
+precision difficult to verify.
+
+However, given their high recall on our task and the global and
+real-time coverage of dictionary based event systems, we want to take
+seriously the possibility that some functional transformation could
+recover the precision of ICBe. For example, (62) attempts to correct for
+the mechanically increasing amount of news coverage each year by
+detrending violent event counts from Phoenix using a human coded
+baseline. Others have focused on verifying precision for ICEWs on
+specific subsets of details against known ground truths,
+e.g.~geolocation (63), protest events (80\%) (64), anti-government
+protest networks (46.1\%) (65).
+
+We take the same approach here in Figure 5, selecting four specific
+CAMEO event codings and checking how often they reflect a true real
+world event. We choose four event types around key moments in the
+crisis. The start of the crisis revolves around Ukraine backing out of
+trade deal with the EU in favor of Russia, but ``sign formal agreement''
+events act more like a topic detector with dozens of events generated by
+discussions of a possible agreement but not the actual agreement which
+never materialized. The switch is caught by the ``reject plan, agreement
+to settle dispute'', but also continues for Victor Yanukovych for even
+after he was removed from power because of articles retroactively
+discussing the cause of his of his removal. Events for ``use
+conventional military force'' capture a threshold around the start of
+hostilities and who the participants were but not any particular battles
+or campaigns. Likewise, ``impose embargo, boycott, or sanctions''
+captures the start of waves of sanctions and from who but are
+effectively constantly as the news coverage does not distinguish between
+subtle changes or additions. In sum, dictionary based methods on news
+corpora tend to have high recall because they parse everything in the
+news, but for the same reason their specificity for most event types is
+too low to back out individual chess like sequencing that ICBe aims to
+record.
 
@@
 
-We investigated event extraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal validity (e.g.~intercoder agreement) and external validity (i.e.~matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes).
-Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.~escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
-
-\showmatmethods
-\showacknow
-\pnasbreak
+We investigated event abstraction from narratives describing key
+historical episodes in international relations. We synthesized a prior
+belief about the latent unobserved phenomena that drive these events in
+international relations and proposed a mapping to observable concepts
+that enter into the observed historical record. We designed an ontology
+with high coverage over those concepts and developed a training
+procedure and technical stack for human coding of historical texts.
+Multiple validity checks find the resulting codings have high internal
+validity (e.g.~intercoder agreement) and external validity
+(i.e.~matching source material in both micro-details at the sentence
+level and macro-details spanning full historical episodes). Further,
+these codings perform much better in terms of recall, precision,
+coverage, and overall coherence in capturing these historical episodes
+than existing event systems used in international relations.
+
+We release several open-source products along with supporting code and
+documentation to further advance the study of IR, event extraction, and
+natural language processing. The first is the International Crisis
+Behavior Events (ICBe) dataset, an event-level aggregation of what took
+place during the crises identified by the ICB project. These data are
+appropriate for statistical analysis of hard questions about the
+sequencing of events (e.g.~escalation and de-escalation of conflicts).
+Second, we provide a coder-level disaggregation with multiple codings of
+each sentence by experts and undergrads that allows for the introduction
+of uncertainty and human interpretation of events. Further, we release a
+direct mapping from the codings to the source text at the sentence level
+as a new resource for natural language processing. Finally, we provide a
+companion website that incorporates detailed visualizations of all of
+the data introduced here (www.crisisevents.org).
 
@@
 \CSLLeftMargin{1. }
-\CSLRightInline{Brecher M (1999) International studies in the twentieth century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA} presidential address.
-\emph{International Studies Quarterly} 43(2):213--264.}
+\CSLRightInline{Brecher M (1999) International studies in the twentieth
+century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA}
+presidential address. \emph{International Studies Quarterly}
+43(2):213--264.}
 
@@
 \CSLLeftMargin{2. }
-\CSLRightInline{Reiter D (2015) \href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu Rev Polit Sci} 18(1):481--499.}
+\CSLRightInline{Reiter D (2015)
+\href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We
+Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu
+Rev Polit Sci} 18(1):481--499.}
 
@@
 \CSLLeftMargin{3. }
-\CSLRightInline{Brecher M, Wilkenfeld J (1982) \href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}. \emph{World Politics} 34(3):380--417.}
+\CSLRightInline{Brecher M, Wilkenfeld J (1982)
+\href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}.
+\emph{World Politics} 34(3):380--417.}
 
@@
 \CSLLeftMargin{4. }
-\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The {International Crisis Behavior Project}.
+\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The
+{International Crisis Behavior Project}.
 doi:\href{https://doi.org/10.1093/acrefore/9780190228637.013.1638}{10.1093/acrefore/9780190228637.013.1638}.}
@@
 \CSLLeftMargin{5. }
-\CSLRightInline{Palmer G, et al.
-(2021) \href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset}, 2011--2014: {Procedures}, coding rules, and description}.
-\emph{Conflict Management and Peace Science}:0738894221995743.}
+\CSLRightInline{Palmer G, et al. (2021)
+\href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset},
+2011--2014: {Procedures}, coding rules, and description}. \emph{Conflict
+Management and Peace Science}:0738894221995743.}
 
@@
 \CSLLeftMargin{6. }
-\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts}, 1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \& Littlefield}) Available at: \url{https://books.google.com?id=_4VTDwAAQBAJ}.}
+\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts},
+1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \&
+Littlefield}) Available at:
+\url{https://books.google.com?id=_4VTDwAAQBAJ}.}
 
@@
 \CSLLeftMargin{7. }
-\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP (2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0: {Logic}, {Characteristics}, and {Comparisons} to {Alternative Datasets}}.
-\emph{Journal of Conflict Resolution} 63(3):811--835.}
+\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP
+(2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic
+Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0:
+{Logic}, {Characteristics}, and {Comparisons} to {Alternative
+Datasets}}. \emph{Journal of Conflict Resolution} 63(3):811--835.}
 
@@
 \CSLLeftMargin{8. }
-\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war: 1816-2007} ({CQ Press}).}
+\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war:
+1816-2007} ({CQ Press}).}
 
@@
 \CSLLeftMargin{9. }
-\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016) \href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at {Interstate Wars}, 1816--2007}.
-\emph{Journal of Conflict Resolution} 60(5):956--976.}
+\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016)
+\href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at
+{Interstate Wars}, 1816--2007}. \emph{Journal of Conflict Resolution}
+60(5):956--976.}
 
@@
 \CSLLeftMargin{10. }
-\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED Codebook} version 5.0} ({Department of Peace and Conflict Research, Uppsala University}).}
+\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED
+Codebook} version 5.0} ({Department of Peace and Conflict Research,
+Uppsala University}).}
 
@@
 \CSLLeftMargin{11. }
-\CSLRightInline{Pettersson T, Eck K (2018) \href{https://doi.org/10.1177/0022343318784101}{Organized violence, 1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}
+\CSLRightInline{Pettersson T, Eck K (2018)
+\href{https://doi.org/10.1177/0022343318784101}{Organized violence,
+1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}
 
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010) Introducing {ACLED}: An armed conflict location and event dataset: Special data feature. \emph{Journal of peace research} 47(5):651--660.}
+\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010)
+Introducing {ACLED}: An armed conflict location and event dataset:
+Special data feature. \emph{Journal of peace research} 47(5):651--660.}
 
@@
 \CSLLeftMargin{13. }
-\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The global sanctions data base}.
-\emph{European Economic Review} 129:103561.}
+\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov
+YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The
+global sanctions data base}. \emph{European Economic Review}
+129:103561.}
 
@@
 \CSLLeftMargin{14. }
-\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the {Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}
+\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the
+{Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}
 
@@
 \CSLLeftMargin{15. }
-\CSLRightInline{Kinne BJ (2020) \href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution} 64(4):729--755.}
+\CSLRightInline{Kinne BJ (2020)
+\href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation
+Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution}
+64(4):729--755.}
 
@@
 \CSLLeftMargin{16. }
-\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018) \href{https://doi.org/10.1177/0738894216646978}{The {International Border Agreements Dataset}}.
-\emph{Conflict Management and Peace Science} 35(5):559--576.}
+\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018)
+\href{https://doi.org/10.1177/0738894216646978}{The {International
+Border Agreements Dataset}}. \emph{Conflict Management and Peace
+Science} 35(5):559--576.}
 
@@
 \CSLLeftMargin{17. }
-\CSLRightInline{Vabulas F, Snidal D (2021) \href{https://doi.org/10.1177/0022343320943920}{Cooperation under autonomy: {Building} and analyzing the {Informal Intergovernmental Organizations} 2.0 dataset}.
-\emph{Journal of Peace Research} 58(4):859--869.}
+\CSLRightInline{Vabulas F, Snidal D (2021)
+\href{https://doi.org/10.1177/0022343320943920}{Cooperation under
+autonomy: {Building} and analyzing the {Informal Intergovernmental
+Organizations} 2.0 dataset}. \emph{Journal of Peace Research}
+58(4):859--869.}
 
@@
 \CSLLeftMargin{18. }
-\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017) \href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates} of {War Territorial Claims Data}, 1816--20011}.
-\emph{Journal of Peace Research} 54(1):99--108.}
+\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017)
+\href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates}
+of {War Territorial Claims Data}, 1816--20011}. \emph{Journal of Peace
+Research} 54(1):99--108.}
 
@@
 \CSLLeftMargin{19. }
-\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020) \href{https://doi.org/10.1177/0022343320929740}{What are the drivers of diplomacy?
-{Introducing} and testing new annual dyadic data measuring diplomatic exchange}.
-\emph{Journal of Peace Research}:0022343320929740.}
+\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020)
+\href{https://doi.org/10.1177/0022343320929740}{What are the drivers of
+diplomacy? {Introducing} and testing new annual dyadic data measuring
+diplomatic exchange}. \emph{Journal of Peace
+Research}:0022343320929740.}
 
@@
 \CSLLeftMargin{20. }
-\CSLRightInline{Sechser TS (2011) \href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent Threats}, 1918--2001}. \emph{Conflict Management and Peace Science} 28(4):377--401.}
+\CSLRightInline{Sechser TS (2011)
+\href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent
+Threats}, 1918--2001}. \emph{Conflict Management and Peace Science}
+28(4):377--401.}
 
@@
 \CSLLeftMargin{21. }
-\CSLRightInline{Li Q, et al.
-(2021) A {Comprehensive Survey} on {Schema-based Event Extraction} with {Deep Learning}.
-Available at: \url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10, 2021{]}.}
+\CSLRightInline{Li Q, et al. (2021) A {Comprehensive Survey} on
+{Schema-based Event Extraction} with {Deep Learning}. Available at:
+\url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10,
+2021{]}.}
 
@@
 \CSLLeftMargin{22. }
-\CSLRightInline{Halterman A (2020) Extracting {Political Events} from {Text Using Syntax} and {Semantics}.}
+\CSLRightInline{Halterman A (2020) Extracting {Political Events} from
+{Text Using Syntax} and {Semantics}.}
 
@@
 \CSLLeftMargin{23. }
-\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018) Phoenix {Real-Time Event Data}. Available at: \url{http://eventdata.utdallas.edu}.}
+\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018)
+Phoenix {Real-Time Event Data}. Available at:
+\url{http://eventdata.utdallas.edu}.}
 
@@
 \CSLLeftMargin{24. }
-\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data. \emph{Harvard Dataverse} 12.}
+\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data.
+\emph{Harvard Dataverse} 12.}
 
@@
 \CSLLeftMargin{25. }
-\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing the {UCDP Candidate Events Dataset}. \emph{Research \& Politics} 7(3):2053168020935257.}
+\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing
+the {UCDP Candidate Events Dataset}. \emph{Research \& Politics}
+7(3):2053168020935257.}
 
@@
 \CSLLeftMargin{26. }
-\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017) {OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/} {[}Accessed September 1, 2021{]}.}
+\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017)
+{OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/}
+{[}Accessed September 1, 2021{]}.}
 
@@
 \CSLLeftMargin{27. }
-\CSLRightInline{Zhang H, Pan J (2019) \href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning Approach} for {Identifying Collective Action Events} with {Text} and {Image Data} from {Social Media}}.
-\emph{Sociological Methodology} 49(1):1--57.}
+\CSLRightInline{Zhang H, Pan J (2019)
+\href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning
+Approach} for {Identifying Collective Action Events} with {Text} and
+{Image Data} from {Social Media}}. \emph{Sociological Methodology}
+49(1):1--57.}
 
@@
 \CSLLeftMargin{28. }
-\CSLRightInline{Steinert-Threlkeld ZC (2019) \href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}
+\CSLRightInline{Steinert-Threlkeld ZC (2019)
+\href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event
+Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}
 
@@
 \CSLLeftMargin{29. }
-\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis escalation to war: {Findings} from the {International Crisis Behavior Project}. \emph{What Do We Know About War}.}
+\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis
+escalation to war: {Findings} from the {International Crisis Behavior
+Project}. \emph{What Do We Know About War}.}
 
@@
 \CSLLeftMargin{30. }
-\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and violence: Twentieth-century findings. \emph{Handbook of war studies II}:282--300.}
+\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and
+violence: Twentieth-century findings. \emph{Handbook of war studies
+II}:282--300.}
 
@@
 \CSLLeftMargin{31. }
-\CSLRightInline{James P (2019) \href{https://doi.org/10.1177/0738894218793135}{What do we know about crisis, escalation and war?
-{A} visual assessment of the {International Crisis Behavior Project}}.
-\emph{Conflict Management and Peace Science} 36(1):3--19.}
+\CSLRightInline{James P (2019)
+\href{https://doi.org/10.1177/0738894218793135}{What do we know about
+crisis, escalation and war? {A} visual assessment of the {International
+Crisis Behavior Project}}. \emph{Conflict Management and Peace Science}
+36(1):3--19.}
 
@@
 \CSLLeftMargin{32. }
-\CSLRightInline{Iakhnis E, James P (2019) \href{https://doi.org/10.1177/0738894219855610}{Near crises in world politics: {A} new dataset}.
-\emph{Conflict Management and Peace Science}:0738894219855610.}
+\CSLRightInline{Iakhnis E, James P (2019)
+\href{https://doi.org/10.1177/0738894219855610}{Near crises in world
+politics: {A} new dataset}. \emph{Conflict Management and Peace
+Science}:0738894219855610.}
 
@@
 \CSLLeftMargin{33. }
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D (2017) \emph{International {Crisis Behavior Data Codebook}} Available at: \url{http://sites.duke.edu/icbdata/data-collections/}.}
+\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D
+(2017) \emph{International {Crisis Behavior Data Codebook}} Available
+at: \url{http://sites.duke.edu/icbdata/data-collections/}.}
 
@@
 \CSLLeftMargin{34. }
-\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of {Crisis}} ({University of Michigan Press}).}
+\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of
+{Crisis}} ({University of Michigan Press}).}
 
@@
 \CSLLeftMargin{35. }
-\CSLRightInline{Holsti OR (1965) \href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The American Political Science Review} 59(2):365--378.}
+\CSLRightInline{Holsti OR (1965)
+\href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The
+American Political Science Review} 59(2):365--378.}
 
@@
 \CSLLeftMargin{36. }
-\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June} 24-30, 1950} ({Free Press}).}
+\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June}
+24-30, 1950} ({Free Press}).}
 
@@
 \CSLLeftMargin{37. }
-\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision: {Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}
+\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision:
+{Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}
 
@@
 \CSLLeftMargin{38. }
-\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among nations: {Bargaining} and decision making in international crises} ({Princeton University Press}).}
+\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among
+nations: {Bargaining} and decision making in international crises}
+({Princeton University Press}).}
 
@@
 \CSLLeftMargin{39. }
-\CSLRightInline{Gavin FJ (2014) \href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies} 37(2):319--331.}
+\CSLRightInline{Gavin FJ (2014)
+\href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security
+Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies}
+37(2):319--331.}
 
@@
 \CSLLeftMargin{40. }
-\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American} foreign policy: {Theory} and practice} ({Columbia University Press}).}
+\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American}
+foreign policy: {Theory} and practice} ({Columbia University Press}).}
 
@@
 \CSLLeftMargin{41. }
-\CSLRightInline{Gaddis JL (1987) \href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}: {Historians}, {Political Scientists}, and the {Enrichment} of {Security Studies}}.
-\emph{International Security} 12(1):3--21.}
+\CSLRightInline{Gaddis JL (1987)
+\href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}:
+{Historians}, {Political Scientists}, and the {Enrichment} of {Security
+Studies}}. \emph{International Security} 12(1):3--21.}
 
@@
 \CSLLeftMargin{42. }
-\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management. \emph{Journal of Conflict Resolution} 32(3):426--456.}
+\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management.
+\emph{Journal of Conflict Resolution} 32(3):426--456.}
 
@@
 \CSLLeftMargin{43. }
-\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of {Asian} security: {Using Europe} to study {Asia}. \emph{Journal of Global Security Studies} 4(3):393--401.}
+\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of
+{Asian} security: {Using Europe} to study {Asia}. \emph{Journal of
+Global Security Studies} 4(3):393--401.}
 
@@
 \CSLLeftMargin{44. }
-\CSLRightInline{Hewitt JJ (2001) \href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to {Teach Conflict} and {Crisis Analysis}}.
-\emph{Int Stud Perspect} 2(4):371--383.}
+\CSLRightInline{Hewitt JJ (2001)
+\href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International
+Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to
+{Teach Conflict} and {Crisis Analysis}}. \emph{Int Stud Perspect}
+2(4):371--383.}
 
@@
 \CSLLeftMargin{45. }
-\CSLRightInline{Miller GA (1995) \href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical database for {English}}. \emph{Commun ACM} 38(11):39--41.}
+\CSLRightInline{Miller GA (1995)
+\href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical
+database for {English}}. \emph{Commun ACM} 38(11):39--41.}
 
@@
 \CSLLeftMargin{46. }
-\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA (2019) Cline {Center Historical Phoenix Event Data Variable Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}
+\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA
+(2019) Cline {Center Historical Phoenix Event Data Variable
+Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}
 
@@
 \CSLLeftMargin{47. }
-\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP} georeferenced event dataset. \emph{Journal of Peace Research} 50(4):523--532.}
+\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP}
+georeferenced event dataset. \emph{Journal of Peace Research}
+50(4):523--532.}
 
@@
 \CSLLeftMargin{48. }
-\CSLRightInline{Leng RJ, Singer JD (1988) \href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}: {The BCOW Typology} and {Its Applications}}.
-\emph{International Studies Quarterly} 32(2):155--173.}
+\CSLRightInline{Leng RJ, Singer JD (1988)
+\href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}:
+{The BCOW Typology} and {Its Applications}}. \emph{International Studies
+Quarterly} 32(2):155--173.}
 
@@
 \CSLLeftMargin{49. }
-\CSLRightInline{McClelland C (1978) World event/interaction survey, 1966-1978. \emph{WEIS Codebook ICPSR} 5211.}
+\CSLRightInline{McClelland C (1978) World event/interaction survey,
+1966-1978. \emph{WEIS Codebook ICPSR} 5211.}
 
@@
 \CSLLeftMargin{50. }
-\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events} of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968: {Version} 1.
+\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events}
+of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968:
+{Version} 1.
 doi:\href{https://doi.org/10.3886/ICPSR05205.V1}{10.3886/ICPSR05205.V1}.}
@@
 \CSLLeftMargin{51. }
-\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}: {Computer-aided} system for analysis of local conflicts. \emph{MIT Center for International Studies, Cambridge}.}
+\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}:
+{Computer-aided} system for analysis of local conflicts. \emph{MIT
+Center for International Studies, Cambridge}.}
 
@@
 \CSLLeftMargin{52. }
-\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm}, {Hierarchical}, and {Contextually-Sensitive International Conflict Dataset}, 1937-1985: {Version} 1.
+\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm},
+{Hierarchical}, and {Contextually-Sensitive International Conflict
+Dataset}, 1937-1985: {Version} 1.
 doi:\href{https://doi.org/10.3886/ICPSR02292.V1}{10.3886/ICPSR02292.V1}.}
@@
 \CSLLeftMargin{53. }
-\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A Comprehensive Ontology} for {Event Extraction} from text.
+\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A
+Comprehensive Ontology} for {Event Extraction} from text.
 doi:\href{https://doi.org/10.48550/arXiv.2107.10326}{10.48550/arXiv.2107.10326}.}
@@
 \CSLLeftMargin{54. }
-\CSLRightInline{Merritt RL (1994) Measuring events for international political analysis. \emph{International Interactions} 20(1-2):3--33.}
+\CSLRightInline{Merritt RL (1994) Measuring events for international
+political analysis. \emph{International Interactions} 20(1-2):3--33.}
 
@@
 \CSLLeftMargin{55. }
-\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas} event data system project. \emph{The political methodologist} 14(1):2--8.}
+\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas}
+event data system project. \emph{The political methodologist}
+14(1):2--8.}
 
@@
 \CSLLeftMargin{56. }
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D International {Crisis Behavior Data Codebook}, {Version} 12. 69.}
+\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D
+International {Crisis Behavior Data Codebook}, {Version} 12. 69.}
 
@@
 \CSLLeftMargin{57. }
-\CSLRightInline{Braithwaite A (2010) \href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing} the {Militarized Interstate Dispute Location} dataset}.
-\emph{Journal of Peace Research} 47(1):91--98.}
+\CSLRightInline{Braithwaite A (2010)
+\href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing}
+the {Militarized Interstate Dispute Location} dataset}. \emph{Journal of
+Peace Research} 47(1):91--98.}
 
@@
 \CSLLeftMargin{58. }
-\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University College London}.}
+\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized
+Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University
+College London}.}
 
@@
 \CSLLeftMargin{59. }
-\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain knowledge: Using hierarchies to improve deep classifiers.
-Available at: \url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}
+\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain
+knowledge: Using hierarchies to improve deep classifiers. Available at:
+\url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}
 
@@
 \CSLLeftMargin{60. }
-\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of nature} ({Freeman}, {New York}).}
+\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of
+nature} ({Freeman}, {New York}).}
 
@@
 \CSLLeftMargin{61. }
-\CSLRightInline{Cormac R, Aldrich RJ (2018) \href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert action and implausible deniability}. \emph{International Affairs} 94(3):477--494.}
+\CSLRightInline{Cormac R, Aldrich RJ (2018)
+\href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert
+action and implausible deniability}. \emph{International Affairs}
+94(3):477--494.}
 
@@
 \CSLLeftMargin{62. }
-\CSLRightInline{Terechshenko Z (2020) \href{https://doi.org/10.1177/0022343320962546}{Hot under the collar: {A} latent measure of interstate hostility}.
-\emph{Journal of Peace Research} 57(6):764--776.}
+\CSLRightInline{Terechshenko Z (2020)
+\href{https://doi.org/10.1177/0022343320962546}{Hot under the collar:
+{A} latent measure of interstate hostility}. \emph{Journal of Peace
+Research} 57(6):764--776.}
 
@@
 \CSLLeftMargin{63. }
-\CSLRightInline{Cook SJ, Weidmann NB (2019) \href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}: {Improving Event Analysis} with {Report-Level Data}}.
-\emph{American Journal of Political Science} 63(1):250--264.}
+\CSLRightInline{Cook SJ, Weidmann NB (2019)
+\href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}:
+{Improving Event Analysis} with {Report-Level Data}}. \emph{American
+Journal of Political Science} 63(1):250--264.}
 
@@
 \CSLLeftMargin{64. }
-\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of protest event analysis. \emph{Contention in times of crisis: Recession and political protest in thirty Euro-pean countries}:49--78.}
+\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of
+protest event analysis. \emph{Contention in times of crisis: Recession
+and political protest in thirty Euro-pean countries}:49--78.}
 
@@
 \CSLLeftMargin{65. }
-\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event Data}: {Evidence} from the {ICEWS Dataset}.}
+\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event
+Data}: {Evidence} from the {ICEWS Dataset}.}
 
@@
 
-% Bibliography
-% \bibliography{pnas-sample}
+\bibliographystyle{unsrt}
+\bibliography{paper.bib}
 

### 2022-07-25 replication_paper/pnas_draft/appendix.Rmd
arxiv draft

@@
 output: 
-  bookdown::pdf_book:
+  pdf_document:
     toc: yes
     latex_engine: xelatex
+    keep_tex:  true
 
@@
 # - \usepackage{tinytex}
+  - \usepackage[backend=bibtex]{biblatex} #if I comment it out and don't have it'll throw an error
+#  - \usepackage{natbib} #added for latex citation within huxtable
   - \usepackage[utf8]{inputenc}
@@
   - \usepackage{ctable} # added for demo
-  - \usepackage{natbib} #added for latex citation within huxtable
+
   - \usepackage{booktabs}
@@
 
+options(tinytex.clean=F)
+
 library(reticulate)
@@
 ```
-
+\clearpage
 # Appendix A Corpus and Cases
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft1.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft1.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft2.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft2.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft3.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft3.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft4.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft4.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft5.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft5.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft6.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft6.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft7.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft7.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft8.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft8.png"), zoom=1)
 
@@
 \caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft1.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft1.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft2.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft2.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft3.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft3.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft4.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft4.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft5.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft5.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft6.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft6.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft7.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft7.png"}}
 \end{figure}
@@
 \begin{figure}[H]
-\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft8.png"}}
+\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft8.png"}}
 \end{figure}
@@
 \caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
-\centering{\includegraphics[width=17cm]{../figures/gui_example}}
+\centering{\includegraphics[width=17cm]{./gui_example}}
 \end{figure}
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_concept.png'), 
                   plot = p_percent_chose_tag_by_concept, width=8, height=8)
@@
 \caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
-\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_concept.png}}
+\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_concept.png}}
 \end{figure}
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_confidence.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_confidence.png'), 
                   plot = p_percent_chose_tag_by_confidence, width=8, height=6)
@@
 \caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
-\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_confidence.png}}
+\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_confidence.png}}
 \end{figure}
+
+\clearpage
 
@@
 \end{algorithm}
+
+\clearpage
 
@@
 
-ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-## Table C3: Synthetic Narrative Matches Crimea-Donbas
-\hphantom{em}
+\clearpage
 
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
-\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part1.png}}
+\centering{\includegraphics[height=21cm]{./case_study_crimea_precision_part1.png}}
 \end{figure}
@@
 
-ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision1.png"), zoom=1) #
+ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision1.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision2.png"), zoom=1) #
+ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision2.png"), zoom=1) #
 
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision2.png"}}
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision2.png"}}
 \end{figure}
@@
     print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/figures/p_icb_metro_plot_",thiscrisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_icb_metro_plot_",thiscrisis,".Rds")
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/figures/p_mids_metro_plot_",thiscrisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_mids_metro_plot_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_phoenix_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_terrier_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/figures/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/figures/p_icews_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
 
@@
 ## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.Rds') 
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
   ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_penta_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_196.Rds')
 subtitle="Phoenix Dyadic Events"
@@
     )
-#ggsave(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_196_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_196_combined.png'),
           p_196_combined, base_height = 12, base_width = 20)
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_196.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_196.png'),
+  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_196.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_196.png'),
             p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_mids_metro_plot_471.Rds') 
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_471.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_471.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_penta_471.Rds')
 subtitle="Terrier Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_penta_471.Rds')
 p_471_icews <- readRDS(save_file)
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_471_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_471_combined.png'),
           p_471_combined, base_height = 12, base_width = 25)
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_phoenix_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_phoenix_plot_lv0_471.png'),
+  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_471.png'),
             p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_terrier_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_terrier_plot_lv0_471.png'),
+  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_terrier_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_lv0_471.png'),
             p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "figures", "p_icews_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/figures/p_icews_plot_lv0_471.png'),
+  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_icews_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_lv0_471.png'),
             p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)

### 2022-07-25 replication_paper/pnas_draft/appendix.Rmd
path update

--- 2022-07-22 replication_paper/pnas_draft/appendix.Rmd
@@
 #use_python("/home/skynet3/anaconda3/bin/python/")
-#reticulate::use_python("/home/tlscherer/anaconda3/bin/python")
+#reticulate::use_python("~/anaconda3/bin/python3.6") # never worked for me
+#reticulate::use_python("~/.local/share/r-miniconda/envs/r-reticulate/bin/python3.6") #works but needed module install
+#conda_install("r-reticulate", "pytorch")
 
@@
 
+fromscratch=False
+
+if fromscratch:
   import torch
@@
       print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)    
-
   import random
@@
   raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
-                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value_normalized) %>% distinct()
+                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value) %>% distinct()
 

### 2022-07-25 replication_paper/pnas_draft/paper.Rmd

--- 2022-07-23 replication_paper/pnas_draft/paper.Rmd
@@
 #https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
-output: 
-  bookdown::pdf_book:
-    toc: no
-    base_format: rticles::pnas_article
-    latex_engine: xelatex
+#https://stackoverflow.com/questions/64700865/using-r-rstudio-knit-to-pdf-how-to-pass-custom-flags-to-the-pdflatex-command
+
+bibliography: arxiv.bib
+biblio-style: unsrt
+output: rticles::arxiv_article
 
@@
 ```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
+print(wd())
 #International Crisis Behavior Events (ICBe) Dataset
 knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
+
+#Execute these lines to get bbl files for the arxiv submission
+options(tinytex.clean=F)
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_recall.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'),
        plot = p_recall ,
@@
 tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))
+tiger2 <- image_read(paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'))
 
@@
 
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
+p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/pnas_draft/crisismaps/p_metro_plot_471.Rds')) +
     labs(
@@
 
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
+p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/pnas_draft/crisismaps/p_metro_plot_471.Rds')) +
     labs(
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = 24)
+ratio=1.5
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_precision_combined.png'),
+          p_precision_combined, base_height = 18, base_width = height*ratio)
 
@@
 \caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=24cm]{../figures/p_precision_combined.png}}
+\centering{\includegraphics[width=24cm]{./p_precision_combined.png}}
 \end{sidewaysfigure}
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
 
@@
 save_plot(file=paste0(here::here(),
-                      '/replication_paper/figures/p_precision_icews.png'),
+                      '/replication_paper/pnas_draft/p_precision_icews.png'),
           p_ICEWS, base_height = 10, base_width = 14)

### 2022-07-25 replication_paper/pnas_draft/paper.qmd

--- 2022-07-23 replication_paper/pnas_draft/paper.Rmd
@@
 ## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
-pnas_type: pnasresearcharticle
+#pnas_type: pnasresearcharticle
 
 bibliography: ICBintro.bib
-csl: pnas.csl
+#csl: pnas.csl
 
@@
 #https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
-output: 
-  bookdown::pdf_book:
-    toc: no
-    base_format: rticles::pnas_article
+format:
+  pdf: 
     latex_engine: xelatex
+    citation_package: biblatex
+    keep-tex: true
+    latex-clean: false
+    cite-method: biblatex
 
-#Disabled several the caused errors
-header-includes:
-  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
-#  - \usepackage{tinytex}
-  - \usepackage[utf8]{inputenc}
-  - \usepackage{pifont}
-  - \usepackage{newunicodechar}
-  - \newunicodechar{✓}{\ding{51}}
-  - \newunicodechar{✗}{\ding{55}}
-  - \usepackage{array}
-  - \usepackage{ctable} # added for demo
-  - \usepackage{natbib} #added for latex citation within huxtable
-  - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage{wrapfig}
-  - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{titlesec}
-  - \usepackage[parfill]{parskip}
-  - \usepackage{makecell}
-  - \usepackage{graphicx}
-#  - \usepackage{caption}
-#  - \usepackage[capposition=top]{floatrow}
-#  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
-#  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
-#  - \DeclareUnicodeCharacter{00A0}{ }
-  - \usepackage{setspace}
-  - \usepackage{cellspace}
-  - \setlength\cellspacetoplimit{0.8ex}
-  - \renewcommand{\arraystretch}{0.8}
-  - \AtBeginEnvironment{tabular}{\singlespacing}
-  - \AtBeginEnvironment{lltable}{\singlespacing}
-#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-#  - \usepackage{subfigure}
-  - \usepackage{subcaption}
-  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
-  - \usepackage{float}
-#  - \usepackage{eso-pic,graphicx,transparent}
-#  - \usepackage[perpage]{footmisc}
-  - \usepackage[algo2e]{algorithm2e}
-#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
 ---
-
-```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
-#International Crisis Behavior Events (ICBe) Dataset
-knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
-
-```
-
-```{r, eval=T, echo=F, cache=F}
-
-#library(pacman)
-library(googlesheets4)
-library(tidyverse)
-library(janitor)
-library(flextable)
-set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`.
-You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
-library(ftExtra)
-options(tidyverse.quiet = TRUE)
-options(gargle_oauth_email = TRUE)
-
-#install.packages('stargazer')
-#install.packages('kableExtra')
-#! sh: 1: pdflatex: not found
-#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended
-
-#! LaTeX Error: File `letltxmacro.sty' not found.
-#sudo apt-get install texlive-latex-extra
-
-#install.packages('tinytex')
-#tinytex::install_tinytex()
-
-```
-
-```{r, echo=F}
-#Notes
-#https://tex.stackexchange.com/questions/83440/inputenc-error-unicode-char-u8-not-set-up-for-use-with-latex
-#- \DeclareUnicodeCharacter{00A0}{ }
-
-```
-
-```{r, include=FALSE}
-# options(tinytex.verbose = TRUE)
-```
-
-```{r, echo=FALSE}
-
-`%>%` <- magrittr::`%>%`
-
-```
-
-```{r, echo=FALSE}
-
-icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds"))
-codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )
-
-ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
-dim(ICBe_events_agreed)
-icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
-dim(icb_events_long)
-
-#oh is it because break is reserved in R? lol
-#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
-icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
-
-#somehow break of all things is a b roken name
-#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
-icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))
-
-```
-
-<!-- note: please start your introduction without including the word "Introduction" as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.
--->
-
-If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
-In other words, what is the entropy of international relations?
-This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
-On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations.
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherCrisisEscalationWar2000; @wilkenfeldInterstateCrisesViolence2000; @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019].
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
-We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
-The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision.
-A final section concludes.
-
-Task Definition {.unnumbered}
-========================================
-
-We consider the measurement task of abstracting discrete events about a historical episode in international relations.
-The easiest way to convey the task is with an example.
-Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine readable abstractive events.
-Formally, a historical episode, $H$, is demarcated by a period of time $[T_{start}, T_{end}] \in T$, a set of Players $p \in P$, and a set of behaviors they undertook during that time $b \in B$.
-International Relations, $IR$, is the system of regularities that govern the strategic interactions that world actors make during a historical episode, given their available options, preferences, beliefs, and expectations of choices made by others.
-We observe neither $H$ nor $IR$ directly.
-Rather the Historical Record, $HR$, produces documents $d \in D$ containing some relevant and true (as well as irrelevant and untrue) information about behaviors that were undertaken recorded in the form of unstructured natural language text.
-The task is to combine informative priors about $IR$ with an unstructured corpus $D$ to produce a series of structured discrete events, $e \in E$, that have high coverage, precision, and recall over what actually took place in history, $H$.
-
-```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
-ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
-
-temp <- ICBe_events_agreed_markdown %>%
-        filter(crisno==196) %>%
-        group_by(crisno, sentence_number_int_aligned) %>%
-          filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
-        ungroup() %>%
-        mutate(banding=sentence_number_int_aligned %% 2)
-temp$is_subsstring <- NA
-for(i in 1:nrow(temp)){
-  temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
-                                                                                pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
-                                                                              ) %>% replace_na(0) %>%  sum()
-}
-temp <-temp %>%
-        mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
-        group_by(sentence_number_int_aligned) %>%
-          filter(value_markdown!='' | length(value_markdown)==1) %>%
-        ungroup() %>%
-        mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
-        mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
-        mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
-      #head(100) %>%
-ft_cuba_precision <- temp %>%
-                     dplyr::select(S=sentence_number_int_aligned, ICB=sentence_span_text, ICBe=value_markdown)  %>%
-                      flextable::as_flextable() %>%
-        flextable::set_header_labels(values =
-        list(
-              S = "S",
-              ICB = "Natural Language Sentences (ICB Corpus)",
-              ICBe = "Machine Readable Events (ICBe)"
-             ) ) %>%
-
-                      flextable::width( j = 1, width=0.25)  %>% 
-                      #flextable::width( j = 2, width=0.25)  %>% 
-                      flextable::width( j = 2, width=8.0)  %>% 
-                      flextable::width( j = 3, width=8.0)  %>% 
-                      flextable::fontsize(size = 9, part = "all") %>%
-                      valign(j = 1:3, valign = "top", part = "body") %>%
-                      flextable::line_spacing( space = 1.0, part = "all") %>% 
-                      padding( padding = 1, part = "all") %>% 
-                      bg( i = which( temp$banding==1 ) , part = "body", bg = "#EFEFEF", j=1:3) %>%
-                      ftExtra::colformat_md(j = 3, part="body")
-#ft_cuba_precision
-
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
-temp <- NULL
-
-```
-
-<!--- REX Remember to put in a Legend for the Icons ---->
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=22cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-\twocolumn
-
-Corpus  {.unnumbered}
-========================================
-
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
-59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art {.unnumbered}
-========================================
-
-Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors, and provide a full codebook in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).
-
-The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Additional relevant but dated or too small of an overlap in domain include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
-With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See [@balaliCOfEEComprehensiveOntology2021] for a recent review of ontological depth and availability of Gold Standard example text.]
-
-\clearpage
-\onecolumn
-
-```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
-#lit_review_pull    <- readxl::read_excel(target_file, sheet="DatasetsComparisonLitReview")
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-lit_review_pull <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/14RHRKgQGHj7Zr4_xt4fq2bIE7mDNayLKj89tYmOOfHQ/edit?usp=sharing", 
-                                sheet="DatasetsComparisonLitReview") #%>% janitor::clean_names() 
-dim(lit_review_pull)
-
-library(flextable)
-library(ftExtra)
-library(tidyverse)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-
-#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
-# NOTE: If one of the citations is degenerate this will throw an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
-set_flextable_defaults(fonts_ignore=TRUE)
-
-lit_review_alt <- lit_review_pull %>% 
-                  mutate(Literature =   paste0(" [",Literature %>% str_replace("; {0,}$","") ,"]")) %>%
-                  mutate(Concept= Concept %>% paste0(Literature)) %>%
-                  mutate(Concept = Concept %>% str_replace(fixed("[NA]"),"") ) %>%
-                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
-                  #dplyr::filter(is.na(group))
-
-n=nrow(lit_review_alt)
-k=ncol(lit_review_alt)
-horizontal = c(1,k)
-r_intro= lit_review_pull$...1 %in% "Domain" %>% sum() #changed to domain
-r_players= ( lit_review_pull$...1 %in% "Players" %>% sum() ) + r_intro
-r_pieces= ( lit_review_pull$...1 %in% "Pieces" %>% sum() ) + r_players
-r_think= ( lit_review_pull$...1 %in% "Think" %>% sum() ) + r_pieces
-r_say= ( lit_review_pull$...1 %in% "Say" %>% sum() ) + r_think
-r_unarmed= ( lit_review_pull$...2 %in% "Unarmed" %>% sum() ) + r_say
-r_armed= ( lit_review_pull$...2 %in% "Armed" %>% sum() ) + r_unarmed
-ft <- NULL
-
-library(officer)
-big_border = fp_border(color="black", width = 2)
-
-bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
-litreview_ft_pnas <- lit_review_alt %>%
-      flextable::as_flextable() %>%
-
-      #add_header( 
-      #        #"ICB Corpus"="Corpus",
-      #        "ICBe"="Ours",
-      #        "Phoenix"="CAMEO Dictionary\nSystems",
-      #        "Terrier"="CAMEO Dictionary\nSystems",
-      #        "ICEWs"="CAMEO Dictionary\nSystems",
-      #        "MIDs Events"="Disputes",
-      #        "UCDP-GED"="Violence",
-      #        "ICB"="Crises",
-      #        "COW"="Wars",
-      #        "MIDs"="Disputes",
-      #        top = T ) %>%
-
-      add_header( 
-                  #"ICB Corpus"="Corpus",
-                  "ICBe"="Events Datasets",
-                  "Phoenix"="Events Datasets",
-                  "Terrier"="Events Datasets",
-                  "ICEWs"="Events Datasets",
-                  "MIDs Incidents"="Events Datasets",
-                  "UCDP-GED"="Events Datasets",
-                  "ICB"="Episodes Datasets",
-                  "COW"="Episodes Datasets",
-                  "MIDs"="Episodes Datasets",
-                  top = T ) %>%
-
-      set_header_labels(
-        values = list("...1" = "" , "...2" = "" ) 
-        ) %>%
-
-      merge_h(part = "header") %>% #it's this merge that's killing us
-
-      #Global Borders
-      flextable::border_remove() %>% 
-      #ok so because of our horizontal merging of headers, we have to manually place a right bar at j=10 2 short of the full width
-      flextable::border_outer( part="all", border = big_border ) %>% #this will have a gap
-      border(j=10:k, i=1 , part="header", border.right = big_border ) %>% #this fills the gap
-      #There's another gap on the bottom left
-      border(j=1, i=(n-15):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
-      border(j=2, i=(n-5):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
-
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #Banding
-      bg( i = bands  , j=3:k, part = "body", bg = "#EFEFEF") %>%
-
-      flextable::rotate(i=2, , j=3:k, rotation="tbrl",part="header") %>%
-      flextable::align(align = "center", part = "body") %>%
-      flextable::align(align = "center", part = "header")   %>%
-
-      flextable::colformat_char(
-          j = 1:ncol(lit_review_alt),
-          na_str = "",
-          prefix = "",
-          suffix = ""
-      ) %>%
-      #Domains
-      hline(i=c(r_intro), border = NULL, part = "body") %>% 
-      merge_at(i = 1:r_intro, j = 1:2, part = "body") %>%  
-      merge_at(i = 4, j = 5:7, part = "body") %>%
-      merge_at(i = 5, j = 5:7, part = "body") %>%
-      merge_at(i = 6, j = 5:7, part = "body") %>%
-      merge_at(i = 7, j = 5:7, part = "body") %>%
-
-      #players
-      hline(i=c(r_players), border = NULL, part = "body") %>% 
-      merge_at(i = (r_intro+1):r_players, j = 1:2, part = "body") %>%  
-      #pieces
-      hline(i=c(r_pieces), border = NULL, part = "body") %>% 
-      merge_at(i = (r_players+1):r_pieces, j = 1:2, part = "body") %>%  
-      #think
-      hline(i=c(r_think), border = NULL, part = "body") %>% 
-      merge_at(i = (r_pieces+1):r_think, j = 1:2, part = "body") %>%  
-      #say
-      hline(i=c(r_say), border = NULL, part = "body") %>% 
-      merge_at(i = (r_think+1):r_say, j = 1:2, part = "body") %>%
-      #Do
-      merge_at(i = (r_say+1):r_armed, j = 1, part = "body") %>%
-
-      #n_unarmed
-      hline(i=c(r_unarmed), border = NULL, part = "body") %>% 
-      merge_at(i = (r_say+1):r_unarmed, j = 2, part = "body") %>%  
-      #n_armed
-      #hline(i=c(r_armed), border = NULL, part = "body") %>% 
-      merge_at(i = (r_unarmed+1):r_armed, j = 2, part = "body") %>%
-
-      #set_table_properties(layout="autofit")  %>%
-      vline( i = 1:2, j = c(3,9), border = NULL, part = "header") %>%
-      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
-      vline( i = 1:(n), j = c(3,9), border = NULL, part = "body")  %>%
-
-      flextable::width( j = 3, width=3) %>% 
-      flextable::width( j = (4):k, width=0.25) %>%
-      flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-
-      flextable::rotate(j=1, rotation="tbrl",part="all") %>%
-      flextable::rotate(j=2, rotation="tbrl",part="all") %>%
-      flextable::width( j = 1:2, width=0.1)  %>%
-      ftExtra::colformat_md(j = 3, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
-
-#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
-#litreview_ft_pnas
-
-#litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
-litreview_ft_pnas %>% 
-  ftExtra::colformat_md(j = 3, part="body") %>%
-  flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
-  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
-  flextable::flextable_to_rmd()
-
-```
-
-\clearpage
-\twocolumn
-
-```{r , eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
-n_crisis <- ICBe_events_agreed %>% dplyr::select(crisno) %>% unique() %>% nrow()
-n_sentences <- ICBe_events_agreed %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
-#n_events <- ICBe_events_agreed %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
-#n_events_cuba <- ICBe_events_agreed %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
-n_coders <- icb_long_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()
-
-avg_coders_per_crisis <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_coders_per_sentence <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-```
-
-ICBe Coding Process {.unnumbered}
-========================================
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-B1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.
-force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
-an offer for the U.S.S.R.
-to remove missiles from Cuba in exchange for the U.S.
-removing missiles from Turkey.
-Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-
-Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.^[Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
-We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
-This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
-
-```{r}
-#We calculate means in the SI appendix on agreement
-means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
-                   group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                   dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)
-
-means_group_keep <- codings_long_agreement %>% filter(value_normalized!='') %>% 
-                    filter(algo1==1) %>%
-                    group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                    dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean)
-```
-
-Internal Consistency {.unnumbered}
-========================================
-
-We evaluate the internal validity of the coding process in several ways.
-For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig.
-B3).
-Across all concepts, the Top 1 Tag Agreement was low among novices (`r means_group_any$Novices %>% round(2) %>% scales::percent()`), moderate for experts (`r means_group_any$Experts %>% round(2) %>% scales::percent()`), and high (`r means_group_keep$Experts_keep %>% round(2) %>% scales::percent()`) following the consensus screening procedure.
-
-We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to be low for 20% of sentences- half due to a mismatch between the ontology and the text ("survey doesn't fit event"-45%) and half due to a lack of information or confused writing in the source text ("more knowledge needed"-40%, "confusing sentence"-6%).
-Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig.
-B4).
-Second, as intended agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50%-60%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.
-some more expressive applying many tags per concept while others focused on only the single best match.
-We further observed unintended synonymity, e.g.
-the same information can be framed as either a threat to do something or a promise not to do something.
-
-Case Study Selection {.unnumbered}
-========================================
-
-The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website.
-In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
-
-Recall {.unnumbered}
-========================================
-
-Recall measures the share of desired information recovered by a sequence of coded events, $Pr(E|H)$, and is poorly defined for historical episodes.
-First, there is no genuine ground truth about what occurred, only surviving texts about it.
-Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events.
-The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
-We need a yardstick for history.
-
-Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative.
-For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
-Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts.
-The more accounts that mention a detail, the more central it is to understanding the true historical episode.
-The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing.
-With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
-Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
-
-Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts.
-First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative.
-Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details.
-Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
-the U.S.
-was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
-a long term lease on naval facilities in Crimea.
-Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode level datasets have very low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
-
-```{r cuban case study recall, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#
-#Lit review
-#child=c('ICBEdataset_paper_litreviewtable.Rmd')
-library(tidyverse)
-library(flextable)
-library(ftExtra)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-case_study_cuban <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names() 
-dim(case_study_cuban)
-#case_study_cuban$date <- case_study_cuban$date %>% lapply(FUN=function(x) { ifelse(is.null(x), "", x[[1]] %>% as.character() )   }   ) %>% unlist() %>% as.Date()
-
-paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")
-
-#Replace emoticons with images
-replace_emoticons <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
-        #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-        #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
-        #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
-        #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
-}
-
-temp1 <- case_study_cuban %>% 
-                #filter(!is.na(date)) %>%
-                #head(2) %>%
-                mutate(date=date %>% anytime::anydate()) %>%
-                mutate(year=year(date) %>% as.character() ) %>%
-                mutate(month=month(date) %>% as.character()) %>%
-                mutate(day=day(date) %>% as.character()) %>%
-                mutate(documents = documents %>% as.numeric()) %>%
-                mutate(Rank=rank(-documents, ties.method="first")  ) %>%
-                dplyr::select(Y=year,M=month, D=day, Rank, Event=event, Docs=documents, icb_narrative=icb_narrative, ICBe=ic_be, ICB=icb, MIDs=mids, phoenix=phoenix) %>% 
-                mutate(Event= Event %>%  replace_emoticons) %>% 
-                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
-                mutate(ICB = ifelse(!is.na(ICB) & !ICB %in% 0, "✓", NA)) %>%
-                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0, "✓", NA)) %>%
-                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0, "✓", NA)) %>%
-                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0, "✓", NA)) %>%
-
-                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
-                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
-                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
-                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
-                mutate(YMD=paste(Y,
-                                 M %>% str_pad(2, pad = "0") ,
-                                 D %>% str_pad(2, pad = "0"), 
-                                 sep="-") %>% trimws() %>%
-                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
-                                 str_replace_all("^NA-","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-","") 
-                       ) %>%
-                dplyr::select(-Y,-M,-D) %>%
-                relocate(YMD, .before = Rank) %>%
-                dplyr::select(-Rank)
-dim(temp1)
-
-#banding <- temp %>% mutate(date=as.Date(paste(Y,M,D, sep="-")) %>% as.numeric() %>% as.factor() %>% as.numeric() ) %>% pull(date) %% 2
-banding <- 1:nrow(temp1) %% 2
-k=ncol(temp1)
-ft <- temp1   %>%
-      flextable::as_flextable() %>% 
-      flextable::set_header_labels(values =
-        list(
-              Event = "Ground\nTruth\nEvents",
-              icb_narrative = "ICB Corpus",
-              ICB = "ICB",
-              MIDs = "MIDs",
-              phoenix = "Phoenix"
-             ) ) %>%
-      flextable::width( j = 1, width=0.6)  %>% 
-      #flextable::width( j = 2, width=0.025)  %>%
-      #flextable::width( j = 3, width=0.025)  %>%
-      #flextable::width( j = 5, width=0.025) %>%
-      flextable::width( j = 2, width=3.0)  %>%
-      flextable::width( j = 3, width=0.03) %>%
-      flextable::width( j = 4:k, width=0.15) %>% #icb
-      #merge_v( j = 1,  part = "body", combine = T) %>%
-      #merge_v( j = 3,  part = "body", combine = F) %>%
-      #merge_v( j = 4,  part = "body", combine = F) %>%
-
-      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
-      align(i = 1,  align = "center", part = "header") %>%
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = NULL, j = 1, align = "right", part = "body")  %>%
-      align(i = NULL, j = 2, align = "left", part = "body")  %>%
-      #align(i = NULL, j = 2, align = "center", part = "body")  %>%
-      #align(i = NULL, j = 3, align = "left", part = "body")  %>%
-      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
-      vline(j=c(1,2,3,4,5,6,7),  border = NULL, part = "all") %>%
-      hline(i=c(26,46)) %>%
-      ftExtra::colformat_md(j = 2, part="body") 
-      #ftExtra::colformat_md(j = 6, part="body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-#Ok rather than try to match up we're going to do this by hand now
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names() 
-dim(case_study_crimea)
-
-#Replace emoticons with images
-replace_emoticons_crimea <- function(x){
-      x %>%
-            #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-            #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
-            #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
-            #
-            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) "))
-                            }
-
-rex_date <- function(x){
-  a <- x[1] %>% as.character() %>% unlist()
-  if(is.null(a)){return('')}
-  return(a)
-}
-case_study_crimea$date <- sapply(sapply(case_study_crimea$date, as.character), rex_date)
-temp2 <- case_study_crimea %>% 
-                filter(keep %in% 1) %>%
-                #filter(!is.na(date)) %>%
-                #head(2) %>%
-                mutate(date=date %>% anytime::anydate()) %>%
-                mutate(year=year(date) %>% as.character() ) %>%
-                mutate(month=month(date) %>% as.character()) %>%
-                mutate(day=day(date) %>% as.character()) %>%
-                mutate(n_sources = n_sources %>% as.numeric()) %>%
-                mutate(Rank=rank(-n_sources, ties.method="first")  ) %>%
-                dplyr::select(Y=year,M=month, D=day, Rank,  Event=event, Docs=n_sources, 
-                              icb_narrative=icb_narrative, ICBe=ic_be, MIDs=mids, phoenix, terrier, icews ) %>%  #, ICB=icb, MIDs=mids, phoenix=phoenix
-                mutate(Event= Event %>%  replace_emoticons_crimea) %>%
-                arrange(Y %>% as.numeric() ,M %>% as.numeric()  ,D %>% as.numeric() ) %>%
-                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
-                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
-                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
-                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
-                mutate(YMD=paste(Y,
-                                 M %>% str_pad(2, pad = "0") ,
-                                 D %>% str_pad(2, pad = "0"), 
-                                 sep="-") %>% trimws() %>%
-                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
-                                 str_replace_all("^NA-","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-","") 
-                       ) %>%
-                dplyr::select(-Y,-M,-D) %>%
-                relocate(YMD, .before = Rank) %>%
-                dplyr::select(-Rank) %>% 
-                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
-                mutate(icews = ifelse(!is.na(icews) & !icews %in% 0 , "✓", NA)) %>%
-                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0  , "✓", NA)) %>%
-                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0  , "✓", NA)) %>%
-                mutate(terrier = ifelse(!is.na(terrier) & !terrier %in% 0  , "✓", NA))  %>%
-                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0  , "✓", NA))
-
-dim(temp2)
-
-banding <- 1:nrow(temp2) %% 2
-k=ncol(temp2)
-ft <- temp2  %>%
-      flextable::as_flextable() %>% 
-      flextable::set_header_labels(values =
-        list(
-              Event = "Ground\nTruth\nEvents",
-              icb_narrative = "ICB Corpus",
-              ICBe = "ICBe",
-              MIDs="MIDs",
-              icews_hash = "ICEWS"
-             ) ) %>%
-      flextable::width( j = 1, width=0.6)  %>% 
-      flextable::width( j = 2, width=3.0)  %>%
-      flextable::width( j = 3:k, width=0.15) %>% #icb
-      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
-      align(i = 1,  align = "center", part = "header") %>%
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = NULL, j = 1, align = "right", part = "body")  %>%
-      align(i = NULL, j = 2, align = "left", part = "body")  %>%
-      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
-      vline(j=1:k,  border = NULL, part = "all") %>%
-      #hline(i=c(26,46)) %>%
-      ftExtra::colformat_md(j = 2, part="body") 
-      #ftExtra::colformat_md(j = 6, part="body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
-                  zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-```
-
-```{r, recall combined, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-temp3 <- temp1 %>% mutate(row=row_number()) %>% full_join(temp2 %>% mutate(row=row_number()), by='row') %>% 
-         mutate(row="") #we're going to use this as our vertical break
-
-n_left <- (!is.na(temp3$Event.x) ) %>% sum()
-n_right <- (!is.na(temp3$Event.y) ) %>% sum()
-
-k=ncol(temp3)
-kleft=ncol(temp1)
-kright=ncol(temp2)
-left_end=kleft
-right_start=left_end+2
-left=c(1:left_end)
-right=c(right_start:k)
-horizontal = c(left,right)
-dates=c(1,right_start)
-events = dates + 1
-checkmarks = c((events[1]+1):left_end , (events[2]+1):k)
-
-library(officer)
-big_border = fp_border(color="black", width = 2)
-
-banding1 <- 1:nrow(temp1) %% 2
-banding2 <- 1:nrow(temp2) %% 2
-ft <- temp3  %>%
-      flextable::as_flextable() %>%
-
-      flextable::line_spacing( space = 1.0, part = "all") %>% # 
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      bg( i = which( banding1==1 ) , part = "body", bg = "#EFEFEF", j=left) %>%
-      bg( i = which( banding2==1 ) , part = "body", bg = "#EFEFEF", j=right) %>%
-
-      #Headers
-      flextable::set_header_labels(values =
-        list(
-              YMD.x = "YMD",
-              Event.x = "Synthetic Narrative",
-              Docs.x = "Mentions",
-              icb_narrative.x = "ICB Corpus",
-              ICBe.x = "ICBe",
-              ICB = "ICB",
-              MIDs.x = "MIDs",
-              phoenix.x = "Phoenix",
-              phoenix.y = "Phoenix",
-              row="",
-              YMD.y = "YMD",
-              Event.y = "Synthetic Narrative",
-              Docs.y = "Mentions",
-              icb_narrative.y = "ICB Corpus",
-              ICBe.y = "ICBe",
-              icews = "ICEWS",
-              MIDs.y = "MIDs",
-              terrier="Terrier"
-             ) ) %>%
-
-      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbass (2014)"), colwidths = c(kleft, 1,kright) ) %>%
-
-      #Global
-      flextable::border_remove() %>% 
-      #Left border
-      border(j=1, i=1:n_left , part="body", border.left =  big_border ) %>% #
-      border(j=1, i=1:2 , part="header", border.left =  big_border ) %>% #
-
-      border(j=left_end, i=1:2 , part="header", border.right =  big_border ) %>% #
-      border(j=left_end, i=1:n_left , part="body", border.right =  big_border ) %>% #
-
-      border(j=1:left_end, i=n_left , part="body", border.bottom =  big_border ) %>% #
-      border(j=1:left_end, i=1 , part="body", border.top =  big_border ) %>% #
-      border(j=1:left_end, i=1:2 , part="header", border.top =  big_border ) %>% #
-
-      #Right border
-      border(j=right_start, i=1:n_right , part="body", border.left =  big_border ) %>% #
-      border(j=k, i=1:n_right , part="body", border.right =  big_border ) %>% #
-
-      border(j=right_start, i=1:2 , part="header", border.left =  big_border ) %>% #
-      border(j=k, i=1:2 , part="header", border.right =  big_border ) %>% #
-      border(j=1:k, i=1 , part="header", border.right =  big_border ) %>% #
-
-      border(j=right_start:k, i=n_right , part="body", border.bottom =  big_border ) %>% #
-      border(j=right_start:k, i=1 , part="body", border.top =  big_border ) %>% #
-      border(j=right_start:k, i=1:2 , part="header", border.top =  big_border ) %>% #
-
-      vline(i=1:n_left, j=1:(left_end-1),  border = NULL, part = "body")  %>%
-      vline(i=1:n_right,j=right_start:(k-1),  border = NULL, part = "body")  %>%
-      vline(i=2, j=1:(left_end-1),  border = NULL, part = "header")  %>%
-      vline(i=2,j=right_start:(k-1),  border = NULL, part = "header")  %>%
-
-      #
-      hline(i=c(26,46), j=left,  border = NULL, part = "body")  %>%
-      hline(i=c(11), j=right,  border = NULL, part = "body")  %>%
-
-      #Header
-      flextable::rotate(i=2, , j=3:left_end, rotation="tbrl", part="header") %>% 
-      flextable::rotate(i=2, , j=(left_end+4):k, rotation="tbrl", part="header") %>%
-
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = 2, j = NULL, align = "center", part = "header")  %>%
-
-      #break
-      flextable::width( j = left_end+1, width=0.25)  %>%
-
-      #Dates
-      flextable::width( j = dates, width=0.6)  %>% 
-      align(i = NULL, j = dates, align = "right", part = "body")   %>%
-
-      #events
-      flextable::width( j = events, width=2.50)  %>%
-      align(i = NULL, j = events, align = "left", part = "body")  %>%
-      ftExtra::colformat_md(j = events, part="body") %>%
-
-      #Checkmarks
-      flextable::width( j = checkmarks, width=0.05) %>%
-      align(i = NULL, j = checkmarks, align = "center", part = "body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#Recall Summary Statistics
-#, icb_narrative_cd=icb_narrative.y, icews_cd=icews_hash
-temp1_long <- temp1 %>% dplyr::select(docs=Docs, ICB_Narrative=icb_narrative, ICBe=ICBe, ICB=ICB,MIDs=MIDs,Phoenix=phoenix) %>% mutate(crisis="Cuban Missile Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
-              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
-
-temp2_long <- temp2 %>% dplyr::select(docs=Docs,ICB_Narrative=icb_narrative,ICBe=ICBe,MIDs=MIDs , Phoenix=phoenix, Terrier=terrier, ICEWS= icews) %>% mutate(crisis="Crimea-Donbas Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
-              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
-
-temp3_long <- bind_rows(temp1_long,temp2_long)
-
-Y_hat <- temp3_long %>% dplyr::select(name) %>% distinct()
-mylogit <- glm(value ~ name, data = temp3_long, family = "binomial")
-Y_hat$fit <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$fit
-Y_hat$se <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$se.fit
-Y_hat$name <- Y_hat$name %>% fct_reorder(Y_hat$fit)
-
-#Y_hat %>% ggplot(aes(name, fit)) +
-#          geom_point(size=4) +
-#          geom_errorbar(aes(ymin = fit-(1.98*se), ymax = fit+(1.98*se)), width = 0.1, linetype="solid") + coord_flip()  + theme_bw() + 
-#          ylab("Mean Recall") + xlab("")
-
-#temp3_long_means <- temp3_long %>% 
-#                    group_by(name) %>%
-#                    summarise(value= value %>%mean() %>% round(2))
-
-#temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + geom_point() +
-#  geom_smooth(method = "glm", method.args = list(family = "binomial"), se=F) + 
-#  ylab("Recall") + xlab("Document Mentions (Log)") +
-#  facet_wrap(~crisis, scales="free_x")
-
-library(geomtextpath)
-temp3_long$crisis <- factor(temp3_long$crisis, levels= temp3_long$crisis %>% as.character() %>% unique() %>% sort() %>% rev() )
-p_recall <- temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + 
-  #geom_point() +
-  geom_textsmooth(aes(label = name), size=3, method = "glm", method.args = list(family = "binomial"), se=F) + 
-  ylab("Recall") + xlab("Document Mentions (Log)") +
-  facet_wrap(~crisis, scales="free_x") +
-  theme_bw() +
-  theme(legend.position="none")
-
-#p_recall
-
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_recall.png'),
-       plot = p_recall ,
-       width=5, height=3.0)
-
-library(magick)
-
-tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))
-
-combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))
-
-```
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
-\end{figure}
-\clearpage
-\twocolumn
-
-Precision {.unnumbered}
-========================================
-
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, $Pr(H|E)$.
-It does little good to recall a historical event but too vaguely (e.g.
-MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
-ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
-D3 and D4) and all crises on the companion website.
-
-```{r crisis map function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-global_check_overlap=F
-library(igraph)
-library(RColorBrewer)
-library(ggraph)
-target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
-dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
-                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
-
-actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
-                                sheet="actor_translator") #%>% janitor::clean_names() 
-#Convert to a local file for pushing
-#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
-pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
-library(pals); #install.packages('pals')
-pallet <- c(pals::glasbey(),  pals::alphabet2())
-pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
-library(colorspace)
-#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
-pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
-actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
-
-icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){
-
-  icb_events_subset <-  ICBe_events_agreed %>% 
-                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
-                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
-                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
-                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
-                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
-                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
-                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
-                         tidyr::fill(decade, .direction="downup") %>%
-                         tidyr::fill(year, .direction="downup") %>%
-                         tidyr::fill(month, .direction="downup") %>%
-                         tidyr::fill(day, .direction="downup") %>% 
-                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
-                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
-                         arrange(decade, year,month,day) %>%
-                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
-
-  icb_events_subset_diad <- icb_events_subset %>% 
-                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                    sent,
-                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                    thinkkind, sayintkind, dokind,
-                                                    point_in_time_year, point_in_time_month
-                                                    ) %>% distinct() %>%
-                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
-
-  notes=NULL
-  if(prune_rare==T){
-    actor_sent_counts <- 
-      bind_rows(
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
-        ) %>% 
-          na.omit() %>%
-          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
-
-      #New pruning rule, either singletons or actors with less than 10% of the max actor
-      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
-      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
-      if(left_over_count<3){
-        #Skip pruning if it leaves less than 3 actors
-      } else {
-
-        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
-        actor_singleton_labels <- actor_map$value_normalized_label
-        names(actor_singleton_labels) <- actor_map$actor
-        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
-
-        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
-
-        #Easiest thing is to just prune the original data
-        icb_events_subset <- icb_events_subset %>%
-          filter(!(
-                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                say_actor_a %in% singleton_actors |
-                say_actor_b %in% singleton_actors |
-                do_actor_a %in% singleton_actors |
-                do_actor_b %in% singleton_actors 
-          ) )
-
-          #recreate diads again using the new sentence numbers
-          icb_events_subset_diad <- icb_events_subset %>% 
-                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                            sent,
-                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                            thinkkind, sayintkind, dokind,
-                                                            point_in_time_year, point_in_time_month
-                                                            ) %>% distinct() %>%
-                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
-                                        filter(!(
-                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                                              say_actor_a %in% singleton_actors |
-                                              say_actor_b %in% singleton_actors |
-                                              do_actor_a %in% singleton_actors |
-                                              do_actor_b %in% singleton_actors 
-                                        ) ) %>% 
-                                       arrange(sent) %>%
-                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
-      }
-  }
-
-  g <- make_empty_graph(n = 0, directed = TRUE)
-    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
-
-  #Order actors by how many interactions they have together
-  temp <- bind_rows(
-    icb_events_subset_diad  %>% 
-      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
-    icb_events_subset_diad %>% 
-      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
-  )  %>% arrange(actor_1, actor_2) %>% distinct()
-
-  #new plan is to minimize the number of crossovers
-  temp2 <- bind_rows(
-    temp,
-    temp %>% setNames(c("actor_2", "actor_1", "sent"))
-  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
-  rowwise() %>%
-  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
-  arrange(desc(n))
-
-  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
-  rownames(temp2_wide) <- temp2_wide$actor_1
-  temp2_wide$actor_1 <- NULL
-  temp2_wide <- temp2_wide %>% as.matrix()
-  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
-  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
-  hc <- hclust(temp2_wide %>% as.dist(), method="single")
-  diag(temp2_wide) <- 0
-  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
-
-  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
-  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
-
-  #####Nodes
-  icb_events_subset_nodes <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
-            )  %>%
-            filter(!is.na(actor)) %>%
-           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
-            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
-                   y=sent*-1 *100)
-
-  icbe_actor_to_qcode <- icb_events_long %>%
-                         dplyr::filter(crisno==thiscrisis  ) %>% 
-                         filter(varname_normalized %>% str_detect("actor")) %>% 
-                         dplyr::select(value_normalized,value_qcode) %>% 
-                         na.omit() %>% distinct()
-
-  actor_colors_df <- icbe_actor_to_qcode %>%
-    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
-  actor_colors <- actor_colors_df$actor_color
-  names(actor_colors) = actor_colors_df$value_normalized
-
-  date_sineposts <- icb_events_subset_nodes  %>%
-                      mutate(x=max(x)+50) %>%
-                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
-                      na.omit() %>% 
-                      distinct() %>%  
-                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
-                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
-                      group_by(sent) %>%
-                       filter(year_float==min(year_float)) %>%
-                      ungroup() %>% as.data.frame() %>%
-                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
-                      filter(!duplicated(year_float ) ) %>%
-                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
-
-  ####Actor levels
-  icb_events_subset_nodes_min <- 
-    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
-    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
-    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
-    rowwise() #%>%
-    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
-
-  for(i in 1:nrow(icb_events_subset_nodes)){
-    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
-                                actor = icb_events_subset_nodes$actor[i], 
-                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
-  }
-
-  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
-
-  #####Time Edges
-  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
-
-  g <- g %>% 
-       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
-
-  ######Monads
-  icb_events_subset_monad <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            filter(!duplicated(paste(sent,actor,leaf))) %>%
-            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
-            distinct() %>% 
-            group_by(sent,actor,actor_sent) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>%
-            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
-
-  ######Directed
-  icb_events_subset_directed <- 
-            #We need to enumerate all the possibilities
-            bind_rows(
-              #Do alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
-              #Say alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
-              #Say Do
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
-              #Think Do
-              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
-            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            arrange(sent, actor_sent_1,leaf) %>%
-            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
-           #It is actually easier just to rejex out some dupes
-            mutate(leaf = leaf %>%
-                     str_replace("accept\naccept","accept") %>%
-                   str_replace("appeal\nappeal","appeal") %>%
-                   str_replace("reject\nreject","reject") %>%
-                   str_replace("express intent\nexpress intent","express intent") 
-                   ) %>%
-           arrange(sent, actor_sent_1,leaf) %>%
-           filter(actor_sent_1!=actor_sent_2)
-
-  #debug
-  icb_events_subset_directed <- icb_events_subset_directed  %>% 
-           group_by(sent, leaf) %>%
-               mutate(bundle_count=n()) %>%
-               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
-            ungroup()
-
-  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                       timeedge=F, 
-                       leaf=icb_events_subset_directed$leaf2, 
-                       eventedge=T,
-                       actor=icb_events_subset_directed$actor_1,
-                       bundle_count=icb_events_subset_directed$bundle_count
-                       )
-
-  ######Put it all together
-  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
-  p_metro_map <- g %>%  
-          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
-
-          #Event edges
-          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
-          geom_edge_arc(aes(  
-                            colour=actor,
-                            label=leaf,
-                            filter=eventedge==T & bundle_count==1 
-                            ),
-                        label_colour=NA, 
-                        vjust = -0.75,
-                        lineheight = .75,
-                        sep = unit(1, 'mm'), 
-                        edge_width=0.25, 
-                        show.legend = F,
-                        arrow = arrow(length = unit(2, 'mm')),
-                        label_size=3,
-                        check_overlap=global_check_overlap,
-                        start_cap = circle(3, 'mm'),
-                        end_cap = circle(3, 'mm'),
-                        angle_calc = 'along' #,
-                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
-                       ) +
-              #Grouped Edges
-              geom_edge_parallel(aes(  
-                                  colour=actor,
-                                  label=leaf,
-                                  filter=eventedge==T & bundle_count>1
-                                  ),
-                              vjust = -0.75,
-                              lineheight = .75,
-                              sep = unit(5, 'mm'), 
-                              edge_width=0.4,  #0.25
-                              show.legend = F,
-                              arrow = arrow(length = unit(1, 'mm')),
-                              label_size=4,
-                              check_overlap=global_check_overlap,
-                              start_cap = circle(3, 'mm'),
-                              end_cap = circle(3, 'mm'),
-                              angle_calc = 'along'
-                             ) +
-
-              #Time edges
-              geom_edge_link(aes(
-                              edge_colour=actor,
-                              filter=timeedge==T
-                              ),
-                              edge_width=0.1, 
-                              show.legend = F,
-                              check_overlap=global_check_overlap
-                             ) +
-              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
-              #Fatalities
-              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
-
-              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
-              #Add Actor Names
-              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
-                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
-                        check_overlap=global_check_overlap) + #-45
-              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
-              scale_color_manual(values = actor_colors)  +
-              scale_edge_color_manual(values = actor_colors) +
-              #theme_bw() + 
-              #labs( title = plot_title ) +
-              theme_graph() +
-              theme(legend.position = "none") #+
-              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
-
-  if(prune_rare==T & !is.null(notes)){
-     p_metro_map <- p_metro_map + labs(caption = notes)
-  }
-
-  return(p_metro_map)
-}
-
-```
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(cowplot)
-
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/figures/crisismaps/p_metro_plot_471.Rds')) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-p_precision_combined <- plot_grid(
-            p_196_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
-               p_471_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
-           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )
-
-save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = 24)
-
-```
-
-\clearpage
-\onecolumn
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=24cm]{../figures/p_precision_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-\twocolumn
-
-We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).
-
-We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark.
-Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(flextable)
-library(ftExtra)
-library(tidyverse)
-
-#Load it here before the python reticulate business
-#devtools::install_github("ropenscilabs/umapr")
-#library(umapr)
-
-ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
-
-ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
-                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
-                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
-                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
-                                                 str_replace_all("[0-9]{4}","Entity") %>% #All years with entity
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("[0-9]","") %>%  #replace all digits with blanks
-                                                 str_replace_all(" {1,}"," ")   
-                                               )  #
-
-sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
-                    dplyr::select(sentences_unique_sanitized) %>% 
-                    distinct() %>%
-                    pull(sentences_unique_sanitized) %>% 
-                    unique() %>% na.omit()
-length(sentences_unique ) #12162
-head(sentences_unique)
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-#To set python, set it in ~/.Renviron.
-`use_python()` doesn't seem to work as desired.
-See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
-
-library(reticulate)
-reticulate::py_discover_config()
-
-#use_python("/home/skynet3/anaconda3/bin/python/")
-#use_python("/home/tlscherer/anaconda3/bin/python3")
-
-```
-
-```{python, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
-#pip install -U sentence-transformers
-
-fromscratch=False
-
-if fromscratch:
-  from sentence_transformers import SentenceTransformer
-  import numpy as np
-  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
-  sentence_chars = np.array([len(q) for q in sentences])
-  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
-  len(sentences) #12161 12162
-  n=len(sentences)
-  chunk_length=100
-  n_chunks = int(np.ceil(n/chunk_length)) #can only 
-  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
-  len(sentences_chunks)
-  len(sentences_chunks[0])  
-  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
-  model = SentenceTransformer('paraphrase-mpnet-base-v2')
-  #sentences
-  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
-  #temp = model.encode(sentences_chunks[0])
-  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
-  sentences_embeddings.shape #(12103, 768)
-
-else:
-  print("Skipping")
-
-```
-
-```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-fromscratch = FALSE
-if(fromscratch){
-  sentences_embeddings <- py$sentences_embeddings
-  dim(sentences_embeddings)
-  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
-}else{
-  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
-  dim(sentences_embeddings)
-}
-
-```
-
-```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.  
-embedding <- umapr::umap(sentences_embeddings)
-#plot(embedding[,c('UMAP1','UMAP2')])
-
-sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
-sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()
-
-sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
-sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique
-
-ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
-                                        left_join(sentences_embeded_umap) %>% 
-                                        left_join(sentences_embeded_mpnet)
-
-ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
-
-ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
-                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
-                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
-                                                arrange(UMAP1,UMAP2) %>%
-                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-library(cowplot)
-ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
-
-value_means <- ICBe_events_agreed_markdown_embedded %>%
-               dplyr::select(UMAP1,UMAP2, contains("escalate"),contains("coop"),contains("sayintkind"), contains("thinkkind")) %>%
-               pivot_longer(cols=-c(UMAP1,UMAP2)) %>% filter(!is.na(value) & value!='') %>% 
-               mutate(value = value %>% str_split(";")) %>% 
-               unnest(value) %>% 
-               mutate(value = value %>% str_trim()) %>%
-               filter(!value %>% str_detect("sentence|^[0-9]")) %>%
-               mutate(color=NA) %>%
-               mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
-               mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
-               dplyr::select(-name) %>%
-               group_by(color, value) %>%
-               mutate(n=n()) %>%
-               filter(n>20) %>% #note require at least 20 examples of that tag
-               dplyr::summarise_all(median)
-
-value_normalized_colors <- value_means$color 
-names(value_normalized_colors) = value_means$value
-
-library(ggplot2)
-library(ggrepel)
-p_semantic_embeddings <-
-      ICBe_events_agreed_markdown_embedded %>%
-      ggplot(aes(x=UMAP2,y=UMAP1)) +
-      geom_point(size=0.5, alpha=0.25) + 
-      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
-      theme_bw() +
-      theme(legend.position = "none") + 
-      geom_label(data=value_means,
-                 aes(x=UMAP2,y=UMAP1, fill = value %>% as.factor(), label=value, size=50), size = 2.5, inherit.aes=F, 
-                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
-                 ) +   
-      #geom_label_repel(data=value_means,
-      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
-      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
-      #           min.segment.length = 0
-      #           ) + 
-      labs(
-          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
-          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
-          caption = ""
-      ) +
-     scale_color_manual(values = value_normalized_colors) +
-     scale_fill_manual(values = value_normalized_colors) +
-     scale_x_continuous(expand = c(0, 0)) +
-     scale_y_continuous( expand = c(0, 0)) #+
-     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
-     #coord_flip()
-
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
-
-#Now do the dendro
-library(ggdendro)
-#We actually need the raw embeddings
-
-#Rex Note to take only one per sentence
-
-#This is unreasonably slow because it's large and in tidy. Couldn't do it every time if we wanted to.
-value_highdim <- ICBe_events_agreed_markdown_embedded %>%
-                 dplyr::select(starts_with("V",  ignore.case = F), contains("escalate"),contains("coop"),contains("sayintkind"), 
-                               contains("thinkkind"), crisno, sentence_number_int_aligned) %>% 
-                 pivot_longer(cols=-c(starts_with("V",  ignore.case = F), crisno, sentence_number_int_aligned) ) %>%
-                 filter(!is.na(value) & value!='') %>% #40,898
-                 filter(!value %>% str_detect("sentence|^[0-9]")) %>% 
-                 mutate(value = value %>% str_split(";")) %>% 
-                 unnest(value) %>% 
-                 mutate(value = value %>% str_trim())   %>% #
-                 mutate(color=NA) %>%
-                 mutate(color=ifelse(name %>% str_detect("_escalate"),"red",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("_deescalate"),"darkgreen",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("sayintkind"),"brown",color)) %>%
-                 mutate(color=ifelse(name %>% str_detect("thinkkind"),"darkorange",color)) %>%
-                 dplyr::select(-name) %>%
-                 group_by(color, value) %>%
-                  mutate(n=n()) %>% 
-                 ungroup() %>%
-                 arrange(n, value) %>%
-                 filter(!duplicated( paste(crisno, sentence_number_int_aligned)) ) %>% #only take one per sentence to break mechanically induced correlations
-                 filter(n>20)
-
-dim(value_highdim)
-
-value_highdim_medians <- value_highdim %>% 
-                           group_by(color, value) %>%
-                           dplyr::summarise_all(median)
-
-value_normalized_colors <- value_highdim_medians$color 
-names(value_normalized_colors) = value_highdim_medians$value
-
-m <- value_highdim_medians %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix() 
-rownames(m) <- value_highdim_medians$value
-d <- m %>% dist()
-hc <- hclust(d, method="ward.D2")
-library(ggplot2)
-library(ggdendro)
-hcdata <- dendro_data(hc, type = "rectangle")
-p_dendro <- ggplot() +
-            geom_segment(data = segment(hcdata), 
-                         aes(x = x, y = y, xend = xend, yend = yend)
-            ) +
-            geom_text(data = label(hcdata) %>% mutate(color=value_highdim_medians$color ), 
-                      aes(x = x, y = y, label = label, hjust = 0, color=color[hc$order]), 
-                      size = 3
-            ) +
-            coord_flip() +
-            scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
-            scale_y_reverse( expand = c(0.1, 0.0, 0.0, 5.0)) +  #limits = c(-10, 10),
-            theme_bw() +
-            theme(legend.position="none")
-#p_dendro
-
-p_combined <- plot_grid(
-  p_semantic_embeddings + xlab("") + ylab("") + 
-  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
-  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
-  p_dendro  + xlab("") + ylab("") + 
-  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
-  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),  
-  labels = c('',''),
-  align = "v", ncol = 2, rel_widths = c(3, 1)  )
-#p_combined
-
-ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
-
-```
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{../figures/p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that tag was applied to by the coders.
-The dendrogram shows hiearchical clustering of the tags.
-If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to visually recognizable.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis.
-On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-library(ggplot2)
-library(readr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(ggtext)
-
-icews_clean_subset_top10_day <- read_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
-
-keys <- c("sign formal agreement") #"express accord", #,"declare truce, ceasefire"
-events1 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p1 <- events1 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2013-11-21'), label="Reject EU\nTrade Deal" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-18'), label="Annex Crimea" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-09-06'), label="MINSK I" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2015-02-21'), label="MINSK II" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-keys <- c("reject plan, agreement to settle dispute") #"express accord", #,"declare truce, ceasefire"
-events2 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p2 <- events2 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2013-11-21'), label="Reject EU\nTrade Deal" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-#,"fight with artillery and tanks","Use unconventional violence", "fight with small arms and light weapons","Mobilize or increase armed forces","Demonstrate military or police power", "Violate ceasefire", "Occupy territory"
-keys <- c("use conventional military force")
-events3 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p3 <- events3 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-02-27'), label="Seize Gov Building Crimea" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-02-18'), label="Rus Annex Crimea" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-16'), label="Fighting Donbas" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-04-06'), label="Fighting Donbas" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-09-06'), label="Continued Fighting Donbas" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-#,"Refuse to ease economic sanctions, boycott, or embargo", "Reduce or stop economic assistance","Reduce or stop material aid","Impose blockade, restrict movement", "Reduce or stop military assistance"
-keys <- c("impose embargo, boycott, or sanctions")
-events4 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p4 <- events4 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-17'), label="US-EU Sanction Rus" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-07-17'), label="EU Sanctions Rus\nRus Sanctions Ukr" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-library(cowplot)
-p_ICEWS <- plot_grid(
-           p1 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           p2 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           p3 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           p4 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           #labels = c('Cuban Missiles','Crimea-Donbas'), 
-           align = "v", ncol = 1 , rel_widths = c(1) )
-
-save_plot(file=paste0(here::here(),
-                      '/replication_paper/figures/p_precision_icews.png'),
-          p_ICEWS, base_height = 10, base_width = 14)
-
-```
-
-However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, [@terechshenkoHotCollarLatent2020] attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
-geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks].
-
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
-We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
-Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
-In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{../figures/p_precision_icews.png}}
-\textit{Notes:Unit of analysis is the Dyad-Day.
-Edges <-> indicates undirected dyad and -> indicates directed dyad.
-Top 10 most active dyads per category shown.
-Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-<!--
-286 Sign formal agreement
-Reject 99
-
-crisis.
-ICEWS Precision bad for networks  for 
-See [@althausTotalErrorApproach2022] for 19 types of errors in event data.
-Agreement between ICEWS, GED, and CINEP [@stundalHumanRightsViolations2021]
-ICEWs and 
-ICEWs protest events about 80% precision [@wangGrowingPainsGlobal2016],
-
-Dictionary based NLP systems based on large news corpora produce many thousands events over a short time which are unintelligible from the standpoint of micro or macro precision as analyzed above.
-
-Dictionary methods are effectively topic detectors. Dozens of events about signing a deal with the EU that didn't happen.
-
-Next, we make available visualizations of every datum in ICBe alongside each of its contemporary competitors in full on the companion website.
-For ICBe, we show the original source text alongside an iconographic representation of coded events as in Figure 1.
--->
-
-Conclusion {#format .unnumbered}
-========================================
-
-We investigated event extraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal validity (e.g.
-intercoder agreement) and external validity (i.e.
-matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes).
-Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
-
-<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
-\showmatmethods
-\showacknow
-\pnasbreak

### 2022-07-25 replication_paper/pnas_draft/paper.tex

@@
-\documentclass[9pt,twocolumn,twoside,]{pnas-new}
-
-% Use the lineno option to display guide line numbers if required.
-% Note that the use of elements such as single-column equations
-% may affect the guide line number alignment.
-
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-% tightlist command for lists without linebreak
 \providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
-\usepackage{longtable,booktabs,array}
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
 \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage[]{biblatex}
+\addbibresource{ICBintro.bib}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises},
+  pdfauthor={Rex W.
+Douglass; Thomas Leo Scherer; J.
+Andrés Gannon; Erik Gartzke; Jon Lindsay; Shannon Carcelli; Jonathan Wilkenfeld; David M.
+Quinn; Catherine Aiken; Jose Miguel Cabezas Navarro; Neil Lund; Egle Murauskaite; Diana Partridge},
+  pdfkeywords={Diplomacy, War, Crises, International
+Affairs, Computational Social Science},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-\usepackage{xr} \externaldocument{appendix}
-\usepackage[utf8]{inputenc}
-\usepackage{pifont}
-\usepackage{newunicodechar}
-\newunicodechar{✓}{\ding{51}}
-\newunicodechar{✗}{\ding{55}}
-\usepackage{array}
-\usepackage{ctable}
-\usepackage{natbib}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{titlesec}
-\usepackage[parfill]{parskip}
-\usepackage{makecell}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage{cellspace}
-\setlength\cellspacetoplimit{0.8ex}
-\renewcommand{\arraystretch}{0.8}
-\AtBeginEnvironment{tabular}{\singlespacing}
-\AtBeginEnvironment{lltable}{\singlespacing}
-\usepackage{subcaption}
-\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
-\usepackage{float}
-\usepackage[algo2e]{algorithm2e}
-\usepackage{fontspec}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
+\title{Introducing ICBe: Very High Recall and Precision Event Extraction
+from Narratives about International Crises}
+\author{Rex W. Douglass \and Thomas Leo Scherer \and J. Andrés
+Gannon \and Erik Gartzke \and Jon Lindsay \and Shannon
+Carcelli \and Jonathan Wilkenfeld \and David M. Quinn \and Catherine
+Aiken \and Jose Miguel Cabezas Navarro \and Neil Lund \and Egle
+Murauskaite \and Diana Partridge}
+\date{}
 
-\templatetype{pnasresearcharticle}  % Choose template
-
-\title{Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises}
-
-\author[a,1,2]{Rex W. Douglass}
-\author[a]{Thomas Leo Scherer}
-\author[b]{J. Andrés Gannon}
-\author[a]{Erik Gartzke}
-\author[c]{Jon Lindsay}
-\author[d]{Shannon Carcelli}
-\author[d]{Jonathan Wilkenfeld}
-\author[e]{David M. Quinn}
-\author[f]{Catherine Aiken}
-\author[g]{Jose Miguel Cabezas Navarro}
-\author[d]{Neil Lund}
-\author[h]{Egle Murauskaite}
-\author[h]{Diana Partridge}
-
-  \affil[a]{Department of Political Science, University of California, San Diego, CA, USA.}
-  \affil[b]{Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.}
-  \affil[c]{School of Cybersecurity and Privacy \textbar{} Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.}
-  \affil[d]{Department of Government and Politics, University of Maryland, College Park, MD, USA.}
-  \affil[e]{Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.}
-  \affil[f]{Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.}
-  \affil[g]{Society and Health Research Center, Universidad Mayor, Santiago, Chile.}
-  \affil[h]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
-  \affil[i]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Douglass}
-
-% Please add here a significance statement to explain the relevance of your work
-\significancestatement{Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
-Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
-This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods.
-It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.}
-
-\authorcontributions{Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D., J.A.G., E.G., T.L.S.;
-Visualization: R.W.D., T.L.S.; Supervision: E.G.; Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.}
-
-\authordeclaration{Please declare any conflict of interest here.}
-
-\correspondingauthor{\textsuperscript{2} To whom correspondence should be addressed. E-mail: \href{mailto:rexdouglass@gmail.com}{\nolinkurl{rexdouglass@gmail.com}}}
-
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
- \keywords{  Diplomacy |  War |  Crises |  International Affairs |  Computational Social Science  }
-
+\begin{document}
+\maketitle
 \begin{abstract}
-How do international crises unfold?
-We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
-We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
-We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
-We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+How do international crises unfold? We conceptualize of international
+relations as a strategic chess game between adversaries and develop a
+systematic way to measure pieces, moves, and gambits accurately and
+consistently over a hundred years of history. We introduce a new
+ontology and dataset of international events called ICBe based on very
+high-quality corpus of narratives from the International Crisis Behavior
+(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
+precision than existing state of the art datasets and conduct two
+detailed case studies of the Cuban Missile Crisis (1962) and
+Crimea-Donbas Crisis (2014). We further introduce two new event
+visualizations (event icongraphy and crisis maps), an automated
+benchmark for measuring event recall using natural language processing
+(sythnetic narratives), and an ontology reconstruction task for
+objectively measuring event precision. We make the data, replication
+material, and visualizations of every historical episode available at a
+companion website www.crisisevents.org.
 \end{abstract}
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi
 
-\begin{document}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-\verticaladjustment{-2pt}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\acknow{We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-We thank the many undergraduate coders for their patience and dedication.
-Thanks to the Center for Peace and Security Studies and its membership for comments.
-Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
-Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.}
-
-If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
-In other words, what is the entropy of international relations?
-This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive (1, 2).
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.\footnote{See work on crises (3, 4), militarized disputes (5--7), wars (8, 9), organized violence (10, 11), political violence (12), sanctions (13), trade (14), and international agreements (15--17), dispute resolution (17, 18), and diplomacy (19, 20).} With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.\footnote{See (21); (22); (23); (24); (25); (26).
-On event-extraction from images and social-media see (27) and (28).} How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations.
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises (1, 29--32).
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
-We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
-The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision.
-A final section concludes.
-
-\hypertarget{task-definition}{%
-\section*{Task Definition}\label{task-definition}}
-\addcontentsline{toc}{section}{Task Definition}
-
-We consider the measurement task of abstracting discrete events about a historical episode in international relations.
-The easiest way to convey the task is with an example.
-Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine readable abstractive events.
-Formally, a historical episode, \(H\), is demarcated by a period of time \([T_{start}, T_{end}] \in T\), a set of Players \(p \in P\), and a set of behaviors they undertook during that time \(b \in B\).
-International Relations, \(IR\), is the system of regularities that govern the strategic interactions that world actors make during a historical episode, given their available options, preferences, beliefs, and expectations of choices made by others.
-We observe neither \(H\) nor \(IR\) directly.
-Rather the Historical Record, \(HR\), produces documents \(d \in D\) containing some relevant and true (as well as irrelevant and untrue) information about behaviors that were undertaken recorded in the form of unstructured natural language text.
-The task is to combine informative priors about \(IR\) with an unstructured corpus \(D\) to produce a series of structured discrete events, \(e \in E\), that have high coverage, precision, and recall over what actually took place in history, \(H\).
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=22cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-\twocolumn
-
-\hypertarget{corpus}{%
-\section*{Corpus}\label{corpus}}
-\addcontentsline{toc}{section}{Corpus}
-
-For our corpus, \(D\), we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project (\(n=471\))(SI Appendix, Table A1)(33, 34).
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system (3).\footnote{On near crises see (32).} Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict (3, 35--42).
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources (33, 43).
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity (44).
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-\hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
-\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
-\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}
-
-Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find 464 actors and 117 different behaviors, and provide a full codebook in the online material.\footnote{See the Github Repository \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet (45), tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).
-
-The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11, 47).\footnote{Additional relevant but dated or too small of an overlap in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51), SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories in (54) and (55)).} The final set of columns compares episode-level datasets beginning with the original ICB project (3, 4, 56); the Militarized Interstate Disputes dataset (5, 6, 57, 58), and the Correlates of War (8).
-With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.\footnote{See (53) for a recent review of ontological depth and availability of Gold Standard example text.}
-
-\clearpage
-\onecolumn
-
-{[}1{]} 37 17
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.75}
-
-\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
-
-\caption{Ontological coverage of ICBe versus existing State of the Art
-}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{15k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\end{longtable}
-
-\clearpage
-\twocolumn
-
-\hypertarget{icbe-coding-process}{%
-\section*{ICBe Coding Process}\label{icbe-coding-process}}
-\addcontentsline{toc}{section}{ICBe Coding Process}
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details (59).\footnote{This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.} Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-B1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players (\(P\)), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.~force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.~an offer for the U.S.S.R.
-to remove missiles from Cuba in exchange for the U.S.
-removing missiles from Turkey.
-Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-
-Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.\footnote{Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.} For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=972,545), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
-We then aggregate those tags into final events (n=18,309), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
-This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
-
-\hypertarget{internal-consistency}{%
-\section*{Internal Consistency}\label{internal-consistency}}
-\addcontentsline{toc}{section}{Internal Consistency}
-
-We evaluate the internal validity of the coding process in several ways.
-For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig.
-B3).
-Across all concepts, the Top 1 Tag Agreement was low among novices (31\%), moderate for experts (65\%), and high (74\%) following the consensus screening procedure.
-
-We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to be low for 20\% of sentences- half due to a mismatch between the ontology and the text (``survey doesn't fit event''-45\%) and half due to a lack of information or confused writing in the source text (``more knowledge needed''-40\%, ``confusing sentence''-6\%).
-Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig.
-B4).
-Second, as intended agreement is higher (75-80\%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50\%-60\%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.~some more expressive applying many tags per concept while others focused on only the single best match.
-We further observed unintended synonymity, e.g.~the same information can be framed as either a threat to do something or a promise not to do something.
-
-\hypertarget{case-study-selection}{%
-\section*{Case Study Selection}\label{case-study-selection}}
-\addcontentsline{toc}{section}{Case Study Selection}
-
-The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website.
-In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
-
-\hypertarget{recall}{%
-\section*{Recall}\label{recall}}
-\addcontentsline{toc}{section}{Recall}
-
-Recall measures the share of desired information recovered by a sequence of coded events, \(Pr(E|H)\), and is poorly defined for historical episodes.
-First, there is no genuine ground truth about what occurred, only surviving texts about it.
-Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox (60) --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events.
-The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
-We need a yardstick for history.
-
-Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative.
-For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
-Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts.
-The more accounts that mention a detail, the more central it is to understanding the true historical episode.
-The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing.
-With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
-Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
-
-Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts.
-First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative.
-Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details.
-Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g.~the U.S.
-was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection (61) and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.~a long term lease on naval facilities in Crimea.
-Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode level datasets have very low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
-\end{figure}
-\clearpage
-\twocolumn
-
-\hypertarget{precision}{%
-\section*{Precision}\label{precision}}
-\addcontentsline{toc}{section}{Precision}
-
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, \(Pr(H|E)\).
-It does little good to recall a historical event but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
-D3 and D4) and all crises on the companion website.
-
-\clearpage
-\onecolumn
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=24cm]{../figures/p_precision_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-\twocolumn
-
-We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).
-
-We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark.
-Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.\footnote{We preprocess sentences to replace named entities with a generic Entity token.} Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.\footnote{Hierchcial clustering on cosine similarity and with Ward's method.}
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{../figures/p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that tag was applied to by the coders.
-The dendrogram shows hiearchical clustering of the tags.
-If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to visually recognizable.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis.
-On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
-
-However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, (62) attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.~geolocation (63), protest events (80\%) (64), anti-government protest networks (46.1\%) (65).
-
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
-We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but ``sign formal agreement'' events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the ``reject plan, agreement to settle dispute'', but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
-Events for ``use conventional military force'' capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, ``impose embargo, boycott, or sanctions'' captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
-In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{../figures/p_precision_icews.png}}
-\textit{Notes:Unit of analysis is the Dyad-Day.
-Edges <-> indicates undirected dyad and -> indicates directed dyad.
-Top 10 most active dyads per category shown.
-Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-\hypertarget{format}{%
-\section*{Conclusion}\label{format}}
-\addcontentsline{toc}{section}{Conclusion}
-
-We investigated event extraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal validity (e.g.~intercoder agreement) and external validity (i.e.~matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes).
-Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.~escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
-
-\showmatmethods
-\showacknow
-\pnasbreak
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Brecher M (1999) International studies in the twentieth century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA} presidential address.
-\emph{International Studies Quarterly} 43(2):213--264.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reiter D (2015) \href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu Rev Polit Sci} 18(1):481--499.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Brecher M, Wilkenfeld J (1982) \href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}. \emph{World Politics} 34(3):380--417.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The {International Crisis Behavior Project}.
-doi:\href{https://doi.org/10.1093/acrefore/9780190228637.013.1638}{10.1093/acrefore/9780190228637.013.1638}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Palmer G, et al.
-(2021) \href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset}, 2011--2014: {Procedures}, coding rules, and description}.
-\emph{Conflict Management and Peace Science}:0738894221995743.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts}, 1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \& Littlefield}) Available at: \url{https://books.google.com?id=_4VTDwAAQBAJ}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP (2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0: {Logic}, {Characteristics}, and {Comparisons} to {Alternative Datasets}}.
-\emph{Journal of Conflict Resolution} 63(3):811--835.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war: 1816-2007} ({CQ Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016) \href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at {Interstate Wars}, 1816--2007}.
-\emph{Journal of Conflict Resolution} 60(5):956--976.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED Codebook} version 5.0} ({Department of Peace and Conflict Research, Uppsala University}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Pettersson T, Eck K (2018) \href{https://doi.org/10.1177/0022343318784101}{Organized violence, 1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010) Introducing {ACLED}: An armed conflict location and event dataset: Special data feature. \emph{Journal of peace research} 47(5):651--660.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The global sanctions data base}.
-\emph{European Economic Review} 129:103561.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the {Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Kinne BJ (2020) \href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution} 64(4):729--755.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018) \href{https://doi.org/10.1177/0738894216646978}{The {International Border Agreements Dataset}}.
-\emph{Conflict Management and Peace Science} 35(5):559--576.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Vabulas F, Snidal D (2021) \href{https://doi.org/10.1177/0022343320943920}{Cooperation under autonomy: {Building} and analyzing the {Informal Intergovernmental Organizations} 2.0 dataset}.
-\emph{Journal of Peace Research} 58(4):859--869.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017) \href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates} of {War Territorial Claims Data}, 1816--20011}.
-\emph{Journal of Peace Research} 54(1):99--108.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020) \href{https://doi.org/10.1177/0022343320929740}{What are the drivers of diplomacy?
-{Introducing} and testing new annual dyadic data measuring diplomatic exchange}.
-\emph{Journal of Peace Research}:0022343320929740.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Sechser TS (2011) \href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent Threats}, 1918--2001}. \emph{Conflict Management and Peace Science} 28(4):377--401.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Li Q, et al.
-(2021) A {Comprehensive Survey} on {Schema-based Event Extraction} with {Deep Learning}.
-Available at: \url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10, 2021{]}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Halterman A (2020) Extracting {Political Events} from {Text Using Syntax} and {Semantics}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018) Phoenix {Real-Time Event Data}. Available at: \url{http://eventdata.utdallas.edu}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data. \emph{Harvard Dataverse} 12.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing the {UCDP Candidate Events Dataset}. \emph{Research \& Politics} 7(3):2053168020935257.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017) {OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/} {[}Accessed September 1, 2021{]}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Zhang H, Pan J (2019) \href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning Approach} for {Identifying Collective Action Events} with {Text} and {Image Data} from {Social Media}}.
-\emph{Sociological Methodology} 49(1):1--57.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Steinert-Threlkeld ZC (2019) \href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis escalation to war: {Findings} from the {International Crisis Behavior Project}. \emph{What Do We Know About War}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and violence: Twentieth-century findings. \emph{Handbook of war studies II}:282--300.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{James P (2019) \href{https://doi.org/10.1177/0738894218793135}{What do we know about crisis, escalation and war?
-{A} visual assessment of the {International Crisis Behavior Project}}.
-\emph{Conflict Management and Peace Science} 36(1):3--19.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Iakhnis E, James P (2019) \href{https://doi.org/10.1177/0738894219855610}{Near crises in world politics: {A} new dataset}.
-\emph{Conflict Management and Peace Science}:0738894219855610.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D (2017) \emph{International {Crisis Behavior Data Codebook}} Available at: \url{http://sites.duke.edu/icbdata/data-collections/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of {Crisis}} ({University of Michigan Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Holsti OR (1965) \href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The American Political Science Review} 59(2):365--378.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June} 24-30, 1950} ({Free Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision: {Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among nations: {Bargaining} and decision making in international crises} ({Princeton University Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Gavin FJ (2014) \href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies} 37(2):319--331.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American} foreign policy: {Theory} and practice} ({Columbia University Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Gaddis JL (1987) \href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}: {Historians}, {Political Scientists}, and the {Enrichment} of {Security Studies}}.
-\emph{International Security} 12(1):3--21.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management. \emph{Journal of Conflict Resolution} 32(3):426--456.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of {Asian} security: {Using Europe} to study {Asia}. \emph{Journal of Global Security Studies} 4(3):393--401.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Hewitt JJ (2001) \href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to {Teach Conflict} and {Crisis Analysis}}.
-\emph{Int Stud Perspect} 2(4):371--383.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Miller GA (1995) \href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical database for {English}}. \emph{Commun ACM} 38(11):39--41.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA (2019) Cline {Center Historical Phoenix Event Data Variable Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP} georeferenced event dataset. \emph{Journal of Peace Research} 50(4):523--532.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Leng RJ, Singer JD (1988) \href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}: {The BCOW Typology} and {Its Applications}}.
-\emph{International Studies Quarterly} 32(2):155--173.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{McClelland C (1978) World event/interaction survey, 1966-1978. \emph{WEIS Codebook ICPSR} 5211.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events} of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968: {Version} 1.
-doi:\href{https://doi.org/10.3886/ICPSR05205.V1}{10.3886/ICPSR05205.V1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}: {Computer-aided} system for analysis of local conflicts. \emph{MIT Center for International Studies, Cambridge}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm}, {Hierarchical}, and {Contextually-Sensitive International Conflict Dataset}, 1937-1985: {Version} 1.
-doi:\href{https://doi.org/10.3886/ICPSR02292.V1}{10.3886/ICPSR02292.V1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A Comprehensive Ontology} for {Event Extraction} from text.
-doi:\href{https://doi.org/10.48550/arXiv.2107.10326}{10.48550/arXiv.2107.10326}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Merritt RL (1994) Measuring events for international political analysis. \emph{International Interactions} 20(1-2):3--33.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas} event data system project. \emph{The political methodologist} 14(1):2--8.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D International {Crisis Behavior Data Codebook}, {Version} 12. 69.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Braithwaite A (2010) \href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing} the {Militarized Interstate Dispute Location} dataset}.
-\emph{Journal of Peace Research} 47(1):91--98.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University College London}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain knowledge: Using hierarchies to improve deep classifiers.
-Available at: \url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of nature} ({Freeman}, {New York}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Cormac R, Aldrich RJ (2018) \href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert action and implausible deniability}. \emph{International Affairs} 94(3):477--494.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Terechshenko Z (2020) \href{https://doi.org/10.1177/0022343320962546}{Hot under the collar: {A} latent measure of interstate hostility}.
-\emph{Journal of Peace Research} 57(6):764--776.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{Cook SJ, Weidmann NB (2019) \href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}: {Improving Event Analysis} with {Report-Level Data}}.
-\emph{American Journal of Political Science} 63(1):250--264.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of protest event analysis. \emph{Contention in times of crisis: Recession and political protest in thirty Euro-pean countries}:49--78.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event Data}: {Evidence} from the {ICEWS Dataset}.}
-
-\end{CSLReferences}
-
-% Bibliography
-% \bibliography{pnas-sample}
+\printbibliography
 

### 2022-07-26 README.Rmd
arXiv submit and readme

@@
 
-[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf).
+[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/arxiv_draft/paper.pdf) (also available on [ArXiv](https://arxiv.org/abs/2202.07081)).
 
-The [ArXiv pre-print](https://arxiv.org/abs/2202.07081) was posted on February 15, 2022.
+The v1.1 Online Appendix can be downloaded [here](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/arxiv_draft/appendix.pdf).
+
+Version 1.1 is the most recent version and was posted on [ArXiv](https://arxiv.org/abs/2202.07081) on July 26, 2022. Version 1.0 was posted on February 15, 2022.
 

### 2022-07-26 replication_paper/arxiv_draft/paper.Rmd
can knit!
arXiv submit and readme

@@
 We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.
 
@@
 
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
+For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).] Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
 Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
@@
 
+if(fromscratch){
+
 library(ggplot2)
@@
 
+}
+
 ```

### 2022-07-26 replication_paper/arxiv_draft/paper.tex
can knit!
arXiv submit and readme

@@
 (sythnetic narratives), and an ontology reconstruction task for
-objectively measuring event precision. We make the data, replication
-material, and visualizations of every historical episode available at a
-companion website www.crisisevents.org.
+objectively measuring event precision. We make the data, online
+appendix, replication material, and visualizations of every historical
+episode available at a companion website www.crisisevents.org and the
+github repository.
 \end{abstract}
@@
 historical narratives from the International Crisis Behavior (ICB)
-project (\(n=471\))(SI Appendix, Table A1)(33, 34). Their domain is 20th
-and 21st-century crises, defined as a change in the type, or an increase
-in the intensity, of disruptive interaction with a heightened
-probability of military hostilities that destabilizes states'
-relationships or challenges the structure of the international system
-(3).\footnote{On near crises see (32).} Crises are a significant focus
-of detailed single case studies and case comparisons because they
-provide an opportunity to examine behaviors in IR short of, or at least
-prior to, full conflict (3, 35--42). Case selection was exhaustive based
-on a survey of world news archives and region experts, cross-checked
-against other databases of war and conflict, and non-English sources
-(33, 43). Each narrative was written by consensus by a small number of
-scholars, using a uniform coding scheme, with similar specificity (44).
-The corpus is unique in IR because it is designed to be used in a
-downstream quantitative coding project.
+project (\(n=471\))(SI Appendix, Table A1)(33, 34).\footnote{The Online
+  Appendix is at the
+  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData
+  Github Repository}.} Their domain is 20th and 21st-century crises,
+defined as a change in the type, or an increase in the intensity, of
+disruptive interaction with a heightened probability of military
+hostilities that destabilizes states' relationships or challenges the
+structure of the international system (3).\footnote{On near crises see
+  (32).} Crises are a significant focus of detailed single case studies
+and case comparisons because they provide an opportunity to examine
+behaviors in IR short of, or at least prior to, full conflict (3,
+35--42). Case selection was exhaustive based on a survey of world news
+archives and region experts, cross-checked against other databases of
+war and conflict, and non-English sources (33, 43). Each narrative was
+written by consensus by a small number of scholars, using a uniform
+coding scheme, with similar specificity (44). The corpus is unique in IR
+because it is designed to be used in a downstream quantitative coding
+project.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
-\CSLLeftMargin{1. }
+\CSLLeftMargin{1. }%
 \CSLRightInline{Brecher M (1999) International studies in the twentieth
@@
 \leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
-\CSLLeftMargin{2. }
+\CSLLeftMargin{2. }%
 \CSLRightInline{Reiter D (2015)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
-\CSLLeftMargin{3. }
+\CSLLeftMargin{3. }%
 \CSLRightInline{Brecher M, Wilkenfeld J (1982)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
-\CSLLeftMargin{4. }
+\CSLLeftMargin{4. }%
 \CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The
@@
 \leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
-\CSLLeftMargin{5. }
+\CSLLeftMargin{5. }%
 \CSLRightInline{Palmer G, et al. (2021)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{6. }%
 \CSLRightInline{Gibler DM (2018) \emph{International {Conflicts},
@@
 \leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{7. }%
 \CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
-\CSLLeftMargin{8. }
+\CSLLeftMargin{8. }%
 \CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
-\CSLLeftMargin{9. }
+\CSLLeftMargin{9. }%
 \CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{10. }%
 \CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED
@@
 \leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{11. }%
 \CSLRightInline{Pettersson T, Eck K (2018)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{12. }%
 \CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{13. }%
 \CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov
@@
 \leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{14. }%
 \CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{15. }%
 \CSLRightInline{Kinne BJ (2020)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{16. }%
 \CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{17. }%
 \CSLRightInline{Vabulas F, Snidal D (2021)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{18. }%
 \CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{19. }%
 \CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{20. }%
 \CSLRightInline{Sechser TS (2011)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{21. }%
 \CSLRightInline{Li Q, et al. (2021) A {Comprehensive Survey} on
@@
 \leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{22. }%
 \CSLRightInline{Halterman A (2020) Extracting {Political Events} from
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{23. }%
 \CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{24. }%
 \CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{25. }%
 \CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing
@@
 \leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{26. }%
 \CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{27. }%
 \CSLRightInline{Zhang H, Pan J (2019)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{28. }%
 \CSLRightInline{Steinert-Threlkeld ZC (2019)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{29. }%
 \CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{30. }%
 \CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{31. }%
 \CSLRightInline{James P (2019)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{32. }%
 \CSLRightInline{Iakhnis E, James P (2019)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{33. }%
 \CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{34. }%
 \CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{35. }%
 \CSLRightInline{Holsti OR (1965)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{36. }%
 \CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{37. }%
 \CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{38. }%
 \CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{39. }%
 \CSLRightInline{Gavin FJ (2014)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{40. }%
 \CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{41. }%
 \CSLRightInline{Gaddis JL (1987)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{42. }%
 \CSLRightInline{Brecher M, James P (1988) Patterns of crisis management.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{43. }%
 \CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{44. }%
 \CSLRightInline{Hewitt JJ (2001)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{45. }%
 \CSLRightInline{Miller GA (1995)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{46. }%
 \CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{47. }%
 \CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{48. }%
 \CSLRightInline{Leng RJ, Singer JD (1988)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{49. }%
 \CSLRightInline{McClelland C (1978) World event/interaction survey,
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{50. }%
 \CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{51. }%
 \CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{52. }%
 \CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm},
@@
 \leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{53. }%
 \CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A
@@
 \leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{54. }%
 \CSLRightInline{Merritt RL (1994) Measuring events for international
@@
 \leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{55. }%
 \CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{56. }%
 \CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D
@@
 \leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{57. }%
 \CSLRightInline{Braithwaite A (2010)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{58. }%
 \CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{59. }%
 \CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{60. }%
 \CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{61. }%
 \CSLRightInline{Cormac R, Aldrich RJ (2018)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{62. }%
 \CSLRightInline{Terechshenko Z (2020)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{63. }%
 \CSLRightInline{Cook SJ, Weidmann NB (2019)
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{64. }%
 \CSLRightInline{Wüest B, Lorenzini J (2020) External validation of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{65. }%
 \CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event

### 2022-07-26 replication_paper/arxiv_draft/paper.Rmd
author fix

@@
 # Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-author:
+authors:
   - name: Rex W. Douglass
-    affiliation: a,1,2
+    affiliation: University of California, San Diego
   - name: Thomas Leo Scherer
-    affiliation: a
+    affiliation: University of California, San Diego
   - name: J. Andrés Gannon
-    affiliation: b
+    affiliation: Vanderbilt University
   - name: Erik Gartzke
-    affiliation: a
+    affiliation: University of California, San Diego
   - name: Jon Lindsay
-    affiliation: c
+    affiliation: Georgia Institute of Technology
   - name: Shannon Carcelli
-    affiliation: d
+    affiliation: University of Maryland
   - name: Jonathan Wilkenfeld
-    affiliation: d
+    affiliation: University of Maryland
   - name: David M. Quinn
-    affiliation: e
+    affiliation: University of Maryland
   - name: Catherine Aiken
-    affiliation: f
+    affiliation: Georgetown University
   - name: Jose Miguel Cabezas Navarro
-    affiliation: g
+    affiliation: Universidad Mayor
   - name: Neil Lund
-    affiliation: d
+    affiliation: University of Maryland
   - name: Egle Murauskaite
-    affiliation: h
+    affiliation: University of Maryland
   - name: Diana Partridge
-    affiliation: h
-
-address:
-  - code: a
-    address: Department of Political Science, University of California, San Diego, CA, USA.
-  - code: b
-    address: Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.
-  - code: c
-    address: School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.
-  - code: d
-    address: Department of Government and Politics, University of Maryland, College Park, MD, USA.
-  - code: e
-    address: Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.
-  - code: f
-    address: Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.
-  - code: g
-    address: Society and Health Research Center, Universidad Mayor, Santiago, Chile.
-  - code: h
-    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
-  - code: i
-    address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
-
-corresponding_author:
-  code: 2
-  text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"
+    affiliation: University of Maryland
+
+# address:
+#   - code: a
+#     address: Department of Political Science, University of California, San Diego, CA, USA.
+#   - code: b
+#     address: Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.
+#   - code: c
+#     address: School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.
+#   - code: d
+#     address: Department of Government and Politics, University of Maryland, College Park, MD, USA.
+#   - code: e
+#     address: Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.
+#   - code: f
+#     address: Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.
+#   - code: g
+#     address: Society and Health Research Center, Universidad Mayor, Santiago, Chile.
+#   - code: h
+#     address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
+#   - code: i
+#     address: ICONS Project // START,  University of Maryland, College Park, MD, USA.
+
+# corresponding_author:
+#   code: 2
+#   text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"
 
@@
 #following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
-author_contributions: |
-  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
-  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
+# author_contributions: |
+#   Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
+#   Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
 
@@
 
-acknowledgements: |
-  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
+# acknowledgements: |
+#   We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
 We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
@@
   - \renewcommand{\arraystretch}{0.8}
-  - \AtBeginEnvironment{tabular}{\singlespacing}
+#  - \AtBeginEnvironment{tabular}{\singlespacing}
   - \AtBeginEnvironment{lltable}{\singlespacing}
@@
 
+Acknowledgements {#format .unnumbered}
+========================================
+  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
+We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
+We thank the many undergraduate coders for their patience and dedication.
+Thanks to the Center for Peace and Security Studies and its membership for comments.
+Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
+Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
+This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
+
+Author Contributions {#format .unnumbered}
+========================================
+  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
+  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
+
+&nbsp;
+
 <!-- PNAS lines Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references

### 2022-07-26 replication_paper/arxiv_draft/subpaper.Rmd
author fix

--- 2022-07-26 replication_paper/arxiv_draft/paper.Rmd
@@
 
-<!--- REX Remember to put in a Legend for the Icons ---->
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=19cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-\twocolumn
-
-Corpus  {.unnumbered}
-========================================
-
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).] Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
-59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art {.unnumbered}
-========================================
-
-Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors, and provide a full codebook in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).
-
-The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Additional relevant but dated or too small of an overlap in domain include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
-With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See [@balaliCOfEEComprehensiveOntology2021] for a recent review of ontological depth and availability of Gold Standard example text.]
-
-\clearpage
-\onecolumn
-
-```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
-#lit_review_pull    <- readxl::read_excel(target_file, sheet="DatasetsComparisonLitReview")
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-lit_review_pull <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/14RHRKgQGHj7Zr4_xt4fq2bIE7mDNayLKj89tYmOOfHQ/edit?usp=sharing", 
-                                sheet="DatasetsComparisonLitReview") #%>% janitor::clean_names() 
-dim(lit_review_pull)
-
-library(flextable)
-library(ftExtra)
-library(tidyverse)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-
-#https://davidgohel.github.io/flextable/reference/knit_print.flextable.html#chunk-options
-# NOTE: If one of the citations is degenerate this will throw an error when knitting that is annoying to track down. You have to remove cite by cite to see which one it is.
-set_flextable_defaults(fonts_ignore=TRUE)
-
-lit_review_alt <- lit_review_pull %>% 
-                  mutate(Literature =   paste0(" [",Literature %>% str_replace("; {0,}$","") ,"]")) %>%
-                  mutate(Concept= Concept %>% paste0(Literature)) %>%
-                  mutate(Concept = Concept %>% str_replace(fixed("[NA]"),"") ) %>%
-                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
-                  #dplyr::filter(is.na(group))
-
-n=nrow(lit_review_alt)
-k=ncol(lit_review_alt)
-horizontal = c(1,k)
-r_intro= lit_review_pull$...1 %in% "Domain" %>% sum() #changed to domain
-r_players= ( lit_review_pull$...1 %in% "Players" %>% sum() ) + r_intro
-r_pieces= ( lit_review_pull$...1 %in% "Pieces" %>% sum() ) + r_players
-r_think= ( lit_review_pull$...1 %in% "Think" %>% sum() ) + r_pieces
-r_say= ( lit_review_pull$...1 %in% "Say" %>% sum() ) + r_think
-r_unarmed= ( lit_review_pull$...2 %in% "Unarmed" %>% sum() ) + r_say
-r_armed= ( lit_review_pull$...2 %in% "Armed" %>% sum() ) + r_unarmed
-ft <- NULL
-
-library(officer)
-big_border = fp_border(color="black", width = 2)
-
-bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
-litreview_ft_pnas <- lit_review_alt %>%
-      flextable::as_flextable() %>%
-
-      add_header( 
-                  #"ICB Corpus"="Corpus",
-                  "ICBe"="Events Datasets",
-                  "Phoenix"="Events Datasets",
-                  "Terrier"="Events Datasets",
-                  "ICEWs"="Events Datasets",
-                  "MIDs Incidents"="Events Datasets",
-                  "UCDP-GED"="Events Datasets",
-                  "ICB"="Episodes Datasets",
-                  "COW"="Episodes Datasets",
-                  "MIDs"="Episodes Datasets",
-                  top = T ) %>%
-
-      set_header_labels(
-        values = list("...1" = "" , "...2" = "" ) 
-        ) %>%
-
-      merge_h(part = "header") %>% #it's this merge that's killing us
-
-      #Global Borders
-      flextable::border_remove() %>% 
-      #ok so because of our horizontal merging of headers, we have to manually place a right bar at j=10 2 short of the full width
-      flextable::border_outer( part="all", border = big_border ) %>% #this will have a gap
-      border(j=10:k, i=1 , part="header", border.right = big_border ) %>% #this fills the gap
-      #There's another gap on the bottom left
-      border(j=1, i=(n-15):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
-      border(j=2, i=(n-5):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
-
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #Banding
-      bg( i = bands  , j=3:k, part = "body", bg = "#EFEFEF") %>%
-
-      flextable::rotate(i=2, , j=3:k, rotation="tbrl",part="header") %>%
-      flextable::align(align = "center", part = "body") %>%
-      flextable::align(align = "center", part = "header")   %>%
-
-      flextable::colformat_char(
-          j = 1:ncol(lit_review_alt),
-          na_str = "",
-          prefix = "",
-          suffix = ""
-      ) %>%
-      #Domains
-      hline(i=c(r_intro), border = NULL, part = "body") %>% 
-      merge_at(i = 1:r_intro, j = 1:2, part = "body") %>%  
-      merge_at(i = 4, j = 5:7, part = "body") %>%
-      merge_at(i = 5, j = 5:7, part = "body") %>%
-      merge_at(i = 6, j = 5:7, part = "body") %>%
-      merge_at(i = 7, j = 5:7, part = "body") %>%
-
-      #players
-      hline(i=c(r_players), border = NULL, part = "body") %>% 
-      merge_at(i = (r_intro+1):r_players, j = 1:2, part = "body") %>%  
-      #pieces
-      hline(i=c(r_pieces), border = NULL, part = "body") %>% 
-      merge_at(i = (r_players+1):r_pieces, j = 1:2, part = "body") %>%  
-      #think
-      hline(i=c(r_think), border = NULL, part = "body") %>% 
-      merge_at(i = (r_pieces+1):r_think, j = 1:2, part = "body") %>%  
-      #say
-      hline(i=c(r_say), border = NULL, part = "body") %>% 
-      merge_at(i = (r_think+1):r_say, j = 1:2, part = "body") %>%
-      #Do
-      merge_at(i = (r_say+1):r_armed, j = 1, part = "body") %>%
-
-      #n_unarmed
-      hline(i=c(r_unarmed), border = NULL, part = "body") %>% 
-      merge_at(i = (r_say+1):r_unarmed, j = 2, part = "body") %>%  
-      #n_armed
-      #hline(i=c(r_armed), border = NULL, part = "body") %>% 
-      merge_at(i = (r_unarmed+1):r_armed, j = 2, part = "body") %>%
-
-      #set_table_properties(layout="autofit")  %>%
-      vline( i = 1:2, j = c(3,9), border = NULL, part = "header") %>%
-      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
-      vline( i = 1:(n), j = c(3,9), border = NULL, part = "body")  %>%
-
-      flextable::width( j = 3, width=3) %>% 
-      flextable::width( j = (4):k, width=0.25) %>%
-      flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-
-      flextable::rotate(j=1, rotation="tbrl",part="all") %>%
-      flextable::rotate(j=2, rotation="tbrl",part="all") %>%
-      flextable::width( j = 1:2, width=0.1)  %>%
-      ftExtra::colformat_md(j = 3, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above
-
-#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
-#litreview_ft_pnas
-
-#litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
-litreview_ft_pnas %>% 
-    flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
-   flextable::flextable_to_rmd()
-
-#litreview_ft_pnas   %>% 
-#    #flextable::flextable_to_rmd()
-#    save_as_image(path=here::here("replication_paper", "arxiv_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-```
-
-\clearpage
-\twocolumn
-
-```{r , eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
-n_crisis <- ICBe_events_agreed %>% dplyr::select(crisno) %>% unique() %>% nrow()
-n_sentences <- ICBe_events_agreed %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
-#n_events <- ICBe_events_agreed %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
-#n_events_cuba <- ICBe_events_agreed %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
-n_coders <- icb_long_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()
-
-avg_coders_per_crisis <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)
-
-avg_coders_per_sentence <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-```
-
-ICBe Coding Process {.unnumbered}
-========================================
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-B1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.
-force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
-an offer for the U.S.S.R.
-to remove missiles from Cuba in exchange for the U.S.
-removing missiles from Turkey.
-Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-
-Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.^[Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
-We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
-This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
-
-```{r}
-#We calculate means in the SI appendix on agreement
-means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
-                   group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                   dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)
-
-means_group_keep <- codings_long_agreement %>% filter(value_normalized!='') %>% 
-                    filter(algo1==1) %>%
-                    group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
-                    dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean)
-```
-
-Internal Consistency {.unnumbered}
-========================================
-
-We evaluate the internal validity of the coding process in several ways.
-For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig.
-B3).
-Across all concepts, the Top 1 Tag Agreement was low among novices (`r means_group_any$Novices %>% round(2) %>% scales::percent()`), moderate for experts (`r means_group_any$Experts %>% round(2) %>% scales::percent()`), and high (`r means_group_keep$Experts_keep %>% round(2) %>% scales::percent()`) following the consensus screening procedure.
-
-We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to be low for 20% of sentences- half due to a mismatch between the ontology and the text ("survey doesn't fit event"-45%) and half due to a lack of information or confused writing in the source text ("more knowledge needed"-40%, "confusing sentence"-6%).
-Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig.
-B4).
-Second, as intended agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50%-60%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.
-some more expressive applying many tags per concept while others focused on only the single best match.
-We further observed unintended synonymity, e.g.
-the same information can be framed as either a threat to do something or a promise not to do something.
-
-Case Study Selection {.unnumbered}
-========================================
-
-The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website.
-In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
-
-Recall {.unnumbered}
-========================================
-
-Recall measures the share of desired information recovered by a sequence of coded events, $Pr(E|H)$, and is poorly defined for historical episodes.
-First, there is no genuine ground truth about what occurred, only surviving texts about it.
-Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events.
-The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
-We need a yardstick for history.
-
-Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative.
-For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
-Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts.
-The more accounts that mention a detail, the more central it is to understanding the true historical episode.
-The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing.
-With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
-Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
-
-Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts.
-First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative.
-Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details.
-Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
-the U.S.
-was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
-a long term lease on naval facilities in Crimea.
-Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode level datasets have very low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
-
-```{r cuban case study recall, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#
-#Lit review
-#child=c('ICBEdataset_paper_litreviewtable.Rmd')
-library(tidyverse)
-library(flextable)
-library(ftExtra)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-case_study_cuban <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names() 
-dim(case_study_cuban)
-#case_study_cuban$date <- case_study_cuban$date %>% lapply(FUN=function(x) { ifelse(is.null(x), "", x[[1]] %>% as.character() )   }   ) %>% unlist() %>% as.Date()
-
-paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")
-
-#Replace emoticons with images
-replace_emoticons <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
-        #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-        #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
-        #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
-        #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
-}
-
-temp1 <- case_study_cuban %>% 
-                #filter(!is.na(date)) %>%
-                #head(2) %>%
-                mutate(date=date %>% anytime::anydate()) %>%
-                mutate(year=year(date) %>% as.character() ) %>%
-                mutate(month=month(date) %>% as.character()) %>%
-                mutate(day=day(date) %>% as.character()) %>%
-                mutate(documents = documents %>% as.numeric()) %>%
-                mutate(Rank=rank(-documents, ties.method="first")  ) %>%
-                dplyr::select(Y=year,M=month, D=day, Rank, Event=event, Docs=documents, icb_narrative=icb_narrative, ICBe=ic_be, ICB=icb, MIDs=mids, phoenix=phoenix) %>% 
-                mutate(Event= Event %>%  replace_emoticons) %>% 
-                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
-                mutate(ICB = ifelse(!is.na(ICB) & !ICB %in% 0, "✓", NA)) %>%
-                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0, "✓", NA)) %>%
-                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0, "✓", NA)) %>%
-                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0, "✓", NA)) %>%
-
-                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
-                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
-                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
-                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
-                mutate(YMD=paste(Y,
-                                 M %>% str_pad(2, pad = "0") ,
-                                 D %>% str_pad(2, pad = "0"), 
-                                 sep="-") %>% trimws() %>%
-                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
-                                 str_replace_all("^NA-","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-","") 
-                       ) %>%
-                dplyr::select(-Y,-M,-D) %>%
-                relocate(YMD, .before = Rank) %>%
-                dplyr::select(-Rank)
-dim(temp1)
-
-#banding <- temp %>% mutate(date=as.Date(paste(Y,M,D, sep="-")) %>% as.numeric() %>% as.factor() %>% as.numeric() ) %>% pull(date) %% 2
-banding <- 1:nrow(temp1) %% 2
-k=ncol(temp1)
-ft <- temp1   %>%
-      flextable::as_flextable() %>% 
-      flextable::set_header_labels(values =
-        list(
-              Event = "Ground\nTruth\nEvents",
-              icb_narrative = "ICB Corpus",
-              ICB = "ICB",
-              MIDs = "MIDs",
-              phoenix = "Phoenix"
-             ) ) %>%
-      flextable::width( j = 1, width=0.6)  %>% 
-      #flextable::width( j = 2, width=0.025)  %>%
-      #flextable::width( j = 3, width=0.025)  %>%
-      #flextable::width( j = 5, width=0.025) %>%
-      flextable::width( j = 2, width=3.0)  %>%
-      flextable::width( j = 3, width=0.03) %>%
-      flextable::width( j = 4:k, width=0.15) %>% #icb
-      #merge_v( j = 1,  part = "body", combine = T) %>%
-      #merge_v( j = 3,  part = "body", combine = F) %>%
-      #merge_v( j = 4,  part = "body", combine = F) %>%
-
-      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
-      align(i = 1,  align = "center", part = "header") %>%
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = NULL, j = 1, align = "right", part = "body")  %>%
-      align(i = NULL, j = 2, align = "left", part = "body")  %>%
-      #align(i = NULL, j = 2, align = "center", part = "body")  %>%
-      #align(i = NULL, j = 3, align = "left", part = "body")  %>%
-      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
-      vline(j=c(1,2,3,4,5,6,7),  border = NULL, part = "all") %>%
-      hline(i=c(26,46)) %>%
-      ftExtra::colformat_md(j = 2, part="body") 
-      #ftExtra::colformat_md(j = 6, part="body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-#Ok rather than try to match up we're going to do this by hand now
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names() 
-dim(case_study_crimea)
-
-#Replace emoticons with images
-replace_emoticons_crimea <- function(x){
-      x %>%
-            #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-            #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
-            #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
-            #
-            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) "))
-                            }
-
-rex_date <- function(x){
-  a <- x[1] %>% as.character() %>% unlist()
-  if(is.null(a)){return('')}
-  return(a)
-}
-case_study_crimea$date <- sapply(sapply(case_study_crimea$date, as.character), rex_date)
-temp2 <- case_study_crimea %>% 
-                filter(keep %in% 1) %>%
-                #filter(!is.na(date)) %>%
-                #head(2) %>%
-                mutate(date=date %>% anytime::anydate()) %>%
-                mutate(year=year(date) %>% as.character() ) %>%
-                mutate(month=month(date) %>% as.character()) %>%
-                mutate(day=day(date) %>% as.character()) %>%
-                mutate(n_sources = n_sources %>% as.numeric()) %>%
-                mutate(Rank=rank(-n_sources, ties.method="first")  ) %>%
-                dplyr::select(Y=year,M=month, D=day, Rank,  Event=event, Docs=n_sources, 
-                              icb_narrative=icb_narrative, ICBe=ic_be, MIDs=mids, phoenix, terrier, icews ) %>%  #, ICB=icb, MIDs=mids, phoenix=phoenix
-                mutate(Event= Event %>%  replace_emoticons_crimea) %>%
-                arrange(Y %>% as.numeric() ,M %>% as.numeric()  ,D %>% as.numeric() ) %>%
-                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
-                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
-                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
-                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
-                mutate(YMD=paste(Y,
-                                 M %>% str_pad(2, pad = "0") ,
-                                 D %>% str_pad(2, pad = "0"), 
-                                 sep="-") %>% trimws() %>%
-                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
-                                 str_replace_all("^NA-","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-","") 
-                       ) %>%
-                dplyr::select(-Y,-M,-D) %>%
-                relocate(YMD, .before = Rank) %>%
-                dplyr::select(-Rank) %>% 
-                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
-                mutate(icews = ifelse(!is.na(icews) & !icews %in% 0 , "✓", NA)) %>%
-                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0  , "✓", NA)) %>%
-                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0  , "✓", NA)) %>%
-                mutate(terrier = ifelse(!is.na(terrier) & !terrier %in% 0  , "✓", NA))  %>%
-                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0  , "✓", NA))
-
-dim(temp2)
-
-banding <- 1:nrow(temp2) %% 2
-k=ncol(temp2)
-ft <- temp2  %>%
-      flextable::as_flextable() %>% 
-      flextable::set_header_labels(values =
-        list(
-              Event = "Ground\nTruth\nEvents",
-              icb_narrative = "ICB Corpus",
-              ICBe = "ICBe",
-              MIDs="MIDs",
-              icews_hash = "ICEWS"
-             ) ) %>%
-      flextable::width( j = 1, width=0.6)  %>% 
-      flextable::width( j = 2, width=3.0)  %>%
-      flextable::width( j = 3:k, width=0.15) %>% #icb
-      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
-      align(i = 1,  align = "center", part = "header") %>%
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = NULL, j = 1, align = "right", part = "body")  %>%
-      align(i = NULL, j = 2, align = "left", part = "body")  %>%
-      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
-      vline(j=1:k,  border = NULL, part = "all") %>%
-      #hline(i=c(26,46)) %>%
-      ftExtra::colformat_md(j = 2, part="body") 
-      #ftExtra::colformat_md(j = 6, part="body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_recall.png"),
-                  zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-```
-
-```{r, recall combined, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-temp3 <- temp1 %>% mutate(row=row_number()) %>% full_join(temp2 %>% mutate(row=row_number()), by='row') %>% 
-         mutate(row="") #we're going to use this as our vertical break
-
-n_left <- (!is.na(temp3$Event.x) ) %>% sum()
-n_right <- (!is.na(temp3$Event.y) ) %>% sum()
-
-k=ncol(temp3)
-kleft=ncol(temp1)
-kright=ncol(temp2)
-left_end=kleft
-right_start=left_end+2
-left=c(1:left_end)
-right=c(right_start:k)
-horizontal = c(left,right)
-dates=c(1,right_start)
-events = dates + 1
-checkmarks = c((events[1]+1):left_end , (events[2]+1):k)
-
-library(officer)
-big_border = fp_border(color="black", width = 2)
-
-banding1 <- 1:nrow(temp1) %% 2
-banding2 <- 1:nrow(temp2) %% 2
-ft <- temp3  %>%
-      flextable::as_flextable() %>%
-
-      flextable::line_spacing( space = 1.0, part = "all") %>% # 
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      bg( i = which( banding1==1 ) , part = "body", bg = "#EFEFEF", j=left) %>%
-      bg( i = which( banding2==1 ) , part = "body", bg = "#EFEFEF", j=right) %>%
-
-      #Headers
-      flextable::set_header_labels(values =
-        list(
-              YMD.x = "YMD",
-              Event.x = "Synthetic Narrative",
-              Docs.x = "Mentions",
-              icb_narrative.x = "ICB Corpus",
-              ICBe.x = "ICBe",
-              ICB = "ICB",
-              MIDs.x = "MIDs",
-              phoenix.x = "Phoenix",
-              phoenix.y = "Phoenix",
-              row="",
-              YMD.y = "YMD",
-              Event.y = "Synthetic Narrative",
-              Docs.y = "Mentions",
-              icb_narrative.y = "ICB Corpus",
-              ICBe.y = "ICBe",
-              icews = "ICEWS",
-              MIDs.y = "MIDs",
-              terrier="Terrier"
-             ) ) %>%
-
-      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbass (2014)"), colwidths = c(kleft, 1,kright) ) %>%
-
-      #Global
-      flextable::border_remove() %>% 
-      #Left border
-      border(j=1, i=1:n_left , part="body", border.left =  big_border ) %>% #
-      border(j=1, i=1:2 , part="header", border.left =  big_border ) %>% #
-
-      border(j=left_end, i=1:2 , part="header", border.right =  big_border ) %>% #
-      border(j=left_end, i=1:n_left , part="body", border.right =  big_border ) %>% #
-
-      border(j=1:left_end, i=n_left , part="body", border.bottom =  big_border ) %>% #
-      border(j=1:left_end, i=1 , part="body", border.top =  big_border ) %>% #
-      border(j=1:left_end, i=1:2 , part="header", border.top =  big_border ) %>% #
-
-      #Right border
-      border(j=right_start, i=1:n_right , part="body", border.left =  big_border ) %>% #
-      border(j=k, i=1:n_right , part="body", border.right =  big_border ) %>% #
-
-      border(j=right_start, i=1:2 , part="header", border.left =  big_border ) %>% #
-      border(j=k, i=1:2 , part="header", border.right =  big_border ) %>% #
-      border(j=1:k, i=1 , part="header", border.right =  big_border ) %>% #
-
-      border(j=right_start:k, i=n_right , part="body", border.bottom =  big_border ) %>% #
-      border(j=right_start:k, i=1 , part="body", border.top =  big_border ) %>% #
-      border(j=right_start:k, i=1:2 , part="header", border.top =  big_border ) %>% #
-
-      vline(i=1:n_left, j=1:(left_end-1),  border = NULL, part = "body")  %>%
-      vline(i=1:n_right,j=right_start:(k-1),  border = NULL, part = "body")  %>%
-      vline(i=2, j=1:(left_end-1),  border = NULL, part = "header")  %>%
-      vline(i=2,j=right_start:(k-1),  border = NULL, part = "header")  %>%
-
-      #
-      hline(i=c(26,46), j=left,  border = NULL, part = "body")  %>%
-      hline(i=c(11), j=right,  border = NULL, part = "body")  %>%
-
-      #Header
-      flextable::rotate(i=2, , j=3:left_end, rotation="tbrl", part="header") %>% 
-      flextable::rotate(i=2, , j=(left_end+4):k, rotation="tbrl", part="header") %>%
-
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = 2, j = NULL, align = "center", part = "header")  %>%
-
-      #break
-      flextable::width( j = left_end+1, width=0.25)  %>%
-
-      #Dates
-      flextable::width( j = dates, width=0.6)  %>% 
-      align(i = NULL, j = dates, align = "right", part = "body")   %>%
-
-      #events
-      flextable::width( j = events, width=2.50)  %>%
-      align(i = NULL, j = events, align = "left", part = "body")  %>%
-      ftExtra::colformat_md(j = events, part="body") %>%
-
-      #Checkmarks
-      flextable::width( j = checkmarks, width=0.05) %>%
-      align(i = NULL, j = checkmarks, align = "center", part = "body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#Recall Summary Statistics
-#, icb_narrative_cd=icb_narrative.y, icews_cd=icews_hash
-temp1_long <- temp1 %>% dplyr::select(docs=Docs, ICB_Narrative=icb_narrative, ICBe=ICBe, ICB=ICB,MIDs=MIDs,Phoenix=phoenix) %>% mutate(crisis="Cuban Missile Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
-              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
-
-temp2_long <- temp2 %>% dplyr::select(docs=Docs,ICB_Narrative=icb_narrative,ICBe=ICBe,MIDs=MIDs , Phoenix=phoenix, Terrier=terrier, ICEWS= icews) %>% mutate(crisis="Crimea-Donbas Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
-              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
-
-temp3_long <- bind_rows(temp1_long,temp2_long)
-
-Y_hat <- temp3_long %>% dplyr::select(name) %>% distinct()
-mylogit <- glm(value ~ name, data = temp3_long, family = "binomial")
-Y_hat$fit <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$fit
-Y_hat$se <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$se.fit
-Y_hat$name <- Y_hat$name %>% fct_reorder(Y_hat$fit)
-
-#Y_hat %>% ggplot(aes(name, fit)) +
-#          geom_point(size=4) +
-#          geom_errorbar(aes(ymin = fit-(1.98*se), ymax = fit+(1.98*se)), width = 0.1, linetype="solid") + coord_flip()  + theme_bw() + 
-#          ylab("Mean Recall") + xlab("")
-
-#temp3_long_means <- temp3_long %>% 
-#                    group_by(name) %>%
-#                    summarise(value= value %>%mean() %>% round(2))
-
-#temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + geom_point() +
-#  geom_smooth(method = "glm", method.args = list(family = "binomial"), se=F) + 
-#  ylab("Recall") + xlab("Document Mentions (Log)") +
-#  facet_wrap(~crisis, scales="free_x")
-
-library(geomtextpath)
-temp3_long$crisis <- factor(temp3_long$crisis, levels= temp3_long$crisis %>% as.character() %>% unique() %>% sort() %>% rev() )
-p_recall <- temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + 
-  #geom_point() +
-  geom_textsmooth(aes(label = name), size=3, method = "glm", method.args = list(family = "binomial"), se=F) + 
-  ylab("Recall") + xlab("Document Mentions (Log)") +
-  facet_wrap(~crisis, scales="free_x") +
-  theme_bw() +
-  theme(legend.position="none")
-
-#p_recall
-
-ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'),
-       plot = p_recall ,
-       width=5, height=3.0)
-
-library(magick)
-
-tiger <- image_read(here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'))
-
-combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea_andcounts.png"))
-
-```
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
-\end{figure}
-\clearpage
-\twocolumn
-
-Precision {.unnumbered}
-========================================
-
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, $Pr(H|E)$.
-It does little good to recall a historical event but too vaguely (e.g.
-MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
-ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
-D3 and D4) and all crises on the companion website.
-
-```{r crisis map function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-global_check_overlap=F
-library(igraph)
-library(RColorBrewer)
-library(ggraph)
-target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
-dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
-                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
-
-actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
-                                sheet="actor_translator") #%>% janitor::clean_names() 
-#Convert to a local file for pushing
-#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
-pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
-library(pals); #install.packages('pals')
-pallet <- c(pals::glasbey(),  pals::alphabet2())
-pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
-library(colorspace)
-#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
-pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
-actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
-
-icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){
-
-  icb_events_subset <-  ICBe_events_agreed %>% 
-                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
-                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
-                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
-                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
-                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
-                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
-                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
-                         tidyr::fill(decade, .direction="downup") %>%
-                         tidyr::fill(year, .direction="downup") %>%
-                         tidyr::fill(month, .direction="downup") %>%
-                         tidyr::fill(day, .direction="downup") %>% 
-                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
-                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
-                         arrange(decade, year,month,day) %>%
-                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
-
-  icb_events_subset_diad <- icb_events_subset %>% 
-                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                    sent,
-                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                    thinkkind, sayintkind, dokind,
-                                                    point_in_time_year, point_in_time_month
-                                                    ) %>% distinct() %>%
-                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
-
-  notes=NULL
-  if(prune_rare==T){
-    actor_sent_counts <- 
-      bind_rows(
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
-        ) %>% 
-          na.omit() %>%
-          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
-
-      #New pruning rule, either singletons or actors with less than 10% of the max actor
-      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
-      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
-      if(left_over_count<3){
-        #Skip pruning if it leaves less than 3 actors
-      } else {
-
-        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
-        actor_singleton_labels <- actor_map$value_normalized_label
-        names(actor_singleton_labels) <- actor_map$actor
-        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
-
-        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
-
-        #Easiest thing is to just prune the original data
-        icb_events_subset <- icb_events_subset %>%
-          filter(!(
-                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                say_actor_a %in% singleton_actors |
-                say_actor_b %in% singleton_actors |
-                do_actor_a %in% singleton_actors |
-                do_actor_b %in% singleton_actors 
-          ) )
-
-          #recreate diads again using the new sentence numbers
-          icb_events_subset_diad <- icb_events_subset %>% 
-                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                            sent,
-                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                            thinkkind, sayintkind, dokind,
-                                                            point_in_time_year, point_in_time_month
-                                                            ) %>% distinct() %>%
-                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
-                                        filter(!(
-                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                                              say_actor_a %in% singleton_actors |
-                                              say_actor_b %in% singleton_actors |
-                                              do_actor_a %in% singleton_actors |
-                                              do_actor_b %in% singleton_actors 
-                                        ) ) %>% 
-                                       arrange(sent) %>%
-                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
-      }
-  }
-
-  g <- make_empty_graph(n = 0, directed = TRUE)
-    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
-
-  #Order actors by how many interactions they have together
-  temp <- bind_rows(
-    icb_events_subset_diad  %>% 
-      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
-    icb_events_subset_diad %>% 
-      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
-  )  %>% arrange(actor_1, actor_2) %>% distinct()
-
-  #new plan is to minimize the number of crossovers
-  temp2 <- bind_rows(
-    temp,
-    temp %>% setNames(c("actor_2", "actor_1", "sent"))
-  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
-  rowwise() %>%
-  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
-  arrange(desc(n))
-
-  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
-  rownames(temp2_wide) <- temp2_wide$actor_1
-  temp2_wide$actor_1 <- NULL
-  temp2_wide <- temp2_wide %>% as.matrix()
-  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
-  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
-  hc <- hclust(temp2_wide %>% as.dist(), method="single")
-  diag(temp2_wide) <- 0
-  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
-
-  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
-  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
-
-  #####Nodes
-  icb_events_subset_nodes <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
-            )  %>%
-            filter(!is.na(actor)) %>%
-           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
-            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
-                   y=sent*-1 *100)
-
-  icbe_actor_to_qcode <- icb_events_long %>%
-                         dplyr::filter(crisno==thiscrisis  ) %>% 
-                         filter(varname_normalized %>% str_detect("actor")) %>% 
-                         dplyr::select(value_normalized,value_qcode) %>% 
-                         na.omit() %>% distinct()
-
-  actor_colors_df <- icbe_actor_to_qcode %>%
-    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
-  actor_colors <- actor_colors_df$actor_color
-  names(actor_colors) = actor_colors_df$value_normalized
-
-  date_sineposts <- icb_events_subset_nodes  %>%
-                      mutate(x=max(x)+50) %>%
-                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
-                      na.omit() %>% 
-                      distinct() %>%  
-                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
-                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
-                      group_by(sent) %>%
-                       filter(year_float==min(year_float)) %>%
-                      ungroup() %>% as.data.frame() %>%
-                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
-                      filter(!duplicated(year_float ) ) %>%
-                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
-
-  ####Actor levels
-  icb_events_subset_nodes_min <- 
-    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
-    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
-    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
-    rowwise() #%>%
-    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
-
-  for(i in 1:nrow(icb_events_subset_nodes)){
-    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
-                                actor = icb_events_subset_nodes$actor[i], 
-                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
-  }
-
-  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
-
-  #####Time Edges
-  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
-
-  g <- g %>% 
-       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
-
-  ######Monads
-  icb_events_subset_monad <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            filter(!duplicated(paste(sent,actor,leaf))) %>%
-            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
-            distinct() %>% 
-            group_by(sent,actor,actor_sent) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>%
-            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
-
-  ######Directed
-  icb_events_subset_directed <- 
-            #We need to enumerate all the possibilities
-            bind_rows(
-              #Do alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
-              #Say alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
-              #Say Do
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
-              #Think Do
-              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
-            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            arrange(sent, actor_sent_1,leaf) %>%
-            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
-           #It is actually easier just to rejex out some dupes
-            mutate(leaf = leaf %>%
-                     str_replace("accept\naccept","accept") %>%
-                   str_replace("appeal\nappeal","appeal") %>%
-                   str_replace("reject\nreject","reject") %>%
-                   str_replace("express intent\nexpress intent","express intent") 
-                   ) %>%
-           arrange(sent, actor_sent_1,leaf) %>%
-           filter(actor_sent_1!=actor_sent_2)
-
-  #debug
-  icb_events_subset_directed <- icb_events_subset_directed  %>% 
-           group_by(sent, leaf) %>%
-               mutate(bundle_count=n()) %>%
-               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
-            ungroup()
-
-  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                       timeedge=F, 
-                       leaf=icb_events_subset_directed$leaf2, 
-                       eventedge=T,
-                       actor=icb_events_subset_directed$actor_1,
-                       bundle_count=icb_events_subset_directed$bundle_count
-                       )
-
-  ######Put it all together
-  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
-  p_metro_map <- g %>%  
-          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
-
-          #Event edges
-          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
-          geom_edge_arc(aes(  
-                            colour=actor,
-                            label=leaf,
-                            filter=eventedge==T & bundle_count==1 
-                            ),
-                        label_colour=NA, 
-                        vjust = -0.75,
-                        lineheight = .75,
-                        sep = unit(1, 'mm'), 
-                        edge_width=0.25, 
-                        show.legend = F,
-                        arrow = arrow(length = unit(2, 'mm')),
-                        label_size=3,
-                        check_overlap=global_check_overlap,
-                        start_cap = circle(3, 'mm'),
-                        end_cap = circle(3, 'mm'),
-                        angle_calc = 'along' #,
-                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
-                       ) +
-              #Grouped Edges
-              geom_edge_parallel(aes(  
-                                  colour=actor,
-                                  label=leaf,
-                                  filter=eventedge==T & bundle_count>1
-                                  ),
-                              vjust = -0.75,
-                              lineheight = .75,
-                              sep = unit(5, 'mm'), 
-                              edge_width=0.4,  #0.25
-                              show.legend = F,
-                              arrow = arrow(length = unit(1, 'mm')),
-                              label_size=4,
-                              check_overlap=global_check_overlap,
-                              start_cap = circle(3, 'mm'),
-                              end_cap = circle(3, 'mm'),
-                              angle_calc = 'along'
-                             ) +
-
-              #Time edges
-              geom_edge_link(aes(
-                              edge_colour=actor,
-                              filter=timeedge==T
-                              ),
-                              edge_width=0.1, 
-                              show.legend = F,
-                              check_overlap=global_check_overlap
-                             ) +
-              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
-              #Fatalities
-              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
-
-              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
-              #Add Actor Names
-              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
-                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
-                        check_overlap=global_check_overlap) + #-45
-              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
-              scale_color_manual(values = actor_colors)  +
-              scale_edge_color_manual(values = actor_colors) +
-              #theme_bw() + 
-              #labs( title = plot_title ) +
-              theme_graph() +
-              theme(legend.position = "none") #+
-              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
-
-  if(prune_rare==T & !is.null(notes)){
-     p_metro_map <- p_metro_map + labs(caption = notes)
-  }
-
-  return(p_metro_map)
-}
-
-```
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(cowplot)
-
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-p_precision_combined <- plot_grid(
-            p_196_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
-               p_471_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
-           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )
-
-ratio=1.5
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = height*ratio)
-
-```
-
-\clearpage
-\onecolumn
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-\twocolumn
-
-We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).
-
-We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark.
-Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(flextable)
-library(ftExtra)
-library(tidyverse)
-
-#Load it here before the python reticulate business
-#devtools::install_github("ropenscilabs/umapr")
-#library(umapr)
-
-ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
-
-ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
-                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
-                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
-                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
-                                                 str_replace_all("[0-9]{4}","Entity") %>% #All years with entity
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("[0-9]","") %>%  #replace all digits with blanks
-                                                 str_replace_all(" {1,}"," ")   
-                                               )  #
-
-sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
-                    dplyr::select(sentences_unique_sanitized) %>% 
-                    distinct() %>%
-                    pull(sentences_unique_sanitized) %>% 
-                    unique() %>% na.omit()
-length(sentences_unique ) #12162
-head(sentences_unique)
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-#To set python, set it in ~/.Renviron.
-`use_python()` doesn't seem to work as desired.
-See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
-
-library(reticulate)
-reticulate::py_discover_config()
-
-#use_python("/home/skynet3/anaconda3/bin/python/")
-#use_python("/home/tlscherer/anaconda3/bin/python3")
-
-```
-
-```{python, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
-#pip install -U sentence-transformers
-
-fromscratch=False
-
-if fromscratch:
-  from sentence_transformers import SentenceTransformer
-  import numpy as np
-  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
-  sentence_chars = np.array([len(q) for q in sentences])
-  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
-  len(sentences) #12161 12162
-  n=len(sentences)
-  chunk_length=100
-  n_chunks = int(np.ceil(n/chunk_length)) #can only 
-  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
-  len(sentences_chunks)
-  len(sentences_chunks[0])  
-  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
-  model = SentenceTransformer('paraphrase-mpnet-base-v2')
-  #sentences
-  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
-  #temp = model.encode(sentences_chunks[0])
-  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
-  sentences_embeddings.shape #(12103, 768)
-
-else:
-  print("Skipping")
-
-```
-
-```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-fromscratch = FALSE
-if(fromscratch){
-  sentences_embeddings <- py$sentences_embeddings
-  dim(sentences_embeddings)
-  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
-}else{
-  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
-  dim(sentences_embeddings)
-}
-
-```
-
-```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.  
-embedding <- umapr::umap(sentences_embeddings)
-#plot(embedding[,c('UMAP1','UMAP2')])
-
-sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
-sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()
-
-sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
-sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique
-
-ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
-                                        left_join(sentences_embeded_umap) %>% 
-                                        left_join(sentences_embeded_mpnet)
-
-ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
-
-ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
-                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
-                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
-                                                arrange(UMAP1,UMAP2) %>%
-                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-library(cowplot)
-ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
-
-newcolors <- pals::glasbey()
-
-value_means <- ICBe_events_agreed_markdown_embedded %>% 
-               left_join(icb_events_long %>% 
-                           filter(varname_normalized %>% str_detect('escalate|coop|sayintkind|thinkkind')) %>%
-                           filter(!value_normalized %>% str_detect('^[0-9]*$'))) %>%
-               mutate(color=NA) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("_escalate"),"red",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("_deescalate"),"darkgreen",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("sayintkind"),"brown",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("thinkkind"),"darkorange",color)) %>%
-               dplyr::select(-varname_normalized,-value_qcode,-varname_normalized,-crisis_text,-crisno,-sentence_number_int_aligned,-sentence_span_text,
-                             -actor_set,-value_markdown,-sentence_span_text_clean,-sentences_unique_sanitized) %>% # 
-               group_by(color, value_normalized) %>%
-               mutate(n=n()) %>%
-               filter(n>20) %>% #note require at least 20 examples of that tag
-               dplyr::summarise_all(median) %>%
-              na.omit()
-
-value_normalized_colors <- value_means$color 
-names(value_normalized_colors) = value_means$value
-
-library(ggplot2)
-library(ggrepel)
-p_semantic_embeddings <-
-      ICBe_events_agreed_markdown_embedded %>%
-      ggplot(aes(x=UMAP2,y=UMAP1)) +
-      geom_point(size=0.5, alpha=0.25) + 
-      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
-      theme_bw() +
-      theme(legend.position = "none") + 
-      geom_label(data=value_means,
-                 aes(x=UMAP2,y=UMAP1,
-                     fill = value_normalized %>% as.factor(),
-                     label=value_normalized, size=50
-                     ), size = 2.5,
-                 inherit.aes=F, 
-                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
-                 ) +   
-      #geom_label_repel(data=value_means,
-      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
-      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
-      #           min.segment.length = 0
-      #           ) + 
-      labs(
-          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
-          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
-          caption = ""
-      ) +
-     #scale_color_manual(values = value_normalized_colors) +
-     scale_fill_manual(values = value_normalized_colors) +
-     scale_x_continuous(expand = c(0, 0)) +
-     scale_y_continuous( expand = c(0, 0)) #+
-     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
-     #coord_flip()
-
-ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
-
-#Now do the dendro
-library(ggdendro)
-#We actually need the raw embeddings
-
-#Rex Note to take only one per sentence
-value_normalized_colors <- value_means$color 
-names(value_normalized_colors) = value_means$value_normalized
-
-m <- value_means %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix() 
-rownames(m) <- value_means$value_normalized
-d <- m %>% dist()
-hc <- hclust(d, method="ward.D2")
-library(ggplot2)
-library(ggdendro)
-hcdata <- dendro_data(hc, type = "rectangle")
-p_dendro <- ggplot() +
-            geom_segment(data = segment(hcdata), 
-                         aes(x = x, y = y, xend = xend, yend = yend)
-            ) +
-            geom_text(data = ggdendro::label(hcdata) %>% mutate(color=value_normalized_colors[hcdata$labels$label] ), 
-                      aes(x = x, y = y, label = label, hjust = 0,
-                          color=label %>% as.factor()), 
-                      size = 3
-            ) +
-            coord_flip() +
-            scale_color_manual(values = value_normalized_colors) +
-            scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
-            scale_y_reverse( expand = c(0.1, 0.0, 0.0, 5.0)) +  #limits = c(-10, 10),
-            theme_bw() +
-            theme(legend.position="none")
-#p_dendro
-
-p_combined <- plot_grid(
-  p_semantic_embeddings + xlab("") + ylab("") + 
-  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
-  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
-  p_dendro  + xlab("") + ylab("") + 
-  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
-  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),  
-  labels = c('',''),
-  align = "v", ncol = 2, rel_widths = c(3, 1)  )
-#p_combined
-
-ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
-
-```
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that tag was applied to by the coders.
-The dendrogram shows hiearchical clustering of the tags.
-If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix Figure D3 and D4).
-On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-if(fromscratch){
-
-library(ggplot2)
-library(readr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(ggtext)
-
-icews_clean_subset_top10_day <- read_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
-
-keys <- c("sign formal agreement") #"express accord", #,"declare truce, ceasefire"
-events1 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p1 <- events1 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2013-11-21'), label="Reject EU\nTrade Deal" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-18'), label="Annex Crimea" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-09-06'), label="MINSK I" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2015-02-21'), label="MINSK II" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-keys <- c("reject plan, agreement to settle dispute") #"express accord", #,"declare truce, ceasefire"
-events2 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p2 <- events2 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2013-11-21'), label="Reject EU\nTrade Deal" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-#,"fight with artillery and tanks","Use unconventional violence", "fight with small arms and light weapons","Mobilize or increase armed forces","Demonstrate military or police power", "Violate ceasefire", "Occupy territory"
-keys <- c("use conventional military force")
-events3 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p3 <- events3 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-02-27'), label="Seize Gov Building Crimea" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-02-18'), label="Rus Annex Crimea" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-16'), label="Fighting Donbas" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-04-06'), label="Fighting Donbas" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-09-06'), label="Continued Fighting Donbas" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-#,"Refuse to ease economic sanctions, boycott, or embargo", "Reduce or stop economic assistance","Reduce or stop material aid","Impose blockade, restrict movement", "Reduce or stop military assistance"
-keys <- c("impose embargo, boycott, or sanctions")
-events4 <- icews_clean_subset_top10_day %>% 
-           filter(cameo_label %in% keys) %>% 
-           group_by(cameo_label, dyad_markdown) %>% mutate(n_all=sum(n, na.rm=T)) %>% ungroup() %>%
-           mutate(dyad_markdown = tidytext::reorder_within(dyad_markdown, n_all, within = cameo_label)) 
-p4 <- events4 %>%
-      ggplot( aes(x = date, y = dyad_markdown)) + #
-      geom_tile(fill="lightblue") + theme_bw() +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-03-17'), label="US-EU Sanction Rus" , linetype="dotted", color = "red", size=3) +
-      geomtextpath::geom_textvline(xintercept = as.Date('2014-07-17'), label="EU Sanctions Rus\nRus Sanctions Ukr" , linetype="dotted", color = "red", size=3) +
-      ylab("") + xlab("") +
-      labs(subtitle=keys %>% paste(collapse="; ")) +
-      tidytext::scale_y_reordered()
-
-library(cowplot)
-p_ICEWS <- plot_grid(
-           p1 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           p2 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           p3 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           p4 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
-           #labels = c('Cuban Missiles','Crimea-Donbas'), 
-           align = "v", ncol = 1 , rel_widths = c(1) )
-
-save_plot(file=paste0(here::here(),
-                      '/replication_paper/arxiv_draft/p_precision_icews.png'),
-          p_ICEWS, base_height = 10, base_width = 14)
-
-}
-
-```
-
-However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, [@terechshenkoHotCollarLatent2020] attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
-geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks].
-
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
-We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
-Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
-In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
-\textit{Notes:Unit of analysis is the Dyad-Day.
-Edges <-> indicates undirected dyad and -> indicates directed dyad.
-Top 10 most active dyads per category shown.
-Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-<!--
-286 Sign formal agreement
-Reject 99
-
-crisis.
-ICEWS Precision bad for networks  for 
-See [@althausTotalErrorApproach2022] for 19 types of errors in event data.
-Agreement between ICEWS, GED, and CINEP [@stundalHumanRightsViolations2021]
-ICEWs and 
-ICEWs protest events about 80% precision [@wangGrowingPainsGlobal2016],
-
-Dictionary based NLP systems based on large news corpora produce many thousands events over a short time which are unintelligible from the standpoint of micro or macro precision as analyzed above.
-
-Dictionary methods are effectively topic detectors. Dozens of events about signing a deal with the EU that didn't happen.
-
-Next, we make available visualizations of every datum in ICBe alongside each of its contemporary competitors in full on the companion website.
-For ICBe, we show the original source text alongside an iconographic representation of coded events as in Figure 1.
--->
-
 Conclusion {#format .unnumbered}
@@
 
+Bibliography {#format .unnumbered}
+========================================
 &nbsp;

### 2022-07-26 replication_paper/arxiv_draft/subpaper.tex
author fix

--- 2022-07-26 replication_paper/arxiv_draft/paper.tex
@@
 \author{
+    Rex W. Douglass
+   \\
+    University of California, San Diego \\
+   \\
+  \texttt{} \\
+   \And
+    Thomas Leo Scherer
+   \\
+    University of California, San Diego \\
+   \\
+  \texttt{} \\
+   \And
+    J. Andrés Gannon
+   \\
+    Vanderbilt University \\
+   \\
+  \texttt{} \\
+   \And
+    Erik Gartzke
+   \\
+    University of California, San Diego \\
+   \\
+  \texttt{} \\
+   \And
+    Jon Lindsay
+   \\
+    Georgia Institute of Technology \\
+   \\
+  \texttt{} \\
+   \And
+    Shannon Carcelli
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Jonathan Wilkenfeld
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    David M. Quinn
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Catherine Aiken
+   \\
+    Georgetown University \\
+   \\
+  \texttt{} \\
+   \And
+    Jose Miguel Cabezas Navarro
+   \\
+    Universidad Mayor \\
+   \\
+  \texttt{} \\
+   \And
+    Neil Lund
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Egle Murauskaite
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Diana Partridge
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
   }
@@
 \renewcommand{\arraystretch}{0.8}
-\AtBeginEnvironment{tabular}{\singlespacing}
 \AtBeginEnvironment{lltable}{\singlespacing}
@@
 \usepackage[algo2e]{algorithm2e}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
 \begin{document}
@@
 
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=19cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-\twocolumn
-
-\hypertarget{corpus}{%
-\section*{Corpus}\label{corpus}}
-\addcontentsline{toc}{section}{Corpus}
-
-For our corpus, \(D\), we select a set of unusually high-quality
-historical narratives from the International Crisis Behavior (ICB)
-project (\(n=471\))(SI Appendix, Table A1)(33, 34).\footnote{The Online
-  Appendix is at the
-  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData
-  Github Repository}.} Their domain is 20th and 21st-century crises,
-defined as a change in the type, or an increase in the intensity, of
-disruptive interaction with a heightened probability of military
-hostilities that destabilizes states' relationships or challenges the
-structure of the international system (3).\footnote{On near crises see
-  (32).} Crises are a significant focus of detailed single case studies
-and case comparisons because they provide an opportunity to examine
-behaviors in IR short of, or at least prior to, full conflict (3,
-35--42). Case selection was exhaustive based on a survey of world news
-archives and region experts, cross-checked against other databases of
-war and conflict, and non-English sources (33, 43). Each narrative was
-written by consensus by a small number of scholars, using a uniform
-coding scheme, with similar specificity (44). The corpus is unique in IR
-because it is designed to be used in a downstream quantitative coding
-project.
-
-\hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
-\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing
-State of the
-Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
-\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological
-Coverage, and the Existing State of the Art}
-
-Next we draw informative prior beliefs about the underlying process of
-IR that we expect to govern behavior during historical episodes and
-their conversion to the historical record. We organize our prior beliefs
-along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to
-find in IR and forms the basis for our proposed ontology. We employ a
-metaphor of a chess game, with players (polities, rebel groups, IGOs,
-etc.), pieces (military platforms, civilians, domains), and behaviors
-(think, say, do). Precise sequencing is required to capture gambits
-(sequences of moves) and outcomes (victory, defeat, peace, etc.), while
-precise geo-coding is required to understand the chessboard (medium of
-conflict). We find 472 actors and 117 different behaviors, and provide a
-full codebook in the online material.\footnote{See the Github Repository
-  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
-
-We base our informed priors primarily on two sources of information. The
-first is the extensive existing measurement efforts of IR which we
-provide citations to alongside each concept. Second, we performed
-preliminary natural language processing of the corpus and identified
-named entities and behaviors mentioned in the text. Verbs were matched
-to the most likely definition found in Wordnet (45), tallied, and then
-aggregated into a smaller number hypernyms balancing conceptual detail
-and manageable sparsity for human coding (SI Appendix, Table A2).
-
-The second axis (columns) compares the very high ontological coverage of
-ICBe to existing state of the art systems in production and with global
-coverage. They begin with our contribution ICBe, alongside other
-event-level datasets including CAMEO dictionary lookup based systems
-(Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized
-Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11,
-47).\footnote{Additional relevant but dated or too small of an overlap
-  in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51),
-  SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories
-  in (54) and (55)).} The final set of columns compares episode-level
-datasets beginning with the original ICB project (3, 4, 56); the
-Militarized Interstate Disputes dataset (5, 6, 57, 58), and the
-Correlates of War (8). With the exception of large scale CAMEO
-dictionary based systems, the existing state of the art quantitative
-datasets ignore the vast majority of the information content found in
-international relations.\footnote{See (53) for a recent review of
-  ontological depth and availability of Gold Standard example text.}
-
-\clearpage
-\onecolumn
-
-{[}1{]} 37 17
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.75}
-
-\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
-
-\caption{Ontological coverage of ICBe versus existing State of the Art
-}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\end{longtable}
-
-\clearpage
-\twocolumn
-
-\hypertarget{icbe-coding-process}{%
-\section*{ICBe Coding Process}\label{icbe-coding-process}}
-\addcontentsline{toc}{section}{ICBe Coding Process}
-
-The ICBe ontology follows a hierarchical design philosophy where a
-smaller number of significant decisions are made early on and then
-progressively refined into more specific details (59).\footnote{This
-  process quickly focuses the coder on a smaller number of relevant
-  options while also allowing them to apply multiple tags if the
-  sentence explicitly includes more than one or there is insufficient
-  evidence to choose only one tag. The guided coding process also allows
-  for the possibility that earlier coarse decisions have less error than
-  later fine-grained decisions.} Each coder was instructed to first
-thoroughly read the full crisis narrative and then presented with a
-custom graphical user interface (SI Appendix, Fig. B1). Coders then
-proceeded sentence by sentence, choosing the number of events (0-3) that
-occurred, the highest behavior (thought, speech, or activity), a set of
-players (\(P\)), whether the means were primarily armed or unarmed,
-whether there was an increase or decrease in aggression
-(uncooperative/escalating or cooperative/de-escalating), and finally one
-or more non-mutually exclusive specific activities. Some additional
-details like location and timing information was always collected while
-other details were only collected if appropriate, e.g.~force size,
-fatalities, domains, units, etc. A unique feature of the ontology is
-that thought, speech, and do behaviors can be nested into combinations,
-e.g.~an offer for the U.S.S.R. to remove missiles from Cuba in exchange
-for the U.S. removing missiles from Turkey. Through compounding, the
-ontology can capture what players were said to have known, learned, or
-said about other specific fully described actions.
-
-Each crisis was typically assigned to 2 expert coders and 2 novice
-coders with an additional tie-breaking expert coder assigned to
-sentences with high disagreement.\footnote{Expert coders were graduate
-  students or postgraduates who collaboratively developed the ontology
-  and documentation for the codebook. Undergraduate coders were students
-  who engaged in classroom workshops.} For the purposes of measuring
-intercoder agreement and consensus, we temporarily disaggregate the unit
-of analysis to the Coder-Crisis-Sentence-Tag (n=993,740), where a tag is
-any unique piece of information a coder can associate with a sentence
-such as an actor, date, behavior, etc. We then aggregate those tags into
-final events (n=18,783), using a consensus procedure (SI Appendix,
-Algorithm B2) that requires a tag to have been chosen by at least one
-expert coder and either a majority of expert or novice coders. This
-screens noisy tags that no expert considered possible but leverages
-novice knowledge to tie-break between equally plausible tags chosen by
-experts.
-
-\hypertarget{internal-consistency}{%
-\section*{Internal Consistency}\label{internal-consistency}}
-\addcontentsline{toc}{section}{Internal Consistency}
-
-We evaluate the internal validity of the coding process in several ways.
-For every tag applied we calculate the observed intercoder agreement as
-the percent of other coders who also applied that same tag (SI Appendix,
-Fig. B3). Across all concepts, the Top 1 Tag Agreement was low among
-novices (31\%), moderate for experts (65\%), and high (73\%) following
-the consensus screening procedure.
-
-We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to
-be low for 20\% of sentences- half due to a mismatch between the
-ontology and the text (``survey doesn't fit event''-45\%) and half due
-to a lack of information or confused writing in the source text (``more
-knowledge needed''-40\%, ``confusing sentence''-6\%). Observed
-disagreement varied predictably with self reported confidence (SI
-Appendix, Fig. B4). Second, as intended agreement is higher (75-80\%)
-for questions with fewer options near the root of the ontology compared
-to agreement for questions near the leafs of the ontology (50\%-60\%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.~some
-more expressive applying many tags per concept while others focused on
-only the single best match. We further observed unintended synonymity,
-e.g.~the same information can be framed as either a threat to do
-something or a promise not to do something.
-
-\hypertarget{case-study-selection}{%
-\section*{Case Study Selection}\label{case-study-selection}}
-\addcontentsline{toc}{section}{Case Study Selection}
-
-The remaining two qualities we seek to measure are recall and precision
-of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read
-icongraphic form, and a wide range of visualizations for every case on
-the companion website. In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place
-primarily in the second half of 1962, involved the United States, the
-Soviet Union, and Cuba, and is widely known for bringing the world to
-the brink of nuclear war (hereafter Cuban Missiles). The second is the
-Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily
-in 2014, involved Russia, Ukraine, and NATO, and within a decade
-spiraled into a full scale invasion (herafter Crimea-Donbas). Both cases
-involve a superpower in crisis with a neighbor, initiated by a change
-from a friendly to hostile regime, with implications for economic and
-military security for the superpower, risked full scale invasion, and
-eventually invited intervention by opposing superpowers. We choose these
-cases because they are substantively significant to 20th and 21st
-century international relations, widely known across scientific
-disciplines and popular culture, and are sufficiently brief to evaluate
-in depth.
-
-\hypertarget{recall}{%
-\section*{Recall}\label{recall}}
-\addcontentsline{toc}{section}{Recall}
-
-Recall measures the share of desired information recovered by a sequence
-of coded events, \(Pr(E|H)\), and is poorly defined for historical
-episodes. First, there is no genuine ground truth about what occurred,
-only surviving texts about it. Second, there is no \textit{a priori}
-guide to what information is necessary detail and what is ignorable
-trivia. History suffers from what is known as the Coastline Paradox (60)
---- it has a fractal dimension greater than one such that the more you
-zoom in the more detail you will find about individual events and in
-between every two discrete events. The ICBe ontology is a proposal about
-what information is important, but we need an independent benchmark to
-evaluate whether that proposal is a good one and that allows for
-comparing proposals from event projects that had different goals. We
-need a yardstick for history.
-
-Our strategy for dealing with both problems is a plausibly objective
-yardstick called a synthetic historical narrative. For both case
-studies, we collect a large diverse corpus of narratives spanning
-timelines, encyclopedia entries, journal articles, news reports,
-websites, and government documents. Using natural language processing
-(fully described in SI Appendix, Algorithm C1), we identify details that
-appear across multiple accounts. The more accounts that mention a
-detail, the more central it is to understanding the true historical
-episode. The theoretical motivation is that authors face word limits
-which force them to pick and choose which details to include, and they
-choose details which serve the specific context of the document they are
-producing. With a sufficiently large and diverse corpus of documents, we
-can vary the context while holding the overall episode constant and see
-which details tend to be invariant to context. Intuitively, a high
-quality event dataset should have high recall for context invariant
-details both because of their broader relevance and also because they
-are easier to find in source material.
-
-Synthetic historical narratives for Cuban Missiles (51 events drawn from
-2020 documents) and Crimea-Donbas (30 events drawn from 971 documents)
-appear in Figure 2. Each row represents a detail which appeared in at
-least five documents along with an approximate start date, a hand
-written summary, the number of documents it was mentioned in, and
-whether it could be identified in the text of our ICB corpus, in our
-ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts. First, there is substantial
-variation in which details any one document will choose to include. Our
-ground truth ICB narratives included 17/51 and 23/30 of the events from
-the synthetic narrative, while including other details that are not in
-the synthetic narrative. Second, mentions of a detail across accounts is
-exponentially distributed with context invariant details appearing
-dozens to hundreds of times more than context dependent details. Third,
-crisis start and stop dates are arbitrary and the historical record
-points to many precursor events as necessary detail for understanding
-later events, e.g.~the U.S. was in a \textit{de facto} grey scale war
-with Cuba before it invited Soviet military protection (61) and Ukraine
-provided several security guarantees to Russia that were potentially
-undone, e.g.~a long term lease on naval facilities in Crimea. Fourth, we
-find variation between the two cases. Cuban Missiles has a cleaner
-canonical end with the Soviets agreeing to withdraw missiles while
-Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II)
-but continued fighting. The canonical narrative of Cuban Missile also
-includes high level previously classified details, while the more recent
-Crimea-Donbas case reflects primarily public reporting.
-
-We find substantive variation in recall across systems. Recall for each
-increases in the number of document mentions which is an important sign
-of validity for both them and our benchmark. The one outlier is Phoenix
-which is so noisy that it's flat to decreasing in mentions. The two
-episode level datasets have very low coverage of contextual details. The
-two other dictionary systems ICEWs and Terrier have high coverage, with
-ICEWs outperforming Terrier. ICBe strictly dominates all of the systems
-but ICEWs in recall though we note that the small sample sizes mean
-these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of
-frequently mentioned details giving us confidence in how those summaries
-were constructed, and ICBe lags only slightly behind showing that it
-left very little additional information on the table.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
-\end{figure}
-\clearpage
-\twocolumn
-
-\hypertarget{precision}{%
-\section*{Precision}\label{precision}}
-\addcontentsline{toc}{section}{Precision}
-
-The other side of event measurement is precision, the degree to which a
-sequence of events correctly and usefully describes the information in
-history, \(Pr(H|E)\). It does little good to recall a historical event
-but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a
-blockade, a show of force, and a stalemate) or with too much error
-(e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between
-1995-2019) to be useful for downstream applications. ICBe's ontology and
-coding system is designed to strike a balance so that the most important
-information is recovered accurately but also abstracted to a level that
-is still useful and interpretable. You should be able to lay out events
-of a crisis on a timeline, as in Figure 3, and read off the macro
-structure of an episode from each individual move. We call this
-visualization a crisis map, a directed graph intersected with a
-timeline, and provide crisis maps for every event dataset for each case
-study (SI Appendix, Fig. D3 and D4) and all crises on the companion
-website.
-
-\clearpage
-\onecolumn
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-\twocolumn
-
-We further want to verify individual event codings, which we can do in
-the case of ICBe because each event is mapped to a specific span of
-text. We develop the iconography system for presenting event codings as
-coherent statements that can be compared side by side to the original
-source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI
-Appendix Table D1), and for every case on the companion website. We
-further provide a stratified sample of event codings alongside their
-source text (SI Appendix Table D2).
-
-We find both the visualizations of macro structure and head-to-head
-comparisons of ICBe codings to the raw text to strongly support the
-quality of ICBe, but as with recall we seek a more objective detached
-universal benchmark. Our proposed measure is a reconstruction task to
-see whether our intended ontology can be recovered through only
-unsupervised clustering of sentences they were applied to. Figure 4
-shows the location of every sentence from the ICBe corpus in semantic
-space as embeded using the same large language model as before, and the
-median location of each ICBe event tag applied to those
-sentences.\footnote{We preprocess sentences to replace named entities
-  with a generic Entity token.} Labels reflect the individual leaves of
-the ontology and colors reflect the higher level coerce branch nodes of
-the ontology. If ICBe has high precision, substantively similar tags
-ought to have been applied to substantively similar source text, which
-is what we see both in two dimensions in the main plot and via
-hierarchical clustering on all dimensions in the dendrogram along the
-righthand side.\footnote{Hierchcial clustering on cosine similarity and
-  with Ward's method.}
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that tag was applied to by the coders.
-The dendrogram shows hiearchical clustering of the tags.
-If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
-Finally, how does ICBe's precision compare to the existing state of the
-art? The crisis-maps reveal the episode level datasets like MIDs or the
-original ICB are too sparse and vague to reconstruct the structure of
-the crisis (SI Appendix Figure D3 and D4). On the other end of the
-spectrum, the high recall dictionary based event datasets like Terrier
-and ICEWs produce so many noisy events (several hundreds thousands) that
-even with heavy filtering their crisis maps are completely
-unintelligible. Further, because of copyright issues, none of these
-datasets directly provide the original text spans making event level
-precision difficult to verify.
-
-However, given their high recall on our task and the global and
-real-time coverage of dictionary based event systems, we want to take
-seriously the possibility that some functional transformation could
-recover the precision of ICBe. For example, (62) attempts to correct for
-the mechanically increasing amount of news coverage each year by
-detrending violent event counts from Phoenix using a human coded
-baseline. Others have focused on verifying precision for ICEWs on
-specific subsets of details against known ground truths,
-e.g.~geolocation (63), protest events (80\%) (64), anti-government
-protest networks (46.1\%) (65).
-
-We take the same approach here in Figure 5, selecting four specific
-CAMEO event codings and checking how often they reflect a true real
-world event. We choose four event types around key moments in the
-crisis. The start of the crisis revolves around Ukraine backing out of
-trade deal with the EU in favor of Russia, but ``sign formal agreement''
-events act more like a topic detector with dozens of events generated by
-discussions of a possible agreement but not the actual agreement which
-never materialized. The switch is caught by the ``reject plan, agreement
-to settle dispute'', but also continues for Victor Yanukovych for even
-after he was removed from power because of articles retroactively
-discussing the cause of his of his removal. Events for ``use
-conventional military force'' capture a threshold around the start of
-hostilities and who the participants were but not any particular battles
-or campaigns. Likewise, ``impose embargo, boycott, or sanctions''
-captures the start of waves of sanctions and from who but are
-effectively constantly as the news coverage does not distinguish between
-subtle changes or additions. In sum, dictionary based methods on news
-corpora tend to have high recall because they parse everything in the
-news, but for the same reason their specificity for most event types is
-too low to back out individual chess like sequencing that ICBe aims to
-record.
-
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
-\textit{Notes:Unit of analysis is the Dyad-Day.
-Edges <-> indicates undirected dyad and -> indicates directed dyad.
-Top 10 most active dyads per category shown.
-Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
 \hypertarget{format}{%
@@
 the data introduced here (www.crisisevents.org).
+
+\hypertarget{format}{%
+\section*{Acknowledgements}\label{format}}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+We thank the ICB Project and its directors and contributors for their
+foundational work and their help with this effort. We make special
+acknowledgment of Michael Brecher for helping found the ICB project in
+1975, creating a resource that continues to spark new insights to this
+day. We thank the many undergraduate coders for their patience and
+dedication. Thanks to the Center for Peace and Security Studies and its
+membership for comments. Special thanks to Rebecca Cordell, Philip
+Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for
+generous feedback. Thank you to the cPASS research assistants that
+contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano
+Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna
+Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and
+Ruixuan Zhang. This project was supported by a grant from the Office of
+Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles
+Koch Foundation's support for the Center for Peace and Security Studies.
+
+\hypertarget{format}{%
+\section*{Author Contributions}\label{format}}
+\addcontentsline{toc}{section}{Author Contributions}
+
+Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.;
+Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D.,
+T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N.,
+D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing -
+Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D.,
+J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.;
+Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
+Funding Acquisition: E.G., J.L.
+
+\hypertarget{format}{%
+\section*{Bibliography}\label{format}}
+\addcontentsline{toc}{section}{Bibliography}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D
-(2017) \emph{International {Crisis Behavior Data Codebook}} Available
-at: \url{http://sites.duke.edu/icbdata/data-collections/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of
-{Crisis}} ({University of Michigan Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Holsti OR (1965)
-\href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The
-American Political Science Review} 59(2):365--378.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June}
-24-30, 1950} ({Free Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision:
-{Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among
-nations: {Bargaining} and decision making in international crises}
-({Princeton University Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Gavin FJ (2014)
-\href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security
-Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies}
-37(2):319--331.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American}
-foreign policy: {Theory} and practice} ({Columbia University Press}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Gaddis JL (1987)
-\href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}:
-{Historians}, {Political Scientists}, and the {Enrichment} of {Security
-Studies}}. \emph{International Security} 12(1):3--21.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management.
-\emph{Journal of Conflict Resolution} 32(3):426--456.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of
-{Asian} security: {Using Europe} to study {Asia}. \emph{Journal of
-Global Security Studies} 4(3):393--401.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Hewitt JJ (2001)
-\href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International
-Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to
-{Teach Conflict} and {Crisis Analysis}}. \emph{Int Stud Perspect}
-2(4):371--383.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Miller GA (1995)
-\href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical
-database for {English}}. \emph{Commun ACM} 38(11):39--41.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA
-(2019) Cline {Center Historical Phoenix Event Data Variable
-Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP}
-georeferenced event dataset. \emph{Journal of Peace Research}
-50(4):523--532.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Leng RJ, Singer JD (1988)
-\href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}:
-{The BCOW Typology} and {Its Applications}}. \emph{International Studies
-Quarterly} 32(2):155--173.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{McClelland C (1978) World event/interaction survey,
-1966-1978. \emph{WEIS Codebook ICPSR} 5211.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events}
-of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968:
-{Version} 1.
-doi:\href{https://doi.org/10.3886/ICPSR05205.V1}{10.3886/ICPSR05205.V1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}:
-{Computer-aided} system for analysis of local conflicts. \emph{MIT
-Center for International Studies, Cambridge}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm},
-{Hierarchical}, and {Contextually-Sensitive International Conflict
-Dataset}, 1937-1985: {Version} 1.
-doi:\href{https://doi.org/10.3886/ICPSR02292.V1}{10.3886/ICPSR02292.V1}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A
-Comprehensive Ontology} for {Event Extraction} from text.
-doi:\href{https://doi.org/10.48550/arXiv.2107.10326}{10.48550/arXiv.2107.10326}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Merritt RL (1994) Measuring events for international
-political analysis. \emph{International Interactions} 20(1-2):3--33.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas}
-event data system project. \emph{The political methodologist}
-14(1):2--8.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D
-International {Crisis Behavior Data Codebook}, {Version} 12. 69.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Braithwaite A (2010)
-\href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing}
-the {Militarized Interstate Dispute Location} dataset}. \emph{Journal of
-Peace Research} 47(1):91--98.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized
-Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University
-College London}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain
-knowledge: Using hierarchies to improve deep classifiers. Available at:
-\url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of
-nature} ({Freeman}, {New York}).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Cormac R, Aldrich RJ (2018)
-\href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert
-action and implausible deniability}. \emph{International Affairs}
-94(3):477--494.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Terechshenko Z (2020)
-\href{https://doi.org/10.1177/0022343320962546}{Hot under the collar:
-{A} latent measure of interstate hostility}. \emph{Journal of Peace
-Research} 57(6):764--776.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Cook SJ, Weidmann NB (2019)
-\href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}:
-{Improving Event Analysis} with {Report-Level Data}}. \emph{American
-Journal of Political Science} 63(1):250--264.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of
-protest event analysis. \emph{Contention in times of crisis: Recession
-and political protest in thirty Euro-pean countries}:49--78.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event
-Data}: {Evidence} from the {ICEWS Dataset}.}
-
 \end{CSLReferences}

### 2022-08-05 replication_paper/pnas_draft/appendix.Rmd
pnas_prep_1

--- 2022-07-25 replication_paper/pnas_draft/appendix.Rmd
@@
 ---
-title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"
-
-#https://bookdown.org/yihui/bookdown/a-single-document.html
-#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
-#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
-#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
+title: "Introducing ICBe: Supplementary Information"
+
+csl: pnas.csl
+bibliography: paper.bib
+biblio-style: unsrt
 output: 
   pdf_document:
-    toc: yes
-    latex_engine: xelatex
-    keep_tex:  true
-
-bibliography: ICBintro.bib
-
-#Disabled several the caused errors
+    toc: true
+
 header-includes:
@@
 #  - \usepackage{tinytex}
-  - \usepackage[backend=bibtex]{biblatex} #if I comment it out and don't have it'll throw an error
-#  - \usepackage{natbib} #added for latex citation within huxtable
   - \usepackage[utf8]{inputenc}
@@
   - \usepackage{ctable} # added for demo
-
+#  - \usepackage{natbib} #added for latex citation within huxtable
+#  - \usepackage{biblatex} #added for latex citation within huxtable
   - \usepackage{booktabs}
@@
 # Appendix A Corpus and Cases
-\hphantom{em}
 ## Table A1: ICBe Crises and Summary Information {#app:crises}
-\hphantom{em}
 
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft1.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft1.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft2.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft2.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft3.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft3.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft4.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft4.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft5.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft5.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft6.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft6.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft7.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft7.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft8.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft8.png"), zoom=1)
 
@@
 \begin{figure}[H]
-\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft1.png"}}
+\caption{ICBe Crises Summary Statistics}
+\centering{\includegraphics[ height=19cm]{"./crisis_text_counts_ft1.png"}}
 \end{figure}
+\clearpage
 
@@
 \end{figure}
+\clearpage
 
@@
 
+```{r}
+ # py_install("tqdm")
+ # py_install("pandas")
+ # py_install("transformers")
+```
+
 ```{python embed glosses, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
@@
 
+# can install python packages in R using code chunk above
+
+fromscratch=False
+
+if fromscratch:
   import torch
@@
   from transformers.pipelines.pt_utils import KeyDataset
-
-fromscratch=False
-
-if fromscratch:
   from sentence_transformers import SentenceTransformer
@@
   glosses_embeddings.shape #(4977, 768)
-
 else:
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_concept.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_concept.png'), 
                   plot = p_percent_chose_tag_by_concept, width=8, height=8)
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_confidence.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_confidence.png'), 
                   plot = p_percent_chose_tag_by_confidence, width=8, height=6)
@@
 \end{figure}
-
 \clearpage
@@
 \end{algorithm}
-
 \clearpage
@@
 
-ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-\clearpage
-
 # Appendix D: Precision
-
-\hphantom{em}
-
-\clearpage
-
 ## Figure D1 Crimea-Donbos 
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
 
@@
 \caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
-\centering{\includegraphics[height=21cm]{./case_study_crimea_precision_part1.png}}
+\centering{\includegraphics[height=19cm]{./case_study_crimea_precision_part1.png}}
 \end{figure}
@@
                                   padding( padding = 1, part = "all") %>% 
-                                  bg( i = which( ((1:56) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  bg( i = which( ((1:22) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                   ftExtra::colformat_md(j = 5, part="body")
 
-ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision1.png"), zoom=1) #
+ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision1.png"), zoom=1) #
 
 ft_sample_precision_precision2 <- temp_sample %>% 
-                                  filter(row_number()>=57) %>%
+                                  filter(row_number() %in% 23:54) %>%
                                   dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
@@
                                   padding( padding = 1, part = "all") %>% 
-                                  bg( i = which( ((1:59) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  bg( i = which( ((23:54) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                   ftExtra::colformat_md(j = 5, part="body")
 
-ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision2.png"), zoom=1) #
+ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision2.png"), zoom=1) #
+
+ft_sample_precision_precision3 <- temp_sample %>% 
+                                  filter(row_number() %in% 55:90) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((55:90) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision3.png"), zoom=1) #
+
+ft_sample_precision_precision4 <- temp_sample %>% 
+                                  filter(row_number() %in% 91:115) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((91:115) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision4.png"), zoom=1) #
 
@@
 \centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision2.png"}}
+\end{figure}
+\clearpage
+
+\hphantom{em}
+\begin{figure}[H]
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision3.png"}}
+\end{figure}
+\clearpage
+
+\hphantom{em}
+\begin{figure}[H]
+\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision4.png"}}
 \end{figure}
@@
     print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_icb_metro_plot_",thiscrisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icb_metro_plot_",thiscrisis,".Rds")
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_mids_metro_plot_",thiscrisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_mids_metro_plot_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icews_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
 
@@
 
+fromscratch=F
+if(fromscratch){
+
 ## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.Rds') 
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
   ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_penta_196.Rds')
 subtitle="Phoenix Dyadic Events"
@@
     )
-#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_196_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_196_combined.png'),
           p_196_combined, base_height = 12, base_width = 20)
@@
 #\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
+}
 ```
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_196.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_196.png'),
+  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_phoenix_plot_lv0_196.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_lv0_196.png'),
             p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 
+fromscratch=F
+if(fromscratch){
+
 library(ggplot2)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_471.Rds') 
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_471.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_penta_471.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_terrier_plot_penta_471.Rds')
 subtitle="Terrier Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icews_plot_penta_471.Rds')
 p_471_icews <- readRDS(save_file)
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_471_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_471_combined.png'),
           p_471_combined, base_height = 12, base_width = 25)
+}
 
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_471.png'),
+  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_phoenix_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_lv0_471.png'),
             p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_terrier_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_lv0_471.png'),
+  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_terrier_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_terrier_plot_lv0_471.png'),
             p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_icews_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_lv0_471.png'),
+  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_icews_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icews_plot_lv0_471.png'),
             p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)

### 2022-08-05 replication_paper/pnas_draft/paper.tex
pnas_prep_1

--- 2022-07-23 replication_paper/pnas_draft/paper.tex
@@
-\documentclass[9pt,twocolumn,twoside,]{pnas-new}
-
-% Use the lineno option to display guide line numbers if required.
-% Note that the use of elements such as single-column equations
-% may affect the guide line number alignment.
-
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
+\documentclass{article}
+
+\usepackage{arxiv}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{graphicx}
+
+\title{Introducing ICBe: Very High Recall and Precision Event Extraction
+from Narratives about International Crises}
+
+\author{
+    Rex W. Douglass
+   \\
+    University of California, San Diego \\
+   \\
+  \texttt{} \\
+   \And
+    Thomas Leo Scherer
+   \\
+    University of California, San Diego \\
+   \\
+  \texttt{} \\
+   \And
+    J. Andrés Gannon
+   \\
+    Vanderbilt University \\
+   \\
+  \texttt{} \\
+   \And
+    Erik Gartzke
+   \\
+    University of California, San Diego \\
+   \\
+  \texttt{} \\
+   \And
+    Jon Lindsay
+   \\
+    Georgia Institute of Technology \\
+   \\
+  \texttt{} \\
+   \And
+    Shannon Carcelli
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Jonathan Wilkenfeld
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    David M. Quinn
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Catherine Aiken
+   \\
+    Georgetown University \\
+   \\
+  \texttt{} \\
+   \And
+    Jose Miguel Cabezas Navarro
+   \\
+    Universidad Mayor \\
+   \\
+  \texttt{} \\
+   \And
+    Neil Lund
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Egle Murauskaite
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+   \And
+    Diana Partridge
+   \\
+    University of Maryland \\
+   \\
+  \texttt{} \\
+  }
 
@@
 \usepackage{hyperref}
-
-\templatetype{pnasresearcharticle}  % Choose template
-
-\title{Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises}
-
-\author[a,1,2]{Rex W. Douglass}
-\author[a]{Thomas Leo Scherer}
-\author[b]{J. Andrés Gannon}
-\author[a]{Erik Gartzke}
-\author[c]{Jon Lindsay}
-\author[d]{Shannon Carcelli}
-\author[d]{Jonathan Wilkenfeld}
-\author[e]{David M. Quinn}
-\author[f]{Catherine Aiken}
-\author[g]{Jose Miguel Cabezas Navarro}
-\author[d]{Neil Lund}
-\author[h]{Egle Murauskaite}
-\author[h]{Diana Partridge}
-
-  \affil[a]{Department of Political Science, University of California, San Diego, CA, USA.}
-  \affil[b]{Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.}
-  \affil[c]{School of Cybersecurity and Privacy \textbar{} Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.}
-  \affil[d]{Department of Government and Politics, University of Maryland, College Park, MD, USA.}
-  \affil[e]{Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.}
-  \affil[f]{Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.}
-  \affil[g]{Society and Health Research Center, Universidad Mayor, Santiago, Chile.}
-  \affil[h]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
-  \affil[i]{ICONS Project // START, University of Maryland, College Park, MD, USA.}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Douglass}
-
-% Please add here a significance statement to explain the relevance of your work
-\significancestatement{Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
-Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
-This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods.
-It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.}
-
-\authorcontributions{Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D., J.A.G., E.G., T.L.S.;
-Visualization: R.W.D., T.L.S.; Supervision: E.G.; Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.}
-
-\authordeclaration{Please declare any conflict of interest here.}
-
-\correspondingauthor{\textsuperscript{2} To whom correspondence should be addressed. E-mail: \href{mailto:rexdouglass@gmail.com}{\nolinkurl{rexdouglass@gmail.com}}}
-
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
- \keywords{  Diplomacy |  War |  Crises |  International Affairs |  Computational Social Science  }
+\begin{document}
+\maketitle
 
 \begin{abstract}
-How do international crises unfold?
-We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
-We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
-We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
-We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+How do international crises unfold? We conceptualize of international
+relations as a strategic chess game between adversaries and develop a
+systematic way to measure pieces, moves, and gambits accurately and
+consistently over a hundred years of history. We introduce a new
+ontology and dataset of international events called ICBe based on a very
+high-quality corpus of narratives from the International Crisis Behavior
+(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
+precision than existing state of the art datasets and conduct two
+detailed case studies of the Cuban Missile Crisis (1962) and
+Crimea-Donbas Crisis (2014). We further introduce two new event
+visualizations (event icongraphy and crisis maps), an automated
+benchmark for measuring event recall using natural language processing
+(sythnetic narratives), and an ontology reconstruction task for
+objectively measuring event precision. We make the data, online
+appendix, replication material, and visualizations of every historical
+episode available at a companion website www.crisisevents.org and the
+github repository.
 \end{abstract}
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
-
-\begin{document}
-
-% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
-% You should only change this length when you've finalised the article contents.
-\verticaladjustment{-2pt}
-
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
-% If your first paragraph (i.e.
-with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
-If this is the case, add \parshape=0 to the end of the list environment.
-
-\acknow{We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-We thank the many undergraduate coders for their patience and dedication.
-Thanks to the Center for Peace and Security Studies and its membership for comments.
-Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
-Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.}
-
-If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
-In other words, what is the entropy of international relations?
-This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive (1, 2).
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.\footnote{See work on crises (3, 4), militarized disputes (5--7), wars (8, 9), organized violence (10, 11), political violence (12), sanctions (13), trade (14), and international agreements (15--17), dispute resolution (17, 18), and diplomacy (19, 20).} With improvements in natural language processing, more open-ended efforts have sought to capture entire unstructured streams of international events drawn from news reports.\footnote{See (21); (22); (23); (24); (25); (26).
-On event-extraction from images and social-media see (27) and (28).} How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations.
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises (1, 29--32).
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
-We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
-The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision.
-A final section concludes.
+\keywords{
+    Diplomacy
+   \and
+    War
+   \and
+    Crises
+   \and
+    International Affairs
+   \and
+    Computational Social Science
+  }
+
+\twocolumn
+
+If we could record every important interaction between countries in all
+of diplomacy, military conflict, and international political economy,
+how much unique information would this chronicle amount to, and how
+surprised would we be to see something new? In other words, what is the
+entropy of international relations? This record could in principle be
+unbounded, but the central conceit of social science is that there are
+structural regularities that limit what actors can do, their best
+options, and even which actors are likely to survive (1, 2). If so, then
+these events can be systematically measured, and accordingly, massive
+effort is expended in social science attempting to record these
+regularities.\footnote{See work on crises (3, 4), militarized disputes
+  (5--7), wars (8, 9), organized violence (10, 11), political violence
+  (12), sanctions (13), trade (14), and international agreements
+  (15--17), dispute resolution (17, 18), and diplomacy (19, 20).} Thanks
+to improvements in natural language processing, more open-ended efforts
+have begun to capture entire unstructured streams of events from
+international news reports.\footnote{See (21); (22); (23); (24); (25);
+  (26). On event-extraction from images and social-media see (27) and
+  (28).} How close these efforts are to accurately measuring all or even
+most of what is essential in international relations is an open
+empirical question, one for which we provide new evidence here.
+
+Our contribution is a high coverage ontology and event dataset for key
+historical episodes in 20th and 21st-century international relations. We
+develop a large, flexible ontology of international events with the help
+of both human coders and natural language processing. We apply it
+sentence-by-sentence to an unusually high-quality corpus of historical
+narratives of international crises (1, 29--32). The result is a new
+lower bound estimate of how much actually happens between states during
+pivotal historical episodes. We then develop several methods for
+objectively gauging how well these event codings reconstruct the
+information contained in the original narrative. We conclude by
+benchmarking our event codings against several current state-of-the-art
+event data collection efforts. We find that existing systems produce
+sequences of events that do not contain enough information to
+reconstruct the underlying historical episode. The underlying
+fine-grained variation in international affairs is unrecognizable
+through the lens of current quantification efforts.
+
+This is a measurement paper that makes the following argument --- there
+is a real-world unobserved latent concept known as international
+relations, we propose a method for systematically measuring it, we
+successfully apply this method producing a new large scale set of
+measurements, those measurements exhibit several desirable kinds of
+internal and external validity, and those measurements out-perform other
+existing approaches. The article organizes that argument into eight
+sections: task definition; corpus; priors/existing state of the art;
+ICBe coding process; internal consistency; case study selection; recall;
+and precision. A final section concludes.
 
@@
 
-For our corpus, \(D\), we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project (\(n=471\))(SI Appendix, Table A1)(33, 34).
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system (3).\footnote{On near crises see (32).} Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict (3, 35--42).
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources (33, 43).
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity (44).
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
+For our corpus, \(D\), we select a set of unusually high-quality
+historical narratives from the International Crisis Behavior (ICB)
+project (\(n=471\))(SI Appendix, Table A1)(33, 34).\footnote{The Online
+  Appendix is at the
+  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData
+  Github Repository}.} Their domain is 20th and 21st-century crises,
+defined as a change in the type, or an increase in the intensity, of
+disruptive interaction with a heightened probability of military
+hostilities that destabilizes states' relationships or challenges the
+structure of the international system (3).\footnote{On near crises see
+  (32).} Crises are a significant focus of detailed single case studies
+and case comparisons because they provide an opportunity to examine
+behaviors in IR short of, or at least prior to, full conflict (3,
+35--42). Case selection was exhaustive based on a survey of world news
+archives and region experts, cross-checked against other databases of
+war and conflict, and non-English sources (33, 43). Each narrative was
+written by consensus by a small number of scholars, using a uniform
+coding scheme, with similar specificity (44). The corpus is unique in IR
+because it is designed to be used in a downstream quantitative coding
+project.
 
 \hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
-\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
-\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art}
-
-Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find 464 actors and 117 different behaviors, and provide a full codebook in the online material.\footnote{See the Github Repository \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet (45), tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).
-
-The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11, 47).\footnote{Additional relevant but dated or too small of an overlap in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51), SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories in (54) and (55)).} The final set of columns compares episode-level datasets beginning with the original ICB project (3, 4, 56); the Militarized Interstate Disputes dataset (5, 6, 57, 58), and the Correlates of War (8).
-With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.\footnote{See (53) for a recent review of ontological depth and availability of Gold Standard example text.}
+\section*{Prior Beliefs about IR, Ontological Coverage, and the Existing
+State of the
+Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
+\addcontentsline{toc}{section}{Prior Beliefs about IR, Ontological
+Coverage, and the Existing State of the Art}
+
+Next we draw informative prior beliefs about the underlying process of
+IR that we expect to govern behavior during historical episodes and
+their conversion to the historical record. We organize our prior beliefs
+along two overarching axes, summarized in detail by Table 1.
+
+The first axis (rows) represents the types of information we expect to
+find in IR and forms the basis for our proposed ontology. We employ a
+metaphor of a chess game, with players (polities, rebel groups, IGOs,
+etc.), pieces (military platforms, civilians, domains), and behaviors
+(think, say, do). Precise sequencing is required to capture gambits
+(sequences of moves) and outcomes (victory, defeat, peace, etc.), while
+precise geo-coding is required to understand the chessboard (medium of
+conflict). We find 472 actors and 117 different behaviors, and provide a
+full codebook in the online material.\footnote{See the Github Repository
+  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
+
+We base our informed priors primarily on two sources of information. The
+first is the extensive existing measurement efforts of IR which we
+provide citations to alongside each concept. Second, we performed
+preliminary natural language processing of the corpus and identified
+named entities and behaviors mentioned in the text. Verbs were matched
+to the most likely definition found in Wordnet (45), tallied, and then
+aggregated into a smaller number hypernyms balancing conceptual detail
+and manageable sparsity for human coding (SI Appendix, Table A2).
+
+The second axis (columns) compares the very high ontological coverage of
+ICBe to existing state of the art systems in production and with global
+coverage. They begin with our contribution ICBe, alongside other
+event-level datasets including CAMEO dictionary lookup based systems
+(Historical Phoenix (46); ICEWS (24, 25); Terrier (26)), the Militarized
+Interstate Disputes Incidents dataset, and the UCDP-GED dataset (10, 11,
+47).\footnote{Additional relevant but dated or too small of an overlap
+  in domain include BCOW (48), WEIS (49), CREON (50), CASCON (51),
+  SHERFACS (52), Real-Time Phoenix (23), and COfEE (53) (see histories
+  in (54) and (55)).} The final set of columns compares episode-level
+datasets beginning with the original ICB project (3, 4, 56); the
+Militarized Interstate Disputes dataset (5, 6, 57, 58), and the
+Correlates of War (8). With the exception of large scale CAMEO
+dictionary based systems, the existing state of the art quantitative
+datasets ignore the vast majority of the information content found in
+international relations.\footnote{See (53) for a recent review of
+  ontological depth and availability of Gold Standard example text.}
 
@@
 
-We investigated event extraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal validity (e.g.~intercoder agreement) and external validity (i.e.~matching source material in both micro-details at the sentence level and macro-details spanning full historical episodes).
-Further, these codings perform much better in terms of recall, precision, coverage, and overall coherence in capturing these historical episodes than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.~escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
-
-\showmatmethods
-\showacknow
-\pnasbreak
+We investigated event abstraction from narratives describing key
+historical episodes in international relations. We synthesized a prior
+belief about the latent unobserved phenomena that drive these events in
+international relations and proposed a mapping to observable concepts
+that enter into the observed historical record. We designed an ontology
+with high coverage over those concepts and developed a training
+procedure and technical stack for human coding of historical texts.
+Multiple validity checks find the resulting codings have high internal
+validity (e.g.~intercoder agreement) and external validity
+(i.e.~matching source material in both micro-details at the sentence
+level and macro-details spanning full historical episodes). Further,
+these codings perform much better in terms of recall, precision,
+coverage, and overall coherence in capturing these historical episodes
+than existing event systems used in international relations.
+
+We release several open-source products along with supporting code and
+documentation to further advance the study of IR, event extraction, and
+natural language processing. The first is the International Crisis
+Behavior Events (ICBe) dataset, an event-level aggregation of what took
+place during the crises identified by the ICB project. These data are
+appropriate for statistical analysis of hard questions about the
+sequencing of events (e.g.~escalation and de-escalation of conflicts).
+Second, we provide a coder-level disaggregation with multiple codings of
+each sentence by experts and undergrads that allows for the introduction
+of uncertainty and human interpretation of events. Further, we release a
+direct mapping from the codings to the source text at the sentence level
+as a new resource for natural language processing. Finally, we provide a
+companion website that incorporates detailed visualizations of all of
+the data introduced here (www.crisisevents.org).
+
+\hypertarget{format}{%
+\section*{Acknowledgements}\label{format}}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+We thank the ICB Project and its directors and contributors for their
+foundational work and their help with this effort. We make special
+acknowledgment of Michael Brecher for helping found the ICB project in
+1975, creating a resource that continues to spark new insights to this
+day. We thank the many undergraduate coders for their patience and
+dedication. Thanks to the Center for Peace and Security Studies and its
+membership for comments. Special thanks to Rebecca Cordell, Philip
+Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for
+generous feedback. Thank you to the cPASS research assistants that
+contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano
+Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna
+Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and
+Ruixuan Zhang. This project was supported by a grant from the Office of
+Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles
+Koch Foundation's support for the Center for Peace and Security Studies.
+
+\hypertarget{format}{%
+\section*{Author Contributions}\label{format}}
+\addcontentsline{toc}{section}{Author Contributions}
+
+Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.;
+Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D.,
+T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N.,
+D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing -
+Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D.,
+J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.;
+Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
+Funding Acquisition: E.G., J.L.
+
+~
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Brecher M (1999) International studies in the twentieth century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA} presidential address.
-\emph{International Studies Quarterly} 43(2):213--264.}
+\CSLLeftMargin{1. }%
+\CSLRightInline{Brecher M (1999) International studies in the twentieth
+century and beyond: {Flawed} dichotomies, synthesis, cumulation: {ISA}
+presidential address. \emph{International Studies Quarterly}
+43(2):213--264.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Reiter D (2015) \href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu Rev Polit Sci} 18(1):481--499.}
+\CSLLeftMargin{2. }%
+\CSLRightInline{Reiter D (2015)
+\href{https://doi.org/10.1146/annurev-polisci-053013-041156}{Should {We
+Leave Behind} the {Subfield} of {International Relations}?} \emph{Annu
+Rev Polit Sci} 18(1):481--499.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Brecher M, Wilkenfeld J (1982) \href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}. \emph{World Politics} 34(3):380--417.}
+\CSLLeftMargin{3. }%
+\CSLRightInline{Brecher M, Wilkenfeld J (1982)
+\href{https://doi.org/10.2307/2010324}{Crises in {World Politics}}.
+\emph{World Politics} 34(3):380--417.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The {International Crisis Behavior Project}.
+\CSLLeftMargin{4. }%
+\CSLRightInline{Beardsley K, James P, Wilkenfeld J, Brecher M (2020) The
+{International Crisis Behavior Project}.
 doi:\href{https://doi.org/10.1093/acrefore/9780190228637.013.1638}{10.1093/acrefore/9780190228637.013.1638}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Palmer G, et al.
-(2021) \href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset}, 2011--2014: {Procedures}, coding rules, and description}.
-\emph{Conflict Management and Peace Science}:0738894221995743.}
+\CSLLeftMargin{5. }%
+\CSLRightInline{Palmer G, et al. (2021)
+\href{https://doi.org/10.1177/0738894221995743}{The {MID5 Dataset},
+2011--2014: {Procedures}, coding rules, and description}. \emph{Conflict
+Management and Peace Science}:0738894221995743.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts}, 1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \& Littlefield}) Available at: \url{https://books.google.com?id=_4VTDwAAQBAJ}.}
+\CSLLeftMargin{6. }%
+\CSLRightInline{Gibler DM (2018) \emph{International {Conflicts},
+1816-2010: {Militarized Interstate Dispute Narratives}} ({Rowman \&
+Littlefield}) Available at:
+\url{https://books.google.com?id=_4VTDwAAQBAJ}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP (2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0: {Logic}, {Characteristics}, and {Comparisons} to {Alternative Datasets}}.
-\emph{Journal of Conflict Resolution} 63(3):811--835.}
+\CSLLeftMargin{7. }%
+\CSLRightInline{Maoz Z, Johnson PL, Kaplan J, Ogunkoya F, Shreve AP
+(2019) \href{https://doi.org/10.1177/0022002718784158}{The {Dyadic
+Militarized Interstate Disputes} ({MIDs}) {Dataset Version} 3.0:
+{Logic}, {Characteristics}, and {Comparisons} to {Alternative
+Datasets}}. \emph{Journal of Conflict Resolution} 63(3):811--835.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war: 1816-2007} ({CQ Press}).}
+\CSLLeftMargin{8. }%
+\CSLRightInline{Sarkees MR, Wayman F (2010) \emph{Resort to war:
+1816-2007} ({CQ Press}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016) \href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at {Interstate Wars}, 1816--2007}.
-\emph{Journal of Conflict Resolution} 60(5):956--976.}
+\CSLLeftMargin{9. }%
+\CSLRightInline{Reiter D, Stam AC, Horowitz MC (2016)
+\href{https://doi.org/10.1177/0022002714553107}{A {Revised Look} at
+{Interstate Wars}, 1816--2007}. \emph{Journal of Conflict Resolution}
+60(5):956--976.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED Codebook} version 5.0} ({Department of Peace and Conflict Research, Uppsala University}).}
+\CSLLeftMargin{10. }%
+\CSLRightInline{Ralph Sundberg, Mihai Croicu (2016) \emph{{UCDP GED
+Codebook} version 5.0} ({Department of Peace and Conflict Research,
+Uppsala University}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Pettersson T, Eck K (2018) \href{https://doi.org/10.1177/0022343318784101}{Organized violence, 1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}
+\CSLLeftMargin{11. }%
+\CSLRightInline{Pettersson T, Eck K (2018)
+\href{https://doi.org/10.1177/0022343318784101}{Organized violence,
+1989--2017}. \emph{Journal of Peace Research} 55(4):535--547.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010) Introducing {ACLED}: An armed conflict location and event dataset: Special data feature. \emph{Journal of peace research} 47(5):651--660.}
+\CSLLeftMargin{12. }%
+\CSLRightInline{Raleigh C, Linke A, Hegre H, Karlsen J (2010)
+Introducing {ACLED}: An armed conflict location and event dataset:
+Special data feature. \emph{Journal of peace research} 47(5):651--660.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The global sanctions data base}.
-\emph{European Economic Review} 129:103561.}
+\CSLLeftMargin{13. }%
+\CSLRightInline{Felbermayr G, Kirilakha A, Syropoulos C, Yalcin E, Yotov
+YV (2020) \href{https://doi.org/10.1016/j.euroecorev.2020.103561}{The
+global sanctions data base}. \emph{European Economic Review}
+129:103561.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the {Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}
+\CSLLeftMargin{14. }%
+\CSLRightInline{Barari S, Kim IS Democracy and {Trade Policy} at the
+{Product Level}: {Evidence} from a {New Tariff-line Dataset}. 16.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Kinne BJ (2020) \href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution} 64(4):729--755.}
+\CSLLeftMargin{15. }%
+\CSLRightInline{Kinne BJ (2020)
+\href{https://doi.org/10.1177/0022002719857796}{The {Defense Cooperation
+Agreement Dataset} ({DCAD})}. \emph{Journal of Conflict Resolution}
+64(4):729--755.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018) \href{https://doi.org/10.1177/0738894216646978}{The {International Border Agreements Dataset}}.
-\emph{Conflict Management and Peace Science} 35(5):559--576.}
+\CSLLeftMargin{16. }%
+\CSLRightInline{Owsiak AP, Cuttner AK, Buck B (2018)
+\href{https://doi.org/10.1177/0738894216646978}{The {International
+Border Agreements Dataset}}. \emph{Conflict Management and Peace
+Science} 35(5):559--576.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Vabulas F, Snidal D (2021) \href{https://doi.org/10.1177/0022343320943920}{Cooperation under autonomy: {Building} and analyzing the {Informal Intergovernmental Organizations} 2.0 dataset}.
-\emph{Journal of Peace Research} 58(4):859--869.}
+\CSLLeftMargin{17. }%
+\CSLRightInline{Vabulas F, Snidal D (2021)
+\href{https://doi.org/10.1177/0022343320943920}{Cooperation under
+autonomy: {Building} and analyzing the {Informal Intergovernmental
+Organizations} 2.0 dataset}. \emph{Journal of Peace Research}
+58(4):859--869.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017) \href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates} of {War Territorial Claims Data}, 1816--20011}.
-\emph{Journal of Peace Research} 54(1):99--108.}
+\CSLLeftMargin{18. }%
+\CSLRightInline{Frederick BA, Hensel PR, Macaulay C (2017)
+\href{https://doi.org/10.1177/0022343316676311}{The {Issue Correlates}
+of {War Territorial Claims Data}, 1816--20011}. \emph{Journal of Peace
+Research} 54(1):99--108.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020) \href{https://doi.org/10.1177/0022343320929740}{What are the drivers of diplomacy?
-{Introducing} and testing new annual dyadic data measuring diplomatic exchange}.
-\emph{Journal of Peace Research}:0022343320929740.}
+\CSLLeftMargin{19. }%
+\CSLRightInline{Moyer JD, Turner SD, Meisel CJ (2020)
+\href{https://doi.org/10.1177/0022343320929740}{What are the drivers of
+diplomacy? {Introducing} and testing new annual dyadic data measuring
+diplomatic exchange}. \emph{Journal of Peace
+Research}:0022343320929740.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Sechser TS (2011) \href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent Threats}, 1918--2001}. \emph{Conflict Management and Peace Science} 28(4):377--401.}
+\CSLLeftMargin{20. }%
+\CSLRightInline{Sechser TS (2011)
+\href{https://doi.org/10.1177/0738894211413066}{Militarized {Compellent
+Threats}, 1918--2001}. \emph{Conflict Management and Peace Science}
+28(4):377--401.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Li Q, et al.
-(2021) A {Comprehensive Survey} on {Schema-based Event Extraction} with {Deep Learning}.
-Available at: \url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10, 2021{]}.}
+\CSLLeftMargin{21. }%
+\CSLRightInline{Li Q, et al. (2021) A {Comprehensive Survey} on
+{Schema-based Event Extraction} with {Deep Learning}. Available at:
+\url{http://arxiv.org/abs/2107.02126} {[}Accessed September 10,
+2021{]}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{Halterman A (2020) Extracting {Political Events} from {Text Using Syntax} and {Semantics}.}
+\CSLLeftMargin{22. }%
+\CSLRightInline{Halterman A (2020) Extracting {Political Events} from
+{Text Using Syntax} and {Semantics}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018) Phoenix {Real-Time Event Data}. Available at: \url{http://eventdata.utdallas.edu}.}
+\CSLLeftMargin{23. }%
+\CSLRightInline{Brandt PT, DOrazio V, Holmes J, Khan L, Ng V (2018)
+Phoenix {Real-Time Event Data}. Available at:
+\url{http://eventdata.utdallas.edu}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data. \emph{Harvard Dataverse} 12.}
+\CSLLeftMargin{24. }%
+\CSLRightInline{Boschee E, et al. (2015) {ICEWS} coded event data.
+\emph{Harvard Dataverse} 12.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing the {UCDP Candidate Events Dataset}. \emph{Research \& Politics} 7(3):2053168020935257.}
+\CSLLeftMargin{25. }%
+\CSLRightInline{Hegre H, Croicu M, Eck K, Högbladh S (2020) Introducing
+the {UCDP Candidate Events Dataset}. \emph{Research \& Politics}
+7(3):2053168020935257.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017) {OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/} {[}Accessed September 1, 2021{]}.}
+\CSLLeftMargin{26. }%
+\CSLRightInline{Grant C, Halterman A, Irvine J, Liang Y, Jabr K (2017)
+{OU Event Data Project}. Available at: \url{https://osf.io/4m2u7/}
+{[}Accessed September 1, 2021{]}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Zhang H, Pan J (2019) \href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning Approach} for {Identifying Collective Action Events} with {Text} and {Image Data} from {Social Media}}.
-\emph{Sociological Methodology} 49(1):1--57.}
+\CSLLeftMargin{27. }%
+\CSLRightInline{Zhang H, Pan J (2019)
+\href{https://doi.org/10.1177/0081175019860244}{{CASM}: {A Deep-Learning
+Approach} for {Identifying Collective Action Events} with {Text} and
+{Image Data} from {Social Media}}. \emph{Sociological Methodology}
+49(1):1--57.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Steinert-Threlkeld ZC (2019) \href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}
+\CSLLeftMargin{28. }%
+\CSLRightInline{Steinert-Threlkeld ZC (2019)
+\href{https://doi.org/10.1177/0081175019860238}{The {Future} of {Event
+Data Is Images}}. \emph{Sociological Methodology} 49(1):68--75.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis escalation to war: {Findings} from the {International Crisis Behavior Project}. \emph{What Do We Know About War}.}
+\CSLLeftMargin{29. }%
+\CSLRightInline{Brecher M, James P, Wilkenfeld J (2000) Crisis
+escalation to war: {Findings} from the {International Crisis Behavior
+Project}. \emph{What Do We Know About War}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and violence: Twentieth-century findings. \emph{Handbook of war studies II}:282--300.}
+\CSLLeftMargin{30. }%
+\CSLRightInline{Wilkenfeld J, Brecher M (2000) Interstate crises and
+violence: Twentieth-century findings. \emph{Handbook of war studies
+II}:282--300.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{James P (2019) \href{https://doi.org/10.1177/0738894218793135}{What do we know about crisis, escalation and war?
-{A} visual assessment of the {International Crisis Behavior Project}}.
-\emph{Conflict Management and Peace Science} 36(1):3--19.}
+\CSLLeftMargin{31. }%
+\CSLRightInline{James P (2019)
+\href{https://doi.org/10.1177/0738894218793135}{What do we know about
+crisis, escalation and war? {A} visual assessment of the {International
+Crisis Behavior Project}}. \emph{Conflict Management and Peace Science}
+36(1):3--19.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Iakhnis E, James P (2019) \href{https://doi.org/10.1177/0738894219855610}{Near crises in world politics: {A} new dataset}.
-\emph{Conflict Management and Peace Science}:0738894219855610.}
+\CSLLeftMargin{32. }%
+\CSLRightInline{Iakhnis E, James P (2019)
+\href{https://doi.org/10.1177/0738894219855610}{Near crises in world
+politics: {A} new dataset}. \emph{Conflict Management and Peace
+Science}:0738894219855610.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D (2017) \emph{International {Crisis Behavior Data Codebook}} Available at: \url{http://sites.duke.edu/icbdata/data-collections/}.}
+\CSLLeftMargin{33. }%
+\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley KC, James P, Quinn D
+(2017) \emph{International {Crisis Behavior Data Codebook}} Available
+at: \url{http://sites.duke.edu/icbdata/data-collections/}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of {Crisis}} ({University of Michigan Press}).}
+\CSLLeftMargin{34. }%
+\CSLRightInline{Brecher M, Wilkenfeld J (1997) \emph{A {Study} of
+{Crisis}} ({University of Michigan Press}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Holsti OR (1965) \href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The American Political Science Review} 59(2):365--378.}
+\CSLLeftMargin{35. }%
+\CSLRightInline{Holsti OR (1965)
+\href{https://doi.org/10.2307/1953055}{The 1914 {Case}}. \emph{The
+American Political Science Review} 59(2):365--378.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June} 24-30, 1950} ({Free Press}).}
+\CSLLeftMargin{36. }%
+\CSLRightInline{Paige GD (1968) \emph{The {Korean Decision}, {June}
+24-30, 1950} ({Free Press}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision: {Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}
+\CSLLeftMargin{37. }%
+\CSLRightInline{Allison GT, Zelikow P (1971) \emph{Essence of decision:
+{Explaining} the {Cuban} missile crisis} ({Little, Brown Boston}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among nations: {Bargaining} and decision making in international crises} ({Princeton University Press}).}
+\CSLLeftMargin{38. }%
+\CSLRightInline{Snyder GH, Diesing P (1977) \emph{Conflict among
+nations: {Bargaining} and decision making in international crises}
+({Princeton University Press}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Gavin FJ (2014) \href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies} 37(2):319--331.}
+\CSLLeftMargin{39. }%
+\CSLRightInline{Gavin FJ (2014)
+\href{https://doi.org/10.1080/01402390.2014.912916}{History, {Security
+Studies}, and the {July Crisis}}. \emph{Journal of Strategic Studies}
+37(2):319--331.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American} foreign policy: {Theory} and practice} ({Columbia University Press}).}
+\CSLLeftMargin{40. }%
+\CSLRightInline{George AL, Smoke R (1974) \emph{Deterrence in {American}
+foreign policy: {Theory} and practice} ({Columbia University Press}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Gaddis JL (1987) \href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}: {Historians}, {Political Scientists}, and the {Enrichment} of {Security Studies}}.
-\emph{International Security} 12(1):3--21.}
+\CSLLeftMargin{41. }%
+\CSLRightInline{Gaddis JL (1987)
+\href{https://doi.org/10.2307/2538915}{Expanding the {Data Base}:
+{Historians}, {Political Scientists}, and the {Enrichment} of {Security
+Studies}}. \emph{International Security} 12(1):3--21.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management. \emph{Journal of Conflict Resolution} 32(3):426--456.}
+\CSLLeftMargin{42. }%
+\CSLRightInline{Brecher M, James P (1988) Patterns of crisis management.
+\emph{Journal of Conflict Resolution} 32(3):426--456.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of {Asian} security: {Using Europe} to study {Asia}. \emph{Journal of Global Security Studies} 4(3):393--401.}
+\CSLLeftMargin{43. }%
+\CSLRightInline{Kang DC, Lin AY-T (2019) {US} bias in the study of
+{Asian} security: {Using Europe} to study {Asia}. \emph{Journal of
+Global Security Studies} 4(3):393--401.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Hewitt JJ (2001) \href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to {Teach Conflict} and {Crisis Analysis}}.
-\emph{Int Stud Perspect} 2(4):371--383.}
+\CSLLeftMargin{44. }%
+\CSLRightInline{Hewitt JJ (2001)
+\href{https://doi.org/10.1111/1528-3577.00066}{Engaging {International
+Data} in the {Classroom}: {Using} the {ICB Interactive Data Library} to
+{Teach Conflict} and {Crisis Analysis}}. \emph{Int Stud Perspect}
+2(4):371--383.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Miller GA (1995) \href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical database for {English}}. \emph{Commun ACM} 38(11):39--41.}
+\CSLLeftMargin{45. }%
+\CSLRightInline{Miller GA (1995)
+\href{https://doi.org/10.1145/219717.219748}{{WordNet}: A lexical
+database for {English}}. \emph{Commun ACM} 38(11):39--41.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA (2019) Cline {Center Historical Phoenix Event Data Variable Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}
+\CSLLeftMargin{46. }%
+\CSLRightInline{Althaus S, Bajjalieh J, Carter JF, Peyton B, Shalmon DA
+(2019) Cline {Center Historical Phoenix Event Data Variable
+Descriptions}. \emph{Cline Center Historical Phoenix Event Data}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP} georeferenced event dataset. \emph{Journal of Peace Research} 50(4):523--532.}
+\CSLLeftMargin{47. }%
+\CSLRightInline{Sundberg R, Melander E (2013) Introducing the {UCDP}
+georeferenced event dataset. \emph{Journal of Peace Research}
+50(4):523--532.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Leng RJ, Singer JD (1988) \href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}: {The BCOW Typology} and {Its Applications}}.
-\emph{International Studies Quarterly} 32(2):155--173.}
+\CSLLeftMargin{48. }%
+\CSLRightInline{Leng RJ, Singer JD (1988)
+\href{https://doi.org/10.2307/2600625}{Militarized {Interstate Crises}:
+{The BCOW Typology} and {Its Applications}}. \emph{International Studies
+Quarterly} 32(2):155--173.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{McClelland C (1978) World event/interaction survey, 1966-1978. \emph{WEIS Codebook ICPSR} 5211.}
+\CSLLeftMargin{49. }%
+\CSLRightInline{McClelland C (1978) World event/interaction survey,
+1966-1978. \emph{WEIS Codebook ICPSR} 5211.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events} of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968: {Version} 1.
+\CSLLeftMargin{50. }%
+\CSLRightInline{Hermann C (1984) Comparative {Research} on the {Events}
+of {Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968:
+{Version} 1.
 doi:\href{https://doi.org/10.3886/ICPSR05205.V1}{10.3886/ICPSR05205.V1}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}: {Computer-aided} system for analysis of local conflicts. \emph{MIT Center for International Studies, Cambridge}.}
+\CSLLeftMargin{51. }%
+\CSLRightInline{Bloomfield LP, Moulton A (1989) {CASCON III}:
+{Computer-aided} system for analysis of local conflicts. \emph{MIT
+Center for International Studies, Cambridge}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm}, {Hierarchical}, and {Contextually-Sensitive International Conflict Dataset}, 1937-1985: {Version} 1.
+\CSLLeftMargin{52. }%
+\CSLRightInline{Sherman FL (2000) {SHERFACS}: {A Cross-Paradigm},
+{Hierarchical}, and {Contextually-Sensitive International Conflict
+Dataset}, 1937-1985: {Version} 1.
 doi:\href{https://doi.org/10.3886/ICPSR02292.V1}{10.3886/ICPSR02292.V1}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A Comprehensive Ontology} for {Event Extraction} from text.
+\CSLLeftMargin{53. }%
+\CSLRightInline{Balali A, Asadpour M, Jafari SH (2021) {COfEE}: {A
+Comprehensive Ontology} for {Event Extraction} from text.
 doi:\href{https://doi.org/10.48550/arXiv.2107.10326}{10.48550/arXiv.2107.10326}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Merritt RL (1994) Measuring events for international political analysis. \emph{International Interactions} 20(1-2):3--33.}
+\CSLLeftMargin{54. }%
+\CSLRightInline{Merritt RL (1994) Measuring events for international
+political analysis. \emph{International Interactions} 20(1-2):3--33.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas} event data system project. \emph{The political methodologist} 14(1):2--8.}
+\CSLLeftMargin{55. }%
+\CSLRightInline{Schrodt PA, Hall B (2006) Twenty years of the {Kansas}
+event data system project. \emph{The political methodologist}
+14(1):2--8.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D International {Crisis Behavior Data Codebook}, {Version} 12. 69.}
+\CSLLeftMargin{56. }%
+\CSLRightInline{Brecher M, Wilkenfeld J, Beardsley K, James P, Quinn D
+International {Crisis Behavior Data Codebook}, {Version} 12. 69.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Braithwaite A (2010) \href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing} the {Militarized Interstate Dispute Location} dataset}.
-\emph{Journal of Peace Research} 47(1):91--98.}
+\CSLLeftMargin{57. }%
+\CSLRightInline{Braithwaite A (2010)
+\href{https://doi.org/10.1177/0022343309350008}{{MIDLOC}: {Introducing}
+the {Militarized Interstate Dispute Location} dataset}. \emph{Journal of
+Peace Research} 47(1):91--98.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University College London}.}
+\CSLLeftMargin{58. }%
+\CSLRightInline{Braithwaite A (2009) Codebook for the {Militarized
+Interstate Dispute Location} ({MIDLOC}) {Data}, v 1.0. \emph{University
+College London}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain knowledge: Using hierarchies to improve deep classifiers.
-Available at: \url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}
+\CSLLeftMargin{59. }%
+\CSLRightInline{Brust C-A, Denzler J (2020) Integrating domain
+knowledge: Using hierarchies to improve deep classifiers. Available at:
+\url{http://arxiv.org/abs/1811.07125} {[}Accessed September 7, 2021{]}.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of nature} ({Freeman}, {New York}).}
+\CSLLeftMargin{60. }%
+\CSLRightInline{Mandelbrot BB (1983) \emph{The fractal geometry of
+nature} ({Freeman}, {New York}).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Cormac R, Aldrich RJ (2018) \href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert action and implausible deniability}. \emph{International Affairs} 94(3):477--494.}
+\CSLLeftMargin{61. }%
+\CSLRightInline{Cormac R, Aldrich RJ (2018)
+\href{https://doi.org/10.1093/ia/iiy067}{Grey is the new black: Covert
+action and implausible deniability}. \emph{International Affairs}
+94(3):477--494.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Terechshenko Z (2020) \href{https://doi.org/10.1177/0022343320962546}{Hot under the collar: {A} latent measure of interstate hostility}.
-\emph{Journal of Peace Research} 57(6):764--776.}
+\CSLLeftMargin{62. }%
+\CSLRightInline{Terechshenko Z (2020)
+\href{https://doi.org/10.1177/0022343320962546}{Hot under the collar:
+{A} latent measure of interstate hostility}. \emph{Journal of Peace
+Research} 57(6):764--776.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{Cook SJ, Weidmann NB (2019) \href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}: {Improving Event Analysis} with {Report-Level Data}}.
-\emph{American Journal of Political Science} 63(1):250--264.}
+\CSLLeftMargin{63. }%
+\CSLRightInline{Cook SJ, Weidmann NB (2019)
+\href{https://doi.org/10.1111/ajps.12398}{Lost in {Aggregation}:
+{Improving Event Analysis} with {Report-Level Data}}. \emph{American
+Journal of Political Science} 63(1):250--264.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of protest event analysis. \emph{Contention in times of crisis: Recession and political protest in thirty Euro-pean countries}:49--78.}
+\CSLLeftMargin{64. }%
+\CSLRightInline{Wüest B, Lorenzini J (2020) External validation of
+protest event analysis. \emph{Contention in times of crisis: Recession
+and political protest in thirty Euro-pean countries}:49--78.}
 
 \leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event Data}: {Evidence} from the {ICEWS Dataset}.}
+\CSLLeftMargin{65. }%
+\CSLRightInline{Jäger K The {Limits} of {Studying Networks} with {Event
+Data}: {Evidence} from the {ICEWS Dataset}.}
 

### 2022-08-10 README.Rmd
readme update

@@
 
-  - [ICBe_V1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
-      + All coded values and information about how often they were selected by coders.  
-  - [ICBe_V1_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_long_agreed.Rds)
-      + `ICBe_V1_long_agreement.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
-  - [ICBe_V1_wide_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
-      + `ICBe_V1_long_agreed.Rds` in wide form where each row is an event.
+  - [ICBe_V1_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_long_agreed.Rds)
+  - [ICBe_V1.1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
+      + All coded values individually along with information about how often they were selected by coders.  
+      + `ICBe_V1_long.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
+  - [ICBe_V1.1_events_agreed_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
+    - [ICBe_V1.1_events_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed_long.Rds)
+
+      + `ICBe_V1.1_events_agreed.Rds` in wide form where each row is an event.
 
@@
 
-### Self Contained Package
+A description of the file and folders in the repository used to create the datasets, tables, figures.
 
-All of the files used to create the datasets, tables, figures.
+## data preparation
 
-## RMarkdown files
+### replication_corpus
 
-### Replication Data
+ - download_and_clean
+    + creates a succinct rds of the crisis narratives: `.replication_corpus/data/out/icb_corpus_V1.0_May_16_2022`
+
+### replication_data
 
  - 01_compile_saves_and_align
-    + compiles the original coding files into `./replication_data/in/icb_coder_crisis_sentence_event.Rds`.
+    + compiles the original coding files into `./replication_data/in/icb_long_spans.Rds`.
 The original coding files are not on the public repository.
-Public users will load `icb_coder_crisis_sentence_event.Rds` directly.
+Public users will load `icb_long_spans.Rds` directly.
     + aligns codings from multiple GUI versions on similar source sentences
-    + creates `./replication_data/temp/ICBe_V1_long_unclean.Rds.Rds` (not included in online repo)
  - 02_format_and_clean
-    + applies cleaning dictionaries to create `./replication_data/temp/ICBe_V1_long_clean.Rds` and `./replication_data/temp/ICBe_V1_long_clean.Rds` (not included in online repo)
+    + applies cleaning dictionaries to create `./replication_data/out/ICBe_V1.1_long_clean.Rds`.
  - 03_aggregation
-    + applies aggregation algorithm to create `./replication_data/out/ICBe_V1_long_agreement.Rds`, `./replication_data/out/ICBe_V1_long_agreed.Rds`, `./replication_data/out/ICBe_V1_wide_agreed.Rds`.
+    + applies aggregation algorithm to create `./replication_data/out/ICBe_V1.1_long_agreement.Rds`, `ICBe_V1.1_long.Rds`,  `./replication_data/out/ICBe_V1.1_events_agreed.Rds`, `./replication_data/out/ICBe_V1.1_events_agreed_long.Rds`.
+ - 04_validation
+    + applies iconography to crises and events to create `ICBe_V1.1_crises_markdown.Rds` and `ICBe_V1.1_events_agreed_markdown.Rds`
 
-### Replication Paper
+### replication_paper
 
-  - 04_ICBEdataset_paper_litreviewtable
-      + creates the table `/tables/litreview_ft.Rds`.
-  - 05_ICBEdataset_paper_PlotInterCoderAgreement
-      + creates the figure `figures/p_percent_chose_tag_by_concept.png`
-  - 06_ICBEdataset_figure_metro_maps
-      + creates the metroplot Rds files in `/figures/metro_plots/.`.
-  - 07_ICBEdataset_figure_semantic_embeddings
-      + creates the figure `/figures/p_semantic_embeddings.png` and the `/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds` and `/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds`
-  - 08_CaseStudy196
-      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
-  - 09_CaseStudy426
-      + creates DRC Civil War comparison table `/tables/CaseStudy426_ft.Rds`. 
-  - 10_ICBEdataset_paper_figure_prep
-      + creates the metroplot pngs in `/figures/.`.
-  - 11_ICBEdataset_paper_appendixICBCrises
-      +  creates `/tables/ft_crisis_text_counts.Rds`.
-  - 12_ICBEdataset_paper_appendixVerbMeanings
-      + creates `/tables/verbs_sentence_wordnet_top_ft.Rds`
+The figures are created in Rmd file for the paper (./replication_paper/pnas_draft/ICBe_pnas_submission_rmd.Rmd).
+In some cases they have been transformed to other formats via GNU Image Manipulation Program.
+
+  - `case_study_cuban_precision.png`
+  - `recall_cuban_and_crimea_andcounts.png`
+    + Draws from the [Cuban Missile Automated Case Study googlesheet](https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing) and the [Crimea-Donbas Automated Case Study (redone) googlesheet](https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing).
+    + uses the iconographry in `./replication_data/in/flags_small/`
+  - `p_precision_combined.png`
+    + combines metro maps of the two case studies using ICBe_V1.1_events_agreed.Rds
+  - `p_semantic_embeddings_dendro.png`
+    + plot of semantic embeddings of ICBe_V1.1_events_agreed_markdown.Rds 
+  - `p_precision_icews.png`
+    + mapping of icews using `./replication_paper/data/out/icews_clean_471_lowest.tsv` (created in `./replication_paper/pnas_draft/appendix.Rmd`)
 
@@
   - [The ICB project](https://sites.duke.edu/icbdata/) 
-    + System-level (./data/icb1v14.Rds) and Actor-level (./data/icb2v14.Rds) datasets
+    + System-level (icb1v14.csv) and Actor-level (icb2v14.csv) datasets
     + Dyadic-Level Crisis Data ([source](https://sites.duke.edu/icbdata/data-collections/))
-  - [Militarized Interstate Disputes (MID)](https://correlatesofwar.org/data-sets/MIDs) version 5.01 at the incident level (MIDI 5.01) and incident-participant level (MIDIP 5.01) converted to Rds. 
-  - [UCDP Georeferenced Event Dataset (GED) Global version 21.1](https://ucdp.uu.se/downloads/index.html#ged_global)
-  - cameo.eventcode.txt adapted from [CAMEO Conflict and Mediation Event Observations Codebook](https://parusanalytics.com/eventdata/cameo.dir/CAMEO.09b6.pdf)
+  - [Militarized Interstate Disputes (MID)](https://correlatesofwar.org/data-sets/MIDs) version 5.01 at the incident level (MIDI_5.01.Rds) and incident-participant level (MIDIP_5.01.Rds) converted to Rds.
+  - [UCDP Georeferenced Event Dataset (GED) Global version 21.1](https://ucdp.uu.se/downloads/index.html#ged_global) (GEDEvent_v23_1.RData)
+  - Cameo Event Codes adapted from [CAMEO Conflict and Mediation Event Observations Codebook](https://parusanalytics.com/eventdata/cameo.dir/CAMEO.09b6.pdf) (cameo.eventcode.txt)
   - [Phoenix Event data](https://databank.illinois.edu/datasets/IDB-2796521)
@@
     + to replicate, download folder 'dataverse_files' to ICBEdata/replication_paper/data/ignore/ and decompress
+
+### Appendix
+
+The v1.1 Online Appendix can be downloaded [here](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/arxiv_draft/appendix.pdf).
 

### 2022-08-10 replication_paper/pnas_draft/ICBe_PNAS_submission_tex.tex
readme update

--- 2022-08-05 replication_paper/pnas_draft/paper.tex
@@
-\documentclass{article}
-
-\usepackage{arxiv}
+\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
+
+\templatetype{pnasresearcharticle} % Choose template 
+% {pnasresearcharticle} = Template for a two-column research article
+% {pnasmathematics} %= Template for a one-column mathematics article
+% {pnasinvited} %= Template for a PNAS invited submission
+
+\title{Introducing ICBe: Very High Recall and Precision Event Extraction
+from Narratives about International Crises}
+
+% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+\author[a,1]{Rex W. Douglass}
+\author[a]{Thomas Leo Scherer} 
+\author[b]{J. Andrés Gannon}
+\author[a]{Erik Gartzke}
+\author[c]{Jon Lindsay}
+\author[d]{Shannon Carcelli}
+\author[d]{Jonathan Wilkenfeld}
+\author[d]{David M. Quinn}
+\author[e]{Catherine Aiken}
+\author[f]{Jose Miguel Cabezas Navarro}
+\author[d]{Neil Lund}
+\author[d]{Egle Murauskaite}
+\author[d]{Diana Partridge}
+
+\affil[a]{University of California, San Diego }
+\affil[b]{Vanderbilt University}
+\affil[c]{Georgia Institute of Technology}
+\affil[d]{University of Maryland}
+\affil[e]{Georgetown University}
+\affil[f]{Universidad Mayor}
+
+% Please give the surname of the lead author for the running footer
+\leadauthor{Douglass}
+
+% Please add here a significance statement to explain the relevance of your work
+\significancestatement{Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
+Instead policy makers typically rely on one or two historical analogies,
+chosen through ad hoc selection criteria, and described in unsystematic terms.
+This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods.
+It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.}
+
+% Please include corresponding author, author contribution and author declaration information
+\authorcontributions{Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing -
+Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D., J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.; Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.}
+% \authordeclaration{Please declare any conflict of interest here.}
+\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: rexdouglass\@gmail.com }
+
+% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
+\keywords{Diplomacy $|$ War $|$ Crises $|$ International Affairs $|$ Computational Social Science}
+
+\begin{abstract}
+How do international crises unfold?
+We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
+We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
+We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
+We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
+We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.
+\end{abstract}
+
+\dates{This manuscript was compiled on \today}
+\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX TO BE ADDED}}
 
@@
 \usepackage{graphicx}
-
-\title{Introducing ICBe: Very High Recall and Precision Event Extraction
-from Narratives about International Crises}
-
-\author{
-    Rex W. Douglass
-   \\
-    University of California, San Diego \\
-   \\
-  \texttt{} \\
-   \And
-    Thomas Leo Scherer
-   \\
-    University of California, San Diego \\
-   \\
-  \texttt{} \\
-   \And
-    J. Andrés Gannon
-   \\
-    Vanderbilt University \\
-   \\
-  \texttt{} \\
-   \And
-    Erik Gartzke
-   \\
-    University of California, San Diego \\
-   \\
-  \texttt{} \\
-   \And
-    Jon Lindsay
-   \\
-    Georgia Institute of Technology \\
-   \\
-  \texttt{} \\
-   \And
-    Shannon Carcelli
-   \\
-    University of Maryland \\
-   \\
-  \texttt{} \\
-   \And
-    Jonathan Wilkenfeld
-   \\
-    University of Maryland \\
-   \\
-  \texttt{} \\
-   \And
-    David M. Quinn
-   \\
-    University of Maryland \\
-   \\
-  \texttt{} \\
-   \And
-    Catherine Aiken
-   \\
-    Georgetown University \\
-   \\
-  \texttt{} \\
-   \And
-    Jose Miguel Cabezas Navarro
-   \\
-    Universidad Mayor \\
-   \\
-  \texttt{} \\
-   \And
-    Neil Lund
-   \\
-    University of Maryland \\
-   \\
-  \texttt{} \\
-   \And
-    Egle Murauskaite
-   \\
-    University of Maryland \\
-   \\
-  \texttt{} \\
-   \And
-    Diana Partridge
-   \\
-    University of Maryland \\
-   \\
-  \texttt{} \\
-  }
-
 % tightlist command for lists without linebreak
@@
 \usepackage{hyperref}
+
 \begin{document}
+
 \maketitle
-
-\begin{abstract}
-How do international crises unfold? We conceptualize of international
-relations as a strategic chess game between adversaries and develop a
-systematic way to measure pieces, moves, and gambits accurately and
-consistently over a hundred years of history. We introduce a new
-ontology and dataset of international events called ICBe based on a very
-high-quality corpus of narratives from the International Crisis Behavior
-(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
-precision than existing state of the art datasets and conduct two
-detailed case studies of the Cuban Missile Crisis (1962) and
-Crimea-Donbas Crisis (2014). We further introduce two new event
-visualizations (event icongraphy and crisis maps), an automated
-benchmark for measuring event recall using natural language processing
-(sythnetic narratives), and an ontology reconstruction task for
-objectively measuring event precision. We make the data, online
-appendix, replication material, and visualizations of every historical
-episode available at a companion website www.crisisevents.org and the
-github repository.
-\end{abstract}
-
-\keywords{
-    Diplomacy
-   \and
-    War
-   \and
-    Crises
-   \and
-    International Affairs
-   \and
-    Computational Social Science
-  }
-
-\twocolumn
-
-If we could record every important interaction between countries in all
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+% If your first paragraph (i.e.
+with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation.
+If this is the case, add \parshape=0 to the end of the list environment.
+
+\dropcap{I}f we could record every important interaction between countries in all
 of diplomacy, military conflict, and international political economy,
@@
 
-\clearpage
-\onecolumn
-\begin{figure}[H]
+\begin{figure*}
 \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=19cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-\twocolumn
+\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
+\end{figure*}
 
@@
   ontological depth and availability of Gold Standard example text.}
-
-\clearpage
-\onecolumn
-
-{[}1{]} 37 17
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.75}
-
-\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
-
-\caption{Ontological coverage of ICBe versus existing State of the Art
-}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\end{longtable}
-
-\clearpage
-\twocolumn
 
@@
 that thought, speech, and do behaviors can be nested into combinations,
-e.g.~an offer for the U.S.S.R. to remove missiles from Cuba in exchange
-for the U.S. removing missiles from Turkey. Through compounding, the
-ontology can capture what players were said to have known, learned, or
+e.g.~an offer for the U.S.S.R. to remove missiles from Cuba in exchange for the U.S. removing \linebreak \clearpage
+\onecolumn
+
+% {[}1{]} 37 17
+
+\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{0.75}
+
+\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
+
+\caption{Ontological coverage of ICBe versus existing State of the Art
+}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\end{longtable}
+
+\clearpage
+\twocolumn
+
+missiles from Turkey. Through compounding, the ontology 
+can capture what players were said to have known, learned, or
 said about other specific fully described actions.
@@
 
-\clearpage
-\onecolumn
-\begin{figure}[H]
+\begin{figure*}
 \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
@@
 Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
-\end{figure}
-\clearpage
-\twocolumn
+\end{figure*}
 
@@
 
-\clearpage
-\onecolumn
-\begin{sidewaysfigure}[ht]
+\begin{sidewaysfigure*}
 \caption{Crisis Maps  \label{fig:p_precision_combined}}
 \centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-\twocolumn
+\end{sidewaysfigure*}
 
@@
 
-\clearpage
-\onecolumn
-\begin{figure}[H]
+\begin{figure*}
 \caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
@@
 }
-\end{figure}
-\clearpage
-\twocolumn
+\end{figure*}
 
@@
 precision difficult to verify.
+
+\begin{figure*}
+\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
+\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
+\textit{Notes:Unit of analysis is the Dyad-Day.
+Edges <-> indicates undirected dyad and -> indicates directed dyad.
+Top 10 most active dyads per category shown.
+Red text shows events from the synthetic narrative relative to that event category.
+Blue bars indicate an event recorded by ICEWs for that dyad on that day.
+}
+\end{figure*}
 
@@
 
-\clearpage
-\onecolumn
-\begin{figure}[H]
-\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
-\textit{Notes:Unit of analysis is the Dyad-Day.
-Edges <-> indicates undirected dyad and -> indicates directed dyad.
-Top 10 most active dyads per category shown.
-Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
-\twocolumn
-
 \hypertarget{format}{%
@@
 
-\hypertarget{format}{%
-\section*{Acknowledgements}\label{format}}
-\addcontentsline{toc}{section}{Acknowledgements}
-
-We thank the ICB Project and its directors and contributors for their
+\matmethods{This paper's data, online appendix, and replication material as well as visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.
+}
+
+\showmatmethods{} % Display the Materials and Methods section
+
+\acknow{We thank the ICB Project and its directors and contributors for their
 foundational work and their help with this effort. We make special
@@
 Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles
-Koch Foundation's support for the Center for Peace and Security Studies.
-
-\hypertarget{format}{%
-\section*{Author Contributions}\label{format}}
-\addcontentsline{toc}{section}{Author Contributions}
-
-Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.;
-Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D.,
-T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N.,
-D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing -
-Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D.,
-J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.;
-Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
-Funding Acquisition: E.G., J.L.
+Koch Foundation's support for the Center for Peace and Security Studies.}
+
+\showacknow{} % Display the acknowledgments section
+
+% Bibliography
 
@@
 \bibliographystyle{unsrt}
+
 \bibliography{paper.bib}

### 2022-08-10 replication_paper/pnas_draft/initial_submission.Rmd
readme update

--- 2022-07-26 replication_paper/arxiv_draft/paper.Rmd
@@
 References in the abstract must be cited in full within the abstract itself and cited in the text.
+
 abstract: |
@@
 
-significance: |
-  Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
+# significance: |
+#   Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
 Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
@@
 
+Significance Statement: Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
+Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
+This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods.
+It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.
+
+***
+
 If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
@@
 
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","arxiv_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
@@
 
-      flextable::rotate(i=2, , j=3:k, rotation="tbrl",part="header") %>%
+      flextable::rotate(i=2, j=3:k, rotation="tbrl",part="header") %>%
       flextable::align(align = "center", part = "body") %>%
@@
 
-#litreview_ft_pnas   %>% 
-#    #flextable::flextable_to_rmd()
-#    save_as_image(path=here::here("replication_paper", "arxiv_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+litreview_ft_pnas   %>% 
+    #flextable::flextable_to_rmd()
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 
+library(dplyr)
 library(googlesheets4) #Do this high up so you get the prompt early
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_recall.png"),
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
                   zoom=1, webshot = "webshot2") # webshot = "webshot2"
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'),
        plot = p_recall ,
@@
 
-tiger <- image_read(here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/arxiv_draft/p_recall.png'))
+tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
+tiger2 <- image_read(paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'))
 
 combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "arxiv_draft", "recall_cuban_and_crimea_andcounts.png"))
+image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))
 
@@
 height=18
-save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_precision_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_precision_combined.png'),
           p_precision_combined, base_height = 18, base_width = height*ratio)
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
 
@@
 save_plot(file=paste0(here::here(),
-                      '/replication_paper/arxiv_draft/p_precision_icews.png'),
+                      '/replication_paper/pnas_draft/p_precision_icews.png'),
           p_ICEWS, base_height = 10, base_width = 14)
@@
 ========================================
-  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
-  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
+Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
 

### 2022-08-10 replication_paper/pnas_draft/paper.Rmd
readme update

@@
 #following https://docs.google.com/document/d/1aJxrQXYHW5U6By3KEAHrx1Iho6ioeh3ohNsRMwsoGPM/edit
-author_contributions: |
-  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
-  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
+# author_contributions: |
+#   Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
+#   Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
 
 ## Remove this if not required
-conflict_of_interest: |
-  Please declare any conflict of interest here.
+#conflict_of_interest: |
+#  Please declare any conflict of interest here.
 
@@
 We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
-We introduce a new ontology and dataset of international events called ICBe based on very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
+We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
 We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
 We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.
 
@@
 
-bibliography: arxiv.bib
+csl: pnas.csl
+bibliography: paper.bib
 biblio-style: unsrt
@@
 ```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
-print(wd())
 #International Crisis Behavior Events (ICBe) Dataset
-knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warnings=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
+knitr::opts_chunk$set(echo=F, cache=TRUE, messages=F, results='hide', warning=F, include=FALSE) #fig.width = 8, fig.height = 8, message=F, warning=F, , results=F
 
@@
 litreview_ft_pnas %>% 
-  ftExtra::colformat_md(j = 3, part="body") %>%
     flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
-  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
    flextable::flextable_to_rmd()
+
+litreview_ft_pnas   %>% 
+    #flextable::flextable_to_rmd()
+    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/pnas_draft/crisismaps/p_metro_plot_471.Rds')) +
+p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
     labs(
@@
 
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/pnas_draft/crisismaps/p_metro_plot_471.Rds')) +
+p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
     labs(
@@
 \caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=24cm]{./p_precision_combined.png}}
+\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
 \end{sidewaysfigure}
@@
 ```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+
+if(fromscratch){
 
@@
 
-<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
+Acknowledgements {#format .unnumbered}
+========================================
+  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
+We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
+We thank the many undergraduate coders for their patience and dedication.
+Thanks to the Center for Peace and Security Studies and its membership for comments.
+Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
+Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
+This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
+
+Author Contributions {#format .unnumbered}
+========================================
+  Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.;  Validation: R.W.D., T.L.S.;  Formal Analysis: R.W.D., T.L.S.;  Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.;  Data Curation: R.W.D., D.Q., T.L.S., J.W.;  Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.;
+  Visualization: R.W.D., T.L.S.;  Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;  Funding Acquisition: E.G., J.L.
+
+&nbsp;
+
+<!-- PNAS lines Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references
 \showmatmethods

### 2022-08-10 replication_paper/pnas_draft/pnas_paper.Rmd
readme update

--- 2022-07-26 replication_paper/arxiv_draft/paper.Rmd
@@
 
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","arxiv_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_precision %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "pnas_litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+
 temp <- NULL

### 2022-08-11 README.Rmd
DOI
readme update

@@
 
-  - [ICBe_V1_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_long_agreed.Rds)
-  - [ICBe_V1.1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
+  - [ICBe_V1.1_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_long.Rds)
+  - [ICBe_V1.1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_long_agreement.Rds)
       + All coded values individually along with information about how often they were selected by coders.  
-      + `ICBe_V1_long.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
-  - [ICBe_V1.1_events_agreed_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
-    - [ICBe_V1.1_events_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed_long.Rds)
-
-      + `ICBe_V1.1_events_agreed.Rds` in wide form where each row is an event.
+      + `ICBe_V1.1_long.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
+  - [ICBe_V1.1_events_agreed_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_events_agreed_long.Rds)
+  - [ICBe_V1.1_events_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_events_agreed.Rds)
 
@@
 
-### License
+### License and DOI
 
@@
 [cc-by-nc-sa-shield]: https://img.shields.io/badge/License-CC%20BY--NC--SA%204.0-lightgrey.svg
+
+[![DOI](https://zenodo.org/badge/450249483.svg)](https://zenodo.org/badge/latestdoi/450249483)

### 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_rmd.Rmd
win update

--- 2022-08-10 replication_paper/pnas_draft/initial_submission.Rmd
@@
 
-Significance Statement: Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
+Significance Statement {.unnumbered}
+========================================
+
+Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
 Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
@@
 
+ICBe Coding Process {.unnumbered}
+========================================
+
+The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
+B1).
+Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
+Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.
+force size, fatalities, domains, units, etc.
+A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
+an offer for the U.S.S.R.
+to remove missiles from Cuba in exchange for the U.S.
+removing missiles from Turkey.
+Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
+
 \clearpage
@@
 
-litreview_ft_pnas   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+# Uncomment for snapshot
+# litreview_ft_pnas %>% 
+#     #flextable::flextable_to_rmd()
+#     save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 ```
-
-ICBe Coding Process {.unnumbered}
-========================================
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-B1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.
-force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
-an offer for the U.S.S.R.
-to remove missiles from Cuba in exchange for the U.S.
-removing missiles from Turkey.
-Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
 

### 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_rmd.tex
win update

--- 2022-08-05 replication_paper/pnas_draft/paper.tex
@@
 
+\hypertarget{significance-statement}{%
+\section*{Significance Statement}\label{significance-statement}}
+\addcontentsline{toc}{section}{Significance Statement}
+
+Countries routinely face crises that risk escalating into full scale war
+but we do not have systematic measurements of the progression of past
+crises and what moves and counter moves led to or helped avoid war.
+Instead policy makers typically rely on one or two historical analogies,
+chosen through ad hoc selection criteria, and described in unsystematic
+terms. This paper introduces a new scientific approach to measuring the
+step by step moves of international crises over the last hundred years,
+combining subject expertise with state of the art natural language
+processing and machine learning methods. It serves as a guide for
+constructing and evaluating large scale measurement collection in the
+social sciences.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
 If we could record every important interaction between countries in all
@@
 
+\clearpage
+\onecolumn
+
+{[}1{]} 37 17
+
+\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{0.75}
+
+\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
+
+\caption{Ontological coverage of ICBe versus existing State of the Art
+}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\end{longtable}
+
+\clearpage
+\twocolumn
+
 Each crisis was typically assigned to 2 expert coders and 2 novice

### 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_tex.tex
win update

--- 2022-08-10 replication_paper/pnas_draft/ICBe_PNAS_submission_tex.tex
@@
 
+% \begin{figure*}
+% \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
+% \centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
+% \end{figure*}
+
 \begin{figure*}
 \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
+\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.pdf"}}
 \end{figure*}
@@
 
+% \begin{figure*}
+% \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
+% \centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
+% \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
+Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
+% \end{figure*}
+
 \begin{figure*}
 \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
+\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.eps}}
 \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
@@
 
+% \begin{sidewaysfigure*}
+% \caption{Crisis Maps  \label{fig:p_precision_combined}}
+% \centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
+% \end{sidewaysfigure*}
+
 \begin{sidewaysfigure*}
 \caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
+\centering{\includegraphics[width=22cm]{./p_precision_combined.eps}}
 \end{sidewaysfigure*}
@@
 
+% \begin{figure*}
+% \caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
+% \centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
+% \textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
+Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
+Label placement is the median of all of the sentences that tag was applied to by the coders.
+The dendrogram shows hiearchical clustering of the tags.
+If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable.
+}
+% \end{figure*}
+
 \begin{figure*}
 \caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
+\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.pdf}}
 \textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
@@
 
+% \begin{figure*}
+% \caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
+% \centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
+% \textit{Notes:Unit of analysis is the Dyad-Day.
+Edges <-> indicates undirected dyad and -> indicates directed dyad.
+Top 10 most active dyads per category shown.
+Red text shows events from the synthetic narrative relative to that event category.
+Blue bars indicate an event recorded by ICEWs for that dyad on that day.
+}
+% \end{figure*}
+
 \begin{figure*}
 \caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
+\centering{\includegraphics[width=17cm]{./p_precision_icews.pdf}}
 \textit{Notes:Unit of analysis is the Dyad-Day.

### 2022-08-24 replication_paper/political_analysis_draft/appendix.Rmd
win update

--- 2022-07-25 replication_paper/pnas_draft/appendix.Rmd
@@
 #use_python("/home/skynet3/anaconda3/bin/python/")
-#reticulate::use_python("~/anaconda3/bin/python3.6") # never worked for me
-#reticulate::use_python("~/.local/share/r-miniconda/envs/r-reticulate/bin/python3.6") #works but needed module install
-#conda_install("r-reticulate", "pytorch")
+#reticulate::use_python("/home/tlscherer/anaconda3/bin/python")
 
@@
 #pip install -U sentence-transformers
+
+# can install python packages in R using code chunk above
 
@@
                                   padding( padding = 1, part = "all") %>% 
-                                  bg( i = which( ((1:56) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  bg( i = which( ((1:22) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                   ftExtra::colformat_md(j = 5, part="body")
@@
 ft_sample_precision_precision2 <- temp_sample %>% 
-                                  filter(row_number()>=57) %>%
+                                  filter(row_number() %in% 23:54) %>%
                                   dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
@@
                                   padding( padding = 1, part = "all") %>% 
-                                  bg( i = which( ((1:59) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  bg( i = which( ((23:54) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                   ftExtra::colformat_md(j = 5, part="body")
@@
 ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision2.png"), zoom=1) #
+
+ft_sample_precision_precision3 <- temp_sample %>% 
+                                  filter(row_number() %in% 55:90) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((55:90) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision3.png"), zoom=1) #
+
+ft_sample_precision_precision4 <- temp_sample %>% 
+                                  filter(row_number() %in% 91:115) %>%
+                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
+                                  flextable::as_flextable() %>%
+                                  flextable::width( j = 1:2, width=0.5)  %>% 
+                                  #flextable::width( j = 2, width=0.25)  %>% 
+                                  flextable::width( j = 3, width=0.5)  %>% 
+                                  flextable::width( j = 4:5, width=12.0)  %>% 
+                                  flextable::fontsize(size = 9, part = "all") %>%
+                                  valign(j = 1:3, valign = "top", part = "body") %>%
+                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
+                                  padding( padding = 1, part = "all") %>% 
+                                  bg( i = which( ((91:115) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
+                                  ftExtra::colformat_md(j = 5, part="body")
+
+ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision4.png"), zoom=1) #
 
@@
 
+fromscratch=F
+if(fromscratch){
+
 ## Dyadic ICB
@@
 #Crisis maps for the non ICBe datasets for the two case studies
+
+fromscratch=F
+if(fromscratch){
 
@@
           p_471_combined, base_height = 12, base_width = 25)
+}
 

### 2022-09-09 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
Political Analysis update

--- 2022-08-10 replication_paper/pnas_draft/initial_submission.Rmd
@@
   - name: Rex W. Douglass
+    thanks: Correspondence should be addressed to Rex W. Douglass at rexdouglass@gmail.com.
     affiliation: University of California, San Diego
@@
 
-# corresponding_author:
-#   code: 2
-#   text: "To whom correspondence should be addressed. E-mail: rexdouglass@gmail.com"
+corresponding_author:
+  text: "Correspondence should be addressed. E-mail: rexdouglass@gmail.com"
 
@@
 
-## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
-
 ## change to true to add optional line numbering
@@
 
-csl: pnas.csl
 bibliography: paper.bib
@@
 #  - \usepackage[backend = biber]{biblatex} #added in hopes of getting a bbl
+  - \usepackage{changepage}
+
 #https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
@@
 -->
-\twocolumn
-
-Significance Statement: Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war.
-Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms.
-This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods.
-It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.
-
-***
+
+<!-- #\twocolumn -->
+
+Introduction
+========================================
 
@@
 
-Task Definition {.unnumbered}
+Task Definition
 ========================================
@@
 for(i in 1:nrow(temp)){
-  temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
-                                                                                pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
+  temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% stringr::str_replace_all('[^a-z0-9]',"") ,
+                                                                                pattern = stringr::fixed(temp$value_markdown[i] %>% tolower() %>% stringr::str_replace_all('[^a-z0-9]',"") )
                                                                               ) %>% replace_na(0) %>%  sum()
@@
 
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","political_analysis_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
@@
 \clearpage
-\onecolumn
+<!-- \onecolumn -->
 \begin{figure}[H]
@@
 \clearpage
-\twocolumn
-
-Corpus  {.unnumbered}
+<!-- \twocolumn -->
+
+Corpus 
 ========================================
@@
 
-Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art {.unnumbered}
+Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art
 ========================================
@@
 \clearpage
-\onecolumn
+<!-- \onecolumn -->
 
@@
                                 sheet="DatasetsComparisonLitReview") #%>% janitor::clean_names() 
-dim(lit_review_pull)
+# dim(lit_review_pull)
 
@@
 lit_review_alt <- lit_review_pull %>% 
-                  mutate(Literature =   paste0(" [",Literature %>% str_replace("; {0,}$","") ,"]")) %>%
+                  mutate(Literature =   paste0(" [",Literature %>% stringr::str_replace("; {0,}$","") ,"]")) %>%
                   mutate(Concept= Concept %>% paste0(Literature)) %>%
-                  mutate(Concept = Concept %>% str_replace(fixed("[NA]"),"") ) %>%
+                  mutate(Concept = Concept %>% stringr::str_replace(stringr::fixed("[NA]"),"") ) %>%
                   dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
@@
 bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
-litreview_ft_pnas <- lit_review_alt %>%
+litreview_ft_political_analysis <- lit_review_alt %>%
       flextable::as_flextable() %>%
@@
 
-      flextable::width( j = 3, width=3) %>% 
+      flextable::width( j = 3, width=3.3) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
       flextable::width( j = (4):k, width=0.25) %>%
@@
 #https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
-#litreview_ft_pnas
-
-#litreview_ft_pnas  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_pnas.Rds'))
-litreview_ft_pnas %>% 
+#litreview_ft_political_analysis
+
+#litreview_ft_political_analysis  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_political_analysis.Rds'))
+litreview_ft_political_analysis %>% 
     flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
@@
 
-litreview_ft_pnas   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+# Uncomment for snapshot
+# litreview_ft_political_analysis %>% 
+#     #flextable::flextable_to_rmd()
+#     save_as_image(path=here::here("replication_paper", "political_analysis_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 \clearpage
-\twocolumn
+<!-- \twocolumn -->
 
@@
 
-ICBe Coding Process {.unnumbered}
+ICBe Coding Process
 ========================================
@@
 
-Internal Consistency {.unnumbered}
+Internal Consistency
 ========================================
@@
 
-Case Study Selection {.unnumbered}
+Case Study Selection
 ========================================
@@
 
-Recall {.unnumbered}
+Recall
 ========================================
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
+    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_recall.png"),
                   zoom=1, webshot = "webshot2") # webshot = "webshot2"
@@
       #Header
-      flextable::rotate(i=2, , j=3:left_end, rotation="tbrl", part="header") %>% 
-      flextable::rotate(i=2, , j=(left_end+4):k, rotation="tbrl", part="header") %>%
+      flextable::rotate(i=2, j=3:left_end, rotation="tbrl", part="header") %>% 
+      flextable::rotate(i=2, j=(left_end+4):k, rotation="tbrl", part="header") %>%
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_recall.png'),
        plot = p_recall ,
@@
 
-tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/pnas_draft/p_recall.png'))
+tiger <- image_read(here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea.png"))
+tiger2 <- image_read(paste0(here::here(), '/replication_paper/political_analysis_draft/p_recall.png'))
 
 combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))
+image_write(combined, here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea_andcounts.png"))
 
@@
 \clearpage
-\twocolumn
-
-Precision {.unnumbered}
+<!-- \twocolumn -->
+
+Precision
 ========================================
@@
 ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
+You should be able to lay out events of a crisis on a timeline, as in Figure 3 and Figure 4, and read off the macro structure of an episode from each individual move.
 We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
@@
 
+ratio=.75
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_196_icbe.png'),
+          p_196_icbe, base_height = 18, base_width = height*ratio)
+
 p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
@@
    scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
+
+ratio=.75
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_icbe.png'),
+          p_471_icbe, base_height = 18, base_width = height*ratio)
 
@@
 height=18
-save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_precision_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_precision_combined.png'),
           p_precision_combined, base_height = 18, base_width = height*ratio)
@@
 ```
-
-\clearpage
-\onecolumn
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps  \label{fig:p_precision_combined}}
-\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
-\end{sidewaysfigure}
-\clearpage
-\twocolumn
 
@@
 If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]
+
+Finally, how does ICBe's precision compare to the existing state of the art?
+The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix Figure D3 and D4).
+On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
+Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
+
+However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
+For example, [@terechshenkoHotCollarLatent2020] attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
+Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
+geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks].
+
+We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
+We choose four event types around key moments in the crisis.
+The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
+The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
+Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
+Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
+In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
+
+<!-- \clearpage -->
+<!-- \onecolumn --> 
+<!-- \begin{sidewaysfigure}[ht] -->
+<!-- \caption{Crisis Maps  \label{fig:p_precision_combined}} -->
+<!-- \centering{\includegraphics[width=22cm]{./p_precision_combined.png}} -->
+<!-- \end{sidewaysfigure} -->
+<!-- \clearpage -->
+<!-- \twocolumn -->
+
+\begin{figure}[H]
+\caption{Crisis Map: Cuban Missile Crisis \label{fig:p_196_icbe}}
+\centering{\includegraphics[width=17cm]{./p_196_icbe.png}}
+\end{figure}
+
+\begin{figure}[H]
+\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
+\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
+\end{figure}
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
 
@@
 \clearpage
-\twocolumn
-
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix Figure D3 and D4).
-On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
+<!-- \twocolumn -->
 
@@
 save_plot(file=paste0(here::here(),
-                      '/replication_paper/pnas_draft/p_precision_icews.png'),
+                      '/replication_paper/political_analysis_draft/p_precision_icews.png'),
           p_ICEWS, base_height = 10, base_width = 14)
@@
 
-However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, [@terechshenkoHotCollarLatent2020] attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
-geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks].
-
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
-We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
-Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
-In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
-
 \clearpage
-\onecolumn
+<!-- \onecolumn -->
 \begin{figure}[H]
@@
 
-Conclusion {#format .unnumbered}
+Conclusion
 ========================================
@@
 Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
+
+Funding {#format .unnumbered}
+========================================
+
+This work was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and from the Charles Koch Foundation [20180481].
 
@@
 
+Data Availability Statement {#format .unnumbered}
+========================================
+This article’s data, online appendix, replication material, and visualizations of every historical episode are available on the github repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.
+
+Conflicts of Interests {#format .unnumbered}
+========================================
+There are no conflicts of interest to disclose.
+
 &nbsp;
-
-<!-- PNAS lines Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references
-\showmatmethods
-\showacknow
-\pnasbreak
--->

### 2022-09-09 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
Political Analysis update

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{Introducing ICBe: Very High Recall and Precision Event Extraction
from Narratives about International Crises}

\author{
    Rex W. Douglass
    \thanks{Correspondence should be addressed to Rex W. Douglass at
\href{mailto:rexdouglass@gmail.com}{\nolinkurl{rexdouglass@gmail.com}}.}
   \\
    University of California, San Diego \\
   \\
  \texttt{} \\
   \And
    Thomas Leo Scherer
   \\
    University of California, San Diego \\
   \\
  \texttt{} \\
   \And
    J. Andrés Gannon
   \\
    Vanderbilt University \\
   \\
  \texttt{} \\
   \And
    Erik Gartzke
   \\
    University of California, San Diego \\
   \\
  \texttt{} \\
   \And
    Jon Lindsay
   \\
    Georgia Institute of Technology \\
   \\
  \texttt{} \\
   \And
    Shannon Carcelli
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Jonathan Wilkenfeld
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    David M. Quinn
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Catherine Aiken
   \\
    Georgetown University \\
   \\
  \texttt{} \\
   \And
    Jose Miguel Cabezas Navarro
   \\
    Universidad Mayor \\
   \\
  \texttt{} \\
   \And
    Neil Lund
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Egle Murauskaite
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Diana Partridge
   \\
    University of Maryland \\
   \\
  \texttt{} \\
  }

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage[utf8]{inputenc}
\usepackage{pifont}
\usepackage{newunicodechar}
\newunicodechar{✓}{\ding{51}}
\newunicodechar{✗}{\ding{55}}
\usepackage{array}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[parfill]{parskip}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{cellspace}
\setlength\cellspacetoplimit{0.8ex}
\renewcommand{\arraystretch}{0.8}
\AtBeginEnvironment{lltable}{\singlespacing}
\usepackage{subcaption}
\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
\usepackage{float}
\usepackage[algo2e]{algorithm2e}
\usepackage{changepage}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\begin{document}
\maketitle

\begin{abstract}
How do international crises unfold? We conceptualize of international
relations as a strategic chess game between adversaries and develop a
systematic way to measure pieces, moves, and gambits accurately and
consistently over a hundred years of history. We introduce a new
ontology and dataset of international events called ICBe based on a very
high-quality corpus of narratives from the International Crisis Behavior
(ICB) Project. We demonstrate that ICBe has higher coverage, recall, and
precision than existing state of the art datasets and conduct two
detailed case studies of the Cuban Missile Crisis (1962) and
Crimea-Donbas Crisis (2014). We further introduce two new event
visualizations (event icongraphy and crisis maps), an automated
benchmark for measuring event recall using natural language processing
(sythnetic narratives), and an ontology reconstruction task for
objectively measuring event precision. We make the data, online
appendix, replication material, and visualizations of every historical
episode available at a companion website www.crisisevents.org and the
github repository.
\end{abstract}

\keywords{
    Diplomacy
   \and
    War
   \and
    Crises
   \and
    International Affairs
   \and
    Computational Social Science
  }

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

If we could record every important interaction between countries in all
of diplomacy, military conflict, and international political economy,
how much unique information would this chronicle amount to, and how
surprised would we be to see something new? In other words, what is the
entropy of international relations? This record could in principle be
unbounded, but the central conceit of social science is that there are
structural regularities that limit what actors can do, their best
options, and even which actors are likely to survive (Brecher 1999;
Reiter 2015). If so, then these events can be systematically measured,
and accordingly, massive effort is expended in social science attempting
to record these regularities.\footnote{See work on crises (Brecher and
  Wilkenfeld 1982; Beardsley et al. 2020), militarized disputes (Palmer
  et al. 2021; Gibler 2018; Maoz et al. 2019), wars (Sarkees and Wayman
  2010; Reiter, Stam, and Horowitz 2016), organized violence (Ralph
  Sundberg and Mihai Croicu 2016; Pettersson and Eck 2018), political
  violence (Raleigh et al. 2010), sanctions (Felbermayr et al. 2020),
  trade (Barari and Kim, n.d.), and international agreements (Kinne
  2020; Owsiak, Cuttner, and Buck 2018; Vabulas and Snidal 2021),
  dispute resolution (Vabulas and Snidal 2021; Frederick, Hensel, and
  Macaulay 2017), and diplomacy (Moyer, Turner, and Meisel 2020; Sechser
  2011).} Thanks to improvements in natural language processing, more
open-ended efforts have begun to capture entire unstructured streams of
events from international news reports.\footnote{See Li et al. (2021);
  Halterman (2020); Brandt et al. (2018); Boschee et al. (2015); Hegre
  et al. (2020); Grant et al. (2017). On event-extraction from images
  and social-media see Zhang and Pan (2019) and Steinert-Threlkeld
  (2019).} How close these efforts are to accurately measuring all or
even most of what is essential in international relations is an open
empirical question, one for which we provide new evidence here.

Our contribution is a high coverage ontology and event dataset for key
historical episodes in 20th and 21st-century international relations. We
develop a large, flexible ontology of international events with the help
of both human coders and natural language processing. We apply it
sentence-by-sentence to an unusually high-quality corpus of historical
narratives of international crises (Brecher 1999; Brecher, James, and
Wilkenfeld 2000; Wilkenfeld and Brecher 2000; James 2019; Iakhnis and
James 2019). The result is a new lower bound estimate of how much
actually happens between states during pivotal historical episodes. We
then develop several methods for objectively gauging how well these
event codings reconstruct the information contained in the original
narrative. We conclude by benchmarking our event codings against several
current state-of-the-art event data collection efforts. We find that
existing systems produce sequences of events that do not contain enough
information to reconstruct the underlying historical episode. The
underlying fine-grained variation in international affairs is
unrecognizable through the lens of current quantification efforts.

This is a measurement paper that makes the following argument --- there
is a real-world unobserved latent concept known as international
relations, we propose a method for systematically measuring it, we
successfully apply this method producing a new large scale set of
measurements, those measurements exhibit several desirable kinds of
internal and external validity, and those measurements out-perform other
existing approaches. The article organizes that argument into eight
sections: task definition; corpus; priors/existing state of the art;
ICBe coding process; internal consistency; case study selection; recall;
and precision. A final section concludes.

\hypertarget{task-definition}{%
\section{Task Definition}\label{task-definition}}

We consider the measurement task of abstracting discrete events about a
historical episode in international relations. The easiest way to convey
the task is with an example. Figure 1 shows a narrative account of the
Cuban Missile Crisis (1962) alongside a mapping from each natural
language sentence to discrete machine readable abstractive events.
Formally, a historical episode, \(H\), is demarcated by a period of time
\([T_{start}, T_{end}] \in T\), a set of Players \(p \in P\), and a set
of behaviors they undertook during that time \(b \in B\). International
Relations, \(IR\), is the system of regularities that govern the
strategic interactions that world actors make during a historical
episode, given their available options, preferences, beliefs, and
expectations of choices made by others. We observe neither \(H\) nor
\(IR\) directly. Rather the Historical Record, \(HR\), produces
documents \(d \in D\) containing some relevant and true (as well as
irrelevant and untrue) information about behaviors that were undertaken
recorded in the form of unstructured natural language text. The task is
to combine informative priors about \(IR\) with an unstructured corpus
\(D\) to produce a series of structured discrete events, \(e \in E\),
that have high coverage, precision, and recall over what actually took
place in history, \(H\).

\clearpage

\begin{figure}[H]
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=19cm]{"./case_study_cuban_precision.png"}}
\end{figure}
\clearpage

\hypertarget{corpus}{%
\section{Corpus}\label{corpus}}

For our corpus, \(D\), we select a set of unusually high-quality
historical narratives from the International Crisis Behavior (ICB)
project (\(n=471\))(SI Appendix, Table A1)(Brecher et al. 2017; Brecher
and Wilkenfeld 1997).\footnote{The Online Appendix is at the
  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData
  Github Repository}.} Their domain is 20th and 21st-century crises,
defined as a change in the type, or an increase in the intensity, of
disruptive interaction with a heightened probability of military
hostilities that destabilizes states' relationships or challenges the
structure of the international system (Brecher and Wilkenfeld
1982).\footnote{On near crises see Iakhnis and James (2019).} Crises are
a significant focus of detailed single case studies and case comparisons
because they provide an opportunity to examine behaviors in IR short of,
or at least prior to, full conflict (Holsti 1965; Paige 1968; Allison
and Zelikow 1971; Snyder and Diesing 1977; Gavin 2014; George and Smoke
1974; Brecher and Wilkenfeld 1982; Gaddis 1987; Brecher and James 1988).
Case selection was exhaustive based on a survey of world news archives
and region experts, cross-checked against other databases of war and
conflict, and non-English sources (Kang and Lin 2019; Brecher et al.
2017, 59). Each narrative was written by consensus by a small number of
scholars, using a uniform coding scheme, with similar specificity
(Hewitt 2001). The corpus is unique in IR because it is designed to be
used in a downstream quantitative coding project.

\hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
\section{Prior Beliefs about IR, Ontological Coverage, and the Existing
State of the
Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}

Next we draw informative prior beliefs about the underlying process of
IR that we expect to govern behavior during historical episodes and
their conversion to the historical record. We organize our prior beliefs
along two overarching axes, summarized in detail by Table 1.

The first axis (rows) represents the types of information we expect to
find in IR and forms the basis for our proposed ontology. We employ a
metaphor of a chess game, with players (polities, rebel groups, IGOs,
etc.), pieces (military platforms, civilians, domains), and behaviors
(think, say, do). Precise sequencing is required to capture gambits
(sequences of moves) and outcomes (victory, defeat, peace, etc.), while
precise geo-coding is required to understand the chessboard (medium of
conflict). We find 472 actors and 117 different behaviors, and provide a
full codebook in the online material.\footnote{See the Github Repository
  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}

We base our informed priors primarily on two sources of information. The
first is the extensive existing measurement efforts of IR which we
provide citations to alongside each concept. Second, we performed
preliminary natural language processing of the corpus and identified
named entities and behaviors mentioned in the text. Verbs were matched
to the most likely definition found in Wordnet (Miller 1995), tallied,
and then aggregated into a smaller number hypernyms balancing conceptual
detail and manageable sparsity for human coding (SI Appendix, Table A2).

The second axis (columns) compares the very high ontological coverage of
ICBe to existing state of the art systems in production and with global
coverage. They begin with our contribution ICBe, alongside other
event-level datasets including CAMEO dictionary lookup based systems
(Historical Phoenix (Althaus et al. 2019); ICEWS (Boschee et al. 2015;
Hegre et al. 2020); Terrier (Grant et al. 2017)), the Militarized
Interstate Disputes Incidents dataset, and the UCDP-GED dataset (Ralph
Sundberg and Mihai Croicu 2016; Pettersson and Eck 2018; Sundberg and
Melander 2013).\footnote{Additional relevant but dated or too small of
  an overlap in domain include BCOW (Leng and Singer 1988), WEIS
  (McClelland 1978), CREON (Hermann 1984), CASCON (Bloomfield and
  Moulton 1989), SHERFACS (Sherman 2000), Real-Time Phoenix (Brandt et
  al. 2018), and COfEE (Balali, Asadpour, and Jafari 2021) (see
  histories in Merritt (1994) and Schrodt and Hall (2006)).} The final
set of columns compares episode-level datasets beginning with the
original ICB project (Brecher et al., n.d.; Brecher and Wilkenfeld 1982;
Beardsley et al. 2020); the Militarized Interstate Disputes dataset
(Palmer et al. 2021; Gibler 2018; Braithwaite 2010, 2009), and the
Correlates of War (Sarkees and Wayman 2010). With the exception of large
scale CAMEO dictionary based systems, the existing state of the art
quantitative datasets ignore the vast majority of the information
content found in international relations.\footnote{See (Balali,
  Asadpour, and Jafari 2021) for a recent review of ontological depth
  and availability of Gold Standard example text.}

\clearpage

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.75}

\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.30in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}

\caption{Ontological coverage of ICBe versus existing State of the Art
}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.5in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.5in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Brecher}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hegre}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Iakhnis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{James}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Kreutz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weisiger}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Fazal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Paul,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ikenberry,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hall}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Haffar}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2002;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hsu}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{et}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{al.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{McMillan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2008)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Bush}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Kim}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2008;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Ben-Yehuda}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{mishali–ram}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Lacina}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gleditsch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Carafano}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1986;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Gartzke}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Horowitz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lanoszka}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hunzeker}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Carter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Lupton}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Goldgeier}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2001;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mercer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Stein}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Russett}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sullivan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Ramsay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wirtz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(O’Neill}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Risse}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Trager}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Zartman}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Faure}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Davis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(R.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Goemans,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Harkness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Jones}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Olken}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Matanock}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Chenoweth,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hendrix,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hunter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Eck}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hultman}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{LaFree}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dugan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Beardsley}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Anac}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gibler}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2004;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Owsiak,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cuttner,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Buck}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2003/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(de}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Lai}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Allen,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Flynn,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Martinez}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Machain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Fortna}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Min}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Levy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Thompson}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reiter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2009)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Frederick,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hensel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1996;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Schultz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\end{longtable}

\clearpage

\hypertarget{icbe-coding-process}{%
\section{ICBe Coding Process}\label{icbe-coding-process}}

The ICBe ontology follows a hierarchical design philosophy where a
smaller number of significant decisions are made early on and then
progressively refined into more specific details (Brust and Denzler
2020).\footnote{This process quickly focuses the coder on a smaller
  number of relevant options while also allowing them to apply multiple
  tags if the sentence explicitly includes more than one or there is
  insufficient evidence to choose only one tag. The guided coding
  process also allows for the possibility that earlier coarse decisions
  have less error than later fine-grained decisions.} Each coder was
instructed to first thoroughly read the full crisis narrative and then
presented with a custom graphical user interface (SI Appendix, Fig. B1).
Coders then proceeded sentence by sentence, choosing the number of
events (0-3) that occurred, the highest behavior (thought, speech, or
activity), a set of players (\(P\)), whether the means were primarily
armed or unarmed, whether there was an increase or decrease in
aggression (uncooperative/escalating or cooperative/de-escalating), and
finally one or more non-mutually exclusive specific activities. Some
additional details like location and timing information was always
collected while other details were only collected if appropriate,
e.g.~force size, fatalities, domains, units, etc. A unique feature of
the ontology is that thought, speech, and do behaviors can be nested
into combinations, e.g.~an offer for the U.S.S.R. to remove missiles
from Cuba in exchange for the U.S. removing missiles from Turkey.
Through compounding, the ontology can capture what players were said to
have known, learned, or said about other specific fully described
actions.

Each crisis was typically assigned to 2 expert coders and 2 novice
coders with an additional tie-breaking expert coder assigned to
sentences with high disagreement.\footnote{Expert coders were graduate
  students or postgraduates who collaboratively developed the ontology
  and documentation for the codebook. Undergraduate coders were students
  who engaged in classroom workshops.} For the purposes of measuring
intercoder agreement and consensus, we temporarily disaggregate the unit
of analysis to the Coder-Crisis-Sentence-Tag (n=993,740), where a tag is
any unique piece of information a coder can associate with a sentence
such as an actor, date, behavior, etc. We then aggregate those tags into
final events (n=18,783), using a consensus procedure (SI Appendix,
Algorithm B2) that requires a tag to have been chosen by at least one
expert coder and either a majority of expert or novice coders. This
screens noisy tags that no expert considered possible but leverages
novice knowledge to tie-break between equally plausible tags chosen by
experts.

\hypertarget{internal-consistency}{%
\section{Internal Consistency}\label{internal-consistency}}

We evaluate the internal validity of the coding process in several ways.
For every tag applied we calculate the observed intercoder agreement as
the percent of other coders who also applied that same tag (SI Appendix,
Fig. B3). Across all concepts, the Top 1 Tag Agreement was low among
novices (31\%), moderate for experts (65\%), and high (73\%) following
the consensus screening procedure.

We attribute the remaining disagreement primarily to three sources.
First, we required coders to rate their confidence which was observed to
be low for 20\% of sentences- half due to a mismatch between the
ontology and the text (``survey doesn't fit event''-45\%) and half due
to a lack of information or confused writing in the source text (``more
knowledge needed''-40\%, ``confusing sentence''-6\%). Observed
disagreement varied predictably with self reported confidence (SI
Appendix, Fig. B4). Second, as intended agreement is higher (75-80\%)
for questions with fewer options near the root of the ontology compared
to agreement for questions near the leafs of the ontology (50\%-60\%).
Third, individual coders exhibiting nontrivial coding styles, e.g.~some
more expressive applying many tags per concept while others focused on
only the single best match. We further observed unintended synonymity,
e.g.~the same information can be framed as either a threat to do
something or a promise not to do something.

\hypertarget{case-study-selection}{%
\section{Case Study Selection}\label{case-study-selection}}

The remaining two qualities we seek to measure are recall and precision
of ICBe events in absolute terms and relative to other existing systems.
We provide full ICB narratives, ICBe coding in an easy to read
icongraphic form, and a wide range of visualizations for every case on
the companion website. In this paper, we focus on two deep case studies.
The first is the Cuban Missile Crisis (Figure 1) which took place
primarily in the second half of 1962, involved the United States, the
Soviet Union, and Cuba, and is widely known for bringing the world to
the brink of nuclear war (hereafter Cuban Missiles). The second is the
Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily
in 2014, involved Russia, Ukraine, and NATO, and within a decade
spiraled into a full scale invasion (herafter Crimea-Donbas). Both cases
involve a superpower in crisis with a neighbor, initiated by a change
from a friendly to hostile regime, with implications for economic and
military security for the superpower, risked full scale invasion, and
eventually invited intervention by opposing superpowers. We choose these
cases because they are substantively significant to 20th and 21st
century international relations, widely known across scientific
disciplines and popular culture, and are sufficiently brief to evaluate
in depth.

\hypertarget{recall}{%
\section{Recall}\label{recall}}

Recall measures the share of desired information recovered by a sequence
of coded events, \(Pr(E|H)\), and is poorly defined for historical
episodes. First, there is no genuine ground truth about what occurred,
only surviving texts about it. Second, there is no \textit{a priori}
guide to what information is necessary detail and what is ignorable
trivia. History suffers from what is known as the Coastline Paradox
(Mandelbrot 1983) --- it has a fractal dimension greater than one such
that the more you zoom in the more detail you will find about individual
events and in between every two discrete events. The ICBe ontology is a
proposal about what information is important, but we need an independent
benchmark to evaluate whether that proposal is a good one and that
allows for comparing proposals from event projects that had different
goals. We need a yardstick for history.

Our strategy for dealing with both problems is a plausibly objective
yardstick called a synthetic historical narrative. For both case
studies, we collect a large diverse corpus of narratives spanning
timelines, encyclopedia entries, journal articles, news reports,
websites, and government documents. Using natural language processing
(fully described in SI Appendix, Algorithm C1), we identify details that
appear across multiple accounts. The more accounts that mention a
detail, the more central it is to understanding the true historical
episode. The theoretical motivation is that authors face word limits
which force them to pick and choose which details to include, and they
choose details which serve the specific context of the document they are
producing. With a sufficiently large and diverse corpus of documents, we
can vary the context while holding the overall episode constant and see
which details tend to be invariant to context. Intuitively, a high
quality event dataset should have high recall for context invariant
details both because of their broader relevance and also because they
are easier to find in source material.

Synthetic historical narratives for Cuban Missiles (51 events drawn from
2020 documents) and Crimea-Donbas (30 events drawn from 971 documents)
appear in Figure 2. Each row represents a detail which appeared in at
least five documents along with an approximate start date, a hand
written summary, the number of documents it was mentioned in, and
whether it could be identified in the text of our ICB corpus, in our
ICBe events, or any of the competing systems.

From them, we draw several stylized facts. First, there is substantial
variation in which details any one document will choose to include. Our
ground truth ICB narratives included 17/51 and 23/30 of the events from
the synthetic narrative, while including other details that are not in
the synthetic narrative. Second, mentions of a detail across accounts is
exponentially distributed with context invariant details appearing
dozens to hundreds of times more than context dependent details. Third,
crisis start and stop dates are arbitrary and the historical record
points to many precursor events as necessary detail for understanding
later events, e.g.~the U.S. was in a \textit{de facto} grey scale war
with Cuba before it invited Soviet military protection (Cormac and
Aldrich 2018) and Ukraine provided several security guarantees to Russia
that were potentially undone, e.g.~a long term lease on naval facilities
in Crimea. Fourth, we find variation between the two cases. Cuban
Missiles has a cleaner canonical end with the Soviets agreeing to
withdraw missiles while Crimea-Donbas meekly ends with a second cease
fire agreement (Minsk II) but continued fighting. The canonical
narrative of Cuban Missile also includes high level previously
classified details, while the more recent Crimea-Donbas case reflects
primarily public reporting.

We find substantive variation in recall across systems. Recall for each
increases in the number of document mentions which is an important sign
of validity for both them and our benchmark. The one outlier is Phoenix
which is so noisy that it's flat to decreasing in mentions. The two
episode level datasets have very low coverage of contextual details. The
two other dictionary systems ICEWs and Terrier have high coverage, with
ICEWs outperforming Terrier. ICBe strictly dominates all of the systems
but ICEWs in recall though we note that the small sample sizes mean
these systems should be considered statistically indistinguishable.
Importantly our corpus of ICB narratives has very high recall of
frequently mentioned details giving us confidence in how those summaries
were constructed, and ICBe lags only slightly behind showing that it
left very little additional information on the table.

\clearpage

\begin{figure}[H]
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure}
\clearpage

\hypertarget{precision}{%
\section{Precision}\label{precision}}

The other side of event measurement is precision, the degree to which a
sequence of events correctly and usefully describes the information in
history, \(Pr(H|E)\). It does little good to recall a historical event
but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a
blockade, a show of force, and a stalemate) or with too much error
(e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between
1995-2019) to be useful for downstream applications. ICBe's ontology and
coding system is designed to strike a balance so that the most important
information is recovered accurately but also abstracted to a level that
is still useful and interpretable. You should be able to lay out events
of a crisis on a timeline, as in Figure 3 and Figure 4, and read off the
macro structure of an episode from each individual move. We call this
visualization a crisis map, a directed graph intersected with a
timeline, and provide crisis maps for every event dataset for each case
study (SI Appendix, Fig. D3 and D4) and all crises on the companion
website.

We further want to verify individual event codings, which we can do in
the case of ICBe because each event is mapped to a specific span of
text. We develop the iconography system for presenting event codings as
coherent statements that can be compared side by side to the original
source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI
Appendix Table D1), and for every case on the companion website. We
further provide a stratified sample of event codings alongside their
source text (SI Appendix Table D2).

We find both the visualizations of macro structure and head-to-head
comparisons of ICBe codings to the raw text to strongly support the
quality of ICBe, but as with recall we seek a more objective detached
universal benchmark. Our proposed measure is a reconstruction task to
see whether our intended ontology can be recovered through only
unsupervised clustering of sentences they were applied to. Figure 4
shows the location of every sentence from the ICBe corpus in semantic
space as embeded using the same large language model as before, and the
median location of each ICBe event tag applied to those
sentences.\footnote{We preprocess sentences to replace named entities
  with a generic Entity token.} Labels reflect the individual leaves of
the ontology and colors reflect the higher level coerce branch nodes of
the ontology. If ICBe has high precision, substantively similar tags
ought to have been applied to substantively similar source text, which
is what we see both in two dimensions in the main plot and via
hierarchical clustering on all dimensions in the dendrogram along the
righthand side.\footnote{Hierchcial clustering on cosine similarity and
  with Ward's method.}

Finally, how does ICBe's precision compare to the existing state of the
art? The crisis-maps reveal the episode level datasets like MIDs or the
original ICB are too sparse and vague to reconstruct the structure of
the crisis (SI Appendix Figure D3 and D4). On the other end of the
spectrum, the high recall dictionary based event datasets like Terrier
and ICEWs produce so many noisy events (several hundreds thousands) that
even with heavy filtering their crisis maps are completely
unintelligible. Further, because of copyright issues, none of these
datasets directly provide the original text spans making event level
precision difficult to verify.

However, given their high recall on our task and the global and
real-time coverage of dictionary based event systems, we want to take
seriously the possibility that some functional transformation could
recover the precision of ICBe. For example, (Terechshenko 2020) attempts
to correct for the mechanically increasing amount of news coverage each
year by detrending violent event counts from Phoenix using a human coded
baseline. Others have focused on verifying precision for ICEWs on
specific subsets of details against known ground truths,
e.g.~geolocation (Cook and Weidmann 2019), protest events (80\%) (Wüest
and Lorenzini 2020), anti-government protest networks (46.1\%) (Jäger,
n.d.).

We take the same approach here in Figure 5, selecting four specific
CAMEO event codings and checking how often they reflect a true real
world event. We choose four event types around key moments in the
crisis. The start of the crisis revolves around Ukraine backing out of
trade deal with the EU in favor of Russia, but ``sign formal agreement''
events act more like a topic detector with dozens of events generated by
discussions of a possible agreement but not the actual agreement which
never materialized. The switch is caught by the ``reject plan, agreement
to settle dispute'', but also continues for Victor Yanukovych for even
after he was removed from power because of articles retroactively
discussing the cause of his of his removal. Events for ``use
conventional military force'' capture a threshold around the start of
hostilities and who the participants were but not any particular battles
or campaigns. Likewise, ``impose embargo, boycott, or sanctions''
captures the start of waves of sanctions and from who but are
effectively constantly as the news coverage does not distinguish between
subtle changes or additions. In sum, dictionary based methods on news
corpora tend to have high recall because they parse everything in the
news, but for the same reason their specificity for most event types is
too low to back out individual chess like sequencing that ICBe aims to
record.

\begin{figure}[H]
\caption{Crisis Map: Cuban Missile Crisis \label{fig:p_196_icbe}}
\centering{\includegraphics[width=17cm]{./p_196_icbe.png}}
\end{figure}

\begin{figure}[H]
\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
\end{figure}

\clearpage

\begin{figure}[H]
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable. }
\end{figure}
\clearpage

\clearpage

\begin{figure}[H]
\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
\textit{Notes:Unit of analysis is the Dyad-Day. Edges <-> indicates undirected dyad and -> indicates directed dyad. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Blue bars indicate an event recorded by ICEWs for that dyad on that day. }
\end{figure}
\clearpage

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

We investigated event abstraction from narratives describing key
historical episodes in international relations. We synthesized a prior
belief about the latent unobserved phenomena that drive these events in
international relations and proposed a mapping to observable concepts
that enter into the observed historical record. We designed an ontology
with high coverage over those concepts and developed a training
procedure and technical stack for human coding of historical texts.
Multiple validity checks find the resulting codings have high internal
validity (e.g.~intercoder agreement) and external validity
(i.e.~matching source material in both micro-details at the sentence
level and macro-details spanning full historical episodes). Further,
these codings perform much better in terms of recall, precision,
coverage, and overall coherence in capturing these historical episodes
than existing event systems used in international relations.

We release several open-source products along with supporting code and
documentation to further advance the study of IR, event extraction, and
natural language processing. The first is the International Crisis
Behavior Events (ICBe) dataset, an event-level aggregation of what took
place during the crises identified by the ICB project. These data are
appropriate for statistical analysis of hard questions about the
sequencing of events (e.g.~escalation and de-escalation of conflicts).
Second, we provide a coder-level disaggregation with multiple codings of
each sentence by experts and undergrads that allows for the introduction
of uncertainty and human interpretation of events. Further, we release a
direct mapping from the codings to the source text at the sentence level
as a new resource for natural language processing. Finally, we provide a
companion website that incorporates detailed visualizations of all of
the data introduced here (www.crisisevents.org).

\hypertarget{format}{%
\section*{Funding}\label{format}}
\addcontentsline{toc}{section}{Funding}

This work was supported by a grant from the Office of Naval Research
{[}N00014-19-1-2491{]} and from the Charles Koch Foundation
{[}20180481{]}.

\hypertarget{format}{%
\section*{Acknowledgements}\label{format}}
\addcontentsline{toc}{section}{Acknowledgements}

We thank the ICB Project and its directors and contributors for their
foundational work and their help with this effort. We make special
acknowledgment of Michael Brecher for helping found the ICB project in
1975, creating a resource that continues to spark new insights to this
day. We thank the many undergraduate coders for their patience and
dedication. Thanks to the Center for Peace and Security Studies and its
membership for comments. Special thanks to Rebecca Cordell, Philip
Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for
generous feedback. Thank you to the cPASS research assistants that
contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano
Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna
Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and
Ruixuan Zhang. This project was supported by a grant from the Office of
Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles
Koch Foundation's support for the Center for Peace and Security Studies.

\hypertarget{format}{%
\section*{Author Contributions}\label{format}}
\addcontentsline{toc}{section}{Author Contributions}

Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.;
Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D.,
T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N.,
D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing -
Original Draft: R.W.D., T.L.S.; Writing - Review \& Editing: R.W.D.,
J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.;
Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.;
Funding Acquisition: E.G., J.L.

\hypertarget{format}{%
\section*{Data Availability Statement}\label{format}}
\addcontentsline{toc}{section}{Data Availability Statement}

This article's data, online appendix, replication material, and
visualizations of every historical episode are available on the github
repository
\href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}
and through the companion website www.crisisevents.org.

\hypertarget{format}{%
\section*{Conflicts of Interests}\label{format}}
\addcontentsline{toc}{section}{Conflicts of Interests}

There are no conflicts of interest to disclose.

~

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
Allison, Graham T., and Philip Zelikow. 1971. \emph{Essence of Decision:
{Explaining} the {Cuban} Missile Crisis}. Vol. 327. 729.1. {Little,
Brown Boston}.

\leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
Althaus, Scott, Joseph Bajjalieh, John F. Carter, Buddy Peyton, and Dan
A. Shalmon. 2019. {``Cline {Center Historical Phoenix Event Data
Variable Descriptions}.''} \emph{Cline Center Historical Phoenix Event
Data}.

\leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
Balali, Ali, Masoud Asadpour, and Seyed Hossein Jafari. 2021.
{``{COfEE}: {A Comprehensive Ontology} for {Event Extraction} from
Text.''} {arXiv}. \url{https://doi.org/10.48550/arXiv.2107.10326}.

\leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
Barari, Soubhik, and In Song Kim. n.d. {``Democracy and {Trade Policy}
at the {Product Level}: {Evidence} from a {New Tariff-line Dataset},''}
16.

\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
Beardsley, Kyle, Patrick James, Jonathan Wilkenfeld, and Michael
Brecher. 2020. {``The {International Crisis Behavior Project}.''}
{Oxford Research Encyclopedia of Politics}. September 28, 2020.
\url{https://doi.org/10.1093/acrefore/9780190228637.013.1638}.

\leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
Bloomfield, Lincoln P., and Allen Moulton. 1989. {``{CASCON III}:
{Computer-aided} System for Analysis of Local Conflicts.''} \emph{MIT
Center for International Studies, Cambridge}.

\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
Boschee, Elizabeth, Jennifer Lautenschlager, Sean O'Brien, Steve
Shellman, James Starz, and Michael Ward. 2015. {``{ICEWS} Coded Event
Data.''} \emph{Harvard Dataverse} 12.

\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
Braithwaite, Alex. 2009. {``Codebook for the {Militarized Interstate
Dispute Location} ({MIDLOC}) {Data}, v 1.0.''} \emph{University College
London}.

\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
---------. 2010. {``{MIDLOC}: {Introducing} the {Militarized Interstate
Dispute Location} Dataset.''} \emph{Journal of Peace Research} 47 (1):
91--98. \url{https://doi.org/10.1177/0022343309350008}.

\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
Brandt, Patrick T., Vito DOrazio, Jennifer Holmes, Latifur Khan, and
Vincent Ng. 2018. {``Phoenix {Real-Time Event Data}.''}
\url{http://eventdata.utdallas.edu}.

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
Brecher, Michael. 1999. {``International Studies in the Twentieth
Century and Beyond: {Flawed} Dichotomies, Synthesis, Cumulation: {ISA}
Presidential Address.''} \emph{International Studies Quarterly} 43 (2):
213--64.

\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
Brecher, Michael, and Patrick James. 1988. {``Patterns of Crisis
Management.''} \emph{Journal of Conflict Resolution} 32 (3): 426--56.

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
Brecher, Michael, Patrick James, and Jonathan Wilkenfeld. 2000.
{``Crisis Escalation to War: {Findings} from the {International Crisis
Behavior Project}.''} \emph{What Do We Know About War}.

\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
Brecher, Michael, and Jonathan Wilkenfeld. 1982. {``Crises in {World
Politics}.''} \emph{World Politics} 34 (3): 380--417.
\url{https://doi.org/10.2307/2010324}.

\leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
---------. 1997. \emph{A {Study} of {Crisis}}. {University of Michigan
Press}.

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
Brecher, Michael, Jonathan Wilkenfeld, Kyle C. Beardsley, Patrick James,
and David Quinn. 2017. {``International {Crisis Behavior Data
Codebook}.''} Codebook Version 12.
\url{http://sites.duke.edu/icbdata/data-collections/}.

\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
Brecher, Michael, Jonathan Wilkenfeld, Kyle Beardsley, Patrick James,
and David Quinn. n.d. {``International {Crisis Behavior Data Codebook},
{Version} 12,''} 69.

\leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
Brust, Clemens-Alexander, and Joachim Denzler. 2020. {``Integrating
Domain Knowledge: Using Hierarchies to Improve Deep Classifiers.''}
\url{http://arxiv.org/abs/1811.07125}.

\leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
Cook, Scott J., and Nils B. Weidmann. 2019. {``Lost in {Aggregation}:
{Improving Event Analysis} with {Report-Level Data}.''} \emph{American
Journal of Political Science} 63 (1): 250--64.
\url{https://doi.org/10.1111/ajps.12398}.

\leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
Cormac, Rory, and Richard J. Aldrich. 2018. {``Grey Is the New Black:
Covert Action and Implausible Deniability.''} \emph{International
Affairs} 94 (3): 477--94. \url{https://doi.org/10.1093/ia/iiy067}.

\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
Felbermayr, Gabriel, Aleksandra Kirilakha, Constantinos Syropoulos,
Erdal Yalcin, and Yoto V. Yotov. 2020. {``The Global Sanctions Data
Base.''} \emph{European Economic Review} 129 (October): 103561.
\url{https://doi.org/10.1016/j.euroecorev.2020.103561}.

\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
Frederick, Bryan A, Paul R Hensel, and Christopher Macaulay. 2017.
{``The {Issue Correlates} of {War Territorial Claims Data},
1816--20011.''} \emph{Journal of Peace Research} 54 (1): 99--108.
\url{https://doi.org/10.1177/0022343316676311}.

\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
Gaddis, John Lewis. 1987. {``Expanding the {Data Base}: {Historians},
{Political Scientists}, and the {Enrichment} of {Security Studies}.''}
\emph{International Security} 12 (1): 3--21.
\url{https://doi.org/10.2307/2538915}.

\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
Gavin, Francis J. 2014. {``History, {Security Studies}, and the {July
Crisis}.''} \emph{Journal of Strategic Studies} 37 (2): 319--31.
\url{https://doi.org/10.1080/01402390.2014.912916}.

\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
George, Alexander L., and Richard Smoke. 1974. \emph{Deterrence in
{American} Foreign Policy: {Theory} and Practice}. {Columbia University
Press}.

\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
Gibler, Douglas M. 2018. \emph{International {Conflicts}, 1816-2010:
{Militarized Interstate Dispute Narratives}}. {Rowman \& Littlefield}.
\url{https://books.google.com?id=_4VTDwAAQBAJ}.

\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
Grant, Christan, Andrew Halterman, Jill Irvine, Yan Liang, and Khaled
Jabr. 2017. {``{OU Event Data Project},''} December.
\url{https://osf.io/4m2u7/}.

\leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
Halterman, Andy. 2020. {``Extracting {Political Events} from {Text Using
Syntax} and {Semantics}.''}

\leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
Hegre, Håvard, Mihai Croicu, Kristine Eck, and Stina Högbladh. 2020.
{``Introducing the {UCDP Candidate Events Dataset}.''} \emph{Research \&
Politics} 7 (3): 2053168020935257.

\leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
Hermann, Charles. 1984. {``Comparative {Research} on the {Events} of
{Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968:
{Version} 1.''} {ICPSR - Interuniversity Consortium for Political and
Social Research}. \url{https://doi.org/10.3886/ICPSR05205.V1}.

\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
Hewitt, J. Joseph. 2001. {``Engaging {International Data} in the
{Classroom}: {Using} the {ICB Interactive Data Library} to {Teach
Conflict} and {Crisis Analysis}.''} \emph{International Studies
Perspectives} 2 (4): 371--83.
\url{https://doi.org/10.1111/1528-3577.00066}.

\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
Holsti, Ole R. 1965. {``The 1914 {Case}.''} \emph{The American Political
Science Review} 59 (2): 365--78. \url{https://doi.org/10.2307/1953055}.

\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
Iakhnis, Evgeniia, and Patrick James. 2019. {``Near Crises in World
Politics: {A} New Dataset.''} \emph{Conflict Management and Peace
Science}, July, 0738894219855610.
\url{https://doi.org/10.1177/0738894219855610}.

\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
Jäger, Kai. n.d. {``The {Limits} of {Studying Networks} with {Event
Data}: {Evidence} from the {ICEWS Dataset}.''}

\leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
James, Patrick. 2019. {``What Do We Know about Crisis, Escalation and
War? {A} Visual Assessment of the {International Crisis Behavior
Project}.''} \emph{Conflict Management and Peace Science} 36 (1): 3--19.
\url{https://doi.org/10.1177/0738894218793135}.

\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
Kang, David C., and Alex Yu-Ting Lin. 2019. {``{US} Bias in the Study of
{Asian} Security: {Using Europe} to Study {Asia}.''} \emph{Journal of
Global Security Studies} 4 (3): 393--401.

\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
Kinne, Brandon J. 2020. {``The {Defense Cooperation Agreement Dataset}
({DCAD}).''} \emph{Journal of Conflict Resolution} 64 (4): 729--55.
\url{https://doi.org/10.1177/0022002719857796}.

\leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
Leng, Russell J., and J. David Singer. 1988. {``Militarized {Interstate
Crises}: {The BCOW Typology} and {Its Applications}.''}
\emph{International Studies Quarterly} 32 (2): 155--73.
\url{https://doi.org/10.2307/2600625}.

\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
Li, Qian, Hao Peng, Jianxin Li, Yiming Hei, Rui Sun, Jiawei Sheng, Shu
Guo, et al. 2021. {``A {Comprehensive Survey} on {Schema-based Event
Extraction} with {Deep Learning}.''}
\url{http://arxiv.org/abs/2107.02126}.

\leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
Mandelbrot, Benoit B. 1983. \emph{The fractal geometry of nature}. {New
York}: {Freeman}.

\leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
Maoz, Zeev, Paul L. Johnson, Jasper Kaplan, Fiona Ogunkoya, and Aaron P.
Shreve. 2019. {``The {Dyadic Militarized Interstate Disputes} ({MIDs})
{Dataset Version} 3.0: {Logic}, {Characteristics}, and {Comparisons} to
{Alternative Datasets}.''} \emph{Journal of Conflict Resolution} 63 (3):
811--35. \url{https://doi.org/10.1177/0022002718784158}.

\leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
McClelland, Charles. 1978. {``World Event/Interaction Survey,
1966-1978.''} \emph{WEIS Codebook ICPSR} 5211.

\leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
Merritt, Richard L. 1994. {``Measuring Events for International
Political Analysis.''} \emph{International Interactions} 20 (1-2):
3--33.

\leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
Miller, George A. 1995. {``{WordNet}: A Lexical Database for
{English}.''} \emph{Communications of the ACM} 38 (11): 39--41.
\url{https://doi.org/10.1145/219717.219748}.

\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
Moyer, Jonathan D, Sara D Turner, and Collin J Meisel. 2020. {``What Are
the Drivers of Diplomacy? {Introducing} and Testing New Annual Dyadic
Data Measuring Diplomatic Exchange.''} \emph{Journal of Peace Research},
September, 0022343320929740.
\url{https://doi.org/10.1177/0022343320929740}.

\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
Owsiak, Andrew P, Allison K Cuttner, and Brent Buck. 2018. {``The
{International Border Agreements Dataset}.''} \emph{Conflict Management
and Peace Science} 35 (5): 559--76.
\url{https://doi.org/10.1177/0738894216646978}.

\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
Paige, Glenn D. 1968. \emph{The {Korean Decision}, {June} 24-30, 1950}.
{Free Press}.

\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
Palmer, Glenn, Roseanne W McManus, Vito D'Orazio, Michael R Kenwick,
Mikaela Karstens, Chase Bloch, Nick Dietrich, Kayla Kahn, Kellan Ritter,
and Michael J Soules. 2021. {``The {Mid5 Dataset}, 2011--2014:
{Procedures}, Coding Rules, and Description.''} \emph{Conflict
Management and Peace Science}, February, 0738894221995743.
\url{https://doi.org/10.1177/0738894221995743}.

\leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
Pettersson, Therése, and Kristine Eck. 2018. {``Organized Violence,
1989--2017.''} \emph{Journal of Peace Research} 55 (4): 535--47.
\url{https://doi.org/10.1177/0022343318784101}.

\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
Raleigh, Clionadh, Andrew Linke, Håavard Hegre, and Joakim Karlsen.
2010. {``Introducing {ACLED}: An Armed Conflict Location and Event
Dataset: Special Data Feature.''} \emph{Journal of Peace Research} 47
(5): 651--60.

\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
Ralph Sundberg, and Mihai Croicu. 2016. {``{UCDP GED Codebook} Version
5.0.''} {Department of Peace and Conflict Research, Uppsala University}.

\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
Reiter, Dan. 2015. {``Should {We Leave Behind} the {Subfield} of
{International Relations}?''} \emph{Annual Review of Political Science}
18 (1): 481--99.
\url{https://doi.org/10.1146/annurev-polisci-053013-041156}.

\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
Reiter, Dan, Allan C. Stam, and Michael C. Horowitz. 2016. {``A {Revised
Look} at {Interstate Wars}, 1816--2007.''} \emph{Journal of Conflict
Resolution} 60 (5): 956--76.
\url{https://doi.org/10.1177/0022002714553107}.

\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
Sarkees, Meredith Reid, and Frank Wayman. 2010. \emph{Resort to War:
1816-2007}. {CQ Press}.

\leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
Schrodt, Philip A., and Blake Hall. 2006. {``Twenty Years of the
{Kansas} Event Data System Project.''} \emph{The Political
Methodologist} 14 (1): 2--8.

\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
Sechser, Todd S. 2011. {``Militarized {Compellent Threats},
1918--2001.''} \emph{Conflict Management and Peace Science} 28 (4):
377--401. \url{https://doi.org/10.1177/0738894211413066}.

\leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
Sherman, Frank L. 2000. {``{SHERFACS}: {A Cross-Paradigm},
{Hierarchical}, and {Contextually-Sensitive International Conflict
Dataset}, 1937-1985: {Version} 1.''} {ICPSR - Interuniversity Consortium
for Political and Social Research}.
\url{https://doi.org/10.3886/ICPSR02292.V1}.

\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
Snyder, Glenn Herald, and Paul Diesing. 1977. \emph{Conflict Among
Nations: {Bargaining} and Decision Making in International Crises}.
{Princeton University Press}.

\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
Steinert-Threlkeld, Zachary C. 2019. {``The {Future} of {Event Data Is
Images}.''} \emph{Sociological Methodology} 49 (1): 68--75.
\url{https://doi.org/10.1177/0081175019860238}.

\leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
Sundberg, Ralph, and Erik Melander. 2013. {``Introducing the {UCDP}
Georeferenced Event Dataset.''} \emph{Journal of Peace Research} 50 (4):
523--32.

\leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
Terechshenko, Zhanna. 2020. {``Hot Under the Collar: {A} Latent Measure
of Interstate Hostility.''} \emph{Journal of Peace Research} 57 (6):
764--76. \url{https://doi.org/10.1177/0022343320962546}.

\leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
Vabulas, Felicity, and Duncan Snidal. 2021. {``Cooperation Under
Autonomy: {Building} and Analyzing the {Informal Intergovernmental
Organizations} 2.0 Dataset.''} \emph{Journal of Peace Research} 58 (4):
859--69. \url{https://doi.org/10.1177/0022343320943920}.

\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
Wilkenfeld, Jonathan, and Michael Brecher. 2000. {``Interstate Crises
and Violence: Twentieth-Century Findings.''} \emph{Handbook of War
Studies II}, 282--300.

\leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
Wüest, Bruno, and Jasmine Lorenzini. 2020. {``External Validation of
Protest Event Analysis.''} \emph{Contention in Times of Crisis:
Recession and Political Protest in Thirty Euro-Pean Countries}, 49--78.

\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
Zhang, Han, and Jennifer Pan. 2019. {``{CASM}: {A Deep-Learning
Approach} for {Identifying Collective Action Events} with {Text} and
{Image Data} from {Social Media}.''} \emph{Sociological Methodology} 49
(1): 1--57. \url{https://doi.org/10.1177/0081175019860244}.

\end{CSLReferences}

\bibliographystyle{unsrt}
\bibliography{paper.bib}

\end{document}

### 2022-09-09 replication_paper/previous_submissions/pnas_draft/initial_submission.tex
Political Analysis update

--- 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_rmd.tex
@@
 
-\hypertarget{significance-statement}{%
-\section*{Significance Statement}\label{significance-statement}}
-\addcontentsline{toc}{section}{Significance Statement}
-
-Countries routinely face crises that risk escalating into full scale war
-but we do not have systematic measurements of the progression of past
-crises and what moves and counter moves led to or helped avoid war.
-Instead policy makers typically rely on one or two historical analogies,
-chosen through ad hoc selection criteria, and described in unsystematic
-terms. This paper introduces a new scientific approach to measuring the
-step by step moves of international crises over the last hundred years,
-combining subject expertise with state of the art natural language
-processing and machine learning methods. It serves as a guide for
-constructing and evaluating large scale measurement collection in the
-social sciences.
+Significance Statement: Countries routinely face crises that risk
+escalating into full scale war but we do not have systematic
+measurements of the progression of past crises and what moves and
+counter moves led to or helped avoid war. Instead policy makers
+typically rely on one or two historical analogies, chosen through ad hoc
+selection criteria, and described in unsystematic terms. This paper
+introduces a new scientific approach to measuring the step by step moves
+of international crises over the last hundred years, combining subject
+expertise with state of the art natural language processing and machine
+learning methods. It serves as a guide for constructing and evaluating
+large scale measurement collection in the social sciences.
 
@@
   ontological depth and availability of Gold Standard example text.}
+
+\clearpage
+\onecolumn
+
+{[}1{]} 37 17
+
+\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{0.75}
+
+\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
+
+\caption{Ontological coverage of ICBe versus existing State of the Art
+}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\end{longtable}
+
+{[}1{]}
+``/home/tlscherer/Desktop/ICBEdataset/replication\_paper/pnas\_draft/litreview\_ft.png''
+
+\clearpage
+\twocolumn
 
@@
 
-\clearpage
-\onecolumn
-
-{[}1{]} 37 17
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.75}
-
-\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.00in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
-
-\caption{Ontological coverage of ICBe versus existing State of the Art
-}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.2in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(1–4)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(5,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{6)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(7–10)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(11–14)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(15–18)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(19,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{20)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(21,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{22)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(23–25)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(26–29)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(30)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(31)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(32,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{33)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(34)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(35)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(36–38)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(39–41)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(42)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(43,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{44)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(45)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(46–50)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(51)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(52,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{53)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(54)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(55–57)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(58)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(59)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(60,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{61)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(62)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(63)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(64,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{65)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(66,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{67)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(68–70)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\end{longtable}
-
-\clearpage
-\twocolumn
-
 Each crisis was typically assigned to 2 expert coders and 2 novice

### 2022-09-12 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
supplemental authors

@@
 ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3 and Figure 4, and read off the macro structure of an episode from each individual move.
+You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
 We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
@@
 
-\begin{figure}[H]
-\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
-\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
-\end{figure}
+<!-- \begin{figure}[H] -->
+<!-- \caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}} -->
+<!-- \centering{\includegraphics[width=17cm]{./p_471_icbe.png}} -->
+<!-- \end{figure} -->
 
@@
 
-Funding {#format .unnumbered}
+Funding {
 ========================================
@@
 
-Acknowledgements {#format .unnumbered}
+Acknowledgements 
 ========================================
@@
 
-Author Contributions {#format .unnumbered}
+Author Contributions 
 ========================================
@@
 
-Data Availability Statement {#format .unnumbered}
+Data Availability Statement 
 ========================================
@@
 
-Conflicts of Interests {#format .unnumbered}
+Conflicts of Interests 
 ========================================
@@
 
-&nbsp;
+\clearpage
+
+Works Cited
+========================================
+\vspace{0pt}

### 2022-09-12 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
supplemental authors

@@
 is still useful and interpretable. You should be able to lay out events
-of a crisis on a timeline, as in Figure 3 and Figure 4, and read off the
-macro structure of an episode from each individual move. We call this
+of a crisis on a timeline, as in Figure 3, and read off the macro
+structure of an episode from each individual move. We call this
 visualization a crisis map, a directed graph intersected with a
@@
 
-\begin{figure}[H]
-\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
-\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
-\end{figure}
-
 \clearpage
@@
 
-\hypertarget{format}{%
-\section*{Funding}\label{format}}
-\addcontentsline{toc}{section}{Funding}
+\hypertarget{funding}{%
+\section{Funding \{}\label{funding}}
 
@@
 
-\hypertarget{format}{%
-\section*{Acknowledgements}\label{format}}
-\addcontentsline{toc}{section}{Acknowledgements}
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
 
@@
 
-\hypertarget{format}{%
-\section*{Author Contributions}\label{format}}
-\addcontentsline{toc}{section}{Author Contributions}
+\hypertarget{author-contributions}{%
+\section{Author Contributions}\label{author-contributions}}
 
@@
 
-\hypertarget{format}{%
-\section*{Data Availability Statement}\label{format}}
-\addcontentsline{toc}{section}{Data Availability Statement}
+\hypertarget{data-availability-statement}{%
+\section{Data Availability
+Statement}\label{data-availability-statement}}
 
@@
 
-\hypertarget{format}{%
-\section*{Conflicts of Interests}\label{format}}
-\addcontentsline{toc}{section}{Conflicts of Interests}
+\hypertarget{conflicts-of-interests}{%
+\section{Conflicts of Interests}\label{conflicts-of-interests}}
 
@@
 
-~
+\clearpage
+
+\hypertarget{works-cited}{%
+\section{Works Cited}\label{works-cited}}
+
+\vspace{0pt}
 

### 2022-09-12 replication_paper/political_analysis_draft/appendix.Rmd
supplemental authors

@@
 
-csl: pnas.csl
+authors:
+  - name: Rex W. Douglass
+    thanks: Correspondence should be addressed to Rex W. Douglass at rexdouglass@gmail.com.
+    affiliation: University of California, San Diego
+  - name: Thomas Leo Scherer
+    affiliation: University of California, San Diego
+  - name: J. Andrés Gannon
+    affiliation: Vanderbilt University
+  - name: Erik Gartzke
+    affiliation: University of California, San Diego
+  - name: Jon Lindsay
+    affiliation: Georgia Institute of Technology
+  - name: Shannon Carcelli
+    affiliation: University of Maryland
+  - name: Jonathan Wilkenfeld
+    affiliation: University of Maryland
+  - name: David M. Quinn
+    affiliation: University of Maryland
+  - name: Catherine Aiken
+    affiliation: Georgetown University
+  - name: Jose Miguel Cabezas Navarro
+    affiliation: Universidad Mayor
+  - name: Neil Lund
+    affiliation: University of Maryland
+  - name: Egle Murauskaite
+    affiliation: University of Maryland
+  - name: Diana Partridge
+    affiliation: University of Maryland
+
 bibliography: paper.bib
 biblio-style: unsrt
-output: 
-  pdf_document:
-    toc: true
+output: rticles::arxiv_article
 
@@
 
+\newpage 
+\tableofcontents 
+\newpage
+
 ```{r library loads, eval=T, echo=F, cache=F, results='hide', message=F}
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft1.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft1.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft2.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft2.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft3.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft3.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft4.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft4.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft5.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft5.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft6.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft6.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft7.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft8.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft7.png"), zoom=1)
+
+temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft()  %>% 
+  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft8.png"), zoom=1)
 
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_concept.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_percent_chose_tag_by_concept.png'), 
                   plot = p_percent_chose_tag_by_concept, width=8, height=8)
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_confidence.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_percent_chose_tag_by_confidence.png'), 
                   plot = p_percent_chose_tag_by_confidence, width=8, height=6)
@@
 
-ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision1.png"), zoom=1) #
+ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision1.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision2.png"), zoom=1) #
+ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision2.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision3.png"), zoom=1) #
+ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision3.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision4.png"), zoom=1) #
+ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision4.png"), zoom=1) #
 
@@
     print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_icb_metro_plot_",thiscrisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icb_metro_plot_",thiscrisis,".Rds")
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_mids_metro_plot_",thiscrisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_mids_metro_plot_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icews_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
 
@@
 ## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.Rds') 
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
   ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_penta_196.Rds')
 subtitle="Phoenix Dyadic Events"
@@
     )
-#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_196_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_196_combined.png'),
           p_196_combined, base_height = 12, base_width = 20)
@@
 \begin{sideways}%[htbp]
-\centering{\includegraphics[width=21cm]{./p_196_combined.png}}
+\centering{\includegraphics[width=20cm]{./p_196_combined.png}}
 \end{sideways}
-\clearpage
 
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_196.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_196.png'),
+  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_phoenix_plot_lv0_196.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_196.png'),
             p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=21cm]{./p_phoenix_plot_lv0_196.png}}
+\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_196.png}}
 \end{sidewaysfigure}
@@
 ## Figure D4 Crisis Maps Crimea-Donbas
-
-\hphantom{em}
 
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_471.Rds') 
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_471.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_penta_471.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_terrier_plot_penta_471.Rds')
 subtitle="Terrier Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icews_plot_penta_471.Rds')
 p_471_icews <- readRDS(save_file)
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_471_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_combined.png'),
           p_471_combined, base_height = 12, base_width = 25)
@@
 \caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
-\centering{\includegraphics[width=21cm]{./p_471_combined.png}}
+\centering{\includegraphics[width=19cm]{./p_471_combined.png}}
 \end{sidewaysfigure}
-\clearpage
 
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_471.png'),
+  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_phoenix_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_471.png'),
             p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{./p_phoenix_plot_lv0_471.png}}
+\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_471.png}}
 \end{sidewaysfigure}
-\clearpage
 
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_terrier_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_lv0_471.png'),
+  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_terrier_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_terrier_plot_lv0_471.png'),
             p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{./p_terrier_plot_lv0_471.png}}
+\centering{\includegraphics[width=20cm]{./p_terrier_plot_lv0_471.png}}
 \end{sidewaysfigure}
-\clearpage
 
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_icews_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_lv0_471.png'),
+  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_icews_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icews_plot_lv0_471.png'),
             p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
-\centering{\includegraphics[width=21cm]{./p_icews_plot_lv0_471.png}}
+\centering{\includegraphics[width=20cm]{./p_icews_plot_lv0_471.png}}
 \end{sidewaysfigure}

### 2022-09-12 replication_paper/political_analysis_draft/appendix.tex
supplemental authors

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{Introducing ICBe: Supplementary Information}

\author{
    Rex W. Douglass
    \thanks{Correspondence should be addressed to Rex W. Douglass at
\href{mailto:rexdouglass@gmail.com}{\nolinkurl{rexdouglass@gmail.com}}.}
   \\
    University of California, San Diego \\
   \\
  \texttt{} \\
   \And
    Thomas Leo Scherer
   \\
    University of California, San Diego \\
   \\
  \texttt{} \\
   \And
    J. Andrés Gannon
   \\
    Vanderbilt University \\
   \\
  \texttt{} \\
   \And
    Erik Gartzke
   \\
    University of California, San Diego \\
   \\
  \texttt{} \\
   \And
    Jon Lindsay
   \\
    Georgia Institute of Technology \\
   \\
  \texttt{} \\
   \And
    Shannon Carcelli
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Jonathan Wilkenfeld
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    David M. Quinn
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Catherine Aiken
   \\
    Georgetown University \\
   \\
  \texttt{} \\
   \And
    Jose Miguel Cabezas Navarro
   \\
    Universidad Mayor \\
   \\
  \texttt{} \\
   \And
    Neil Lund
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Egle Murauskaite
   \\
    University of Maryland \\
   \\
  \texttt{} \\
   \And
    Diana Partridge
   \\
    University of Maryland \\
   \\
  \texttt{} \\
  }

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage[utf8]{inputenc}
\usepackage{pifont}
\usepackage{newunicodechar}
\newunicodechar{✓}{\ding{51}}
\newunicodechar{✗}{\ding{55}}
\usepackage{array}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{cellspace}
\setlength\cellspacetoplimit{0.8ex}
\renewcommand{\arraystretch}{0.8}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\usepackage{subcaption}
\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
\usepackage{float}
\usepackage{algorithm2e}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\newpage 
\tableofcontents 
\newpage

\clearpage

\hypertarget{appendix-a-corpus-and-cases}{%
\section{Appendix A Corpus and
Cases}\label{appendix-a-corpus-and-cases}}

\hypertarget{app:crises}{%
\subsection{Table A1: ICBe Crises and Summary
Information}\label{app:crises}}

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics}
\centering{\includegraphics[ height=19cm]{"./crisis_text_counts_ft1.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft2.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft3.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft4.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft5.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft6.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft7.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft8.png"}}
\end{figure}
\clearpage

\hypertarget{app:verbs}{%
\subsection{Table A2: Verb Meanings (Glosses) found in the ICB Corpus
(top 200)}\label{app:verbs}}

\hphantom{em}

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.75}

\begin{longtable}[c]{|p{0.30in}|p{0.75in}|p{6.00in}}

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{uses}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Lemma}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Gloss}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{uses}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Lemma}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Gloss}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}\endhead

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{381}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{end}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ to\ an\ end\ or\ halt\ "She\ ended\ their\ friendship\ when\ she\ found\ out\ that\ he\ had\ once\ been\ convicted\ of\ a\ crime"\ "The\ attack\ on\ Poland\ terminated\ the\ relatively\ peaceful\ period\ after\ WW\ I"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{365}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{trigger}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{release\ or\ pull\ the\ trigger\ on\ "Trigger\ a\ gun"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{323}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{involve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{engage\ as\ a\ participant\ "Dont\ involve\ me\ in\ your\ family\ affairs"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{309}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{begin}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ a\ beginning,\ of\ a\ temporal\ event\ "WW\ II\ began\ in\ 1939\ when\ Hitler\ marched\ into\ Poland"\ "The\ companys\ Asia\ tour\ begins\ next\ month"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{278}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{trigger}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{put\ in\ motion\ or\ move\ to\ act\ "trigger\ a\ reaction"\ "actuate\ the\ circuits"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{260}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce\ publicly\ or\ officially\ "The\ President\ declared\ war"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{236}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond\ favorably\ or\ as\ hoped\ "The\ cancer\ responded\ to\ the\ aggressive\ therapy"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{212}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{call}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{call\ a\ meeting\ invite\ or\ command\ to\ meet\ "The\ Wannsee\ Conference\ was\ called\ to\ discuss\ the\ Final\ Solution"\ "The\ new\ dean\ calls\ meetings\ every\ week"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{194}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{occur}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{come\ to\ pass\ "What\ is\ happening"\ "The\ meeting\ took\ place\ off\ without\ an\ incidence"\ "Nothing\ occurred\ that\ seemed\ important"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{194}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{sign}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{approve\ and\ express\ assent,\ responsibility,\ or\ obligation\ "All\ parties\ ratified\ the\ peace\ treaty"\ "Have\ you\ signed\ your\ contract\ yet"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{185}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{terminate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ to\ an\ end\ or\ halt\ "She\ ended\ their\ friendship\ when\ she\ found\ out\ that\ he\ had\ once\ been\ convicted\ of\ a\ crime"\ "The\ attack\ on\ Poland\ terminated\ the\ relatively\ peaceful\ period\ after\ WW\ I"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{178}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{begin}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{set\ in\ motion,\ cause\ to\ start\ "The\ U.S.\ started\ a\ war\ in\ the\ Middle\ East"\ "The\ Iraqis\ began\ hostilities"\ "begin\ a\ new\ chapter\ in\ your\ life"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{160}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{meet}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{come\ together\ "Ill\ probably\ see\ you\ at\ the\ meeting"\ "How\ nice\ to\ see\ you\ again"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{146}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ cause\ or\ order\ to\ be\ taken,\ directed,\ or\ transmitted\ to\ another\ place\ "He\ had\ sent\ the\ dispatches\ downtown\ to\ the\ proper\ people\ and\ had\ slept"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{145}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{occupy}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{march\ aggressively\ into\ anothers\ territory\ by\ military\ force\ for\ the\ purposes\ of\ conquest\ and\ occupation\ "Hitler\ invaded\ Poland\ on\ September\ 1,\ 1939"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{135}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{happen,\ occur,\ take\ place\ "I\ lost\ my\ wallet\ this\ was\ during\ the\ visit\ to\ my\ parents\ house"\ "There\ were\ two\ hundred\ people\ at\ his\ funeral"\ "There\ was\ a\ lot\ of\ noise\ in\ the\ kitchen"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{128}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{perceive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become\ conscious\ of\ "She\ finally\ perceived\ the\ futility\ of\ her\ protest"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{126}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{undergo\ a\ change\ or\ development\ "The\ water\ turned\ into\ ice"\ "Her\ former\ friend\ became\ her\ worst\ enemy"\ "He\ turned\ traitor"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{125}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{condemn}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ strong\ disapproval\ of\ "We\ condemn\ the\ racism\ in\ South\ Africa"\ "These\ ideas\ were\ reprobated"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{125}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ by\ force\ "Hitler\ took\ the\ Baltic\ Republics"\ "The\ army\ took\ the\ fort\ on\ the\ hill"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{124}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{escalate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{increase\ in\ extent\ or\ intensity\ "The\ Allies\ escalated\ the\ bombing"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{119}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reject}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{refuse\ to\ accept\ or\ acknowledge\ "I\ reject\ the\ idea\ of\ starting\ a\ war"\ "The\ journal\ rejected\ the\ students\ paper"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{117}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{react\ verbally\ "She\ didnt\ want\ to\ answer"\ "answer\ the\ question"\ "We\ answered\ that\ we\ would\ accept\ the\ invitation"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{116}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{demand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{request\ urgently\ and\ forcefully\ "The\ victims\ family\ is\ demanding\ compensation"\ "The\ boss\ demanded\ that\ he\ be\ fired\ immediately"\ "She\ demanded\ to\ see\ the\ manager"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{112}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ remain\ unmolested,\ undisturbed,\ or\ uninterrupted\ \ used\ only\ in\ infinitive\ form\ "let\ her\ be"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{111}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{agree}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ in\ accord\ be\ in\ agreement\ "We\ agreed\ on\ the\ terms\ of\ the\ settlement"\ "I\ cant\ agree\ with\ you"\ "I\ hold\ with\ those\ who\ say\ life\ is\ sacred"\ "Both\ philosophers\ concord\ on\ this\ point"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{110}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ in\ or\ establish\ communication\ with\ "Our\ advertisements\ reach\ millions"\ "He\ never\ contacted\ his\ children\ after\ he\ emigrated\ to\ Australia"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{106}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{withdraw}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pull\ back\ or\ move\ away\ or\ backward\ "The\ enemy\ withdrew"\ "The\ limo\ pulled\ away\ from\ the\ curb"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{105}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{blame\ for,\ make\ a\ claim\ of\ wrongdoing\ or\ misbehavior\ against\ "he\ charged\ the\ director\ with\ indifference"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{105}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{dispute}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ a\ disagreement\ over\ something\ "We\ quarreled\ over\ the\ question\ as\ to\ who\ discovered\ America"\ "These\ two\ fellows\ are\ always\ scrapping\ over\ something"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{105}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fight}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ engaged\ in\ a\ fight\ carry\ on\ a\ fight\ "the\ tribesmen\ fought\ each\ other"\ "Siblings\ are\ always\ fighting"\ "Militant\ groups\ are\ contending\ for\ control\ of\ the\ country"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{102}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue\ talking\ "I\ know\ its\ hard,\ he\ continued,\ but\ there\ is\ no\ choice"\ "carry\ onpretend\ we\ are\ not\ in\ the\ room"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{100}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{include}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{consider\ as\ part\ of\ something\ "I\ include\ you\ in\ the\ list\ of\ culprits"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{99}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{remain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ left\ of\ persons,\ questions,\ problems,\ results,\ evidence,\ etc.\ "There\ remains\ the\ question\ of\ who\ pulled\ the\ trigger"\ "Carter\ remains\ the\ only\ President\ in\ recent\ history\ under\ whose\ Presidency\ the\ U.S.\ did\ not\ fight\ a\ war"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{98}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{experience}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{undergo\ or\ live\ through\ a\ difficult\ experience\ "We\ had\ many\ trials\ to\ go\ through"\ "he\ saw\ action\ in\ Viet\ Nam"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{97}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attempt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ an\ effort\ or\ attempt\ "He\ tried\ to\ shake\ off\ his\ fears"\ "The\ infant\ had\ essayed\ a\ few\ wobbly\ steps"\ "The\ police\ attempted\ to\ stop\ the\ thief"\ "He\ sought\ to\ improve\ himself"\ "She\ always\ seeks\ to\ do\ good\ in\ the\ world"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{increase}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ bigger\ or\ more\ "The\ boss\ finally\ increased\ her\ salary"\ "The\ university\ increased\ the\ number\ of\ students\ it\ admitted"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{mediate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{act\ between\ parties\ with\ a\ view\ to\ reconciling\ differences\ "He\ interceded\ in\ the\ family\ dispute"\ "He\ mediated\ a\ settlement"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{threaten}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ utter\ intentions\ of\ injury\ or\ punishment\ against\ "He\ threatened\ me\ when\ I\ tried\ to\ call\ the\ police"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{93}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{request}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{inquire\ for\ information\ "I\ requested\ information\ from\ the\ secretary"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{92}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{withdraw}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ a\ retreat\ from\ an\ earlier\ commitment\ or\ activity\ "Well\ have\ to\ crawfish\ out\ from\ meeting\ with\ him"\ "He\ backed\ out\ of\ his\ earlier\ promise"\ "The\ aggressive\ investment\ company\ pulled\ in\ its\ horns"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{91}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stop\ dealing\ with\ "hold\ all\ calls\ to\ the\ Presidents\ office\ while\ he\ is\ in\ a\ meeting"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{90}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{invade}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{march\ aggressively\ into\ anothers\ territory\ by\ military\ force\ for\ the\ purposes\ of\ conquest\ and\ occupation\ "Hitler\ invaded\ Poland\ on\ September\ 1,\ 1939"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{87}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ go\ somewhere\ "The\ explosion\ sent\ the\ car\ flying\ in\ the\ air"\ "She\ sent\ her\ children\ to\ camp"\ "He\ directed\ all\ his\ energies\ into\ his\ dissertation"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{86}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{launch}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{begin\ with\ vigor\ "He\ launched\ into\ a\ long\ diatribe"\ "She\ plunged\ into\ a\ dangerous\ adventure"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{84}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{report}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce\ as\ the\ result\ of\ an\ investigation\ or\ experience\ or\ finding\ "Dozens\ of\ incidents\ of\ wife\ beatings\ are\ reported\ daily\ in\ this\ city"\ "The\ team\ reported\ significant\ advances\ in\ their\ research"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{84}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{see}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{perceive\ or\ be\ contemporaneous\ with\ "We\ found\ Republicans\ winning\ the\ offices"\ "Youll\ see\ a\ lot\ of\ cheating\ in\ this\ school"\ "The\ 1960s\ saw\ the\ rebellion\ of\ the\ younger\ generation\ against\ established\ traditions"\ "I\ want\ to\ see\ results"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{81}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{perceive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ become\ aware\ of\ through\ the\ senses\ "I\ could\ perceive\ the\ ship\ coming\ over\ the\ horizon"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{80}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ an\ accusation\ against\ level\ a\ charge\ against\ "The\ neighbors\ accused\ the\ man\ of\ spousal\ abuse"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{77}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attack}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{launch\ an\ attack\ or\ assault\ on\ begin\ hostilities\ or\ start\ warfare\ with\ "Hitler\ attacked\ Poland\ on\ September\ 1,\ 1939\ and\ started\ World\ War\ II"\ "Serbian\ forces\ assailed\ Bosnian\ towns\ all\ week"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{77}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{dispatch}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill\ without\ delay\ "the\ traitor\ was\ dispatched\ by\ the\ conspirators"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{77}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{end}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{put\ an\ end\ to\ "The\ terrible\ news\ ended\ our\ hopes\ that\ he\ had\ survived"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{74}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{declare}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce\ publicly\ or\ officially\ "The\ President\ declared\ war"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{74}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{discuss}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{speak\ with\ others\ about\ something\ talk\ something\ over\ in\ detail\ have\ a\ discussion\ "We\ discussed\ our\ household\ budget"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{74}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ under\ surveillance\ "The\ police\ had\ been\ following\ him\ for\ weeks\ but\ they\ could\ not\ prove\ his\ involvement\ in\ the\ bombing"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{73}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{tend\ to\ or\ result\ in\ "This\ remark\ lead\ to\ further\ arguments\ among\ the\ guests"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{73}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{remain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stay\ behind\ "The\ smell\ stayed\ in\ the\ room"\ "The\ hostility\ remained\ long\ after\ they\ made\ up"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{72}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{propose}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{present\ for\ consideration,\ examination,\ criticism,\ etc.\ "He\ proposed\ a\ new\ plan\ for\ dealing\ with\ terrorism"\ "She\ proposed\ a\ new\ theory\ of\ relativity"\ "The\ candidate\ projects\ himself\ as\ a\ moderate\ and\ a\ reformer"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{72}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{recognize}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept\ someone\ to\ be\ what\ is\ claimed\ or\ accept\ his\ power\ and\ authority\ "The\ Crown\ Prince\ was\ acknowledged\ as\ the\ true\ heir\ to\ the\ throne"\ "We\ do\ not\ recognize\ your\ gods"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{70}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{capture}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ possession\ of\ by\ force,\ as\ after\ an\ invasion\ "the\ invaders\ seized\ the\ land\ and\ property\ of\ the\ inhabitants"\ "The\ army\ seized\ the\ town"\ "The\ militia\ captured\ the\ castle"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{70}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deny}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deny\ formally\ an\ allegation\ of\ fact\ by\ the\ opposing\ party\ in\ a\ legal\ suit}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{69}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{exist\ over\ a\ prolonged\ period\ of\ time\ "The\ bad\ weather\ continued\ for\ two\ more\ weeks"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{69}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{issue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ out\ an\ official\ document\ such\ as\ a\ warrant}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{67}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{declare}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{proclaim\ ones\ support,\ sympathy,\ or\ opinion\ for\ or\ against\ "His\ wife\ declared\ at\ once\ for\ moving\ to\ the\ West\ Coast"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{66}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stretch\ out\ over\ a\ distance,\ space,\ time,\ or\ scope\ run\ or\ extend\ between\ two\ points\ or\ beyond\ a\ certain\ point\ "Service\ runs\ all\ the\ way\ to\ Cranbury"\ "His\ knowledge\ doesnt\ go\ very\ far"\ "My\ memory\ extends\ back\ to\ my\ fourth\ year\ of\ life"\ "The\ facts\ extend\ beyond\ a\ consideration\ of\ her\ personal\ assets"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{65}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{renew}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reestablish\ on\ a\ new,\ usually\ improved,\ basis\ or\ make\ new\ or\ like\ new\ "We\ renewed\ our\ friendship\ after\ a\ hiatus\ of\ twenty\ years"\ "They\ renewed\ their\ membership"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{64}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{achieve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ gain\ with\ effort\ "she\ achieved\ her\ goal\ despite\ setbacks"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{63}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{provide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{determine\ what\ is\ to\ happen\ in\ certain\ contingencies,\ especially\ by\ including\ a\ proviso\ condition\ or\ stipulation\ "The\ will\ provides\ that\ each\ child\ should\ receive\ half\ of\ the\ money"\ "The\ Constitution\ provides\ for\ the\ right\ to\ free\ speech"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{61}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{appeal}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ a\ court\ case\ to\ a\ higher\ court\ for\ review\ "He\ was\ found\ guilty\ but\ appealed\ immediately"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{61}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{seek}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ an\ effort\ or\ attempt\ "He\ tried\ to\ shake\ off\ his\ fears"\ "The\ infant\ had\ essayed\ a\ few\ wobbly\ steps"\ "The\ police\ attempted\ to\ stop\ the\ thief"\ "He\ sought\ to\ improve\ himself"\ "She\ always\ seeks\ to\ do\ good\ in\ the\ world"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{60}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attack}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ the\ initiative\ and\ go\ on\ the\ offensive\ "The\ Serbs\ attacked\ the\ village\ at\ night"\ "The\ visiting\ team\ started\ to\ attack"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{60}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pass}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{go\ unchallenged\ be\ approved\ "The\ bill\ cleared\ the\ House"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{59}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{agree}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{achieve\ harmony\ of\ opinion,\ feeling,\ or\ purpose\ "No\ two\ of\ my\ colleagues\ would\ agree\ on\ whom\ to\ elect\ chairman"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{59}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{last}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{persist\ for\ a\ specified\ period\ of\ time\ "The\ bad\ weather\ lasted\ for\ three\ days"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{58}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{claim}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{demand\ as\ being\ ones\ due\ or\ property\ assert\ ones\ right\ or\ title\ to\ "He\ claimed\ his\ suitcases\ at\ the\ airline\ counter"\ "Mr.\ Smith\ claims\ special\ tax\ exemptions\ because\ he\ is\ a\ foreign\ resident"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{57}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{establish}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ about\ "The\ trompe\ loeilillusion\ establishes\ depth"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{57}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{inform}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impart\ knowledge\ of\ some\ fact,\ state\ of\ affairs,\ or\ event\ to\ "I\ informed\ him\ of\ his\ rights"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{57}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{warn}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{notify,\ usually\ in\ advance\ "I\ warned\ you\ that\ I\ would\ ask\ some\ difficult\ questions"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{56}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{offer}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{threaten\ to\ do\ something\ "I\ offered\ to\ leave\ the\ committee\ if\ they\ did\ not\ accept\ my\ proposal"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{56}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{restore}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ back\ into\ original\ existence,\ use,\ function,\ or\ position\ "restore\ law\ and\ order"\ "reestablish\ peace\ in\ the\ region"\ "restore\ the\ emperor\ to\ the\ throne"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{create}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ or\ cause\ to\ be\ or\ to\ become\ "make\ a\ mess\ in\ ones\ office"\ "create\ a\ furor"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{issue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{circulate\ or\ distribute\ or\ equip\ with\ "issue\ a\ new\ uniform\ to\ the\ children"\ "supply\ blankets\ for\ the\ beds"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{prevent}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ from\ happening\ or\ arising\ make\ impossible\ "My\ sense\ of\ tact\ forbids\ an\ honest\ answer"\ "Your\ role\ in\ the\ projects\ precludes\ your\ involvement\ in\ the\ competitive\ project"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{support}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{argue\ or\ speak\ in\ defense\ of\ "She\ supported\ the\ motion\ to\ strike"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cross}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{travel\ across\ or\ pass\ over\ "The\ caravan\ covered\ almost\ 100\ miles\ each\ day"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{include}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{allow\ participation\ in\ or\ the\ right\ to\ be\ part\ of\ permit\ to\ exercise\ the\ rights,\ functions,\ and\ responsibilities\ of\ "admit\ someone\ to\ the\ profession"\ "She\ was\ admitted\ to\ the\ New\ Jersey\ Bar"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{urge}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{push\ for\ something\ "The\ travel\ agent\ recommended\ strongly\ that\ we\ not\ travel\ on\ Thanksgiving\ Day"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{agree}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{consent\ or\ assent\ to\ a\ condition,\ or\ agree\ to\ do\ something\ "She\ agreed\ to\ all\ my\ conditions"\ "He\ agreed\ to\ leave\ her\ alone"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{do\ something\ repeatedly\ and\ showing\ no\ intention\ to\ stop\ "We\ continued\ our\ research\ into\ the\ cause\ of\ the\ illness"\ "The\ landlord\ persists\ in\ asking\ us\ to\ move"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{transfer\ "The\ spy\ sent\ the\ classified\ information\ off\ to\ Russia"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{support}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ behind\ approve\ of\ "He\ plumped\ for\ the\ Labor\ Party"\ "I\ backed\ Kennedy\ in\ 1960"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{erupt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{erupt\ or\ intensify\ suddenly\ "Unrest\ erupted\ in\ the\ country"\ "Tempers\ flared\ at\ the\ meeting"\ "The\ crowd\ irrupted\ into\ a\ burst\ of\ patriotism"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resolve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach\ a\ conclusion\ after\ a\ discussion\ or\ deliberation}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{view}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deem\ to\ be\ "She\ views\ this\ quite\ differently\ from\ me"\ "I\ consider\ her\ to\ be\ shallow"\ "I\ dont\ see\ the\ situation\ quite\ as\ negatively\ as\ you\ do"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{50}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{occur}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ be\ found\ to\ exist\ "sexism\ occurs\ in\ many\ workplaces"\ "precious\ stones\ occur\ in\ a\ large\ area\ in\ Brazil"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{50}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{admit\ into\ a\ group\ or\ community\ "accept\ students\ for\ graduate\ study"\ "Well\ have\ to\ vote\ on\ whether\ or\ not\ to\ admit\ a\ new\ member"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{claim}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ as\ an\ undesirable\ consequence\ of\ some\ event\ or\ state\ of\ affairs\ "the\ accident\ claimed\ three\ lives"\ "The\ hard\ work\ took\ its\ toll\ on\ her"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fade}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{disappear\ gradually\ "The\ pain\ eventually\ passed\ off"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{intervene}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{get\ involved,\ so\ as\ to\ alter\ or\ hinder\ an\ action,\ or\ through\ force\ or\ threat\ of\ force\ "Why\ did\ the\ U.S.\ not\ intervene\ earlier\ in\ WW\ II"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deprive\ of\ life\ "AIDS\ has\ killed\ thousands\ in\ Africa"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{note}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ mention\ of\ "She\ observed\ that\ his\ presentation\ took\ up\ too\ much\ time"\ "They\ noted\ that\ it\ was\ a\ fine\ day\ to\ go\ sailing"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{suspend}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stop\ a\ process\ or\ a\ habit\ by\ imposing\ a\ freeze\ on\ it\ "Suspend\ the\ aid\ to\ the\ wartorn\ country"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deploy}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ distribute\ systematically\ or\ strategically\ "The\ U.S.\ deploys\ its\ weapons\ in\ the\ Middle\ East"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{overthrow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ the\ downfall\ of\ of\ rulers\ "The\ Czar\ was\ overthrown"\ "subvert\ the\ ruling\ class"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resolve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ to\ an\ end\ settle\ conclusively\ "The\ case\ was\ decided"\ "The\ judge\ decided\ the\ case\ in\ favor\ of\ the\ plaintiff"\ "The\ father\ adjudicated\ when\ the\ sons\ were\ quarreling\ over\ their\ inheritance"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{state}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ in\ words\ "He\ said\ that\ he\ wanted\ to\ marry\ her"\ "tell\ me\ what\ is\ bothering\ you"\ "state\ your\ opinion"\ "state\ your\ name"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{47}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ an\ affirmative\ reply\ to\ respond\ favorably\ to\ "I\ cannot\ accept\ your\ invitation"\ "I\ go\ for\ this\ resolution"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{47}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{form}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{develop\ into\ a\ distinctive\ entity\ "our\ plans\ began\ to\ take\ shape"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{47}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{use}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{avail\ oneself\ to\ "apply\ a\ principle"\ "practice\ a\ religion"\ "use\ care\ when\ going\ down\ the\ stairs"\ "use\ your\ common\ sense"\ "practice\ nonviolent\ resistance"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{allege}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{report\ or\ maintain\ "He\ alleged\ that\ he\ was\ the\ victim\ of\ a\ crime"\ "He\ said\ it\ was\ too\ late\ to\ intervene\ in\ the\ war"\ "The\ registrar\ says\ that\ I\ owe\ the\ school\ money"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{approve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ sanction\ to\ "I\ approve\ of\ his\ educational\ policies"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{arrive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach\ a\ destination\ arrive\ by\ movement\ or\ progress\ "She\ arrived\ home\ at\ 7\ oclock"\ "She\ didnt\ get\ to\ Chicago\ until\ after\ midnight"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{break}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ a\ rupture\ in\ the\ ranks\ of\ the\ enemy\ or\ ones\ own\ by\ quitting\ or\ fleeing\ "The\ ranks\ broke"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resume}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ up\ or\ begin\ anew\ "We\ resumed\ the\ negotiations"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{45}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{negotiate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{discuss\ the\ terms\ of\ an\ arrangement\ "They\ negotiated\ the\ sale\ of\ the\ house"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{45}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{protect}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{shield\ from\ danger,\ injury,\ destruction,\ or\ damage\ "Weatherbeater\ protects\ your\ roof\ from\ the\ rain"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{45}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{protract}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lengthen\ in\ time\ cause\ to\ be\ or\ last\ longer\ "We\ prolonged\ our\ stay"\ "She\ extended\ her\ visit\ by\ another\ day"\ "The\ meeting\ was\ drawn\ out\ until\ midnight"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{44}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ bring\ something\ about\ at\ a\ later\ time\ than\ "She\ followed\ dinner\ with\ a\ brandy"\ "He\ followed\ his\ lecture\ with\ a\ question\ and\ answer\ period"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{44}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{leave}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{remove\ oneself\ from\ an\ association\ with\ or\ participation\ in\ "She\ wants\ to\ leave"\ "The\ teenager\ left\ home"\ "She\ left\ her\ position\ with\ the\ Red\ Cross"\ "He\ left\ the\ Senate\ after\ two\ terms"\ "after\ 20\ years\ with\ the\ same\ company,\ she\ pulled\ up\ stakes"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{react\ favorably\ to\ consider\ right\ and\ proper\ "People\ did\ not\ accept\ atonal\ music\ at\ that\ time"\ "We\ accept\ the\ idea\ of\ universal\ health\ care"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{comply}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{act\ in\ accordance\ with\ someones\ rules,\ commands,\ or\ wishes\ "He\ complied\ with\ my\ instructions"\ "You\ must\ comply\ or\ else"\ "Follow\ these\ simple\ rules"\ "abide\ by\ the\ rules"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{generate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ into\ existence\ "The\ new\ manager\ generated\ a\ lot\ of\ problems"\ "The\ computer\ bug\ generated\ chaos\ in\ the\ office"\ "The\ computer\ generated\ this\ image"\ "The\ earthquake\ generated\ a\ tsunami"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{increase}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become\ bigger\ or\ greater\ in\ amount\ "The\ amount\ of\ work\ increased"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{initiate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{set\ in\ motion,\ start\ an\ event\ or\ prepare\ the\ way\ for\ "Hitlers\ attack\ on\ Poland\ led\ up\ to\ World\ War\ II"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{meet}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{experience\ as\ a\ reaction\ "My\ proposal\ met\ with\ much\ opposition"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{refuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{show\ unwillingness\ towards\ "he\ declined\ to\ join\ the\ group\ on\ a\ hike"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{succeed}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attain\ success\ or\ reach\ a\ desired\ goal\ "The\ enterprise\ succeeded"\ "We\ succeeded\ in\ getting\ tickets\ to\ the\ show"\ "she\ struggled\ to\ overcome\ her\ handicap\ and\ won"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{come}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ received\ "News\ came\ in\ of\ the\ massacre\ in\ Rwanda"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{launch}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{propel\ with\ force\ "launch\ the\ space\ shuttle"\ "Launch\ a\ ship"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{move}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow\ a\ procedure\ or\ take\ a\ course\ "We\ should\ go\ farther\ in\ this\ matter"\ "She\ went\ through\ a\ lot\ of\ trouble"\ "go\ about\ the\ world\ in\ a\ certain\ manner"\ "Messages\ must\ go\ through\ diplomatic\ channels"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reaffirm}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{affirm\ once\ again\ "He\ reaffirmed\ his\ faith\ in\ the\ church"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ into\ consideration\ for\ exemplifying\ purposes\ "Take\ the\ case\ of\ China"\ "Consider\ the\ following\ case"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{adopt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ up\ the\ cause,\ ideology,\ practice,\ method,\ of\ someone\ and\ use\ it\ as\ ones\ own\ "She\ embraced\ Catholicism"\ "They\ adopted\ the\ Jewish\ faith"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{control}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{exercise\ authoritative\ control\ or\ power\ over\ "control\ the\ budget"\ "Command\ the\ military\ forces"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{proclaim}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{state\ or\ announce\ "I\ am\ not\ a\ Communist,\ he\ exclaimed"\ "The\ King\ will\ proclaim\ an\ amnesty"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{threaten}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pose\ a\ threat\ to\ present\ a\ danger\ to\ "The\ pollution\ is\ endangering\ the\ crops"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{40}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bomb}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{throw\ bombs\ at\ or\ attack\ with\ bombs\ "The\ Americans\ bombed\ Dresden"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{40}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{last}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue\ to\ live\ and\ avoid\ dying\ "We\ went\ without\ water\ and\ food\ for\ 3\ days"\ "These\ superstitions\ survive\ in\ the\ backwaters\ of\ America"\ "The\ race\ car\ driver\ lived\ through\ several\ very\ serious\ accidents"\ "how\ long\ can\ a\ person\ last\ without\ food\ and\ water"\ "One\ crash\ victim\ died,\ the\ other\ lived"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{39}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{implement}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pursue\ to\ a\ conclusion\ or\ bring\ to\ a\ successful\ issue\ "Did\ he\ go\ through\ with\ the\ treatment"\ "He\ implemented\ a\ new\ economic\ plan"\ "She\ followed\ up\ his\ recommendations\ with\ a\ written\ proposal"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{38}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{strengthen}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ strong\ or\ stronger\ "This\ exercise\ will\ strengthen\ your\ upper\ body"\ "strengthen\ the\ relations\ between\ the\ two\ countries"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{consider}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{think\ about\ carefully\ weigh\ "They\ considered\ the\ possibility\ of\ a\ strike"\ "Turn\ the\ proposal\ over\ in\ your\ mind"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{decide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach,\ make,\ or\ come\ to\ a\ decision\ about\ something\ "We\ finally\ decided\ after\ lengthy\ deliberations"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{do}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{carry\ on\ or\ function\ "We\ could\ do\ with\ a\ little\ more\ help\ around\ here"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ move\ cause\ to\ be\ in\ a\ certain\ position\ or\ condition\ "He\ got\ his\ squad\ on\ the\ ball"\ "This\ let\ me\ in\ for\ a\ big\ surprise"\ "He\ got\ a\ girl\ into\ trouble"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{help}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{contribute\ to\ the\ furtherance\ of\ "This\ money\ will\ help\ the\ development\ of\ literacy\ in\ developing\ countries"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ and\ maintain\ control\ over,\ often\ by\ violent\ means\ "The\ dissatisfied\ students\ held\ the\ Presidents\ office\ for\ almost\ a\ week"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose\ and\ collect\ "levy\ a\ fine"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{indicate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ a\ signal\ for\ or\ a\ symptom\ of\ "These\ symptoms\ indicate\ a\ serious\ illness"\ "Her\ behavior\ points\ to\ a\ severe\ neurosis"\ "The\ economic\ indicators\ signal\ that\ the\ euro\ is\ undervalued"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{order}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{issue\ commands\ or\ orders\ for}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{36}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{enter\ or\ assume\ a\ certain\ state\ or\ condition\ "He\ became\ annoyed\ when\ he\ heard\ the\ bad\ news"\ "It\ must\ be\ getting\ more\ serious"\ "her\ face\ went\ red\ with\ anger"\ "She\ went\ into\ ecstasy"\ "Get\ going"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{36}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{participate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become\ a\ participant\ be\ involved\ in\ "enter\ a\ race"\ "enter\ an\ agreement"\ "enter\ a\ drug\ treatment\ program"\ "enter\ negotiations"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{call}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{order,\ summon,\ or\ request\ for\ a\ specific\ duty\ or\ activity,\ work,\ role\ "He\ was\ already\ called\ 4\ times\ for\ jury\ duty"\ "They\ called\ him\ to\ active\ military\ duty"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ do\ cause\ to\ act\ in\ a\ specified\ manner\ "The\ ads\ induced\ me\ to\ buy\ a\ VCR"\ "My\ children\ finally\ got\ me\ to\ buy\ a\ computer"\ "My\ wife\ made\ me\ buy\ a\ new\ sofa"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{enmesh}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{entangle\ or\ catch\ in\ or\ as\ if\ in\ a\ mesh}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ confronted\ with\ "What\ do\ we\ have\ here"\ "Now\ we\ have\ a\ fine\ mess"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ certain\ properties\ to\ something\ "get\ someone\ mad"\ "She\ made\ us\ look\ silly"\ "He\ made\ a\ fool\ of\ himself\ at\ the\ meeting"\ "Dont\ make\ this\ into\ a\ big\ deal"\ "This\ invention\ will\ make\ you\ a\ millionaire"\ "Make\ yourself\ clear"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{evacuate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{move\ out\ of\ an\ unsafe\ location\ into\ safety\ "After\ the\ earthquake,\ residents\ were\ evacuated"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fire}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{drive\ out\ or\ away\ by\ or\ as\ if\ by\ fire\ "The\ soldiers\ were\ fired"\ "Surrender\ fires\ the\ cold\ skepticism"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{intend}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ in\ mind\ as\ a\ purpose\ "I\ mean\ no\ harm"\ "I\ only\ meant\ to\ help\ you"\ "She\ didnt\ think\ to\ harm\ me"\ "We\ thought\ to\ return\ early\ that\ night"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{preside\ over\ "John\ moderated\ the\ discussion"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{refuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resist\ immunologically\ the\ introduction\ of\ some\ foreign\ tissue\ or\ organ\ "His\ body\ rejected\ the\ liver\ of\ the\ donor"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{warn}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{notify\ of\ danger,\ potential\ harm,\ or\ risk\ "The\ director\ warned\ him\ that\ he\ might\ be\ fired"\ "The\ doctor\ warned\ me\ about\ the\ dangers\ of\ smoking"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ into\ a\ different\ state\ "this\ may\ land\ you\ in\ jail"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{provide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ a\ possibility\ or\ provide\ opportunity\ for\ permit\ to\ be\ attainable\ or\ cause\ to\ remain\ "This\ leaves\ no\ room\ for\ improvement"\ "The\ evidence\ allows\ only\ one\ conclusion"\ "allow\ for\ mistakes"\ "leave\ lots\ of\ time\ for\ the\ trip"\ "This\ procedure\ provides\ for\ lots\ of\ leeway"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{show\ a\ response\ or\ a\ reaction\ to\ something}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{shoot}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill\ by\ firing\ a\ missile}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stop}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold\ back,\ as\ of\ a\ danger\ or\ an\ enemy\ check\ the\ expansion\ or\ influence\ of\ "Arrest\ the\ downward\ trend"\ "Check\ the\ growth\ of\ communism\ in\ South\ East\ Asia"\ "Contain\ the\ rebel\ movement"\ "Turn\ back\ the\ tide\ of\ communism"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{use}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{seek\ or\ achieve\ an\ end\ by\ using\ to\ ones\ advantage\ "She\ uses\ her\ influential\ friends\ to\ get\ jobs"\ "The\ presidents\ wife\ used\ her\ good\ connections"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accord}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{go\ together\ "The\ colors\ dont\ harmonize"\ "Their\ ideas\ concorded"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{broker}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{act\ as\ a\ broker}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{span\ an\ interval\ of\ distance,\ space\ or\ time\ "The\ war\ extended\ over\ five\ years"\ "The\ period\ covered\ the\ turn\ of\ the\ century"\ "My\ land\ extends\ over\ the\ hills\ on\ the\ horizon"\ "This\ farm\ covers\ some\ 200\ acres"\ "The\ Archipelago\ continues\ for\ another\ 500\ miles"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fail}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fall\ short\ in\ what\ is\ expected\ "She\ failed\ in\ her\ obligations\ as\ a\ good\ daughterinlaw"\ "We\ must\ not\ fail\ his\ obligation\ to\ the\ victims\ of\ the\ Holocaust"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{flee}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{run\ away\ quickly\ "He\ threw\ down\ his\ gun\ and\ fled"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{involve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{connect\ closely\ and\ often\ incriminatingly\ "This\ new\ ruling\ affects\ your\ business"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{maintain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ in\ safety\ and\ protect\ from\ harm,\ decay,\ loss,\ or\ destruction\ "We\ preserve\ these\ archeological\ findings"\ "The\ old\ lady\ could\ not\ keep\ up\ the\ building"\ "children\ must\ be\ taught\ to\ conserve\ our\ national\ heritage"\ "The\ museum\ curator\ conserved\ the\ ancient\ manuscripts"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{adopt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{choose\ and\ follow\ as\ of\ theories,\ ideas,\ policies,\ strategies\ or\ plans\ "She\ followed\ the\ feminist\ movement"\ "The\ candidate\ espouses\ Republican\ ideals"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{assist}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ help\ or\ assistance\ be\ of\ service\ "Everyone\ helped\ out\ during\ the\ earthquake"\ "Can\ you\ help\ me\ carry\ this\ table"\ "She\ never\ helps\ around\ the\ house"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fail}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{disappoint,\ prove\ undependable\ to\ abandon,\ forsake\ "His\ sense\ of\ smell\ failed\ him\ this\ time"\ "His\ strength\ finally\ failed\ him"\ "His\ children\ failed\ him\ in\ the\ crisis"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept\ and\ follow\ the\ leadership\ or\ command\ or\ guidance\ of\ "Lets\ follow\ our\ great\ helmsman"\ "She\ followed\ a\ guru\ for\ years"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{force}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ by\ force\ "Storm\ the\ fort"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ close\ within\ bounds,\ or\ otherwise\ limit\ or\ deprive\ of\ free\ movement\ "This\ holds\ the\ local\ until\ the\ express\ passengers\ change\ trains"\ "About\ a\ dozen\ animals\ were\ held\ inside\ the\ stockade"\ "The\ illegal\ immigrants\ were\ held\ at\ a\ detention\ center"\ "The\ terrorists\ held\ the\ journalists\ for\ ransom"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{monitor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ tabs\ on\ keep\ an\ eye\ on\ keep\ under\ surveillance\ "we\ are\ monitoring\ the\ air\ quality"\ "the\ police\ monitor\ the\ suspects\ moves"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{move}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{change\ location\ move,\ travel,\ or\ proceed,\ also\ metaphorically\ "How\ fast\ does\ your\ new\ car\ go"\ "We\ travelled\ from\ Rome\ to\ Naples\ by\ bus"\ "The\ policemen\ went\ from\ door\ to\ door\ looking\ for\ the\ suspect"\ "The\ soldiers\ moved\ towards\ the\ city\ in\ an\ attempt\ to\ take\ it\ before\ night\ fell"\ "news\ travelled\ fast"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{order}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ instructions\ to\ or\ direct\ somebody\ to\ do\ something\ with\ authority\ "I\ said\ to\ him\ to\ go\ home"\ "She\ ordered\ him\ to\ do\ the\ shopping"\ "The\ mother\ told\ the\ child\ to\ get\ dressed"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{receive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{receive\ a\ specified\ treatment\ abstract\ "These\ aspects\ of\ civilization\ do\ not\ find\ expression\ or\ receive\ an\ interpretation"\ "His\ movie\ received\ a\ good\ review"\ "I\ got\ nothing\ but\ trouble\ for\ my\ good\ intentions"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{engage}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{carry\ on\ wars,\ battles,\ or\ campaigns\ "Napoleon\ and\ Hitler\ waged\ war\ against\ all\ of\ Europe"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send\ by\ rapid\ transport\ or\ special\ messenger\ service\ "She\ expressed\ the\ letter\ to\ Florida"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose\ something\ unpleasant\ "The\ principal\ visited\ his\ rage\ on\ the\ students"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{mark\ for\ deletion,\ rub\ off,\ or\ erase\ "kill\ these\ lines\ in\ the\ Presidents\ speech"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{seek}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{try\ to\ locate\ or\ discover,\ or\ try\ to\ establish\ the\ existence\ of\ "The\ police\ are\ searching\ for\ clues"\ "They\ are\ searching\ for\ the\ missing\ man\ in\ the\ entire\ county"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{conclude}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach\ agreement\ on\ "They\ concluded\ an\ economic\ agreement"\ "We\ concluded\ a\ ceasefire"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{decide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ decide\ "This\ new\ development\ finally\ decided\ me"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{include}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{add\ as\ part\ of\ something\ else\ put\ in\ as\ part\ of\ a\ set,\ group,\ or\ category\ "We\ must\ include\ this\ chemical\ element\ in\ the\ group"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{plan}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ the\ will\ and\ intention\ to\ carry\ out\ some\ action\ "He\ plans\ to\ be\ in\ graduate\ school\ next\ year"\ "The\ rebels\ had\ planned\ turmoil\ and\ confusion"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{protest}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ opposition\ through\ action\ or\ words\ "dissent\ to\ the\ laws\ of\ the\ country"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{receive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ willingness\ to\ have\ in\ ones\ home\ or\ environs\ "The\ community\ warmly\ received\ the\ refugees"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{regard}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{connect\ closely\ and\ often\ incriminatingly\ "This\ new\ ruling\ affects\ your\ business"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{say}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{report\ or\ maintain\ "He\ alleged\ that\ he\ was\ the\ victim\ of\ a\ crime"\ "He\ said\ it\ was\ too\ late\ to\ intervene\ in\ the\ war"\ "The\ registrar\ says\ that\ I\ owe\ the\ school\ money"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ or\ maintain\ a\ position\ or\ stand\ on\ an\ issue\ "Where\ do\ you\ stand\ on\ the\ War"}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{undermine}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{destroy\ property\ or\ hinder\ normal\ operations\ "The\ Resistance\ sabotaged\ railroad\ operations\ during\ the\ war"}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}

\end{longtable}

\clearpage

\hypertarget{appendix-b-coding-process}{%
\section{Appendix B: Coding Process}\label{appendix-b-coding-process}}

\hphantom{em}

\hypertarget{app:gui}{%
\subsection{Figure B1: Graphical User Interface}\label{app:gui}}

\hphantom{em}

\begin{figure}[H]
\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{./gui_example}}
\end{figure}
\clearpage

\hypertarget{app:algo1}{%
\subsection{Algorithm B2: Coding Aggregation and
Filtering}\label{app:algo1}}

\hphantom{em}

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Coder-Sentence-Tokens}
\KwResult{Sentence-Events}
\ForEach{sentence in sentences}{
  \ForEach{concept in concepts}{
    \ForEach{token in tokens}{
      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
      \uElseIf{expert votes >= expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
      \uElseIf{novice votes >= novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
    }
    \If{sum(accepted) == 0}{
      sort tags by votes;
      head 1;
      accept; \tcc*[f]{If still no tag, take one with most votes}
    }
  }
  \ForEach{ActorSet in unique(ActorSets)}{
    emit event;
  }
}
\caption{Aggregating Coder-Tokens into Sentence-Events}
\end{algorithm}
\clearpage

\hypertarget{app:intercoderagreement}{%
\subsection{Figure B3 : Intercoder
Agreement}\label{app:intercoderagreement}}

\hphantom{em}

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_concept.png}}
\end{figure}
\clearpage

\hypertarget{app:agreement_by_confidence}{%
\subsection{Figure B4 : Intercoder Agreement by
Confidence}\label{app:agreement_by_confidence}}

\hphantom{em}

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_confidence.png}}
\end{figure}
\clearpage

\hypertarget{appendix-c-recall}{%
\section{Appendix C: Recall}\label{appendix-c-recall}}

\hphantom{em}

\hypertarget{algorithm-c1-synthetic-narratives}{%
\subsection{Algorithm C1: Synthetic
Narratives}\label{algorithm-c1-synthetic-narratives}}

\hphantom{em}

A synthetic narrative is constructed as follows. First, compile a large
corpus, \(D\), of timelines, encyclopedia entries, journal articles,
news reports, websites, and government documents. Next, segment into
sentences, \(s \in S\), clean, filter, and break into simpler concise
sentences, \(s^* \in S^*\), using a large natural language model, BART
(Lewis et al. 2019), fine-tuned on summarization tasks,
distilbart-cnn-12-6 (Shleifer and Rush 2020). Then, calculate semantic
similarity between each \(S*\) by embedding them with a different large
language model, MPNet (Song et al., n.d.), fine tuned to identify
paraphrasing (Reimers and Gurevych 2019, 2020). Next, constructed an
undirected weighted graph of pair above 95th percentile cosine
similarity and hierarchically cluster them into potential events
\(e^* \in E^*\) (Clauset, Newman, and Moore 2004). The resulting set of
\(E^*\) are small enough to check by hand, summarize, and place in
chronological order. The relevant formulas and algorithm are shown
below.

Cosine Similarity \begin{equation}
cosine\;similarity = \frac{a \cdot b}{ || a  ||\;|| b  || }
\end{equation}

Adjacency Matrix \begin{equation} \label{eq:sclrec2}
A_{vw}= \begin{cases} 1 \text{ if vertices v and w are connected} \\ 0 \text{ otherwise } \end{cases}
\end{equation}

Identity Function \begin{equation}
\delta(i,j)= \begin{cases} 1 \text{ if i=j} \\ 0 \text{ otherwise } \end{cases}
\end{equation}

Degree of a vertex \begin{equation}
k_v = \sum_{w}A_{vw}
\end{equation}

Modularity - Is the difference between observed within-community edges
and average expected edges on a random graph
\begin{equation} \label{eq:sclrec2}
Q = \frac{1}{2m}\sum_{vw}[A_{vw}-\frac{k_vk_w}{2m}]\delta(C_w,C_w)
\end{equation}

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Document-Sentences}
\KwResult{Event-Mentions}
\tcc{ Embed text as a 768 dimensional semantic vector with a large language model}
\ForEach{document in Document}{
  \ForEach{sentence in sentence}{
    embedding=distilbart-cnn-6-6(sentence);
  }
}

similarity = cosine similarity(embeddings,embeddings);

\tcc{ Threshold similarity matrix and create weighted undirected graph }

\tcc{ Frame as adding edges so efficient nearest neighbor lookup can be used }

g=EmptyUndirectedWeightedGraph();\tcc*[f]{Sparse undirected graph to store edges}

\ForEach{v in 1:rows(similarity)}{
  \ForEach{w in 1:cols(similarity)}{ 
    \lIf{similarity[v,w]>0.96 and doc(V)!=doc(W)}{append edge v<->w to g}\tcc*[f]{If similar append as undirected edge to graph}
  }
}

\tcc{ Community detection with greedy hierarchically clustering (Clauset et al. 2004)}

gClustered=EmptyUndirectedGraph(vertices(g)); \tcc*[f]{Sparse undirected graph to store edges}
dendrogram=list()
\While{length(edges(g))>1}{

  \ForEach{edge in edges(g)}{
    Qpossible[edge]=Q(gClustered + edge)
  }

  \ForEach{ edge in edges(g) } {
    \tcc{ Add the edge with the maximum increase in modularity }
    \tcc{ Remove from original graph as a housekeeping trick }
    \lIf{ QPossible[edge]=max(QPossible) }{ append edge to gClustered and remove edge from g; append QPossible to dendrogram }
  }
}
\tcc{ Cut the dendrogram to maximize modularity and return event clusters}
\Return dendrogram where Q(dendrogram)==max(dendrogram) \tcc*[f]{}
\caption{Clustering and counting sentences about the same event}
\end{algorithm}
\clearpage

\hypertarget{table-c2-synthetic-narrative-matches-cuban-missile}{%
\subsection{Table C2: Synthetic Narrative Matches Cuban
Missile}\label{table-c2-synthetic-narrative-matches-cuban-missile}}

\hphantom{em}

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{./ft_cuba_recall.png}}
\end{figure}
\clearpage

\hypertarget{table-c3-synthetic-narrative-matches-crimea-donbas}{%
\subsection{Table C3: Synthetic Narrative Matches
Crimea-Donbas}\label{table-c3-synthetic-narrative-matches-crimea-donbas}}

\hphantom{em}

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{./ft_crimea_recall.png}}
\end{figure}
\clearpage

\hypertarget{appendix-d-precision}{%
\section{Appendix D: Precision}\label{appendix-d-precision}}

\hypertarget{figure-d1-crimea-donbos}{%
\subsection{Figure D1 Crimea-Donbos}\label{figure-d1-crimea-donbos}}

\hphantom{em}

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=19cm]{./case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{./case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

\hypertarget{table-d2-stratified-sentence-examples}{%
\subsection{Table D2: Stratified Sentence
Examples}\label{table-d2-stratified-sentence-examples}}

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision1.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision2.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision3.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision4.png"}}
\end{figure}
\clearpage

\hypertarget{figure-d3-crisis-maps-cuban-missiles}{%
\subsection{Figure D3 Crisis Maps Cuban
Missiles}\label{figure-d3-crisis-maps-cuban-missiles}}

\hphantom{em}

\begin{sideways}%[htbp]
\centering{\includegraphics[width=20cm]{./p_196_combined.png}}
\end{sideways}

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_196.png}}
\end{sidewaysfigure}
\clearpage

\hypertarget{figure-d4-crisis-maps-crimea-donbas}{%
\subsection{Figure D4 Crisis Maps
Crimea-Donbas}\label{figure-d4-crisis-maps-crimea-donbas}}

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
\centering{\includegraphics[width=19cm]{./p_471_combined.png}}
\end{sidewaysfigure}

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_471.png}}
\end{sidewaysfigure}

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
\centering{\includegraphics[width=20cm]{./p_terrier_plot_lv0_471.png}}
\end{sidewaysfigure}

\hphantom{em}
\begin{sidewaysfigure}[ht]
\caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
\centering{\includegraphics[width=20cm]{./p_icews_plot_lv0_471.png}}
\end{sidewaysfigure}
\clearpage

\hypertarget{references}{%
\section{References}\label{references}}

\hphantom{em}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-clausetFindingCommunityStructure2004}{}}%
Clauset, Aaron, M. E. J. Newman, and Cristopher Moore. 2004. {``Finding
Community Structure in Very Large Networks.''} \emph{Physical Review E}
70 (6): 066111. \url{https://doi.org/10.1103/PhysRevE.70.066111}.

\leavevmode\vadjust pre{\hypertarget{ref-lewisBARTDenoisingSequencetoSequence2019}{}}%
Lewis, Mike, Yinhan Liu, Naman Goyal, Marjan Ghazvininejad, Abdelrahman
Mohamed, Omer Levy, Ves Stoyanov, and Luke Zettlemoyer. 2019. {``{BART}:
{Denoising Sequence-to-Sequence Pre-training} for {Natural Language
Generation}, {Translation}, and {Comprehension}.''} {arXiv}.
\url{https://doi.org/10.48550/arXiv.1910.13461}.

\leavevmode\vadjust pre{\hypertarget{ref-reimersSentenceBERTSentenceEmbeddings2019}{}}%
Reimers, Nils, and Iryna Gurevych. 2019. {``Sentence-{BERT}: {Sentence
Embeddings} Using {Siamese BERT-Networks}.''}
\url{http://arxiv.org/abs/1908.10084}.

\leavevmode\vadjust pre{\hypertarget{ref-reimersMakingMonolingualSentence2020}{}}%
---------. 2020. {``Making {Monolingual Sentence Embeddings
Multilingual} Using {Knowledge Distillation}.''}
\url{http://arxiv.org/abs/2004.09813}.

\leavevmode\vadjust pre{\hypertarget{ref-shleiferPretrainedSummarizationDistillation2020}{}}%
Shleifer, Sam, and Alexander M. Rush. 2020. {``Pre-Trained
{Summarization Distillation}.''} \url{http://arxiv.org/abs/2010.13002}.

\leavevmode\vadjust pre{\hypertarget{ref-songMPNetMaskedPermuted}{}}%
Song, Kaitao, Xu Tan, Tao Qin, Jianfeng Lu, and Tie-Yan Liu. n.d.
{``{MPNet}: {Masked} and {Permuted Pre-training} for {Language
Understanding},''} 14.

\end{CSLReferences}

\bibliographystyle{unsrt}
\bibliography{paper.bib}

\end{document}

### 2022-09-12 replication_paper/political_analysis_draft/appendix.Rmd
nothing

@@
 
+abstract: |
+  This is the online appendix to the article "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises".
+In the article, we conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
+We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
+We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
+We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
+We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.
+
 header-includes:
@@
   - \usepackage{titlesec}
-#  - \usepackage[parfill]{parskip}
+  - \usepackage[parfill]{parskip}
   - \usepackage{makecell}
   - \usepackage{graphicx}
+  - \usepackage{rotating}
+  - \usepackage{float}
+  # - \usepackage{showframe}
 #  - \usepackage{caption}
@@
 #https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
+  - \usepackage{changepage}
+
 ---
-
 \newpage
@@
 \caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
-\centering{\includegraphics[height=21cm]{./ft_cuba_recall.png}}
+\centering{\includegraphics[height=19cm]{./ft_cuba_recall.png}}
 \end{figure}
@@
 \caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
-\centering{\includegraphics[height=21cm]{./ft_crimea_recall.png}}
+\centering{\includegraphics[height=19cm]{./ft_crimea_recall.png}}
 \end{figure}
@@
 # Appendix D: Precision
-## Figure D1 Crimea-Donbos 
+## Figure D1 Crimea-Donbas 
 \hphantom{em}
@@
 \begin{figure}[H]
-\centering{\includegraphics[height=21cm]{./case_study_crimea_precision_part2.png}}
+\centering{\includegraphics[height=11cm]{./case_study_crimea_precision_part2.png}}
 \end{figure}
@@
 
+<!-- current -->
+
 \hphantom{em}
@@
 \caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
-\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision1.png"}}
+\centering{\includegraphics[height=15cm]{"./ft_sample_precision_precision1.png"}} 
 \end{figure}
@@
 ## Figure D3 Crisis Maps Cuban Missiles
-
-\hphantom{em}
 
@@
 
-\begin{sideways}%[htbp]
-\centering{\includegraphics[width=20cm]{./p_196_combined.png}}
-\end{sideways}
+\begin{sidewaysfigure}[ht]
+\caption{Crisis Maps - Cuban Missiles \label{fig:p_196_combined}}
+\centering{\includegraphics[width=0.8\textwidth]{./p_196_combined.png}}
+\end{sidewaysfigure}
+\clearpage
 
@@
 
-\hphantom{em}
 \begin{sidewaysfigure}[ht]
 \caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_196.png}}
+\centering{\includegraphics[width=0.9\textwidth]{./p_phoenix_plot_lv0_196.png}}
 \end{sidewaysfigure}
@@
 
+save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_mids.png'),
+          p_471_mids, base_height = 18, base_width = 13.5)
+
 library(cowplot)
@@
 save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_combined.png'),
-          p_471_combined, base_height = 12, base_width = 25)
+          p_471_combined, base_height = 14, base_width = 23)
 }
@@
 ```
+
+<!-- \begin{figure}[H] -->
+<!-- \caption{Crisis Map: Cuban Missile Crisis \label{fig:p_471_mids.png}} -->
+<!-- \centering{\includegraphics[width=17cm]{./p_471_mids.png}} -->
+<!-- \end{figure} -->
 
@@
 \caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
-\centering{\includegraphics[width=19cm]{./p_471_combined.png}}
+\includegraphics[width=0.9\textwidth]{./p_471_combined.png}
 \end{sidewaysfigure}
@@
 \caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
-\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_471.png}}
+\centering{\includegraphics[width=0.75\textwidth]{./p_phoenix_plot_lv0_471.png}}
 \end{sidewaysfigure}

### 2022-09-12 replication_paper/political_analysis_draft/appendix.tex
nothing

@@
 \usepackage{titlesec}
+\usepackage[parfill]{parskip}
 \usepackage{makecell}
 \usepackage{graphicx}
+\usepackage{rotating}
+\usepackage{float}
 \usepackage{setspace}
@@
 \usepackage{amsmath}
+\usepackage{changepage}
 \usepackage{multirow}
@@
 \begin{abstract}
-
+This is the online appendix to the article ``Introducing ICBe: Very High
+Recall and Precision Event Extraction from Narratives about
+International Crises''. In the article, we conceptualize of
+international relations as a strategic chess game between adversaries
+and develop a systematic way to measure pieces, moves, and gambits
+accurately and consistently over a hundred years of history. We
+introduce a new ontology and dataset of international events called ICBe
+based on a very high-quality corpus of narratives from the International
+Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher
+coverage, recall, and precision than existing state of the art datasets
+and conduct two detailed case studies of the Cuban Missile Crisis (1962)
+and Crimea-Donbas Crisis (2014). We further introduce two new event
+visualizations (event icongraphy and crisis maps), an automated
+benchmark for measuring event recall using natural language processing
+(sythnetic narratives), and an ontology reconstruction task for
+objectively measuring event precision. We make the data, online
+appendix, replication material, and visualizations of every historical
+episode available at a companion website www.crisisevents.org and the
+github repository.
 \end{abstract}
@@
 
-\hypertarget{figure-d1-crimea-donbos}{%
-\subsection{Figure D1 Crimea-Donbos}\label{figure-d1-crimea-donbos}}
+\hypertarget{figure-d1-crimea-donbas}{%
+\subsection{Figure D1 Crimea-Donbas}\label{figure-d1-crimea-donbas}}
 
@@
 
-\hphantom{em}
-
-\begin{sideways}%[htbp]
-\centering{\includegraphics[width=20cm]{./p_196_combined.png}}
-\end{sideways}
-
-\hphantom{em}
+\begin{sidewaysfigure}[ht]
+\caption{Crisis Maps - Cuban Missiles \label{fig:p_196_combined}}
+\centering{\includegraphics[width=0.8\textwidth]{./p_196_combined.png}}
+\end{sidewaysfigure}
+\clearpage
+
 \begin{sidewaysfigure}[ht]
 \caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_196.png}}
+\centering{\includegraphics[width=0.9\textwidth]{./p_phoenix_plot_lv0_196.png}}
 \end{sidewaysfigure}

### 2022-09-14 replication_paper/political_analysis_draft/appendix.Rmd
white space and appendix

@@
 
-abstract: |
-  This is the online appendix to the article "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises".
+# abstract: |
+#   This is the online appendix to the article "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises".
 In the article, we conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
@@
   - \usepackage{changepage}
+  - \renewenvironment{abstract}{}{}
+  - \usepackage{adjustbox}
 
@@
 
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Cuban Missiles \label{fig:p_196_combined}}
-\centering{\includegraphics[width=0.8\textwidth]{./p_196_combined.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Cuban Missiles}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_196_combined.png}
+\label{fig:p_196_combined}
+\end{adjustbox}
+\end{figure}
 \clearpage
@@
 
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=0.9\textwidth]{./p_phoenix_plot_lv0_196.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_phoenix_plot_lv0_196.png}
+\label{fig:p_phoenix_plot_lv0_196}
+\end{adjustbox}
+\end{figure}
 \clearpage
@@
 \hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
-\includegraphics[width=0.9\textwidth]{./p_471_combined.png}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=.9\paperwidth]{./p_471_combined.png}
+\label{fig:p_471_combined}
+\end{adjustbox}
+\end{figure}
 
@@
 \hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
-\centering{\includegraphics[width=0.75\textwidth]{./p_phoenix_plot_lv0_471.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_phoenix_plot_lv0_471.png}
+\label{fig:p_phoenix_plot_lv0_471}
+\end{adjustbox}
+\end{figure}
 
@@
 \hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
-\centering{\includegraphics[width=20cm]{./p_terrier_plot_lv0_471.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_terrier_plot_lv0_471.png}
+\label{fig:p_terrier_plot_lv0_471}
+\end{adjustbox}
+\end{figure}
 
@@
 \hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
-\centering{\includegraphics[width=20cm]{./p_icews_plot_lv0_471.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_icews_plot_lv0_471.png}
+\label{fig:p_icews_plot_lv0_471}
+\end{adjustbox}
+\end{figure}
+
 \clearpage

### 2022-09-14 replication_paper/political_analysis_draft/appendix.tex
white space and appendix

--- 2022-09-12 replication_paper/political_analysis_draft/appendix.tex
@@
 \usepackage{amsmath}
+\usepackage{changepage}
+\renewenvironment{abstract}{}{}
+\usepackage{adjustbox}
 \usepackage{multirow}
@@
 
-\hphantom{em}
-
-\begin{sideways}%[htbp]
-\centering{\includegraphics[width=20cm]{./p_196_combined.png}}
-\end{sideways}
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_196}}
-\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_196.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Cuban Missiles}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_196_combined.png}
+\label{fig:p_196_combined}
+\end{adjustbox}
+\end{figure}
+\clearpage
+
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Cuban Missiles - Phoenix Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_phoenix_plot_lv0_196.png}
+\label{fig:p_phoenix_plot_lv0_196}
+\end{adjustbox}
+\end{figure}
 \clearpage
@@
 \hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas \label{fig:p_471_combined}}
-\centering{\includegraphics[width=19cm]{./p_471_combined.png}}
-\end{sidewaysfigure}
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated \label{fig:p_phoenix_plot_lv0_471}}
-\centering{\includegraphics[width=20cm]{./p_phoenix_plot_lv0_471.png}}
-\end{sidewaysfigure}
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated \label{fig:p_terrier_plot_lv0_471}}
-\centering{\includegraphics[width=20cm]{./p_terrier_plot_lv0_471.png}}
-\end{sidewaysfigure}
-
-\hphantom{em}
-\begin{sidewaysfigure}[ht]
-\caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated \label{fig:p_icews_plot_lv0_471}}
-\centering{\includegraphics[width=20cm]{./p_icews_plot_lv0_471.png}}
-\end{sidewaysfigure}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=.9\paperwidth]{./p_471_combined.png}
+\label{fig:p_471_combined}
+\end{adjustbox}
+\end{figure}
+
+\hphantom{em}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas Phoenix Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_phoenix_plot_lv0_471.png}
+\label{fig:p_phoenix_plot_lv0_471}
+\end{adjustbox}
+\end{figure}
+
+\hphantom{em}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas Terrier Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_terrier_plot_lv0_471.png}
+\label{fig:p_terrier_plot_lv0_471}
+\end{adjustbox}
+\end{figure}
+
+\hphantom{em}
+\begin{figure}[H]
+\begin{adjustbox}{
+  addcode={\begin{minipage}{\width}
+           \caption{Crisis Maps - Crimea-Donbas ICEWs Disaggregated}}
+          {\end{minipage}},
+  rotate=90}
+\includegraphics[width=1\paperwidth]{./p_icews_plot_lv0_471.png}
+\label{fig:p_icews_plot_lv0_471}
+\end{adjustbox}
+\end{figure}
+
 \clearpage

### 2022-09-21 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
white space and appendix
all the fixes

@@
 We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.
+We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
 
@@
         group_by(sentence_number_int_aligned) %>%
-          filter(value_markdown!='' | length(value_markdown)==1) %>%
+          filter(value_markdown!='' | length(value_markdown)==1) %>% # also added below to handle sentence 6
         ungroup() %>%
@@
         mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
-        mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
+        mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text)) %>% 
+            filter(value_markdown!='' | length(value_markdown)==1) 
+      #C=crisno, 
       #head(100) %>%
@@
 \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[ height=19cm]{"./case_study_cuban_precision.png"}}
+\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
 \end{figure}
@@
 ========================================
-
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).] Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
+<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
+
+For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
+Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
 Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
@@
 Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors, and provide a full codebook in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.^[See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
 
@@
 Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix, Table A2).
+Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
 
@@
                   mutate(Literature = paste0(" [",Literature %>% stringr::str_replace("; {0,}$","") ,"]")) %>%
-                  mutate(Concept= Concept %>% paste0(Literature)) %>%
+                  mutate(Concept= paste0("**", Concept, "**", Literature)) %>%
                   mutate(Concept = Concept %>% stringr::str_replace(stringr::fixed("[NA]"),"") ) %>%
+                  mutate(Concept = Concept %>% stringr::str_replace(stringr::fixed(" ["),stringr::fixed(" - ["))) %>%
                   dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
@@
 r_say= ( lit_review_pull$...1 %in% "Say" %>% sum() ) + r_think
-r_unarmed= ( lit_review_pull$...2 %in% "Unarmed" %>% sum() ) + r_say
-r_armed= ( lit_review_pull$...2 %in% "Armed" %>% sum() ) + r_unarmed
+r_unarmed= ( lit_review_pull$...1 %in% "Do - Unarmed" %>% sum() ) + r_say
+r_armed= ( lit_review_pull$...1 %in% "Do - Armed" %>% sum() ) + r_unarmed
 ft <- NULL
@@
 
-      add_header( 
-                  #"ICB Corpus"="Corpus",
-                  "ICBe"="Events Datasets",
-                  "Phoenix"="Events Datasets",
-                  "Terrier"="Events Datasets",
-                  "ICEWs"="Events Datasets",
-                  "MIDs Incidents"="Events Datasets",
-                  "UCDP-GED"="Events Datasets",
-                  "ICB"="Episodes Datasets",
-                  "COW"="Episodes Datasets",
-                  "MIDs"="Episodes Datasets",
-                  top = T ) %>%
+      # add_header(
+      #             #"ICB Corpus"="Corpus",
+      #             "ICBe"="Events Datasets",
+      #             "Phoenix"="Events Datasets",
+      #             "Terrier"="Events Datasets",
+      #             "ICEWs"="Events Datasets",
+      #             "MIDs Incidents"="Events Datasets",
+      #             "UCDP-GED"="Events Datasets",
+      #             "ICB"="Episodes Datasets",
+      #             "COW"="Episodes Datasets",
+      #             "MIDs"="Episodes Datasets",
+      #             top = T ) %>%
 
@@
 
-      merge_h(part = "header") %>% #it's this merge that's killing us
+      # undo merge of the header
+      # merge_h(part = "header") %>% #it's this merge that's killing us
 
@@
       #ok so because of our horizontal merging of headers, we have to manually place a right bar at j=10 2 short of the full width
-      flextable::border_outer( part="all", border = big_border ) %>% #this will have a gap
-      border(j=10:k, i=1 , part="header", border.right = big_border ) %>% #this fills the gap
+      flextable::border_outer(part="all", border = big_border) %>% #this will have a gap
+      # border(j=10:k, i=1 , part="header", border.right = big_border ) %>% #this fills the gap
+
       #There's another gap on the bottom left
-      border(j=1, i=(n-15):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
-      border(j=2, i=(n-5):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
+      # border(j=1, i=(n-15):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
+      # border(j=2, i=(n-5):n , part="body", border.bottom =  big_border ) %>% #this fills the gap
 
@@
       flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
+      flextable::fontsize(size = 6.5, part = "all") %>%
       #Banding
-      bg( i = bands  , j=3:k, part = "body", bg = "#EFEFEF") %>%
-
-      flextable::rotate(i=2, j=3:k, rotation="tbrl",part="header") %>%
+      bg( i = bands, j=2:k, part = "body", bg = "#EFEFEF") %>%
+
+      flextable::rotate(i=1, j=2:k, rotation="tbrl", part="header") %>%
       flextable::align(align = "center", part = "body") %>%
@@
       hline(i=c(r_intro), border = NULL, part = "body") %>% 
-      merge_at(i = 1:r_intro, j = 1:2, part = "body") %>%  
-      merge_at(i = 4, j = 5:7, part = "body") %>%
-      merge_at(i = 5, j = 5:7, part = "body") %>%
-      merge_at(i = 6, j = 5:7, part = "body") %>%
-      merge_at(i = 7, j = 5:7, part = "body") %>%
+      merge_at(i = 1:r_intro, j = 1, part = "body") %>%  
+      # merge_at(i = 4, j = 5:7, part = "body") %>%
+      # merge_at(i = 5, j = 5:7, part = "body") %>%
+      # merge_at(i = 6, j = 5:7, part = "body") %>%
+      # merge_at(i = 7, j = 5:7, part = "body") %>%
 
@@
       hline(i=c(r_players), border = NULL, part = "body") %>% 
-      merge_at(i = (r_intro+1):r_players, j = 1:2, part = "body") %>%  
+      merge_at(i = (r_intro+1):r_players, j = 1, part = "body") %>%  
       #pieces
       hline(i=c(r_pieces), border = NULL, part = "body") %>% 
-      merge_at(i = (r_players+1):r_pieces, j = 1:2, part = "body") %>%  
+      merge_at(i = (r_players+1):r_pieces, j = 1, part = "body") %>%  
       #think
       hline(i=c(r_think), border = NULL, part = "body") %>% 
-      merge_at(i = (r_pieces+1):r_think, j = 1:2, part = "body") %>%  
+      merge_at(i = (r_pieces+1):r_think, j = 1, part = "body") %>%  
       #say
       hline(i=c(r_say), border = NULL, part = "body") %>% 
-      merge_at(i = (r_think+1):r_say, j = 1:2, part = "body") %>%
+      merge_at(i = (r_think+1):r_say, j = 1, part = "body") %>%
       #Do
-      merge_at(i = (r_say+1):r_armed, j = 1, part = "body") %>%
+      #merge_at(i = (r_say+1):r_armed, j = 1, part = "body") %>%
 
       #n_unarmed
-      hline(i=c(r_unarmed), border = NULL, part = "body") %>% 
-      merge_at(i = (r_say+1):r_unarmed, j = 2, part = "body") %>%  
+      hline(i=c(r_unarmed), j = 1:k, part = "body") %>% 
+      merge_at(i = (r_say+1):r_unarmed, j = 1, part = "body") %>%  
       #n_armed
       #hline(i=c(r_armed), border = NULL, part = "body") %>% 
-      merge_at(i = (r_unarmed+1):r_armed, j = 2, part = "body") %>%
+      merge_at(i = (r_unarmed+1):r_armed, j = 1, part = "body") %>%
 
       #set_table_properties(layout="autofit")  %>%
-      vline( i = 1:2, j = c(3,9), border = NULL, part = "header") %>%
-      vline( i = 1:(n), j = 1:2, border = NULL, part = "body")  %>%
-      vline( i = 1:(n), j = c(3,9), border = NULL, part = "body")  %>%
-
-      flextable::width( j = 3, width=3.3) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
-      flextable::width( j = (4):k, width=0.25) %>%
+      vline( i = 1, j = c(2,8), border = NULL, part = "header") %>%
+      vline( i = 1:(n), j = 1, border = NULL, part = "body")  %>%
+      vline( i = 1:(n), j = c(2,8), border = NULL, part = "body")  %>%
+
+      flextable::width( j = 2, width=3.1) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
+      flextable::width( j = (3):k, width=0.25) %>%
       flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-
-      flextable::rotate(j=1, rotation="tbrl",part="all") %>%
-      flextable::rotate(j=2, rotation="tbrl",part="all") %>%
-      flextable::width( j = 1:2, width=0.1)  %>%
-      ftExtra::colformat_md(j = 3, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above
+      flextable::padding(padding = 0, part = "all") %>%
+
+      flextable::rotate(j=1, rotation="tbrl",part="all", align="center") %>%
+      #flextable::rotate(j=2, rotation="tbrl",part="all") %>%
+      flextable::width(j = 1, width=0.1)  %>%
+      ftExtra::colformat_md(j = 2, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above
 
@@
 The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix, Fig.
-B1).
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
 Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
@@
 Undergraduate coders were students who engaged in classroom workshops.] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
-We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix, Algorithm B2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
+We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix 2.2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
 This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
@@
 We evaluate the internal validity of the coding process in several ways.
-For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix, Fig.
-B3).
+For every tag applied we calculate the observed intercoder agreement as the percent of other coders who also applied that same tag (SI Appendix 2.3).
 Across all concepts, the Top 1 Tag Agreement was low among novices (`r means_group_any$Novices %>% round(2) %>% scales::percent()`), moderate for experts (`r means_group_any$Experts %>% round(2) %>% scales::percent()`), and high (`r means_group_keep$Experts_keep %>% round(2) %>% scales::percent()`) following the consensus screening procedure.
@@
 First, we required coders to rate their confidence which was observed to be low for 20% of sentences- half due to a mismatch between the ontology and the text ("survey doesn't fit event"-45%) and half due to a lack of information or confused writing in the source text ("more knowledge needed"-40%, "confusing sentence"-6%).
-Observed disagreement varied predictably with self reported confidence (SI Appendix, Fig.
-B4).
-Second, as intended agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50%-60%).
+Observed disagreement varied predictably with self reported confidence (SI Appendix 2.4).
+Second, as intended, agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50%-60%).
 Third, individual coders exhibiting nontrivial coding styles, e.g.
@@
 The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
+The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
 Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers.
@@
 History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events.
-The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
+The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one that allows for comparing proposals from event projects that had different goals.
 We need a yardstick for history.
@@
 For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
-Using natural language processing (fully described in SI Appendix, Algorithm C1), we identify details that appear across multiple accounts.
+Using natural language processing (fully described in SI Appendix 3.1), we identify details that appear across multiple accounts.
 The more accounts that mention a detail, the more central it is to understanding the true historical episode.
@@
             #
-            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) "))
+            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>% 
+            #
+            str_replace_all('🇪🇺', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
                             }
@@
 \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
+Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).}
 \end{figure}
@@
 You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig.
-D3 and D4) and all crises on the companion website.
+We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study in SI Appendix 4.3 and 4.4 and for all crises on the companion website.
 
@@
 We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix Table D1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix Table D2).
+We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix 4.1), and for every case on the companion website.
+We further provide a stratified sample of event codings alongside their source text (SI Appendix 4.2).
 
@@
 Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coerce branch nodes of the ontology.
+Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
 If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]
@@
 Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix Figure D3 and D4).
+The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
 On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
@@
 However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, [@terechshenkoHotCollarLatent2020] attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
+For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
 Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
-geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks].
+geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks2018].
 
@@
 #use_python("/home/tlscherer/anaconda3/bin/python3")
+#py_install("sentence-transformers")
 
@@
       #           ) + 
-      labs(
-          title = "Variation in Tags by Semantic Embeddings of Source Sentences",
-          subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
-          caption = ""
-      ) +
+      # labs(
+      #     title = "Variation in Tags by Semantic Embeddings of Source Sentences",
+      #     subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
+      #     caption = ""
+      # ) +
      #scale_color_manual(values = value_normalized_colors) +
@@
 
+ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)
+
 p_combined <- plot_grid(
+  NULL,
   p_semantic_embeddings + xlab("") + ylab("") + 
@@
   theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
+  NULL,
   p_dendro  + xlab("") + ylab("") + 
@@
   labels = c('',''),
-  align = "v", ncol = 2, rel_widths = c(3, 1)  )
+  align = "v", nrow = 1, rel_widths = c(-.2, 3.5, -.4, 1.5)  ) #increase the second width to give the dendro more room
 #p_combined
@@
 
-if(fromscratch){
+#if(fromscratch){
 
@@
 icews_clean_subset_top10_day <- read_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
+
+icews_clean_subset_top10_day <- icews_clean_subset_top10_day %>% 
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all("/mnt/8tb_a/rwd_github_private/ICBEdataset", here::here())) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(" ", "")) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all("VladimirPutin", "Putin")) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("png))"), stringr::fixed("png)"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("(!"), stringr::fixed("!"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("ViktorYanukovych->![](/"), stringr::fixed("Yanukovych->.![](/"))) %>% 
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Putin->![](/"), stringr::fixed("Putin->![](/"))) %>%  
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Military![]"), stringr::fixed("Military-![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Police![]"), stringr::fixed("Police.![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Citizen![]"), stringr::fixed("Citizen..![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("ArmedRebel![]"), stringr::fixed("ArmedRebel-![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Bank![]"), stringr::fixed("Bank.![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Business![]"), stringr::fixed("Business.![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Insurgent![]"), stringr::fixed("Insurgent-![]"))) %>%
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("Separatist![]"), stringr::fixed("Separatist-![]"))) %>%  
+  dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("BarackObama->![](/"), stringr::fixed("Obama->.![](/")))
+
+#Separatist(![](/home/tlscherer/Desktop/ICBEdataset/replication_data/in/flags_small//Q212.png))->Military(![](/home/tlscherer/Desktop/ICBEdataset/replication_data/in/flags_small//Q212.png))
+
+  #dplyr::mutate(dyad_markdown = dyad_markdown %>% stringr::str_replace_all(stringr::fixed("(!"), stringr::fixed("--!"))) %>%
+
+#/replication_data/in/flags_small//Q159.png
 
@@
            p1 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) +
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
+             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)) +
+             # theme(axis.ticks=element_blank()),
+            theme(axis.title=element_blank(),
+                axis.ticks.length = unit(.2, "cm"),
+                axis.ticks=element_blank()),
            p2 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
+             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)) +
+             theme(axis.ticks=element_blank()),
            p3 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
+             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)) +
+             theme(axis.ticks=element_blank()),
            p4 + xlim(as.Date('2013-07-01'), as.Date('2015-07-01')) + 
-             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)  ),
+             theme(legend.position="none")  + theme(plot.margin = unit(c(0,0,0,0), "cm")) + theme( axis.text.y = element_markdown(size = 12, lineheight = 0.1)) +
+             theme(axis.ticks=element_blank()),
            #labels = c('Cuban Missiles','Crimea-Donbas'), 
@@
 
-}
+#}
 
@@
 \begin{figure}[H]
-\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
+\caption{ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
 \centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
 \textit{Notes:Unit of analysis is the Dyad-Day.
-Edges <-> indicates undirected dyad and -> indicates directed dyad.
 Top 10 most active dyads per category shown.
@@
 <!-- \twocolumn -->
+<!-- Edges <-> indicates undirected dyad and -> indicates directed dyad.  # removed from legend with update-->
 
@@
 
-Funding {
+Funding
 ========================================
@@
 ========================================
+
 We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
@@
 Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
-This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.
 

### 2022-09-21 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
all the fixes

@@
 appendix, replication material, and visualizations of every historical
-episode available at a companion website www.crisisevents.org and the
-github repository.
+episode available at a companion website www.crisisevents.org.
 \end{abstract}
@@
 historical narratives from the International Crisis Behavior (ICB)
-project (\(n=471\))(SI Appendix, Table A1)(Brecher et al. 2017; Brecher
-and Wilkenfeld 1997).\footnote{The Online Appendix is at the
-  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData
-  Github Repository}.} Their domain is 20th and 21st-century crises,
-defined as a change in the type, or an increase in the intensity, of
-disruptive interaction with a heightened probability of military
-hostilities that destabilizes states' relationships or challenges the
-structure of the international system (Brecher and Wilkenfeld
-1982).\footnote{On near crises see Iakhnis and James (2019).} Crises are
-a significant focus of detailed single case studies and case comparisons
-because they provide an opportunity to examine behaviors in IR short of,
-or at least prior to, full conflict (Holsti 1965; Paige 1968; Allison
-and Zelikow 1971; Snyder and Diesing 1977; Gavin 2014; George and Smoke
-1974; Brecher and Wilkenfeld 1982; Gaddis 1987; Brecher and James 1988).
-Case selection was exhaustive based on a survey of world news archives
-and region experts, cross-checked against other databases of war and
-conflict, and non-English sources (Kang and Lin 2019; Brecher et al.
-2017, 59). Each narrative was written by consensus by a small number of
-scholars, using a uniform coding scheme, with similar specificity
-(Hewitt 2001). The corpus is unique in IR because it is designed to be
-used in a downstream quantitative coding project.
+project (\(n=471\))(Supplementary Information (SI) Appendix 1.1)(Brecher
+et al. 2017; Brecher and Wilkenfeld 1997). Their domain is 20th and
+21st-century crises, defined as a change in the type, or an increase in
+the intensity, of disruptive interaction with a heightened probability
+of military hostilities that destabilizes states' relationships or
+challenges the structure of the international system (Brecher and
+Wilkenfeld 1982).\footnote{On near crises see Iakhnis and James (2019).}
+Crises are a significant focus of detailed single case studies and case
+comparisons because they provide an opportunity to examine behaviors in
+IR short of, or at least prior to, full conflict (Holsti 1965; Paige
+1968; Allison and Zelikow 1971; Snyder and Diesing 1977; Gavin 2014;
+George and Smoke 1974; Brecher and Wilkenfeld 1982; Gaddis 1987; Brecher
+and James 1988). Case selection was exhaustive based on a survey of
+world news archives and region experts, cross-checked against other
+databases of war and conflict, and non-English sources (Kang and Lin
+2019; Brecher et al. 2017, 59). Each narrative was written by consensus
+by a small number of scholars, using a uniform coding scheme, with
+similar specificity (Hewitt 2001). The corpus is unique in IR because it
+is designed to be used in a downstream quantitative coding project.
 
@@
 precise geo-coding is required to understand the chessboard (medium of
-conflict). We find 472 actors and 117 different behaviors, and provide a
-full codebook in the online material.\footnote{See the Github Repository
+conflict). We find 472 actors and 117 different behaviors.\footnote{See
+  the full codebook on Github Repository
   \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
@@
 and then aggregated into a smaller number hypernyms balancing conceptual
-detail and manageable sparsity for human coding (SI Appendix, Table A2).
+detail and manageable sparsity for human coding (SI Appendix 1.2).
 
@@
 
-\begin{longtable}[c]{|p{0.10in}|p{0.10in}|p{3.30in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
+\begin{longtable}[c]{|p{0.10in}|p{3.10in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.5in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{3}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 3.5in+4\tabcolsep+2\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{6}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 1.5in+10\tabcolsep+5\arrayrulewidth}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Events\ Datasets}}} & \multicolumn{3}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Episodes\ Datasets}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{7}{7}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Start}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Brecher}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hegre}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Iakhnis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{James}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Kreutz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weisiger}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{32k}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{128k}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coders}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Automated\ (CAMEO)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hand}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Date}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Article}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-7}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Location}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.75in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{States}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Fazal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Paul,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ikenberry,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hall}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Subnational}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Actors}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Haffar}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2002;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hsu}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{et}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{al.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{McMillan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2008)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Bush}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Kim}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2008;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Ben-Yehuda}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{mishali–ram}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fatalities}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Lacina}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gleditsch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Size}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Carafano}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1986;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Gartzke}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Horowitz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lanoszka}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hunzeker}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Geography}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(location,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{territorial}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{change)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Carter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Start/End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Crisis)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Lupton}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wishes}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Desire/Fear)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Goldgeier}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2001;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mercer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evaluation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Victory/Defeat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Stein}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Russett}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aims}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Policy,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Regime,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preemption)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sullivan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Awareness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discover,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Become}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Convinced)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Ramsay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Wirtz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{React}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{to}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{past}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Praise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Disapprove,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accept,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reject,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Accuse)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(O’Neill}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Risse}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Trager}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Request}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Appeal,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Demand)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Zartman}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Faure}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{future}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{event}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Promise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Threaten,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Express}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intent,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Offer}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Without}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Condition)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Davis}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{2}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.2in+2\tabcolsep+1\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Predict}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{with}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{condition}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Offer,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ultimatum)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(R.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Government}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leadership/Institution}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Change,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Coup,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assasination)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Goemans,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Harkness}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Jones}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Olken}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Matanock}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{By}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Protest/Riot/Strike)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Chenoweth,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hendrix,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hunter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Civilians}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Terrorism,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Domestic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Rights,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mass}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Killing,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Evacuate)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Eck}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hultman}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{LaFree}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dugan}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomacy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Discussion,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Meeting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mediation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Break}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{off}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{negotiations,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw/Expel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Diplomats,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Propoganda)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Beardsley}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Legal}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreements}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Sign}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Settle}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Dispute,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{on}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Behalf}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Ally,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Defense}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Pact,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Open}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cede}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Territory,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Allow}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Inspections,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Succession,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Leave}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Alliance,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terminate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Treaty)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Anac}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2005;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Gibler}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2004;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Owsiak,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cuttner,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Buck}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Violate}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Terms}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Agreement)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2003/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mutual}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{cooperation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{or}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooperation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Directed}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(General}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Support,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Economic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Humanitarian}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Military}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Intelligence}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Unspecified}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Aid)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(de}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{~>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Preparation}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Alert,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Mobilization,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fortify,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Exercise,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Weapons}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Test)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Lai}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Maneuver}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Deployment,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Show}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{of}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Force,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Blockade,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{No}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fly}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Zone,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Border}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Violation)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Allen,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Flynn,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Martinez}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Machain}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Combat}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Battle/Clash,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Attack,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Invasion/Occupation,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Bombard,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Cease}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fire,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Retreat)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Fortna}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Min}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Strategic}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Declare}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Join}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Continue}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Fighting,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Surrender,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{End}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Withdraw}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{from}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{War,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Switch}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Sides)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Levy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Thompson}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reiter}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2009)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-13}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Do}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Political}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Assert}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Autonomy}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Against,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Annex,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Reduce}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Control}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Over,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Decolonize)}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{(Frederick,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Hensel}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{1996;}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{Schultz}}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{2015)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{7}{4}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Type}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Episode}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Event)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Start}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Brecher}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hegre}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Iakhnis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{James}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Kreutz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Weisiger}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{N}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Coders}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Hand}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Automated)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Corpus}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Date}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Article)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Location}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{States}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Paul,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ikenberry,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hall}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Subnational}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Actors}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2002;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hsu}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{et}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{al.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McMillan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2008)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{IGO/NGO}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kim}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2008;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{mishaliram}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fatalities}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Force}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Size}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Carafano}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1986;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Force}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Domain}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Horowitz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunzeker}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Geography}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(location,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{territorial}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{change)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Carter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Alert}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Start/End}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Crisis)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Lupton}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Wishes}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Desire/Fear)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Goldgeier}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2001;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mercer}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Evaluation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Victory/Defeat)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Stein}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Russett}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aims}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Territory,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Policy,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Regime,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Preemption)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Sullivan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Awareness}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Discover,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Become}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Convinced)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Ramsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wirtz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{React}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{to}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{past}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Praise,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Disapprove,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Accept,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Reject,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Accuse)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(O’Neill}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Risse}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Trager}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Request}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{future}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Appeal,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Demand)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Zartman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Faure}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Predict}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{future}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Promise,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Threaten,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Express}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Intent,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Offer}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Without}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Condition)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Davis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Predict}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{with}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{condition}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Offer,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Ultimatum)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(R.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Government}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Leadership/Institution}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Change,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Coup,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Assasination)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Goemans,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Harkness}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Jones}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olken}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Matanock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{By}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Protest/Riot/Strike)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Chenoweth,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hendrix,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Against}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Terrorism,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Domestic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Rights,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mass}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Killing,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Evacuate)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Eck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hultman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{LaFree}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Dugan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Diplomacy}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Discussion,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Meeting,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mediation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Break}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{off}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{negotiations,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Withdraw/Expel}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Diplomats,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Propoganda)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Beardsley}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Legal}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreements}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Sign}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreement,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Settle}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Dispute,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Join}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{on}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Behalf}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{of,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Ally,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mutual}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Defense}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Pact,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Open}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Border,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cede}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Territory,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Allow}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Inspections,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Political}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Succession,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Leave}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Alliance,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Terminate}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Treaty)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Anac}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gibler}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2004;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Owsiak,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cuttner,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Buck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Violate}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreement}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Violate}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Terms}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{of}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreement)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2003/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mutual}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cooperation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Directed}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Economic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{cooperation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Military}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cooperation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Intelligence}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cooperation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Unspecified)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Directed}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(General}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Political}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Support,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Economic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Humanitarian}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Military}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Intelligence}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Unspecified}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Preparation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Alert,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mobilization,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fortify,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Exercise,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Weapons}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Test)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Lai}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Maneuver}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Deployment,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Show}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{of}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Force,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Blockade,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{No}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fly}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Zone,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Border}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Violation)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Allen,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Flynn,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Martinez}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Machain}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Combat}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Battle/Clash,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Attack,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Invasion/Occupation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Bombard,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cease}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fire,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Retreat)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Fortna}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Min}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Strategic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Declare}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Join}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Continue}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fighting,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Surrender,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Withdraw}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{from}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Switch}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Sides)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Levy}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thompson}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Reiter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2009)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Autonomy}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Assert}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Political}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Control}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Over,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Assert}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Autonomy}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Against,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Annex,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Reduce}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Control}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Over,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Decolonize)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Frederick,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1996;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Schultz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
 
@@
 instructed to first thoroughly read the full crisis narrative and then
-presented with a custom graphical user interface (SI Appendix, Fig. B1).
+presented with a custom graphical user interface (SI Appendix 2.1).
 Coders then proceeded sentence by sentence, choosing the number of
@@
 such as an actor, date, behavior, etc. We then aggregate those tags into
-final events (n=18,783), using a consensus procedure (SI Appendix,
-Algorithm B2) that requires a tag to have been chosen by at least one
-expert coder and either a majority of expert or novice coders. This
-screens noisy tags that no expert considered possible but leverages
-novice knowledge to tie-break between equally plausible tags chosen by
-experts.
+final events (n=18,783), using a consensus procedure (SI Appendix 2.2)
+that requires a tag to have been chosen by at least one expert coder and
+either a majority of expert or novice coders. This screens noisy tags
+that no expert considered possible but leverages novice knowledge to
+tie-break between equally plausible tags chosen by experts.
 
@@
 For every tag applied we calculate the observed intercoder agreement as
-the percent of other coders who also applied that same tag (SI Appendix,
-Fig. B3). Across all concepts, the Top 1 Tag Agreement was low among
-novices (31\%), moderate for experts (65\%), and high (73\%) following
-the consensus screening procedure.
+the percent of other coders who also applied that same tag (SI Appendix
+2.3). Across all concepts, the Top 1 Tag Agreement was low among novices
+(31\%), moderate for experts (65\%), and high (73\%) following the
+consensus screening procedure.
 
@@
 disagreement varied predictably with self reported confidence (SI
-Appendix, Fig. B4). Second, as intended agreement is higher (75-80\%)
-for questions with fewer options near the root of the ontology compared
-to agreement for questions near the leafs of the ontology (50\%-60\%).
+Appendix 2.4). Second, as intended, agreement is higher (75-80\%) for
+questions with fewer options near the root of the ontology compared to
+agreement for questions near the leafs of the ontology (50\%-60\%).
 Third, individual coders exhibiting nontrivial coding styles, e.g.~some
@@
 the brink of nuclear war (hereafter Cuban Missiles). The second is the
-Crimea-Donbas Crisis (SI Appendix Figure D1) which took place primarily
-in 2014, involved Russia, Ukraine, and NATO, and within a decade
-spiraled into a full scale invasion (herafter Crimea-Donbas). Both cases
-involve a superpower in crisis with a neighbor, initiated by a change
-from a friendly to hostile regime, with implications for economic and
-military security for the superpower, risked full scale invasion, and
-eventually invited intervention by opposing superpowers. We choose these
-cases because they are substantively significant to 20th and 21st
-century international relations, widely known across scientific
-disciplines and popular culture, and are sufficiently brief to evaluate
-in depth.
+Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in
+2014, involved Russia, Ukraine, and NATO, and within a decade spiraled
+into a full scale invasion (herafter Crimea-Donbas). Both cases involve
+a superpower in crisis with a neighbor, initiated by a change from a
+friendly to hostile regime, with implications for economic and military
+security for the superpower, risked full scale invasion, and eventually
+invited intervention by opposing superpowers. We choose these cases
+because they are substantively significant to 20th and 21st century
+international relations, widely known across scientific disciplines and
+popular culture, and are sufficiently brief to evaluate in depth.
 
@@
 proposal about what information is important, but we need an independent
-benchmark to evaluate whether that proposal is a good one and that
-allows for comparing proposals from event projects that had different
-goals. We need a yardstick for history.
+benchmark to evaluate whether that proposal is a good one that allows
+for comparing proposals from event projects that had different goals. We
+need a yardstick for history.
 
@@
 websites, and government documents. Using natural language processing
-(fully described in SI Appendix, Algorithm C1), we identify details that
-appear across multiple accounts. The more accounts that mention a
-detail, the more central it is to understanding the true historical
-episode. The theoretical motivation is that authors face word limits
-which force them to pick and choose which details to include, and they
-choose details which serve the specific context of the document they are
-producing. With a sufficiently large and diverse corpus of documents, we
-can vary the context while holding the overall episode constant and see
-which details tend to be invariant to context. Intuitively, a high
-quality event dataset should have high recall for context invariant
-details both because of their broader relevance and also because they
-are easier to find in source material.
+(fully described in SI Appendix 3.1), we identify details that appear
+across multiple accounts. The more accounts that mention a detail, the
+more central it is to understanding the true historical episode. The
+theoretical motivation is that authors face word limits which force them
+to pick and choose which details to include, and they choose details
+which serve the specific context of the document they are producing.
+With a sufficiently large and diverse corpus of documents, we can vary
+the context while holding the overall episode constant and see which
+details tend to be invariant to context. Intuitively, a high quality
+event dataset should have high recall for context invariant details both
+because of their broader relevance and also because they are easier to
+find in source material.
 
@@
 timeline, and provide crisis maps for every event dataset for each case
-study (SI Appendix, Fig. D3 and D4) and all crises on the companion
+study in SI Appendix 4.3 and 4.4 and for all crises on the companion
 website.
@@
 source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI
-Appendix Table D1), and for every case on the companion website. We
-further provide a stratified sample of event codings alongside their
-source text (SI Appendix Table D2).
+Appendix 4.1), and for every case on the companion website. We further
+provide a stratified sample of event codings alongside their source text
+(SI Appendix 4.2).
 
@@
   with a generic Entity token.} Labels reflect the individual leaves of
-the ontology and colors reflect the higher level coerce branch nodes of
+the ontology and colors reflect the higher level coarse branch nodes of
 the ontology. If ICBe has high precision, substantively similar tags
@@
 original ICB are too sparse and vague to reconstruct the structure of
-the crisis (SI Appendix Figure D3 and D4). On the other end of the
-spectrum, the high recall dictionary based event datasets like Terrier
-and ICEWs produce so many noisy events (several hundreds thousands) that
-even with heavy filtering their crisis maps are completely
-unintelligible. Further, because of copyright issues, none of these
-datasets directly provide the original text spans making event level
-precision difficult to verify.
+the crisis (SI Appendix 4.3 and 4.4). On the other end of the spectrum,
+the high recall dictionary based event datasets like Terrier and ICEWs
+produce so many noisy events (several hundreds thousands) that even with
+heavy filtering their crisis maps are completely unintelligible.
+Further, because of copyright issues, none of these datasets directly
+provide the original text spans making event level precision difficult
+to verify.
 
@@
 seriously the possibility that some functional transformation could
-recover the precision of ICBe. For example, (Terechshenko 2020) attempts
+recover the precision of ICBe. For example, Terechshenko (2020) attempts
 to correct for the mechanically increasing amount of news coverage each
@@
 e.g.~geolocation (Cook and Weidmann 2019), protest events (80\%) (Wüest
-and Lorenzini 2020), anti-government protest networks (46.1\%) (Jäger,
-n.d.).
+and Lorenzini 2020), anti-government protest networks (46.1\%) (Jäger
+2018).
 
@@
 \hypertarget{funding}{%
-\section{Funding \{}\label{funding}}
+\section{Funding}\label{funding}}
 
@@
 Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and
-Ruixuan Zhang. This project was supported by a grant from the Office of
-Naval Research {[}N00014-19-1-2491{]} and benefited from the Charles
-Koch Foundation's support for the Center for Peace and Security Studies.
+Ruixuan Zhang.
 
@@
 Allison, Graham T., and Philip Zelikow. 1971. \emph{Essence of Decision:
-{Explaining} the {Cuban} Missile Crisis}. Vol. 327. 729.1. {Little,
-Brown Boston}.
+{Explaining} the {Cuban} Missile Crisis}. Vol. 327. {Little, Brown
+Boston}.
 
@@
 Brecher. 2020. {``The {International Crisis Behavior Project}.''}
-{Oxford Research Encyclopedia of Politics}. September 28, 2020.
+\emph{Oxford Research Encyclopedia of Politics}.
+https://oxfordre.com/politics/view/10.1093/acrefore/9780190228637.001.0001/acrefore-9780190228637-e-1638.
 \url{https://doi.org/10.1093/acrefore/9780190228637.013.1638}.
@@
 Vincent Ng. 2018. {``Phoenix {Real-Time Event Data}.''}
-\url{http://eventdata.utdallas.edu}.
 
@@
 Codebook}.''} Codebook Version 12.
-\url{http://sites.duke.edu/icbdata/data-collections/}.
 
@@
 Domain Knowledge: Using Hierarchies to Improve Deep Classifiers.''}
-\url{http://arxiv.org/abs/1811.07125}.
+\emph{arXiv:1811.07125 {[}Cs{]}}, January.
+\url{https://arxiv.org/abs/1811.07125}.
 
@@
 {``The {Issue Correlates} of {War Territorial Claims Data},
-1816--20011.''} \emph{Journal of Peace Research} 54 (1): 99--108.
-\url{https://doi.org/10.1177/0022343316676311}.
+1816\textendash 20011.''} \emph{Journal of Peace Research} 54 (1):
+99--108. \url{https://doi.org/10.1177/0022343316676311}.
 
@@
 {Militarized Interstate Dispute Narratives}}. {Rowman \& Littlefield}.
-\url{https://books.google.com?id=_4VTDwAAQBAJ}.
 
@@
 Jabr. 2017. {``{OU Event Data Project},''} December.
-\url{https://osf.io/4m2u7/}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks}{}}%
-Jäger, Kai. n.d. {``The {Limits} of {Studying Networks} with {Event
-Data}: {Evidence} from the {ICEWS Dataset}.''}
+\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks2018}{}}%
+Jäger, Kai. 2018. {``The {Limits} of {Studying Networks} with {Event
+Data}: {Evidence} from the {ICEWS Dataset}.''} \emph{Journal of Global
+Security Studies} 3 (4): 498--511.
 
@@
 Guo, et al. 2021. {``A {Comprehensive Survey} on {Schema-based Event
-Extraction} with {Deep Learning}.''}
-\url{http://arxiv.org/abs/2107.02126}.
+Extraction} with {Deep Learning}.''} \emph{arXiv:2107.02126 {[}Cs{]}},
+August. \url{https://arxiv.org/abs/2107.02126}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
-Mandelbrot, Benoit B. 1983. \emph{The fractal geometry of nature}. {New
-York}: {Freeman}.
+Mandelbrot, Benoit B. 1983. \emph{{The fractal geometry of nature}}.
+{New York}: {Freeman}.
 
@@
 Mikaela Karstens, Chase Bloch, Nick Dietrich, Kayla Kahn, Kellan Ritter,
-and Michael J Soules. 2021. {``The {Mid5 Dataset}, 2011--2014:
+and Michael J Soules. 2021. {``The {Mid5 Dataset}, 2011\textendash 2014:
 {Procedures}, Coding Rules, and Description.''} \emph{Conflict
@@
 Pettersson, Therése, and Kristine Eck. 2018. {``Organized Violence,
-1989--2017.''} \emph{Journal of Peace Research} 55 (4): 535--47.
-\url{https://doi.org/10.1177/0022343318784101}.
+1989\textendash 2017.''} \emph{Journal of Peace Research} 55 (4):
+535--47. \url{https://doi.org/10.1177/0022343318784101}.
 
@@
 Reiter, Dan, Allan C. Stam, and Michael C. Horowitz. 2016. {``A {Revised
-Look} at {Interstate Wars}, 1816--2007.''} \emph{Journal of Conflict
-Resolution} 60 (5): 956--76.
+Look} at {Interstate Wars}, 1816\textendash 2007.''} \emph{Journal of
+Conflict Resolution} 60 (5): 956--76.
 \url{https://doi.org/10.1177/0022002714553107}.
@@
 Sechser, Todd S. 2011. {``Militarized {Compellent Threats},
-1918--2001.''} \emph{Conflict Management and Peace Science} 28 (4):
-377--401. \url{https://doi.org/10.1177/0738894211413066}.
+1918\textendash 2001.''} \emph{Conflict Management and Peace Science} 28
+(4): 377--401. \url{https://doi.org/10.1177/0738894211413066}.
 

### 2022-09-21 replication_paper/political_analysis_draft/appendix.tex
all the fixes

@@
 \usepackage{subcaption}
+\captionsetup[algorithm]{labelformat=empty}
+\captionsetup[figure]{labelformat=empty}
 \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
@@
 
-\hypertarget{appendix-a-corpus-and-cases}{%
-\section{Appendix A Corpus and
-Cases}\label{appendix-a-corpus-and-cases}}
+\hypertarget{corpus-and-cases}{%
+\section{Corpus and Cases}\label{corpus-and-cases}}
 
 \hypertarget{app:crises}{%
-\subsection{Table A1: ICBe Crises and Summary
-Information}\label{app:crises}}
+\subsection{ICBe Crises and Summary Information}\label{app:crises}}
 
@@
 \hypertarget{app:verbs}{%
-\subsection{Table A2: Verb Meanings (Glosses) found in the ICB Corpus
-(top 200)}\label{app:verbs}}
+\subsection{Verb Meanings (Glosses) found in the ICB Corpus (top
+200)}\label{app:verbs}}
 
@@
 
-\hypertarget{appendix-b-coding-process}{%
-\section{Appendix B: Coding Process}\label{appendix-b-coding-process}}
+\hypertarget{coding-process}{%
+\section{Coding Process}\label{coding-process}}
 
@@
 \hypertarget{app:gui}{%
-\subsection{Figure B1: Graphical User Interface}\label{app:gui}}
+\subsection{Graphical User Interface}\label{app:gui}}
 
@@
 \hypertarget{app:algo1}{%
-\subsection{Algorithm B2: Coding Aggregation and
-Filtering}\label{app:algo1}}
+\subsection{Coding Aggregation and Filtering}\label{app:algo1}}
 
@@
 \hypertarget{app:intercoderagreement}{%
-\subsection{Figure B3 : Intercoder
-Agreement}\label{app:intercoderagreement}}
+\subsection{Intercoder Agreement}\label{app:intercoderagreement}}
 
@@
 \hypertarget{app:agreement_by_confidence}{%
-\subsection{Figure B4 : Intercoder Agreement by
+\subsection{Intercoder Agreement by
 Confidence}\label{app:agreement_by_confidence}}
@@
 
-\hypertarget{appendix-c-recall}{%
-\section{Appendix C: Recall}\label{appendix-c-recall}}
-
-\hphantom{em}
-
-\hypertarget{algorithm-c1-synthetic-narratives}{%
-\subsection{Algorithm C1: Synthetic
-Narratives}\label{algorithm-c1-synthetic-narratives}}
+\hypertarget{recall}{%
+\section{Recall}\label{recall}}
+
+\hphantom{em}
+
+\hypertarget{synthetic-narratives}{%
+\subsection{Synthetic Narratives}\label{synthetic-narratives}}
 
@@
 
-\hypertarget{table-c2-synthetic-narrative-matches-cuban-missile}{%
-\subsection{Table C2: Synthetic Narrative Matches Cuban
-Missile}\label{table-c2-synthetic-narrative-matches-cuban-missile}}
+\hypertarget{synthetic-narrative-matches-cuban-missile}{%
+\subsection{Synthetic Narrative Matches Cuban
+Missile}\label{synthetic-narrative-matches-cuban-missile}}
 
@@
 
-\hypertarget{table-c3-synthetic-narrative-matches-crimea-donbas}{%
-\subsection{Table C3: Synthetic Narrative Matches
-Crimea-Donbas}\label{table-c3-synthetic-narrative-matches-crimea-donbas}}
+\hypertarget{synthetic-narrative-matches-crimea-donbas}{%
+\subsection{Synthetic Narrative Matches
+Crimea-Donbas}\label{synthetic-narrative-matches-crimea-donbas}}
 
@@
 
-\hypertarget{appendix-d-precision}{%
-\section{Appendix D: Precision}\label{appendix-d-precision}}
-
-\hypertarget{figure-d1-crimea-donbas}{%
-\subsection{Figure D1 Crimea-Donbas}\label{figure-d1-crimea-donbas}}
+\hypertarget{precision}{%
+\section{Precision}\label{precision}}
+
+\hypertarget{crimea-donbas-narrative}{%
+\subsection{Crimea-Donbas Narrative}\label{crimea-donbas-narrative}}
 
@@
 
-\hypertarget{table-d2-stratified-sentence-examples}{%
-\subsection{Table D2: Stratified Sentence
-Examples}\label{table-d2-stratified-sentence-examples}}
+\hypertarget{stratified-sentence-examples}{%
+\subsection{Stratified Sentence
+Examples}\label{stratified-sentence-examples}}
 
@@
 \end{figure}
-\clearpage
-
-\hypertarget{figure-d3-crisis-maps-cuban-missiles}{%
-\subsection{Figure D3 Crisis Maps Cuban
-Missiles}\label{figure-d3-crisis-maps-cuban-missiles}}
+
+\hypertarget{cuban-missiles-crisis-maps}{%
+\subsection{Cuban Missiles Crisis
+Maps}\label{cuban-missiles-crisis-maps}}
+
+\begin{figure}[H]
+\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
+\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
+\end{figure}
 
@@
 
-\hypertarget{figure-d4-crisis-maps-crimea-donbas}{%
-\subsection{Figure D4 Crisis Maps
-Crimea-Donbas}\label{figure-d4-crisis-maps-crimea-donbas}}
+\hypertarget{crimea-donbas-crisis-maps}{%
+\subsection{Crimea-Donbas Crisis Maps}\label{crimea-donbas-crisis-maps}}
 
@@
 Reimers, Nils, and Iryna Gurevych. 2019. {``Sentence-{BERT}: {Sentence
-Embeddings} Using {Siamese BERT-Networks}.''}
-\url{http://arxiv.org/abs/1908.10084}.
+Embeddings} Using {Siamese BERT-Networks}.''} \emph{arXiv:1908.10084
+{[}Cs{]}}, August. \url{https://arxiv.org/abs/1908.10084}.
 
@@
 ---------. 2020. {``Making {Monolingual Sentence Embeddings
-Multilingual} Using {Knowledge Distillation}.''}
-\url{http://arxiv.org/abs/2004.09813}.
+Multilingual} Using {Knowledge Distillation}.''} \emph{arXiv:2004.09813
+{[}Cs{]}}, October. \url{https://arxiv.org/abs/2004.09813}.
 
@@
 Shleifer, Sam, and Alexander M. Rush. 2020. {``Pre-Trained
-{Summarization Distillation}.''} \url{http://arxiv.org/abs/2010.13002}.
+{Summarization Distillation}.''} \emph{arXiv:2010.13002 {[}Cs{]}},
+October. \url{https://arxiv.org/abs/2010.13002}.
 

### 2022-09-23 replication_paper/political_analysis_draft/ICBe_online_supplemental_information.Rmd
lit review trims

--- 2022-09-14 replication_paper/political_analysis_draft/appendix.Rmd
@@
   - \usepackage{subcaption}
+  - \captionsetup[algorithm]{labelformat=empty}
+  - \captionsetup[figure]{labelformat=empty}
   - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
@@
 \clearpage
-# Appendix A Corpus and Cases
-## Table A1: ICBe Crises and Summary Information {#app:crises}
+# Corpus and Cases
+## ICBe Crises and Summary Information {#app:crises}
 
@@
 
-## Table A2: Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}
+## Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}
 \hphantom{em}
@@
 
-# Appendix B: Coding Process
+# Coding Process
 \hphantom{em}
 
-## Figure B1: Graphical User Interface {#app:gui}
+## Graphical User Interface {#app:gui}
 \hphantom{em}
@@
 
-## Algorithm B2: Coding Aggregation and Filtering {#app:algo1}
+## Coding Aggregation and Filtering {#app:algo1}
 \hphantom{em}
@@
 
-## Figure B3 : Intercoder Agreement {#app:intercoderagreement}
+## Intercoder Agreement {#app:intercoderagreement}
 \hphantom{em}
@@
 
-## Figure B4 : Intercoder Agreement by Confidence {#app:agreement_by_confidence}
+## Intercoder Agreement by Confidence {#app:agreement_by_confidence}
 \hphantom{em}
@@
 
-# Appendix C: Recall
+# Recall
 \hphantom{em}
 
-## Algorithm C1: Synthetic Narratives
+## Synthetic Narratives
 \hphantom{em}
@@
 
-## Table C2: Synthetic Narrative Matches Cuban Missile
+## Synthetic Narrative Matches Cuban Missile
 \hphantom{em}
@@
 
-## Table C3: Synthetic Narrative Matches Crimea-Donbas
+## Synthetic Narrative Matches Crimea-Donbas
 \hphantom{em}
@@
 
-# Appendix D: Precision
-## Figure D1 Crimea-Donbas 
+# Precision
+## Crimea-Donbas Narrative
 \hphantom{em}
@@
 
-## Table D2: Stratified Sentence Examples
+## Stratified Sentence Examples
 
@@
 \end{figure}
-\clearpage
-
-## Figure D3 Crisis Maps Cuban Missiles
+
+## Cuban Missiles Crisis Maps
 
@@
 \begin{figure}[H]
+\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
+\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
+\end{figure}
+
+\begin{figure}[H]
 \begin{adjustbox}{
@@
 
-## Figure D4 Crisis Maps Crimea-Donbas
+## Crimea-Donbas Crisis Maps
 

### 2022-09-23 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
lit review trims

@@
 output: rticles::arxiv_article
+
+nocite: |
+  @fazalStateDeathPolitics2011, @ryanNationStatesEmpiresWars2021, @spruytSovereignStateIts1996, @haffarEmergentPeacemakersCataloguing2002, @kuznetsovTheoryPracticeParadiplomacy2014,  @bushDensityDeclineFounding2019, @mcclearyPrivateVoluntaryOrganizations2008, @olterIntergovernmentalOrganizationsIGOs2021, @benyehudaEthnicActorsInternational2006, @buenodemesquitaDomesticExplanationsInternational2012, @lacinaExplainingSeverityCivil2006, @lacinaMonitoringTrendsGlobal2005, @carafanoMeasuringMilitaryPower2014, @goertzMeasuringMilitaryAllocations1986, @mcnabbcochranMeasuringMilitaryEffectiveness2017, @gartzkeCrossDomainDeterrenceStrategy2019, @lanoszkaLandpowerAmericanCredibility2016, @lindsayPoliticsManyOther2020, @carterStrategyTerritorialConflict2010, @luptonReexaminingReputationResolve2018, @goldgeierPsychologyInternationalRelations2001, @mercerProspectTheoryPolitical2005, @steinEvaluatingWarOutcomes1980, @sullivanWarAimsWar2007, @ramsayInformationUncertaintyWar2017, @yarhi-miloEyeBeholderHow2013, @oneillInternationalNegotiationConceptual2018, @tragerDiplomacyWarPeace2016, @zartmanEscalationNegotiationInternational2005, @davisThreatsPromisesPursuit2000, @sechserMilitarizedCompellentThreats2011, @powellBargainingTheoryInternational2002, @goemansIntroducingArchigosDataset2009, @harknessEthnicArmyState2016, @jonesHitMissEffect2009, @matanockElectingPeaceCivil2017, @powellGlobalInstancesCoups2011, @chenowethIntroducingNonviolentAction2019, @eckOneSidedViolenceCivilians2007, @lafreeIntroducingGlobalTerrorism2007, @beardsleyMediationDilemma2011, @giblerMeasuringAlliancesCorrelates2004, @owsiakInternationalBorderAgreements2018, @leedsAllianceReliabilityTimes2003, @leedsDomesticPoliticalInstitutions1999, @demesquitaForeignAidPolicy2007, @yarhi-miloArmAllyPatron2016, @laiEffectsDifferentTypes2004, @allenUSGlobalMilitary2021, @fortnaPeaceTime2018, @minInterstateWarBattle2021, @levyCausesWar2011, @reiterHowWarsEnd2009, @frederickIssueCorrelatesWar2017, @henselChartingCourseConflict1996
 
@@
   - \usepackage{changepage}
+#  - \renewenvironment{references}{}{}
+  - \renewcommand{\bibliography}[1]{} # removes the superflusous references section
+#  - \renewcommand{\bibliographystyle}[1]{} # might be an alternative to renewcommand bibliography
+#  - \renewenvironment{bibliography}{}{} # this drops the references but leaves an unnecessary paper. bib
 
@@
 lit_review_alt <- lit_review_pull %>% 
-                  mutate(Literature = paste0(" [",Literature %>% stringr::str_replace("; {0,}$","") ,"]")) %>%
-                  mutate(Concept= paste0("**", Concept, "**", Literature)) %>%
-                  mutate(Concept = Concept %>% stringr::str_replace(stringr::fixed("[NA]"),"") ) %>%
+                  mutate(Literature = paste0("",Literature %>% stringr::str_replace("; {0,}$","") ,"")) %>%
+                  mutate(Literature = paste0("",Literature %>% stringr::str_replace(";",",") ,"")) %>%
+                  #mutate(Literature = paste0("  [",Literature %>% stringr::str_replace("; {0,}$","") ,"]")) %>%
+                  #mutate(Concept= paste0("**", Concept, "**", Literature)) %>%
+                  mutate(Concept= paste0(Concept)) %>%
+                  mutate(Literature = Literature %>% stringr::str_replace_all(stringr::fixed("NA"),"") ) %>%
                   mutate(Concept = Concept %>% stringr::str_replace(stringr::fixed(" ["),stringr::fixed(" - ["))) %>%
-                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, -Literature, -`ICB Corpus`) 
+                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, Literature, -`ICB Corpus`, -`Removed Literature`) 
                   #dplyr::filter(is.na(group))
@@
       flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
       flextable::fontsize(size = 6.5, part = "all") %>%
@@
       flextable::rotate(i=1, j=2:k, rotation="tbrl", part="header") %>%
+      flextable::height(i=1, height=100, part="header") %>% 
+      flextable::padding(padding = 0, part = "body") %>%
       flextable::align(align = "center", part = "body") %>%
@@
       #set_table_properties(layout="autofit")  %>%
-      vline( i = 1, j = c(2,8), border = NULL, part = "header") %>%
+      vline( i = 1, j = c(3,8), border = NULL, part = "header") %>%
       vline( i = 1:(n), j = 1, border = NULL, part = "body")  %>%
-      vline( i = 1:(n), j = c(2,8), border = NULL, part = "body")  %>%
-
-      flextable::width( j = 2, width=3.1) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
-      flextable::width( j = (3):k, width=0.25) %>%
+      vline( i = 1:(n), j = c(3,8), border = NULL, part = "body")  %>%
+
+      flextable::bold(i = 1:k, j=2, bold = TRUE, part = "body") %>%
+
+      flextable::width(j = 1, width=0.1)  %>%
+      flextable::width( j = 2, width=2) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
+      flextable::width( j = 3, width=1.6) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
+      flextable::width( j = (4):k, width=0.22) %>%
       flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "all") %>%
-
+      flextable::padding(padding = 0, part = "body") %>%
       flextable::rotate(j=1, rotation="tbrl",part="all", align="center") %>%
       #flextable::rotate(j=2, rotation="tbrl",part="all") %>%
-      flextable::width(j = 1, width=0.1)  %>%
-      ftExtra::colformat_md(j = 2, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above
+      ftExtra::colformat_md(j = 3, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above
 

### 2022-09-23 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
lit review trims

@@
 \usepackage{changepage}
+\renewcommand{\bibliography}[1]{}
 \usepackage{multirow}
@@
 
-\begin{longtable}[c]{|p{0.10in}|p{3.10in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
+\begin{longtable}[c]{|p{0.10in}|p{2.00in}|p{1.60in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Type}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Episode}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Event)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Start}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Brecher}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hegre}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Iakhnis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{James}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sambanis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Kreutz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Weisiger}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{N}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Coders}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Hand}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Automated)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Corpus}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Date}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Article)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Location}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Actor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Event}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Actor}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{States}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Paul,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ikenberry,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hall}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Subnational}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Actors}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2002;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hsu}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{et}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{al.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McMillan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2008)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{IGO/NGO}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kim}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2008;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{mishaliram}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fatalities}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Force}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Size}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Carafano}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1986;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Force}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Domain}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Horowitz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunzeker}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Geography}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(location,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{territorial}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{change)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Carter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Alert}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Start/End}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Crisis)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Lupton}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Wishes}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Desire/Fear)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Goldgeier}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2001;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mercer}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Evaluation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Victory/Defeat)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Stein}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Russett}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aims}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Territory,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Policy,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Regime,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Preemption)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Sullivan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Awareness}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Discover,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Become}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Convinced)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Ramsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wirtz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2006;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{React}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{to}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{past}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Praise,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Disapprove,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Accept,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Reject,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Accuse)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(O’Neill}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Risse}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Trager}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Request}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{future}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Appeal,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Demand)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Zartman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Faure}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Predict}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{future}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{event}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Promise,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Threaten,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Express}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Intent,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Offer}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Without}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Condition)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Davis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2000;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Predict}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{with}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{condition}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Offer,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Ultimatum)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(R.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Government}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Leadership/Institution}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Change,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Coup,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Assasination)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Goemans,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Harkness}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Jones}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olken}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2009;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Matanock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{By}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Protest/Riot/Strike)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Chenoweth,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hendrix,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Against}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Terrorism,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Domestic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Rights,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mass}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Killing,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Evacuate)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Eck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hultman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{LaFree}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Dugan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Diplomacy}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Discussion,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Meeting,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mediation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Break}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{off}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{negotiations,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Withdraw/Expel}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Diplomats,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Propoganda)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Beardsley}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Legal}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreements}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Sign}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreement,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Settle}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Dispute,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Join}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{on}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Behalf}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{of,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Ally,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mutual}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Defense}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Pact,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Open}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Border,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cede}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Territory,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Allow}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Inspections,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Political}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Succession,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Leave}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Alliance,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Terminate}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Treaty)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Anac}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2005;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gibler}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2004;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Owsiak,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cuttner,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Buck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Violate}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreement}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Violate}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Terms}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{of}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Agreement)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2003/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mutual}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cooperation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Directed}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Economic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{cooperation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{or}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Military}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cooperation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Intelligence}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cooperation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Unspecified)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Directed}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(General}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Political}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Support,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Economic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Humanitarian}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Military}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Intelligence}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Unspecified}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Aid)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Preparation}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Alert,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Mobilization,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fortify,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Exercise,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Weapons}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Test)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Lai}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Maneuver}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Deployment,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Show}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{of}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Force,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Blockade,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{No}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fly}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Zone,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Border}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Violation)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Allen,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Flynn,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Martinez}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Machain}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Combat}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Battle/Clash,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Attack,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Invasion/Occupation,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Bombard,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Cease}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fire,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Retreat)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Fortna}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Min}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Strategic}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Declare}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Join}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Continue}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Fighting,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Surrender,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Withdraw}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{from}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{War,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Switch}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Sides)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Levy}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thompson}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2011;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Reiter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2009)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 3.1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Autonomy}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{(Assert}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Political}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Control}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Over,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Assert}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Autonomy}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Against,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Annex,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Reduce}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Control}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Over,}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{\ }}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Decolonize)}}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{-}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(Frederick,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1996;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Schultz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.25in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Type\ (Episode\ or\ Event)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Start}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{N}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Coders\ (Hand\ or\ Automated)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Corpus}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Date\ source\ (Event\ or\ Article)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Location\ source\ (Event\ or\ Actor)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{States}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Subnational\ Actors}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{IGO/NGO}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2008)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{mishaliram}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fatalities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Size}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Carafano}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1986)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Domain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunzeker}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Carter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lupton}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goldgeier}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2001)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mercer}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Stein}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Russett}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sullivan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ramsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{O’Neill}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Trager}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Zartman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Faure}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Davis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2000)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{R.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goemans,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Harkness}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Jones}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olken}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Matanock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chenoweth,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hendrix,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Eck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hultman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{LaFree}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Dugan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Beardsley}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gibler}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2004)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Owsiak,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cuttner,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Buck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2003/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lai}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Allen,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Flynn,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Martinez}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Machain}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fortna}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Min}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Levy}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thompson}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Reiter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Frederick,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-allenUSGlobalMilitary2021}{}}%
+Allen, Michael A, Michael E Flynn, and Carla Martinez Machain. 2021.
+{``{US} Global Military Deployments, 1950\textendash 2020*.''}
+\emph{Conflict Management and Peace Science}, July, 07388942211030885.
+\url{https://doi.org/10.1177/07388942211030885}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
@@
 16.
+
+\leavevmode\vadjust pre{\hypertarget{ref-beardsleyMediationDilemma2011}{}}%
+Beardsley, Kyle. 2011. \emph{The Mediation Dilemma}. {Cornell University
+Press}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-benyehudaEthnicActorsInternational2006}{}}%
+Ben-Yehuda, Hemda, and Meirav mishaliram. 2006. {``Ethnic {Actors} and
+{International Crises}: {Theory} and {Findings},
+1918\textendash 2001.''} \emph{International Interactions} 32 (1):
+49--78. \url{https://doi.org/10.1080/03050620600584435}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-buenodemesquitaDomesticExplanationsInternational2012}{}}%
+Bueno de Mesquita, Bruce, and Alastair Smith. 2012. {``Domestic
+{Explanations} of {International Relations}.''} \emph{Annual Review of
+Political Science} 15 (1): 161--81.
+\url{https://doi.org/10.1146/annurev-polisci-070209-174835}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bushDensityDeclineFounding2019}{}}%
+Bush, Sarah Sunn, and Jennifer Hadden. 2019. {``Density and {Decline} in
+the {Founding} of {International NGOs} in the {United States}.''}
+\emph{International Studies Quarterly} 63 (4): 1133--46.
+\url{https://doi.org/10.1093/isq/sqz061}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carafanoMeasuringMilitaryPower2014}{}}%
+Carafano, James Jay. 2014. {``Measuring {Military Power}.''}
+\emph{Strategic Studies Quarterly} 8 (3): 11--18.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carterStrategyTerritorialConflict2010}{}}%
+Carter, David B. 2010. {``The {Strategy} of {Territorial Conflict}.''}
+\emph{American Journal of Political Science} 54 (4): 969--87.
+\url{https://doi.org/10.1111/j.1540-5907.2010.00471.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chenowethIntroducingNonviolentAction2019}{}}%
+Chenoweth, Erica, Cullen S Hendrix, and Kyleanne Hunter. 2019.
+{``Introducing the {Nonviolent Action} in {Violent Contexts} ({NVAVC})
+Dataset.''} \emph{Journal of Peace Research} 56 (2): 295--305.
+\url{https://doi.org/10.1177/0022343318804855}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-davisThreatsPromisesPursuit2000}{}}%
+Davis, James W. 2000. \emph{Threats and {Promises}: {The Pursuit} of
+{International Influence}}. {JHU Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-demesquitaForeignAidPolicy2007}{}}%
+de Mesquita, Bruce Bueno, and Alastair Smith. 2007. {``Foreign {Aid} and
+{Policy Concessions}.''} \emph{Journal of Conflict Resolution} 51 (2):
+251--84. \url{https://doi.org/10.1177/0022002706297696}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eckOneSidedViolenceCivilians2007}{}}%
+Eck, Kristine, and Lisa Hultman. 2007. {``One-{Sided Violence Against
+Civilians} in {War}: {Insights} from {New Fatality Data}.''}
+\emph{Journal of Peace Research} 44 (2): 233--46.
+\url{https://doi.org/10.1177/0022343307075124}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fazalStateDeathPolitics2011}{}}%
+Fazal, Tanisha M. 2011. \emph{State {Death}: {The Politics} and
+{Geography} of {Conquest}, {Occupation}, and {Annexation}}. \emph{State
+Death}. {Princeton University Press}.
+\url{https://doi.org/10.1515/9781400841448}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-fortnaPeaceTime2018}{}}%
+Fortna, Virginia Page. 2018. \emph{Peace Time}. {Princeton University
+Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gartzkeCrossDomainDeterrenceStrategy2019}{}}%
+Gartzke, Erik, and Jon R. Lindsay. 2019. \emph{Cross-{Domain
+Deterrence}: {Strategy} in an {Era} of {Complexity}}. {Oxford University
+Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-giblerMeasuringAlliancesCorrelates2004}{}}%
+Gibler, Douglas M., and Meredith Reid Sarkees. 2004. {``Measuring
+{Alliances}: The {Correlates} of {War Formal Interstate Alliance}
+{Dataset}, 1816\textendash 2000.''} \emph{Journal of Peace Research} 41
+(2): 211--22. \url{https://doi.org/10.1177/0022343304041061}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goemansIntroducingArchigosDataset2009}{}}%
+Goemans, Henk E., Kristian Skrede Gleditsch, and Giacomo Chiozza. 2009.
+{``Introducing {Archigos}: {A} Dataset of Political Leaders.''}
+\emph{Journal of Peace Research} 46 (2): 269--83.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goertzMeasuringMilitaryAllocations1986}{}}%
+Goertz, Gary, and Paul F. Diehl. 1986. {``Measuring {Military
+Allocations}: {A Comparison} of {Different Approaches}.''} \emph{Journal
+of Conflict Resolution} 30 (3): 553--81.
+\url{https://doi.org/10.1177/0022002786030003009}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldgeierPsychologyInternationalRelations2001}{}}%
+Goldgeier, J. M., and P. E. Tetlock. 2001. {``Psychology and
+{International Relations Theory}.''} \emph{Annual Review of Political
+Science} 4 (1): 67--92.
+\url{https://doi.org/10.1146/annurev.polisci.4.1.67}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-haffarEmergentPeacemakersCataloguing2002}{}}%
+Haffar, Warren. 2002. {``Emergent {Peacemakers}: {Cataloguing New
+Patterns} of {Activity} in {Post-Cold War Conflict}.''} \emph{Peace
+Economics, Peace Science and Public Policy} 8 (2).
+\url{https://doi.org/10.2202/1554-8597.1054}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
@@
 Syntax} and {Semantics}.''}
+
+\leavevmode\vadjust pre{\hypertarget{ref-harknessEthnicArmyState2016}{}}%
+Harkness, Kristen A. 2016. {``The Ethnic Army and the State:
+{Explaining} Coup Traps and the Difficulties of Democratization in
+{Africa}.''} \emph{Journal of Conflict Resolution} 60 (4): 587--616.
 
@@
 Politics} 7 (3): 2053168020935257.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henselChartingCourseConflict1996}{}}%
+Hensel, Paul R. 1996. {``Charting {A Course To Conflict}: {Territorial
+Issues} and {Interstate Conflict}, 1816-1992.''} \emph{Conflict
+Management and Peace Science} 15 (1): 43--73.
+\url{https://doi.org/10.1177/073889429601500103}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-jonesHitMissEffect2009}{}}%
+Jones, Benjamin F., and Benjamin A. Olken. 2009. {``Hit or {Miss}? {The
+Effect} of {Assassinations} on {Institutions} and {War}.''}
+\emph{American Economic Journal: Macroeconomics} 1 (2): 55--87.
+\url{https://doi.org/10.1257/mac.1.2.55}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
@@
 \url{https://doi.org/10.1177/0022002719857796}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kuznetsovTheoryPracticeParadiplomacy2014}{}}%
+Kuznetsov, Alexander. 2014. \emph{Theory and {Practice} of
+{Paradiplomacy}: {Subnational Governments} in {International Affairs}}.
+{London}: {Routledge}. \url{https://doi.org/10.4324/9781315817088}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lacinaExplainingSeverityCivil2006}{}}%
+Lacina, Bethany. 2006. {``Explaining the {Severity} of {Civil Wars}.''}
+\emph{Journal of Conflict Resolution} 50 (2): 276--89.
+\url{https://doi.org/10.1177/0022002705284828}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lacinaMonitoringTrendsGlobal2005}{}}%
+Lacina, Bethany, and Nils Petter Gleditsch. 2005. {``Monitoring {Trends}
+in {Global Combat}: {A New Dataset} of {Battle Deaths}.''}
+\emph{European Journal of Population / Revue Européenne de Démographie}
+21 (2): 145--66. \url{https://doi.org/10.1007/s10680-005-6851-6}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lafreeIntroducingGlobalTerrorism2007}{}}%
+LaFree, Gary, and Laura Dugan. 2007. {``Introducing the Global Terrorism
+Database.''} \emph{Terrorism and Political Violence} 19 (2): 181--204.
+
+\leavevmode\vadjust pre{\hypertarget{ref-laiEffectsDifferentTypes2004}{}}%
+Lai, Brian. 2004. {``The Effects of Different Types of Military
+Mobilization on the Outcome of International Crises.''} \emph{Journal of
+Conflict Resolution} 48 (2): 211--29.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lanoszkaLandpowerAmericanCredibility2016}{}}%
+Lanoszka, Alexander, and Michael A. Hunzeker. 2016. {``Landpower and
+{American} Credibility.''} \emph{Parameters: The United States Army's
+Senior Professional Journal} 45 (4): 17--26.
+
+\leavevmode\vadjust pre{\hypertarget{ref-leedsAllianceReliabilityTimes2003}{}}%
+Leeds, Brett Ashley. 2003/ed. {``Alliance {Reliability} in {Times} of
+{War}: {Explaining State Decisions} to {Violate Treaties}.''}
+\emph{International Organization} 57 (4): 801--27.
+\url{https://doi.org/10.1017/S0020818303574057}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-leedsDomesticPoliticalInstitutions1999}{}}%
+---------. 1999. {``Domestic {Political Institutions}, {Credible
+Commitments}, and {International Cooperation}.''} \emph{American Journal
+of Political Science} 43 (4): 979--1002.
+\url{https://doi.org/10.2307/2991814}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-levyCausesWar2011}{}}%
+Levy, Jack S., and William R. Thompson. 2011. \emph{Causes of War}.
+{John Wiley \& Sons}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
@@
 August. \url{https://arxiv.org/abs/2107.02126}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lindsayPoliticsManyOther2020}{}}%
+Lindsay, Jon R., and Erik Gartzke. 2020. {``Politics by Many Other
+Means: {The} Comparative Strategic Advantages of Operational Domains.''}
+\emph{Journal of Strategic Studies} 0 (0): 1--34.
+\url{https://doi.org/10.1080/01402390.2020.1768372}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-luptonReexaminingReputationResolve2018}{}}%
+Lupton, Danielle L. 2018. {``Reexamining {Reputation} for {Resolve}:
+{Leaders}, {States}, and the {Onset} of {International Crises}.''}
+\emph{Journal of Global Security Studies} 3 (2): 198--216.
+\url{https://doi.org/10.1093/jogss/ogy004}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-matanockElectingPeaceCivil2017}{}}%
+Matanock, Aila M. 2017. \emph{Electing {Peace}: {From Civil Conflict} to
+{Political Participation}}. {Cambridge}: {Cambridge University Press}.
+\url{https://doi.org/10.1017/9781316987179}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcclearyPrivateVoluntaryOrganizations2008}{}}%
+McCleary, Rachel M., and Robert J. Barro. 2008. {``Private {Voluntary
+Organizations Engaged} in {International Assistance}, 1939-2004.''}
+\emph{Nonprofit and Voluntary Sector Quarterly} 37 (3): 512--36.
+\url{https://doi.org/10.1177/0899764007313719}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
@@
 1966-1978.''} \emph{WEIS Codebook ICPSR} 5211.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcnabbcochranMeasuringMilitaryEffectiveness2017}{}}%
+McNabb Cochran, Kathryn, and Stephen B. Long. 2017. {``Measuring
+{Military Effectiveness}: {Calculating Casualty Loss-Exchange Ratios}
+for {Multilateral Wars}, 1816\textendash 1990.''} \emph{International
+Interactions} 43 (6): 1019--40.
+\url{https://doi.org/10.1080/03050629.2017.1273914}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mercerProspectTheoryPolitical2005}{}}%
+Mercer, Jonathan. 2005. {``Prospect {Theory} and {Political Science}.''}
+\emph{Annual Review of Political Science} 8 (1): 1--21.
+\url{https://doi.org/10.1146/annurev.polisci.8.082103.104911}.
 
@@
 \url{https://doi.org/10.1145/219717.219748}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-minInterstateWarBattle2021}{}}%
+Min, Eric. 2021. {``Interstate {War Battle} Dataset
+(1823\textendash 2003).''} \emph{Journal of Peace Research} 58 (2):
+294--303. \url{https://doi.org/10.1177/0022343320913305}.
 
@@
 \url{https://doi.org/10.1177/0022343320929740}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-oneillInternationalNegotiationConceptual2018}{}}%
+O'Neill, Barry. 2018. {``International {Negotiation}: {Some Conceptual
+Developments}.''} \emph{Annual Review of Political Science} 21 (1):
+515--33. \url{https://doi.org/10.1146/annurev-polisci-031416-092909}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-olterIntergovernmentalOrganizationsIGOs2021}{}}%
+Olter, Agnieszka. 2021. {``Intergovernmental Organizations ({IGOs}) as
+Relevant Actors in {International Relations}.''} \emph{Repositorio
+Institucional - Ulima}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-powellGlobalInstancesCoups2011}{}}%
+Powell, Jonathan M, and Clayton L Thyne. 2011. {``Global Instances of
+Coups from 1950 to 2010: {A} New Dataset.''} \emph{Journal of Peace
+Research} 48 (2): 249--59.
+\url{https://doi.org/10.1177/0022343310397436}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-powellBargainingTheoryInternational2002}{}}%
+Powell, Robert. 2002. {``Bargaining {Theory} and {International
+Conflict}.''} \emph{Annual Review of Political Science} 5 (1): 1--30.
+\url{https://doi.org/10.1146/annurev.polisci.5.092601.141138}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ramsayInformationUncertaintyWar2017}{}}%
+Ramsay, Kristopher W. 2017. {``Information, {Uncertainty}, and {War}.''}
+\emph{Annual Review of Political Science} 20 (1): 505--27.
+\url{https://doi.org/10.1146/annurev-polisci-051215-022729}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-reiterHowWarsEnd2009}{}}%
+Reiter, Dan. 2009. \emph{How Wars End}. {Princeton University Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
-Reiter, Dan. 2015. {``Should {We Leave Behind} the {Subfield} of
+---------. 2015. {``Should {We Leave Behind} the {Subfield} of
 {International Relations}?''} \emph{Annual Review of Political Science}
@@
 \url{https://doi.org/10.1177/0022002714553107}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ryanNationStatesEmpiresWars2021}{}}%
+Ryan, Cheyney. 2021. {``Nation-{States}, {Empires}, {Wars},
+{Hostilities}.''} \emph{Ethics \& International Affairs} 35 (3):
+367--79.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-spruytSovereignStateIts1996}{}}%
+Spruyt, Hendrik. 1996. \emph{The {Sovereign State} and {Its
+Competitors}: {An Analysis} of {Systems Change}}. {Princeton University
+Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-steinEvaluatingWarOutcomes1980}{}}%
+Stein, Arthur A., and Bruce M. Russett. 1980. {``Evaluating War:
+{Outcomes} and Consequences.''} In \emph{Handbook of Political Conflict:
+Theory and Research}, 399--422. {Free Press New York}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-sullivanWarAimsWar2007}{}}%
+Sullivan, Patricia L. 2007. {``War {Aims} and {War Outcomes}: {Why
+Powerful States Lose Limited Wars}.''} \emph{Journal of Conflict
+Resolution} 51 (3): 496--524.
+\url{https://doi.org/10.1177/0022002707300187}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
@@
 764--76. \url{https://doi.org/10.1177/0022343320962546}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tragerDiplomacyWarPeace2016}{}}%
+Trager, Robert F. 2016. {``The {Diplomacy} of {War} and {Peace}.''}
+\emph{Annual Review of Political Science} 19 (1): 205--28.
+\url{https://doi.org/10.1146/annurev-polisci-051214-100534}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-yarhi-miloEyeBeholderHow2013}{}}%
+Yarhi-Milo, Keren. 2013. {``In the {Eye} of the {Beholder}: {How
+Leaders} and {Intelligence Communities Assess} the {Intentions} of
+{Adversaries}.''} \emph{International Security} 38 (1): 7--51.
+\url{https://doi.org/10.1162/ISEC_a_00128}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-yarhi-miloArmAllyPatron2016}{}}%
+Yarhi-Milo, Keren, Alexander Lanoszka, and Zack Cooper. 2016. {``To
+{Arm} or to {Ally}? {The Patron}'s {Dilemma} and the {Strategic Logic}
+of {Arms Transfers} and {Alliances}.''} \emph{International Security} 41
+(2): 90--139. \url{https://doi.org/10.1162/ISEC_a_00250}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zartmanEscalationNegotiationInternational2005}{}}%
+Zartman, I. William, and Guy Olivier Faure. 2005. \emph{Escalation and
+Negotiation in International Conflicts}. {Cambridge University Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%

### 2022-09-28 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
Sept 28 edits

@@
 We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+We make the data, supplementary appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
 
@@
 \begin{figure}[H]
-\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
+\caption{Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
 \centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
@@
 
-      flextable::bold(i = 1:k, j=2, bold = TRUE, part = "body") %>%
+      # flextable::bold(i = 1:n, j=2, bold = TRUE, part = "body") %>%
 
@@
 We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to be low for 20% of sentences- half due to a mismatch between the ontology and the text ("survey doesn't fit event"-45%) and half due to a lack of information or confused writing in the source text ("more knowledge needed"-40%, "confusing sentence"-6%).
+First, we required coders to rate and justify their confidence in the coding.
+They reported low confidence for 20% of sentences; 45% of those were due to a mismatch between the ontology and the text ("survey doesn't fit event") and 46% were from a lack of information or confused writing in the source text (40% "more knowledge needed", 6% "confusing sentence").
 Observed disagreement varied predictably with self reported confidence (SI Appendix 2.4).
@@
                   zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
 ```
@@
 
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
+p_196_icbe <- icbe_crisismaps(thiscrisis=196) +
     labs(
@@
       theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
+  scale_x_continuous(expand = expansion(mult = c(0.06, 0.05))) +
    scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
@@
 \caption{Crisis Map: Cuban Missile Crisis \label{fig:p_196_icbe}}
-\centering{\includegraphics[width=17cm]{./p_196_icbe.png}}
+\centering{\includegraphics[width=16cm]{./p_196_icbe.png}}
 \end{figure}
@@
 The dendrogram shows hiearchical clustering of the tags.
-If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable.
+If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.
 }
@@
 ========================================
-This article’s data, online appendix, replication material, and visualizations of every historical episode are available on the github repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.
+This article’s data, supplementary appendix, replication material, and visualizations of every historical episode are available on the github repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.
 
@@
 ========================================
-\vspace{0pt}

### 2022-09-28 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
Sept 28 edits

@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Type\ (Episode\ or\ Event)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Start}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{N}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Coders\ (Hand\ or\ Automated)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Corpus}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Date\ source\ (Event\ or\ Article)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Location\ source\ (Event\ or\ Actor)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Start}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{End}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{States}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Subnational\ Actors}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{IGO/NGO}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2008)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Civilians}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{mishaliram}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{States}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Subnational\ Actors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2008)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Civilians}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{mishaliram}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2003/ed)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 We attribute the remaining disagreement primarily to three sources.
-First, we required coders to rate their confidence which was observed to
-be low for 20\% of sentences- half due to a mismatch between the
-ontology and the text (``survey doesn't fit event''-45\%) and half due
-to a lack of information or confused writing in the source text (``more
-knowledge needed''-40\%, ``confusing sentence''-6\%). Observed
-disagreement varied predictably with self reported confidence (SI
-Appendix 2.4). Second, as intended, agreement is higher (75-80\%) for
-questions with fewer options near the root of the ontology compared to
-agreement for questions near the leafs of the ontology (50\%-60\%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.~some
-more expressive applying many tags per concept while others focused on
-only the single best match. We further observed unintended synonymity,
-e.g.~the same information can be framed as either a threat to do
-something or a promise not to do something.
+First, we required coders to rate and justify their confidence in the
+coding. They reported low confidence for 20\% of sentences; 45\% of
+those were due to a mismatch between the ontology and the text (``survey
+doesn't fit event'') and 46\% were from a lack of information or
+confused writing in the source text (40\% ``more knowledge needed'', 6\%
+``confusing sentence''). Observed disagreement varied predictably with
+self reported confidence (SI Appendix 2.4). Second, as intended,
+agreement is higher (75-80\%) for questions with fewer options near the
+root of the ontology compared to agreement for questions near the leafs
+of the ontology (50\%-60\%). Third, individual coders exhibiting
+nontrivial coding styles, e.g.~some more expressive applying many tags
+per concept while others focused on only the single best match. We
+further observed unintended synonymity, e.g.~the same information can be
+framed as either a threat to do something or a promise not to do
+something.
 
@@
 \hypertarget{works-cited}{%
-\section{Works Cited}\label{works-cited}}
-
-\vspace{0pt}
+\section*{Works Cited}\label{works-cited}}
+\addcontentsline{toc}{section}{Works Cited}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-leedsDomesticPoliticalInstitutions1999}{}}%
+Leeds, Brett Ashley. 1999. {``Domestic {Political Institutions},
+{Credible Commitments}, and {International Cooperation}.''}
+\emph{American Journal of Political Science} 43 (4): 979--1002.
+\url{https://doi.org/10.2307/2991814}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-leedsAllianceReliabilityTimes2003}{}}%
-Leeds, Brett Ashley. 2003/ed. {``Alliance {Reliability} in {Times} of
-{War}: {Explaining State Decisions} to {Violate Treaties}.''}
+---------. 2003. {``Alliance {Reliability} in {Times} of {War}:
+{Explaining State Decisions} to {Violate Treaties}.''}
 \emph{International Organization} 57 (4): 801--27.
 \url{https://doi.org/10.1017/S0020818303574057}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-leedsDomesticPoliticalInstitutions1999}{}}%
----------. 1999. {``Domestic {Political Institutions}, {Credible
-Commitments}, and {International Cooperation}.''} \emph{American Journal
-of Political Science} 43 (4): 979--1002.
-\url{https://doi.org/10.2307/2991814}.
 

### 2022-09-29 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
spell-check

@@
   How do international crises unfold?
-We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
+We conceptualize international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history.
 We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project.
-We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014).
-We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision.
+We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and the Crimea-Donbas Crisis (2014).
+We further introduce two new event visualizations (event iconography and crisis maps), an automated benchmark for measuring event recall using natural language processing (synthetic narratives), and an ontology reconstruction task for objectively measuring event precision.
 We make the data, supplementary appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
@@
 If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
-On event-extraction from images and social-media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
+On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
 
@@
 We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
-We conclude by benchmarking our event codings against several current state-of-the-art event data collection efforts.
+We conclude by benchmarking our event codings against several current state of the art event data collection efforts.
 We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
@@
 
-This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large scale set of measurements, those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
+This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large-scale set of measurements, and those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
 The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision.
@@
 
-We consider the measurement task of abstracting discrete events about a historical episode in international relations.
+We consider the measurement task of absstracting discrete events about a historical episode in international relations.
 The easiest way to convey the task is with an example.
-Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine readable abstractive events.
+Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine-readable abstractive events.
 Formally, a historical episode, $H$, is demarcated by a period of time $[T_{start}, T_{end}] \in T$, a set of Players $p \in P$, and a set of behaviors they undertook during that time $b \in B$.
@@
               ICB = "Natural Language Sentences (ICB Corpus)",
-              ICBe = "Machine Readable Events (ICBe)"
+              ICBe = "Machine-Readable Events (ICBe)"
              ) ) %>%
@@
 
-Next we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
+Next, we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
 We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
@@
 We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations to alongside each concept.
+The first is the extensive existing measurement efforts of IR which we provide citations alongside each concept.
 Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
+Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number of hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
 
 The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Additional relevant but dated or too small of an overlap in domain include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
-With the exception of large scale CAMEO dictionary based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See [@balaliCOfEEComprehensiveOntology2021] for a recent review of ontological depth and availability of Gold Standard example text.]
+They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Other datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See [@balaliCOfEEComprehensiveOntology2021] for a recent review of ontological depth and availability of Gold Standard example text.]
 
@@
 Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information was always collected while other details were only collected if appropriate, e.g.
+Some additional details like location and timing information were always collected while other details were only collected if appropriate, e.g.
 force size, fatalities, domains, units, etc.
@@
 They reported low confidence for 20% of sentences; 45% of those were due to a mismatch between the ontology and the text ("survey doesn't fit event") and 46% were from a lack of information or confused writing in the source text (40% "more knowledge needed", 6% "confusing sentence").
-Observed disagreement varied predictably with self reported confidence (SI Appendix 2.4).
-Second, as intended, agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leafs of the ontology (50%-60%).
-Third, individual coders exhibiting nontrivial coding styles, e.g.
-some more expressive applying many tags per concept while others focused on only the single best match.
+Observed disagreement varied predictably with self-reported confidence (SI Appendix 2.4).
+Second, as intended, agreement is higher (75-80%) for questions with fewer options near the root of the ontology compared to agreement for questions near the leaves of the ontology (50%-60%).
+Third, individual coders exhibit nontrivial coding styles, e.g.
+some more expressive coders applied many tags per concept while others focused on only the single best match.
 We further observed unintended synonymity, e.g.
@@
 The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read icongraphic form, and a wide range of visualizations for every case on the companion website.
+We provide full ICB narratives, ICBe coding in an easy-to-read iconographic form, and a wide range of visualizations for every case on the companion website.
 In this paper, we focus on two deep case studies.
 The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full scale invasion (herafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to hostile regime, with implications for economic and military security for the superpower, risked full scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
+The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion (hereafter Crimea-Donbas).
+Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to a hostile regime, with implications for economic and military security for the superpower, risked full-scale invasion, and eventually invited intervention by opposing superpowers.
+We choose these cases because they are substantively significant to 20th and 21st-century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
 
@@
 Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in the more detail you will find about individual events and in between every two discrete events.
-The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one that allows for comparing proposals from event projects that had different goals.
+History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in, the more detail you will find about individual events and in between every two discrete events.
+The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
 We need a yardstick for history.
@@
 The more accounts that mention a detail, the more central it is to understanding the true historical episode.
-The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details which serve the specific context of the document they are producing.
+The theoretical motivation is that authors face word limits which force them to pick and choose which details to include, and they choose details that serve the specific context of the document they are producing.
 With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
-Intuitively, a high quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
+Intuitively, a high-quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
 
 Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail which appeared in at least five documents along with an approximate start date, a hand written summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
+Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
 
@@
 First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives included 17/51 and 23/30 of the events from the synthetic narrative, while including other details that are not in the synthetic narrative.
-Second, mentions of a detail across accounts is exponentially distributed with context invariant details appearing dozens to hundreds of times more than context dependent details.
-Third, crisis start and stop dates are arbitrary and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
+Our ground truth ICB narratives contain 17/51 and 23/30 of the events from the synthetic narrative and include other details that are not in the synthetic narrative.
+Second, mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.
+Third, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
 the U.S.
-was in a \textit{de facto} grey scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
+was in a \textit{de facto} grey-scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
 a long term lease on naval facilities in Crimea.
 Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missile also includes high level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
+Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease-fire agreement (Minsk II) but continued fighting.
+The canonical narrative of Cuban Missiles also includes high-level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
 
@@
 The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode level datasets have very low coverage of contextual details.
+The two episode-level datasets have very low coverage of contextual details.
 The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
@@
 
-      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbass (2014)"), colwidths = c(kleft, 1,kright) ) %>%
+      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbas (2014)"), colwidths = c(kleft, 1,kright) ) %>%
 
@@
 It does little good to recall a historical event but too vaguely (e.g.
-MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
+MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
 ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move.
+ICBe's ontology and coding system are designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
+You should be able to lay out the events of a crisis on a timeline, as in Figure 3, and read off the macrostructure of an episode from each individual move.
 We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study in SI Appendix 4.3 and 4.4 and for all crises on the companion website.
@@
 We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix 4.1), and for every case on the companion website.
+We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix 4.1), and for every case on the companion website.
 We further provide a stratified sample of event codings alongside their source text (SI Appendix 4.2).
 
-We find both the visualizations of macro structure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall we seek a more objective detached universal benchmark.
+We find both the visualizations of macrostructure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall, we seek a more objective detached universal benchmark.
 Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embeded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
+Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
 If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]
@@
 Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis-maps reveal the episode level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
-On the other end of the spectrum, the high recall dictionary based event datasets like Terrier and ICEWs produce so many noisy events (several hundreds thousands) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event level precision difficult to verify.
-
-However, given their high recall on our task and the global and real-time coverage of dictionary based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human coded baseline.
+The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
+On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
+Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
+
+However, given their high recall on our task and the global and real-time coverage of dictionary-based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
+For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human-coded baseline.
 Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
@@
 
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real world event.
+We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
 We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych for even after he was removed from power because of articles retroactively discussing the cause of his of his removal.
+The start of the crisis revolves around Ukraine backing out of a trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
+The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych even after he was removed from power because of articles retroactively discussing the cause of his removal.
 Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
-Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constantly as the news coverage does not distinguish between subtle changes or additions.
-In sum, dictionary based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason their specificity for most event types is too low to back out individual chess like sequencing that ICBe aims to record.
+Likewise, "impose embargo, boycott, or sanctions" captures the start of waves of sanctions and from who but are effectively constant as the news coverage does not distinguish between subtle changes or additions.
+In sum, dictionary-based methods on news corpora tend to have high recall because they parse everything in the news, but for the same reason, their specificity for most event types is too low to back out individual chess-like sequencing that ICBe aims to record.
 
@@
 \centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
+\textit{Notes: Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
 Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that tag was applied to by the coders.
-The dendrogram shows hiearchical clustering of the tags.
+Label placement is the median of all of the sentences that the tag was applied to by the coders.
+The dendrogram shows hierarchical clustering of the tags.
 If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.
@@
 \centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
-\textit{Notes:Unit of analysis is the Dyad-Day.
+\textit{Notes: The unit of analysis is the Dyad-Day.
 Top 10 most active dyads per category shown.
@@
 These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
+escalation and de-escalation of conflicts).^[Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
@@
 Thanks to the Center for Peace and Security Studies and its membership for comments.
-Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback.
+Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for their generous feedback.
 Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
@@
 ========================================
-This article’s data, supplementary appendix, replication material, and visualizations of every historical episode are available on the github repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.
+This article’s data, supplementary appendix, replication material, and visualizations of every historical episode are available on the GitHub repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.
 

### 2022-09-29 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
spell-check

@@
 \begin{abstract}
-How do international crises unfold? We conceptualize of international
+How do international crises unfold? We conceptualize international
 relations as a strategic chess game between adversaries and develop a
@@
 precision than existing state of the art datasets and conduct two
-detailed case studies of the Cuban Missile Crisis (1962) and
+detailed case studies of the Cuban Missile Crisis (1962) and the
 Crimea-Donbas Crisis (2014). We further introduce two new event
-visualizations (event icongraphy and crisis maps), an automated
+visualizations (event iconography and crisis maps), an automated
 benchmark for measuring event recall using natural language processing
-(sythnetic narratives), and an ontology reconstruction task for
-objectively measuring event precision. We make the data, online
+(synthetic narratives), and an ontology reconstruction task for
+objectively measuring event precision. We make the data, supplementary
 appendix, replication material, and visualizations of every historical
@@
   Halterman (2020); Brandt et al. (2018); Boschee et al. (2015); Hegre
-  et al. (2020); Grant et al. (2017). On event-extraction from images
-  and social-media see Zhang and Pan (2019) and Steinert-Threlkeld
+  et al. (2020); Grant et al. (2017). On event extraction from images
+  and social media see Zhang and Pan (2019) and Steinert-Threlkeld
   (2019).} How close these efforts are to accurately measuring all or
@@
 narrative. We conclude by benchmarking our event codings against several
-current state-of-the-art event data collection efforts. We find that
+current state of the art event data collection efforts. We find that
 existing systems produce sequences of events that do not contain enough
@@
 relations, we propose a method for systematically measuring it, we
-successfully apply this method producing a new large scale set of
-measurements, those measurements exhibit several desirable kinds of
+successfully apply this method producing a new large-scale set of
+measurements, and those measurements exhibit several desirable kinds of
 internal and external validity, and those measurements out-perform other
@@
 
-We consider the measurement task of abstracting discrete events about a
+We consider the measurement task of absstracting discrete events about a
 historical episode in international relations. The easiest way to convey
@@
 Cuban Missile Crisis (1962) alongside a mapping from each natural
-language sentence to discrete machine readable abstractive events.
+language sentence to discrete machine-readable abstractive events.
 Formally, a historical episode, \(H\), is demarcated by a period of time
@@
 
-Next we draw informative prior beliefs about the underlying process of
+Next, we draw informative prior beliefs about the underlying process of
 IR that we expect to govern behavior during historical episodes and
@@
 first is the extensive existing measurement efforts of IR which we
-provide citations to alongside each concept. Second, we performed
+provide citations alongside each concept. Second, we performed
 preliminary natural language processing of the corpus and identified
@@
 to the most likely definition found in Wordnet (Miller 1995), tallied,
-and then aggregated into a smaller number hypernyms balancing conceptual
-detail and manageable sparsity for human coding (SI Appendix 1.2).
+and then aggregated into a smaller number of hypernyms balancing
+conceptual detail and manageable sparsity for human coding (SI Appendix
+1.2).
 
@@
 coverage. They begin with our contribution ICBe, alongside other
-event-level datasets including CAMEO dictionary lookup based systems
+event-level datasets including CAMEO dictionary lookup-based systems
 (Historical Phoenix (Althaus et al. 2019); ICEWS (Boschee et al. 2015;
@@
 Sundberg and Mihai Croicu 2016; Pettersson and Eck 2018; Sundberg and
-Melander 2013).\footnote{Additional relevant but dated or too small of
-  an overlap in domain include BCOW (Leng and Singer 1988), WEIS
+Melander 2013).\footnote{Other datasets that insufficiently overlap
+  ICBe's domain for comparison include BCOW (Leng and Singer 1988), WEIS
   (McClelland 1978), CREON (Hermann 1984), CASCON (Bloomfield and
@@
 (Palmer et al. 2021; Gibler 2018; Braithwaite 2010, 2009), and the
-Correlates of War (Sarkees and Wayman 2010). With the exception of large
-scale CAMEO dictionary based systems, the existing state of the art
-quantitative datasets ignore the vast majority of the information
+Correlates of War (Sarkees and Wayman 2010). With the exception of
+large-scale CAMEO dictionary-based systems, the existing state of the
+art quantitative datasets ignore the vast majority of the information
 content found in international relations.\footnote{See (Balali,
@@
 finally one or more non-mutually exclusive specific activities. Some
-additional details like location and timing information was always
+additional details like location and timing information were always
 collected while other details were only collected if appropriate,
@@
 ``confusing sentence''). Observed disagreement varied predictably with
-self reported confidence (SI Appendix 2.4). Second, as intended,
+self-reported confidence (SI Appendix 2.4). Second, as intended,
 agreement is higher (75-80\%) for questions with fewer options near the
-root of the ontology compared to agreement for questions near the leafs
-of the ontology (50\%-60\%). Third, individual coders exhibiting
-nontrivial coding styles, e.g.~some more expressive applying many tags
-per concept while others focused on only the single best match. We
-further observed unintended synonymity, e.g.~the same information can be
-framed as either a threat to do something or a promise not to do
-something.
+root of the ontology compared to agreement for questions near the leaves
+of the ontology (50\%-60\%). Third, individual coders exhibit nontrivial
+coding styles, e.g.~some more expressive coders applied many tags per
+concept while others focused on only the single best match. We further
+observed unintended synonymity, e.g.~the same information can be framed
+as either a threat to do something or a promise not to do something.
 
@@
 of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy to read
-icongraphic form, and a wide range of visualizations for every case on
+We provide full ICB narratives, ICBe coding in an easy-to-read
+iconographic form, and a wide range of visualizations for every case on
 the companion website. In this paper, we focus on two deep case studies.
@@
 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled
-into a full scale invasion (herafter Crimea-Donbas). Both cases involve
+into a full-scale invasion (hereafter Crimea-Donbas). Both cases involve
 a superpower in crisis with a neighbor, initiated by a change from a
-friendly to hostile regime, with implications for economic and military
-security for the superpower, risked full scale invasion, and eventually
-invited intervention by opposing superpowers. We choose these cases
-because they are substantively significant to 20th and 21st century
-international relations, widely known across scientific disciplines and
-popular culture, and are sufficiently brief to evaluate in depth.
+friendly to a hostile regime, with implications for economic and
+military security for the superpower, risked full-scale invasion, and
+eventually invited intervention by opposing superpowers. We choose these
+cases because they are substantively significant to 20th and
+21st-century international relations, widely known across scientific
+disciplines and popular culture, and are sufficiently brief to evaluate
+in depth.
 
@@
 (Mandelbrot 1983) --- it has a fractal dimension greater than one such
-that the more you zoom in the more detail you will find about individual
-events and in between every two discrete events. The ICBe ontology is a
-proposal about what information is important, but we need an independent
-benchmark to evaluate whether that proposal is a good one that allows
-for comparing proposals from event projects that had different goals. We
-need a yardstick for history.
+that the more you zoom in, the more detail you will find about
+individual events and in between every two discrete events. The ICBe
+ontology is a proposal about what information is important, but we need
+an independent benchmark to evaluate whether that proposal is a good one
+and that allows for comparing proposals from event projects that had
+different goals. We need a yardstick for history.
 
@@
 to pick and choose which details to include, and they choose details
-which serve the specific context of the document they are producing.
-With a sufficiently large and diverse corpus of documents, we can vary
-the context while holding the overall episode constant and see which
-details tend to be invariant to context. Intuitively, a high quality
-event dataset should have high recall for context invariant details both
+that serve the specific context of the document they are producing. With
+a sufficiently large and diverse corpus of documents, we can vary the
+context while holding the overall episode constant and see which details
+tend to be invariant to context. Intuitively, a high-quality event
+dataset should have high recall for context invariant details both
 because of their broader relevance and also because they are easier to
@@
 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents)
-appear in Figure 2. Each row represents a detail which appeared in at
-least five documents along with an approximate start date, a hand
-written summary, the number of documents it was mentioned in, and
-whether it could be identified in the text of our ICB corpus, in our
-ICBe events, or any of the competing systems.
+appear in Figure 2. Each row represents a detail that appeared in at
+least five documents along with an approximate start date, a handwritten
+summary, the number of documents it was mentioned in, and whether it
+could be identified in the text of our ICB corpus, in our ICBe events,
+or any of the competing systems.
 
@@
 variation in which details any one document will choose to include. Our
-ground truth ICB narratives included 17/51 and 23/30 of the events from
-the synthetic narrative, while including other details that are not in
-the synthetic narrative. Second, mentions of a detail across accounts is
-exponentially distributed with context invariant details appearing
-dozens to hundreds of times more than context dependent details. Third,
-crisis start and stop dates are arbitrary and the historical record
+ground truth ICB narratives contain 17/51 and 23/30 of the events from
+the synthetic narrative and include other details that are not in the
+synthetic narrative. Second, mentions of a detail across accounts are
+exponentially distributed with context-invariant details appearing
+dozens to hundreds of times more than context-dependent details. Third,
+crisis start and stop dates are arbitrary, and the historical record
 points to many precursor events as necessary detail for understanding
-later events, e.g.~the U.S. was in a \textit{de facto} grey scale war
+later events, e.g.~the U.S. was in a \textit{de facto} grey-scale war
 with Cuba before it invited Soviet military protection (Cormac and
@@
 Missiles has a cleaner canonical end with the Soviets agreeing to
-withdraw missiles while Crimea-Donbas meekly ends with a second cease
-fire agreement (Minsk II) but continued fighting. The canonical
-narrative of Cuban Missile also includes high level previously
+withdraw missiles while Crimea-Donbas meekly ends with a second
+cease-fire agreement (Minsk II) but continued fighting. The canonical
+narrative of Cuban Missiles also includes high-level previously
 classified details, while the more recent Crimea-Donbas case reflects
@@
 which is so noisy that it's flat to decreasing in mentions. The two
-episode level datasets have very low coverage of contextual details. The
+episode-level datasets have very low coverage of contextual details. The
 two other dictionary systems ICEWs and Terrier have high coverage, with
@@
 history, \(Pr(H|E)\). It does little good to recall a historical event
-but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a
+but too vaguely (e.g.~MIDs describes the Cuban Missile Crisis as a
 blockade, a show of force, and a stalemate) or with too much error
@@
 1995-2019) to be useful for downstream applications. ICBe's ontology and
-coding system is designed to strike a balance so that the most important
-information is recovered accurately but also abstracted to a level that
-is still useful and interpretable. You should be able to lay out events
-of a crisis on a timeline, as in Figure 3, and read off the macro
-structure of an episode from each individual move. We call this
+coding system are designed to strike a balance so that the most
+important information is recovered accurately but also abstracted to a
+level that is still useful and interpretable. You should be able to lay
+out the events of a crisis on a timeline, as in Figure 3, and read off
+the macrostructure of an episode from each individual move. We call this
 visualization a crisis map, a directed graph intersected with a
@@
 coherent statements that can be compared side by side to the original
-source narrative as for Cuban Missiles (Figure 1), Crimea-Donbas (SI
+source narrative for Cuban Missiles (Figure 1), Crimea-Donbas (SI
 Appendix 4.1), and for every case on the companion website. We further
@@
 
-We find both the visualizations of macro structure and head-to-head
+We find both the visualizations of macrostructure and head-to-head
 comparisons of ICBe codings to the raw text to strongly support the
-quality of ICBe, but as with recall we seek a more objective detached
+quality of ICBe, but as with recall, we seek a more objective detached
 universal benchmark. Our proposed measure is a reconstruction task to
@@
 shows the location of every sentence from the ICBe corpus in semantic
-space as embeded using the same large language model as before, and the
+space as embedded using the same large language model as before, and the
 median location of each ICBe event tag applied to those
@@
 Finally, how does ICBe's precision compare to the existing state of the
-art? The crisis-maps reveal the episode level datasets like MIDs or the
+art? The crisis maps reveal the episode-level datasets like MIDs or the
 original ICB are too sparse and vague to reconstruct the structure of
 the crisis (SI Appendix 4.3 and 4.4). On the other end of the spectrum,
-the high recall dictionary based event datasets like Terrier and ICEWs
-produce so many noisy events (several hundreds thousands) that even with
+the high recall dictionary-based event datasets like Terrier and ICEWs
+produce so many noisy events (several hundred thousand) that even with
 heavy filtering their crisis maps are completely unintelligible.
 Further, because of copyright issues, none of these datasets directly
-provide the original text spans making event level precision difficult
+provide the original text spans making event-level precision difficult
 to verify.
@@
 However, given their high recall on our task and the global and
-real-time coverage of dictionary based event systems, we want to take
+real-time coverage of dictionary-based event systems, we want to take
 seriously the possibility that some functional transformation could
@@
 to correct for the mechanically increasing amount of news coverage each
-year by detrending violent event counts from Phoenix using a human coded
+year by detrending violent event counts from Phoenix using a human-coded
 baseline. Others have focused on verifying precision for ICEWs on
@@
 We take the same approach here in Figure 5, selecting four specific
-CAMEO event codings and checking how often they reflect a true real
-world event. We choose four event types around key moments in the
-crisis. The start of the crisis revolves around Ukraine backing out of
-trade deal with the EU in favor of Russia, but ``sign formal agreement''
-events act more like a topic detector with dozens of events generated by
-discussions of a possible agreement but not the actual agreement which
-never materialized. The switch is caught by the ``reject plan, agreement
-to settle dispute'', but also continues for Victor Yanukovych for even
-after he was removed from power because of articles retroactively
-discussing the cause of his of his removal. Events for ``use
-conventional military force'' capture a threshold around the start of
-hostilities and who the participants were but not any particular battles
-or campaigns. Likewise, ``impose embargo, boycott, or sanctions''
-captures the start of waves of sanctions and from who but are
-effectively constantly as the news coverage does not distinguish between
-subtle changes or additions. In sum, dictionary based methods on news
-corpora tend to have high recall because they parse everything in the
-news, but for the same reason their specificity for most event types is
-too low to back out individual chess like sequencing that ICBe aims to
-record.
+CAMEO event codings and checking how often they reflect a true
+real-world event from the Crimea-Donbas synthetic narrative. We choose
+four event types around key moments in the crisis. The start of the
+crisis revolves around Ukraine backing out of a trade deal with the EU
+in favor of Russia, but ``sign formal agreement'' events act more like a
+topic detector with dozens of events generated by discussions of a
+possible agreement but not the actual agreement which never
+materialized. The switch is caught by the ``reject plan, agreement to
+settle dispute'', but also continues for Victor Yanukovych even after he
+was removed from power because of articles retroactively discussing the
+cause of his removal. Events for ``use conventional military force''
+capture a threshold around the start of hostilities and who the
+participants were but not any particular battles or campaigns. Likewise,
+``impose embargo, boycott, or sanctions'' captures the start of waves of
+sanctions and from who but are effectively constant as the news coverage
+does not distinguish between subtle changes or additions. In sum,
+dictionary-based methods on news corpora tend to have high recall
+because they parse everything in the news, but for the same reason,
+their specificity for most event types is too low to back out individual
+chess-like sequencing that ICBe aims to record.
 
@@
 appropriate for statistical analysis of hard questions about the
-sequencing of events (e.g.~escalation and de-escalation of conflicts).
-Second, we provide a coder-level disaggregation with multiple codings of
-each sentence by experts and undergrads that allows for the introduction
-of uncertainty and human interpretation of events. Further, we release a
-direct mapping from the codings to the source text at the sentence level
-as a new resource for natural language processing. Finally, we provide a
-companion website that incorporates detailed visualizations of all of
-the data introduced here (www.crisisevents.org).
+sequencing of events (e.g.~escalation and de-escalation of
+conflicts).\footnote{Using ICBe data Gannon (2022) finds that
+  cross-domain crises are shorter and less violent than same-domain
+  crises.} Second, we provide a coder-level disaggregation with multiple
+codings of each sentence by experts and undergrads that allows for the
+introduction of uncertainty and human interpretation of events. Further,
+we release a direct mapping from the codings to the source text at the
+sentence level as a new resource for natural language processing.
+Finally, we provide a companion website that incorporates detailed
+visualizations of all of the data introduced here
+(www.crisisevents.org).
 
@@
 membership for comments. Special thanks to Rebecca Cordell, Philip
-Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for
+Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for their
 generous feedback. Thank you to the cPASS research assistants that
@@
 
-This article's data, online appendix, replication material, and
-visualizations of every historical episode are available on the github
+This article's data, supplementary appendix, replication material, and
+visualizations of every historical episode are available on the GitHub
 repository
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gannonOneIfLand2022}{}}%
+Gannon, J Andrés. 2022. {``One If by {Land}, and {Two} If by {Sea}:
+{Cross-Domain Contests} and the {Escalation} of {International
+Crises}.''} \emph{International Studies Quarterly} 66 (4): sqac065.
+\url{https://doi.org/10.1093/isq/sqac065}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-gartzkeCrossDomainDeterrenceStrategy2019}{}}%

### 2022-09-29 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
small edit

@@
 The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Other datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
-With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See [@balaliCOfEEComprehensiveOntology2021] for a recent review of ontological depth and availability of Gold Standard example text.]
+They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.]
 

### 2022-09-29 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
small edit

@@
 Sundberg and Mihai Croicu 2016; Pettersson and Eck 2018; Sundberg and
-Melander 2013).\footnote{Other datasets that insufficiently overlap
-  ICBe's domain for comparison include BCOW (Leng and Singer 1988), WEIS
-  (McClelland 1978), CREON (Hermann 1984), CASCON (Bloomfield and
-  Moulton 1989), SHERFACS (Sherman 2000), Real-Time Phoenix (Brandt et
-  al. 2018), and COfEE (Balali, Asadpour, and Jafari 2021) (see
-  histories in Merritt (1994) and Schrodt and Hall (2006)).} The final
-set of columns compares episode-level datasets beginning with the
-original ICB project (Brecher et al., n.d.; Brecher and Wilkenfeld 1982;
-Beardsley et al. 2020); the Militarized Interstate Disputes dataset
-(Palmer et al. 2021; Gibler 2018; Braithwaite 2010, 2009), and the
-Correlates of War (Sarkees and Wayman 2010). With the exception of
+Melander 2013).\footnote{Other related datasets that insufficiently
+  overlap ICBe's domain for comparison include BCOW (Leng and Singer
+  1988), WEIS (McClelland 1978), CREON (Hermann 1984), CASCON
+  (Bloomfield and Moulton 1989), SHERFACS (Sherman 2000), Real-Time
+  Phoenix (Brandt et al. 2018), and COfEE (Balali, Asadpour, and Jafari
+  2021) (see histories in Merritt (1994) and Schrodt and Hall (2006)).}
+The final set of columns compares episode-level datasets beginning with
+the original ICB project (Brecher et al., n.d.; Brecher and Wilkenfeld
+1982; Beardsley et al. 2020); the Militarized Interstate Disputes
+dataset (Palmer et al. 2021; Gibler 2018; Braithwaite 2010, 2009), and
+the Correlates of War (Sarkees and Wayman 2010). With the exception of
 large-scale CAMEO dictionary-based systems, the existing state of the

### 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
trim down

@@
 nocite: |
-  @fazalStateDeathPolitics2011, @ryanNationStatesEmpiresWars2021, @spruytSovereignStateIts1996, @haffarEmergentPeacemakersCataloguing2002, @kuznetsovTheoryPracticeParadiplomacy2014,  @bushDensityDeclineFounding2019, @mcclearyPrivateVoluntaryOrganizations2008, @olterIntergovernmentalOrganizationsIGOs2021, @benyehudaEthnicActorsInternational2006, @buenodemesquitaDomesticExplanationsInternational2012, @lacinaExplainingSeverityCivil2006, @lacinaMonitoringTrendsGlobal2005, @carafanoMeasuringMilitaryPower2014, @goertzMeasuringMilitaryAllocations1986, @mcnabbcochranMeasuringMilitaryEffectiveness2017, @gartzkeCrossDomainDeterrenceStrategy2019, @lanoszkaLandpowerAmericanCredibility2016, @lindsayPoliticsManyOther2020, @carterStrategyTerritorialConflict2010, @luptonReexaminingReputationResolve2018, @goldgeierPsychologyInternationalRelations2001, @mercerProspectTheoryPolitical2005, @steinEvaluatingWarOutcomes1980, @sullivanWarAimsWar2007, @ramsayInformationUncertaintyWar2017, @yarhi-miloEyeBeholderHow2013, @oneillInternationalNegotiationConceptual2018, @tragerDiplomacyWarPeace2016, @zartmanEscalationNegotiationInternational2005, @davisThreatsPromisesPursuit2000, @sechserMilitarizedCompellentThreats2011, @powellBargainingTheoryInternational2002, @goemansIntroducingArchigosDataset2009, @harknessEthnicArmyState2016, @jonesHitMissEffect2009, @matanockElectingPeaceCivil2017, @powellGlobalInstancesCoups2011, @chenowethIntroducingNonviolentAction2019, @eckOneSidedViolenceCivilians2007, @lafreeIntroducingGlobalTerrorism2007, @beardsleyMediationDilemma2011, @giblerMeasuringAlliancesCorrelates2004, @owsiakInternationalBorderAgreements2018, @leedsAllianceReliabilityTimes2003, @leedsDomesticPoliticalInstitutions1999, @demesquitaForeignAidPolicy2007, @yarhi-miloArmAllyPatron2016, @laiEffectsDifferentTypes2004, @allenUSGlobalMilitary2021, @fortnaPeaceTime2018, @minInterstateWarBattle2021, @levyCausesWar2011, @reiterHowWarsEnd2009, @frederickIssueCorrelatesWar2017, @henselChartingCourseConflict1996
+  @fazalStateDeathPolitics2011, @spruytSovereignStateIts1996, @haffarEmergentPeacemakersCataloguing2002, @bushDensityDeclineFounding2019, @benyehudaEthnicActorsInternational2006, @lacinaExplainingSeverityCivil2006; @mcnabbcochranMeasuringMilitaryEffectiveness2017, @carafanoMeasuringMilitaryPower2014, @goertzMeasuringMilitaryAllocations1986, @gartzkeCrossDomainDeterrenceStrategy2019, @lindsayPoliticsManyOther2020, @carterStrategyTerritorialConflict2010, @goldgeierPsychologyInternationalRelations2001, @steinEvaluatingWarOutcomes1980, @sullivanWarAimsWar2007, @ramsayInformationUncertaintyWar2017, @yarhi-miloEyeBeholderHow2013, @oneillInternationalNegotiationConceptual2018, @zartmanEscalationNegotiationInternational2005, @sechserMilitarizedCompellentThreats2011, @powellBargainingTheoryInternational2002, @goemansIntroducingArchigosDataset2009, @powellGlobalInstancesCoups2011, @chenowethIntroducingNonviolentAction2019, @eckOneSidedViolenceCivilians2007, @lafreeIntroducingGlobalTerrorism2007, @beardsleyMediationDilemma2011, @giblerMeasuringAlliancesCorrelates2004, @owsiakInternationalBorderAgreements2018, @leedsAllianceReliabilityTimes2003, @leedsDomesticPoliticalInstitutions1999, @yarhi-miloArmAllyPatron2016, @laiEffectsDifferentTypes2004, @allenUSGlobalMilitary2021, @fortnaPeaceTime2018, @minInterstateWarBattle2021, @frederickIssueCorrelatesWar2017, @sarkeesResortWar181620072010, @reiterRevisedLookInterstate2016
 
@@
 This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018; @maozDyadicMilitarizedInterstate2019], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], trade [@barariDemocracyTradePolicy], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018; @vabulasCooperationAutonomyBuilding2021], dispute resolution [@vabulasCooperationAutonomyBuilding2021; @frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @liComprehensiveSurveySchemabased2021; @haltermanExtractingPoliticalEvents2020; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017.
+If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @liComprehensiveSurveySchemabased2021; @beielerGeneratingPoliticalEvent2016; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015.
 On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
+
+<!-- removedcites trade @barariDemocracyTradePolicy,  @vabulasCooperationAutonomyBuilding2021 -->
+<!-- removedcites @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019, @vabulasCooperationAutonomyBuilding2021;  -->
 
@@
 We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherCrisisEscalationWar2000; @wilkenfeldInterstateCrisesViolence2000; @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019].
+We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherEscalationWarTwentieth2000; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
 The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
@@
 
+<!-- removedcites  @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019 -->
+
 This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large-scale set of measurements, and those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
@@
 
-We consider the measurement task of absstracting discrete events about a historical episode in international relations.
+We consider the measurement task of abstracting discrete events about a historical episode in international relations.
 The easiest way to convey the task is with an example.
@@
 
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p.
+For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
+Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].
+Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
 59].
@@
 The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
+
+<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
 
@@
 The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018;@braithwaiteMIDLOCIntroducingMilitarized2010;@braithwaiteCodebookMilitarizedInterstate2009], and the Correlates of War [@sarkeesResortWar181620072010].
+They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
 With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.]
+
+<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; -->
 
@@
                   mutate(Literature = paste0("",Literature %>% stringr::str_replace("; {0,}$","") ,"")) %>%
-                  mutate(Literature = paste0("",Literature %>% stringr::str_replace(";",",") ,"")) %>%
+                  mutate(Literature = paste0("",Literature %>% stringr::str_replace_all(";",",") ,"")) %>%
                   #mutate(Literature = paste0("  [",Literature %>% stringr::str_replace("; {0,}$","") ,"]")) %>%
@@
                   mutate(Concept = Concept %>% stringr::str_replace(stringr::fixed(" ["),stringr::fixed(" - ["))) %>%
-                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, Literature, -`ICB Corpus`, -`Removed Literature`) 
+                  dplyr::select(-Codebook, -`Cameo Codes`, -`ICB Codes`, Literature, -`ICB Corpus`, -`Removed Literature`) # %>% 
+                  # dplyr::rename(`Illustrative Literature` = Literature)
                   #dplyr::filter(is.na(group))
@@
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here (www.crisisevents.org).
+Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here at www.crisisevents.org.
 

### 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
trim down

@@
   Wilkenfeld 1982; Beardsley et al. 2020), militarized disputes (Palmer
-  et al. 2021; Gibler 2018; Maoz et al. 2019), wars (Sarkees and Wayman
-  2010; Reiter, Stam, and Horowitz 2016), organized violence (Ralph
-  Sundberg and Mihai Croicu 2016; Pettersson and Eck 2018), political
-  violence (Raleigh et al. 2010), sanctions (Felbermayr et al. 2020),
-  trade (Barari and Kim, n.d.), and international agreements (Kinne
-  2020; Owsiak, Cuttner, and Buck 2018; Vabulas and Snidal 2021),
-  dispute resolution (Vabulas and Snidal 2021; Frederick, Hensel, and
-  Macaulay 2017), and diplomacy (Moyer, Turner, and Meisel 2020; Sechser
-  2011).} Thanks to improvements in natural language processing, more
-open-ended efforts have begun to capture entire unstructured streams of
-events from international news reports.\footnote{See Li et al. (2021);
-  Halterman (2020); Brandt et al. (2018); Boschee et al. (2015); Hegre
-  et al. (2020); Grant et al. (2017). On event extraction from images
-  and social media see Zhang and Pan (2019) and Steinert-Threlkeld
-  (2019).} How close these efforts are to accurately measuring all or
-even most of what is essential in international relations is an open
-empirical question, one for which we provide new evidence here.
+  et al. 2021; Gibler 2018), wars (Sarkees and Wayman 2010; Reiter,
+  Stam, and Horowitz 2016), organized violence (Ralph Sundberg and Mihai
+  Croicu 2016; Pettersson and Eck 2018), political violence (Raleigh et
+  al. 2010), sanctions (Felbermayr et al. 2020), and international
+  agreements (Kinne 2020; Owsiak, Cuttner, and Buck 2018), dispute
+  resolution (Frederick, Hensel, and Macaulay 2017), and diplomacy
+  (Moyer, Turner, and Meisel 2020; Sechser 2011).} Thanks to
+improvements in natural language processing, more open-ended efforts
+have begun to capture entire unstructured streams of events from
+international news reports.\footnote{See Li et al. (2021); Beieler et
+  al. (2016); Brandt et al. (2018); Boschee et al. (2015). On event
+  extraction from images and social media see Zhang and Pan (2019) and
+  Steinert-Threlkeld (2019).} How close these efforts are to accurately
+measuring all or even most of what is essential in international
+relations is an open empirical question, one for which we provide new
+evidence here.
 
@@
 narratives of international crises (Brecher 1999; Brecher, James, and
-Wilkenfeld 2000; Wilkenfeld and Brecher 2000; James 2019; Iakhnis and
-James 2019). The result is a new lower bound estimate of how much
-actually happens between states during pivotal historical episodes. We
-then develop several methods for objectively gauging how well these
-event codings reconstruct the information contained in the original
-narrative. We conclude by benchmarking our event codings against several
-current state of the art event data collection efforts. We find that
-existing systems produce sequences of events that do not contain enough
-information to reconstruct the underlying historical episode. The
-underlying fine-grained variation in international affairs is
-unrecognizable through the lens of current quantification efforts.
+Wilkenfeld 2000; Wilkenfeld and Brecher 2000; Brecher et al. 2021). The
+result is a new lower bound estimate of how much actually happens
+between states during pivotal historical episodes. We then develop
+several methods for objectively gauging how well these event codings
+reconstruct the information contained in the original narrative. We
+conclude by benchmarking our event codings against several current state
+of the art event data collection efforts. We find that existing systems
+produce sequences of events that do not contain enough information to
+reconstruct the underlying historical episode. The underlying
+fine-grained variation in international affairs is unrecognizable
+through the lens of current quantification efforts.
 
@@
 
-We consider the measurement task of absstracting discrete events about a
+We consider the measurement task of abstracting discrete events about a
 historical episode in international relations. The easiest way to convey
@@
 project (\(n=471\))(Supplementary Information (SI) Appendix 1.1)(Brecher
-et al. 2017; Brecher and Wilkenfeld 1997). Their domain is 20th and
+et al. 2021; Brecher and Wilkenfeld 1997). Their domain is 20th and
 21st-century crises, defined as a change in the type, or an increase in
@@
 challenges the structure of the international system (Brecher and
-Wilkenfeld 1982).\footnote{On near crises see Iakhnis and James (2019).}
-Crises are a significant focus of detailed single case studies and case
-comparisons because they provide an opportunity to examine behaviors in
-IR short of, or at least prior to, full conflict (Holsti 1965; Paige
-1968; Allison and Zelikow 1971; Snyder and Diesing 1977; Gavin 2014;
-George and Smoke 1974; Brecher and Wilkenfeld 1982; Gaddis 1987; Brecher
-and James 1988). Case selection was exhaustive based on a survey of
-world news archives and region experts, cross-checked against other
-databases of war and conflict, and non-English sources (Kang and Lin
-2019; Brecher et al. 2017, 59). Each narrative was written by consensus
-by a small number of scholars, using a uniform coding scheme, with
-similar specificity (Hewitt 2001). The corpus is unique in IR because it
-is designed to be used in a downstream quantitative coding project.
+Wilkenfeld 1982). Crises are a significant focus of detailed single case
+studies and case comparisons because they provide an opportunity to
+examine behaviors in IR short of, or at least prior to, full conflict
+(Holsti 1965; Paige 1968; Allison and Zelikow 1971; Gavin 2014; Brecher
+and Wilkenfeld 1982; Iakhnis and James 2019). Case selection was
+exhaustive based on a survey of world news archives and region experts,
+cross-checked against other databases of war and conflict, and
+non-English sources (Kang and Lin 2019; Brecher et al. 2021, 59). Each
+narrative was written by consensus by a small number of scholars, using
+a uniform coding scheme, with similar specificity (Hewitt 2001). The
+corpus is unique in IR because it is designed to be used in a downstream
+quantitative coding project.
 
@@
 The final set of columns compares episode-level datasets beginning with
-the original ICB project (Brecher et al., n.d.; Brecher and Wilkenfeld
+the original ICB project (Brecher et al. 2021; Brecher and Wilkenfeld
 1982; Beardsley et al. 2020); the Militarized Interstate Disputes
-dataset (Palmer et al. 2021; Gibler 2018; Braithwaite 2010, 2009), and
-the Correlates of War (Sarkees and Wayman 2010). With the exception of
-large-scale CAMEO dictionary-based systems, the existing state of the
-art quantitative datasets ignore the vast majority of the information
-content found in international relations.\footnote{See (Balali,
-  Asadpour, and Jafari 2021) for a recent review of ontological depth
-  and availability of Gold Standard example text.}
+dataset (Palmer et al. 2021; Gibler 2018), and the Correlates of War
+(Sarkees and Wayman 2010). With the exception of large-scale CAMEO
+dictionary-based systems, the existing state of the art quantitative
+datasets ignore the vast majority of the information content found in
+international relations.\footnote{See Balali, Asadpour, and Jafari
+  (2021) for a recent review of ontological depth and availability of
+  Gold Standard example text.}
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{States}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ryan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Subnational\ Actors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Kuznetsov}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McCleary}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Barro}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2008)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Civilians}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{mishaliram}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bueno}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2012)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{States}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Subnational\ Actors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Civilians}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{MishaliRam}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fatalities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Size}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Carafano}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1986)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Domain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunzeker}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fatalities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Size}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Carafano}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Domain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lupton}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goldgeier}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2001)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mercer}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Brecher}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wilkenfeld}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goldgeier}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{O’Neill}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Trager}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{O’Neill}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Davis}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2000)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goemans,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Harkness}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Jones}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Olken}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Matanock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{;}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goemans,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{de}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mesquita}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Smith}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Levy}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thompson}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Reiter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Frederick,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wayman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2010)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Reiter,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Stam,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Horowitz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Frederick,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
 
@@
 Finally, we provide a companion website that incorporates detailed
-visualizations of all of the data introduced here
-(www.crisisevents.org).
+visualizations of all of the data introduced here at
+www.crisisevents.org.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-barariDemocracyTradePolicy}{}}%
-Barari, Soubhik, and In Song Kim. n.d. {``Democracy and {Trade Policy}
-at the {Product Level}: {Evidence} from a {New Tariff-line Dataset},''}
-16.
-
 \leavevmode\vadjust pre{\hypertarget{ref-beardsleyMediationDilemma2011}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-beielerGeneratingPoliticalEvent2016}{}}%
+Beieler, John, Patrick T. Brandt, Andrew Halterman, Philip A. Schrodt,
+Erin M. Simpson, and R. Michael Alvarez. 2016. {``Generating Political
+Event Data in Near Real Time.''} In \emph{Computational Social Science},
+98. {Cambridge University Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-benyehudaEthnicActorsInternational2006}{}}%
-Ben-Yehuda, Hemda, and Meirav mishaliram. 2006. {``Ethnic {Actors} and
+Ben-Yehuda, Hemda, and Meirav MishaliRam. 2006. {``Ethnic {Actors} and
 {International Crises}: {Theory} and {Findings},
@@
 Data.''} \emph{Harvard Dataverse} 12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteCodebookMilitarizedInterstate2009}{}}%
-Braithwaite, Alex. 2009. {``Codebook for the {Militarized Interstate
-Dispute Location} ({MIDLOC}) {Data}, v 1.0.''} \emph{University College
-London}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-braithwaiteMIDLOCIntroducingMilitarized2010}{}}%
----------. 2010. {``{MIDLOC}: {Introducing} the {Militarized Interstate
-Dispute Location} Dataset.''} \emph{Journal of Peace Research} 47 (1):
-91--98. \url{https://doi.org/10.1177/0022343309350008}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brecherPatternsCrisisManagement1988}{}}%
-Brecher, Michael, and Patrick James. 1988. {``Patterns of Crisis
-Management.''} \emph{Journal of Conflict Resolution} 32 (3): 426--56.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisisEscalationWar2000}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-brecherEscalationWarTwentieth2000}{}}%
 Brecher, Michael, Patrick James, and Jonathan Wilkenfeld. 2000.
-{``Crisis Escalation to War: {Findings} from the {International Crisis
-Behavior Project}.''} \emph{What Do We Know About War}.
+{``Escalation and War in the Twentieth Century: {Findings} from the
+{International Crisis Behavior Project}.''} \emph{What Do We Know about
+War}, 37--53.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2017}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2021}{}}%
 Brecher, Michael, Jonathan Wilkenfeld, Kyle C. Beardsley, Patrick James,
-and David Quinn. 2017. {``International {Crisis Behavior Data
-Codebook}.''} Codebook Version 12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior}{}}%
-Brecher, Michael, Jonathan Wilkenfeld, Kyle Beardsley, Patrick James,
-and David Quinn. n.d. {``International {Crisis Behavior Data Codebook},
-{Version} 12,''} 69.
+and David Quinn. 2021. {``International {Crisis Behavior Data
+Codebook}.''} Codebook Version 14.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-buenodemesquitaDomesticExplanationsInternational2012}{}}%
-Bueno de Mesquita, Bruce, and Alastair Smith. 2012. {``Domestic
-{Explanations} of {International Relations}.''} \emph{Annual Review of
-Political Science} 15 (1): 161--81.
-\url{https://doi.org/10.1146/annurev-polisci-070209-174835}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bushDensityDeclineFounding2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-davisThreatsPromisesPursuit2000}{}}%
-Davis, James W. 2000. \emph{Threats and {Promises}: {The Pursuit} of
-{International Influence}}. {JHU Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-demesquitaForeignAidPolicy2007}{}}%
-de Mesquita, Bruce Bueno, and Alastair Smith. 2007. {``Foreign {Aid} and
-{Policy Concessions}.''} \emph{Journal of Conflict Resolution} 51 (2):
-251--84. \url{https://doi.org/10.1177/0022002706297696}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-eckOneSidedViolenceCivilians2007}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gaddisExpandingDataBase1987}{}}%
-Gaddis, John Lewis. 1987. {``Expanding the {Data Base}: {Historians},
-{Political Scientists}, and the {Enrichment} of {Security Studies}.''}
-\emph{International Security} 12 (1): 3--21.
-\url{https://doi.org/10.2307/2538915}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-gannonOneIfLand2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-georgeDeterrenceAmericanForeign1974}{}}%
-George, Alexander L., and Richard Smoke. 1974. \emph{Deterrence in
-{American} Foreign Policy: {Theory} and Practice}. {Columbia University
-Press}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-haltermanExtractingPoliticalEvents2020}{}}%
-Halterman, Andy. 2020. {``Extracting {Political Events} from {Text Using
-Syntax} and {Semantics}.''}
-
-\leavevmode\vadjust pre{\hypertarget{ref-harknessEthnicArmyState2016}{}}%
-Harkness, Kristen A. 2016. {``The Ethnic Army and the State:
-{Explaining} Coup Traps and the Difficulties of Democratization in
-{Africa}.''} \emph{Journal of Conflict Resolution} 60 (4): 587--616.
-
 \leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
@@
 Politics} 7 (3): 2053168020935257.
-
-\leavevmode\vadjust pre{\hypertarget{ref-henselChartingCourseConflict1996}{}}%
-Hensel, Paul R. 1996. {``Charting {A Course To Conflict}: {Territorial
-Issues} and {Interstate Conflict}, 1816-1992.''} \emph{Conflict
-Management and Peace Science} 15 (1): 43--73.
-\url{https://doi.org/10.1177/073889429601500103}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jamesWhatWeKnow2019}{}}%
-James, Patrick. 2019. {``What Do We Know about Crisis, Escalation and
-War? {A} Visual Assessment of the {International Crisis Behavior
-Project}.''} \emph{Conflict Management and Peace Science} 36 (1): 3--19.
-\url{https://doi.org/10.1177/0738894218793135}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jonesHitMissEffect2009}{}}%
-Jones, Benjamin F., and Benjamin A. Olken. 2009. {``Hit or {Miss}? {The
-Effect} of {Assassinations} on {Institutions} and {War}.''}
-\emph{American Economic Journal: Macroeconomics} 1 (2): 55--87.
-\url{https://doi.org/10.1257/mac.1.2.55}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kuznetsovTheoryPracticeParadiplomacy2014}{}}%
-Kuznetsov, Alexander. 2014. \emph{Theory and {Practice} of
-{Paradiplomacy}: {Subnational Governments} in {International Affairs}}.
-{London}: {Routledge}. \url{https://doi.org/10.4324/9781315817088}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-lacinaExplainingSeverityCivil2006}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lacinaMonitoringTrendsGlobal2005}{}}%
-Lacina, Bethany, and Nils Petter Gleditsch. 2005. {``Monitoring {Trends}
-in {Global Combat}: {A New Dataset} of {Battle Deaths}.''}
-\emph{European Journal of Population / Revue Européenne de Démographie}
-21 (2): 145--66. \url{https://doi.org/10.1007/s10680-005-6851-6}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-lafreeIntroducingGlobalTerrorism2007}{}}%
@@
 Conflict Resolution} 48 (2): 211--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lanoszkaLandpowerAmericanCredibility2016}{}}%
-Lanoszka, Alexander, and Michael A. Hunzeker. 2016. {``Landpower and
-{American} Credibility.''} \emph{Parameters: The United States Army's
-Senior Professional Journal} 45 (4): 17--26.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-levyCausesWar2011}{}}%
-Levy, Jack S., and William R. Thompson. 2011. \emph{Causes of War}.
-{John Wiley \& Sons}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-luptonReexaminingReputationResolve2018}{}}%
-Lupton, Danielle L. 2018. {``Reexamining {Reputation} for {Resolve}:
-{Leaders}, {States}, and the {Onset} of {International Crises}.''}
-\emph{Journal of Global Security Studies} 3 (2): 198--216.
-\url{https://doi.org/10.1093/jogss/ogy004}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
@@
 {New York}: {Freeman}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-maozDyadicMilitarizedInterstate2019}{}}%
-Maoz, Zeev, Paul L. Johnson, Jasper Kaplan, Fiona Ogunkoya, and Aaron P.
-Shreve. 2019. {``The {Dyadic Militarized Interstate Disputes} ({MIDs})
-{Dataset Version} 3.0: {Logic}, {Characteristics}, and {Comparisons} to
-{Alternative Datasets}.''} \emph{Journal of Conflict Resolution} 63 (3):
-811--35. \url{https://doi.org/10.1177/0022002718784158}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-matanockElectingPeaceCivil2017}{}}%
-Matanock, Aila M. 2017. \emph{Electing {Peace}: {From Civil Conflict} to
-{Political Participation}}. {Cambridge}: {Cambridge University Press}.
-\url{https://doi.org/10.1017/9781316987179}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcclearyPrivateVoluntaryOrganizations2008}{}}%
-McCleary, Rachel M., and Robert J. Barro. 2008. {``Private {Voluntary
-Organizations Engaged} in {International Assistance}, 1939-2004.''}
-\emph{Nonprofit and Voluntary Sector Quarterly} 37 (3): 512--36.
-\url{https://doi.org/10.1177/0899764007313719}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mercerProspectTheoryPolitical2005}{}}%
-Mercer, Jonathan. 2005. {``Prospect {Theory} and {Political Science}.''}
-\emph{Annual Review of Political Science} 8 (1): 1--21.
-\url{https://doi.org/10.1146/annurev.polisci.8.082103.104911}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
@@
 515--33. \url{https://doi.org/10.1146/annurev-polisci-031416-092909}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-olterIntergovernmentalOrganizationsIGOs2021}{}}%
-Olter, Agnieszka. 2021. {``Intergovernmental Organizations ({IGOs}) as
-Relevant Actors in {International Relations}.''} \emph{Repositorio
-Institucional - Ulima}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-reiterHowWarsEnd2009}{}}%
-Reiter, Dan. 2009. \emph{How Wars End}. {Princeton University Press}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
----------. 2015. {``Should {We Leave Behind} the {Subfield} of
+Reiter, Dan. 2015. {``Should {We Leave Behind} the {Subfield} of
 {International Relations}?''} \emph{Annual Review of Political Science}
@@
 \url{https://doi.org/10.1177/0022002714553107}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ryanNationStatesEmpiresWars2021}{}}%
-Ryan, Cheyney. 2021. {``Nation-{States}, {Empires}, {Wars},
-{Hostilities}.''} \emph{Ethics \& International Affairs} 35 (3):
-367--79.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-snyderConflictNationsBargaining1977}{}}%
-Snyder, Glenn Herald, and Paul Diesing. 1977. \emph{Conflict Among
-Nations: {Bargaining} and Decision Making in International Crises}.
-{Princeton University Press}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-spruytSovereignStateIts1996}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tragerDiplomacyWarPeace2016}{}}%
-Trager, Robert F. 2016. {``The {Diplomacy} of {War} and {Peace}.''}
-\emph{Annual Review of Political Science} 19 (1): 205--28.
-\url{https://doi.org/10.1146/annurev-polisci-051214-100534}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vabulasCooperationAutonomyBuilding2021}{}}%
-Vabulas, Felicity, and Duncan Snidal. 2021. {``Cooperation Under
-Autonomy: {Building} and Analyzing the {Informal Intergovernmental
-Organizations} 2.0 Dataset.''} \emph{Journal of Peace Research} 58 (4):
-859--69. \url{https://doi.org/10.1177/0022343320943920}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%

### 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
pa submission

@@
 We further introduce two new event visualizations (event iconography and crisis maps), an automated benchmark for measuring event recall using natural language processing (synthetic narratives), and an ontology reconstruction task for objectively measuring event precision.
-We make the data, supplementary appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.
+We make the data, supplementary appendix, replication material, and visualizations of every historical episode available at a companion website crisisevents.org.
 
@@
 nocite: |
-  @fazalStateDeathPolitics2011, @spruytSovereignStateIts1996, @haffarEmergentPeacemakersCataloguing2002, @bushDensityDeclineFounding2019, @benyehudaEthnicActorsInternational2006, @lacinaExplainingSeverityCivil2006; @mcnabbcochranMeasuringMilitaryEffectiveness2017, @carafanoMeasuringMilitaryPower2014, @goertzMeasuringMilitaryAllocations1986, @gartzkeCrossDomainDeterrenceStrategy2019, @lindsayPoliticsManyOther2020, @carterStrategyTerritorialConflict2010, @goldgeierPsychologyInternationalRelations2001, @steinEvaluatingWarOutcomes1980, @sullivanWarAimsWar2007, @ramsayInformationUncertaintyWar2017, @yarhi-miloEyeBeholderHow2013, @oneillInternationalNegotiationConceptual2018, @zartmanEscalationNegotiationInternational2005, @sechserMilitarizedCompellentThreats2011, @powellBargainingTheoryInternational2002, @goemansIntroducingArchigosDataset2009, @powellGlobalInstancesCoups2011, @chenowethIntroducingNonviolentAction2019, @eckOneSidedViolenceCivilians2007, @lafreeIntroducingGlobalTerrorism2007, @beardsleyMediationDilemma2011, @giblerMeasuringAlliancesCorrelates2004, @owsiakInternationalBorderAgreements2018, @leedsAllianceReliabilityTimes2003, @leedsDomesticPoliticalInstitutions1999, @yarhi-miloArmAllyPatron2016, @laiEffectsDifferentTypes2004, @allenUSGlobalMilitary2021, @fortnaPeaceTime2018, @minInterstateWarBattle2021, @frederickIssueCorrelatesWar2017, @sarkeesResortWar181620072010, @reiterRevisedLookInterstate2016
+  @fazalStateDeathPolitics2011, @spruytSovereignStateIts1996, @haffarEmergentPeacemakersCataloguing2002, @bushDensityDeclineFounding2019, @benyehudaEthnicActorsInternational2006, @lacinaExplainingSeverityCivil2006, @mcnabbcochranMeasuringMilitaryEffectiveness2017, @carafanoMeasuringMilitaryPower2014, @goertzMeasuringMilitaryAllocations1986, @gartzkeCrossDomainDeterrenceStrategy2019,  @lindsayPoliticsManyOther2020, @carterStrategyTerritorialConflict2010, @brecher_study_1997, @goldgeierPsychologyInternationalRelations2001, @steinEvaluatingWarOutcomes1980, @sullivanWarAimsWar2007, @ramsayInformationUncertaintyWar2017, @yarhi-miloEyeBeholderHow2013, @oneillInternationalNegotiationConceptual2018, @zartmanEscalationNegotiationInternational2005, @sechserMilitarizedCompellentThreats2011, @powellBargainingTheoryInternational2002, @goemansIntroducingArchigosDataset2009,  @powellGlobalInstancesCoups2011, @chenowethIntroducingNonviolentAction2019, @eckOneSidedViolenceCivilians2007, @lafreeIntroducingGlobalTerrorism2007, @beardsleyMediationDilemma2011, @giblerMeasuringAlliancesCorrelates2004, @owsiakInternationalBorderAgreements2018, @leedsAllianceReliabilityTimes2003, @leedsDomesticPoliticalInstitutions1999, @yarhi-miloArmAllyPatron2016, @laiEffectsDifferentTypes2004, @allenUSGlobalMilitary2021, @fortnaPeaceTime2018, @minInterstateWarBattle2021, @sarkeesResortWar181620072010, @reiterRevisedLookInterstate2016, @frederickIssueCorrelatesWar2017
 
@@
 This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @liComprehensiveSurveySchemabased2021; @beielerGeneratingPoliticalEvent2016; @brandtPhoenixRealTimeEvent2018; @boscheeICEWSCodedEvent2015.
+If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
 On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
@@
 <!-- removedcites trade @barariDemocracyTradePolicy,  @vabulasCooperationAutonomyBuilding2021 -->
-<!-- removedcites @hegreIntroducingUCDPCandidate2020; @grantOUEventData2017; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019, @vabulasCooperationAutonomyBuilding2021;  -->
+<!-- removedcites @hegreIntroducingUCDPCandidate2020; ; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019, @vabulasCooperationAutonomyBuilding2021;  -->
 
@@
 We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @brecherEscalationWarTwentieth2000; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
+We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
 The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
@@
 
-<!-- removedcites  @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019 -->
+<!-- removedcites  @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019; @brecherEscalationWarTwentieth2000; -->
 
@@
 The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015; @hegreIntroducingUCDPCandidate2020]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@ralphsundbergUCDPGEDCodebook2016; @petterssonOrganizedViolence19892018; @sundbergIntroducingUCDPGeoreferenced2013].^[Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].^[Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
 With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.]
 
-<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; -->
+<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; @hegreIntroducingUCDPCandidate2020, @ralphsundbergUCDPGEDCodebook2016-->
 
@@
 Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierchcial clustering on cosine similarity and with Ward's method.]
+If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierarchical clustering on cosine similarity and with Ward's method.]
 
@@
 The start of the crisis revolves around Ukraine backing out of a trade deal with the EU in favor of Russia, but "sign formal agreement" events act more like a topic detector with dozens of events generated by discussions of a possible agreement but not the actual agreement which never materialized.
-The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Victor Yanukovych even after he was removed from power because of articles retroactively discussing the cause of his removal.
+The switch is caught by the "reject plan, agreement to settle dispute", but also continues for Viktor Yanukovych even after he was removed from power because of articles retroactively discussing the cause of his removal.
 Events for "use conventional military force" capture a threshold around the start of hostilities and who the participants were but not any particular battles or campaigns.
@@
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here at www.crisisevents.org.
+Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here at crisisevents.org.
 
@@
 We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
-We thank the many undergraduate coders for their patience and dedication.
+We thank the many undergraduate coders.
 Thanks to the Center for Peace and Security Studies and its membership for comments.
 Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for their generous feedback.
-Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
+Thank you to the cPASS research assistants: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang.
 
@@
 ========================================
-This article’s data, supplementary appendix, replication material, and visualizations of every historical episode are available on the GitHub repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.
+This article’s data, supplementary appendix, replication material, and visualizations of every historical episode are available on the GitHub repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website crisisevents.org.
 

### 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
pa submission

@@
 appendix, replication material, and visualizations of every historical
-episode available at a companion website www.crisisevents.org.
+episode available at a companion website crisisevents.org.
 \end{abstract}
@@
   Stam, and Horowitz 2016), organized violence (Ralph Sundberg and Mihai
-  Croicu 2016; Pettersson and Eck 2018), political violence (Raleigh et
-  al. 2010), sanctions (Felbermayr et al. 2020), and international
-  agreements (Kinne 2020; Owsiak, Cuttner, and Buck 2018), dispute
-  resolution (Frederick, Hensel, and Macaulay 2017), and diplomacy
-  (Moyer, Turner, and Meisel 2020; Sechser 2011).} Thanks to
+  Croicu 2016; Davies, Pettersson, and Öberg 2022), political violence
+  (Raleigh et al. 2010), sanctions (Felbermayr et al. 2020), and
+  international agreements (Kinne 2020; Owsiak, Cuttner, and Buck 2018),
+  dispute resolution (Frederick, Hensel, and Macaulay 2017), and
+  diplomacy (Moyer, Turner, and Meisel 2020; Sechser 2011).} Thanks to
 improvements in natural language processing, more open-ended efforts
 have begun to capture entire unstructured streams of events from
-international news reports.\footnote{See Li et al. (2021); Beieler et
-  al. (2016); Brandt et al. (2018); Boschee et al. (2015). On event
-  extraction from images and social media see Zhang and Pan (2019) and
-  Steinert-Threlkeld (2019).} How close these efforts are to accurately
-measuring all or even most of what is essential in international
-relations is an open empirical question, one for which we provide new
-evidence here.
+international news reports.\footnote{See Beieler et al. (2016); Boschee
+  et al. (2015); Brandt et al. (2018); Grant et al. (2017); Li et al.
+  (2021). On event extraction from images and social media see Zhang and
+  Pan (2019) and Steinert-Threlkeld (2019).} How close these efforts are
+to accurately measuring all or even most of what is essential in
+international relations is an open empirical question, one for which we
+provide new evidence here.
 
@@
 sentence-by-sentence to an unusually high-quality corpus of historical
-narratives of international crises (Brecher 1999; Brecher, James, and
-Wilkenfeld 2000; Wilkenfeld and Brecher 2000; Brecher et al. 2021). The
-result is a new lower bound estimate of how much actually happens
-between states during pivotal historical episodes. We then develop
-several methods for objectively gauging how well these event codings
-reconstruct the information contained in the original narrative. We
-conclude by benchmarking our event codings against several current state
-of the art event data collection efforts. We find that existing systems
-produce sequences of events that do not contain enough information to
-reconstruct the underlying historical episode. The underlying
-fine-grained variation in international affairs is unrecognizable
-through the lens of current quantification efforts.
+narratives of international crises (Brecher 1999; Wilkenfeld and Brecher
+2000; Brecher et al. 2021). The result is a new lower bound estimate of
+how much actually happens between states during pivotal historical
+episodes. We then develop several methods for objectively gauging how
+well these event codings reconstruct the information contained in the
+original narrative. We conclude by benchmarking our event codings
+against several current state of the art event data collection efforts.
+We find that existing systems produce sequences of events that do not
+contain enough information to reconstruct the underlying historical
+episode. The underlying fine-grained variation in international affairs
+is unrecognizable through the lens of current quantification efforts.
 
@@
 event-level datasets including CAMEO dictionary lookup-based systems
-(Historical Phoenix (Althaus et al. 2019); ICEWS (Boschee et al. 2015;
-Hegre et al. 2020); Terrier (Grant et al. 2017)), the Militarized
-Interstate Disputes Incidents dataset, and the UCDP-GED dataset (Ralph
-Sundberg and Mihai Croicu 2016; Pettersson and Eck 2018; Sundberg and
-Melander 2013).\footnote{Other related datasets that insufficiently
-  overlap ICBe's domain for comparison include BCOW (Leng and Singer
-  1988), WEIS (McClelland 1978), CREON (Hermann 1984), CASCON
-  (Bloomfield and Moulton 1989), SHERFACS (Sherman 2000), Real-Time
-  Phoenix (Brandt et al. 2018), and COfEE (Balali, Asadpour, and Jafari
-  2021) (see histories in Merritt (1994) and Schrodt and Hall (2006)).}
-The final set of columns compares episode-level datasets beginning with
-the original ICB project (Brecher et al. 2021; Brecher and Wilkenfeld
-1982; Beardsley et al. 2020); the Militarized Interstate Disputes
-dataset (Palmer et al. 2021; Gibler 2018), and the Correlates of War
-(Sarkees and Wayman 2010). With the exception of large-scale CAMEO
-dictionary-based systems, the existing state of the art quantitative
-datasets ignore the vast majority of the information content found in
-international relations.\footnote{See Balali, Asadpour, and Jafari
-  (2021) for a recent review of ontological depth and availability of
-  Gold Standard example text.}
+(Historical Phoenix (Althaus et al. 2019); ICEWS (Boschee et al. 2015);
+Terrier (Grant et al. 2017)), the Militarized Interstate Disputes
+Incidents dataset, and the UCDP-GED dataset (Davies, Pettersson, and
+Öberg 2022; Sundberg and Melander 2013).\footnote{Other related datasets
+  that insufficiently overlap ICBe's domain for comparison include BCOW
+  (Leng and Singer 1988), WEIS (McClelland 1978), CREON (Hermann 1984),
+  CASCON (Bloomfield and Moulton 1989), SHERFACS (Sherman 2000),
+  Real-Time Phoenix (Brandt et al. 2018), and COfEE (Balali, Asadpour,
+  and Jafari 2021) (see histories in Merritt (1994) and Schrodt and Hall
+  (2006)).} The final set of columns compares episode-level datasets
+beginning with the original ICB project (Brecher et al. 2021; Brecher
+and Wilkenfeld 1982; Beardsley et al. 2020); the Militarized Interstate
+Disputes dataset (Palmer et al. 2021; Gibler 2018), and the Correlates
+of War (Sarkees and Wayman 2010). With the exception of large-scale
+CAMEO dictionary-based systems, the existing state of the art
+quantitative datasets ignore the vast majority of the information
+content found in international relations.\footnote{See Balali, Asadpour,
+  and Jafari (2021) for a recent review of ontological depth and
+  availability of Gold Standard example text.}
 
@@
 hierarchical clustering on all dimensions in the dendrogram along the
-righthand side.\footnote{Hierchcial clustering on cosine similarity and
-  with Ward's method.}
+righthand side.\footnote{Hierarchical clustering on cosine similarity
+  and with Ward's method.}
 
@@
 materialized. The switch is caught by the ``reject plan, agreement to
-settle dispute'', but also continues for Victor Yanukovych even after he
+settle dispute'', but also continues for Viktor Yanukovych even after he
 was removed from power because of articles retroactively discussing the
@@
 Finally, we provide a companion website that incorporates detailed
-visualizations of all of the data introduced here at
-www.crisisevents.org.
+visualizations of all of the data introduced here at crisisevents.org.
 
@@
 1975, creating a resource that continues to spark new insights to this
-day. We thank the many undergraduate coders for their patience and
-dedication. Thanks to the Center for Peace and Security Studies and its
-membership for comments. Special thanks to Rebecca Cordell, Philip
-Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for their
-generous feedback. Thank you to the cPASS research assistants that
-contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano
-Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna
-Pedro, Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and
-Ruixuan Zhang.
+day. We thank the many undergraduate coders. Thanks to the Center for
+Peace and Security Studies and its membership for comments. Special
+thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld,
+and Zhanna Terechshenko for their generous feedback. Thank you to the
+cPASS research assistants: Helen Chung, Daman Heer, Syeda ShahBano Ijaz,
+Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro,
+Tobias Stodiek, Yiyi `Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan
+Zhang.
 
@@
 \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}
-and through the companion website www.crisisevents.org.
+and through the companion website crisisevents.org.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brecherEscalationWarTwentieth2000}{}}%
-Brecher, Michael, Patrick James, and Jonathan Wilkenfeld. 2000.
-{``Escalation and War in the Twentieth Century: {Findings} from the
-{International Crisis Behavior Project}.''} \emph{What Do We Know about
-War}, 37--53.
-
 \leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-daviesOrganizedViolence19892022}{}}%
+Davies, Shawn, Therése Pettersson, and Magnus Öberg. 2022. {``Organized
+Violence 1989\textendash 2021 and Drone Warfare.''} \emph{Journal of
+Peace Research} 59 (4): 593--610.
+
 \leavevmode\vadjust pre{\hypertarget{ref-eckOneSidedViolenceCivilians2007}{}}%
@@
 \url{https://doi.org/10.2202/1554-8597.1054}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hegreIntroducingUCDPCandidate2020}{}}%
-Hegre, Håvard, Mihai Croicu, Kristine Eck, and Stina Högbladh. 2020.
-{``Introducing the {UCDP Candidate Events Dataset}.''} \emph{Research \&
-Politics} 7 (3): 2053168020935257.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-petterssonOrganizedViolence19892018}{}}%
-Pettersson, Therése, and Kristine Eck. 2018. {``Organized Violence,
-1989\textendash 2017.''} \emph{Journal of Peace Research} 55 (4):
-535--47. \url{https://doi.org/10.1177/0022343318784101}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-powellGlobalInstancesCoups2011}{}}%

### 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
pa submission

@@
 
-#oh is it because break is reserved in R? lol
+#oh is it because break is reserved in R? 
 #icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
@@
 
-#somehow break of all things is a b roken name
+#somehow break of all things is a broken name
 #icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))

### 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
pa submission

@@
 foundational work and their help with this effort. We make special
-acknowledgment of Michael Brecher for helping found the ICB project in
+acknowledgement of Michael Brecher for helping found the ICB project in
 1975, creating a resource that continues to spark new insights to this

### 2022-10-24 replication_paper/previous_submissions/political_analysis_draft/ICBe_manuscript_tex.tex
psrm prep

\documentclass{cup-pan}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}

\title{Submission Template for the Cambridge University Press' Political Analysis Journal}

\author[1]{Author One}
\author[2]{Author Two}
\author[3]{Author Three}
\author[2]{Author Four}

\affil[1]{Department One, Institution One, Address One. Email: \url{abc@example.edu}}
\affil[2]{Department Two, Institution Two, Address Two.}
\affil[3]{Department Three, Institution Three, Address Three.}

%% Corresponding author
\corrauthor{Author One}

%% Abbreviated author list for the running footer
\runningauthor{One et al.}

\addbibresource{refs.bib}

\begin{document}

\maketitle

\begin{abstract}
Only two levels of sectional headings, \verb|\section| and \verb|\subsection|, should be used. Ad nemo aut quae dolores nesciunt reprehenderit occaecati. Optio distinctio at aliquam odit dolores laudantium. Illum et qui iste et laudantium dolorum. Nihil quis qui at quia alias. Quisquam ea sit aspernatur. Labore at hic voluptas cumque eum officia repellat.

\keywords{Quisquam, labore at hic, voluptas cumque, eum officia repellat.}
\end{abstract}

\section{Example of a first section}
\label{sec:overview}

Here's an example parenthetical citation \citep{lees2010theoretical} and a text citation: \citet{urmson2008autonomous}. There isn't a good, up-to-date BibTeX style for the Chicago style, so we're using \texttt{biblatex-chicago} instead. This means you'll need to run \texttt{biber} instead of \texttt{bibtex} if you're compiling this template on your local \LaTeX{} installation: on Overleaf, \texttt{biber} is run automatically. You can add pre-notes with citations \citep[see also][]{urmson2008autonomous} too, as well as multiple citations \citep{geiger2012we,leesother} in a single \verb|\citep{...}| or \verb|\citet{...}|.

This is an equation, numbered
\begin{equation}
l(\Lambda)=\sum_{i=1}^{n} \sum_{w=1}^{q} (z_{i w} \ln (\lambda_{i w}) - \lambda_{i w} - \ln (z_{i w}!))
\label{eq:poisson}
\end{equation}
and one that is not numbered
\begin{equation*}
\int_0^{+\infty}e^{-x^2}dx=\frac{\sqrt{\pi}}{2}
\end{equation*}
and one inlined: $e^{i\pi}=-1$. As usual you can cross-reference equations with Equation \ref{eq:poisson} or \eqref{eq:poisson}.

Figure \ref{fig:example} shows a normal figure, while figure \ref{fig:twosubs} show one made up of two sub-figures. Figure \ref{fig:landscape} is an example of a landscaped figure. You can use the \verb|\subcaption{...}| command from the \texttt{subcaption} package to add captions for subfigures and subtables, but do not use the \texttt{subfigure} package: it is incompatible with this template.

\begin{figure}[bt]
\centering
\includegraphics[width=0.6\textwidth]{example-image}
\caption{This is a figure caption. Let's see what happens when it's long and contains citations \citep{geiger2012we} and cross-references: \ref{sec:overview}. Yep, works. Captions should not contain manual line breaks!}
\label{fig:example}
\end{figure}

\begin{table}[bt]
\caption{Automobile Land Speed Records (GR 5-10). Source: \url{https://www.sedl.org/afterschool/toolkits/science/pdf/ast_sci_data_tables_sample.pdf}}
\label{tab:example}
\centering
\begin{tabular}{l l l l r}
\headrow \thead{Speed (mph)} & \thead{Driver} & \thead{Car} & \thead{Engine} & \thead{Date} \\
407.447     & Craig Breedlove & Spirit of America          & GE J47    & 8/5/63   \\
413.199     & Tom Green       & Wingfoot Express           & WE J46    & 10/2/64  \\
434.22      & Art Arfons      & Green Monster              & GE J79    & 10/5/64  \\
468.719     & Craig Breedlove & Spirit of America          & GE J79    & 10/13/64 \\
526.277     & Craig Breedlove & Spirit of America          & GE J79    & 10/15/65 \\
536.712     & Art Arfons      & Green Monster              & GE J79    & 10/27/65 \\
555.127     & Craig Breedlove & Spirit of America, Sonic 1 & GE J79    & 11/2/65  \\
576.553     & Art Arfons      & Green Monster              & GE J79    & 11/7/65  \\
600.601     & Craig Breedlove & Spirit of America, Sonic 1 & GE J79    & 11/15/65 \\
622.407     & Gary Gabelich   & Blue Flame                 & Rocket    & 10/23/70 \\
633.468     & Richard Noble   & Thrust 2                   & RR RG 146 & 10/4/83  \\
763.035     & Andy Green      & Thrust SSC                 & RR Spey   & 10/15/97\\
\end{tabular}

\end{table}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit, qui in ea voluptate velit esse, quam nihil molestiae consequatur, vel illum, qui dolorem eum fugiat, quo voluptas nulla pariatur?

Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit, qui in ea voluptate velit esse, quam nihil molestiae consequatur, vel illum, qui dolorem eum fugiat, quo voluptas nulla pariatur?

\begin{figure}
\begin{minipage}{0.47\textwidth}
\includegraphics[width=\linewidth]{example-image}
\subcaption{This is a subfigure}
\end{minipage}
\hfill
\begin{minipage}{0.47\textwidth}
\includegraphics[width=\linewidth]{example-image}
\subcaption{This is another subfigure}
\end{minipage}

\caption{This is a caption for the entire figure}
\label{fig:twosubs}
\end{figure}

\begin{sidewaysfigure}
\centering
\includegraphics[width=19cm]{example-image}
\caption{This is a figure caption}
\label{fig:landscape}
\end{sidewaysfigure}

At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint, obcaecati cupiditate non-provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non-recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat

At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint, obcaecati cupiditate non-provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates\footnote{Sed ut perspiciatis, unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam eaque ipsa, quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt, explicabo. Nemo enim ipsam voluptatem, quia voluptas sit, aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos, qui ratione voluptatem sequi nesciunt, neque porro quisquam est, qui dolorem ipsum, quia dolor sit amet consectetur adipisci[ng] velit, sed quia non-numquam [do] eius modi tempora inci[di]dunt, ut labore et dolore magnam aliquam quaerat voluptatem.} repudiandae sint et molestiae non-recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\blinddocument

A supplementary material section will always appear before the Reference list. If you're certain that your submission won't have any supplementary material, you can add the \texttt{nosupp} option to the document class declaration, i.e. 
\begin{quote}
\verb|\documentclass[nosupp]{cup-pan}|
\end{quote}

\printbibliography
\end{document}

### 2022-10-24 replication_paper/psrm_draft/ICBe_political_analysis_submission_rmd.Rmd
psrm prep

--- 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
@@
 
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","political_analysis_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","psrm_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
@@
 bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
-litreview_ft_political_analysis <- lit_review_alt %>%
+litreview_ft_psrm <- lit_review_alt %>%
       flextable::as_flextable() %>%
@@
 #https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
-#litreview_ft_political_analysis
-
-#litreview_ft_political_analysis  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_political_analysis.Rds'))
-litreview_ft_political_analysis %>% 
+#litreview_ft_psrm
+
+#litreview_ft_psrm  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_psrm.Rds'))
+litreview_ft_psrm %>% 
     flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
@@
 # Uncomment for snapshot
-# litreview_ft_political_analysis %>% 
+# litreview_ft_psrm %>% 
 #     #flextable::flextable_to_rmd()
-#     save_as_image(path=here::here("replication_paper", "political_analysis_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+#     save_as_image(path=here::here("replication_paper", "psrm_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_recall.png"),
+    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_recall.png"),
                   zoom=1, webshot = "webshot2") # webshot = "webshot2"
@@
     #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+    save_as_image(path=here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_recall.png'),
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'),
        plot = p_recall ,
@@
 
-tiger <- image_read(here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/political_analysis_draft/p_recall.png'))
+tiger <- image_read(here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"))
+tiger2 <- image_read(paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'))
 
 combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea_andcounts.png"))
+image_write(combined, here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea_andcounts.png"))
 
@@
 height=18
-save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_196_icbe.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_icbe.png'),
           p_196_icbe, base_height = 18, base_width = height*ratio)
@@
 height=18
-save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_icbe.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_icbe.png'),
           p_471_icbe, base_height = 18, base_width = height*ratio)
@@
 height=18
-save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_precision_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_precision_combined.png'),
           p_precision_combined, base_height = 18, base_width = height*ratio)
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)
 
@@
 
-ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
 
@@
 save_plot(file=paste0(here::here(),
-                      '/replication_paper/political_analysis_draft/p_precision_icews.png'),
+                      '/replication_paper/psrm_draft/p_precision_icews.png'),
           p_ICEWS, base_height = 10, base_width = 14)
@@
 We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort.
-We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
+We make special acknowledgement of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.
 We thank the many undergraduate coders.

### 2022-10-24 replication_paper/psrm_draft/ICBe_supplemental_information.Rmd
psrm prep

--- 2022-09-23 replication_paper/political_analysis_draft/ICBe_online_supplemental_information.Rmd
@@
 temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft1.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft2.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft2.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft3.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft3.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft4.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft4.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft5.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft5.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft6.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft6.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft7.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft7.png"), zoom=1)
 
 temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft8.png"), zoom=1)
+  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft8.png"), zoom=1)
 
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_percent_chose_tag_by_concept.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_concept.png'), 
                   plot = p_percent_chose_tag_by_concept, width=8, height=8)
@@
 
-  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_percent_chose_tag_by_confidence.png'), 
+  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_confidence.png'), 
                   plot = p_percent_chose_tag_by_confidence, width=8, height=6)
@@
 
-ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
+ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"
 
@@
 
-ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision1.png"), zoom=1) #
+ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision1.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision2.png"), zoom=1) #
+ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision2.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision3.png"), zoom=1) #
+ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision3.png"), zoom=1) #
 
@@
 
-ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision4.png"), zoom=1) #
+ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision4.png"), zoom=1) #
 
@@
     print(thiscrisis)
-    save_icb_file <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icb_metro_plot_",thiscrisis,".Rds")
+    save_icb_file <- paste0(here::here(), "/replication_paper/psrm_draft/p_icb_metro_plot_",thiscrisis,".Rds")
 
@@
   plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-  save_mids_file <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_mids_metro_plot_",thiscrisis,".Rds")
+  save_mids_file <- paste0(here::here(), "/replication_paper/psrm_draft/p_mids_metro_plot_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/psrm_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/psrm_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/psrm_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/psrm_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")
 
@@
     plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
-    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icews_plot_penta_",thiscrisis,".Rds")
-    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
+    save_file_penta <- paste0(here::here(), "/replication_paper/psrm_draft/p_icews_plot_penta_",thiscrisis,".Rds")
+    save_file_lv0 <- paste0(here::here(), "/replication_paper/psrm_draft/p_icews_plot_lv0_",thiscrisis,".Rds")
 
@@
 ## Dyadic ICB
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icb_metro_plot_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icb_metro_plot_196.Rds')
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.Rds') 
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_196.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
   ) 
-#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_penta_196.Rds')
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_penta_196.Rds')
 subtitle="Phoenix Dyadic Events"
@@
     )
-#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_metro_plot_196.png'),
+#ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_metro_plot_196.png'),
 #       plot = p_metro_plot ,
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_196_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_combined.png'),
           p_196_combined, base_height = 12, base_width = 20)
@@
 ```
-
-\begin{figure}[H]
-\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
-\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
-\end{figure}
 
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_phoenix_plot_lv0_196.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_196.png'),
+  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "psrm_draft", "p_phoenix_plot_lv0_196.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_lv0_196.png'),
             p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 \end{figure}
-\clearpage
 
 ## Crimea-Donbas Crisis Maps
+
+\begin{figure}[H]
+\caption{Crisis Map - Crimea-Donbas - ICBe \label{fig:p_471_icbe}}
+\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
+\end{figure}
 
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_471.Rds') 
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_471.Rds') 
 p_metro_plot <- readRDS(save_file)
@@
 library(ggplot2)
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_penta_471.Rds')
 subtitle="Phoenix Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_terrier_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_terrier_plot_penta_471.Rds')
 subtitle="Terrier Dyadic Events"
@@
 
-save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icews_plot_penta_471.Rds')
+save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icews_plot_penta_471.Rds')
 p_471_icews <- readRDS(save_file)
 
-save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_mids.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_mids.png'),
           p_471_mids, base_height = 18, base_width = 13.5)
@@
 
-save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_combined.png'),
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_combined.png'),
           p_471_combined, base_height = 14, base_width = 23)
@@
 if(fromscratch){
-  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_phoenix_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_471.png'),
+  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_phoenix_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_lv0_471.png'),
             p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 if(fromscratch){
-  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_terrier_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_terrier_plot_lv0_471.png'),
+  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_terrier_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_terrier_plot_lv0_471.png'),
             p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
@@
 if(fromscratch){
-  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_icews_plot_lv0_471.Rds"))
-  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icews_plot_lv0_471.png'),
+  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_icews_plot_lv0_471.Rds"))
+  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_icews_plot_lv0_471.png'),
             p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)

### 2022-11-02 replication_paper/psrm_draft/ICBe_manuscript.Rmd
psrm prep

--- 2022-10-24 replication_paper/psrm_draft/ICBe_political_analysis_submission_rmd.Rmd
@@
 This work was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and from the Charles Koch Foundation [20180481].
+The financial sponsors played no in the design, execution, analysis and interpretation of data, or writing of the study.
 
@@
 
-Conflicts of Interests 
+Competing Interests Declaration 
 ========================================
-There are no conflicts of interest to disclose.
+The authors declare that there are no competing interestes.
 

### 2022-11-02 replication_paper/psrm_draft/ICBe_manuscript.tex
psrm prep

--- 2022-09-30 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
@@
 {[}N00014-19-1-2491{]} and from the Charles Koch Foundation
-{[}20180481{]}.
+{[}20180481{]}. The financial sponsors played no in the design,
+execution, analysis and interpretation of data, or writing of the study.
 
@@
 
-\hypertarget{conflicts-of-interests}{%
-\section{Conflicts of Interests}\label{conflicts-of-interests}}
-
-There are no conflicts of interest to disclose.
+\hypertarget{competing-interests-declaration}{%
+\section{Competing Interests
+Declaration}\label{competing-interests-declaration}}
+
+The authors declare that there are no competing interestes.
 

### 2023-05-25 replication_paper/psrm_draft/initial_submission/ICBe_manuscript.Rmd
prep for R&R

--- 2022-11-02 replication_paper/psrm_draft/ICBe_manuscript.Rmd
@@
 
-keywords:
-  - Diplomacy
-  - War
-  - Crises
-  - International Affairs
-  - Computational Social Science
+# keywords:
+#   - Diplomacy
+#   - War
+#   - Crises
+#   - International Affairs
+#   - Computational Social Science
 
@@
 
+\doublespacing
+
 Introduction
@@
 The task is to combine informative priors about $IR$ with an unstructured corpus $D$ to produce a series of structured discrete events, $e \in E$, that have high coverage, precision, and recall over what actually took place in history, $H$.
+
+Corpus 
+========================================
+<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
+
+For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
+Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].
+Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
+59].
+Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
+The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
+
+<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
 
@@
 
-Corpus 
-========================================
-<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
-
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].
-Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
-59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
-
 Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art
@@
 \clearpage
+\singlespacing
 <!-- \onecolumn -->
@@
 \clearpage
+\doublespacing
 <!-- \twocolumn -->
@@
 The canonical narrative of Cuban Missiles also includes high-level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode-level datasets have very low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
 
@@
 \clearpage
+\doublespacing
 <!-- \twocolumn -->
+
+We find substantive variation in recall across systems.
+Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
+The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
+The two episode-level datasets have very low coverage of contextual details.
+The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
+ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
+Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
 
@@
 
+\singlespacing
 \begin{figure}[H]
@@
 \end{figure}
+\doublespacing
 

### 2023-05-30 replication_paper/psrm_draft/ICBe_manuscript.Rmd
no keywords
into scoping, very, lit rev par order, ICB def, synthetic econ missing

@@
 
-Introduction
-========================================
-
-If we could record every important interaction between countries in all of diplomacy, military conflict, and international political economy, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
+\doublespacing
+
+# Introduction
+
+If we could record every international interaction in the realms of diplomacy, conflict, economy, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
 In other words, what is the entropy of international relations?
-This record could in principle be unbounded, but the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
-If so, then these events can be systematically measured, and accordingly, massive effort is expended in social science attempting to record these regularities.^[See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.^[See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
-On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.] How close these efforts are to accurately measuring all or even most of what is essential in international relations is an open empirical question, one for which we provide new evidence here.
+While this record could in principle be unbounded, the central conceit of social science is that there are structural regularities that limit what actors can do, their best options, and even which actors are likely to survive [@brecherInternationalStudiesTwentieth1999; @reiterShouldWeLeave2015].
+If so, then these events can be recorded and systematically measured by social scientists interested in these regularities.[^1] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.[^2] This has invited fruitful efforts to evaluate the coverage, quality, and accuracy of attempts to measure international affairs.
+
+[^1]: See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].
+
+[^2]: See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
+On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.
 
 <!-- removedcites trade @barariDemocracyTradePolicy,  @vabulasCooperationAutonomyBuilding2021 -->
+
 <!-- removedcites @hegreIntroducingUCDPCandidate2020; ; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019, @vabulasCooperationAutonomyBuilding2021;  -->
 
-Our contribution is a high coverage ontology and event dataset for key historical episodes in 20th and 21st-century international relations.
-We develop a large, flexible ontology of international events with the help of both human coders and natural language processing.
-We apply it sentence-by-sentence to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
-The result is a new lower bound estimate of how much actually happens between states during pivotal historical episodes.
-We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original narrative.
+Our contribution is using human coders and natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying the ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
+We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original crisis narrative.
 We conclude by benchmarking our event codings against several current state of the art event data collection efforts.
@@
 The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
+In focusing this initial effort on international crises as a proof of concept sample, we demonstrate our ontology and method's potential to improve upon existing empirical identifications of patterns of international interactions.
 
@@
 
-This is a measurement paper that makes the following argument --- there is a real-world unobserved latent concept known as international relations, we propose a method for systematically measuring it, we successfully apply this method producing a new large-scale set of measurements, and those measurements exhibit several desirable kinds of internal and external validity, and those measurements out-perform other existing approaches.
-The article organizes that argument into eight sections: task definition; corpus; priors/existing state of the art; ICBe coding process; internal consistency; case study selection; recall; and precision.
+This measurement paper makes the following arguments.
+First, there is a real-world unobserved latent concept known as international relations that can be systematically measured.
+Second, we propose a method for systematic large-scale measurement of the actors and behaviors in international affairs and as a proof of concept apply that method to a well-regarded and salient sample of international events known as international crises.
+Third, in doing so we confirm that those measurements exhibit several desirable kinds of internal and external validity and out-perform existing approaches.
+The article organizes that argument into sections.
 A final section concludes.
 
-Task Definition
-========================================
+# Task Definition
 
@@
 Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine-readable abstractive events.
-Formally, a historical episode, $H$, is demarcated by a period of time $[T_{start}, T_{end}] \in T$, a set of Players $p \in P$, and a set of behaviors they undertook during that time $b \in B$.
-International Relations, $IR$, is the system of regularities that govern the strategic interactions that world actors make during a historical episode, given their available options, preferences, beliefs, and expectations of choices made by others.
-We observe neither $H$ nor $IR$ directly.
-Rather the Historical Record, $HR$, produces documents $d \in D$ containing some relevant and true (as well as irrelevant and untrue) information about behaviors that were undertaken recorded in the form of unstructured natural language text.
-The task is to combine informative priors about $IR$ with an unstructured corpus $D$ to produce a series of structured discrete events, $e \in E$, that have high coverage, precision, and recall over what actually took place in history, $H$.
+Each event occurs over a marked time period where we observe the behaviors of a given set of actors.
+Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
+The task is to produced a structured account of the historical event by combining the unstructured corpus of historical records with informative priors about international relations.
+The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of historical political events from which we can garner novel insight given the data's high coverage, precision, and recall.
+
+# Corpus
+
+<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
+
+For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
+ICB defines a crisis as meeting three conditions: (1) an actor perceives a threat to one of more of its basic values, (2) the actor has a finite time horizon for responding to the perceived threat, and (3) the probability of military hostility has increased [@brecherCrisesWorldPolitics1982].
+Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
+59].
+Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
+The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
+
+<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
 
@@
 \clearpage
+
 <!-- \onecolumn -->
+
+```{=tex}
 \begin{figure}[H]
@@
 \clearpage
+```
 <!-- \twocolumn -->
 
-Corpus 
-========================================
-<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
-
-For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
-Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].
-Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
-59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
-
-Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art
-========================================
+# Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art
 
@@
 We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.^[See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]
 
@@
 
-The second axis (columns) compares the very high ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].^[Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
-With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.^[See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.]
+The columns compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
+They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.[^4]
+
+[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
+
+[^4]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
+
+The rows represent the types of information we expect to find in IR and forms the basis for our proposed ontology.
+We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
+Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^5]
+
+[^5]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
 
@@
 
+```{=tex}
 \clearpage
+\singlespacing
+```
 <!-- \onecolumn -->
@@
 
+```{=tex}
 \clearpage
+\doublespacing
+```
 <!-- \twocolumn -->
@@
 
-ICBe Coding Process
-========================================
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].^[This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players ($P$), whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
+# ICBe Coding Process
+
+The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^6] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
+Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
 Some additional details like location and timing information were always collected while other details were only collected if appropriate, e.g.
@@
 
-Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.^[Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
+[^6]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
+
+Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.[^7] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
 We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix 2.2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
 This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
+
+[^7]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
+Undergraduate coders were students who engaged in classroom workshops.
 
@@
 
-Internal Consistency
-========================================
+# Internal Consistency
 
@@
 
-Case Study Selection
-========================================
+# Case Study Selection
 
@@
 
-Recall
-========================================
-
-Recall measures the share of desired information recovered by a sequence of coded events, $Pr(E|H)$, and is poorly defined for historical episodes.
+# Recall
+
+Recall measures the share of desired information recovered by a sequence of coded events, and is poorly defined for historical episodes.
 First, there is no genuine ground truth about what occurred, only surviving texts about it.
@@
 First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives contain 17/51 and 23/30 of the events from the synthetic narrative and include other details that are not in the synthetic narrative.
-Second, mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.
+Our ground truth ICB narratives contain 17/51 and 23/30 of the events from the synthetic narrative and include other details that are not in the synthetic narrative.[^8] Second, mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.
 Third, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
@@
 
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode-level datasets have very low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have high coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left very little additional information on the table.
+[^8]: As the ICB narratives and ICBe are intended to explain the conflictual behavior in a political context, many of the missing events concern the economic components of conflict events (eg.
+nationalizing a foreign business).
+ICBe's limitation at this stage is its focus on international events that involve conflict (ICB crises), but even with this limitation in the information we trained on ICBe is more comprehensive than the existing datasets that *do* try to code the economic dimensions of these conflicts.
+Since expanding the ontology to broader international phenomenon is an easier problem to address than the over-inclusion of irrelevant information, we see this as promising for future implementation of our model.
 
@@
 
+```{=tex}
 \clearpage
+\singlespacing
+```
 <!-- \onecolumn -->
+
+```{=tex}
 \begin{figure}[H]
@@
 \clearpage
+\doublespacing
+```
 <!-- \twocolumn -->
 
-Precision
-========================================
-
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, $Pr(H|E)$.
+We find substantive variation in recall across systems.
+Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
+The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
+The two episode-level datasets have low coverage of contextual details.
+The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
+ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
+Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
+
+# Precision
+
+The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history.
 It does little good to recall a historical event but too vaguely (e.g.
@@
 Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.^[We preprocess sentences to replace named entities with a generic Entity token.] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.^[Hierarchical clustering on cosine similarity and with Ward's method.]
+Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^9] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
+If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.[^10]
+
+[^9]: We preprocess sentences to replace named entities with a generic Entity token.
+
+[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
 
@@
 <!-- \clearpage -->
+
 <!-- \onecolumn -->
+
 <!-- \begin{sidewaysfigure}[ht] -->
+
 <!-- \caption{Crisis Maps  \label{fig:p_precision_combined}} -->
+
 <!-- \centering{\includegraphics[width=22cm]{./p_precision_combined.png}} -->
+
 <!-- \end{sidewaysfigure} -->
+
 <!-- \clearpage -->
+
 <!-- \twocolumn -->
 
+```{=tex}
+\singlespacing
 \begin{figure}[H]
@@
 \end{figure}
-
+\doublespacing
+```
 <!-- \begin{figure}[H] -->
+
 <!-- \caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}} -->
+
 <!-- \centering{\includegraphics[width=17cm]{./p_471_icbe.png}} -->
+
 <!-- \end{figure} -->
@@
 \clearpage
+\doublespacing
+```
 <!-- \twocolumn -->
@@
 \clearpage
+\doublespacing
+```
 <!-- \twocolumn -->
+
 <!-- Edges <-> indicates undirected dyad and -> indicates directed dyad.  # removed from legend with update-->
 
+```{=html}
 <!--
@@
 -->
-
-Conclusion
-========================================
+```
+# Conclusion
 
@@
 These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).^[Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
+escalation and de-escalation of conflicts).[^11] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
@@
 
-Funding
-========================================
+[^11]: Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
+
+# Funding
 
@@
 
-Acknowledgements 
-========================================
+# Acknowledgements
 
@@
 
-Author Contributions 
-========================================
+# Author Contributions
+
 Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.; Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.; Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.
 
-Data Availability Statement 
-========================================
-This article’s data, supplementary appendix, replication material, and visualizations of every historical episode are available on the GitHub repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website crisisevents.org.
-
-Competing Interests Declaration 
-========================================
+# Data Availability Statement
+
+This article's data, supplementary appendix, replication material, and visualizations of every historical episode are available on the GitHub repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website crisisevents.org.
+
+# Competing Interests Declaration
+
 The authors declare that there are no competing interestes.
@@
 
-Works Cited
-========================================
+# Works Cited

### 2023-05-30 replication_paper/psrm_draft/ICBe_manuscript.Rmd
start clarifying new elements of ontology

@@
 Third, in doing so we confirm that those measurements exhibit several desirable kinds of internal and external validity and out-perform existing approaches.
-The article organizes that argument into sections.
+The article organizes that argument into XX sections.
 A final section concludes.
@@
 They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
-With the exception of large-scale CAMEO dictionary-based systems, the existing state of the art quantitative datasets ignore the vast majority of the information content found in international relations.[^4]
 
 [^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
-
-[^4]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
 
@@
 Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^5]
-
-[^5]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^4]
+
+[^4]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
+
+Table 1 demonstrates that with the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^5] In particular,
+
+[^5]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
+
+-   separating chess pieces from players (military vs civilian)
+
+-   addition of domains
 
@@
 
-[^8]: As the ICB narratives and ICBe are intended to explain the conflictual behavior in a political context, many of the missing events concern the economic components of conflict events (eg.
+[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
 nationalizing a foreign business).
-ICBe's limitation at this stage is its focus on international events that involve conflict (ICB crises), but even with this limitation in the information we trained on ICBe is more comprehensive than the existing datasets that *do* try to code the economic dimensions of these conflicts.
-Since expanding the ontology to broader international phenomenon is an easier problem to address than the over-inclusion of irrelevant information, we see this as promising for future implementation of our model.
+Even when they occur in the context of a crisis, these events largely fall outside the sample of information on which ICBe's ontology is currently trained.
+Even with this limitation, ICBe is more comprehensive than the existing datasets that *do* try to code the economic dimensions of these crises.
+We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
 

### 2023-06-03 replication_paper/psrm_draft/ICBe_manuscript.Rmd
ontology innovation para added. intro header deleted

@@
 
-# Introduction
-
 If we could record every international interaction in the realms of diplomacy, conflict, economy, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
@@
 
-Our contribution is using human coders and natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying the ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
+We advance existing efforts to identify and structure regularized events and actor in international politics by using human coders and natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying our ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
 We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original crisis narrative.
@@
 
-Table 1 demonstrates that with the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^5] In particular,
+Table 1 demonstrates that with the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^5] In particular, we highlight two innovations in our ontology.
+First, we separate the chess pieces from the chess players in not only identifying what states were involved in each crisis, but distinguishing between different actors within a state.
+By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning topics like civilian military relations as well as evolution in what actors are engaged in crises - a topic of increasing interest as states engage in "gray zone conflict" by employing "chess pieces" like the coast guard instead of military navy.
+Second, we add information about the domains in which actors behave - whether in land, air, sea, space, or cyber - since they differ in their technology, tactics, geography, and purpose [@gartzkeCrossDomainDeterrenceStrategy2019].
+Doing so allows researchers to identify and explain patterns in escalation conditional on the military means states use in conflict.
+Recent concerns about cross-domain conflict and the effect of new domains of conflict like space and cyber have made this an endeavor of increased interest to practitioners [@gannonOneIfLand2022].
 
 [^5]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
-
--   separating chess pieces from players (military vs civilian)
-
--   addition of domains
 

### 2023-07-11 replication_paper/psrm_draft/ICBe_manuscript.qmd
r and r re-org

--- 2023-06-03 replication_paper/psrm_draft/ICBe_manuscript.Rmd
@@
 
-```{r, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
+```{r options, echo=F, cache=F, messages=F, results='hide', warnings=F, include=FALSE}
 #International Crisis Behavior Events (ICBe) Dataset
@@
 options(tinytex.clean=F)
-
-```
-
-```{r, eval=T, echo=F, cache=F}
-
+```
+
+```{r package-load, eval=T, echo=F, cache=F}
 #library(pacman)
@@
 
+`%>%` <- magrittr::`%>%`
+
 #install.packages('stargazer')
@@
 #tinytex::install_tinytex()
-
-```
-
-```{r, echo=F}
+```
+
+```{r borked, echo=F, include=F}
 #Notes
@@
 #- \DeclareUnicodeCharacter{00A0}{ }
-
-```
-
-```{r, include=FALSE}
 # options(tinytex.verbose = TRUE)
@@
 
-```{r, echo=FALSE}
-
-`%>%` <- magrittr::`%>%`
-
-```
-
-```{r, echo=FALSE}
-
+```{r load-data, echo=FALSE}
 icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds"))
@@
 
-#oh is it because break is reserved in R? 
-#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
 icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
 
-#somehow break of all things is a broken name
-#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
 icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))
-
-```
-
-<!-- note: please start your introduction without including the word "Introduction" as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.
--->
-
-<!-- #\twocolumn -->
+```
 
@@
 
-[^1]: See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].
-
-[^2]: See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
-On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.
-
-<!-- removedcites trade @barariDemocracyTradePolicy,  @vabulasCooperationAutonomyBuilding2021 -->
-
-<!-- removedcites @hegreIntroducingUCDPCandidate2020; ; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019, @vabulasCooperationAutonomyBuilding2021;  -->
+<!-- removedcites @barariDemocracyTradePolicy; @vabulasCooperationAutonomyBuilding2021; @hegreIntroducingUCDPCandidate2020; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019; @vabulasCooperationAutonomyBuilding2021; -->
 
@@
 
-<!-- removedcites  @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019; @brecherEscalationWarTwentieth2000; -->
-
-This measurement paper makes the following arguments.
+<!-- removedcites @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019; @brecherEscalationWarTwentieth2000 -->
+
+This measurement paper proceeds in four sections that make the following arguments.
 First, there is a real-world unobserved latent concept known as international relations that can be systematically measured.
@@
 Third, in doing so we confirm that those measurements exhibit several desirable kinds of internal and external validity and out-perform existing approaches.
-The article organizes that argument into XX sections.
+Fourth, this validation can be evaluated in detail via new event visualizations, with examples provided for case studies of the 1962 Cuban Missile Crisis and 2014 Crimea-Donbas crisis.
 A final section concludes.
 
-# Task Definition
+# Identifying and measuring international relations
+
+## Task definition
 
 We consider the measurement task of abstracting discrete events about a historical episode in international relations.
-The easiest way to convey the task is with an example.
-Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine-readable abstractive events.
+We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
+Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
 Each event occurs over a marked time period where we observe the behaviors of a given set of actors.
 Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
+
 The task is to produced a structured account of the historical event by combining the unstructured corpus of historical records with informative priors about international relations.
 The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of historical political events from which we can garner novel insight given the data's high coverage, precision, and recall.
-
-# Corpus
-
-<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
-
-For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
-ICB defines a crisis as meeting three conditions: (1) an actor perceives a threat to one of more of its basic values, (2) the actor has a finite time horizon for responding to the perceived threat, and (3) the probability of military hostility has increased [@brecherCrisesWorldPolitics1982].
-Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
-59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
-
-```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+The easiest way to convey the task is with an example.
+@fig-cuba-narrative shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine-readable abstractive events.
+
+```{r cuban-case-study-precision, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+# AG temp edit: revert by setting eval=T
 
@@
 temp <- NULL
-
-```
-
-<!--- REX Remember to put in a Legend for the Icons ---->
-
-\clearpage
-
-<!-- \onecolumn -->
-
-```{=tex}
-\begin{figure}[H]
-\caption{Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-```
-<!-- \twocolumn -->
-
-# Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art
-
-Next, we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations alongside each concept.
+```
+
+![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative}
+
+## Existing state of the art measurements
+
+We draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
+We organize our prior beliefs along two overarching axes.
+The first is the extensive existing measurement efforts of IR, detailed below.
 Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
@@
 
+Table 1 describes the underlying structure of international crises that we hope to uncover as well as existing efforts to identify the actors and actions of international relations.
+The rows represent the types of information we expect to find in IR and forms the basis for our proposed ontology.
 The columns compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
 They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
-
-[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
-
-The rows represent the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^4]
-
-[^4]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
-
-Table 1 demonstrates that with the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^5] In particular, we highlight two innovations in our ontology.
-First, we separate the chess pieces from the chess players in not only identifying what states were involved in each crisis, but distinguishing between different actors within a state.
-By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning topics like civilian military relations as well as evolution in what actors are engaged in crises - a topic of increasing interest as states engage in "gray zone conflict" by employing "chess pieces" like the coast guard instead of military navy.
-Second, we add information about the domains in which actors behave - whether in land, air, sea, space, or cyber - since they differ in their technology, tactics, geography, and purpose [@gartzkeCrossDomainDeterrenceStrategy2019].
-Doing so allows researchers to identify and explain patterns in escalation conditional on the military means states use in conflict.
-Recent concerns about cross-domain conflict and the effect of new domains of conflict like space and cyber have made this an endeavor of increased interest to practitioners [@gannonOneIfLand2022].
-
-[^5]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
-
-<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; @hegreIntroducingUCDPCandidate2020, @ralphsundbergUCDPGEDCodebook2016-->
 
@@
 ```
-<!-- \onecolumn -->
-
-```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 
@@
 #     save_as_image(path=here::here("replication_paper", "psrm_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
 ```
@@
 ```
-<!-- \twocolumn -->
-
-```{r , eval=T, results='hide', echo=F, include=T, message=F, cache=F}
-
+```{r coder-counts, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
 n_crisis <- ICBe_events_agreed %>% dplyr::select(crisno) %>% unique() %>% nrow()
@@
 avg_coders_per_sentence <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-```
-
-# ICBe Coding Process
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^6] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
+```
+
+With the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^4] In particular, we highlight two innovations in our ontology.
+First, we separate the chess pieces from the chess players in not only identifying what states were involved in each crisis, but distinguishing between different actors within a state.
+By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning topics like civilian military relations as well as evolution in what actors are engaged in crises - a topic of increasing interest as states engage in "gray zone conflict" by employing "chess pieces" like the coast guard instead of military navy.
+Second, we add information about the domains in which actors behave - whether in land, air, sea, space, or cyber - since they differ in their technology, tactics, geography, and purpose [@gartzkeCrossDomainDeterrenceStrategy2019].
+Doing so allows researchers to identify and explain patterns in escalation conditional on the military means states use in conflict.
+Recent concerns about cross-domain conflict and the effect of new domains of conflict like space and cyber have made this an endeavor of increased interest to practitioners [@gannonOneIfLand2022].
+
+<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; @hegreIntroducingUCDPCandidate2020, @ralphsundbergUCDPGEDCodebook2016-->
+
+# Methodology and data
+
+## Corpus
+
+For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
+ICB defines a crisis as meeting three conditions: (1) an actor perceives a threat to one of more of its basic values, (2) the actor has a finite time horizon for responding to the perceived threat, and (3) the probability of military hostility has increased [@brecherCrisesWorldPolitics1982].
+Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
+59].
+Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
+The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
+
+<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988 -->
+
+## Coding Process
+
+The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^5] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
 Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
@@
 Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-
-[^6]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6]
 
@@
 
-[^7]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.
-
-```{r}
+```{r means}
 #We calculate means in the SI appendix on agreement
@@
 
-# Internal Consistency
+# Performance comparison
+
+## Internal consistency
 
@@
 
-# Case Study Selection
-
-The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
+## Improvement over existing efforts
+
+To evaluate our coding process relative to existing datasets, we measure the recall and precision of ICBe events in absolute terms and relative to other existing systems.
+Recall measures the share of desired information recovered by a sequence of coded events while precision measures the degree to which a sequence of events correctly and usefully describes the information in history.
 We provide full ICB narratives, ICBe coding in an easy-to-read iconographic form, and a wide range of visualizations for every case on the companion website.
-In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion (hereafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to a hostile regime, with implications for economic and military security for the superpower, risked full-scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st-century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
-
-# Recall
-
-Recall measures the share of desired information recovered by a sequence of coded events, and is poorly defined for historical episodes.
+
+Recall is poorly defined for historical episodes.
 First, there is no genuine ground truth about what occurred, only surviving texts about it.
-Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in, the more detail you will find about individual events and in between every two discrete events.
+Second, there is no *a priori* guide to what information is necessary detail and what is ignorable trivia.
+History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in, the more detail you will find about individual events as well as in between any two discrete events.
 The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
@@
 Our strategy for dealing with both problems is a plausibly objective yardstick called a synthetic historical narrative.
-For both case studies, we collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
+We collect a large diverse corpus of narratives spanning timelines, encyclopedia entries, journal articles, news reports, websites, and government documents.
 Using natural language processing (fully described in SI Appendix 3.1), we identify details that appear across multiple accounts.
@@
 
-Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts.
-First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives contain 17/51 and 23/30 of the events from the synthetic narrative and include other details that are not in the synthetic narrative.[^8] Second, mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.
-Third, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
-the U.S.
-was in a \textit{de facto} grey-scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
-a long term lease on naval facilities in Crimea.
-Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease-fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missiles also includes high-level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
-nationalizing a foreign business).
-Even when they occur in the context of a crisis, these events largely fall outside the sample of information on which ICBe's ontology is currently trained.
-Even with this limitation, ICBe is more comprehensive than the existing datasets that *do* try to code the economic dimensions of these crises.
-We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
-
-```{r cuban case study recall, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#
+We find substantive variation in recall across existing state of the art methods.
+Mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.[^8] Furthermore, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events.
+@fig-recall-cases compares ICBe's recall with that of existing datasets for the two case studies in the next section.
+Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
+The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
+The two episode-level datasets have low coverage of contextual details.
+The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
+ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
+Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
+
+![Recall comparison of two cases across existing state of the art efforts.
+Higher y-axis values represent higher recall and higher x-axis values represent number of times that detail is mentioned across the full corpus used to construct the synthetic narrative.](p_recall.png){#fig-recall-cases}
+
+The second component of event measurement is precision.
+It does little good to recall a historical event but too vaguely (e.g.
+MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
+ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
+ICBe's ontology and coding system are designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
+You should be able to lay out the events of a crisis on a timeline, as in Figure 3, and read off the macrostructure of an episode from each individual move.
+We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study in SI Appendix 4.3 and 4.4 and for all crises on the companion website.
+
+We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
+We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative for every case on the companion website.
+We further provide a stratified sample of event codings alongside their source text (SI Appendix 4.2).
+We find both the visualizations of macrostructure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe.
+
+```{r crisis-map-function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+global_check_overlap=F
+library(igraph)
+library(RColorBrewer)
+library(ggraph)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
+dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
+                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
+
+actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
+                                sheet="actor_translator") #%>% janitor::clean_names() 
+#Convert to a local file for pushing
+#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
+pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
+library(pals); #install.packages('pals')
+pallet <- c(pals::glasbey(),  pals::alphabet2())
+pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
+library(colorspace)
+#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
+pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
+actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
+
+icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){
+
+  icb_events_subset <-  ICBe_events_agreed %>% 
+                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
+                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
+                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
+                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
+                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
+                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
+                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
+                         tidyr::fill(decade, .direction="downup") %>%
+                         tidyr::fill(year, .direction="downup") %>%
+                         tidyr::fill(month, .direction="downup") %>%
+                         tidyr::fill(day, .direction="downup") %>% 
+                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
+                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
+                         arrange(decade, year,month,day) %>%
+                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
+
+  icb_events_subset_diad <- icb_events_subset %>% 
+                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
+                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
+                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
+                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
+                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
+                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
+                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
+                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
+                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
+                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
+                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
+                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
+                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
+                                                    sent,
+                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
+                                                    thinkkind, sayintkind, dokind,
+                                                    point_in_time_year, point_in_time_month
+                                                    ) %>% distinct() %>%
+                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
+
+  notes=NULL
+  if(prune_rare==T){
+    actor_sent_counts <- 
+      bind_rows(
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+        ) %>% 
+          na.omit() %>%
+          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+      #New pruning rule, either singletons or actors with less than 10% of the max actor
+      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
+      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
+      if(left_over_count<3){
+        #Skip pruning if it leaves less than 3 actors
+      } else {
+
+        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
+        actor_singleton_labels <- actor_map$value_normalized_label
+        names(actor_singleton_labels) <- actor_map$actor
+        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
+
+        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
+
+        #Easiest thing is to just prune the original data
+        icb_events_subset <- icb_events_subset %>%
+          filter(!(
+                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
+                say_actor_a %in% singleton_actors |
+                say_actor_b %in% singleton_actors |
+                do_actor_a %in% singleton_actors |
+                do_actor_b %in% singleton_actors 
+          ) )
+
+          #recreate diads again using the new sentence numbers
+          icb_events_subset_diad <- icb_events_subset %>% 
+                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
+                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
+                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
+                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
+                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
+                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
+                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
+                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
+                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
+                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
+                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
+                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
+                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
+                                                            sent,
+                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
+                                                            thinkkind, sayintkind, dokind,
+                                                            point_in_time_year, point_in_time_month
+                                                            ) %>% distinct() %>%
+                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
+                                        filter(!(
+                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
+                                              say_actor_a %in% singleton_actors |
+                                              say_actor_b %in% singleton_actors |
+                                              do_actor_a %in% singleton_actors |
+                                              do_actor_b %in% singleton_actors 
+                                        ) ) %>% 
+                                       arrange(sent) %>%
+                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
+      }
+  }
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  #Order actors by how many interactions they have together
+  temp <- bind_rows(
+    icb_events_subset_diad  %>% 
+      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
+    icb_events_subset_diad %>% 
+      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
+  )  %>% arrange(actor_1, actor_2) %>% distinct()
+
+  #new plan is to minimize the number of crossovers
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("actor_2", "actor_1", "sent"))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
+  rowwise() %>%
+  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
+  arrange(desc(n))
+
+  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+  diag(temp2_wide) <- 0
+  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
+
+  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
+            )  %>%
+            filter(!is.na(actor)) %>%
+           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  icbe_actor_to_qcode <- icb_events_long %>%
+                         dplyr::filter(crisno==thiscrisis  ) %>% 
+                         filter(varname_normalized %>% str_detect("actor")) %>% 
+                         dplyr::select(value_normalized,value_qcode) %>% 
+                         na.omit() %>% distinct()
+
+  actor_colors_df <- icbe_actor_to_qcode %>%
+    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
+  actor_colors <- actor_colors_df$actor_color
+  names(actor_colors) = actor_colors_df$value_normalized
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                      mutate(x=max(x)+50) %>%
+                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
+                      na.omit() %>% 
+                      distinct() %>%  
+                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                      group_by(sent) %>%
+                       filter(year_float==min(year_float)) %>%
+                      ungroup() %>% as.data.frame() %>%
+                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                      filter(!duplicated(year_float ) ) %>%
+                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+  ####Actor levels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
+    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
+    rowwise() #%>%
+    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
+
+  ######Monads
+  icb_events_subset_monad <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
+                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
+                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
+            ) %>% 
+            na.omit() %>% 
+            distinct() %>% 
+            filter(!duplicated(paste(sent,actor,leaf))) %>%
+            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
+            distinct() %>% 
+            group_by(sent,actor,actor_sent) %>%
+              summarise(leaf=paste(leaf, collapse="\n") ) %>%
+            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
+
+  ######Directed
+  icb_events_subset_directed <- 
+            #We need to enumerate all the possibilities
+            bind_rows(
+              #Do alone
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
+              #Say alone
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
+              #Say Do
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
+                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
+              #Think Do
+              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
+            ) %>% 
+            na.omit() %>% 
+            distinct() %>% 
+            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            arrange(sent, actor_sent_1,leaf) %>%
+            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
+           #It is actually easier just to rejex out some dupes
+            mutate(leaf = leaf %>%
+                     str_replace("accept\naccept","accept") %>%
+                   str_replace("appeal\nappeal","appeal") %>%
+                   str_replace("reject\nreject","reject") %>%
+                   str_replace("express intent\nexpress intent","express intent") 
+                   ) %>%
+           arrange(sent, actor_sent_1,leaf) %>%
+           filter(actor_sent_1!=actor_sent_2)
+
+  #debug
+  icb_events_subset_directed <- icb_events_subset_directed  %>% 
+           group_by(sent, leaf) %>%
+               mutate(bundle_count=n()) %>%
+               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
+            ungroup()
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf2, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1,
+                       bundle_count=icb_events_subset_directed$bundle_count
+                       )
+
+  ######Put it all together
+  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
+  p_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                            colour=actor,
+                            label=leaf,
+                            filter=eventedge==T & bundle_count==1 
+                            ),
+                        label_colour=NA, 
+                        vjust = -0.75,
+                        lineheight = .75,
+                        sep = unit(1, 'mm'), 
+                        edge_width=0.25, 
+                        show.legend = F,
+                        arrow = arrow(length = unit(2, 'mm')),
+                        label_size=3,
+                        check_overlap=global_check_overlap,
+                        start_cap = circle(3, 'mm'),
+                        end_cap = circle(3, 'mm'),
+                        angle_calc = 'along' #,
+                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
+                       ) +
+              #Grouped Edges
+              geom_edge_parallel(aes(  
+                                  colour=actor,
+                                  label=leaf,
+                                  filter=eventedge==T & bundle_count>1
+                                  ),
+                              vjust = -0.75,
+                              lineheight = .75,
+                              sep = unit(5, 'mm'), 
+                              edge_width=0.4,  #0.25
+                              show.legend = F,
+                              arrow = arrow(length = unit(1, 'mm')),
+                              label_size=4,
+                              check_overlap=global_check_overlap,
+                              start_cap = circle(3, 'mm'),
+                              end_cap = circle(3, 'mm'),
+                              angle_calc = 'along'
+                             ) +
+
+              #Time edges
+              geom_edge_link(aes(
+                              edge_colour=actor,
+                              filter=timeedge==T
+                              ),
+                              edge_width=0.1, 
+                              show.legend = F,
+                              check_overlap=global_check_overlap
+                             ) +
+              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+              #Fatalities
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
+
+              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
+              #Add Actor Names
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
+                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
+                        check_overlap=global_check_overlap) + #-45
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  if(prune_rare==T & !is.null(notes)){
+     p_metro_map <- p_metro_map + labs(caption = notes)
+  }
+
+  return(p_metro_map)
+}
+```
+
+```{r precision-combined, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+library(ggplot2)
+library(cowplot)
+
+p_196_icbe <- icbe_crisismaps(thiscrisis=196) +
+    labs(
+      #title = plot_title ,
+      #subtitle = subtitle ,
+      caption = NULL
+    ) +
+      theme(plot.margin=unit(c(0,0,0,0),"in")) +
+  scale_x_continuous(expand = expansion(mult = c(0.06, 0.05))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
+
+ratio=.75
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_icbe.png'),
+          p_196_icbe, base_height = 18, base_width = height*ratio)
+
+p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
+    labs(
+      #title = plot_title ,
+      #subtitle = subtitle ,
+      caption = NULL
+    ) +
+    theme(plot.margin=unit(c(0,0,0,0),"in")) +
+   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
+
+ratio=.75
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_icbe.png'),
+          p_471_icbe, base_height = 18, base_width = height*ratio)
+
+p_precision_combined <- plot_grid(
+            p_196_icbe +
+    theme(plot.margin=unit(c(0,0,0,0),"in")) +
+   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
+               p_471_icbe +
+    theme(plot.margin=unit(c(0,0,0,0),"in")) +
+   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
+           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )
+
+ratio=1.5
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_precision_combined.png'),
+          p_precision_combined, base_height = 18, base_width = height*ratio)
+
+```
+
+```{r sentences-unique, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+library(flextable)
+library(ftExtra)
+library(tidyverse)
+
+#Load it here before the python reticulate business
+#devtools::install_github("ropenscilabs/umapr")
+#library(umapr)
+
+ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
+
+ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
+                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
+                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
+                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
+                                                 str_replace_all("[0-9]{4}","Entity") %>% #All years with entity
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("[0-9]","") %>%  #replace all digits with blanks
+                                                 str_replace_all(" {1,}"," ")   
+                                               )  #
+
+sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
+                    dplyr::select(sentences_unique_sanitized) %>% 
+                    distinct() %>%
+                    pull(sentences_unique_sanitized) %>% 
+                    unique() %>% na.omit()
+length(sentences_unique ) #12162
+head(sentences_unique)
+```
+
+```{r reticulate, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+#To set python, set it in ~/.Renviron.
+`use_python()` doesn't seem to work as desired.
+See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
+
+library(reticulate)
+reticulate::py_discover_config()
+
+#use_python("/home/skynet3/anaconda3/bin/python/")
+#use_python("/home/tlscherer/anaconda3/bin/python3")
+#py_install("sentence-transformers")
+```
+
+```{python sentence-transformers, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
+#pip install -U sentence-transformers
+
+fromscratch=False
+
+if fromscratch:
+  from sentence_transformers import SentenceTransformer
+  import numpy as np
+  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
+  sentence_chars = np.array([len(q) for q in sentences])
+  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
+  len(sentences) #12161 12162
+  n=len(sentences)
+  chunk_length=100
+  n_chunks = int(np.ceil(n/chunk_length)) #can only 
+  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
+  len(sentences_chunks)
+  len(sentences_chunks[0])  
+  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
+  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
+  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
+  model = SentenceTransformer('paraphrase-mpnet-base-v2')
+  #sentences
+  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
+  #temp = model.encode(sentences_chunks[0])
+  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
+  sentences_embeddings.shape #(12103, 768)
+
+else:
+  print("Skipping")
+```
+
+```{r sentence-embeddings, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+fromscratch = FALSE
+if(fromscratch){
+  sentences_embeddings <- py$sentences_embeddings
+  dim(sentences_embeddings)
+  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
+}else{
+  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
+  dim(sentences_embeddings)
+}
+```
+
+```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=F}
+#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.
+
+# AG temp edit: revert by deleting 'eval=F' above
+
+embedding <- umapr::umap(sentences_embeddings)
+#plot(embedding[,c('UMAP1','UMAP2')])
+
+sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
+sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()
+
+sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
+sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique
+
+ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
+                                        left_join(sentences_embeded_umap) %>% 
+                                  --------------------------      left_join(sentences_embeded_mpnet)
+
+ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
+
+ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
+                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
+                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
+                                                arrange(UMAP1,UMAP2) %>%
+                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis
+```
+
+```{r sentence-embeddings-dendro, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+
+# AG temp edit: revert by setting 'eval=T'
+
+library(cowplot)
+ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
+
+newcolors <- pals::glasbey()
+
+value_means <- ICBe_events_agreed_markdown_embedded %>% 
+               left_join(icb_events_long %>% 
+                           filter(varname_normalized %>% str_detect('escalate|coop|sayintkind|thinkkind')) %>%
+                           filter(!value_normalized %>% str_detect('^[0-9]*$'))) %>%
+               mutate(color=NA) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_escalate"),"red",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_deescalate"),"darkgreen",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("sayintkind"),"brown",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("thinkkind"),"darkorange",color)) %>%
+               dplyr::select(-varname_normalized,-value_qcode,-varname_normalized,-crisis_text,-crisno,-sentence_number_int_aligned,-sentence_span_text,
+                             -actor_set,-value_markdown,-sentence_span_text_clean,-sentences_unique_sanitized) %>% # 
+               group_by(color, value_normalized) %>%
+               mutate(n=n()) %>%
+               filter(n>20) %>% #note require at least 20 examples of that tag
+               dplyr::summarise_all(median) %>%
+              na.omit()
+
+value_normalized_colors <- value_means$color 
+names(value_normalized_colors) = value_means$value
+
+library(ggplot2)
+library(ggrepel)
+p_semantic_embeddings <-
+      ICBe_events_agreed_markdown_embedded %>%
+      ggplot(aes(x=UMAP2,y=UMAP1)) +
+      geom_point(size=0.5, alpha=0.25) + 
+      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
+      theme_bw() +
+      theme(legend.position = "none") + 
+      geom_label(data=value_means,
+                 aes(x=UMAP2,y=UMAP1,
+                     fill = value_normalized %>% as.factor(),
+                     label=value_normalized, size=50
+                     ), size = 2.5,
+                 inherit.aes=F, 
+                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
+                 ) +   
+      #geom_label_repel(data=value_means,
+      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
+      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
+      #           min.segment.length = 0
+      #           ) + 
+      # labs(
+      #     title = "Variation in Tags by Semantic Embeddings of Source Sentences",
+      #     subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
+      #     caption = ""
+      # ) +
+     #scale_color_manual(values = value_normalized_colors) +
+     scale_fill_manual(values = value_normalized_colors) +
+     scale_x_continuous(expand = c(0, 0)) +
+     scale_y_continuous( expand = c(0, 0)) #+
+     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
+     #coord_flip()
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+
+#Now do the dendro
+library(ggdendro)
+#We actually need the raw embeddings
+
+#Rex Note to take only one per sentence
+value_normalized_colors <- value_means$color 
+names(value_normalized_colors) = value_means$value_normalized
+
+m <- value_means %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix()
+rownames(m) <- value_means$value_normalized
+d <- m %>% dist()
+hc <- hclust(d, method="ward.D2")
+library(ggplot2)
+library(ggdendro)
+hcdata <- dendro_data(hc, type = "rectangle")
+p_dendro <- ggplot() +
+            geom_segment(data = segment(hcdata), 
+                         aes(x = x, y = y, xend = xend, yend = yend)
+            ) +
+            geom_text(data = ggdendro::label(hcdata) %>% mutate(color=value_normalized_colors[hcdata$labels$label] ), 
+                      aes(x = x, y = y, label = label, hjust = 0,
+                          color=label %>% as.factor()), 
+                      size = 3
+            ) +
+            coord_flip() +
+            scale_color_manual(values = value_normalized_colors) +
+            scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
+            scale_y_reverse( expand = c(0.1, 0.0, 0.0, 5.0)) +  #limits = c(-10, 10),
+            theme_bw() +
+            theme(legend.position="none")
+#p_dendro
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)
+
+p_combined <- plot_grid(
+  NULL,
+  p_semantic_embeddings + xlab("") + ylab("") + 
+  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
+  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
+  NULL,
+  p_dendro  + xlab("") + ylab("") + 
+  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
+  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),  
+  labels = c('',''),
+  align = "v", nrow = 1, rel_widths = c(-.2, 3.5, -.4, 1.5)  ) #increase the second width to give the dendro more room
+#p_combined
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+```
+
+@fig-umap shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^9] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
+If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the right-hand side.[^10]
+
+![Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
+Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
+Label placement is the median of all of the sentences that the tag was applied to by the coders.
+The dendrogram shows hierarchical clustering of the tags.
+If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap}
+
+Finally, how does ICBe's precision compare to the existing state of the art?
+The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
+On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
+Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
+
+However, given their high recall on our task and the global and real-time coverage of dictionary-based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
+For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by de-trending violent event counts from Phoenix using a human-coded baseline.
+Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
+geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks2018].
+
+# Case illustrations
+
+In this section, we focus our validation on two case studies for which we have produced synthetic narratives using the method described above.
+Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
+The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
+The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion (hereafter Crimea-Donbas).
+We choose these cases because they are substantively significant to 20th and 21st-century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
+Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to a hostile regime, with implications for economic and military security for the superpower, risked full-scale invasion, and eventually invited intervention by opposing superpowers.
+
+```{r recall-cuba, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 #Lit review
@@
 
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
+```{r recall-crimea, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 library(dplyr)
@@
 
-```{r, recall combined, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+```{r recall-combined, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+
+# AG temp edit: revert by setting 'eval=T'
 
@@
     save_as_image(path=here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
+```
+
+```{r recall-all, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 #Recall Summary Statistics
@@
 image_write(combined, here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea_andcounts.png"))
-
-```
-
-```{=tex}
-\clearpage
-\singlespacing
-```
-<!-- \onecolumn -->
-
-```{=tex}
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).}
-\end{figure}
-\clearpage
-\doublespacing
-```
-<!-- \twocolumn -->
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode-level datasets have low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
-
-# Precision
-
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history.
-It does little good to recall a historical event but too vaguely (e.g.
-MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
-ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system are designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out the events of a crisis on a timeline, as in Figure 3, and read off the macrostructure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study in SI Appendix 4.3 and 4.4 and for all crises on the companion website.
-
-```{r crisis map function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-global_check_overlap=F
-library(igraph)
-library(RColorBrewer)
-library(ggraph)
-target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
-dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
-                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
-
-actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
-                                sheet="actor_translator") #%>% janitor::clean_names() 
-#Convert to a local file for pushing
-#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
-pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
-library(pals); #install.packages('pals')
-pallet <- c(pals::glasbey(),  pals::alphabet2())
-pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
-library(colorspace)
-#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
-pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
-actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
-
-icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){
-
-  icb_events_subset <-  ICBe_events_agreed %>% 
-                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
-                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
-                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
-                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
-                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
-                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
-                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
-                         tidyr::fill(decade, .direction="downup") %>%
-                         tidyr::fill(year, .direction="downup") %>%
-                         tidyr::fill(month, .direction="downup") %>%
-                         tidyr::fill(day, .direction="downup") %>% 
-                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
-                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
-                         arrange(decade, year,month,day) %>%
-                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
-
-  icb_events_subset_diad <- icb_events_subset %>% 
-                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                    sent,
-                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                    thinkkind, sayintkind, dokind,
-                                                    point_in_time_year, point_in_time_month
-                                                    ) %>% distinct() %>%
-                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
-
-  notes=NULL
-  if(prune_rare==T){
-    actor_sent_counts <- 
-      bind_rows(
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
-        ) %>% 
-          na.omit() %>%
-          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
-
-      #New pruning rule, either singletons or actors with less than 10% of the max actor
-      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
-      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
-      if(left_over_count<3){
-        #Skip pruning if it leaves less than 3 actors
-      } else {
-
-        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
-        actor_singleton_labels <- actor_map$value_normalized_label
-        names(actor_singleton_labels) <- actor_map$actor
-        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
-
-        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
-
-        #Easiest thing is to just prune the original data
-        icb_events_subset <- icb_events_subset %>%
-          filter(!(
-                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                say_actor_a %in% singleton_actors |
-                say_actor_b %in% singleton_actors |
-                do_actor_a %in% singleton_actors |
-                do_actor_b %in% singleton_actors 
-          ) )
-
-          #recreate diads again using the new sentence numbers
-          icb_events_subset_diad <- icb_events_subset %>% 
-                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                            sent,
-                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                            thinkkind, sayintkind, dokind,
-                                                            point_in_time_year, point_in_time_month
-                                                            ) %>% distinct() %>%
-                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
-                                        filter(!(
-                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                                              say_actor_a %in% singleton_actors |
-                                              say_actor_b %in% singleton_actors |
-                                              do_actor_a %in% singleton_actors |
-                                              do_actor_b %in% singleton_actors 
-                                        ) ) %>% 
-                                       arrange(sent) %>%
-                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
-      }
-  }
-
-  g <- make_empty_graph(n = 0, directed = TRUE)
-    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
-
-  #Order actors by how many interactions they have together
-  temp <- bind_rows(
-    icb_events_subset_diad  %>% 
-      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
-    icb_events_subset_diad %>% 
-      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
-  )  %>% arrange(actor_1, actor_2) %>% distinct()
-
-  #new plan is to minimize the number of crossovers
-  temp2 <- bind_rows(
-    temp,
-    temp %>% setNames(c("actor_2", "actor_1", "sent"))
-  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
-  rowwise() %>%
-  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
-  arrange(desc(n))
-
-  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
-  rownames(temp2_wide) <- temp2_wide$actor_1
-  temp2_wide$actor_1 <- NULL
-  temp2_wide <- temp2_wide %>% as.matrix()
-  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
-  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
-  hc <- hclust(temp2_wide %>% as.dist(), method="single")
-  diag(temp2_wide) <- 0
-  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
-
-  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
-  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
-
-  #####Nodes
-  icb_events_subset_nodes <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
-            )  %>%
-            filter(!is.na(actor)) %>%
-           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
-            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
-                   y=sent*-1 *100)
-
-  icbe_actor_to_qcode <- icb_events_long %>%
-                         dplyr::filter(crisno==thiscrisis  ) %>% 
-                         filter(varname_normalized %>% str_detect("actor")) %>% 
-                         dplyr::select(value_normalized,value_qcode) %>% 
-                         na.omit() %>% distinct()
-
-  actor_colors_df <- icbe_actor_to_qcode %>%
-    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
-  actor_colors <- actor_colors_df$actor_color
-  names(actor_colors) = actor_colors_df$value_normalized
-
-  date_sineposts <- icb_events_subset_nodes  %>%
-                      mutate(x=max(x)+50) %>%
-                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
-                      na.omit() %>% 
-                      distinct() %>%  
-                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
-                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
-                      group_by(sent) %>%
-                       filter(year_float==min(year_float)) %>%
-                      ungroup() %>% as.data.frame() %>%
-                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
-                      filter(!duplicated(year_float ) ) %>%
-                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
-
-  ####Actor levels
-  icb_events_subset_nodes_min <- 
-    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
-    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
-    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
-    rowwise() #%>%
-    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
-
-  for(i in 1:nrow(icb_events_subset_nodes)){
-    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
-                                actor = icb_events_subset_nodes$actor[i], 
-                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
-  }
-
-  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
-
-  #####Time Edges
-  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
-
-  g <- g %>% 
-       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
-
-  ######Monads
-  icb_events_subset_monad <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            filter(!duplicated(paste(sent,actor,leaf))) %>%
-            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
-            distinct() %>% 
-            group_by(sent,actor,actor_sent) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>%
-            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
-
-  ######Directed
-  icb_events_subset_directed <- 
-            #We need to enumerate all the possibilities
-            bind_rows(
-              #Do alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
-              #Say alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
-              #Say Do
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
-              #Think Do
-              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
-            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            arrange(sent, actor_sent_1,leaf) %>%
-            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
-           #It is actually easier just to rejex out some dupes
-            mutate(leaf = leaf %>%
-                     str_replace("accept\naccept","accept") %>%
-                   str_replace("appeal\nappeal","appeal") %>%
-                   str_replace("reject\nreject","reject") %>%
-                   str_replace("express intent\nexpress intent","express intent") 
-                   ) %>%
-           arrange(sent, actor_sent_1,leaf) %>%
-           filter(actor_sent_1!=actor_sent_2)
-
-  #debug
-  icb_events_subset_directed <- icb_events_subset_directed  %>% 
-           group_by(sent, leaf) %>%
-               mutate(bundle_count=n()) %>%
-               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
-            ungroup()
-
-  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                       timeedge=F, 
-                       leaf=icb_events_subset_directed$leaf2, 
-                       eventedge=T,
-                       actor=icb_events_subset_directed$actor_1,
-                       bundle_count=icb_events_subset_directed$bundle_count
-                       )
-
-  ######Put it all together
-  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
-  p_metro_map <- g %>%  
-          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
-
-          #Event edges
-          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
-          geom_edge_arc(aes(  
-                            colour=actor,
-                            label=leaf,
-                            filter=eventedge==T & bundle_count==1 
-                            ),
-                        label_colour=NA, 
-                        vjust = -0.75,
-                        lineheight = .75,
-                        sep = unit(1, 'mm'), 
-                        edge_width=0.25, 
-                        show.legend = F,
-                        arrow = arrow(length = unit(2, 'mm')),
-                        label_size=3,
-                        check_overlap=global_check_overlap,
-                        start_cap = circle(3, 'mm'),
-                        end_cap = circle(3, 'mm'),
-                        angle_calc = 'along' #,
-                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
-                       ) +
-              #Grouped Edges
-              geom_edge_parallel(aes(  
-                                  colour=actor,
-                                  label=leaf,
-                                  filter=eventedge==T & bundle_count>1
-                                  ),
-                              vjust = -0.75,
-                              lineheight = .75,
-                              sep = unit(5, 'mm'), 
-                              edge_width=0.4,  #0.25
-                              show.legend = F,
-                              arrow = arrow(length = unit(1, 'mm')),
-                              label_size=4,
-                              check_overlap=global_check_overlap,
-                              start_cap = circle(3, 'mm'),
-                              end_cap = circle(3, 'mm'),
-                              angle_calc = 'along'
-                             ) +
-
-              #Time edges
-              geom_edge_link(aes(
-                              edge_colour=actor,
-                              filter=timeedge==T
-                              ),
-                              edge_width=0.1, 
-                              show.legend = F,
-                              check_overlap=global_check_overlap
-                             ) +
-              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
-              #Fatalities
-              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
-
-              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
-              #Add Actor Names
-              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
-                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
-                        check_overlap=global_check_overlap) + #-45
-              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
-              scale_color_manual(values = actor_colors)  +
-              scale_edge_color_manual(values = actor_colors) +
-              #theme_bw() + 
-              #labs( title = plot_title ) +
-              theme_graph() +
-              theme(legend.position = "none") #+
-              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
-
-  if(prune_rare==T & !is.null(notes)){
-     p_metro_map <- p_metro_map + labs(caption = notes)
-  }
-
-  return(p_metro_map)
-}
-
-```
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(cowplot)
-
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-      theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  scale_x_continuous(expand = expansion(mult = c(0.06, 0.05))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-ratio=.75
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_icbe.png'),
-          p_196_icbe, base_height = 18, base_width = height*ratio)
-
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-ratio=.75
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_icbe.png'),
-          p_471_icbe, base_height = 18, base_width = height*ratio)
-
-p_precision_combined <- plot_grid(
-            p_196_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
-               p_471_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
-           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )
-
-ratio=1.5
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = height*ratio)
-
-```
-
-We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix 4.1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix 4.2).
-
-We find both the visualizations of macrostructure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall, we seek a more objective detached universal benchmark.
-Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^9] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.[^10]
-
-[^9]: We preprocess sentences to replace named entities with a generic Entity token.
-
-[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
-
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
-On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
-
-However, given their high recall on our task and the global and real-time coverage of dictionary-based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human-coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
-geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks2018].
-
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
+```
+
+## Cuban Missile Crisis (1962)
+
+A synthetic historical narrative for Cuban Missiles appears in @fig-recall-cuba, with 51 events drawn from 2,020 documents.
+Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
+
+Our ground truth ICB narrative contains 17/51 of the events from the synthetic narrative.
+Regarding the crisis start and end dates, the U.S.
+was in a *de facto* grey-scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] but the crisis narrative has a clean canonical end with the Soviets agreeing to withdraw missiles.
+The canonical narrative of this case includes high-level previously classified details.
+
+![Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
+Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).](case_study_cuban_recall.png){#fig-recall-cuba}
+
+@fig-cuba-crisismap shows the crisis map for the Cuban Missile Crisis.
+Looking at the crisis on a timeline, one can now identify the structure of actors and the environment, along with its supporting details, in a way that validates the precision of ICBe.
+
+![Crisis map for the Cuban Missile Crisis.
+The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap}
+
+## Crimea-Donbas (2014)
+
+A synthetic historical narrative for the 2014 Crimea-Donbas crisis (30 events drawn from 971 documents) appears in @fig-recall-crimea.
+As in the earlier case, rows represent details that appeared in at least five documents and whether it is identified in ICBe and existing datasets.
+
+In this case, our ground truth ICB narrative contains 23/30 of the events from the synthetic narrative.
+Like the grey-scale precursor to the Cuban Missile crisis, Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
+a long term lease on naval facilities in Crimea.
+But unlike the Cuban Missile crisis, the end of this crisis is unclear, with the event meekly ending with a second cease-fire agreement (Minsk II) but continued fighting.
+Rather than featuring previously classified details, this more recent case reflects primarily public reporting.
+
+![Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
+Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).](case_study_crimea_recall.png){#fig-recall-crimea}
+
+We take the same approach here in @fig-precision-icews, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
 We choose four event types around key moments in the crisis.
@@
 
-<!-- \clearpage -->
-
-<!-- \onecolumn -->
-
-<!-- \begin{sidewaysfigure}[ht] -->
-
-<!-- \caption{Crisis Maps  \label{fig:p_precision_combined}} -->
-
-<!-- \centering{\includegraphics[width=22cm]{./p_precision_combined.png}} -->
-
-<!-- \end{sidewaysfigure} -->
-
-<!-- \clearpage -->
-
-<!-- \twocolumn -->
-
-```{=tex}
-\singlespacing
-\begin{figure}[H]
-\caption{Crisis Map: Cuban Missile Crisis \label{fig:p_196_icbe}}
-\centering{\includegraphics[width=16cm]{./p_196_icbe.png}}
-\end{figure}
-\doublespacing
-```
-<!-- \begin{figure}[H] -->
-
-<!-- \caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}} -->
-
-<!-- \centering{\includegraphics[width=17cm]{./p_471_icbe.png}} -->
-
-<!-- \end{figure} -->
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(flextable)
-library(ftExtra)
-library(tidyverse)
-
-#Load it here before the python reticulate business
-#devtools::install_github("ropenscilabs/umapr")
-#library(umapr)
-
-ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
-
-ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
-                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
-                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
-                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
-                                                 str_replace_all("[0-9]{4}","Entity") %>% #All years with entity
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("Entity Entity","Entity") %>%
-                                                 str_replace_all("[0-9]","") %>%  #replace all digits with blanks
-                                                 str_replace_all(" {1,}"," ")   
-                                               )  #
-
-sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
-                    dplyr::select(sentences_unique_sanitized) %>% 
-                    distinct() %>%
-                    pull(sentences_unique_sanitized) %>% 
-                    unique() %>% na.omit()
-length(sentences_unique ) #12162
-head(sentences_unique)
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-#To set python, set it in ~/.Renviron.
-`use_python()` doesn't seem to work as desired.
-See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
-
-library(reticulate)
-reticulate::py_discover_config()
-
-#use_python("/home/skynet3/anaconda3/bin/python/")
-#use_python("/home/tlscherer/anaconda3/bin/python3")
-#py_install("sentence-transformers")
-
-```
-
-```{python, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
-#pip install -U sentence-transformers
-
-fromscratch=False
-
-if fromscratch:
-  from sentence_transformers import SentenceTransformer
-  import numpy as np
-  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
-  sentence_chars = np.array([len(q) for q in sentences])
-  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
-  len(sentences) #12161 12162
-  n=len(sentences)
-  chunk_length=100
-  n_chunks = int(np.ceil(n/chunk_length)) #can only 
-  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
-  len(sentences_chunks)
-  len(sentences_chunks[0])  
-  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
-  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
-  model = SentenceTransformer('paraphrase-mpnet-base-v2')
-  #sentences
-  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
-  #temp = model.encode(sentences_chunks[0])
-  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
-  sentences_embeddings.shape #(12103, 768)
-
-else:
-  print("Skipping")
-
-```
-
-```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-fromscratch = FALSE
-if(fromscratch){
-  sentences_embeddings <- py$sentences_embeddings
-  dim(sentences_embeddings)
-  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
-}else{
-  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
-  dim(sentences_embeddings)
-}
-
-```
-
-```{r, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.  
-embedding <- umapr::umap(sentences_embeddings)
-#plot(embedding[,c('UMAP1','UMAP2')])
-
-sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
-sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()
-
-sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
-sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique
-
-ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
-                                        left_join(sentences_embeded_umap) %>% 
-                                        left_join(sentences_embeded_mpnet)
-
-ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
-
-ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
-                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
-                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
-                                                arrange(UMAP1,UMAP2) %>%
-                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis
-
-```
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-library(cowplot)
-ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
-
-newcolors <- pals::glasbey()
-
-value_means <- ICBe_events_agreed_markdown_embedded %>% 
-               left_join(icb_events_long %>% 
-                           filter(varname_normalized %>% str_detect('escalate|coop|sayintkind|thinkkind')) %>%
-                           filter(!value_normalized %>% str_detect('^[0-9]*$'))) %>%
-               mutate(color=NA) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("_escalate"),"red",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("_deescalate"),"darkgreen",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("sayintkind"),"brown",color)) %>%
-               mutate(color=ifelse(varname_normalized %>% str_detect("thinkkind"),"darkorange",color)) %>%
-               dplyr::select(-varname_normalized,-value_qcode,-varname_normalized,-crisis_text,-crisno,-sentence_number_int_aligned,-sentence_span_text,
-                             -actor_set,-value_markdown,-sentence_span_text_clean,-sentences_unique_sanitized) %>% # 
-               group_by(color, value_normalized) %>%
-               mutate(n=n()) %>%
-               filter(n>20) %>% #note require at least 20 examples of that tag
-               dplyr::summarise_all(median) %>%
-              na.omit()
-
-value_normalized_colors <- value_means$color 
-names(value_normalized_colors) = value_means$value
-
-library(ggplot2)
-library(ggrepel)
-p_semantic_embeddings <-
-      ICBe_events_agreed_markdown_embedded %>%
-      ggplot(aes(x=UMAP2,y=UMAP1)) +
-      geom_point(size=0.5, alpha=0.25) + 
-      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
-      theme_bw() +
-      theme(legend.position = "none") + 
-      geom_label(data=value_means,
-                 aes(x=UMAP2,y=UMAP1,
-                     fill = value_normalized %>% as.factor(),
-                     label=value_normalized, size=50
-                     ), size = 2.5,
-                 inherit.aes=F, 
-                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
-                 ) +   
-      #geom_label_repel(data=value_means,
-      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
-      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
-      #           min.segment.length = 0
-      #           ) + 
-      # labs(
-      #     title = "Variation in Tags by Semantic Embeddings of Source Sentences",
-      #     subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
-      #     caption = ""
-      # ) +
-     #scale_color_manual(values = value_normalized_colors) +
-     scale_fill_manual(values = value_normalized_colors) +
-     scale_x_continuous(expand = c(0, 0)) +
-     scale_y_continuous( expand = c(0, 0)) #+
-     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
-     #coord_flip()
-
-ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
-
-#Now do the dendro
-library(ggdendro)
-#We actually need the raw embeddings
-
-#Rex Note to take only one per sentence
-value_normalized_colors <- value_means$color 
-names(value_normalized_colors) = value_means$value_normalized
-
-m <- value_means %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix() 
-rownames(m) <- value_means$value_normalized
-d <- m %>% dist()
-hc <- hclust(d, method="ward.D2")
-library(ggplot2)
-library(ggdendro)
-hcdata <- dendro_data(hc, type = "rectangle")
-p_dendro <- ggplot() +
-            geom_segment(data = segment(hcdata), 
-                         aes(x = x, y = y, xend = xend, yend = yend)
-            ) +
-            geom_text(data = ggdendro::label(hcdata) %>% mutate(color=value_normalized_colors[hcdata$labels$label] ), 
-                      aes(x = x, y = y, label = label, hjust = 0,
-                          color=label %>% as.factor()), 
-                      size = 3
-            ) +
-            coord_flip() +
-            scale_color_manual(values = value_normalized_colors) +
-            scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
-            scale_y_reverse( expand = c(0.1, 0.0, 0.0, 5.0)) +  #limits = c(-10, 10),
-            theme_bw() +
-            theme(legend.position="none")
-#p_dendro
-
-ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)
-
-p_combined <- plot_grid(
-  NULL,
-  p_semantic_embeddings + xlab("") + ylab("") + 
-  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
-  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
-  NULL,
-  p_dendro  + xlab("") + ylab("") + 
-  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
-  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),  
-  labels = c('',''),
-  align = "v", nrow = 1, rel_widths = c(-.2, 3.5, -.4, 1.5)  ) #increase the second width to give the dendro more room
-#p_combined
-
-ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
-
-```
-
-```{=tex}
-\clearpage
-\singlespacing
-```
-<!-- \onecolumn -->
-
-```{=tex}
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that the tag was applied to by the coders.
-The dendrogram shows hierarchical clustering of the tags.
-If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.
-}
-\end{figure}
-\clearpage
-\doublespacing
-```
-<!-- \twocolumn -->
-
-```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+```{r precision, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+
+# AG temp edit: revert by setting 'eval=T'
 
@@
 #}
-
-```
-
-```{=tex}
-\clearpage
-\singlespacing
-```
-<!-- \onecolumn -->
-
-```{=tex}
-\begin{figure}[H]
-\caption{ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
-\textit{Notes: The unit of analysis is the Dyad-Day.
+```
+
+![The unit of analysis is the dyad-day.
 Top 10 most active dyads per category shown.
 Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
-\doublespacing
-```
-<!-- \twocolumn -->
-
-<!-- Edges <-> indicates undirected dyad and -> indicates directed dyad.  # removed from legend with update-->
-
-```{=html}
-<!--
-286 Sign formal agreement
-Reject 99
-
-crisis.
-ICEWS Precision bad for networks  for 
-See [@althausTotalErrorApproach2022] for 19 types of errors in event data.
-Agreement between ICEWS, GED, and CINEP [@stundalHumanRightsViolations2021]
-ICEWs and 
-ICEWs protest events about 80% precision [@wangGrowingPainsGlobal2016],
-
-Dictionary based NLP systems based on large news corpora produce many thousands events over a short time which are unintelligible from the standpoint of micro or macro precision as analyzed above.
-
-Dictionary methods are effectively topic detectors. Dozens of events about signing a deal with the EU that didn't happen.
-
-Next, we make available visualizations of every datum in ICBe alongside each of its contemporary competitors in full on the companion website.
-For ICBe, we show the original source text alongside an iconographic representation of coded events as in Figure 1.
--->
-```
+Blue bars indicate an event recorded by ICEWs for that dyad on that day.](p_precision_icews.png){#fig-precision-icews}
+
 # Conclusion
@@
 
-[^11]: Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
-
 # Funding
 
-This work was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and from the Charles Koch Foundation [20180481].
+This work was supported by a grant from the Office of Naval Research \[N00014-19-1-2491\] and from the Charles Koch Foundation \[20180481\].
 The financial sponsors played no in the design, execution, analysis and interpretation of data, or writing of the study.
@@
 
-The authors declare that there are no competing interestes.
+The authors declare that there are no competing interests.
 
@@
 # Works Cited
+
+[^1]: See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].
+
+[^2]: See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
+On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.
+
+[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
+
+[^4]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
+
+[^5]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
+
+[^6]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
+
+[^7]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
+Undergraduate coders were students who engaged in classroom workshops.
+
+[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
+nationalizing a foreign business).
+Even when they occur in the context of a crisis, these events largely fall outside the sample of information on which ICBe's ontology is currently trained.
+Even with this limitation, ICBe is more comprehensive than the existing datasets that do try to code the economic dimensions of these crises.
+We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
+
+[^9]: We preprocess sentences to replace named entities with a generic Entity token.
+
+[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
+
+[^11]: Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.

### 2023-07-12 replication_paper/psrm_draft/ICBe_manuscript.qmd
AG edits, precision and recall focused

@@
 ---
-title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"
+title: "Introducing ICBe: An Event Extraction Dataset from Narratives about International Crises"
 
@@
 
-If we could record every international interaction in the realms of diplomacy, conflict, economy, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
+If we could record every international interaction in the realms of diplomacy, conflict, economics, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
 In other words, what is the entropy of international relations?
@@
 
-We advance existing efforts to identify and structure regularized events and actor in international politics by using human coders and natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying our ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
+We advance existing efforts to identify and structure regularized events and actor in international politics by combining human coding with natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying our ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
 We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original crisis narrative.
 We conclude by benchmarking our event codings against several current state of the art event data collection efforts.
-We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
 The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
+We find that existing models produce data on historical episodes that do not contain enough information to reconstruct the underlying event.
 In focusing this initial effort on international crises as a proof of concept sample, we demonstrate our ontology and method's potential to improve upon existing empirical identifications of patterns of international interactions.
@@
 
-This measurement paper proceeds in four sections that make the following arguments.
-First, there is a real-world unobserved latent concept known as international relations that can be systematically measured.
-Second, we propose a method for systematic large-scale measurement of the actors and behaviors in international affairs and as a proof of concept apply that method to a well-regarded and salient sample of international events known as international crises.
+In the proceeding four sections, this measurement paper makes the following arguments.
+First, there is a real-world unobserved latent concept known as international relations that can and should be systematically measured.
+Second, we propose a method for systematic large-scale measurement of the actors and behaviors in international affairs and as a proof of concept apply that method to a well-regarded and salient sample of events known as international crises.
 Third, in doing so we confirm that those measurements exhibit several desirable kinds of internal and external validity and out-perform existing approaches.
@@
 
-## Task definition
-
-We consider the measurement task of abstracting discrete events about a historical episode in international relations.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-Each event occurs over a marked time period where we observe the behaviors of a given set of actors.
-Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
-
-The task is to produced a structured account of the historical event by combining the unstructured corpus of historical records with informative priors about international relations.
-The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of historical political events from which we can garner novel insight given the data's high coverage, precision, and recall.
-The easiest way to convey the task is with an example.
-@fig-cuba-narrative shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine-readable abstractive events.
+## Motivation
+
+How can scholars abstract and measure discrete events about a historical episode in international relations?
+We employ a metaphor of chess, a game that despite its complexity can nonetheless be recorded in a standardized and structured manner.
+Like chess, international interactions involve a finite set of players (e.g.
+polities, rebel groups, IGOs) expressing their behaviors (e.g.
+thinking, saying, and doing) by moving pieces (e.g.
+military platforms, civilian personnel, diplomats) from and onto identifiable locations (geo-coded coordinates).
+These moves occur over a marked time period (start and end of a historical episode) and gambits occur in recordable sequences (actions and reactions) to produce observable, if still disputable, outcomes (e.g.
+victory, defeat, stalemate, peace).
+Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
+
+Much like the recording of chess evolved from natural language descriptive text notation to the modern figurine algebra notion, international relations scholars have recently sought to produce a structured account of historical events by combining the unstructured corpus of historical records with informative priors about international relations.
+The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of political events from which we can garner novel insight, assuming the underlying data have high coverage, precision, and recall.
+The easiest way to convey the desired produced of this task is with an example.
+@fig-cuba-narrative shows a narrative account of the Cuban Missile Crisis (1962) in natural language sentences alongside a mapping to discrete machine-readable abstractive events.
+From the structured data, scholars can identify similarities and differences across events concerning important concepts like when particular foreign policy actions deter versus inflame [@jervisCooperationSecurityDilemma1978; @glaserCausesConsequencesArms2000], when third parties mediate in interstate disputes [@haffarEmergentPeacemakersCataloguing2002; @quinnPowerPlayMediation2006], and how actors try to communicate resolve [@tragerDiplomacyWarPeace2016; @luptonReexaminingReputationResolve2018].
+Identifying patterns of international interactions is not just an inherently interesting enterprise; it is a necessary precondition to important efforts to predict where policymakers should turn their attention to improve global welfare [@wardLearningSteppingFuture2013; @begerReassessingRoleTheory2021].
 
@@
 
-We draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes.
-The first is the extensive existing measurement efforts of IR, detailed below.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number of hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
-
-Table 1 describes the underlying structure of international crises that we hope to uncover as well as existing efforts to identify the actors and actions of international relations.
-The rows represent the types of information we expect to find in IR and forms the basis for our proposed ontology.
-The columns compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+We draw informative prior beliefs about the underlying process of international relations that we expect to govern behavior during historical episodes and their conversion to the historical record.
+We organize our prior beliefs along two overarching axes: existing efforts to identify the actors/actions of international relations and identifying a corpus that can be used to produce an ontology of the information we hope to recover.
+Table 1 describes these two axes as columns and rows, respectively.
+
+As we are not the first to attempt to measure international relations in a structured manner, the columns of Table 1 compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
+We choose these datasets and models as they represent frequently used and reputable efforts to structure and describe historical events of interest to scholars of international politics.
+The first column starts with our contribution, ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+There is imperfect overlap concerning their intended depth and scope of coverage; 'international crises' are similar, but not identical to, 'interstate wars' and 'militarized interstate disputes' which differ yet again from 'individual events of organized violence' and 'non-violent action'.
+Even like-concepts require care in comparison, as an 'aim' in ICBe is the same as in MIPS, but an 'alert' in ICBe is not the same as an 'alert' in MID.
+Definitions for each ICBe variable are provided in the codebook.
+
+<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; @hegreIntroducingUCDPCandidate2020, @ralphsundbergUCDPGEDCodebook2016-->
 
@@
 
-With the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^4] In particular, we highlight two innovations in our ontology.
-First, we separate the chess pieces from the chess players in not only identifying what states were involved in each crisis, but distinguishing between different actors within a state.
-By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning topics like civilian military relations as well as evolution in what actors are engaged in crises - a topic of increasing interest as states engage in "gray zone conflict" by employing "chess pieces" like the coast guard instead of military navy.
+The rows in Table 1 represent the types of information we expect to find in international relations and forms the basis for our proposed ontology.
+We create this by performing preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
+Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number of hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
+This comparison is not intended to fault existing data and models for not including every variable in ICBe's ontology, as some of these variables fall outside the scope of a particular dataset's intended purpose.
+Rather, it serves as an initial basis for identifying the heterogeneity in existing efforts to abstract and measure discrete historical events of interest and to provide theoretical justifications from existing research about what is included in our dataset's ontology and where ICBe's detail about historical events can be compared to the current state of the art.
+
+With the exception of large-scale CAMEO dictionary-based systems (the first grouping of columns), our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^4] We highlight two particular innovations.
+First, we separate the 'chess pieces' from the 'chess players' in distinguishing between different actors within a state.
+By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning civilian-military relations [@narangCivilmilitaryPathologiesDefeat2017], Track Two diplomacy and the role of sub-national actors [@hsuStatesHarnessingSubnational2020], and the evolution of what actors are engaged in crises - a topic of increasing interest as states engage in gray zone conflict by employing the coast guard or paramilitary mercenaries instead of internationally recognized state militaries [@gannon_shadowdeterrencewhy_2023].
 Second, we add information about the domains in which actors behave - whether in land, air, sea, space, or cyber - since they differ in their technology, tactics, geography, and purpose [@gartzkeCrossDomainDeterrenceStrategy2019].
@@
 
-<!-- removedcites @braithwaiteMIDLOCIntroducingMilitarized2010; @braithwaiteCodebookMilitarizedInterstate2009; @hegreIntroducingUCDPCandidate2020, @ralphsundbergUCDPGEDCodebook2016-->
-
 # Methodology and data
@@
 
-For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
+For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$) with coverage spanning 1918-2017 (Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
 ICB defines a crisis as meeting three conditions: (1) an actor perceives a threat to one of more of its basic values, (2) the actor has a finite time horizon for responding to the perceived threat, and (3) the probability of military hostility has increased [@brecherCrisesWorldPolitics1982].
-Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in international relations short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+The corpus is also unique in being designed to be used in a downstream quantitative coding project, meaning each narrative was written by consensus by a small number of scholars using a uniform coding scheme where things like word choice, writing style, and level of specificity were deliberately done in a consistent manner [@hewittEngagingInternationalData2001].
 Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
 59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
 
@@
 
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^5] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information were always collected while other details were only collected if appropriate, e.g.
-force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
+The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^5] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (GUI) (SI Appendix 2.1).
+Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more specific and non-mutually exclusive activities.
+Some additional details were always collected (e.g.
+location and timing) while other details were only collected if appropriate (e.g.
+force size, fatalities, domains, units).
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6] A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
 an offer for the U.S.S.R.
@@
 Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6]
 
@@
 Recall measures the share of desired information recovered by a sequence of coded events while precision measures the degree to which a sequence of events correctly and usefully describes the information in history.
-We provide full ICB narratives, ICBe coding in an easy-to-read iconographic form, and a wide range of visualizations for every case on the companion website.
-
-Recall is poorly defined for historical episodes.
-First, there is no genuine ground truth about what occurred, only surviving texts about it.
+To aid in subjective evaluation of the precision and recall of ICBe for each event, we provide full ICB narratives, ICBe coding in an easy-to-read iconographic form, and a wide range of visualizations for every case on the companion website.
+
+Recall for historical episodes is poorly defined for two reasons.
+History may or may not be written by the victors but by virtue of being written by *someone* there is no genuine ground truth about what occurred, only surviving texts about it [@turberville_historyobjectivesubjective_1933].
 Second, there is no *a priori* guide to what information is necessary detail and what is ignorable trivia.
@@
 Mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.[^8] Furthermore, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events.
-@fig-recall-cases compares ICBe's recall with that of existing datasets for the two case studies in the next section.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode-level datasets have low coverage of contextual details.
+@fig-recall-cases compares ICBe's recall with that of existing datasets for the two case studies detailed in Section 4.
+ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
+Across all existing datasets and ICBe, recall increases with the number of document mentions which is an important sign of validity for both them and our benchmark.
+The one outlier is Phoenix which in the Cuban Missile Crisis case is so noisy that it's recall curve is flat to decreasing as mentions increase.
+The two episode-level datasets (MIDs and ICM) have low coverage of contextual details.
 The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
 Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
@@
 
-The second component of event measurement is precision.
+The second component of event measurement validation is precision.
 It does little good to recall a historical event but too vaguely (e.g.
-MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
-ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
+MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error to be useful for downstream applications (e.g.
+ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019).
 ICBe's ontology and coding system are designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out the events of a crisis on a timeline, as in Figure 3, and read off the macrostructure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study in SI Appendix 4.3 and 4.4 and for all crises on the companion website.
+
+How does ICBe's precision compare to the existing state of the art?
+A researcher should be able to lay out the events of a crisis on a timeline and read off the macrostructure of an episode from each individual move.
+We call this visualization a crisis map, a directed graph intersected with a timeline.
+A crisis map using ICBe for the Cuban Missile Crisis case study is provided in @fig-cuba-crisismap, and crisis maps for the two case studies using existing event datasets can be found in SI Appendix 4.3 and 4.4 and crisis maps for all crises using all datasets can be found on the companion website.
+The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
+On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
+Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
 
@@
 
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
-On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
-
-However, given their high recall on our task and the global and real-time coverage of dictionary-based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by de-trending violent event counts from Phoenix using a human-coded baseline.
-Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
-geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks2018].
-
 # Case illustrations
 
-In this section, we focus our validation on two case studies for which we have produced synthetic narratives using the method described above.
+In this section, we focus our validation on two case studies for which we have produced synthetic narratives using the method described in Section 3.2.
 Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion (hereafter Crimea-Donbas).
-We choose these cases because they are substantively significant to 20th and 21st-century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to a hostile regime, with implications for economic and military security for the superpower, risked full-scale invasion, and eventually invited intervention by opposing superpowers.
+The first (@fig-cuba-narrative) is the Cuban Missile Crisis (hereafter Cuban Missiles) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war.
+The second (SI Appendix 4.1) is the Crimea-Donbas Crisis (hereafter Crimea-Donbas) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion.
+We choose these cases because they are significant in contemporary international relations, are widely known across academic disciplines as well as among the public, and are sufficiently brief to evaluate in depth.
+They are similar in that both cases involve a superpower in crisis with a neighbor that changed from a friendly to a hostile regime, both held implications for the economic and military security for the superpower by risking full-scale invasion, and both eventually invited intervention by an opposing superpower.
 
@@
 A synthetic historical narrative for Cuban Missiles appears in @fig-recall-cuba, with 51 events drawn from 2,020 documents.
-Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-Our ground truth ICB narrative contains 17/51 of the events from the synthetic narrative.
-Regarding the crisis start and end dates, the U.S.
-was in a *de facto* grey-scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] but the crisis narrative has a clean canonical end with the Soviets agreeing to withdraw missiles.
-The canonical narrative of this case includes high-level previously classified details.
+Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of the original ICB corpus, our ICBe events, and any of the competing existing models.
+
+ICB's improved recall of Cuban Missiles was relative to the state of the art was summarized in Section 3.2 (@fig-recall-cases), but the events that explain that improvement can now be seen.
+Our ground truth ICB narrative contains 17/51 of the events from the synthetic narrative of a case that includes high-level previously classified details.
+ICBe captures nearly all details included in ICB as well as more details from the synthetic narrative than any competing dataset.
+Phoenix includes some earlier information than ICBe like the nationalization of businesses and back channel negotiations, but the crisis narrative has a clean canonical end with the Soviets agreeing to withdraw missiles.
+ICBe stands out in including more communicative behavior (do -- speech) than existing datasets like US threats to attack and later promises not to invade.
+Given the recognized importance of threat credibility for understanding international conflict, the addition of this information is a substantively important improvement over the existing state of the art [@slantchev_militarythreatscosts_2011].
 
@@
 Looking at the crisis on a timeline, one can now identify the structure of actors and the environment, along with its supporting details, in a way that validates the precision of ICBe.
+Although harder to measure objectively, this crisis map provides face valid evidence that ICBe's account is not too vague, but also not unnecessarily detailed.
+We include much of the geopolitically important details like Soviet deployment, US discovery of that deployment, heightened alert levels, a blockade, and negotiations that ended with a formal agreement.
+At the same time, the crisis map indicates that ICBe does not include unnecessary nuances that preclude useful comparison to other international events.
 
@@
 
-In this case, our ground truth ICB narrative contains 23/30 of the events from the synthetic narrative.
-Like the grey-scale precursor to the Cuban Missile crisis, Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
+Again quantitatively summarized earlier in Section 3.2 (@fig-recall-cases), our ground truth ICB narrative contains 23/30 of the events from the synthetic narrative.
+Like the gray zone precursor to the Cuban Missile crisis [@cormacGreyNewBlack2018], Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
 a long term lease on naval facilities in Crimea.
 But unlike the Cuban Missile crisis, the end of this crisis is unclear, with the event meekly ending with a second cease-fire agreement (Minsk II) but continued fighting.
-Rather than featuring previously classified details, this more recent case reflects primarily public reporting.
+ICBe again recalls more important information about the crisis than any existing dataset, particularly information concerning the behavior of non-state separatist groups like the Donetsk People's Republic (DPR) and Luhansk People's Republic (LPR).
 
@@
 Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).](case_study_crimea_recall.png){#fig-recall-crimea}
+
+As this more recent case reflects primarily public reporting rather than the previously classified details relevant for the Cuban Missile Crisis, ICBe's improvement relative to the global and real-time coverage of dictionary-based event systems is still present, but less pronounced.
+We want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
+For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by de-trending violent event counts from Phoenix using a human-coded baseline.
+Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
+geolocation [@cookLostAggregationImproving2019], protest events (80%) [@wuestExternalValidationProtest2020], anti-government protest networks (46.1%) [@jagerLimitsStudyingNetworks2018].
 
@@
 
-We release several open-source products along with supporting code and documentation to further advance the study of IR, event extraction, and natural language processing.
+We release several open-source products along with supporting code and documentation to further advance the study of international relations, event extraction, and natural language processing.
 The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.

### 2023-07-12 replication_paper/psrm_draft/ICBe_manuscript.Rmd
pre-pull

@@
 Table 1 demonstrates that with the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^5] In particular, we highlight two innovations in our ontology.
-First, we separate the chess pieces from the chess players in not only identifying what states were involved in each crisis, but distinguishing between different actors within a state.
+First, we separate the chess pieces from the chess players in not only identifying what states were involved in each crisis, but distinguishing between different actors within a state [@gartzkeCrossDomainDeterrenceStrategy2019].
 By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning topics like civilian military relations as well as evolution in what actors are engaged in crises - a topic of increasing interest as states engage in "gray zone conflict" by employing "chess pieces" like the coast guard instead of military navy.

### 2023-07-13 replication_paper/psrm_draft/ICBe_manuscript.Rmd

--- 2023-05-30 replication_paper/psrm_draft/ICBe_manuscript.Rmd
@@
 
-# Introduction
-
-If we could record every international interaction in the realms of diplomacy, conflict, economy, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
+If we could record every international interaction in the realms of diplomacy, conflict, economics, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
 In other words, what is the entropy of international relations?
@@
 
-[^1]: See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].
-
-[^2]: See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
-On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.
-
-<!-- removedcites trade @barariDemocracyTradePolicy,  @vabulasCooperationAutonomyBuilding2021 -->
-
-<!-- removedcites @hegreIntroducingUCDPCandidate2020; ; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019, @vabulasCooperationAutonomyBuilding2021;  -->
-
-Our contribution is using human coders and natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying the ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
+<!-- removedcites @barariDemocracyTradePolicy; @vabulasCooperationAutonomyBuilding2021; @hegreIntroducingUCDPCandidate2020; @haltermanExtractingPoliticalEvents2020; @maozDyadicMilitarizedInterstate2019; @vabulasCooperationAutonomyBuilding2021; -->
+
+We advance existing efforts to identify and structure regularized events and actor in international politics by combining human coding with natural language processing to develop (1) a large, flexible ontology of international affairs and (2) a fine-grained and structured event dataset of international crises from 1918-2017 developed by applying our ontology to an unusually high-quality corpus of historical narratives of international crises [@brecherInternationalStudiesTwentieth1999; @wilkenfeldInterstateCrisesViolence2000; @brecherInternationalCrisisBehavior2021].
 We then develop several methods for objectively gauging how well these event codings reconstruct the information contained in the original crisis narrative.
 We conclude by benchmarking our event codings against several current state of the art event data collection efforts.
-We find that existing systems produce sequences of events that do not contain enough information to reconstruct the underlying historical episode.
 The underlying fine-grained variation in international affairs is unrecognizable through the lens of current quantification efforts.
+We find that existing models produce data on historical episodes that do not contain enough information to reconstruct the underlying event.
 In focusing this initial effort on international crises as a proof of concept sample, we demonstrate our ontology and method's potential to improve upon existing empirical identifications of patterns of international interactions.
 
-<!-- removedcites  @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019; @brecherEscalationWarTwentieth2000; -->
-
-This measurement paper makes the following arguments.
-First, there is a real-world unobserved latent concept known as international relations that can be systematically measured.
-Second, we propose a method for systematic large-scale measurement of the actors and behaviors in international affairs and as a proof of concept apply that method to a well-regarded and salient sample of international events known as international crises.
+<!-- removedcites @jamesWhatWeKnow2019; @iakhnisCrisesWorldPolitics2019; @brecherEscalationWarTwentieth2000 -->
+
+In the proceeding four sections, this measurement paper makes the following arguments.
+First, there is a real-world unobserved latent concept known as international relations that can and should be systematically measured.
+Second, we propose a method for systematic large-scale measurement of the actors and behaviors in international affairs and as a proof of concept apply that method to a well-regarded and salient sample of events known as international crises.
 Third, in doing so we confirm that those measurements exhibit several desirable kinds of internal and external validity and out-perform existing approaches.
-The article organizes that argument into XX sections.
+Fourth, this validation can be evaluated in detail via new event visualizations, with examples provided for case studies of the 1962 Cuban Missile Crisis and 2014 Crimea-Donbas crisis.
 A final section concludes.
 
-# Task Definition
-
-We consider the measurement task of abstracting discrete events about a historical episode in international relations.
-The easiest way to convey the task is with an example.
-Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) alongside a mapping from each natural language sentence to discrete machine-readable abstractive events.
-Each event occurs over a marked time period where we observe the behaviors of a given set of actors.
-Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
-The task is to produced a structured account of the historical event by combining the unstructured corpus of historical records with informative priors about international relations.
-The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of historical political events from which we can garner novel insight given the data's high coverage, precision, and recall.
-
-# Corpus
-
-<!-- ^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]  -->
-
-For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
-ICB defines a crisis as meeting three conditions: (1) an actor perceives a threat to one of more of its basic values, (2) the actor has a finite time horizon for responding to the perceived threat, and (3) the probability of military hostility has increased [@brecherCrisesWorldPolitics1982].
-Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
-Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
-59].
-Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001].
-The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.
-
-<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988; -->
-
-```{r cuban case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+# Identifying and measuring international relations
+
+## Motivation
+
+How can scholars abstract and measure discrete events about a historical episode in international relations?
+We employ a metaphor of chess, a game that despite its complexity can nonetheless be recorded in a standardized and structured manner.
+Like chess, international interactions involve a finite set of players (e.g.
+polities, rebel groups, IGOs) expressing their behaviors (e.g.
+thinking, saying, and doing) by moving pieces (e.g.
+military platforms, civilian personnel, diplomats) from and onto identifiable locations (geo-coded coordinates).
+These moves occur over a marked time period (start and end of a historical episode) and gambits occur in recordable sequences (actions and reactions) to produce observable, if still disputable, outcomes (e.g.
+victory, defeat, stalemate, peace).
+Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
+
+Much like the recording of chess evolved from natural language descriptive text notation to the modern figurine algebra notion, international relations scholars have recently sought to produce a structured account of historical events by combining the unstructured corpus of historical records with informative priors about international relations.
+The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of political events from which we can garner novel insight, assuming the underlying data have high coverage, precision, and recall.
+The easiest way to convey the desired produced of this task is with an example.
+@fig-cuba-narrative shows a narrative account of the Cuban Missile Crisis (1962) in natural language sentences alongside a mapping to discrete machine-readable abstractive events.
+From the structured data, scholars can identify similarities and differences across events concerning important concepts like when particular foreign policy actions deter versus inflame [@jervisCooperationSecurityDilemma1978; @glaserCausesConsequencesArms2000], when third parties mediate in interstate disputes [@haffarEmergentPeacemakersCataloguing2002; @quinnPowerPlayMediation2006], and how actors try to communicate resolve [@tragerDiplomacyWarPeace2016; @luptonReexaminingReputationResolve2018].
+Identifying patterns of international interactions is not just an inherently interesting enterprise; it is a necessary precondition to important efforts to predict where policymakers should turn their attention to improve global welfare [@wardLearningSteppingFuture2013; @begerReassessingRoleTheory2021].
+
+```{r cuban-case-study-precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+# AG temp edit: revert by setting eval=T DONE
 
@@
 
-ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","psrm_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+# TS temp edit: following line plotted for temporary fix
+# ft_cuba_precision %>% flextable::save_as_image(path=here::here("replication_paper","psrm_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
-
-```
-
-<!--- REX Remember to put in a Legend for the Icons ---->
-
-\clearpage
-
-<!-- \onecolumn -->
-
-```{=tex}
-\begin{figure}[H]
-\caption{Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
-\clearpage
-```
-<!-- \twocolumn -->
-
-# Prior Beliefs about IR, Ontological Coverage, and the Existing State of the Art
-
-Next, we draw informative prior beliefs about the underlying process of IR that we expect to govern behavior during historical episodes and their conversion to the historical record.
-We organize our prior beliefs along two overarching axes, summarized in detail by Table 1.
-
-We base our informed priors primarily on two sources of information.
-The first is the extensive existing measurement efforts of IR which we provide citations alongside each concept.
-Second, we performed preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number of hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
-
-The columns compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
-They begin with our contribution ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
-
-[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
-
-The rows represent the types of information we expect to find in IR and forms the basis for our proposed ontology.
-We employ a metaphor of a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do).
-Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^4]
-
-[^4]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
-
-Table 1 demonstrates that with the exception of large-scale CAMEO dictionary-based systems, our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^5] In particular,
-
-[^5]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
-
--   separating chess pieces from players (military vs civilian)
-
--   addition of domains
+```
+
+![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative}
+
+## Existing state of the art measurements
+
+We draw informative prior beliefs about the underlying process of international relations that we expect to govern behavior during historical episodes and their conversion to the historical record.
+We organize our prior beliefs along two overarching axes: existing efforts to identify the actors/actions of international relations and identifying a corpus that can be used to produce an ontology of the information we hope to recover.
+Table 1 describes these two axes as columns and rows, respectively.
+
+As we are not the first to attempt to measure international relations in a structured manner, the columns of Table 1 compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
+We choose these datasets and models as they represent frequently used and reputable efforts to structure and describe historical events of interest to scholars of international politics.
+The first column starts with our contribution, ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+There is imperfect overlap concerning their intended depth and scope of coverage; 'international crises' are similar, but not identical to, 'interstate wars' and 'militarized interstate disputes' which differ yet again from 'individual events of organized violence' and 'non-violent action'.
+Even like-concepts require care in comparison, as an 'aim' in ICBe is the same as in MIPS, but an 'alert' in ICBe is not the same as an 'alert' in MID.
+Definitions for each ICBe variable are provided in the codebook.
 
@@
 avg_coders_per_sentence <- icb_long_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_sent = paste(crisno, sentence_number_int_aligned)) %>% dplyr::select(cris_sent, email_id) %>% unique() %>% dplyr::count(cris_sent) %>% dplyr::select(n) %>% lapply(mean)
-
-```
-
-# ICBe Coding Process
-
-The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^6] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (SI Appendix 2.1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more non-mutually exclusive specific activities.
-Some additional details like location and timing information were always collected while other details were only collected if appropriate, e.g.
-force size, fatalities, domains, units, etc.
-A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
+```
+
+The rows in Table 1 represent the types of information we expect to find in international relations and forms the basis for our proposed ontology.
+We create this by performing preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
+Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number of hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
+This comparison is not intended to fault existing data and models for not including every variable in ICBe's ontology, as some of these variables fall outside the scope of a particular dataset's intended purpose.
+Rather, it serves as an initial basis for identifying the heterogeneity in existing efforts to abstract and measure discrete historical events of interest and to provide theoretical justifications from existing research about what is included in our dataset's ontology and where ICBe's detail about historical events can be compared to the current state of the art.
+
+With the exception of large-scale CAMEO dictionary-based systems (the first grouping of columns), our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^4] We highlight two particular innovations.
+First, we separate the 'chess pieces' from the 'chess players' in distinguishing between different actors within a state.
+By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning civilian-military relations [@narangCivilmilitaryPathologiesDefeat2017], Track Two diplomacy and the role of sub-national actors [@hsuStatesHarnessingSubnational2020], and the evolution of what actors are engaged in crises - a topic of increasing interest as states engage in gray zone conflict by employing the coast guard or paramilitary mercenaries instead of internationally recognized state militaries [@gannon_shadowdeterrencewhy_2023].
+Second, we add information about the domains in which actors behave - whether in land, air, sea, space, or cyber - since they differ in their technology, tactics, geography, and purpose [@gartzkeCrossDomainDeterrenceStrategy2019].
+Doing so allows researchers to identify and explain patterns in escalation conditional on the military means states use in conflict.
+Recent concerns about cross-domain conflict and the effect of new domains of conflict like space and cyber have made this an endeavor of increased interest to practitioners [@gannonOneIfLand2022].
+
+# Methodology and data
+
+## Corpus
+
+For our corpus, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$) with coverage spanning 1918-2017 (Supplementary Information (SI) Appendix 1.1)[@brecherInternationalCrisisBehavior2021; @brecher_study_1997].
+ICB defines a crisis as meeting three conditions: (1) an actor perceives a threat to one of more of its basic values, (2) the actor has a finite time horizon for responding to the perceived threat, and (3) the probability of military hostility has increased [@brecherCrisesWorldPolitics1982].
+Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in international relations short of, or at least prior to, full conflict [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @gavinHistorySecurityStudies2014; @brecherCrisesWorldPolitics1982; @iakhnisCrisesWorldPolitics2019].
+The corpus is also unique in being designed to be used in a downstream quantitative coding project, meaning each narrative was written by consensus by a small number of scholars using a uniform coding scheme where things like word choice, writing style, and level of specificity were deliberately done in a consistent manner [@hewittEngagingInternationalData2001].
+Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2021 p.
+59].
+
+<!-- removedcites @snyderConflictNationsBargaining1977; @gaddisExpandingDataBase1987; @georgeDeterrenceAmericanForeign1974; @brecherPatternsCrisisManagement1988 -->
+
+## Coding Process
+
+The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^5] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (GUI) (SI Appendix 2.1).
+Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more specific and non-mutually exclusive activities.
+Some additional details were always collected (e.g.
+location and timing) while other details were only collected if appropriate (e.g.
+force size, fatalities, domains, units).
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6] A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
 an offer for the U.S.S.R.
@@
 
-[^6]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
-
 Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.[^7] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
@@
 
-# Case Study Selection
-
-The remaining two qualities we seek to measure are recall and precision of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy-to-read iconographic form, and a wide range of visualizations for every case on the companion website.
-In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war (hereafter Cuban Missiles).
-The second is the Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion (hereafter Crimea-Donbas).
-Both cases involve a superpower in crisis with a neighbor, initiated by a change from a friendly to a hostile regime, with implications for economic and military security for the superpower, risked full-scale invasion, and eventually invited intervention by opposing superpowers.
-We choose these cases because they are substantively significant to 20th and 21st-century international relations, widely known across scientific disciplines and popular culture, and are sufficiently brief to evaluate in depth.
-
-# Recall
-
-Recall measures the share of desired information recovered by a sequence of coded events, and is poorly defined for historical episodes.
-First, there is no genuine ground truth about what occurred, only surviving texts about it.
-Second, there is no \textit{a priori} guide to what information is necessary detail and what is ignorable trivia.
-History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in, the more detail you will find about individual events and in between every two discrete events.
+## Improvement over existing efforts
+
+To evaluate our coding process relative to existing datasets, we measure the recall and precision of ICBe events in absolute terms and relative to other existing systems.
+Recall measures the share of desired information recovered by a sequence of coded events while precision measures the degree to which a sequence of events correctly and usefully describes the information in history.
+To aid in subjective evaluation of the precision and recall of ICBe for each event, we provide full ICB narratives, ICBe coding in an easy-to-read iconographic form, and a wide range of visualizations for every case on the companion website.
+
+Recall for historical episodes is poorly defined for two reasons.
+History may or may not be written by the victors but by virtue of being written by *someone* there is no genuine ground truth about what occurred, only surviving texts about it [@turberville_historyobjectivesubjective_1933].
+Second, there is no *a priori* guide to what information is necessary detail and what is ignorable trivia.
+History suffers from what is known as the Coastline Paradox [@mandelbrotFractalGeometryNature1983] --- it has a fractal dimension greater than one such that the more you zoom in, the more detail you will find about individual events as well as in between any two discrete events.
 The ICBe ontology is a proposal about what information is important, but we need an independent benchmark to evaluate whether that proposal is a good one and that allows for comparing proposals from event projects that had different goals.
@@
 
-Synthetic historical narratives for Cuban Missiles (51 events drawn from 2020 documents) and Crimea-Donbas (30 events drawn from 971 documents) appear in Figure 2.
-Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of our ICB corpus, in our ICBe events, or any of the competing systems.
-
-From them, we draw several stylized facts.
-First, there is substantial variation in which details any one document will choose to include.
-Our ground truth ICB narratives contain 17/51 and 23/30 of the events from the synthetic narrative and include other details that are not in the synthetic narrative.[^8] Second, mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.
-Third, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events, e.g.
-the U.S.
-was in a \textit{de facto} grey-scale war with Cuba before it invited Soviet military protection [@cormacGreyNewBlack2018] and Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
-a long term lease on naval facilities in Crimea.
-Fourth, we find variation between the two cases.
-Cuban Missiles has a cleaner canonical end with the Soviets agreeing to withdraw missiles while Crimea-Donbas meekly ends with a second cease-fire agreement (Minsk II) but continued fighting.
-The canonical narrative of Cuban Missiles also includes high-level previously classified details, while the more recent Crimea-Donbas case reflects primarily public reporting.
-
-[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
-nationalizing a foreign business).
-Even when they occur in the context of a crisis, these events largely fall outside the sample of information on which ICBe's ontology is currently trained.
-Even with this limitation, ICBe is more comprehensive than the existing datasets that *do* try to code the economic dimensions of these crises.
-We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
-
-```{r cuban case study recall, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-#
+We find substantive variation in recall across existing state of the art methods.
+Mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.[^8] Furthermore, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events.
+@fig-recall-cases compares ICBe's recall with that of existing datasets for the two case studies detailed in Section 4.
+ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
+Across all existing datasets and ICBe, recall increases with the number of document mentions which is an important sign of validity for both them and our benchmark.
+The one outlier is Phoenix which in the Cuban Missile Crisis case is so noisy that it's recall curve is flat to decreasing as mentions increase.
+The two episode-level datasets (MIDs and ICM) have low coverage of contextual details.
+The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
+Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
+
+![Recall comparison of two cases across existing state of the art efforts.
+Higher y-axis values represent higher recall and higher x-axis values represent number of times that detail is mentioned across the full corpus used to construct the synthetic narrative.](p_recall.png){#fig-recall-cases}
+
+The second component of event measurement validation is precision.
+It does little good to recall a historical event but too vaguely (e.g.
+MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error to be useful for downstream applications (e.g.
+ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019).
+ICBe's ontology and coding system are designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
+
+How does ICBe's precision compare to the existing state of the art?
+A researcher should be able to lay out the events of a crisis on a timeline and read off the macrostructure of an episode from each individual move.
+We call this visualization a crisis map, a directed graph intersected with a timeline.
+A crisis map using ICBe for the Cuban Missile Crisis case study is provided in @fig-cuba-crisismap, and crisis maps for the two case studies using existing event datasets can be found in SI Appendix 4.3 and 4.4 and crisis maps for all crises using all datasets can be found on the companion website.
+The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
+On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
+Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
+
+We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
+We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative for every case on the companion website.
+We further provide a stratified sample of event codings alongside their source text (SI Appendix 4.2).
+We find both the visualizations of macrostructure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe.
+
+```{r crisis-map-function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+global_check_overlap=F
+library(igraph)
+library(RColorBrewer)
+library(ggraph)
+target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
+dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
+                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
+
+actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
+                                sheet="actor_translator") #%>% janitor::clean_names() 
+#Convert to a local file for pushing
+#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
+pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
+library(pals); #install.packages('pals')
+pallet <- c(pals::glasbey(),  pals::alphabet2())
+pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
+library(colorspace)
+#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
+pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
+actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
+
+icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){
+
+  icb_events_subset <-  ICBe_events_agreed %>% 
+                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
+                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
+                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
+                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
+                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
+                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
+                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
+                         tidyr::fill(decade, .direction="downup") %>%
+                         tidyr::fill(year, .direction="downup") %>%
+                         tidyr::fill(month, .direction="downup") %>%
+                         tidyr::fill(day, .direction="downup") %>% 
+                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
+                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
+                         arrange(decade, year,month,day) %>%
+                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
+
+  icb_events_subset_diad <- icb_events_subset %>% 
+                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
+                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
+                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
+                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
+                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
+                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
+                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
+                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
+                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
+                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
+                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
+                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
+                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
+                                                    sent,
+                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
+                                                    thinkkind, sayintkind, dokind,
+                                                    point_in_time_year, point_in_time_month
+                                                    ) %>% distinct() %>%
+                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
+
+  notes=NULL
+  if(prune_rare==T){
+    actor_sent_counts <- 
+      bind_rows(
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
+          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
+        ) %>% 
+          na.omit() %>%
+          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
+
+      #New pruning rule, either singletons or actors with less than 10% of the max actor
+      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
+      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
+      if(left_over_count<3){
+        #Skip pruning if it leaves less than 3 actors
+      } else {
+
+        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
+        actor_singleton_labels <- actor_map$value_normalized_label
+        names(actor_singleton_labels) <- actor_map$actor
+        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
+
+        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
+
+        #Easiest thing is to just prune the original data
+        icb_events_subset <- icb_events_subset %>%
+          filter(!(
+                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
+                say_actor_a %in% singleton_actors |
+                say_actor_b %in% singleton_actors |
+                do_actor_a %in% singleton_actors |
+                do_actor_b %in% singleton_actors 
+          ) )
+
+          #recreate diads again using the new sentence numbers
+          icb_events_subset_diad <- icb_events_subset %>% 
+                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
+                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
+                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
+                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
+                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
+                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
+                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
+                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
+                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
+                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
+                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
+                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
+                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
+                                                            sent,
+                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
+                                                            thinkkind, sayintkind, dokind,
+                                                            point_in_time_year, point_in_time_month
+                                                            ) %>% distinct() %>%
+                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
+                                        filter(!(
+                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
+                                              say_actor_a %in% singleton_actors |
+                                              say_actor_b %in% singleton_actors |
+                                              do_actor_a %in% singleton_actors |
+                                              do_actor_b %in% singleton_actors 
+                                        ) ) %>% 
+                                       arrange(sent) %>%
+                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
+      }
+  }
+
+  g <- make_empty_graph(n = 0, directed = TRUE)
+    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
+
+  #Order actors by how many interactions they have together
+  temp <- bind_rows(
+    icb_events_subset_diad  %>% 
+      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
+    icb_events_subset_diad %>% 
+      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
+  )  %>% arrange(actor_1, actor_2) %>% distinct()
+
+  #new plan is to minimize the number of crossovers
+  temp2 <- bind_rows(
+    temp,
+    temp %>% setNames(c("actor_2", "actor_1", "sent"))
+  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
+  rowwise() %>%
+  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
+  arrange(desc(n))
+
+  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
+  rownames(temp2_wide) <- temp2_wide$actor_1
+  temp2_wide$actor_1 <- NULL
+  temp2_wide <- temp2_wide %>% as.matrix()
+  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
+  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
+  hc <- hclust(temp2_wide %>% as.dist(), method="single")
+  diag(temp2_wide) <- 0
+  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
+
+  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
+
+  #####Nodes
+  icb_events_subset_nodes <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
+            )  %>%
+            filter(!is.na(actor)) %>%
+           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
+            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
+                   y=sent*-1 *100)
+
+  icbe_actor_to_qcode <- icb_events_long %>%
+                         dplyr::filter(crisno==thiscrisis  ) %>% 
+                         filter(varname_normalized %>% str_detect("actor")) %>% 
+                         dplyr::select(value_normalized,value_qcode) %>% 
+                         na.omit() %>% distinct()
+
+  actor_colors_df <- icbe_actor_to_qcode %>%
+    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
+  actor_colors <- actor_colors_df$actor_color
+  names(actor_colors) = actor_colors_df$value_normalized
+
+  date_sineposts <- icb_events_subset_nodes  %>%
+                      mutate(x=max(x)+50) %>%
+                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
+                      na.omit() %>% 
+                      distinct() %>%  
+                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
+                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
+                      group_by(sent) %>%
+                       filter(year_float==min(year_float)) %>%
+                      ungroup() %>% as.data.frame() %>%
+                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
+                      filter(!duplicated(year_float ) ) %>%
+                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
+
+  ####Actor levels
+  icb_events_subset_nodes_min <- 
+    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
+    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
+    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
+    rowwise() #%>%
+    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
+
+  for(i in 1:nrow(icb_events_subset_nodes)){
+    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
+                                actor = icb_events_subset_nodes$actor[i], 
+                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
+  }
+
+  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
+
+  #####Time Edges
+  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
+
+  g <- g %>% 
+       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
+
+  ######Monads
+  icb_events_subset_monad <- 
+            bind_rows(
+                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
+                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
+                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
+            ) %>% 
+            na.omit() %>% 
+            distinct() %>% 
+            filter(!duplicated(paste(sent,actor,leaf))) %>%
+            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
+            distinct() %>% 
+            group_by(sent,actor,actor_sent) %>%
+              summarise(leaf=paste(leaf, collapse="\n") ) %>%
+            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
+
+  ######Directed
+  icb_events_subset_directed <- 
+            #We need to enumerate all the possibilities
+            bind_rows(
+              #Do alone
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
+              #Say alone
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
+              #Say Do
+              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
+                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
+              #Think Do
+              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
+                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
+            ) %>% 
+            na.omit() %>% 
+            distinct() %>% 
+            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
+            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
+            arrange(sent, actor_sent_1,leaf) %>%
+            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
+              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
+           #It is actually easier just to rejex out some dupes
+            mutate(leaf = leaf %>%
+                     str_replace("accept\naccept","accept") %>%
+                   str_replace("appeal\nappeal","appeal") %>%
+                   str_replace("reject\nreject","reject") %>%
+                   str_replace("express intent\nexpress intent","express intent") 
+                   ) %>%
+           arrange(sent, actor_sent_1,leaf) %>%
+           filter(actor_sent_1!=actor_sent_2)
+
+  #debug
+  icb_events_subset_directed <- icb_events_subset_directed  %>% 
+           group_by(sent, leaf) %>%
+               mutate(bundle_count=n()) %>%
+               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
+            ungroup()
+
+  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
+                       timeedge=F, 
+                       leaf=icb_events_subset_directed$leaf2, 
+                       eventedge=T,
+                       actor=icb_events_subset_directed$actor_1,
+                       bundle_count=icb_events_subset_directed$bundle_count
+                       )
+
+  ######Put it all together
+  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
+  p_metro_map <- g %>%  
+          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
+
+          #Event edges
+          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
+          geom_edge_arc(aes(  
+                            colour=actor,
+                            label=leaf,
+                            filter=eventedge==T & bundle_count==1 
+                            ),
+                        label_colour=NA, 
+                        vjust = -0.75,
+                        lineheight = .75,
+                        sep = unit(1, 'mm'), 
+                        edge_width=0.25, 
+                        show.legend = F,
+                        arrow = arrow(length = unit(2, 'mm')),
+                        label_size=3,
+                        check_overlap=global_check_overlap,
+                        start_cap = circle(3, 'mm'),
+                        end_cap = circle(3, 'mm'),
+                        angle_calc = 'along' #,
+                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
+                       ) +
+              #Grouped Edges
+              geom_edge_parallel(aes(  
+                                  colour=actor,
+                                  label=leaf,
+                                  filter=eventedge==T & bundle_count>1
+                                  ),
+                              vjust = -0.75,
+                              lineheight = .75,
+                              sep = unit(5, 'mm'), 
+                              edge_width=0.4,  #0.25
+                              show.legend = F,
+                              arrow = arrow(length = unit(1, 'mm')),
+                              label_size=4,
+                              check_overlap=global_check_overlap,
+                              start_cap = circle(3, 'mm'),
+                              end_cap = circle(3, 'mm'),
+                              angle_calc = 'along'
+                             ) +
+
+              #Time edges
+              geom_edge_link(aes(
+                              edge_colour=actor,
+                              filter=timeedge==T
+                              ),
+                              edge_width=0.1, 
+                              show.legend = F,
+                              check_overlap=global_check_overlap
+                             ) +
+              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
+              #Fatalities
+              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
+
+              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
+              #Add Actor Names
+              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
+                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
+                        check_overlap=global_check_overlap) + #-45
+              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
+              scale_color_manual(values = actor_colors)  +
+              scale_edge_color_manual(values = actor_colors) +
+              #theme_bw() + 
+              #labs( title = plot_title ) +
+              theme_graph() +
+              theme(legend.position = "none") #+
+              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
+
+  if(prune_rare==T & !is.null(notes)){
+     p_metro_map <- p_metro_map + labs(caption = notes)
+  }
+
+  return(p_metro_map)
+}
+```
+
+```{r precision-combined, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+library(ggplot2)
+library(cowplot)
+
+p_196_icbe <- icbe_crisismaps(thiscrisis=196) +
+    labs(
+      #title = plot_title ,
+      #subtitle = subtitle ,
+      caption = NULL
+    ) +
+      theme(plot.margin=unit(c(0,0,0,0),"in")) +
+  scale_x_continuous(expand = expansion(mult = c(0.06, 0.05))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
+
+ratio=.75
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_icbe.png'),
+          p_196_icbe, base_height = 18, base_width = height*ratio)
+
+p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
+    labs(
+      #title = plot_title ,
+      #subtitle = subtitle ,
+      caption = NULL
+    ) +
+    theme(plot.margin=unit(c(0,0,0,0),"in")) +
+   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
+
+ratio=.75
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_icbe.png'),
+          p_471_icbe, base_height = 18, base_width = height*ratio)
+
+p_precision_combined <- plot_grid(
+            p_196_icbe +
+    theme(plot.margin=unit(c(0,0,0,0),"in")) +
+   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
+               p_471_icbe +
+    theme(plot.margin=unit(c(0,0,0,0),"in")) +
+   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
+   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
+           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )
+
+ratio=1.5
+height=18
+save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_precision_combined.png'),
+          p_precision_combined, base_height = 18, base_width = height*ratio)
+
+```
+
+```{r sentences-unique, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+library(flextable)
+library(ftExtra)
+library(tidyverse)
+
+#Load it here before the python reticulate business
+#devtools::install_github("ropenscilabs/umapr")
+#library(umapr)
+
+ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
+
+ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown %>%
+                                        mutate(sentence_span_text_clean = sentence_span_text %>% str_replace_all("\\(.*?\\)|\\[.*?\\]","") ) %>%
+                                        mutate(sentences_unique_sanitized = sentence_span_text_clean %>%
+                                                 str_replace_all("[A-Z][a-z]*","Entity") %>%
+                                                 str_replace_all("[0-9]{4}","Entity") %>% #All years with entity
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("Entity Entity","Entity") %>%
+                                                 str_replace_all("[0-9]","") %>%  #replace all digits with blanks
+                                                 str_replace_all(" {1,}"," ")   
+                                               )  #
+
+sentences_unique <- ICBe_events_agreed_markdown_embedded %>% 
+                    dplyr::select(sentences_unique_sanitized) %>% 
+                    distinct() %>%
+                    pull(sentences_unique_sanitized) %>% 
+                    unique() %>% na.omit()
+length(sentences_unique ) #12162
+head(sentences_unique)
+```
+
+```{r reticulate, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+#To set python, set it in ~/.Renviron.
+`use_python()` doesn't seem to work as desired.
+See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).
+
+library(reticulate)
+reticulate::py_discover_config()
+
+#use_python("/home/skynet3/anaconda3/bin/python/")
+#use_python("/home/tlscherer/anaconda3/bin/python3")
+#py_install("sentence-transformers")
+```
+
+```{python sentence-transformers, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+#Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
+#pip install -U sentence-transformers
+
+fromscratch=False
+
+if fromscratch:
+  from sentence_transformers import SentenceTransformer
+  import numpy as np
+  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
+  sentence_chars = np.array([len(q) for q in sentences])
+  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
+  len(sentences) #12161 12162
+  n=len(sentences)
+  chunk_length=100
+  n_chunks = int(np.ceil(n/chunk_length)) #can only 
+  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
+  len(sentences_chunks)
+  len(sentences_chunks[0])  
+  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
+  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
+  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
+  model = SentenceTransformer('paraphrase-mpnet-base-v2')
+  #sentences
+  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
+  #temp = model.encode(sentences_chunks[0])
+  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
+  sentences_embeddings.shape #(12103, 768)
+
+else:
+  print("Skipping")
+```
+
+```{r sentence-embeddings, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+fromscratch = FALSE
+if(fromscratch){
+  sentences_embeddings <- py$sentences_embeddings
+  dim(sentences_embeddings)
+  sentences_embeddings %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
+}else{
+  sentences_embeddings <- readRDS(paste0(here::here(), '/replication_paper/data/temp/sentences_embeddings.Rds'))
+  dim(sentences_embeddings)
+}
+```
+
+```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=T}
+#The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.
+
+# AG temp edit: revert by deleting 'eval=F' above DONE
+
+embedding <- umapr::umap(sentences_embeddings)
+#plot(embedding[,c('UMAP1','UMAP2')])
+
+sentences_embeded_mpnet <- as.data.frame(sentences_embeddings)
+sentences_embeded_umap <- embedding[,c('UMAP1','UMAP2')] %>% as.data.frame()
+
+sentences_embeded_mpnet$sentences_unique_sanitized <- sentences_unique
+sentences_embeded_umap$sentences_unique_sanitized <- sentences_unique
+
+ICBe_events_agreed_markdown_embedded <- ICBe_events_agreed_markdown_embedded %>% ungroup() %>% 
+                                        left_join(sentences_embeded_umap) %>% 
+                                  --------------------------      left_join(sentences_embeded_mpnet)
+
+ICBe_events_agreed_markdown_embedded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
+
+ICBe_events_agreed_markdown_embedded_sample  <- ICBe_events_agreed_markdown_embedded %>% 
+                                                mutate(UMAP1_round=UMAP1 %>%  round(), UMAP2_round=UMAP2 %>%  round()) %>%
+                                                dplyr::group_by(UMAP1_round,UMAP2_round) %>%
+                                                arrange(UMAP1,UMAP2) %>%
+                                                filter(crisno==crisno[1], sentence_number_int_aligned==sentence_number_int_aligned[1] ) #only take one per crisis
+```
+
+```{r sentence-embeddings-dendro, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+
+# AG temp edit: revert by setting 'eval=T'
+
+library(cowplot)
+ICBe_events_agreed_markdown_embedded <- readRDS(paste0(here::here(), '/replication_paper/data/temp/ICBe_events_agreed_markdown_embedded.Rds'))
+
+newcolors <- pals::glasbey()
+
+value_means <- ICBe_events_agreed_markdown_embedded %>% 
+               left_join(icb_events_long %>% 
+                           filter(varname_normalized %>% str_detect('escalate|coop|sayintkind|thinkkind')) %>%
+                           filter(!value_normalized %>% str_detect('^[0-9]*$'))) %>%
+               mutate(color=NA) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_escalate"),"red",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_deescalate"),"darkgreen",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("uncoop|decreasecoop"),"purple",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("_coop|_increasecoop"),"blue",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("sayintkind"),"brown",color)) %>%
+               mutate(color=ifelse(varname_normalized %>% str_detect("thinkkind"),"darkorange",color)) %>%
+               dplyr::select(-varname_normalized,-value_qcode,-varname_normalized,-crisis_text,-crisno,-sentence_number_int_aligned,-sentence_span_text,
+                             -actor_set,-value_markdown,-sentence_span_text_clean,-sentences_unique_sanitized) %>% # 
+               group_by(color, value_normalized) %>%
+               mutate(n=n()) %>%
+               filter(n>20) %>% #note require at least 20 examples of that tag
+               dplyr::summarise_all(median) %>%
+              na.omit()
+
+value_normalized_colors <- value_means$color 
+names(value_normalized_colors) = value_means$value
+
+library(ggplot2)
+library(ggrepel)
+p_semantic_embeddings <-
+      ICBe_events_agreed_markdown_embedded %>%
+      ggplot(aes(x=UMAP2,y=UMAP1)) +
+      geom_point(size=0.5, alpha=0.25) + 
+      #geom_text(data=value_means, aes(x=UMAP1, y=UMAP2, label=value, color=value %>% as.factor()),size=1.5) + 
+      theme_bw() +
+      theme(legend.position = "none") + 
+      geom_label(data=value_means,
+                 aes(x=UMAP2,y=UMAP1,
+                     fill = value_normalized %>% as.factor(),
+                     label=value_normalized, size=50
+                     ), size = 2.5,
+                 inherit.aes=F, 
+                 colour = "white", fontface = "bold", label.padding = unit(0.1, "lines")
+                 ) +   
+      #geom_label_repel(data=value_means,
+      #           aes(x=UMAP1,y=UMAP2, fill = value %>% as.factor(), label=value, size=20), size = 3, inherit.aes=F, 
+      #           colour = "white", fontface = "bold", label.padding = unit(0.1, "lines"),
+      #           min.segment.length = 0
+      #           ) + 
+      # labs(
+      #     title = "Variation in Tags by Semantic Embeddings of Source Sentences",
+      #     subtitle = "Sentence Embedding Paraphrase-MPNET-base-v2, UMAP Projection ",
+      #     caption = ""
+      # ) +
+     #scale_color_manual(values = value_normalized_colors) +
+     scale_fill_manual(values = value_normalized_colors) +
+     scale_x_continuous(expand = c(0, 0)) +
+     scale_y_continuous( expand = c(0, 0)) #+
+     #coord_cartesian( xlim=c(0.75,6.5), ylim=c(7,12)) #+  #you can't do this because umap is stochastic and you'd have to pick by hand each time
+     #coord_flip()
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)
+
+#Now do the dendro
+library(ggdendro)
+#We actually need the raw embeddings
+
+#Rex Note to take only one per sentence
+value_normalized_colors <- value_means$color 
+names(value_normalized_colors) = value_means$value_normalized
+
+m <- value_means %>% dplyr::select(starts_with("V",  ignore.case = F)) %>% as.matrix()
+rownames(m) <- value_means$value_normalized
+d <- m %>% dist()
+hc <- hclust(d, method="ward.D2")
+library(ggplot2)
+library(ggdendro)
+hcdata <- dendro_data(hc, type = "rectangle")
+p_dendro <- ggplot() +
+            geom_segment(data = segment(hcdata), 
+                         aes(x = x, y = y, xend = xend, yend = yend)
+            ) +
+            geom_text(data = ggdendro::label(hcdata) %>% mutate(color=value_normalized_colors[hcdata$labels$label] ), 
+                      aes(x = x, y = y, label = label, hjust = 0,
+                          color=label %>% as.factor()), 
+                      size = 3
+            ) +
+            coord_flip() +
+            scale_color_manual(values = value_normalized_colors) +
+            scale_x_continuous(expand = c(0.02, 0.00, 0.02, 0.0) ) +
+            scale_y_reverse( expand = c(0.1, 0.0, 0.0, 5.0)) +  #limits = c(-10, 10),
+            theme_bw() +
+            theme(legend.position="none")
+#p_dendro
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)
+
+p_combined <- plot_grid(
+  NULL,
+  p_semantic_embeddings + xlab("") + ylab("") + 
+  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
+  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),
+  NULL,
+  p_dendro  + xlab("") + ylab("") + 
+  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + 
+  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()),  
+  labels = c('',''),
+  align = "v", nrow = 1, rel_widths = c(-.2, 3.5, -.4, 1.5)  ) #increase the second width to give the dendro more room
+#p_combined
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)
+```
+
+@fig-umap shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^9] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
+If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the right-hand side.[^10]
+
+![Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
+Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
+Label placement is the median of all of the sentences that the tag was applied to by the coders.
+The dendrogram shows hierarchical clustering of the tags.
+If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap}
+
+# Case illustrations
+
+In this section, we focus our validation on two case studies for which we have produced synthetic narratives using the method described in Section 3.2.
+Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
+The first (@fig-cuba-narrative) is the Cuban Missile Crisis (hereafter Cuban Missiles) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war.
+The second (SI Appendix 4.1) is the Crimea-Donbas Crisis (hereafter Crimea-Donbas) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion.
+We choose these cases because they are significant in contemporary international relations, are widely known across academic disciplines as well as among the public, and are sufficiently brief to evaluate in depth.
+They are similar in that both cases involve a superpower in crisis with a neighbor that changed from a friendly to a hostile regime, both held implications for the economic and military security for the superpower by risking full-scale invasion, and both eventually invited intervention by an opposing superpower.
+
+```{r recall-cuba, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 #Lit review
@@
 image_write(combined, here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea_andcounts.png"))
-
-```
-
-```{=tex}
-\clearpage
-\singlespacing
-```
-<!-- \onecolumn -->
-
-```{=tex}
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).}
-\end{figure}
-\clearpage
-\doublespacing
-```
-<!-- \twocolumn -->
-
-We find substantive variation in recall across systems.
-Recall for each increases in the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which is so noisy that it's flat to decreasing in mentions.
-The two episode-level datasets have low coverage of contextual details.
-The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
-ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
-
-# Precision
-
-The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history.
-It does little good to recall a historical event but too vaguely (e.g.
-MIDs describes the Cuban Missile Crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g.
-ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications.
-ICBe's ontology and coding system are designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable.
-You should be able to lay out the events of a crisis on a timeline, as in Figure 3, and read off the macrostructure of an episode from each individual move.
-We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study in SI Appendix 4.3 and 4.4 and for all crises on the companion website.
-
-```{r crisis map function, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-global_check_overlap=F
-library(igraph)
-library(RColorBrewer)
-library(ggraph)
-target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
-dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
-                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()
-
-actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
-                                sheet="actor_translator") #%>% janitor::clean_names() 
-#Convert to a local file for pushing
-#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
-pallet <- c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Set2"), brewer.pal(n=20, "Paired")) %>% unique()
-library(pals); #install.packages('pals')
-pallet <- c(pals::glasbey(),  pals::alphabet2())
-pallet <- setdiff(pallet, c("#666666", "#999999", "#FFFF99","#FFFF33","#B2DF8A","#B3B3B3","#0000FF")) 
-library(colorspace)
-#cols <- c("#CDE4F3","#E7F3D3","#F7F0C7","#EFCFE5","#D0D1E7")    
-pallet <- rgb(hex2RGB(pallet)@coords * 0.7)
-actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))
-
-icbe_crisismaps <- function(thiscrisis=471, prune_rare=T){
-
-  icb_events_subset <-  ICBe_events_agreed %>% 
-                         dplyr::filter(crisno==thiscrisis) %>%  #417 196
-                         dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
-                         dplyr::mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
-                         dplyr::mutate(year=date_earliest_year %>% as.numeric() ) %>%
-                         dplyr::mutate(month= date_earliest_month %>% as.numeric() ) %>%
-                         dplyr::mutate(day= date_earliest_day %>% as.numeric()  ) %>%
-                         dplyr::arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
-                         tidyr::fill(decade, .direction="downup") %>%
-                         tidyr::fill(year, .direction="downup") %>%
-                         tidyr::fill(month, .direction="downup") %>%
-                         tidyr::fill(day, .direction="downup") %>% 
-                         dplyr::mutate(point_in_time_year = year %>% as.numeric())  %>% 
-                         dplyr::mutate(point_in_time_month = month %>% as.numeric()) %>% 
-                         arrange(decade, year,month,day) %>%
-                         mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order
-
-  icb_events_subset_diad <- icb_events_subset %>% 
-                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                    sent,
-                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                    thinkkind, sayintkind, dokind,
-                                                    point_in_time_year, point_in_time_month
-                                                    ) %>% distinct() %>%
-                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))
-
-  notes=NULL
-  if(prune_rare==T){
-    actor_sent_counts <- 
-      bind_rows(
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
-          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
-        ) %>% 
-          na.omit() %>%
-          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )
-
-      #New pruning rule, either singletons or actors with less than 10% of the max actor
-      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
-      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
-      if(left_over_count<3){
-        #Skip pruning if it leaves less than 3 actors
-      } else {
-
-        actor_map <- dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) 
-        actor_singleton_labels <- actor_map$value_normalized_label
-        names(actor_singleton_labels) <- actor_map$actor
-        actor_singleton_labels <- actor_singleton_labels[singleton_actors]
-
-        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")
-
-        #Easiest thing is to just prune the original data
-        icb_events_subset <- icb_events_subset %>%
-          filter(!(
-                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                say_actor_a %in% singleton_actors |
-                say_actor_b %in% singleton_actors |
-                do_actor_a %in% singleton_actors |
-                do_actor_b %in% singleton_actors 
-          ) )
-
-          #recreate diads again using the new sentence numbers
-          icb_events_subset_diad <- icb_events_subset %>% 
-                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
-                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
-                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
-                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
-                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
-                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
-                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
-                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
-                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
-                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
-                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
-                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
-                                                            sent,
-                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
-                                                            thinkkind, sayintkind, dokind,
-                                                            point_in_time_year, point_in_time_month
-                                                            ) %>% distinct() %>%
-                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
-                                        filter(!(
-                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
-                                              say_actor_a %in% singleton_actors |
-                                              say_actor_b %in% singleton_actors |
-                                              do_actor_a %in% singleton_actors |
-                                              do_actor_b %in% singleton_actors 
-                                        ) ) %>% 
-                                       arrange(sent) %>%
-                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
-      }
-  }
-
-  g <- make_empty_graph(n = 0, directed = TRUE)
-    #graph_from_data_frame(vertices=nodes) #relations, directed=TRUE,
-
-  #Order actors by how many interactions they have together
-  temp <- bind_rows(
-    icb_events_subset_diad  %>% 
-      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
-    icb_events_subset_diad %>% 
-      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
-  )  %>% arrange(actor_1, actor_2) %>% distinct()
-
-  #new plan is to minimize the number of crossovers
-  temp2 <- bind_rows(
-    temp,
-    temp %>% setNames(c("actor_2", "actor_1", "sent"))
-  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
-  rowwise() %>%
-  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
-  arrange(desc(n))
-
-  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
-  rownames(temp2_wide) <- temp2_wide$actor_1
-  temp2_wide$actor_1 <- NULL
-  temp2_wide <- temp2_wide %>% as.matrix()
-  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
-  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
-  hc <- hclust(temp2_wide %>% as.dist(), method="single")
-  diag(temp2_wide) <- 0
-  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue
-
-  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
-  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events
-
-  #####Nodes
-  icb_events_subset_nodes <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
-            )  %>%
-            filter(!is.na(actor)) %>%
-           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
-            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
-                   y=sent*-1 *100)
-
-  icbe_actor_to_qcode <- icb_events_long %>%
-                         dplyr::filter(crisno==thiscrisis  ) %>% 
-                         filter(varname_normalized %>% str_detect("actor")) %>% 
-                         dplyr::select(value_normalized,value_qcode) %>% 
-                         na.omit() %>% distinct()
-
-  actor_colors_df <- icbe_actor_to_qcode %>%
-    left_join(actor_translator %>% dplyr::select(value_qcode=QCode, actor_color))
-  actor_colors <- actor_colors_df$actor_color
-  names(actor_colors) = actor_colors_df$value_normalized
-
-  date_sineposts <- icb_events_subset_nodes  %>%
-                      mutate(x=max(x)+50) %>%
-                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
-                      na.omit() %>% 
-                      distinct() %>%  
-                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
-                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
-                      group_by(sent) %>%
-                       filter(year_float==min(year_float)) %>%
-                      ungroup() %>% as.data.frame() %>%
-                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
-                      filter(!duplicated(year_float ) ) %>%
-                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))
-
-  ####Actor levels
-  icb_events_subset_nodes_min <- 
-    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
-    left_join(dictionary_actors_labels %>% filter(crisno==thiscrisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
-    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
-    rowwise() #%>%
-    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors
-
-  for(i in 1:nrow(icb_events_subset_nodes)){
-    g <- g %>%  add_vertices(1, name=icb_events_subset_nodes$actor_sent[i],
-                                actor = icb_events_subset_nodes$actor[i], 
-                                sent = icb_events_subset_nodes$sent[i]  ) #, type = nodes$type[i] #, leaf = nodes$leaf[i]
-  }
-
-  xy <- cbind(icb_events_subset_nodes$x, icb_events_subset_nodes$y )
-
-  #####Time Edges
-  icb_events_subset_nodes_edges_time <- cbind(icb_events_subset_nodes, bind_rows(icb_events_subset_nodes[-1,],icb_events_subset_nodes[1,] ) ) %>% janitor::clean_names() %>% filter(actor==actor_2 & sent_2>sent) %>% distinct()
-
-  g <- g %>% 
-       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
-
-  ######Monads
-  icb_events_subset_monad <- 
-            bind_rows(
-                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a,leaf=thinkkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(say_actor_a) & is.na(say_actor_b)) %>% dplyr::select(sent,actor=say_actor_a,leaf=sayintkind) ,
-                      icb_events_subset_diad %>% filter(!is.na(do_actor_a) & is.na(do_actor_b)) %>% dplyr::select( sent,actor=do_actor_a,leaf=dokind) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            filter(!duplicated(paste(sent,actor,leaf))) %>%
-            mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>%
-            distinct() %>% 
-            group_by(sent,actor,actor_sent) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>%
-            left_join( icb_events_subset_nodes %>% dplyr::select(actor_sent,x,y))
-
-  ######Directed
-  icb_events_subset_directed <- 
-            #We need to enumerate all the possibilities
-            bind_rows(
-              #Do alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                             dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=dokind) ,
-              #Say alone
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & is.na(dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=sayintkind) ,
-              #Say Do
-              icb_events_subset_diad %>% filter(is.na(thinkkind) & !is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(sayintkind,"-",dokind)) %>% dplyr::select(sent,actor_1=say_actor_a, actor_2=say_actor_b, leaf=leaf),
-              #Think Do
-              icb_events_subset_diad %>% filter(!is.na(thinkkind) & is.na(sayintkind) & !is.na(dokind)) %>% 
-                mutate(leaf=paste0(dokind)) %>% dplyr::select(sent,actor_1=do_actor_a, actor_2=do_actor_b, leaf=leaf) 
-            ) %>% 
-            na.omit() %>% 
-            distinct() %>% 
-            #mutate(leaf = strsplit(as.character(leaf), ";")) %>% unnest(leaf) %>% distinct() %>% 
-            mutate(actor_sent_1= actor_1 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            mutate(actor_sent_2= actor_2 %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
-            arrange(sent, actor_sent_1,leaf) %>%
-            group_by(sent,actor_1, actor_sent_1,actor_sent_2) %>%
-              summarise(leaf=paste(leaf, collapse="\n") ) %>% 
-           #It is actually easier just to rejex out some dupes
-            mutate(leaf = leaf %>%
-                     str_replace("accept\naccept","accept") %>%
-                   str_replace("appeal\nappeal","appeal") %>%
-                   str_replace("reject\nreject","reject") %>%
-                   str_replace("express intent\nexpress intent","express intent") 
-                   ) %>%
-           arrange(sent, actor_sent_1,leaf) %>%
-           filter(actor_sent_1!=actor_sent_2)
-
-  #debug
-  icb_events_subset_directed <- icb_events_subset_directed  %>% 
-           group_by(sent, leaf) %>%
-               mutate(bundle_count=n()) %>%
-               mutate(leaf2=ifelse(bundle_count>1 & row_number()>1,'',leaf)) %>%  
-            ungroup()
-
-  g <- g %>% add_edges(icb_events_subset_directed[,c('actor_sent_1','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
-                       timeedge=F, 
-                       leaf=icb_events_subset_directed$leaf2, 
-                       eventedge=T,
-                       actor=icb_events_subset_directed$actor_1,
-                       bundle_count=icb_events_subset_directed$bundle_count
-                       )
-
-  ######Put it all together
-  wrap_names <- function(x){sapply(x, FUN=function(x) x %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n') ) }
-  p_metro_map <- g %>%  
-          ggraph("manual",x=xy[,1],y=xy[,2]) +  #geom_edge_parallel
-
-          #Event edges
-          #geom_path(data = hbundle, aes(x, y, group = group), col = "#9d0191", size = 0.05) +
-          geom_edge_arc(aes(  
-                            colour=actor,
-                            label=leaf,
-                            filter=eventedge==T & bundle_count==1 
-                            ),
-                        label_colour=NA, 
-                        vjust = -0.75,
-                        lineheight = .75,
-                        sep = unit(1, 'mm'), 
-                        edge_width=0.25, 
-                        show.legend = F,
-                        arrow = arrow(length = unit(2, 'mm')),
-                        label_size=3,
-                        check_overlap=global_check_overlap,
-                        start_cap = circle(3, 'mm'),
-                        end_cap = circle(3, 'mm'),
-                        angle_calc = 'along' #,
-                        #label_push=unit(20, units='mm') #This shifts the curved labels toward the target
-                       ) +
-              #Grouped Edges
-              geom_edge_parallel(aes(  
-                                  colour=actor,
-                                  label=leaf,
-                                  filter=eventedge==T & bundle_count>1
-                                  ),
-                              vjust = -0.75,
-                              lineheight = .75,
-                              sep = unit(5, 'mm'), 
-                              edge_width=0.4,  #0.25
-                              show.legend = F,
-                              arrow = arrow(length = unit(1, 'mm')),
-                              label_size=4,
-                              check_overlap=global_check_overlap,
-                              start_cap = circle(3, 'mm'),
-                              end_cap = circle(3, 'mm'),
-                              angle_calc = 'along'
-                             ) +
-
-              #Time edges
-              geom_edge_link(aes(
-                              edge_colour=actor,
-                              filter=timeedge==T
-                              ),
-                              edge_width=0.1, 
-                              show.legend = F,
-                              check_overlap=global_check_overlap
-                             ) +
-              geom_node_point(aes(color=actor),size=1,stroke=0.5) +
-              #Fatalities
-              #geom_text(data=fatalities %>% filter(interact_fatalities>1), aes(x=x+4,y=y, size=interact_fatalities+1), color='black', label='☠', angle=0, check_overlap=global_check_overlap) +
-
-              geom_text(data=icb_events_subset_monad, aes(x=x,y=y, label=leaf), nudge_y=40, angle=0, lineheight = .75, size=3, check_overlap=global_check_overlap) +
-              #Add Actor Names
-              geom_text(data=icb_events_subset_nodes_min, aes(x=x,y=y, label=actor  %>% wrap_names() , color=actor),
-                        nudge_y=150, angle=0, size=4, lineheight = .75, fontface = "bold",
-                        check_overlap=global_check_overlap) + #-45
-              geom_text(data=date_sineposts, aes(x=x,y=y, label=label), color="grey", nudge_y=0, angle=0, size=4, lineheight = .75, fontface = "bold",check_overlap=global_check_overlap) + #-45
-              scale_color_manual(values = actor_colors)  +
-              scale_edge_color_manual(values = actor_colors) +
-              #theme_bw() + 
-              #labs( title = plot_title ) +
-              theme_graph() +
-              theme(legend.position = "none") #+
-              #ggimage::geom_image(data= units, aes(x=x+offeset,y=y-30, image = IMAGE), size = 0.015)
-
-  if(prune_rare==T & !is.null(notes)){
-     p_metro_map <- p_metro_map + labs(caption = notes)
-  }
-
-  return(p_metro_map)
-}
-
-```
-
-```{r eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-library(ggplot2)
-library(cowplot)
-
-p_196_icbe <- icbe_crisismaps(thiscrisis=196) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-      theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  scale_x_continuous(expand = expansion(mult = c(0.06, 0.05))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-ratio=.75
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_icbe.png'),
-          p_196_icbe, base_height = 18, base_width = height*ratio)
-
-p_471_icbe <- icbe_crisismaps(thiscrisis=471) #readRDS(file=paste0(here::here(), '/replication_paper/arxiv_draft/crisismaps/p_metro_plot_471.Rds')) +
-    labs(
-      #title = plot_title ,
-      #subtitle = subtitle ,
-      caption = NULL
-    ) +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.025, 0.025))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01)))
-
-ratio=.75
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_icbe.png'),
-          p_471_icbe, base_height = 18, base_width = height*ratio)
-
-p_precision_combined <- plot_grid(
-            p_196_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,
-               p_471_icbe +
-    theme(plot.margin=unit(c(0,0,0,0),"in")) +
-   scale_x_continuous(expand = expansion(mult = c(0.1, 0.1))) +
-   scale_y_continuous(expand = expansion(mult = c(0.01, 0.01))) ,  
-           labels = c('Cuban Missiles','Crimea-Donbas'), align = "v", ncol = 2 , rel_widths = c(1, 1) )
-
-ratio=1.5
-height=18
-save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_precision_combined.png'),
-          p_precision_combined, base_height = 18, base_width = height*ratio)
-
-```
-
-We further want to verify individual event codings, which we can do in the case of ICBe because each event is mapped to a specific span of text.
-We develop the iconography system for presenting event codings as coherent statements that can be compared side by side to the original source narrative for Cuban Missiles (Figure 1), Crimea-Donbas (SI Appendix 4.1), and for every case on the companion website.
-We further provide a stratified sample of event codings alongside their source text (SI Appendix 4.2).
-
-We find both the visualizations of macrostructure and head-to-head comparisons of ICBe codings to the raw text to strongly support the quality of ICBe, but as with recall, we seek a more objective detached universal benchmark.
-Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-Figure 4 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^9] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the righthand side.[^10]
-
-[^9]: We preprocess sentences to replace named entities with a generic Entity token.
-
-[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
-
-Finally, how does ICBe's precision compare to the existing state of the art?
-The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
-On the other end of the spectrum, the high recall dictionary-based event datasets like Terrier and ICEWs produce so many noisy events (several hundred thousand) that even with heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly provide the original text spans making event-level precision difficult to verify.
-
-However, given their high recall on our task and the global and real-time coverage of dictionary-based event systems, we want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
-For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by detrending violent event counts from Phoenix using a human-coded baseline.
+```
+
+## Cuban Missile Crisis (1962)
+
+A synthetic historical narrative for Cuban Missiles appears in @fig-recall-cuba, with 51 events drawn from 2,020 documents.
+Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of the original ICB corpus, our ICBe events, and any of the competing existing models.
+
+ICB's improved recall of Cuban Missiles was relative to the state of the art was summarized in Section 3.2 (@fig-recall-cases), but the events that explain that improvement can now be seen.
+Our ground truth ICB narrative contains 17/51 of the events from the synthetic narrative of a case that includes high-level previously classified details.
+ICBe captures nearly all details included in ICB as well as more details from the synthetic narrative than any competing dataset.
+Phoenix includes some earlier information than ICBe like the nationalization of businesses and back channel negotiations, but the crisis narrative has a clean canonical end with the Soviets agreeing to withdraw missiles.
+ICBe stands out in including more communicative behavior (do -- speech) than existing datasets like US threats to attack and later promises not to invade.
+Given the recognized importance of threat credibility for understanding international conflict, the addition of this information is a substantively important improvement over the existing state of the art [@slantchev_militarythreatscosts_2011].
+
+![Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
+Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).](case_study_cuban_recall.png){#fig-recall-cuba}
+
+@fig-cuba-crisismap shows the crisis map for the Cuban Missile Crisis.
+Looking at the crisis on a timeline, one can now identify the structure of actors and the environment, along with its supporting details, in a way that validates the precision of ICBe.
+Although harder to measure objectively, this crisis map provides face valid evidence that ICBe's account is not too vague, but also not unnecessarily detailed.
+We include much of the geopolitically important details like Soviet deployment, US discovery of that deployment, heightened alert levels, a blockade, and negotiations that ended with a formal agreement.
+At the same time, the crisis map indicates that ICBe does not include unnecessary nuances that preclude useful comparison to other international events.
+
+![Crisis map for the Cuban Missile Crisis.
+The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap}
+
+## Crimea-Donbas (2014)
+
+A synthetic historical narrative for the 2014 Crimea-Donbas crisis (30 events drawn from 971 documents) appears in @fig-recall-crimea.
+As in the earlier case, rows represent details that appeared in at least five documents and whether it is identified in ICBe and existing datasets.
+
+Again quantitatively summarized earlier in Section 3.2 (@fig-recall-cases), our ground truth ICB narrative contains 23/30 of the events from the synthetic narrative.
+Like the gray zone precursor to the Cuban Missile crisis [@cormacGreyNewBlack2018], Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
+a long term lease on naval facilities in Crimea.
+But unlike the Cuban Missile crisis, the end of this crisis is unclear, with the event meekly ending with a second cease-fire agreement (Minsk II) but continued fighting.
+ICBe again recalls more important information about the crisis than any existing dataset, particularly information concerning the behavior of non-state separatist groups like the Donetsk People's Republic (DPR) and Luhansk People's Republic (LPR).
+
+![Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
+Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).](case_study_crimea_recall.png){#fig-recall-crimea}
+
+As this more recent case reflects primarily public reporting rather than the previously classified details relevant for the Cuban Missile Crisis, ICBe's improvement relative to the global and real-time coverage of dictionary-based event systems is still present, but less pronounced.
+We want to take seriously the possibility that some functional transformation could recover the precision of ICBe.
+For example, @terechshenkoHotCollarLatent2020 attempts to correct for the mechanically increasing amount of news coverage each year by de-trending violent event counts from Phoenix using a human-coded baseline.
 Others have focused on verifying precision for ICEWs on specific subsets of details against known ground truths, e.g.
@@
 
-We take the same approach here in Figure 5, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
+We take the same approach here in @fig-precision-icews, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
 We choose four event types around key moments in the crisis.

### 2023-07-13 replication_paper/psrm_draft/ICBe_manuscript.tex
no keywords
doublespacing

@@
 
-\title{Introducing ICBe: Very High Recall and Precision Event Extraction
-from Narratives about International Crises}
+\title{Introducing ICBe: An Event Extraction Dataset from Narratives
+about International Crises}
 
@@
 \usepackage{hhline}
+\newlength\Oldarrayrulewidth
+\newlength\Oldtabcolsep
 \usepackage{longtable}
@@
 
-\keywords{
-    Diplomacy
-   \and
-    War
-   \and
-    Crises
-   \and
-    International Affairs
-   \and
-    Computational Social Science
-  }
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-If we could record every important interaction between countries in all
-of diplomacy, military conflict, and international political economy,
-how much unique information would this chronicle amount to, and how
-surprised would we be to see something new? In other words, what is the
-entropy of international relations? This record could in principle be
-unbounded, but the central conceit of social science is that there are
-structural regularities that limit what actors can do, their best
-options, and even which actors are likely to survive (Brecher 1999;
-Reiter 2015). If so, then these events can be systematically measured,
-and accordingly, massive effort is expended in social science attempting
-to record these regularities.\footnote{See work on crises (Brecher and
-  Wilkenfeld 1982; Beardsley et al. 2020), militarized disputes (Palmer
-  et al. 2021; Gibler 2018), wars (Sarkees and Wayman 2010; Reiter,
-  Stam, and Horowitz 2016), organized violence (Ralph Sundberg and Mihai
-  Croicu 2016; Davies, Pettersson, and Öberg 2022), political violence
-  (Raleigh et al. 2010), sanctions (Felbermayr et al. 2020), and
-  international agreements (Kinne 2020; Owsiak, Cuttner, and Buck 2018),
-  dispute resolution (Frederick, Hensel, and Macaulay 2017), and
-  diplomacy (Moyer, Turner, and Meisel 2020; Sechser 2011).} Thanks to
+\doublespacing
+
+If we could record every international interaction in the realms of
+diplomacy, conflict, economics, and beyond, how much unique information
+would this chronicle amount to, and how surprised would we be to see
+something new? In other words, what is the entropy of international
+relations? While this record could in principle be unbounded, the
+central conceit of social science is that there are structural
+regularities that limit what actors can do, their best options, and even
+which actors are likely to survive
+(\textbf{brecherInternationalStudiesTwentieth1999?};
+\textbf{reiterShouldWeLeave2015?}). If so, then these events can be
+recorded and systematically measured by social scientists interested in
+these regularities.\footnote{See work on crises
+  (\textbf{brecherCrisesWorldPolitics1982?};
+  \textbf{beardsleyInternationalCrisisBehavior2020?}), militarized
+  disputes (\textbf{palmerMID5Dataset20112021?};
+  \textbf{giblerInternationalConflicts181620102018?}), wars
+  (\textbf{sarkeesResortWar181620072010?};
+  \textbf{reiterRevisedLookInterstate2016?}), organized violence
+  (\textbf{ralphsundbergUCDPGEDCodebook2016?};
+  \textbf{daviesOrganizedViolence19892022?}), political violence
+  (\textbf{raleighIntroducingACLEDArmed2010?}), sanctions
+  (\textbf{felbermayrGlobalSanctionsData2020?}), and international
+  agreements (\textbf{kinneDefenseCooperationAgreement2020?};
+  \textbf{owsiakInternationalBorderAgreements2018?}), dispute resolution
+  (\textbf{frederickIssueCorrelatesWar2017?}), and diplomacy
+  (\textbf{moyerWhatAreDrivers2020?};
+  \textbf{sechserMilitarizedCompellentThreats2011?}).} Thanks to
 improvements in natural language processing, more open-ended efforts
 have begun to capture entire unstructured streams of events from
-international news reports.\footnote{See Beieler et al. (2016); Boschee
-  et al. (2015); Brandt et al. (2018); Grant et al. (2017); Li et al.
-  (2021). On event extraction from images and social media see Zhang and
-  Pan (2019) and Steinert-Threlkeld (2019).} How close these efforts are
-to accurately measuring all or even most of what is essential in
-international relations is an open empirical question, one for which we
-provide new evidence here.
-
-Our contribution is a high coverage ontology and event dataset for key
-historical episodes in 20th and 21st-century international relations. We
-develop a large, flexible ontology of international events with the help
-of both human coders and natural language processing. We apply it
-sentence-by-sentence to an unusually high-quality corpus of historical
-narratives of international crises (Brecher 1999; Wilkenfeld and Brecher
-2000; Brecher et al. 2021). The result is a new lower bound estimate of
-how much actually happens between states during pivotal historical
-episodes. We then develop several methods for objectively gauging how
-well these event codings reconstruct the information contained in the
-original narrative. We conclude by benchmarking our event codings
-against several current state of the art event data collection efforts.
-We find that existing systems produce sequences of events that do not
-contain enough information to reconstruct the underlying historical
-episode. The underlying fine-grained variation in international affairs
-is unrecognizable through the lens of current quantification efforts.
-
-This is a measurement paper that makes the following argument --- there
-is a real-world unobserved latent concept known as international
-relations, we propose a method for systematically measuring it, we
-successfully apply this method producing a new large-scale set of
-measurements, and those measurements exhibit several desirable kinds of
-internal and external validity, and those measurements out-perform other
-existing approaches. The article organizes that argument into eight
-sections: task definition; corpus; priors/existing state of the art;
-ICBe coding process; internal consistency; case study selection; recall;
-and precision. A final section concludes.
-
-\hypertarget{task-definition}{%
-\section{Task Definition}\label{task-definition}}
-
-We consider the measurement task of abstracting discrete events about a
-historical episode in international relations. The easiest way to convey
-the task is with an example. Figure 1 shows a narrative account of the
-Cuban Missile Crisis (1962) alongside a mapping from each natural
-language sentence to discrete machine-readable abstractive events.
-Formally, a historical episode, \(H\), is demarcated by a period of time
-\([T_{start}, T_{end}] \in T\), a set of Players \(p \in P\), and a set
-of behaviors they undertook during that time \(b \in B\). International
-Relations, \(IR\), is the system of regularities that govern the
-strategic interactions that world actors make during a historical
-episode, given their available options, preferences, beliefs, and
-expectations of choices made by others. We observe neither \(H\) nor
-\(IR\) directly. Rather the Historical Record, \(HR\), produces
-documents \(d \in D\) containing some relevant and true (as well as
-irrelevant and untrue) information about behaviors that were undertaken
-recorded in the form of unstructured natural language text. The task is
-to combine informative priors about \(IR\) with an unstructured corpus
-\(D\) to produce a series of structured discrete events, \(e \in E\),
-that have high coverage, precision, and recall over what actually took
-place in history, \(H\).
+international news reports.\footnote{See
+  (\textbf{beielerGeneratingPoliticalEvent2016?});
+  (\textbf{boscheeICEWSCodedEvent2015?});
+  (\textbf{brandtPhoenixRealTimeEvent2018?});
+  (\textbf{grantOUEventData2017?});
+  (\textbf{liComprehensiveSurveySchemabased2021?}). On event extraction
+  from images and social media see
+  (\textbf{zhangCASMDeepLearningApproach2019?}) and
+  (\textbf{steinert-threlkeldFutureEventData2019?}).} This has invited
+fruitful efforts to evaluate the coverage, quality, and accuracy of
+attempts to measure international affairs.
+
+We advance existing efforts to identify and structure regularized events
+and actor in international politics by combining human coding with
+natural language processing to develop (1) a large, flexible ontology of
+international affairs and (2) a fine-grained and structured event
+dataset of international crises from 1918-2017 developed by applying our
+ontology to an unusually high-quality corpus of historical narratives of
+international crises
+(\textbf{brecherInternationalStudiesTwentieth1999?};
+\textbf{wilkenfeldInterstateCrisesViolence2000?};
+\textbf{brecherInternationalCrisisBehavior2021?}). We then develop
+several methods for objectively gauging how well these event codings
+reconstruct the information contained in the original crisis narrative.
+We conclude by benchmarking our event codings against several current
+state of the art event data collection efforts. The underlying
+fine-grained variation in international affairs is unrecognizable
+through the lens of current quantification efforts. We find that
+existing models produce data on historical episodes that do not contain
+enough information to reconstruct the underlying event. In focusing this
+initial effort on international crises as a proof of concept sample, we
+demonstrate our ontology and method's potential to improve upon existing
+empirical identifications of patterns of international interactions.
+
+In the proceeding four sections, this measurement paper makes the
+following arguments. First, there is a real-world unobserved latent
+concept known as international relations that can and should be
+systematically measured. Second, we propose a method for systematic
+large-scale measurement of the actors and behaviors in international
+affairs and as a proof of concept apply that method to a well-regarded
+and salient sample of events known as international crises. Third, in
+doing so we confirm that those measurements exhibit several desirable
+kinds of internal and external validity and out-perform existing
+approaches. Fourth, this validation can be evaluated in detail via new
+event visualizations, with examples provided for case studies of the
+1962 Cuban Missile Crisis and 2014 Crimea-Donbas crisis. A final section
+concludes.
+
+\hypertarget{identifying-and-measuring-international-relations}{%
+\section{Identifying and measuring international
+relations}\label{identifying-and-measuring-international-relations}}
+
+\hypertarget{motivation}{%
+\subsection{Motivation}\label{motivation}}
+
+How can scholars abstract and measure discrete events about a historical
+episode in international relations? We employ a metaphor of chess, a
+game that despite its complexity can nonetheless be recorded in a
+standardized and structured manner. Like chess, international
+interactions involve a finite set of players (e.g.~polities, rebel
+groups, IGOs) expressing their behaviors (e.g.~thinking, saying, and
+doing) by moving pieces (e.g.~military platforms, civilian personnel,
+diplomats) from and onto identifiable locations (geo-coded coordinates).
+These moves occur over a marked time period (start and end of a
+historical episode) and gambits occur in recordable sequences (actions
+and reactions) to produce observable, if still disputable, outcomes
+(e.g.~victory, defeat, stalemate, peace). Our knowledge of this
+historical episode, including the actors involved as well as their
+preferences, behaviors, and beliefs are only indirectly observed from
+historical records that most often take the form of unstructured natural
+language text.
+
+Much like the recording of chess evolved from natural language
+descriptive text notation to the modern figurine algebra notion,
+international relations scholars have recently sought to produce a
+structured account of historical events by combining the unstructured
+corpus of historical records with informative priors about international
+relations. The resulting structured account of information about a
+historical episode can be combined with that of other events to produce
+a systematic account of political events from which we can garner novel
+insight, assuming the underlying data have high coverage, precision, and
+recall. The easiest way to convey the desired produced of this task is
+with an example. (\textbf{fig-cuba-narrative?}) shows a narrative
+account of the Cuban Missile Crisis (1962) in natural language sentences
+alongside a mapping to discrete machine-readable abstractive events.
+From the structured data, scholars can identify similarities and
+differences across events concerning important concepts like when
+particular foreign policy actions deter versus inflame
+(\textbf{jervisCooperationSecurityDilemma1978?};
+\textbf{glaserCausesConsequencesArms2000?}), when third parties mediate
+in interstate disputes
+(\textbf{haffarEmergentPeacemakersCataloguing2002?};
+\textbf{quinnPowerPlayMediation2006?}), and how actors try to
+communicate resolve (\textbf{tragerDiplomacyWarPeace2016?};
+\textbf{luptonReexaminingReputationResolve2018?}). Identifying patterns
+of international interactions is not just an inherently interesting
+enterprise; it is a necessary precondition to important efforts to
+predict where policymakers should turn their attention to improve global
+welfare (\textbf{wardLearningSteppingFuture2013?};
+\textbf{begerReassessingRoleTheory2021?}).
+
+\begin{figure}
+\hypertarget{fig-cuba-narrative}{%
+\centering
+\includegraphics{case_study_cuban_precision.png}
+\caption{Cuban Missile Crisis (1962) - ICB Narrative vs.~ICBe
+Events}\label{fig-cuba-narrative}
+}
+\end{figure}
+
+\hypertarget{existing-state-of-the-art-measurements}{%
+\subsection{Existing state of the art
+measurements}\label{existing-state-of-the-art-measurements}}
+
+We draw informative prior beliefs about the underlying process of
+international relations that we expect to govern behavior during
+historical episodes and their conversion to the historical record. We
+organize our prior beliefs along two overarching axes: existing efforts
+to identify the actors/actions of international relations and
+identifying a corpus that can be used to produce an ontology of the
+information we hope to recover. Table 1 describes these two axes as
+columns and rows, respectively.
+
+As we are not the first to attempt to measure international relations in
+a structured manner, the columns of Table 1 compare the ontological
+coverage of ICBe to existing state of the art systems in production and
+with global coverage. We choose these datasets and models as they
+represent frequently used and reputable efforts to structure and
+describe historical events of interest to scholars of international
+politics. The first column starts with our contribution, ICBe, alongside
+other event-level datasets including CAMEO dictionary lookup-based
+systems (Historical Phoenix
+(\textbf{althausClineCenterHistorical2019?}); ICEWS
+(\textbf{boscheeICEWSCodedEvent2015?}); Terrier
+(\textbf{grantOUEventData2017?})), the Militarized Interstate Disputes
+Incidents dataset, and the UCDP-GED dataset
+(\textbf{daviesOrganizedViolence19892022?};
+\textbf{sundbergIntroducingUCDPGeoreferenced2013?}).\footnote{Other
+  related datasets that insufficiently overlap ICBe's domain for
+  comparison include BCOW
+  (\textbf{lengMilitarizedInterstateCrises1988?}), WEIS
+  (\textbf{mcclellandWorldEventInteraction1978?}), CREON
+  (\textbf{hermannComparativeResearchEvents1984?}), CASCON
+  (\textbf{bloomfieldCASCONIIIComputeraided1989?}), SHERFACS
+  (\textbf{shermanSHERFACSCrossParadigmHierarchical2000?}), Real-Time
+  Phoenix (\textbf{brandtPhoenixRealTimeEvent2018?}), and COfEE
+  (\textbf{balaliCOfEEComprehensiveOntology2021?}) (see histories in
+  (\textbf{merrittMeasuringEventsInternational1994?}) and
+  (\textbf{schrodtTwentyYearsKansas2006?})).} The final set of columns
+compares episode-level datasets beginning with the original ICB project
+(\textbf{brecherInternationalCrisisBehavior2021?};
+\textbf{brecherCrisesWorldPolitics1982?};
+\textbf{beardsleyInternationalCrisisBehavior2020?}); the Militarized
+Interstate Disputes dataset (\textbf{palmerMID5Dataset20112021?};
+\textbf{giblerInternationalConflicts181620102018?}), and the Correlates
+of War (\textbf{sarkeesResortWar181620072010?}). There is imperfect
+overlap concerning their intended depth and scope of coverage;
+`international crises' are similar, but not identical to, `interstate
+wars' and `militarized interstate disputes' which differ yet again from
+`individual events of organized violence' and `non-violent action'. Even
+like-concepts require care in comparison, as an `aim' in ICBe is the
+same as in MIPS, but an `alert' in ICBe is not the same as an `alert' in
+MID. Definitions for each ICBe variable are provided in the codebook.
 
 \clearpage
-
-\begin{figure}[H]
-\caption{Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
-\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
-\end{figure}
+\singlespacing
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
+
+\renewcommand*{\arraystretch}{0.75}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{|p{0.10in}|p{2.00in}|p{1.60in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}}
+
+\caption{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endfirsthead \caption[]{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Start}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1945}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1977}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1995}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1989}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{End}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2019}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2018}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2020}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2015}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2014}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2007}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{N}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{32K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{8.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{28.4M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{17.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{128K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{5.9K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Corpus}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{ICB}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{fazalStateDeathPolitics2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{spruytSovereignStateIts1996?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{haffarEmergentPeacemakersCataloguing2002?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{bushDensityDeclineFounding2019?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mishali–Ram}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{lacinaExplainingSeverityCivil2006?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{mcnabbcochranMeasuringMilitaryEffectiveness2017?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{carafanoMeasuringMilitaryPower2014?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{goertzMeasuringMilitaryAllocations1986?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{gartzkeCrossDomainDeterrenceStrategy2019?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{lindsayPoliticsManyOther2020?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{carterStrategyTerritorialConflict2010?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Brecher}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wilkenfeld}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{goldgeierPsychologyInternationalRelations2001?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{steinEvaluatingWarOutcomes1980?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{sullivanWarAimsWar2007?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{ramsayInformationUncertaintyWar2017?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{yarhi-miloEyeBeholderHow2013?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{oneillInternationalNegotiationConceptual2018?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{zartmanEscalationNegotiationInternational2005?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{sechserMilitarizedCompellentThreats2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{powellBargainingTheoryInternational2002?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{goemansIntroducingArchigosDataset2009?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{powellGlobalInstancesCoups2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{chenowethIntroducingNonviolentAction2019?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{eckOneSidedViolenceCivilians2007?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{lafreeIntroducingGlobalTerrorism2007?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{beardsleyMediationDilemma2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{giblerMeasuringAlliancesCorrelates2004?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{owsiakInternationalBorderAgreements2018?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{leedsAllianceReliabilityTimes2003?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{leedsDomesticPoliticalInstitutions1999?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{yarhi-miloArmAllyPatron2016?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{laiEffectsDifferentTypes2004?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{allenUSGlobalMilitary2021?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{fortnaPeaceTime2018?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{minInterstateWarBattle2021?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{sarkeesResortWar181620072010?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{reiterRevisedLookInterstate2016?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{frederickIssueCorrelatesWar2017?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
 \clearpage
-
-\hypertarget{corpus}{%
-\section{Corpus}\label{corpus}}
-
-For our corpus, \(D\), we select a set of unusually high-quality
-historical narratives from the International Crisis Behavior (ICB)
-project (\(n=471\))(Supplementary Information (SI) Appendix 1.1)(Brecher
-et al. 2021; Brecher and Wilkenfeld 1997). Their domain is 20th and
-21st-century crises, defined as a change in the type, or an increase in
-the intensity, of disruptive interaction with a heightened probability
-of military hostilities that destabilizes states' relationships or
-challenges the structure of the international system (Brecher and
-Wilkenfeld 1982). Crises are a significant focus of detailed single case
-studies and case comparisons because they provide an opportunity to
-examine behaviors in IR short of, or at least prior to, full conflict
-(Holsti 1965; Paige 1968; Allison and Zelikow 1971; Gavin 2014; Brecher
-and Wilkenfeld 1982; Iakhnis and James 2019). Case selection was
-exhaustive based on a survey of world news archives and region experts,
-cross-checked against other databases of war and conflict, and
-non-English sources (Kang and Lin 2019; Brecher et al. 2021, 59). Each
-narrative was written by consensus by a small number of scholars, using
-a uniform coding scheme, with similar specificity (Hewitt 2001). The
-corpus is unique in IR because it is designed to be used in a downstream
-quantitative coding project.
-
-\hypertarget{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}{%
-\section{Prior Beliefs about IR, Ontological Coverage, and the Existing
-State of the
-Art}\label{prior-beliefs-about-ir-ontological-coverage-and-the-existing-state-of-the-art}}
-
-Next, we draw informative prior beliefs about the underlying process of
-IR that we expect to govern behavior during historical episodes and
-their conversion to the historical record. We organize our prior beliefs
-along two overarching axes, summarized in detail by Table 1.
-
-The first axis (rows) represents the types of information we expect to
-find in IR and forms the basis for our proposed ontology. We employ a
-metaphor of a chess game, with players (polities, rebel groups, IGOs,
-etc.), pieces (military platforms, civilians, domains), and behaviors
-(think, say, do). Precise sequencing is required to capture gambits
-(sequences of moves) and outcomes (victory, defeat, peace, etc.), while
-precise geo-coding is required to understand the chessboard (medium of
-conflict). We find 472 actors and 117 different behaviors.\footnote{See
-  the full codebook on Github Repository
-  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
-
-We base our informed priors primarily on two sources of information. The
-first is the extensive existing measurement efforts of IR which we
-provide citations alongside each concept. Second, we performed
-preliminary natural language processing of the corpus and identified
-named entities and behaviors mentioned in the text. Verbs were matched
-to the most likely definition found in Wordnet (Miller 1995), tallied,
+\doublespacing
+
+The rows in Table 1 represent the types of information we expect to find
+in international relations and forms the basis for our proposed
+ontology. We create this by performing preliminary natural language
+processing of the corpus and identified named entities and behaviors
+mentioned in the text. Verbs were matched to the most likely definition
+found in Wordnet (\textbf{millerWordNetLexicalDatabase1995?}), tallied,
 and then aggregated into a smaller number of hypernyms balancing
 conceptual detail and manageable sparsity for human coding (SI Appendix
-1.2).
-
-The second axis (columns) compares the very high ontological coverage of
-ICBe to existing state of the art systems in production and with global
-coverage. They begin with our contribution ICBe, alongside other
-event-level datasets including CAMEO dictionary lookup-based systems
-(Historical Phoenix (Althaus et al. 2019); ICEWS (Boschee et al. 2015);
-Terrier (Grant et al. 2017)), the Militarized Interstate Disputes
-Incidents dataset, and the UCDP-GED dataset (Davies, Pettersson, and
-Öberg 2022; Sundberg and Melander 2013).\footnote{Other related datasets
-  that insufficiently overlap ICBe's domain for comparison include BCOW
-  (Leng and Singer 1988), WEIS (McClelland 1978), CREON (Hermann 1984),
-  CASCON (Bloomfield and Moulton 1989), SHERFACS (Sherman 2000),
-  Real-Time Phoenix (Brandt et al. 2018), and COfEE (Balali, Asadpour,
-  and Jafari 2021) (see histories in Merritt (1994) and Schrodt and Hall
-  (2006)).} The final set of columns compares episode-level datasets
-beginning with the original ICB project (Brecher et al. 2021; Brecher
-and Wilkenfeld 1982; Beardsley et al. 2020); the Militarized Interstate
-Disputes dataset (Palmer et al. 2021; Gibler 2018), and the Correlates
-of War (Sarkees and Wayman 2010). With the exception of large-scale
-CAMEO dictionary-based systems, the existing state of the art
-quantitative datasets ignore the vast majority of the information
-content found in international relations.\footnote{See Balali, Asadpour,
-  and Jafari (2021) for a recent review of ontological depth and
-  availability of Gold Standard example text.}
-
-\clearpage
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.75}
-
-\begin{longtable}[c]{|p{0.10in}|p{2.00in}|p{1.60in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}}
-
-\caption{Ontological coverage of ICBe versus existing State of the Art
-}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Concept}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICBe}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Phoenix}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Terrier}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICEWs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{UCDP-GED}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{ICB}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{MIDs}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{COW}}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Start}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{End}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{E}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{States}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fazal}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Spruyt}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Subnational\ Actors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Haffar}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{IGO/NGO}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Bush}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hadden}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Civilians}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ben-Yehuda}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{MishaliRam}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fatalities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lacina}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2006)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{McNabb}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cochran}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Long}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Size}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Carafano}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2014)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goertz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diehl}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Force\ Domain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lindsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gartzke}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Carter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Brecher}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wilkenfeld}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goldgeier}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Tetlock}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Stein}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Russett}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sullivan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ramsay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{O’Neill}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Zartman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Faure}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sechser}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{R.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Goemans,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gleditsch,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chiozza}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2009)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{J.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{M.}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Powell}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Thyne}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Chenoweth,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hendrix,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hunter}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Eck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hultman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{LaFree}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Dugan}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Beardsley}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Gibler}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2004)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Owsiak,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cuttner,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Buck}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Leeds}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Yarhi-Milo,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lanoszka,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Cooper}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Lai}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Allen,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Flynn,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Martinez}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Machain}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Fortna}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2018)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Min}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Sarkees}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Wayman}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2010)}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Reiter,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Stam,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Horowitz}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\rotatebox[origin=c]{270}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Frederick,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Hensel,}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{and}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Macaulay}}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\ }}\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{✓}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\end{longtable}
-
-\clearpage
-
-\hypertarget{icbe-coding-process}{%
-\section{ICBe Coding Process}\label{icbe-coding-process}}
+1.2). This comparison is not intended to fault existing data and models
+for not including every variable in ICBe's ontology, as some of these
+variables fall outside the scope of a particular dataset's intended
+purpose. Rather, it serves as an initial basis for identifying the
+heterogeneity in existing efforts to abstract and measure discrete
+historical events of interest and to provide theoretical justifications
+from existing research about what is included in our dataset's ontology
+and where ICBe's detail about historical events can be compared to the
+current state of the art.
+
+With the exception of large-scale CAMEO dictionary-based systems (the
+first grouping of columns), our ontology improves upon the the existing
+state of the art quantitative datasets that ignore important information
+content about international interactions.\footnote{See
+  (\textbf{balaliCOfEEComprehensiveOntology2021?}) for a recent review
+  of ontological depth and availability of Gold Standard example text.}
+We highlight two particular innovations. First, we separate the `chess
+pieces' from the `chess players' in distinguishing between different
+actors within a state. By virtue of our ontology coding military versus
+civilian actors and national leaders versus bureaucrats, our data can be
+used to explore important questions concerning civilian-military
+relations (\textbf{narangCivilmilitaryPathologiesDefeat2017?}), Track
+Two diplomacy and the role of sub-national actors
+(\textbf{hsuStatesHarnessingSubnational2020?}), and the evolution of
+what actors are engaged in crises - a topic of increasing interest as
+states engage in gray zone conflict by employing the coast guard or
+paramilitary mercenaries instead of internationally recognized state
+militaries (Gannon et al. 2023). Second, we add information about the
+domains in which actors behave - whether in land, air, sea, space, or
+cyber - since they differ in their technology, tactics, geography, and
+purpose (\textbf{gartzkeCrossDomainDeterrenceStrategy2019?}). Doing so
+allows researchers to identify and explain patterns in escalation
+conditional on the military means states use in conflict. Recent
+concerns about cross-domain conflict and the effect of new domains of
+conflict like space and cyber have made this an endeavor of increased
+interest to practitioners (\textbf{gannonOneIfLand2022?}).
+
+\hypertarget{methodology-and-data}{%
+\section{Methodology and data}\label{methodology-and-data}}
+
+\hypertarget{corpus}{%
+\subsection{Corpus}\label{corpus}}
+
+For our corpus, we select a set of unusually high-quality historical
+narratives from the International Crisis Behavior (ICB) project
+(\(n=471\)) with coverage spanning 1918-2017 (Supplementary Information
+(SI) Appendix 1.1)(\textbf{brecherInternationalCrisisBehavior2021?};
+Brecher and Wilkenfeld 1997). ICB defines a crisis as meeting three
+conditions: (1) an actor perceives a threat to one of more of its basic
+values, (2) the actor has a finite time horizon for responding to the
+perceived threat, and (3) the probability of military hostility has
+increased (\textbf{brecherCrisesWorldPolitics1982?}). Crises are a
+significant focus of detailed single case studies and case comparisons
+because they provide an opportunity to examine behaviors in
+international relations short of, or at least prior to, full conflict
+(\textbf{holsti1914Case1965?}; \textbf{paigeKoreanDecisionJune1968?};
+\textbf{allisonEssenceDecisionExplaining1971?};
+\textbf{gavinHistorySecurityStudies2014?};
+\textbf{brecherCrisesWorldPolitics1982?};
+\textbf{iakhnisCrisesWorldPolitics2019?}). The corpus is also unique in
+being designed to be used in a downstream quantitative coding project,
+meaning each narrative was written by consensus by a small number of
+scholars using a uniform coding scheme where things like word choice,
+writing style, and level of specificity were deliberately done in a
+consistent manner (\textbf{hewittEngagingInternationalData2001?}). Case
+selection was exhaustive based on a survey of world news archives and
+region experts, cross-checked against other databases of war and
+conflict, and non-English sources (\textbf{kangUSBiasStudy2019?};
+\textbf{brecherInternationalCrisisBehavior2021?}).
+
+\hypertarget{coding-process}{%
+\subsection{Coding Process}\label{coding-process}}
 
@@
 smaller number of significant decisions are made early on and then
-progressively refined into more specific details (Brust and Denzler
-2020).\footnote{This process quickly focuses the coder on a smaller
-  number of relevant options while also allowing them to apply multiple
-  tags if the sentence explicitly includes more than one or there is
-  insufficient evidence to choose only one tag. The guided coding
-  process also allows for the possibility that earlier coarse decisions
-  have less error than later fine-grained decisions.} Each coder was
-instructed to first thoroughly read the full crisis narrative and then
-presented with a custom graphical user interface (SI Appendix 2.1).
-Coders then proceeded sentence by sentence, choosing the number of
-events (0-3) that occurred, the highest behavior (thought, speech, or
-activity), a set of players (\(P\)), whether the means were primarily
-armed or unarmed, whether there was an increase or decrease in
-aggression (uncooperative/escalating or cooperative/de-escalating), and
-finally one or more non-mutually exclusive specific activities. Some
-additional details like location and timing information were always
-collected while other details were only collected if appropriate,
-e.g.~force size, fatalities, domains, units, etc. A unique feature of
-the ontology is that thought, speech, and do behaviors can be nested
-into combinations, e.g.~an offer for the U.S.S.R. to remove missiles
-from Cuba in exchange for the U.S. removing missiles from Turkey.
-Through compounding, the ontology can capture what players were said to
-have known, learned, or said about other specific fully described
-actions.
+progressively refined into more specific details
+(\textbf{brustIntegratingDomainKnowledge2020?}).\footnote{This process
+  quickly focuses the coder on a smaller number of relevant options
+  while also allowing them to apply multiple tags if the sentence
+  explicitly includes more than one or there is insufficient evidence to
+  choose only one tag. The guided coding process also allows for the
+  possibility that earlier coarse decisions have less error than later
+  fine-grained decisions.} Each coder was instructed to first thoroughly
+read the full crisis narrative and then presented with a custom
+graphical user interface (GUI) (SI Appendix 2.1). Coders then proceeded
+sentence by sentence, choosing the number of events (0-3) that occurred,
+the highest behavior (thought, speech, or activity), a set of players,
+whether the means were primarily armed or unarmed, whether there was an
+increase or decrease in aggression (uncooperative/escalating or
+cooperative/de-escalating), and finally one or more specific and
+non-mutually exclusive activities. Some additional details were always
+collected (e.g.~location and timing) while other details were only
+collected if appropriate (e.g.~force size, fatalities, domains, units).
+We find 472 actors and 117 different behaviors.\footnote{See the full
+  codebook on Github Repository
+  \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
+A unique feature of the ontology is that thought, speech, and do
+behaviors can be nested into combinations, e.g.~an offer for the
+U.S.S.R. to remove missiles from Cuba in exchange for the U.S. removing
+missiles from Turkey. Through compounding, the ontology can capture what
+players were said to have known, learned, or said about other specific
+fully described actions.
 
@@
 
+\hypertarget{performance-comparison}{%
+\section{Performance comparison}\label{performance-comparison}}
+
 \hypertarget{internal-consistency}{%
-\section{Internal Consistency}\label{internal-consistency}}
+\subsection{Internal consistency}\label{internal-consistency}}
 
@@
 
-\hypertarget{case-study-selection}{%
-\section{Case Study Selection}\label{case-study-selection}}
-
-The remaining two qualities we seek to measure are recall and precision
-of ICBe events in absolute terms and relative to other existing systems.
-We provide full ICB narratives, ICBe coding in an easy-to-read
-iconographic form, and a wide range of visualizations for every case on
-the companion website. In this paper, we focus on two deep case studies.
-The first is the Cuban Missile Crisis (Figure 1) which took place
-primarily in the second half of 1962, involved the United States, the
-Soviet Union, and Cuba, and is widely known for bringing the world to
-the brink of nuclear war (hereafter Cuban Missiles). The second is the
-Crimea-Donbas Crisis (SI Appendix 4.1) which took place primarily in
-2014, involved Russia, Ukraine, and NATO, and within a decade spiraled
-into a full-scale invasion (hereafter Crimea-Donbas). Both cases involve
-a superpower in crisis with a neighbor, initiated by a change from a
-friendly to a hostile regime, with implications for economic and
-military security for the superpower, risked full-scale invasion, and
-eventually invited intervention by opposing superpowers. We choose these
-cases because they are substantively significant to 20th and
-21st-century international relations, widely known across scientific
-disciplines and popular culture, and are sufficiently brief to evaluate
-in depth.
-
-\hypertarget{recall}{%
-\section{Recall}\label{recall}}
-
-Recall measures the share of desired information recovered by a sequence
-of coded events, \(Pr(E|H)\), and is poorly defined for historical
-episodes. First, there is no genuine ground truth about what occurred,
-only surviving texts about it. Second, there is no \textit{a priori}
-guide to what information is necessary detail and what is ignorable
-trivia. History suffers from what is known as the Coastline Paradox
-(Mandelbrot 1983) --- it has a fractal dimension greater than one such
-that the more you zoom in, the more detail you will find about
-individual events and in between every two discrete events. The ICBe
-ontology is a proposal about what information is important, but we need
-an independent benchmark to evaluate whether that proposal is a good one
-and that allows for comparing proposals from event projects that had
-different goals. We need a yardstick for history.
+\hypertarget{improvement-over-existing-efforts}{%
+\subsection{Improvement over existing
+efforts}\label{improvement-over-existing-efforts}}
+
+To evaluate our coding process relative to existing datasets, we measure
+the recall and precision of ICBe events in absolute terms and relative
+to other existing systems. Recall measures the share of desired
+information recovered by a sequence of coded events while precision
+measures the degree to which a sequence of events correctly and usefully
+describes the information in history. To aid in subjective evaluation of
+the precision and recall of ICBe for each event, we provide full ICB
+narratives, ICBe coding in an easy-to-read iconographic form, and a wide
+range of visualizations for every case on the companion website.
+
+Recall for historical episodes is poorly defined for two reasons.
+History may or may not be written by the victors but by virtue of being
+written by \emph{someone} there is no genuine ground truth about what
+occurred, only surviving texts about it (Turberville 1933). Second,
+there is no \emph{a priori} guide to what information is necessary
+detail and what is ignorable trivia. History suffers from what is known
+as the Coastline Paradox (\textbf{mandelbrotFractalGeometryNature1983?})
+--- it has a fractal dimension greater than one such that the more you
+zoom in, the more detail you will find about individual events as well
+as in between any two discrete events. The ICBe ontology is a proposal
+about what information is important, but we need an independent
+benchmark to evaluate whether that proposal is a good one and that
+allows for comparing proposals from event projects that had different
+goals. We need a yardstick for history.
 
 Our strategy for dealing with both problems is a plausibly objective
-yardstick called a synthetic historical narrative. For both case
-studies, we collect a large diverse corpus of narratives spanning
-timelines, encyclopedia entries, journal articles, news reports,
-websites, and government documents. Using natural language processing
-(fully described in SI Appendix 3.1), we identify details that appear
-across multiple accounts. The more accounts that mention a detail, the
-more central it is to understanding the true historical episode. The
-theoretical motivation is that authors face word limits which force them
-to pick and choose which details to include, and they choose details
-that serve the specific context of the document they are producing. With
-a sufficiently large and diverse corpus of documents, we can vary the
-context while holding the overall episode constant and see which details
-tend to be invariant to context. Intuitively, a high-quality event
-dataset should have high recall for context invariant details both
-because of their broader relevance and also because they are easier to
-find in source material.
-
-Synthetic historical narratives for Cuban Missiles (51 events drawn from
-2020 documents) and Crimea-Donbas (30 events drawn from 971 documents)
-appear in Figure 2. Each row represents a detail that appeared in at
-least five documents along with an approximate start date, a handwritten
-summary, the number of documents it was mentioned in, and whether it
-could be identified in the text of our ICB corpus, in our ICBe events,
-or any of the competing systems.
-
-From them, we draw several stylized facts. First, there is substantial
-variation in which details any one document will choose to include. Our
-ground truth ICB narratives contain 17/51 and 23/30 of the events from
-the synthetic narrative and include other details that are not in the
-synthetic narrative. Second, mentions of a detail across accounts are
-exponentially distributed with context-invariant details appearing
-dozens to hundreds of times more than context-dependent details. Third,
-crisis start and stop dates are arbitrary, and the historical record
-points to many precursor events as necessary detail for understanding
-later events, e.g.~the U.S. was in a \textit{de facto} grey-scale war
-with Cuba before it invited Soviet military protection (Cormac and
-Aldrich 2018) and Ukraine provided several security guarantees to Russia
-that were potentially undone, e.g.~a long term lease on naval facilities
-in Crimea. Fourth, we find variation between the two cases. Cuban
-Missiles has a cleaner canonical end with the Soviets agreeing to
-withdraw missiles while Crimea-Donbas meekly ends with a second
-cease-fire agreement (Minsk II) but continued fighting. The canonical
-narrative of Cuban Missiles also includes high-level previously
-classified details, while the more recent Crimea-Donbas case reflects
-primarily public reporting.
-
-We find substantive variation in recall across systems. Recall for each
-increases in the number of document mentions which is an important sign
-of validity for both them and our benchmark. The one outlier is Phoenix
-which is so noisy that it's flat to decreasing in mentions. The two
-episode-level datasets have very low coverage of contextual details. The
-two other dictionary systems ICEWs and Terrier have high coverage, with
-ICEWs outperforming Terrier. ICBe strictly dominates all of the systems
-but ICEWs in recall though we note that the small sample sizes mean
-these systems should be considered statistically indistinguishable.
-Importantly our corpus of ICB narratives has very high recall of
+yardstick called a synthetic historical narrative. We collect a large
+diverse corpus of narratives spanning timelines, encyclopedia entries,
+journal articles, news reports, websites, and government documents.
+Using natural language processing (fully described in SI Appendix 3.1),
+we identify details that appear across multiple accounts. The more
+accounts that mention a detail, the more central it is to understanding
+the true historical episode. The theoretical motivation is that authors
+face word limits which force them to pick and choose which details to
+include, and they choose details that serve the specific context of the
+document they are producing. With a sufficiently large and diverse
+corpus of documents, we can vary the context while holding the overall
+episode constant and see which details tend to be invariant to context.
+Intuitively, a high-quality event dataset should have high recall for
+context invariant details both because of their broader relevance and
+also because they are easier to find in source material.
+
+We find substantive variation in recall across existing state of the art
+methods. Mentions of a detail across accounts are exponentially
+distributed with context-invariant details appearing dozens to hundreds
+of times more than context-dependent details.\footnote{As the ICB
+  narratives are intended to explain conflictual behavior in a political
+  context, many of the missing events concern more economic components
+  of conflict (eg. nationalizing a foreign business). Even when they
+  occur in the context of a crisis, these events largely fall outside
+  the sample of information on which ICBe's ontology is currently
+  trained. Even with this limitation, ICBe is more comprehensive than
+  the existing datasets that do try to code the economic dimensions of
+  these crises. We see expanding the ontology to broader international
+  phenomenon as a promising future implementation of our model.}
+Furthermore, crisis start and stop dates are arbitrary, and the
+historical record points to many precursor events as necessary detail
+for understanding later events. (\textbf{fig-recall-cases?}) compares
+ICBe's recall with that of existing datasets for the two case studies
+detailed in Section 4. ICBe strictly dominates all of the systems but
+ICEWs in recall though we note that the small sample sizes mean these
+systems should be considered statistically indistinguishable. Across all
+existing datasets and ICBe, recall increases with the number of document
+mentions which is an important sign of validity for both them and our
+benchmark. The one outlier is Phoenix which in the Cuban Missile Crisis
+case is so noisy that it's recall curve is flat to decreasing as
+mentions increase. The two episode-level datasets (MIDs and ICM) have
+low coverage of contextual details. The two other dictionary systems
+ICEWs and Terrier have higher coverage, with ICEWs outperforming
+Terrier. Importantly our corpus of ICB narratives has high recall of
 frequently mentioned details giving us confidence in how those summaries
 were constructed, and ICBe lags only slightly behind showing that it
-left very little additional information on the table.
-
-\clearpage
-
-\begin{figure}[H]
-\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
-\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
-\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents.
-Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets (SI Appendix 3.2 and 3.3).}
+left little additional information on the table.
+
+\begin{figure}
+\hypertarget{fig-recall-cases}{%
+\centering
+\includegraphics{p_recall.png}
+\caption{Recall comparison of two cases across existing state of the art
+efforts. Higher y-axis values represent higher recall and higher x-axis
+values represent number of times that detail is mentioned across the
+full corpus used to construct the synthetic
+narrative.}\label{fig-recall-cases}
+}
 \end{figure}
-\clearpage
-
-\hypertarget{precision}{%
-\section{Precision}\label{precision}}
-
-The other side of event measurement is precision, the degree to which a
-sequence of events correctly and usefully describes the information in
-history, \(Pr(H|E)\). It does little good to recall a historical event
-but too vaguely (e.g.~MIDs describes the Cuban Missile Crisis as a
-blockade, a show of force, and a stalemate) or with too much error
-(e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between
-1995-2019) to be useful for downstream applications. ICBe's ontology and
-coding system are designed to strike a balance so that the most
-important information is recovered accurately but also abstracted to a
-level that is still useful and interpretable. You should be able to lay
-out the events of a crisis on a timeline, as in Figure 3, and read off
-the macrostructure of an episode from each individual move. We call this
-visualization a crisis map, a directed graph intersected with a
-timeline, and provide crisis maps for every event dataset for each case
-study in SI Appendix 4.3 and 4.4 and for all crises on the companion
-website.
+
+The second component of event measurement validation is precision. It
+does little good to recall a historical event but too vaguely (e.g.~MIDs
+describes the Cuban Missile Crisis as a blockade, a show of force, and a
+stalemate) or with too much error to be useful for downstream
+applications (e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events
+between 1995-2019). ICBe's ontology and coding system are designed to
+strike a balance so that the most important information is recovered
+accurately but also abstracted to a level that is still useful and
+interpretable.
+
+How does ICBe's precision compare to the existing state of the art? A
+researcher should be able to lay out the events of a crisis on a
+timeline and read off the macrostructure of an episode from each
+individual move. We call this visualization a crisis map, a directed
+graph intersected with a timeline. A crisis map using ICBe for the Cuban
+Missile Crisis case study is provided in (\textbf{fig-cuba-crisismap?}),
+and crisis maps for the two case studies using existing event datasets
+can be found in SI Appendix 4.3 and 4.4 and crisis maps for all crises
+using all datasets can be found on the companion website. The crisis
+maps reveal the episode-level datasets like MIDs or the original ICB are
+too sparse and vague to reconstruct the structure of the crisis (SI
+Appendix 4.3 and 4.4). On the other end of the spectrum, the high recall
+dictionary-based event datasets like Terrier and ICEWs produce so many
+noisy events (several hundred thousand) that even with heavy filtering
+their crisis maps are completely unintelligible. Further, because of
+copyright issues, none of these datasets directly provide the original
+text spans making event-level precision difficult to verify.
 
@@
 coherent statements that can be compared side by side to the original
-source narrative for Cuban Missiles (Figure 1), Crimea-Donbas (SI
-Appendix 4.1), and for every case on the companion website. We further
+source narrative for every case on the companion website. We further
 provide a stratified sample of event codings alongside their source text
-(SI Appendix 4.2).
-
-We find both the visualizations of macrostructure and head-to-head
-comparisons of ICBe codings to the raw text to strongly support the
-quality of ICBe, but as with recall, we seek a more objective detached
-universal benchmark. Our proposed measure is a reconstruction task to
-see whether our intended ontology can be recovered through only
-unsupervised clustering of sentences they were applied to. Figure 4
-shows the location of every sentence from the ICBe corpus in semantic
-space as embedded using the same large language model as before, and the
-median location of each ICBe event tag applied to those
-sentences.\footnote{We preprocess sentences to replace named entities
-  with a generic Entity token.} Labels reflect the individual leaves of
-the ontology and colors reflect the higher level coarse branch nodes of
-the ontology. If ICBe has high precision, substantively similar tags
-ought to have been applied to substantively similar source text, which
-is what we see both in two dimensions in the main plot and via
+(SI Appendix 4.2). We find both the visualizations of macrostructure and
+head-to-head comparisons of ICBe codings to the raw text to strongly
+support the quality of ICBe.
+
+(\textbf{fig-umap?}) shows the location of every sentence from the ICBe
+corpus in semantic space as embedded using the same large language model
+as before, and the median location of each ICBe event tag applied to
+those sentences.\footnote{We preprocess sentences to replace named
+  entities with a generic Entity token.} Labels reflect the individual
+leaves of the ontology and colors reflect the higher level coarse branch
+nodes of the ontology. If ICBe has high precision, substantively similar
+tags ought to have been applied to substantively similar source text,
+which is what we see both in two dimensions in the main plot and via
 hierarchical clustering on all dimensions in the dendrogram along the
-righthand side.\footnote{Hierarchical clustering on cosine similarity
+right-hand side.\footnote{Hierarchical clustering on cosine similarity
   and with Ward's method.}
 
-Finally, how does ICBe's precision compare to the existing state of the
-art? The crisis maps reveal the episode-level datasets like MIDs or the
-original ICB are too sparse and vague to reconstruct the structure of
-the crisis (SI Appendix 4.3 and 4.4). On the other end of the spectrum,
-the high recall dictionary-based event datasets like Terrier and ICEWs
-produce so many noisy events (several hundred thousand) that even with
-heavy filtering their crisis maps are completely unintelligible.
-Further, because of copyright issues, none of these datasets directly
-provide the original text spans making event-level precision difficult
-to verify.
-
-However, given their high recall on our task and the global and
-real-time coverage of dictionary-based event systems, we want to take
-seriously the possibility that some functional transformation could
-recover the precision of ICBe. For example, Terechshenko (2020) attempts
-to correct for the mechanically increasing amount of news coverage each
-year by detrending violent event counts from Phoenix using a human-coded
-baseline. Others have focused on verifying precision for ICEWs on
-specific subsets of details against known ground truths,
-e.g.~geolocation (Cook and Weidmann 2019), protest events (80\%) (Wüest
-and Lorenzini 2020), anti-government protest networks (46.1\%) (Jäger
-2018).
-
-We take the same approach here in Figure 5, selecting four specific
-CAMEO event codings and checking how often they reflect a true
-real-world event from the Crimea-Donbas synthetic narrative. We choose
-four event types around key moments in the crisis. The start of the
-crisis revolves around Ukraine backing out of a trade deal with the EU
-in favor of Russia, but ``sign formal agreement'' events act more like a
-topic detector with dozens of events generated by discussions of a
-possible agreement but not the actual agreement which never
-materialized. The switch is caught by the ``reject plan, agreement to
-settle dispute'', but also continues for Viktor Yanukovych even after he
-was removed from power because of articles retroactively discussing the
-cause of his removal. Events for ``use conventional military force''
+\begin{figure}
+\hypertarget{fig-umap}{%
+\centering
+\includegraphics{p_semantic_embeddings_dendro.png}
+\caption{Dots represent individual ICB narrative sentences, as embedded
+by the Paraphrase-MPNET-base-v2 large language model and flattened into
+two dimensions with UMAP. Text labels reflect individual leaves of the
+ICBe ontology, and colors represent intermediate branches of the
+ontology. Label placement is the median of all of the sentences that the
+tag was applied to by the coders. The dendrogram shows hierarchical
+clustering of the tags. If ICBe precision is high, then the sentences
+that tags were applied to ought to say similar things and the intended
+shape of the ontology ought to be visually
+recognizable.}\label{fig-umap}
+}
+\end{figure}
+
+\hypertarget{case-illustrations}{%
+\section{Case illustrations}\label{case-illustrations}}
+
+In this section, we focus our validation on two case studies for which
+we have produced synthetic narratives using the method described in
+Section 3.2. Our proposed measure is a reconstruction task to see
+whether our intended ontology can be recovered through only unsupervised
+clustering of sentences they were applied to. The first
+((\textbf{fig-cuba-narrative?})) is the Cuban Missile Crisis (hereafter
+Cuban Missiles) which took place primarily in the second half of 1962,
+involved the United States, the Soviet Union, and Cuba, and is widely
+known for bringing the world to the brink of nuclear war. The second (SI
+Appendix 4.1) is the Crimea-Donbas Crisis (hereafter Crimea-Donbas)
+which took place primarily in 2014, involved Russia, Ukraine, and NATO,
+and within a decade spiraled into a full-scale invasion. We choose these
+cases because they are significant in contemporary international
+relations, are widely known across academic disciplines as well as among
+the public, and are sufficiently brief to evaluate in depth. They are
+similar in that both cases involve a superpower in crisis with a
+neighbor that changed from a friendly to a hostile regime, both held
+implications for the economic and military security for the superpower
+by risking full-scale invasion, and both eventually invited intervention
+by an opposing superpower.
+
+\hypertarget{cuban-missile-crisis-1962}{%
+\subsection{Cuban Missile Crisis
+(1962)}\label{cuban-missile-crisis-1962}}
+
+A synthetic historical narrative for Cuban Missiles appears in
+(\textbf{fig-recall-cuba?}), with 51 events drawn from 2,020 documents.
+Each row represents a detail that appeared in at least five documents
+along with an approximate start date, a handwritten summary, the number
+of documents it was mentioned in, and whether it could be identified in
+the text of the original ICB corpus, our ICBe events, and any of the
+competing existing models.
+
+ICB's improved recall of Cuban Missiles was relative to the state of the
+art was summarized in Section 3.2 ((\textbf{fig-recall-cases?})), but
+the events that explain that improvement can now be seen. Our ground
+truth ICB narrative contains 17/51 of the events from the synthetic
+narrative of a case that includes high-level previously classified
+details. ICBe captures nearly all details included in ICB as well as
+more details from the synthetic narrative than any competing dataset.
+Phoenix includes some earlier information than ICBe like the
+nationalization of businesses and back channel negotiations, but the
+crisis narrative has a clean canonical end with the Soviets agreeing to
+withdraw missiles. ICBe stands out in including more communicative
+behavior (do -- speech) than existing datasets like US threats to attack
+and later promises not to invade. Given the recognized importance of
+threat credibility for understanding international conflict, the
+addition of this information is a substantively important improvement
+over the existing state of the art (Slantchev 2011).
+
+\begin{figure}
+\hypertarget{fig-recall-cuba}{%
+\centering
+\includegraphics{case_study_cuban_recall.png}
+\caption{Synthetic narratives combine several thousand accounts of each
+crisis into a single timeline of events, taking only those mentioned in
+at least 5 or more documents. Checkmarks represent whether that event
+could be hand matched to any detail in the ICB corpus, ICBe dataset, or
+any of the other event datasets (SI Appendix 3.2 and
+3.3).}\label{fig-recall-cuba}
+}
+\end{figure}
+
+(\textbf{fig-cuba-crisismap?}) shows the crisis map for the Cuban
+Missile Crisis. Looking at the crisis on a timeline, one can now
+identify the structure of actors and the environment, along with its
+supporting details, in a way that validates the precision of ICBe.
+Although harder to measure objectively, this crisis map provides face
+valid evidence that ICBe's account is not too vague, but also not
+unnecessarily detailed. We include much of the geopolitically important
+details like Soviet deployment, US discovery of that deployment,
+heightened alert levels, a blockade, and negotiations that ended with a
+formal agreement. At the same time, the crisis map indicates that ICBe
+does not include unnecessary nuances that preclude useful comparison to
+other international events.
+
+\begin{figure}
+\hypertarget{fig-cuba-crisismap}{%
+\centering
+\includegraphics{p_196_icbe.png}
+\caption{Crisis map for the Cuban Missile Crisis. The start of the
+crisis is at the top and end of the crisis is the bottom, with each
+actor in a column with labeled points identifying their speeches,
+actions, and thoughts.}\label{fig-cuba-crisismap}
+}
+\end{figure}
+
+\hypertarget{crimea-donbas-2014}{%
+\subsection{Crimea-Donbas (2014)}\label{crimea-donbas-2014}}
+
+A synthetic historical narrative for the 2014 Crimea-Donbas crisis (30
+events drawn from 971 documents) appears in
+(\textbf{fig-recall-crimea?}). As in the earlier case, rows represent
+details that appeared in at least five documents and whether it is
+identified in ICBe and existing datasets.
+
+Again quantitatively summarized earlier in Section 3.2
+((\textbf{fig-recall-cases?})), our ground truth ICB narrative contains
+23/30 of the events from the synthetic narrative. Like the gray zone
+precursor to the Cuban Missile crisis
+(\textbf{cormacGreyNewBlack2018?}), Ukraine provided several security
+guarantees to Russia that were potentially undone, e.g.~a long term
+lease on naval facilities in Crimea. But unlike the Cuban Missile
+crisis, the end of this crisis is unclear, with the event meekly ending
+with a second cease-fire agreement (Minsk II) but continued fighting.
+ICBe again recalls more important information about the crisis than any
+existing dataset, particularly information concerning the behavior of
+non-state separatist groups like the Donetsk People's Republic (DPR) and
+Luhansk People's Republic (LPR).
+
+\begin{figure}
+\hypertarget{fig-recall-crimea}{%
+\centering
+\includegraphics{case_study_crimea_recall.png}
+\caption{Synthetic narratives combine several thousand accounts of each
+crisis into a single timeline of events, taking only those mentioned in
+at least 5 or more documents. Checkmarks represent whether that event
+could be hand matched to any detail in the ICB corpus, ICBe dataset, or
+any of the other event datasets (SI Appendix 3.2 and
+3.3).}\label{fig-recall-crimea}
+}
+\end{figure}
+
+As this more recent case reflects primarily public reporting rather than
+the previously classified details relevant for the Cuban Missile Crisis,
+ICBe's improvement relative to the global and real-time coverage of
+dictionary-based event systems is still present, but less pronounced. We
+want to take seriously the possibility that some functional
+transformation could recover the precision of ICBe. For example,
+(\textbf{terechshenkoHotCollarLatent2020?}) attempts to correct for the
+mechanically increasing amount of news coverage each year by de-trending
+violent event counts from Phoenix using a human-coded baseline. Others
+have focused on verifying precision for ICEWs on specific subsets of
+details against known ground truths, e.g.~geolocation
+(\textbf{cookLostAggregationImproving2019?}), protest events (80\%)
+(\textbf{wuestExternalValidationProtest2020?}), anti-government protest
+networks (46.1\%) (\textbf{jagerLimitsStudyingNetworks2018?}).
+
+We take the same approach here in (\textbf{fig-precision-icews?}),
+selecting four specific CAMEO event codings and checking how often they
+reflect a true real-world event from the Crimea-Donbas synthetic
+narrative. We choose four event types around key moments in the crisis.
+The start of the crisis revolves around Ukraine backing out of a trade
+deal with the EU in favor of Russia, but ``sign formal agreement''
+events act more like a topic detector with dozens of events generated by
+discussions of a possible agreement but not the actual agreement which
+never materialized. The switch is caught by the ``reject plan, agreement
+to settle dispute'', but also continues for Viktor Yanukovych even after
+he was removed from power because of articles retroactively discussing
+the cause of his removal. Events for ``use conventional military force''
 capture a threshold around the start of hostilities and who the
@@
 
-\begin{figure}[H]
-\caption{Crisis Map: Cuban Missile Crisis \label{fig:p_196_icbe}}
-\centering{\includegraphics[width=16cm]{./p_196_icbe.png}}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[H]
-\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
-\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
-\textit{Notes: Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that the tag was applied to by the coders.
-The dendrogram shows hierarchical clustering of the tags.
-If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.
+\begin{figure}
+\hypertarget{fig-precision-icews}{%
+\centering
+\includegraphics{p_precision_icews.png}
+\caption{The unit of analysis is the dyad-day. Top 10 most active dyads
+per category shown. Red text shows events from the synthetic narrative
+relative to that event category. Blue bars indicate an event recorded by
+ICEWs for that dyad on that day.}\label{fig-precision-icews}
 }
 \end{figure}
-\clearpage
-
-\clearpage
-
-\begin{figure}[H]
-\caption{ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
-\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
-\textit{Notes: The unit of analysis is the Dyad-Day.
-Top 10 most active dyads per category shown.
-Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.
-}
-\end{figure}
-\clearpage
 
@@
 We release several open-source products along with supporting code and
-documentation to further advance the study of IR, event extraction, and
-natural language processing. The first is the International Crisis
-Behavior Events (ICBe) dataset, an event-level aggregation of what took
-place during the crises identified by the ICB project. These data are
-appropriate for statistical analysis of hard questions about the
-sequencing of events (e.g.~escalation and de-escalation of
-conflicts).\footnote{Using ICBe data Gannon (2022) finds that
-  cross-domain crises are shorter and less violent than same-domain
-  crises.} Second, we provide a coder-level disaggregation with multiple
-codings of each sentence by experts and undergrads that allows for the
-introduction of uncertainty and human interpretation of events. Further,
-we release a direct mapping from the codings to the source text at the
-sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed
-visualizations of all of the data introduced here at crisisevents.org.
+documentation to further advance the study of international relations,
+event extraction, and natural language processing. The first is the
+International Crisis Behavior Events (ICBe) dataset, an event-level
+aggregation of what took place during the crises identified by the ICB
+project. These data are appropriate for statistical analysis of hard
+questions about the sequencing of events (e.g.~escalation and
+de-escalation of conflicts).\footnote{Using ICBe data
+  (\textbf{gannonOneIfLand2022?}) finds that cross-domain crises are
+  shorter and less violent than same-domain crises.} Second, we provide
+a coder-level disaggregation with multiple codings of each sentence by
+experts and undergrads that allows for the introduction of uncertainty
+and human interpretation of events. Further, we release a direct mapping
+from the codings to the source text at the sentence level as a new
+resource for natural language processing. Finally, we provide a
+companion website that incorporates detailed visualizations of all of
+the data introduced here at crisisevents.org.
 
@@
 This work was supported by a grant from the Office of Naval Research
-{[}N00014-19-1-2491{]} and from the Charles Koch Foundation
-{[}20180481{]}. The financial sponsors played no in the design,
-execution, analysis and interpretation of data, or writing of the study.
+\[N00014-19-1-2491\] and from the Charles Koch Foundation \[20180481\].
+The financial sponsors played no in the design, execution, analysis and
+interpretation of data, or writing of the study.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-allenUSGlobalMilitary2021}{}}%
-Allen, Michael A, Michael E Flynn, and Carla Martinez Machain. 2021.
-{``{US} Global Military Deployments, 1950\textendash 2020*.''}
-\emph{Conflict Management and Peace Science}, July, 07388942211030885.
-\url{https://doi.org/10.1177/07388942211030885}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
-Allison, Graham T., and Philip Zelikow. 1971. \emph{Essence of Decision:
-{Explaining} the {Cuban} Missile Crisis}. Vol. 327. {Little, Brown
-Boston}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
-Althaus, Scott, Joseph Bajjalieh, John F. Carter, Buddy Peyton, and Dan
-A. Shalmon. 2019. {``Cline {Center Historical Phoenix Event Data
-Variable Descriptions}.''} \emph{Cline Center Historical Phoenix Event
-Data}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
-Balali, Ali, Masoud Asadpour, and Seyed Hossein Jafari. 2021.
-{``{COfEE}: {A Comprehensive Ontology} for {Event Extraction} from
-Text.''} {arXiv}. \url{https://doi.org/10.48550/arXiv.2107.10326}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-beardsleyMediationDilemma2011}{}}%
-Beardsley, Kyle. 2011. \emph{The Mediation Dilemma}. {Cornell University
-Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
-Beardsley, Kyle, Patrick James, Jonathan Wilkenfeld, and Michael
-Brecher. 2020. {``The {International Crisis Behavior Project}.''}
-\emph{Oxford Research Encyclopedia of Politics}.
-https://oxfordre.com/politics/view/10.1093/acrefore/9780190228637.001.0001/acrefore-9780190228637-e-1638.
-\url{https://doi.org/10.1093/acrefore/9780190228637.013.1638}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-beielerGeneratingPoliticalEvent2016}{}}%
-Beieler, John, Patrick T. Brandt, Andrew Halterman, Philip A. Schrodt,
-Erin M. Simpson, and R. Michael Alvarez. 2016. {``Generating Political
-Event Data in Near Real Time.''} In \emph{Computational Social Science},
-98. {Cambridge University Press}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-benyehudaEthnicActorsInternational2006}{}}%
-Ben-Yehuda, Hemda, and Meirav MishaliRam. 2006. {``Ethnic {Actors} and
-{International Crises}: {Theory} and {Findings},
-1918\textendash 2001.''} \emph{International Interactions} 32 (1):
-49--78. \url{https://doi.org/10.1080/03050620600584435}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
-Bloomfield, Lincoln P., and Allen Moulton. 1989. {``{CASCON III}:
-{Computer-aided} System for Analysis of Local Conflicts.''} \emph{MIT
-Center for International Studies, Cambridge}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
-Boschee, Elizabeth, Jennifer Lautenschlager, Sean O'Brien, Steve
-Shellman, James Starz, and Michael Ward. 2015. {``{ICEWS} Coded Event
-Data.''} \emph{Harvard Dataverse} 12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
-Brandt, Patrick T., Vito DOrazio, Jennifer Holmes, Latifur Khan, and
-Vincent Ng. 2018. {``Phoenix {Real-Time Event Data}.''}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
-Brecher, Michael. 1999. {``International Studies in the Twentieth
-Century and Beyond: {Flawed} Dichotomies, Synthesis, Cumulation: {ISA}
-Presidential Address.''} \emph{International Studies Quarterly} 43 (2):
-213--64.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
-Brecher, Michael, and Jonathan Wilkenfeld. 1982. {``Crises in {World
-Politics}.''} \emph{World Politics} 34 (3): 380--417.
-\url{https://doi.org/10.2307/2010324}.
+Ben-Yehuda, Hemda, and Meirav Mishali--Ram. 2006. {``Ethnic {Actors} and
+{International} {Crises}: {Theory} and {Findings}, 1918--2001.''}
+\emph{International Interactions} 32 (1): 49--78.
+\url{https://doi.org/10.1080/03050620600584435}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
----------. 1997. \emph{A {Study} of {Crisis}}. {University of Michigan
-Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2021}{}}%
-Brecher, Michael, Jonathan Wilkenfeld, Kyle C. Beardsley, Patrick James,
-and David Quinn. 2021. {``International {Crisis Behavior Data
-Codebook}.''} Codebook Version 14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
-Brust, Clemens-Alexander, and Joachim Denzler. 2020. {``Integrating
-Domain Knowledge: Using Hierarchies to Improve Deep Classifiers.''}
-\emph{arXiv:1811.07125 {[}Cs{]}}, January.
-\url{https://arxiv.org/abs/1811.07125}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bushDensityDeclineFounding2019}{}}%
-Bush, Sarah Sunn, and Jennifer Hadden. 2019. {``Density and {Decline} in
-the {Founding} of {International NGOs} in the {United States}.''}
-\emph{International Studies Quarterly} 63 (4): 1133--46.
-\url{https://doi.org/10.1093/isq/sqz061}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carafanoMeasuringMilitaryPower2014}{}}%
-Carafano, James Jay. 2014. {``Measuring {Military Power}.''}
-\emph{Strategic Studies Quarterly} 8 (3): 11--18.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carterStrategyTerritorialConflict2010}{}}%
-Carter, David B. 2010. {``The {Strategy} of {Territorial Conflict}.''}
-\emph{American Journal of Political Science} 54 (4): 969--87.
-\url{https://doi.org/10.1111/j.1540-5907.2010.00471.x}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chenowethIntroducingNonviolentAction2019}{}}%
-Chenoweth, Erica, Cullen S Hendrix, and Kyleanne Hunter. 2019.
-{``Introducing the {Nonviolent Action} in {Violent Contexts} ({NVAVC})
-Dataset.''} \emph{Journal of Peace Research} 56 (2): 295--305.
-\url{https://doi.org/10.1177/0022343318804855}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
-Cook, Scott J., and Nils B. Weidmann. 2019. {``Lost in {Aggregation}:
-{Improving Event Analysis} with {Report-Level Data}.''} \emph{American
-Journal of Political Science} 63 (1): 250--64.
-\url{https://doi.org/10.1111/ajps.12398}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
-Cormac, Rory, and Richard J. Aldrich. 2018. {``Grey Is the New Black:
-Covert Action and Implausible Deniability.''} \emph{International
-Affairs} 94 (3): 477--94. \url{https://doi.org/10.1093/ia/iiy067}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-daviesOrganizedViolence19892022}{}}%
-Davies, Shawn, Therése Pettersson, and Magnus Öberg. 2022. {``Organized
-Violence 1989\textendash 2021 and Drone Warfare.''} \emph{Journal of
-Peace Research} 59 (4): 593--610.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eckOneSidedViolenceCivilians2007}{}}%
-Eck, Kristine, and Lisa Hultman. 2007. {``One-{Sided Violence Against
-Civilians} in {War}: {Insights} from {New Fatality Data}.''}
-\emph{Journal of Peace Research} 44 (2): 233--46.
-\url{https://doi.org/10.1177/0022343307075124}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fazalStateDeathPolitics2011}{}}%
-Fazal, Tanisha M. 2011. \emph{State {Death}: {The Politics} and
-{Geography} of {Conquest}, {Occupation}, and {Annexation}}. \emph{State
-Death}. {Princeton University Press}.
-\url{https://doi.org/10.1515/9781400841448}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
-Felbermayr, Gabriel, Aleksandra Kirilakha, Constantinos Syropoulos,
-Erdal Yalcin, and Yoto V. Yotov. 2020. {``The Global Sanctions Data
-Base.''} \emph{European Economic Review} 129 (October): 103561.
-\url{https://doi.org/10.1016/j.euroecorev.2020.103561}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fortnaPeaceTime2018}{}}%
-Fortna, Virginia Page. 2018. \emph{Peace Time}. {Princeton University
-Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
-Frederick, Bryan A, Paul R Hensel, and Christopher Macaulay. 2017.
-{``The {Issue Correlates} of {War Territorial Claims Data},
-1816\textendash 20011.''} \emph{Journal of Peace Research} 54 (1):
-99--108. \url{https://doi.org/10.1177/0022343316676311}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gannonOneIfLand2022}{}}%
-Gannon, J Andrés. 2022. {``One If by {Land}, and {Two} If by {Sea}:
-{Cross-Domain Contests} and the {Escalation} of {International
-Crises}.''} \emph{International Studies Quarterly} 66 (4): sqac065.
-\url{https://doi.org/10.1093/isq/sqac065}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gartzkeCrossDomainDeterrenceStrategy2019}{}}%
-Gartzke, Erik, and Jon R. Lindsay. 2019. \emph{Cross-{Domain
-Deterrence}: {Strategy} in an {Era} of {Complexity}}. {Oxford University
-Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
-Gavin, Francis J. 2014. {``History, {Security Studies}, and the {July
-Crisis}.''} \emph{Journal of Strategic Studies} 37 (2): 319--31.
-\url{https://doi.org/10.1080/01402390.2014.912916}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
-Gibler, Douglas M. 2018. \emph{International {Conflicts}, 1816-2010:
-{Militarized Interstate Dispute Narratives}}. {Rowman \& Littlefield}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-giblerMeasuringAlliancesCorrelates2004}{}}%
-Gibler, Douglas M., and Meredith Reid Sarkees. 2004. {``Measuring
-{Alliances}: The {Correlates} of {War Formal Interstate Alliance}
-{Dataset}, 1816\textendash 2000.''} \emph{Journal of Peace Research} 41
-(2): 211--22. \url{https://doi.org/10.1177/0022343304041061}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goemansIntroducingArchigosDataset2009}{}}%
-Goemans, Henk E., Kristian Skrede Gleditsch, and Giacomo Chiozza. 2009.
-{``Introducing {Archigos}: {A} Dataset of Political Leaders.''}
-\emph{Journal of Peace Research} 46 (2): 269--83.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goertzMeasuringMilitaryAllocations1986}{}}%
-Goertz, Gary, and Paul F. Diehl. 1986. {``Measuring {Military
-Allocations}: {A Comparison} of {Different Approaches}.''} \emph{Journal
-of Conflict Resolution} 30 (3): 553--81.
-\url{https://doi.org/10.1177/0022002786030003009}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldgeierPsychologyInternationalRelations2001}{}}%
-Goldgeier, J. M., and P. E. Tetlock. 2001. {``Psychology and
-{International Relations Theory}.''} \emph{Annual Review of Political
-Science} 4 (1): 67--92.
-\url{https://doi.org/10.1146/annurev.polisci.4.1.67}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
-Grant, Christan, Andrew Halterman, Jill Irvine, Yan Liang, and Khaled
-Jabr. 2017. {``{OU Event Data Project},''} December.
-
-\leavevmode\vadjust pre{\hypertarget{ref-haffarEmergentPeacemakersCataloguing2002}{}}%
-Haffar, Warren. 2002. {``Emergent {Peacemakers}: {Cataloguing New
-Patterns} of {Activity} in {Post-Cold War Conflict}.''} \emph{Peace
-Economics, Peace Science and Public Policy} 8 (2).
-\url{https://doi.org/10.2202/1554-8597.1054}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
-Hermann, Charles. 1984. {``Comparative {Research} on the {Events} of
-{Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968:
-{Version} 1.''} {ICPSR - Interuniversity Consortium for Political and
-Social Research}. \url{https://doi.org/10.3886/ICPSR05205.V1}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
-Hewitt, J. Joseph. 2001. {``Engaging {International Data} in the
-{Classroom}: {Using} the {ICB Interactive Data Library} to {Teach
-Conflict} and {Crisis Analysis}.''} \emph{International Studies
-Perspectives} 2 (4): 371--83.
-\url{https://doi.org/10.1111/1528-3577.00066}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
-Holsti, Ole R. 1965. {``The 1914 {Case}.''} \emph{The American Political
-Science Review} 59 (2): 365--78. \url{https://doi.org/10.2307/1953055}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
-Iakhnis, Evgeniia, and Patrick James. 2019. {``Near Crises in World
-Politics: {A} New Dataset.''} \emph{Conflict Management and Peace
-Science}, July, 0738894219855610.
-\url{https://doi.org/10.1177/0738894219855610}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks2018}{}}%
-Jäger, Kai. 2018. {``The {Limits} of {Studying Networks} with {Event
-Data}: {Evidence} from the {ICEWS Dataset}.''} \emph{Journal of Global
-Security Studies} 3 (4): 498--511.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
-Kang, David C., and Alex Yu-Ting Lin. 2019. {``{US} Bias in the Study of
-{Asian} Security: {Using Europe} to Study {Asia}.''} \emph{Journal of
-Global Security Studies} 4 (3): 393--401.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
-Kinne, Brandon J. 2020. {``The {Defense Cooperation Agreement Dataset}
-({DCAD}).''} \emph{Journal of Conflict Resolution} 64 (4): 729--55.
-\url{https://doi.org/10.1177/0022002719857796}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lacinaExplainingSeverityCivil2006}{}}%
-Lacina, Bethany. 2006. {``Explaining the {Severity} of {Civil Wars}.''}
-\emph{Journal of Conflict Resolution} 50 (2): 276--89.
-\url{https://doi.org/10.1177/0022002705284828}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lafreeIntroducingGlobalTerrorism2007}{}}%
-LaFree, Gary, and Laura Dugan. 2007. {``Introducing the Global Terrorism
-Database.''} \emph{Terrorism and Political Violence} 19 (2): 181--204.
-
-\leavevmode\vadjust pre{\hypertarget{ref-laiEffectsDifferentTypes2004}{}}%
-Lai, Brian. 2004. {``The Effects of Different Types of Military
-Mobilization on the Outcome of International Crises.''} \emph{Journal of
-Conflict Resolution} 48 (2): 211--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-leedsDomesticPoliticalInstitutions1999}{}}%
-Leeds, Brett Ashley. 1999. {``Domestic {Political Institutions},
-{Credible Commitments}, and {International Cooperation}.''}
-\emph{American Journal of Political Science} 43 (4): 979--1002.
-\url{https://doi.org/10.2307/2991814}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-leedsAllianceReliabilityTimes2003}{}}%
----------. 2003. {``Alliance {Reliability} in {Times} of {War}:
-{Explaining State Decisions} to {Violate Treaties}.''}
-\emph{International Organization} 57 (4): 801--27.
-\url{https://doi.org/10.1017/S0020818303574057}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
-Leng, Russell J., and J. David Singer. 1988. {``Militarized {Interstate
-Crises}: {The BCOW Typology} and {Its Applications}.''}
-\emph{International Studies Quarterly} 32 (2): 155--73.
-\url{https://doi.org/10.2307/2600625}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
-Li, Qian, Hao Peng, Jianxin Li, Yiming Hei, Rui Sun, Jiawei Sheng, Shu
-Guo, et al. 2021. {``A {Comprehensive Survey} on {Schema-based Event
-Extraction} with {Deep Learning}.''} \emph{arXiv:2107.02126 {[}Cs{]}},
-August. \url{https://arxiv.org/abs/2107.02126}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lindsayPoliticsManyOther2020}{}}%
-Lindsay, Jon R., and Erik Gartzke. 2020. {``Politics by Many Other
-Means: {The} Comparative Strategic Advantages of Operational Domains.''}
-\emph{Journal of Strategic Studies} 0 (0): 1--34.
-\url{https://doi.org/10.1080/01402390.2020.1768372}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
-Mandelbrot, Benoit B. 1983. \emph{{The fractal geometry of nature}}.
-{New York}: {Freeman}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
-McClelland, Charles. 1978. {``World Event/Interaction Survey,
-1966-1978.''} \emph{WEIS Codebook ICPSR} 5211.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcnabbcochranMeasuringMilitaryEffectiveness2017}{}}%
-McNabb Cochran, Kathryn, and Stephen B. Long. 2017. {``Measuring
-{Military Effectiveness}: {Calculating Casualty Loss-Exchange Ratios}
-for {Multilateral Wars}, 1816\textendash 1990.''} \emph{International
-Interactions} 43 (6): 1019--40.
-\url{https://doi.org/10.1080/03050629.2017.1273914}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
-Merritt, Richard L. 1994. {``Measuring Events for International
-Political Analysis.''} \emph{International Interactions} 20 (1-2):
-3--33.
-
-\leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
-Miller, George A. 1995. {``{WordNet}: A Lexical Database for
-{English}.''} \emph{Communications of the ACM} 38 (11): 39--41.
-\url{https://doi.org/10.1145/219717.219748}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-minInterstateWarBattle2021}{}}%
-Min, Eric. 2021. {``Interstate {War Battle} Dataset
-(1823\textendash 2003).''} \emph{Journal of Peace Research} 58 (2):
-294--303. \url{https://doi.org/10.1177/0022343320913305}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
-Moyer, Jonathan D, Sara D Turner, and Collin J Meisel. 2020. {``What Are
-the Drivers of Diplomacy? {Introducing} and Testing New Annual Dyadic
-Data Measuring Diplomatic Exchange.''} \emph{Journal of Peace Research},
-September, 0022343320929740.
-\url{https://doi.org/10.1177/0022343320929740}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-oneillInternationalNegotiationConceptual2018}{}}%
-O'Neill, Barry. 2018. {``International {Negotiation}: {Some Conceptual
-Developments}.''} \emph{Annual Review of Political Science} 21 (1):
-515--33. \url{https://doi.org/10.1146/annurev-polisci-031416-092909}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
-Owsiak, Andrew P, Allison K Cuttner, and Brent Buck. 2018. {``The
-{International Border Agreements Dataset}.''} \emph{Conflict Management
-and Peace Science} 35 (5): 559--76.
-\url{https://doi.org/10.1177/0738894216646978}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
-Paige, Glenn D. 1968. \emph{The {Korean Decision}, {June} 24-30, 1950}.
-{Free Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
-Palmer, Glenn, Roseanne W McManus, Vito D'Orazio, Michael R Kenwick,
-Mikaela Karstens, Chase Bloch, Nick Dietrich, Kayla Kahn, Kellan Ritter,
-and Michael J Soules. 2021. {``The {Mid5 Dataset}, 2011\textendash 2014:
-{Procedures}, Coding Rules, and Description.''} \emph{Conflict
-Management and Peace Science}, February, 0738894221995743.
-\url{https://doi.org/10.1177/0738894221995743}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-powellGlobalInstancesCoups2011}{}}%
-Powell, Jonathan M, and Clayton L Thyne. 2011. {``Global Instances of
-Coups from 1950 to 2010: {A} New Dataset.''} \emph{Journal of Peace
-Research} 48 (2): 249--59.
-\url{https://doi.org/10.1177/0022343310397436}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-powellBargainingTheoryInternational2002}{}}%
-Powell, Robert. 2002. {``Bargaining {Theory} and {International
-Conflict}.''} \emph{Annual Review of Political Science} 5 (1): 1--30.
-\url{https://doi.org/10.1146/annurev.polisci.5.092601.141138}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
-Raleigh, Clionadh, Andrew Linke, Håavard Hegre, and Joakim Karlsen.
-2010. {``Introducing {ACLED}: An Armed Conflict Location and Event
-Dataset: Special Data Feature.''} \emph{Journal of Peace Research} 47
-(5): 651--60.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
-Ralph Sundberg, and Mihai Croicu. 2016. {``{UCDP GED Codebook} Version
-5.0.''} {Department of Peace and Conflict Research, Uppsala University}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ramsayInformationUncertaintyWar2017}{}}%
-Ramsay, Kristopher W. 2017. {``Information, {Uncertainty}, and {War}.''}
-\emph{Annual Review of Political Science} 20 (1): 505--27.
-\url{https://doi.org/10.1146/annurev-polisci-051215-022729}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
-Reiter, Dan. 2015. {``Should {We Leave Behind} the {Subfield} of
-{International Relations}?''} \emph{Annual Review of Political Science}
-18 (1): 481--99.
-\url{https://doi.org/10.1146/annurev-polisci-053013-041156}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
-Reiter, Dan, Allan C. Stam, and Michael C. Horowitz. 2016. {``A {Revised
-Look} at {Interstate Wars}, 1816\textendash 2007.''} \emph{Journal of
-Conflict Resolution} 60 (5): 956--76.
-\url{https://doi.org/10.1177/0022002714553107}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
-Sarkees, Meredith Reid, and Frank Wayman. 2010. \emph{Resort to War:
-1816-2007}. {CQ Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
-Schrodt, Philip A., and Blake Hall. 2006. {``Twenty Years of the
-{Kansas} Event Data System Project.''} \emph{The Political
-Methodologist} 14 (1): 2--8.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
-Sechser, Todd S. 2011. {``Militarized {Compellent Threats},
-1918\textendash 2001.''} \emph{Conflict Management and Peace Science} 28
-(4): 377--401. \url{https://doi.org/10.1177/0738894211413066}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
-Sherman, Frank L. 2000. {``{SHERFACS}: {A Cross-Paradigm},
-{Hierarchical}, and {Contextually-Sensitive International Conflict
-Dataset}, 1937-1985: {Version} 1.''} {ICPSR - Interuniversity Consortium
-for Political and Social Research}.
-\url{https://doi.org/10.3886/ICPSR02292.V1}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-spruytSovereignStateIts1996}{}}%
-Spruyt, Hendrik. 1996. \emph{The {Sovereign State} and {Its
-Competitors}: {An Analysis} of {Systems Change}}. {Princeton University
-Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-steinEvaluatingWarOutcomes1980}{}}%
-Stein, Arthur A., and Bruce M. Russett. 1980. {``Evaluating War:
-{Outcomes} and Consequences.''} In \emph{Handbook of Political Conflict:
-Theory and Research}, 399--422. {Free Press New York}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
-Steinert-Threlkeld, Zachary C. 2019. {``The {Future} of {Event Data Is
-Images}.''} \emph{Sociological Methodology} 49 (1): 68--75.
-\url{https://doi.org/10.1177/0081175019860238}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sullivanWarAimsWar2007}{}}%
-Sullivan, Patricia L. 2007. {``War {Aims} and {War Outcomes}: {Why
-Powerful States Lose Limited Wars}.''} \emph{Journal of Conflict
-Resolution} 51 (3): 496--524.
-\url{https://doi.org/10.1177/0022002707300187}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
-Sundberg, Ralph, and Erik Melander. 2013. {``Introducing the {UCDP}
-Georeferenced Event Dataset.''} \emph{Journal of Peace Research} 50 (4):
-523--32.
-
-\leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
-Terechshenko, Zhanna. 2020. {``Hot Under the Collar: {A} Latent Measure
-of Interstate Hostility.''} \emph{Journal of Peace Research} 57 (6):
-764--76. \url{https://doi.org/10.1177/0022343320962546}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
-Wilkenfeld, Jonathan, and Michael Brecher. 2000. {``Interstate Crises
-and Violence: Twentieth-Century Findings.''} \emph{Handbook of War
-Studies II}, 282--300.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
-Wüest, Bruno, and Jasmine Lorenzini. 2020. {``External Validation of
-Protest Event Analysis.''} \emph{Contention in Times of Crisis:
-Recession and Political Protest in Thirty Euro-Pean Countries}, 49--78.
-
-\leavevmode\vadjust pre{\hypertarget{ref-yarhi-miloEyeBeholderHow2013}{}}%
-Yarhi-Milo, Keren. 2013. {``In the {Eye} of the {Beholder}: {How
-Leaders} and {Intelligence Communities Assess} the {Intentions} of
-{Adversaries}.''} \emph{International Security} 38 (1): 7--51.
-\url{https://doi.org/10.1162/ISEC_a_00128}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-yarhi-miloArmAllyPatron2016}{}}%
-Yarhi-Milo, Keren, Alexander Lanoszka, and Zack Cooper. 2016. {``To
-{Arm} or to {Ally}? {The Patron}'s {Dilemma} and the {Strategic Logic}
-of {Arms Transfers} and {Alliances}.''} \emph{International Security} 41
-(2): 90--139. \url{https://doi.org/10.1162/ISEC_a_00250}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zartmanEscalationNegotiationInternational2005}{}}%
-Zartman, I. William, and Guy Olivier Faure. 2005. \emph{Escalation and
-Negotiation in International Conflicts}. {Cambridge University Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
-Zhang, Han, and Jennifer Pan. 2019. {``{CASM}: {A Deep-Learning
-Approach} for {Identifying Collective Action Events} with {Text} and
-{Image Data} from {Social Media}.''} \emph{Sociological Methodology} 49
-(1): 1--57. \url{https://doi.org/10.1177/0081175019860244}.
+Brecher, Michael, and Jonathan Wilkenfeld. 1997. \emph{A {Study} of
+{Crisis}}. University of Michigan Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gannon_shadowdeterrencewhy_2023}{}}%
+Gannon, J Andrés, Erik Gartzke, Jon R. Lindsay, and Peter Schram. 2023.
+{``The {Shadow} of {Deterrence}: {Why Capable Actors Engage} in
+{Contests Short} of {War}.''} \emph{Journal of Conflict Resolution},
+April. \url{https://doi.org/10.1177/00220027231166345}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-slantchev_militarythreatscosts_2011}{}}%
+Slantchev, Branislav L. 2011. \emph{Military Threats: The Costs of
+Coercion and the Price of Peace}. Cambridge ; New York: Cambridge
+University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-turberville_historyobjectivesubjective_1933}{}}%
+Turberville, A. S. 1933. {``History {Objective} and {Subjective}.''}
+\emph{History} 17 (68): 289--302.
+\url{https://www.jstor.org/stable/24400365}.
 

### 2023-07-13 replication_paper/psrm_draft/ICBe_manuscript.Rmd
no qmd for me

@@
 
-```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=T}
+```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=F}
 #The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.

### 2023-07-28 replication_paper/psrm_draft/ICBe_manuscript.Rmd
pdf and bib

@@
 First, we separate the 'chess pieces' from the 'chess players' in distinguishing between different actors within a state.
-By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning civilian-military relations [@narangCivilmilitaryPathologiesDefeat2017], Track Two diplomacy and the role of sub-national actors [@hsuStatesHarnessingSubnational2020], and the evolution of what actors are engaged in crises - a topic of increasing interest as states engage in gray zone conflict by employing the coast guard or paramilitary mercenaries instead of internationally recognized state militaries [@gannon_shadowdeterrencewhy_2023].
+By virtue of our ontology coding military versus civilian actors and national leaders versus bureaucrats, our data can be used to explore important questions concerning civilian-military relations [@narangCivilmilitaryPathologiesDefeat2017], Track Two diplomacy and the role of sub-national actors [@hsuStatesHarnessingSubnational2020], and the evolution of what actors are engaged in crises - a topic of increasing interest as states engage in gray zone conflict by employing the coast guard or paramilitary mercenaries instead of internationally recognized state militaries [@gannonShadowDeterrenceWhy2022].
 Second, we add information about the domains in which actors behave - whether in land, air, sea, space, or cyber - since they differ in their technology, tactics, geography, and purpose [@gartzkeCrossDomainDeterrenceStrategy2019].
@@
 Recall for historical episodes is poorly defined for two reasons.
-History may or may not be written by the victors but by virtue of being written by *someone* there is no genuine ground truth about what occurred, only surviving texts about it [@turberville_historyobjectivesubjective_1933].
+History may or may not be written by the victors but by virtue of being written by *someone* there is no genuine ground truth about what occurred, only surviving texts about it [@turbervilleHistoryObjectiveSubjective1933].
 Second, there is no *a priori* guide to what information is necessary detail and what is ignorable trivia.
@@
 ICBe stands out in including more communicative behavior (do -- speech) than existing datasets like US threats to attack and later promises not to invade.
-Given the recognized importance of threat credibility for understanding international conflict, the addition of this information is a substantively important improvement over the existing state of the art [@slantchev_militarythreatscosts_2011].
+Given the recognized importance of threat credibility for understanding international conflict, the addition of this information is a substantively important improvement over the existing state of the art [@slantchevMilitaryThreatsCosts2011].
 

### 2023-07-28 replication_paper/psrm_draft/ICBe_manuscript.tex
pdf and bib

@@
 regularities that limit what actors can do, their best options, and even
-which actors are likely to survive
-(\textbf{brecherInternationalStudiesTwentieth1999?};
-\textbf{reiterShouldWeLeave2015?}). If so, then these events can be
-recorded and systematically measured by social scientists interested in
-these regularities.\footnote{See work on crises
-  (\textbf{brecherCrisesWorldPolitics1982?};
-  \textbf{beardsleyInternationalCrisisBehavior2020?}), militarized
-  disputes (\textbf{palmerMID5Dataset20112021?};
-  \textbf{giblerInternationalConflicts181620102018?}), wars
-  (\textbf{sarkeesResortWar181620072010?};
-  \textbf{reiterRevisedLookInterstate2016?}), organized violence
-  (\textbf{ralphsundbergUCDPGEDCodebook2016?};
-  \textbf{daviesOrganizedViolence19892022?}), political violence
-  (\textbf{raleighIntroducingACLEDArmed2010?}), sanctions
-  (\textbf{felbermayrGlobalSanctionsData2020?}), and international
-  agreements (\textbf{kinneDefenseCooperationAgreement2020?};
-  \textbf{owsiakInternationalBorderAgreements2018?}), dispute resolution
-  (\textbf{frederickIssueCorrelatesWar2017?}), and diplomacy
-  (\textbf{moyerWhatAreDrivers2020?};
-  \textbf{sechserMilitarizedCompellentThreats2011?}).} Thanks to
-improvements in natural language processing, more open-ended efforts
+which actors are likely to survive (Brecher 1999; Reiter 2015). If so,
+then these events can be recorded and systematically measured by social
+scientists interested in these regularities.\footnote{See work on crises
+  (Brecher and Wilkenfeld 1982; Beardsley et al. 2020), militarized
+  disputes (Palmer et al. 2021; Gibler 2018), wars (Sarkees and Wayman
+  2010; Reiter, Stam, and Horowitz 2016), organized violence (Ralph
+  Sundberg and Mihai Croicu 2016; Davies, Pettersson, and Öberg 2022),
+  political violence (Raleigh et al. 2010), sanctions (Felbermayr et al.
+  2020), and international agreements (Kinne 2020; Owsiak, Cuttner, and
+  Buck 2018), dispute resolution (Frederick, Hensel, and Macaulay 2017),
+  and diplomacy (Moyer, Turner, and Meisel 2020; Sechser 2011).} Thanks
+to improvements in natural language processing, more open-ended efforts
 have begun to capture entire unstructured streams of events from
-international news reports.\footnote{See
-  (\textbf{beielerGeneratingPoliticalEvent2016?});
-  (\textbf{boscheeICEWSCodedEvent2015?});
-  (\textbf{brandtPhoenixRealTimeEvent2018?});
-  (\textbf{grantOUEventData2017?});
-  (\textbf{liComprehensiveSurveySchemabased2021?}). On event extraction
-  from images and social media see
-  (\textbf{zhangCASMDeepLearningApproach2019?}) and
-  (\textbf{steinert-threlkeldFutureEventData2019?}).} This has invited
-fruitful efforts to evaluate the coverage, quality, and accuracy of
-attempts to measure international affairs.
+international news reports.\footnote{See Beieler et al. (2016); Boschee
+  et al. (2015); Brandt et al. (2018); Grant et al. (2017); Li et al.
+  (2021). On event extraction from images and social media see Zhang and
+  Pan (2019) and Steinert-Threlkeld (2019).} This has invited fruitful
+efforts to evaluate the coverage, quality, and accuracy of attempts to
+measure international affairs.
 
@@
 ontology to an unusually high-quality corpus of historical narratives of
-international crises
-(\textbf{brecherInternationalStudiesTwentieth1999?};
-\textbf{wilkenfeldInterstateCrisesViolence2000?};
-\textbf{brecherInternationalCrisisBehavior2021?}). We then develop
-several methods for objectively gauging how well these event codings
-reconstruct the information contained in the original crisis narrative.
-We conclude by benchmarking our event codings against several current
-state of the art event data collection efforts. The underlying
-fine-grained variation in international affairs is unrecognizable
-through the lens of current quantification efforts. We find that
-existing models produce data on historical episodes that do not contain
-enough information to reconstruct the underlying event. In focusing this
-initial effort on international crises as a proof of concept sample, we
-demonstrate our ontology and method's potential to improve upon existing
-empirical identifications of patterns of international interactions.
+international crises (Brecher 1999; Wilkenfeld and Brecher 2000; Brecher
+et al. 2021). We then develop several methods for objectively gauging
+how well these event codings reconstruct the information contained in
+the original crisis narrative. We conclude by benchmarking our event
+codings against several current state of the art event data collection
+efforts. The underlying fine-grained variation in international affairs
+is unrecognizable through the lens of current quantification efforts. We
+find that existing models produce data on historical episodes that do
+not contain enough information to reconstruct the underlying event. In
+focusing this initial effort on international crises as a proof of
+concept sample, we demonstrate our ontology and method's potential to
+improve upon existing empirical identifications of patterns of
+international interactions.
 
@@
 differences across events concerning important concepts like when
-particular foreign policy actions deter versus inflame
-(\textbf{jervisCooperationSecurityDilemma1978?};
-\textbf{glaserCausesConsequencesArms2000?}), when third parties mediate
-in interstate disputes
-(\textbf{haffarEmergentPeacemakersCataloguing2002?};
-\textbf{quinnPowerPlayMediation2006?}), and how actors try to
-communicate resolve (\textbf{tragerDiplomacyWarPeace2016?};
-\textbf{luptonReexaminingReputationResolve2018?}). Identifying patterns
-of international interactions is not just an inherently interesting
-enterprise; it is a necessary precondition to important efforts to
-predict where policymakers should turn their attention to improve global
-welfare (\textbf{wardLearningSteppingFuture2013?};
-\textbf{begerReassessingRoleTheory2021?}).
+particular foreign policy actions deter versus inflame (Jervis 1978;
+Glaser 2000), when third parties mediate in interstate disputes (Haffar
+2002; Quinn et al. 2006), and how actors try to communicate resolve
+(Trager 2016; Lupton 2018). Identifying patterns of international
+interactions is not just an inherently interesting enterprise; it is a
+necessary precondition to important efforts to predict where
+policymakers should turn their attention to improve global welfare (Ward
+et al. 2013; Beger, Morgan, and Ward 2021).
 
@@
 other event-level datasets including CAMEO dictionary lookup-based
-systems (Historical Phoenix
-(\textbf{althausClineCenterHistorical2019?}); ICEWS
-(\textbf{boscheeICEWSCodedEvent2015?}); Terrier
-(\textbf{grantOUEventData2017?})), the Militarized Interstate Disputes
-Incidents dataset, and the UCDP-GED dataset
-(\textbf{daviesOrganizedViolence19892022?};
-\textbf{sundbergIntroducingUCDPGeoreferenced2013?}).\footnote{Other
-  related datasets that insufficiently overlap ICBe's domain for
-  comparison include BCOW
-  (\textbf{lengMilitarizedInterstateCrises1988?}), WEIS
-  (\textbf{mcclellandWorldEventInteraction1978?}), CREON
-  (\textbf{hermannComparativeResearchEvents1984?}), CASCON
-  (\textbf{bloomfieldCASCONIIIComputeraided1989?}), SHERFACS
-  (\textbf{shermanSHERFACSCrossParadigmHierarchical2000?}), Real-Time
-  Phoenix (\textbf{brandtPhoenixRealTimeEvent2018?}), and COfEE
-  (\textbf{balaliCOfEEComprehensiveOntology2021?}) (see histories in
-  (\textbf{merrittMeasuringEventsInternational1994?}) and
-  (\textbf{schrodtTwentyYearsKansas2006?})).} The final set of columns
-compares episode-level datasets beginning with the original ICB project
-(\textbf{brecherInternationalCrisisBehavior2021?};
-\textbf{brecherCrisesWorldPolitics1982?};
-\textbf{beardsleyInternationalCrisisBehavior2020?}); the Militarized
-Interstate Disputes dataset (\textbf{palmerMID5Dataset20112021?};
-\textbf{giblerInternationalConflicts181620102018?}), and the Correlates
-of War (\textbf{sarkeesResortWar181620072010?}). There is imperfect
-overlap concerning their intended depth and scope of coverage;
-`international crises' are similar, but not identical to, `interstate
-wars' and `militarized interstate disputes' which differ yet again from
-`individual events of organized violence' and `non-violent action'. Even
-like-concepts require care in comparison, as an `aim' in ICBe is the
-same as in MIPS, but an `alert' in ICBe is not the same as an `alert' in
-MID. Definitions for each ICBe variable are provided in the codebook.
+systems (Historical Phoenix (Althaus et al. 2019); ICEWS (Boschee et al.
+2015); Terrier (Grant et al. 2017)), the Militarized Interstate Disputes
+Incidents dataset, and the UCDP-GED dataset (Davies, Pettersson, and
+Öberg 2022; Sundberg and Melander 2013).\footnote{Other related datasets
+  that insufficiently overlap ICBe's domain for comparison include BCOW
+  (Leng and Singer 1988), WEIS (McClelland 1978), CREON (Hermann 1984),
+  CASCON (Bloomfield and Moulton 1989), SHERFACS (Sherman 2000),
+  Real-Time Phoenix (Brandt et al. 2018), and COfEE (Balali, Asadpour,
+  and Jafari 2021) (see histories in Merritt (1994) and Schrodt and Hall
+  (2006)).} The final set of columns compares episode-level datasets
+beginning with the original ICB project (Brecher et al. 2021; Brecher
+and Wilkenfeld 1982; Beardsley et al. 2020); the Militarized Interstate
+Disputes dataset (Palmer et al. 2021; Gibler 2018), and the Correlates
+of War (Sarkees and Wayman 2010). There is imperfect overlap concerning
+their intended depth and scope of coverage; `international crises' are
+similar, but not identical to, `interstate wars' and `militarized
+interstate disputes' which differ yet again from `individual events of
+organized violence' and `non-violent action'. Even like-concepts require
+care in comparison, as an `aim' in ICBe is the same as in MIPS, but an
+`alert' in ICBe is not the same as an `alert' in MID. Definitions for
+each ICBe variable are provided in the codebook.
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{fazalStateDeathPolitics2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{spruytSovereignStateIts1996?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{haffarEmergentPeacemakersCataloguing2002?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{bushDensityDeclineFounding2019?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mishali–Ram}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fazal}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Spruyt}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Haffar}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Bush}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hadden}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{MishaliRam}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{lacinaExplainingSeverityCivil2006?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{mcnabbcochranMeasuringMilitaryEffectiveness2017?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{carafanoMeasuringMilitaryPower2014?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{goertzMeasuringMilitaryAllocations1986?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{gartzkeCrossDomainDeterrenceStrategy2019?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{lindsayPoliticsManyOther2020?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{carterStrategyTerritorialConflict2010?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lacina}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{McNabb}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cochran}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Long}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carafano}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2014)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goertz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diehl}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{goldgeierPsychologyInternationalRelations2001?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{steinEvaluatingWarOutcomes1980?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{sullivanWarAimsWar2007?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{ramsayInformationUncertaintyWar2017?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{yarhi-miloEyeBeholderHow2013?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goldgeier}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Tetlock}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stein}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Russett}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sullivan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ramsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{oneillInternationalNegotiationConceptual2018?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{zartmanEscalationNegotiationInternational2005?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{sechserMilitarizedCompellentThreats2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{powellBargainingTheoryInternational2002?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{O’Neill}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Zartman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Faure}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sechser}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{R.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{goemansIntroducingArchigosDataset2009?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{powellGlobalInstancesCoups2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{chenowethIntroducingNonviolentAction2019?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{eckOneSidedViolenceCivilians2007?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{lafreeIntroducingGlobalTerrorism2007?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{beardsleyMediationDilemma2011?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{giblerMeasuringAlliancesCorrelates2004?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{owsiakInternationalBorderAgreements2018?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{leedsAllianceReliabilityTimes2003?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{leedsDomesticPoliticalInstitutions1999?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{yarhi-miloArmAllyPatron2016?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goemans,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gleditsch,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chiozza}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2009)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{J.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{M.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Thyne}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chenoweth,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hendrix,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hunter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Eck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hultman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{LaFree}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Dugan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Beardsley}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gibler}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Owsiak,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cuttner,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Buck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lanoszka,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cooper}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{laiEffectsDifferentTypes2004?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{allenUSGlobalMilitary2021?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{fortnaPeaceTime2018?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{minInterstateWarBattle2021?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{sarkeesResortWar181620072010?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{reiterRevisedLookInterstate2016?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\textbf{frederickIssueCorrelatesWar2017?}}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lai}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Allen,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Flynn,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Martinez}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Machain}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fortna}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Min}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wayman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Reiter,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stam,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Horowitz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Frederick,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hensel,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Macaulay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
 
@@
 mentioned in the text. Verbs were matched to the most likely definition
-found in Wordnet (\textbf{millerWordNetLexicalDatabase1995?}), tallied,
-and then aggregated into a smaller number of hypernyms balancing
-conceptual detail and manageable sparsity for human coding (SI Appendix
-1.2). This comparison is not intended to fault existing data and models
-for not including every variable in ICBe's ontology, as some of these
-variables fall outside the scope of a particular dataset's intended
-purpose. Rather, it serves as an initial basis for identifying the
-heterogeneity in existing efforts to abstract and measure discrete
-historical events of interest and to provide theoretical justifications
-from existing research about what is included in our dataset's ontology
-and where ICBe's detail about historical events can be compared to the
-current state of the art.
+found in Wordnet (Miller 1995), tallied, and then aggregated into a
+smaller number of hypernyms balancing conceptual detail and manageable
+sparsity for human coding (SI Appendix 1.2). This comparison is not
+intended to fault existing data and models for not including every
+variable in ICBe's ontology, as some of these variables fall outside the
+scope of a particular dataset's intended purpose. Rather, it serves as
+an initial basis for identifying the heterogeneity in existing efforts
+to abstract and measure discrete historical events of interest and to
+provide theoretical justifications from existing research about what is
+included in our dataset's ontology and where ICBe's detail about
+historical events can be compared to the current state of the art.
 
@@
 state of the art quantitative datasets that ignore important information
-content about international interactions.\footnote{See
-  (\textbf{balaliCOfEEComprehensiveOntology2021?}) for a recent review
-  of ontological depth and availability of Gold Standard example text.}
-We highlight two particular innovations. First, we separate the `chess
-pieces' from the `chess players' in distinguishing between different
-actors within a state. By virtue of our ontology coding military versus
-civilian actors and national leaders versus bureaucrats, our data can be
-used to explore important questions concerning civilian-military
-relations (\textbf{narangCivilmilitaryPathologiesDefeat2017?}), Track
-Two diplomacy and the role of sub-national actors
-(\textbf{hsuStatesHarnessingSubnational2020?}), and the evolution of
-what actors are engaged in crises - a topic of increasing interest as
-states engage in gray zone conflict by employing the coast guard or
-paramilitary mercenaries instead of internationally recognized state
-militaries (Gannon et al. 2023). Second, we add information about the
-domains in which actors behave - whether in land, air, sea, space, or
-cyber - since they differ in their technology, tactics, geography, and
-purpose (\textbf{gartzkeCrossDomainDeterrenceStrategy2019?}). Doing so
-allows researchers to identify and explain patterns in escalation
-conditional on the military means states use in conflict. Recent
-concerns about cross-domain conflict and the effect of new domains of
-conflict like space and cyber have made this an endeavor of increased
-interest to practitioners (\textbf{gannonOneIfLand2022?}).
+content about international interactions.\footnote{See Balali, Asadpour,
+  and Jafari (2021) for a recent review of ontological depth and
+  availability of Gold Standard example text.} We highlight two
+particular innovations. First, we separate the `chess pieces' from the
+`chess players' in distinguishing between different actors within a
+state. By virtue of our ontology coding military versus civilian actors
+and national leaders versus bureaucrats, our data can be used to explore
+important questions concerning civilian-military relations (Narang and
+Talmadge 2017), Track Two diplomacy and the role of sub-national actors
+(Hsu et al. 2020), and the evolution of what actors are engaged in
+crises - a topic of increasing interest as states engage in gray zone
+conflict by employing the coast guard or paramilitary mercenaries
+instead of internationally recognized state militaries (J. Andrés Gannon
+et al. 2022). Second, we add information about the domains in which
+actors behave - whether in land, air, sea, space, or cyber - since they
+differ in their technology, tactics, geography, and purpose (Gartzke and
+Lindsay 2019). Doing so allows researchers to identify and explain
+patterns in escalation conditional on the military means states use in
+conflict. Recent concerns about cross-domain conflict and the effect of
+new domains of conflict like space and cyber have made this an endeavor
+of increased interest to practitioners (J. Andrés Gannon 2022).
 
@@
 (\(n=471\)) with coverage spanning 1918-2017 (Supplementary Information
-(SI) Appendix 1.1)(\textbf{brecherInternationalCrisisBehavior2021?};
-Brecher and Wilkenfeld 1997). ICB defines a crisis as meeting three
-conditions: (1) an actor perceives a threat to one of more of its basic
-values, (2) the actor has a finite time horizon for responding to the
-perceived threat, and (3) the probability of military hostility has
-increased (\textbf{brecherCrisesWorldPolitics1982?}). Crises are a
-significant focus of detailed single case studies and case comparisons
-because they provide an opportunity to examine behaviors in
-international relations short of, or at least prior to, full conflict
-(\textbf{holsti1914Case1965?}; \textbf{paigeKoreanDecisionJune1968?};
-\textbf{allisonEssenceDecisionExplaining1971?};
-\textbf{gavinHistorySecurityStudies2014?};
-\textbf{brecherCrisesWorldPolitics1982?};
-\textbf{iakhnisCrisesWorldPolitics2019?}). The corpus is also unique in
-being designed to be used in a downstream quantitative coding project,
-meaning each narrative was written by consensus by a small number of
-scholars using a uniform coding scheme where things like word choice,
-writing style, and level of specificity were deliberately done in a
-consistent manner (\textbf{hewittEngagingInternationalData2001?}). Case
-selection was exhaustive based on a survey of world news archives and
-region experts, cross-checked against other databases of war and
-conflict, and non-English sources (\textbf{kangUSBiasStudy2019?};
-\textbf{brecherInternationalCrisisBehavior2021?}).
+(SI) Appendix 1.1)(Brecher et al. 2021; Brecher and Wilkenfeld 1997).
+ICB defines a crisis as meeting three conditions: (1) an actor perceives
+a threat to one of more of its basic values, (2) the actor has a finite
+time horizon for responding to the perceived threat, and (3) the
+probability of military hostility has increased (Brecher and Wilkenfeld
+1982). Crises are a significant focus of detailed single case studies
+and case comparisons because they provide an opportunity to examine
+behaviors in international relations short of, or at least prior to,
+full conflict (Holsti 1965; Paige 1968; Allison and Zelikow 1971; Gavin
+2014; Brecher and Wilkenfeld 1982; Iakhnis and James 2019). The corpus
+is also unique in being designed to be used in a downstream quantitative
+coding project, meaning each narrative was written by consensus by a
+small number of scholars using a uniform coding scheme where things like
+word choice, writing style, and level of specificity were deliberately
+done in a consistent manner (Hewitt 2001). Case selection was exhaustive
+based on a survey of world news archives and region experts,
+cross-checked against other databases of war and conflict, and
+non-English sources (Kang and Lin 2019; Brecher et al. 2021, 59).
 
@@
 smaller number of significant decisions are made early on and then
-progressively refined into more specific details
-(\textbf{brustIntegratingDomainKnowledge2020?}).\footnote{This process
-  quickly focuses the coder on a smaller number of relevant options
-  while also allowing them to apply multiple tags if the sentence
-  explicitly includes more than one or there is insufficient evidence to
-  choose only one tag. The guided coding process also allows for the
-  possibility that earlier coarse decisions have less error than later
-  fine-grained decisions.} Each coder was instructed to first thoroughly
-read the full crisis narrative and then presented with a custom
-graphical user interface (GUI) (SI Appendix 2.1). Coders then proceeded
-sentence by sentence, choosing the number of events (0-3) that occurred,
-the highest behavior (thought, speech, or activity), a set of players,
-whether the means were primarily armed or unarmed, whether there was an
-increase or decrease in aggression (uncooperative/escalating or
-cooperative/de-escalating), and finally one or more specific and
-non-mutually exclusive activities. Some additional details were always
-collected (e.g.~location and timing) while other details were only
-collected if appropriate (e.g.~force size, fatalities, domains, units).
-We find 472 actors and 117 different behaviors.\footnote{See the full
-  codebook on Github Repository
+progressively refined into more specific details (Brust and Denzler
+2020).\footnote{This process quickly focuses the coder on a smaller
+  number of relevant options while also allowing them to apply multiple
+  tags if the sentence explicitly includes more than one or there is
+  insufficient evidence to choose only one tag. The guided coding
+  process also allows for the possibility that earlier coarse decisions
+  have less error than later fine-grained decisions.} Each coder was
+instructed to first thoroughly read the full crisis narrative and then
+presented with a custom graphical user interface (GUI) (SI Appendix
+2.1). Coders then proceeded sentence by sentence, choosing the number of
+events (0-3) that occurred, the highest behavior (thought, speech, or
+activity), a set of players, whether the means were primarily armed or
+unarmed, whether there was an increase or decrease in aggression
+(uncooperative/escalating or cooperative/de-escalating), and finally one
+or more specific and non-mutually exclusive activities. Some additional
+details were always collected (e.g.~location and timing) while other
+details were only collected if appropriate (e.g.~force size, fatalities,
+domains, units). We find 472 actors and 117 different
+behaviors.\footnote{See the full codebook on Github Repository
   \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
@@
 detail and what is ignorable trivia. History suffers from what is known
-as the Coastline Paradox (\textbf{mandelbrotFractalGeometryNature1983?})
---- it has a fractal dimension greater than one such that the more you
-zoom in, the more detail you will find about individual events as well
-as in between any two discrete events. The ICBe ontology is a proposal
-about what information is important, but we need an independent
-benchmark to evaluate whether that proposal is a good one and that
-allows for comparing proposals from event projects that had different
-goals. We need a yardstick for history.
+as the Coastline Paradox (Mandelbrot 1983) --- it has a fractal
+dimension greater than one such that the more you zoom in, the more
+detail you will find about individual events as well as in between any
+two discrete events. The ICBe ontology is a proposal about what
+information is important, but we need an independent benchmark to
+evaluate whether that proposal is a good one and that allows for
+comparing proposals from event projects that had different goals. We
+need a yardstick for history.
 
@@
 23/30 of the events from the synthetic narrative. Like the gray zone
-precursor to the Cuban Missile crisis
-(\textbf{cormacGreyNewBlack2018?}), Ukraine provided several security
-guarantees to Russia that were potentially undone, e.g.~a long term
-lease on naval facilities in Crimea. But unlike the Cuban Missile
-crisis, the end of this crisis is unclear, with the event meekly ending
-with a second cease-fire agreement (Minsk II) but continued fighting.
-ICBe again recalls more important information about the crisis than any
-existing dataset, particularly information concerning the behavior of
-non-state separatist groups like the Donetsk People's Republic (DPR) and
-Luhansk People's Republic (LPR).
+precursor to the Cuban Missile crisis (Cormac and Aldrich 2018), Ukraine
+provided several security guarantees to Russia that were potentially
+undone, e.g.~a long term lease on naval facilities in Crimea. But unlike
+the Cuban Missile crisis, the end of this crisis is unclear, with the
+event meekly ending with a second cease-fire agreement (Minsk II) but
+continued fighting. ICBe again recalls more important information about
+the crisis than any existing dataset, particularly information
+concerning the behavior of non-state separatist groups like the Donetsk
+People's Republic (DPR) and Luhansk People's Republic (LPR).
 
@@
 transformation could recover the precision of ICBe. For example,
-(\textbf{terechshenkoHotCollarLatent2020?}) attempts to correct for the
-mechanically increasing amount of news coverage each year by de-trending
-violent event counts from Phoenix using a human-coded baseline. Others
-have focused on verifying precision for ICEWs on specific subsets of
-details against known ground truths, e.g.~geolocation
-(\textbf{cookLostAggregationImproving2019?}), protest events (80\%)
-(\textbf{wuestExternalValidationProtest2020?}), anti-government protest
-networks (46.1\%) (\textbf{jagerLimitsStudyingNetworks2018?}).
+Terechshenko (2020) attempts to correct for the mechanically increasing
+amount of news coverage each year by de-trending violent event counts
+from Phoenix using a human-coded baseline. Others have focused on
+verifying precision for ICEWs on specific subsets of details against
+known ground truths, e.g.~geolocation (Cook and Weidmann 2019), protest
+events (80\%) (Wüest and Lorenzini 2020), anti-government protest
+networks (46.1\%) (Jäger 2018).
 
@@
 questions about the sequencing of events (e.g.~escalation and
-de-escalation of conflicts).\footnote{Using ICBe data
-  (\textbf{gannonOneIfLand2022?}) finds that cross-domain crises are
-  shorter and less violent than same-domain crises.} Second, we provide
-a coder-level disaggregation with multiple codings of each sentence by
-experts and undergrads that allows for the introduction of uncertainty
-and human interpretation of events. Further, we release a direct mapping
-from the codings to the source text at the sentence level as a new
-resource for natural language processing. Finally, we provide a
-companion website that incorporates detailed visualizations of all of
-the data introduced here at crisisevents.org.
+de-escalation of conflicts).\footnote{Using ICBe data J. Andrés Gannon
+  (2022) finds that cross-domain crises are shorter and less violent
+  than same-domain crises.} Second, we provide a coder-level
+disaggregation with multiple codings of each sentence by experts and
+undergrads that allows for the introduction of uncertainty and human
+interpretation of events. Further, we release a direct mapping from the
+codings to the source text at the sentence level as a new resource for
+natural language processing. Finally, we provide a companion website
+that incorporates detailed visualizations of all of the data introduced
+here at crisisevents.org.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-allenUSGlobalMilitary2021}{}}%
+Allen, Michael A, Michael E Flynn, and Carla Martinez Machain. 2021.
+{``{US} Global Military Deployments, 1950\textendash 2020*.''}
+\emph{Conflict Management and Peace Science}, July, 07388942211030885.
+\url{https://doi.org/10.1177/07388942211030885}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-allisonEssenceDecisionExplaining1971}{}}%
+Allison, Graham T., and Philip Zelikow. 1971. \emph{Essence of Decision:
+{Explaining} the {Cuban} Missile Crisis}. Vol. 327. {Little, Brown
+Boston}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-althausClineCenterHistorical2019}{}}%
+Althaus, Scott, Joseph Bajjalieh, John F. Carter, Buddy Peyton, and Dan
+A. Shalmon. 2019. {``Cline {Center Historical Phoenix Event Data
+Variable Descriptions}.''} \emph{Cline Center Historical Phoenix Event
+Data}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-balaliCOfEEComprehensiveOntology2021}{}}%
+Balali, Ali, Masoud Asadpour, and Seyed Hossein Jafari. 2021.
+{``{COfEE}: {A Comprehensive Ontology} for {Event Extraction} from
+Text.''} {arXiv}. \url{https://doi.org/10.48550/arXiv.2107.10326}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-beardsleyMediationDilemma2011}{}}%
+Beardsley, Kyle. 2011. \emph{The Mediation Dilemma}. {Cornell University
+Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-beardsleyInternationalCrisisBehavior2020}{}}%
+Beardsley, Kyle, Patrick James, Jonathan Wilkenfeld, and Michael
+Brecher. 2020. {``The {International Crisis Behavior Project}.''}
+\emph{Oxford Research Encyclopedia of Politics}.
+https://oxfordre.com/politics/view/10.1093/acrefore/9780190228637.001.0001/acrefore-9780190228637-e-1638.
+\url{https://doi.org/10.1093/acrefore/9780190228637.013.1638}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-begerReassessingRoleTheory2021}{}}%
+Beger, Andreas, Richard K. Morgan, and Michael D. Ward. 2021.
+{``Reassessing the {Role} of {Theory} and {Machine Learning} in
+{Forecasting Civil Conflict}.''} \emph{Journal of Conflict Resolution}
+65 (7-8): 1405--26. \url{https://doi.org/10.1177/0022002720982358}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-beielerGeneratingPoliticalEvent2016}{}}%
+Beieler, John, Patrick T. Brandt, Andrew Halterman, Philip A. Schrodt,
+Erin M. Simpson, and R. Michael Alvarez. 2016. {``Generating Political
+Event Data in Near Real Time.''} In \emph{Computational Social Science},
+98. {Cambridge University Press}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-benyehudaEthnicActorsInternational2006}{}}%
-Ben-Yehuda, Hemda, and Meirav Mishali--Ram. 2006. {``Ethnic {Actors} and
-{International} {Crises}: {Theory} and {Findings}, 1918--2001.''}
-\emph{International Interactions} 32 (1): 49--78.
-\url{https://doi.org/10.1080/03050620600584435}.
+Ben-Yehuda, Hemda, and Meirav MishaliRam. 2006. {``Ethnic {Actors} and
+{International Crises}: {Theory} and {Findings},
+1918\textendash 2001.''} \emph{International Interactions} 32 (1):
+49--78. \url{https://doi.org/10.1080/03050620600584435}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bloomfieldCASCONIIIComputeraided1989}{}}%
+Bloomfield, Lincoln P., and Allen Moulton. 1989. {``{CASCON III}:
+{Computer-aided} System for Analysis of Local Conflicts.''} \emph{MIT
+Center for International Studies, Cambridge}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boscheeICEWSCodedEvent2015}{}}%
+Boschee, Elizabeth, Jennifer Lautenschlager, Sean O'Brien, Steve
+Shellman, James Starz, and Michael Ward. 2015. {``{ICEWS} Coded Event
+Data.''} \emph{Harvard Dataverse} 12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brandtPhoenixRealTimeEvent2018}{}}%
+Brandt, Patrick T., Vito DOrazio, Jennifer Holmes, Latifur Khan, and
+Vincent Ng. 2018. {``Phoenix {Real-Time Event Data}.''}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalStudiesTwentieth1999}{}}%
+Brecher, Michael. 1999. {``International Studies in the Twentieth
+Century and Beyond: {Flawed} Dichotomies, Synthesis, Cumulation: {ISA}
+Presidential Address.''} \emph{International Studies Quarterly} 43 (2):
+213--64.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brecherCrisesWorldPolitics1982}{}}%
+Brecher, Michael, and Jonathan Wilkenfeld. 1982. {``Crises in {World
+Politics}.''} \emph{World Politics} 34 (3): 380--417.
+\url{https://doi.org/10.2307/2010324}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-brecher_study_1997}{}}%
-Brecher, Michael, and Jonathan Wilkenfeld. 1997. \emph{A {Study} of
-{Crisis}}. University of Michigan Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gannon_shadowdeterrencewhy_2023}{}}%
-Gannon, J Andrés, Erik Gartzke, Jon R. Lindsay, and Peter Schram. 2023.
+---------. 1997. \emph{A {Study} of {Crisis}}. {University of Michigan
+Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brecherInternationalCrisisBehavior2021}{}}%
+Brecher, Michael, Jonathan Wilkenfeld, Kyle C. Beardsley, Patrick James,
+and David Quinn. 2021. {``International {Crisis Behavior Data
+Codebook}.''} Codebook Version 14.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brustIntegratingDomainKnowledge2020}{}}%
+Brust, Clemens-Alexander, and Joachim Denzler. 2020. {``Integrating
+Domain Knowledge: Using Hierarchies to Improve Deep Classifiers.''}
+\emph{arXiv:1811.07125 {[}Cs{]}}, January.
+\url{https://arxiv.org/abs/1811.07125}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bushDensityDeclineFounding2019}{}}%
+Bush, Sarah Sunn, and Jennifer Hadden. 2019. {``Density and {Decline} in
+the {Founding} of {International NGOs} in the {United States}.''}
+\emph{International Studies Quarterly} 63 (4): 1133--46.
+\url{https://doi.org/10.1093/isq/sqz061}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carafanoMeasuringMilitaryPower2014}{}}%
+Carafano, James Jay. 2014. {``Measuring {Military Power}.''}
+\emph{Strategic Studies Quarterly} 8 (3): 11--18.
+\url{https://www.jstor.org/stable/26270616}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carterStrategyTerritorialConflict2010}{}}%
+Carter, David B. 2010. {``The {Strategy} of {Territorial Conflict}.''}
+\emph{American Journal of Political Science} 54 (4): 969--87.
+\url{https://doi.org/10.1111/j.1540-5907.2010.00471.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chenowethIntroducingNonviolentAction2019}{}}%
+Chenoweth, Erica, Cullen S Hendrix, and Kyleanne Hunter. 2019.
+{``Introducing the {Nonviolent Action} in {Violent Contexts} ({NVAVC})
+Dataset.''} \emph{Journal of Peace Research} 56 (2): 295--305.
+\url{https://doi.org/10.1177/0022343318804855}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cookLostAggregationImproving2019}{}}%
+Cook, Scott J., and Nils B. Weidmann. 2019. {``Lost in {Aggregation}:
+{Improving Event Analysis} with {Report-Level Data}.''} \emph{American
+Journal of Political Science} 63 (1): 250--64.
+\url{https://doi.org/10.1111/ajps.12398}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cormacGreyNewBlack2018}{}}%
+Cormac, Rory, and Richard J. Aldrich. 2018. {``Grey Is the New Black:
+Covert Action and Implausible Deniability.''} \emph{International
+Affairs} 94 (3): 477--94. \url{https://doi.org/10.1093/ia/iiy067}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-daviesOrganizedViolence19892022}{}}%
+Davies, Shawn, Therése Pettersson, and Magnus Öberg. 2022. {``Organized
+Violence 1989\textendash 2021 and Drone Warfare.''} \emph{Journal of
+Peace Research} 59 (4): 593--610.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eckOneSidedViolenceCivilians2007}{}}%
+Eck, Kristine, and Lisa Hultman. 2007. {``One-{Sided Violence Against
+Civilians} in {War}: {Insights} from {New Fatality Data}.''}
+\emph{Journal of Peace Research} 44 (2): 233--46.
+\url{https://doi.org/10.1177/0022343307075124}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fazalStateDeathPolitics2011}{}}%
+Fazal, Tanisha M. 2011. \emph{State {Death}: {The Politics} and
+{Geography} of {Conquest}, {Occupation}, and {Annexation}}. \emph{State
+Death}. {Princeton University Press}.
+\url{https://doi.org/10.1515/9781400841448}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-felbermayrGlobalSanctionsData2020}{}}%
+Felbermayr, Gabriel, Aleksandra Kirilakha, Constantinos Syropoulos,
+Erdal Yalcin, and Yoto V. Yotov. 2020. {``The Global Sanctions Data
+Base.''} \emph{European Economic Review} 129 (October): 103561.
+\url{https://doi.org/10.1016/j.euroecorev.2020.103561}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fortnaPeaceTime2018}{}}%
+Fortna, Virginia Page. 2018. \emph{Peace Time}. {Princeton University
+Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-frederickIssueCorrelatesWar2017}{}}%
+Frederick, Bryan A, Paul R Hensel, and Christopher Macaulay. 2017.
+{``The {Issue Correlates} of {War Territorial Claims Data},
+1816\textendash 20011.''} \emph{Journal of Peace Research} 54 (1):
+99--108. \url{https://doi.org/10.1177/0022343316676311}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gannonOneIfLand2022}{}}%
+Gannon, J Andrés. 2022. {``One If by {Land}, and {Two} If by {Sea}:
+{Cross-Domain Contests} and the {Escalation} of {International
+Crises}.''} \emph{International Studies Quarterly} 66 (4): sqac065.
+\url{https://doi.org/10.1093/isq/sqac065}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gannonShadowDeterrenceWhy2022}{}}%
+Gannon, J. Andrés, Erik Gartzke, Jon R. Lindsay, and Peter Schram. 2022.
 {``The {Shadow} of {Deterrence}: {Why Capable Actors Engage} in
 {Contests Short} of {War}.''} \emph{Journal of Conflict Resolution},
-April. \url{https://doi.org/10.1177/00220027231166345}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-slantchev_militarythreatscosts_2011}{}}%
+00220027231166345.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gartzkeCrossDomainDeterrenceStrategy2019}{}}%
+Gartzke, Erik, and Jon R. Lindsay. 2019. \emph{Cross-{Domain
+Deterrence}: {Strategy} in an {Era} of {Complexity}}. {Oxford University
+Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gavinHistorySecurityStudies2014}{}}%
+Gavin, Francis J. 2014. {``History, {Security Studies}, and the {July
+Crisis}.''} \emph{Journal of Strategic Studies} 37 (2): 319--31.
+\url{https://doi.org/10.1080/01402390.2014.912916}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-giblerInternationalConflicts181620102018}{}}%
+Gibler, Douglas M. 2018. \emph{International {Conflicts}, 1816-2010:
+{Militarized Interstate Dispute Narratives}}. {Rowman \& Littlefield}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-giblerMeasuringAlliancesCorrelates2004}{}}%
+Gibler, Douglas M., and Meredith Reid Sarkees. 2004. {``Measuring
+{Alliances}: The {Correlates} of {War Formal Interstate Alliance}
+{Dataset}, 1816\textendash 2000.''} \emph{Journal of Peace Research} 41
+(2): 211--22. \url{https://doi.org/10.1177/0022343304041061}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-glaserCausesConsequencesArms2000}{}}%
+Glaser, Charles L. 2000. {``The {Causes} and {Consequences} of {Arms
+Races}.''} \emph{Annual Review of Political Science} 3 (1): 251--76.
+\url{https://doi.org/10.1146/annurev.polisci.3.1.251}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goemansIntroducingArchigosDataset2009}{}}%
+Goemans, Henk E., Kristian Skrede Gleditsch, and Giacomo Chiozza. 2009.
+{``Introducing {Archigos}: {A} Dataset of Political Leaders.''}
+\emph{Journal of Peace Research} 46 (2): 269--83.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goertzMeasuringMilitaryAllocations1986}{}}%
+Goertz, Gary, and Paul F. Diehl. 1986. {``Measuring {Military
+Allocations}: {A Comparison} of {Different Approaches}.''} \emph{Journal
+of Conflict Resolution} 30 (3): 553--81.
+\url{https://doi.org/10.1177/0022002786030003009}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldgeierPsychologyInternationalRelations2001}{}}%
+Goldgeier, J. M., and P. E. Tetlock. 2001. {``Psychology and
+{International Relations Theory}.''} \emph{Annual Review of Political
+Science} 4 (1): 67--92.
+\url{https://doi.org/10.1146/annurev.polisci.4.1.67}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-grantOUEventData2017}{}}%
+Grant, Christan, Andrew Halterman, Jill Irvine, Yan Liang, and Khaled
+Jabr. 2017. {``{OU Event Data Project},''} December.
+
+\leavevmode\vadjust pre{\hypertarget{ref-haffarEmergentPeacemakersCataloguing2002}{}}%
+Haffar, Warren. 2002. {``Emergent {Peacemakers}: {Cataloguing New
+Patterns} of {Activity} in {Post-Cold War Conflict}.''} \emph{Peace
+Economics, Peace Science and Public Policy} 8 (2).
+\url{https://doi.org/10.2202/1554-8597.1054}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hermannComparativeResearchEvents1984}{}}%
+Hermann, Charles. 1984. {``Comparative {Research} on the {Events} of
+{Nations} ({CREON}) {Project}: {Foreign Policy Events}, 1959-1968:
+{Version} 1.''} {ICPSR - Interuniversity Consortium for Political and
+Social Research}. \url{https://doi.org/10.3886/ICPSR05205.V1}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hewittEngagingInternationalData2001}{}}%
+Hewitt, J. Joseph. 2001. {``Engaging {International Data} in the
+{Classroom}: {Using} the {ICB Interactive Data Library} to {Teach
+Conflict} and {Crisis Analysis}.''} \emph{International Studies
+Perspectives} 2 (4): 371--83.
+\url{https://doi.org/10.1111/1528-3577.00066}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-holsti1914Case1965}{}}%
+Holsti, Ole R. 1965. {``The 1914 {Case}.''} \emph{The American Political
+Science Review} 59 (2): 365--78. \url{https://doi.org/10.2307/1953055}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hsuStatesHarnessingSubnational2020}{}}%
+Hsu, Angel, Niklas Höhne, Takeshi Kuramochi, Virginia Vilariño, and
+Benjamin K. Sovacool. 2020. {``Beyond States: {Harnessing} Sub-National
+Actors for the Deep Decarbonisation of Cities, Regions, and
+Businesses.''} \emph{Energy Research \& Social Science} 70 (December):
+101738. \url{https://doi.org/10.1016/j.erss.2020.101738}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-iakhnisCrisesWorldPolitics2019}{}}%
+Iakhnis, Evgeniia, and Patrick James. 2019. {``Near Crises in World
+Politics: {A} New Dataset.''} \emph{Conflict Management and Peace
+Science}, July, 0738894219855610.
+\url{https://doi.org/10.1177/0738894219855610}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jagerLimitsStudyingNetworks2018}{}}%
+Jäger, Kai. 2018. {``The {Limits} of {Studying Networks} with {Event
+Data}: {Evidence} from the {ICEWS Dataset}.''} \emph{Journal of Global
+Security Studies} 3 (4): 498--511.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jervisCooperationSecurityDilemma1978}{}}%
+Jervis, Robert. 1978. {``Cooperation {Under} the {Security Dilemma}.''}
+\emph{World Politics} 30 (2): 167--214.
+\url{https://doi.org/10.2307/2009958}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kangUSBiasStudy2019}{}}%
+Kang, David C., and Alex Yu-Ting Lin. 2019. {``{US} Bias in the Study of
+{Asian} Security: {Using Europe} to Study {Asia}.''} \emph{Journal of
+Global Security Studies} 4 (3): 393--401.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kinneDefenseCooperationAgreement2020}{}}%
+Kinne, Brandon J. 2020. {``The {Defense Cooperation Agreement Dataset}
+({DCAD}).''} \emph{Journal of Conflict Resolution} 64 (4): 729--55.
+\url{https://doi.org/10.1177/0022002719857796}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lacinaExplainingSeverityCivil2006}{}}%
+Lacina, Bethany. 2006. {``Explaining the {Severity} of {Civil Wars}.''}
+\emph{Journal of Conflict Resolution} 50 (2): 276--89.
+\url{https://doi.org/10.1177/0022002705284828}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lafreeIntroducingGlobalTerrorism2007}{}}%
+LaFree, Gary, and Laura Dugan. 2007. {``Introducing the Global Terrorism
+Database.''} \emph{Terrorism and Political Violence} 19 (2): 181--204.
+
+\leavevmode\vadjust pre{\hypertarget{ref-laiEffectsDifferentTypes2004}{}}%
+Lai, Brian. 2004. {``The Effects of Different Types of Military
+Mobilization on the Outcome of International Crises.''} \emph{Journal of
+Conflict Resolution} 48 (2): 211--29.
+
+\leavevmode\vadjust pre{\hypertarget{ref-leedsDomesticPoliticalInstitutions1999}{}}%
+Leeds, Brett Ashley. 1999. {``Domestic {Political Institutions},
+{Credible Commitments}, and {International Cooperation}.''}
+\emph{American Journal of Political Science} 43 (4): 979--1002.
+\url{https://doi.org/10.2307/2991814}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-leedsAllianceReliabilityTimes2003}{}}%
+---------. 2003. {``Alliance {Reliability} in {Times} of {War}:
+{Explaining State Decisions} to {Violate Treaties}.''}
+\emph{International Organization} 57 (4): 801--27.
+\url{https://doi.org/10.1017/S0020818303574057}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lengMilitarizedInterstateCrises1988}{}}%
+Leng, Russell J., and J. David Singer. 1988. {``Militarized {Interstate
+Crises}: {The BCOW Typology} and {Its Applications}.''}
+\emph{International Studies Quarterly} 32 (2): 155--73.
+\url{https://doi.org/10.2307/2600625}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-liComprehensiveSurveySchemabased2021}{}}%
+Li, Qian, Hao Peng, Jianxin Li, Yiming Hei, Rui Sun, Jiawei Sheng, Shu
+Guo, et al. 2021. {``A {Comprehensive Survey} on {Schema-based Event
+Extraction} with {Deep Learning}.''} \emph{arXiv:2107.02126 {[}Cs{]}},
+August. \url{https://arxiv.org/abs/2107.02126}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lindsayPoliticsManyOther2020}{}}%
+Lindsay, Jon R., and Erik Gartzke. 2020. {``Politics by Many Other
+Means: {The} Comparative Strategic Advantages of Operational Domains.''}
+\emph{Journal of Strategic Studies} 0 (0): 1--34.
+\url{https://doi.org/10.1080/01402390.2020.1768372}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-luptonReexaminingReputationResolve2018}{}}%
+Lupton, Danielle L. 2018. {``Reexamining {Reputation} for {Resolve}:
+{Leaders}, {States}, and the {Onset} of {International Crises}.''}
+\emph{Journal of Global Security Studies} 3 (2): 198--216.
+\url{https://doi.org/10.1093/jogss/ogy004}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mandelbrotFractalGeometryNature1983}{}}%
+Mandelbrot, Benoit B. 1983. \emph{{The fractal geometry of nature}}.
+{New York}: {Freeman}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcclellandWorldEventInteraction1978}{}}%
+McClelland, Charles. 1978. {``World Event/Interaction Survey,
+1966-1978.''} \emph{WEIS Codebook ICPSR} 5211.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcnabbcochranMeasuringMilitaryEffectiveness2017}{}}%
+McNabb Cochran, Kathryn, and Stephen B. Long. 2017. {``Measuring
+{Military Effectiveness}: {Calculating Casualty Loss-Exchange Ratios}
+for {Multilateral Wars}, 1816\textendash 1990.''} \emph{International
+Interactions} 43 (6): 1019--40.
+\url{https://doi.org/10.1080/03050629.2017.1273914}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-merrittMeasuringEventsInternational1994}{}}%
+Merritt, Richard L. 1994. {``Measuring Events for International
+Political Analysis.''} \emph{International Interactions} 20 (1-2):
+3--33.
+
+\leavevmode\vadjust pre{\hypertarget{ref-millerWordNetLexicalDatabase1995}{}}%
+Miller, George A. 1995. {``{WordNet}: A Lexical Database for
+{English}.''} \emph{Communications of the ACM} 38 (11): 39--41.
+\url{https://doi.org/10.1145/219717.219748}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-minInterstateWarBattle2021}{}}%
+Min, Eric. 2021. {``Interstate {War Battle} Dataset
+(1823\textendash 2003).''} \emph{Journal of Peace Research} 58 (2):
+294--303. \url{https://doi.org/10.1177/0022343320913305}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moyerWhatAreDrivers2020}{}}%
+Moyer, Jonathan D, Sara D Turner, and Collin J Meisel. 2020. {``What Are
+the Drivers of Diplomacy? {Introducing} and Testing New Annual Dyadic
+Data Measuring Diplomatic Exchange.''} \emph{Journal of Peace Research},
+September, 0022343320929740.
+\url{https://doi.org/10.1177/0022343320929740}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-narangCivilmilitaryPathologiesDefeat2017}{}}%
+Narang, Vipin, and Caitlin Talmadge. 2017. {``Civil-Military
+{Pathologies} and {Defeat} in {War}: {Tests Using New Data}.''}
+\emph{Journal of Conflict Resolution}, January, 0022002716684627.
+\url{https://doi.org/10.1177/0022002716684627}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-oneillInternationalNegotiationConceptual2018}{}}%
+O'Neill, Barry. 2018. {``International {Negotiation}: {Some Conceptual
+Developments}.''} \emph{Annual Review of Political Science} 21 (1):
+515--33. \url{https://doi.org/10.1146/annurev-polisci-031416-092909}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-owsiakInternationalBorderAgreements2018}{}}%
+Owsiak, Andrew P, Allison K Cuttner, and Brent Buck. 2018. {``The
+{International Border Agreements Dataset}.''} \emph{Conflict Management
+and Peace Science} 35 (5): 559--76.
+\url{https://doi.org/10.1177/0738894216646978}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-paigeKoreanDecisionJune1968}{}}%
+Paige, Glenn D. 1968. \emph{The {Korean Decision}, {June} 24-30, 1950}.
+{Free Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-palmerMID5Dataset20112021}{}}%
+Palmer, Glenn, Roseanne W McManus, Vito D'Orazio, Michael R Kenwick,
+Mikaela Karstens, Chase Bloch, Nick Dietrich, Kayla Kahn, Kellan Ritter,
+and Michael J Soules. 2021. {``The {MID5 Dataset}, 2011\textendash 2014:
+{Procedures}, Coding Rules, and Description.''} \emph{Conflict
+Management and Peace Science}, February, 0738894221995743.
+\url{https://doi.org/10.1177/0738894221995743}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-powellGlobalInstancesCoups2011}{}}%
+Powell, Jonathan M, and Clayton L Thyne. 2011. {``Global Instances of
+Coups from 1950 to 2010: {A} New Dataset.''} \emph{Journal of Peace
+Research} 48 (2): 249--59.
+\url{https://doi.org/10.1177/0022343310397436}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-powellBargainingTheoryInternational2002}{}}%
+Powell, Robert. 2002. {``Bargaining {Theory} and {International
+Conflict}.''} \emph{Annual Review of Political Science} 5 (1): 1--30.
+\url{https://doi.org/10.1146/annurev.polisci.5.092601.141138}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-quinnPowerPlayMediation2006}{}}%
+Quinn, David, Jonathan Wilkenfeld, Kathleen Smarick, and Victor Asal.
+2006. {``Power {Play}: {Mediation} in {Symmetric} and {Asymmetric
+International Crises}.''} \emph{International Interactions} 32 (4):
+441--70. \url{https://doi.org/10.1080/03050620601011107}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-raleighIntroducingACLEDArmed2010}{}}%
+Raleigh, Clionadh, Andrew Linke, Håavard Hegre, and Joakim Karlsen.
+2010. {``Introducing {ACLED}: An Armed Conflict Location and Event
+Dataset: Special Data Feature.''} \emph{Journal of Peace Research} 47
+(5): 651--60.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ralphsundbergUCDPGEDCodebook2016}{}}%
+Ralph Sundberg, and Mihai Croicu. 2016. {``{UCDP GED Codebook} Version
+5.0.''} {Department of Peace and Conflict Research, Uppsala University}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ramsayInformationUncertaintyWar2017}{}}%
+Ramsay, Kristopher W. 2017. {``Information, {Uncertainty}, and {War}.''}
+\emph{Annual Review of Political Science} 20 (1): 505--27.
+\url{https://doi.org/10.1146/annurev-polisci-051215-022729}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-reiterShouldWeLeave2015}{}}%
+Reiter, Dan. 2015. {``Should {We Leave Behind} the {Subfield} of
+{International Relations}?''} \emph{Annual Review of Political Science}
+18 (1): 481--99.
+\url{https://doi.org/10.1146/annurev-polisci-053013-041156}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-reiterRevisedLookInterstate2016}{}}%
+Reiter, Dan, Allan C. Stam, and Michael C. Horowitz. 2016. {``A {Revised
+Look} at {Interstate Wars}, 1816\textendash 2007.''} \emph{Journal of
+Conflict Resolution} 60 (5): 956--76.
+\url{https://doi.org/10.1177/0022002714553107}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sarkeesResortWar181620072010}{}}%
+Sarkees, Meredith Reid, and Frank Wayman. 2010. \emph{Resort to War:
+1816-2007}. {CQ Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schrodtTwentyYearsKansas2006}{}}%
+Schrodt, Philip A., and Blake Hall. 2006. {``Twenty Years of the
+{Kansas} Event Data System Project.''} \emph{The Political
+Methodologist} 14 (1): 2--8.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sechserMilitarizedCompellentThreats2011}{}}%
+Sechser, Todd S. 2011. {``Militarized {Compellent Threats},
+1918\textendash 2001.''} \emph{Conflict Management and Peace Science} 28
+(4): 377--401. \url{https://doi.org/10.1177/0738894211413066}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-shermanSHERFACSCrossParadigmHierarchical2000}{}}%
+Sherman, Frank L. 2000. {``{SHERFACS}: {A Cross-Paradigm},
+{Hierarchical}, and {Contextually-Sensitive International Conflict
+Dataset}, 1937-1985: {Version} 1.''} {ICPSR - Interuniversity Consortium
+for Political and Social Research}.
+\url{https://doi.org/10.3886/ICPSR02292.V1}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-slantchevMilitaryThreatsCosts2011}{}}%
 Slantchev, Branislav L. 2011. \emph{Military Threats: The Costs of
-Coercion and the Price of Peace}. Cambridge ; New York: Cambridge
-University Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-turberville_historyobjectivesubjective_1933}{}}%
+Coercion and the Price of Peace}. {Cambridge University Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-spruytSovereignStateIts1996}{}}%
+Spruyt, Hendrik. 1996. \emph{The {Sovereign State} and {Its
+Competitors}: {An Analysis} of {Systems Change}}. {Princeton University
+Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-steinEvaluatingWarOutcomes1980}{}}%
+Stein, Arthur A., and Bruce M. Russett. 1980. {``Evaluating War:
+{Outcomes} and Consequences.''} In \emph{Handbook of Political Conflict:
+Theory and Research}, 399--422. {Free Press New York}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-steinert-threlkeldFutureEventData2019}{}}%
+Steinert-Threlkeld, Zachary C. 2019. {``The {Future} of {Event Data Is
+Images}.''} \emph{Sociological Methodology} 49 (1): 68--75.
+\url{https://doi.org/10.1177/0081175019860238}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sullivanWarAimsWar2007}{}}%
+Sullivan, Patricia L. 2007. {``War {Aims} and {War Outcomes}: {Why
+Powerful States Lose Limited Wars}.''} \emph{Journal of Conflict
+Resolution} 51 (3): 496--524.
+\url{https://doi.org/10.1177/0022002707300187}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sundbergIntroducingUCDPGeoreferenced2013}{}}%
+Sundberg, Ralph, and Erik Melander. 2013. {``Introducing the {UCDP}
+Georeferenced Event Dataset.''} \emph{Journal of Peace Research} 50 (4):
+523--32.
+
+\leavevmode\vadjust pre{\hypertarget{ref-terechshenkoHotCollarLatent2020}{}}%
+Terechshenko, Zhanna. 2020. {``Hot Under the Collar: {A} Latent Measure
+of Interstate Hostility.''} \emph{Journal of Peace Research} 57 (6):
+764--76. \url{https://doi.org/10.1177/0022343320962546}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tragerDiplomacyWarPeace2016}{}}%
+Trager, Robert F. 2016. {``The {Diplomacy} of {War} and {Peace}.''}
+\emph{Annual Review of Political Science} 19 (1): 205--28.
+\url{https://doi.org/10.1146/annurev-polisci-051214-100534}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-turbervilleHistoryObjectiveSubjective1933}{}}%
 Turberville, A. S. 1933. {``History {Objective} and {Subjective}.''}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wardLearningSteppingFuture2013}{}}%
+Ward, Michael D., Nils W. Metternich, Cassy L. Dorff, Max Gallop,
+Florian M. Hollenbach, Anna Schultz, and Simon Weschle. 2013.
+{``Learning from the Past and Stepping into the Future: {Toward} a New
+Generation of Conflict Prediction.''} \emph{International Studies
+Review} 15 (4): 473--90.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilkenfeldInterstateCrisesViolence2000}{}}%
+Wilkenfeld, Jonathan, and Michael Brecher. 2000. {``Interstate Crises
+and Violence: Twentieth-Century Findings.''} \emph{Handbook of War
+Studies II}, 282--300.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wuestExternalValidationProtest2020}{}}%
+Wüest, Bruno, and Jasmine Lorenzini. 2020. {``External Validation of
+Protest Event Analysis.''} \emph{Contention in Times of Crisis:
+Recession and Political Protest in Thirty Euro-Pean Countries}, 49--78.
+
+\leavevmode\vadjust pre{\hypertarget{ref-yarhi-miloEyeBeholderHow2013}{}}%
+Yarhi-Milo, Keren. 2013. {``In the {Eye} of the {Beholder}: {How
+Leaders} and {Intelligence Communities Assess} the {Intentions} of
+{Adversaries}.''} \emph{International Security} 38 (1): 7--51.
+\url{https://doi.org/10.1162/ISEC/_a/_00128}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-yarhi-miloArmAllyPatron2016}{}}%
+Yarhi-Milo, Keren, Alexander Lanoszka, and Zack Cooper. 2016. {``To
+{Arm} or to {Ally}? {The Patron}'s {Dilemma} and the {Strategic Logic}
+of {Arms Transfers} and {Alliances}.''} \emph{International Security} 41
+(2): 90--139. \url{https://doi.org/10.1162/ISEC/_a/_00250}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zartmanEscalationNegotiationInternational2005}{}}%
+Zartman, I. William, and Guy Olivier Faure. 2005. \emph{Escalation and
+Negotiation in International Conflicts}. {Cambridge University Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhangCASMDeepLearningApproach2019}{}}%
+Zhang, Han, and Jennifer Pan. 2019. {``{CASM}: {A Deep-Learning
+Approach} for {Identifying Collective Action Events} with {Text} and
+{Image Data} from {Social Media}.''} \emph{Sociological Methodology} 49
+(1): 1--57. \url{https://doi.org/10.1177/0081175019860244}.
+
 \end{CSLReferences}

### 2023-08-04 replication_paper/psrm_draft/ICBe_manuscript.Rmd
fig size fix

@@
 \doublespacing
+\newpage
 
@@
 If so, then these events can be recorded and systematically measured by social scientists interested in these regularities.[^1] Thanks to improvements in natural language processing, more open-ended efforts have begun to capture entire unstructured streams of events from international news reports.[^2] This has invited fruitful efforts to evaluate the coverage, quality, and accuracy of attempts to measure international affairs.
+
+[^1]: See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].
+
+[^2]: See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
+On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.
 
@@
 
-![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative}
+![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative width="7in" height="8in"}
 
@@
 Definitions for each ICBe variable are provided in the codebook.
+
+[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
 
@@
 
+[^4]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
+
 # Methodology and data
@@
 
+[^5]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
+
+[^6]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
+
 Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.[^7] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
@@
 This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
+
+[^7]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
+Undergraduate coders were students who engaged in classroom workshops.
 
@@
 Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
+
+[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
+nationalizing a foreign business).
+Even when they occur in the context of a crisis, these events largely fall outside the sample of information on which ICBe's ontology is currently trained.
+Even with this limitation, ICBe is more comprehensive than the existing datasets that do try to code the economic dimensions of these crises.
+We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
 
@@
 
+[^9]: We preprocess sentences to replace named entities with a generic Entity token.
+
+[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
+
 ![Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
@@
 The dendrogram shows hierarchical clustering of the tags.
-If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap}
+If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap width="7in" height="7in"}
 
@@
 ![Crisis map for the Cuban Missile Crisis.
-The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap}
+The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap width="6in"}
 
@@
 Red text shows events from the synthetic narrative relative to that event category.
-Blue bars indicate an event recorded by ICEWs for that dyad on that day.](p_precision_icews.png){#fig-precision-icews}
+Blue bars indicate an event recorded by ICEWs for that dyad on that day.](p_precision_icews.png){#fig-precision-icews width="7in" height="5in"}
 
@@
 
+[^11]: Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
+
 # Funding
 
-This work was supported by a grant from the Office of Naval Research \[N00014-19-1-2491\] and from the Charles Koch Foundation \[20180481\].
+This work was supported by a grant from the Office of Naval Research $N00014-19-1-2491$ and from the Charles Koch Foundation $20180481$.
 The financial sponsors played no in the design, execution, analysis and interpretation of data, or writing of the study.
@@
 # Works Cited
-
-[^1]: See work on crises [@brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020], militarized disputes [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], wars [@sarkeesResortWar181620072010; @reiterRevisedLookInterstate2016], organized violence [@ralphsundbergUCDPGEDCodebook2016; @daviesOrganizedViolence19892022], political violence [@raleighIntroducingACLEDArmed2010], sanctions [@felbermayrGlobalSanctionsData2020], and international agreements [@kinneDefenseCooperationAgreement2020; @owsiakInternationalBorderAgreements2018], dispute resolution [@frederickIssueCorrelatesWar2017], and diplomacy [@moyerWhatAreDrivers2020; @sechserMilitarizedCompellentThreats2011].
-
-[^2]: See @beielerGeneratingPoliticalEvent2016; @boscheeICEWSCodedEvent2015; @brandtPhoenixRealTimeEvent2018; @grantOUEventData2017; @liComprehensiveSurveySchemabased2021.
-On event extraction from images and social media see @zhangCASMDeepLearningApproach2019 and @steinert-threlkeldFutureEventData2019.
-
-[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
-
-[^4]: See @balaliCOfEEComprehensiveOntology2021 for a recent review of ontological depth and availability of Gold Standard example text.
-
-[^5]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
-
-[^6]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
-
-[^7]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
-Undergraduate coders were students who engaged in classroom workshops.
-
-[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
-nationalizing a foreign business).
-Even when they occur in the context of a crisis, these events largely fall outside the sample of information on which ICBe's ontology is currently trained.
-Even with this limitation, ICBe is more comprehensive than the existing datasets that do try to code the economic dimensions of these crises.
-We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
-
-[^9]: We preprocess sentences to replace named entities with a generic Entity token.
-
-[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
-
-[^11]: Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.

### 2023-08-04 replication_paper/psrm_draft/ICBe_manuscript.tex
fig size fix

@@
 \centering
-\includegraphics{case_study_cuban_precision.png}
+\includegraphics[width=7in,height=8in]{case_study_cuban_precision.png}
 \caption{Cuban Missile Crisis (1962) - ICB Narrative vs.~ICBe
@@
 \caption{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endfirsthead \caption[]{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
 
@@
 \centering
-\includegraphics{p_semantic_embeddings_dendro.png}
+\includegraphics[width=7in,height=7in]{p_semantic_embeddings_dendro.png}
 \caption{Dots represent individual ICB narrative sentences, as embedded
@@
 \centering
-\includegraphics{p_196_icbe.png}
+\includegraphics[width=6in,height=\textheight]{p_196_icbe.png}
 \caption{Crisis map for the Cuban Missile Crisis. The start of the
@@
 \centering
-\includegraphics{p_precision_icews.png}
+\includegraphics[width=7in,height=5in]{p_precision_icews.png}
 \caption{The unit of analysis is the dyad-day. Top 10 most active dyads
@@
 This work was supported by a grant from the Office of Naval Research
-\[N00014-19-1-2491\] and from the Charles Koch Foundation \[20180481\].
+\(N00014-19-1-2491\) and from the Charles Koch Foundation \(20180481\).
 The financial sponsors played no in the design, execution, analysis and

### 2023-08-16 replication_paper/psrm_draft/ICBe_manuscript.Rmd
AG penultimate RR

@@
     affiliation: University of California, San Diego
-  - name: J. Andrés Gannon
+  - name: J Andrés Gannon
     affiliation: Vanderbilt University
@@
 
+```{=tex}
 \doublespacing
 \newpage
-
+```
 If we could record every international interaction in the realms of diplomacy, conflict, economics, and beyond, how much unique information would this chronicle amount to, and how surprised would we be to see something new?
@@
 The easiest way to convey the desired produced of this task is with an example.
-@fig-cuba-narrative shows a narrative account of the Cuban Missile Crisis (1962) in natural language sentences alongside a mapping to discrete machine-readable abstractive events.
+Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) in natural language sentences alongside a mapping to discrete machine-readable abstractive events.
 From the structured data, scholars can identify similarities and differences across events concerning important concepts like when particular foreign policy actions deter versus inflame [@jervisCooperationSecurityDilemma1978; @glaserCausesConsequencesArms2000], when third parties mediate in interstate disputes [@haffarEmergentPeacemakersCataloguing2002; @quinnPowerPlayMediation2006], and how actors try to communicate resolve [@tragerDiplomacyWarPeace2016; @luptonReexaminingReputationResolve2018].
@@
 
-![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cuba-narrative width="7in" height="8in"}
+![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cubanarrative width="7in" height="8in"}
 
@@
 force size, fatalities, domains, units).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6] A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
+We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6]
+
+[^5]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
+The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
+
+[^6]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
+
+A unique feature of the ontology is that thought, speech, and do behaviors can be nested into combinations, e.g.
 an offer for the U.S.S.R.
@@
 Through compounding, the ontology can capture what players were said to have known, learned, or said about other specific fully described actions.
-
-[^5]: This process quickly focuses the coder on a smaller number of relevant options while also allowing them to apply multiple tags if the sentence explicitly includes more than one or there is insufficient evidence to choose only one tag.
-The guided coding process also allows for the possibility that earlier coarse decisions have less error than later fine-grained decisions.
-
-[^6]: See the full codebook on Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).
-
-Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.[^7] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
+Two other novel features of our data -- its re-programmamable coding and its inclusion of thought, speech, and action -- intersect to provide a unique contribution.
+No existing event data distinguishes thoughts, speeches, and actions and most are limited to just coding actions given they are the most readily observable and thus the full universe could at least theoretically be included.[^7] Yet, methods like archival work and expert interviews continue to improve identification of thoughts and speeches that help us understand the reasoning process underlying political decisions and what actually occurred behind the scenes.
+This is an improvement over the state of the art that omits these by design in allowing scholars to identify thoughts associated with things like crisis escalation as well as patterns of omission to be advanced in future work, but the modular nature of our coding means the inclusion of a non-random sample of thoughts and speeches is neither necessary nor does it have inevitable downstream effects on the rest of the coding in ways that produce unwanted bias.
+
+[^7]: Even the coding of overt actions like MIDs is not without contention [@giblerInternationalConflicts181620102018].
+
+Each crisis was typically assigned to 2 expert coders and 2 novice coders with an additional tie-breaking expert coder assigned to sentences with high disagreement.[^8] For the purposes of measuring intercoder agreement and consensus, we temporarily disaggregate the unit of analysis to the Coder-Crisis-Sentence-Tag (n=`r icb_long_clean %>% nrow() %>% scales::comma()`), where a tag is any unique piece of information a coder can associate with a sentence such as an actor, date, behavior, etc.
 We then aggregate those tags into final events (n=`r ICBe_events_agreed %>% nrow() %>% scales::comma()`), using a consensus procedure (SI Appendix 2.2) that requires a tag to have been chosen by at least one expert coder and either a majority of expert or novice coders.
@@
 
-[^7]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
+[^8]: Expert coders were graduate students or postgraduates who collaboratively developed the ontology and documentation for the codebook.
 Undergraduate coders were students who engaged in classroom workshops.
@@
 With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
-Intuitively, a high-quality event dataset should have high recall for context invariant details both because of their broader relevance and also because they are easier to find in source material.
+This presents a harder evaluation baseline than comparing ICBe's recall to just that of ICB since there are non-crisis aspects of these events that may be included in other narratives but are out of the scope of our data.
+For example, the nationalization of businesses in Cuba may be included as important context in the Cuban Missile Crisis in documents that do not focus on the crisis dimensions like ICB.
+Using this hard case, a recall measure of ICBe on the synthetic narratives thus serves as a way to evaluate the breadth of ICBe's ontology and potential application to non-crisis international events.
 
 We find substantive variation in recall across existing state of the art methods.
-Mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.[^8] Furthermore, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events.
-@fig-recall-cases compares ICBe's recall with that of existing datasets for the two case studies detailed in Section 4.
+Mentions of a detail across accounts are exponentially distributed with context-invariant details appearing dozens to hundreds of times more than context-dependent details.[^9] Furthermore, crisis start and stop dates are arbitrary, and the historical record points to many precursor events as necessary detail for understanding later events.
+Figure 2 compares ICBe's recall with that of existing datasets for the two case studies detailed in Section 4.
 ICBe strictly dominates all of the systems but ICEWs in recall though we note that the small sample sizes mean these systems should be considered statistically indistinguishable.
@@
 
-[^8]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
+[^9]: As the ICB narratives are intended to explain conflictual behavior in a political context, many of the missing events concern more economic components of conflict (eg.
 nationalizing a foreign business).
@@
 We call this visualization a crisis map, a directed graph intersected with a timeline.
-A crisis map using ICBe for the Cuban Missile Crisis case study is provided in @fig-cuba-crisismap, and crisis maps for the two case studies using existing event datasets can be found in SI Appendix 4.3 and 4.4 and crisis maps for all crises using all datasets can be found on the companion website.
+A crisis map using ICBe for the Cuban Missile Crisis case study is provided in Figure 2, and crisis maps for the two case studies using existing event datasets can be found in SI Appendix 4.3 and 4.4 and crisis maps for all crises using all datasets can be found on the companion website.
 The crisis maps reveal the episode-level datasets like MIDs or the original ICB are too sparse and vague to reconstruct the structure of the crisis (SI Appendix 4.3 and 4.4).
@@
 
-@fig-umap shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^9] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the right-hand side.[^10]
-
-[^9]: We preprocess sentences to replace named entities with a generic Entity token.
-
-[^10]: Hierarchical clustering on cosine similarity and with Ward's method.
+Figure 3 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^10] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
+If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the right-hand side.[^11]
+
+[^10]: We preprocess sentences to replace named entities with a generic Entity token.
+
+[^11]: Hierarchical clustering on cosine similarity and with Ward's method.
 
@@
 Our proposed measure is a reconstruction task to see whether our intended ontology can be recovered through only unsupervised clustering of sentences they were applied to.
-The first (@fig-cuba-narrative) is the Cuban Missile Crisis (hereafter Cuban Missiles) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war.
+The first (Figure 1) is the Cuban Missile Crisis (hereafter Cuban Missiles) which took place primarily in the second half of 1962, involved the United States, the Soviet Union, and Cuba, and is widely known for bringing the world to the brink of nuclear war.
 The second (SI Appendix 4.1) is the Crimea-Donbas Crisis (hereafter Crimea-Donbas) which took place primarily in 2014, involved Russia, Ukraine, and NATO, and within a decade spiraled into a full-scale invasion.
@@
 
-A synthetic historical narrative for Cuban Missiles appears in @fig-recall-cuba, with 51 events drawn from 2,020 documents.
+A synthetic historical narrative for Cuban Missiles appears in Figure 4, with 51 events drawn from 2,020 documents.
 Each row represents a detail that appeared in at least five documents along with an approximate start date, a handwritten summary, the number of documents it was mentioned in, and whether it could be identified in the text of the original ICB corpus, our ICBe events, and any of the competing existing models.
 
-ICB's improved recall of Cuban Missiles was relative to the state of the art was summarized in Section 3.2 (@fig-recall-cases), but the events that explain that improvement can now be seen.
+ICB's improved recall of Cuban Missiles was relative to the state of the art was summarized in Section 3.2 (Figure 2), but the events that explain that improvement can now be seen.
 Our ground truth ICB narrative contains 17/51 of the events from the synthetic narrative of a case that includes high-level previously classified details.
@@
 
-@fig-cuba-crisismap shows the crisis map for the Cuban Missile Crisis.
+Figure 5 shows the crisis map for the Cuban Missile Crisis.
 Looking at the crisis on a timeline, one can now identify the structure of actors and the environment, along with its supporting details, in a way that validates the precision of ICBe.
@@
 
-A synthetic historical narrative for the 2014 Crimea-Donbas crisis (30 events drawn from 971 documents) appears in @fig-recall-crimea.
+A synthetic historical narrative for the 2014 Crimea-Donbas crisis (30 events drawn from 971 documents) appears in Figure 6.
 As in the earlier case, rows represent details that appeared in at least five documents and whether it is identified in ICBe and existing datasets.
 
-Again quantitatively summarized earlier in Section 3.2 (@fig-recall-cases), our ground truth ICB narrative contains 23/30 of the events from the synthetic narrative.
+Again quantitatively summarized earlier in Section 3.2 (Figure 2), our ground truth ICB narrative contains 23/30 of the events from the synthetic narrative.
 Like the gray zone precursor to the Cuban Missile crisis [@cormacGreyNewBlack2018], Ukraine provided several security guarantees to Russia that were potentially undone, e.g.
@@
 
-We take the same approach here in @fig-precision-icews, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
+We take the same approach here in Figure 7, selecting four specific CAMEO event codings and checking how often they reflect a true real-world event from the Crimea-Donbas synthetic narrative.
 We choose four event types around key moments in the crisis.
@@
 These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).[^11] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
+escalation and de-escalation of conflicts).[^12] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
@@
 
-[^11]: Using ICBe data @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
+[^12]: Using ICBe data, @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
 

### 2023-08-16 replication_paper/psrm_draft/ICBe_manuscript.tex
AG penultimate RR

@@
    \And
-    J. Andrés Gannon
+    J Andrés Gannon
    \\
@@
 recall. The easiest way to convey the desired produced of this task is
-with an example. (\textbf{fig-cuba-narrative?}) shows a narrative
-account of the Cuban Missile Crisis (1962) in natural language sentences
-alongside a mapping to discrete machine-readable abstractive events.
-From the structured data, scholars can identify similarities and
-differences across events concerning important concepts like when
-particular foreign policy actions deter versus inflame (Jervis 1978;
-Glaser 2000), when third parties mediate in interstate disputes (Haffar
-2002; Quinn et al. 2006), and how actors try to communicate resolve
-(Trager 2016; Lupton 2018). Identifying patterns of international
-interactions is not just an inherently interesting enterprise; it is a
-necessary precondition to important efforts to predict where
-policymakers should turn their attention to improve global welfare (Ward
-et al. 2013; Beger, Morgan, and Ward 2021).
+with an example. Figure 1 shows a narrative account of the Cuban Missile
+Crisis (1962) in natural language sentences alongside a mapping to
+discrete machine-readable abstractive events. From the structured data,
+scholars can identify similarities and differences across events
+concerning important concepts like when particular foreign policy
+actions deter versus inflame (Jervis 1978; Glaser 2000), when third
+parties mediate in interstate disputes (Haffar 2002; Quinn et al. 2006),
+and how actors try to communicate resolve (Trager 2016; Lupton 2018).
+Identifying patterns of international interactions is not just an
+inherently interesting enterprise; it is a necessary precondition to
+important efforts to predict where policymakers should turn their
+attention to improve global welfare (Ward et al. 2013; Beger, Morgan,
+and Ward 2021).
 
 \begin{figure}
-\hypertarget{fig-cuba-narrative}{%
+\hypertarget{fig-cubanarrative}{%
 \centering
@@
 \caption{Cuban Missile Crisis (1962) - ICB Narrative vs.~ICBe
-Events}\label{fig-cuba-narrative}
+Events}\label{fig-cubanarrative}
 }
@@
 conflict by employing the coast guard or paramilitary mercenaries
-instead of internationally recognized state militaries (J. Andrés Gannon
-et al. 2022). Second, we add information about the domains in which
-actors behave - whether in land, air, sea, space, or cyber - since they
-differ in their technology, tactics, geography, and purpose (Gartzke and
+instead of internationally recognized state militaries (Gannon et al.
+2022). Second, we add information about the domains in which actors
+behave - whether in land, air, sea, space, or cyber - since they differ
+in their technology, tactics, geography, and purpose (Gartzke and
 Lindsay 2019). Doing so allows researchers to identify and explain
@@
 new domains of conflict like space and cyber have made this an endeavor
-of increased interest to practitioners (J. Andrés Gannon 2022).
+of increased interest to practitioners (Gannon 2022).
 
@@
   \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
+
 A unique feature of the ontology is that thought, speech, and do
@@
 players were said to have known, learned, or said about other specific
-fully described actions.
+fully described actions. Two other novel features of our data -- its
+re-programmamable coding and its inclusion of thought, speech, and
+action -- intersect to provide a unique contribution. No existing event
+data distinguishes thoughts, speeches, and actions and most are limited
+to just coding actions given they are the most readily observable and
+thus the full universe could at least theoretically be
+included.\footnote{Even the coding of overt actions like MIDs is not
+  without contention (Gibler 2018).} Yet, methods like archival work and
+expert interviews continue to improve identification of thoughts and
+speeches that help us understand the reasoning process underlying
+political decisions and what actually occurred behind the scenes. This
+is an improvement over the state of the art that omits these by design
+in allowing scholars to identify thoughts associated with things like
+crisis escalation as well as patterns of omission to be advanced in
+future work, but the modular nature of our coding means the inclusion of
+a non-random sample of thoughts and speeches is neither necessary nor
+does it have inevitable downstream effects on the rest of the coding in
+ways that produce unwanted bias.
 
@@
 episode constant and see which details tend to be invariant to context.
-Intuitively, a high-quality event dataset should have high recall for
-context invariant details both because of their broader relevance and
-also because they are easier to find in source material.
+This presents a harder evaluation baseline than comparing ICBe's recall
+to just that of ICB since there are non-crisis aspects of these events
+that may be included in other narratives but are out of the scope of our
+data. For example, the nationalization of businesses in Cuba may be
+included as important context in the Cuban Missile Crisis in documents
+that do not focus on the crisis dimensions like ICB. Using this hard
+case, a recall measure of ICBe on the synthetic narratives thus serves
+as a way to evaluate the breadth of ICBe's ontology and potential
+application to non-crisis international events.
 
@@
 historical record points to many precursor events as necessary detail
-for understanding later events. (\textbf{fig-recall-cases?}) compares
-ICBe's recall with that of existing datasets for the two case studies
-detailed in Section 4. ICBe strictly dominates all of the systems but
-ICEWs in recall though we note that the small sample sizes mean these
-systems should be considered statistically indistinguishable. Across all
-existing datasets and ICBe, recall increases with the number of document
-mentions which is an important sign of validity for both them and our
-benchmark. The one outlier is Phoenix which in the Cuban Missile Crisis
-case is so noisy that it's recall curve is flat to decreasing as
-mentions increase. The two episode-level datasets (MIDs and ICM) have
-low coverage of contextual details. The two other dictionary systems
-ICEWs and Terrier have higher coverage, with ICEWs outperforming
-Terrier. Importantly our corpus of ICB narratives has high recall of
-frequently mentioned details giving us confidence in how those summaries
-were constructed, and ICBe lags only slightly behind showing that it
-left little additional information on the table.
+for understanding later events. Figure 2 compares ICBe's recall with
+that of existing datasets for the two case studies detailed in Section
+4. ICBe strictly dominates all of the systems but ICEWs in recall though
+we note that the small sample sizes mean these systems should be
+considered statistically indistinguishable. Across all existing datasets
+and ICBe, recall increases with the number of document mentions which is
+an important sign of validity for both them and our benchmark. The one
+outlier is Phoenix which in the Cuban Missile Crisis case is so noisy
+that it's recall curve is flat to decreasing as mentions increase. The
+two episode-level datasets (MIDs and ICM) have low coverage of
+contextual details. The two other dictionary systems ICEWs and Terrier
+have higher coverage, with ICEWs outperforming Terrier. Importantly our
+corpus of ICB narratives has high recall of frequently mentioned details
+giving us confidence in how those summaries were constructed, and ICBe
+lags only slightly behind showing that it left little additional
+information on the table.
 
@@
 graph intersected with a timeline. A crisis map using ICBe for the Cuban
-Missile Crisis case study is provided in (\textbf{fig-cuba-crisismap?}),
-and crisis maps for the two case studies using existing event datasets
-can be found in SI Appendix 4.3 and 4.4 and crisis maps for all crises
-using all datasets can be found on the companion website. The crisis
-maps reveal the episode-level datasets like MIDs or the original ICB are
-too sparse and vague to reconstruct the structure of the crisis (SI
-Appendix 4.3 and 4.4). On the other end of the spectrum, the high recall
-dictionary-based event datasets like Terrier and ICEWs produce so many
-noisy events (several hundred thousand) that even with heavy filtering
-their crisis maps are completely unintelligible. Further, because of
-copyright issues, none of these datasets directly provide the original
-text spans making event-level precision difficult to verify.
+Missile Crisis case study is provided in Figure 2, and crisis maps for
+the two case studies using existing event datasets can be found in SI
+Appendix 4.3 and 4.4 and crisis maps for all crises using all datasets
+can be found on the companion website. The crisis maps reveal the
+episode-level datasets like MIDs or the original ICB are too sparse and
+vague to reconstruct the structure of the crisis (SI Appendix 4.3 and
+4.4). On the other end of the spectrum, the high recall dictionary-based
+event datasets like Terrier and ICEWs produce so many noisy events
+(several hundred thousand) that even with heavy filtering their crisis
+maps are completely unintelligible. Further, because of copyright
+issues, none of these datasets directly provide the original text spans
+making event-level precision difficult to verify.
 
@@
 
-(\textbf{fig-umap?}) shows the location of every sentence from the ICBe
-corpus in semantic space as embedded using the same large language model
-as before, and the median location of each ICBe event tag applied to
-those sentences.\footnote{We preprocess sentences to replace named
-  entities with a generic Entity token.} Labels reflect the individual
-leaves of the ontology and colors reflect the higher level coarse branch
-nodes of the ontology. If ICBe has high precision, substantively similar
-tags ought to have been applied to substantively similar source text,
-which is what we see both in two dimensions in the main plot and via
+Figure 3 shows the location of every sentence from the ICBe corpus in
+semantic space as embedded using the same large language model as
+before, and the median location of each ICBe event tag applied to those
+sentences.\footnote{We preprocess sentences to replace named entities
+  with a generic Entity token.} Labels reflect the individual leaves of
+the ontology and colors reflect the higher level coarse branch nodes of
+the ontology. If ICBe has high precision, substantively similar tags
+ought to have been applied to substantively similar source text, which
+is what we see both in two dimensions in the main plot and via
 hierarchical clustering on all dimensions in the dendrogram along the
@@
 whether our intended ontology can be recovered through only unsupervised
-clustering of sentences they were applied to. The first
-((\textbf{fig-cuba-narrative?})) is the Cuban Missile Crisis (hereafter
-Cuban Missiles) which took place primarily in the second half of 1962,
-involved the United States, the Soviet Union, and Cuba, and is widely
-known for bringing the world to the brink of nuclear war. The second (SI
-Appendix 4.1) is the Crimea-Donbas Crisis (hereafter Crimea-Donbas)
-which took place primarily in 2014, involved Russia, Ukraine, and NATO,
-and within a decade spiraled into a full-scale invasion. We choose these
-cases because they are significant in contemporary international
-relations, are widely known across academic disciplines as well as among
-the public, and are sufficiently brief to evaluate in depth. They are
+clustering of sentences they were applied to. The first (Figure 1) is
+the Cuban Missile Crisis (hereafter Cuban Missiles) which took place
+primarily in the second half of 1962, involved the United States, the
+Soviet Union, and Cuba, and is widely known for bringing the world to
+the brink of nuclear war. The second (SI Appendix 4.1) is the
+Crimea-Donbas Crisis (hereafter Crimea-Donbas) which took place
+primarily in 2014, involved Russia, Ukraine, and NATO, and within a
+decade spiraled into a full-scale invasion. We choose these cases
+because they are significant in contemporary international relations,
+are widely known across academic disciplines as well as among the
+public, and are sufficiently brief to evaluate in depth. They are
 similar in that both cases involve a superpower in crisis with a
@@
 
-A synthetic historical narrative for Cuban Missiles appears in
-(\textbf{fig-recall-cuba?}), with 51 events drawn from 2,020 documents.
-Each row represents a detail that appeared in at least five documents
-along with an approximate start date, a handwritten summary, the number
-of documents it was mentioned in, and whether it could be identified in
-the text of the original ICB corpus, our ICBe events, and any of the
-competing existing models.
+A synthetic historical narrative for Cuban Missiles appears in Figure 4,
+with 51 events drawn from 2,020 documents. Each row represents a detail
+that appeared in at least five documents along with an approximate start
+date, a handwritten summary, the number of documents it was mentioned
+in, and whether it could be identified in the text of the original ICB
+corpus, our ICBe events, and any of the competing existing models.
 
 ICB's improved recall of Cuban Missiles was relative to the state of the
-art was summarized in Section 3.2 ((\textbf{fig-recall-cases?})), but
-the events that explain that improvement can now be seen. Our ground
-truth ICB narrative contains 17/51 of the events from the synthetic
-narrative of a case that includes high-level previously classified
-details. ICBe captures nearly all details included in ICB as well as
-more details from the synthetic narrative than any competing dataset.
-Phoenix includes some earlier information than ICBe like the
-nationalization of businesses and back channel negotiations, but the
-crisis narrative has a clean canonical end with the Soviets agreeing to
-withdraw missiles. ICBe stands out in including more communicative
-behavior (do -- speech) than existing datasets like US threats to attack
-and later promises not to invade. Given the recognized importance of
-threat credibility for understanding international conflict, the
-addition of this information is a substantively important improvement
-over the existing state of the art (Slantchev 2011).
+art was summarized in Section 3.2 (Figure 2), but the events that
+explain that improvement can now be seen. Our ground truth ICB narrative
+contains 17/51 of the events from the synthetic narrative of a case that
+includes high-level previously classified details. ICBe captures nearly
+all details included in ICB as well as more details from the synthetic
+narrative than any competing dataset. Phoenix includes some earlier
+information than ICBe like the nationalization of businesses and back
+channel negotiations, but the crisis narrative has a clean canonical end
+with the Soviets agreeing to withdraw missiles. ICBe stands out in
+including more communicative behavior (do -- speech) than existing
+datasets like US threats to attack and later promises not to invade.
+Given the recognized importance of threat credibility for understanding
+international conflict, the addition of this information is a
+substantively important improvement over the existing state of the art
+(Slantchev 2011).
 
@@
 
-(\textbf{fig-cuba-crisismap?}) shows the crisis map for the Cuban
-Missile Crisis. Looking at the crisis on a timeline, one can now
-identify the structure of actors and the environment, along with its
-supporting details, in a way that validates the precision of ICBe.
-Although harder to measure objectively, this crisis map provides face
-valid evidence that ICBe's account is not too vague, but also not
-unnecessarily detailed. We include much of the geopolitically important
-details like Soviet deployment, US discovery of that deployment,
-heightened alert levels, a blockade, and negotiations that ended with a
-formal agreement. At the same time, the crisis map indicates that ICBe
-does not include unnecessary nuances that preclude useful comparison to
-other international events.
+Figure 5 shows the crisis map for the Cuban Missile Crisis. Looking at
+the crisis on a timeline, one can now identify the structure of actors
+and the environment, along with its supporting details, in a way that
+validates the precision of ICBe. Although harder to measure objectively,
+this crisis map provides face valid evidence that ICBe's account is not
+too vague, but also not unnecessarily detailed. We include much of the
+geopolitically important details like Soviet deployment, US discovery of
+that deployment, heightened alert levels, a blockade, and negotiations
+that ended with a formal agreement. At the same time, the crisis map
+indicates that ICBe does not include unnecessary nuances that preclude
+useful comparison to other international events.
 
@@
 A synthetic historical narrative for the 2014 Crimea-Donbas crisis (30
-events drawn from 971 documents) appears in
-(\textbf{fig-recall-crimea?}). As in the earlier case, rows represent
-details that appeared in at least five documents and whether it is
-identified in ICBe and existing datasets.
-
-Again quantitatively summarized earlier in Section 3.2
-((\textbf{fig-recall-cases?})), our ground truth ICB narrative contains
-23/30 of the events from the synthetic narrative. Like the gray zone
-precursor to the Cuban Missile crisis (Cormac and Aldrich 2018), Ukraine
-provided several security guarantees to Russia that were potentially
-undone, e.g.~a long term lease on naval facilities in Crimea. But unlike
-the Cuban Missile crisis, the end of this crisis is unclear, with the
-event meekly ending with a second cease-fire agreement (Minsk II) but
-continued fighting. ICBe again recalls more important information about
-the crisis than any existing dataset, particularly information
-concerning the behavior of non-state separatist groups like the Donetsk
-People's Republic (DPR) and Luhansk People's Republic (LPR).
+events drawn from 971 documents) appears in Figure 6. As in the earlier
+case, rows represent details that appeared in at least five documents
+and whether it is identified in ICBe and existing datasets.
+
+Again quantitatively summarized earlier in Section 3.2 (Figure 2), our
+ground truth ICB narrative contains 23/30 of the events from the
+synthetic narrative. Like the gray zone precursor to the Cuban Missile
+crisis (Cormac and Aldrich 2018), Ukraine provided several security
+guarantees to Russia that were potentially undone, e.g.~a long term
+lease on naval facilities in Crimea. But unlike the Cuban Missile
+crisis, the end of this crisis is unclear, with the event meekly ending
+with a second cease-fire agreement (Minsk II) but continued fighting.
+ICBe again recalls more important information about the crisis than any
+existing dataset, particularly information concerning the behavior of
+non-state separatist groups like the Donetsk People's Republic (DPR) and
+Luhansk People's Republic (LPR).
 
@@
 
-We take the same approach here in (\textbf{fig-precision-icews?}),
-selecting four specific CAMEO event codings and checking how often they
-reflect a true real-world event from the Crimea-Donbas synthetic
-narrative. We choose four event types around key moments in the crisis.
-The start of the crisis revolves around Ukraine backing out of a trade
-deal with the EU in favor of Russia, but ``sign formal agreement''
-events act more like a topic detector with dozens of events generated by
-discussions of a possible agreement but not the actual agreement which
-never materialized. The switch is caught by the ``reject plan, agreement
-to settle dispute'', but also continues for Viktor Yanukovych even after
-he was removed from power because of articles retroactively discussing
-the cause of his removal. Events for ``use conventional military force''
+We take the same approach here in Figure 7, selecting four specific
+CAMEO event codings and checking how often they reflect a true
+real-world event from the Crimea-Donbas synthetic narrative. We choose
+four event types around key moments in the crisis. The start of the
+crisis revolves around Ukraine backing out of a trade deal with the EU
+in favor of Russia, but ``sign formal agreement'' events act more like a
+topic detector with dozens of events generated by discussions of a
+possible agreement but not the actual agreement which never
+materialized. The switch is caught by the ``reject plan, agreement to
+settle dispute'', but also continues for Viktor Yanukovych even after he
+was removed from power because of articles retroactively discussing the
+cause of his removal. Events for ``use conventional military force''
 capture a threshold around the start of hostilities and who the
@@
 questions about the sequencing of events (e.g.~escalation and
-de-escalation of conflicts).\footnote{Using ICBe data J. Andrés Gannon
-  (2022) finds that cross-domain crises are shorter and less violent
-  than same-domain crises.} Second, we provide a coder-level
-disaggregation with multiple codings of each sentence by experts and
-undergrads that allows for the introduction of uncertainty and human
-interpretation of events. Further, we release a direct mapping from the
-codings to the source text at the sentence level as a new resource for
-natural language processing. Finally, we provide a companion website
-that incorporates detailed visualizations of all of the data introduced
-here at crisisevents.org.
+de-escalation of conflicts).\footnote{Using ICBe data, Gannon (2022)
+  finds that cross-domain crises are shorter and less violent than
+  same-domain crises.} Second, we provide a coder-level disaggregation
+with multiple codings of each sentence by experts and undergrads that
+allows for the introduction of uncertainty and human interpretation of
+events. Further, we release a direct mapping from the codings to the
+source text at the sentence level as a new resource for natural language
+processing. Finally, we provide a companion website that incorporates
+detailed visualizations of all of the data introduced here at
+crisisevents.org.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gannonShadowDeterrenceWhy2022}{}}%
-Gannon, J. Andrés, Erik Gartzke, Jon R. Lindsay, and Peter Schram. 2022.
+Gannon, J Andrés, Erik Gartzke, Jon R. Lindsay, and Peter Schram. 2022.
 {``The {Shadow} of {Deterrence}: {Why Capable Actors Engage} in

### 2023-08-19 replication_paper/psrm_draft/ICBe_manuscript.tex

@@
 
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endfirsthead \caption[]{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
 \hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead

### 2023-08-19 replication_paper/psrm_draft/ICBe_manuscript.Rmd
TLS 3/4 R&R

@@
 
+The rows in Table 1 represent the types of information we expect to find in international relations and forms the basis for our proposed ontology.
+We created this ontology by performing  of the corpus and identifying named entities and verbs mentioned in the text.
+To identify possible behaviors, we matched verbs to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied (SI Appendix 1.2), and then aggregated them into a smaller number of behaviors balancing conceptual detail with manageable sparsity for human coding, informed by existing conceptual ("Literature" column) and measurement research (discussed below).
+We used the ICB project actor level data to identify likely actors for each crisis and location options relative to each actor.
+For behavior, actor, and location, coders could write-in a value if the given options were insufficient.
+The codebook lists 11 behaviors added post-coding as coders flagged events that were not captured by the initial ontology (e.g.
+propaganda).
+
 As we are not the first to attempt to measure international relations in a structured manner, the columns of Table 1 compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage.
@@
 Even like-concepts require care in comparison, as an 'aim' in ICBe is the same as in MIPS, but an 'alert' in ICBe is not the same as an 'alert' in MID.
-Definitions for each ICBe variable are provided in the codebook.
+
+This comparison is not intended to fault existing data and models for not including every variable in ICBe's ontology, as some of these variables fall outside the scope of a particular dataset's intended purpose.
+Rather, it serves as an initial basis for identifying the heterogeneity in existing efforts to abstract and measure discrete historical events of interest and to provide theoretical justifications from existing research about what is included in our dataset's ontology and where ICBe's detail about historical events can be compared to the current state of the art.
 
@@
 
-The rows in Table 1 represent the types of information we expect to find in international relations and forms the basis for our proposed ontology.
-We create this by performing preliminary natural language processing of the corpus and identified named entities and behaviors mentioned in the text.
-Verbs were matched to the most likely definition found in Wordnet [@millerWordNetLexicalDatabase1995], tallied, and then aggregated into a smaller number of hypernyms balancing conceptual detail and manageable sparsity for human coding (SI Appendix 1.2).
-This comparison is not intended to fault existing data and models for not including every variable in ICBe's ontology, as some of these variables fall outside the scope of a particular dataset's intended purpose.
-Rather, it serves as an initial basis for identifying the heterogeneity in existing efforts to abstract and measure discrete historical events of interest and to provide theoretical justifications from existing research about what is included in our dataset's ontology and where ICBe's detail about historical events can be compared to the current state of the art.
-
 With the exception of large-scale CAMEO dictionary-based systems (the first grouping of columns), our ontology improves upon the the existing state of the art quantitative datasets that ignore important information content about international interactions.[^4] We highlight two particular innovations.
@@
 force size, fatalities, domains, units).
-We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.[^6]
+While each event was matched to a sentence, coders could fill in details outside that sentence (e.g.
+antecedents to pronouns).
+We reviewed, standardized, and normalized where coders listed a behavior, actor, or location outside the ontology.[^6] We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.
 
@@
 This screens noisy tags that no expert considered possible but leverages novice knowledge to tie-break between equally plausible tags chosen by experts.
+Requiring sentence-tag matching may underestimate agreement but minimizes the inclusion of noise and allows for additional validation.
 

### 2023-08-19 replication_paper/psrm_draft/ICBe_manuscript.tex
TLS 3/4 R&R

--- 2023-08-16 replication_paper/psrm_draft/ICBe_manuscript.tex
@@
 
+The rows in Table 1 represent the types of information we expect to find
+in international relations and forms the basis for our proposed
+ontology. We created this ontology by performing of the corpus and
+identifying named entities and verbs mentioned in the text. To identify
+possible behaviors, we matched verbs to the most likely definition found
+in Wordnet (Miller 1995), tallied (SI Appendix 1.2), and then aggregated
+them into a smaller number of behaviors balancing conceptual detail with
+manageable sparsity for human coding, informed by existing conceptual
+(``Literature'' column) and measurement research (discussed below). We
+used the ICB project actor level data to identify likely actors for each
+crisis and location options relative to each actor. For behavior, actor,
+and location, coders could write-in a value if the given options were
+insufficient. The codebook lists 11 behaviors added post-coding as
+coders flagged events that were not captured by the initial ontology
+(e.g.~propaganda).
+
 As we are not the first to attempt to measure international relations in
@@
 care in comparison, as an `aim' in ICBe is the same as in MIPS, but an
-`alert' in ICBe is not the same as an `alert' in MID. Definitions for
-each ICBe variable are provided in the codebook.
+`alert' in ICBe is not the same as an `alert' in MID.
+
+This comparison is not intended to fault existing data and models for
+not including every variable in ICBe's ontology, as some of these
+variables fall outside the scope of a particular dataset's intended
+purpose. Rather, it serves as an initial basis for identifying the
+heterogeneity in existing efforts to abstract and measure discrete
+historical events of interest and to provide theoretical justifications
+from existing research about what is included in our dataset's ontology
+and where ICBe's detail about historical events can be compared to the
+current state of the art.
 
@@
 
-\begin{longtable}[c]{|p{0.10in}|p{2.00in}|p{1.60in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}}
+\begin{longtable}[c]{|p{0.10in}|p{2.00in}|p{1.60in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Start}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1945}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1977}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1995}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1989}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{End}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2019}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2018}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2020}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2015}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2014}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2007}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{N}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{32K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{8.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{28.4M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{17.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{128K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{5.9K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Corpus}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{ICB}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fazal}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Spruyt}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Haffar}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Bush}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hadden}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{MishaliRam}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lacina}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{McNabb}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cochran}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Long}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carafano}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2014)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goertz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diehl}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Brecher}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wilkenfeld}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goldgeier}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Tetlock}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stein}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Russett}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sullivan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ramsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{O’Neill}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Zartman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Faure}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sechser}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{R.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goemans,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gleditsch,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chiozza}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2009)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{J.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{M.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Thyne}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chenoweth,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hendrix,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hunter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Eck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hultman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{LaFree}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Dugan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Beardsley}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gibler}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Owsiak,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cuttner,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Buck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lanoszka,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cooper}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lai}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Allen,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Flynn,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Martinez}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Machain}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fortna}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Min}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wayman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Reiter,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stam,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Horowitz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Frederick,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hensel,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Macaulay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ACLED}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endfirsthead \caption[]{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ACLED}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Start}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1945}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1977}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1995}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1989}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{End}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2019}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2018}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2020}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2015}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2014}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2007}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{N}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{32K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{8.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{28.4M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{17.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{128K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{5.9K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Corpus}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{ICB}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fazal}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Spruyt}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Haffar}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Bush}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hadden}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{MishaliRam}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lacina}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{McNabb}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cochran}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Long}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carafano}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2014)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goertz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diehl}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Brecher}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wilkenfeld}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goldgeier}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Tetlock}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stein}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Russett}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sullivan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ramsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{O’Neill}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Zartman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Faure}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sechser}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{R.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goemans,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gleditsch,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chiozza}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2009)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{J.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{M.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Thyne}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chenoweth,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hendrix,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hunter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Eck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hultman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{LaFree}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Dugan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Beardsley}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gibler}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Owsiak,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cuttner,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Buck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lanoszka,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cooper}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lai}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Allen,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Flynn,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Martinez}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Machain}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fortna}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Min}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wayman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Reiter,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stam,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Horowitz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Frederick,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hensel,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Macaulay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
 
@@
 \doublespacing
-
-The rows in Table 1 represent the types of information we expect to find
-in international relations and forms the basis for our proposed
-ontology. We create this by performing preliminary natural language
-processing of the corpus and identified named entities and behaviors
-mentioned in the text. Verbs were matched to the most likely definition
-found in Wordnet (Miller 1995), tallied, and then aggregated into a
-smaller number of hypernyms balancing conceptual detail and manageable
-sparsity for human coding (SI Appendix 1.2). This comparison is not
-intended to fault existing data and models for not including every
-variable in ICBe's ontology, as some of these variables fall outside the
-scope of a particular dataset's intended purpose. Rather, it serves as
-an initial basis for identifying the heterogeneity in existing efforts
-to abstract and measure discrete historical events of interest and to
-provide theoretical justifications from existing research about what is
-included in our dataset's ontology and where ICBe's detail about
-historical events can be compared to the current state of the art.
 
@@
 details were only collected if appropriate (e.g.~force size, fatalities,
-domains, units). We find 472 actors and 117 different
-behaviors.\footnote{See the full codebook on Github Repository
+domains, units). While each event was matched to a sentence, coders
+could fill in details outside that sentence (e.g.~antecedents to
+pronouns). We reviewed, standardized, and normalized where coders listed
+a behavior, actor, or location outside the ontology.\footnote{See the
+  full codebook on Github Repository
   \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
+We find 472 actors and 117 different behaviors.
 
@@
 that no expert considered possible but leverages novice knowledge to
-tie-break between equally plausible tags chosen by experts.
+tie-break between equally plausible tags chosen by experts. Requiring
+sentence-tag matching may underestimate agreement but minimizes the
+inclusion of noise and allows for additional validation.
 

### 2023-08-19 replication_paper/psrm_draft/ICBe_supplemental_information.Rmd
TLS 3/4 R&R

@@
 
-```{r ICBe Crisis Summaries, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F}
+```{r ICBe Crisis Summaries, eval=F, echo=F, results='hide', include=T, message=F, cache=F, warning=F}
+
+# Not evaluated for R&R
 
@@
 
-temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
+temp_all %>% ungroup() %>% filter(crisno %in% c(1:60)) %>% convert_to_ft() %>%
   save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)
@@
 # Recall
-\hphantom{em}
 
 ## Synthetic Narratives
-\hphantom{em}
+
+\doublespacing
 
@@
 The relevant formulas and algorithm are shown below.
+
+\singlespacing
 
@@
 
-```{r crimea case study precision, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
+```{r crimea case study precision, eval=F, results='hide', echo=F, include=T, message=F, cache=F}
 
@@
 
-```{r Stratified Sentence Examples, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
+```{r Stratified Sentence Examples, eval=F, results='hide', echo=F, include=T, message=F, cache=F}
 

### 2023-08-19 replication_paper/psrm_draft/ICBe_supplemental_information.tex
psrm prep
TLS 3/4 R&R

--- 2022-09-21 replication_paper/political_analysis_draft/appendix.tex
@@
 \usepackage{hyperref}
+\usepackage{float}
+\usepackage{wrapfig}
 \begin{document}
@@
 
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{0pt}
 
@@
 
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
 \begin{longtable}[c]{|p{0.30in}|p{0.75in}|p{6.00in}}
 
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{uses}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Lemma}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Gloss}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{uses}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Lemma}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{Gloss}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{381}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{end}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ to\ an\ end\ or\ halt\ "She\ ended\ their\ friendship\ when\ she\ found\ out\ that\ he\ had\ once\ been\ convicted\ of\ a\ crime"\ "The\ attack\ on\ Poland\ terminated\ the\ relatively\ peaceful\ period\ after\ WW\ I"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{365}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{trigger}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{release\ or\ pull\ the\ trigger\ on\ "Trigger\ a\ gun"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{323}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{involve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{engage\ as\ a\ participant\ "Dont\ involve\ me\ in\ your\ family\ affairs"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{309}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{begin}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ a\ beginning,\ of\ a\ temporal\ event\ "WW\ II\ began\ in\ 1939\ when\ Hitler\ marched\ into\ Poland"\ "The\ companys\ Asia\ tour\ begins\ next\ month"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{278}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{trigger}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{put\ in\ motion\ or\ move\ to\ act\ "trigger\ a\ reaction"\ "actuate\ the\ circuits"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{260}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce\ publicly\ or\ officially\ "The\ President\ declared\ war"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{236}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond\ favorably\ or\ as\ hoped\ "The\ cancer\ responded\ to\ the\ aggressive\ therapy"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{212}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{call}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{call\ a\ meeting\ invite\ or\ command\ to\ meet\ "The\ Wannsee\ Conference\ was\ called\ to\ discuss\ the\ Final\ Solution"\ "The\ new\ dean\ calls\ meetings\ every\ week"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{194}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{occur}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{come\ to\ pass\ "What\ is\ happening"\ "The\ meeting\ took\ place\ off\ without\ an\ incidence"\ "Nothing\ occurred\ that\ seemed\ important"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{194}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{sign}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{approve\ and\ express\ assent,\ responsibility,\ or\ obligation\ "All\ parties\ ratified\ the\ peace\ treaty"\ "Have\ you\ signed\ your\ contract\ yet"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{185}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{terminate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ to\ an\ end\ or\ halt\ "She\ ended\ their\ friendship\ when\ she\ found\ out\ that\ he\ had\ once\ been\ convicted\ of\ a\ crime"\ "The\ attack\ on\ Poland\ terminated\ the\ relatively\ peaceful\ period\ after\ WW\ I"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{178}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{begin}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{set\ in\ motion,\ cause\ to\ start\ "The\ U.S.\ started\ a\ war\ in\ the\ Middle\ East"\ "The\ Iraqis\ began\ hostilities"\ "begin\ a\ new\ chapter\ in\ your\ life"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{160}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{meet}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{come\ together\ "Ill\ probably\ see\ you\ at\ the\ meeting"\ "How\ nice\ to\ see\ you\ again"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{146}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ cause\ or\ order\ to\ be\ taken,\ directed,\ or\ transmitted\ to\ another\ place\ "He\ had\ sent\ the\ dispatches\ downtown\ to\ the\ proper\ people\ and\ had\ slept"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{145}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{occupy}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{march\ aggressively\ into\ anothers\ territory\ by\ military\ force\ for\ the\ purposes\ of\ conquest\ and\ occupation\ "Hitler\ invaded\ Poland\ on\ September\ 1,\ 1939"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{135}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{happen,\ occur,\ take\ place\ "I\ lost\ my\ wallet\ this\ was\ during\ the\ visit\ to\ my\ parents\ house"\ "There\ were\ two\ hundred\ people\ at\ his\ funeral"\ "There\ was\ a\ lot\ of\ noise\ in\ the\ kitchen"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{128}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{perceive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become\ conscious\ of\ "She\ finally\ perceived\ the\ futility\ of\ her\ protest"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{126}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{undergo\ a\ change\ or\ development\ "The\ water\ turned\ into\ ice"\ "Her\ former\ friend\ became\ her\ worst\ enemy"\ "He\ turned\ traitor"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{125}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{condemn}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ strong\ disapproval\ of\ "We\ condemn\ the\ racism\ in\ South\ Africa"\ "These\ ideas\ were\ reprobated"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{125}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ by\ force\ "Hitler\ took\ the\ Baltic\ Republics"\ "The\ army\ took\ the\ fort\ on\ the\ hill"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{124}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{escalate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{increase\ in\ extent\ or\ intensity\ "The\ Allies\ escalated\ the\ bombing"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{119}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reject}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{refuse\ to\ accept\ or\ acknowledge\ "I\ reject\ the\ idea\ of\ starting\ a\ war"\ "The\ journal\ rejected\ the\ students\ paper"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{117}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{react\ verbally\ "She\ didnt\ want\ to\ answer"\ "answer\ the\ question"\ "We\ answered\ that\ we\ would\ accept\ the\ invitation"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{116}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{demand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{request\ urgently\ and\ forcefully\ "The\ victims\ family\ is\ demanding\ compensation"\ "The\ boss\ demanded\ that\ he\ be\ fired\ immediately"\ "She\ demanded\ to\ see\ the\ manager"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{112}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ remain\ unmolested,\ undisturbed,\ or\ uninterrupted\ \ used\ only\ in\ infinitive\ form\ "let\ her\ be"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{111}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{agree}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ in\ accord\ be\ in\ agreement\ "We\ agreed\ on\ the\ terms\ of\ the\ settlement"\ "I\ cant\ agree\ with\ you"\ "I\ hold\ with\ those\ who\ say\ life\ is\ sacred"\ "Both\ philosophers\ concord\ on\ this\ point"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{110}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ in\ or\ establish\ communication\ with\ "Our\ advertisements\ reach\ millions"\ "He\ never\ contacted\ his\ children\ after\ he\ emigrated\ to\ Australia"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{106}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{withdraw}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pull\ back\ or\ move\ away\ or\ backward\ "The\ enemy\ withdrew"\ "The\ limo\ pulled\ away\ from\ the\ curb"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{105}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{blame\ for,\ make\ a\ claim\ of\ wrongdoing\ or\ misbehavior\ against\ "he\ charged\ the\ director\ with\ indifference"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{105}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{dispute}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ a\ disagreement\ over\ something\ "We\ quarreled\ over\ the\ question\ as\ to\ who\ discovered\ America"\ "These\ two\ fellows\ are\ always\ scrapping\ over\ something"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{105}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fight}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ engaged\ in\ a\ fight\ carry\ on\ a\ fight\ "the\ tribesmen\ fought\ each\ other"\ "Siblings\ are\ always\ fighting"\ "Militant\ groups\ are\ contending\ for\ control\ of\ the\ country"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{102}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue\ talking\ "I\ know\ its\ hard,\ he\ continued,\ but\ there\ is\ no\ choice"\ "carry\ onpretend\ we\ are\ not\ in\ the\ room"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{100}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{include}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{consider\ as\ part\ of\ something\ "I\ include\ you\ in\ the\ list\ of\ culprits"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{99}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{remain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ left\ of\ persons,\ questions,\ problems,\ results,\ evidence,\ etc.\ "There\ remains\ the\ question\ of\ who\ pulled\ the\ trigger"\ "Carter\ remains\ the\ only\ President\ in\ recent\ history\ under\ whose\ Presidency\ the\ U.S.\ did\ not\ fight\ a\ war"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{98}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{experience}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{undergo\ or\ live\ through\ a\ difficult\ experience\ "We\ had\ many\ trials\ to\ go\ through"\ "he\ saw\ action\ in\ Viet\ Nam"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{97}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attempt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ an\ effort\ or\ attempt\ "He\ tried\ to\ shake\ off\ his\ fears"\ "The\ infant\ had\ essayed\ a\ few\ wobbly\ steps"\ "The\ police\ attempted\ to\ stop\ the\ thief"\ "He\ sought\ to\ improve\ himself"\ "She\ always\ seeks\ to\ do\ good\ in\ the\ world"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{increase}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ bigger\ or\ more\ "The\ boss\ finally\ increased\ her\ salary"\ "The\ university\ increased\ the\ number\ of\ students\ it\ admitted"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{mediate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{act\ between\ parties\ with\ a\ view\ to\ reconciling\ differences\ "He\ interceded\ in\ the\ family\ dispute"\ "He\ mediated\ a\ settlement"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{94}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{threaten}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ utter\ intentions\ of\ injury\ or\ punishment\ against\ "He\ threatened\ me\ when\ I\ tried\ to\ call\ the\ police"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{93}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{request}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{inquire\ for\ information\ "I\ requested\ information\ from\ the\ secretary"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{92}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{withdraw}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ a\ retreat\ from\ an\ earlier\ commitment\ or\ activity\ "Well\ have\ to\ crawfish\ out\ from\ meeting\ with\ him"\ "He\ backed\ out\ of\ his\ earlier\ promise"\ "The\ aggressive\ investment\ company\ pulled\ in\ its\ horns"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{91}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stop\ dealing\ with\ "hold\ all\ calls\ to\ the\ Presidents\ office\ while\ he\ is\ in\ a\ meeting"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{90}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{invade}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{march\ aggressively\ into\ anothers\ territory\ by\ military\ force\ for\ the\ purposes\ of\ conquest\ and\ occupation\ "Hitler\ invaded\ Poland\ on\ September\ 1,\ 1939"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{87}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ go\ somewhere\ "The\ explosion\ sent\ the\ car\ flying\ in\ the\ air"\ "She\ sent\ her\ children\ to\ camp"\ "He\ directed\ all\ his\ energies\ into\ his\ dissertation"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{86}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{launch}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{begin\ with\ vigor\ "He\ launched\ into\ a\ long\ diatribe"\ "She\ plunged\ into\ a\ dangerous\ adventure"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{84}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{report}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce\ as\ the\ result\ of\ an\ investigation\ or\ experience\ or\ finding\ "Dozens\ of\ incidents\ of\ wife\ beatings\ are\ reported\ daily\ in\ this\ city"\ "The\ team\ reported\ significant\ advances\ in\ their\ research"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{84}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{see}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{perceive\ or\ be\ contemporaneous\ with\ "We\ found\ Republicans\ winning\ the\ offices"\ "Youll\ see\ a\ lot\ of\ cheating\ in\ this\ school"\ "The\ 1960s\ saw\ the\ rebellion\ of\ the\ younger\ generation\ against\ established\ traditions"\ "I\ want\ to\ see\ results"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{81}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{perceive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ become\ aware\ of\ through\ the\ senses\ "I\ could\ perceive\ the\ ship\ coming\ over\ the\ horizon"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{80}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ an\ accusation\ against\ level\ a\ charge\ against\ "The\ neighbors\ accused\ the\ man\ of\ spousal\ abuse"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{77}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attack}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{launch\ an\ attack\ or\ assault\ on\ begin\ hostilities\ or\ start\ warfare\ with\ "Hitler\ attacked\ Poland\ on\ September\ 1,\ 1939\ and\ started\ World\ War\ II"\ "Serbian\ forces\ assailed\ Bosnian\ towns\ all\ week"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{77}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{dispatch}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill\ without\ delay\ "the\ traitor\ was\ dispatched\ by\ the\ conspirators"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{77}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{end}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{put\ an\ end\ to\ "The\ terrible\ news\ ended\ our\ hopes\ that\ he\ had\ survived"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{74}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{declare}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{announce\ publicly\ or\ officially\ "The\ President\ declared\ war"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{74}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{discuss}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{speak\ with\ others\ about\ something\ talk\ something\ over\ in\ detail\ have\ a\ discussion\ "We\ discussed\ our\ household\ budget"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{74}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ under\ surveillance\ "The\ police\ had\ been\ following\ him\ for\ weeks\ but\ they\ could\ not\ prove\ his\ involvement\ in\ the\ bombing"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{73}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{tend\ to\ or\ result\ in\ "This\ remark\ lead\ to\ further\ arguments\ among\ the\ guests"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{73}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{remain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stay\ behind\ "The\ smell\ stayed\ in\ the\ room"\ "The\ hostility\ remained\ long\ after\ they\ made\ up"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{72}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{propose}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{present\ for\ consideration,\ examination,\ criticism,\ etc.\ "He\ proposed\ a\ new\ plan\ for\ dealing\ with\ terrorism"\ "She\ proposed\ a\ new\ theory\ of\ relativity"\ "The\ candidate\ projects\ himself\ as\ a\ moderate\ and\ a\ reformer"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{72}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{recognize}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept\ someone\ to\ be\ what\ is\ claimed\ or\ accept\ his\ power\ and\ authority\ "The\ Crown\ Prince\ was\ acknowledged\ as\ the\ true\ heir\ to\ the\ throne"\ "We\ do\ not\ recognize\ your\ gods"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{70}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{capture}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ possession\ of\ by\ force,\ as\ after\ an\ invasion\ "the\ invaders\ seized\ the\ land\ and\ property\ of\ the\ inhabitants"\ "The\ army\ seized\ the\ town"\ "The\ militia\ captured\ the\ castle"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{70}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deny}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deny\ formally\ an\ allegation\ of\ fact\ by\ the\ opposing\ party\ in\ a\ legal\ suit}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{69}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{exist\ over\ a\ prolonged\ period\ of\ time\ "The\ bad\ weather\ continued\ for\ two\ more\ weeks"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{69}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{issue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ out\ an\ official\ document\ such\ as\ a\ warrant}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{67}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{declare}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{proclaim\ ones\ support,\ sympathy,\ or\ opinion\ for\ or\ against\ "His\ wife\ declared\ at\ once\ for\ moving\ to\ the\ West\ Coast"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{66}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stretch\ out\ over\ a\ distance,\ space,\ time,\ or\ scope\ run\ or\ extend\ between\ two\ points\ or\ beyond\ a\ certain\ point\ "Service\ runs\ all\ the\ way\ to\ Cranbury"\ "His\ knowledge\ doesnt\ go\ very\ far"\ "My\ memory\ extends\ back\ to\ my\ fourth\ year\ of\ life"\ "The\ facts\ extend\ beyond\ a\ consideration\ of\ her\ personal\ assets"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{65}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{renew}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reestablish\ on\ a\ new,\ usually\ improved,\ basis\ or\ make\ new\ or\ like\ new\ "We\ renewed\ our\ friendship\ after\ a\ hiatus\ of\ twenty\ years"\ "They\ renewed\ their\ membership"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{64}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{achieve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ gain\ with\ effort\ "she\ achieved\ her\ goal\ despite\ setbacks"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{63}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{provide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{determine\ what\ is\ to\ happen\ in\ certain\ contingencies,\ especially\ by\ including\ a\ proviso\ condition\ or\ stipulation\ "The\ will\ provides\ that\ each\ child\ should\ receive\ half\ of\ the\ money"\ "The\ Constitution\ provides\ for\ the\ right\ to\ free\ speech"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{61}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{appeal}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ a\ court\ case\ to\ a\ higher\ court\ for\ review\ "He\ was\ found\ guilty\ but\ appealed\ immediately"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{61}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{seek}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ an\ effort\ or\ attempt\ "He\ tried\ to\ shake\ off\ his\ fears"\ "The\ infant\ had\ essayed\ a\ few\ wobbly\ steps"\ "The\ police\ attempted\ to\ stop\ the\ thief"\ "He\ sought\ to\ improve\ himself"\ "She\ always\ seeks\ to\ do\ good\ in\ the\ world"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{60}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attack}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ the\ initiative\ and\ go\ on\ the\ offensive\ "The\ Serbs\ attacked\ the\ village\ at\ night"\ "The\ visiting\ team\ started\ to\ attack"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{60}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pass}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{go\ unchallenged\ be\ approved\ "The\ bill\ cleared\ the\ House"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{59}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{agree}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{achieve\ harmony\ of\ opinion,\ feeling,\ or\ purpose\ "No\ two\ of\ my\ colleagues\ would\ agree\ on\ whom\ to\ elect\ chairman"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{59}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{last}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{persist\ for\ a\ specified\ period\ of\ time\ "The\ bad\ weather\ lasted\ for\ three\ days"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{58}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{claim}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{demand\ as\ being\ ones\ due\ or\ property\ assert\ ones\ right\ or\ title\ to\ "He\ claimed\ his\ suitcases\ at\ the\ airline\ counter"\ "Mr.\ Smith\ claims\ special\ tax\ exemptions\ because\ he\ is\ a\ foreign\ resident"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{57}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{establish}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ about\ "The\ trompe\ loeilillusion\ establishes\ depth"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{57}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{inform}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impart\ knowledge\ of\ some\ fact,\ state\ of\ affairs,\ or\ event\ to\ "I\ informed\ him\ of\ his\ rights"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{57}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{warn}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{notify,\ usually\ in\ advance\ "I\ warned\ you\ that\ I\ would\ ask\ some\ difficult\ questions"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{56}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{offer}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{threaten\ to\ do\ something\ "I\ offered\ to\ leave\ the\ committee\ if\ they\ did\ not\ accept\ my\ proposal"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{56}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{restore}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ back\ into\ original\ existence,\ use,\ function,\ or\ position\ "restore\ law\ and\ order"\ "reestablish\ peace\ in\ the\ region"\ "restore\ the\ emperor\ to\ the\ throne"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{create}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ or\ cause\ to\ be\ or\ to\ become\ "make\ a\ mess\ in\ ones\ office"\ "create\ a\ furor"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{issue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{circulate\ or\ distribute\ or\ equip\ with\ "issue\ a\ new\ uniform\ to\ the\ children"\ "supply\ blankets\ for\ the\ beds"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{prevent}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ from\ happening\ or\ arising\ make\ impossible\ "My\ sense\ of\ tact\ forbids\ an\ honest\ answer"\ "Your\ role\ in\ the\ projects\ precludes\ your\ involvement\ in\ the\ competitive\ project"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{55}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{support}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{argue\ or\ speak\ in\ defense\ of\ "She\ supported\ the\ motion\ to\ strike"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cross}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{travel\ across\ or\ pass\ over\ "The\ caravan\ covered\ almost\ 100\ miles\ each\ day"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{include}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{allow\ participation\ in\ or\ the\ right\ to\ be\ part\ of\ permit\ to\ exercise\ the\ rights,\ functions,\ and\ responsibilities\ of\ "admit\ someone\ to\ the\ profession"\ "She\ was\ admitted\ to\ the\ New\ Jersey\ Bar"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{54}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{urge}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{push\ for\ something\ "The\ travel\ agent\ recommended\ strongly\ that\ we\ not\ travel\ on\ Thanksgiving\ Day"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{agree}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{consent\ or\ assent\ to\ a\ condition,\ or\ agree\ to\ do\ something\ "She\ agreed\ to\ all\ my\ conditions"\ "He\ agreed\ to\ leave\ her\ alone"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{do\ something\ repeatedly\ and\ showing\ no\ intention\ to\ stop\ "We\ continued\ our\ research\ into\ the\ cause\ of\ the\ illness"\ "The\ landlord\ persists\ in\ asking\ us\ to\ move"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{transfer\ "The\ spy\ sent\ the\ classified\ information\ off\ to\ Russia"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{53}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{support}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ behind\ approve\ of\ "He\ plumped\ for\ the\ Labor\ Party"\ "I\ backed\ Kennedy\ in\ 1960"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{erupt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{erupt\ or\ intensify\ suddenly\ "Unrest\ erupted\ in\ the\ country"\ "Tempers\ flared\ at\ the\ meeting"\ "The\ crowd\ irrupted\ into\ a\ burst\ of\ patriotism"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resolve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach\ a\ conclusion\ after\ a\ discussion\ or\ deliberation}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{52}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{view}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deem\ to\ be\ "She\ views\ this\ quite\ differently\ from\ me"\ "I\ consider\ her\ to\ be\ shallow"\ "I\ dont\ see\ the\ situation\ quite\ as\ negatively\ as\ you\ do"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{50}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{occur}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ be\ found\ to\ exist\ "sexism\ occurs\ in\ many\ workplaces"\ "precious\ stones\ occur\ in\ a\ large\ area\ in\ Brazil"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{50}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{admit\ into\ a\ group\ or\ community\ "accept\ students\ for\ graduate\ study"\ "Well\ have\ to\ vote\ on\ whether\ or\ not\ to\ admit\ a\ new\ member"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{claim}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ as\ an\ undesirable\ consequence\ of\ some\ event\ or\ state\ of\ affairs\ "the\ accident\ claimed\ three\ lives"\ "The\ hard\ work\ took\ its\ toll\ on\ her"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fade}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{disappear\ gradually\ "The\ pain\ eventually\ passed\ off"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{intervene}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{get\ involved,\ so\ as\ to\ alter\ or\ hinder\ an\ action,\ or\ through\ force\ or\ threat\ of\ force\ "Why\ did\ the\ U.S.\ not\ intervene\ earlier\ in\ WW\ II"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deprive\ of\ life\ "AIDS\ has\ killed\ thousands\ in\ Africa"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{note}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ mention\ of\ "She\ observed\ that\ his\ presentation\ took\ up\ too\ much\ time"\ "They\ noted\ that\ it\ was\ a\ fine\ day\ to\ go\ sailing"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{49}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{suspend}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stop\ a\ process\ or\ a\ habit\ by\ imposing\ a\ freeze\ on\ it\ "Suspend\ the\ aid\ to\ the\ wartorn\ country"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{deploy}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ distribute\ systematically\ or\ strategically\ "The\ U.S.\ deploys\ its\ weapons\ in\ the\ Middle\ East"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{overthrow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ the\ downfall\ of\ of\ rulers\ "The\ Czar\ was\ overthrown"\ "subvert\ the\ ruling\ class"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resolve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ to\ an\ end\ settle\ conclusively\ "The\ case\ was\ decided"\ "The\ judge\ decided\ the\ case\ in\ favor\ of\ the\ plaintiff"\ "The\ father\ adjudicated\ when\ the\ sons\ were\ quarreling\ over\ their\ inheritance"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{48}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{state}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ in\ words\ "He\ said\ that\ he\ wanted\ to\ marry\ her"\ "tell\ me\ what\ is\ bothering\ you"\ "state\ your\ opinion"\ "state\ your\ name"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{47}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ an\ affirmative\ reply\ to\ respond\ favorably\ to\ "I\ cannot\ accept\ your\ invitation"\ "I\ go\ for\ this\ resolution"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{47}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{form}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{develop\ into\ a\ distinctive\ entity\ "our\ plans\ began\ to\ take\ shape"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{47}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{use}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{avail\ oneself\ to\ "apply\ a\ principle"\ "practice\ a\ religion"\ "use\ care\ when\ going\ down\ the\ stairs"\ "use\ your\ common\ sense"\ "practice\ nonviolent\ resistance"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{allege}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{report\ or\ maintain\ "He\ alleged\ that\ he\ was\ the\ victim\ of\ a\ crime"\ "He\ said\ it\ was\ too\ late\ to\ intervene\ in\ the\ war"\ "The\ registrar\ says\ that\ I\ owe\ the\ school\ money"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{approve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ sanction\ to\ "I\ approve\ of\ his\ educational\ policies"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{arrive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach\ a\ destination\ arrive\ by\ movement\ or\ progress\ "She\ arrived\ home\ at\ 7\ oclock"\ "She\ didnt\ get\ to\ Chicago\ until\ after\ midnight"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{break}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ a\ rupture\ in\ the\ ranks\ of\ the\ enemy\ or\ ones\ own\ by\ quitting\ or\ fleeing\ "The\ ranks\ broke"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{46}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resume}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ up\ or\ begin\ anew\ "We\ resumed\ the\ negotiations"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{45}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{negotiate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{discuss\ the\ terms\ of\ an\ arrangement\ "They\ negotiated\ the\ sale\ of\ the\ house"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{45}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{protect}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{shield\ from\ danger,\ injury,\ destruction,\ or\ damage\ "Weatherbeater\ protects\ your\ roof\ from\ the\ rain"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{45}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{protract}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lengthen\ in\ time\ cause\ to\ be\ or\ last\ longer\ "We\ prolonged\ our\ stay"\ "She\ extended\ her\ visit\ by\ another\ day"\ "The\ meeting\ was\ drawn\ out\ until\ midnight"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{44}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ bring\ something\ about\ at\ a\ later\ time\ than\ "She\ followed\ dinner\ with\ a\ brandy"\ "He\ followed\ his\ lecture\ with\ a\ question\ and\ answer\ period"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{44}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{leave}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{remove\ oneself\ from\ an\ association\ with\ or\ participation\ in\ "She\ wants\ to\ leave"\ "The\ teenager\ left\ home"\ "She\ left\ her\ position\ with\ the\ Red\ Cross"\ "He\ left\ the\ Senate\ after\ two\ terms"\ "after\ 20\ years\ with\ the\ same\ company,\ she\ pulled\ up\ stakes"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{react\ favorably\ to\ consider\ right\ and\ proper\ "People\ did\ not\ accept\ atonal\ music\ at\ that\ time"\ "We\ accept\ the\ idea\ of\ universal\ health\ care"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{comply}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{act\ in\ accordance\ with\ someones\ rules,\ commands,\ or\ wishes\ "He\ complied\ with\ my\ instructions"\ "You\ must\ comply\ or\ else"\ "Follow\ these\ simple\ rules"\ "abide\ by\ the\ rules"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{generate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ into\ existence\ "The\ new\ manager\ generated\ a\ lot\ of\ problems"\ "The\ computer\ bug\ generated\ chaos\ in\ the\ office"\ "The\ computer\ generated\ this\ image"\ "The\ earthquake\ generated\ a\ tsunami"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{increase}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become\ bigger\ or\ greater\ in\ amount\ "The\ amount\ of\ work\ increased"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{initiate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{set\ in\ motion,\ start\ an\ event\ or\ prepare\ the\ way\ for\ "Hitlers\ attack\ on\ Poland\ led\ up\ to\ World\ War\ II"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{meet}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{experience\ as\ a\ reaction\ "My\ proposal\ met\ with\ much\ opposition"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{refuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{show\ unwillingness\ towards\ "he\ declined\ to\ join\ the\ group\ on\ a\ hike"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{43}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{succeed}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{attain\ success\ or\ reach\ a\ desired\ goal\ "The\ enterprise\ succeeded"\ "We\ succeeded\ in\ getting\ tickets\ to\ the\ show"\ "she\ struggled\ to\ overcome\ her\ handicap\ and\ won"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{come}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ received\ "News\ came\ in\ of\ the\ massacre\ in\ Rwanda"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{launch}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{propel\ with\ force\ "launch\ the\ space\ shuttle"\ "Launch\ a\ ship"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{move}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow\ a\ procedure\ or\ take\ a\ course\ "We\ should\ go\ farther\ in\ this\ matter"\ "She\ went\ through\ a\ lot\ of\ trouble"\ "go\ about\ the\ world\ in\ a\ certain\ manner"\ "Messages\ must\ go\ through\ diplomatic\ channels"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reaffirm}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{affirm\ once\ again\ "He\ reaffirmed\ his\ faith\ in\ the\ church"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{42}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ into\ consideration\ for\ exemplifying\ purposes\ "Take\ the\ case\ of\ China"\ "Consider\ the\ following\ case"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{adopt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ up\ the\ cause,\ ideology,\ practice,\ method,\ of\ someone\ and\ use\ it\ as\ ones\ own\ "She\ embraced\ Catholicism"\ "They\ adopted\ the\ Jewish\ faith"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{control}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{exercise\ authoritative\ control\ or\ power\ over\ "control\ the\ budget"\ "Command\ the\ military\ forces"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{proclaim}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{state\ or\ announce\ "I\ am\ not\ a\ Communist,\ he\ exclaimed"\ "The\ King\ will\ proclaim\ an\ amnesty"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{41}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{threaten}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pose\ a\ threat\ to\ present\ a\ danger\ to\ "The\ pollution\ is\ endangering\ the\ crops"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{40}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bomb}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{throw\ bombs\ at\ or\ attack\ with\ bombs\ "The\ Americans\ bombed\ Dresden"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{40}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{last}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue\ to\ live\ and\ avoid\ dying\ "We\ went\ without\ water\ and\ food\ for\ 3\ days"\ "These\ superstitions\ survive\ in\ the\ backwaters\ of\ America"\ "The\ race\ car\ driver\ lived\ through\ several\ very\ serious\ accidents"\ "how\ long\ can\ a\ person\ last\ without\ food\ and\ water"\ "One\ crash\ victim\ died,\ the\ other\ lived"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{39}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{implement}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{pursue\ to\ a\ conclusion\ or\ bring\ to\ a\ successful\ issue\ "Did\ he\ go\ through\ with\ the\ treatment"\ "He\ implemented\ a\ new\ economic\ plan"\ "She\ followed\ up\ his\ recommendations\ with\ a\ written\ proposal"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{38}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{strengthen}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ strong\ or\ stronger\ "This\ exercise\ will\ strengthen\ your\ upper\ body"\ "strengthen\ the\ relations\ between\ the\ two\ countries"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{consider}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{think\ about\ carefully\ weigh\ "They\ considered\ the\ possibility\ of\ a\ strike"\ "Turn\ the\ proposal\ over\ in\ your\ mind"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{decide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach,\ make,\ or\ come\ to\ a\ decision\ about\ something\ "We\ finally\ decided\ after\ lengthy\ deliberations"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{do}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{carry\ on\ or\ function\ "We\ could\ do\ with\ a\ little\ more\ help\ around\ here"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ move\ cause\ to\ be\ in\ a\ certain\ position\ or\ condition\ "He\ got\ his\ squad\ on\ the\ ball"\ "This\ let\ me\ in\ for\ a\ big\ surprise"\ "He\ got\ a\ girl\ into\ trouble"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{help}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{contribute\ to\ the\ furtherance\ of\ "This\ money\ will\ help\ the\ development\ of\ literacy\ in\ developing\ countries"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ and\ maintain\ control\ over,\ often\ by\ violent\ means\ "The\ dissatisfied\ students\ held\ the\ Presidents\ office\ for\ almost\ a\ week"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose\ and\ collect\ "levy\ a\ fine"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{indicate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ a\ signal\ for\ or\ a\ symptom\ of\ "These\ symptoms\ indicate\ a\ serious\ illness"\ "Her\ behavior\ points\ to\ a\ severe\ neurosis"\ "The\ economic\ indicators\ signal\ that\ the\ euro\ is\ undervalued"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{37}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{order}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{issue\ commands\ or\ orders\ for}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{36}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{enter\ or\ assume\ a\ certain\ state\ or\ condition\ "He\ became\ annoyed\ when\ he\ heard\ the\ bad\ news"\ "It\ must\ be\ getting\ more\ serious"\ "her\ face\ went\ red\ with\ anger"\ "She\ went\ into\ ecstasy"\ "Get\ going"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{36}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{participate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{become\ a\ participant\ be\ involved\ in\ "enter\ a\ race"\ "enter\ an\ agreement"\ "enter\ a\ drug\ treatment\ program"\ "enter\ negotiations"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{call}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{order,\ summon,\ or\ request\ for\ a\ specific\ duty\ or\ activity,\ work,\ role\ "He\ was\ already\ called\ 4\ times\ for\ jury\ duty"\ "They\ called\ him\ to\ active\ military\ duty"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ do\ cause\ to\ act\ in\ a\ specified\ manner\ "The\ ads\ induced\ me\ to\ buy\ a\ VCR"\ "My\ children\ finally\ got\ me\ to\ buy\ a\ computer"\ "My\ wife\ made\ me\ buy\ a\ new\ sofa"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{enmesh}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{entangle\ or\ catch\ in\ or\ as\ if\ in\ a\ mesh}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{be\ confronted\ with\ "What\ do\ we\ have\ here"\ "Now\ we\ have\ a\ fine\ mess"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{35}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ certain\ properties\ to\ something\ "get\ someone\ mad"\ "She\ made\ us\ look\ silly"\ "He\ made\ a\ fool\ of\ himself\ at\ the\ meeting"\ "Dont\ make\ this\ into\ a\ big\ deal"\ "This\ invention\ will\ make\ you\ a\ millionaire"\ "Make\ yourself\ clear"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{evacuate}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{move\ out\ of\ an\ unsafe\ location\ into\ safety\ "After\ the\ earthquake,\ residents\ were\ evacuated"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fire}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{drive\ out\ or\ away\ by\ or\ as\ if\ by\ fire\ "The\ soldiers\ were\ fired"\ "Surrender\ fires\ the\ cold\ skepticism"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{intend}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ in\ mind\ as\ a\ purpose\ "I\ mean\ no\ harm"\ "I\ only\ meant\ to\ help\ you"\ "She\ didnt\ think\ to\ harm\ me"\ "We\ thought\ to\ return\ early\ that\ night"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{lead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{preside\ over\ "John\ moderated\ the\ discussion"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{refuse}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{resist\ immunologically\ the\ introduction\ of\ some\ foreign\ tissue\ or\ organ\ "His\ body\ rejected\ the\ liver\ of\ the\ donor"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{34}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{warn}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{notify\ of\ danger,\ potential\ harm,\ or\ risk\ "The\ director\ warned\ him\ that\ he\ might\ be\ fired"\ "The\ doctor\ warned\ me\ about\ the\ dangers\ of\ smoking"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{bring\ into\ a\ different\ state\ "this\ may\ land\ you\ in\ jail"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{provide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{make\ a\ possibility\ or\ provide\ opportunity\ for\ permit\ to\ be\ attainable\ or\ cause\ to\ remain\ "This\ leaves\ no\ room\ for\ improvement"\ "The\ evidence\ allows\ only\ one\ conclusion"\ "allow\ for\ mistakes"\ "leave\ lots\ of\ time\ for\ the\ trip"\ "This\ procedure\ provides\ for\ lots\ of\ leeway"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{respond}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{show\ a\ response\ or\ a\ reaction\ to\ something}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{shoot}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill\ by\ firing\ a\ missile}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stop}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold\ back,\ as\ of\ a\ danger\ or\ an\ enemy\ check\ the\ expansion\ or\ influence\ of\ "Arrest\ the\ downward\ trend"\ "Check\ the\ growth\ of\ communism\ in\ South\ East\ Asia"\ "Contain\ the\ rebel\ movement"\ "Turn\ back\ the\ tide\ of\ communism"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{33}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{use}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{seek\ or\ achieve\ an\ end\ by\ using\ to\ ones\ advantage\ "She\ uses\ her\ influential\ friends\ to\ get\ jobs"\ "The\ presidents\ wife\ used\ her\ good\ connections"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accord}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{go\ together\ "The\ colors\ dont\ harmonize"\ "Their\ ideas\ concorded"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{broker}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{act\ as\ a\ broker}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{continue}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{span\ an\ interval\ of\ distance,\ space\ or\ time\ "The\ war\ extended\ over\ five\ years"\ "The\ period\ covered\ the\ turn\ of\ the\ century"\ "My\ land\ extends\ over\ the\ hills\ on\ the\ horizon"\ "This\ farm\ covers\ some\ 200\ acres"\ "The\ Archipelago\ continues\ for\ another\ 500\ miles"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fail}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fall\ short\ in\ what\ is\ expected\ "She\ failed\ in\ her\ obligations\ as\ a\ good\ daughterinlaw"\ "We\ must\ not\ fail\ his\ obligation\ to\ the\ victims\ of\ the\ Holocaust"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{flee}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{run\ away\ quickly\ "He\ threw\ down\ his\ gun\ and\ fled"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{involve}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{connect\ closely\ and\ often\ incriminatingly\ "This\ new\ ruling\ affects\ your\ business"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{32}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{maintain}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ in\ safety\ and\ protect\ from\ harm,\ decay,\ loss,\ or\ destruction\ "We\ preserve\ these\ archeological\ findings"\ "The\ old\ lady\ could\ not\ keep\ up\ the\ building"\ "children\ must\ be\ taught\ to\ conserve\ our\ national\ heritage"\ "The\ museum\ curator\ conserved\ the\ ancient\ manuscripts"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{adopt}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{choose\ and\ follow\ as\ of\ theories,\ ideas,\ policies,\ strategies\ or\ plans\ "She\ followed\ the\ feminist\ movement"\ "The\ candidate\ espouses\ Republican\ ideals"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{assist}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ help\ or\ assistance\ be\ of\ service\ "Everyone\ helped\ out\ during\ the\ earthquake"\ "Can\ you\ help\ me\ carry\ this\ table"\ "She\ never\ helps\ around\ the\ house"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{fail}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{disappoint,\ prove\ undependable\ to\ abandon,\ forsake\ "His\ sense\ of\ smell\ failed\ him\ this\ time"\ "His\ strength\ finally\ failed\ him"\ "His\ children\ failed\ him\ in\ the\ crisis"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{follow}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{accept\ and\ follow\ the\ leadership\ or\ command\ or\ guidance\ of\ "Lets\ follow\ our\ great\ helmsman"\ "She\ followed\ a\ guru\ for\ years"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{force}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{take\ by\ force\ "Storm\ the\ fort"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{hold}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{to\ close\ within\ bounds,\ or\ otherwise\ limit\ or\ deprive\ of\ free\ movement\ "This\ holds\ the\ local\ until\ the\ express\ passengers\ change\ trains"\ "About\ a\ dozen\ animals\ were\ held\ inside\ the\ stockade"\ "The\ illegal\ immigrants\ were\ held\ at\ a\ detention\ center"\ "The\ terrorists\ held\ the\ journalists\ for\ ransom"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{monitor}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{keep\ tabs\ on\ keep\ an\ eye\ on\ keep\ under\ surveillance\ "we\ are\ monitoring\ the\ air\ quality"\ "the\ police\ monitor\ the\ suspects\ moves"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{move}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{change\ location\ move,\ travel,\ or\ proceed,\ also\ metaphorically\ "How\ fast\ does\ your\ new\ car\ go"\ "We\ travelled\ from\ Rome\ to\ Naples\ by\ bus"\ "The\ policemen\ went\ from\ door\ to\ door\ looking\ for\ the\ suspect"\ "The\ soldiers\ moved\ towards\ the\ city\ in\ an\ attempt\ to\ take\ it\ before\ night\ fell"\ "news\ travelled\ fast"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{order}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{give\ instructions\ to\ or\ direct\ somebody\ to\ do\ something\ with\ authority\ "I\ said\ to\ him\ to\ go\ home"\ "She\ ordered\ him\ to\ do\ the\ shopping"\ "The\ mother\ told\ the\ child\ to\ get\ dressed"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{31}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{receive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{receive\ a\ specified\ treatment\ abstract\ "These\ aspects\ of\ civilization\ do\ not\ find\ expression\ or\ receive\ an\ interpretation"\ "His\ movie\ received\ a\ good\ review"\ "I\ got\ nothing\ but\ trouble\ for\ my\ good\ intentions"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{engage}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{carry\ on\ wars,\ battles,\ or\ campaigns\ "Napoleon\ and\ Hitler\ waged\ war\ against\ all\ of\ Europe"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{send\ by\ rapid\ transport\ or\ special\ messenger\ service\ "She\ expressed\ the\ letter\ to\ Florida"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{impose\ something\ unpleasant\ "The\ principal\ visited\ his\ rage\ on\ the\ students"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{kill}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{mark\ for\ deletion,\ rub\ off,\ or\ erase\ "kill\ these\ lines\ in\ the\ Presidents\ speech"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{30}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{seek}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{try\ to\ locate\ or\ discover,\ or\ try\ to\ establish\ the\ existence\ of\ "The\ police\ are\ searching\ for\ clues"\ "They\ are\ searching\ for\ the\ missing\ man\ in\ the\ entire\ county"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{conclude}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{reach\ agreement\ on\ "They\ concluded\ an\ economic\ agreement"\ "We\ concluded\ a\ ceasefire"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{decide}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{cause\ to\ decide\ "This\ new\ development\ finally\ decided\ me"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{include}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{add\ as\ part\ of\ something\ else\ put\ in\ as\ part\ of\ a\ set,\ group,\ or\ category\ "We\ must\ include\ this\ chemical\ element\ in\ the\ group"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{plan}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ the\ will\ and\ intention\ to\ carry\ out\ some\ action\ "He\ plans\ to\ be\ in\ graduate\ school\ next\ year"\ "The\ rebels\ had\ planned\ turmoil\ and\ confusion"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{protest}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ opposition\ through\ action\ or\ words\ "dissent\ to\ the\ laws\ of\ the\ country"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{receive}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{express\ willingness\ to\ have\ in\ ones\ home\ or\ environs\ "The\ community\ warmly\ received\ the\ refugees"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{regard}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{connect\ closely\ and\ often\ incriminatingly\ "This\ new\ ruling\ affects\ your\ business"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{say}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{report\ or\ maintain\ "He\ alleged\ that\ he\ was\ the\ victim\ of\ a\ crime"\ "He\ said\ it\ was\ too\ late\ to\ intervene\ in\ the\ war"\ "The\ registrar\ says\ that\ I\ owe\ the\ school\ money"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{stand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{have\ or\ maintain\ a\ position\ or\ stand\ on\ an\ issue\ "Where\ do\ you\ stand\ on\ the\ War"}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedleft}p{\dimexpr 0.3in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{29}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{undermine}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 6in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{6}{6}\selectfont{\textcolor[HTML]{000000}{destroy\ property\ or\ hinder\ normal\ operations\ "The\ Resistance\ sabotaged\ railroad\ operations\ during\ the\ war"}}} \\
-
-\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{uses}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lemma}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Gloss}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{uses}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lemma}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Gloss}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endhead
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{381}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{end}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ to\ an\ end\ or\ halt\ "She\ ended\ their\ friendship\ when\ she\ found\ out\ that\ he\ had\ once\ been\ convicted\ of\ a\ crime"\ "The\ attack\ on\ Poland\ terminated\ the\ relatively\ peaceful\ period\ after\ WW\ I"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{365}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{trigger}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{release\ or\ pull\ the\ trigger\ on\ "Trigger\ a\ gun"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{323}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{involve}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{engage\ as\ a\ participant\ "Dont\ involve\ me\ in\ your\ family\ affairs"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{309}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{begin}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have\ a\ beginning,\ of\ a\ temporal\ event\ "WW\ II\ began\ in\ 1939\ when\ Hitler\ marched\ into\ Poland"\ "The\ companys\ Asia\ tour\ begins\ next\ month"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{278}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{trigger}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{put\ in\ motion\ or\ move\ to\ act\ "trigger\ a\ reaction"\ "actuate\ the\ circuits"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{260}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{announce}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{announce\ publicly\ or\ officially\ "The\ President\ declared\ war"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{236}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{respond}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{respond\ favorably\ or\ as\ hoped\ "The\ cancer\ responded\ to\ the\ aggressive\ therapy"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{212}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{call}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{call\ a\ meeting\ invite\ or\ command\ to\ meet\ "The\ Wannsee\ Conference\ was\ called\ to\ discuss\ the\ Final\ Solution"\ "The\ new\ dean\ calls\ meetings\ every\ week"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{194}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{occur}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{come\ to\ pass\ "What\ is\ happening"\ "The\ meeting\ took\ place\ off\ without\ an\ incidence"\ "Nothing\ occurred\ that\ seemed\ important"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{194}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{sign}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{approve\ and\ express\ assent,\ responsibility,\ or\ obligation\ "All\ parties\ ratified\ the\ peace\ treaty"\ "Have\ you\ signed\ your\ contract\ yet"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{185}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{terminate}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ to\ an\ end\ or\ halt\ "She\ ended\ their\ friendship\ when\ she\ found\ out\ that\ he\ had\ once\ been\ convicted\ of\ a\ crime"\ "The\ attack\ on\ Poland\ terminated\ the\ relatively\ peaceful\ period\ after\ WW\ I"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{178}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{begin}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{set\ in\ motion,\ cause\ to\ start\ "The\ U.S.\ started\ a\ war\ in\ the\ Middle\ East"\ "The\ Iraqis\ began\ hostilities"\ "begin\ a\ new\ chapter\ in\ your\ life"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{160}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{meet}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{come\ together\ "Ill\ probably\ see\ you\ at\ the\ meeting"\ "How\ nice\ to\ see\ you\ again"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{146}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{send}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ cause\ or\ order\ to\ be\ taken,\ directed,\ or\ transmitted\ to\ another\ place\ "He\ had\ sent\ the\ dispatches\ downtown\ to\ the\ proper\ people\ and\ had\ slept"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{145}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{occupy}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{march\ aggressively\ into\ anothers\ territory\ by\ military\ force\ for\ the\ purposes\ of\ conquest\ and\ occupation\ "Hitler\ invaded\ Poland\ on\ September\ 1,\ 1939"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{135}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{happen,\ occur,\ take\ place\ "I\ lost\ my\ wallet\ this\ was\ during\ the\ visit\ to\ my\ parents\ house"\ "There\ were\ two\ hundred\ people\ at\ his\ funeral"\ "There\ was\ a\ lot\ of\ noise\ in\ the\ kitchen"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{128}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{perceive}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{become\ conscious\ of\ "She\ finally\ perceived\ the\ futility\ of\ her\ protest"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{126}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{become}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{undergo\ a\ change\ or\ development\ "The\ water\ turned\ into\ ice"\ "Her\ former\ friend\ became\ her\ worst\ enemy"\ "He\ turned\ traitor"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{125}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{condemn}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{express\ strong\ disapproval\ of\ "We\ condemn\ the\ racism\ in\ South\ Africa"\ "These\ ideas\ were\ reprobated"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{125}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ by\ force\ "Hitler\ took\ the\ Baltic\ Republics"\ "The\ army\ took\ the\ fort\ on\ the\ hill"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{124}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{escalate}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{increase\ in\ extent\ or\ intensity\ "The\ Allies\ escalated\ the\ bombing"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{119}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reject}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{refuse\ to\ accept\ or\ acknowledge\ "I\ reject\ the\ idea\ of\ starting\ a\ war"\ "The\ journal\ rejected\ the\ students\ paper"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{117}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{respond}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{react\ verbally\ "She\ didnt\ want\ to\ answer"\ "answer\ the\ question"\ "We\ answered\ that\ we\ would\ accept\ the\ invitation"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{116}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{demand}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{request\ urgently\ and\ forcefully\ "The\ victims\ family\ is\ demanding\ compensation"\ "The\ boss\ demanded\ that\ he\ be\ fired\ immediately"\ "She\ demanded\ to\ see\ the\ manager"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{112}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ remain\ unmolested,\ undisturbed,\ or\ uninterrupted\ \ used\ only\ in\ infinitive\ form\ "let\ her\ be"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{111}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{agree}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ in\ accord\ be\ in\ agreement\ "We\ agreed\ on\ the\ terms\ of\ the\ settlement"\ "I\ cant\ agree\ with\ you"\ "I\ hold\ with\ those\ who\ say\ life\ is\ sacred"\ "Both\ philosophers\ concord\ on\ this\ point"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{110}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reach}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ in\ or\ establish\ communication\ with\ "Our\ advertisements\ reach\ millions"\ "He\ never\ contacted\ his\ children\ after\ he\ emigrated\ to\ Australia"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{106}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{withdraw}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{pull\ back\ or\ move\ away\ or\ backward\ "The\ enemy\ withdrew"\ "The\ limo\ pulled\ away\ from\ the\ curb"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{105}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accuse}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{blame\ for,\ make\ a\ claim\ of\ wrongdoing\ or\ misbehavior\ against\ "he\ charged\ the\ director\ with\ indifference"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{105}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{dispute}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have\ a\ disagreement\ over\ something\ "We\ quarreled\ over\ the\ question\ as\ to\ who\ discovered\ America"\ "These\ two\ fellows\ are\ always\ scrapping\ over\ something"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{105}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{fight}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ engaged\ in\ a\ fight\ carry\ on\ a\ fight\ "the\ tribesmen\ fought\ each\ other"\ "Siblings\ are\ always\ fighting"\ "Militant\ groups\ are\ contending\ for\ control\ of\ the\ country"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{102}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{continue}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{continue\ talking\ "I\ know\ its\ hard,\ he\ continued,\ but\ there\ is\ no\ choice"\ "carry\ onpretend\ we\ are\ not\ in\ the\ room"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{100}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{include}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{consider\ as\ part\ of\ something\ "I\ include\ you\ in\ the\ list\ of\ culprits"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{99}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{remain}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ left\ of\ persons,\ questions,\ problems,\ results,\ evidence,\ etc.\ "There\ remains\ the\ question\ of\ who\ pulled\ the\ trigger"\ "Carter\ remains\ the\ only\ President\ in\ recent\ history\ under\ whose\ Presidency\ the\ U.S.\ did\ not\ fight\ a\ war"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{98}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{experience}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{undergo\ or\ live\ through\ a\ difficult\ experience\ "We\ had\ many\ trials\ to\ go\ through"\ "he\ saw\ action\ in\ Viet\ Nam"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{97}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{attempt}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ an\ effort\ or\ attempt\ "He\ tried\ to\ shake\ off\ his\ fears"\ "The\ infant\ had\ essayed\ a\ few\ wobbly\ steps"\ "The\ police\ attempted\ to\ stop\ the\ thief"\ "He\ sought\ to\ improve\ himself"\ "She\ always\ seeks\ to\ do\ good\ in\ the\ world"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{94}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{increase}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ bigger\ or\ more\ "The\ boss\ finally\ increased\ her\ salary"\ "The\ university\ increased\ the\ number\ of\ students\ it\ admitted"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{94}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{mediate}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{act\ between\ parties\ with\ a\ view\ to\ reconciling\ differences\ "He\ interceded\ in\ the\ family\ dispute"\ "He\ mediated\ a\ settlement"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{94}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{threaten}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ utter\ intentions\ of\ injury\ or\ punishment\ against\ "He\ threatened\ me\ when\ I\ tried\ to\ call\ the\ police"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{93}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{request}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{inquire\ for\ information\ "I\ requested\ information\ from\ the\ secretary"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{92}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{withdraw}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ a\ retreat\ from\ an\ earlier\ commitment\ or\ activity\ "Well\ have\ to\ crawfish\ out\ from\ meeting\ with\ him"\ "He\ backed\ out\ of\ his\ earlier\ promise"\ "The\ aggressive\ investment\ company\ pulled\ in\ its\ horns"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{91}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{hold}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{stop\ dealing\ with\ "hold\ all\ calls\ to\ the\ Presidents\ office\ while\ he\ is\ in\ a\ meeting"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{90}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{invade}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{march\ aggressively\ into\ anothers\ territory\ by\ military\ force\ for\ the\ purposes\ of\ conquest\ and\ occupation\ "Hitler\ invaded\ Poland\ on\ September\ 1,\ 1939"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{87}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{send}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cause\ to\ go\ somewhere\ "The\ explosion\ sent\ the\ car\ flying\ in\ the\ air"\ "She\ sent\ her\ children\ to\ camp"\ "He\ directed\ all\ his\ energies\ into\ his\ dissertation"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{86}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{launch}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{begin\ with\ vigor\ "He\ launched\ into\ a\ long\ diatribe"\ "She\ plunged\ into\ a\ dangerous\ adventure"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{84}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{report}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{announce\ as\ the\ result\ of\ an\ investigation\ or\ experience\ or\ finding\ "Dozens\ of\ incidents\ of\ wife\ beatings\ are\ reported\ daily\ in\ this\ city"\ "The\ team\ reported\ significant\ advances\ in\ their\ research"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{84}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{see}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{perceive\ or\ be\ contemporaneous\ with\ "We\ found\ Republicans\ winning\ the\ offices"\ "Youll\ see\ a\ lot\ of\ cheating\ in\ this\ school"\ "The\ 1960s\ saw\ the\ rebellion\ of\ the\ younger\ generation\ against\ established\ traditions"\ "I\ want\ to\ see\ results"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{81}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{perceive}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ become\ aware\ of\ through\ the\ senses\ "I\ could\ perceive\ the\ ship\ coming\ over\ the\ horizon"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{80}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accuse}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ an\ accusation\ against\ level\ a\ charge\ against\ "The\ neighbors\ accused\ the\ man\ of\ spousal\ abuse"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{77}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{attack}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{launch\ an\ attack\ or\ assault\ on\ begin\ hostilities\ or\ start\ warfare\ with\ "Hitler\ attacked\ Poland\ on\ September\ 1,\ 1939\ and\ started\ World\ War\ II"\ "Serbian\ forces\ assailed\ Bosnian\ towns\ all\ week"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{77}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{dispatch}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{kill\ without\ delay\ "the\ traitor\ was\ dispatched\ by\ the\ conspirators"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{77}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{end}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{put\ an\ end\ to\ "The\ terrible\ news\ ended\ our\ hopes\ that\ he\ had\ survived"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{74}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{declare}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{announce\ publicly\ or\ officially\ "The\ President\ declared\ war"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{74}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{discuss}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{speak\ with\ others\ about\ something\ talk\ something\ over\ in\ detail\ have\ a\ discussion\ "We\ discussed\ our\ household\ budget"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{74}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{follow}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{keep\ under\ surveillance\ "The\ police\ had\ been\ following\ him\ for\ weeks\ but\ they\ could\ not\ prove\ his\ involvement\ in\ the\ bombing"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{73}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{lead}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{tend\ to\ or\ result\ in\ "This\ remark\ lead\ to\ further\ arguments\ among\ the\ guests"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{73}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{remain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{stay\ behind\ "The\ smell\ stayed\ in\ the\ room"\ "The\ hostility\ remained\ long\ after\ they\ made\ up"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{72}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{propose}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{present\ for\ consideration,\ examination,\ criticism,\ etc.\ "He\ proposed\ a\ new\ plan\ for\ dealing\ with\ terrorism"\ "She\ proposed\ a\ new\ theory\ of\ relativity"\ "The\ candidate\ projects\ himself\ as\ a\ moderate\ and\ a\ reformer"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{72}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{recognize}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accept\ someone\ to\ be\ what\ is\ claimed\ or\ accept\ his\ power\ and\ authority\ "The\ Crown\ Prince\ was\ acknowledged\ as\ the\ true\ heir\ to\ the\ throne"\ "We\ do\ not\ recognize\ your\ gods"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{70}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{capture}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ possession\ of\ by\ force,\ as\ after\ an\ invasion\ "the\ invaders\ seized\ the\ land\ and\ property\ of\ the\ inhabitants"\ "The\ army\ seized\ the\ town"\ "The\ militia\ captured\ the\ castle"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{70}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{deny}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{deny\ formally\ an\ allegation\ of\ fact\ by\ the\ opposing\ party\ in\ a\ legal\ suit}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{69}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{continue}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{exist\ over\ a\ prolonged\ period\ of\ time\ "The\ bad\ weather\ continued\ for\ two\ more\ weeks"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{69}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{issue}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ out\ an\ official\ document\ such\ as\ a\ warrant}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{67}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{declare}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{proclaim\ ones\ support,\ sympathy,\ or\ opinion\ for\ or\ against\ "His\ wife\ declared\ at\ once\ for\ moving\ to\ the\ West\ Coast"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{66}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{lead}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{stretch\ out\ over\ a\ distance,\ space,\ time,\ or\ scope\ run\ or\ extend\ between\ two\ points\ or\ beyond\ a\ certain\ point\ "Service\ runs\ all\ the\ way\ to\ Cranbury"\ "His\ knowledge\ doesnt\ go\ very\ far"\ "My\ memory\ extends\ back\ to\ my\ fourth\ year\ of\ life"\ "The\ facts\ extend\ beyond\ a\ consideration\ of\ her\ personal\ assets"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{65}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{renew}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reestablish\ on\ a\ new,\ usually\ improved,\ basis\ or\ make\ new\ or\ like\ new\ "We\ renewed\ our\ friendship\ after\ a\ hiatus\ of\ twenty\ years"\ "They\ renewed\ their\ membership"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{64}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{achieve}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ gain\ with\ effort\ "she\ achieved\ her\ goal\ despite\ setbacks"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{63}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{provide}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{determine\ what\ is\ to\ happen\ in\ certain\ contingencies,\ especially\ by\ including\ a\ proviso\ condition\ or\ stipulation\ "The\ will\ provides\ that\ each\ child\ should\ receive\ half\ of\ the\ money"\ "The\ Constitution\ provides\ for\ the\ right\ to\ free\ speech"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{61}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{appeal}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ a\ court\ case\ to\ a\ higher\ court\ for\ review\ "He\ was\ found\ guilty\ but\ appealed\ immediately"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{61}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{seek}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ an\ effort\ or\ attempt\ "He\ tried\ to\ shake\ off\ his\ fears"\ "The\ infant\ had\ essayed\ a\ few\ wobbly\ steps"\ "The\ police\ attempted\ to\ stop\ the\ thief"\ "He\ sought\ to\ improve\ himself"\ "She\ always\ seeks\ to\ do\ good\ in\ the\ world"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{60}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{attack}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ the\ initiative\ and\ go\ on\ the\ offensive\ "The\ Serbs\ attacked\ the\ village\ at\ night"\ "The\ visiting\ team\ started\ to\ attack"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{60}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{pass}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{go\ unchallenged\ be\ approved\ "The\ bill\ cleared\ the\ House"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{59}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{agree}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{achieve\ harmony\ of\ opinion,\ feeling,\ or\ purpose\ "No\ two\ of\ my\ colleagues\ would\ agree\ on\ whom\ to\ elect\ chairman"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{59}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{last}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{persist\ for\ a\ specified\ period\ of\ time\ "The\ bad\ weather\ lasted\ for\ three\ days"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{58}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{claim}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{demand\ as\ being\ ones\ due\ or\ property\ assert\ ones\ right\ or\ title\ to\ "He\ claimed\ his\ suitcases\ at\ the\ airline\ counter"\ "Mr.\ Smith\ claims\ special\ tax\ exemptions\ because\ he\ is\ a\ foreign\ resident"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{57}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{establish}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ about\ "The\ trompe\ loeilillusion\ establishes\ depth"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{57}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{inform}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{impart\ knowledge\ of\ some\ fact,\ state\ of\ affairs,\ or\ event\ to\ "I\ informed\ him\ of\ his\ rights"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{57}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{warn}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{notify,\ usually\ in\ advance\ "I\ warned\ you\ that\ I\ would\ ask\ some\ difficult\ questions"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{56}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{offer}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{threaten\ to\ do\ something\ "I\ offered\ to\ leave\ the\ committee\ if\ they\ did\ not\ accept\ my\ proposal"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{56}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{restore}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ back\ into\ original\ existence,\ use,\ function,\ or\ position\ "restore\ law\ and\ order"\ "reestablish\ peace\ in\ the\ region"\ "restore\ the\ emperor\ to\ the\ throne"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{55}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{create}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ or\ cause\ to\ be\ or\ to\ become\ "make\ a\ mess\ in\ ones\ office"\ "create\ a\ furor"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{55}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{issue}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{circulate\ or\ distribute\ or\ equip\ with\ "issue\ a\ new\ uniform\ to\ the\ children"\ "supply\ blankets\ for\ the\ beds"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{55}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{prevent}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{keep\ from\ happening\ or\ arising\ make\ impossible\ "My\ sense\ of\ tact\ forbids\ an\ honest\ answer"\ "Your\ role\ in\ the\ projects\ precludes\ your\ involvement\ in\ the\ competitive\ project"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{55}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{support}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{argue\ or\ speak\ in\ defense\ of\ "She\ supported\ the\ motion\ to\ strike"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{54}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cross}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{travel\ across\ or\ pass\ over\ "The\ caravan\ covered\ almost\ 100\ miles\ each\ day"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{54}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{include}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{allow\ participation\ in\ or\ the\ right\ to\ be\ part\ of\ permit\ to\ exercise\ the\ rights,\ functions,\ and\ responsibilities\ of\ "admit\ someone\ to\ the\ profession"\ "She\ was\ admitted\ to\ the\ New\ Jersey\ Bar"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{54}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{urge}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{push\ for\ something\ "The\ travel\ agent\ recommended\ strongly\ that\ we\ not\ travel\ on\ Thanksgiving\ Day"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{53}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{agree}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{consent\ or\ assent\ to\ a\ condition,\ or\ agree\ to\ do\ something\ "She\ agreed\ to\ all\ my\ conditions"\ "He\ agreed\ to\ leave\ her\ alone"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{53}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{continue}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{do\ something\ repeatedly\ and\ showing\ no\ intention\ to\ stop\ "We\ continued\ our\ research\ into\ the\ cause\ of\ the\ illness"\ "The\ landlord\ persists\ in\ asking\ us\ to\ move"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{53}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{send}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{transfer\ "The\ spy\ sent\ the\ classified\ information\ off\ to\ Russia"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{53}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{support}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ behind\ approve\ of\ "He\ plumped\ for\ the\ Labor\ Party"\ "I\ backed\ Kennedy\ in\ 1960"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{52}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{erupt}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{erupt\ or\ intensify\ suddenly\ "Unrest\ erupted\ in\ the\ country"\ "Tempers\ flared\ at\ the\ meeting"\ "The\ crowd\ irrupted\ into\ a\ burst\ of\ patriotism"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{52}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{resolve}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reach\ a\ conclusion\ after\ a\ discussion\ or\ deliberation}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{52}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{view}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{deem\ to\ be\ "She\ views\ this\ quite\ differently\ from\ me"\ "I\ consider\ her\ to\ be\ shallow"\ "I\ dont\ see\ the\ situation\ quite\ as\ negatively\ as\ you\ do"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{50}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{occur}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ be\ found\ to\ exist\ "sexism\ occurs\ in\ many\ workplaces"\ "precious\ stones\ occur\ in\ a\ large\ area\ in\ Brazil"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{50}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{admit\ into\ a\ group\ or\ community\ "accept\ students\ for\ graduate\ study"\ "Well\ have\ to\ vote\ on\ whether\ or\ not\ to\ admit\ a\ new\ member"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{49}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{claim}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ as\ an\ undesirable\ consequence\ of\ some\ event\ or\ state\ of\ affairs\ "the\ accident\ claimed\ three\ lives"\ "The\ hard\ work\ took\ its\ toll\ on\ her"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{49}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{fade}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{disappear\ gradually\ "The\ pain\ eventually\ passed\ off"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{49}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{intervene}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{get\ involved,\ so\ as\ to\ alter\ or\ hinder\ an\ action,\ or\ through\ force\ or\ threat\ of\ force\ "Why\ did\ the\ U.S.\ not\ intervene\ earlier\ in\ WW\ II"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{49}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{kill}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{deprive\ of\ life\ "AIDS\ has\ killed\ thousands\ in\ Africa"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{49}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{note}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ mention\ of\ "She\ observed\ that\ his\ presentation\ took\ up\ too\ much\ time"\ "They\ noted\ that\ it\ was\ a\ fine\ day\ to\ go\ sailing"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{49}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{suspend}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{stop\ a\ process\ or\ a\ habit\ by\ imposing\ a\ freeze\ on\ it\ "Suspend\ the\ aid\ to\ the\ wartorn\ country"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{48}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{deploy}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ distribute\ systematically\ or\ strategically\ "The\ U.S.\ deploys\ its\ weapons\ in\ the\ Middle\ East"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{48}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{overthrow}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cause\ the\ downfall\ of\ of\ rulers\ "The\ Czar\ was\ overthrown"\ "subvert\ the\ ruling\ class"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{48}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{resolve}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ to\ an\ end\ settle\ conclusively\ "The\ case\ was\ decided"\ "The\ judge\ decided\ the\ case\ in\ favor\ of\ the\ plaintiff"\ "The\ father\ adjudicated\ when\ the\ sons\ were\ quarreling\ over\ their\ inheritance"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{48}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{state}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{express\ in\ words\ "He\ said\ that\ he\ wanted\ to\ marry\ her"\ "tell\ me\ what\ is\ bothering\ you"\ "state\ your\ opinion"\ "state\ your\ name"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{47}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accept}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{give\ an\ affirmative\ reply\ to\ respond\ favorably\ to\ "I\ cannot\ accept\ your\ invitation"\ "I\ go\ for\ this\ resolution"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{47}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{form}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{develop\ into\ a\ distinctive\ entity\ "our\ plans\ began\ to\ take\ shape"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{47}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{use}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{avail\ oneself\ to\ "apply\ a\ principle"\ "practice\ a\ religion"\ "use\ care\ when\ going\ down\ the\ stairs"\ "use\ your\ common\ sense"\ "practice\ nonviolent\ resistance"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{46}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{allege}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{report\ or\ maintain\ "He\ alleged\ that\ he\ was\ the\ victim\ of\ a\ crime"\ "He\ said\ it\ was\ too\ late\ to\ intervene\ in\ the\ war"\ "The\ registrar\ says\ that\ I\ owe\ the\ school\ money"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{46}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{approve}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{give\ sanction\ to\ "I\ approve\ of\ his\ educational\ policies"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{46}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{arrive}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reach\ a\ destination\ arrive\ by\ movement\ or\ progress\ "She\ arrived\ home\ at\ 7\ oclock"\ "She\ didnt\ get\ to\ Chicago\ until\ after\ midnight"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{46}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{break}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ a\ rupture\ in\ the\ ranks\ of\ the\ enemy\ or\ ones\ own\ by\ quitting\ or\ fleeing\ "The\ ranks\ broke"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{46}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{resume}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ up\ or\ begin\ anew\ "We\ resumed\ the\ negotiations"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{45}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{negotiate}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{discuss\ the\ terms\ of\ an\ arrangement\ "They\ negotiated\ the\ sale\ of\ the\ house"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{45}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{protect}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{shield\ from\ danger,\ injury,\ destruction,\ or\ damage\ "Weatherbeater\ protects\ your\ roof\ from\ the\ rain"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{45}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{protract}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{lengthen\ in\ time\ cause\ to\ be\ or\ last\ longer\ "We\ prolonged\ our\ stay"\ "She\ extended\ her\ visit\ by\ another\ day"\ "The\ meeting\ was\ drawn\ out\ until\ midnight"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{44}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{follow}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ bring\ something\ about\ at\ a\ later\ time\ than\ "She\ followed\ dinner\ with\ a\ brandy"\ "He\ followed\ his\ lecture\ with\ a\ question\ and\ answer\ period"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{44}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{leave}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{remove\ oneself\ from\ an\ association\ with\ or\ participation\ in\ "She\ wants\ to\ leave"\ "The\ teenager\ left\ home"\ "She\ left\ her\ position\ with\ the\ Red\ Cross"\ "He\ left\ the\ Senate\ after\ two\ terms"\ "after\ 20\ years\ with\ the\ same\ company,\ she\ pulled\ up\ stakes"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accept}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{react\ favorably\ to\ consider\ right\ and\ proper\ "People\ did\ not\ accept\ atonal\ music\ at\ that\ time"\ "We\ accept\ the\ idea\ of\ universal\ health\ care"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{comply}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{act\ in\ accordance\ with\ someones\ rules,\ commands,\ or\ wishes\ "He\ complied\ with\ my\ instructions"\ "You\ must\ comply\ or\ else"\ "Follow\ these\ simple\ rules"\ "abide\ by\ the\ rules"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{generate}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ into\ existence\ "The\ new\ manager\ generated\ a\ lot\ of\ problems"\ "The\ computer\ bug\ generated\ chaos\ in\ the\ office"\ "The\ computer\ generated\ this\ image"\ "The\ earthquake\ generated\ a\ tsunami"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{increase}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{become\ bigger\ or\ greater\ in\ amount\ "The\ amount\ of\ work\ increased"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{initiate}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{set\ in\ motion,\ start\ an\ event\ or\ prepare\ the\ way\ for\ "Hitlers\ attack\ on\ Poland\ led\ up\ to\ World\ War\ II"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{meet}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{experience\ as\ a\ reaction\ "My\ proposal\ met\ with\ much\ opposition"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{refuse}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{show\ unwillingness\ towards\ "he\ declined\ to\ join\ the\ group\ on\ a\ hike"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{43}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{succeed}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{attain\ success\ or\ reach\ a\ desired\ goal\ "The\ enterprise\ succeeded"\ "We\ succeeded\ in\ getting\ tickets\ to\ the\ show"\ "she\ struggled\ to\ overcome\ her\ handicap\ and\ won"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{42}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{come}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ received\ "News\ came\ in\ of\ the\ massacre\ in\ Rwanda"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{42}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{launch}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{propel\ with\ force\ "launch\ the\ space\ shuttle"\ "Launch\ a\ ship"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{42}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{move}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{follow\ a\ procedure\ or\ take\ a\ course\ "We\ should\ go\ farther\ in\ this\ matter"\ "She\ went\ through\ a\ lot\ of\ trouble"\ "go\ about\ the\ world\ in\ a\ certain\ manner"\ "Messages\ must\ go\ through\ diplomatic\ channels"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{42}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reaffirm}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{affirm\ once\ again\ "He\ reaffirmed\ his\ faith\ in\ the\ church"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{42}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ into\ consideration\ for\ exemplifying\ purposes\ "Take\ the\ case\ of\ China"\ "Consider\ the\ following\ case"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{41}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{adopt}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ up\ the\ cause,\ ideology,\ practice,\ method,\ of\ someone\ and\ use\ it\ as\ ones\ own\ "She\ embraced\ Catholicism"\ "They\ adopted\ the\ Jewish\ faith"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{41}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{control}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{exercise\ authoritative\ control\ or\ power\ over\ "control\ the\ budget"\ "Command\ the\ military\ forces"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{41}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{proclaim}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{state\ or\ announce\ "I\ am\ not\ a\ Communist,\ he\ exclaimed"\ "The\ King\ will\ proclaim\ an\ amnesty"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{41}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{threaten}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{pose\ a\ threat\ to\ present\ a\ danger\ to\ "The\ pollution\ is\ endangering\ the\ crops"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{40}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bomb}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{throw\ bombs\ at\ or\ attack\ with\ bombs\ "The\ Americans\ bombed\ Dresden"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{40}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{last}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{continue\ to\ live\ and\ avoid\ dying\ "We\ went\ without\ water\ and\ food\ for\ 3\ days"\ "These\ superstitions\ survive\ in\ the\ backwaters\ of\ America"\ "The\ race\ car\ driver\ lived\ through\ several\ very\ serious\ accidents"\ "how\ long\ can\ a\ person\ last\ without\ food\ and\ water"\ "One\ crash\ victim\ died,\ the\ other\ lived"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{39}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{implement}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{pursue\ to\ a\ conclusion\ or\ bring\ to\ a\ successful\ issue\ "Did\ he\ go\ through\ with\ the\ treatment"\ "He\ implemented\ a\ new\ economic\ plan"\ "She\ followed\ up\ his\ recommendations\ with\ a\ written\ proposal"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{38}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{strengthen}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ strong\ or\ stronger\ "This\ exercise\ will\ strengthen\ your\ upper\ body"\ "strengthen\ the\ relations\ between\ the\ two\ countries"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{consider}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{think\ about\ carefully\ weigh\ "They\ considered\ the\ possibility\ of\ a\ strike"\ "Turn\ the\ proposal\ over\ in\ your\ mind"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{decide}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reach,\ make,\ or\ come\ to\ a\ decision\ about\ something\ "We\ finally\ decided\ after\ lengthy\ deliberations"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{do}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{carry\ on\ or\ function\ "We\ could\ do\ with\ a\ little\ more\ help\ around\ here"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cause\ to\ move\ cause\ to\ be\ in\ a\ certain\ position\ or\ condition\ "He\ got\ his\ squad\ on\ the\ ball"\ "This\ let\ me\ in\ for\ a\ big\ surprise"\ "He\ got\ a\ girl\ into\ trouble"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{help}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{contribute\ to\ the\ furtherance\ of\ "This\ money\ will\ help\ the\ development\ of\ literacy\ in\ developing\ countries"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{hold}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ and\ maintain\ control\ over,\ often\ by\ violent\ means\ "The\ dissatisfied\ students\ held\ the\ Presidents\ office\ for\ almost\ a\ week"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{impose}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{impose\ and\ collect\ "levy\ a\ fine"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{indicate}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ a\ signal\ for\ or\ a\ symptom\ of\ "These\ symptoms\ indicate\ a\ serious\ illness"\ "Her\ behavior\ points\ to\ a\ severe\ neurosis"\ "The\ economic\ indicators\ signal\ that\ the\ euro\ is\ undervalued"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{37}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{order}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{issue\ commands\ or\ orders\ for}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{36}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{become}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{enter\ or\ assume\ a\ certain\ state\ or\ condition\ "He\ became\ annoyed\ when\ he\ heard\ the\ bad\ news"\ "It\ must\ be\ getting\ more\ serious"\ "her\ face\ went\ red\ with\ anger"\ "She\ went\ into\ ecstasy"\ "Get\ going"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{36}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{participate}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{become\ a\ participant\ be\ involved\ in\ "enter\ a\ race"\ "enter\ an\ agreement"\ "enter\ a\ drug\ treatment\ program"\ "enter\ negotiations"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{35}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{call}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{order,\ summon,\ or\ request\ for\ a\ specific\ duty\ or\ activity,\ work,\ role\ "He\ was\ already\ called\ 4\ times\ for\ jury\ duty"\ "They\ called\ him\ to\ active\ military\ duty"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{35}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cause}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cause\ to\ do\ cause\ to\ act\ in\ a\ specified\ manner\ "The\ ads\ induced\ me\ to\ buy\ a\ VCR"\ "My\ children\ finally\ got\ me\ to\ buy\ a\ computer"\ "My\ wife\ made\ me\ buy\ a\ new\ sofa"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{35}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{enmesh}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{entangle\ or\ catch\ in\ or\ as\ if\ in\ a\ mesh}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{35}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{be\ confronted\ with\ "What\ do\ we\ have\ here"\ "Now\ we\ have\ a\ fine\ mess"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{35}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{give\ certain\ properties\ to\ something\ "get\ someone\ mad"\ "She\ made\ us\ look\ silly"\ "He\ made\ a\ fool\ of\ himself\ at\ the\ meeting"\ "Dont\ make\ this\ into\ a\ big\ deal"\ "This\ invention\ will\ make\ you\ a\ millionaire"\ "Make\ yourself\ clear"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{34}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{evacuate}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{move\ out\ of\ an\ unsafe\ location\ into\ safety\ "After\ the\ earthquake,\ residents\ were\ evacuated"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{34}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{fire}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{drive\ out\ or\ away\ by\ or\ as\ if\ by\ fire\ "The\ soldiers\ were\ fired"\ "Surrender\ fires\ the\ cold\ skepticism"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{34}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{intend}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have\ in\ mind\ as\ a\ purpose\ "I\ mean\ no\ harm"\ "I\ only\ meant\ to\ help\ you"\ "She\ didnt\ think\ to\ harm\ me"\ "We\ thought\ to\ return\ early\ that\ night"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{34}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{lead}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{preside\ over\ "John\ moderated\ the\ discussion"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{34}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{refuse}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{resist\ immunologically\ the\ introduction\ of\ some\ foreign\ tissue\ or\ organ\ "His\ body\ rejected\ the\ liver\ of\ the\ donor"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{34}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{warn}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{notify\ of\ danger,\ potential\ harm,\ or\ risk\ "The\ director\ warned\ him\ that\ he\ might\ be\ fired"\ "The\ doctor\ warned\ me\ about\ the\ dangers\ of\ smoking"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{33}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{bring\ into\ a\ different\ state\ "this\ may\ land\ you\ in\ jail"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{33}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{provide}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{make\ a\ possibility\ or\ provide\ opportunity\ for\ permit\ to\ be\ attainable\ or\ cause\ to\ remain\ "This\ leaves\ no\ room\ for\ improvement"\ "The\ evidence\ allows\ only\ one\ conclusion"\ "allow\ for\ mistakes"\ "leave\ lots\ of\ time\ for\ the\ trip"\ "This\ procedure\ provides\ for\ lots\ of\ leeway"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{33}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{respond}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{show\ a\ response\ or\ a\ reaction\ to\ something}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{33}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{shoot}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{kill\ by\ firing\ a\ missile}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{33}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{stop}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{hold\ back,\ as\ of\ a\ danger\ or\ an\ enemy\ check\ the\ expansion\ or\ influence\ of\ "Arrest\ the\ downward\ trend"\ "Check\ the\ growth\ of\ communism\ in\ South\ East\ Asia"\ "Contain\ the\ rebel\ movement"\ "Turn\ back\ the\ tide\ of\ communism"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{33}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{use}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{seek\ or\ achieve\ an\ end\ by\ using\ to\ ones\ advantage\ "She\ uses\ her\ influential\ friends\ to\ get\ jobs"\ "The\ presidents\ wife\ used\ her\ good\ connections"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accord}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{go\ together\ "The\ colors\ dont\ harmonize"\ "Their\ ideas\ concorded"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{broker}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{act\ as\ a\ broker}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{continue}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{span\ an\ interval\ of\ distance,\ space\ or\ time\ "The\ war\ extended\ over\ five\ years"\ "The\ period\ covered\ the\ turn\ of\ the\ century"\ "My\ land\ extends\ over\ the\ hills\ on\ the\ horizon"\ "This\ farm\ covers\ some\ 200\ acres"\ "The\ Archipelago\ continues\ for\ another\ 500\ miles"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{fail}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{fall\ short\ in\ what\ is\ expected\ "She\ failed\ in\ her\ obligations\ as\ a\ good\ daughterinlaw"\ "We\ must\ not\ fail\ his\ obligation\ to\ the\ victims\ of\ the\ Holocaust"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{flee}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{run\ away\ quickly\ "He\ threw\ down\ his\ gun\ and\ fled"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{involve}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{connect\ closely\ and\ often\ incriminatingly\ "This\ new\ ruling\ affects\ your\ business"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{maintain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{keep\ in\ safety\ and\ protect\ from\ harm,\ decay,\ loss,\ or\ destruction\ "We\ preserve\ these\ archeological\ findings"\ "The\ old\ lady\ could\ not\ keep\ up\ the\ building"\ "children\ must\ be\ taught\ to\ conserve\ our\ national\ heritage"\ "The\ museum\ curator\ conserved\ the\ ancient\ manuscripts"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{adopt}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{choose\ and\ follow\ as\ of\ theories,\ ideas,\ policies,\ strategies\ or\ plans\ "She\ followed\ the\ feminist\ movement"\ "The\ candidate\ espouses\ Republican\ ideals"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{assist}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{give\ help\ or\ assistance\ be\ of\ service\ "Everyone\ helped\ out\ during\ the\ earthquake"\ "Can\ you\ help\ me\ carry\ this\ table"\ "She\ never\ helps\ around\ the\ house"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{fail}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{disappoint,\ prove\ undependable\ to\ abandon,\ forsake\ "His\ sense\ of\ smell\ failed\ him\ this\ time"\ "His\ strength\ finally\ failed\ him"\ "His\ children\ failed\ him\ in\ the\ crisis"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{follow}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{accept\ and\ follow\ the\ leadership\ or\ command\ or\ guidance\ of\ "Lets\ follow\ our\ great\ helmsman"\ "She\ followed\ a\ guru\ for\ years"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{force}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{take\ by\ force\ "Storm\ the\ fort"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{hold}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{to\ close\ within\ bounds,\ or\ otherwise\ limit\ or\ deprive\ of\ free\ movement\ "This\ holds\ the\ local\ until\ the\ express\ passengers\ change\ trains"\ "About\ a\ dozen\ animals\ were\ held\ inside\ the\ stockade"\ "The\ illegal\ immigrants\ were\ held\ at\ a\ detention\ center"\ "The\ terrorists\ held\ the\ journalists\ for\ ransom"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{monitor}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{keep\ tabs\ on\ keep\ an\ eye\ on\ keep\ under\ surveillance\ "we\ are\ monitoring\ the\ air\ quality"\ "the\ police\ monitor\ the\ suspects\ moves"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{move}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{change\ location\ move,\ travel,\ or\ proceed,\ also\ metaphorically\ "How\ fast\ does\ your\ new\ car\ go"\ "We\ travelled\ from\ Rome\ to\ Naples\ by\ bus"\ "The\ policemen\ went\ from\ door\ to\ door\ looking\ for\ the\ suspect"\ "The\ soldiers\ moved\ towards\ the\ city\ in\ an\ attempt\ to\ take\ it\ before\ night\ fell"\ "news\ travelled\ fast"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{order}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{give\ instructions\ to\ or\ direct\ somebody\ to\ do\ something\ with\ authority\ "I\ said\ to\ him\ to\ go\ home"\ "She\ ordered\ him\ to\ do\ the\ shopping"\ "The\ mother\ told\ the\ child\ to\ get\ dressed"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{31}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{receive}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{receive\ a\ specified\ treatment\ abstract\ "These\ aspects\ of\ civilization\ do\ not\ find\ expression\ or\ receive\ an\ interpretation"\ "His\ movie\ received\ a\ good\ review"\ "I\ got\ nothing\ but\ trouble\ for\ my\ good\ intentions"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{30}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{engage}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{carry\ on\ wars,\ battles,\ or\ campaigns\ "Napoleon\ and\ Hitler\ waged\ war\ against\ all\ of\ Europe"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{30}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{express}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{send\ by\ rapid\ transport\ or\ special\ messenger\ service\ "She\ expressed\ the\ letter\ to\ Florida"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{30}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{impose}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{impose\ something\ unpleasant\ "The\ principal\ visited\ his\ rage\ on\ the\ students"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{30}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{kill}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{mark\ for\ deletion,\ rub\ off,\ or\ erase\ "kill\ these\ lines\ in\ the\ Presidents\ speech"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{30}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{seek}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{try\ to\ locate\ or\ discover,\ or\ try\ to\ establish\ the\ existence\ of\ "The\ police\ are\ searching\ for\ clues"\ "They\ are\ searching\ for\ the\ missing\ man\ in\ the\ entire\ county"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{conclude}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{reach\ agreement\ on\ "They\ concluded\ an\ economic\ agreement"\ "We\ concluded\ a\ ceasefire"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{decide}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{cause\ to\ decide\ "This\ new\ development\ finally\ decided\ me"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{include}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{add\ as\ part\ of\ something\ else\ put\ in\ as\ part\ of\ a\ set,\ group,\ or\ category\ "We\ must\ include\ this\ chemical\ element\ in\ the\ group"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{plan}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have\ the\ will\ and\ intention\ to\ carry\ out\ some\ action\ "He\ plans\ to\ be\ in\ graduate\ school\ next\ year"\ "The\ rebels\ had\ planned\ turmoil\ and\ confusion"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{protest}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{express\ opposition\ through\ action\ or\ words\ "dissent\ to\ the\ laws\ of\ the\ country"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{receive}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{express\ willingness\ to\ have\ in\ ones\ home\ or\ environs\ "The\ community\ warmly\ received\ the\ refugees"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{regard}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{connect\ closely\ and\ often\ incriminatingly\ "This\ new\ ruling\ affects\ your\ business"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{say}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{report\ or\ maintain\ "He\ alleged\ that\ he\ was\ the\ victim\ of\ a\ crime"\ "He\ said\ it\ was\ too\ late\ to\ intervene\ in\ the\ war"\ "The\ registrar\ says\ that\ I\ owe\ the\ school\ money"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{stand}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{have\ or\ maintain\ a\ position\ or\ stand\ on\ an\ issue\ "Where\ do\ you\ stand\ on\ the\ War"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\multicolumn{1}{>{\raggedleft}m{\dimexpr 0.3in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{29}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{undermine}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{destroy\ property\ or\ hinder\ normal\ operations\ "The\ Resistance\ sabotaged\ railroad\ operations\ during\ the\ war"}}} \\
+
+\noalign{\global\arrayrulewidth 0pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}
 
 \end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
 
@@
 
-\hphantom{em}
-
 \hypertarget{synthetic-narratives}{%
@@
 
-\hphantom{em}
+\doublespacing
 
@@
 
+\singlespacing
+
 Cosine Similarity \begin{equation}
@@
 \begin{figure}[H]
-\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
-\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
-\end{figure}
-
-\begin{figure}[H]
 \begin{adjustbox}{
@@
 \end{figure}
-\clearpage
 
@@
 \subsection{Crimea-Donbas Crisis Maps}\label{crimea-donbas-crisis-maps}}
+
+\begin{figure}[H]
+\caption{Crisis Map - Crimea-Donbas - ICBe \label{fig:p_471_icbe}}
+\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
+\end{figure}
 

### 2023-08-20 replication_paper/psrm_draft/ICBe_manuscript.Rmd
TLS R&R

@@
 We choose these datasets and models as they represent frequently used and reputable efforts to structure and describe historical events of interest to scholars of international politics.
-The first column starts with our contribution, ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+The first column starts with our contribution, ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013], and ACLED [@raleighIntroducingACLEDArmed2010].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010].
+We include episode-level datasets as they remain and common and trusted tool for analyzing international relations, and because ICBe is unique among event-level datasets as events are matched to crises and so can be aggregated to the episode level.
 There is imperfect overlap concerning their intended depth and scope of coverage; 'international crises' are similar, but not identical to, 'interstate wars' and 'militarized interstate disputes' which differ yet again from 'individual events of organized violence' and 'non-violent action'.
@@
 ```
-```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}
 
@@
       #set_table_properties(layout="autofit")  %>%
-      vline( i = 1, j = c(3,8), border = NULL, part = "header") %>%
+      vline( i = 1, j = c(3,10), border = NULL, part = "header") %>%
       vline( i = 1:(n), j = 1, border = NULL, part = "body")  %>%
-      vline( i = 1:(n), j = c(3,8), border = NULL, part = "body")  %>%
+      vline( i = 1:(n), j = c(3,10), border = NULL, part = "body")  %>%
 
@@
       flextable::width(j = 1, width=0.1)  %>%
-      flextable::width( j = 2, width=2) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
-      flextable::width( j = 3, width=1.6) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
-      flextable::width( j = (4):k, width=0.22) %>%
-      flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
+      flextable::width( j = 2, width=1.8) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
+      flextable::width( j = 3, width=1.5) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
+      flextable::width( j = (4):k, width=0.25) %>%
+      flextable::line_spacing( space = 1.0, part = "body") %>% #i=1:nrow(lit_review_alt),
       flextable::padding(padding = 0, part = "body") %>%
@@
 # litreview_ft_psrm %>% 
-#     #flextable::flextable_to_rmd()
+     #flextable::flextable_to_rmd()
 #     save_as_image(path=here::here("replication_paper", "psrm_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

### 2023-08-20 replication_paper/psrm_draft/ICBe_manuscript.tex
TLS R&R

--- 2023-08-16 replication_paper/psrm_draft/ICBe_manuscript.tex
@@
 2015); Terrier (Grant et al. 2017)), the Militarized Interstate Disputes
-Incidents dataset, and the UCDP-GED dataset (Davies, Pettersson, and
-Öberg 2022; Sundberg and Melander 2013).\footnote{Other related datasets
-  that insufficiently overlap ICBe's domain for comparison include BCOW
-  (Leng and Singer 1988), WEIS (McClelland 1978), CREON (Hermann 1984),
-  CASCON (Bloomfield and Moulton 1989), SHERFACS (Sherman 2000),
-  Real-Time Phoenix (Brandt et al. 2018), and COfEE (Balali, Asadpour,
-  and Jafari 2021) (see histories in Merritt (1994) and Schrodt and Hall
-  (2006)).} The final set of columns compares episode-level datasets
-beginning with the original ICB project (Brecher et al. 2021; Brecher
-and Wilkenfeld 1982; Beardsley et al. 2020); the Militarized Interstate
-Disputes dataset (Palmer et al. 2021; Gibler 2018), and the Correlates
-of War (Sarkees and Wayman 2010). There is imperfect overlap concerning
-their intended depth and scope of coverage; `international crises' are
-similar, but not identical to, `interstate wars' and `militarized
-interstate disputes' which differ yet again from `individual events of
-organized violence' and `non-violent action'. Even like-concepts require
-care in comparison, as an `aim' in ICBe is the same as in MIPS, but an
-`alert' in ICBe is not the same as an `alert' in MID. Definitions for
-each ICBe variable are provided in the codebook.
+Incidents dataset, the UCDP-GED dataset (Davies, Pettersson, and Öberg
+2022; Sundberg and Melander 2013), and ACLED (Raleigh et al.
+2010).\footnote{Other related datasets that insufficiently overlap
+  ICBe's domain for comparison include BCOW (Leng and Singer 1988), WEIS
+  (McClelland 1978), CREON (Hermann 1984), CASCON (Bloomfield and
+  Moulton 1989), SHERFACS (Sherman 2000), Real-Time Phoenix (Brandt et
+  al. 2018), and COfEE (Balali, Asadpour, and Jafari 2021) (see
+  histories in Merritt (1994) and Schrodt and Hall (2006)).} The final
+set of columns compares episode-level datasets beginning with the
+original ICB project (Brecher et al. 2021; Brecher and Wilkenfeld 1982;
+Beardsley et al. 2020); the Militarized Interstate Disputes dataset
+(Palmer et al. 2021; Gibler 2018), and the Correlates of War (Sarkees
+and Wayman 2010). We include episode-level datasets as they remain and
+common and trusted tool for analyzing international relations, and
+because ICBe is unique among event-level datasets as events are matched
+to crises and so can be aggregated to the episode level. There is
+imperfect overlap concerning their intended depth and scope of coverage;
+`international crises' are similar, but not identical to, `interstate
+wars' and `militarized interstate disputes' which differ yet again from
+`individual events of organized violence' and `non-violent action'. Even
+like-concepts require care in comparison, as an `aim' in ICBe is the
+same as in MIPS, but an `alert' in ICBe is not the same as an `alert' in
+MID.
+
+This comparison is not intended to fault existing data and models for
+not including every variable in ICBe's ontology, as some of these
+variables fall outside the scope of a particular dataset's intended
+purpose. Rather, it serves as an initial basis for identifying the
+heterogeneity in existing efforts to abstract and measure discrete
+historical events of interest and to provide theoretical justifications
+from existing research about what is included in our dataset's ontology
+and where ICBe's detail about historical events can be compared to the
+current state of the art.
 
@@
 
-\renewcommand*{\arraystretch}{0.75}
+\renewcommand*{\arraystretch}{1}
 
@@
 
-\begin{longtable}[c]{|p{0.10in}|p{2.00in}|p{1.60in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}|p{0.22in}}
+\begin{longtable}[c]{|p{0.10in}|p{1.80in}|p{1.50in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}|p{0.25in}}
 
@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ev}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Start}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1945}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1977}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1995}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1989}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1816}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{End}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2019}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2018}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2020}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2015}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2014}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{2007}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{N}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{32K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{8.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{28.4M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{17.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{128K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{5.9K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{1K}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{H}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Corpus}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{ICB}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mix}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{A}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fazal}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Spruyt}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Haffar}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Bush}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hadden}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{MishaliRam}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lacina}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2006)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{McNabb}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cochran}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Long}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carafano}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2014)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goertz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diehl}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Carter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Brecher}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wilkenfeld}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goldgeier}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Tetlock}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stein}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Russett}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sullivan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Ramsay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{O’Neill}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Zartman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Faure}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sechser}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{R.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Goemans,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gleditsch,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chiozza}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2009)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{J.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{M.}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Thyne}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Chenoweth,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hendrix,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hunter}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Eck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hultman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{LaFree}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Dugan}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Beardsley}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Gibler}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Owsiak,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cuttner,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Buck}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Mutual\ Cooperation\ or\ Directed\ Aid\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Yarhi-Milo,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lanoszka,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Cooper}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Lai}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Allen,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Flynn,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Martinez}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Machain}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Fortna}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2018)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Min}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Wayman}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2010)}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Reiter,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Stam,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Horowitz}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~|~~~~}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Frederick,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Hensel,}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{Macaulay}}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.22in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{3}\selectfont{}}} \\
-
-\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
-
-\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ACLED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endfirsthead \caption[]{Ontological\ coverage\ of\ ICBe\ versus\ existing\ State\ of\ the\ Art}\\
+
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Concept}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Literature}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICBe}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Phoenix}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Terrier}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICEWs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MID\ Incidents}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{UCDP-GED}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ACLED}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MIDs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{COW}}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}\endhead
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ev}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ep}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ep}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Start}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1945}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1977}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1995}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1993}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2015}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1997}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1918}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1816}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1816}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{End}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2019}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2018}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2020}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2010}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2022}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2023}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2017}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2014}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{2007}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{N}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{32K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{8.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{28.4M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{17.5M}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{9.6K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{128K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1M}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{5.9K}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{1K}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{H}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Corpus}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{ICB}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{News}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Mix}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Mix}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Date\ source\ (Event\ or\ Article)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Domain}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Location\ source\ (Event\ or\ Actor)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{E}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{A}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{States}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Fazal}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2011)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Spruyt}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(1996)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Subnational\ Actors}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Haffar}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{IGO/NGO}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Bush}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Hadden}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Players}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Civilians}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ben-Yehuda}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{MishaliRam}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2006)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Fatalities}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lacina}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2006)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{McNabb}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Cochran}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Long}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Force\ Size}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Carafano}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2014)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Goertz}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Diehl}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(1986)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Force\ Domain}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2019)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lindsay}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Gartzke}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2020)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Pieces}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Geography\ (location,\ territorial\ change)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Carter}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2010)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Alert\ (Start/End\ Crisis)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Brecher}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Wilkenfeld}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(1997)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Wishes\ (Desire/Fear)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Goldgeier}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Tetlock}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2001)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Evaluation\ (Victory/Defeat)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Stein}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Russett}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(1980)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Aims\ (Territory,\ Policy,\ Regime,\ Preemption)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Sullivan}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Think}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Awareness\ (Discover,\ Become\ Convinced)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Ramsay}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2017)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Yarhi-Milo}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2013)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{React\ to\ past\ event\ (Praise,\ Disapprove,\ Accept,\ Reject,\ Accuse)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{O’Neill}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Request\ future\ event\ (Appeal,\ Demand)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Zartman}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Faure}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2005)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Predict\ future\ event\ (Promise,\ Threaten,\ Express\ Intent,\ Offer\ Without\ Condition)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Sechser}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-4}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Say}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Predict\ with\ condition\ (Offer,\ Ultimatum)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{R.}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2002)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Government\ (Leadership/Institution\ Change,\ Coup,\ Assasination)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Goemans,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Gleditsch,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Chiozza}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2009)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{J.}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{M.}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Powell}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Thyne}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{By\ Civilians\ (Protest/Riot/Strike)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Chenoweth,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Hendrix,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Hunter}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2019)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Against\ Civilians\ (Terrorism,\ Domestic\ Rights,\ Mass\ Killing,\ Evacuate)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Eck}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Hultman}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2007)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{LaFree}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Dugan}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2007)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Diplomacy\ (Discussion,\ Meeting,\ Mediation,\ Break\ off\ negotiations,\ Withdraw/Expel\ Diplomats,\ Propoganda)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Beardsley}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2011)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Legal\ Agreements\ (Sign\ Agreement,\ Settle\ Dispute,\ Join\ War\ on\ Behalf\ of,\ Ally,\ Mutual\ Defense\ Pact,\ Open\ Border,\ Cede\ Territory,\ Allow\ Inspections,\ Political\ Succession,\ Leave\ Alliance,\ Terminate\ Treaty)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Gibler}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2004)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Owsiak,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Cuttner,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Buck}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2018)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Violate\ Agreement\ (Violate\ Terms\ of\ Agreement)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2003)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Mutual\ Cooperation\ (Economic\ cooperation\ or\ Aid,\ Military\ Cooperation,\ Intelligence\ Cooperation,\ Unspecified)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Leeds}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(1999)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-8}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Do\ -\ Unarmed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Directed\ Aid\ (General\ Political\ Support,\ Economic\ Aid,\ Humanitarian\ Aid,\ Military\ Aid,\ Intelligence\ Aid,\ Unspecified\ Aid)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Yarhi-Milo,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lanoszka,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Cooper}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Preparation\ (Alert,\ Mobilization,\ Fortify,\ Exercise,\ Weapons\ Test)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Lai}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2004)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Maneuver\ (Deployment,\ Show\ of\ Force,\ Blockade,\ No\ Fly\ Zone,\ Border\ Violation)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Allen,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Flynn,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Martinez}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Machain}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Combat\ (Battle/Clash,\ Attack,\ Invasion/Occupation,\ Bombard,\ Cease\ Fire,\ Retreat)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Fortna}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2018)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Min}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2021)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Strategic\ (Declare\ War,\ Join\ War,\ Continue\ Fighting,\ Surrender,\ End\ War,\ Withdraw\ from\ War,\ Switch\ Sides)}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Sarkees}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Wayman}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2010)}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Reiter,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Stam,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Horowitz}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2016)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+
+\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}m{\dimexpr 0.1in+0\tabcolsep}}{\multirow[c]{-5}{*}{\parbox{0.1in}{\centering \rotatebox[origin=c]{270}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Do\ -\ Armed}}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 1.8in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Autonomy\ (Assert\ Political\ Control\ Over,\ Assert\ Autonomy\ Against,\ Annex,\ Reduce\ Control\ Over,\ Decolonize)}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Frederick,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Hensel,}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{and}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{Macaulay}}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{\ }}\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{(2017)}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{✓}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.25in+0\tabcolsep}!{\color[HTML]{000000}\vrule width 2pt}}{\textcolor[HTML]{000000}{\fontsize{6}{6}\selectfont{}}} \\
+
+\noalign{\global\arrayrulewidth 2pt}\arrayrulecolor[HTML]{000000}
+
+\hhline{|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-|>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
 

### 2023-08-20 replication_data/rmd/02_format_and_clean.rmd
v1.1 first self contained hopefully
R&R

@@
 dictionary_actions  <- readxl::read_excel(target_file, sheet="actions") %>% dplyr::distinct() 
+dictionary_condition_actions  <- readxl::read_excel(target_file, sheet="condition_actions") %>% dplyr::distinct()
+
 dictionary_actors    <- readxl::read_excel(target_file, sheet="actors") %>% dplyr::select(crisno,value, value_qcode=value_normalized_wikidata_id, value_normalized=value_normalized_label) %>% dplyr::distinct() %>%
@@
 normalization_dictionaries <- bind_rows(dictionary_actions %>% rename(varname=variable, varname_normalized=variable_normalized),
+                                        dictionary_condition_actions %>% rename(varname=variable, varname_normalized=variable_normalized),
                                         dictionary_locations,
@@
 
-icb_long_spans_clean_normalized %>% saveRDS(paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
+icb_long_spans_clean_normalized %>% saveRDS(paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds"))
 

### 2023-08-20 replication_paper/psrm_draft/ICBe_manuscript.Rmd
R&R

@@
 icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))
+
 ```
@@
 The ICBe ontology follows a hierarchical design philosophy where a smaller number of significant decisions are made early on and then progressively refined into more specific details [@brustIntegratingDomainKnowledge2020].[^5] Each coder was instructed to first thoroughly read the full crisis narrative and then presented with a custom graphical user interface (GUI) (SI Appendix 2.1).
-Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or activity), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more specific and non-mutually exclusive activities.
+Coders then proceeded sentence by sentence, choosing the number of events (0-3) that occurred, the highest behavior (thought, speech, or action), a set of players, whether the means were primarily armed or unarmed, whether there was an increase or decrease in aggression (uncooperative/escalating or cooperative/de-escalating), and finally one or more specific and non-mutually exclusive activities.
 Some additional details were always collected (e.g.
@@
 antecedents to pronouns).
-We reviewed, standardized, and normalized where coders listed a behavior, actor, or location outside the ontology.[^6] We find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and 117 different behaviors.
+We reviewed, standardized, and normalized where coders listed a behavior, actor, or location outside the ontology.[^6]
 
@@
 Requiring sentence-tag matching may underestimate agreement but minimizes the inclusion of noise and allows for additional validation.
+Once filtered for agreement, we find `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("actor")) %>% pull(value_normalized) %>% unique() %>% length()` actors and `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("act_cooperative|interact_increasecoop|act_uncooperative|interact_decreasecoop|act_escalate|interact_escalate|act_deescalate|interact_deescalate|sayintkind|thinkkind")) %>% filter(grepl("[A-Za-z]", value_normalized)) %>% pull(value_normalized) %>% unique() %>% length()` different behaviors: `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("thinkkind")) %>% filter(grepl("[A-Za-z]", value_normalized)) %>% pull(value_normalized) %>% unique()  %>% length()` thought, `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("sayintkind")) %>% filter(grepl("[A-Za-z]", value_normalized)) %>% pull(value_normalized) %>% unique()  %>% length()` speech, and `r codings_long_agreement %>% filter(varname_normalized %>% str_detect("act_cooperative|interact_increasecoop|act_uncooperative|interact_decreasecoop|act_escalate|interact_escalate|act_deescalate|interact_deescalate")) %>% pull(value_normalized) %>% unique() %>% length()` actions.
 

### 2023-08-20 replication_paper/psrm_draft/ICBe_manuscript.tex
R&R

@@
 events (0-3) that occurred, the highest behavior (thought, speech, or
-activity), a set of players, whether the means were primarily armed or
+action), a set of players, whether the means were primarily armed or
 unarmed, whether there was an increase or decrease in aggression
@@
   \href{https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$}{ICBEventData}.}
-We find 472 actors and 117 different behaviors.
 
@@
 intercoder agreement and consensus, we temporarily disaggregate the unit
-of analysis to the Coder-Crisis-Sentence-Tag (n=993,740), where a tag is
+of analysis to the Coder-Crisis-Sentence-Tag (n=993,731), where a tag is
 any unique piece of information a coder can associate with a sentence
@@
 sentence-tag matching may underestimate agreement but minimizes the
-inclusion of noise and allows for additional validation.
+inclusion of noise and allows for additional validation. Once filtered
+for agreement, we find 472 actors and 119 different behaviors: 12
+thought, 13 speech, and 94 actions.
 

### 2023-11-20 replication_paper/psrm_draft/ICBe_manuscript.Rmd
AG rr 2 edits

@@
 
+[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
+
 This comparison is not intended to fault existing data and models for not including every variable in ICBe's ontology, as some of these variables fall outside the scope of a particular dataset's intended purpose.
 Rather, it serves as an initial basis for identifying the heterogeneity in existing efforts to abstract and measure discrete historical events of interest and to provide theoretical justifications from existing research about what is included in our dataset's ontology and where ICBe's detail about historical events can be compared to the current state of the art.
-
-[^3]: Other related datasets that insufficiently overlap ICBe's domain for comparison include BCOW [@lengMilitarizedInterstateCrises1988], WEIS [@mcclellandWorldEventInteraction1978], CREON [@hermannComparativeResearchEvents1984], CASCON [@bloomfieldCASCONIIIComputeraided1989], SHERFACS [@shermanSHERFACSCrossParadigmHierarchical2000], Real-Time Phoenix [@brandtPhoenixRealTimeEvent2018], and COfEE [@balaliCOfEEComprehensiveOntology2021] (see histories in @merrittMeasuringEventsInternational1994 and @schrodtTwentyYearsKansas2006).
 
@@
 Two other novel features of our data -- its re-programmamable coding and its inclusion of thought, speech, and action -- intersect to provide a unique contribution.
-No existing event data distinguishes thoughts, speeches, and actions and most are limited to just coding actions given they are the most readily observable and thus the full universe could at least theoretically be included.[^7] Yet, methods like archival work and expert interviews continue to improve identification of thoughts and speeches that help us understand the reasoning process underlying political decisions and what actually occurred behind the scenes.
-This is an improvement over the state of the art that omits these by design in allowing scholars to identify thoughts associated with things like crisis escalation as well as patterns of omission to be advanced in future work, but the modular nature of our coding means the inclusion of a non-random sample of thoughts and speeches is neither necessary nor does it have inevitable downstream effects on the rest of the coding in ways that produce unwanted bias.
+
+First, re-programmable coding means scholars can make modifications to the ontology we provide and re-run the code script to produce a modified dataset.
+For example, if thoughts and speech acts are immaterial for a particular research question, those higher-level categories can be modified in a way that does not produce inevitable downstream effects on the rest of the coding.
+This is necessary because unlike existing datasets where variable values are largely independent, the nested nature of the ICBe variables means filtering out speech acts also requires filtered out variables about the actors, locations, and timing of those speech acts.
+
+Second, no existing event data distinguishes thoughts, speeches, and actions.
+In fact, most only try to code actions and entirely omit thoughts and speech acts despite recognition of their importance in international politics [@smithInternationalCrisesDomestic1998].
+Scholars have opted against coding thoughts and speech acts because of a lack of confidence the full universe could be readily observed and consequently at least theoretically be included.[^7] But the perfect should not be the enemy of the good, and measurement challenges are only overcome after an initial attempt to estimate difficult to observe concepts of interest.
+The ICB narratives are one of the better sources for this endeavor due to the consistent use of high-quality primary source material that takes advantage of qualitative methods well-suited to identifying thoughts and speech acts like archival work and expert interviews.
+Important questions about potential bias remain like whether a thought was known at the time by those involved or only recorded long afterwards by historians, but data validation required there to be data to be validated.
+By design, existing datasets largely omit thoughts and speech acts and also treat the resulting dataset as the static product of hardwired coding decisions.
+In allowing scholars to identify actions, thoughts, and speech acts as distinct characteristics of international crises while also granting flexibility about the inclusion of a non-random sample of novel variables, our approach is a notable improvement over the state of the art.
 
@@
 Using natural language processing (fully described in SI Appendix 3.1), we identify details that appear across multiple accounts.
+A detail refers to the smallest textual unit (a word or n-gram) for which we can calculate similarity across corpora to identify whether sentences semantically refer to the same broader observed event [@narayanDontGiveMe2018].
 The more accounts that mention a detail, the more central it is to understanding the true historical episode.
@@
 With a sufficiently large and diverse corpus of documents, we can vary the context while holding the overall episode constant and see which details tend to be invariant to context.
+Sufficiently similar details were binned together and then summarized so they could be compared to the coding in ICBe.
 This presents a harder evaluation baseline than comparing ICBe's recall to just that of ICB since there are non-crisis aspects of these events that may be included in other narratives but are out of the scope of our data.

### 2023-11-20 replication_paper/psrm_draft/ICBe_manuscript.tex
AG rr 2 edits

@@
 
-\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
 
@@
 re-programmamable coding and its inclusion of thought, speech, and
-action -- intersect to provide a unique contribution. No existing event
-data distinguishes thoughts, speeches, and actions and most are limited
-to just coding actions given they are the most readily observable and
-thus the full universe could at least theoretically be
-included.\footnote{Even the coding of overt actions like MIDs is not
-  without contention (Gibler 2018).} Yet, methods like archival work and
-expert interviews continue to improve identification of thoughts and
-speeches that help us understand the reasoning process underlying
-political decisions and what actually occurred behind the scenes. This
-is an improvement over the state of the art that omits these by design
-in allowing scholars to identify thoughts associated with things like
-crisis escalation as well as patterns of omission to be advanced in
-future work, but the modular nature of our coding means the inclusion of
-a non-random sample of thoughts and speeches is neither necessary nor
-does it have inevitable downstream effects on the rest of the coding in
-ways that produce unwanted bias.
+action -- intersect to provide a unique contribution.
+
+First, re-programmable coding means scholars can make modifications to
+the ontology we provide and re-run the code script to produce a modified
+dataset. For example, if thoughts and speech acts are immaterial for a
+particular research question, those higher-level categories can be
+modified in a way that does not produce inevitable downstream effects on
+the rest of the coding. This is necessary because unlike existing
+datasets where variable values are largely independent, the nested
+nature of the ICBe variables means filtering out speech acts also
+requires filtered out variables about the actors, locations, and timing
+of those speech acts.
+
+Second, no existing event data distinguishes thoughts, speeches, and
+actions. In fact, most only try to code actions and entirely omit
+thoughts and speech acts despite recognition of their importance in
+international politics (Smith 1998). Scholars have opted against coding
+thoughts and speech acts because of a lack of confidence the full
+universe could be readily observed and consequently at least
+theoretically be included.\footnote{Even the coding of overt actions
+  like MIDs is not without contention (Gibler 2018).} But the perfect
+should not be the enemy of the good, and measurement challenges are only
+overcome after an initial attempt to estimate difficult to observe
+concepts of interest. The ICB narratives are one of the better sources
+for this endeavor due to the consistent use of high-quality primary
+source material that takes advantage of qualitative methods well-suited
+to identifying thoughts and speech acts like archival work and expert
+interviews. Important questions about potential bias remain like whether
+a thought was known at the time by those involved or only recorded long
+afterwards by historians, but data validation required there to be data
+to be validated. By design, existing datasets largely omit thoughts and
+speech acts and also treat the resulting dataset as the static product
+of hardwired coding decisions. In allowing scholars to identify actions,
+thoughts, and speech acts as distinct characteristics of international
+crises while also granting flexibility about the inclusion of a
+non-random sample of novel variables, our approach is a notable
+improvement over the state of the art.
 
@@
 Using natural language processing (fully described in SI Appendix 3.1),
-we identify details that appear across multiple accounts. The more
-accounts that mention a detail, the more central it is to understanding
-the true historical episode. The theoretical motivation is that authors
-face word limits which force them to pick and choose which details to
-include, and they choose details that serve the specific context of the
-document they are producing. With a sufficiently large and diverse
-corpus of documents, we can vary the context while holding the overall
-episode constant and see which details tend to be invariant to context.
-This presents a harder evaluation baseline than comparing ICBe's recall
-to just that of ICB since there are non-crisis aspects of these events
-that may be included in other narratives but are out of the scope of our
-data. For example, the nationalization of businesses in Cuba may be
-included as important context in the Cuban Missile Crisis in documents
-that do not focus on the crisis dimensions like ICB. Using this hard
-case, a recall measure of ICBe on the synthetic narratives thus serves
-as a way to evaluate the breadth of ICBe's ontology and potential
-application to non-crisis international events.
+we identify details that appear across multiple accounts. A detail
+refers to the smallest textual unit (a word or n-gram) for which we can
+calculate similarity across corpora to identify whether sentences
+semantically refer to the same broader observed event (Narayan, Cohen,
+and Lapata 2018). The more accounts that mention a detail, the more
+central it is to understanding the true historical episode. The
+theoretical motivation is that authors face word limits which force them
+to pick and choose which details to include, and they choose details
+that serve the specific context of the document they are producing. With
+a sufficiently large and diverse corpus of documents, we can vary the
+context while holding the overall episode constant and see which details
+tend to be invariant to context. Sufficiently similar details were
+binned together and then summarized so they could be compared to the
+coding in ICBe. This presents a harder evaluation baseline than
+comparing ICBe's recall to just that of ICB since there are non-crisis
+aspects of these events that may be included in other narratives but are
+out of the scope of our data. For example, the nationalization of
+businesses in Cuba may be included as important context in the Cuban
+Missile Crisis in documents that do not focus on the crisis dimensions
+like ICB. Using this hard case, a recall measure of ICBe on the
+synthetic narratives thus serves as a way to evaluate the breadth of
+ICBe's ontology and potential application to non-crisis international
+events.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-narayanDontGiveMe2018}{}}%
+Narayan, Shashi, Shay B Cohen, and Mirella Lapata. 2018. {``Don't Give
+Me the Details, Just the Summary! Topic-Aware Convolutional Neural
+Networks for Extreme Summarization.''} \emph{arXiv Preprint
+arXiv:1808.08745}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-oneillInternationalNegotiationConceptual2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-smithInternationalCrisesDomestic1998}{}}%
+Smith, Alastair. 1998. {``International {Crises} and {Domestic
+Politics}.''} \emph{American Political Science Review} 92 (3): 623--38.
+\url{https://doi.org/10.2307/2585485}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-spruytSovereignStateIts1996}{}}%

### 2023-11-20 replication_paper/psrm_draft/ICBe_manuscript.Rmd
fig 2 footnote future research

@@
 The two other dictionary systems ICEWs and Terrier have higher coverage, with ICEWs outperforming Terrier.
-Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.
+Importantly our corpus of ICB narratives has high recall of frequently mentioned details giving us confidence in how those summaries were constructed, and ICBe lags only slightly behind showing that it left little additional information on the table.[^10]
 
@@
 We see expanding the ontology to broader international phenomenon as a promising future implementation of our model.
+
+[^10]: Although Figure 2 focuses only on two crises, the synthetic narrative approach and recall comparison can, and should, be more broadly applied to all international crises in a way that could reveal systematic blindspots across datasets.
 
@@
 
-Figure 3 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^10] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
-If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the right-hand side.[^11]
-
-[^10]: We preprocess sentences to replace named entities with a generic Entity token.
-
-[^11]: Hierarchical clustering on cosine similarity and with Ward's method.
+Figure 3 shows the location of every sentence from the ICBe corpus in semantic space as embedded using the same large language model as before, and the median location of each ICBe event tag applied to those sentences.[^11] Labels reflect the individual leaves of the ontology and colors reflect the higher level coarse branch nodes of the ontology.
+If ICBe has high precision, substantively similar tags ought to have been applied to substantively similar source text, which is what we see both in two dimensions in the main plot and via hierarchical clustering on all dimensions in the dendrogram along the right-hand side.[^12]
+
+[^11]: We preprocess sentences to replace named entities with a generic Entity token.
+
+[^12]: Hierarchical clustering on cosine similarity and with Ward's method.
 
@@
 These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).[^12] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
+escalation and de-escalation of conflicts).[^13] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
 Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
@@
 
-[^12]: Using ICBe data, @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
+[^13]: Using ICBe data, @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
 

### 2023-11-20 replication_paper/psrm_draft/ICBe_manuscript.tex
fig 2 footnote future research

@@
 lags only slightly behind showing that it left little additional
-information on the table.
+information on the table.\footnote{Although Figure 2 focuses only on two
+  crises, the synthetic narrative approach and recall comparison can,
+  and should, be more broadly applied to all international crises in a
+  way that could reveal systematic blindspots across datasets.}
 

### 2023-11-21 replication_paper/psrm_draft/ICBe_manuscript.Rmd
small edit

@@
 For example, if thoughts and speech acts are immaterial for a particular research question, those higher-level categories can be modified in a way that does not produce inevitable downstream effects on the rest of the coding.
-This is necessary because unlike existing datasets where variable values are largely independent, the nested nature of the ICBe variables means filtering out speech acts also requires filtered out variables about the actors, locations, and timing of those speech acts.
+This is necessary because unlike existing datasets where variable values are largely independent, the nested nature of the ICBe variables means filtering out speech acts also requires filtering out variables about the actors, locations, and timing of those speech acts.
 
@@
 In fact, most only try to code actions and entirely omit thoughts and speech acts despite recognition of their importance in international politics [@smithInternationalCrisesDomestic1998].
-Scholars have opted against coding thoughts and speech acts because of a lack of confidence the full universe could be readily observed and consequently at least theoretically be included.[^7] But the perfect should not be the enemy of the good, and measurement challenges are only overcome after an initial attempt to estimate difficult to observe concepts of interest.
+Scholars have opted against coding thoughts and speech acts because of a lack of confidence the full universe could be readily observed and consequently at least theoretically be included.[^7] But the perfect should not be the enemy of the good, and measurement challenges are only overcome after an initial attempt to estimate difficult-to-observe concepts of interest.
 The ICB narratives are one of the better sources for this endeavor due to the consistent use of high-quality primary source material that takes advantage of qualitative methods well-suited to identifying thoughts and speech acts like archival work and expert interviews.

### 2023-11-21 replication_paper/psrm_draft/ICBe_manuscript.tex
small edit

@@
 
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
+\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}
 
@@
 nature of the ICBe variables means filtering out speech acts also
-requires filtered out variables about the actors, locations, and timing
+requires filtering out variables about the actors, locations, and timing
 of those speech acts.
@@
 should not be the enemy of the good, and measurement challenges are only
-overcome after an initial attempt to estimate difficult to observe
+overcome after an initial attempt to estimate difficult-to-observe
 concepts of interest. The ICB narratives are one of the better sources

### 2024-02-16 replication_paper/psrm_draft/ICBe_manuscript.Rmd
conditional accept edits to fig 1 and 3 and sec 1.1 and 5

@@
 
-How can scholars abstract and measure discrete events about a historical episode in international relations?
-We employ a metaphor of chess, a game that despite its complexity can nonetheless be recorded in a standardized and structured manner.
-Like chess, international interactions involve a finite set of players (e.g.
-polities, rebel groups, IGOs) expressing their behaviors (e.g.
-thinking, saying, and doing) by moving pieces (e.g.
-military platforms, civilian personnel, diplomats) from and onto identifiable locations (geo-coded coordinates).
-These moves occur over a marked time period (start and end of a historical episode) and gambits occur in recordable sequences (actions and reactions) to produce observable, if still disputable, outcomes (e.g.
-victory, defeat, stalemate, peace).
-Our knowledge of this historical episode, including the actors involved as well as their preferences, behaviors, and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
-
-Much like the recording of chess evolved from natural language descriptive text notation to the modern figurine algebra notion, international relations scholars have recently sought to produce a structured account of historical events by combining the unstructured corpus of historical records with informative priors about international relations.
-The resulting structured account of information about a historical episode can be combined with that of other events to produce a systematic account of political events from which we can garner novel insight, assuming the underlying data have high coverage, precision, and recall.
-The easiest way to convey the desired produced of this task is with an example.
+Our knowledge of any historical episode, including the participants and their preferences, behaviors, and beliefs are only indirectly observed from historical records that most often take the form of unstructured natural language text.
+Despite its complexity, all international interactions fundamentally involve a finite set of actors expressing their interests through at least theoretically observable behaviors.
+So how can scholars abstract and measure discrete events about a historical episode in international relations?
+Scholars have recently sought to produce a structured account of world events by combining the unstructured corpus of historical records with informative priors about international relations.
+The result can produce novel insight from a systematic account of political events.
+The easiest way to convey the desired product is with an example.
 Figure 1 shows a narrative account of the Cuban Missile Crisis (1962) in natural language sentences alongside a mapping to discrete machine-readable abstractive events.
-From the structured data, scholars can identify similarities and differences across events concerning important concepts like when particular foreign policy actions deter versus inflame [@jervisCooperationSecurityDilemma1978; @glaserCausesConsequencesArms2000], when third parties mediate in interstate disputes [@haffarEmergentPeacemakersCataloguing2002; @quinnPowerPlayMediation2006], and how actors try to communicate resolve [@tragerDiplomacyWarPeace2016; @luptonReexaminingReputationResolve2018].
+From this, scholars can identify similarities and differences across events like what foreign policy actions deter versus inflame [@jervisCooperationSecurityDilemma1978; @glaserCausesConsequencesArms2000], when third parties mediate [@haffarEmergentPeacemakersCataloguing2002; @quinnPowerPlayMediation2006], and how actors communicate resolve [@tragerDiplomacyWarPeace2016; @luptonReexaminingReputationResolve2018].
 Identifying patterns of international interactions is not just an inherently interesting enterprise; it is a necessary precondition to important efforts to predict where policymakers should turn their attention to improve global welfare [@wardLearningSteppingFuture2013; @begerReassessingRoleTheory2021].
@@
 
-![Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events](case_study_cuban_precision.png){#fig-cubanarrative width="7in" height="8in"}
+![Comparison of a natural language and machine-readable abstractive account of the Cuban Missile Crisis (1962).
+The text on the left is a summary of the event from the ICB Crisis Narrative.
+The mapping on the right shows the corresponding ICBe coding](case_study_cuban_precision.png){#fig-cubanarrative width="7in" height="8in"}
 
@@
 
-![Dots represent individual ICB narrative sentences, as embedded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP.
-Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology.
-Label placement is the median of all of the sentences that the tag was applied to by the coders.
-The dendrogram shows hierarchical clustering of the tags.
-If ICBe precision is high, then the sentences that tags were applied to ought to say similar things and the intended shape of the ontology ought to be visually recognizable.](p_semantic_embeddings_dendro.png){#fig-umap width="7in" height="7in"}
+![Computational evaluation of the precision of ICBe event codings.
+The plot on the left is a map of the semantic meaning of every sentence in the corpus (black points) as assigned by a large language model (Paraphrase-MPNET-base-v2) and projected down into two dimensions (UMAP).
+Overlaid are the average semantic locations of each label assigned by ICBe coders (colored labels).
+The labels with similar meaning are assigned to sentences with similar semantic meaning, creating an observable structure and pattern we would not observe with low quality coding where tag location would instead appear random.
+The plot on the right shows a hierarchical dendrogram clustering labels into groups by their average semantic location with more similar labels being more closely connected on the tree.
+The clustering by color indicates it closely mirrors the intended ICBe ontology, suggesting high precision in the coding.](p_semantic_embeddings_dendro.png){#fig-umap width="7in" height="7in"}
 
@@
 
-We investigated event abstraction from narratives describing key historical episodes in international relations.
-We synthesized a prior belief about the latent unobserved phenomena that drive these events in international relations and proposed a mapping to observable concepts that enter into the observed historical record.
-We designed an ontology with high coverage over those concepts and developed a training procedure and technical stack for human coding of historical texts.
+The scope and complexity of international politics should not discourage the identification of trends, patterns, and regularities.
+In undertaking event abstraction from narratives about key historical episodes in international relations, this paper has proposed a mapping between unstructured historical records and a structured ontology of these events with high coverage of concepts of interest.
 Multiple validity checks find the resulting codings have high internal validity (e.g.
@@
 
-We release several open-source products along with supporting code and documentation to further advance the study of international relations, event extraction, and natural language processing.
-The first is the International Crisis Behavior Events (ICBe) dataset, an event-level aggregation of what took place during the crises identified by the ICB project.
-These data are appropriate for statistical analysis of hard questions about the sequencing of events (e.g.
-escalation and de-escalation of conflicts).[^13] Second, we provide a coder-level disaggregation with multiple codings of each sentence by experts and undergrads that allows for the introduction of uncertainty and human interpretation of events.
-Further, we release a direct mapping from the codings to the source text at the sentence level as a new resource for natural language processing.
-Finally, we provide a companion website that incorporates detailed visualizations of all of the data introduced here at crisisevents.org.
-
-[^13]: Using ICBe data, @gannonOneIfLand2022 finds that cross-domain crises are shorter and less violent than same-domain crises.
+These data, along with the open-source code, documentation, and companion website provide several substantive and methodological contributions to the discipline.
+Substantively, these data are appropriate for statistical analysis of hard questions in the study of crises like interactions between means of warfare and the preconditions for conflict escalation [@gannonOneIfLand2022].
+Methodologically, our mapping from codings to source text at the sentence level provide a new resource for natural language processing with access to coder-level disaggregation that furthers the study of uncertainty in the interpretation of international events and in the quantitative coding of historical events.
+Finally, we provide a companion website (crisisevents.org) that incorporates detailed visualizations of all the data introduced here as a new resource for the study of international crises in a scalable, yet detailed, manner.
 

### 2024-02-16 replication_paper/psrm_draft/ICBe_manuscript.tex
conditional accept edits to fig 1 and 3 and sec 1.1 and 5

@@
 
-How can scholars abstract and measure discrete events about a historical
-episode in international relations? We employ a metaphor of chess, a
-game that despite its complexity can nonetheless be recorded in a
-standardized and structured manner. Like chess, international
-interactions involve a finite set of players (e.g.~polities, rebel
-groups, IGOs) expressing their behaviors (e.g.~thinking, saying, and
-doing) by moving pieces (e.g.~military platforms, civilian personnel,
-diplomats) from and onto identifiable locations (geo-coded coordinates).
-These moves occur over a marked time period (start and end of a
-historical episode) and gambits occur in recordable sequences (actions
-and reactions) to produce observable, if still disputable, outcomes
-(e.g.~victory, defeat, stalemate, peace). Our knowledge of this
-historical episode, including the actors involved as well as their
-preferences, behaviors, and beliefs are only indirectly observed from
-historical records that most often take the form of unstructured natural
-language text.
-
-Much like the recording of chess evolved from natural language
-descriptive text notation to the modern figurine algebra notion,
-international relations scholars have recently sought to produce a
-structured account of historical events by combining the unstructured
-corpus of historical records with informative priors about international
-relations. The resulting structured account of information about a
-historical episode can be combined with that of other events to produce
-a systematic account of political events from which we can garner novel
-insight, assuming the underlying data have high coverage, precision, and
-recall. The easiest way to convey the desired produced of this task is
-with an example. Figure 1 shows a narrative account of the Cuban Missile
-Crisis (1962) in natural language sentences alongside a mapping to
-discrete machine-readable abstractive events. From the structured data,
-scholars can identify similarities and differences across events
-concerning important concepts like when particular foreign policy
-actions deter versus inflame (Jervis 1978; Glaser 2000), when third
-parties mediate in interstate disputes (Haffar 2002; Quinn et al. 2006),
-and how actors try to communicate resolve (Trager 2016; Lupton 2018).
-Identifying patterns of international interactions is not just an
+Our knowledge of any historical episode, including the participants and
+their preferences, behaviors, and beliefs are only indirectly observed
+from historical records that most often take the form of unstructured
+natural language text. Despite its complexity, all international
+interactions fundamentally involve a finite set of actors expressing
+their interests through at least theoretically observable behaviors. So
+how can scholars abstract and measure discrete events about a historical
+episode in international relations? Scholars have recently sought to
+produce a structured account of world events by combining the
+unstructured corpus of historical records with informative priors about
+international relations. The result can produce novel insight from a
+systematic account of political events. The easiest way to convey the
+desired product is with an example. Figure 1 shows a narrative account
+of the Cuban Missile Crisis (1962) in natural language sentences
+alongside a mapping to discrete machine-readable abstractive events.
+From this, scholars can identify similarities and differences across
+events like what foreign policy actions deter versus inflame (Jervis
+1978; Glaser 2000), when third parties mediate (Haffar 2002; Quinn et
+al. 2006), and how actors communicate resolve (Trager 2016; Lupton
+2018). Identifying patterns of international interactions is not just an
 inherently interesting enterprise; it is a necessary precondition to
@@
 \includegraphics[width=7in,height=8in]{case_study_cuban_precision.png}
-\caption{Cuban Missile Crisis (1962) - ICB Narrative vs.~ICBe
-Events}\label{fig-cubanarrative}
+\caption{Comparison of a natural language and machine-readable
+abstractive account of the Cuban Missile Crisis (1962). The text on the
+left is a summary of the event from the ICB Crisis Narrative. The
+mapping on the right shows the corresponding ICBe
+coding}\label{fig-cubanarrative}
 }
@@
 \includegraphics[width=7in,height=7in]{p_semantic_embeddings_dendro.png}
-\caption{Dots represent individual ICB narrative sentences, as embedded
-by the Paraphrase-MPNET-base-v2 large language model and flattened into
-two dimensions with UMAP. Text labels reflect individual leaves of the
-ICBe ontology, and colors represent intermediate branches of the
-ontology. Label placement is the median of all of the sentences that the
-tag was applied to by the coders. The dendrogram shows hierarchical
-clustering of the tags. If ICBe precision is high, then the sentences
-that tags were applied to ought to say similar things and the intended
-shape of the ontology ought to be visually
-recognizable.}\label{fig-umap}
+\caption{Computational evaluation of the precision of ICBe event
+codings. The plot on the left is a map of the semantic meaning of every
+sentence in the corpus (black points) as assigned by a large language
+model (Paraphrase-MPNET-base-v2) and projected down into two dimensions
+(UMAP). Overlaid are the average semantic locations of each label
+assigned by ICBe coders (colored labels). The labels with similar
+meaning are assigned to sentences with similar semantic meaning,
+creating an observable structure and pattern we would not observe with
+low quality coding where tag location would instead appear random. The
+plot on the right shows a hierarchical dendrogram clustering labels into
+groups by their average semantic location with more similar labels being
+more closely connected on the tree. The clustering by color indicates it
+closely mirrors the intended ICBe ontology, suggesting high precision in
+the coding.}\label{fig-umap}
 }
@@
 
-We investigated event abstraction from narratives describing key
-historical episodes in international relations. We synthesized a prior
-belief about the latent unobserved phenomena that drive these events in
-international relations and proposed a mapping to observable concepts
-that enter into the observed historical record. We designed an ontology
-with high coverage over those concepts and developed a training
-procedure and technical stack for human coding of historical texts.
-Multiple validity checks find the resulting codings have high internal
-validity (e.g.~intercoder agreement) and external validity
-(i.e.~matching source material in both micro-details at the sentence
-level and macro-details spanning full historical episodes). Further,
-these codings perform much better in terms of recall, precision,
-coverage, and overall coherence in capturing these historical episodes
-than existing event systems used in international relations.
-
-We release several open-source products along with supporting code and
-documentation to further advance the study of international relations,
-event extraction, and natural language processing. The first is the
-International Crisis Behavior Events (ICBe) dataset, an event-level
-aggregation of what took place during the crises identified by the ICB
-project. These data are appropriate for statistical analysis of hard
-questions about the sequencing of events (e.g.~escalation and
-de-escalation of conflicts).\footnote{Using ICBe data, Gannon (2022)
-  finds that cross-domain crises are shorter and less violent than
-  same-domain crises.} Second, we provide a coder-level disaggregation
-with multiple codings of each sentence by experts and undergrads that
-allows for the introduction of uncertainty and human interpretation of
-events. Further, we release a direct mapping from the codings to the
-source text at the sentence level as a new resource for natural language
-processing. Finally, we provide a companion website that incorporates
-detailed visualizations of all of the data introduced here at
-crisisevents.org.
+The scope and complexity of international politics should not discourage
+the identification of trends, patterns, and regularities. In undertaking
+event abstraction from narratives about key historical episodes in
+international relations, this paper has proposed a mapping between
+unstructured historical records and a structured ontology of these
+events with high coverage of concepts of interest. Multiple validity
+checks find the resulting codings have high internal validity
+(e.g.~intercoder agreement) and external validity (i.e.~matching source
+material in both micro-details at the sentence level and macro-details
+spanning full historical episodes). Further, these codings perform much
+better in terms of recall, precision, coverage, and overall coherence in
+capturing these historical episodes than existing event systems used in
+international relations.
+
+These data, along with the open-source code, documentation, and
+companion website provide several substantive and methodological
+contributions to the discipline. Substantively, these data are
+appropriate for statistical analysis of hard questions in the study of
+crises like interactions between means of warfare and the preconditions
+for conflict escalation (Gannon 2022). Methodologically, our mapping
+from codings to source text at the sentence level provide a new resource
+for natural language processing with access to coder-level
+disaggregation that furthers the study of uncertainty in the
+interpretation of international events and in the quantitative coding of
+historical events. Finally, we provide a companion website
+(crisisevents.org) that incorporates detailed visualizations of all the
+data introduced here as a new resource for the study of international
+crises in a scalable, yet detailed, manner.
 

### 2024-04-08 replication_paper/psrm_draft/ICBe_manuscript.Rmd
replication merge

@@
 options(tinytex.clean=F)
+fromscratch = FALSE #Set to TRUE to repull google docs
 ```
@@
 ```
+
 ```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}
@@
 library(lubridate, warn.conflicts = FALSE)
-lit_review_pull <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/14RHRKgQGHj7Zr4_xt4fq2bIE7mDNayLKj89tYmOOfHQ/edit?usp=sharing", 
-                                sheet="DatasetsComparisonLitReview") #%>% janitor::clean_names() 
+
+if(fromscratch){googlesheets4::gs4_deauth()}
+
+if(fromscratch){
+  lit_review_pull <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/14RHRKgQGHj7Zr4_xt4fq2bIE7mDNayLKj89tYmOOfHQ/edit?usp=sharing", sheet="DatasetsComparisonLitReview") #%>% janitor::clean_names()
+  saveRDS(lit_review_pull ,
+            file=paste0(here::here(),"/replication_data/out/lit_review_pull.Rds")) 
+} else {lit_review_pull <- readRDS( paste0(here::here(), "/replication_data/out/lit_review_pull.Rds"))}
+
 # dim(lit_review_pull)
@@
 
+```{r recall-cuba, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+#Lit review
+#child=c('ICBEdataset_paper_litreviewtable.Rmd')
+library(tidyverse)
+library(flextable)
+library(ftExtra)
+flextable::set_flextable_defaults(fonts_ignore=TRUE)
+
+library(googlesheets4) #Do this high up so you get the prompt early
+library(lubridate, warn.conflicts = FALSE)
+
+if(fromscratch){
+  case_study_cuban <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", sheet="final") %>% janitor::clean_names() 
+  saveRDS(case_study_cuban, file=paste0(here::here(),"/replication_data/out/case_study_cuban.Rds")) 
+} else {case_study_cuban <- readRDS( paste0(here::here(), "/replication_data/out/case_study_cuban.Rds"))}
+
+dim(case_study_cuban)
+#case_study_cuban$date <- case_study_cuban$date %>% lapply(FUN=function(x) { ifelse(is.null(x), "", x[[1]] %>% as.character() )   }   ) %>% unlist() %>% as.Date()
+
+#Replace emoticons with images
+replace_emoticons <- function(x){
+  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
+        #https://emojiterra.com/flag-for-united-states/
+        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
+        #https://emojiterra.com/flag-for-russia/
+        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
+        #Turkey
+        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
+        #U.N.
+        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
+}
+
+temp1 <- case_study_cuban %>% 
+                #filter(!is.na(date)) %>%
+                #head(2) %>%
+                mutate(date=date %>% anytime::anydate()) %>%
+                mutate(year=year(date) %>% as.character() ) %>%
+                mutate(month=month(date) %>% as.character()) %>%
+                mutate(day=day(date) %>% as.character()) %>%
+                mutate(documents = documents %>% as.numeric()) %>%
+                mutate(Rank=rank(-documents, ties.method="first")  ) %>%
+                dplyr::select(Y=year,M=month, D=day, Rank, Event=event, Docs=documents, icb_narrative=icb_narrative, ICBe=ic_be, ICB=icb, MIDs=mids, phoenix=phoenix) %>% 
+                # mutate(Event= Event %>%  replace_emoticons) %>% 
+                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
+                mutate(ICB = ifelse(!is.na(ICB) & !ICB %in% 0, "✓", NA)) %>%
+                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0, "✓", NA)) %>%
+                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0, "✓", NA)) %>%
+                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0, "✓", NA)) %>%
+
+                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
+                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
+                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
+                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
+                mutate(YMD=paste(Y,
+                                 M %>% str_pad(2, pad = "0") ,
+                                 D %>% str_pad(2, pad = "0"), 
+                                 sep="-") %>% trimws() %>%
+                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
+                                 str_replace_all("^NA-","") %>% 
+                                 str_replace_all("^-00|^00","") %>% 
+                                 str_replace_all("^-00|^00","") %>% 
+                                 str_replace_all("^-","") 
+                       ) %>%
+                dplyr::select(-Y,-M,-D) %>%
+                relocate(YMD, .before = Rank) %>%
+                dplyr::select(-Rank)
+dim(temp1)
+
+#banding <- temp %>% mutate(date=as.Date(paste(Y,M,D, sep="-")) %>% as.numeric() %>% as.factor() %>% as.numeric() ) %>% pull(date) %% 2
+banding <- 1:nrow(temp1) %% 2
+k=ncol(temp1)
+ft <- temp1   %>%
+      flextable::as_flextable() %>% 
+      flextable::set_header_labels(values =
+        list(
+              Event = "Ground\nTruth\nEvents",
+              icb_narrative = "ICB Corpus",
+              ICB = "ICB",
+              MIDs = "MIDs",
+              phoenix = "Phoenix"
+             ) ) %>%
+      flextable::width( j = 1, width=0.6)  %>% 
+      #flextable::width( j = 2, width=0.025)  %>%
+      #flextable::width( j = 3, width=0.025)  %>%
+      #flextable::width( j = 5, width=0.025) %>%
+      flextable::width( j = 2, width=3.0)  %>%
+      flextable::width( j = 3, width=0.03) %>%
+      flextable::width( j = 4:k, width=0.15) %>% #icb
+      #merge_v( j = 1,  part = "body", combine = T) %>%
+      #merge_v( j = 3,  part = "body", combine = F) %>%
+      #merge_v( j = 4,  part = "body", combine = F) %>%
+
+      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
+      align(i = 1,  align = "center", part = "header") %>%
+      valign(j = 1:2, valign = "center", part = "all") %>%
+      align(i = NULL, j = 1, align = "right", part = "body")  %>%
+      align(i = NULL, j = 2, align = "left", part = "body")  %>%
+      #align(i = NULL, j = 2, align = "center", part = "body")  %>%
+      #align(i = NULL, j = 3, align = "left", part = "body")  %>%
+      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
+      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
+      flextable::padding(padding = 0, part = "body") %>%
+      flextable::fontsize(size = 7, part = "all") %>%
+      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
+      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
+      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
+      vline(j=c(1,2,3,4,5,6,7),  border = NULL, part = "all") %>%
+      hline(i=c(26,46)) %>%
+      ftExtra::colformat_md(j = 2, part="body") 
+      #ftExtra::colformat_md(j = 6, part="body")
+
+ft   %>% 
+    #flextable::flextable_to_rmd()
+    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+
+```
+
+```{r recall-crimea, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+library(dplyr)
+library(googlesheets4) #Do this high up so you get the prompt early
+library(lubridate, warn.conflicts = FALSE)
+
+if(fromscratch){
+  case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", sheet="final") %>% janitor::clean_names() 
+  saveRDS(case_study_crimea, file=paste0(here::here(),"/replication_data/out/case_study_crimea.Rds")) 
+} else {case_study_crimea <- readRDS( paste0(here::here(), "/replication_data/out/case_study_crimea.Rds"))}
+
+dim(case_study_crimea)
+
+#Replace emoticons with images
+replace_emoticons_crimea <- function(x){
+      x %>%
+            #https://emojiterra.com/flag-for-united-states/
+            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
+            #https://emojiterra.com/flag-for-russia/
+            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
+            #Ukraine
+            str_replace_all('\U0001f1fA\U0001f1e6',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
+            #
+            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>% 
+            #
+            str_replace_all('🇪🇺', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
+                            }
+
+rex_date <- function(x){
+  a <- x[1] %>% as.character() %>% unlist()
+  if(is.null(a)){return('')}
+  return(a)
+}
+case_study_crimea$date <- sapply(sapply(case_study_crimea$date, as.character), rex_date)
+temp2 <- case_study_crimea %>% 
+                filter(keep %in% 1) %>%
+                #filter(!is.na(date)) %>%
+                #head(2) %>%
+                mutate(date=date %>% anytime::anydate()) %>%
+                mutate(year=year(date) %>% as.character() ) %>%
+                mutate(month=month(date) %>% as.character()) %>%
+                mutate(day=day(date) %>% as.character()) %>%
+                mutate(n_sources = n_sources %>% as.numeric()) %>%
+                mutate(Rank=rank(-n_sources, ties.method="first")  ) %>%
+                dplyr::select(Y=year,M=month, D=day, Rank,  Event=event, Docs=n_sources, 
+                              icb_narrative=icb_narrative, ICBe=ic_be, MIDs=mids, phoenix, terrier, icews ) %>%  #, ICB=icb, MIDs=mids, phoenix=phoenix
+                # mutate(Event= Event %>%  replace_emoticons_crimea) %>%
+                arrange(Y %>% as.numeric() ,M %>% as.numeric()  ,D %>% as.numeric() ) %>%
+                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
+                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
+                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
+                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
+                mutate(YMD=paste(Y,
+                                 M %>% str_pad(2, pad = "0") ,
+                                 D %>% str_pad(2, pad = "0"), 
+                                 sep="-") %>% trimws() %>%
+                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
+                                 str_replace_all("^NA-","") %>% 
+                                 str_replace_all("^-00|^00","") %>% 
+                                 str_replace_all("^-00|^00","") %>% 
+                                 str_replace_all("^-","") 
+                       ) %>%
+                dplyr::select(-Y,-M,-D) %>%
+                relocate(YMD, .before = Rank) %>%
+                dplyr::select(-Rank) %>% 
+                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
+                mutate(icews = ifelse(!is.na(icews) & !icews %in% 0 , "✓", NA)) %>%
+                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0  , "✓", NA)) %>%
+                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0  , "✓", NA)) %>%
+                mutate(terrier = ifelse(!is.na(terrier) & !terrier %in% 0  , "✓", NA))  %>%
+                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0  , "✓", NA))
+
+dim(temp2)
+
+banding <- 1:nrow(temp2) %% 2
+k=ncol(temp2)
+ft <- temp2  %>%
+      flextable::as_flextable() %>% 
+      flextable::set_header_labels(values =
+        list(
+              Event = "Ground\nTruth\nEvents",
+              icb_narrative = "ICB Corpus",
+              ICBe = "ICBe",
+              MIDs="MIDs",
+              icews_hash = "ICEWS"
+             ) ) %>%
+      flextable::width( j = 1, width=0.6)  %>% 
+      flextable::width( j = 2, width=3.0)  %>%
+      flextable::width( j = 3:k, width=0.15) %>% #icb
+      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
+      align(i = 1,  align = "center", part = "header") %>%
+      valign(j = 1:2, valign = "center", part = "all") %>%
+      align(i = NULL, j = 1, align = "right", part = "body")  %>%
+      align(i = NULL, j = 2, align = "left", part = "body")  %>%
+      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
+      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
+      flextable::padding(padding = 0, part = "body") %>%
+      flextable::fontsize(size = 7, part = "all") %>%
+      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
+      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
+      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
+      vline(j=1:k,  border = NULL, part = "all") %>%
+      #hline(i=c(26,46)) %>%
+      ftExtra::colformat_md(j = 2, part="body") 
+      #ftExtra::colformat_md(j = 6, part="body")
+
+ft   %>% 
+    #flextable::flextable_to_rmd()
+    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_recall.png"),
+                  zoom=1, webshot = "webshot2") # webshot = "webshot2"
+```
+
+```{r recall-combined, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+
+# AG temp edit: revert by setting 'eval=T'
+
+temp3 <- temp1 %>% mutate(row=row_number()) %>% full_join(temp2 %>% mutate(row=row_number()), by='row') %>% 
+         mutate(row="") #we're going to use this as our vertical break
+
+n_left <- (!is.na(temp3$Event.x) ) %>% sum()
+n_right <- (!is.na(temp3$Event.y) ) %>% sum()
+
+k=ncol(temp3)
+kleft=ncol(temp1)
+kright=ncol(temp2)
+left_end=kleft
+right_start=left_end+2
+left=c(1:left_end)
+right=c(right_start:k)
+horizontal = c(left,right)
+dates=c(1,right_start)
+events = dates + 1
+checkmarks = c((events[1]+1):left_end , (events[2]+1):k)
+
+library(officer)
+big_border = fp_border(color="black", width = 2)
+
+banding1 <- 1:nrow(temp1) %% 2
+banding2 <- 1:nrow(temp2) %% 2
+ft <- temp3  %>%
+      flextable::as_flextable() %>%
+
+      flextable::line_spacing( space = 1.0, part = "all") %>% # 
+      flextable::padding(padding = 0, part = "body") %>%
+      flextable::fontsize(size = 7, part = "all") %>%
+      bg( i = which( banding1==1 ) , part = "body", bg = "#EFEFEF", j=left) %>%
+      bg( i = which( banding2==1 ) , part = "body", bg = "#EFEFEF", j=right) %>%
+
+      #Headers
+      flextable::set_header_labels(values =
+        list(
+              YMD.x = "YMD",
+              Event.x = "Synthetic Narrative",
+              Docs.x = "Mentions",
+              icb_narrative.x = "ICB Corpus",
+              ICBe.x = "ICBe",
+              ICB = "ICB",
+              MIDs.x = "MIDs",
+              phoenix.x = "Phoenix",
+              phoenix.y = "Phoenix",
+              row="",
+              YMD.y = "YMD",
+              Event.y = "Synthetic Narrative",
+              Docs.y = "Mentions",
+              icb_narrative.y = "ICB Corpus",
+              ICBe.y = "ICBe",
+              icews = "ICEWS",
+              MIDs.y = "MIDs",
+              terrier="Terrier"
+             ) ) %>%
+
+      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbas (2014)"), colwidths = c(kleft, 1,kright) ) %>%
+
+      #Global
+      flextable::border_remove() %>% 
+      #Left border
+      border(j=1, i=1:n_left , part="body", border.left =  big_border ) %>% #
+      border(j=1, i=1:2 , part="header", border.left =  big_border ) %>% #
+
+      border(j=left_end, i=1:2 , part="header", border.right =  big_border ) %>% #
+      border(j=left_end, i=1:n_left , part="body", border.right =  big_border ) %>% #
+
+      border(j=1:left_end, i=n_left , part="body", border.bottom =  big_border ) %>% #
+      border(j=1:left_end, i=1 , part="body", border.top =  big_border ) %>% #
+      border(j=1:left_end, i=1:2 , part="header", border.top =  big_border ) %>% #
+
+      #Right border
+      border(j=right_start, i=1:n_right , part="body", border.left =  big_border ) %>% #
+      border(j=k, i=1:n_right , part="body", border.right =  big_border ) %>% #
+
+      border(j=right_start, i=1:2 , part="header", border.left =  big_border ) %>% #
+      border(j=k, i=1:2 , part="header", border.right =  big_border ) %>% #
+      border(j=1:k, i=1 , part="header", border.right =  big_border ) %>% #
+
+      border(j=right_start:k, i=n_right , part="body", border.bottom =  big_border ) %>% #
+      border(j=right_start:k, i=1 , part="body", border.top =  big_border ) %>% #
+      border(j=right_start:k, i=1:2 , part="header", border.top =  big_border ) %>% #
+
+      vline(i=1:n_left, j=1:(left_end-1),  border = NULL, part = "body")  %>%
+      vline(i=1:n_right,j=right_start:(k-1),  border = NULL, part = "body")  %>%
+      vline(i=2, j=1:(left_end-1),  border = NULL, part = "header")  %>%
+      vline(i=2,j=right_start:(k-1),  border = NULL, part = "header")  %>%
+
+      #
+      hline(i=c(26,46), j=left,  border = NULL, part = "body")  %>%
+      hline(i=c(11), j=right,  border = NULL, part = "body")  %>%
+
+      #Header
+      flextable::rotate(i=2, j=3:left_end, rotation="tbrl", part="header") %>% 
+      flextable::rotate(i=2, j=(left_end+4):k, rotation="tbrl", part="header") %>%
+
+      valign(j = 1:2, valign = "center", part = "all") %>%
+      align(i = 2, j = NULL, align = "center", part = "header")  %>%
+
+      #break
+      flextable::width( j = left_end+1, width=0.25)  %>%
+
+      #Dates
+      flextable::width( j = dates, width=0.6)  %>% 
+      align(i = NULL, j = dates, align = "right", part = "body")   %>%
+
+      #events
+      flextable::width( j = events, width=2.50)  %>%
+      align(i = NULL, j = events, align = "left", part = "body")  %>%
+      ftExtra::colformat_md(j = events, part="body") %>%
+
+      #Checkmarks
+      flextable::width( j = checkmarks, width=0.05) %>%
+      align(i = NULL, j = checkmarks, align = "center", part = "body")
+
+ft   %>% 
+    #flextable::flextable_to_rmd()
+    save_as_image(path=here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
+```
+
+```{r recall-all, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+#Recall Summary Statistics
+#, icb_narrative_cd=icb_narrative.y, icews_cd=icews_hash
+temp1_long <- temp1 %>% dplyr::select(docs=Docs, ICB_Narrative=icb_narrative, ICBe=ICBe, ICB=ICB,MIDs=MIDs,Phoenix=phoenix) %>% mutate(crisis="Cuban Missile Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
+              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
+
+temp2_long <- temp2 %>% dplyr::select(docs=Docs,ICB_Narrative=icb_narrative,ICBe=ICBe,MIDs=MIDs , Phoenix=phoenix, Terrier=terrier, ICEWS= icews) %>% mutate(crisis="Crimea-Donbas Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
+              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
+
+temp3_long <- bind_rows(temp1_long,temp2_long)
+
+Y_hat <- temp3_long %>% dplyr::select(name) %>% distinct()
+mylogit <- glm(value ~ name, data = temp3_long, family = "binomial")
+Y_hat$fit <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$fit
+Y_hat$se <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$se.fit
+Y_hat$name <- Y_hat$name %>% fct_reorder(Y_hat$fit)
+
+#Y_hat %>% ggplot(aes(name, fit)) +
+#          geom_point(size=4) +
+#          geom_errorbar(aes(ymin = fit-(1.98*se), ymax = fit+(1.98*se)), width = 0.1, linetype="solid") + coord_flip()  + theme_bw() + 
+#          ylab("Mean Recall") + xlab("")
+
+#temp3_long_means <- temp3_long %>% 
+#                    group_by(name) %>%
+#                    summarise(value= value %>%mean() %>% round(2))
+
+#temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + geom_point() +
+#  geom_smooth(method = "glm", method.args = list(family = "binomial"), se=F) + 
+#  ylab("Recall") + xlab("Document Mentions (Log)") +
+#  facet_wrap(~crisis, scales="free_x")
+
+library(geomtextpath)
+temp3_long$crisis <- factor(temp3_long$crisis, levels= temp3_long$crisis %>% as.character() %>% unique() %>% sort() %>% rev() )
+p_recall <- temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + 
+  #geom_point() +
+  geom_textsmooth(aes(label = name), size=3, method = "glm", method.args = list(family = "binomial"), se=F) + 
+  ylab("Recall") + xlab("Document Mentions (Log)") +
+  facet_wrap(~crisis, scales="free_x") +
+  theme_bw() +
+  theme(legend.position="none")
+
+#p_recall
+
+ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'),
+       plot = p_recall ,
+       width=5, height=3.0)
+
+library(magick)
+
+tiger <- image_read(here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"))
+tiger2 <- image_read(paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'))
+
+combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
+image_write(combined, here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea_andcounts.png"))
+```
+
 ![Recall comparison of two cases across existing state of the art efforts.
@@
 
-actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
-                                sheet="actor_translator") #%>% janitor::clean_names() 
+if(fromscratch){
+  actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", sheet="actor_translator") #%>% janitor::clean_names()
+  saveRDS(actor_translator,
+            file=paste0(here::here(),"/replication_data/out/actor_translator.Rds")) 
+} else {actor_translator <- readRDS( paste0(here::here(), "/replication_data/out/actor_translator.Rds"))}
+
 #Convert to a local file for pushing
@@
 
-```{python sentence-transformers, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+```{python sentence-transformers, eval=fromscratch, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
 #Can't get this and spacy to work in the same run. Once reticulate loads once it sticks with the environment that came first and I can't figure out how to switch it.
 #pip install -U sentence-transformers
-
-fromscratch=False
-
-if fromscratch:
   from sentence_transformers import SentenceTransformer
@@
   sentences_embeddings.shape #(12103, 768)
-
-else:
-  print("Skipping")
 ```
@@
 ```{r sentence-embeddings, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-fromscratch = FALSE
 if(fromscratch){
@@
 
-```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=F}
+```{r umap, results='hide', echo=F, include=T, message=F, cache=F, warning=F, eval=fromscratch}
 #The [umapr](https://github.com/ropensci-archive/umapr) package requires python and [umap](https://github.com/lmcinnes/umap#installing). Please check their repos for installation details.
@@
 
-```{r sentence-embeddings-dendro, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+```{r sentence-embeddings-dendro, eval=fromscratch, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 
@@
 
-```{r recall-cuba, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-#Lit review
-#child=c('ICBEdataset_paper_litreviewtable.Rmd')
-library(tidyverse)
-library(flextable)
-library(ftExtra)
-flextable::set_flextable_defaults(fonts_ignore=TRUE)
-
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-case_study_cuban <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names() 
-dim(case_study_cuban)
-#case_study_cuban$date <- case_study_cuban$date %>% lapply(FUN=function(x) { ifelse(is.null(x), "", x[[1]] %>% as.character() )   }   ) %>% unlist() %>% as.Date()
-
-paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")
-
-#Replace emoticons with images
-replace_emoticons <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
-        #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-        #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
-        #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
-        #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
-}
-
-temp1 <- case_study_cuban %>% 
-                #filter(!is.na(date)) %>%
-                #head(2) %>%
-                mutate(date=date %>% anytime::anydate()) %>%
-                mutate(year=year(date) %>% as.character() ) %>%
-                mutate(month=month(date) %>% as.character()) %>%
-                mutate(day=day(date) %>% as.character()) %>%
-                mutate(documents = documents %>% as.numeric()) %>%
-                mutate(Rank=rank(-documents, ties.method="first")  ) %>%
-                dplyr::select(Y=year,M=month, D=day, Rank, Event=event, Docs=documents, icb_narrative=icb_narrative, ICBe=ic_be, ICB=icb, MIDs=mids, phoenix=phoenix) %>% 
-                mutate(Event= Event %>%  replace_emoticons) %>% 
-                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
-                mutate(ICB = ifelse(!is.na(ICB) & !ICB %in% 0, "✓", NA)) %>%
-                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0, "✓", NA)) %>%
-                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0, "✓", NA)) %>%
-                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0, "✓", NA)) %>%
-
-                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
-                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
-                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
-                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
-                mutate(YMD=paste(Y,
-                                 M %>% str_pad(2, pad = "0") ,
-                                 D %>% str_pad(2, pad = "0"), 
-                                 sep="-") %>% trimws() %>%
-                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
-                                 str_replace_all("^NA-","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-","") 
-                       ) %>%
-                dplyr::select(-Y,-M,-D) %>%
-                relocate(YMD, .before = Rank) %>%
-                dplyr::select(-Rank)
-dim(temp1)
-
-#banding <- temp %>% mutate(date=as.Date(paste(Y,M,D, sep="-")) %>% as.numeric() %>% as.factor() %>% as.numeric() ) %>% pull(date) %% 2
-banding <- 1:nrow(temp1) %% 2
-k=ncol(temp1)
-ft <- temp1   %>%
-      flextable::as_flextable() %>% 
-      flextable::set_header_labels(values =
-        list(
-              Event = "Ground\nTruth\nEvents",
-              icb_narrative = "ICB Corpus",
-              ICB = "ICB",
-              MIDs = "MIDs",
-              phoenix = "Phoenix"
-             ) ) %>%
-      flextable::width( j = 1, width=0.6)  %>% 
-      #flextable::width( j = 2, width=0.025)  %>%
-      #flextable::width( j = 3, width=0.025)  %>%
-      #flextable::width( j = 5, width=0.025) %>%
-      flextable::width( j = 2, width=3.0)  %>%
-      flextable::width( j = 3, width=0.03) %>%
-      flextable::width( j = 4:k, width=0.15) %>% #icb
-      #merge_v( j = 1,  part = "body", combine = T) %>%
-      #merge_v( j = 3,  part = "body", combine = F) %>%
-      #merge_v( j = 4,  part = "body", combine = F) %>%
-
-      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
-      align(i = 1,  align = "center", part = "header") %>%
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = NULL, j = 1, align = "right", part = "body")  %>%
-      align(i = NULL, j = 2, align = "left", part = "body")  %>%
-      #align(i = NULL, j = 2, align = "center", part = "body")  %>%
-      #align(i = NULL, j = 3, align = "left", part = "body")  %>%
-      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
-      vline(j=c(1,2,3,4,5,6,7),  border = NULL, part = "all") %>%
-      hline(i=c(26,46)) %>%
-      ftExtra::colformat_md(j = 2, part="body") 
-      #ftExtra::colformat_md(j = 6, part="body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-
-#Ok rather than try to match up we're going to do this by hand now
-
-```
-
-```{r recall-crimea, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-library(dplyr)
-library(googlesheets4) #Do this high up so you get the prompt early
-library(lubridate, warn.conflicts = FALSE)
-case_study_crimea <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names() 
-dim(case_study_crimea)
-
-#Replace emoticons with images
-replace_emoticons_crimea <- function(x){
-      x %>%
-            #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-            #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
-            #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
-            #
-            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>% 
-            #
-            str_replace_all('🇪🇺', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
-                            }
-
-rex_date <- function(x){
-  a <- x[1] %>% as.character() %>% unlist()
-  if(is.null(a)){return('')}
-  return(a)
-}
-case_study_crimea$date <- sapply(sapply(case_study_crimea$date, as.character), rex_date)
-temp2 <- case_study_crimea %>% 
-                filter(keep %in% 1) %>%
-                #filter(!is.na(date)) %>%
-                #head(2) %>%
-                mutate(date=date %>% anytime::anydate()) %>%
-                mutate(year=year(date) %>% as.character() ) %>%
-                mutate(month=month(date) %>% as.character()) %>%
-                mutate(day=day(date) %>% as.character()) %>%
-                mutate(n_sources = n_sources %>% as.numeric()) %>%
-                mutate(Rank=rank(-n_sources, ties.method="first")  ) %>%
-                dplyr::select(Y=year,M=month, D=day, Rank,  Event=event, Docs=n_sources, 
-                              icb_narrative=icb_narrative, ICBe=ic_be, MIDs=mids, phoenix, terrier, icews ) %>%  #, ICB=icb, MIDs=mids, phoenix=phoenix
-                mutate(Event= Event %>%  replace_emoticons_crimea) %>%
-                arrange(Y %>% as.numeric() ,M %>% as.numeric()  ,D %>% as.numeric() ) %>%
-                mutate(D=ifelse(!is.na(lag(D)) & D==lag(D) & M==lag(M),'',D )) %>%
-                mutate(M=ifelse(!is.na(lag(M)) & M==lag(M),'',M )) %>%
-                mutate(Y=ifelse(!is.na(lag(Y)) & Y==lag(Y),'',Y )) %>%
-                mutate(Y=ifelse(duplicated(Y), NA, Y)) %>%
-                mutate(YMD=paste(Y,
-                                 M %>% str_pad(2, pad = "0") ,
-                                 D %>% str_pad(2, pad = "0"), 
-                                 sep="-") %>% trimws() %>%
-                                 str_replace_all("^NA-","") %>%  #There's like a carriage return and tab in there somehow!
-                                 str_replace_all("^NA-","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-00|^00","") %>% 
-                                 str_replace_all("^-","") 
-                       ) %>%
-                dplyr::select(-Y,-M,-D) %>%
-                relocate(YMD, .before = Rank) %>%
-                dplyr::select(-Rank) %>% 
-                mutate(icb_narrative = ifelse(!is.na(icb_narrative), "✓", NA)) %>%
-                mutate(icews = ifelse(!is.na(icews) & !icews %in% 0 , "✓", NA)) %>%
-                mutate(MIDs = ifelse(!is.na(MIDs) & !MIDs %in% 0  , "✓", NA)) %>%
-                mutate(phoenix = ifelse(!is.na(phoenix) & !phoenix %in% 0  , "✓", NA)) %>%
-                mutate(terrier = ifelse(!is.na(terrier) & !terrier %in% 0  , "✓", NA))  %>%
-                mutate(ICBe = ifelse(!is.na(ICBe) & !ICBe %in% 0  , "✓", NA))
-
-dim(temp2)
-
-banding <- 1:nrow(temp2) %% 2
-k=ncol(temp2)
-ft <- temp2  %>%
-      flextable::as_flextable() %>% 
-      flextable::set_header_labels(values =
-        list(
-              Event = "Ground\nTruth\nEvents",
-              icb_narrative = "ICB Corpus",
-              ICBe = "ICBe",
-              MIDs="MIDs",
-              icews_hash = "ICEWS"
-             ) ) %>%
-      flextable::width( j = 1, width=0.6)  %>% 
-      flextable::width( j = 2, width=3.0)  %>%
-      flextable::width( j = 3:k, width=0.15) %>% #icb
-      flextable::rotate(i=1, rotation="tbrl", part="header") %>% 
-      align(i = 1,  align = "center", part = "header") %>%
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = NULL, j = 1, align = "right", part = "body")  %>%
-      align(i = NULL, j = 2, align = "left", part = "body")  %>%
-      align(i = NULL, j = 3:k, align = "center", part = "body")  %>%
-      flextable::line_spacing( space = 1.0, part = "all") %>% #i=1:nrow(lit_review_alt),
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      #bg( i = which( 1:nrow(temp) %% 2 == 1) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      bg( i = which( banding==1 ) , part = "body", bg = "#EFEFEF", j=1:k) %>%
-      #hline(i=c(26,46), j=3:k,  border = NULL, part = "body") %>%
-      vline(j=1:k,  border = NULL, part = "all") %>%
-      #hline(i=c(26,46)) %>%
-      ftExtra::colformat_md(j = 2, part="body") 
-      #ftExtra::colformat_md(j = 6, part="body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_recall.png"),
-                  zoom=1, webshot = "webshot2") # webshot = "webshot2"
-```
-
-```{r recall-combined, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-
-# AG temp edit: revert by setting 'eval=T'
-
-temp3 <- temp1 %>% mutate(row=row_number()) %>% full_join(temp2 %>% mutate(row=row_number()), by='row') %>% 
-         mutate(row="") #we're going to use this as our vertical break
-
-n_left <- (!is.na(temp3$Event.x) ) %>% sum()
-n_right <- (!is.na(temp3$Event.y) ) %>% sum()
-
-k=ncol(temp3)
-kleft=ncol(temp1)
-kright=ncol(temp2)
-left_end=kleft
-right_start=left_end+2
-left=c(1:left_end)
-right=c(right_start:k)
-horizontal = c(left,right)
-dates=c(1,right_start)
-events = dates + 1
-checkmarks = c((events[1]+1):left_end , (events[2]+1):k)
-
-library(officer)
-big_border = fp_border(color="black", width = 2)
-
-banding1 <- 1:nrow(temp1) %% 2
-banding2 <- 1:nrow(temp2) %% 2
-ft <- temp3  %>%
-      flextable::as_flextable() %>%
-
-      flextable::line_spacing( space = 1.0, part = "all") %>% # 
-      flextable::padding(padding = 0, part = "body") %>%
-      flextable::fontsize(size = 7, part = "all") %>%
-      bg( i = which( banding1==1 ) , part = "body", bg = "#EFEFEF", j=left) %>%
-      bg( i = which( banding2==1 ) , part = "body", bg = "#EFEFEF", j=right) %>%
-
-      #Headers
-      flextable::set_header_labels(values =
-        list(
-              YMD.x = "YMD",
-              Event.x = "Synthetic Narrative",
-              Docs.x = "Mentions",
-              icb_narrative.x = "ICB Corpus",
-              ICBe.x = "ICBe",
-              ICB = "ICB",
-              MIDs.x = "MIDs",
-              phoenix.x = "Phoenix",
-              phoenix.y = "Phoenix",
-              row="",
-              YMD.y = "YMD",
-              Event.y = "Synthetic Narrative",
-              Docs.y = "Mentions",
-              icb_narrative.y = "ICB Corpus",
-              ICBe.y = "ICBe",
-              icews = "ICEWS",
-              MIDs.y = "MIDs",
-              terrier="Terrier"
-             ) ) %>%
-
-      add_header_row(values = c("Cuban Missile Crisis (1962)", "", "Crimea-Donbas (2014)"), colwidths = c(kleft, 1,kright) ) %>%
-
-      #Global
-      flextable::border_remove() %>% 
-      #Left border
-      border(j=1, i=1:n_left , part="body", border.left =  big_border ) %>% #
-      border(j=1, i=1:2 , part="header", border.left =  big_border ) %>% #
-
-      border(j=left_end, i=1:2 , part="header", border.right =  big_border ) %>% #
-      border(j=left_end, i=1:n_left , part="body", border.right =  big_border ) %>% #
-
-      border(j=1:left_end, i=n_left , part="body", border.bottom =  big_border ) %>% #
-      border(j=1:left_end, i=1 , part="body", border.top =  big_border ) %>% #
-      border(j=1:left_end, i=1:2 , part="header", border.top =  big_border ) %>% #
-
-      #Right border
-      border(j=right_start, i=1:n_right , part="body", border.left =  big_border ) %>% #
-      border(j=k, i=1:n_right , part="body", border.right =  big_border ) %>% #
-
-      border(j=right_start, i=1:2 , part="header", border.left =  big_border ) %>% #
-      border(j=k, i=1:2 , part="header", border.right =  big_border ) %>% #
-      border(j=1:k, i=1 , part="header", border.right =  big_border ) %>% #
-
-      border(j=right_start:k, i=n_right , part="body", border.bottom =  big_border ) %>% #
-      border(j=right_start:k, i=1 , part="body", border.top =  big_border ) %>% #
-      border(j=right_start:k, i=1:2 , part="header", border.top =  big_border ) %>% #
-
-      vline(i=1:n_left, j=1:(left_end-1),  border = NULL, part = "body")  %>%
-      vline(i=1:n_right,j=right_start:(k-1),  border = NULL, part = "body")  %>%
-      vline(i=2, j=1:(left_end-1),  border = NULL, part = "header")  %>%
-      vline(i=2,j=right_start:(k-1),  border = NULL, part = "header")  %>%
-
-      #
-      hline(i=c(26,46), j=left,  border = NULL, part = "body")  %>%
-      hline(i=c(11), j=right,  border = NULL, part = "body")  %>%
-
-      #Header
-      flextable::rotate(i=2, j=3:left_end, rotation="tbrl", part="header") %>% 
-      flextable::rotate(i=2, j=(left_end+4):k, rotation="tbrl", part="header") %>%
-
-      valign(j = 1:2, valign = "center", part = "all") %>%
-      align(i = 2, j = NULL, align = "center", part = "header")  %>%
-
-      #break
-      flextable::width( j = left_end+1, width=0.25)  %>%
-
-      #Dates
-      flextable::width( j = dates, width=0.6)  %>% 
-      align(i = NULL, j = dates, align = "right", part = "body")   %>%
-
-      #events
-      flextable::width( j = events, width=2.50)  %>%
-      align(i = NULL, j = events, align = "left", part = "body")  %>%
-      ftExtra::colformat_md(j = events, part="body") %>%
-
-      #Checkmarks
-      flextable::width( j = checkmarks, width=0.05) %>%
-      align(i = NULL, j = checkmarks, align = "center", part = "body")
-
-ft   %>% 
-    #flextable::flextable_to_rmd()
-    save_as_image(path=here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
-```
-
-```{r recall-all, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
-#Recall Summary Statistics
-#, icb_narrative_cd=icb_narrative.y, icews_cd=icews_hash
-temp1_long <- temp1 %>% dplyr::select(docs=Docs, ICB_Narrative=icb_narrative, ICBe=ICBe, ICB=ICB,MIDs=MIDs,Phoenix=phoenix) %>% mutate(crisis="Cuban Missile Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
-              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
-
-temp2_long <- temp2 %>% dplyr::select(docs=Docs,ICB_Narrative=icb_narrative,ICBe=ICBe,MIDs=MIDs , Phoenix=phoenix, Terrier=terrier, ICEWS= icews) %>% mutate(crisis="Crimea-Donbas Crisis") %>% pivot_longer(cols=-c(crisis, docs)) %>%
-              mutate(value=ifelse(!is.na(value) & !value %in% 0,1,0))
-
-temp3_long <- bind_rows(temp1_long,temp2_long)
-
-Y_hat <- temp3_long %>% dplyr::select(name) %>% distinct()
-mylogit <- glm(value ~ name, data = temp3_long, family = "binomial")
-Y_hat$fit <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$fit
-Y_hat$se <- predict(mylogit, temp3_long %>% dplyr::select(name) %>% distinct() , type='response', se.fit=TRUE)$se.fit
-Y_hat$name <- Y_hat$name %>% fct_reorder(Y_hat$fit)
-
-#Y_hat %>% ggplot(aes(name, fit)) +
-#          geom_point(size=4) +
-#          geom_errorbar(aes(ymin = fit-(1.98*se), ymax = fit+(1.98*se)), width = 0.1, linetype="solid") + coord_flip()  + theme_bw() + 
-#          ylab("Mean Recall") + xlab("")
-
-#temp3_long_means <- temp3_long %>% 
-#                    group_by(name) %>%
-#                    summarise(value= value %>%mean() %>% round(2))
-
-#temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + geom_point() +
-#  geom_smooth(method = "glm", method.args = list(family = "binomial"), se=F) + 
-#  ylab("Recall") + xlab("Document Mentions (Log)") +
-#  facet_wrap(~crisis, scales="free_x")
-
-library(geomtextpath)
-temp3_long$crisis <- factor(temp3_long$crisis, levels= temp3_long$crisis %>% as.character() %>% unique() %>% sort() %>% rev() )
-p_recall <- temp3_long %>% ggplot(aes(x=log(docs), y=value, color=name)) + 
-  #geom_point() +
-  geom_textsmooth(aes(label = name), size=3, method = "glm", method.args = list(family = "binomial"), se=F) + 
-  ylab("Recall") + xlab("Document Mentions (Log)") +
-  facet_wrap(~crisis, scales="free_x") +
-  theme_bw() +
-  theme(legend.position="none")
-
-#p_recall
-
-ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'),
-       plot = p_recall ,
-       width=5, height=3.0)
-
-library(magick)
-
-tiger <- image_read(here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"))
-tiger2 <- image_read(paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'))
-
-combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
-image_write(combined, here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea_andcounts.png"))
-```
-
 ## Cuban Missile Crisis (1962)
@@
 
-```{r precision, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
+```{r precision, eval=fromscratch, results='hide', echo=F, include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}
 

### 2024-06-16 replication_paper/psrm_draft/ICBe_manuscript.Rmd
pre-pull

@@
       #head(100) %>%
+
+temp <- temp %>% dplyr::mutate(value_markdown = value_markdown %>% 
+            stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed(""))) # %>% 
+            # dplyr::mutate(value_markdown = value_markdown %>% replace_emoticons)
+
 ft_cuba_precision <- temp %>%
@@
                       ftExtra::colformat_md(j = 3, part="body")
-#ft_cuba_precision
-
-# TS temp edit: following line plotted for temporary fix
-# ft_cuba_precision %>% flextable::save_as_image(path=here::here("replication_paper","psrm_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
+ft_cuba_precision
+
+#ft_cuba_precision %>% flextable::save_as_image(path=here::here("replication_paper","psrm_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
 temp <- NULL
@@
 Doing so allows researchers to identify and explain patterns in escalation conditional on the military means states use in conflict.
-Recent concerns about cross-domain conflict and the effect of new domains of conflict like space and cyber have made this an endeavor of increased interest to practitioners [@gannonOneIfLand2022].
+Recent concerns about cross-domain conflict and the effect of new domains of conflict like space and cyber have made this an endeavor of increased interest to practitioners.
+[@gannonOneIfLand2022]
 
@@
 Across all existing datasets and ICBe, recall increases with the number of document mentions which is an important sign of validity for both them and our benchmark.
-The one outlier is Phoenix which in the Cuban Missile Crisis case is so noisy that it's recall curve is flat to decreasing as mentions increase.
+The one outlier is Phoenix which in the Cuban Missile Crisis case is so noisy that its recall curve is flat to decreasing as mentions increase.
 The two episode-level datasets (MIDs and ICM) have low coverage of contextual details.
@@
 ![Crisis map for the Cuban Missile Crisis.
-The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap width="6in"}
+The start of the crisis is at the top and end of the crisis is the bottom, with each actor in a column with labeled points identifying their speeches, actions, and thoughts.](p_196_icbe.png){#fig-cuba-crisismap width="5.5in"}
 

### 2024-06-16 replication_paper/psrm_draft/ICBe_manuscript.tex
pre-pull

@@
 new domains of conflict like space and cyber have made this an endeavor
-of increased interest to practitioners (Gannon 2022).
+of increased interest to practitioners. (Gannon 2022)
 
@@
 outlier is Phoenix which in the Cuban Missile Crisis case is so noisy
-that it's recall curve is flat to decreasing as mentions increase. The
+that its recall curve is flat to decreasing as mentions increase. The
 two episode-level datasets (MIDs and ICM) have low coverage of
@@
 \centering
-\includegraphics[width=6in,height=\textheight]{p_196_icbe.png}
+\includegraphics[width=5.5in,height=\textheight]{p_196_icbe.png}
 \caption{Crisis map for the Cuban Missile Crisis. The start of the

### 2024-06-16 replication_paper/psrm_draft/ICBe_supplemental_information.Rmd
pre-pull

--- 2022-10-24 replication_paper/psrm_draft/ICBe_supplemental_information.Rmd
@@
 
-#oh is it because break is reserved in R? lol
 #icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
@@
 
-#somehow break of all things is a b roken name
 #icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
@@
 ```{r ICBe Crisis Summaries, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F}
-
-#The answer is I have to include it as an image, none of the table options were compiling correctly without error
-#,  ft.arraystretch=0.75
 
@@
   mutate_all(as.character) %>%
-              mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II"))
+  mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II")) %>%
+  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed(""))) %>%
+  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("Columbia;Cuba;Mexico;United States;Uruguay"), stringr::fixed("![](flags_small//Q739.png);![](flags_small//Q241.png);![](flags_small//Q96.png)"))) %>%
+  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("Belgium;France;Germany;Italy;United Kingdom"), stringr::fixed(""))) %>%
+  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("France;United Kingdom"), stringr::fixed(""))) %>%
+  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed(";Soviet Union;United States of America"), stringr::fixed(""))) %>%
+  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed(";Saudi Arabia"), stringr::fixed(""))) %>%
+  dplyr::mutate(units_domains = units_domains %>% stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed(""))) %>%
+  dplyr::mutate(forces_fatalities = forces_fatalities %>% stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed("")))
+## DOUBLE CHECK ABOVE
 
@@
                 coders_expert = "Coders",
-                coders_novice = "Coders"#,
+                coders_novice = "Coders"
                 #value_markdown = "Abstract"
@@
 }
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft2.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft3.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft4.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft5.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft6.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft7.png"), zoom=1)
-
-temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft()  %>% 
-  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft8.png"), zoom=1)
-
+```
+
+```{r}
+## Double Check Below
+
+crisis_text_counts_ft1 <- temp_all %>% ungroup() %>% filter(crisno %in% c(1:60)) %>% convert_to_ft() 
+#crisis_text_counts_ft1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)
+crisis_text_counts_ft1
+
+crisis_text_counts_ft2 <- temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  
+#crisis_text_counts_ft2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft2.png"), zoom=1)
+crisis_text_counts_ft2
+
+crisis_text_counts_ft3 <- temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft() 
+#crisis_text_counts_ft3 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft3.png"), zoom=1)
+crisis_text_counts_ft3
+
+crisis_text_counts_ft4 <- temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()
+#crisis_text_counts_ft4 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft4.png"), zoom=1)
+crisis_text_counts_ft4
+
+crisis_text_counts_ft5 <- temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft() 
+#crisis_text_counts_ft5 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft5.png"), zoom=1)
+crisis_text_counts_ft5
+
+crisis_text_counts_ft6 <- temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft() 
+#crisis_text_counts_ft6 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft6.png"), zoom=1)
+crisis_text_counts_ft6
+
+crisis_text_counts_ft7 <- temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft() 
+#crisis_text_counts_ft7 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft7.png"), zoom=1)
+crisis_text_counts_ft7
+
+crisis_text_counts_ft8 <- temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft() 
+#crisis_text_counts_ft8 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft8.png"), zoom=1)
+crisis_text_counts_ft8
 ```
@@
 # writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)
-
-fromscratch=F
+fromscratch=FALSE
 if(fromscratch){
@@
   p_load("spacyr")
-  #spacy_install() 
-  spacy_initialize(model = "en_core_web_sm")
+  spacyr::spacy_install() 
+  spacy_initialize(model = "en_core_web_sm") # if this initially doesn't work, try the previous spacy_install command and restart R.
 
@@
 #wordnet rdf (in tripple format)
-fromscratch=F
 
@@
 verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
-#oh got it this is all possible matching glosses per ICBe sentence
+#this is all possible matching glosses per ICBe sentence
 #dim(verbs_sentence_wordnet) #227,426
-
-#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances
 
@@
  # py_install("transformers")
+ # py_install("torch")
+ # py_install("sentence_transformers")
 ```
@@
 # can install python packages in R using code chunk above
-
-fromscratch=False
-
-if fromscratch:
 import torch
@@
     print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
-      print('__CUDA Device Name:',torch.cuda.get_device_name(1))
-      print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)    
+#    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
+#    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)    
 import random
@@
 glosses_embeddings.shape #(4977, 768)
-else:
-  print("Skipping")
 
@@
 
-```{python embed sentences for wordnet , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
-
-#Make sure you have a gpu if you want to run thi
+```{python embed sentences for wordnet, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}
+
+#Make sure you have a gpu if you want to run this
 
@@
 
-fromscratch=False
-if fromscratch:
 from sentence_transformers import SentenceTransformer
@@
 sentences_embeddings.shape #(12103, 768)
-else:
-  print("Skipping")
 
@@
 
-fromsrcatch=F
-if(fromsrcatch){
-  #py$sentences
-  #py$glosses
+  # py$sentences
+  # py$glosses
   glosses_embeddings <- py$glosses_embeddings
@@
   gloss_clean <- verbs_sentence_wordnet$gloss
-  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
+  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #
   glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
@@
   sentences_clean <- verbs_sentence_wordnet$sentence
-  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
+  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #
   sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
@@
 
-  #Isn't it just one minus the other?
   verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
@@
   verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
-
-} else {
-
-  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
-
-}
 
@@
         #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
-        #fit_to_width(max_width=12) #This is crazy slow
+        #fit_to_width(max_width=12) #This is slow
         #flextable::autofit() 
@@
 ```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
-
-fromscratch=F
-if(fromscratch){
   means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
@@
                 group_by(varname_normalized) %>%
-                #filter(votes_total>1) %>% #What work is this doing?
+                #filter(votes_total>1) %>% 
                 #filter(selected_by_experts>=1) %>%
@@
                   plot = p_percent_chose_tag_by_concept, width=8, height=8)
-}
-
 ```
@@
 
-fromscratch=F
-if(fromscratch){
   raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
@@
                   plot = p_percent_chose_tag_by_confidence, width=8, height=6)
-}
 
@@
 
+```{r}
+rm(list = ls())
+gc() 
+#.rs.restartR()
+```
+
 # Recall
-\hphantom{em}
 
 ## Synthetic Narratives
-\hphantom{em}
+
+\doublespacing
 
@@
 
-```{r}
-
-cuba_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names()
-
-replace_emoticons_cuba <- function(x){
-  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
-        #https://emojiterra.com/flag-for-united-states/
-        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-        #https://emojiterra.com/flag-for-russia/
-        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
-        #Turkey
-        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
-        #U.N.
-        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
-}
+```{r, eval=T}
+
+paste0(here::here(), '/replication_data/out/case_study_cuban.Rds')
+
+# cuba_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
+#                                 sheet="final") %>% janitor::clean_names() 
+# cuba_recall  %>% saveRDS(paste0(here::here(), '/replication_data/out/case_study_cuban.Rds'))
+cuba_recall <- readRDS(paste0(here::here(), '/replication_data/out/case_study_cuban.Rds'))
+
+# replace_emoticons_cuba <- function(x){
+#   x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
+#         #https://emojiterra.com/flag-for-united-states/
+#         str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
+#         #https://emojiterra.com/flag-for-russia/
+#         str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
+#         #Turkey
+#         str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
+#         #U.N.
+#         str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
+# }
 
@@
                             dplyr::select(date, event, documents, icb_narrative, icbe=ic_be, icb, mids, phoenix_2)  %>%
-                            mutate(event = event %>% replace_emoticons_cuba() ) %>%
+                            #mutate(event = event %>% replace_emoticons_cuba() ) %>%
                             flextable::as_flextable() %>%
@@
                             flextable::width( j =2, width=2.0)  %>% 
+                            #flextable::width( j = 3, width=.3)  %>% 
+                            #flextable::width( j = 4, width=.3)  %>% 
+                            #flextable::width( j = 5, width=.25)  %>% 
                             flextable::width( j = 6:8, width=2.0)  %>% 
+                            #flextable::width( j = 6, width=1)  %>%
+                            #flextable::width( j = 7, width=1.2)  %>% 
+                            #flextable::width( j = 8, width=2)  %>% 
                             flextable::fontsize(size = 7, part = "all") %>%
@@
 
-```{r}
-
-crimea_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
-                                sheet="final") %>% janitor::clean_names()
-
-replace_emoticons_crimea <- function(x){
-      x %>%
-            #https://emojiterra.com/flag-for-united-states/
-            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
-            #https://emojiterra.com/flag-for-russia/
-            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
-            #Ukraine
-            str_replace_all('\U0001f1fA\U0001f1e6', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
-            #Crimea
-            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>%
-            #EU
-            str_replace_all('\U0001f1EA\U0001f1FA', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
-}
+```{r, eval=T}
+
+#crimea_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
+#                                sheet="final") %>% janitor::clean_names()                                
+# crimea_recall  %>% saveRDS(paste0(here::here(), '/replication_data/out/case_study_crimea.Rds'))
+crimea_recall <- readRDS(paste0(here::here(), '/replication_data/out/case_study_crimea.Rds'))
+
+# 
+# replace_emoticons_crimea <- function(x){
+#       x %>%
+#             #https://emojiterra.com/flag-for-united-states/
+#             str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
+#             #https://emojiterra.com/flag-for-russia/
+#             str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
+#             #Ukraine
+#             str_replace_all('\U0001f1fA\U0001f1e6', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
+#             #Crimea
+#             str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) ")) %>%
+#             #EU
+#             str_replace_all('\U0001f1EA\U0001f1FA', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q458.png) "))
+# }
 
@@
                             dplyr::select(date, event, documents=n_sources, icb_narrative, icbe=ic_be,  phoenix, terrier, icews)  %>%
-                            mutate(event = event %>% replace_emoticons_crimea() ) %>%
+                            # mutate(event = event %>% replace_emoticons_crimea() ) %>%
                             mutate(date = date %>% as.Date()) %>%
@@
 
+```{r}
+rm(ft_cuba_recall, ft_crimea_recall)
+gc()
+```
+
 # Precision
@@
 
-#<!-- Rex remember that sentence 19 broken and cuts off 
+#<!-- remember that sentence 19 broken and cuts off 
 #"Ukraine’s major response to its crisis was verbal and began on 27 February, when it sent a note to Russia demanding that Russian troops stay on base in Crimea, called for #calm, and discussed the" -->
@@
 #ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))
-fromscratch=T
-if(fromscratch){
+
 temp <- ICBe_events_agreed_markdown %>%
@@
         group_by(crisno, sentence_number_int_aligned) %>%
-            filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
+          filter(!duplicated(value_markdown %>% trimws() )) %>% 
         ungroup() %>%
@@
   ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"
+  ft_crimea_precision_part1
+
+```
+
+```{r}
 
@@
 
+ft_crimea_precision_part2
   temp <- NULL
-
-}
 ```
@@
 ```{r Stratified Sentence Examples, eval=T, results='hide', echo=F, include=T, message=F, cache=F}
+ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds"))
 
@@
     unnest(value)
+
+# temp <- temp %>% dplyr::mutate(value_markdown = value_markdown %>% 
+#          stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/flags_small//"), stringr::fixed("")))
+
+temp <- temp %>% dplyr::mutate(value_markdown = value_markdown %>% 
+                               stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed("")))
 
@@
 ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision1.png"), zoom=1) # 
+ft_sample_precision_precision1
 
@@
 ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision2.png"), zoom=1) # 
+ft_sample_precision_precision2
 
@@
 ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision3.png"), zoom=1) # 
+ft_sample_precision_precision3
 
@@
 ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision4.png"), zoom=1) # 
-
+ft_sample_precision_precision4
+
+rm(temp, temp_sample)
 ```
-
-<!-- current -->
 
@@
 \end{figure}
+
+```{r}
+rm(case_study_crimea_precision_part1.png, case_study_crimea_precision_part2.png, ft_sample_precision_precision1.png, ft_sample_precision_precision2.png, ft_sample_precision_precision3.png, ft_sample_precision_precision4.png)
+gc()
+```
 
@@
 
+icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
+icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
+icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)
+
 actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
                                 sheet="actor_translator") #%>% janitor::clean_names()
+
 #Convert to a local file for pushing
@@
 crisno_name_years <- icb_crises %>% dplyr::select(crisno, crisname, yrtrig, yrterm)
+
+icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds"))
 
@@
          )
+
+saveRDS(cameo_actor_codes,paste0(here::here(), "/replication_paper/data/out/cameo_actor_codes.Rds")
 dim(cameo_actor_codes)
+
+replace_emoticons <- function(x){
+  x %>% stringr::str_replace_all(stringr::fixed("![](flags_small//"), stringr::fixed("")) %>%
+  stringr::str_replace_all(stringr::fixed(".png)"), stringr::fixed("")) %>%
+  stringr::str_replace_all(stringr::fixed("Q47488"), stringr::fixed("ICC")) %>%
+  stringr::str_replace_all(stringr::fixed("Q1065"), stringr::fixed("\U0001f1fa\U0001f1f3")) %>%
+  stringr::str_replace_all(stringr::fixed("Q7184"), stringr::fixed("NATO")) %>%
+  stringr::str_replace_all(stringr::fixed("Q1014"), stringr::fixed("\U0001f1f1\U0001f1f7")) %>%
+  stringr::str_replace_all(stringr::fixed("Q1027"), stringr::fixed("\U0001f1f2\U0001f1fa")) %>% #Mauritius
+  stringr::str_replace_all(stringr::fixed("Q1028"), stringr::fixed("\U0001f1f2\U0001f1e6")) %>%
+  stringr::str_replace_all(stringr::fixed("Q1033"), stringr::fixed("\U0001f1f3\U0001f1ec")) %>% #Nigeria
+  stringr::str_replace_all(stringr::fixed("Q241"), stringr::fixed("\U0001f1e8\U0001f1fa")) %>%
+  stringr::str_replace_all(stringr::fixed("Q159"), stringr::fixed("\U0001f1f7\U0001f1fa")) %>%
+  stringr::str_replace_all(stringr::fixed("Q148"), stringr::fixed("\U0001f1e8\U0001f1f3")) %>%
+  stringr::str_replace_all(stringr::fixed("Q794"), stringr::fixed("\U0001f1ee\U0001f1f7")) %>%
+  stringr::str_replace_all(stringr::fixed("Q458"), stringr::fixed("\U0001f1ea\U0001f1fa")) %>%
+  stringr::str_replace_all(stringr::fixed("Q212"), stringr::fixed("\U0001f1fa\U0001f1e6")) %>%
+  stringr::str_replace_all(stringr::fixed("Q810"), stringr::fixed("\U0001f1ef\U0001f1f4")) %>% #Jordan
+  stringr::str_replace_all(stringr::fixed("Q142"), stringr::fixed("\U0001f1eb\U0001f1f7")) %>%
+  stringr::str_replace_all(stringr::fixed("Q183"), stringr::fixed("\U0001f1e9\U0001f1ea")) %>%
+  stringr::str_replace_all(stringr::fixed("Q801"), stringr::fixed("\U0001f1ee\U0001f1f1")) %>%
+  stringr::str_replace_all(stringr::fixed("Q750"), stringr::fixed("\U0001f1e7\U0001f1f4")) %>%
+  stringr::str_replace_all(stringr::fixed("Q298"), stringr::fixed("\U0001f1e8\U0001f1f1")) %>%
+  stringr::str_replace_all(stringr::fixed("Q804"), stringr::fixed("\U0001f1f5\U0001f1e6")) %>%
+  stringr::str_replace_all(stringr::fixed("Q155"), stringr::fixed("\U0001f1e7\U0001f1f7")) %>%
+  stringr::str_replace_all(stringr::fixed("Q145"), stringr::fixed("\U0001f1ec\U0001f1e7")) %>%
+  stringr::str_replace_all(stringr::fixed("Q783"), stringr::fixed("\U0001f1ed\U0001f1f3")) %>%
+  stringr::str_replace_all(stringr::fixed("Q252"), stringr::fixed("\U0001f1ee\U0001f1e9")) %>%
+  stringr::str_replace_all(stringr::fixed("Q912"), stringr::fixed("\U0001f1f2\U0001f1f1")) %>% #Mali
+  stringr::str_replace_all(stringr::fixed("Q929"), stringr::fixed("\U0001f1e8\U0001f1eb")) %>% #Central African Republic
+  stringr::str_replace_all(stringr::fixed("Q184"), stringr::fixed("\U0001f1e7\U0001f1fe")) %>% #Belarus
+  stringr::str_replace_all(stringr::fixed("Q796"), stringr::fixed("\U0001f1ee\U0001f1f6")) %>% #Iraq 	
+  stringr::str_replace_all(stringr::fixed("Q423"), stringr::fixed("\U0001f1f0\U0001f1f5")) %>% #North Korea
+  stringr::str_replace_all(stringr::fixed("Q843"), stringr::fixed("\U0001f1f5\U0001f1f0")) %>%
+  stringr::str_replace_all(stringr::fixed("Q668"), stringr::fixed("\U0001f1ee\U0001f1f3")) %>%
+  stringr::str_replace_all(stringr::fixed("Q262"), stringr::fixed("\U0001f1e9\U0001f1ff")) %>%
+  stringr::str_replace_all(stringr::fixed("Q766"), stringr::fixed("\U0001f1ef\U0001f1f2")) %>%
+  stringr::str_replace_all(stringr::fixed("Q408"), stringr::fixed("\U0001f1e6\U0001f1fa")) %>% #Australia
+  stringr::str_replace_all(stringr::fixed("Q858"), stringr::fixed("\U0001f1f8\U0001f1fe")) %>% #Syria
+  stringr::str_replace_all(stringr::fixed("Q958"), stringr::fixed("\U0001f1f8\U0001f1f8")) %>% #South Sudan
+  stringr::str_replace_all(stringr::fixed("Q211"), stringr::fixed("\U0001f1f1\U0001f1fb")) %>% #Latvia
+  stringr::str_replace_all(stringr::fixed("Q833"), stringr::fixed("\U0001f1f2\U0001f1fe")) %>% #Malaysia
+  stringr::str_replace_all(stringr::fixed("Q217"), stringr::fixed("\U0001f1f2\U0001f1e9")) %>% #Moldova
+  stringr::str_replace_all(stringr::fixed("Q822"), stringr::fixed("\U0001f1f1\U0001f1e7")) %>% #Lebanon
+  stringr::str_replace_all(stringr::fixed("Q889"), stringr::fixed("\U0001f1e6\U0001f1eb")) %>% #Afghanistan
+  stringr::str_replace_all(stringr::fixed("Q43"), stringr::fixed("\U0001f1f9\U0001f1f7")) %>%
+  stringr::str_replace_all(stringr::fixed("Q31"), stringr::fixed("\U0001f1e7\U0001f1ea")) %>% #Belgium
+  stringr::str_replace_all(stringr::fixed("Q41"), stringr::fixed("\U0001f1ed\U0001f1f3")) %>%
+  stringr::str_replace_all(stringr::fixed("Q38"), stringr::fixed("\U0001f1ee\U0001f1f9")) %>% #Italy
+  stringr::str_replace_all(stringr::fixed("Q39"), stringr::fixed("\U0001f1e8\U0001f1ed")) %>%
+  stringr::str_replace_all(stringr::fixed("Q16"), stringr::fixed("\U0001f1e8\U0001f1e6")) %>% #Canada
+  stringr::str_replace_all(stringr::fixed("Q37"), stringr::fixed("\U0001f1f1\U0001f1f9")) %>% #Lithuania
+  stringr::str_replace_all(stringr::fixed("Q36"), stringr::fixed("\U0001f1f5\U0001f1f1")) %>%
+  stringr::str_replace_all(stringr::fixed("Q29"), stringr::fixed("\U0001f1ea\U0001f1f8")) %>%
+  stringr::str_replace_all(stringr::fixed("Q17"), stringr::fixed("\U0001f1ef\U0001f1f5")) %>%
+  stringr::str_replace_all(stringr::fixed("Q20"), stringr::fixed("\U0001f1f3\U0001f1f4")) %>% #Norway
+  stringr::str_replace_all(stringr::fixed("Q30"), stringr::fixed("\U0001f1fA\U0001f1f8")) 
+}
 
@@
 icb2v14_clean <- icb2v14 %>% 
-                 left_join(icb_df %>% dplyr::select(cracid=icb_code, actor_label=icb_name ) %>% mutate(cracid=cracid %>% as.numeric()) ) %>%  #you can't actually match on the letter codes you have to match on the numbers, uhhhhhg
+                 left_join(icb_df %>% dplyr::select(cracid=icb_code, actor_label=icb_name ) %>% mutate(cracid=cracid %>% as.numeric()) ) %>%  
                  left_join( df_trigger  ) %>% 
@@
     #  arrange(across(starts_with("V")))
-    ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+    ideal_ordering <- hc$labels[hc$order]
 
@@
     actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
-    actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+    actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #pick a bewer pallet with lots of values and then assign it to specific values
     names(actor_colors) = levels(actors)
@@
 
-c(196, 471) %>% sapply(FUN=function(x) icb_crisismaps(x)) #This just runs every time no from scratch because the files are small
+c(196) %>% sapply(FUN=function(x) icb_crisismaps(x)) #This just runs every time no from scratch because the files are small
+
+c(471) %>% sapply(FUN=function(x) icb_crisismaps(x)) #This just runs every time no from scratch because the files are small
 
@@
 ```{r mids data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
 mid4_df <- data.frame(
@@
 dyadic_mid_clean <- dyadic_mid %>% distinct() %>%
-                      left_join(actor_translator %>% dplyr::select(statea=COWcode, actor_1=QCode_name, actor_1_qcode=QCode)) %>% #I think we add color here
+                      left_join(actor_translator %>% dplyr::select(statea=COWcode, actor_1=QCode_name, actor_1_qcode=QCode)) %>% # we add color here
                       left_join(actor_translator %>% dplyr::select(stateb=COWcode, actor_2=QCode_name, actor_2_qcode=QCode)) %>%
@@
   #  arrange(across(starts_with("V")))
-  ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
+  ideal_ordering <- hc$labels[hc$order]
 
@@
   actors=icb_events_subset_nodes$actor %>% unique() %>% as.factor()
-  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #ok so pick a bewer pallet with lots of values and then assign it to specific values
+  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #pick a bewer pallet with lots of values and then assign it to specific values
   names(actor_colors) = levels(actors)
@@
 
-```{r phoenix data loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F,}
+```{r}
+rm(dyadic_mid, dyadic_mid_clean)
+gc()
+```
+
+```{r phoenix data loads, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F,}
 #[@althausClineCenterHistorical2020a]
@@
 library(ggraph)
-
-#8,491,556
 library(stringr)
-fromscratch=F
-if(fromscratch){
 
@@
 
-  #phoenix_clean_471 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_471.tsv")
+  phoenix_clean_471 %>% write_tsv(paste0(here::here(), "/replication_data/out/phoenix_clean_471.tsv"))
   dim(phoenix_clean_471)
@@
 
-  #phoenix_clean_196 %>% write_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/phoenix_clean_196.tsv")
+  phoenix_clean_196 %>% write_tsv(paste0(here::here(), "/replication_data/out/phoenix_clean_196.tsv"))
   #dim(phoenix_clean_196)
@@
 }
-
 ```
@@
 
-phoenix_barmaps <- function(thiscrisis=196, topactor=F){
+phoenix_barmaps <- function(thiscrisis=196, phoenix_subset="phoenix_clean_196.tsv", topactor=F){
 
@@
 
-    phoenix_clean_subset <- phoenix_clean %>% 
+    phoenix <- read_tsv(paste0(here::here(), "/replication_data/out/phoenix_clean_196.tsv"))
+
+    phoenix_clean_subset <- phoenix %>% 
                             mutate(story_date = story_date %>% lubridate::mdy()) %>%
                             filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>% 
+                            # phoenix_clean() %>%
                             unite('dyad_a', source_root_label, source_agent_label, source_others1_label, source_others2_label, source_others3_label, na.rm = TRUE, remove = FALSE) %>%
@@
                        pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
+                       mutate(markdown = glue::glue("![](flags_small//{QCode}.png)") ) 
     names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
@@
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("\\(tertiary role code\\)","")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force"))
+                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force")) %>%
+                                   dplyr::mutate(dyad_markdown = dyad_markdown %>% replace_emoticons)
 
@@
                        pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
+                       mutate(markdown = glue::glue("![](flags_small//{QCode}.png)") )  # since direct flags are not working
     names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
@@
                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("\\(tertiary role code\\)","")) %>%
-                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force"))
+                                   mutate(dyad_markdown = dyad_markdown %>% str_replace_all("unidentified armed force"," unknown force")) %>%
+                                   dplyr::mutate(dyad_markdown = dyad_markdown %>% replace_emoticons) # since direct flags are not working
 
@@
         p_phoenix_lv0 %>% saveRDS(save_file_lv0)         
-
 }
 
-fromscratch=F
-if(fromscratch){
-  phoenix_clean <- arrow::read_parquet(here::here("git_ignore_folder", "phoenix_clean.parquet") ) 
-  c(196, 471) %>% sapply(FUN=function(x) phoenix_barmaps(x))
-}
-
+phoenix_barmaps(thiscrisis=196, phoenix_subset="phoenix_clean_196.tsv" , topactor=F)
+phoenix_barmaps(thiscrisis=471, phoenix_subset="phoenix_clean_471.tsv" , topactor=F)
 ```
 
-```{r Terrierr Data Loads, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
+```{r Terrierr Data Loads, eval=F, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
 
@@
 
-    terrier_clean_subset <- terrier_clean %>% 
-                    mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() ) %>%
-                    filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) %>%  
+    # terrier_clean_subset <- terrier_clean %>% 
+    #                 mutate(story_date=paste(month, day, year, sep="/")  %>% lubridate::mdy() ) %>%
+    #                 filter(story_date>=(date_start-lubridate::years(1)) & story_date<=(date_end+lubridate::years(1))) 
+    #                terrier_clean_subset  %>%   arrow::write_parquet("terrier_clean.parquet")
+
+    terrier_clean_subset <- terrier_clean_subset %>%   
                     unite('temp', src_country_label,src_agent_label,src_other_agent1_label,src_other_agent2_label,src_other_agent3_label,
@@
                        pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
+                       mutate(markdown = glue::glue("![](flags_small//{QCode}.png)") ) # since direct flags are not working
     names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
@@
     terrier_clean_subset_top10_day <- terrier_clean_subset_top10_day %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government|Government","gov")) %>%
+                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government[^a-z]|Government[^a-z]","gov")) %>%
+                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Government","gov")) %>%
                                      mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                      mutate(dyad_markdown = dyad_markdown %>% str_replace_all(fixed("(tertiary role code)"),"")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil."))
+                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil.")) %>%
+                                   dplyr::mutate(dyad_markdown = dyad_markdown %>% replace_emoticons) # since direct flags are not working
 
@@
                                      mutate(dyad_markdown = dyad_markdown %>% str_replace_all("government[^a-z]|Government[^a-z]","gov")) %>%
+                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Government","gov")) %>%
                                      mutate(dyad_markdown = dyad_markdown %>% str_replace_all("law enforcement agencies","law enforcement")) %>%
                                      mutate(dyad_markdown = dyad_markdown %>% str_replace_all(fixed("(tertiary role code)"),"")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil."))
+                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("Unidentified Armed Force","Unknown Mil.")) %>% 
+                                     dplyr::mutate(dyad_markdown = dyad_markdown %>% replace_emoticons) # since direct flags are not working
 
@@
 
-fromscratch=F
-if(fromscratch){
-  #done
-  #install.packages("arrow")
-  terrier_clean <-  arrow::read_parquet( here::here("git_ignore_folder", "terrier_clean.parquet")) #203mb
+  terrier_clean <-  arrow::read_parquet("terrier_clean.parquet") 
   dim(terrier_clean) #28,438,029 #39,322,909 #7,847,463
 
-  c(196, 471) %>% sapply(FUN=function(x) terrier_barmaps(x))
+  c(471) %>% sapply(FUN=function(x) terrier_barmaps(x))
+  # c(196) %>% sapply(FUN=function(x) terrier_barmaps(x))
 }
@@
               dplyr::select(value_normalized,value_qcode) %>% distinct()
-    #library(re2r) #didn't speed it up and enabling parallel was actually slower, not sure what's going on usually very fast
+    #library(re2r) #didn't speed it up and enabling parallel was actually slower,
     library(tictoc)
@@
                                 source_q_label_country,target_q_label_country,  source_label, target_label,who_a, who_b,province, district, city,
-                                na.rm = TRUE, remove = FALSE) %>% #this is probably slow need to check
+                                na.rm = TRUE, remove = FALSE) %>% 
                           filter(temp %>% str_detect(actors$value_normalized %>% paste0(collapse="|"))) %>% #this is slow and maybe replacing with re2r will fix
@@
                                      mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
-                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
+                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross")) %>% 
+                                     dplyr::mutate(dyad_markdown = dyad_markdown %>% replace_emoticons) # since direct flags are not working
 
@@
                        pivot_longer(-c(QCode)) %>% na.omit() %>% dplyr::select(-name) %>% distinct() %>%
-                       mutate(markdown = glue::glue("![]({flag_folder_small}/{QCode}.png)") ) 
+                       mutate(markdown = glue::glue("![](flags_small//{QCode}.png)") )  # since direct flags are not working
+
     names_to_qcodes <- bind_rows(names_to_qcodes, names_to_qcodes %>% mutate(value= value %>% tolower() )) %>% distinct() %>%
@@
                                     mutate(dyad_markdown = dyad_markdown %>% str_replace_all("(tertiary role code)","")) %>%
-                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross"))
+                                    mutate(dyad_markdown = dyad_markdown %>% str_replace_all("International Committee of the Red Cross","Red Cross")) %>% 
+                                   dplyr::mutate(dyad_markdown = dyad_markdown %>% replace_emoticons) # since direct flags are not working
 
@@
     icews_clean_subset_top10_day %>% write_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
-    #just out the tsv and plot how you want in the main paper
 
@@
 
-fromscratch=F
-if(fromscratch){
+# fromscratch=F
+# if(fromscratch){
   #done
   #install.packages("arrow")
-  icews_clean <-  arrow::read_parquet(here::here("git_ignore_folder", "icews_clean.parquet") )
+  icews_clean <-  arrow::read_parquet("icews_clean.parquet")
 
   c( 471) %>% sapply(FUN=function(x) icews_barmaps(x))
-}
+#}
 
@@
 
+```{r}
+rm(icews_clean)
+gc()
+```
+
 ```{r crisis 196, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-fromscratch=F
-if(fromscratch){
+library(ggplot2)
+library(cowplot)
+library(ggraph)
 
@@
 p_196_icb <- p_metro_plot +
-           theme(plot.margin=unit(c(0,0,0,0),"in")) +
-  labs(
-    #title = plot_title ,
-    #subtitle = subtitle ,
-    #caption = caption
-  )
-
-save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icb_metro_plot_196.Rds')
-p_metro_plot <- readRDS(save_file)
-p_196_phoenix <- p_metro_plot +
            theme(plot.margin=unit(c(0,0,0,0),"in")) +
@@
 
-library(cowplot)
 p_196_combined <- 
@@
           p_196_combined, base_height = 12, base_width = 20)
-#I'm just going to rotate on disk and load it as a normal figure
-#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
-}
+#\begin{sidewaysfigure}[H] 
 ```
@@
 ```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-if(fromscratch){
   p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "psrm_draft", "p_phoenix_plot_lv0_196.Rds"))
@@
             p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
 ```
@@
 
+<!-- p_471_icbe.png is created in ICBe_manuscript -->
+
 \begin{figure}[H]
@@
 #Crisis maps for the non ICBe datasets for the two case studies
-
-fromscratch=F
-if(fromscratch){
 
@@
           p_471_combined, base_height = 14, base_width = 23)
-}
 
@@
 
-if(fromscratch){
 p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_phoenix_plot_lv0_471.Rds"))
@@
           p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
+
 ```
@@
 ```{r, eval=T, results='hide', echo=F, include=T, message=F, cache=F, warning=F}
-
-if(fromscratch){
   p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_terrier_plot_lv0_471.Rds"))
@@
             p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
 ```
@@
 
-if(fromscratch){
   p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_icews_plot_lv0_471.Rds"))
@@
             p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
-}
 ```

### 2024-06-16 replication_paper/psrm_draft/ICBe_supplemental_information.tex
pre-pull

@@
 
+\begin{verbatim}
+## Warning: package 'googlesheets4' was built under R version 4.3.1
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'tidyverse' was built under R version 4.2.2
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'tibble' was built under R version 4.3.1
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'tidyr' was built under R version 4.3.2
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'readr' was built under R version 4.3.2
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'purrr' was built under R version 4.3.1
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'dplyr' was built under R version 4.3.2
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'stringr' was built under R version 4.3.2
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'forcats' was built under R version 4.2.2
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'lubridate' was built under R version 4.3.1
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'rvest' was built under R version 4.2.1
+\end{verbatim}
+
 \clearpage
